### 2015-11-02 intro.tex
converted google doc text into LaTeX

\section{Introduction}
\paragraph{Basic issues. }
\begin{itemize}
\item [NY] formalize and investigate a security notion of limited interest
\item The proposed construction won’t scale in common network applications
\item The main results are of theoretical interest only
\item The basic syntax and operation of their Bloom filter formalization is underdefined.  (This really irritates me.)  It isn’t clear that their Bloom filter formalization actually captures traditional Bloom filters!
\end{itemize}

\paragraph{Critique. }
The traditional definition of Bloom filter soundness is information theoretic.  Effectively, it states that an IT adversary cannot find a false positive with probability more than some small value.  (That value is a function of the size of the set being represented, the representation size, the size of the universe, and the number of hash functions.)  This paper ([NY]) replaces the traditional IT notion with a computational notion, and casts it as a security experiment/goal.  Namely: given the set S that is represented by the Bloom filter, and access to an oracle for Bloom filter set-membership queries, an attacker must find a false positive.

\jknote{Of course, [NY] discusses an info-theoretic notion also. So in some sense what is really new here is consideration of adaptivity...}
\tsnote{Yes, defining soundness with respect to explicit adversaries, who are also adaptive, does seem to be the novel piece.}

Security relative to this notion appears to have some practical relevance.  [NY] points to whitelisting spam filters as an example.  That is, a Bloom filter is populated with set S of whitelisted email addresses, so a false positive translates to an attacker finding an email address that sneaks through the filter.  [NY] suggest a second example of content-caching servers that keep a Bloom filter of their own storage contents.  A false positive causes the server to search its local store, which is slow, only to find nothing.

To the first example, I suspect that spam filters are far more sophisticated than simply looking for whitelisted email addresses.  So the example feels artificial and overblown as practical motivation.  But more to the point, the security notion proposed by [NY] gives S ---the set of whitelisted email addresses--- to the adversary.  In practice, knowledge of these email addresses may be more damaging than creating a false-positive email address! (Keep in mind that the attacker wins, in this scenario, by creating any email address that passes the filter, even ones that bear no resemblance to real email addresses.)  From this perspective, the [NY] security definition is narrow in its scope, even assuming it says something useful about spam filtering.

\jknote{Yes, although another way to interpret this is that the adversary cannot find a false positive EVEN IF it had the whitelisted email addresses, even if in practice it does not.}
\tsnote{Fair enough. And this potentially unrealistic attack is preventable by a simple countermeasure.  That said, I’m not convinced the countermeasure is easy to deploy at scale, or that it meshes well with real deployments.  (See below.)  }

I am less critical of the second example, although this is mostly because I feel ignorant of how real CDNs operate.  However, I believe that the following is common.  Say I’m a caching server.  If my Bloom filter tells me that some requested content is not locally stored, then I check the Bloom filters of my network neighbors, these having been shared with me.  When a neighbor’s Bloom filter is positive for the requested content, I contact that neighbor, and that neighbor only.  (If no neighbor has it, then I have to retrieve it from some slower and more distant source, like the Web.)  Now, the [NY] construction uses a PRP, meaning that a secret key is involved in evaluating the Bloom filter.  Thus, I need to know the secret keys of my neighbors in order to operate in the way just described.  This seems troublesome in practice, at scale.  Thus, their solution to a (potentially) real problem seems to be a non-solution.

Note that there is at least one way to avoid this knowledge of secret keys issues.  Namely, assume that content-caching servers distinguish between Bloom filter queries that originate from outside the CDN (e.g. users’ browsers) and those from within (e.g. other servers), and that the attacker only makes the former type of queries.  Then each server could store its neighbors’ Bloom filters in the clear, as normal, and only use the PRP construction when responding to external queries.  I don’t know how realistic this separation of queries is, in practice, nor how easy it would be to deploy such a strategy.  I also don’t know if this restricted attack scenario is interesting or plausible.

Moving on, the paper spends too much time asking and answering questions that are interesting to theoreticians, only.  Specifically, the relationship between the existence of one-way functions and Bloom filters that are secure relative to their definition.

\jknote{Agreed. =)}

Finally, the Bloom filter formalization that is given does not obviously capture traditional Bloom filters!  Traditionally, both Bloom filter population and querying procedures use hash functions $h_1,h_2,...h_k$ that each map from some universe $U$ to $[m]$, where $m$ is the bit-length of the array $M$ that represents a given set $S$.  These hash functions are missing from the authors’ definition, apparently swept into the algorithms $B_1$ (population) and $B_2$ (querying).  I don’t really understand how, though. They allow $B_1$ to be randomized, which would let $B_1$ pick the hash functions.  But the security definition provides no way for $B_1$ to share these with $B_2$.  So how would $B_2$ be able to process set-membership queries?  (Note: based on how they define the size of the representation M, $B_1$ cannot include descriptions of $h_1, h_2, \ldots , h_k$ in $M$.  They really mean $M$ to be the array that represents the set $S$.)  In general, their formalization of the Bloom filter primitive is badly underdefined.

\jknote{You had me for a minute...but actually I think the representations of the hash functions ARE included in the representation. This is not explicit, but is consistent with the way they state their positive result in the computational setting (“...if there is a Bloom filter using m bits of memory, then there is a strongly resilient Bloom filter using $m + \lambda$ bits of memory…”); more importantly, it seems explicit from their treatment of the IT case.}

\tsnote{Perhaps.  I’m still not convinced.  If you read the text preceding the statement of Theorem 1.2 (page 4), you’ll see their discussion of lower bounds on “memory” required for a given set size and FP rate.  This bound is the classical one for Bloom filters and speaks only of the (bit)size of the array.  It says nothing about the description of the hash functions needed to populate the array.  In fact, this lower bound is for any method of representing set S in a bit array, not only for hashing-based methods.

Maybe they are defining “memory” differently in this discussion than in their theorems.  This would be annoying, and I think it isn’t the case.  So for the moment, I’ll continue to hold my position on this.

(I’ll also point out that they explicitly say that $B_1$ outputs “compressed representation of [set $S$] $B_1(S)=M$”.  But it would be easy to have small sets $S$ for which the bitsize of the array is smaller than the total bitsize of $S$, yet the combined bitsize of array + hash functions is larger.)

But for the sake of argument, say that their representation size m does include the description of the hash functions.  To me, this is a clunky way to handle this matter.  For one thing, it doesn’t play well with analysis in the ROM, which is the traditional way to establish results relating FP rate, set size and array size for Bloom filters.  (I know there are standard model assumptions that suffice, too.)  For another, this way of accounting makes unnecessarily hard to answer the two important operational questions: how big is the array, and how many hash function calls do I need to make per item/query?

I’ll agree that this syntactic issue does not matter for theorem statements such as “...if there is a Bloom filter using $m$ bits of memory, then there is a strongly resilient Bloom filter using $m + \lambda$ bits of memory…”  In fact, this statement would be true for the traditional way of defining Bloom filter memory (array size), since the extra space is basically for a PRP key.}

\paragraph{Obvious Tasks. }

\begin{itemize}
\item Get a solid handle on how Bloom filters are used in practice, and what generalizations have gained traction in the academic literature. (See wikipedia, a section of which I’ve pasted in at the end of this doc.)
\item Work out a proper “cryptographic” syntax for the Bloom filter primitive.  (Possibly something more general, see number 5.)
\item Establish security notions that are appropriate for broader use cases (e.g. privacy of $S$, privacy of the representation $M$, authenticity of representation $M$), potentially distinguishing between “external” and “internal” attacks for, say, CDN scenarios
\item Develop constructions that are secure and are supported by a practice-informed argument for deployment
\item Expand from Bloom filters to “Approximate Set Membership” primitives, i.e. more general compressed representations (of sets) that admit queries  Note: this should be done only if it makes sense -- i.e. it doesn’t explode the scope, it doesn’t send us off too far into theoryland.
\end{itemize}

\jknote{I think privacy is an interesting question. I also thought that both privacy and soundness could be considered both in the setting when the representation is “hidden” from the adversary (as in the paper under discussion) as well as in the setting where the representation is public. [Ahh...I see you have some similar thoughts further below.] Some thoughts about this:}

\begin{itemize}
\item Privacy in the “hidden” setting. Here the idea would be that queries about whether $x \in S$ reveal only the result of the query and nothing else.

\item Privacy in the “public” setting. Here we could assume the elements of $S$ have high entropy, and $S$ has low density, and require that the attacker cannot find $x \in S$ even when given the representation(!) I see no reason why this should not be achievable in the random oracle model, or possibly even in the standard model.

\item Soundness in the “public” setting. Note that if the soundness is 0.5 then the attacker can simply guess random elements until it finds a false positive. So one way to approach this is to look at negligible soundness error only. Or, in the random oracle model, you could count queries to the RO and bound the attacker’s success as a function of the number of queries it makes.
\end{itemize}

\paragraph{Basic Bloom filter syntax.}
As a first step, let us try to better formalize Bloom filters as a primitive.

Fix integers $m,k > 0$ and a nonempty set $U$.  Fix a symbol $\bot \not\in U$.  A “Bloom filter” is a triple  $B=(H,\mathsc{Rep},\mathsc{Qry})$.

The hash family $H = \{h_i : U \rightarrow [m]  | i in [k]\}$ is  set of~$k$ hash functions.

The representation mapping $\mathsc{Rep}: 2^U \rightarrow \bits^m$ takes a set $S \subseteq U$ as input, and outputs an $m$-bit representation~$M$ of $S$.  The query mapping $\mathsc{Qry}: \bits^m x U \rightarrow \bits$ takes a representation $M$ and an element $x \in U$ and returns a bit.  We assume that both $\mathsc{Rep}$ and $\mathsc{Qry}$ may make (black-box) calls to the functions in~$H$.  Both $\mathsc{Rep}$ and $\mathsc{Qry}$ are deterministic.

Note that this is already a slight generalization of a true Bloom filter, because the syntax does not proscribe how Rep and Qry operate.

\jknote{Why not simply include the description of the hash function(s) as part of the size of the representation? I.e., Have $B_1$, $B_2$ exactly as in the paper, but explicitly count the bits needed to represent the hash functions as part of the representation output by $B_1$.}
\tsnote{See my comments above.}
\jknote{There could be some advantages to your formulation, though, if you imagine choosing the hash functions “once and for all” and then running Rep on many different sets$ S_1, S_2, \ldots$ in that case we would care about the amortized size of the representation, and so not count the bits needed to describe the hash functions.}

For proper operation, we demand that for all $S$, and for all $x \in S, \mathsc{Qry}(\mathsc{Rep}(S),x)=1$.  Observe that this is only a correctness condition.  Soundness will be cast as a security experiment, following [NY].

\paragraph{Bloom filters with operations. }

Here we extend the basic Bloom filter syntax to allow for variations on the traditional Bloom filter, e.g. counting Bloom filters.  [We should find out what are the important variations! I only know of a few.  None of these require randomness, so I’ll continue to formalize everything as deterministic.][“Scaling Bloom filters”, appear to allow the parameter m, below, to vary.][This syntax might naturally support count-min sketches, too.]

\jknote{You probably want to even be more general and talk about “data structures” more abstractly.}
\tsnote{Sure, but I’d rather take it a step at a time.  First, restrict to this class of Bloom filters with operations, and see what can be said that is interesting and practically relevant.  (There may already be quite a bit.)  Only once that picture starts to emerge would I want to expand to a more general class of primitives.
Expanding the class to “data structures” likely brings other related work into scope.  Haven’t Goodrich and various coauthors worked on data structures with security?}

Fix integers $m,k > 0$, and nonempty sets $U$ (the universe) and $A$ (the output alphabet).  Fix a symbol $\bot \not\in U$.

A “Bloom filter with operations” is a four-tuple  $B=(H,\mathsc{Rep},\mathsc{Qry}, \mathsc{Ops})$.

As before, the hash family $H = \{h_i : U \rightarrow [m]  | i in [k] \}$ is  set of~$k$ hash functions.

The set $\mathsc{Ops}$ is the finite collection of allowable operations.  All operations are of the form 
$f: U^* x U^* \rightarrow U^* \cup \{\bot\}$.  That is, an operation takes tuples $S$ and $T$ as input, and returns either tuple $S’$ or the distinguished symbol $\bot$.  (Examples: $f_{\mathrm{add}}((a,b,c,c),(c,d,d)) = (a,b,c,c,c,d,d); f_{\mathrm{del}}((a,b,c),(c))=(a,b); f_{\mathrm{del}}((a,b,c),(c,d)) = \bot$.  Could allow more advanced things like $f_{\mathrm{setify}}((a,b,c,c),(c,d,a)) = (a,b,c,d))$ to support what already exists in the literature and (more importantly) in practice.)  We assume that if an operation~$f$ is called outside of its domain, it returns $\bot$.

The representation mapping $P: U^* \rightarrow A^m \cup \{\bot\}$.  It takes a tuple~$S$, and returns an $m$-vector~$M$ of elements from the alphabet~$A$, or the distinguished symbol~$\bot$.  We call the (non-$\bot$) output of $P(S)$ the representation $S$.

The query mapping $Q: A^m x U \rightarrow \{0,1\}$ takes a representation $M$ and an element $x \in U$ and returns a bit.  We assume that both~$P$ and~$Q$ may make (black-box) calls to the functions in~$H$.

Correctness is defined as follows.  Let $S,T$ be arbitrary elements of $U^*$, and let~$f$ be an arbitrary operation in $\mathsc{Ops}$.  If $f(S,T) = S’$ is in $U^*$ (i.e. is not $\bot$), then for all $x \in S’$ we demand that $\mathsc{Qry}(\mathsc{Rep}(S’),x)=1$. [Note: might need a stronger condition that this holds for any sequence of operations that do not result in $\bot$.]

\paragraph{Further Syntactic Generalizations. }

Allow $\mathsc{Ops}, P, Q$ to be randomized?  Replace hash function family with something more general?  Note that we shouldn’t just generalize for the sake of it.  Let’s try to stay motivated by reality...

\paragraph{Alternative Security Definitions. }

NOTE: this section is very sketchy.  It was actually written first, before I realized how underspecified the [NY] syntax is.

The first alternative I’ll call “partial-inversion resistance”.  It captures privacy of the Bloom filter input.  Sticking with the [NY] notation, let $B=(B_1, B_2)$ be the bloom filter population and querying algorithms, respectively.  Fix integers $n,m > 0$.  The (still informal) experiment is as follows:

$S=\{x_1,x_2,..., x_n\}$ sampled from U according to some distribution $D_U$.  $B_1(S,m)$ returns~$M$, an array of~$m$ bits. Adversary~$\advA$ is given an oracle for $B_2(M,\cdot)$  (and assume $B_2$ outputs 0 or 1).  Adversary~$\advA$ halts with output $z$, and wins if $z \in S$.

Essentially, $B_1$ is a mapping from $n$-tuples (over $S$) to $m$-tuples (over $\{0,1\}$, in typical bloom filters).  The adversary’s job is to determine some component of the input to $B_1$, i.e. partial inversion of M. \tsnote{How does this relate to Ristenpart et al.’s recent work on model-inversion attacks?}

Definitional choices remain...

Should $B_1$ be randomized, as it is in [NY]?  Traditionally, no: population of the Bloom filter array is a deterministic process.  (Here I’m viewing the sampling of the hash functions as external to $B_1$.)   An implication of deterministic $B_1$ seems to be that distribution $D_U$ must have reasonable min-entropy.  
Should the hash functions used by $B_1$ and $B_2$ in traditional Bloom filters be explicit in the syntax, and explicitly surfaced in the security notion?  
Should they be given as oracles to $\advA$?  That is, should we assume that attackers know the hash functions begin used? Should $\advA$ be given $m = |M|$ as input?  That is, should we assume that attackers know the size of the representation?
Should $B_2$ be deterministic?  Traditionally, yes.  But I allowing it to be stateful admits more advanced Bloom filter constructions, e.g. counting Bloom filters.  [NY] do consider the case that $B_2$ is randomized (“unstable representations”), but I don’t know of any Bloom filters whose array representations are probabilistic over time.

Note that false positives do not count as wins in this experiment.  They could be by, say, changing the winning condition to “Adversary $\advA$ wins if $B_2(M,\cdot)$ ever returns 1”.  But I think this muddles together separate security goals --- forging a bogus input, and learning one of the real inputs.  So I prefer to keep them separate.  (I’d want to rewrite the [NY] notion, however.)

=================================
From the Wikipedia page...
Examples[edit]
Google BigTable, Apache HBase and Apache Cassandra use Bloom filters to reduce the disk lookups for non-existent rows or columns. Avoiding costly disk lookups considerably increases the performance of a database query operation.[7][8]
The Google Chrome web browser used to use a Bloom filter to identify malicious URLs. Any URL was first checked against a local Bloom filter, and only if the Bloom filter returned a positive result was a full check of the URL performed (and the user warned, if that too returned a positive result).[9][10]
The Squid Web Proxy Cache uses Bloom filters for cache digests.[11]
Bitcoin uses Bloom filters to speed up wallet synchronization.[12][13]
The Venti archival storage system uses Bloom filters to detect previously stored data.[14]
The SPIN model checker uses Bloom filters to track the reachable state space for large verification problems.[15]
The Cascading analytics framework uses Bloom filters to speed up asymmetric joins, where one of the joined data sets is significantly larger than the other (often called Bloom join[16] in the database literature).[17]
The Exim mail transfer agent (MTA) uses bloom filters in its rate-limit feature.[18]

### 2015-11-02 intro.tex
cheers

@@
 In fact, this lower bound is for any method of representing set S in a bit array, not only for hashing-based methods.
-
+%
 Maybe they are defining “memory” differently in this discussion than in their theorems.
@@
 So for the moment, I’ll continue to hold my position on this.
-
+%
 (I’ll also point out that they explicitly say that $B_1$ outputs “compressed representation of [set $S$] $B_1(S)=M$”.
 But it would be easy to have small sets $S$ for which the bitsize of the array is smaller than the total bitsize of $S$, yet the combined bitsize of array + hash functions is larger.)
-
+%
 But for the sake of argument, say that their representation size m does include the description of the hash functions.
@@
 (I know there are standard model assumptions that suffice, too.)  For another, this way of accounting makes unnecessarily hard to answer the two important operational questions: how big is the array, and how many hash function calls do I need to make per item/query?
-
+% 
 I’ll agree that this syntactic issue does not matter for theorem statements such as “...if there is a Bloom filter using $m$ bits of memory, then there is a strongly resilient Bloom filter using $m + \lambda$ bits of memory…”  In fact, this statement would be true for the traditional way of defining Bloom filter memory (array size), since the extra space is basically for a PRP key.}
@@
 \item Establish security notions that are appropriate for broader use cases (e.g.
-privacy of $S$, privacy of the representation $M$, authenticity of representation $M$), potentially distinguishing between “external” and “internal” attacks for, say, CDN scenarios
+privacy of~$S$, privacy of the representation~$M$, authenticity of representation~$M$), potentially distinguishing between “external” and “internal” attacks for, say, CDN scenarios
 \item Develop constructions that are secure and are supported by a practice-informed argument for deployment
@@
 I also thought that both privacy and soundness could be considered both in the setting when the representation is “hidden” from the adversary (as in the paper under discussion) as well as in the setting where the representation is public.
-[Ahh...I see you have some similar thoughts further below.] Some thoughts about this:}
-
-\begin{itemize}
-\item Privacy in the “hidden” setting. Here the idea would be that queries about whether $x \in S$ reveal only the result of the query and nothing else.
-
-\item Privacy in the “public” setting.
-Here we could assume the elements of $S$ have high entropy, and $S$ has low density, and require that the attacker cannot find $x \in S$ even when given the representation(!) I see no reason why this should not be achievable in the random oracle model, or possibly even in the standard model.
-
-\item Soundness in the “public” setting.
+[Ahh...I see you have some similar thoughts further below.] Some thoughts about this:
+(1) Privacy in the “hidden” setting. Here the idea would be that queries about whether $x \in S$ reveal only the result of the query and nothing else;  
+(2) Privacy in the “public” setting.
+Here we could assume the elements of~$S$ have high entropy, and~$S$ has low density, and require that the attacker cannot find~$x \in S$ even when given the representation(!) I see no reason why this should not be achievable in the random oracle model, or possibly even in the standard model;
+(3) Soundness in the “public” setting.
 Note that if the soundness is 0.5 then the attacker can simply guess random elements until it finds a false positive.
@@
 Or, in the random oracle model, you could count queries to the RO and bound the attacker’s success as a function of the number of queries it makes.
-\end{itemize}
+}
 
@@
 The representation mapping $\mathsc{Rep}: 2^U \rightarrow \bits^m$ takes a set $S \subseteq U$ as input, and outputs an $m$-bit representation~$M$ of $S$.
-The query mapping $\mathsc{Qry}: \bits^m x U \rightarrow \bits$ takes a representation $M$ and an element $x \in U$ and returns a bit.
+The query mapping $\mathsc{Qry}: \bits^m \times U \rightarrow \bits$ takes a representation $M$ and an element $x \in U$ and returns a bit.
 We assume that both $\mathsc{Rep}$ and $\mathsc{Qry}$ may make (black-box) calls to the functions in~$H$.
@@
 The set $\mathsc{Ops}$ is the finite collection of allowable operations.  All operations are of the form 
-$f: U^* x U^* \rightarrow U^* \cup \{\bot\}$.
-That is, an operation takes tuples $S$ and $T$ as input, and returns either tuple $S’$ or the distinguished symbol $\bot$.
+$f: U^* \times U^* \rightarrow U^* \cup \{\bot\}$.
+That is, an operation takes tuples~$S$ and~$T$ as input, and returns either tuple~$S’$ or the distinguished symbol $\bot$.
 (Examples: $f_{\mathrm{add}}((a,b,c,c),(c,d,d)) = (a,b,c,c,c,d,d); f_{\mathrm{del}}((a,b,c),(c))=(a,b); f_{\mathrm{del}}((a,b,c),(c,d)) = \bot$.
@@
 
-The query mapping $Q: A^m x U \rightarrow \{0,1\}$ takes a representation $M$ and an element $x \in U$ and returns a bit.
+The query mapping $Q: A^m \times U \rightarrow \{0,1\}$ takes a representation $M$ and an element $x \in U$ and returns a bit.
 We assume that both~$P$ and~$Q$ may make (black-box) calls to the functions in~$H$.

### 2015-12-08 intro.tex
cheers

@@
 \begin{itemize}
-\item [NY] formalize and investigate a security notion of limited interest
+\item The NY paper formalizes and investigates a security notion of limited interest
 \item The proposed construction won’t scale in common network applications
@@
 more general compressed representations (of sets) that admit queries  Note: this should be done only if it makes sense -- i.e.
+it doesn’t explode the scope, it doesn’t send us off too far into theoryland.
+\item Expand more generally to hash-based approximate set operations, e.g.\ minhash methods for approximating $J(A,B)$ for sets $A,B$.
+Note: this should be done only if it makes sense -- i.e.
 it doesn’t explode the scope, it doesn’t send us off too far into theoryland.

### 2016-05-17 intro.tex
restructuring, fixing typos

@@
 (That value is a function of the size of the set being represented, the representation size, the size of the universe, and the number of hash functions.)  This paper ([NY]) replaces the traditional IT notion with a computational notion, and casts it as a security experiment/goal.
-Namely: given the set S that is represented by the Bloom filter, and access to an oracle for Bloom filter set-membership queries, an attacker must find a false positive.
+Namely: given the set~$S$ that is represented by the Bloom filter, and access to an oracle for Bloom filter set-membership queries, an attacker must find a false positive.
 
@@
 [NY] points to whitelisting spam filters as an example.
-That is, a Bloom filter is populated with set S of whitelisted email addresses, so a false positive translates to an attacker finding an email address that sneaks through the filter.
+That is, a Bloom filter is populated with set~$S$ of whitelisted email addresses, so a false positive translates to an attacker finding an email address that sneaks through the filter.
 [NY] suggest a second example of content-caching servers that keep a Bloom filter of their own storage contents.
@@
 So the example feels artificial and overblown as practical motivation.
-But more to the point, the security notion proposed by [NY] gives S ---the set of whitelisted email addresses--- to the adversary.
+But more to the point, the security notion proposed by [NY] gives~$S$ ---the set of whitelisted email addresses--- to the adversary.
 In practice, knowledge of these email addresses may be more damaging than creating a false-positive email address!
@@
 And this potentially unrealistic attack is preventable by a simple countermeasure.
-That said, I’m not convinced the countermeasure is easy to deploy at scale, or that it meshes well with real deployments.
+That said, I'm not convinced the countermeasure is easy to deploy at scale, or that it meshes well with real deployments.
 (See below.)  }
@@
 However, I believe that the following is common.
-Say I’m a caching server.
+Say I'm a caching server.
 If my Bloom filter tells me that some requested content is not locally stored, then I check the Bloom filters of my network neighbors, these having been shared with me.
-When a neighbor’s Bloom filter is positive for the requested content, I contact that neighbor, and that neighbor only.
+When a neighbor's Bloom filter is positive for the requested content, I contact that neighbor, and that neighbor only.
 (If no neighbor has it, then I have to retrieve it from some slower and more distant source, like the Web.)  Now, the [NY] construction uses a PRP, meaning that a secret key is involved in evaluating the Bloom filter.
@@
 These hash functions are missing from the authors’ definition, apparently swept into the algorithms $B_1$ (population) and $B_2$ (querying).
-I don’t really understand how, though.
+I don't really understand how, though.
 They allow $B_1$ to be randomized, which would let $B_1$ pick the hash functions.
@@
 \jknote{You had me for a minute...but actually I think the representations of the hash functions ARE included in the representation.
-This is not explicit, but is consistent with the way they state their positive result in the computational setting (“...if there is a Bloom filter using m bits of memory, then there is a strongly resilient Bloom filter using $m + \lambda$ bits of memory…”); more importantly, it seems explicit from their treatment of the IT case.}
+This is not explicit, but is consistent with the way they state their positive result in the computational setting (“...if there is a Bloom filter using $m$ bits of memory, then there is a strongly resilient Bloom filter using $m + \lambda$ bits of memory…”); more importantly, it seems explicit from their treatment of the IT case.}
 
 \tsnote{Perhaps.
-I’m still not convinced.
-If you read the text preceding the statement of Theorem 1.2 (page 4), you’ll see their discussion of lower bounds on “memory” required for a given set size and FP rate.
+I'm still not convinced.
+If you read the text preceding the statement of Theorem 1.2 (page 4), you'll see their discussion of lower bounds on “memory” required for a given set size and FP rate.
 This bound is the classical one for Bloom filters and speaks only of the (bit)size of the array.
 It says nothing about the description of the hash functions needed to populate the array.
-In fact, this lower bound is for any method of representing set S in a bit array, not only for hashing-based methods.
+In fact, this lower bound is for any method of representing set $S$ in a bit array, not only for hashing-based methods.
 %
 Maybe they are defining “memory” differently in this discussion than in their theorems.
-This would be annoying, and I think it isn’t the case.
-So for the moment, I’ll continue to hold my position on this.
+This would be annoying, and I think it isn't the case.
+So for the moment, I'll continue to hold my position on this.
 %
-(I’ll also point out that they explicitly say that $B_1$ outputs “compressed representation of [set $S$] $B_1(S)=M$”.
+(I'll also point out that they explicitly say that $B_1$ outputs “compressed representation of [set $S$] $B_1(S)=M$”.
 But it would be easy to have small sets $S$ for which the bitsize of the array is smaller than the total bitsize of $S$, yet the combined bitsize of array + hash functions is larger.)
@@
 To me, this is a clunky way to handle this matter.
-For one thing, it doesn’t play well with analysis in the ROM, which is the traditional way to establish results relating FP rate, set size and array size for Bloom filters.
+For one thing, it doesn't play well with analysis in the ROM, which is the traditional way to establish results relating FP rate, set size and array size for Bloom filters.
 (I know there are standard model assumptions that suffice, too.)  For another, this way of accounting makes unnecessarily hard to answer the two important operational questions: how big is the array, and how many hash function calls do I need to make per item/query?
 % 
-I’ll agree that this syntactic issue does not matter for theorem statements such as “...if there is a Bloom filter using $m$ bits of memory, then there is a strongly resilient Bloom filter using $m + \lambda$ bits of memory…”  In fact, this statement would be true for the traditional way of defining Bloom filter memory (array size), since the extra space is basically for a PRP key.}
+I'll agree that this syntactic issue does not matter for theorem statements such as “...if there is a Bloom filter using $m$ bits of memory, then there is a strongly resilient Bloom filter using $m + \lambda$ bits of memory…”  In fact, this statement would be true for the traditional way of defining Bloom filter memory (array size), since the extra space is basically for a PRP key.}
 
@@
 \item Get a solid handle on how Bloom filters are used in practice, and what generalizations have gained traction in the academic literature.
-(See wikipedia, a section of which I’ve pasted in at the end of this doc.)
+(See wikipedia, a section of which I've pasted in at the end of this doc.)
 \item Work out a proper “cryptographic” syntax for the Bloom filter primitive.  (Possibly something more general, see number 5.)
@@
 more general compressed representations (of sets) that admit queries  Note: this should be done only if it makes sense -- i.e.
-it doesn’t explode the scope, it doesn’t send us off too far into theoryland.
+it doesn't explode the scope, it doesn't send us off too far into theoryland.
 \item Expand more generally to hash-based approximate set operations, e.g.\ minhash methods for approximating $J(A,B)$ for sets $A,B$.
 Note: this should be done only if it makes sense -- i.e.
-it doesn’t explode the scope, it doesn’t send us off too far into theoryland.
+it doesn't explode the scope, it doesn't send us off too far into theoryland.
 \end{itemize}
@@
 So one way to approach this is to look at negligible soundness error only.
-Or, in the random oracle model, you could count queries to the RO and bound the attacker’s success as a function of the number of queries it makes.
+Or, in the random oracle model, you could count queries to the RO and bound the attacker's success as a function of the number of queries it makes.
 }
 
-\paragraph{Basic Bloom filter syntax.}
-As a first step, let us try to better formalize Bloom filters as a primitive.
-
-Fix integers $m,k > 0$ and a nonempty set $U$.  Fix a symbol $\bot \not\in U$.  A “Bloom filter” is a triple  $B=(H,\mathsc{Rep},\mathsc{Qry})$.
-
-The hash family $H = \{h_i : U \rightarrow [m]  | i in [k]\}$ is  set of~$k$ hash functions.
-
-The representation mapping $\mathsc{Rep}: 2^U \rightarrow \bits^m$ takes a set $S \subseteq U$ as input, and outputs an $m$-bit representation~$M$ of $S$.
-The query mapping $\mathsc{Qry}: \bits^m \times U \rightarrow \bits$ takes a representation $M$ and an element $x \in U$ and returns a bit.
-We assume that both $\mathsc{Rep}$ and $\mathsc{Qry}$ may make (black-box) calls to the functions in~$H$.
-Both $\mathsc{Rep}$ and $\mathsc{Qry}$ are deterministic.
-
-Note that this is already a slight generalization of a true Bloom filter, because the syntax does not proscribe how Rep and Qry operate.
-
-\jknote{Why not simply include the description of the hash function(s) as part of the size of the representation?
-I.e., Have $B_1$, $B_2$ exactly as in the paper, but explicitly count the bits needed to represent the hash functions as part of the representation output by $B_1$.}
-\tsnote{See my comments above.}
-\jknote{There could be some advantages to your formulation, though, if you imagine choosing the hash functions “once and for all” and then running Rep on many different sets$ S_1, S_2, \ldots$ in that case we would care about the amortized size of the representation, and so not count the bits needed to describe the hash functions.}
-
-For proper operation, we demand that for all $S$, and for all $x \in S, \mathsc{Qry}(\mathsc{Rep}(S),x)=1$.
-Observe that this is only a correctness condition.
-Soundness will be cast as a security experiment, following [NY].
-
-\paragraph{Bloom filters with operations. }
-
-Here we extend the basic Bloom filter syntax to allow for variations on the traditional Bloom filter, e.g.
-counting Bloom filters.
-[We should find out what are the important variations!
-I only know of a few.
-None of these require randomness, so I’ll continue to formalize everything as deterministic.][“Scaling Bloom filters”, appear to allow the parameter m, below, to vary.][This syntax might naturally support count-min sketches, too.]
-
-\jknote{You probably want to even be more general and talk about “data structures” more abstractly.}
-\tsnote{Sure, but I’d rather take it a step at a time.
-First, restrict to this class of Bloom filters with operations, and see what can be said that is interesting and practically relevant.
-(There may already be quite a bit.)  Only once that picture starts to emerge would I want to expand to a more general class of primitives.
-Expanding the class to “data structures” likely brings other related work into scope.  Haven’t Goodrich and various coauthors worked on data structures with security?}
-
-Fix integers $m,k > 0$, and nonempty sets $U$ (the universe) and $A$ (the output alphabet).  Fix a symbol $\bot \not\in U$.
-
-A “Bloom filter with operations” is a four-tuple  $B=(H,\mathsc{Rep},\mathsc{Qry}, \mathsc{Ops})$.
-
-As before, the hash family $H = \{h_i : U \rightarrow [m]  | i in [k] \}$ is  set of~$k$ hash functions.
-
-The set $\mathsc{Ops}$ is the finite collection of allowable operations.  All operations are of the form 
-$f: U^* \times U^* \rightarrow U^* \cup \{\bot\}$.
-That is, an operation takes tuples~$S$ and~$T$ as input, and returns either tuple~$S’$ or the distinguished symbol $\bot$.
-(Examples: $f_{\mathrm{add}}((a,b,c,c),(c,d,d)) = (a,b,c,c,c,d,d); f_{\mathrm{del}}((a,b,c),(c))=(a,b); f_{\mathrm{del}}((a,b,c),(c,d)) = \bot$.
-Could allow more advanced things like $f_{\mathrm{setify}}((a,b,c,c),(c,d,a)) = (a,b,c,d))$ to support what already exists in the literature and (more importantly) in practice.)  We assume that if an operation~$f$ is called outside of its domain, it returns $\bot$.
-
-The representation mapping $P: U^* \rightarrow A^m \cup \{\bot\}$.
-It takes a tuple~$S$, and returns an $m$-vector~$M$ of elements from the alphabet~$A$, or the distinguished symbol~$\bot$.
-We call the (non-$\bot$) output of $P(S)$ the representation $S$.
-
-The query mapping $Q: A^m \times U \rightarrow \{0,1\}$ takes a representation $M$ and an element $x \in U$ and returns a bit.
-We assume that both~$P$ and~$Q$ may make (black-box) calls to the functions in~$H$.
-
-Correctness is defined as follows.
-Let $S,T$ be arbitrary elements of $U^*$, and let~$f$ be an arbitrary operation in $\mathsc{Ops}$.
-If $f(S,T) = S’$ is in $U^*$ (i.e.
-is not $\bot$), then for all $x \in S’$ we demand that $\mathsc{Qry}(\mathsc{Rep}(S’),x)=1$.
-[Note: might need a stronger condition that this holds for any sequence of operations that do not result in $\bot$.]
-
-\paragraph{Further Syntactic Generalizations. }
-
-Allow $\mathsc{Ops}, P, Q$ to be randomized?
-Replace hash function family with something more general?
-Note that we shouldn’t just generalize for the sake of it.
-Let’s try to stay motivated by reality...
-
-\paragraph{Alternative Security Definitions. }
-
-NOTE: this section is very sketchy.  It was actually written first, before I realized how underspecified the [NY] syntax is.
-
-The first alternative I’ll call “partial-inversion resistance”.
-It captures privacy of the Bloom filter input.
-Sticking with the [NY] notation, let $B=(B_1, B_2)$ be the bloom filter population and querying algorithms, respectively.
-Fix integers $n,m > 0$.
-The (still informal) experiment is as follows:
-
-$S=\{x_1,x_2,..., x_n\}$ sampled from U according to some distribution $D_U$.
-$B_1(S,m)$ returns~$M$, an array of~$m$ bits.
-Adversary~$\advA$ is given an oracle for $B_2(M,\cdot)$  (and assume $B_2$ outputs 0 or 1).
-Adversary~$\advA$ halts with output $z$, and wins if $z \in S$.
-
-Essentially, $B_1$ is a mapping from $n$-tuples (over $S$) to $m$-tuples (over $\{0,1\}$, in typical bloom filters).
-The adversary’s job is to determine some component of the input to $B_1$, i.e.
-partial inversion of M.
-\tsnote{How does this relate to Ristenpart et al.’s recent work on model-inversion attacks?}
-
-Definitional choices remain...
-
-Should $B_1$ be randomized, as it is in [NY]?
-Traditionally, no: population of the Bloom filter array is a deterministic process.
-(Here I’m viewing the sampling of the hash functions as external to $B_1$.)   An implication of deterministic $B_1$ seems to be that distribution $D_U$ must have reasonable min-entropy.
-Should the hash functions used by $B_1$ and $B_2$ in traditional Bloom filters be explicit in the syntax, and explicitly surfaced in the security notion?  
-Should they be given as oracles to $\advA$?
-That is, should we assume that attackers know the hash functions begin used?
-Should $\advA$ be given $m = |M|$ as input?
-That is, should we assume that attackers know the size of the representation?
-Should $B_2$ be deterministic?
-Traditionally, yes.
-But I allowing it to be stateful admits more advanced Bloom filter constructions, e.g.
-counting Bloom filters.
-[NY] do consider the case that $B_2$ is randomized (“unstable representations”), but I don’t know of any Bloom filters whose array representations are probabilistic over time.
-
-Note that false positives do not count as wins in this experiment.
-They could be by, say, changing the winning condition to “Adversary $\advA$ wins if $B_2(M,\cdot)$ ever returns 1”.
-But I think this muddles together separate security goals --- forging a bogus input, and learning one of the real inputs.
-So I prefer to keep them separate.
-(I’d want to rewrite the [NY] notion, however.)
-
-=================================
-From the Wikipedia page...
-Examples[edit]
+\paragraph{From the Wikipedia page...}
 Google BigTable, Apache HBase and Apache Cassandra use Bloom filters to reduce the disk lookups for non-existent rows or columns.

### 2016-05-17 security-notions.tex
restructuring, fixing typos

\section{Security notions}
\tsnote{Begin by giving the [NY] FP-notion in our experiment format}

\paragraph{Alternative Security Definitions. }
NOTE: this section is very sketchy.  It was actually written first, before I realized how underspecified the [NY] syntax is.

The first alternative I'll call “partial-inversion resistance”.  It captures privacy of the Bloom filter input.  Sticking with the [NY] notation, let $B=(B_1, B_2)$ be the bloom filter population and querying algorithms, respectively.  Fix integers $n,m > 0$.  The (still informal) experiment is as follows:

$S=\{x_1,x_2,..., x_n\}$ sampled from U according to some distribution $D_U$.  $B_1(S,m)$ returns~$M$, an array of~$m$ bits. Adversary~$\advA$ is given an oracle for $B_2(M,\cdot)$  (and assume $B_2$ outputs 0 or 1).  Adversary~$\advA$ halts with output $z$, and wins if $z \in S$.

Essentially, $B_1$ is a mapping from $n$-tuples (over $S$) to $m$-tuples (over $\{0,1\}$, in typical bloom filters).  The adversary's job is to determine some component of the input to $B_1$, i.e. partial inversion of M. \tsnote{How does this relate to Ristenpart et al.'s recent work on model-inversion attacks?}

Definitional choices remain...

Should $B_1$ be randomized, as it is in [NY]?  Traditionally, no: population of the Bloom filter array is a deterministic process.  (Here I'm viewing the sampling of the hash functions as external to $B_1$.)   An implication of deterministic $B_1$ seems to be that distribution $D_U$ must have reasonable min-entropy.  
Should the hash functions used by $B_1$ and $B_2$ in traditional Bloom filters be explicit in the syntax, and explicitly surfaced in the security notion?  
Should they be given as oracles to $\advA$?  That is, should we assume that attackers know the hash functions begin used? Should $\advA$ be given $m = |M|$ as input?  That is, should we assume that attackers know the size of the representation?
Should $B_2$ be deterministic?  Traditionally, yes.  But I allowing it to be stateful admits more advanced Bloom filter constructions, e.g. counting Bloom filters.  [NY] do consider the case that $B_2$ is randomized (“unstable representations”), but I don't know of any Bloom filters whose array representations are probabilistic over time.

Note that false positives do not count as wins in this experiment.  They could be by, say, changing the winning condition to “Adversary $\advA$ wins if $B_2(M,\cdot)$ ever returns 1”.  But I think this muddles together separate security goals --- forging a bogus input, and learning one of the real inputs.  So I prefer to keep them separate.  (I'd want to rewrite the [NY] notion, however.)

### 2016-05-17 syntax.tex
restructuring, fixing typos

\section{Syntax}
As a first step, let us try to better formalize Bloom filters as a primitive.

\paragraph{Basic Bloom filter syntax.}
Fix integers $m,k > 0$ and a nonempty set $U$.  Fix a symbol $\bot \not\in U$.  A “Bloom filter” is a triple  $B=(H,\mathsc{Rep},\mathsc{Qry})$.

The hash family $H = \{h_i : U \rightarrow [m]  | i in [k]\}$ is  set of~$k$ hash functions.

The representation mapping $\mathsc{Rep}: 2^U \rightarrow \bits^m$ takes a set $S \subseteq U$ as input, and outputs an $m$-bit representation~$M$ of $S$.  The query mapping $\mathsc{Qry}: \bits^m \times U \rightarrow \bits$ takes a representation $M$ and an element $x \in U$ and returns a bit.  We assume that both $\mathsc{Rep}$ and $\mathsc{Qry}$ may make (black-box) calls to the functions in~$H$.  Both $\mathsc{Rep}$ and $\mathsc{Qry}$ are deterministic.

Note that this is already a slight generalization of a true Bloom filter, because the syntax does not proscribe how Rep and Qry operate.

\jknote{Why not simply include the description of the hash function(s) as part of the size of the representation? I.e., Have $B_1$, $B_2$ exactly as in the paper, but explicitly count the bits needed to represent the hash functions as part of the representation output by $B_1$.}
\tsnote{See my comments above.}
\jknote{There could be some advantages to your formulation, though, if you imagine choosing the hash functions “once and for all” and then running Rep on many different sets$ S_1, S_2, \ldots$ in that case we would care about the amortized size of the representation, and so not count the bits needed to describe the hash functions.}

For proper operation, we demand that for all $S$, and for all $x \in S, \mathsc{Qry}(\mathsc{Rep}(S),x)=1$.  Observe that this is only a correctness condition.  Soundness will be cast as a security experiment, following [NY].

\paragraph{Bloom filters with operations. }
Here we extend the basic Bloom filter syntax to allow for variations on the traditional Bloom filter, e.g. counting Bloom filters.  [We should find out what are the important variations! I only know of a few.  None of these require randomness, so I'll continue to formalize everything as deterministic.][“Scaling Bloom filters”, appear to allow the parameter m, below, to vary.][This syntax might naturally support count-min sketches, too.]

\jknote{You probably want to even be more general and talk about “data structures” more abstractly.}
\tsnote{Sure, but I'd rather take it a step at a time.  First, restrict to this class of Bloom filters with operations, and see what can be said that is interesting and practically relevant.  (There may already be quite a bit.)  Only once that picture starts to emerge would I want to expand to a more general class of primitives.
Expanding the class to “data structures” likely brings other related work into scope.  Haven't Goodrich and various coauthors worked on data structures with security?}

Fix integers $m,k > 0$, and nonempty sets $U$ (the universe) and $A$ (the output alphabet).  Fix a symbol $\bot \not\in U$.

A “Bloom filter with operations” is a four-tuple  $B=(H,\mathsc{Rep},\mathsc{Qry}, \mathsc{Ops})$.

As before, the hash family $H = \{h_i : U \rightarrow [m]  | i in [k] \}$ is  set of~$k$ hash functions.

The set $\mathsc{Ops}$ is the finite collection of allowable operations.  All operations are of the form 
$f: U^* \times U^* \rightarrow U^* \cup \{\bot\}$.  That is, an operation takes tuples~$S$ and~$T$ as input, and returns either tuple~$S'$ or the distinguished symbol $\bot$.  (Examples: $f_{\mathrm{add}}((a,b,c,c),(c,d,d)) = (a,b,c,c,c,d,d); f_{\mathrm{del}}((a,b,c),(c))=(a,b); f_{\mathrm{del}}((a,b,c),(c,d)) = \bot$.  Could allow more advanced things like $f_{\mathrm{setify}}((a,b,c,c),(c,d,a)) = (a,b,c,d))$ to support what already exists in the literature and (more importantly) in practice.)  We assume that if an operation~$f$ is called outside of its domain, it returns $\bot$.

The representation mapping $P: U^* \rightarrow A^m \cup \{\bot\}$.  It takes a tuple~$S$, and returns an $m$-vector~$M$ of elements from the alphabet~$A$, or the distinguished symbol~$\bot$.  We call the (non-$\bot$) output of $P(S)$ the representation $S$.

The query mapping $Q: A^m \times U \rightarrow \{0,1\}$ takes a representation $M$ and an element $x \in U$ and returns a bit.  We assume that both~$P$ and~$Q$ may make (black-box) calls to the functions in~$H$.

Correctness is defined as follows.  Let $S,T$ be arbitrary elements of $U^*$, and let~$f$ be an arbitrary operation in $\mathsc{Ops}$.  If $f(S,T) = S'$ is in $U^*$ (i.e. is not $\bot$), then for all $x \in S'$ we demand that $\mathsc{Qry}(\mathsc{Rep}(S'),x)=1$. [Note: might need a stronger condition that this holds for any sequence of operations that do not result in $\bot$.]

\paragraph{Further Syntactic Generalizations. }

Allow $\mathsc{Ops}, P, Q$ to be randomized?  Replace hash function family with something more general?  Note that we shouldn't just generalize for the sake of it.  Let's try to stay motivated by reality...

### 2016-05-17 syntax.tex
cheers

@@
 \paragraph{Basic Bloom filter syntax.}
-Fix integers $m,k > 0$ and a nonempty set $U$.  Fix a symbol $\bot \not\in U$.  A “Bloom filter” is a triple  $B=(H,\mathsc{Rep},\mathsc{Qry})$.
-
-The hash family $H = \{h_i : U \rightarrow [m]  | i in [k]\}$ is  set of~$k$ hash functions.
+Fix integers $m,k > 0$ and a nonempty set $U$.
+Fix a symbol $\bot \not\in U$.
+A “Bloom filter” is a triple  $B=(\mathcal{H},\mathsc{Rep},\mathsc{Qry})$.
+The hash family $\mathcal{H} = \{h_i : U \rightarrow [m]  \,|\,  i \in [k]\}$ is  set of~$k$ hash functions.
 
@@
 The query mapping $\mathsc{Qry}: \bits^m \times U \rightarrow \bits$ takes a representation $M$ and an element $x \in U$ and returns a bit.
-We assume that both $\mathsc{Rep}$ and $\mathsc{Qry}$ may make (black-box) calls to the functions in~$H$.
+We assume that both $\mathsc{Rep}$ and $\mathsc{Qry}$ may make (black-box) calls to the functions in~$\mathcal{H}$.
 Both $\mathsc{Rep}$ and $\mathsc{Qry}$ are deterministic.
@@
 \tsnote{See my comments above.}
-\jknote{There could be some advantages to your formulation, though, if you imagine choosing the hash functions “once and for all” and then running Rep on many different sets$ S_1, S_2, \ldots$ in that case we would care about the amortized size of the representation, and so not count the bits needed to describe the hash functions.}
+\jknote{There could be some advantages to your formulation, though, if you imagine choosing the hash functions “once and for all” and then running Rep on many different sets $ S_1, S_2, \ldots$ in that case we would care about the amortized size of the representation, and so not count the bits needed to describe the hash functions.}
 
@@
 Fix integers $m,k > 0$, and nonempty sets $U$ (the universe) and $A$ (the output alphabet).  Fix a symbol $\bot \not\in U$.  
-
-A “Bloom filter with operations” is a four-tuple  $B=(H,\mathsc{Rep},\mathsc{Qry}, \mathsc{Ops})$.
-
-As before, the hash family $H = \{h_i : U \rightarrow [m]  | i in [k] \}$ is  set of~$k$ hash functions.
+A “Bloom filter with operations” is a four-tuple  $B=(\mathcal{H},\mathsc{Rep},\mathsc{Qry}, \mathsc{Ops})$.  
+As before, the hash family $\mathcal{H} = \{h_i : U \rightarrow [m]  \,|\,  i \in [k] \}$ is  set of~$k$ hash functions.
 
@@
 The query mapping $Q: A^m \times U \rightarrow \{0,1\}$ takes a representation $M$ and an element $x \in U$ and returns a bit.
-We assume that both~$P$ and~$Q$ may make (black-box) calls to the functions in~$H$.
+We assume that both~$P$ and~$Q$ may make (black-box) calls to the functions in~$\mathcal{H}$.
 

### 2016-05-19 intro.tex
cheers
added another complaint to the opening list

@@
 \section{Introduction}
-\paragraph{Basic issues. }
+\paragraph{Basic issues in Naor-Yogev. }
 \begin{itemize}
 \item The NY paper formalizes and investigates a security notion of limited interest
-\item The proposed construction won’t scale in common network applications
+\item The proposed construction won't scale in common network applications
 \item The main results are of theoretical interest only
@@
 (This really irritates me.)  It isn’t clear that their Bloom filter formalization actually captures traditional Bloom filters!
+\item The ``adversarial-resilient Bloom Filter'' definition does not give the adversary access to the hash functions that created the representation; effectively, they are secret.
+This strikes me as quite odd, and seems to miss the point that finding a false positive should be hard, in practice, even if you know that the hash functions are $h_i(X)=\mathrm{SHA256}(\langle i \rangle \concat X)$.
 \end{itemize}
@@
 
-\begin{itemize}
+\begin{enumerate}
 \item Get a solid handle on how Bloom filters are used in practice, and what generalizations have gained traction in the academic literature.
@@
 it doesn't explode the scope, it doesn't send us off too far into theoryland.
-\end{itemize}
+\end{enumerate}
 

### 2016-05-20 intro.tex
more complaining :)

@@
 This strikes me as quite odd, and seems to miss the point that finding a false positive should be hard, in practice, even if you know that the hash functions are $h_i(X)=\mathrm{SHA256}(\langle i \rangle \concat X)$.
+(If the hash functions are not kept secret, the whole [NY] security notion kind of unravels; the adversary already is given~$S$, so if it knows the hash functions then you might as well just give it the whole Bloom filter data structure.)
+\item Not sure what Bloom filter-like data structures would have randomized querying procedures (``unsteady representations'').
+They mention the possibility of differential privacy mechanisms being incorporated into the querying procedure.
+But what's the purpose of this, if the security definition gives the adversary the set~$S$?
+(What are you keeping private?)
 \end{itemize}
@@
 So how would $B_2$ be able to process set-membership queries?
-(Note: based on how they define the size of the representation M, $B_1$ cannot include descriptions of $h_1, h_2, \ldots , h_k$ in $M$.
+(Note: based on how they define the size of the representation $M$, $B_1$ cannot include descriptions of $h_1, h_2, \ldots , h_k$ in $M$.
 They really mean $M$ to be the array that represents the set $S$.)  In general, their formalization of the Bloom filter primitive is badly underdefined.
@@
 %
-But for the sake of argument, say that their representation size m does include the description of the hash functions.
+But for the sake of argument, say that their representation size~$m$ does include the description of the hash functions.
 To me, this is a clunky way to handle this matter.
@@
 % 
-I'll agree that this syntactic issue does not matter for theorem statements such as “...if there is a Bloom filter using $m$ bits of memory, then there is a strongly resilient Bloom filter using $m + \lambda$ bits of memory…”  In fact, this statement would be true for the traditional way of defining Bloom filter memory (array size), since the extra space is basically for a PRP key.}
+I'll agree that this syntactic issue does not matter for theorem statements such as ``...if there is a Bloom filter using $m$ bits of memory, then there is a strongly resilient Bloom filter using $m + \lambda$ bits of memory…''.
+In fact, this statement would be true for the traditional way of defining Bloom filter memory (array size), since the extra space is basically for a PRP key.}
 

### 2016-05-20 intro.tex
I am now convinced that their syntax does *not* capture real Bloom filters.  I added a note to argue this even more forcefully than before :)

@@
 
+\tsnote{UPDATE (5/20/16): I'm now convinced that what they call memory size~$m$, when applied to real Bloom filters, is \emph{only} the size of the bit array, and does \emph{not} include a description of the hash functions.
+The memory size comparisons that are made throughout the paper are to classical memory lowerbounds that account only for the bitsize of the array.
+Concretely: in the abstract they say ``...
+we show thre exists a Bloom filter for sets of size~$n$ and error~$\epsilon$ , that is secure against~$t$ queries and uses only $O(n\log\frac{1}{\varepsilon} + t)$ bits of memory.
+In comparison, $n \log\frac{1}{\varepsilon}$ is the best possible under a non-adaptive adversary.''  The latter bound is the classical one.
+If you look in the paper for this actual result, it's in Theorem 6.2.
+So, we look at the theorem and the construction that proves it.
+It uses a specially constructed function~$g$ and a Cuckoo hashing dictionary~$D$, consisting of two tables~$T_1,T_2$ and two hash functions~$h_1,h_2$.
+Here is a quote from the proof ``The final memory of the Bloom filter is the memory of~$D$ and the representation of~$g$.
+The dictionary~$D$ consists of $O(n)$ cells, each of size $|g(x)|=O(\log\frac{1}{\varepsilon})$ bits and therefore~$D$ and~$g$ together can be represented using $O(n\log\frac{1}{\varepsilon} + t)$ bits'', where earlier they say ``the representation of~$g$ requires $O(t)$ bits''.
+Thus they are \emph{not} considering the size of the hash functions~$h_1,h_2$ that are used to populate the cells of~$D$.
+So, as I said, I'm now convinced that their Bloom filter syntax does not actually capture real Bloom filters.}
+
 \paragraph{Obvious Tasks. }

### 2016-05-20 intro.tex
cheers

@@
 (This really irritates me.)  It isn’t clear that their Bloom filter formalization actually captures traditional Bloom filters!
+\tsnote{UPDATE (5/20/16): It is clear, now, that it \emph{does not}.}
 \item The ``adversarial-resilient Bloom Filter'' definition does not give the adversary access to the hash functions that created the representation; effectively, they are secret.
@@
 That said, I'm not convinced the countermeasure is easy to deploy at scale, or that it meshes well with real deployments.
-(See below.)  }
+(See below.)  } \tsnote{Also, while the adversary is given~$S$ (the whitelisted email addresses), the hash functions used to create the Bloom filter are \emph{secret}.
+I'm not convinced this is realistic.}
 
@@
 Concretely: in the abstract they say ``...
-we show thre exists a Bloom filter for sets of size~$n$ and error~$\epsilon$ , that is secure against~$t$ queries and uses only $O(n\log\frac{1}{\varepsilon} + t)$ bits of memory.
+we show there exists a Bloom filter for sets of size~$n$ and error~$\epsilon$, that is secure against~$t$ queries and uses only $O(n\log\frac{1}{\varepsilon} + t)$ bits of memory.
 In comparison, $n \log\frac{1}{\varepsilon}$ is the best possible under a non-adaptive adversary.''  The latter bound is the classical one.

### 2016-05-20 intro.tex
the hash-functions-are-secret idea is not real -- Squid proxy, for example, uses MD5 and you can look at the source code to see exactly how.  No secrets.

@@
 This strikes me as quite odd, and seems to miss the point that finding a false positive should be hard, in practice, even if you know that the hash functions are $h_i(X)=\mathrm{SHA256}(\langle i \rangle \concat X)$.
-(If the hash functions are not kept secret, the whole [NY] security notion kind of unravels; the adversary already is given~$S$, so if it knows the hash functions then you might as well just give it the whole Bloom filter data structure.)
+(If the hash functions are not kept secret, the whole [NY] security notion kind of unravels; the adversary already is given~$S$, so if it knows the hash functions then you might as well just give it the whole Bloom filter data structure.) \tsnote{In the Squid proxy, the hash functions are not secret: you can download the source code, and the docs (available online even!) tell you that ``The protocol design allows for a variable number of hash functions (k).
+However, Squid employs a very efficient method using a fixed number - four.
+Rather than computing a number of independent hash functions over a URL Squid uses a 128-bit MD5 hash of the key (actually a combination of the URL and the HTTP retrieval method) and then splits this into four equal chunks.
+Each chunk, modulo the digest size (m), is used as the value for one of the hash functions - i.e.
+an index into the bit array.
+Note: As Squid retrieves objects and stores them in its cache on disk, it adds them to the in-RAM index using a lookup key which is an MD5 hash - the very one discussed above.
+This means that the values for the Cache Digest hash functions are already available and consequently the operations are extremely efficient!''  (``Key'' here just means hash input, as in ``key-value pair''.)}
 \item Not sure what Bloom filter-like data structures would have randomized querying procedures (``unsteady representations'').

### 2016-05-20 intro.tex
cheers

@@
 However, Squid employs a very efficient method using a fixed number - four.
-Rather than computing a number of independent hash functions over a URL Squid uses a 128-bit MD5 hash of the key (actually a combination of the URL and the HTTP retrieval method) and then splits this into four equal chunks.
+{\bf Rather than computing a number of independent hash functions over a URL Squid uses a 128-bit MD5 hash of the key (actually a combination of the URL and the HTTP retrieval method) and then splits this into four equal chunks.
 Each chunk, modulo the digest size (m), is used as the value for one of the hash functions - i.e.
-an index into the bit array.
-Note: As Squid retrieves objects and stores them in its cache on disk, it adds them to the in-RAM index using a lookup key which is an MD5 hash - the very one discussed above.
+an index into the bit array.}  Note: As Squid retrieves objects and stores them in its cache on disk, it adds them to the in-RAM index using a lookup key which is an MD5 hash - the very one discussed above.
 This means that the values for the Cache Digest hash functions are already available and consequently the operations are extremely efficient!''  (``Key'' here just means hash input, as in ``key-value pair''.)}

### 2016-05-20 intro.tex
cheers

@@
 \item The ``adversarial-resilient Bloom Filter'' definition does not give the adversary access to the hash functions that created the representation; effectively, they are secret.
-This strikes me as quite odd, and seems to miss the point that finding a false positive should be hard, in practice, even if you know that the hash functions are $h_i(X)=\mathrm{SHA256}(\langle i \rangle \concat X)$.
-(If the hash functions are not kept secret, the whole [NY] security notion kind of unravels; the adversary already is given~$S$, so if it knows the hash functions then you might as well just give it the whole Bloom filter data structure.) \tsnote{In the Squid proxy, the hash functions are not secret: you can download the source code, and the docs (available online even!) tell you that ``The protocol design allows for a variable number of hash functions (k).
+This strikes me as quite odd, and seems to miss the point that finding a false positive should be hard, in practice, even if you know that the hash functions are, say,  $h_i(X)=\mathrm{SHA256}(\langle i \rangle \concat X)$.
+(If the hash functions are not kept secret, the whole [NY] security notion kind of unravels; the adversary already is given~$S$, so if it knows the hash functions then you might as well just give it the whole Bloom filter data structure.) \tsnote{In the Squid proxy, the hash functions are not secret: you can download the source code, and the docs~\footnote{http://wiki.squid-cache.org/SquidFaq/CacheDigests} (available online even!) tell you that ``The protocol design allows for a variable number of hash functions (k).
 However, Squid employs a very efficient method using a fixed number - four.

### 2016-05-20 intro.tex
cheers

@@
 \item The ``adversarial-resilient Bloom Filter'' definition does not give the adversary access to the hash functions that created the representation; effectively, they are secret.
-This strikes me as quite odd, and seems to miss the point that finding a false positive should be hard, in practice, even if you know that the hash functions are, say,  $h_i(X)=\mathrm{SHA256}(\langle i \rangle \concat X)$.
-(If the hash functions are not kept secret, the whole [NY] security notion kind of unravels; the adversary already is given~$S$, so if it knows the hash functions then you might as well just give it the whole Bloom filter data structure.) \tsnote{In the Squid proxy, the hash functions are not secret: you can download the source code, and the docs~\footnote{http://wiki.squid-cache.org/SquidFaq/CacheDigests} (available online even!) tell you that ``The protocol design allows for a variable number of hash functions (k).
-However, Squid employs a very efficient method using a fixed number - four.
-{\bf Rather than computing a number of independent hash functions over a URL Squid uses a 128-bit MD5 hash of the key (actually a combination of the URL and the HTTP retrieval method) and then splits this into four equal chunks.
-Each chunk, modulo the digest size (m), is used as the value for one of the hash functions - i.e.
-an index into the bit array.}  Note: As Squid retrieves objects and stores them in its cache on disk, it adds them to the in-RAM index using a lookup key which is an MD5 hash - the very one discussed above.
-This means that the values for the Cache Digest hash functions are already available and consequently the operations are extremely efficient!''  (``Key'' here just means hash input, as in ``key-value pair''.)}
-\item Not sure what Bloom filter-like data structures would have randomized querying procedures (``unsteady representations'').
+(No matter if the [NY] syntax does or does not allow them to be encoded in the representation.)  This is odd and does not match reality, e.g.
+the popular Squid proxy uses plain MD5, splits the output into four chunks, and defines these as four hash functions.
+Hardly secret.
+\item The ``unsteady representation'' does not seem well founded.
+Not sure what Bloom filter-like data structures would have randomized querying procedures.
 They mention the possibility of differential privacy mechanisms being incorporated into the querying procedure.
@@
 
+Finally, the security definitions do not give the adversary access to the hash functions that created the representation; effectively, they are secret.
+This strikes me as quite odd, and seems to miss the point that finding a false positive should be hard, in practice, even if you know that the hash functions are, say,  $h_i(X)=\mathrm{SHA256}(\langle i \rangle \concat X)$.
+(If the hash functions are not kept secret, the whole [NY] security notion kind of unravels; the adversary already is given~$S$, so if it knows the hash functions then you might as well just give it the whole Bloom filter data structure.) \tsnote{In the Squid proxy, the hash functions are not secret: you can download the source code, and the docs~\footnote{http://wiki.squid-cache.org/SquidFaq/CacheDigests} (available online even!) tell you that ``The protocol design allows for a variable number of hash functions (k).
+However, Squid employs a very efficient method using a fixed number - four.
+{\bf Rather than computing a number of independent hash functions over a URL Squid uses a 128-bit MD5 hash of the key (actually a combination of the URL and the HTTP retrieval method) and then splits this into four equal chunks.
+Each chunk, modulo the digest size (m), is used as the value for one of the hash functions - i.e.
+an index into the bit array.}  Note: As Squid retrieves objects and stores them in its cache on disk, it adds them to the in-RAM index using a lookup key which is an MD5 hash - the very one discussed above.
+This means that the values for the Cache Digest hash functions are already available and consequently the operations are extremely efficient!''  (``Key'' here just means hash input, as in ``key-value pair''.)}
+
 \paragraph{Obvious Tasks. }

### 2016-05-23 intro.tex
adding note about Bloom filters with secret keys, in practice

@@
 Hardly secret.
+\tsnote{I did find a setting where Bloom filters use secret keys: privacy-preserving record linkage.
+Here one wants to know if two databases contain information about the same person (abstractly, a set of record identifiers).
+Suggested hash functions are $H_j(x) = g(x) + j\cdot h(x) \bmod m$ for $j=\{0,1,\ldots,k-1\}$, and $g,h$ are (e.g.) HMAC-SHA1 with different keys.
+In practice, apparently the~$x$ are bigrams extracted from string identifiers (e.g.
+``Thomas''); papers show how to break this ``encrypted'' Bloom filter by recovering a large fraction of names, via (roughly) frequency analysis.}
 \item The ``unsteady representation'' does not seem well founded.

### 2016-05-23 intro.tex
cheers

@@
 \item Establish security notions that are appropriate for broader use cases (e.g.
-privacy of~$S$, privacy of the representation~$M$, authenticity of representation~$M$), potentially distinguishing between “external” and “internal” attacks for, say, CDN scenarios
+privacy of~$S$, privacy of the representation~$M$, authenticity of representation~$M$), single Bloom filter vs.\ multiple Bloom filter settings (e.g.
+attacking a CDN by querying multiple servers)
 \item Develop constructions that are secure and are supported by a practice-informed argument for deployment

### 2016-05-23 intro.tex
updating tasks list

@@
 \item Get a solid handle on how Bloom filters are used in practice, and what generalizations have gained traction in the academic literature.
-(See wikipedia, a section of which I've pasted in at the end of this doc.)
+(See wikipedia, a section of which I've pasted in at the end of this doc.) \tsnote{5/23: lots of uses to consider --CDNs/load balancers, peer-to-peer networks, medical record linkage, model checking, etc.
+Might be good to try to characterize by, say, setting (distributed vs.
+local), typical BF instance size (e.g.
+local whitelist of emails = ``small'', CDN server-cache summary = ``large''), security concerns, and estimated severity of security violation (e.g.
+FP at CDN server = ``low'' or ``medium'', deanonymizing medical record = ``high'').
+Just throwing out ideas...}
 \item Work out a proper “cryptographic” syntax for the Bloom filter primitive.  (Possibly something more general, see number 5.)
@@
 \item Develop constructions that are secure and are supported by a practice-informed argument for deployment
+\item Break some stuff :-)
 \item Expand from Bloom filters to “Approximate Set Membership” primitives, i.e.

### 2016-05-23 intro.tex
cheers

@@
 A false positive causes the server to search its local store, which is slow, only to find nothing.
+\tsnote{Question: in their security notions, the adversary wins by returning an $x^*$ that is not in~$S$ and is not one of the queries it asked to $B_2$; why the latter?
+I understand why you shouldn't get credit for output something in~$S$ when~$S$ is given to you, but what if one of the queries to~$B_2$ is not in~$S$ and is a FP?
+Shouldn't the adversary already win?}
 
@@
 Thus, I need to know the secret keys of my neighbors in order to operate in the way just described.
-This seems troublesome in practice, at scale.
-Thus, their solution to a (potentially) real problem seems to be a non-solution.
+This seems troublesome in practice, at CDN-sized scale.
+(Also in P2P networks, where peers are joining/leaving frequently.)  Thus, their solution to a (potentially) real problem seems to be a non-solution.
 

### 2016-05-23 intro.tex
cheers

@@
 \item The NY paper formalizes and investigates a security notion of limited interest
-\item The proposed construction won't scale in common network applications
-\item The main results are of theoretical interest only
+\item The proposed construction won't scale in common network applications (e.g. large CDN, P2P networks)
+\item The main (im)possibility results are of theoretical interest only
 \item The basic syntax and operation of their Bloom filter formalization is underdefined.
 (This really irritates me.)  It isn’t clear that their Bloom filter formalization actually captures traditional Bloom filters!
-\tsnote{UPDATE (5/20/16): It is clear, now, that it \emph{does not}.}
+\tsnote{UPDATE (5/20/16): It is clear, now, that it \emph{does not}.} \tsnote{Also, why isn't the size of the representation somehow a part of the syntax or correctness/soundness conditions?
+The fact that the representation is supposed to be small doesn't appear in the syntax anywhere.}
 \item The ``adversarial-resilient Bloom Filter'' definition does not give the adversary access to the hash functions that created the representation; effectively, they are secret.
@@
 
-\paragraph{Critique. }
+\paragraph{Discussion. }
 The traditional definition of Bloom filter soundness is information theoretic.

### 2016-05-23 intro.tex
cheers

@@
 \tsnote{I did find a setting where Bloom filters use secret keys: privacy-preserving record linkage.
-Here one wants to know if two databases contain information about the same person (abstractly, a set of record identifiers).
+Here one wants to know if two databases contain information about the same person (abstractly, a set of record identifiers); you create a Bloom filter for each record, one for each unique identifier in some cases.
 Suggested hash functions are $H_j(x) = g(x) + j\cdot h(x) \bmod m$ for $j=\{0,1,\ldots,k-1\}$, and $g,h$ are (e.g.) HMAC-SHA1 with different keys.

### 2016-05-23 intro.tex
cheers

@@
 \tsnote{UPDATE (5/20/16): It is clear, now, that it \emph{does not}.} \tsnote{Also, why isn't the size of the representation somehow a part of the syntax or correctness/soundness conditions?
-The fact that the representation is supposed to be small doesn't appear in the syntax anywhere.}
+The fact that the representation is supposed to be small doesn't appear in the syntax anywhere so, syntactically, $B_1(S)=S$ and $B_2(S,x)=1 \Leftrightarrow x \in S$ works just fine, and is trivially secure by their definition!}
 \item The ``adversarial-resilient Bloom Filter'' definition does not give the adversary access to the hash functions that created the representation; effectively, they are secret.

### 2016-05-23 intro.tex
cheers

@@
 The dictionary~$D$ consists of $O(n)$ cells, each of size $|g(x)|=O(\log\frac{1}{\varepsilon})$ bits and therefore~$D$ and~$g$ together can be represented using $O(n\log\frac{1}{\varepsilon} + t)$ bits'', where earlier they say ``the representation of~$g$ requires $O(t)$ bits''.
-Thus they are \emph{not} considering the size of the hash functions~$h_1,h_2$ that are used to populate the cells of~$D$.
+(Note that this~$g$ is only used to determined \emph{what} is stored at the indicated array/table positions, not \emph{where}.)  Thus they are not considering the size of the hash functions~$h_1,h_2$ that are used to indicated which cells of~$D$ need to be altered.
 So, as I said, I'm now convinced that their Bloom filter syntax does not actually capture real Bloom filters.}
@@
 Finally, the security definitions do not give the adversary access to the hash functions that created the representation; effectively, they are secret.
-This strikes me as quite odd, and seems to miss the point that finding a false positive should be hard, in practice, even if you know that the hash functions are, say,  $h_i(X)=\mathrm{SHA256}(\langle i \rangle \concat X)$.
+\tsnote{Unless they are assuming that the hash functions are fixed, part of the algorithms $B_1$ and $B_2$?
+In which case, $A$~knows them too; and the security notion gives~$S$ to~$A$, so...}  This strikes me as quite odd, and seems to miss the point that finding a false positive should be hard, in practice, even if you know that the hash functions are, say,  $h_i(X)=\mathrm{SHA256}(\langle i \rangle \concat X)$.
 (If the hash functions are not kept secret, the whole [NY] security notion kind of unravels; the adversary already is given~$S$, so if it knows the hash functions then you might as well just give it the whole Bloom filter data structure.) \tsnote{In the Squid proxy, the hash functions are not secret: you can download the source code, and the docs~\footnote{http://wiki.squid-cache.org/SquidFaq/CacheDigests} (available online even!) tell you that ``The protocol design allows for a variable number of hash functions (k).

### 2016-05-23 intro.tex
a contradiction to their main theoretical result on the equiv. between secure BFs and one-way functions?

@@
 \tsnote{UPDATE (5/20/16): It is clear, now, that it \emph{does not}.} \tsnote{Also, why isn't the size of the representation somehow a part of the syntax or correctness/soundness conditions?
-The fact that the representation is supposed to be small doesn't appear in the syntax anywhere so, syntactically, $B_1(S)=S$ and $B_2(S,x)=1 \Leftrightarrow x \in S$ works just fine, and is trivially secure by their definition!}
+The fact that the representation is supposed to be small doesn't appear in the syntax anywhere so, syntactically, $B_1(S)=S$ and $B_2(S,x)=1 \Leftrightarrow x \in S$ works just fine, and is trivially secure by their definition!
+In fact, I think this contradicts their main claim that secure ``Bloom filters'' exist iff one-way functions exist :-)}
 \item The ``adversarial-resilient Bloom Filter'' definition does not give the adversary access to the hash functions that created the representation; effectively, they are secret.

### 2016-05-24 critique/intro.tex
creating critique directory, to separate the critique document from the actual paper

--- 2016-05-23 intro.tex
@@
 The fact that the representation is supposed to be small doesn't appear in the syntax anywhere so, syntactically, $B_1(S)=S$ and $B_2(S,x)=1 \Leftrightarrow x \in S$ works just fine, and is trivially secure by their definition!
-In fact, I think this contradicts their main claim that secure ``Bloom filters'' exist iff one-way functions exist :-)}
+}
 \item The ``adversarial-resilient Bloom Filter'' definition does not give the adversary access to the hash functions that created the representation; effectively, they are secret.
@@
 \item Break some stuff :-)
-\item Expand from Bloom filters to “Approximate Set Membership” primitives, i.e.
-more general compressed representations (of sets) that admit queries  Note: this should be done only if it makes sense -- i.e.
+\item Starting with a secure ``basic'' Bloom filter, develop results for more complicated Bloom filter constructions (e.g. hierarchical Bloom filters, attenuated BFs), and Bloom-filter-based protocols
+\item Expand from Bloom filters to  approximate-set-membership primitives, i.e.
+more general compressed representations (of sets) that admit queries  Note: this should be done only if it makes sense~---i.e.
 it doesn't explode the scope, it doesn't send us off too far into theoryland.
 \item Expand more generally to hash-based approximate set operations, e.g.\ minhash methods for approximating $J(A,B)$ for sets $A,B$.
-Note: this should be done only if it makes sense -- i.e.
+Note: this should be done only if it makes sense~---i.e.
 it doesn't explode the scope, it doesn't send us off too far into theoryland.

### 2016-05-24 intro.tex
I guess it is not a counterxample after all
beginning to craft a proper intro to the paper

@@
 \section{Introduction}
+We revisit the formalization of Bloom filters~\cite{xxx} and closely related data structures as primitives with explicit security goals.
+Recently, Naor and Yogev~\cite{xxx} (hereafter NY) gave such a formalization, providing syntax for a generalized abstraction of Bloom filters, as well as casting the classical Bloom filter soundness condition as a security experiment admiting adaptive adversaries.
+To briefly summarize, a Bloom filter is a data structure for compactly representing a set~$\mathcal{S}$ in a way that supports constant time responses to set-membership queries.
+The representation of~$\mathcal{S}$ is an indexed array~$M$ of~$m$-bits, all initally set to 0.
+To insert $x \in \mathcal{S}$ into~$M$, one computes indices $h_1(x),h_2(x),\ldots,h_k(x)$ where each $h_i \colon \mathcal{U} \to \{0,1,\ldots m-1\}$ maps from a universe~$\mathcal{U}$ (which contains $\mathcal{S}$) to indices of~$M$.
+The bits at positions $h_1(x),h_2(x),\ldots,h_k(x)$ are set to 1; if a bit is already 1, due to inserting some previous element of~$\mathcal{S}$, then it is left alone.
+After all elements of~$\mathcal{S}$ have been inserted, the resulting bit-array~$M$ is taken as the representation.
+To test if $y \in \mathcal{S}$, one checks if  $(h_1(y)=1 \wedge h_2(y)=1 \wedge \cdots \wedge h_k(y)=1)$, returning ``yes'' if so, and ``no'' otherwise.
+Bloom filters are correct, in the sense that if $y \in \mathcal{S}$, the set-membership test always returns ``yes''.
+The classical soundness condition asserts that for all $y \notin\mathcal{S}$,  $\Prob{h_1,h_2,\ldots,h_k \getsr \mathrm{Func(\mathcal{U},\mathbb{Z}_m)}\colon h_1(y)=1 \wedge h_2(y)=1 \wedge \cdots \wedge h_k(y)=1} \leq \epsilon$ where $\epsilon$, the false-positive rate, is a parameter of the Bloom filter.
+(The values of~$\epsilon,m,k,|\mathcal{S}|$ are related in a well known way.)  NY recast this soundness condition as a game in which an adversary~$A$ is given~$\mathcal{S}$ and an oracle for set-membership queries, and it attempts to find a false-positive.
+The fact that~$A$ can \emph{adapt} its queries and its output based on what it learns from the set-membership oracle is the key definitional constribution of NY.
+
+\if{0}
 \paragraph{Basic issues in Naor-Yogev. }
@@
 The Exim mail transfer agent (MTA) uses bloom filters in its rate-limit feature.[18]
+
+\fi

### 2016-05-24 intro.tex
hacking together an intro

@@
 The fact that~$A$ can \emph{adapt} its queries and its output based on what it learns from the set-membership oracle is the key definitional constribution of NY.
+
+Bloom filters have a broad range of practical applications, for example, in content-distribution networks, large database query processing, routing algorithms for peer-to-peer networks, protocols for establishing linkages between medical-record databases, fair routing of TCP packets, Bitcoin wallet synchonization.
+\tsnote{need citations}  Given that NY is addressing such a useful real-world object, we find their formalism, both the syntax and security notions, to be less precise and useful than one would want.
+Let us explain.
+
+ Syntactically, NY says a Bloom filter (with a steady representation) is a pair of algorithms $\mathbf{B}=(\mathbf{B}_1, \mathbf{B}_2)$.
+The setup algorithm~$\mathbf{B}_1$ is randomized, and on input a set~$\mathcal{S}$ it returns a representation~$M$ (from some undefined, implicit set of representations).
+The query algorithm~$\mathcal{B}_2$ is determinisic, and on input a representation~$M$ and an element~$x \in \mathcal{U}$, it returns a bit.
+For correctness they make the classical demand, that for all $x \in \mathcal{S}$ we have $\Prob{\mathbf{B}_2(\mathbf{B}_1(S),x)=1}=1$.
+For soundness, adversary~$A$ plays the following game, ``Adversarial-resilient Bloom Filter with a steady representation''.
+First, $M \getsr \mathbf{B}_1(\mathcal{S})$.
+Then the adversary is given the set~$\mathcal{S}$ and may make queries $x_1,x_2,\ldots,x_q$ to an oracle for $\mathbf{B}_2(M,\cdot)$.
+At the end of its execution, the adversary outputs~$x^*$ and wins the game if (1) $x^* \not\in \mathcal{S} \cup \{x_1,x_2,\ldots,x_q\}$, and (2) $\mathbf{B}_2(M,x^*)=1$.
+
+First, we note that the security notion forbids~$A$ to win if it outputs $x^* \in \{x_1,x_2,\ldots,x_q\}$, even if one of these was a false-positive.  
+%
+Second, we note that the NY syntax does not capture the size of~$M$ as a parameter; the surrounding text does say that $\mathbf{B}_1$ ``outputs a compressed representation [of $\mathcal{S}$] $\mathbf{B}_1(\mathcal{S})=M$'' but what exactly this means is never addressed.
+The formal syntax admits $\mathbf{B}_1(\mathcal{S})=\mathcal{S}$ and $\mathbf{B}_2(\mathcal{S},x)=1 \Leftrightarrow x \in \mathcal{S}$, which is also trivially secure by their definition.
+These are both small, but important complaints.
+But a larger complaint, and one that is much harder to see, is that that it is not clear that the NY formalism actually captures real world Bloom filters.
+
+In particular, say that $\mathbf{B}_1$ is implementing a classic Bloom filter.
+Then the hash functions $h_1,h_2,\ldots,h_k$ are either sampled from some implicit family~$\mathcal{H}$ by~$\mathbf{B}_1$ (recall that this algorithm is randomized), or they are hard-coded into the description of~$B_1$.
+Let's assume the former, for the moment.
+In order for~$B_2$ to be able to respond to set-membership queries, it must have $h_1,h_2,\ldots,h_k$ as well.
+Since~$B_2$ receives only the representation~$M$ as input, it must be the case that $h_1,h_2,\ldots,h_k$ are encoded into~$M$ somehow.
+But the text strongly suggests, in several places, that~$M$ does \emph{not} include these.
+Both NY and classical analysis of Bloom filters speak of the number of bits used to represent the set~$\mathcal{S}$: the classical analysis means only the number of bits in the actual array, and NY make comparisons throughout between the number of bits~$m$ used by their instantiations and the classical bounds.
+Morevover, the Bloom filter they construct in one of their main positive results clearly \emph{does not} count as part of the representation size the hash functions used to indicate array locations.
+Thus, if we assume that $\mathbf{B}_1$ is sampling $h_1,h_2,\ldots,h_k$, it seems that their formalization fails to capture the basic Bloom filter construction; at best, it is hard to see clearly that it does.
+
+On the other hand, we can assume that the hash functions are implicitly hard-coded into~$\mathbf{B}_1$ (and $\mathbf{B}_2$).
+Then we can treat~$\mathbf{B}_1$ as deterministic, since it will simply carry out the steps required to populate an array using these hash functions, and output the array~$M$ as the representation.
+If we apply Kirchoff's rule, the descriptions of~$\mathbf{B}_1,\mathbf{B}_2$ are known to the adversary, who is also provided with~$\mathcal{S}$.
+In this case, the adversary can compute~$M$ itself, as well as test for false-positives itself.
+So it isn't clear how the security notion helps to reason about difficulty of finding a false-positive.
+Moreover, NY stresses (at least once) that the representation is \emph{not} given to the adversary in their notions.
+So it seems unlikely that they intended for $h_1,h_2,\ldots,h_k$ to be hard-coded into the algorithms.
 

### 2016-05-24 intro.tex
intro hacking still

@@
 So it seems unlikely that they intended for $h_1,h_2,\ldots,h_k$ to be hard-coded into the algorithms.
+
+Continuing on this point, it seems that the coins of~$\mathbf{B}_1$, whatever their use, are intended to be kept secret from the adversary.
+Thus, to the extent that it addresses real Bloom filters at all, it only addresses applications in which the representation is created using secret coins.
+But many real-world applications of Bloom filters have no secrets.
+NY point to web proxies, which use Bloom filters to compactly represent the objects they store locally, as motivation for their work.
+But real web proxies like Squid~\cite{xxx} do \emph{not} use secrets in their Bloom filters.
+They use the basic Bloom filter with four hash functions, used to populate the array and respond to queries, defined as follows: $h_1(x) = \mathrm{MD5}(x)[0,\ldots,31]$, $h_2(x)=\mathrm{MD5}(x)[32,\ldots,63]$, $h_3(x)=\mathrm{MD5}(x)[64,\ldots,95]$, and $h_4(x)=\mathrm{MD5}(x)[96,\ldots,127]$.
+Likewise, there are no secrets in the Bloom filters used by Google's BigTable~\cite{xxx}, HBase~\cite{xxx}, \tsnote{make an impressive list.}  There are applications in which the proposed Bloom filter instantiations do use secretly keyed hash functions, e.g.
+$H_j(x) = (f(K_0,x) + j\cdot g(K_1,x))\bmod m$, where $j\in[1,k]$, $m$ is the number of bits in the array, and where $f,g$ are PRFs keyed by secrets $K_0,K_1$.
+This particular ``encrypted Bloom filter'' instantiation was suggested for use in efficient linking of records across separate medical record databases~\cite{xxx}.
+(It was subsequently shown not to be secure by Niedermeier et al.~\cite{xxx}, where a clever use of frequency analysis recovered the last names of patients given access only to the Bloom filter array.)  In any case, it is clear that the NY definition does not capture the most widely used applications of Bloom filters, e.g.
+CDN summary caches, P2P network routing algorithms, etc.
+
+\tsnote{Could also point out that their positive results use constructions that have secret keys, and these are unlikely to be of any use in major applications like CDNs or P2P networks.
+But maybe the horse is sufficiently beaten by now...}
+
+\heading{Our contributions. }
+Given these shortcomings and the prevalent use of Bloom filters in practice, we revisit the matter of formalizing them as primitives with explicit security goals, these goals being abstracted from the attack surface they expose in practice.
+We begin by giving a new syntax for an approximate-set-membership primitive (ASM) that clearly captures Bloom filters...
+\tsnote{finish}
+
+We provided various security notions for ASMs...
+FP with private, public representation coins; set privacy with private, public representation coins; FP/set privacy in the multi-representation setting (outsider attack, think CDNs); FP/set privacy in the multi-representation setting with corruptions (insider attack, think P2P networks) \tsnote{Those are just the ones that come to mind now.
+Could also consider authenicity of representations, think CDN or P2P settings.}
+
+Later, we give syntax for ASM primitives that also admit operations upon the set representation.
+This captures so-called counting Bloom filters that are used, for example, in fairness-enforcing algorithms for routing of TCP streams.
+It also captures...
+\tsnote{finish}
+
+We show that... \tsnote{finish}
 

### 2016-05-24 intro.tex
intro hacking still

@@
 In particular, say that $\mathbf{B}_1$ is implementing a classic Bloom filter.
-Then the hash functions $h_1,h_2,\ldots,h_k$ are either sampled from some implicit family~$\mathcal{H}$ by~$\mathbf{B}_1$ (recall that this algorithm is randomized), or they are hard-coded into the description of~$B_1$.
+Then the hash functions $h_1,h_2,\ldots,h_k$ are either sampled from some implicit family~$\mathcal{H}$ by~$\mathbf{B}_1$ (recall that this algorithm is randomized), or they are hard-coded into the description of~$\mathbf{B}_1$.
 Let's assume the former, for the moment.
-In order for~$B_2$ to be able to respond to set-membership queries, it must have $h_1,h_2,\ldots,h_k$ as well.
+In order for~$\mathbf{B}_2$ to be able to respond to set-membership queries, it must have $h_1,h_2,\ldots,h_k$ as well.
 Since~$B_2$ receives only the representation~$M$ as input, it must be the case that $h_1,h_2,\ldots,h_k$ are encoded into~$M$ somehow.
@@
 It also captures...
-\tsnote{finish}
 
-We show that... \tsnote{finish}
+We show that...
+
+\heading{Related work. }
+
+\tsnote{Stopped here.}
 

### 2016-05-24 intro.tex
intro hacking still

@@
 In order for~$\mathbf{B}_2$ to be able to respond to set-membership queries, it must have $h_1,h_2,\ldots,h_k$ as well.
-Since~$B_2$ receives only the representation~$M$ as input, it must be the case that $h_1,h_2,\ldots,h_k$ are encoded into~$M$ somehow.
+Since~$\mathbf{B}_2$ receives only the representation~$M$ as input, it must be the case that $h_1,h_2,\ldots,h_k$ are encoded into~$M$ somehow.
 But the text strongly suggests, in several places, that~$M$ does \emph{not} include these.
@@
 
-Continuing on this point, it seems that the coins of~$\mathbf{B}_1$, whatever their use, are intended to be kept secret from the adversary.
+Continuing on this point, it seems that the coins of~$\mathbf{B}_1$ (whatever their use) are intended to be kept secret from the adversary.
 Thus, to the extent that it addresses real Bloom filters at all, it only addresses applications in which the representation is created using secret coins.

### 2016-05-24 intro.tex
intro hacking still

@@
 Continuing on this point, it seems that the coins of~$\mathbf{B}_1$ (whatever their use) are intended to be kept secret from the adversary.
-Thus, to the extent that it addresses real Bloom filters at all, it only addresses applications in which the representation is created using secret coins.
+Thus, to the extent that it addresses real Bloom filters at all, the NY security notion only addresses applications in which the representation is created using secret coins.
 But many real-world applications of Bloom filters have no secrets.

### 2016-05-24 intro.tex
intro hacking still

@@
 But real web proxies like Squid~\cite{xxx} do \emph{not} use secrets in their Bloom filters.
-They use the basic Bloom filter with four hash functions, used to populate the array and respond to queries, defined as follows: $h_1(x) = \mathrm{MD5}(x)[0,\ldots,31]$, $h_2(x)=\mathrm{MD5}(x)[32,\ldots,63]$, $h_3(x)=\mathrm{MD5}(x)[64,\ldots,95]$, and $h_4(x)=\mathrm{MD5}(x)[96,\ldots,127]$.
+They use the basic Bloom filter with four hash functions, defined as follows: $h_1(x) = \mathrm{MD5}(x)[0,\ldots,31]$, $h_2(x)=\mathrm{MD5}(x)[32,\ldots,63]$, $h_3(x)=\mathrm{MD5}(x)[64,\ldots,95]$, and $h_4(x)=\mathrm{MD5}(x)[96,\ldots,127]$.
 Likewise, there are no secrets in the Bloom filters used by Google's BigTable~\cite{xxx}, HBase~\cite{xxx}, \tsnote{make an impressive list.}  There are applications in which the proposed Bloom filter instantiations do use secretly keyed hash functions, e.g.

### 2016-05-24 intro.tex
intro hacking still

@@
 Likewise, there are no secrets in the Bloom filters used by Google's BigTable~\cite{xxx}, HBase~\cite{xxx}, \tsnote{make an impressive list.}  There are applications in which the proposed Bloom filter instantiations do use secretly keyed hash functions, e.g.
-$H_j(x) = (f(K_0,x) + j\cdot g(K_1,x))\bmod m$, where $j\in[1,k]$, $m$ is the number of bits in the array, and where $f,g$ are PRFs keyed by secrets $K_0,K_1$.
+$h_j(x) = (f(K_0,x) + j\cdot g(K_1,x))\bmod m$, where $j\in[1,k]$, $m$ is the number of bits in the array, and where $f,g$ are PRFs keyed by secrets $K_0,K_1$.
 This particular ``encrypted Bloom filter'' instantiation was suggested for use in efficient linking of records across separate medical record databases~\cite{xxx}.

### 2016-05-25 syntax.tex
syntax work

--- 2016-05-17 syntax.tex
@@
 \section{Syntax}
+\tsnote{Very much a work-in-progress.}
 As a first step, let us try to better formalize Bloom filters as a primitive.
 
-\paragraph{Basic Bloom filter syntax.}
-Fix integers $m,k > 0$ and a nonempty set $U$.  Fix a symbol $\bot \not\in U$.  A “Bloom filter” is a triple  $B=(H,\mathsc{Rep},\mathsc{Qry})$.
+\heading{Hash-based (Bloom) filter syntax.}
+Fix a nonempty sets $U,\Sigma$ and integers $k,m,n>0$.  Fix a symbol $\bot \not\in U$.  An $(n,k,m)$-filter (over universe~$U$) is a triple  $B=(\mathsc{H},\mathsc{Rep},\mathsc{Qry})$.   
+%
+The randomized \emph{hash-sampling} algorithm~$\mathsc{H}$ samples a size~$k$ subset~$\mathcal{H} \subset \mathrm{Func}(U,\{0,1,\ldots,m-1\})$.
+We write $\mathcal{H} \getsr \mathsc{H}$ for this operation.
+%
+The deterministic representation algorithm $\mathsc{Rep}: [U]^n \rightarrow \Sigma^m$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m$.
+(Recall that $[U]^n$ denotes subsets of~$U$ of size~$n$.)
+%
+The determinisitc query algorithm $\mathsc{Qry}: \Sigma^m \times U \rightarrow \bits$ takes a representation $M$ and an element $x \in U$ and returns a bit.  
+%
+We assume that both $\mathsc{Rep}$ and $\mathsc{Qry}$ have the following blackbox access to the functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$, which we denote by writing~$\mathcal{H}$ as a superscript.
+Thus, we write $M \gets \mathsc{Rep}^{\mathcal{H}}(S)$ and $b \gets \mathsc{Qry}^{\mathcal{H}}(M,x)$ for the execution of the representation and query algorithms, respectively.
 
-The hash family $H = \{h_i : U \rightarrow [m]  | i in [k]\}$ is  set of~$k$ hash functions.
+For correctness, we demand that for all $\mathcal{H}$ and $S$, and for all $x \in S, \mathsc{Qry}^{\mathcal{H}}(\mathsc{Rep}^{\mathcal{H}}(S),x)=1$.
 
-The representation mapping $\mathsc{Rep}: 2^U \rightarrow \bits^m$ takes a set $S \subseteq U$ as input, and outputs an $m$-bit representation~$M$ of $S$.
-The query mapping $\mathsc{Qry}: \bits^m \times U \rightarrow \bits$ takes a representation $M$ and an element $x \in U$ and returns a bit.
-We assume that both $\mathsc{Rep}$ and $\mathsc{Qry}$ may make (black-box) calls to the functions in~$H$.
-Both $\mathsc{Rep}$ and $\mathsc{Qry}$ are deterministic.
+\heading{Discusssion.}
+This syntax captures classical Bloom filters by setting~$\Sigma=\bits$ and defining $\mathsc{Rep},\mathsc{Qry}$ in the obvious way.
+Setting $\Sigma=\bits^{\leq L}$ allows one to store a bitstring of length at most~$L$ at each location.
+\tsnote{Would let us capture a construction from NY, among other things.}
 
-Note that this is already a slight generalization of a true Bloom filter, because the syntax does not proscribe how Rep and Qry operate.
-
-\jknote{Why not simply include the description of the hash function(s) as part of the size of the representation?
-I.e., Have $B_1$, $B_2$ exactly as in the paper, but explicitly count the bits needed to represent the hash functions as part of the representation output by $B_1$.}
-\tsnote{See my comments above.}
-\jknote{There could be some advantages to your formulation, though, if you imagine choosing the hash functions “once and for all” and then running Rep on many different sets$ S_1, S_2, \ldots$ in that case we would care about the amortized size of the representation, and so not count the bits needed to describe the hash functions.}
-
-For proper operation, we demand that for all $S$, and for all $x \in S, \mathsc{Qry}(\mathsc{Rep}(S),x)=1$.
-Observe that this is only a correctness condition.
-Soundness will be cast as a security experiment, following [NY].
-
-\paragraph{Bloom filters with operations. }
+\heading{Hash-based filters with operations. }
 Here we extend the basic Bloom filter syntax to allow for variations on the traditional Bloom filter, e.g.
 counting Bloom filters.
-[We should find out what are the important variations!
+\tsnote{We should find out what are the important variations!
 I only know of a few.
-None of these require randomness, so I'll continue to formalize everything as deterministic.][“Scaling Bloom filters”, appear to allow the parameter m, below, to vary.][This syntax might naturally support count-min sketches, too.]
+None of these require randomness, so I'll continue to formalize everything as deterministic.}\tsnote{“Scaling Bloom filters”, appear to allow the parameter~$m$, below, to vary.
+Syntax doesn't address this.}\tsnote{This syntax might naturally support count-min sketches, too.}
 
-\jknote{You probably want to even be more general and talk about “data structures” more abstractly.}
-\tsnote{Sure, but I'd rather take it a step at a time.
-First, restrict to this class of Bloom filters with operations, and see what can be said that is interesting and practically relevant.
-(There may already be quite a bit.)  Only once that picture starts to emerge would I want to expand to a more general class of primitives.
-Expanding the class to “data structures” likely brings other related work into scope.  Haven't Goodrich and various coauthors worked on data structures with security?}
+Let $\mathbb{M}_\mathcal{U}$ be the set of multisets over~$\mathcal{U}$.
+We can denote any multiset as $\{(x,\ell) \,|\, x \in \mathcal{U}, \ell \in \mathbb{N}\}$, and for a particular multiset~$S$ we define the multiplicity of~$x$ as $\mu_S(x) = \ell$ where $(x,\ell)\in S$.
 
-Fix integers $m,k > 0$, and nonempty sets $U$ (the universe) and $A$ (the output alphabet).  Fix a symbol $\bot \not\in U$.
-
-A “Bloom filter with operations” is a four-tuple  $B=(H,\mathsc{Rep},\mathsc{Qry}, \mathsc{Ops})$.
-
-As before, the hash family $H = \{h_i : U \rightarrow [m]  | i in [k] \}$ is  set of~$k$ hash functions.
-
-The set $\mathsc{Ops}$ is the finite collection of allowable operations.  All operations are of the form 
-$f: U^* \times U^* \rightarrow U^* \cup \{\bot\}$.
-That is, an operation takes tuples~$S$ and~$T$ as input, and returns either tuple~$S'$ or the distinguished symbol $\bot$.
-(Examples: $f_{\mathrm{add}}((a,b,c,c),(c,d,d)) = (a,b,c,c,c,d,d); f_{\mathrm{del}}((a,b,c),(c))=(a,b); f_{\mathrm{del}}((a,b,c),(c,d)) = \bot$.
-Could allow more advanced things like $f_{\mathrm{setify}}((a,b,c,c),(c,d,a)) = (a,b,c,d))$ to support what already exists in the literature and (more importantly) in practice.)  We assume that if an operation~$f$ is called outside of its domain, it returns $\bot$.
-
-The representation mapping $P: U^* \rightarrow A^m \cup \{\bot\}$.
-It takes a tuple~$S$, and returns an $m$-vector~$M$ of elements from the alphabet~$A$, or the distinguished symbol~$\bot$.
-We call the (non-$\bot$) output of $P(S)$ the representation $S$.
-
-The query mapping $Q: A^m \times U \rightarrow \{0,1\}$ takes a representation $M$ and an element $x \in U$ and returns a bit.
-We assume that both~$P$ and~$Q$ may make (black-box) calls to the functions in~$H$.
+An $(k,m)$-filter with operations is a tuple  $B=(\mathsc{H},\mathsc{Rep},\mathsc{Qry}, \mathcal{F})$.  
+The set $\mathcal{F}$ is the finite collection of allowable operations.  All operations are of the form 
+$f: \mathbb{M}_{\mathcal{U}} \times \mathbb{M}_{\mathcal{U}} \rightarrow \mathbb{M}_{\mathcal{U}} \cup \{\bot\}$.  
+%
+The deterministic representation algorithm $\mathsc{Rep}: \mathbb{M}_\mathcal{U} \rightarrow \Sigma^m$ takes a multiset~$S$, and outputs representation~$M$ of length~$m$.
+The randomized hash-sampling algorithm and deterministic query algorithm is defined as before.
 
 Correctness is defined as follows.
-Let $S,T$ be arbitrary elements of $U^*$, and let~$f$ be an arbitrary operation in $\mathsc{Ops}$.
-If $f(S,T) = S'$ is in $U^*$ (i.e.
-is not $\bot$), then for all $x \in S'$ we demand that $\mathsc{Qry}(\mathsc{Rep}(S'),x)=1$.
-[Note: might need a stronger condition that this holds for any sequence of operations that do not result in $\bot$.]
+Let $S,T$ be arbitrary multisets and let~$f$ be an arbitrary operation in $\mathcal{F}$.
+If $f(S,T) = S'\neq \bot$, then for all $x \in S'$ we demand that $\mathsc{Qry}(\mathsc{Rep}(S'),x)=1$.
+\tsnote{might need a stronger condition that this holds for any sequence of operations that do not result in $\bot$.}
 
-\paragraph{Further Syntactic Generalizations. }
+Let us see how this syntax captures various kinds of Bloom filters.
+First, let $\Sigma = \mathbb{N}$ and define $f_{\mathrm{add}}(S,T)=\{(x,\mu_S(x)+\mu_T(x)) \,|\, x \in \mathcal{U}\}$ and $f_\mathrm{del}(S,T) = \{(x,\min\{0,\mu_S(x)-\mu_T(x)\}) \,|\, x \in \mathcal{U} \}$.
+Define $\mathsc{Rep}(S')$ as follows: for each $(x,\ell)\in S'$ and $j\in\{1,2,\ldots,k\}$, set $M[h_j(x)]=\ell$.
+Finally, define $\mathsc{Qry}(M,x) = 1 \Leftrightarrow \forall j \in \{1,2,\ldots,k\},\; M[h_j(x)] > 0$.
+This allows us to capture counting Bloom filters.
 
-Allow $\mathsc{Ops}, P, Q$ to be randomized?
-Replace hash function family with something more general?
-Note that we shouldn't just generalize for the sake of it.
-Let's try to stay motivated by reality...
+\tsnote{There are more direct ways to formalize counting Bloom filters.
+But this less direct way will allow us to capture other kinds ``advanced'' Bloom filters proposed in the literature or (more importantly) used in practice.
+For example, $f_{\mathrm{setify}}(S,T)=\{(x,1) \,|\, x \in \mathcal{U} \mbox{s.t.
+} \mu_S(x)>0, \mu_T(x)>0\}$.
+On the other hand, we may end up deciding it is overkill...
+}

### 2016-05-26 syntax.tex
hammering on syntax

@@
 
-\heading{Hash-based (Bloom) filter syntax.}
+\heading{Hash-based (Bloom) filters.}
 Fix a nonempty sets $U,\Sigma$ and integers $k,m,n>0$.  Fix a symbol $\bot \not\in U$.  An $(n,k,m)$-filter (over universe~$U$) is a triple  $B=(\mathsc{H},\mathsc{Rep},\mathsc{Qry})$.   
@@
 %
-The deterministic representation algorithm $\mathsc{Rep}: [U]^n \rightarrow \Sigma^m$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m$.
+The deterministic representation algorithm $\mathsc{Rep}\colon [U]^n \rightarrow \Sigma^m$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m$.
 (Recall that $[U]^n$ denotes subsets of~$U$ of size~$n$.)
 %
-The determinisitc query algorithm $\mathsc{Qry}: \Sigma^m \times U \rightarrow \bits$ takes a representation $M$ and an element $x \in U$ and returns a bit.  
+The determinisitc query algorithm $\mathsc{Qry}\colon \Sigma^m \times U \rightarrow \bits$ takes a representation $M$ and an element $x \in U$ and returns a bit.  
 %
@@
 
-\heading{Hash-based filters with operations. }
+\heading{Mutuable hash-based filters. }
+Fix a nonempty sets $U,\Sigma$ and integers $k,m_1,m_2,>0$ with $m_1 \leq m_2$.
+Fix a symbol $\bot \not\in U$.
+An $(k,[m_1,m_2])$-filter (over universe~$U$) is a tuple  $B=(\mathsc{H},\mathsc{Rep},\mathsc{Qry},\mathsc{Up})$.
+%
+The randomized \emph{hash-sampling} algorithm~$\mathsc{H}$ samples a size~$k$ subset~$\mathcal{H} \subset \mathrm{Func}(U,\{0,1,\ldots,m_2-1\})$.
+We write $\mathcal{H} \getsr \mathsc{H}$ for this operation.
+%
+The deterministic representation algorithm $\mathsc{Rep}\colon [U]^n \rightarrow \bigcup_{m=m_1}^{m_2}\Sigma^m$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m_1 \leq m \leq m_2$.
+%\mbox{s.t. } \mu_S(x)>0, \mu_T(x)>0\}$.  On the other hand, we may end up deciding it is overkill... }
+%
+The determinisitc query algorithm $\mathsc{Qry}\colon \bigcup_{m=m_1}^{m_2}\Sigma^m \times U \rightarrow \bits$ takes a representation $M$ and an element $x \in U$ and returns a bit.  
+%
+The deterministic \emph{update} algorithm $\mathsc{Up}\colon \bigcup_{m=m_1}^{m_2}\Sigma^m \times \bits^* \rightarrow \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right) \cup \{\bot\}$ takes a representation and an update string, and returns an updated representation or the distinguished symbol~$\bot$.
+%
+%
+We assume that $\mathsc{Rep}$, $\mathsc{Qry}$ and $\mathsc{Up}$ have the following blackbox access to the functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$, which we denote by writing~$\mathcal{H}$ as a superscript.
+Thus, we write $M \gets \mathsc{Rep}^{\mathcal{H}}(S)$, $b \gets \mathsc{Qry}^{\mathcal{H}}(M,x)$, $M' \gets \mathsc{Up}(M,\sigma)$ for the execution of the representation, query and update algorithms, respectively.
+
+For correctness, we demand that...
+
+\heading{Multiset-oriented hash-based filters. }
 Here we extend the basic Bloom filter syntax to allow for variations on the traditional Bloom filter, e.g.
@@
 None of these require randomness, so I'll continue to formalize everything as deterministic.}\tsnote{“Scaling Bloom filters”, appear to allow the parameter~$m$, below, to vary.
-Syntax doesn't address this.}\tsnote{This syntax might naturally support count-min sketches, too.}
+I've altered the syntax to allow this.}\tsnote{This syntax might naturally support count-min sketches, too.}
 
@@
 
-An $(k,m)$-filter with operations is a tuple  $B=(\mathsc{H},\mathsc{Rep},\mathsc{Qry}, \mathcal{F})$.  
+An $(k,[m_1,m_2])$-filter with operations is a tuple  $B=(\mathsc{H},\mathsc{Rep},\mathsc{Qry}, \mathcal{F})$.  
 The set $\mathcal{F}$ is the finite collection of allowable operations.  All operations are of the form 
@@
 %
-The deterministic representation algorithm $\mathsc{Rep}: \mathbb{M}_\mathcal{U} \rightarrow \Sigma^m$ takes a multiset~$S$, and outputs representation~$M$ of length~$m$.
-The randomized hash-sampling algorithm and deterministic query algorithm is defined as before.
+The deterministic representation algorithm $\mathsc{Rep}\colon \mathbb{M}_\mathcal{U} \rightarrow \bigcup_{m=m_1}^{m_2}\Sigma^m$ takes a multiset~$S$, and outputs representation~$M$ of length~$m_1 \leq m m_2$.
+%
+The randomized hash-sampling algorithm~$\mathsc{H}$ is as before.
+%
+The determinisitic query algorithm $\mathsc{Qry}$ \tsnote{Not sure how to define this!  See my comment, below...}
 
-Correctness is defined as follows.
+%Correctness is defined as follows.
 Let $S,T$ be arbitrary multisets and let~$f$ be an arbitrary operation in $\mathcal{F}$.
@@
 This allows us to capture counting Bloom filters.
+\tsnote{Does it?
+Acutally, you might want $\mathsc{Qry}(M,x)$ to return a number, i.e., a counter value.
+How do you define correctness then?}
 

### 2016-05-26 syntax.tex
hammering on syntax

@@
 \section{Syntax}
-\tsnote{Very much a work-in-progress.}
 As a first step, let us try to better formalize Bloom filters as a primitive.
@@
 
+\tsnote{Very much a work-in-progress.}
+
 \heading{Mutuable hash-based filters. }
@@
 For correctness, we demand that...
+
+\tsnote{Below is an alternative way to formalize things like counting Bloom filters, count-min sketch, scaling Bloom filters, etc.  Neither is solid, yet.}
 

### 2016-05-26 syntax.tex
hammering on syntax

@@
 
-For correctness, we demand that for all $\mathcal{H}$ and $S$, and for all $x \in S, \mathsc{Qry}^{\mathcal{H}}(\mathsc{Rep}^{\mathcal{H}}(S),x)=1$.
+For correctness, we demand that for all $\mathcal{H}$ and~$S$, and for all $x \in S, \mathsc{Qry}^{\mathcal{H}}(\mathsc{Rep}^{\mathcal{H}}(S),x)=1$.
 
@@
 Fix a symbol $\bot \not\in U$.
-An $(k,[m_1,m_2])$-filter (over universe~$U$) is a tuple  $B=(\mathsc{H},\mathsc{Rep},\mathsc{Qry},\mathsc{Up})$.
+An $(k,[m_1,m_2])$-filter (over universe~$U$) is a tuple  $B=(\mathsc{H},\mathsc{Rep},\mathsc{Qry},\mathsc{Up}, \mathsc{Test})$.
 %
@@
 %
-The determinisitc query algorithm $\mathsc{Qry}\colon \bigcup_{m=m_1}^{m_2}\Sigma^m \times U \rightarrow \bits$ takes a representation $M$ and an element $x \in U$ and returns a bit.  
+The determinisitc query algorithm $\mathsc{Qry}\colon \bigcup_{m=m_1}^{m_2}\Sigma^m \times U \rightarrow \bits^*$ takes a representation $M$ and an element $x \in U$ and returns a bitstring.  
 %
@@
 %
+The deterministic \emph{test} algorithm $\mathsc{Test} \colon \bigcup_{m=m_1}^{m_2}\Sigma^m \times U \rightarrow \bits$ takes a representation~$M$ and an element~$x \in U$ and returns a bit.
 %
-We assume that $\mathsc{Rep}$, $\mathsc{Qry}$ and $\mathsc{Up}$ have the following blackbox access to the functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$, which we denote by writing~$\mathcal{H}$ as a superscript.
-Thus, we write $M \gets \mathsc{Rep}^{\mathcal{H}}(S)$, $b \gets \mathsc{Qry}^{\mathcal{H}}(M,x)$, $M' \gets \mathsc{Up}(M,\sigma)$ for the execution of the representation, query and update algorithms, respectively.
+We assume that all $\mathsc{Rep},\mathsc{Qry},\mathsc{Up},\mathsc{Test}$ all have blackbox access to the functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$, which we denote by writing~$\mathcal{H}$ as a superscript.
 
-For correctness, we demand that...
+\tsnote{Not sure how to define correctness.
+Intuitively, it should be something like, at any point in time, if $x\in S$ then $\Prob{\mathsc{Test}(M,x)=1} \geq \epsilon$ for some correctness parameter~$\epsilon$, where the probablilty is over...?
+Coins of~$\mathsc{H}$, perhaps.
+(Alternatively, could require for all outputs of~$\mathsc{H}$, as above.)  But perhaps this should be an adversarial game, in which case it is over the coins of the adversary, too.}
 

### 2016-05-26 syntax.tex
hammering on syntax

@@
 %
-The deterministic representation algorithm $\mathsc{Rep}\colon [U]^n \rightarrow \bigcup_{m=m_1}^{m_2}\Sigma^m$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m_1 \leq m \leq m_2$.
+The deterministic representation algorithm $\mathsc{Rep}\colon [U]^n \rightarrow \left(\bigcup_{m=m_1}^{m_2}\Sigma^m\right)$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m_1 \leq m \leq m_2$.
 %\mbox{s.t. } \mu_S(x)>0, \mu_T(x)>0\}$.  On the other hand, we may end up deciding it is overkill... }
 %
-The determinisitc query algorithm $\mathsc{Qry}\colon \bigcup_{m=m_1}^{m_2}\Sigma^m \times U \rightarrow \bits^*$ takes a representation $M$ and an element $x \in U$ and returns a bitstring.  
+The determinisitc query algorithm $\mathsc{Qry}\colon \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right)\times U \rightarrow \bits^*$ takes a representation $M$ and an element $x \in U$ and returns a bitstring.
 %
-The deterministic \emph{update} algorithm $\mathsc{Up}\colon \bigcup_{m=m_1}^{m_2}\Sigma^m \times \bits^* \rightarrow \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right) \cup \{\bot\}$ takes a representation and an update string, and returns an updated representation or the distinguished symbol~$\bot$.
+The deterministic \emph{update} algorithm $\mathsc{Up}\colon \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right)\times \bits^* \rightarrow \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right) \cup \{\bot\}$ takes a representation and an update string, and returns an updated representation or the distinguished symbol~$\bot$.
 %
-The deterministic \emph{test} algorithm $\mathsc{Test} \colon \bigcup_{m=m_1}^{m_2}\Sigma^m \times U \rightarrow \bits$ takes a representation~$M$ and an element~$x \in U$ and returns a bit.
+The deterministic \emph{test} algorithm $\mathsc{Test} \colon \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right) \times U \rightarrow \bits$ takes a representation~$M$ and an element~$x \in U$ and returns a bit.
 %

### 2016-05-26 syntax.tex
hammering on syntax

@@
 Thus, we write $M \gets \mathsc{Rep}^{\mathcal{H}}(S)$ and $b \gets \mathsc{Qry}^{\mathcal{H}}(M,x)$ for the execution of the representation and query algorithms, respectively.
-
-For correctness, we demand that for all $\mathcal{H}$ and~$S$, and for all $x \in S, \mathsc{Qry}^{\mathcal{H}}(\mathsc{Rep}^{\mathcal{H}}(S),x)=1$.
+%
+For correctness, we demand that for all~$S$ of size~$n$, we have that for all $x \in S, \Prob{\mathsc{Qry}^{\mathcal{H}}(\mathsc{Rep}^{\mathcal{H}}(S),x)=1}$, where the probability is over the sampling $\mathcal{H}\getsr\mathsc{H}$.
 
@@
 Setting $\Sigma=\bits^{\leq L}$ allows one to store a bitstring of length at most~$L$ at each location.
-\tsnote{Would let us capture a construction from NY, among other things.}
+\tsnote{Would let us capture a construction from NY, among other things.}  We note that even though this would allow for the storage of counters (say) at each filter location, our restriction that~$\mathsc{Qry}$ returns a bit does not capture functionality of Bloom filters that employ counters, e.g., returning a counter value.
+
+Our syntax also does not capture filters that are allowed to grow over time (e.g. ``scalable Bloom filters'') or cdertain kinds of hierarchical Bloom filters.  We turn our attention to this next.
 

### 2016-05-26 syntax.tex
hammering on syntax

@@
 \tsnote{Would let us capture a construction from NY, among other things.}  We note that even though this would allow for the storage of counters (say) at each filter location, our restriction that~$\mathsc{Qry}$ returns a bit does not capture functionality of Bloom filters that employ counters, e.g., returning a counter value.
+(One could, however, have $\mathsc{Qry}$ compute an arbitrary, fixed predicate.
+For example, ``has~$x$ been seen at least 5 times?''.)  Nonetheless, this restriction allows us to state a simple correctness condition, and covers a broad range of hash-based filters.
 
@@
 \heading{Mutuable hash-based filters. }
+Here we extend the basic Bloom filter syntax to allow for variations on the traditional Bloom filter, e.g.
+counting Bloom filters, spectral Bloom filters, count-min sketches.
+\tsnote{We should find out what are the important variations!
+I only know of a few.
+None of them require randomness for representation or querying, so I'll continue to formalize everything as deterministic.}
+
 Fix a nonempty sets $U,\Sigma$ and integers $k,m_1,m_2,>0$ with $m_1 \leq m_2$.
@@
 
-\tsnote{Below is an alternative way to formalize things like counting Bloom filters, count-min sketch, scaling Bloom filters, etc.  Neither is solid, yet.}
-
 \heading{Multiset-oriented hash-based filters. }
-Here we extend the basic Bloom filter syntax to allow for variations on the traditional Bloom filter, e.g.
-counting Bloom filters.
-\tsnote{We should find out what are the important variations!
-I only know of a few.
-None of these require randomness, so I'll continue to formalize everything as deterministic.}\tsnote{“Scaling Bloom filters”, appear to allow the parameter~$m$, below, to vary.
-I've altered the syntax to allow this.}\tsnote{This syntax might naturally support count-min sketches, too.}
+\tsnote{Below is an alternative way to formalize mutable hash-based filters.
+This way directly address the inputs as multisets, instead of starting with a set and then updating the represenation a step at a time.
+Not sure which is cleaner and more easily applied to real problems, yet.}
 
@@
 %
-The deterministic representation algorithm $\mathsc{Rep}\colon \mathbb{M}_\mathcal{U} \rightarrow \bigcup_{m=m_1}^{m_2}\Sigma^m$ takes a multiset~$S$, and outputs representation~$M$ of length~$m_1 \leq m m_2$.
+The deterministic representation algorithm $\mathsc{Rep}\colon \mathbb{M}_\mathcal{U} \rightarrow \bigcup_{m=m_1}^{m_2}\Sigma^m$ takes a multiset~$S$, and outputs representation~$M$ of length~$m_1 \leq m \leq m_2$.
 %
@@
 %
-The determinisitic query algorithm $\mathsc{Qry}$ \tsnote{Not sure how to define this!  See my comment, below...}
+The determinisitic query algorithm $\mathsc{Qry}$... \tsnote{Not sure how to define this!  See my comment, below...}
 
@@
 
-\tsnote{There are more direct ways to formalize counting Bloom filters.
+\tsnote{There are more direct ways to formalize counting Bloom filters, like the syntax above.
 But this less direct way will allow us to capture other kinds ``advanced'' Bloom filters proposed in the literature or (more importantly) used in practice.

### 2016-05-26 syntax.tex
hammering on syntax

@@
 
-Fix a nonempty sets $U,\Sigma$ and integers $k,m_1,m_2,>0$ with $m_1 \leq m_2$.
+Fix a nonempty sets $U,\Sigma$ and integers $k,m_1,m_2,n>0$ with $m_1 \leq m_2$.
 Fix a symbol $\bot \not\in U$.
-An $(k,[m_1,m_2])$-filter (over universe~$U$) is a tuple  $B=(\mathsc{H},\mathsc{Rep},\mathsc{Qry},\mathsc{Up}, \mathsc{Test})$.
+An $(n,k,[m_1,m_2])$-filter (over universe~$U$) is a tuple  $B=(\mathsc{H},\mathsc{Rep},\mathsc{Qry},\mathsc{Up}, \mathsc{Test})$.
 %
@@
 The deterministic representation algorithm $\mathsc{Rep}\colon [U]^n \rightarrow \left(\bigcup_{m=m_1}^{m_2}\Sigma^m\right)$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m_1 \leq m \leq m_2$.
-%\mbox{s.t. } \mu_S(x)>0, \mu_T(x)>0\}$.  On the other hand, we may end up deciding it is overkill... }
 %
@@
 
-An $(k,[m_1,m_2])$-filter with operations is a tuple  $B=(\mathsc{H},\mathsc{Rep},\mathsc{Qry}, \mathcal{F})$.  
+An $(n,k,[m_1,m_2])$-filter with operations is a tuple  $B=(\mathsc{H},\mathsc{Rep},\mathsc{Qry}, \mathcal{F})$.  
 The set $\mathcal{F}$ is the finite collection of allowable operations.  All operations are of the form 
@@
 %
-The deterministic representation algorithm $\mathsc{Rep}\colon \mathbb{M}_\mathcal{U} \rightarrow \bigcup_{m=m_1}^{m_2}\Sigma^m$ takes a multiset~$S$, and outputs representation~$M$ of length~$m_1 \leq m \leq m_2$.
+The deterministic representation algorithm $\mathsc{Rep}\colon \mathbb{M}_\mathcal{U} \rightarrow \bigcup_{m=m_1}^{m_2}\Sigma^m$ takes a multiset~$S$, and outputs representation~$M$ of length~$m_1 \leq m \leq m_2$, or the distinguished symbol~$\bot$.
+We assume that if the multiset~$S=\{(x_1,\ell_1),(x_2,\ell_2),\ldots,(x_t,\ell_t)\}$ is such that $n < \sum_{i=1}^t \ell_i$ then $\mathsc{Rep}(S)=\bot$.
 %

### 2016-05-26 syntax.tex
hacking on syntax

@@
 \heading{Hash-based (Bloom) filters.}
-Fix a nonempty sets $U,\Sigma$ and integers $k,m,n>0$.  Fix a symbol $\bot \not\in U$.  An $(n,k,m)$-filter (over universe~$U$) is a triple  $B=(\mathsc{H},\mathsc{Rep},\mathsc{Qry})$.   
+Fix a nonempty sets $U,\Sigma$ and integers $k,m,n>0$.  Fix a symbol $\bot \not\in U$.  An $(n,k,m)$-filter (over universe~$U$) is a triple  $B=(\mathsc{Hash},\mathsc{Rep},\mathsc{Qry})$.   
 %
-The randomized \emph{hash-sampling} algorithm~$\mathsc{H}$ samples a size~$k$ subset~$\mathcal{H} \subset \mathrm{Func}(U,\{0,1,\ldots,m-1\})$.
-We write $\mathcal{H} \getsr \mathsc{H}$ for this operation.
+The randomized \emph{hash-sampling} algorithm~$\mathsc{Hash}$ samples a size~$k$ subset~$\mathcal{H} \subset \mathrm{Func}(U,\{0,1,\ldots,m-1\})$.
+We write $\mathcal{H} \getsr \mathsc{Hash}$ for this operation.
 %
@@
 %
-For correctness, we demand that for all~$S$ of size~$n$, we have that for all $x \in S, \Prob{\mathsc{Qry}^{\mathcal{H}}(\mathsc{Rep}^{\mathcal{H}}(S),x)=1}$, where the probability is over the sampling $\mathcal{H}\getsr\mathsc{H}$.
+For correctness, we demand that for all~$S$ of size~$n$, we have that for all $x \in S, \Prob{\mathsc{Qry}^{\mathcal{H}}(\mathsc{Rep}^{\mathcal{H}}(S),x)=1}=1$, where the probability is over the sampling $\mathcal{H}\getsr\mathsc{Hash}$.
 
@@
 Fix a symbol $\bot \not\in U$.
-An $(n,k,[m_1,m_2])$-filter (over universe~$U$) is a tuple  $B=(\mathsc{H},\mathsc{Rep},\mathsc{Qry},\mathsc{Up}, \mathsc{Test})$.
+An $(n,k,[m_1,m_2])$-filter (over universe~$U$) is a tuple  $B=(\mathsc{Hash},\mathsc{Rep},\mathsc{Qry},\mathsc{Up}, \mathsc{Test})$.
 %
-The randomized \emph{hash-sampling} algorithm~$\mathsc{H}$ samples a size~$k$ subset~$\mathcal{H} \subset \mathrm{Func}(U,\{0,1,\ldots,m_2-1\})$.
-We write $\mathcal{H} \getsr \mathsc{H}$ for this operation.
+The randomized \emph{hash-sampling} algorithm~$\mathsc{Hash}$ samples a size~$k$ subset~$\mathcal{H} \subset \mathrm{Func}(U,\{0,1,\ldots,m_2-1\})$.
+We write $\mathcal{H} \getsr \mathsc{Hash}$ for this operation.
 %
@@
 \tsnote{Not sure how to define correctness.
-Intuitively, it should be something like, at any point in time, if $x\in S$ then $\Prob{\mathsc{Test}(M,x)=1} \geq \epsilon$ for some correctness parameter~$\epsilon$, where the probablilty is over...?
-Coins of~$\mathsc{H}$, perhaps.
-(Alternatively, could require for all outputs of~$\mathsc{H}$, as above.)  But perhaps this should be an adversarial game, in which case it is over the coins of the adversary, too.}
+Intuitively, it should be something like, at any point in time, if $x\in S$ then $\Prob{\mathsc{Test}(M,x)=1} \geq 1-\epsilon$ for some correctness parameter~$\epsilon$, where the probablilty is over (at least) the coins of~$\mathsc{Hash}$.
+But perhaps this should be an adversarial game, in which case it is over the coins of the adversary, too...}
+
+\heading{Discussion.
+} Our syntax captures settings in which there is some (potentially empty) initial set~$S$, whose representation~$M$ may undergo updates over time.
+Effectively, this allows for expansion of~$S$ to a larger set, or even a multiset, as new elements ``arrive''.
+The update algorithm is responsible for altering the current representation.
+We allow it to take in a string that encodes inputs needed to carry out the updating.
+For example, counting Bloom filters may receive update strings that encode $(x,c)$ where $x \in U$ is the element whose representation should be incremented, and $c \in \mathbb{N}$ is the amount of the increment.
+Network applications, such as looking for heavy-hitters across TCP/IP streams seen by a router, may have $x = (\mathrm{IP_{src}},\mathrm{IP_{dst}})$, the source and destintation address of a packet, and~$c$ the number of bytes in the packet payload.
+When necessary we will specify what is encoded in the update string, but will assume some implicit and fixed encoding scheme.
 
@@
 
-An $(n,k,[m_1,m_2])$-filter with operations is a tuple  $B=(\mathsc{H},\mathsc{Rep},\mathsc{Qry}, \mathcal{F})$.  
+An $(n,k,[m_1,m_2])$-filter with operations is a tuple  $B=(\mathsc{Hash},\mathsc{Rep},\mathsc{Qry}, \mathcal{F})$.  
 The set $\mathcal{F}$ is the finite collection of allowable operations.  All operations are of the form 
@@
 %
-The randomized hash-sampling algorithm~$\mathsc{H}$ is as before.
+The randomized hash-sampling algorithm~$\mathsc{Hash}$ is as before.
 %

### 2016-05-27 syntax.tex
hacking on syntax

@@
 %
-The deterministic \emph{update} algorithm $\mathsc{Up}\colon \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right)\times \bits^* \rightarrow \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right) \cup \{\bot\}$ takes a representation and an update string, and returns an updated representation or the distinguished symbol~$\bot$.
+The randomized \emph{update} algorithm $\mathsc{Up}\colon \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right)\times \bits^* \rightarrow \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right) \cup \{\bot\}$ takes a representation and an update string, and returns an updated representation or the distinguished symbol~$\bot$.
+\tsnote{I allow randomized update to admit things like the ``Stable Bloom filter'' construction, which has a randomized forgetting feature.
+Other constructions may have something similar.}
 %

### 2016-05-30 syntax.tex
hacking on syntax

--- 2016-05-26 syntax.tex
@@
+\newcommand{\Rep}{\mathsc{Rep}}
+\newcommand{\Hash}{\mathsc{Hash}}
+\newcommand{\Qry}{\mathsc{Qry}}
+\newcommand{\Update}{\mathsc{Up}}
+\newcommand{\Init}{\mathsc{Init}}
+\newcommand{\Test}{\mathsc{Test}}
+
 \section{Syntax}
@@
 \heading{Hash-based (Bloom) filters.}
-Fix a nonempty sets $U,\Sigma$ and integers $k,m,n>0$.  Fix a symbol $\bot \not\in U$.  An $(n,k,m)$-filter (over universe~$U$) is a triple  $B=(\mathsc{Hash},\mathsc{Rep},\mathsc{Qry})$.   
+Fix a nonempty sets $U,\Sigma$ and integers $k,m,n>0$.  Fix a symbol $\bot \not\in U$.  An $(n,k,m)$-filter (over universe~$U$) is a triple  $B=(\Hash,\Rep,\Qry)$.   
 %
-The randomized \emph{hash-sampling} algorithm~$\mathsc{Hash}$ samples a size~$k$ subset~$\mathcal{H} \subset \mathrm{Func}(U,\{0,1,\ldots,m-1\})$.
-We write $\mathcal{H} \getsr \mathsc{Hash}$ for this operation.
+The randomized \emph{hash-sampling} algorithm~$\Hash$ samples a size~$k$ subset~$\mathcal{H} \subset \mathrm{Func}(U,\{0,1,\ldots,m-1\})$.  We write $\mathcal{H} \getsr \Hash$ for this operation.
 %
-The deterministic representation algorithm $\mathsc{Rep}\colon [U]^n \rightarrow \Sigma^m$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m$.
+The deterministic representation algorithm $\Rep\colon [U]^n \rightarrow \Sigma^m$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m$.
 (Recall that $[U]^n$ denotes subsets of~$U$ of size~$n$.)
 %
-The determinisitc query algorithm $\mathsc{Qry}\colon \Sigma^m \times U \rightarrow \bits$ takes a representation $M$ and an element $x \in U$ and returns a bit.  
+The determinisitc query algorithm $\Qry\colon \Sigma^m \times U \rightarrow \bits$ takes a representation $M$ and an element $x \in U$ and returns a bit.  
 %
-We assume that both $\mathsc{Rep}$ and $\mathsc{Qry}$ have the following blackbox access to the functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$, which we denote by writing~$\mathcal{H}$ as a superscript.
-Thus, we write $M \gets \mathsc{Rep}^{\mathcal{H}}(S)$ and $b \gets \mathsc{Qry}^{\mathcal{H}}(M,x)$ for the execution of the representation and query algorithms, respectively.
+We assume that both $\Rep$ and $\Qry$ have the following blackbox access to the functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$, which we denote by writing~$\mathcal{H}$ as a superscript.
+Thus, we write $M \gets \Rep^{\mathcal{H}}(S)$ and $b \gets \Qry^{\mathcal{H}}(M,x)$ for the execution of the representation and query algorithms, respectively.
 %
-For correctness, we demand that for all~$S$ of size~$n$, we have that for all $x \in S, \Prob{\mathsc{Qry}^{\mathcal{H}}(\mathsc{Rep}^{\mathcal{H}}(S),x)=1}=1$, where the probability is over the sampling $\mathcal{H}\getsr\mathsc{Hash}$.
+For correctness, we demand that for all~$S$ of size~$n$, we have that for all $x \in S, \Prob{\Qry^{\mathcal{H}}(\Rep^{\mathcal{H}}(S),x)=1}=1$, where the probability is over the sampling $\mathcal{H}\getsr\Hash$.
 
 \heading{Discusssion.}
-This syntax captures classical Bloom filters by setting~$\Sigma=\bits$ and defining $\mathsc{Rep},\mathsc{Qry}$ in the obvious way.
+This syntax captures classical Bloom filters by setting~$\Sigma=\bits$ and defining $\Rep,\Qry$ in the obvious way.
 Setting $\Sigma=\bits^{\leq L}$ allows one to store a bitstring of length at most~$L$ at each location.
-\tsnote{Would let us capture a construction from NY, among other things.}  We note that even though this would allow for the storage of counters (say) at each filter location, our restriction that~$\mathsc{Qry}$ returns a bit does not capture functionality of Bloom filters that employ counters, e.g., returning a counter value.
-(One could, however, have $\mathsc{Qry}$ compute an arbitrary, fixed predicate.
+\tsnote{Would let us capture a construction from NY, among other things.}  We note that even though this would allow for the storage of counters (say) at each filter location, our restriction that~$\Qry$ returns a bit does not capture functionality of Bloom filters that employ counters, e.g., returning a counter value.
+(One could, however, have $\Qry$ compute an arbitrary, fixed predicate.
 For example, ``has~$x$ been seen at least 5 times?''.)  Nonetheless, this restriction allows us to state a simple correctness condition, and covers a broad range of hash-based filters.
@@
 
-\tsnote{Very much a work-in-progress.}
-
 \heading{Mutuable hash-based filters. }
 Here we extend the basic Bloom filter syntax to allow for variations on the traditional Bloom filter, e.g.
-counting Bloom filters, spectral Bloom filters, count-min sketches.
-\tsnote{We should find out what are the important variations!
-I only know of a few.
-None of them require randomness for representation or querying, so I'll continue to formalize everything as deterministic.}
-
-Fix a nonempty sets $U,\Sigma$ and integers $k,m_1,m_2,n>0$ with $m_1 \leq m_2$.
-Fix a symbol $\bot \not\in U$.
-An $(n,k,[m_1,m_2])$-filter (over universe~$U$) is a tuple  $B=(\mathsc{Hash},\mathsc{Rep},\mathsc{Qry},\mathsc{Up}, \mathsc{Test})$.
-%
-The randomized \emph{hash-sampling} algorithm~$\mathsc{Hash}$ samples a size~$k$ subset~$\mathcal{H} \subset \mathrm{Func}(U,\{0,1,\ldots,m_2-1\})$.
-We write $\mathcal{H} \getsr \mathsc{Hash}$ for this operation.
-%
-The deterministic representation algorithm $\mathsc{Rep}\colon [U]^n \rightarrow \left(\bigcup_{m=m_1}^{m_2}\Sigma^m\right)$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m_1 \leq m \leq m_2$.
-%
-The determinisitc query algorithm $\mathsc{Qry}\colon \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right)\times U \rightarrow \bits^*$ takes a representation $M$ and an element $x \in U$ and returns a bitstring.
-%
-The deterministic \emph{update} algorithm $\mathsc{Up}\colon \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right)\times \bits^* \rightarrow \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right) \cup \{\bot\}$ takes a representation and an update string, and returns an updated representation or the distinguished symbol~$\bot$.
-%
-The deterministic \emph{test} algorithm $\mathsc{Test} \colon \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right) \times U \rightarrow \bits$ takes a representation~$M$ and an element~$x \in U$ and returns a bit.
-%
-We assume that all $\mathsc{Rep},\mathsc{Qry},\mathsc{Up},\mathsc{Test}$ all have blackbox access to the functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$, which we denote by writing~$\mathcal{H}$ as a superscript.
-
-\tsnote{Not sure how to define correctness.
-Intuitively, it should be something like, at any point in time, if $x\in S$ then $\Prob{\mathsc{Test}(M,x)=1} \geq 1-\epsilon$ for some correctness parameter~$\epsilon$, where the probablilty is over (at least) the coins of~$\mathsc{Hash}$.
-But perhaps this should be an adversarial game, in which case it is over the coins of the adversary, too...}
-
-\heading{Discussion.
-} Our syntax captures settings in which there is some (potentially empty) initial set~$S$, whose representation~$M$ may undergo updates over time.
+counting Bloom filters~\cite{xxx}, spectral Bloom filters~\cite{xxx}, count-min sketches~\cite{xxx}, stable Bloom filters~\cite{xxx}, etc.
+Before giving it, let us briefly describe what is formalized.
+Our syntax captures settings in which there is some (potentially empty) initial set~$S$, whose representation~$M$ may undergo updates over time.
 Effectively, this allows for expansion of~$S$ to a larger set, or even a multiset, as new elements ``arrive''.
@@
 When necessary we will specify what is encoded in the update string, but will assume some implicit and fixed encoding scheme.
+Note that our syntax allows for randomized updating.
+This accommodates stable Bloom filters, for example, which has a randomized ``forgetting'' feature as part of its update.
+
+\tsnote{Very much a work-in-progress.}
+Fix a nonempty sets $U,\Sigma$ and integers $k,m_1,m_2,n>0$ with $m_1 \leq m_2$.
+Fix a symbol $\bot \not\in U$.
+An $(n,k,[m_1,m_2])$-filter (over universe~$U$) is a tuple  $B=(\Hash,\Init,\Qry,\Update, \Test)$.
+%
+The randomized \emph{hash-sampling} algorithm~$\Hash$ samples a size~$k$ subset~$\mathcal{H} \subset \mathrm{Func}(U,\{0,1,\ldots,m_2-1\})$.  We write $\mathcal{H} \getsr \Hash$ for this operation.
+%
+The deterministic initial-representation algorithm $\Init\colon [U]^n \rightarrow \left(\bigcup_{m=m_1}^{m_2}\Sigma^m\right)$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m_1 \leq m \leq m_2$.
+%
+The determinisitc query algorithm $\Qry\colon \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right)\times U \rightarrow \bits^*$ takes a representation $M$ and an element $x \in U$ and returns a bitstring.  
+%
+The randomized \emph{update} algorithm $\Update\colon \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right)\times \bits^* \rightarrow \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right) \cup \{\bot\}$ takes a representation and an update string, and returns an updated representation or the distinguished symbol~$\bot$.
+%
+The deterministic \emph{test} algorithm $\Test \colon \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right) \times U \rightarrow \bits$ takes a representation~$M$ and an element~$x \in U$ and returns a bit.
+%
+We assume that all $\Init,\Qry,\Update,\Test$ all have blackbox access to the functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$, which we denote by writing~$\mathcal{H}$ as a superscript.
+
+\tsnote{Not sure how to define correctness.
+Intuitively, it should be something like, at any point in time, if $x\in S$ then $\Prob{\Test(M,x)=1} \geq 1-\epsilon$ for some correctness parameter~$\epsilon$, where the probablilty is over (at least) the coins of~$\Hash$.
+But perhaps this should be an adversarial game, in which case it is over the coins of the adversary, too...}
 
 \heading{Multiset-oriented hash-based filters. }
-\tsnote{Below is an alternative way to formalize mutable hash-based filters.
+\tsnote{Commented out, but in the source: an alternative way to formalize mutable hash-based filters.
 This way directly address the inputs as multisets, instead of starting with a set and then updating the represenation a step at a time.
 Not sure which is cleaner and more easily applied to real problems, yet.}
+\if{0}
 
@@
 
-An $(n,k,[m_1,m_2])$-filter with operations is a tuple  $B=(\mathsc{Hash},\mathsc{Rep},\mathsc{Qry}, \mathcal{F})$.  
+An $(n,k,[m_1,m_2])$-filter with operations is a tuple  $B=(\Hash,\Rep,\Qry, \mathcal{F})$.  
 The set $\mathcal{F}$ is the finite collection of allowable operations.  All operations are of the form 
@@
 %
-The deterministic representation algorithm $\mathsc{Rep}\colon \mathbb{M}_\mathcal{U} \rightarrow \bigcup_{m=m_1}^{m_2}\Sigma^m$ takes a multiset~$S$, and outputs representation~$M$ of length~$m_1 \leq m \leq m_2$, or the distinguished symbol~$\bot$.
-We assume that if the multiset~$S=\{(x_1,\ell_1),(x_2,\ell_2),\ldots,(x_t,\ell_t)\}$ is such that $n < \sum_{i=1}^t \ell_i$ then $\mathsc{Rep}(S)=\bot$.
+The deterministic representation algorithm $\Rep\colon \mathbb{M}_\mathcal{U} \rightarrow \bigcup_{m=m_1}^{m_2}\Sigma^m$ takes a multiset~$S$, and outputs representation~$M$ of length~$m_1 \leq m \leq m_2$, or the distinguished symbol~$\bot$.
+We assume that if the multiset~$S=\{(x_1,\ell_1),(x_2,\ell_2),\ldots,(x_t,\ell_t)\}$ is such that $n < \sum_{i=1}^t \ell_i$ then $\Rep(S)=\bot$.
 %
-The randomized hash-sampling algorithm~$\mathsc{Hash}$ is as before.
+The randomized hash-sampling algorithm~$\Hash$ is as before.
 %
-The determinisitic query algorithm $\mathsc{Qry}$... \tsnote{Not sure how to define this!  See my comment, below...}
+The determinisitic query algorithm $\Qry$... \tsnote{Not sure how to define this!  See my comment, below...}
 
@@
 Let $S,T$ be arbitrary multisets and let~$f$ be an arbitrary operation in $\mathcal{F}$.
-If $f(S,T) = S'\neq \bot$, then for all $x \in S'$ we demand that $\mathsc{Qry}(\mathsc{Rep}(S'),x)=1$.
+If $f(S,T) = S'\neq \bot$, then for all $x \in S'$ we demand that $\Qry(\Rep(S'),x)=1$.
 \tsnote{might need a stronger condition that this holds for any sequence of operations that do not result in $\bot$.}
@@
 First, let $\Sigma = \mathbb{N}$ and define $f_{\mathrm{add}}(S,T)=\{(x,\mu_S(x)+\mu_T(x)) \,|\, x \in \mathcal{U}\}$ and $f_\mathrm{del}(S,T) = \{(x,\min\{0,\mu_S(x)-\mu_T(x)\}) \,|\, x \in \mathcal{U} \}$.
-Define $\mathsc{Rep}(S')$ as follows: for each $(x,\ell)\in S'$ and $j\in\{1,2,\ldots,k\}$, set $M[h_j(x)]=\ell$.
-Finally, define $\mathsc{Qry}(M,x) = 1 \Leftrightarrow \forall j \in \{1,2,\ldots,k\},\; M[h_j(x)] > 0$.
+Define $\Rep(S')$ as follows: for each $(x,\ell)\in S'$ and $j\in\{1,2,\ldots,k\}$, set $M[h_j(x)]=\ell$.
+Finally, define $\Qry(M,x) = 1 \Leftrightarrow \forall j \in \{1,2,\ldots,k\},\; M[h_j(x)] > 0$.
 This allows us to capture counting Bloom filters.
 \tsnote{Does it?
-Acutally, you might want $\mathsc{Qry}(M,x)$ to return a number, i.e., a counter value.
+Acutally, you might want $\Qry(M,x)$ to return a number, i.e., a counter value.
 How do you define correctness then?}
@@
 }
+\fi

### 2016-05-30 syntax.tex
hacking on syntax

@@
 \newcommand{\Test}{\mathsc{Test}}
+\newcommand{\multiset}[1]{\mathbb{M}_{#1}}
+\newcommand{\ExpCorrectSecHash}[2]{\mathrm{Exp}^{\mathrm{cor\mbox{-}prv}}_{#1}(#2)}
+\newcommand{\ExpCorrectPubHash}[2]{\mathrm{Exp}^{\mathrm{cor\mbox{-}pub}}_{#1}(#2)}
+\newcommand{\ExpCorrect}[2]{\mathrm{Exp}^{\mathrm{cor}}_{#1}(#2)}
+
+\newcommand{\QryOracle}{\mathsf{Query}}
+\newcommand{\UpdateOracle}{\mathsf{Update}}
+\newcommand{\HashOracle}{\mathsf{Hash}}
 
 \section{Syntax}
-As a first step, let us try to better formalize Bloom filters as a primitive.
+\heading{Preliminaries.}
+When~$U$ is a set and $n>0$ is an integer, we let $[U]^n$ denote the set of all size-$n$ subsets of~$U$.
+We let $\multiset{U}$ denote the set of all finite multisets of~$U$.
+We can denote any multiset~$S$ as $\{(x,\ell) \,|\, x \in U, \ell > 0\}$ where each~$x$ appears exactly once, and each~$\ell$ is an integer.
+We define the multiplicity of~$x$ as $\mu_S(x) = \ell$.
+We write $|S|= \sum_{(x,\ell)\in S}\mu_S(x)$, and let $\multiset{U,n}$ denote the set of multisets~$S$ where $|S|=n$.
 
-\heading{Hash-based (Bloom) filters.}
-Fix a nonempty sets $U,\Sigma$ and integers $k,m,n>0$.  Fix a symbol $\bot \not\in U$.  An $(n,k,m)$-filter (over universe~$U$) is a triple  $B=(\Hash,\Rep,\Qry)$.   
+We write $x \getsr U$ to denote sampling an element from~$U$ and assigning this to~$x$, and we extend this notation to randomized algorithms.
+
+\heading{Hash-based filters.}
+Fix a nonempty sets $U,\Sigma$ and integers $k,m,n>0$.  Fix a symbol $\bot \not\in U$.  An $(n,k,m)$-filter (over universe~$U$) is a tuple  $B=(\Hash,\Rep,\Qry)$.   
 %
-The randomized \emph{hash-sampling} algorithm~$\Hash$ samples a size~$k$ subset~$\mathcal{H} \subset \mathrm{Func}(U,\{0,1,\ldots,m-1\})$.  We write $\mathcal{H} \getsr \Hash$ for this operation.
+The randomized \emph{hash-sampling} algorithm~$\Hash$ samples a size~$k$ family of functions~$\mathcal{H}=\{h_1,h_2,\ldots,h_k\}$ where each $h_i \in  \mathrm{Func}(U,\{0,1,\ldots,m-1\})$.
+We write $\mathcal{H} \getsr \Hash$ for this operation.
 %
@@
 %
-We assume that both $\Rep$ and $\Qry$ have the following blackbox access to the functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$, which we denote by writing~$\mathcal{H}$ as a superscript.
-Thus, we write $M \gets \Rep^{\mathcal{H}}(S)$ and $b \gets \Qry^{\mathcal{H}}(M,x)$ for the execution of the representation and query algorithms, respectively.
+We assume that both $\Rep$ and $\Qry$ have the following blackbox access to the functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$.
+%which we denote by writing~$\mathcal{H}$ as a superscript.   
+%Thus, we write $M \gets \Rep^{\mathcal{H}}(S)$ and $b \gets \Qry^{\mathcal{H}}(M,x)$ for the execution of the representation and query algorithms, respectively.
 %
-For correctness, we demand that for all~$S$ of size~$n$, we have that for all $x \in S, \Prob{\Qry^{\mathcal{H}}(\Rep^{\mathcal{H}}(S),x)=1}=1$, where the probability is over the sampling $\mathcal{H}\getsr\Hash$.
+%We write $M \gets \Rep(S)$ and $b \gets \Qry(M,x)$ for the execution of the representation and query algorithms, respectively.
+For correctness, we demand that for all~$S$ of size~$n$, we have that for all $x \in S, \Prob{\Qry(\Rep(S),x)=1}=1$, where the probability is over the coins of $\Hash$.
 
-\heading{Discusssion.}
-This syntax captures classical Bloom filters by setting~$\Sigma=\bits$ and defining $\Rep,\Qry$ in the obvious way.
+%\heading{Discusssion.}
+This syntax captures classical Bloom filters by setting~$\Sigma=\bits$,  and defining $\Rep,\Qry$ in the obvious way.
 Setting $\Sigma=\bits^{\leq L}$ allows one to store a bitstring of length at most~$L$ at each location.
-\tsnote{Would let us capture a construction from NY, among other things.}  We note that even though this would allow for the storage of counters (say) at each filter location, our restriction that~$\Qry$ returns a bit does not capture functionality of Bloom filters that employ counters, e.g., returning a counter value.
+\tsnote{Would let us capture a construction from NY, among other things.}  We note that even though this would allow for the storage of counters (say) at each filter location, our restriction that~$\Qry$ returns a bit does not capture functionality typically demanded of Bloom filters that employ counters, e.g., returning a counter value.
 (One could, however, have $\Qry$ compute an arbitrary, fixed predicate.
 For example, ``has~$x$ been seen at least 5 times?''.)  Nonetheless, this restriction allows us to state a simple correctness condition, and covers a broad range of hash-based filters.
-
-Our syntax also does not capture filters that are allowed to grow over time (e.g. ``scalable Bloom filters'') or cdertain kinds of hierarchical Bloom filters.  We turn our attention to this next.
+Our syntax also does not capture filters that are mutable, that is, whose representation may change over time.  We address these generalizations next.
 
@@
 
-\tsnote{Very much a work-in-progress.}
-Fix a nonempty sets $U,\Sigma$ and integers $k,m_1,m_2,n>0$ with $m_1 \leq m_2$.
+Fix nonempty sets $U,\Sigma$ and integers $k,m_1,m_2,n>0$ with $m_1 \leq m_2$.
 Fix a symbol $\bot \not\in U$.
@@
 %
-The randomized \emph{hash-sampling} algorithm~$\Hash$ samples a size~$k$ subset~$\mathcal{H} \subset \mathrm{Func}(U,\{0,1,\ldots,m_2-1\})$.  We write $\mathcal{H} \getsr \Hash$ for this operation.
+The randomized \emph{hash-sampling} algorithm~$\Hash$ samples a size~$k$ family of functions~$\mathcal{H}=\{h_1,h_2,\ldots,h_k\}$ where each $h_i \in  \mathrm{Func}(U,\{0,1,\ldots,m_2-1\})$.
+We write $\mathcal{H} \getsr \Hash$ for this operation.
 %
-The deterministic initial-representation algorithm $\Init\colon [U]^n \rightarrow \left(\bigcup_{m=m_1}^{m_2}\Sigma^m\right)$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m_1 \leq m \leq m_2$.
+The deterministic \emph{initial-representation} algorithm $\Init\colon \multiset{U,n} \rightarrow \left(\bigcup_{m=m_1}^{m_2}\Sigma^m\right)$ takes a multiset~$S$ of size~$n$ as input, and outputs representation~$M$ of length~$m_1 \leq m \leq m_2$.
 %
@@
 %
-The deterministic \emph{test} algorithm $\Test \colon \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right) \times U \rightarrow \bits$ takes a representation~$M$ and an element~$x \in U$ and returns a bit.
+The deterministic \emph{test} algorithm $\Test \colon \multiset{U}\times \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right)\cup\{\bot\} \times U \rightarrow \bits$ takes a multiset~$S$, a representation~$M$ and an element~$x \in U$ and returns a bit.
 %
-We assume that all $\Init,\Qry,\Update,\Test$ all have blackbox access to the functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$, which we denote by writing~$\mathcal{H}$ as a superscript.
+%We assume that all $\Init,\Qry,\Update,\Test$ all have blackbox access to the functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$, which we denote by writing~$\mathcal{H}$ as a superscript.
 
-\tsnote{Not sure how to define correctness.
-Intuitively, it should be something like, at any point in time, if $x\in S$ then $\Prob{\Test(M,x)=1} \geq 1-\epsilon$ for some correctness parameter~$\epsilon$, where the probablilty is over (at least) the coins of~$\Hash$.
-But perhaps this should be an adversarial game, in which case it is over the coins of the adversary, too...}
+\begin{figure}
+\centering
+\fpage{.6}{
+\hpagess{.6}{.35}
+{
+\experimentv{$\ExpCorrectSecHash{S,B}{A}$}\\
+$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
+$M \gets \Init^{\HashOracle}(S)$\\
+$x \getsr A^{\QryOracle,\UpdateOracle}(S)$\\
+if $\Test^{\HashOracle}(S,M,x) \neq 0$ then Ret 1\\
+Ret 0\\
+
+\medskip
+\experimentv{$\ExpCorrectPubHash{S,B}{A}$}\\
+$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
+$M \gets \Init^{\HashOracle}(S)$\\
+$x \getsr A^{\QryOracle,\UpdateOracle,\HashOracle}(S)$\\
+if $\Test^{\HashOracle}(S,M,x) \neq 0$ then Ret 1\\
+Ret 0
+}
+%
+{
+\oracle{$\QryOracle(x)$}\\
+if $M = \bot$ then Ret $\bot$\\
+Ret $\Qry^{\HashOracle}(M,x)$\\
+
+\medskip
+\oracle{$\UpdateOracle(\sigma)$}\\
+if $M = \bot$ then Ret $\bot$ \\
+$S \gets S \uplus \{\sigma\}$\\
+$M \getsr \Update^{\HashOracle}(M,\sigma)$\\
+
+\medskip
+\oracle{$\HashOracle(i,x)$}\\
+Ret $h_i(x)$\\
+}
+}
+\caption{Trying to define correctness for an $(n,k,[m_1,m_2])$-filter~$B$.}
+\label{fig:correctness-mutable}
+\end{figure}
+
+\tsnote{Not sure how to define correctness, since these kinds of filters/sketches can have two-sided error.}
 

### 2016-05-30 syntax.tex
hacking on syntax

@@
 The deterministic representation algorithm $\Rep\colon [U]^n \rightarrow \Sigma^m$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m$.
-(Recall that $[U]^n$ denotes subsets of~$U$ of size~$n$.)
 %
@@
 (One could, however, have $\Qry$ compute an arbitrary, fixed predicate.
-For example, ``has~$x$ been seen at least 5 times?''.)  Nonetheless, this restriction allows us to state a simple correctness condition, and covers a broad range of hash-based filters.
-Our syntax also does not capture filters that are mutable, that is, whose representation may change over time.  We address these generalizations next.
+For example, ``has~$x$ been seen at least 5 times?''.)
+Our syntax also does not capture filters that are mutable, that is, whose representation may change over time. 
+On the other hand, we can state a simple correctness condition for these kinds of filters; this will not be true when we further generalize to capture, properly, counters and mutability.
 
@@
 $x \getsr A^{\QryOracle,\UpdateOracle}(S)$\\
-if $\Test^{\HashOracle}(S,M,x) \neq 0$ then Ret 1\\
+if $\Test^{\HashOracle}(S,M,x) \neq 1$ then Ret 1\\
 Ret 0\\
@@
 $x \getsr A^{\QryOracle,\UpdateOracle,\HashOracle}(S)$\\
-if $\Test^{\HashOracle}(S,M,x) \neq 0$ then Ret 1\\
+if $\Test^{\HashOracle}(S,M,x) \neq 1$ then Ret 1\\
 Ret 0

### 2016-05-30 syntax.tex
hacking on syntax

@@
 
-\section{Syntax}
+\section{Hash-based Filters}
 \heading{Preliminaries.}
@@
 
-\heading{Hash-based filters.}
+\heading{Syntax.}
 Fix a nonempty sets $U,\Sigma$ and integers $k,m,n>0$.  Fix a symbol $\bot \not\in U$.  An $(n,k,m)$-filter (over universe~$U$) is a tuple  $B=(\Hash,\Rep,\Qry)$.   
@@
 
-\heading{Mutuable hash-based filters. }
+\heading{Soundness of hash-based filters.} \tsnote{To do.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Mutuable hash-based filters}
 Here we extend the basic Bloom filter syntax to allow for variations on the traditional Bloom filter, e.g.
@@
 
+\heading{Syntax. }
 Fix nonempty sets $U,\Sigma$ and integers $k,m_1,m_2,n>0$ with $m_1 \leq m_2$.
@@
 %We assume that all $\Init,\Qry,\Update,\Test$ all have blackbox access to the functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$, which we denote by writing~$\mathcal{H}$ as a superscript.
+
+\heading{Correctness.
+} The kind of filters we capture, here, can have \emph{two-sided} error.
+That is, they may result in false-negatives as well as false-positives.
+We captures two versions of correctness in Figure~\ref{fig:correctness-mutable}, corresponding to whether or not the adversary is given access to the hash functions used to create and update the multiset representation.
 
@@
 
-\tsnote{Not sure how to define correctness, since these kinds of filters/sketches can have two-sided error.}
+\heading{Soundness for mutable hash-based filters. } \tsnote{To do.}
 
+\if{0}
 \heading{Multiset-oriented hash-based filters. }
@@
 Not sure which is cleaner and more easily applied to real problems, yet.}
-\if{0}
 

### 2016-05-30 intro.tex
syntax work
cheers

@@
 This particular ``encrypted Bloom filter'' instantiation was suggested for use in efficient linking of records across separate medical record databases~\cite{xxx}.
-(It was subsequently shown not to be secure by Niedermeier et al.~\cite{xxx}, where a clever use of frequency analysis recovered the last names of patients given access only to the Bloom filter array.)  In any case, it is clear that the NY definition does not capture the most widely used applications of Bloom filters, e.g.
+(It was subsequently shown not to be secure by Niedermeier et al.~\cite{xxx}, where a clever use of frequency analysis recovered the last names of patients given access only to the Bloom filter array.\tsnote{This shows that having secret hash functions does not automatically give privacy.})  In any case, it is clear that the NY definition does not capture the most widely used applications of Bloom filters, e.g.
 CDN summary caches, P2P network routing algorithms, etc.
@@
 \heading{Related work. }
-
-\tsnote{Stopped here.}
 

### 2016-05-30 syntax.tex
cheers

@@
 
-\heading{Soundness of hash-based filters.} \tsnote{To do.}
+\heading{Soundness of hash-based filters.} \tsnote{To do.
+Note that it makes sense to consider soundness both in the public and private hash setting.
+NY give it in the private hash setting (sort of); but, intuitively, it should be hard to find false-positives even if you know that MD5 or SHA-x are the hash functions  It might be interesting to run some experiments, e.g.
+set up a bloom filter of URLs or IP/port information, and then open up a network tap and see how many false positives we observe.}
 
@@
 
-\heading{Soundness for mutable hash-based filters. } \tsnote{To do.}
+\heading{Soundness for mutable hash-based filters. } \tsnote{To do.  Same comments as for the simple case, only it's more complicated here what it means to violate soundness.}
 

### 2016-05-30 intro.tex
cheers

--- 2016-05-24 intro.tex
@@
 This particular ``encrypted Bloom filter'' instantiation was suggested for use in efficient linking of records across separate medical record databases~\cite{xxx}.
-(It was subsequently shown not to be secure by Niedermeier et al.~\cite{xxx}, where a clever use of frequency analysis recovered the last names of patients given access only to the Bloom filter array.)  In any case, it is clear that the NY definition does not capture the most widely used applications of Bloom filters, e.g.
+(It was subsequently shown not to be secure by Niedermeier et al.~\cite{xxx}, where a clever use of frequency analysis recovered the last names of patients given access only to the Bloom filter array.\tsnote{This shows that false-positive security and privacy (whatever it is) are orthogonal, since I'm pretty sure this ``encrypted'' bloom filter resists FPs.})  In any case, it is clear that the NY definition does not capture the most widely used applications of Bloom filters, e.g.
 CDN summary caches, P2P network routing algorithms, etc.
@@
 \heading{Related work. }
-
-\tsnote{Stopped here.}
+Mitzenmacher and Vadhan.
 

### 2016-05-30 syntax.tex
cheers

@@
 NY give it in the private hash setting (sort of); but, intuitively, it should be hard to find false-positives even if you know that MD5 or SHA-x are the hash functions  It might be interesting to run some experiments, e.g.
-set up a bloom filter of URLs or IP/port information, and then open up a network tap and see how many false positives we observe.}
+set up a bloom filter of URLs or IP/port information, and then open up a network tap and see how many false positives we observe.} \tsnote{Actually, I think Mitzenmacher and Vadhan address this (somewhat) in their paper about using hash functions in practice.}
 

### 2016-05-31 syntax.tex
hacking syntax

--- 2016-05-30 syntax.tex
@@
 \newcommand{\ExpCorrect}[2]{\mathrm{Exp}^{\mathrm{cor}}_{#1}(#2)}
+
+\newcommand{\ExpFPSecHash}[2]{\mathrm{Exp}^{\mathrm{fp\mbox{-}prv}}_{#1}(#2)}
+\newcommand{\ExpFPPubHash}[2]{\mathrm{Exp}^{\mathrm{fp\mbox{-}pub}}_{#1}(#2)}
+\newcommand{\ExpFP}[2]{\mathrm{Exp}^{\mathrm{fp}}_{#1}(#2)}
 
@@
 
-\heading{Soundness of hash-based filters.} \tsnote{To do.
+\heading{FP-security of hash-based filters.} \tsnote{Write text.
 Note that it makes sense to consider soundness both in the public and private hash setting.
@@
 set up a bloom filter of URLs or IP/port information, and then open up a network tap and see how many false positives we observe.}
+
+\begin{figure}
+\centering
+\fpage{.6}{
+\hpagess{.6}{.35}
+{
+\experimentv{$\ExpFPSecHash{S,B}{A}$}\\
+$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
+$M \gets \Init^{\HashOracle}(S)$\\
+$x \getsr A^{\QryOracle}(S)$\\
+if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
+\nudge Ret 1\\
+Ret 0\\
+
+\medskip
+\experimentv{$\ExpFPPubHash{S,B}{A}$}\\
+$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
+$M \gets \Init^{\HashOracle}(S)$\\
+$x \getsr A^{\QryOracle,\HashOracle}(S)$\\
+if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
+\nudge Ret 1\\
+Ret 0
+}
+%
+{
+\oracle{$\QryOracle(x)$}\\
+if $M = \bot$ then Ret $\bot$\\
+Ret $\Qry^{\HashOracle}(M,x)$\\
+
+\medskip
+\oracle{$\HashOracle(i,x)$}\\
+Ret $h_i(x)$\\
+}
+}
+\caption{False-positive security (soundness) for an $(n,k,m)$-filter~$B$.  {\bf Top:} when the hash functions are private.  {\bf Bottom:} when the hash functions are public.}
+\label{fig:fp-filter}
+\end{figure}
+
+\heading{Privacy of hash-based filters.} \tsnote{To-do.}
 
@@
 
-\heading{Soundness for mutable hash-based filters. } \tsnote{To do.  Same comments as for the simple case, only it's more complicated here what it means to violate soundness.}
+\heading{Soundness for mutable hash-based filters.
+} \tsnote{To do.
+Same comments as for the simple case, only it's more complicated here because I have no idea what soundness even means in this setting.
+Might generically specify two tests as part of the syntax, one for correctness and one for soundness?}
+
+\heading{Privacy of hash-based filters.} \tsnote{To-do.}
 

### 2016-05-31 filters.tex
restructuring files

--- 2016-05-31 syntax.tex
@@
-\newcommand{\Rep}{\mathsc{Rep}}
-\newcommand{\Hash}{\mathsc{Hash}}
-\newcommand{\Qry}{\mathsc{Qry}}
-\newcommand{\Update}{\mathsc{Up}}
-\newcommand{\Init}{\mathsc{Init}}
-\newcommand{\Test}{\mathsc{Test}}
-\newcommand{\multiset}[1]{\mathbb{M}_{#1}}
-\newcommand{\ExpCorrectSecHash}[2]{\mathrm{Exp}^{\mathrm{cor\mbox{-}prv}}_{#1}(#2)}
-\newcommand{\ExpCorrectPubHash}[2]{\mathrm{Exp}^{\mathrm{cor\mbox{-}pub}}_{#1}(#2)}
-\newcommand{\ExpCorrect}[2]{\mathrm{Exp}^{\mathrm{cor}}_{#1}(#2)}
-
-\newcommand{\ExpFPSecHash}[2]{\mathrm{Exp}^{\mathrm{fp\mbox{-}prv}}_{#1}(#2)}
-\newcommand{\ExpFPPubHash}[2]{\mathrm{Exp}^{\mathrm{fp\mbox{-}pub}}_{#1}(#2)}
-\newcommand{\ExpFP}[2]{\mathrm{Exp}^{\mathrm{fp}}_{#1}(#2)}
-
-\newcommand{\QryOracle}{\mathsf{Query}}
-\newcommand{\UpdateOracle}{\mathsf{Update}}
-\newcommand{\HashOracle}{\mathsf{Hash}}
-
 \section{Hash-based Filters}
@@
 \heading{Privacy of hash-based filters.} \tsnote{To-do.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Mutuable hash-based filters}
-Here we extend the basic Bloom filter syntax to allow for variations on the traditional Bloom filter, e.g.
-counting Bloom filters~\cite{xxx}, spectral Bloom filters~\cite{xxx}, count-min sketches~\cite{xxx}, stable Bloom filters~\cite{xxx}, etc.
-Before giving it, let us briefly describe what is formalized.
-Our syntax captures settings in which there is some (potentially empty) initial set~$S$, whose representation~$M$ may undergo updates over time.
-Effectively, this allows for expansion of~$S$ to a larger set, or even a multiset, as new elements ``arrive''.
-The update algorithm is responsible for altering the current representation.
-We allow it to take in a string that encodes inputs needed to carry out the updating.
-For example, counting Bloom filters may receive update strings that encode $(x,c)$ where $x \in U$ is the element whose representation should be incremented, and $c \in \mathbb{N}$ is the amount of the increment.
-Network applications, such as looking for heavy-hitters across TCP/IP streams seen by a router, may have $x = (\mathrm{IP_{src}},\mathrm{IP_{dst}})$, the source and destintation address of a packet, and~$c$ the number of bytes in the packet payload.
-When necessary we will specify what is encoded in the update string, but will assume some implicit and fixed encoding scheme.
-Note that our syntax allows for randomized updating.
-This accommodates stable Bloom filters, for example, which has a randomized ``forgetting'' feature as part of its update.
-
-\heading{Syntax. }
-Fix nonempty sets $U,\Sigma$ and integers $k,m_1,m_2,n>0$ with $m_1 \leq m_2$.
-Fix a symbol $\bot \not\in U$.
-An $(n,k,[m_1,m_2])$-filter (over universe~$U$) is a tuple  $B=(\Hash,\Init,\Qry,\Update, \Test)$.
-%
-The randomized \emph{hash-sampling} algorithm~$\Hash$ samples a size~$k$ family of functions~$\mathcal{H}=\{h_1,h_2,\ldots,h_k\}$ where each $h_i \in  \mathrm{Func}(U,\{0,1,\ldots,m_2-1\})$.
-We write $\mathcal{H} \getsr \Hash$ for this operation.
-%
-The deterministic \emph{initial-representation} algorithm $\Init\colon \multiset{U,n} \rightarrow \left(\bigcup_{m=m_1}^{m_2}\Sigma^m\right)$ takes a multiset~$S$ of size~$n$ as input, and outputs representation~$M$ of length~$m_1 \leq m \leq m_2$.
-%
-The determinisitc query algorithm $\Qry\colon \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right)\times U \rightarrow \bits^*$ takes a representation $M$ and an element $x \in U$ and returns a bitstring.  
-%
-The randomized \emph{update} algorithm $\Update\colon \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right)\times \bits^* \rightarrow \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right) \cup \{\bot\}$ takes a representation and an update string, and returns an updated representation or the distinguished symbol~$\bot$.
-%
-The deterministic \emph{test} algorithm $\Test \colon \multiset{U}\times \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right)\cup\{\bot\} \times U \rightarrow \bits$ takes a multiset~$S$, a representation~$M$ and an element~$x \in U$ and returns a bit.
-%
-%We assume that all $\Init,\Qry,\Update,\Test$ all have blackbox access to the functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$, which we denote by writing~$\mathcal{H}$ as a superscript.
-
-\heading{Correctness.
-} The kind of filters we capture, here, can have \emph{two-sided} error.
-That is, they may result in false-negatives as well as false-positives.
-We captures two versions of correctness in Figure~\ref{fig:correctness-mutable}, corresponding to whether or not the adversary is given access to the hash functions used to create and update the multiset representation.
-
-\begin{figure}
-\centering
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpCorrectSecHash{S,B}{A}$}\\
-$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-$M \gets \Init^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle,\UpdateOracle}(S)$\\
-if $\Test^{\HashOracle}(S,M,x) \neq 1$ then Ret 1\\
-Ret 0\\
-
-\medskip
-\experimentv{$\ExpCorrectPubHash{S,B}{A}$}\\
-$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-$M \gets \Init^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle,\UpdateOracle,\HashOracle}(S)$\\
-if $\Test^{\HashOracle}(S,M,x) \neq 1$ then Ret 1\\
-Ret 0
-}
-%
-{
-\oracle{$\QryOracle(x)$}\\
-if $M = \bot$ then Ret $\bot$\\
-Ret $\Qry^{\HashOracle}(M,x)$\\
-
-\medskip
-\oracle{$\UpdateOracle(\sigma)$}\\
-if $M = \bot$ then Ret $\bot$ \\
-$S \gets S \uplus \{\sigma\}$\\
-$M \getsr \Update^{\HashOracle}(M,\sigma)$\\
-
-\medskip
-\oracle{$\HashOracle(i,x)$}\\
-Ret $h_i(x)$\\
-}
-}
-\caption{Trying to define correctness for an $(n,k,[m_1,m_2])$-filter~$B$.}
-\label{fig:correctness-mutable}
-\end{figure}
-
-\heading{Soundness for mutable hash-based filters.
-} \tsnote{To do.
-Same comments as for the simple case, only it's more complicated here because I have no idea what soundness even means in this setting.
-Might generically specify two tests as part of the syntax, one for correctness and one for soundness?}
-
-\heading{Privacy of hash-based filters.} \tsnote{To-do.}
-
-\if{0}
-\heading{Multiset-oriented hash-based filters. }
-\tsnote{Commented out, but in the source: an alternative way to formalize mutable hash-based filters.
-This way directly address the inputs as multisets, instead of starting with a set and then updating the represenation a step at a time.
-Not sure which is cleaner and more easily applied to real problems, yet.}
-
-Let $\mathbb{M}_\mathcal{U}$ be the set of multisets over~$\mathcal{U}$.
-We can denote any multiset as $\{(x,\ell) \,|\, x \in \mathcal{U}, \ell \in \mathbb{N}\}$, and for a particular multiset~$S$ we define the multiplicity of~$x$ as $\mu_S(x) = \ell$ where $(x,\ell)\in S$.
-
-An $(n,k,[m_1,m_2])$-filter with operations is a tuple  $B=(\Hash,\Rep,\Qry, \mathcal{F})$.  
-The set $\mathcal{F}$ is the finite collection of allowable operations.  All operations are of the form 
-$f: \mathbb{M}_{\mathcal{U}} \times \mathbb{M}_{\mathcal{U}} \rightarrow \mathbb{M}_{\mathcal{U}} \cup \{\bot\}$.  
-%
-The deterministic representation algorithm $\Rep\colon \mathbb{M}_\mathcal{U} \rightarrow \bigcup_{m=m_1}^{m_2}\Sigma^m$ takes a multiset~$S$, and outputs representation~$M$ of length~$m_1 \leq m \leq m_2$, or the distinguished symbol~$\bot$.
-We assume that if the multiset~$S=\{(x_1,\ell_1),(x_2,\ell_2),\ldots,(x_t,\ell_t)\}$ is such that $n < \sum_{i=1}^t \ell_i$ then $\Rep(S)=\bot$.
-%
-The randomized hash-sampling algorithm~$\Hash$ is as before.
-%
-The determinisitic query algorithm $\Qry$... \tsnote{Not sure how to define this!  See my comment, below...}
-
-%Correctness is defined as follows.
-Let $S,T$ be arbitrary multisets and let~$f$ be an arbitrary operation in $\mathcal{F}$.
-If $f(S,T) = S'\neq \bot$, then for all $x \in S'$ we demand that $\Qry(\Rep(S'),x)=1$.
-\tsnote{might need a stronger condition that this holds for any sequence of operations that do not result in $\bot$.}
-
-Let us see how this syntax captures various kinds of Bloom filters.
-First, let $\Sigma = \mathbb{N}$ and define $f_{\mathrm{add}}(S,T)=\{(x,\mu_S(x)+\mu_T(x)) \,|\, x \in \mathcal{U}\}$ and $f_\mathrm{del}(S,T) = \{(x,\min\{0,\mu_S(x)-\mu_T(x)\}) \,|\, x \in \mathcal{U} \}$.
-Define $\Rep(S')$ as follows: for each $(x,\ell)\in S'$ and $j\in\{1,2,\ldots,k\}$, set $M[h_j(x)]=\ell$.
-Finally, define $\Qry(M,x) = 1 \Leftrightarrow \forall j \in \{1,2,\ldots,k\},\; M[h_j(x)] > 0$.
-This allows us to capture counting Bloom filters.
-\tsnote{Does it?
-Acutally, you might want $\Qry(M,x)$ to return a number, i.e., a counter value.
-How do you define correctness then?}
-
-\tsnote{There are more direct ways to formalize counting Bloom filters, like the syntax above.
-But this less direct way will allow us to capture other kinds ``advanced'' Bloom filters proposed in the literature or (more importantly) used in practice.
-For example, $f_{\mathrm{setify}}(S,T)=\{(x,1) \,|\, x \in \mathcal{U} \mbox{s.t.
-} \mu_S(x)>0, \mu_T(x)>0\}$.
-On the other hand, we may end up deciding it is overkill...
-}
-\fi

### 2016-05-31 mutable-filters.tex
restructuring files

--- 2016-05-30 syntax.tex
@@
-\newcommand{\Rep}{\mathsc{Rep}}
-\newcommand{\Hash}{\mathsc{Hash}}
-\newcommand{\Qry}{\mathsc{Qry}}
-\newcommand{\Update}{\mathsc{Up}}
-\newcommand{\Init}{\mathsc{Init}}
-\newcommand{\Test}{\mathsc{Test}}
-\newcommand{\multiset}[1]{\mathbb{M}_{#1}}
-\newcommand{\ExpCorrectSecHash}[2]{\mathrm{Exp}^{\mathrm{cor\mbox{-}prv}}_{#1}(#2)}
-\newcommand{\ExpCorrectPubHash}[2]{\mathrm{Exp}^{\mathrm{cor\mbox{-}pub}}_{#1}(#2)}
-\newcommand{\ExpCorrect}[2]{\mathrm{Exp}^{\mathrm{cor}}_{#1}(#2)}
-
-\newcommand{\QryOracle}{\mathsf{Query}}
-\newcommand{\UpdateOracle}{\mathsf{Update}}
-\newcommand{\HashOracle}{\mathsf{Hash}}
-
-\section{Hash-based Filters}
-\heading{Preliminaries.}
-When~$U$ is a set and $n>0$ is an integer, we let $[U]^n$ denote the set of all size-$n$ subsets of~$U$.
-We let $\multiset{U}$ denote the set of all finite multisets of~$U$.
-We can denote any multiset~$S$ as $\{(x,\ell) \,|\, x \in U, \ell > 0\}$ where each~$x$ appears exactly once, and each~$\ell$ is an integer.
-We define the multiplicity of~$x$ as $\mu_S(x) = \ell$.
-We write $|S|= \sum_{(x,\ell)\in S}\mu_S(x)$, and let $\multiset{U,n}$ denote the set of multisets~$S$ where $|S|=n$.
-
-We write $x \getsr U$ to denote sampling an element from~$U$ and assigning this to~$x$, and we extend this notation to randomized algorithms.
-
-\heading{Syntax.}
-Fix a nonempty sets $U,\Sigma$ and integers $k,m,n>0$.  Fix a symbol $\bot \not\in U$.  An $(n,k,m)$-filter (over universe~$U$) is a tuple  $B=(\Hash,\Rep,\Qry)$.   
-%
-The randomized \emph{hash-sampling} algorithm~$\Hash$ samples a size~$k$ family of functions~$\mathcal{H}=\{h_1,h_2,\ldots,h_k\}$ where each $h_i \in  \mathrm{Func}(U,\{0,1,\ldots,m-1\})$.
-We write $\mathcal{H} \getsr \Hash$ for this operation.
-%
-The deterministic representation algorithm $\Rep\colon [U]^n \rightarrow \Sigma^m$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m$.
-%
-The determinisitc query algorithm $\Qry\colon \Sigma^m \times U \rightarrow \bits$ takes a representation $M$ and an element $x \in U$ and returns a bit.  
-%
-We assume that both $\Rep$ and $\Qry$ have the following blackbox access to the functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$.
-%which we denote by writing~$\mathcal{H}$ as a superscript.   
-%Thus, we write $M \gets \Rep^{\mathcal{H}}(S)$ and $b \gets \Qry^{\mathcal{H}}(M,x)$ for the execution of the representation and query algorithms, respectively.
-%
-%We write $M \gets \Rep(S)$ and $b \gets \Qry(M,x)$ for the execution of the representation and query algorithms, respectively.
-For correctness, we demand that for all~$S$ of size~$n$, we have that for all $x \in S, \Prob{\Qry(\Rep(S),x)=1}=1$, where the probability is over the coins of $\Hash$.
-
-%\heading{Discusssion.}
-This syntax captures classical Bloom filters by setting~$\Sigma=\bits$,  and defining $\Rep,\Qry$ in the obvious way.
-Setting $\Sigma=\bits^{\leq L}$ allows one to store a bitstring of length at most~$L$ at each location.
-\tsnote{Would let us capture a construction from NY, among other things.}  We note that even though this would allow for the storage of counters (say) at each filter location, our restriction that~$\Qry$ returns a bit does not capture functionality typically demanded of Bloom filters that employ counters, e.g., returning a counter value.
-(One could, however, have $\Qry$ compute an arbitrary, fixed predicate.
-For example, ``has~$x$ been seen at least 5 times?''.)
-Our syntax also does not capture filters that are mutable, that is, whose representation may change over time. 
-On the other hand, we can state a simple correctness condition for these kinds of filters; this will not be true when we further generalize to capture, properly, counters and mutability.
-
-\heading{Soundness of hash-based filters.} \tsnote{To do.
-Note that it makes sense to consider soundness both in the public and private hash setting.
-NY give it in the private hash setting (sort of); but, intuitively, it should be hard to find false-positives even if you know that MD5 or SHA-x are the hash functions  It might be interesting to run some experiments, e.g.
-set up a bloom filter of URLs or IP/port information, and then open up a network tap and see how many false positives we observe.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Mutuable hash-based filters}

### 2016-05-31 filters.tex
changes to candidate security notions

@@
 
-\heading{FP-security of hash-based filters.} \tsnote{Write text.
-Note that it makes sense to consider soundness both in the public and private hash setting.
-NY give it in the private hash setting (sort of); but, intuitively, it should be hard to find false-positives even if you know that MD5 or SHA-x are the hash functions  It might be interesting to run some experiments, e.g.
-set up a bloom filter of URLs or IP/port information, and then open up a network tap and see how many false positives we observe.}
+\heading{FP-security of hash-based filters.} \tsnote{NY give it in the private hash setting (sort of); but, intuitively, it should be hard to find false-positives even if you know that MD5 or SHA-x are the hash functions.
+Not totally sure how to capture this intuition nicely.}
 
@@
 \nudge Ret 1\\
-Ret 0\\
+Ret 0
+}
+%
+{
+\oracle{$\QryOracle(x)$}\\
+Ret $\Qry^{\HashOracle}(M,x)$\\
 
 \medskip
-\experimentv{$\ExpFPPubHash{S,B}{A}$}\\
+\oracle{$\HashOracle(i,x)$}\\
+Ret $h_i(x)$\\
+}
+}
+%%%%%%%
+\fpage{.6}{
+\hpagess{.6}{.35}
+{
+\experimentv{$\ExpFPPubHashBB{S,B}{A}$}\\
 $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
@@
 \oracle{$\QryOracle(x)$}\\
-if $M = \bot$ then Ret $\bot$\\
 Ret $\Qry^{\HashOracle}(M,x)$\\
@@
 }
-\caption{False-positive security (soundness) for an $(n,k,m)$-filter~$B$.  {\bf Top:} when the hash functions are private.  {\bf Bottom:} when the hash functions are public.}
+%%%%%%%
+\fpage{.6}{
+\hpagess{.6}{.35}
+{
+\experimentv{$\ExpFPPubHash{S,B}{A}$}\\
+$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
+$M \gets \Init^{\HashOracle}(S)$\\
+$x \getsr A^{\QryOracle}(S,\{h_1,h_2,\ldots,h_k\})$\\
+if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
+\nudge Ret 1\\
+Ret 0
+}
+%
+{
+\oracle{$\QryOracle(x)$}\\
+Ret $\Qry^{\HashOracle}(M,x)$\\
+
+\medskip
+\oracle{$\HashOracle(i,x)$}\\
+Ret $h_i(x)$\\
+}
+}
+\caption{False-positive security (soundness) for an $(n,k,m)$-filter~$B$ with private hash functions (top); black-box queriable hash functions (middle), and public hash functions (bottom). }
 \label{fig:fp-filter}
@@
 
-\heading{Privacy of hash-based filters.} \tsnote{To-do.}
+\tsnote{It might be interesting to run some experiments, e.g.
+set up a bloom filter of URLs or IP/port information, and then open up a network tap and see how many false positives we observe.
+I quite like the idea of empirically supported/driven crypto.}
+
+\heading{Privacy of hash-based filters.} \tsnote{This is wide open.  Privacy of~$S$?  Privacy of~$M$?  (The latter may or may not imply the former, depending on how we define things.)  }
+
+\begin{figure}
+\centering
+\fpage{.6}{
+\hpagess{.6}{.35}
+{
+\experimentv{$\ExpPrivSecHash{S,B}{A}$}\\
+$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
+$M \gets \Init^{\HashOracle}(S)$\\
+$x \getsr A^{\QryOracle}()$\\
+if $x\in S$ then Ret 1\\
+Ret 0\\
+
+\medskip
+\experimentv{$\ExpPrivPubHash{S,B}{A}$}\\
+$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
+$M \gets \Init^{\HashOracle}(S)$\\
+$x \getsr A^{\QryOracle}(\{h_1,h_2,\ldots,h_k\})$\\
+if $x\in S$ then Ret 1\\
+Ret 0\\
+}
+%
+{
+\oracle{$\QryOracle(x)$}\\
+Ret $\Qry^{\HashOracle}(M,x)$\\
+
+\medskip
+\oracle{$\HashOracle(i,x)$}\\
+Ret $h_i(x)$\\
+}
+}
+\caption{Set-privacy for an $(n,k,m)$-filter~$B$ for private (top) and public (bottom) hash functions. \textcolor{cyan}{Revisit when the FP notion settles out.}}
+\label{fig:fp-filter}
+\end{figure}

### 2016-05-31 filters.tex
notions

@@
 }
-\caption{False-positive security (soundness) for an $(n,k,m)$-filter~$B$ with private hash functions (top); black-box queriable hash functions (middle), and public hash functions (bottom). }
+\caption{False-positive security (soundness) for an $(n,k,m)$-filter~$B$ with private hash functions (top), black-box queriable hash functions (middle), and public hash functions (bottom). }
 \label{fig:fp-filter}
@@
 if $x\in S$ then Ret 1\\
-Ret 0\\
+Ret 0
+}
+%
+{
+\oracle{$\QryOracle(x)$}\\
+Ret $\Qry^{\HashOracle}(M,x)$\\
 
 \medskip
+\oracle{$\HashOracle(i,x)$}\\
+Ret $h_i(x)$\\
+}
+}
+%%%%%%%%%%
+\fpage{.6}{
+\hpagess{.6}{.35}
+{
+\experimentv{$\ExpPrivPubHashBB{S,B}{A}$}\\
+$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
+$M \gets \Init^{\HashOracle}(S)$\\
+$x \getsr A^{\QryOracle,\HashOracle}()$\\
+if $x\in S$ then Ret 1\\
+Ret 0\\
+}
+%
+{
+\oracle{$\QryOracle(x)$}\\
+Ret $\Qry^{\HashOracle}(M,x)$\\
+
+\medskip
+\oracle{$\HashOracle(i,x)$}\\
+Ret $h_i(x)$\\
+}
+}
+%%%%%%%
+\fpage{.6}{
+\hpagess{.6}{.35}
+{
 \experimentv{$\ExpPrivPubHash{S,B}{A}$}\\
@@
 }
-\caption{Set-privacy for an $(n,k,m)$-filter~$B$ for private (top) and public (bottom) hash functions. \textcolor{cyan}{Revisit when the FP notion settles out.}}
+\caption{Set-privacy for an $(n,k,m)$-filter~$B$ for private (top), black-box queriable (middle),  and public (bottom) hash functions. \textcolor{cyan}{Revisit when the FP notion settles out.}}
 \label{fig:fp-filter}

### 2016-05-31 filters.tex
intro updates

@@
 
-\heading{Privacy of hash-based filters.} \tsnote{This is wide open.  Privacy of~$S$?  Privacy of~$M$?  (The latter may or may not imply the former, depending on how we define things.)  }
+\heading{Privacy of hash-based filters.} \tsnote{This is wide open.
+Privacy of~$S$?
+Privacy of~$M$?
+(The latter may or may not imply the former, depending on how we define things.)  Under what assumptions on~$S$ --~min-entropy, computational unguessability, other?
+Do we want to allow for explicit side information/precomputation?
+We want something that captures realistic scenarios.}
 

### 2016-05-31 intro.tex
hacking syntax
intro updates

@@
 Given these shortcomings and the prevalent use of Bloom filters in practice, we revisit the matter of formalizing them as primitives with explicit security goals, these goals being abstracted from the attack surface they expose in practice.
-We begin by giving a new syntax for an approximate-set-membership primitive (ASM) that clearly captures Bloom filters...
-\tsnote{finish}
+We begin by giving a new syntax for hash-based filters, which more clearly captures Bloom filters...
 
-We provided various security notions for ASMs...
+We generalize this syntax to hash-based filters that are mutable, in the sense that they allow for updating of the representation.
+This allows us to capture counting Bloom filters, spectral Bloom filters, stable Bloom filters, count-min sketches, and other compact set respresentation data structures...
+
+We provide various security notions for these primitives...
 FP with private, public representation coins; set privacy with private, public representation coins; FP/set privacy in the multi-representation setting (outsider attack, think CDNs); FP/set privacy in the multi-representation setting with corruptions (insider attack, think P2P networks) \tsnote{Those are just the ones that come to mind now.
 Could also consider authenicity of representations, think CDN or P2P settings.}
-
-Later, we give syntax for ASM primitives that also admit operations upon the set representation.
-This captures so-called counting Bloom filters that are used, for example, in fairness-enforcing algorithms for routing of TCP streams.
-It also captures...
 
@@
 \heading{Related work. }
-Mitzenmacher and Vadhan.
+Niedermayer et al., breaking privacy of secret-hash-function Bloom filters.
+Mitzenmacher and Vadhan.\tsnote{Might only be tangential.}
 

### 2016-05-31 intro.tex
intro updates

@@
 This particular ``encrypted Bloom filter'' instantiation was suggested for use in efficient linking of records across separate medical record databases~\cite{xxx}.
-(It was subsequently shown not to be secure by Niedermeier et al.~\cite{xxx}, where a clever use of frequency analysis recovered the last names of patients given access only to the Bloom filter array.\tsnote{This shows that false-positive security and privacy (whatever it is) are orthogonal, since I'm pretty sure this ``encrypted'' bloom filter resists FPs.})  In any case, it is clear that the NY definition does not capture the most widely used applications of Bloom filters, e.g.
+(It was subsequently shown not to be secure by Niedermeier et al.~\cite{xxx}, where a clever use of frequency analysis recovered the last names of patients given access only to the Bloom filter array.\tsnote{This shows that false-positive security and privacy (whatever it is) are orthogonal, since I'm pretty sure this ``encrypted'' bloom filter resists FPs.
+Proving this is a good task for a student.})  In any case, it is clear that the NY definition does not capture the most widely used applications of Bloom filters, e.g.
 CDN summary caches, P2P network routing algorithms, etc.

### 2016-05-31 filters.tex
intro updates

@@
 When~$U$ is a set and $n>0$ is an integer, we let $[U]^n$ denote the set of all size-$n$ subsets of~$U$.  
-We let $\multiset{U}$ denote the set of all finite multisets of~$U$.
-We can denote any multiset~$S$ as $\{(x,\ell) \,|\, x \in U, \ell > 0\}$ where each~$x$ appears exactly once, and each~$\ell$ is an integer.
-We define the multiplicity of~$x$ as $\mu_S(x) = \ell$.
-We write $|S|= \sum_{(x,\ell)\in S}\mu_S(x)$, and let $\multiset{U,n}$ denote the set of multisets~$S$ where $|S|=n$.
-
 We write $x \getsr U$ to denote sampling an element from~$U$ and assigning this to~$x$, and we extend this notation to randomized algorithms.

### 2016-05-31 mutable-filters.tex
changes to candidate security notions
intro updates

@@
 This accommodates stable Bloom filters, for example, which has a randomized ``forgetting'' feature as part of its update.
+
+\heading{Preliminaries.}
+When~$U$ is a set, we let $\multiset{U}$ denote the set of all finite multisets of~$U$.
+We can denote any multiset~$S$ as $\{(x,\ell) \,|\, x \in U, \ell > 0\}$ where each~$x$ appears exactly once, and each~$\ell$ is an integer.
+We define the multiplicity of~$x$ as $\mu_S(x) = \ell$.
+We write $|S|= \sum_{(x,\ell)\in S}\mu_S(x)$, and let $\multiset{U,n}$ denote the set of multisets~$S$ where $|S|=n$.
+The notation $S \uplus \{x\}$ denotes multiset union.
 
@@
 if $\Test^{\HashOracle}(S,M,x) \neq 1$ then Ret 1\\
-Ret 0\\
+Ret 0
+}
+%
+{
+\oracle{$\QryOracle(x)$}\\
+if $M = \bot$ then Ret $\bot$\\
+Ret $\Qry^{\HashOracle}(M,x)$\\
 
 \medskip
-\experimentv{$\ExpCorrectPubHash{S,B}{A}$}\\
+\oracle{$\UpdateOracle(\sigma)$}\\
+if $M = \bot$ then Ret $\bot$ \\
+$S \gets S \uplus \{\sigma\}$\\
+$M \getsr \Update^{\HashOracle}(M,\sigma)$\\
+
+\medskip
+\oracle{$\HashOracle(i,x)$}\\
+Ret $h_i(x)$\\
+}
+}
+%%%%%%%%%%
+\fpage{.6}{
+\hpagess{.6}{.35}
+{
+\experimentv{$\ExpCorrectPubHashBB{S,B}{A}$}\\
 $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
@@
 }
-\caption{Trying to define correctness for an $(n,k,[m_1,m_2])$-filter~$B$.}
+%%%%%%%%%%%
+\fpage{.6}{
+\hpagess{.6}{.35}
+{
+\experimentv{$\ExpCorrectPubHash{S,B}{A}$}\\
+$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
+$M \gets \Init^{\HashOracle}(S)$\\
+$x \getsr A^{\QryOracle,\UpdateOracle}(S,\{h_1,h_2,\ldots,h_k\})$\\
+if $\Test^{\HashOracle}(S,M,x) \neq 1$ then Ret 1\\
+Ret 0
+}
+%
+{
+\oracle{$\QryOracle(x)$}\\
+if $M = \bot$ then Ret $\bot$\\
+Ret $\Qry^{\HashOracle}(M,x)$\\
+
+\medskip
+\oracle{$\UpdateOracle(\sigma)$}\\
+if $M = \bot$ then Ret $\bot$ \\
+$S \gets S \uplus \{\sigma\}$\\
+$M \getsr \Update^{\HashOracle}(M,\sigma)$\\
+
+\medskip
+\oracle{$\HashOracle(i,x)$}\\
+Ret $h_i(x)$\\
+}
+}
+\caption{Trying to define correctness for an $(n,k,[m_1,m_2])$-filter~$B$.  \textcolor{cyan}{Revisit once picture for ``plain'' filters settles.}}
 \label{fig:correctness-mutable}

### 2016-06-02 tasks_and_ideas.tex
added tasks and ideas section

\section{Tasks, and Ideas for Tasks}

\begin{itemize}
\item Prove that a Bloom filter using hash functions defined by $h_j(x) = \left( f_{K0}(x) + j\cdot g_{K1}(x)\right) \bmod m$, for secret keys $K0,K1$, is FP-secure when either~$f$ or~$g$ is a secure PRF.  (This is a real proposal, see the intro.)  Interesting that these $h_j$ are not independent, even if $f_{K0},g_{K1}$ are replaced by independent random functions, whereas the traditional BF false positive analysis treats the $h_j$ as independent.  I wonder if the analysis for determining the number of hash functions still holds when the $h_j$ are dependent?  Note: definitely not in general, just consider $h_j$ a fixed function for all $j$; but it's an interesting question to ask for this particular kind of dependence.  (Should check the Kirsh, Mitzenmacher paper first; they probably address this.)

\item Show the same thing for the simpler $h_j(x) = f_{K}(\langle j \rangle \concat x) \bmod m$.  This, by the way, does give independent $h_j$ when you replace~$f_k$ by a random function.

\item Break a Squid server!  I'm thinking about a privacy break here.  One could start by simulating the (very simple) Bloom filter that Squid implements, and eventually stand up an actual Squid proxy.  Perhaps populate the filter with a random sampling of URLs from the Alexa top 1000.  (How large a sample?)  Given access to the filter, we can probably use the same attacks leveraged by Niedermayer et al.\ to infer information about which URLs are cached.  Of course, there's a timing based attack, just pinging the Squid proxy with URLs.   But this is probably harder than it sounds, and I don't know if/how Squid updates its filter on false-positive/cache misses.

\item Fix a Squid server!  Implement a fix that is *fast* and doesn't suffer from deployment headaches at interesting scales.  If the attack is bad enough, and the fix is efficient enough, we might even get this pushed into the Squid codebase.

\item Find measurement info on false positive rates for Squid filters/HTTP proxies in practice.  This must have been done already.

\item Considering the P2P setting, how should we formalize insider attacks?  I'm thinking something like FP and privacy with corruptions.  What about authenticity of published Bloom filters?

\item What about content-based routing (or whatever they are calling that area now)?  A Bloom filter seems like an obvious tool for that setting, and the content-seeker might want to keep its preferences private.

\item Formalize a security goal for Stochastic Fair Blue (or similar TCP stream routing primitives) and prove that a secure, mutable hash-based filter implies secure Stochastic Fair Blue.

\item Do the same for other applications of Bloom-filter-like primitives.  (For example, attenuated Bloom filters, used in the OceanStore project (at least).)

\item Would a secure Bloom filter (of some kind) give us a secure strike list (whatever secure means), like what was originally proposed in QUIC?

\end{itemize}

### 2016-06-02 tasks_and_ideas.tex
added tasks and ideas section
adding tasks

@@
 But this is probably harder than it sounds, and I don't know if/how Squid updates its filter on false-positive/cache misses.
+(Note that, if I recall properly, a Bloom filter leaks the number of elements that it represents, if you know the filter size and the number of hash functions.) (Also, what about set-intersection attacks on Bloom filters?)
 
@@
 
-\item What about content-based routing (or whatever they are calling that area now)?
-A Bloom filter seems like an obvious tool for that setting, and the content-seeker might want to keep its preferences private.
-
 \item Formalize a security goal for Stochastic Fair Blue (or similar TCP stream routing primitives) and prove that a secure, mutable hash-based filter implies secure Stochastic Fair Blue.
@@
 
+\item What about content-based routing (or whatever they are calling that area now)?
+A Bloom filter seems like an obvious tool for that setting, and the content-seeker might want to keep its preferences private.
+
+\item What about Google's BigTable or HBase?  What is the security threat there?
+
 \item Would a secure Bloom filter (of some kind) give us a secure strike list (whatever secure means), like what was originally proposed in QUIC?

### 2016-06-02 tasks_and_ideas.tex
adding tasks

--- 2016-06-02 tasks_and_ideas.tex
@@
 
+\item  If I recall properly, a Bloom filter leaks the number of elements that it represents, if you know the filter size and the number of hash functions.
+Verify this.
+Also, what about set-intersection attacks on Bloom filters?
+
+\item Find measurement info on false positive rates for Squid filters/HTTP proxies in practice.  This must have been done already.
+
 \item Break a Squid server!
@@
 \item Fix a Squid server!
-Implement a fix that is *fast* and doesn't suffer from deployment headaches at interesting scales.
+Implement a fix that is \emph{fast} and doesn't suffer from deployment headaches at interesting scales.
 If the attack is bad enough, and the fix is efficient enough, we might even get this pushed into the Squid codebase.
 
-\item Find measurement info on false positive rates for Squid filters/HTTP proxies in practice.  This must have been done already.
-
 \item Considering the P2P setting, how should we formalize insider attacks?  I'm thinking something like FP and privacy with corruptions.  What about authenticity of published Bloom filters?
-
-\item What about content-based routing (or whatever they are calling that area now)?
-A Bloom filter seems like an obvious tool for that setting, and the content-seeker might want to keep its preferences private.
 
@@
 
+\item What about content-based routing (or whatever they are calling that area now)?
+A Bloom filter seems like an obvious tool for that setting, and the content-seeker might want to keep its preferences private.
+
+\item What about Google's BigTable or HBase?  What is the security threat there?
+
 \item Would a secure Bloom filter (of some kind) give us a secure strike list (whatever secure means), like what was originally proposed in QUIC?
+Are Bloom filters used in edge network servers for big providers like Facebook, LinkedIn, Google, etc.?
+
+\item Generally speaking, can we characterize operational settings in a way that surfaces an interesting security/performance trade-off?
+For example, the Bloom filters used by Akamai's CDN are on the order of 600-700MB in size and are shared among several machines in a local area.
+The Bloom filters used in a simple spam-detection system (do these exist) are likely to be much smaller, maintained locally on a single machine, and much easier to update.
+Solutions in one setting are not going to be useful in another....
 

### 2016-06-02 tasks_and_ideas.tex
adding tasks

@@
 
-\item Show the same thing for the simpler $h_j(x) = f_{K}(\langle j \rangle \concat x) \bmod m$.  This, by the way, does give independent $h_j$ when you replace~$f_k$ by a random function.
+\item Show the same thing for the simpler $h_j(x) = f_{K}(\langle j \rangle \concat x) \bmod m$.
+This, by the way, does give independent $h_j$ when you replace~$f_k$ by a random function.
+(The previous ``double hashing'' construction seems clunky if you're going to assume you have a PRF and secret keys; is this just an example of people in one domain naively using a tool developed for another?
+)
 
@@
 If the attack is bad enough, and the fix is efficient enough, we might even get this pushed into the Squid codebase.
+
+\item Speaking of the Niedermayer et al.
+attacks, these exploit the fact that there are different bloom filters for different record identifiers (i.e.
+one for last name, one for first name, one for city, etc.).
+They propose various way to render their attacks useless, or at least very inefficient.
+Can we actually prove something about one or more of the proposed countermeasures?
 

### 2016-06-02 tasks_and_ideas.tex
adding tasks
tasks

@@
 Note: definitely not in general, just consider $h_j$ a fixed function for all $j$; but it's an interesting question to ask for this particular kind of dependence.
-(Should check the Kirsh, Mitzenmacher paper first; they probably address this.)
+(Should check the Kirsh, Mitzenmacher paper first; they probably address this.
+\tsnote{They show that two random functions, combined in this way (for a prime~$m$), suffices.
+No increase in asymptotic FP probability.
+They also argue that construction of $h_j$ is thus better than one can do using generic pairwise-independent $h_j$.
+They also point out the difference between the FP \emph{probability} (the probability that a particular $x \not\in S$ causes a FP) and the FP \emph{rate} (the average FP probability over $x \not\in S$), which I hadn't really considered before.
+})
 
 \item Show the same thing for the simpler $h_j(x) = f_{K}(\langle j \rangle \concat x) \bmod m$.
-This, by the way, does give independent $h_j$ when you replace~$f_k$ by a random function.
+This, by the way, does give independent $h_j$ when you replace~$f_K$ by a random function.
 (The previous ``double hashing'' construction seems clunky if you're going to assume you have a PRF and secret keys; is this just an example of people in one domain naively using a tool developed for another?
@@
 
+\item This raises the more general question of schemes/protocols that use multiple Bloom filters to represent a single set based on distinct features of set elements.  We should dig into this.
+
 \item Considering the P2P setting, how should we formalize insider attacks?  I'm thinking something like FP and privacy with corruptions.  What about authenticity of published Bloom filters?

### 2016-06-02 intro.tex
intro
adding tasks
adding interesting papers

--- 2016-05-31 intro.tex
@@
 CDN summary caches, P2P network routing algorithms, etc.
-
 \tsnote{Could also point out that their positive results use constructions that have secret keys, and these are unlikely to be of any use in major applications like CDNs or P2P networks.
 But maybe the horse is sufficiently beaten by now...}
+
+%\tsnote{What about content-based routing, or whatever that field is calling itself now?  A Bloom filter seems likely to be used there, and you'd want privacy for at least the content-seeker.}
 
@@
 \heading{Related work. }
-Niedermayer et al., breaking privacy of secret-hash-function Bloom filters.
-Mitzenmacher and Vadhan.\tsnote{Might only be tangential.}
+\begin{itemize}
+\item Niedermayer et al., breaking privacy of secret-hash-function Bloom filters.
+\item Mitzenmacher and Vadhan.\tsnote{Might only be tangential.}
+\item Gerbet, Kumar and Lauradoux, ``The power of evil choices in bloom filters''.  \tsnote{Looks like a real goldmine of related work!}
+\item Nojima and Kadobayashi, ``Cryptographically Secure Bloom Filters''.
+\item Kerschbaum , ``Public-Key Encrypted Bloom Filters with Applications to Supply Chain Integrity''.
+\item S\"{a}rell\"{a} et al. ``BloomCasting: Security in Bloom Filter Based Multicast''.
+\end{itemize}
 

### 2016-06-02 intro.tex
adding related work

@@
 \item Kerschbaum , ``Public-Key Encrypted Bloom Filters with Applications to Supply Chain Integrity''.
-\item S\"{a}rell\"{a} et al. ``BloomCasting: Security in Bloom Filter Based Multicast''.
+\item S\"{a}rell\"{a} et al., ``BloomCasting: Security in Bloom Filter Based Multicast''.
+\item Gao et al., ``Internet Cache Pollution Attacks and Countermeasures''
+\item Dong, Chen, Wen, ``When Private Set Intersection Meets Big Data: An Efficient and Scaleable Protocol'' \tsnote{``garbled bloom filters'' (which actually store the set element by storing~$k$ xor-shares, one at each of the hash indices),``oblivious bloom intersection''}
 \end{itemize}

### 2016-06-03 tasks_and_ideas.tex
adding interesting papers
cheers

@@
 But this is probably harder than it sounds, and I don't know if/how Squid updates its filter on false-positive/cache misses.
+\tsnote{Apparently Crosby and Wallach gives some attacks.} \tsnote{Gerbet et al.
+give some generic attacks that are interesting.
+I wonder if Squid, because it uses MD5, admits faster ``pollution attacks'' on the filter, e.g.
+where the adversary finds URLs that would set far more bits to 1 than one would expect?}
 
@@
 If the attack is bad enough, and the fix is efficient enough, we might even get this pushed into the Squid codebase.
+\tsnote{Not surprisingly, people have addressed this.
+See the related work section in the intro.
+Need to review what's been done, what has proofs, etc.}
 

### 2016-06-03 tasks_and_ideas.tex
cheers
tasks

@@
 I wonder if Squid, because it uses MD5, admits faster ``pollution attacks'' on the filter, e.g.
-where the adversary finds URLs that would set far more bits to 1 than one would expect?}
+where the adversary finds URLs that would set far more bits to 1 than one would expect?
+(Yep, see Crosby and Wallach.)}
 
@@
 Need to review what's been done, what has proofs, etc.}
+
+\item What about breaking, via a real attack that we implement, things like HBase that use non-cryptographic hash functions?
+(HBase apparently uses the Murmur hash.)  If there's a really damaging attack, and a plausible opportunity for someone to mount it, then that would be pretty slashy.
 

### 2016-06-03 filters.tex
adding quick note about defineing FP security under adversarially influenced sets
cheers

@@
 Not totally sure how to capture this intuition nicely.}
+The traditional notion of soundness for a Bloom filter captures the difficulty of finding false-positives when the attacker is non-adaptive.
+Following NY, we consider soundness against adaptive adversaries.
+But we further generalize to allow for settings in which the attacker may have some a priori knowledge about the contents of~$S$.
+(The Niedermaier et al.~\cite{xxx} attacks, for example, exploit knowledge about the distribution of German last names.)   In particular, our notions take as input an explicit distribution $\distr{U}{n}$ over $[U]^n$.
 
+In Figure~\ref{fig:fp-notions} we give three distinct notions, characterized by what access the adversary has to the underlying hash functions used by the filter.
+In the top notion, the hash functions are secret.
+This is the setting addressed by NY, and it capture applications in which the ``hash functions'' are (say) secretly keyed PRFs, and in which no explicit, external interface to these is surfaced.
+%
+The bottom notion considers the case that the full code of the hash functions is known to the attacker.
+This is the case, for example, when attacking the Bloom filters used in the Squid proxy~\cite{xxx}.
+%
+The middle notion is a compromise: it makes the hash functions public, but assumes that the adversary only accesses them in a black-box manner.
+That is, the adversary does not exploit structural features of the hash functions in its attack.
+This notion makes it easy to track the query complexity of an attack.
+
+\begin{figure}
+\centering
+\fpage{.6}{
+\hpagess{.6}{.35}
+{
+\experimentv{$\ExpFPSecHash{B}{\distr{U}{n},A}$}\\
+$S \getsr \distr{U}{n}$\\
+$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
+$M \gets \Init^{\HashOracle}(S)$\\
+$x \getsr A^{\QryOracle}(S)$\\
+if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
+\nudge Ret 1\\
+Ret 0
+}
+%
+{
+\oracle{$\QryOracle(x)$}\\
+Ret $\Qry^{\HashOracle}(M,x)$\\
+
+\medskip
+\oracle{$\HashOracle(i,x)$}\\
+Ret $h_i(x)$\\
+}
+}
+%%%%%%%
+\fpage{.6}{
+\hpagess{.6}{.35}
+{
+\experimentv{$\ExpFPPubHashBB{B}{\distr{U}{n}, A}$}\\
+$S \getsr \distr{U}{n}$\\
+$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
+$M \gets \Init^{\HashOracle}(S)$\\
+$x \getsr A^{\QryOracle,\HashOracle}(S)$\\
+if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
+\nudge Ret 1\\
+Ret 0
+}
+%
+{
+\oracle{$\QryOracle(x)$}\\
+Ret $\Qry^{\HashOracle}(M,x)$\\
+
+\medskip
+\oracle{$\HashOracle(i,x)$}\\
+Ret $h_i(x)$\\
+}
+}
+%%%%%%%
+\fpage{.6}{
+\hpagess{.6}{.35}
+{
+\experimentv{$\ExpFPPubHash{B}{\distr{U}{n}, A}$}\\
+$S \getsr \distr{U}{n}$\\
+$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
+$M \gets \Init^{\HashOracle}(S)$\\
+$x \getsr A^{\QryOracle}(S,\{h_1,h_2,\ldots,h_k\})$\\
+if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
+\nudge Ret 1\\
+Ret 0
+}
+%
+{
+\oracle{$\QryOracle(x)$}\\
+Ret $\Qry^{\HashOracle}(M,x)$\\
+
+\medskip
+\oracle{$\HashOracle(i,x)$}\\
+Ret $h_i(x)$\\
+}
+}
+\caption{False-positive security (soundness) for an $(n,k,m)$-filter~$B$ with private hash functions (top), black-box queriable hash functions (middle), and public hash functions (bottom).  }
+\label{fig:fp-filter}
+\end{figure}
+
+\if{0}
 \begin{figure}
@@
 \end{figure}
+\fi
 

### 2016-06-03 intro.tex
cheers

@@
 \item Mitzenmacher and Vadhan.\tsnote{Might only be tangential.}
-\item Gerbet, Kumar and Lauradoux, ``The power of evil choices in bloom filters''.  \tsnote{Looks like a real goldmine of related work!}
-\item Nojima and Kadobayashi, ``Cryptographically Secure Bloom Filters''.
+\item Gerbet, Kumar and Lauradoux, ``The power of evil choices in bloom filters''.  \tsnote{DSN'15: Looks like a real goldmine of related work!}
+\item Nojima and Kadobayashi, ``Cryptographically Secure Bloom Filters''. \tsnote{Gives some security definitions for privacy. Quick scan, not super clear what they achieve.}
+\item Crosby and Wallach, ``Denial of Service via Algorithmic Complexity Attacks'' \tsnote{Gives attacks on Squid}
 \item Kerschbaum , ``Public-Key Encrypted Bloom Filters with Applications to Supply Chain Integrity''.

### 2016-06-03 filters.tex
updating FP notions to take xplicit distributions for sampling S

@@
 
-In Figure~\ref{fig:fp-notions} we give three distinct notions, characterized by what access the adversary has to the underlying hash functions used by the filter.
+In Figure~\ref{fig:fp-filter} we give three distinct notions, characterized by what access the adversary has to the underlying hash functions used by the filter.
 In the top notion, the hash functions are secret.
@@
 This notion makes it easy to track the query complexity of an attack.
+
+For each experiment, we define an associated advantage notion.  Namely, given an $(n,k,m)$-filter~$B=(\Hash,\Rep,\Qry)$, distribution~$\distr{U}{n}$ and adversary~$A$, we define:
+\begin{align*}
+\AdvFPSecHash{B}{\distr{U}{n},A} &= \Prob{\ExpFPSecHash{B}{\distr{U}{n},A}} \\
+\AdvFPPubHashBB{B}{\distr{U}{n},A} &= \Prob{\ExpFPPubHashBB{B}{\distr{U}{n},A}} \\
+\AdvFPSecHash{B}{\distr{U}{n},A} &= \Prob{\ExpFPPubHash{B}{\distr{U}{n},A}}
+\end{align*}
+The probabilities are over the sampling of the set~$S$ and the hash functions $h_1,h_2,\ldots,h_k$, as well as the coins of the adversary.
+In all experiments, we track time-complexity~$t$ of~$A$, as well as the number of set-membership ($\QryOracle$ oracle) queries~$q_{\mathrm{sm}}$ that it makes.
+In the second, we also track the number of hash-queries $q_{\mathrm{h}}$ that the adversary makes.
 
@@
 
-\if{0}
-\begin{figure}
-\centering
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpFPSecHash{S,B}{A}$}\\
-$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-$M \gets \Init^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle}(S)$\\
-if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
-\nudge Ret 1\\
-Ret 0
-}
-%
-{
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,x)$\\
+%%%%
+% \if{0}
+% \begin{figure}
+% \centering
+% \fpage{.6}{
+% \hpagess{.6}{.35}
+% {
+% \experimentv{$\ExpFPSecHash{S,B}{A}$}\\
+% $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
+% $M \gets \Init^{\HashOracle}(S)$\\
+% $x \getsr A^{\QryOracle}(S)$\\
+% if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
+% \nudge Ret 1\\
+% Ret 0
+% }
+% %
+% {
+% \oracle{$\QryOracle(x)$}\\
+% Ret $\Qry^{\HashOracle}(M,x)$\\
 
-\medskip
-\oracle{$\HashOracle(i,x)$}\\
-Ret $h_i(x)$\\
-}
-}
-%%%%%%%
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpFPPubHashBB{S,B}{A}$}\\
-$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-$M \gets \Init^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle,\HashOracle}(S)$\\
-if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
-\nudge Ret 1\\
-Ret 0
-}
-%
-{
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,x)$\\
+% \medskip
+% \oracle{$\HashOracle(i,x)$}\\
+% Ret $h_i(x)$\\
+% }
+% }
+% %%%%%%%
+% \fpage{.6}{
+% \hpagess{.6}{.35}
+% {
+% \experimentv{$\ExpFPPubHashBB{S,B}{A}$}\\
+% $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
+% $M \gets \Init^{\HashOracle}(S)$\\
+% $x \getsr A^{\QryOracle,\HashOracle}(S)$\\
+% if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
+% \nudge Ret 1\\
+% Ret 0
+% }
+% %
+% {
+% \oracle{$\QryOracle(x)$}\\
+% Ret $\Qry^{\HashOracle}(M,x)$\\
 
-\medskip
-\oracle{$\HashOracle(i,x)$}\\
-Ret $h_i(x)$\\
-}
-}
-%%%%%%%
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpFPPubHash{S,B}{A}$}\\
-$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-$M \gets \Init^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle}(S,\{h_1,h_2,\ldots,h_k\})$\\
-if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
-\nudge Ret 1\\
-Ret 0
-}
-%
-{
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,x)$\\
+% \medskip
+% \oracle{$\HashOracle(i,x)$}\\
+% Ret $h_i(x)$\\
+% }
+% }
+% %%%%%%%
+% \fpage{.6}{
+% \hpagess{.6}{.35}
+% {
+% \experimentv{$\ExpFPPubHash{S,B}{A}$}\\
+% $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
+% $M \gets \Init^{\HashOracle}(S)$\\
+% $x \getsr A^{\QryOracle}(S,\{h_1,h_2,\ldots,h_k\})$\\
+% if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
+% \nudge Ret 1\\
+% Ret 0
+% }
+% %
+% {
+% \oracle{$\QryOracle(x)$}\\
+% Ret $\Qry^{\HashOracle}(M,x)$\\
 
-\medskip
-\oracle{$\HashOracle(i,x)$}\\
-Ret $h_i(x)$\\
-}
-}
-\caption{False-positive security (soundness) for an $(n,k,m)$-filter~$B$ with private hash functions (top), black-box queriable hash functions (middle), and public hash functions (bottom). }
-\label{fig:fp-filter}
-\end{figure}
-\fi
-
-\tsnote{It might be interesting to run some experiments, e.g.
-set up a bloom filter of URLs or IP/port information, and then open up a network tap and see how many false positives we observe.
-I quite like the idea of empirically supported/driven crypto.}
+% \medskip
+% \oracle{$\HashOracle(i,x)$}\\
+% Ret $h_i(x)$\\
+% }
+% }
+% \caption{False-positive security (soundness) for an $(n,k,m)$-filter~$B$ with private hash functions (top), black-box queriable hash functions (middle), and public hash functions (bottom). }
+% \label{fig:fp-filter}
+% \end{figure}
+%\fi
+%%%%%
 
@@
 {
-\experimentv{$\ExpPrivSecHash{S,B}{A}$}\\
+\experimentv{$\ExpPrivSecHash{B}{\distr{U}{n}, A}$}\\
+$S \getsr \distr{U}{n}$\\
 $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
@@
 {
-\experimentv{$\ExpPrivPubHashBB{S,B}{A}$}\\
+\experimentv{$\ExpPrivPubHashBB{B}{\distr{U}{n}, A}$}\\
+$ S \getsr \distr{U}{n}$\\
 $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
@@
 {
-\experimentv{$\ExpPrivPubHash{S,B}{A}$}\\
+\experimentv{$\ExpPrivPubHash{B}{\distr{U}{n}, A}$}\\
+$ S \getsr \distr{U}{n}$\\
 $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\

### 2016-06-03 mutable-filters.tex
cheers

--- 2016-05-31 mutable-filters.tex
@@
 
+\heading{Preliminaries.}
+When~$U$ is a set, we let $\multiset{U}{}$ denote the set of all finite multisets of~$U$.
+We can denote any multiset~$S$ as $\{(x,\ell) \,|\, x \in U, \ell > 0\}$ where each~$x$ appears exactly once, and each~$\ell$ is an integer.
+We define the multiplicity of~$x$ as $\mu_S(x) = \ell$.
+We write $|S|= \sum_{(x,\ell)\in S}\mu_S(x)$, and let $\multiset{U}{n}$ denote the set of multisets~$S$ where $|S|=n$.
+The notation $S \uplus \{x\}$ denotes multiset union.
+
 \heading{Syntax. }
@@
 %
-The deterministic \emph{initial-representation} algorithm $\Init\colon \multiset{U,n} \rightarrow \left(\bigcup_{m=m_1}^{m_2}\Sigma^m\right)$ takes a multiset~$S$ of size~$n$ as input, and outputs representation~$M$ of length~$m_1 \leq m \leq m_2$.
+The deterministic \emph{initial-representation} algorithm $\Init\colon \multiset{U}{n} \rightarrow \left(\bigcup_{m=m_1}^{m_2}\Sigma^m\right)$ takes a multiset~$S$ of size~$n$ as input, and outputs representation~$M$ of length~$m_1 \leq m \leq m_2$.
 %
@@
 %
-The deterministic \emph{test} algorithm $\Test \colon \multiset{U}\times \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right)\cup\{\bot\} \times U \rightarrow \bits$ takes a multiset~$S$, a representation~$M$ and an element~$x \in U$ and returns a bit.
+The deterministic \emph{test} algorithm $\Test \colon \multiset{U}{} \times \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right)\cup\{\bot\} \times U \rightarrow \bits$ takes a multiset~$S$, a representation~$M$ and an element~$x \in U$ and returns a bit.
 %
@@
 {
-\experimentv{$\ExpCorrectSecHash{S,B}{A}$}\\
+\experimentv{$\ExpCorrectSecHash{B}{\distr{U}{n}, A}$}\\
+$S \getsr \distr{U}{n}$\\
 $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
@@
 if $\Test^{\HashOracle}(S,M,x) \neq 1$ then Ret 1\\
-Ret 0\\
+Ret 0
+}
+%
+{
+\oracle{$\QryOracle(x)$}\\
+if $M = \bot$ then Ret $\bot$\\
+Ret $\Qry^{\HashOracle}(M,x)$\\
 
 \medskip
-\experimentv{$\ExpCorrectPubHash{S,B}{A}$}\\
+\oracle{$\UpdateOracle(\sigma)$}\\
+if $M = \bot$ then Ret $\bot$ \\
+$\mathrm{op},\mathrm{val} \gets \sigma$\\
+$S \gets S \uplus \{\mathrm{val}\}$\\
+$M \getsr \Update^{\HashOracle}(M,\sigma)$\\
+
+\medskip
+\oracle{$\HashOracle(i,x)$}\\
+Ret $h_i(x)$\\
+}
+}
+%%%%%%%%%%
+\fpage{.6}{
+\hpagess{.6}{.35}
+{
+\experimentv{$\ExpCorrectPubHashBB{B}{\distr{U}{n} , A}$}\\
+$S \getsr \distr{U}{n}$\\
 $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
@@
 if $M = \bot$ then Ret $\bot$ \\
-$S \gets S \uplus \{\sigma\}$\\
+$\mathrm{op},\mathrm{val} \gets \sigma$\\
+$S \gets S \uplus \{\mathrm{val}\}$\\
 $M \getsr \Update^{\HashOracle}(M,\sigma)$\\
@@
 }
-\caption{Trying to define correctness for an $(n,k,[m_1,m_2])$-filter~$B$.}
+%%%%%%%%%%%
+\fpage{.6}{
+\hpagess{.6}{.35}
+{
+\experimentv{$\ExpCorrectPubHash{B}{\distr{U}{n} , A}$}\\
+$S \getsr \distr{U}{n}$\\
+$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
+$M \gets \Init^{\HashOracle}(S)$\\
+$x \getsr A^{\QryOracle,\UpdateOracle}(S,\{h_1,h_2,\ldots,h_k\})$\\
+if $\Test^{\HashOracle}(S,M,x) \neq 1$ then Ret 1\\
+Ret 0
+}
+%
+{
+\oracle{$\QryOracle(x)$}\\
+if $M = \bot$ then Ret $\bot$\\
+Ret $\Qry^{\HashOracle}(M,x)$\\
+
+\medskip
+\oracle{$\UpdateOracle(\sigma)$}\\
+if $M = \bot$ then Ret $\bot$ \\
+$\mathrm{op},\mathrm{val} \gets \sigma$\\
+$S \gets S \uplus \{\\mathrm{val}\}$\\
+$M \getsr \Update^{\HashOracle}(M,\sigma)$\\
+
+\medskip
+\oracle{$\HashOracle(i,x)$}\\
+Ret $h_i(x)$\\
+}
+}
+\caption{Trying to define correctness for an $(n,k,[m_1,m_2])$-filter~$B$.
+\textcolor{cyan}{Revisit once picture for ``plain'' filters settles.
+Also, not exactly right since $\distr{U}{n}$ currently defined to sample from $[U]^n$; here should be multisets.}}
 \label{fig:correctness-mutable}

### 2016-06-07 filters.tex
adding security notions for multiple-server setting

@@
 $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-$M \gets \Init^{\HashOracle}(S)$\\
+$M \gets \Rep^{\HashOracle}(S)$\\
 $x \getsr A^{\QryOracle}(S)$\\
@@
 $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-$M \gets \Init^{\HashOracle}(S)$\\
+$M \gets \Rep^{\HashOracle}(S)$\\
 $x \getsr A^{\QryOracle,\HashOracle}(S)$\\
@@
 $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-$M \gets \Init^{\HashOracle}(S)$\\
+$M \gets \Rep^{\HashOracle}(S)$\\
 $x \getsr A^{\QryOracle}(S,\{h_1,h_2,\ldots,h_k\})$\\
@@
 % $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-% $M \gets \Init^{\HashOracle}(S)$\\
+% $M \gets \Rep^{\HashOracle}(S)$\\
 % $x \getsr A^{\QryOracle}(S)$\\
@@
 % $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-% $M \gets \Init^{\HashOracle}(S)$\\
+% $M \gets \Rep^{\HashOracle}(S)$\\
 % $x \getsr A^{\QryOracle,\HashOracle}(S)$\\
@@
 % $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-% $M \gets \Init^{\HashOracle}(S)$\\
+% $M \gets \Rep^{\HashOracle}(S)$\\
 % $x \getsr A^{\QryOracle}(S,\{h_1,h_2,\ldots,h_k\})$\\
@@
 $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-$M \gets \Init^{\HashOracle}(S)$\\
+$M \gets \Rep^{\HashOracle}(S)$\\
 $x \getsr A^{\QryOracle}()$\\
@@
 $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-$M \gets \Init^{\HashOracle}(S)$\\
+$M \gets \Rep^{\HashOracle}(S)$\\
 $x \getsr A^{\QryOracle,\HashOracle}()$\\
@@
 $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-$M \gets \Init^{\HashOracle}(S)$\\
+$M \gets \Rep^{\HashOracle}(S)$\\
 $x \getsr A^{\QryOracle}(\{h_1,h_2,\ldots,h_k\})$\\
@@
 \end{figure}
+
+\heading{Security in multiple-server settings. }
+\begin{figure}
+\centering
+\fpage{.6}{
+\hpagess{.6}{.35}
+{
+\experimentv{$\ExpFPSecHash{B,\ell}{\distr{U}{n}, A}$}\\
+$S_1,S_2,\ldots,S_\ell \getsr \distr{U}{n}$\\
+$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
+$\mathcal{C} \gets \emptyset$\\
+for $i=1$ to $\ell$\\
+\nudge $M_i \gets \Rep^{\HashOracle}(S_i)$\\
+$(i,x) \getsr A^{\QryOracle,\CorruptOracle}()$\\
+if $i \not\in \mathcal{C} \wedge \Qry^{\HashOracle}(M_i,x)=1$ then \\
+\nudge Ret 1\\
+Ret 0
+}
+%
+{
+\oracle{$\QryOracle(i,x)$}\\
+Ret $\Qry^{\HashOracle}(M_i,x)$\\
+
+\medskip
+\oracle{$\HashOracle(i,x)$}\\
+Ret $h_i(x)$\\
+
+\medskip
+\oracle{$\CorruptOracle(i,x)$}\\
+$\mathcal{C} \gets \mathcal{C} \cup \{i\}$\\
+Ret $S_i,M_i$\\
+}
+}
+%%%%%%%%%%
+\fpage{.6}{
+\hpagess{.6}{.35}
+{
+\experimentv{$\ExpFPPubHashBB{B,\ell}{\distr{U}{n}, A}$}\\
+$S_1,S_2,\ldots,S_\ell \getsr \distr{U}{n}$\\
+$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
+$\mathcal{C} \gets \emptyset$\\
+for $i=1$ to $\ell$\\
+\nudge $M_i \gets \Rep^{\HashOracle}(S_i)$\\
+$(i,x) \getsr A^{\QryOracle,\HashOracle,\CorruptOracle}()$\\
+if $i \not\in \mathcal{C} \wedge \Qry^{\HashOracle}(M_i,x)=1$ then \\
+\nudge Ret 1\\ 
+Ret 0
+}
+%
+{
+\oracle{$\QryOracle(i,x)$}\\
+Ret $\Qry^{\HashOracle}(M_i,x)$\\
+
+\medskip
+\oracle{$\HashOracle(i,x)$}\\
+Ret $h_i(x)$\\
+
+\medskip
+\oracle{$\CorruptOracle(i,x)$}\\
+$\mathcal{C} \gets \mathcal{C} \cup \{i\}$\\
+Ret $S_i,M_i$\\
+}
+}
+%%%%%%%
+\fpage{.6}{
+\hpagess{.6}{.35}
+{
+\experimentv{$\ExpFPPubHash{B,\ell}{\distr{U}{n}, A}$}\\
+$S_1,S_2,\ldots,S_\ell \getsr \distr{U}{n}$\\
+$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
+$\mathcal{C} \gets \emptyset$\\
+for $i=1$ to $\ell$\\
+\nudge $M_i \gets \Rep^{\HashOracle}(S_i)$\\
+$(i,x) \getsr A^{\QryOracle,\CorruptOracle}(\{h_1,h_2,\ldots,h_k\})$\\
+if $i \not\in \mathcal{C} \wedge \Qry^{\HashOracle}(M_i,x)=1$ then \\
+\nudge Ret 1\\
+Ret 0
+}
+%
+{
+\oracle{$\QryOracle(i,x)$}\\
+Ret $\Qry^{\HashOracle}(M_i,x)$\\
+
+\medskip
+\oracle{$\HashOracle(i,x)$}\\
+Ret $h_i(x)$\\
+
+\medskip
+\oracle{$\CorruptOracle(i,x)$}\\
+$\mathcal{C} \gets \mathcal{C} \cup \{i\}$\\
+Ret $S_i,M_i$\\
+}
+}
+\caption{False-positive security for an $(n,k,m)$-filter~$B$ in the multiple-server setting.
+(Three variations, depending on access to/knowledge of hash functions.) In these notions, the same hash functions are used across multiple servers, and each server has its own, independent set to represent.
+\textcolor{cyan}{This is a reasonable(?) modeling of the Squid setting.}}
+\label{fig:fp-filter}
+\end{figure}

### 2016-06-07 filters.tex
notions for multi-server setting

@@
 {
-\experimentv{$\ExpFPSecHash{B,\ell}{\distr{U}{n}, A}$}\\
-$S_1,S_2,\ldots,S_\ell \getsr \distr{U}{n}$\\
-$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
+\experimentv{$\ExpFPSecHash{B_1,B_2,\ldots,B_\ell}{\distr{U}{n}, A}$}\\
 $\mathcal{C} \gets \emptyset$\\
 for $i=1$ to $\ell$\\
-\nudge $M_i \gets \Rep^{\HashOracle}(S_i)$\\
+\nudge $S_i \getsr \distr{U}{n}$\\
+\nudge $ \{h^i_1,h^i_2,\ldots,h^i_k\} \getsr \Hash_i$\\
+\nudge $M_i \gets \Rep_i^{\HashOracle}(S_i)$\\
 $(i,x) \getsr A^{\QryOracle,\CorruptOracle}()$\\
-if $i \not\in \mathcal{C} \wedge \Qry^{\HashOracle}(M_i,x)=1$ then \\
+if $i \not\in \mathcal{C} \wedge \Qry_i^{\HashOracle}(M_i,x)=1$ then \\
+\nudge Ret 1\\
+Ret 0
+}
+%
+{
+\oracle{$\QryOracle(i,x)$}\\
+Ret $\Qry_i^{\HashOracle}(M_i,x)$\\
+
+\medskip
+\oracle{$\HashOracle(i,j,x)$}\\
+Ret $h^i_j(x)$\\
+
+\medskip
+\oracle{$\CorruptOracle(i,x)$}\\
+$\mathcal{C} \gets \mathcal{C} \cup \{i\}$\\
+Ret $S_i,M_i,\{h^i_1,\ldots,h^i_k\}$\\
+}
+}
+%%%%%%%%%%
+\fpage{.6}{
+\hpagess{.6}{.35}
+{
+\experimentv{$\ExpFPPubHashBB{B_1,B_2,\ldots, B_\ell}{\distr{U}{n}, A}$}\\
+$\mathcal{C} \gets \emptyset$\\
+for $i=1$ to $\ell$\\
+\nudge $S_i \getsr \distr{U}{n}$\\
+\nudge $ \{h^i_1,h^i_2,\ldots,h^i_k\} \getsr \Hash_i$\\
+\nudge $M_i \gets \Rep_i^{\HashOracle}(S_i)$\\
+$(i,x) \getsr A^{\QryOracle,\HashOracle,\CorruptOracle}()$\\
+if $i \not\in \mathcal{C} \wedge \Qry_i^{\HashOracle}(M_i,x)=1$ then \\
 \nudge Ret 1\\ 
@@
 \medskip
-\oracle{$\HashOracle(i,x)$}\\
-Ret $h_i(x)$\\
-
-\medskip
-\oracle{$\CorruptOracle(i,x)$}\\
-$\mathcal{C} \gets \mathcal{C} \cup \{i\}$\\
-Ret $S_i,M_i$\\
-}
-}
-%%%%%%%%%%
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpFPPubHashBB{B,\ell}{\distr{U}{n}, A}$}\\
-$S_1,S_2,\ldots,S_\ell \getsr \distr{U}{n}$\\
-$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-$\mathcal{C} \gets \emptyset$\\
-for $i=1$ to $\ell$\\
-\nudge $M_i \gets \Rep^{\HashOracle}(S_i)$\\
-$(i,x) \getsr A^{\QryOracle,\HashOracle,\CorruptOracle}()$\\
-if $i \not\in \mathcal{C} \wedge \Qry^{\HashOracle}(M_i,x)=1$ then \\
-\nudge Ret 1\\ 
-Ret 0
-}
-%
-{
-\oracle{$\QryOracle(i,x)$}\\
-Ret $\Qry^{\HashOracle}(M_i,x)$\\
-
-\medskip
-\oracle{$\HashOracle(i,x)$}\\
-Ret $h_i(x)$\\
+\oracle{$\HashOracle(i,j,x)$}\\
+Ret $h^i_j(x)$\\
 
@@
 {
-\experimentv{$\ExpFPPubHash{B,\ell}{\distr{U}{n}, A}$}\\
-$S_1,S_2,\ldots,S_\ell \getsr \distr{U}{n}$\\
-$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
+\experimentv{$\ExpFPPubHash{B_1,B_2,\ldots,B_\ell}{\distr{U}{n}, A}$}\\
 $\mathcal{C} \gets \emptyset$\\
 for $i=1$ to $\ell$\\
-\nudge $M_i \gets \Rep^{\HashOracle}(S_i)$\\
-$(i,x) \getsr A^{\QryOracle,\CorruptOracle}(\{h_1,h_2,\ldots,h_k\})$\\
-if $i \not\in \mathcal{C} \wedge \Qry^{\HashOracle}(M_i,x)=1$ then \\
+\nudge $S_i \getsr \distr{U}{n}$\\
+\nudge $ \mathcal{H}_i \gets \{h^i_1,h^i_2,\ldots,h^i_k\} \getsr \Hash_i$\\
+\nudge $M_i \gets \Rep_i^{\HashOracle}(S_i)$\\
+$(i,x) \getsr A^{\QryOracle,\CorruptOracle}(\mathcal{H}_1,\mathcal{H}_2,\ldots,\mathcal{H}_\ell)$\\
+if $i \not\in \mathcal{C} \wedge \Qry_i^{\HashOracle}(M_i,x)=1$ then \\
 \nudge Ret 1\\
@@
 \medskip
-\oracle{$\HashOracle(i,x)$}\\
-Ret $h_i(x)$\\
+\oracle{$\HashOracle(i,j,x)$}\\
+Ret $h^i_j(x)$\\
 
@@
 }
-\caption{False-positive security for an $(n,k,m)$-filter~$B$ in the multiple-server setting.
-(Three variations, depending on access to/knowledge of hash functions.) In these notions, the same hash functions are used across multiple servers, and each server has its own, independent set to represent.
-\textcolor{cyan}{This is a reasonable(?) modeling of the Squid setting.}}
+\caption{False-positive security for an $(n,k,m)$-filter~$B$ in the multiple-server setting.  (Three variations, depending on access to/knowledge of hash functions.) }
 \label{fig:fp-filter}

### 2016-06-07 filters.tex
notions for multi-server setting

@@
 
-\heading{Security in multiple-server settings. }
+\heading{Security in multiple-server settings.
+}  In this section, we consider security notions for settings in which there may be multiple servers, each holding a filter representation of a set.
+To allow for each server to embed server-specific information into its representation, we abstract the servers as $B_1,B_2,\ldots,B_\ell$ where each $B_i=(\Hash_i,\Rep_i,\Qry_i)$ is an $(n,k,m)$-filter.
+\tsnote{Still some kinks to be ironed out though.
+The current notions sample fresh hash functions for each server.
+But in, say, the Squid setting, the same hash functions are used across all Squid instances.}
+
 \begin{figure}
@@
 \nudge $S_i \getsr \distr{U}{n}$\\
-\nudge $ \{h^i_1,h^i_2,\ldots,h^i_k\} \getsr \Hash_i$\\
+\nudge $ \mathcal{H}_i \gets \{h^i_1,h^i_2,\ldots,h^i_k\} \getsr \Hash_i$\\
 \nudge $M_i \gets \Rep_i^{\HashOracle}(S_i)$\\
-$(i,x) \getsr A^{\QryOracle,\CorruptOracle}()$\\
+$(i,x) \getsr A^{\QryOracle,\CorruptOracle}(S_1,S_2,\ldots,S_\ell)$\\
 if $i \not\in \mathcal{C} \wedge \Qry_i^{\HashOracle}(M_i,x)=1$ then \\
@@
 $\mathcal{C} \gets \mathcal{C} \cup \{i\}$\\
-Ret $S_i,M_i,\{h^i_1,\ldots,h^i_k\}$\\
+Ret $M_i,\mathcal{H}_i$\\
 }
@@
 \nudge $M_i \gets \Rep_i^{\HashOracle}(S_i)$\\
-$(i,x) \getsr A^{\QryOracle,\HashOracle,\CorruptOracle}()$\\
+$(i,x) \getsr A^{\QryOracle,\HashOracle,\CorruptOracle}(S_1,S_2,\ldots,S_\ell)$\\
 if $i \not\in \mathcal{C} \wedge \Qry_i^{\HashOracle}(M_i,x)=1$ then \\
@@
 $\mathcal{C} \gets \mathcal{C} \cup \{i\}$\\
-Ret $S_i,M_i$\\
+Ret $M_i$\\
 }
@@
 \nudge $M_i \gets \Rep_i^{\HashOracle}(S_i)$\\
-$(i,x) \getsr A^{\QryOracle,\CorruptOracle}(\mathcal{H}_1,\mathcal{H}_2,\ldots,\mathcal{H}_\ell)$\\
+$(i,x) \getsr A^{\QryOracle,\CorruptOracle}(S_1,S_2,\ldots,S_\ell,\mathcal{H}_1,\mathcal{H}_2,\ldots,\mathcal{H}_\ell)$\\
 if $i \not\in \mathcal{C} \wedge \Qry_i^{\HashOracle}(M_i,x)=1$ then \\
@@
 $\mathcal{C} \gets \mathcal{C} \cup \{i\}$\\
-Ret $S_i,M_i$\\
+Ret $M_i$\\
 }
 }
-\caption{False-positive security for an $(n,k,m)$-filter~$B$ in the multiple-server setting.  (Three variations, depending on access to/knowledge of hash functions.) }
+\caption{False-positive security for an $(n,k,m)$-filter~$B$ in the multiple-server setting.
+(Three variations, depending on access to/knowledge of hash functions.) \textcolor{cyan}{Not clear which of these notions really makes sense.}}
 \label{fig:fp-filter}

### 2016-06-07 filters.tex
notions for multi-server setting

@@
 The current notions sample fresh hash functions for each server.
-But in, say, the Squid setting, the same hash functions are used across all Squid instances.}
+But in (say) the Squid setting, the same hash functions are used across all Squid instances...
+maybe it suffices, for that setting, to say that the $\Hash_i$ are all the same, and each simply returns a fixed set of~$k$ hash functions (i.e., deterministic).}
 
@@
 \nudge $ \mathcal{H}_i \gets \{h^i_1,h^i_2,\ldots,h^i_k\} \getsr \Hash_i$\\
-\nudge $M_i \gets \Rep_i^{\HashOracle}(S_i)$\\
-$(i,x) \getsr A^{\QryOracle,\CorruptOracle}(S_1,S_2,\ldots,S_\ell)$\\
-if $i \not\in \mathcal{C} \wedge \Qry_i^{\HashOracle}(M_i,x)=1$ then \\
+\nudge $M_i \gets \Rep_i^{\HashOracle(i,\cdot,\cdot)}(S_i)$\\
+$(i,x) \getsr A^{\QryOracle,\CorruptOracle}(\{S_i\}_{i=1}^{\ell})$\\
+if $i \not\in \mathcal{C} \wedge \Qry_i^{\HashOracle(i,\cdot,\cdot)}(M_i,x)=1$ then \\
 \nudge Ret 1\\
@@
 \nudge $ \{h^i_1,h^i_2,\ldots,h^i_k\} \getsr \Hash_i$\\
-\nudge $M_i \gets \Rep_i^{\HashOracle}(S_i)$\\
-$(i,x) \getsr A^{\QryOracle,\HashOracle,\CorruptOracle}(S_1,S_2,\ldots,S_\ell)$\\
-if $i \not\in \mathcal{C} \wedge \Qry_i^{\HashOracle}(M_i,x)=1$ then \\
+\nudge $M_i \gets \Rep_i^{\HashOracle(i,\cdot,\cdot)}(S_i)$\\
+$(i,x) \getsr A^{\QryOracle,\HashOracle,\CorruptOracle}(\{S_i\}_{i=1}^{\ell})$\\
+if $i \not\in \mathcal{C} \wedge \Qry_i^{\HashOracle(i,\cdot,\cdot)}(M_i,x)=1$ then \\
 \nudge Ret 1\\ 
@@
 \nudge $ \mathcal{H}_i \gets \{h^i_1,h^i_2,\ldots,h^i_k\} \getsr \Hash_i$\\
-\nudge $M_i \gets \Rep_i^{\HashOracle}(S_i)$\\
-$(i,x) \getsr A^{\QryOracle,\CorruptOracle}(S_1,S_2,\ldots,S_\ell,\mathcal{H}_1,\mathcal{H}_2,\ldots,\mathcal{H}_\ell)$\\
-if $i \not\in \mathcal{C} \wedge \Qry_i^{\HashOracle}(M_i,x)=1$ then \\
+\nudge $M_i \gets \Rep_i^{\HashOracle(i,\cdot,\cdot)}(S_i)$\\
+$(i,x) \getsr A^{\QryOracle,\CorruptOracle}(\{S_i\}_{i=1}^{\ell},\{\mathcal{H}_i\}_{i=1}^{\ell})$\\
+if $i \not\in \mathcal{C} \wedge \Qry_i^{\HashOracle(i,\cdot,\cdot)}(M_i,x)=1$ then \\
 \nudge Ret 1\\

### 2016-06-07 filters.tex
notions for multi-server setting

@@
 But in (say) the Squid setting, the same hash functions are used across all Squid instances...
-maybe it suffices, for that setting, to say that the $\Hash_i$ are all the same, and each simply returns a fixed set of~$k$ hash functions (i.e., deterministic).}
+maybe it suffices, for that setting, to say that the $\Hash_i$ are all the same, and each simply returns a fixed set of~$k$ hash functions (i.e., deterministic).}  To model insider attacks, we give the adversary the ability to corrupt (adaptively) instances of the filter.
+Such attacks capture P2P settings, in which the adversary may join the network as a peer.
 
@@
 \oracle{$\QryOracle(i,x)$}\\
-Ret $\Qry^{\HashOracle}(M_i,x)$\\
+Ret $\Qry_i^{\HashOracle}(M_i,x)$\\
 

### 2016-06-07 tasks_and_ideas.tex
cheers
added task: definiing unlinkability as a security notion

@@
 
+\heading{Theory tasks.}
 \begin{itemize}
@@
 Verify this.
-Also, what about set-intersection attacks on Bloom filters?
+\tsnote{Approximately true.
+If the distribution of the expected number of zero bits is tight around its mean, then you can use the actual number of 0-bits as the expected number, and then deduce the size of the set.}  Also, what about set-intersection attacks on Bloom filters?
+\item This raises the more general question of schemes/protocols that use multiple Bloom filters to represent a single set based on distinct features of set elements.  We should dig into this.
 
+\item Considering the P2P setting, how should we formalize insider attacks?  I'm thinking something like FP and privacy with corruptions.  What about authenticity of published Bloom filters?
+
+\item Formalize ``unlinkability'', i.e.
+given some initial information about two representations $M_0,M_1$ before an element~$x$ is added, an adversary can't distinguish between $M_0 \cup x$ and $M_1 \cup x$ (abusing notation).
+\tsnote{This is somewhat defined in Kerschbaum.}
+
+\item Formalize a security goal for Stochastic Fair Blue (or similar TCP stream routing primitives) and prove that a secure, mutable hash-based filter implies secure Stochastic Fair Blue.
+
+\item Do the same for other applications of Bloom-filter-like primitives.  (For example, attenuated Bloom filters, used in the OceanStore project (at least).)
+
+\item Would a secure Bloom filter (of some kind) give us a secure strike list (whatever secure means), like what was originally proposed in QUIC?
+Are Bloom filters used in edge network servers for big providers like Facebook, LinkedIn, Google, etc.?
+\end{itemize}
+
+\heading{Systems-y tasks.}
+\begin{itemize}
 \item Find measurement info on false positive rates for Squid filters/HTTP proxies in practice.  This must have been done already.
@@
 
-\item This raises the more general question of schemes/protocols that use multiple Bloom filters to represent a single set based on distinct features of set elements.  We should dig into this.
-
-\item Considering the P2P setting, how should we formalize insider attacks?  I'm thinking something like FP and privacy with corruptions.  What about authenticity of published Bloom filters?
-
-\item Formalize a security goal for Stochastic Fair Blue (or similar TCP stream routing primitives) and prove that a secure, mutable hash-based filter implies secure Stochastic Fair Blue.
-
-\item Do the same for other applications of Bloom-filter-like primitives.  (For example, attenuated Bloom filters, used in the OceanStore project (at least).)
-
 \item What about content-based routing (or whatever they are calling that area now)?
@@
 
-\item Would a secure Bloom filter (of some kind) give us a secure strike list (whatever secure means), like what was originally proposed in QUIC?
-Are Bloom filters used in edge network servers for big providers like Facebook, LinkedIn, Google, etc.?
-
 \item Generally speaking, can we characterize operational settings in a way that surfaces an interesting security/performance trade-off?
@@
 The Bloom filters used in a simple spam-detection system (do these exist) are likely to be much smaller, maintained locally on a single machine, and much easier to update.
-Solutions in one setting are not going to be useful in another....
+Solutions in one setting are not going to be useful in another.
+Likewise, attacks in one setting may not scale to another, e.g.
+the preimage-finding/polluting-point attacks in that INRIA whitepaper.
 

### 2016-06-08 intro.tex
cheers
added task: definiing unlinkability as a security notion
added comment about 'secure sketches'

@@
 \item Crosby and Wallach, ``Denial of Service via Algorithmic Complexity Attacks'' \tsnote{Gives attacks on Squid}
+\item Bellovin and Cheswick, ``Privacy-Enhanced Searches Using Encrypted Bloom Filters''.
 \item Kerschbaum , ``Public-Key Encrypted Bloom Filters with Applications to Supply Chain Integrity''.
@@
 \item Dong, Chen, Wen, ``When Private Set Intersection Meets Big Data: An Efficient and Scaleable Protocol'' \tsnote{``garbled bloom filters'' (which actually store the set element by storing~$k$ xor-shares, one at each of the hash indices),``oblivious bloom intersection''}
+\item Tarkoma, Rothenberg, Lagerspetz ``Theory and Practice of Bloom Filters in Distributed Systems'' \tsnote{Great high-level coverage.  Only found preprint version though.}
+\item Dodis et al.
+``Fuzzy Extractors: How to Generate Strong Keys from Biometrics and Other Noisy Data'' \tsnote{Introduces ``secure sketches'', which is a representation of a single-element set that is information theoretically private (up to some function of the min-entropy of the element); only tangentially related to ``sketches'' as defined in the Bloom filter literature.}
 \end{itemize}

### 2016-06-08 intro.tex
comments about Dong, Chen, Wen, including an attack for small but interesting parameters

@@
 \item Gerbet, Kumar and Lauradoux, ``The power of evil choices in bloom filters''.  \tsnote{DSN'15: Looks like a real goldmine of related work!}
-\item Nojima and Kadobayashi, ``Cryptographically Secure Bloom Filters''. \tsnote{Gives some security definitions for privacy. Quick scan, not super clear what they achieve.}
+\item Nojima and Kadobayashi, ``Cryptographically Secure Bloom Filters''.
+\tsnote{Gives some security definitions for privacy.
+Quick scan, not super clear what they achieve.
+The definition of client-privacy (Definition 1) for example, makes no sense to me.
+Actually, likewise for server-privacy (Definition 2).
+Both seem vague and thoroughly underspecified.}
 \item Crosby and Wallach, ``Denial of Service via Algorithmic Complexity Attacks'' \tsnote{Gives attacks on Squid}
@@
 \item Gao et al., ``Internet Cache Pollution Attacks and Countermeasures''
-\item Dong, Chen, Wen, ``When Private Set Intersection Meets Big Data: An Efficient and Scaleable Protocol'' \tsnote{``garbled bloom filters'' (which actually store the set element by storing~$k$ xor-shares, one at each of the hash indices),``oblivious bloom intersection''}
+\item Dong, Chen, Wen, ``When Private Set Intersection Meets Big Data: An Efficient and Scaleable Protocol'' \tsnote{``garbled bloom filters'', which actually store the set element by storing~$k$ xor-shares, one at each of the~$k$ hash indices (with care for reusing shares if hash collisions occur), and``oblivious bloom intersection''}\tsnote{If the filter and the hash functions are public, there is a (naive, not terribly efficient) attack that works for some interesting parameters.
+Pick~$k$ positions $i_1,i_2,\ldots,i_k$, xor strings at these positions to get a candidate~$x$.
+If $h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots \wedge h_k(x) = i_k$ then either $x \in S$ or~$x$ is a false-positive.
+(You don't have to do all~$k$ hashes, you can stop as soon as one fails to match the index.)  Say you have a 1000-position filter ($m=1000$) and a 100-element set ($n=100$), and you are willing to tolerate a 1\% FP rate.
+Then you'd set $k=4$ (a la Squid).
+There are roughly $2^{35}$ subsets of 4 indices to consider, which is reasonable on a laptop these days.
+With the FP rate of 1\%, if you find a winner then almost certainly it is in the set.
+Granted, this attack is naive, but notice that you \emph{cannot} mount it against a standard Bloom filter.
+}
 \item Tarkoma, Rothenberg, Lagerspetz ``Theory and Practice of Bloom Filters in Distributed Systems'' \tsnote{Great high-level coverage.  Only found preprint version though.}

### 2016-06-09 intro.tex
cheers

@@
 \item Gao et al., ``Internet Cache Pollution Attacks and Countermeasures''
-\item Dong, Chen, Wen, ``When Private Set Intersection Meets Big Data: An Efficient and Scaleable Protocol'' \tsnote{``garbled bloom filters'', which actually store the set element by storing~$k$ xor-shares, one at each of the~$k$ hash indices (with care for reusing shares if hash collisions occur), and``oblivious bloom intersection''}\tsnote{If the filter and the hash functions are public, there is a (naive, not terribly efficient) attack that works for some interesting parameters.
+\item Dong, Chen, Wen, ``When Private Set Intersection Meets Big Data: An Efficient and Scaleable Protocol'' \tsnote{``garbled bloom filters'', which actually store the set element by storing~$k$ xor-shares, one at each of the~$k$ hash indices (with care for reusing shares if hash collisions occur), and``oblivious bloom intersection''}\tsnote{If the filter and the hash functions are public, there is a naive attack that works for some interesting parameters.
 Pick~$k$ positions $i_1,i_2,\ldots,i_k$, xor strings at these positions to get a candidate~$x$.
@@
 Granted, this attack is naive, but notice that you \emph{cannot} mount it against a standard Bloom filter.
+Also notice that this attack might be significantly more efficient than brute force guessing over the universe of inputs (imagine that $U=\bits^{64}$), even if you know that the distribution deviates significantly from uniform.
 }

### 2016-06-09 filters.tex
cheers

@@
 %
-The deterministic representation algorithm $\Rep\colon [U]^n \rightarrow \Sigma^m$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m$.
+The randomized representation algorithm $\Rep\colon [U]^n \rightarrow \Sigma^m$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m$.
 %
@@
 This syntax captures classical Bloom filters by setting~$\Sigma=\bits$,  and defining $\Rep,\Qry$ in the obvious way.
+We note that even though $\Rep$ may be randomized, it does not have to be; for the classical Bloom filter, it is deterministic.
+
 Setting $\Sigma=\bits^{\leq L}$ allows one to store a bitstring of length at most~$L$ at each location.
-\tsnote{Would let us capture a construction from NY, among other things.}  We note that even though this would allow for the storage of counters (say) at each filter location, our restriction that~$\Qry$ returns a bit does not capture functionality typically demanded of Bloom filters that employ counters, e.g., returning a counter value.
+This allows our syntax to capture the cuckoo-hashing construction from NY, as well as the ``garbled Bloom filter'' from Dong, Chen and Wen, among other things.
+We note that even though this would allow for the storage of counters (say) at each filter location, our restriction that~$\Qry$ returns a bit does not capture functionality typically demanded of Bloom filters that employ counters, e.g., returning a counter value.
 (One could, however, have $\Qry$ compute an arbitrary, fixed predicate.
@@
 \nudge $ \mathcal{H}_i \gets \{h^i_1,h^i_2,\ldots,h^i_k\} \getsr \Hash_i$\\
-\nudge $M_i \gets \Rep_i^{\HashOracle(i,\cdot,\cdot)}(S_i)$\\
+\nudge $M_i \getsr \Rep_i^{\HashOracle(i,\cdot,\cdot)}(S_i)$\\
 $(i,x) \getsr A^{\QryOracle,\CorruptOracle}(\{S_i\}_{i=1}^{\ell})$\\

### 2016-06-09 filters.tex
cheers

@@
 %We write $M \gets \Rep(S)$ and $b \gets \Qry(M,x)$ for the execution of the representation and query algorithms, respectively.
-For correctness, we demand that for all~$S$ of size~$n$, we have that for all $x \in S, \Prob{\Qry(\Rep(S),x)=1}=1$, where the probability is over the coins of $\Hash$.
+For correctness, we demand that for all~$S$ of size~$n$, we have that for all $x \in S, \Prob{\Qry(\Rep(S),x)=1}=1$, where the probability is over the coins of $\Hash$ and $\Rep$.
 
@@
 \end{align*}
-The probabilities are over the sampling of the set~$S$ and the hash functions $h_1,h_2,\ldots,h_k$, as well as the coins of the adversary.
+The probabilities are over the coins of the indicated experiment, and he coins of the adversary.
 In all experiments, we track time-complexity~$t$ of~$A$, as well as the number of set-membership ($\QryOracle$ oracle) queries~$q_{\mathrm{sm}}$ that it makes.
@@
 $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-$M \gets \Rep^{\HashOracle}(S)$\\
+$M \getsr \Rep^{\HashOracle}(S)$\\
 $x \getsr A^{\QryOracle}(S)$\\
@@
 $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-$M \gets \Rep^{\HashOracle}(S)$\\
+$M \getsr \Rep^{\HashOracle}(S)$\\
 $x \getsr A^{\QryOracle,\HashOracle}(S)$\\
@@
 \nudge $ \{h^i_1,h^i_2,\ldots,h^i_k\} \getsr \Hash_i$\\
-\nudge $M_i \gets \Rep_i^{\HashOracle(i,\cdot,\cdot)}(S_i)$\\
+\nudge $M_i \getsr \Rep_i^{\HashOracle(i,\cdot,\cdot)}(S_i)$\\
 $(i,x) \getsr A^{\QryOracle,\HashOracle,\CorruptOracle}(\{S_i\}_{i=1}^{\ell})$\\
@@
 \nudge $ \mathcal{H}_i \gets \{h^i_1,h^i_2,\ldots,h^i_k\} \getsr \Hash_i$\\
-\nudge $M_i \gets \Rep_i^{\HashOracle(i,\cdot,\cdot)}(S_i)$\\
+\nudge $M_i \getsr \Rep_i^{\HashOracle(i,\cdot,\cdot)}(S_i)$\\
 $(i,x) \getsr A^{\QryOracle,\CorruptOracle}(\{S_i\}_{i=1}^{\ell},\{\mathcal{H}_i\}_{i=1}^{\ell})$\\

### 2016-06-09 filters.tex
cheers

@@
 Setting $\Sigma=\bits^{\leq L}$ allows one to store a bitstring of length at most~$L$ at each location.
-This allows our syntax to capture the cuckoo-hashing construction from NY, as well as the ``garbled Bloom filter'' from Dong, Chen and Wen, among other things.
+This allows our syntax to capture the cuckoo-hashing construction from NY, as well as the ``garbled Bloom filter'' from Dong, Chen and Wen~\cite{xxx}, among other things.
 We note that even though this would allow for the storage of counters (say) at each filter location, our restriction that~$\Qry$ returns a bit does not capture functionality typically demanded of Bloom filters that employ counters, e.g., returning a counter value.

### 2016-06-09 mutable-filters.tex
cheers

@@
 %
-The deterministic \emph{initial-representation} algorithm $\Init\colon \multiset{U}{n} \rightarrow \left(\bigcup_{m=m_1}^{m_2}\Sigma^m\right)$ takes a multiset~$S$ of size~$n$ as input, and outputs representation~$M$ of length~$m_1 \leq m \leq m_2$.
+The randomized \emph{initial-representation} algorithm $\Init\colon \multiset{U}{n} \rightarrow \left(\bigcup_{m=m_1}^{m_2}\Sigma^m\right)$ takes a multiset~$S$ of size~$n$ as input, and outputs representation~$M$ of length~$m_1 \leq m \leq m_2$.
 %
@@
 $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-$M \gets \Init^{\HashOracle}(S)$\\
+$M \getsr \Init^{\HashOracle}(S)$\\
 $x \getsr A^{\QryOracle,\UpdateOracle}(S)$\\
@@
 $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-$M \gets \Init^{\HashOracle}(S)$\\
+$M \getsr \Init^{\HashOracle}(S)$\\
 $x \getsr A^{\QryOracle,\UpdateOracle,\HashOracle}(S)$\\
@@
 $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-$M \gets \Init^{\HashOracle}(S)$\\
+$M \getsr \Init^{\HashOracle}(S)$\\
 $x \getsr A^{\QryOracle,\UpdateOracle}(S,\{h_1,h_2,\ldots,h_k\})$\\

### 2016-06-09 intro.tex
cheers

@@
 \begin{itemize}
-\item Niedermayer et al., breaking privacy of secret-hash-function Bloom filters.
+\item Niedermayer et al., ``Cryptanalysis of Basic Bloom Filters Used for Privacy-Preserving Record Linkage'', breaking privacy of secret-hash-function Bloom filters.
+\tsnote{Journal of Privacy and Confidentiality, 2014}
 \item Mitzenmacher and Vadhan.\tsnote{Might only be tangential.}
@@
 There are roughly $2^{35}$ subsets of 4 indices to consider, which is reasonable on a laptop these days.
-With the FP rate of 1\%, if you find a winner then almost certainly it is in the set.
+(Also, since $n=100$ the expected number of trials is roughly $2^{28}$.)  With the FP rate of 1\%, if you find a winner then almost certainly it is in the set.
 Granted, this attack is naive, but notice that you \emph{cannot} mount it against a standard Bloom filter.

### 2016-06-13 Proofs.tex
Proof of task#1 and minor changes

\section{Theorems and proofs}
\begin{theorem}
Fix $n,k, m > 0$ and define a hash-based filter as in section \ref{sec:hbf}, except the hash functions are defined by $h_j(x) = \left( f_{K0}(x) + j\cdot g_{K1}(x)\right) \bmod m$. Let $Func(m,m)$ be the set of all functions $\rho \colon \calK \times \bits^m \sends \bits^m$. Let $B_1, B_2$ be 2 adversaries with keys $K_1, K_2 \getsr \calK$ attacking the PRF advantage of $F \colon \calK \times \bits^m \sends \bits^m$ and $A$ be another adversary attacking the false positive game of hash-based filters, then 
\begin{equation}
\AdvFPSecHash{B}{\distr{U}{n},A}  = 0.5\Big[\AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}\Big] + \varepsilon, \nudge where \nudge \varepsilon = (1-(1-e^{-kn/m})^k)
\end{equation}

\end{theorem}

\begin{proof}
Let adversary $B$ simulate the fp-priv game of $A$ as shown in Fig. \ref{fig:AdvB}, where the hash functions are defined as $h_j(x) = \left( f_{K0}(x) + j\cdot g_{K1}(x)\right) \bmod m$. Based on the variable $c(c\getsr \bits)$,  $B$ either acts as adversary $B_1$ or $B_2$. Fig. \ref{fig:PRFexp} shows the PRF experiment of $B$. When $B$ makes an oracle query on behalf of $A$ and  $b=0$, it exactly simulates $A's$ experiment as the hash functions are uniformly random. When $b=1$, it exactly simulates the double hashing scheme proposed by Kirsh and Mitzenmacher. The fp-error($\varepsilon$)  for the double hashing scheme for large $n$ is $\varepsilon = (1-e^{-kn/m})^k$ \cite{less hashing paper}.

\begin{figure}[t]
\centering
\fpage{.5}
{
\experimentv{Adversary $B^{\calO}$:}\\
$c \getsr \bits$\\
$K \getsr \calK$\\
$S \getsr \distr{U}{n}$\\
if $c=0$\\
$ \nudge h_j = \calO(\cdot) + jF_K(\cdot), \nudge \mathrm{where} \nudge j \in [1,k]$\\
else\\
$\nudge  h_j = F_K(\cdot) + j\calO(\cdot), \nudge \mathrm{where} \nudge j \in [1,k]$\\
$M \getsr \Rep^{h_1, \cdots, h_k}(S)$\\
Run $A$\\
When $A$ asks $\QryOracle(x)$: \\
$\nudge$ Ret $\QryOracle^{h_1, \cdots, h_k}(M, x)$ to $A$\\
When $A$ halts with output $x^{'}$: \\
if $x^{'} \not\in S \wedge \Qry^{h_1, \cdots, h_k}(M,x^{'})=1$ then\\
$\nudge$ Ret 1\\
Ret 0
}
\caption{Adversary $B$ simulating $A^{'}s$ fp-prv game}\label{fig:AdvB}
\end{figure}

\begin{figure}[h]
\center
\fpage{.45}{
\hpagess{.4}{.5}
{
\experimentv{$\ExpPRF{F}{B}$:}\\
$b \getsr \bits$\\
$\rho \getsr Func(m,m)$\\
$K_1 \getsr \calK$\\
$b^{'} \getsr B^{\calO(\cdot,\cdot)}$\\
Ret $[b=b']$
}
{
\oracle{$\calO(x)$}\\
$Y \gets \calF_{K_1}(M)$\\
if $b=0$\\
\nudge$Y \getsr \rho(x)$\\
Ret $Y$
}
}
\caption{PRF experiment}\label{fig:PRFexp}
\end{figure}
\acnote{Equations to be aligned}
\begin{multline*}
\Prob{\ExpPRF{F}{B} = 1} =   .5\Prob{\ExpPRF{F}{B} = 1 | b =0} + .5\Prob{\ExpPRF{F}{B} = 1 | b = 1}\\
.5\Prob{\ExpPRF{F}{B} = 1|c=0} + .5\Prob{\ExpPRF{F}{B} = 1|c=1}  = .5\Prob{\ExpFPSecHash{B}{\distr{U}{n},A}=1} + .5(1-e^{-kn/m})^k  \\
.5\Prob{\ExpPRF{F}{B} = 1|c=0} + .5\Prob{\ExpPRF{F}{B} = 1|c=1}  = .5\Prob{\ExpFPSecHash{B}{\distr{U}{n},A}=1} + .5(1-e^{-kn/m})^k \\
\Prob{\ExpPRF{F}{B} = 1|c=0} + \Prob{\ExpPRF{F}{B} = 1|c=1} = \Prob{\ExpFPSecHash{B}{\distr{U}{n},A}=1} + (1-e^{-kn/m})^k \\
 2\Prob{\ExpPRF{F}{B_1} = 1} - 1 + 2\Prob{\ExpPRF{F}{B_2} = 1} - 1 = 2\AdvFPSecHash{B}{\distr{U}{n},A} + 2(1-e^{-kn/m})^k -2\\
\AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} = 2\AdvFPSecHash{B}{\distr{U}{n},A} + 2(1-e^{-kn/m})^k -2\\
 \AdvFPSecHash{B}{\distr{U}{n},A} = 0.5(\AdvPRF{F}{B_1} + \AdvPRF{F}{B_2})  + \varepsilon, \nudge \mathrm{where} \nudge \varepsilon = 1-(1-e^{-kn/m})^k
\end{multline*}

\end{proof}

### 2016-06-17 Proofs.tex
Modified proof

@@
-\section{Theorems and proofs}
+\section{Proofs}
 \begin{theorem}
@@
 \begin{equation}
-\AdvFPSecHash{B}{\distr{U}{n},A}  = 0.5\Big[\AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}\Big] + \varepsilon, \nudge where \nudge \varepsilon = (1-(1-e^{-kn/m})^k)
+\AdvFPSecHash{B}{\distr{U}{n},A}  = 0.5\Big[\AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}\Big] + 1-\epsilon, \nudge where \nudge \epsilon = (1-e^{-kn/m})^k
 \end{equation}
-
+Note: $\epsilon$ is the false positive error in the double hashing scheme given by Kirsch and Mitzenmacher \cite{xxx}
 \end{theorem}
@@
 \begin{proof}
-Let adversary $B$ simulate the fp-priv game of $A$ as shown in Fig.
-\ref{fig:AdvB}, where the hash functions are defined as $h_j(x) = \left( f_{K0}(x) + j\cdot g_{K1}(x)\right) \bmod m$.
-Based on the variable $c(c\getsr \bits)$,  $B$ either acts as adversary $B_1$ or $B_2$.
-Fig.
-\ref{fig:PRFexp} shows the PRF experiment of $B$.
-When $B$ makes an oracle query on behalf of $A$ and  $b=0$, it exactly simulates $A's$ experiment as the hash functions are uniformly random.
-When $b=1$, it exactly simulates the double hashing scheme proposed by Kirsh and Mitzenmacher.
-The fp-error($\varepsilon$)  for the double hashing scheme for large $n$ is $\varepsilon = (1-e^{-kn/m})^k$ \cite{less hashing paper}.
+The proof of the theorem will use a game playing argument as shown in Fig.
+\ref{fig:Game}.
+In $\game{0}$, the hash functions are uniformly random functions sampled from $Func(m,m)$, whereas in $\game{1}$ and $\game{2}$, the hash functions are linear combinations of a PRF and a random function.
+It can be seen that, $\game{0}$ exactly simulates $\ExpFPSecHash{B}{A}$.
+So, $\AdvFPSecHash{B}{A}=\Prob{\game{0}(A)=1}$.
+Also, the probability of winning $\game{1}$ and $\game{2}$ are equal, i.e.,$\Prob{\game{1}(A)=1}=\Prob{\game{2}(A)=1}$.
+The hash functions in $\game{3}$ are linear combinations of 2 random functions or 2 PRF's.
 
-\begin{figure}[t]
+\begin{figure}[h]
+\fpage{.9}{
+\hpagessd{.5}{.5}
+{
+\underline{\game{0}(A)}\\
+$h_1,h_2, \cdots, h_k \getsr Func(m,m)$\\
+%$K \getsr \calK$\\
+$S \getsr \distr{U}{n}$\\
+$M \getsr \Rep^{h_1, \cdots, h_k}(S)$\\
+$x \getsr A^{\QryOracle(\cdot)}(S)$\\
+if $x \not\in S \wedge \Qry^{h_1, \cdots, h_k}(M,x)=1$ then\\
+\nudge Ret 1\\
+Ret 0\\\\\\
+%
+\oracle{$\QryOracle(x)$}\\
+Ret $\Qry^{h_1, \cdots, h_k}(M,x)$
+}
+{
+\underline{\game{1}(A)}\\
+$K \getsr \calK$\\
+$h_j(\cdot) \getsr F_K(\cdot)+j\calO_2(.), \nudge \mathrm{where} \nudge j \in [1,k]$\\
+$S \getsr \distr{U}{n}$\\
+$M \getsr \Rep^{h_1, \cdots, h_k}(S)$\\
+$x \getsr A^{\QryOracle(\cdot)}(S)$\\
+if $x \not\in S \wedge \Qry^{h_1, \cdots, h_k}(M,x)=1$ then\\
+\nudge Ret 1\\
+Ret 0\\\\
+%
+\oracle{$\QryOracle(x)$}\\
+Ret $\Qry^{h_1, \cdots, h_k}(M,x)$
+}
+{
+\underline{\game{2}(A)}\\
+$K \getsr \calK$\\
+$h_j = \calO_1(\cdot) + jF_K(\cdot), \nudge \mathrm{where} \nudge j \in [1,k]$\\
+$S \getsr \distr{U}{n}$\\
+$M \getsr \Rep^{h_1, \cdots, h_k}(S)$\\
+$x \getsr A^{\QryOracle(\cdot)}(S)$\\
+if $x \not\in S \wedge \Qry^{h_1, \cdots, h_k}(M,x)=1$ then\\
+\nudge Ret 1\\
+Ret 0\\\\\\
+%
+\oracle{$\QryOracle(x)$}\\
+Ret $\Qry^{h_1, \cdots, h_k}(M,x)$
+}
+{
+\underline{\game{3}(A)}\\
+$h_j = \calO_1(\cdot) + j\calO_2(\cdot), \nudge \mathrm{where} \nudge j \in [1,k]$\\
+$S \getsr \distr{U}{n}$\\
+$M \getsr \Rep^{h_1, \cdots, h_k}(S)$\\
+$x \getsr A^{\QryOracle(\cdot)}(S)$\\
+if $x \not\in S \wedge \Qry^{h_1, \cdots, h_k}(M,x)=1$ then\\
+\nudge Ret 1\\
+Ret 0\\\\\\\\
+%
+\oracle{$\QryOracle(x)$}\\
+Ret $\Qry^{h_1, \cdots, h_k}(M,x)$
+}
+}
+\caption{Game playing argument}\label{fig:Game}
+\end{figure}
+
+\begin{eqnarray*}
+\Prob{\game{3}(A)=1} &=&\frac{1}{4}\Prob{\game{3}(A)=1|b_1=0, b_2=0} + \frac{1}{4}\Prob{\game{3}(A)=1|b_1=0, b_2=1}\\
+& + & \frac{1}{4}\Prob{\game{3}(A)=1|b_1=1, b_2=0}+ \frac{1}{4}\Prob{\game{3}(A)=1|b_1=1, b_2=1}\\
+& = & \frac{1}{4}\Prob{\game{0}(A)=1} + \frac{1}{4}\Prob{\game{2}(A)=1}\\
+&\nudge + & \frac{1}{4}\Prob{\game{3}(A)=1} + \frac{1}{4}\Prob{\game{2}(A)=1|b=1}\\
+& = & \frac{1}{4}\Prob{\game{0}(A)=1} + \frac{1}{4}\Prob{\game{2}(A)=1}\\
+&\nudge + & \frac{1}{4}\Prob{\game{2}(A)=1} + \frac{1}{4}\Prob{\game{2}(A)=1|b=1}\\
+& = & \frac{1}{4}\Prob{\game{0}(A)=1} + \frac{1}{2}\Prob{\game{2}(A)=1}\\
+&\nudge + & \frac{1}{4}\Prob{\game{2}(A)=1|b=1}\\
+& = & \frac{1}{4}\Prob{\game{0}(A)=1} + \frac{1}{2}\Big[\frac{1}{2}\Prob{\game{2}(A)=1|b=0}\\
+	& \nudge + & \frac{1}{2}\Prob{\game{2}(A)=1|b=1}\Big] + \frac{1}{4}\Prob{\game{2}(A)=1|b=1}\\
+& = & \frac{1}{4}\Prob{\game{0}(A)=1} + \frac{1}{4}\Prob{\game{0}(A)=1}\\
+& \nudge + & \frac{1}{4}\Prob{\game{2}(A)=1|b=1} + \frac{1}{4}\Prob{\game{2}(A)=1|b=1}\\
+& = & \frac{1}{2}\Prob{\game{0}(A)=1} + \frac{1}{2}\Prob{\game{2}(A)=1|b=1}
+\end{eqnarray*}
+
+The PRF-adversary $B$ simulates $\game{3}(A)$ as shown in Fig. \ref{fig:AdvB}. 
+\begin{figure}[h]
 \centering
-\fpage{.5}
+\fpage{0.6}{
+\hpagess{0.5}{0.2}
 {
-\experimentv{Adversary $B^{\calO}$:}\\
-$c \getsr \bits$\\
-$K \getsr \calK$\\
-$S \getsr \distr{U}{n}$\\
-if $c=0$\\
-$ \nudge h_j = \calO(\cdot) + jF_K(\cdot), \nudge \mathrm{where} \nudge j \in [1,k]$\\
-else\\
-$\nudge  h_j = F_K(\cdot) + j\calO(\cdot), \nudge \mathrm{where} \nudge j \in [1,k]$\\
-$M \getsr \Rep^{h_1, \cdots, h_k}(S)$\\
-Run $A$\\
-When $A$ asks $\QryOracle(x)$: \\
-$\nudge$ Ret $\QryOracle^{h_1, \cdots, h_k}(M, x)$ to $A$\\
+$\experimentv{Adversary \nudge B^{\calO}:}$\\
+$d \getsr \bits$\\
+if $d=0$\\
+$\nudge \calO_1 \gets \calO$\\
+$\nudge K \getsr \calK$\\
+$\nudge \rho \getsr Func(m,m)$\\
+$\nudge c \getsr \bits$\\
+$\nudge$if $c=0$\\
+$\nudge \nudge \calO_2 \gets \rho$\\
+$\nudge$else\\
+$\nudge \nudge \calO_2 \gets F_K$\\
+Run $\game{3}$\\
+When $A$ asks $\QryOracle(x)$:\\
+$\nudge$ Ret $\Qry^{h_1, \cdots, h_k}(M,x^{'})$\\
 When $A$ halts with output $x^{'}$: \\
@@
 }
-\caption{Adversary $B$ simulating $A^{'}s$ fp-prv game}\label{fig:AdvB}
+{
+\vspace{.6cm}
+if $d=1$\\
+$\nudge \calO_2 \gets \calO$\\
+$\nudge K \getsr \calK$\\
+$\nudge \rho \getsr Func(m,m)$\\
+$\nudge c \getsr \bits$\\
+$\nudge$if $c=0$\\
+$\nudge \nudge \calO_1 \gets \rho$\\
+$\nudge$else\\
+$\nudge \nudge \calO_1 \gets F_K$\\
+}
+}
+\caption{Adversary $B$ simulating $\game{3}$}\label{fig:AdvB}
 \end{figure}
 
-\begin{figure}[h]
-\center
-\fpage{.45}{
-\hpagess{.4}{.5}
-{
-\experimentv{$\ExpPRF{F}{B}$:}\\
-$b \getsr \bits$\\
-$\rho \getsr Func(m,m)$\\
-$K_1 \getsr \calK$\\
-$b^{'} \getsr B^{\calO(\cdot,\cdot)}$\\
-Ret $[b=b']$
-}
-{
-\oracle{$\calO(x)$}\\
-$Y \gets \calF_{K_1}(M)$\\
-if $b=0$\\
-\nudge$Y \getsr \rho(x)$\\
-Ret $Y$
-}
-}
-\caption{PRF experiment}\label{fig:PRFexp}
-\end{figure}
-\acnote{Equations to be aligned}
-\begin{multline*}
-\Prob{\ExpPRF{F}{B} = 1} =   .5\Prob{\ExpPRF{F}{B} = 1 | b =0} + .5\Prob{\ExpPRF{F}{B} = 1 | b = 1}\\
-.5\Prob{\ExpPRF{F}{B} = 1|c=0} + .5\Prob{\ExpPRF{F}{B} = 1|c=1}  = .5\Prob{\ExpFPSecHash{B}{\distr{U}{n},A}=1} + .5(1-e^{-kn/m})^k  \\
-.5\Prob{\ExpPRF{F}{B} = 1|c=0} + .5\Prob{\ExpPRF{F}{B} = 1|c=1}  = .5\Prob{\ExpFPSecHash{B}{\distr{U}{n},A}=1} + .5(1-e^{-kn/m})^k \\
-\Prob{\ExpPRF{F}{B} = 1|c=0} + \Prob{\ExpPRF{F}{B} = 1|c=1} = \Prob{\ExpFPSecHash{B}{\distr{U}{n},A}=1} + (1-e^{-kn/m})^k \\
- 2\Prob{\ExpPRF{F}{B_1} = 1} - 1 + 2\Prob{\ExpPRF{F}{B_2} = 1} - 1 = 2\AdvFPSecHash{B}{\distr{U}{n},A} + 2(1-e^{-kn/m})^k -2\\
-\AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} = 2\AdvFPSecHash{B}{\distr{U}{n},A} + 2(1-e^{-kn/m})^k -2\\
- \AdvFPSecHash{B}{\distr{U}{n},A} = 0.5(\AdvPRF{F}{B_1} + \AdvPRF{F}{B_2})  + \varepsilon, \nudge \mathrm{where} \nudge \varepsilon = 1-(1-e^{-kn/m})^k
-\end{multline*}
+$B$ exactly simulates \game{3}(A).
+\setlength{\mathindent}{1pt}
+\begin{eqnarray*}
+\Prob{\ExpPRF{F}{B} = 1} &=&  \Prob{\game{3}(A)=1}\\
+ &=& \frac{1}{2}\Prob{\game{0}(A)=1} + \frac{1}{2}\Prob{\game{2}(A)=1|b=1}\\
+ &=&  \frac{1}{2}\Prob{\ExpFPSecHash{B}{A}=1} + \frac{1}{2}\epsilon\\
+ & \mathrm{where}& \epsilon = (1-e^{-kn/m})^k = \text{FP-error in double hashing scheme}
+\end{eqnarray*}
+\setlength{\mathindent}{1pt}
+\begin{eqnarray*}
+\Prob{\ExpPRF{F}{B} = 1|d=1} &= \Prob{\ExpPRF{F}{B_1} = 1}\\
+\Prob{\ExpPRF{F}{B} = 1|d=0} &= \Prob{\ExpPRF{F}{B_2} = 1}
+\end{eqnarray*}
+\setlength{\mathindent}{1pt}
+\begin{eqnarray*}
+\Prob{\ExpPRF{F}{B} = 1} &=& \frac{1}{2}\Prob{\ExpPRF{F}{B} = 1|d=1}  + \frac{1}{2}\Prob{\ExpPRF{F}{B} = 1|d=0}\\
+ &=&  \frac{1}{2}\Big[\Prob{\ExpPRF{F}{B_1} = 1} + \Prob{\ExpPRF{F}{B_2} = 1}\Big]
+\end{eqnarray*}
+\setlength{\mathindent}{1pt}
+\begin{flalign*}
+\frac{1}{2}\Big[\Prob{\ExpPRF{F}{B_1} = 1} &+ \Prob{\ExpPRF{F}{B_2} = 1}\Big] = \frac{1}{2}\Prob{\ExpFPSecHash{B}{A}=1} + \frac{1}{2}\epsilon\\
+2\Prob{\ExpPRF{F}{B_1} = 1}-1 &+ 2\Prob{\ExpPRF{F}{B_2} = 1}-1  = 2\Big[\Prob{\ExpFPSecHash{B}{A}=1} + \epsilon -1\Big]\\
+\frac{1}{2}\Big[\AdvPRF{B_1}{A} &+ \AdvPRF{B_2}{A}\Big]  =  \AdvFPSecHash{B}{A} + \epsilon -1\\
+\AdvFPSecHash{B}{A}  &=  \frac{1}{2}\Big[\AdvPRF{B_1}{A} + \AdvPRF{B_2}{A}\Big] + \Big[1-\epsilon\Big]
+\end{flalign*}
 

### 2016-06-20 Proofs.tex
Proof Task#2

@@
 \section{Proofs}
-\begin{theorem}
+\begin{theorem}\label{thm}
 Fix $n,k, m > 0$ and define a hash-based filter as in section \ref{sec:hbf}, except the hash functions are defined by $h_j(x) = \left( f_{K0}(x) + j\cdot g_{K1}(x)\right) \bmod m$.
@@
 Let $B_1, B_2$ be 2 adversaries with keys $K_1, K_2 \getsr \calK$ attacking the PRF advantage of $F \colon \calK \times \bits^m \sends \bits^m$ and $A$ be another adversary attacking the false positive game of hash-based filters, then
+
 \begin{equation}
@@
 
-\begin{eqnarray*}
-\Prob{\game{3}(A)=1} &=&\frac{1}{4}\Prob{\game{3}(A)=1|b_1=0, b_2=0} + \frac{1}{4}\Prob{\game{3}(A)=1|b_1=0, b_2=1}\\
-& + & \frac{1}{4}\Prob{\game{3}(A)=1|b_1=1, b_2=0}+ \frac{1}{4}\Prob{\game{3}(A)=1|b_1=1, b_2=1}\\
-& = & \frac{1}{4}\Prob{\game{0}(A)=1} + \frac{1}{4}\Prob{\game{2}(A)=1}\\
-&\nudge + & \frac{1}{4}\Prob{\game{3}(A)=1} + \frac{1}{4}\Prob{\game{2}(A)=1|b=1}\\
-& = & \frac{1}{4}\Prob{\game{0}(A)=1} + \frac{1}{4}\Prob{\game{2}(A)=1}\\
-&\nudge + & \frac{1}{4}\Prob{\game{2}(A)=1} + \frac{1}{4}\Prob{\game{2}(A)=1|b=1}\\
-& = & \frac{1}{4}\Prob{\game{0}(A)=1} + \frac{1}{2}\Prob{\game{2}(A)=1}\\
-&\nudge + & \frac{1}{4}\Prob{\game{2}(A)=1|b=1}\\
-& = & \frac{1}{4}\Prob{\game{0}(A)=1} + \frac{1}{2}\Big[\frac{1}{2}\Prob{\game{2}(A)=1|b=0}\\
-	& \nudge + & \frac{1}{2}\Prob{\game{2}(A)=1|b=1}\Big] + \frac{1}{4}\Prob{\game{2}(A)=1|b=1}\\
-& = & \frac{1}{4}\Prob{\game{0}(A)=1} + \frac{1}{4}\Prob{\game{0}(A)=1}\\
-& \nudge + & \frac{1}{4}\Prob{\game{2}(A)=1|b=1} + \frac{1}{4}\Prob{\game{2}(A)=1|b=1}\\
+\begin{eqnarray}
+\nonumber \Prob{\game{3}(A)=1} &=&\frac{1}{4}\Prob{\game{3}(A)=1|b_1=0, b_2=0} + \frac{1}{4}\Prob{\game{3}(A)=1|b_1=0, b_2=1}\\
+\nonumber & + & \frac{1}{4}\Prob{\game{3}(A)=1|b_1=1, b_2=0}+ \frac{1}{4}\Prob{\game{3}(A)=1|b_1=1, b_2=1}\\
+\nonumber & = & \frac{1}{4}\Prob{\game{0}(A)=1} + \frac{1}{4}\Prob{\game{2}(A)=1}\\
+\nonumber &\nudge + & \frac{1}{4}\Prob{\game{3}(A)=1} + \frac{1}{4}\Prob{\game{2}(A)=1|b=1}\\
+\nonumber & = & \frac{1}{4}\Prob{\game{0}(A)=1} + \frac{1}{4}\Prob{\game{2}(A)=1}\\
+\nonumber&\nudge + & \frac{1}{4}\Prob{\game{2}(A)=1} + \frac{1}{4}\Prob{\game{2}(A)=1|b=1}\\
+\nonumber& = & \frac{1}{4}\Prob{\game{0}(A)=1} + \frac{1}{2}\Prob{\game{2}(A)=1}\\
+\nonumber &\nudge + & \frac{1}{4}\Prob{\game{2}(A)=1|b=1}\\
+\nonumber & = & \frac{1}{4}\Prob{\game{0}(A)=1} + \frac{1}{2}\Big[\frac{1}{2}\Prob{\game{2}(A)=1|b=0}\\
+\nonumber	& \nudge + & \frac{1}{2}\Prob{\game{2}(A)=1|b=1}\Big] + \frac{1}{4}\Prob{\game{2}(A)=1|b=1}\\
+\nonumber & = & \frac{1}{4}\Prob{\game{0}(A)=1} + \frac{1}{4}\Prob{\game{0}(A)=1}\\
+\nonumber & \nudge + & \frac{1}{4}\Prob{\game{2}(A)=1|b=1} + \frac{1}{4}\Prob{\game{2}(A)=1|b=1}\\
 & = & \frac{1}{2}\Prob{\game{0}(A)=1} + \frac{1}{2}\Prob{\game{2}(A)=1|b=1}
-\end{eqnarray*}
+\end{eqnarray}
 
@@
 $B$ exactly simulates \game{3}(A).
-\setlength{\mathindent}{1pt}
-\begin{eqnarray*}
-\Prob{\ExpPRF{F}{B} = 1} &=&  \Prob{\game{3}(A)=1}\\
- &=& \frac{1}{2}\Prob{\game{0}(A)=1} + \frac{1}{2}\Prob{\game{2}(A)=1|b=1}\\
- &=&  \frac{1}{2}\Prob{\ExpFPSecHash{B}{A}=1} + \frac{1}{2}\epsilon\\
+%\setlength{\mathindent}{1pt}
+\begin{eqnarray}
+\nonumber\Prob{\ExpPRF{F}{B} = 1} &=&  \Prob{\game{3}(A)=1}\\
+\nonumber &=& \frac{1}{2}\Prob{\game{0}(A)=1} + \frac{1}{2}\Prob{\game{2}(A)=1|b=1}\\
+\nonumber &=&  \frac{1}{2}\Prob{\ExpFPSecHash{B}{A}=1} + \frac{1}{2}\epsilon\\
  & \mathrm{where}& \epsilon = (1-e^{-kn/m})^k = \text{FP-error in double hashing scheme}
-\end{eqnarray*}
-\setlength{\mathindent}{1pt}
-\begin{eqnarray*}
+\end{eqnarray}
+
+%\setlength{\mathindent}{1pt}
+\begin{eqnarray}
 \Prob{\ExpPRF{F}{B} = 1|d=1} &= \Prob{\ExpPRF{F}{B_1} = 1}\\
 \Prob{\ExpPRF{F}{B} = 1|d=0} &= \Prob{\ExpPRF{F}{B_2} = 1}
-\end{eqnarray*}
-\setlength{\mathindent}{1pt}
-\begin{eqnarray*}
-\Prob{\ExpPRF{F}{B} = 1} &=& \frac{1}{2}\Prob{\ExpPRF{F}{B} = 1|d=1}  + \frac{1}{2}\Prob{\ExpPRF{F}{B} = 1|d=0}\\
+\end{eqnarray}
+
+%\setlength{\mathindent}{1pt}
+\begin{eqnarray}
+\nonumber\Prob{\ExpPRF{F}{B} = 1} &=& \frac{1}{2}\Prob{\ExpPRF{F}{B} = 1|d=1}  + \frac{1}{2}\Prob{\ExpPRF{F}{B} = 1|d=0}\\
  &=&  \frac{1}{2}\Big[\Prob{\ExpPRF{F}{B_1} = 1} + \Prob{\ExpPRF{F}{B_2} = 1}\Big]
-\end{eqnarray*}
-\setlength{\mathindent}{1pt}
-\begin{flalign*}
-\frac{1}{2}\Big[\Prob{\ExpPRF{F}{B_1} = 1} &+ \Prob{\ExpPRF{F}{B_2} = 1}\Big] = \frac{1}{2}\Prob{\ExpFPSecHash{B}{A}=1} + \frac{1}{2}\epsilon\\
-2\Prob{\ExpPRF{F}{B_1} = 1}-1 &+ 2\Prob{\ExpPRF{F}{B_2} = 1}-1  = 2\Big[\Prob{\ExpFPSecHash{B}{A}=1} + \epsilon -1\Big]\\
-\frac{1}{2}\Big[\AdvPRF{B_1}{A} &+ \AdvPRF{B_2}{A}\Big]  =  \AdvFPSecHash{B}{A} + \epsilon -1\\
+\end{eqnarray}
+%\setlength{\mathindent}{1pt}
+\begin{flalign}
+\nonumber\frac{1}{2}\Big[\Prob{\ExpPRF{F}{B_1} = 1} &+ \Prob{\ExpPRF{F}{B_2} = 1}\Big] = \frac{1}{2}\Prob{\ExpFPSecHash{B}{A}=1} + \frac{1}{2}\epsilon\\
+\nonumber2\Prob{\ExpPRF{F}{B_1} = 1}-1 &+ 2\Prob{\ExpPRF{F}{B_2} = 1}-1  = 2\Big[\Prob{\ExpFPSecHash{B}{A}=1} + \epsilon -1\Big]\\
+\nonumber \frac{1}{2}\Big[\AdvPRF{B_1}{A} &+ \AdvPRF{B_2}{A}\Big]  =  \AdvFPSecHash{B}{A} + \epsilon -1\\
 \AdvFPSecHash{B}{A}  &=  \frac{1}{2}\Big[\AdvPRF{B_1}{A} + \AdvPRF{B_2}{A}\Big] + \Big[1-\epsilon\Big]
-\end{flalign*}
+\end{flalign}
 
 \end{proof}
+
+%***Theorem 2
+\begin{theorem}
+In Theorem \ref{thm}, let $h_j(x) = f_{K}(\langle j \rangle \concat x) \bmod m$, where $f$ is a PRF.
+This setting compared to the double hashing scheme ensures independence of hash functions.
+Let $B$ be an adversary attacking the PRF advantage of $F \colon \calK \times \bits^m \sends \bits^m$ and $A$ be another adversary attacking the false positive game of the modified hash-based filter, then
+
+\begin{equation}
+\AdvFPSecHash{B}{\distr{U}{n},A}  = 0.5\Big[\AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}\Big] + 1-\epsilon, \nudge \mathrm{where} \nudge \epsilon = (1-e^{-kn/m})^k
+\end{equation}
+\end{theorem}
+
+\begin{proof}
+
+\begin{figure}[h]
+\centering
+\fpage{0.6}{
+$\experimentv{Adversary \nudge B^{\calO}:}$\\
+$h_j \getsr \calO(j\times \cdot), \nudge \mathrm{where} \nudge j\in [k]$\\
+$S \getsr \distr{U}{n}$\\
+$M \getsr \Rep^{h_1, \cdots, h_k}(S)$\\
+$x \getsr A^{\QryOracle(\cdot)}(S)$\\
+if $x \not\in S \wedge \Qry^{h_1, \cdots, h_k}(M,x)=1$ then\\
+\nudge Ret 1\\
+Ret 0\\
+%
+\oracle{$\QryOracle(x)$}\\
+Ret $\Qry^{h_1, \cdots, h_k}(M,x)$
+}
+\caption{Adversary $B$ simulating modified hash-based filter}\label{fig:AdvB1}
+\end{figure}
+
+Adversary $B$ simulates $A^{'}s$ game as shown in Fig. \ref{fig:AdvB1}. When, $b=0$, $B$ exactly simulates $\ExpFPSecHash{B}{A}$.
+
+\begin{eqnarray*}
+\Prob{\ExpPRF{F}{B} = 1|b=0} &=&  \Prob{\ExpFPSecHash{B}{A}=1}
+\end{eqnarray*}
+
+When $b=1$, adversary $B$ attacks fp-priv game of the modified scheme.
+The false positive error of this scheme is calculated in section \ref{sec:fpe_calculation} using Lemma 4.1 of Kirch et.
+al.
+paper\cite{xxx}.
+
+\subsection{False positive error of hash-based filter with $h_j(x) = f_{K}(\langle j \rangle \concat x) \bmod m$ }\label{sec:fpe_calculation}
+
+In the proposed hash-based filter, since, $f_K$ is a PRF, each hash function $h_j$ is independent and uniformly distributed over $[m]$, and hence, satisifies condition 1 of Lemma 4.1\cite{xxx}.
+Conditions $2$ and $5$ are trivially satisfied.
+Fix $u \in U$, $r, r_1, r_2 \in [m]$ and $j, j_1, j_2 \in [k]$.
+
+\begin{eqnarray}
+\nonumber\Prob{\exists j | h_j(u)=r} & \leq & \sum_{j}\Prob{f_K(\langle j \rangle \concat x)=r}\\
+& = & \frac{k}{m}\\\nonumber & &\\
+\nonumber\Prob{h_{j1}(u) = r_1, h_{j2}(u) = r_2} & = & \Prob{h_{j1}(u) = r_1}\Prob{h_{j2}(u) = r_2 | h_{j1}(u) = r_1}\\
+\nonumber& = & \frac{1}{m} \times \frac{k}{m}\\
+&=&	 O\Big(\frac{1}{n^2}\Big)\\\nonumber & &\\
+\nonumber \Prob{\exists j | h_j(u)=r } & \geq & \sum_{j} \Prob{h_j(u)=r} - \sum_{j_1 < j_2}\Prob{h_{j1}(u) = r, h_{j2}(u) = r}\\
+& = & \frac{k}{m} - k^2O\Big(\frac{1}{n^2}\Big)\label{eq:1}\
+\end{eqnarray}
+
+For $\lambda = k^2/c, \nudge \mathrm{where} \nudge c=n/m$,  and $\gamma(n)=\frac{1}{n^2}$, $\Prob{r\in H(u)} = \Prob{\exists j \in {k}: h_j(u)=r }$ which satisfies condition 3 of Lemma 4.1. 
+\begin{eqnarray}
+\nonumber\Prob{r_1, r_2 \in H(u)} & \leq & \sum_{j_1 < j_2}\Prob{h_{j1}(u) = r_1, h_{j2}(u) = r_2} \\
+\nonumber& = & k^2O\Big(\frac{1}{n^2}\Big)\\
+& = & O\Big(\frac{1}{n^2}\Big)\label{eq:2}
+\end{eqnarray}
+From eqn.
+\ref{eq:2}, condition 4 of Lemma 4.1 is satisfied.
+Since, all conditions of the Lemma are satisfied, Theorem 4.1 can be applied to the proposed hash-based filter.
+Let $\calF$ is the false positive probability of the proposed scheme.
+\begin{eqnarray}
+\nonumber\lim_{n \rightarrow \infty}\Prob{\calF} & = & (1-e^{-\lambda/k})^k \\
+\nonumber& = & (1-e^{-\frac{k^2/c}{k}})^k\\
+& = & (1-e^{-\frac{kn}{m}})^k
+\end{eqnarray}
+Let $\epsilon = (1-e^{-\frac{kn}{m}})^k$.
+\begin{eqnarray}
+\nonumber\Prob{\ExpPRF{F}{B}=} & = & .5\Prob{\ExpPRF{F}{B}=1|b=0} + .5\Prob{\ExpPRF{F}{B}=1|b=1}\\
+\nonumber\Prob{\ExpPRF{F}{B}=} & = & .5\Prob{\ExpFPSecHash{B}{A}=1} + .5\Prob{\calF}\\
+\nonumber 2\Prob{\ExpPRF{F}{B}=}-1 & = & \Prob{\ExpFPSecHash{B}{A}=1} + \epsilon - 1\\
+\AdvFPSecHash{B}{A} & = & \AdvPRF{F}{B} + [1-\epsilon]
+\end{eqnarray}
+\end{proof}

### 2016-06-22 filters.tex
cheers
Proof of task#1 and minor changes
Notes

@@
 %
-The randomized \emph{hash-sampling} algorithm~$\Hash$ samples a size~$k$ family of functions~$\mathcal{H}=\{h_1,h_2,\ldots,h_k\}$ where each $h_i \in  \mathrm{Func}(U,\{0,1,\ldots,m-1\})$.
-We write $\mathcal{H} \getsr \Hash$ for this operation.
+The randomized \emph{hash-sampling} algorithm~$\Hash$ samples a
+size~$k$  family of functions~$\mathcal{H}=\{h_1,h_2,\ldots,h_k\}$
+where each $h_i \in  \mathrm{Func}(U,[m])$.  We write $\mathcal{H}
+\getsr \Hash$ for this operation.
 %
@@
 %
-The determinisitc query algorithm $\Qry\colon \Sigma^m \times U \rightarrow \bits$ takes a representation $M$ and an element $x \in U$ and returns a bit.  
+The deterministic query algorithm $\Qry\colon \Sigma^m \times U
+\rightarrow \bits$ takes a representation $M$ and an element $x \in
+U$ and returns a bit.
 %
-We assume that both $\Rep$ and $\Qry$ have the following blackbox access to the functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$.
+We assume that both $\Rep$ and $\Qry$ have blackbox access to the
+functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$.
 %which we denote by writing~$\mathcal{H}$ as a superscript.
@@
 %We write $M \gets \Rep(S)$ and $b \gets \Qry(M,x)$ for the execution of the representation and query algorithms, respectively.
-For correctness, we demand that for all~$S$ of size~$n$, we have that for all $x \in S, \Prob{\Qry(\Rep(S),x)=1}=1$, where the probability is over the coins of $\Hash$ and $\Rep$.
+For correctness, we demand that for all~$S$ of size~$n$ and all $x
+\in S$, it holds that $\Prob{\Qry(\Rep(S),x)=1}=1$, where the
+probability is over the coins of $\Hash$ and~$\Rep$.
 
-%\heading{Discusssion.}
+%\heading{Discussion.}
 This syntax captures classical Bloom filters by setting~$\Sigma=\bits$,  and defining $\Rep,\Qry$ in the obvious way.
@@
 
-\heading{FP-security of hash-based filters.} \tsnote{NY give it in the private hash setting (sort of); but, intuitively, it should be hard to find false-positives even if you know that MD5 or SHA-x are the hash functions.
-Not totally sure how to capture this intuition nicely.}
-The traditional notion of soundness for a Bloom filter captures the difficulty of finding false-positives when the attacker is non-adaptive.
-Following NY, we consider soundness against adaptive adversaries.
-But we further generalize to allow for settings in which the attacker may have some a priori knowledge about the contents of~$S$.
-(The Niedermaier et al.~\cite{xxx} attacks, for example, exploit knowledge about the distribution of German last names.)   In particular, our notions take as input an explicit distribution $\distr{U}{n}$ over $[U]^n$.
+\heading{FP-security of hash-based filters.} \tsnote{NY give it in
+the private hash setting (sort of); but, intuitively, it should be
+hard to find false-positives even if you know that MD5 or SHA-x are
+the hash functions.  Not totally sure how to capture this intuition
+nicely.} \jnote{Not sure I agree. First of all, if $\epsilon$ is not
+negligible then a random element is a false positive with noticeable
+probability. Beyond that, I think that intuitively it makes sense
+that if you want false positives to be hard to find then you need to
+make the hash functions secret.} The traditional notion of soundness
+for a Bloom filter captures the difficulty of finding false
+positives when the attacker is non-adaptive. Following NY, we
+consider soundness against adaptive adversaries. But we further
+generalize to allow for settings in which the attacker may have some
+a priori knowledge about the contents of~$S$. (The Niedermaier et
+al.~\cite{xxx} attacks, for example, exploit knowledge about the
+distribution of German last names.)   In particular, our notions
+take as input an explicit distribution $\distr{U}{n}$ over~$[U]^n$.
 
-In Figure~\ref{fig:fp-filter} we give three distinct notions, characterized by what access the adversary has to the underlying hash functions used by the filter.
-In the top notion, the hash functions are secret.
-This is the setting addressed by NY, and it capture applications in which the ``hash functions'' are (say) secretly keyed PRFs, and in which no explicit, external interface to these is surfaced.
+\jknote{We also want to capture the fact that finding the first
+false positive should not make it any easier to find subsequent
+false positives. This is not really captured by the Naor paper,
+either (at least not directly, though it may end up being implied by
+their definition).}
+
+In Figure~\ref{fig:fp-filter} we give three distinct notions,
+characterized by what access the adversary has to the underlying
+hash functions used by the filter.  In the top notion, the hash
+functions are secret.  This is the setting addressed by NY, and it
+captures applications in which the hash functions are (say) secretly
+keyed PRFs, and in which no explicit, external interface to these is
+surfaced.
 %
@@
 %
-The middle notion is a compromise: it makes the hash functions public, but assumes that the adversary only accesses them in a black-box manner.
-That is, the adversary does not exploit structural features of the hash functions in its attack.
-This notion makes it easy to track the query complexity of an attack.
+The middle notion is a compromise: it makes the hash functions
+public, but assumes that the adversary only accesses them in a
+black-box manner.  That is, the adversary does not exploit
+structural features of the hash functions in its attack.  This
+notion makes it easy to track the query complexity of an attack, and
+also allows us to capture constructions in the random-oracle model.
 
-For each experiment, we define an associated advantage notion.  Namely, given an $(n,k,m)$-filter~$B=(\Hash,\Rep,\Qry)$, distribution~$\distr{U}{n}$ and adversary~$A$, we define:
+For each experiment, we define an associated advantage
+notion.Namely, given an $(n,k,m)$-filter~$B=(\Hash,\Rep,\Qry)$,
+distribution~$\distr{U}{n}$ and adversary~$A$, we define:
 \begin{align*}
@@
 \end{align*}
-The probabilities are over the coins of the indicated experiment, and he coins of the adversary.
-In all experiments, we track time-complexity~$t$ of~$A$, as well as the number of set-membership ($\QryOracle$ oracle) queries~$q_{\mathrm{sm}}$ that it makes.
-In the second, we also track the number of hash-queries $q_{\mathrm{h}}$ that the adversary makes.
+The probabilities are over the coins of the indicated experiment,
+and the coins of the adversary.   In all experiments, we track the
+time-complexity~$t$ of~$A$, as well as the number of set-membership
+($\QryOracle$ oracle) queries~$q_{\mathrm{sm}}$ that it makes.   In
+the second, we also track the number of hash-queries
+$q_{\mathrm{h}}$ that the adversary makes.
+
+\jnote{How do we want to define a ``secure'' Bloom filter (even
+informally)? Do we want to say that the probability of finding a
+false positive is negligible? Or that if we set the FP rate to
+$\epsilon$ then the best an attacker can do with $q$ hash queries is
+$1-(1-\epsilon)^q$ plus negligible? One thing that is nice about the
+NY notion is that you get a ``clean'' definition of security: no
+matter how many FPs the attacker has found so far, the probability
+that it can output a fresh FP is still $\epsilon$.}
+
+\jnote{What parameters are needed to get negligible $\epsilon$? Are
+they reasonable in practice?}
 
@@
 $S \getsr \distr{U}{n}$\\
-$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
+$h_1,\ldots,h_k \getsr \Hash$\\
+$\HashOracle = (h_1, \ldots, h_k)$\\
 $M \getsr \Rep^{\HashOracle}(S)$\\
@@
 $S \getsr \distr{U}{n}$\\
-$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
+$h_1,\ldots,h_k \getsr \Hash$\\
+$\HashOracle = (h_1, \ldots, h_k)$\\
 $M \gets \Rep^{\HashOracle}(S)$\\
@@
 Ret $h_i(x)$\\
-}
-}
-\caption{False-positive security (soundness) for an $(n,k,m)$-filter~$B$ with private hash functions (top), black-box queriable hash functions (middle), and public hash functions (bottom).  }
-\label{fig:fp-filter}
+} } \caption{False-positive security (soundness) for an
+$(n,k,m)$-filter~$B$ with private hash functions (top), black-box
+queriable hash functions (middle), and public hash functions
+(bottom). \jnote{Could also consider not giving $S$ to the
+adversary.} } \label{fig:fp-filter}
 \end{figure}
@@
 $S \getsr \distr{U}{n}$\\
-$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-$M \gets \Rep^{\HashOracle}(S)$\\
+$h_1,\ldots,h_k \getsr \Hash$\\
+$\HashOracle = (h_1, \ldots, h_k)$\\
+$M \getsr \Rep^{\HashOracle}(S)$\\
 $x \getsr A^{\QryOracle}()$\\
@@
 $ S \getsr \distr{U}{n}$\\
-$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-$M \gets \Rep^{\HashOracle}(S)$\\
+$h_1,\ldots,h_k \getsr \Hash$\\
+$\HashOracle = (h_1, \ldots, h_k)$\\
+$M \getsr \Rep^{\HashOracle}(S)$\\
 $x \getsr A^{\QryOracle,\HashOracle}()$\\
@@
 $ S \getsr \distr{U}{n}$\\
-$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-$M \gets \Rep^{\HashOracle}(S)$\\
+$h_1,\ldots,h_k \getsr \Hash$\\
+$\HashOracle = (h_1, \ldots, h_k)$\\
+$M \getsr \Rep^{\HashOracle}(S)$\\
 $x \getsr A^{\QryOracle}(\{h_1,h_2,\ldots,h_k\})$\\
@@
 
-\heading{Security in multiple-server settings.
-}  In this section, we consider security notions for settings in which there may be multiple servers, each holding a filter representation of a set.
-To allow for each server to embed server-specific information into its representation, we abstract the servers as $B_1,B_2,\ldots,B_\ell$ where each $B_i=(\Hash_i,\Rep_i,\Qry_i)$ is an $(n,k,m)$-filter.
-\tsnote{Still some kinks to be ironed out though.
-The current notions sample fresh hash functions for each server.
-But in (say) the Squid setting, the same hash functions are used across all Squid instances...
-maybe it suffices, for that setting, to say that the $\Hash_i$ are all the same, and each simply returns a fixed set of~$k$ hash functions (i.e., deterministic).}  To model insider attacks, we give the adversary the ability to corrupt (adaptively) instances of the filter.
-Such attacks capture P2P settings, in which the adversary may join the network as a peer.
+\heading{Security in multiple-server settings. }  \jnote{What is the
+goal here? If they don't share hash functions, I'm not sure what is
+gained by considering this definition.} In this section, we consider
+security notions for settings in which there may be multiple
+servers, each holding a filter representation of a set.  To allow
+for each server to embed server-specific information into its
+representation, we abstract the servers as $B_1,B_2,\ldots,B_\ell$
+where each $B_i=(\Hash_i,\Rep_i,\Qry_i)$ is an $(n,k,m)$-filter.
+\tsnote{Still some kinks to be ironed out though.  The current
+notions sample fresh hash functions for each server.  But in (say)
+the Squid setting, the same hash functions are used across all Squid
+instances... maybe it suffices, for that setting, to say that the
+$\Hash_i$ are all the same, and each simply returns a fixed set
+of~$k$ hash functions (i.e., deterministic).} To model insider
+attacks, we give the adversary the ability to corrupt (adaptively)
+instances of the filter.  Such attacks capture P2P settings, in
+which the adversary may join the network as a peer.
 

### 2016-06-22 intro.tex
Notes

@@
+\jnote{Are we being too specific by focusing on hash-based
+set-membership only? It would be nice to give general definitions
+that apply to arbitrary data structures (constructed in arbitrary
+ways) and then only later specialized to hash-based Bloom filters.}
+
 \section{Introduction}
-We revisit the formalization of Bloom filters~\cite{xxx} and closely related data structures as primitives with explicit security goals.
-Recently, Naor and Yogev~\cite{xxx} (hereafter NY) gave such a formalization, providing syntax for a generalized abstraction of Bloom filters, as well as casting the classical Bloom filter soundness condition as a security experiment admiting adaptive adversaries.
-To briefly summarize, a Bloom filter is a data structure for compactly representing a set~$\mathcal{S}$ in a way that supports constant time responses to set-membership queries.
-The representation of~$\mathcal{S}$ is an indexed array~$M$ of~$m$-bits, all initally set to 0.
-To insert $x \in \mathcal{S}$ into~$M$, one computes indices $h_1(x),h_2(x),\ldots,h_k(x)$ where each $h_i \colon \mathcal{U} \to \{0,1,\ldots m-1\}$ maps from a universe~$\mathcal{U}$ (which contains $\mathcal{S}$) to indices of~$M$.
-The bits at positions $h_1(x),h_2(x),\ldots,h_k(x)$ are set to 1; if a bit is already 1, due to inserting some previous element of~$\mathcal{S}$, then it is left alone.
-After all elements of~$\mathcal{S}$ have been inserted, the resulting bit-array~$M$ is taken as the representation.
-To test if $y \in \mathcal{S}$, one checks if  $(h_1(y)=1 \wedge h_2(y)=1 \wedge \cdots \wedge h_k(y)=1)$, returning ``yes'' if so, and ``no'' otherwise.
-Bloom filters are correct, in the sense that if $y \in \mathcal{S}$, the set-membership test always returns ``yes''.
-The classical soundness condition asserts that for all $y \notin\mathcal{S}$,  $\Prob{h_1,h_2,\ldots,h_k \getsr \mathrm{Func(\mathcal{U},\mathbb{Z}_m)}\colon h_1(y)=1 \wedge h_2(y)=1 \wedge \cdots \wedge h_k(y)=1} \leq \epsilon$ where $\epsilon$, the false-positive rate, is a parameter of the Bloom filter.
-(The values of~$\epsilon,m,k,|\mathcal{S}|$ are related in a well known way.)  NY recast this soundness condition as a game in which an adversary~$A$ is given~$\mathcal{S}$ and an oracle for set-membership queries, and it attempts to find a false-positive.
-The fact that~$A$ can \emph{adapt} its queries and its output based on what it learns from the set-membership oracle is the key definitional constribution of NY.
+We revisit the formalization of Bloom filters~\cite{xxx} and closely
+related data structures as primitives with explicit security goals.
+Recently, Naor and Yogev~\cite{xxx} (hereafter NY) gave such a
+formalization, providing syntax for a generalized abstraction of
+Bloom filters, as well as casting the classical Bloom filter
+soundness condition as a security experiment admiting adaptive
+adversaries.  To briefly summarize, a Bloom filter is a data
+structure for compactly representing a set~$\mathcal{S}$ in a way
+that supports constant-time responses to set-membership queries. The
+representation of~$\mathcal{S}$ is an bit-array~$M$ of length~$m$,
+all initially set to~0.  To insert $x \in \mathcal{S}$ into~$M$, one
+computes indices $h_1(x),h_2(x),\ldots,h_k(x)$ where each $h_i
+\colon \mathcal{U} \to \{0,1,\ldots m-1\}$ maps from a
+universe~$\mathcal{U}$ (which contains $\mathcal{S}$) to indices
+of~$M$.  The bits at positions $h_1(x),h_2(x),\ldots,h_k(x)$ are set
+to 1; if a bit is already 1, due to inserting some previous element
+of~$\mathcal{S}$, then it is left alone.  After all elements
+of~$\mathcal{S}$ have been inserted, the resulting bit-array~$M$ is
+taken as the representation.  To test if $y \in \mathcal{S}$, one
+checks if \[(M[h_1(y)]=1 \wedge M[h_2(y)]=1 \wedge \cdots \wedge
+M[h_k(y)]=1),\] returning ``yes'' if so, and ``no'' otherwise. Bloom
+filters are correct, in the sense that if $y \in \mathcal{S}$, the
+set-membership test always returns ``yes''.  The classical soundness
+condition asserts that for all $\mathcal{S}$ and any $y
+\notin\mathcal{S}$, we have $\Prob{h_1,h_2,\ldots,h_k \getsr
+\mathrm{Func}(\mathcal{U},[m])\colon M[h_1(y)]=1 \wedge \cdots
+\wedge M[h_k(y)]=1} \leq \epsilon$ where $\epsilon$, the
+false-positive rate, is a parameter of the Bloom filter.  (The
+values of~$\epsilon,m,k$, and $|\mathcal{S}|$ are related in a
+well-known way.) NY recast this soundness condition as a game in
+which an adversary~$A$ is given~$\mathcal{S}$ and an oracle for
+set-membership queries, and it attempts to find a false positive.
+The fact that~$A$ can \emph{adapt} its queries and its output based
+on what it learns from the set-membership oracle is the key
+definitional distribution of~NY.
 
-Bloom filters have a broad range of practical applications, for example, in content-distribution networks, large database query processing, routing algorithms for peer-to-peer networks, protocols for establishing linkages between medical-record databases, fair routing of TCP packets, Bitcoin wallet synchonization.
-\tsnote{need citations}  Given that NY is addressing such a useful real-world object, we find their formalism, both the syntax and security notions, to be less precise and useful than one would want.
-Let us explain.
+Bloom filters have a broad range of practical applications, for
+example, in content-distribution networks, large database query
+processing, routing algorithms for peer-to-peer networks, protocols
+for establishing linkages between medical-record databases, fair
+routing of TCP packets, Bitcoin wallet synchonization. \tsnote{need
+citations}  Given that NY is addressing such a useful real-world
+object, we find their formalism, both the syntax and security
+notions, to be less precise and useful than one would want.  Let us
+explain.
 
-Syntactically, NY says a Bloom filter (with a steady representation) is a pair of algorithms $\mathbf{B}=(\mathbf{B}_1, \mathbf{B}_2)$.
-The setup algorithm~$\mathbf{B}_1$ is randomized, and on input a set~$\mathcal{S}$ it returns a representation~$M$ (from some undefined, implicit set of representations).
-The query algorithm~$\mathcal{B}_2$ is determinisic, and on input a representation~$M$ and an element~$x \in \mathcal{U}$, it returns a bit.
-For correctness they make the classical demand, that for all $x \in \mathcal{S}$ we have $\Prob{\mathbf{B}_2(\mathbf{B}_1(S),x)=1}=1$.
-For soundness, adversary~$A$ plays the following game, ``Adversarial-resilient Bloom Filter with a steady representation''.
-First, $M \getsr \mathbf{B}_1(\mathcal{S})$.
-Then the adversary is given the set~$\mathcal{S}$ and may make queries $x_1,x_2,\ldots,x_q$ to an oracle for $\mathbf{B}_2(M,\cdot)$.
-At the end of its execution, the adversary outputs~$x^*$ and wins the game if (1) $x^* \not\in \mathcal{S} \cup \{x_1,x_2,\ldots,x_q\}$, and (2) $\mathbf{B}_2(M,x^*)=1$.
+Syntactically, NY says a Bloom filter (with a steady representation)
+is a pair of algorithms $\mathbf{B}=(\mathbf{B}_1, \mathbf{B}_2)$.
+The setup algorithm~$\mathbf{B}_1$ is randomized, and on input a
+set~$\mathcal{S}$ it returns a representation~$M$ (from some
+undefined, implicit set of representations).  The query
+algorithm~$\mathcal{B}_2$ is deterministic, and on input a
+representation~$M$ and an element~$x \in \mathcal{U}$, it returns a
+bit.  For correctness they make the classical demand, that for all
+$x \in \mathcal{S}$ we have
+$\Prob{\mathbf{B}_2(\mathbf{B}_1(\mathcal{S}),x)=1}=1$.  For
+soundness, adversary~$A$ plays the following game,
+``Adversarial-resilient Bloom Filter with a steady representation''.
+First, $M \getsr \mathbf{B}_1(\mathcal{S})$. \jnote{Where does the
+set come from? Is it random? Adversarially chosen?} Then the
+adversary is given the set~$\mathcal{S}$ and may make queries
+$x_1,x_2,\ldots,x_q$ to an oracle for $\mathbf{B}_2(M,\cdot)$.  At
+the end of its execution, the adversary outputs~$x^*$ and wins the
+game if (1) $x^* \not\in \mathcal{S} \cup \{x_1,x_2,\ldots,x_q\}$,
+and (2) $\mathbf{B}_2(M,x^*)=1$.
 
-First, we note that the security notion forbids~$A$ to win if it outputs $x^* \in \{x_1,x_2,\ldots,x_q\}$, even if one of these was a false-positive.  
+First, we note that the security notion forbids~$A$ to win if it
+outputs $x^* \in \{x_1,x_2,\ldots,x_q\}$, even if one of these was a
+false positive. \jnote{We discussed this on the phone, but let me
+put it in writing here. I think this is actually a reasonable choice
+because it captures the notion that ``even after finding some false
+positives, it remains hard to find additional false positives.''
+Note that in practice finding false positives is ``easy'' since
+$\epsilon$ might be $1/1000$ rather than negligible.}
 %
-Second, we note that the NY syntax does not capture the size of~$M$ as a parameter; the surrounding text does say that $\mathbf{B}_1$ ``outputs a compressed representation [of $\mathcal{S}$] $\mathbf{B}_1(\mathcal{S})=M$'' but what exactly this means is never addressed.
-The formal syntax admits $\mathbf{B}_1(\mathcal{S})=\mathcal{S}$ and $\mathbf{B}_2(\mathcal{S},x)=1 \Leftrightarrow x \in \mathcal{S}$, which is also trivially secure by their definition.
-These are both small, but important complaints.
-But a larger complaint, and one that is much harder to see, is that that it is not clear that the NY formalism actually captures real world Bloom filters.
+Second, we note that the NY syntax does not capture the size of~$M$
+as a parameter \jnote{I think this is also reasonable; typically
+security is defined without regard for efficiency}; the surrounding
+text does say that $\mathbf{B}_1$ ``outputs a compressed
+representation [of $\mathcal{S}$] $\mathbf{B}_1(\mathcal{S})=M$''
+but what exactly this means is never addressed.  The formal syntax
+admits $\mathbf{B}_1(\mathcal{S})=\mathcal{S}$ and
+$\mathbf{B}_2(\mathcal{S},x)=1 \Leftrightarrow x \in \mathcal{S}$,
+which is also trivially secure by their definition.  These are both
+small, but important complaints.  But a larger complaint, and one
+that is much harder to see, is that that it is not clear that the NY
+formalism actually captures real world Bloom filters.
 
-In particular, say that $\mathbf{B}_1$ is implementing a classic Bloom filter.
-Then the hash functions $h_1,h_2,\ldots,h_k$ are either sampled from some implicit family~$\mathcal{H}$ by~$\mathbf{B}_1$ (recall that this algorithm is randomized), or they are hard-coded into the description of~$\mathbf{B}_1$.
-Let's assume the former, for the moment.
-In order for~$\mathbf{B}_2$ to be able to respond to set-membership queries, it must have $h_1,h_2,\ldots,h_k$ as well.
-Since~$\mathbf{B}_2$ receives only the representation~$M$ as input, it must be the case that $h_1,h_2,\ldots,h_k$ are encoded into~$M$ somehow.
-But the text strongly suggests, in several places, that~$M$ does \emph{not} include these.
-Both NY and classical analysis of Bloom filters speak of the number of bits used to represent the set~$\mathcal{S}$: the classical analysis means only the number of bits in the actual array, and NY make comparisons throughout between the number of bits~$m$ used by their instantiations and the classical bounds.
-Morevover, the Bloom filter they construct in one of their main positive results clearly \emph{does not} count as part of the representation size the hash functions used to indicate array locations.
-Thus, if we assume that $\mathbf{B}_1$ is sampling $h_1,h_2,\ldots,h_k$, it seems that their formalization fails to capture the basic Bloom filter construction; at best, it is hard to see clearly that it does.
+In particular, say we implement a classic Bloom filter.  Then the
+hash functions $h_1, h_2, \ldots, h_k$ are either sampled from some
+family~$\mathcal{H}$ by~$\mathbf{B}_1$ (recall that this algorithm
+is randomized), or they are hard-coded into the description
+of~$\mathbf{B}_1$.  Let's assume the former for the moment.  In
+order for~$\mathbf{B}_2$ to be able to respond to set-membership
+queries, it must have $h_1,h_2,\ldots,h_k$ as well.
+Since~$\mathbf{B}_2$ receives only the representation~$M$ as input,
+it must be the case that $h_1,h_2,\ldots,h_k$ are encoded into~$M$
+somehow.  But the text strongly suggests, in several places,
+that~$M$ does \emph{not} include these.  Both NY and classical
+analysis of Bloom filters speak of the number of bits used to
+represent the set~$\mathcal{S}$: the classical analysis means only
+the number of bits in the actual array, and NY make comparisons
+throughout between the number of bits~$m$ used by their
+instantiations and the classical bounds. Moreover, the Bloom filter
+they construct in one of their main positive results clearly
+\emph{does not} count as part of the representation size the hash
+functions used to indicate array locations.
+%Thus, if we assume that
+%$\mathbf{B}_1$ is sampling $h_1,h_2,\ldots,h_k$, it seems that their
+%formalization fails to capture the basic Bloom filter construction;
+%at best, it is hard to see clearly that it does.
 
-On the other hand, we can assume that the hash functions are implicitly hard-coded into~$\mathbf{B}_1$ (and $\mathbf{B}_2$).
-Then we can treat~$\mathbf{B}_1$ as deterministic, since it will simply carry out the steps required to populate an array using these hash functions, and output the array~$M$ as the representation.
-If we apply Kirchoff's rule, the descriptions of~$\mathbf{B}_1,\mathbf{B}_2$ are known to the adversary, who is also provided with~$\mathcal{S}$.
-In this case, the adversary can compute~$M$ itself, as well as test for false-positives itself.
-So it isn't clear how the security notion helps to reason about difficulty of finding a false-positive.
-Moreover, NY stresses (at least once) that the representation is \emph{not} given to the adversary in their notions.
-So it seems unlikely that they intended for $h_1,h_2,\ldots,h_k$ to be hard-coded into the algorithms.
+\jnote{FWIW, I think the classical description of Bloom filters has
+the same problem. I.e., if the hash functions are not fixed, then
+their description should be counted as part of the length of the
+data structure. On the other hand, if they are fixed, then the
+false-positive rate is not well-defined (since there is no
+probability space to speak of). So in that sense, NY just carried
+over the problem from the classical literature.}
 
-Continuing on this point, it seems that the coins of~$\mathbf{B}_1$ (whatever their use) are intended to be kept secret from the adversary.
-Thus, to the extent that it addresses real Bloom filters at all, the NY security notion only addresses applications in which the representation is created using secret coins.
-But many real-world applications of Bloom filters have no secrets.
-NY point to web proxies, which use Bloom filters to compactly represent the objects they store locally, as motivation for their work.
-But real web proxies like Squid~\cite{xxx} do \emph{not} use secrets in their Bloom filters.
-They use the basic Bloom filter with four hash functions, defined as follows: $h_1(x) = \mathrm{MD5}(x)[0,\ldots,31]$, $h_2(x)=\mathrm{MD5}(x)[32,\ldots,63]$, $h_3(x)=\mathrm{MD5}(x)[64,\ldots,95]$, and $h_4(x)=\mathrm{MD5}(x)[96,\ldots,127]$.
-Likewise, there are no secrets in the Bloom filters used by Google's BigTable~\cite{xxx}, HBase~\cite{xxx}, \tsnote{make an impressive list.}  There are applications in which the proposed Bloom filter instantiations do use secretly keyed hash functions, e.g.
-$h_j(x) = (f(K_0,x) + j\cdot g(K_1,x))\bmod m$, where $j\in[1,k]$, $m$ is the number of bits in the array, and where $f,g$ are PRFs keyed by secrets $K_0,K_1$.
-This particular ``encrypted Bloom filter'' instantiation was suggested for use in efficient linking of records across separate medical record databases~\cite{xxx}.
-(It was subsequently shown not to be secure by Niedermeier et al.~\cite{xxx}, where a clever use of frequency analysis recovered the last names of patients given access only to the Bloom filter array.\tsnote{This shows that false-positive security and privacy (whatever it is) are orthogonal, since I'm pretty sure this ``encrypted'' bloom filter resists FPs.})  In any case, it is clear that the NY definition does not capture the most widely used applications of Bloom filters, e.g.
-CDN summary caches, P2P network routing algorithms, etc.
-\tsnote{Could also point out that their positive results use constructions that have secret keys, and these are unlikely to be of any use in major applications like CDNs or P2P networks.
-But maybe the horse is sufficiently beaten by now...}
+On the other hand, assume the hash functions are implicitly
+hard-coded into~$\mathbf{B}_1$ (and $\mathbf{B}_2$). Then we can
+treat~$\mathbf{B}_1$ as deterministic, since it will simply carry
+out the steps required to populate an array using these hash
+functions, and output the array~$M$ as the representation.  If the
+descriptions of~$\mathbf{B}_1,\mathbf{B}_2$ are known to the
+adversary, who is also provided with~$\mathcal{S}$, then the
+adversary can compute~$M$ itself, as well as test for false
+positives itself. So it isn't clear how the security notion helps to
+reason about difficulty of finding a false-positive. Moreover, NY
+stresses (at least once) that the representation is \emph{not} given
+to the adversary in their notions.  So it seems unlikely that they
+intended for $h_1,h_2,\ldots,h_k$ to be hard-coded into the
+algorithms. \jnote{Perhaps it is reasonable to consider a definition
+in which the set is not given to the adversary?}
+
+Continuing on this point, it seems that the coins of~$\mathbf{B}_1$
+(whatever their use) are intended to be kept secret from the
+adversary.  Thus, to the extent that it addresses real Bloom filters
+at all, the NY security notion only addresses applications in which
+the representation is created using secret coins.  But many
+real-world applications of Bloom filters have no secrets.  NY point
+to web proxies, which use Bloom filters to compactly represent the
+objects they store locally, as motivation for their work.  But real
+web proxies like Squid~\cite{xxx} do \emph{not} use secrets in their
+Bloom filters.  They use the basic Bloom filter with four hash
+functions, defined as follows: $h_1(x) =
+\mathrm{MD5}(x)[0,\ldots,31]$,
+$h_2(x)=\mathrm{MD5}(x)[32,\ldots,63]$,
+$h_3(x)=\mathrm{MD5}(x)[64,\ldots,95]$, and
+$h_4(x)=\mathrm{MD5}(x)[96,\ldots,127]$.  Likewise, there are no
+secrets in the Bloom filters used by Google's BigTable~\cite{xxx},
+HBase~\cite{xxx}, \tsnote{make an impressive list.}  There are
+applications in which the proposed Bloom filter instantiations do
+use secretly keyed hash functions, e.g. $h_j(x) = (f(K_0,x) + j\cdot
+g(K_1,x))\bmod m$, where $j\in[1,k]$, $m$ is the number of bits in
+the array, and where $f,g$ are PRFs keyed by secrets $K_0,K_1$.
+This particular ``encrypted Bloom filter'' instantiation was
+suggested for use in efficient linking of records across separate
+medical record databases~\cite{xxx}.  (It was subsequently shown not
+to be secure by Niedermeier et al.~\cite{xxx}, where a clever use of
+frequency analysis recovered the last names of patients given access
+only to the Bloom filter array.\tsnote{This shows that
+false-positive security and privacy (whatever it is) are orthogonal,
+since I'm pretty sure this ``encrypted'' bloom filter resists FPs.})
+In any case, it is clear that the NY definition does not capture the
+most widely used applications of Bloom filters, e.g. CDN summary
+caches, P2P network routing algorithms, etc. \tsnote{Could also
+point out that their positive results use constructions that have
+secret keys, and these are unlikely to be of any use in major
+applications like CDNs or P2P networks.  But maybe the horse is
+sufficiently beaten by now...}
 
@@
 
-We generalize this syntax to hash-based filters that are mutable, in the sense that they allow for updating of the representation.
-This allows us to capture counting Bloom filters, spectral Bloom filters, stable Bloom filters, count-min sketches, and other compact set respresentation data structures...
+We generalize this syntax to hash-based filters that are mutable
+\jnote{I find ``mutable'' a slightly awkward term,  maybe because it
+makes me think of mutability in the context of programming
+languages. In much data structures literature, this is called the
+``dynamic'' case, in contrast to the ``static'' case.}, in the sense
+that they allow for updating of the representation. This allows us
+to capture counting Bloom filters, spectral Bloom filters, stable
+Bloom filters, count-min sketches, and other compact set
+representation data structures...
 

### 2016-06-22 tasks_and_ideas.tex
no message
notes

@@
 \begin{itemize}
-\item Prove that a Bloom filter using hash functions defined by $h_j(x) = \left( f_{K0}(x) + j\cdot g_{K1}(x)\right) \bmod m$, for secret keys $K0,K1$, is FP-secure when either~$f$ or~$g$ is a secure PRF.
-(This is a real proposal, see the intro.)  Interesting that these $h_j$ are not independent, even if $f_{K0},g_{K1}$ are replaced by independent random functions, whereas the traditional BF false positive analysis treats the $h_j$ as independent.
-I wonder if the analysis for determining the number of hash functions still holds when the $h_j$ are dependent?
-Note: definitely not in general, just consider $h_j$ a fixed function for all $j$; but it's an interesting question to ask for this particular kind of dependence.
-(Should check the Kirsh, Mitzenmacher paper first; they probably address this.
-\tsnote{They show that two random functions, combined in this way (for a prime~$m$), suffices.
-No increase in asymptotic FP probability.
-They also argue that construction of $h_j$ is thus better than one can do using generic pairwise-independent $h_j$.
-They also point out the difference between the FP \emph{probability} (the probability that a particular $x \not\in S$ causes a FP) and the FP \emph{rate} (the average FP probability over $x \not\in S$), which I hadn't really considered before.
-})
+\item Prove that a Bloom filter using hash functions defined by
+    $h_j(x) = \left( f_{K0}(x) + j\cdot g_{K1}(x)\right) \bmod
+    m$, for secret keys $K0,K1$, is FP-secure when either~$f$
+    or~$g$ is a secure PRF.  (This is a real proposal, see the
+    intro.)  Interesting that these $h_j$ are not independent,
+    even if $f_{K0},g_{K1}$ are replaced by independent random
+    functions, whereas the traditional BF false positive
+    analysis treats the $h_j$ as independent.  I wonder if the
+    analysis for determining the number of hash functions still
+    holds when the $h_j$ are dependent?  Note: definitely not in
+    general, just consider $h_j$ a fixed function for all $j$;
+    but it's an interesting question to ask for this particular
+    kind of dependence.  (Should check the Kirsh, Mitzenmacher
+    paper first; they probably address this. \tsnote{They show
+    that two random functions, combined in this way (for a
+    prime~$m$), suffices.  No increase in asymptotic FP
+    probability.  They also argue that construction of $h_j$ is
+    thus better than one can do using generic
+    pairwise-independent $h_j$.  They also point out the
+    difference between the FP \emph{probability} (the
+    probability that a particular $x \not\in S$ causes a FP) and
+    the FP \emph{rate} (the average FP probability over $x
+    \not\in S$), which I hadn't really considered before. })
 
-\item Show the same thing for the simpler $h_j(x) = f_{K}(\langle j \rangle \concat x) \bmod m$.
-This, by the way, does give independent $h_j$ when you replace~$f_K$ by a random function.
-(The previous ``double hashing'' construction seems clunky if you're going to assume you have a PRF and secret keys; is this just an example of people in one domain naively using a tool developed for another?
-)
+\item Show the same thing for the simpler $h_j(x) =
+    f_{K}(\langle j \rangle \concat x) \bmod m$.  This, by the
+    way, does give independent $h_j$ when you replace~$f_K$ by a
+    random function.  (The previous ``double hashing''
+    construction seems clunky if you're going to assume you have
+    a PRF and secret keys; is this just an example of people in
+    one domain naively using a tool developed for another? )
 

### 2016-06-23 filters.tex
responding to JK's comments

@@
 that if you want false positives to be hard to find then you need to
-make the hash functions secret.} The traditional notion of soundness
+make the hash functions secret.} \tsnote{I don't think it makes sense
+to talk about asymptotics or negligibility, for exactly the reason you
+state. I think the key point here is: what is ``hard''?   The designer decides what FP rate is
+acceptable for a given application, a given set of efficiency
+constraints, the side-effects of a FP, etc.  For a fixed FP target,
+she optimizes the filter size and/or the number of hash functions for
+her setting. Whether the target FP rate is 0.01 or $2^{-80}$, we should be able to say (in the ROM, at least)
+that it will take this-many hash computations, and this many on-line
+set-membership queries, to find the first FP.  In the standard model,
+with public hash functions, it is clearly more difficult to make
+formal claims.  Even so, in practice I expect it would be quite expensive to
+find a string~$x$ such that $(h_1(x),h_2(x),\ldots,h_k(x))$
+falls in a given set of tuples when $h_i(x)=\mathrm{truncate}(\mathrm{SHA256}(\langle i \rangle
+\concat x), m)$, say. (Even more so if my setting admits relatively
+expensive hash computations, e.g. SCRYPT.)  BTW, your suggestion to
+have a FP notion with secret~$\mathrm{S}$ is interesting here. }
+
+The traditional notion of soundness
 for a Bloom filter captures the difficulty of finding false
@@
 either (at least not directly, though it may end up being implied by
-their definition).}
+their definition).} \tsnote{See my comment in the intro.}
 
@@
 $\epsilon$ then the best an attacker can do with $q$ hash queries is
-$1-(1-\epsilon)^q$ plus negligible? One thing that is nice about the
+$1-(1-\epsilon)^q$ plus negligible?} 
+\tsnote{Formally, I don't think we can (and still be rooted in
+  reality.)  Even informally it's hard, since the fact is that the
+  designer decides what is ``secure'' for her setting.  I think we
+  just say something like ``A bloom filter is
+  $(t,q_h,q_m,\epsilon)$-secure if no attacker running in time at
+  most~$t$, asking at most~$q_h$ hash queries and $q_m$ set-membership
+  queries, has probability more than~$\epsilon$ of finding a FP.''  (If
+you like, we can throw a paramter~$n$ in there, for the number of FPs
+it must find.)  Perhaps informally we say that a bloom filter is
+secure if, for ``reasonable'' $t,q_h,q_m$, the value of~$\epsilon$ is
+not ``significantly larger'' than the designer's target.}
+
+\jnote{One thing that is nice about the
 NY notion is that you get a ``clean'' definition of security: no

### 2016-06-23 intro.tex
responding to JK's comments

@@
 The fact that~$A$ can \emph{adapt} its queries and its output based
-on what it learns from the set-membership oracle is the key
-definitional distribution of~NY.
+on what it learns from the set-membership oracle (but, as we will see,
+not upon the hash functions) is the key definitional contribution of~NY.
 
@@
 First, $M \getsr \mathbf{B}_1(\mathcal{S})$. \jnote{Where does the
-set come from? Is it random? Adversarially chosen?} Then the
+set come from? Is it random? Adversarially chosen?}
+\tsnote{In their formalism, it is implicitly an input to the security experiment.
+Security is universally quantified over sets~$\mathcal{S}$.  This
+would seem to be equivalent to letting the adversary
+pick~$\mathcal{S}$ (prior to the hash functions being picked), with
+the time to compute and write out~$\mathcal{S}$ folded into the
+adversary's running time. } 
+Then the
 adversary is given the set~$\mathcal{S}$ and may make queries
@@
 outputs $x^* \in \{x_1,x_2,\ldots,x_q\}$, even if one of these was a
-false positive. \jnote{We discussed this on the phone, but let me
+false positive. 
+\jnote{We discussed this on the phone, but let me
 put it in writing here. I think this is actually a reasonable choice
@@
 $\epsilon$ might be $1/1000$ rather than negligible.} 
-%
+\tsnote{For me the question is: is security violated once the first FP is found, or
+the second?  My answer, which is in line with the traditional
+soundness notion, is that the first FP is a security violation
+even if finding it isn't ``hard'' by cryptographic standards.
+But I do appreciate your point.  A natural goal is to say that, in some sense,
+\emph{adaptivity doesn't make it any easier} to find a FP.  Adapting
+to what, though?  In the traditional notion, $x$~is picked before the
+coins of~$\mathbf{B}_1$ are flipped, i.e., before the hash functions
+are sampled.  The direct non-adaptive generalization is to say that
+$x_1,x_2,\ldots,x_q$ are all picked up front.  The direct
+\emph{adaptive} generalization would allow $x_1,x_2,\ldots,x_q$ to
+depend in the coins of~$\mathbf{B}_1$, i.e., the hash functions.  The
+NY definition captures only indirect dependence: adversaries that can adapt to set-membership queries,
+but \emph{not} (directly) to the input-output behaviors of the hash
+functions. }
+\tsnote{Perhaps a more obvious way to capture the idea that ``finding
+  some FPs doesn't help find additional ones'' is to parameterize my notion(s) with a number~$n$, and say
+that that the adversary wins iff it outputs~$n$ FPs (these may have
+been previously queried to the set-membership oracle).  
+Note that in the ROM (and probably in practice) finding~$n>1$ FPs will
+require~$n$ times the work; finding the first won't help in finding
+the second.} 
+%\tsnote{Here's an off-the-wall idea.  What if the basic FP security
+%notion gave the adversary an oracle for set-membership (and the hash functions, depending on the setting), and after interacting with these
+%it is challenged with either $x_0$ or $x_1$, where $x_0$ is a random
+%point from the set of non-FPs, and $x_1$ is a random point from the
+%set of FPs?  (No oracles after being challenged.)  The adversary has
+%to decide which it received.}
+
 Second, we note that the NY syntax does not capture the size of~$M$
-as a parameter \jnote{I think this is also reasonable; typically
-security is defined without regard for efficiency}; the surrounding
+as a parameter; 
+\jnote{I think this is also reasonable; typically
+security is defined without regard for efficiency}
+\tsnote{My complaint isn't about efficiency. It's about the fact that,
+by not including $|M|$ in the definition, the trivial scheme I give
+(just below) is allowed, and is secure.  Anyway, as I say at the end
+of this paragraph, this is a small(er) complaint that what follows}. The surrounding
 text does say that $\mathbf{B}_1$ ``outputs a compressed
@@
 over the problem from the classical literature.}
+\tsnote{One can suggest that it \emph{should} be counted in the classical
+  description, but the fact is that it isn't :)  And in the 30+ years
+  since the original paper, no one saw fit to correct this?  From an
+  algorithmic perspective, I think the classical approach makes
+  sense.  The questions being answered are: how many bits do I need to
+  store a representation of the set for a given FP rate, and how does this compare to the
+  combinatorially computed lower-bound?  The description length of the
+hash functions may be bigger or smaller, but the number of bits you
+need to hold the set representation is independent of that.  (Imagine
+that you have long random bitstrings in the set~$\mathcal{S}$.  Then
+whether your hash functions simply truncate, or they are random
+oracles, the size of the representation as a function of the target FP
+rate doesn't change.  Yet the description lengths of the hash
+functions are drastically different.)}
 
@@
 intended for $h_1,h_2,\ldots,h_k$ to be hard-coded into the
-algorithms. \jnote{Perhaps it is reasonable to consider a definition
+algorithms. 
+\jnote{Perhaps it is reasonable to consider a definition
 in which the set is not given to the adversary?}
+\tsnote{A FP security notion?  Yes, perhaps so.  It's probably a more
+  realistic notion anyway -- is a spammer really going to know my
+  whitelist a priori?  (If he does, I probably have bigger problems in
+my system than receiving new spam email.)  Or set of URLs cached by a
+CDN server?}
 
@@
 languages. In much data structures literature, this is called the
-``dynamic'' case, in contrast to the ``static'' case.}, in the sense
+``dynamic'' case, in contrast to the ``static'' case.} \tsnote{I
+adopted this term after reading it in some bloom filter
+paper(s). Ironically, I liked it for the same reason you think it is
+awkward :)  My PL association to the term is that an immutable object
+is one whose state cannot be modified after it is created, and a
+mutable object is the opposite.  ButI don't really care too much.}, in the sense
 that they allow for updating of the representation. This allows us

### 2016-06-23 intro.tex
responding to JK's comments

@@
 but \emph{not} (directly) to the input-output behaviors of the hash
-functions. }
+functions.  The three notions I've proposed in Figure 1 cover a
+spectrum adaptivity: the first is adapting to set-membership queries
+only, the second to those and hash input-output behavior, the third to
+set-membership queries and full knowledge of the hash functions.  Each
+has it's own associated (informal) security interpretation.}
 \tsnote{Perhaps a more obvious way to capture the idea that ``finding
-  some FPs doesn't help find additional ones'' is to parameterize my notion(s) with a number~$n$, and say
-that that the adversary wins iff it outputs~$n$ FPs (these may have
+  some FPs doesn't help find additional ones'' is to parameterize my notion(s) with a number~$f$, and say
+that that the adversary wins iff it outputs~$f$ FPs (these may have
 been previously queried to the set-membership oracle).  
-Note that in the ROM (and probably in practice) finding~$n>1$ FPs will
-require~$n$ times the work; finding the first won't help in finding
-the second.} 
+Note that in the ROM (and probably in practice) finding~$f>1$ FPs will
+require~$f$ times the work.  Right?} 
 %\tsnote{Here's an off-the-wall idea.  What if the basic FP security

### 2016-06-23 filters.tex
responses to JK's comments

@@
 expensive hash computations, e.g. SCRYPT.)  BTW, your suggestion to
-have a FP notion with secret~$\mathrm{S}$ is interesting here. }
+have a FP notion with secret~$\mathcal{S}$ is interesting here. }
 
@@
 secure if, for ``reasonable'' $t,q_h,q_m$, the value of~$\epsilon$ is
-not ``significantly larger'' than the designer's target.}
+not ``significantly larger'' than the designer's target.  I guess
+that's not far off from one of your suggestions.}
 
@@
 \jnote{What parameters are needed to get negligible $\epsilon$? Are
-they reasonable in practice?}
+they reasonable in practice?} \tsnote{Again, I don't think that
+negligible is reasonable in practice :P}
 
@@
 goal here? If they don't share hash functions, I'm not sure what is
-gained by considering this definition.} In this section, we consider
+gained by considering this definition.} \tsnote{Perhaps not the same
+hash functions, but correlated ones.  For example, server~$j$ uses
+hash functions $\tilde{h}_i(x) = h_i(\langle \mathrm{id}_j \rangle \concat x)$ for
+some $h_i$ shared among servers.  The $\mathrm{id}_j$ may or may not
+be public, e.g. in a P2P network your ID might be a nonce learned only
+when you join.  Also, the sets $\mathcal{S_j}$ stored at each server
+might be correlated.} In this section, we consider
 security notions for settings in which there may be multiple

### 2016-06-25 Proofs.tex
cheers
New proof of Theorem 1

--- 2016-06-13 Proofs.tex
@@
-\section{Theorems and proofs}
-\begin{theorem}
-Fix $n,k, m > 0$ and define a hash-based filter as in section \ref{sec:hbf}, except the hash functions are defined by $h_j(x) = \left( f_{K0}(x) + j\cdot g_{K1}(x)\right) \bmod m$.
+\section{Proofs}
+\tsnote{Jon: ignore these for now.  This is Animesh's workspace.}
+\begin{theorem}\label{thm}
+Fix $k, m, n > 0$ and define a hash-based filter as in section \ref{sec:hbf}, except the hash functions are defined by $h_j(x) = \left( f_{K_0}(x) + j\cdot g_{K_1}(x)\right) \bmod m$.
 Let $Func(m,m)$ be the set of all functions $\rho \colon \calK \times \bits^m \sends \bits^m$.
-Let $B_1, B_2$ be 2 adversaries with keys $K_1, K_2 \getsr \calK$ attacking the PRF advantage of $F \colon \calK \times \bits^m \sends \bits^m$ and $A$ be another adversary attacking the false positive game of hash-based filters, then
+Let $B_1, B_2$ be 2 adversaries attacking the PRF advantage of $F \colon \calK \times \bits^m \sends \bits^m$ and $A$ be another adversary attacking the false positive game of hash-based filters, then
+
 \begin{equation}
-\AdvFPSecHash{B}{\distr{U}{n},A}  = 0.5\Big[\AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}\Big] + \varepsilon, \nudge where \nudge \varepsilon = (1-(1-e^{-kn/m})^k)
+\AdvFPSecHash{B}{A} = \abs{ \AdvPRF{F}{B_2} - \AdvPRF{F}{B_1}} \pm q \cdot \epsilon
 \end{equation}
-
+Note: Here, $q$ is the number of queries made to the $\QryOracle$ oracle and $\epsilon$ is the false positive error in the double hashing scheme given by Kirsch and Mitzenmacher.
+$\epsilon \rightarrow 0$, if $m/n \rightarrow \infty$ and/or $k \rightarrow \infty$ \cite{xxx}
 \end{theorem}
@@
 \begin{proof}
-Let adversary $B$ simulate the fp-priv game of $A$ as shown in Fig.
-\ref{fig:AdvB}, where the hash functions are defined as $h_j(x) = \left( f_{K0}(x) + j\cdot g_{K1}(x)\right) \bmod m$.
-Based on the variable $c(c\getsr \bits)$,  $B$ either acts as adversary $B_1$ or $B_2$.
-Fig.
-\ref{fig:PRFexp} shows the PRF experiment of $B$.
-When $B$ makes an oracle query on behalf of $A$ and  $b=0$, it exactly simulates $A's$ experiment as the hash functions are uniformly random.
-When $b=1$, it exactly simulates the double hashing scheme proposed by Kirsh and Mitzenmacher.
-The fp-error($\varepsilon$)  for the double hashing scheme for large $n$ is $\varepsilon = (1-e^{-kn/m})^k$ \cite{less hashing paper}.
+The proof of the theorem will use a game playing argument as shown in Fig.
+\ref{fig:Game}.
+$\game{0}(A)$ exactly simulates $\ExpFPSecHash{B}{A}$ with hash functions $h_j(x) = \left( f_{K_0}(x) + j\cdot g_{K_1}(x)\right) \bmod m$.
+So,
+\begin{equation}
+\AdvFPSecHash{B}{A} = \Prob{\game{0}(A)=1}\label{eq:0}
+\end{equation}
+ $\game{1}(A)$ and $\game{2}(A)$ attack 2 different filters, $B_1$ and $B_2$, with hash functions 
+\begin{eqnarray*}
+h_j(x) &=& ( f_{K_0}(x) + j\cdot \rho_2(x)) \bmod m\\
+h_j(x) &=& ( \rho_1(x) + j \cdot \rho_2(x)) \bmod m 
+\end{eqnarray*}
+Here, $\rho_1$ and $\rho_2$ are random functions sampled from $Func(m,m)$. Let adversary $B_1, B_2$ simulate $\game{1}(A)$ and $\game{2}(A)$ respectively as shown in Fig. \ref{fig:BGame1}.
 
-\begin{figure}[t]
-\centering
-\fpage{.5}
+\par{In a classical Bloom filter, adversary $A^{'}$ is non-adaptive, i.e., for some fixed $x \notin S$, $A^{'}$ targets the false-positive error conditioned on randomness of hash functions.
+But in the $\ExpFPSecHash{B}{A}$ game, $A$ is adaptive, as it can adapt its queries as well as its output based on response of $\QryOracle$ oracle.
+Let $A$ makes $q$ queries $x_1, x_2, ..., x_q$ to the $\QryOracle$ oracle.
+$\game{3}(A)$ simulates $fp-error$ game of $A^{'}$ as shown in Fig.
+\ref{fig:Game}.}
+
+%\caption{Game playing argument}\label{fig:Game}
+\begin{figure}[h]
+\fpage{.95}{
+\hpagessd{.5}{.5}
 {
-\experimentv{Adversary $B^{\calO}$:}\\
-$c \getsr \bits$\\
-$K \getsr \calK$\\
+\underline{\game{0}(A)}\\
+$K_1, K_2 \getsr \calK$\\
 $S \getsr \distr{U}{n}$\\
-if $c=0$\\
-$ \nudge h_j = \calO(\cdot) + jF_K(\cdot), \nudge \mathrm{where} \nudge j \in [1,k]$\\
-else\\
-$\nudge  h_j = F_K(\cdot) + j\calO(\cdot), \nudge \mathrm{where} \nudge j \in [1,k]$\\
-$M \getsr \Rep^{h_1, \cdots, h_k}(S)$\\
-Run $A$\\
-When $A$ asks $\QryOracle(x)$: \\
-$\nudge$ Ret $\QryOracle^{h_1, \cdots, h_k}(M, x)$ to $A$\\
-When $A$ halts with output $x^{'}$: \\
-if $x^{'} \not\in S \wedge \Qry^{h_1, \cdots, h_k}(M,x^{'})=1$ then\\
-$\nudge$ Ret 1\\
-Ret 0
+$M \getsr \Rep^{\HashOracle(\cdot, \cdot)}(S)$\\
+$x \getsr A^{\QryOracle(\cdot)}(S)$\\
+if $x \not\in S \wedge \Qry^{\HashOracle(\cdot, \cdot)}(M,x)=1$ then\\
+\nudge Ret 1\\
+Ret 0\\\\
+%
+\oracle{$\QryOracle(x)$}\\
+Ret $\Qry^{\HashOracle(\cdot, \cdot)}(M,x)$\\\\
+%
+\oracle{$\HashOracle(i,x)$}\\
+$h_i(x) = F_{K_1}(x)+i \cdot F_{K_2}(x)$\\
+Ret $h_i(x)$
 }
-\caption{Adversary $B$ simulating $A^{'}s$ fp-prv game}\label{fig:AdvB}
+{
+\underline{\game{1}(A)}\\
+$K_1 \getsr \calK$\\
+$\rho \getsr Func(m,m)$\\
+$S \getsr \distr{U}{n}$\\
+$M \getsr \Rep^{\HashOracle(\cdot, \cdot)}(S)$\\
+$x \getsr A^{\QryOracle(\cdot)}(S)$\\
+if $x \not\in S \wedge \Qry^{\HashOracle(\cdot, \cdot)}(M,x)=1$ then\\
+\nudge Ret 1\\
+Ret 0\\\\
+%
+\oracle{$\QryOracle(x)$}\\
+Ret $\Qry^{\HashOracle(\cdot, \cdot)}(M,x)$\\\\
+%
+\oracle{$\HashOracle(i,x)$}\\
+$h_i(x) = F_{K_1}(x)+i \cdot \rho(x)$\\
+Ret $h_i(x)$
+}
+{
+\underline{\game{2}(A)}\\
+$\rho_1,\rho_2 \getsr Func(m,m)$\\
+$S \getsr \distr{U}{n}$\\
+$M \getsr \Rep^{\HashOracle(\cdot, \cdot)}(S)$\\
+$x \getsr A^{\QryOracle(\cdot)}(S)$\\
+if $x \not\in S \wedge \Qry^{\HashOracle(\cdot, \cdot)}(M,x)=1$ then\\
+\nudge Ret 1\\
+Ret 0\\\\
+%
+\oracle{$\QryOracle(x)$}\\
+Ret $\Qry^{\HashOracle(\cdot, \cdot)}(M,x)$\\\\
+%
+\oracle{$\HashOracle(i,x)$}\\
+$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$\\
+Ret $h_i(x)$
+}
+{
+\underline{$\game{3}(A)$}\\
+$t \getsr [q]$, where $[q] = {0,1, \cdots, q-1}$\\
+$count = 0$ \\%count will be used to keep track of queries made to $\QryOracle$\\
+$win \gets false$\\
+$\rho_1,\rho_2 \getsr Func(m,m)$\\
+$S \getsr \distr{U}{n}$\\
+$M \getsr \Rep^{\HashOracle(\cdot, \cdot)}(S)$\\
+$x \getsr A^{\QryOracle(\cdot)}(S)$\\
+if $x \not\in S \wedge \Qry^{\HashOracle(\cdot, \cdot)}(M,x)=1$ then\\
+$\nudge $ Ret 1\\
+Ret 0\\\\
+%
+\oracle{$\QryOracle(x)$}\\
+$count=count +1$\\
+if $(count == t)$\\
+$\nudge win = true$\\
+$\nudge \mathrm{Ret} \nudge \Qry^{\HashOracle(\cdot, \cdot)}(M,x)$\\
+else \\
+$\nudge \mathrm{Ret}\nudge 0$\\\\
+%
+\oracle{$\HashOracle(i,x)$}\\
+$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$\\
+Ret $h_i(x)$
+}
+}
+\caption{Game playing argument}\label{fig:Game}
 \end{figure}
 
+%\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
 \begin{figure}[h]
-\center
-\fpage{.45}{
-\hpagess{.4}{.5}
+\centering
+\fpage{0.9}{
+\hpagessl{0.5}{0.5}
 {
-\experimentv{$\ExpPRF{F}{B}$:}\\
-$b \getsr \bits$\\
-$\rho \getsr Func(m,m)$\\
-$K_1 \getsr \calK$\\
-$b^{'} \getsr B^{\calO(\cdot,\cdot)}$\\
-Ret $[b=b']$
+$\experimentv{Adversary \nudge B_1^{\calO}:}$\\
+$K_1 \getsr \calK $\\
+$S \getsr \distr{U}{n}$\\
+$M \getsr \Rep^{\HashOracle(\cdot, \cdot)}(S)$\\
+When $A$ asks $\QryOracle(x)$:\\
+$\nudge$ Ret $\Qry^{\HashOracle(\cdot, \cdot)}(M,x)$\\
+When $A$ halts with output $x^{'}$: \\
+$\nudge$if $x^{'} \not\in S \wedge \Qry^{\HashOracle(\cdot, \cdot)}(M,x^{'})=1$ then\\
+$\nudge$ $\nudge$ Ret 1\\
+$\nudge$ Ret 0\\\\
+\oracle{$\HashOracle(i,x)$}\\
+$ \mathrm{Ret} \nudge F_{K_1}(x) + i\cdot \calO(x)$\\
 }
 {
-\oracle{$\calO(x)$}\\
-$Y \gets \calF_{K_1}(M)$\\
-if $b=0$\\
-\nudge$Y \getsr \rho(x)$\\
-Ret $Y$
+$\experimentv{Adversary \nudge B_2^{\calO}:}$\\
+%$d \getsr \bits $\\
+$\rho_2 \getsr Func(m,m)$\\
+$S \getsr \distr{U}{n}$\\
+$M \getsr \Rep^{\HashOracle(\cdot, \cdot)}(S)$\\
+When $A$ asks $\QryOracle(x)$:\\
+$\nudge$ Ret $\Qry^{\HashOracle(\cdot, \cdot)}(M,x)$\\
+When $A$ halts with output $x^{'}$: \\
+$\nudge$if $x^{'} \not\in S \wedge \Qry^{\HashOracle(\cdot, \cdot)}(M,x^{'})=1$ then\\
+$\nudge$$\nudge$ Ret 1\\
+$\nudge$Ret 0\\\\
+\oracle{$\HashOracle(i,x)$}\\
+%if $d=0$\\
+$\mathrm{Ret} \nudge \calO(x) + i\cdot \rho_2(x)$
 }
 }
-\caption{PRF experiment}\label{fig:PRFexp}
+\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
 \end{figure}
-\acnote{Equations to be aligned}
-\begin{multline*}
-\Prob{\ExpPRF{F}{B} = 1} =   .5\Prob{\ExpPRF{F}{B} = 1 | b =0} + .5\Prob{\ExpPRF{F}{B} = 1 | b = 1}\\
-.5\Prob{\ExpPRF{F}{B} = 1|c=0} + .5\Prob{\ExpPRF{F}{B} = 1|c=1}  = .5\Prob{\ExpFPSecHash{B}{\distr{U}{n},A}=1} + .5(1-e^{-kn/m})^k  \\
-.5\Prob{\ExpPRF{F}{B} = 1|c=0} + .5\Prob{\ExpPRF{F}{B} = 1|c=1}  = .5\Prob{\ExpFPSecHash{B}{\distr{U}{n},A}=1} + .5(1-e^{-kn/m})^k \\
-\Prob{\ExpPRF{F}{B} = 1|c=0} + \Prob{\ExpPRF{F}{B} = 1|c=1} = \Prob{\ExpFPSecHash{B}{\distr{U}{n},A}=1} + (1-e^{-kn/m})^k \\
- 2\Prob{\ExpPRF{F}{B_1} = 1} - 1 + 2\Prob{\ExpPRF{F}{B_2} = 1} - 1 = 2\AdvFPSecHash{B}{\distr{U}{n},A} + 2(1-e^{-kn/m})^k -2\\
-\AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} = 2\AdvFPSecHash{B}{\distr{U}{n},A} + 2(1-e^{-kn/m})^k -2\\
- \AdvFPSecHash{B}{\distr{U}{n},A} = 0.5(\AdvPRF{F}{B_1} + \AdvPRF{F}{B_2})  + \varepsilon, \nudge \mathrm{where} \nudge \varepsilon = 1-(1-e^{-kn/m})^k
-\end{multline*}
 
+\begin{eqnarray}
+\nonumber \Prob{\ExpPRF{F}{B_1} = 1} &=& .5\Prob{\ExpPRF{F}{B_1}=1|b=0} + .5\Prob{\ExpPRF{F}{B_1} = 1|b=1}\\
+\nonumber (2\Prob{\ExpPRF{F}{B_1} = 1} - 1) + 1 &=& \Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1}\\
+ 1 + \AdvPRF{F}{B_1} &=& \Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1} \label{eq:1}\\
+\nonumber& &\\
+\nonumber \Prob{\ExpPRF{F}{B_2} = 1} &=& .5\Prob{\ExpPRF{F}{B_2}=1|b=0} + .5\Prob{\ExpPRF{F}{B_2} = 1|b=1}\\
+\nonumber (2\Prob{\ExpPRF{F}{B_2} = 1} - 1) + 1 &=& \Prob{\game{2}(A)=1} + \Prob{\game{1}(A)=1}\\
+ 1 + \AdvPRF{F}{B_2} &=& \Prob{\game{2}(A)=1} + \Prob{\game{1}(A)=1}\label{eq:2}
+\end{eqnarray}
+
+Subtracting \ref{eq:1} from \ref{eq:2}, we have
+\begin{eqnarray}
+\abs{ \AdvPRF{F}{B_2} - \AdvPRF{F}{B_1}} &= \abs{\Prob{\game{2}(A)=1} - \Prob{\game{0}(A)=1}}\label{eq:2a}
+\end{eqnarray}
+
+In $\game{3}(A)$, assume, without loss of generality that $A$ halts with output $x$ immediately, if it asks $x$ to $\QryOracle$ and $\QryOracle$ returns $1$.
+Thus, all queries to $\QryOracle$ return 0 until the first one.
+Hence,
+
+\begin{equation}
+\Prob{\game{2}(A)=1} \leq q \cdot \Prob{\game{3}(A)=1} = q \cdot \Prob{\game{3}(A)=1|win=true}\label{eq:3}
+\end{equation}
+
+In Fig. \ref{AGame3}, adversary $A^{'}$ simulates $\game{3}(A)$. Since, adversary $A^{'}$ exactly simulates $\game{3}(A)$ conditioned on $win = true$, 
+\begin{eqnarray}
+\nonumber \Prob{\game{3}(A)|win=true} &=& \Prob{A^{'} \mathrm{outputs \nudge FP}}\\
+& \leq & \epsilon, \nudge \mathrm{where} \nudge \epsilon = (1-e^{-kn/m})^k\label{eq:4}
+\end{eqnarray}
+
+%\caption{Adversary $A^{'}$ simulating $\game{3}(A)$} \label{AGame3}
+\begin{figure}
+\centering
+\fpage{0.4}{
+$\experimentv{Adversary \nudge A^{{'}\HashOracle(\cdot, \cdot)}:}$\\
+$t \getsr [q]$, where $[q] = {0,1, \cdots, q-1}$\\
+$count = 0$\\
+$\rho_1,\rho_2 \getsr Func(m,m)$\\
+$S \getsr \distr{U}{n}$\\
+$M \getsr \Rep^{\HashOracle(\cdot, \cdot)}(S)$\\
+When $A$ asks $\QryOracle(x)$:\\
+$\nudge cnt = cnt + 1$\\
+$\nudge \mathrm{if} \nudge count == t$\\
+$\nudge r \gets \Qry^{\HashOracle(\cdot, \cdot)}(M,x)$\\
+if $r==1$\\
+$\nudge$ $A$ halts with output $x$\\
+$\nudge$ Ret 1\\
+else\\
+$\nudge$ $A$ outputs NULL\\
+$\nudge$ Ret 0\\\\
+%
+\oracle{$\HashOracle(i,x)$}\\
+$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$\\
+Ret $h_i(x)$
+}
+\caption{Adversary $A^{'}$ simulating $\game{3}(A)$} \label{AGame3}
+\end{figure}
+
+From eqn. \ref{eq:0}, \ref{eq:2a}, \ref{eq:3} and \ref{eq:4}: \\
+\begin{eqnarray}
+\nonumber \abs{ \AdvPRF{F}{B_2} - \AdvPRF{F}{B_1}} &=& \abs{q \cdot \epsilon - \Prob{\ExpFPSecHash{B}{A}=1}}\\
+\AdvFPSecHash{B}{A} &=& \abs{ \AdvPRF{F}{B_2} - \AdvPRF{F}{B_1}} \pm q \cdot \epsilon
+\end{eqnarray}
 \end{proof}

### 2016-07-05 intro.tex
responding to JK's comments
new related work

@@
 functions.  The three notions I've proposed in Figure 1 cover a
-spectrum adaptivity: the first is adapting to set-membership queries
+spectrum of adaptivity: the first is adapting to set-membership queries
 only, the second to those and hash input-output behavior, the third to
@@
 has it's own associated (informal) security interpretation.}
+
 \tsnote{Perhaps a more obvious way to capture the idea that ``finding
@@
 (just below) is allowed, and is secure.  Anyway, as I say at the end
-of this paragraph, this is a small(er) complaint that what follows}. The surrounding
+of this paragraph, this is a small(er) complaint than what follows}. The surrounding
 text does say that $\mathbf{B}_1$ ``outputs a compressed
@@
 is one whose state cannot be modified after it is created, and a
-mutable object is the opposite.  ButI don't really care too much.}, in the sense
+mutable object is the opposite.  But I don't really care too much.}, in the sense
 that they allow for updating of the representation. This allows us
@@
 
-\heading{Related work. }
+\heading{Related work: attacks}
 \begin{itemize}
@@
 \tsnote{Journal of Privacy and Confidentiality, 2014}
-\item Mitzenmacher and Vadhan.\tsnote{Might only be tangential.}
 \item Gerbet, Kumar and Lauradoux, ``The power of evil choices in bloom filters''.  \tsnote{DSN'15: Looks like a real goldmine of related work!}
+\item Crosby and Wallach, ``Denial of Service via Algorithmic Complexity Attacks'' \tsnote{Gives attacks on Squid}
+\item Gao et al., ``Internet Cache Pollution Attacks and Countermeasures''
+\end{itemize}
+
+\heading{Related work: definitions(?)}
+\begin{itemize}
 \item Nojima and Kadobayashi, ``Cryptographically Secure Bloom Filters''.
@@
 Both seem vague and thoroughly underspecified.}
-\item Crosby and Wallach, ``Denial of Service via Algorithmic Complexity Attacks'' \tsnote{Gives attacks on Squid}
+\item Naor and Yogev
+\end{itemize}
+
+\heading{Related work: constructions}
+\begin{itemize}
 \item Bellovin and Cheswick, ``Privacy-Enhanced Searches Using Encrypted Bloom Filters''.
@@
 \item S\"{a}rell\"{a} et al., ``BloomCasting: Security in Bloom Filter Based Multicast''.
-\item Gao et al., ``Internet Cache Pollution Attacks and Countermeasures''
 \item Dong, Chen, Wen, ``When Private Set Intersection Meets Big Data: An Efficient and Scaleable Protocol'' \tsnote{``garbled bloom filters'', which actually store the set element by storing~$k$ xor-shares, one at each of the~$k$ hash indices (with care for reusing shares if hash collisions occur), and``oblivious bloom intersection''}\tsnote{If the filter and the hash functions are public, there is a naive attack that works for some interesting parameters.
@@
 \item Tarkoma, Rothenberg, Lagerspetz ``Theory and Practice of Bloom Filters in Distributed Systems'' \tsnote{Great high-level coverage.  Only found preprint version though.}
+\item Durham, Kantarcioglu, Xue, Kuzu, Malin ``Composite Bloom Filters for Secure Record Linkage'' \tsnote{Per-field BFs, sampled and composed into single BF that is then permuted by a secret random permtation.
+No clear statement of the problem that is being solved.}
+\end{itemize}
+
+\heading{Related work: tangential}
+\begin{itemize}
+\item Mitzenmacher and Vadhan.\tsnote{Might only be tangential.}
 \item Dodis et al.

### 2016-07-05 filters.tex
adding side-information to syntax

@@
 %
-The randomized representation algorithm $\Rep\colon [U]^n \rightarrow \Sigma^m$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m$.
+The randomized representation algorithm $\Rep\colon [U]^n \rightarrow
+\Sigma^m \times \bits^*$ takes a set~$S$ of~$n$ elements as input, and outputs
+representation~$M$ of length~$m$ along with (possibly empty) side-information~$\tau$.
 %
-The deterministic query algorithm $\Qry\colon \Sigma^m \times U
-\rightarrow \bits$ takes a representation $M$ and an element $x \in
-U$ and returns a bit.
+The deterministic query algorithm $\Qry\colon \Sigma^m \times \bits^* \times U
+\rightarrow \bits$ takes a representation $M$, side-information~$\tau$, and an element $x \in
+U$, and returns a bit.
 %
@@
 functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$.
+Typically this access will be implicit, but when we need to make it explicit we will write~$\mathcal{H}$ (or the individual hash functions) as superscripts.
 %which we denote by writing~$\mathcal{H}$ as a superscript.
@@
 For correctness, we demand that for all~$S$ of size~$n$ and all $x
-\in S$, it holds that $\Prob{\Qry(\Rep(S),x)=1}=1$, where the
+\in S$, it holds that $\Prob{\mathcal{H}\getsr\Hash;\,(M,\tau)\getsr\Rep(S)\,:\,\Qry(M,\tau,x)=1}=1$, where the
 probability is over the coins of $\Hash$ and~$\Rep$.
@@
 %\heading{Discussion.}
-This syntax captures classical Bloom filters by setting~$\Sigma=\bits$,  and defining $\Rep,\Qry$ in the obvious way.
+This syntax captures classical Bloom filters by setting~$\Sigma=\bits$,  and defining $\Rep,\Qry$ in the obvious way, with $\tau=\emptystring$.
 We note that even though $\Rep$ may be randomized, it does not have to be; for the classical Bloom filter, it is deterministic.
+
+By allowing $\Rep$ to output side-information, we allow for (say) $\Rep$ and $\Qry$ to share a secret key selected during representation generation.\tsnote{Ultimately it might be cleaner to fold the hash functions into the side-information, too.
+But in that case, we will likely want an explicit separation between private side-information (e.g.
+the key for a secret permutation of the bits of~$M$) and public side-information (e.g.
+the hash functions used to create~$M$).
+For now, since the only public side-information I see in the literature are the hash functions, I'm leaving it as is.}
 

### 2016-07-05 filters.tex
adding side-information to syntax

@@
 the hash functions used to create~$M$).
-For now, since the only public side-information I see in the literature are the hash functions, I'm leaving it as is.}
+For now, since the only public side-information I see in the literature are the hash functions, I'm leaving it as is.}  In our security notions, any side-information will be kept secret from the adversary.
 
@@
 $\HashOracle = (h_1, \ldots, h_k)$\\
-$M \getsr \Rep^{\HashOracle}(S)$\\
+$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
 $x \getsr A^{\QryOracle}(S)$\\
-if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
+if $x \not\in S \wedge \Qry^{\HashOracle}(M,\tau,x)=1$ then\\
 \nudge Ret 1\\
@@
 \oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,x)$\\
+Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
 
@@
 $\HashOracle = (h_1, \ldots, h_k)$\\
-$M \getsr \Rep^{\HashOracle}(S)$\\
+$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
 $x \getsr A^{\QryOracle,\HashOracle}(S)$\\
-if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
+if $x \not\in S \wedge \Qry^{\HashOracle}(M,\tau,x)=1$ then\\
 \nudge Ret 1\\
@@
 $\HashOracle = (h_1, \ldots, h_k)$\\
-$M \gets \Rep^{\HashOracle}(S)$\\
+$(M,\tau) \gets \Rep^{\HashOracle}(S)$\\
 $x \getsr A^{\QryOracle}(S,\{h_1,h_2,\ldots,h_k\})$\\
-if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
+if $x \not\in S \wedge \Qry^{\HashOracle}(M,\tau,x)=1$ then\\
 \nudge Ret 1\\

### 2016-07-05 filters.tex
adding side-information to syntax

@@
 
-By allowing $\Rep$ to output side-information, we allow for (say) $\Rep$ and $\Qry$ to share a secret key selected during representation generation.\tsnote{Ultimately it might be cleaner to fold the hash functions into the side-information, too.
-But in that case, we will likely want an explicit separation between private side-information (e.g.
-the key for a secret permutation of the bits of~$M$) and public side-information (e.g.
-the hash functions used to create~$M$).
-For now, since the only public side-information I see in the literature are the hash functions, I'm leaving it as is.}  In our security notions, any side-information will be kept secret from the adversary.
+By allowing $\Rep$ to output side-information, we allow for (say) $\Rep$ and $\Qry$ to share a secret key selected during representation generation.
+\tsnote{Ultimately it might be cleaner to fold the hash functions into the side-information, too.
+But in that case, we will likely want an explicit separation between private side-information (e.g., the key for a secret permutation of the bits of~$M$) and public side-information (e.g., the hash functions used to create~$M$).
+Note that we do see constructions that have \emph{no} ``stand-alone'' hash functions yet use a secret key (e.g., the PRF-based double-hashing construction), and also schemes that employ \emph{both} stand-alone hash functions and a secret key (e.g.
+the record BF from Durham et al.)}  In our security notions, any side-information will be kept secret from the adversary.
 
@@
 $\HashOracle = (h_1, \ldots, h_k)$\\
-$M \getsr \Rep^{\HashOracle}(S)$\\
+$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
 $x \getsr A^{\QryOracle}()$\\
@@
 $\HashOracle = (h_1, \ldots, h_k)$\\
-$M \getsr \Rep^{\HashOracle}(S)$\\
+$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
 $x \getsr A^{\QryOracle,\HashOracle}()$\\
@@
 $\HashOracle = (h_1, \ldots, h_k)$\\
-$M \getsr \Rep^{\HashOracle}(S)$\\
+$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
 $x \getsr A^{\QryOracle}(\{h_1,h_2,\ldots,h_k\})$\\

### 2016-07-05 intro.tex
adding side-information to syntax
adding related work

@@
 \item Naor and Yogev
+\item Eujin Goh, ``Secure Indexes'' \tsnote{A secure index can be used for set membership.
+Builds a secret-key data structure (an Index) that allows searching for keyword~$w$ if one holds the trapdoor $T_w$ for~$w$, where the trapdoor depends on the secret key.
+Main construction uses traditional Bloom filters and a PRF.
+Construction appears quite inefficient, needing a very long secret key, turning a keyword~$w$ into a bunch of PRF outputs, and then storing each of these PRF outputs in the BF.
+Havent read the full analysis; don't know if this was ever published.
+}
 \end{itemize}
@@
 \item Durham, Kantarcioglu, Xue, Kuzu, Malin ``Composite Bloom Filters for Secure Record Linkage'' \tsnote{Per-field BFs, sampled and composed into single BF that is then permuted by a secret random permtation.
-No clear statement of the problem that is being solved.}
+No clear statement of the problem that is being solved.
+Should pull full version and get details.}
 \end{itemize}

### 2016-07-06 filters.tex
syntax, new auth notes

@@
 For each experiment, we define an associated advantage
-notion.Namely, given an $(n,k,m)$-filter~$B=(\Hash,\Rep,\Qry)$,
+notion.  Namely, given an $(n,k,m)$-filter~$B=(\Hash,\Rep,\Qry)$,
 distribution~$\distr{U}{n}$ and adversary~$A$, we define:
@@
 $q_{\mathrm{h}}$ that the adversary makes.
+
+We note that the distribution~$\distr{U}{n}$ must be independent of the hash functions $h_1,h_2,\ldots,h_k$ that are used to create~$M$.
+Otherwise, when (say) $\Sigma=\bits$, the distribution may only assign positive probability to sets~$S$ that cause an abnormally large number of bits in~$M$ to be set to 1.
+Our security notions enforce this independence.
 
@@
 
-\heading{Privacy of hash-based filters.} \tsnote{This is wide open.
-Privacy of~$S$?
-Privacy of~$M$?
-(The latter may or may not imply the former, depending on how we define things.)  Under what assumptions on~$S$ --~min-entropy, computational unguessability, other?
-Do we want to allow for explicit side information/precomputation?
-We want something that captures realistic scenarios.}
+\heading{Privacy of hash-based filters.} We now define privacy notions for $(n,k,m)$-filters.
+Informally, the adversary's goal is to guess one of the elements of the set~$S$.
+Of course, if the distribution~$\distr{U}{n}$ has low min-entropy with respect to any particular element $x \in U$, then it will be relatively easy to guess~$x$.
+To capture this min-entropy, let $p_{\mathrm{max}} = \max_{x \in U} \Prob{S \getsr \distr{U}{n}:\, x \in S}$ and define $\mu = -\log_2 p_{\mathrm{max}}$ to be the (element-wise) min-entropy of distribution $\distr{U}{n}$.
+
+We note that~$S$ must be independent of the hash functions~$h_1,h_2,\ldots,h_k$ used to create the representation of~$S$.  \tsnote{I thought this would be needed, but now I'm not sure it is. }
 

### 2016-07-06 mutable-filters.tex
syntax, new auth notes

@@
 The deterministic \emph{test} algorithm $\Test \colon \multiset{U}{} \times \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right)\cup\{\bot\} \times U \rightarrow \bits$ takes a multiset~$S$, a representation~$M$ and an element~$x \in U$ and returns a bit.
+\tsnote{The point of $\Test$ is to capture correctness, which is not guaranteed in this setting.
+(It isn't something one would actually implement in practice.)  Intuitively, $\Test$ outputs 1 iff $x \in S$ but the representation~$M$ ``says'' it is not.}
 %
@@
 We captures two versions of correctness in Figure~\ref{fig:correctness-mutable}, corresponding to whether or not the adversary is given access to the hash functions used to create and update the multiset representation.
+\tsnote{These are draft experiments!}
 
@@
 $x \getsr A^{\QryOracle,\UpdateOracle}(S)$\\
-if $\Test^{\HashOracle}(S,M,x) \neq 1$ then Ret 1\\
+if $\Test^{\HashOracle}(S,M,x) \neq 1$ then\\
+\nudge Ret 1\\
 Ret 0
@@
 
-\heading{Privacy of hash-based filters.} \tsnote{To-do.}
+\heading{Privacy of Mutable hash-based filters.} \tsnote{To-do.}
 

### 2016-07-06 tasks_and_ideas.tex
syntax, new auth notes

@@
 If the distribution of the expected number of zero bits is tight around its mean, then you can use the actual number of 0-bits as the expected number, and then deduce the size of the set.}  Also, what about set-intersection attacks on Bloom filters?
-\item This raises the more general question of schemes/protocols that use multiple Bloom filters to represent a single set based on distinct features of set elements.  We should dig into this.
+
+\item This raises the more general question of schemes/protocols that use multiple Bloom filters to represent a single set based on distinct features of set elements.
+We should dig into this.
+\tsnote{Not sure if this requires new syntax and/or notions.
+But basically this is what the Neidermayer et al.\ attacks exploit -- that medical records consist of multiple fields, and the record-linkage protocol produces a BF for each field.
+(If you think of records as rows in a DB, there's a BF for each column.) One of the fields is the patient's surname, and the attack uses clever frequency analysis to recover surnames.}
 

### 2016-07-06 intro.tex
adding related work
syntax, new auth notes

@@
 Note that in the ROM (and probably in practice) finding~$f>1$ FPs will
-require~$f$ times the work.  Right?} 
+require~$f$ times the work.  Right?} \tsnote{FYI: this is how MAC security against multiple forgeries is defined.  See \texttt{https://eprint.iacr.org/2006/095.pdf} for details.}
 %\tsnote{Here's an off-the-wall idea.  What if the basic FP security
@@
 \begin{itemize}
-\item Mitzenmacher and Vadhan.\tsnote{Might only be tangential.}
+\item Chang and Mitzenmacher ``Privacy Preserving Keyword Searches on Remote Encrypted Data''.
+\item Mitzenmacher and Vadhan. ``Why Simple Hash Functions Work: Exploiting the Entropy in a Data Stream''.
 \item Dodis et al.

### 2016-07-06 filters.tex
syntax, new auth notes
privacy notions now give the representation M to the adversary; this was missing before, and the notions did not capture real privacy attacks

@@
 also allows us to capture constructions in the random-oracle model.
+\tsnote{I'm not sure this is really useful for anything other than ROM analysis.
+Perhaps for settings in which the hash-functions are secret, but the attack surface expose a way for the adversary to see their outputs?}
 
@@
 \heading{Privacy of hash-based filters.} We now define privacy notions for $(n,k,m)$-filters.
-Informally, the adversary's goal is to guess one of the elements of the set~$S$.
+Informally, the adversary is given the representation~$M$ of a secret set~$S$, and its goal is to guess one of the elements of~$S$.
 Of course, if the distribution~$\distr{U}{n}$ has low min-entropy with respect to any particular element $x \in U$, then it will be relatively easy to guess~$x$.
@@
 We note that~$S$ must be independent of the hash functions~$h_1,h_2,\ldots,h_k$ used to create the representation of~$S$.  \tsnote{I thought this would be needed, but now I'm not sure it is. }
+
+A weaker notion of privacy would not give~$M$ to the adversary.
+However, this would not capture attacks such as those mounted by Neidermayer et al.\cite{XXX}, and would not speak to settings in which (say) an honest-but-curious third party is given the representation~$M$ in order to carry out some task on behalf of the holder of~$S$.
 
@@
 $(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle}()$\\
+$x \getsr A^{\QryOracle}(M)$\\
 if $x\in S$ then Ret 1\\
@@
 $(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle,\HashOracle}()$\\
+$x \getsr A^{\QryOracle,\HashOracle}(M)$\\
 if $x\in S$ then Ret 1\\
@@
 $(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle}(\{h_1,h_2,\ldots,h_k\})$\\
+$x \getsr A^{\QryOracle}(M,\{h_1,h_2,\ldots,h_k\})$\\
 if $x\in S$ then Ret 1\\

### 2016-07-06 intro.tex
privacy notions now give the representation M to the adversary; this was missing before, and the notions did not capture real privacy attacks

@@
 web proxies like Squid~\cite{xxx} do \emph{not} use secrets in their
-Bloom filters.  They use the basic Bloom filter with four hash
+Bloom filters.  Squid, in particular, uses the basic Bloom filter with four hash
 functions, defined as follows: $h_1(x) =
@@
 secrets in the Bloom filters used by Google's BigTable~\cite{xxx},
-HBase~\cite{xxx}, \tsnote{make an impressive list.}  There are
-applications in which the proposed Bloom filter instantiations do
+HBase~\cite{xxx}, \tsnote{make an impressive list.}
+
+There are applications in which the proposed Bloom filter instantiations do
 use secretly keyed hash functions, e.g. $h_j(x) = (f(K_0,x) + j\cdot

### 2016-07-06 filters.tex
adding a new heading/placeholder for results about the privacy of certain BF schemes

@@
 
+\heading{Achieving FP-security and privacy.}
+\tsnote{Under our current notions, you can never hope to prove privacy bounds that beat the min-entropy of $\distr{U}{n}$.}
+\tsnote{We should prove privacy for the bigram/PRF-based double-hashing construction that Neidermayer et al.\ attacks.
+I'm pretty sure the attack is in the public-BB setting, and the provable security bound is considerably worse than the min-entropy because of the way the representation is made.
+(Essentially, the Hamming weight of the representation is a good estimate of the length of the longest surname in filter.)  Note that their attack would allow one to recover \emph{every} name, not just one.}
+\tsnote{Prove that the basic BF, in the ROM, is private.
+This also shows that the basic BF with $h_j(x)=F_K(\langle j,x \rangle)$ is private.
+I believe this also shows that the bigram approach examined by Neidermayer et al.\ is secure when the hash functions are the $h_j(x)$ just described.
+}
+\tsnote{Prove privacy of other suggestions, such as the record-level BF from Durham et al.?}
+
 \heading{Security in multiple-server settings. }  \jnote{What is the

### 2016-07-06 intro.tex
adding a new heading/placeholder for results about the privacy of certain BF schemes

@@
 frequency analysis recovered the last names of patients given access
-only to the Bloom filter array.\tsnote{This shows that
-false-positive security and privacy (whatever it is) are orthogonal,
-since I'm pretty sure this ``encrypted'' bloom filter resists FPs.})
+only to the Bloom filter array.)
+%\tsnote{This shows that false-positive security and privacy (whatever it is) are orthogonal,
+%since I'm pretty sure this ``encrypted'' bloom filter resists FPs.})
 In any case, it is clear that the NY definition does not capture the

### 2016-07-06 filters-multi-server.tex
restructuring and other updates

--- 2016-07-06 filters.tex
@@
-\section{Hash-based Filters}
-\heading{Preliminaries.}
-When~$U$ is a set and $n>0$ is an integer, we let $[U]^n$ denote the set of all size-$n$ subsets of~$U$.
-We write $x \getsr U$ to denote sampling an element from~$U$ and assigning this to~$x$, and we extend this notation to randomized algorithms.
-
-\heading{Syntax.}
-Fix a nonempty sets $U,\Sigma$ and integers $k,m,n>0$.  Fix a symbol $\bot \not\in U$.  An $(n,k,m)$-filter (over universe~$U$) is a tuple  $B=(\Hash,\Rep,\Qry)$.
-%
-The randomized \emph{hash-sampling} algorithm~$\Hash$ samples a
-size~$k$  family of functions~$\mathcal{H}=\{h_1,h_2,\ldots,h_k\}$
-where each $h_i \in  \mathrm{Func}(U,[m])$.  We write $\mathcal{H}
-\getsr \Hash$ for this operation.
-%
-The randomized representation algorithm $\Rep\colon [U]^n \rightarrow
-\Sigma^m \times \bits^*$ takes a set~$S$ of~$n$ elements as input, and outputs
-representation~$M$ of length~$m$ along with (possibly empty) side-information~$\tau$.
-%
-The deterministic query algorithm $\Qry\colon \Sigma^m \times \bits^* \times U
-\rightarrow \bits$ takes a representation $M$, side-information~$\tau$, and an element $x \in
-U$, and returns a bit.
-%
-We assume that both $\Rep$ and $\Qry$ have blackbox access to the
-functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$.
-Typically this access will be implicit, but when we need to make it explicit we will write~$\mathcal{H}$ (or the individual hash functions) as superscripts.
-%which we denote by writing~$\mathcal{H}$ as a superscript.
-%Thus, we write $M \gets \Rep^{\mathcal{H}}(S)$ and $b \gets \Qry^{\mathcal{H}}(M,x)$ for the execution of the representation and query algorithms, respectively.
-%
-%We write $M \gets \Rep(S)$ and $b \gets \Qry(M,x)$ for the execution of the representation and query algorithms, respectively.
-For correctness, we demand that for all~$S$ of size~$n$ and all $x
-\in S$, it holds that $\Prob{\mathcal{H}\getsr\Hash;\,(M,\tau)\getsr\Rep(S)\,:\,\Qry(M,\tau,x)=1}=1$, where the
-probability is over the coins of $\Hash$ and~$\Rep$.
-
-%\heading{Discussion.}
-This syntax captures classical Bloom filters by setting~$\Sigma=\bits$,  and defining $\Rep,\Qry$ in the obvious way, with $\tau=\emptystring$.
-We note that even though $\Rep$ may be randomized, it does not have to be; for the classical Bloom filter, it is deterministic.
-
-By allowing $\Rep$ to output side-information, we allow for (say) $\Rep$ and $\Qry$ to share a secret key selected during representation generation.
-\tsnote{Ultimately it might be cleaner to fold the hash functions into the side-information, too.
-But in that case, we will likely want an explicit separation between private side-information (e.g., the key for a secret permutation of the bits of~$M$) and public side-information (e.g., the hash functions used to create~$M$).
-Note that we do see constructions that have \emph{no} ``stand-alone'' hash functions yet use a secret key (e.g., the PRF-based double-hashing construction), and also schemes that employ \emph{both} stand-alone hash functions and a secret key (e.g.
-the record BF from Durham et al.)}  In our security notions, any side-information will be kept secret from the adversary.
-
-Setting $\Sigma=\bits^{\leq L}$ allows one to store a bitstring of length at most~$L$ at each location.
-This allows our syntax to capture the cuckoo-hashing construction from NY, as well as the ``garbled Bloom filter'' from Dong, Chen and Wen~\cite{xxx}, among other things.
-We note that even though this would allow for the storage of counters (say) at each filter location, our restriction that~$\Qry$ returns a bit does not capture functionality typically demanded of Bloom filters that employ counters, e.g., returning a counter value.
-(One could, however, have $\Qry$ compute an arbitrary, fixed predicate.
-For example, ``has~$x$ been seen at least 5 times?''.)
-Our syntax also does not capture filters that are mutable, that is, whose representation may change over time.
-On the other hand, we can state a simple correctness condition for these kinds of filters; this will not be true when we further generalize to capture, properly, counters and mutability.
-
-\heading{FP-security of hash-based filters.} \tsnote{NY give it in
-the private hash setting (sort of); but, intuitively, it should be
-hard to find false-positives even if you know that MD5 or SHA-x are
-the hash functions.  Not totally sure how to capture this intuition
-nicely.} \jnote{Not sure I agree. First of all, if $\epsilon$ is not
-negligible then a random element is a false positive with noticeable
-probability. Beyond that, I think that intuitively it makes sense
-that if you want false positives to be hard to find then you need to
-make the hash functions secret.} \tsnote{I don't think it makes sense
-to talk about asymptotics or negligibility, for exactly the reason you
-state. I think the key point here is: what is ``hard''?   The designer decides what FP rate is
-acceptable for a given application, a given set of efficiency
-constraints, the side-effects of a FP, etc.  For a fixed FP target,
-she optimizes the filter size and/or the number of hash functions for
-her setting. Whether the target FP rate is 0.01 or $2^{-80}$, we should be able to say (in the ROM, at least)
-that it will take this-many hash computations, and this many on-line
-set-membership queries, to find the first FP.  In the standard model,
-with public hash functions, it is clearly more difficult to make
-formal claims.  Even so, in practice I expect it would be quite expensive to
-find a string~$x$ such that $(h_1(x),h_2(x),\ldots,h_k(x))$
-falls in a given set of tuples when $h_i(x)=\mathrm{truncate}(\mathrm{SHA256}(\langle i \rangle
-\concat x), m)$, say. (Even more so if my setting admits relatively
-expensive hash computations, e.g. SCRYPT.)  BTW, your suggestion to
-have a FP notion with secret~$\mathcal{S}$ is interesting here. }
-
-The traditional notion of soundness
-for a Bloom filter captures the difficulty of finding false
-positives when the attacker is non-adaptive. Following NY, we
-consider soundness against adaptive adversaries. But we further
-generalize to allow for settings in which the attacker may have some
-a priori knowledge about the contents of~$S$. (The Niedermaier et
-al.~\cite{xxx} attacks, for example, exploit knowledge about the
-distribution of German last names.)   In particular, our notions
-take as input an explicit distribution $\distr{U}{n}$ over~$[U]^n$.
-
-\jknote{We also want to capture the fact that finding the first
-false positive should not make it any easier to find subsequent
-false positives. This is not really captured by the Naor paper,
-either (at least not directly, though it may end up being implied by
-their definition).} \tsnote{See my comment in the intro.}
-
-In Figure~\ref{fig:fp-filter} we give three distinct notions,
-characterized by what access the adversary has to the underlying
-hash functions used by the filter.  In the top notion, the hash
-functions are secret.  This is the setting addressed by NY, and it
-captures applications in which the hash functions are (say) secretly
-keyed PRFs, and in which no explicit, external interface to these is
-surfaced.
-%
-The bottom notion considers the case that the full code of the hash functions is known to the attacker.
-This is the case, for example, when attacking the Bloom filters used in the Squid proxy~\cite{xxx}.
-%
-The middle notion is a compromise: it makes the hash functions
-public, but assumes that the adversary only accesses them in a
-black-box manner.  That is, the adversary does not exploit
-structural features of the hash functions in its attack.  This
-notion makes it easy to track the query complexity of an attack, and
-also allows us to capture constructions in the random-oracle model.
-
-For each experiment, we define an associated advantage
-notion.  Namely, given an $(n,k,m)$-filter~$B=(\Hash,\Rep,\Qry)$,
-distribution~$\distr{U}{n}$ and adversary~$A$, we define:
-\begin{align*}
-\AdvFPSecHash{B}{\distr{U}{n},A} &= \Prob{\ExpFPSecHash{B}{\distr{U}{n},A}} \\
-\AdvFPPubHashBB{B}{\distr{U}{n},A} &= \Prob{\ExpFPPubHashBB{B}{\distr{U}{n},A}} \\
-\AdvFPSecHash{B}{\distr{U}{n},A} &= \Prob{\ExpFPPubHash{B}{\distr{U}{n},A}}
-\end{align*}
-The probabilities are over the coins of the indicated experiment,
-and the coins of the adversary.   In all experiments, we track the
-time-complexity~$t$ of~$A$, as well as the number of set-membership
-($\QryOracle$ oracle) queries~$q_{\mathrm{sm}}$ that it makes.   In
-the second, we also track the number of hash-queries
-$q_{\mathrm{h}}$ that the adversary makes.
-
-We note that the distribution~$\distr{U}{n}$ must be independent of the hash functions $h_1,h_2,\ldots,h_k$ that are used to create~$M$.
-Otherwise, when (say) $\Sigma=\bits$, the distribution may only assign positive probability to sets~$S$ that cause an abnormally large number of bits in~$M$ to be set to 1.
-Our security notions enforce this independence.
-
-\jnote{How do we want to define a ``secure'' Bloom filter (even
-informally)? Do we want to say that the probability of finding a
-false positive is negligible? Or that if we set the FP rate to
-$\epsilon$ then the best an attacker can do with $q$ hash queries is
-$1-(1-\epsilon)^q$ plus negligible?} 
-\tsnote{Formally, I don't think we can (and still be rooted in
-  reality.)  Even informally it's hard, since the fact is that the
-  designer decides what is ``secure'' for her setting.  I think we
-  just say something like ``A bloom filter is
-  $(t,q_h,q_m,\epsilon)$-secure if no attacker running in time at
-  most~$t$, asking at most~$q_h$ hash queries and $q_m$ set-membership
-  queries, has probability more than~$\epsilon$ of finding a FP.''  (If
-you like, we can throw a paramter~$n$ in there, for the number of FPs
-it must find.)  Perhaps informally we say that a bloom filter is
-secure if, for ``reasonable'' $t,q_h,q_m$, the value of~$\epsilon$ is
-not ``significantly larger'' than the designer's target.  I guess
-that's not far off from one of your suggestions.}
-
-\jnote{One thing that is nice about the
-NY notion is that you get a ``clean'' definition of security: no
-matter how many FPs the attacker has found so far, the probability
-that it can output a fresh FP is still $\epsilon$.}
-
-\jnote{What parameters are needed to get negligible $\epsilon$? Are
-they reasonable in practice?} \tsnote{Again, I don't think that
-negligible is reasonable in practice :P}
-
-\begin{figure}
-\centering
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpFPSecHash{B}{\distr{U}{n},A}$}\\
-$S \getsr \distr{U}{n}$\\
-$h_1,\ldots,h_k \getsr \Hash$\\
-$\HashOracle = (h_1, \ldots, h_k)$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle}(S)$\\
-if $x \not\in S \wedge \Qry^{\HashOracle}(M,\tau,x)=1$ then\\
-\nudge Ret 1\\
-Ret 0
-}
-%
-{
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
-
-\medskip
-\oracle{$\HashOracle(i,x)$}\\
-Ret $h_i(x)$\\
-}
-}
-%%%%%%%
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpFPPubHashBB{B}{\distr{U}{n}, A}$}\\
-$S \getsr \distr{U}{n}$\\
-$h_1,\ldots,h_k \getsr \Hash$\\
-$\HashOracle = (h_1, \ldots, h_k)$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle,\HashOracle}(S)$\\
-if $x \not\in S \wedge \Qry^{\HashOracle}(M,\tau,x)=1$ then\\
-\nudge Ret 1\\
-Ret 0
-}
-%
-{
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
-
-\medskip
-\oracle{$\HashOracle(i,x)$}\\
-Ret $h_i(x)$\\
-}
-}
-%%%%%%%
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpFPPubHash{B}{\distr{U}{n}, A}$}\\
-$S \getsr \distr{U}{n}$\\
-$h_1,\ldots,h_k \getsr \Hash$\\
-$\HashOracle = (h_1, \ldots, h_k)$\\
-$(M,\tau) \gets \Rep^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle}(S,\{h_1,h_2,\ldots,h_k\})$\\
-if $x \not\in S \wedge \Qry^{\HashOracle}(M,\tau,x)=1$ then\\
-\nudge Ret 1\\
-Ret 0
-}
-%
-{
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
-
-\medskip
-\oracle{$\HashOracle(i,x)$}\\
-Ret $h_i(x)$\\
-} } \caption{False-positive security (soundness) for an
-$(n,k,m)$-filter~$B$ with private hash functions (top), black-box
-queriable hash functions (middle), and public hash functions
-(bottom). \jnote{Could also consider not giving $S$ to the
-adversary.} } \label{fig:fp-filter}
-\end{figure}
-
-%%%%
-% \if{0}
-% \begin{figure}
-% \centering
-% \fpage{.6}{
-% \hpagess{.6}{.35}
-% {
-% \experimentv{$\ExpFPSecHash{S,B}{A}$}\\
-% $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-% $M \gets \Rep^{\HashOracle}(S)$\\
-% $x \getsr A^{\QryOracle}(S)$\\
-% if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
-% \nudge Ret 1\\
-% Ret 0
-% }
-% %
-% {
-% \oracle{$\QryOracle(x)$}\\
-% Ret $\Qry^{\HashOracle}(M,x)$\\
-
-% \medskip
-% \oracle{$\HashOracle(i,x)$}\\
-% Ret $h_i(x)$\\
-% }
-% }
-% %%%%%%%
-% \fpage{.6}{
-% \hpagess{.6}{.35}
-% {
-% \experimentv{$\ExpFPPubHashBB{S,B}{A}$}\\
-% $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-% $M \gets \Rep^{\HashOracle}(S)$\\
-% $x \getsr A^{\QryOracle,\HashOracle}(S)$\\
-% if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
-% \nudge Ret 1\\
-% Ret 0
-% }
-% %
-% {
-% \oracle{$\QryOracle(x)$}\\
-% Ret $\Qry^{\HashOracle}(M,x)$\\
-
-% \medskip
-% \oracle{$\HashOracle(i,x)$}\\
-% Ret $h_i(x)$\\
-% }
-% }
-% %%%%%%%
-% \fpage{.6}{
-% \hpagess{.6}{.35}
-% {
-% \experimentv{$\ExpFPPubHash{S,B}{A}$}\\
-% $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-% $M \gets \Rep^{\HashOracle}(S)$\\
-% $x \getsr A^{\QryOracle}(S,\{h_1,h_2,\ldots,h_k\})$\\
-% if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
-% \nudge Ret 1\\
-% Ret 0
-% }
-% %
-% {
-% \oracle{$\QryOracle(x)$}\\
-% Ret $\Qry^{\HashOracle}(M,x)$\\
-
-% \medskip
-% \oracle{$\HashOracle(i,x)$}\\
-% Ret $h_i(x)$\\
-% }
-% }
-% \caption{False-positive security (soundness) for an $(n,k,m)$-filter~$B$ with private hash functions (top), black-box queriable hash functions (middle), and public hash functions (bottom). }
-% \label{fig:fp-filter}
-% \end{figure}
-%\fi
-%%%%%
-
-\heading{Privacy of hash-based filters.} We now define privacy notions for $(n,k,m)$-filters.
-Informally, the adversary's goal is to guess one of the elements of the set~$S$.
-Of course, if the distribution~$\distr{U}{n}$ has low min-entropy with respect to any particular element $x \in U$, then it will be relatively easy to guess~$x$.
-To capture this min-entropy, let $p_{\mathrm{max}} = \max_{x \in U} \Prob{S \getsr \distr{U}{n}:\, x \in S}$ and define $\mu = -\log_2 p_{\mathrm{max}}$ to be the (element-wise) min-entropy of distribution $\distr{U}{n}$.
-
-We note that~$S$ must be independent of the hash functions~$h_1,h_2,\ldots,h_k$ used to create the representation of~$S$.  \tsnote{I thought this would be needed, but now I'm not sure it is. }
-
-\begin{figure}
-\centering
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpPrivSecHash{B}{\distr{U}{n}, A}$}\\
-$S \getsr \distr{U}{n}$\\
-$h_1,\ldots,h_k \getsr \Hash$\\
-$\HashOracle = (h_1, \ldots, h_k)$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle}()$\\
-if $x\in S$ then Ret 1\\
-Ret 0
-}
-%
-{
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
-
-\medskip
-\oracle{$\HashOracle(i,x)$}\\
-Ret $h_i(x)$\\
-}
-}
-%%%%%%%%%%
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpPrivPubHashBB{B}{\distr{U}{n}, A}$}\\
-$ S \getsr \distr{U}{n}$\\
-$h_1,\ldots,h_k \getsr \Hash$\\
-$\HashOracle = (h_1, \ldots, h_k)$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle,\HashOracle}()$\\
-if $x\in S$ then Ret 1\\
-Ret 0\\
-}
-%
-{
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
-
-\medskip
-\oracle{$\HashOracle(i,x)$}\\
-Ret $h_i(x)$\\
-}
-}
-%%%%%%%
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpPrivPubHash{B}{\distr{U}{n}, A}$}\\
-$ S \getsr \distr{U}{n}$\\
-$h_1,\ldots,h_k \getsr \Hash$\\
-$\HashOracle = (h_1, \ldots, h_k)$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle}(\{h_1,h_2,\ldots,h_k\})$\\
-if $x\in S$ then Ret 1\\
-Ret 0\\
-}
-%
-{
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
-
-\medskip
-\oracle{$\HashOracle(i,x)$}\\
-Ret $h_i(x)$\\
-}
-}
-\caption{Set-privacy for an $(n,k,m)$-filter~$B$ for private (top), black-box queriable (middle),  and public (bottom) hash functions. \textcolor{cyan}{Revisit when the FP notion settles out.}}
-\label{fig:fp-filter}
-\end{figure}
-
-\heading{Security in multiple-server settings. }  \jnote{What is the
+\section{Security in multiple-server settings. }  \jnote{What is the
 goal here? If they don't share hash functions, I'm not sure what is

### 2016-07-06 filters-notions.tex
restructuring and other updates

--- 2016-07-06 filters.tex
@@
-\section{Hash-based Filters}
-\heading{Preliminaries.}
-When~$U$ is a set and $n>0$ is an integer, we let $[U]^n$ denote the set of all size-$n$ subsets of~$U$.
-We write $x \getsr U$ to denote sampling an element from~$U$ and assigning this to~$x$, and we extend this notation to randomized algorithms.
-
-\heading{Syntax.}
-Fix a nonempty sets $U,\Sigma$ and integers $k,m,n>0$.  Fix a symbol $\bot \not\in U$.  An $(n,k,m)$-filter (over universe~$U$) is a tuple  $B=(\Hash,\Rep,\Qry)$.
-%
-The randomized \emph{hash-sampling} algorithm~$\Hash$ samples a
-size~$k$  family of functions~$\mathcal{H}=\{h_1,h_2,\ldots,h_k\}$
-where each $h_i \in  \mathrm{Func}(U,[m])$.  We write $\mathcal{H}
-\getsr \Hash$ for this operation.
-%
-The randomized representation algorithm $\Rep\colon [U]^n \rightarrow
-\Sigma^m \times \bits^*$ takes a set~$S$ of~$n$ elements as input, and outputs
-representation~$M$ of length~$m$ along with (possibly empty) side-information~$\tau$.
-%
-The deterministic query algorithm $\Qry\colon \Sigma^m \times \bits^* \times U
-\rightarrow \bits$ takes a representation $M$, side-information~$\tau$, and an element $x \in
-U$, and returns a bit.
-%
-We assume that both $\Rep$ and $\Qry$ have blackbox access to the
-functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$.
-Typically this access will be implicit, but when we need to make it explicit we will write~$\mathcal{H}$ (or the individual hash functions) as superscripts.
-%which we denote by writing~$\mathcal{H}$ as a superscript.
-%Thus, we write $M \gets \Rep^{\mathcal{H}}(S)$ and $b \gets \Qry^{\mathcal{H}}(M,x)$ for the execution of the representation and query algorithms, respectively.
-%
-%We write $M \gets \Rep(S)$ and $b \gets \Qry(M,x)$ for the execution of the representation and query algorithms, respectively.
-For correctness, we demand that for all~$S$ of size~$n$ and all $x
-\in S$, it holds that $\Prob{\mathcal{H}\getsr\Hash;\,(M,\tau)\getsr\Rep(S)\,:\,\Qry(M,\tau,x)=1}=1$, where the
-probability is over the coins of $\Hash$ and~$\Rep$.
-
-%\heading{Discussion.}
-This syntax captures classical Bloom filters by setting~$\Sigma=\bits$,  and defining $\Rep,\Qry$ in the obvious way, with $\tau=\emptystring$.
-We note that even though $\Rep$ may be randomized, it does not have to be; for the classical Bloom filter, it is deterministic.
-
-By allowing $\Rep$ to output side-information, we allow for (say) $\Rep$ and $\Qry$ to share a secret key selected during representation generation.
-\tsnote{Ultimately it might be cleaner to fold the hash functions into the side-information, too.
-But in that case, we will likely want an explicit separation between private side-information (e.g., the key for a secret permutation of the bits of~$M$) and public side-information (e.g., the hash functions used to create~$M$).
-Note that we do see constructions that have \emph{no} ``stand-alone'' hash functions yet use a secret key (e.g., the PRF-based double-hashing construction), and also schemes that employ \emph{both} stand-alone hash functions and a secret key (e.g.
-the record BF from Durham et al.)}  In our security notions, any side-information will be kept secret from the adversary.
-
-Setting $\Sigma=\bits^{\leq L}$ allows one to store a bitstring of length at most~$L$ at each location.
-This allows our syntax to capture the cuckoo-hashing construction from NY, as well as the ``garbled Bloom filter'' from Dong, Chen and Wen~\cite{xxx}, among other things.
-We note that even though this would allow for the storage of counters (say) at each filter location, our restriction that~$\Qry$ returns a bit does not capture functionality typically demanded of Bloom filters that employ counters, e.g., returning a counter value.
-(One could, however, have $\Qry$ compute an arbitrary, fixed predicate.
-For example, ``has~$x$ been seen at least 5 times?''.)
-Our syntax also does not capture filters that are mutable, that is, whose representation may change over time.
-On the other hand, we can state a simple correctness condition for these kinds of filters; this will not be true when we further generalize to capture, properly, counters and mutability.
+\section{Security Notions for Hash-Based Filters}
 
@@
 \end{figure}
-
-\heading{Security in multiple-server settings. }  \jnote{What is the
-goal here? If they don't share hash functions, I'm not sure what is
-gained by considering this definition.} \tsnote{Perhaps not the same
-hash functions, but correlated ones.  For example, server~$j$ uses
-hash functions $\tilde{h}_i(x) = h_i(\langle \mathrm{id}_j \rangle \concat x)$ for
-some $h_i$ shared among servers.  The $\mathrm{id}_j$ may or may not
-be public, e.g. in a P2P network your ID might be a nonce learned only
-when you join.  Also, the sets $\mathcal{S_j}$ stored at each server
-might be correlated.} In this section, we consider
-security notions for settings in which there may be multiple
-servers, each holding a filter representation of a set.  To allow
-for each server to embed server-specific information into its
-representation, we abstract the servers as $B_1,B_2,\ldots,B_\ell$
-where each $B_i=(\Hash_i,\Rep_i,\Qry_i)$ is an $(n,k,m)$-filter.
-\tsnote{Still some kinks to be ironed out though.  The current
-notions sample fresh hash functions for each server.  But in (say)
-the Squid setting, the same hash functions are used across all Squid
-instances... maybe it suffices, for that setting, to say that the
-$\Hash_i$ are all the same, and each simply returns a fixed set
-of~$k$ hash functions (i.e., deterministic).} To model insider
-attacks, we give the adversary the ability to corrupt (adaptively)
-instances of the filter.  Such attacks capture P2P settings, in
-which the adversary may join the network as a peer.
-
-\begin{figure}
-\centering
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpFPSecHash{B_1,B_2,\ldots,B_\ell}{\distr{U}{n}, A}$}\\
-$\mathcal{C} \gets \emptyset$\\
-for $i=1$ to $\ell$\\
-\nudge $S_i \getsr \distr{U}{n}$\\
-\nudge $ \mathcal{H}_i \gets \{h^i_1,h^i_2,\ldots,h^i_k\} \getsr \Hash_i$\\
-\nudge $M_i \getsr \Rep_i^{\HashOracle(i,\cdot,\cdot)}(S_i)$\\
-$(i,x) \getsr A^{\QryOracle,\CorruptOracle}(\{S_i\}_{i=1}^{\ell})$\\
-if $i \not\in \mathcal{C} \wedge \Qry_i^{\HashOracle(i,\cdot,\cdot)}(M_i,x)=1$ then \\
-\nudge Ret 1\\
-Ret 0
-}
-%
-{
-\oracle{$\QryOracle(i,x)$}\\
-Ret $\Qry_i^{\HashOracle}(M_i,x)$\\
-
-\medskip
-\oracle{$\HashOracle(i,j,x)$}\\
-Ret $h^i_j(x)$\\
-
-\medskip
-\oracle{$\CorruptOracle(i,x)$}\\
-$\mathcal{C} \gets \mathcal{C} \cup \{i\}$\\
-Ret $M_i,\mathcal{H}_i$\\
-}
-}
-%%%%%%%%%%
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpFPPubHashBB{B_1,B_2,\ldots, B_\ell}{\distr{U}{n}, A}$}\\
-$\mathcal{C} \gets \emptyset$\\
-for $i=1$ to $\ell$\\
-\nudge $S_i \getsr \distr{U}{n}$\\
-\nudge $ \{h^i_1,h^i_2,\ldots,h^i_k\} \getsr \Hash_i$\\
-\nudge $M_i \getsr \Rep_i^{\HashOracle(i,\cdot,\cdot)}(S_i)$\\
-$(i,x) \getsr A^{\QryOracle,\HashOracle,\CorruptOracle}(\{S_i\}_{i=1}^{\ell})$\\
-if $i \not\in \mathcal{C} \wedge \Qry_i^{\HashOracle(i,\cdot,\cdot)}(M_i,x)=1$ then \\
-\nudge Ret 1\\
-Ret 0
-}
-%
-{
-\oracle{$\QryOracle(i,x)$}\\
-Ret $\Qry_i^{\HashOracle}(M_i,x)$\\
-
-\medskip
-\oracle{$\HashOracle(i,j,x)$}\\
-Ret $h^i_j(x)$\\
-
-\medskip
-\oracle{$\CorruptOracle(i,x)$}\\
-$\mathcal{C} \gets \mathcal{C} \cup \{i\}$\\
-Ret $M_i$\\
-}
-}
-%%%%%%%
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpFPPubHash{B_1,B_2,\ldots,B_\ell}{\distr{U}{n}, A}$}\\
-$\mathcal{C} \gets \emptyset$\\
-for $i=1$ to $\ell$\\
-\nudge $S_i \getsr \distr{U}{n}$\\
-\nudge $ \mathcal{H}_i \gets \{h^i_1,h^i_2,\ldots,h^i_k\} \getsr \Hash_i$\\
-\nudge $M_i \getsr \Rep_i^{\HashOracle(i,\cdot,\cdot)}(S_i)$\\
-$(i,x) \getsr A^{\QryOracle,\CorruptOracle}(\{S_i\}_{i=1}^{\ell},\{\mathcal{H}_i\}_{i=1}^{\ell})$\\
-if $i \not\in \mathcal{C} \wedge \Qry_i^{\HashOracle(i,\cdot,\cdot)}(M_i,x)=1$ then \\
-\nudge Ret 1\\
-Ret 0
-}
-%
-{
-\oracle{$\QryOracle(i,x)$}\\
-Ret $\Qry_i^{\HashOracle}(M_i,x)$\\
-
-\medskip
-\oracle{$\HashOracle(i,j,x)$}\\
-Ret $h^i_j(x)$\\
-
-\medskip
-\oracle{$\CorruptOracle(i,x)$}\\
-$\mathcal{C} \gets \mathcal{C} \cup \{i\}$\\
-Ret $M_i$\\
-}
-}
-\caption{False-positive security for an $(n,k,m)$-filter~$B$ in the multiple-server setting.
-(Three variations, depending on access to/knowledge of hash functions.) \textcolor{cyan}{Not clear which of these notions really makes sense.}}
-\label{fig:fp-filter}
-\end{figure}

### 2016-07-06 filters-results.tex
restructuring and other updates

--- 2016-07-06 filters.tex
@@
-\section{Hash-based Filters}
-\heading{Preliminaries.}
-When~$U$ is a set and $n>0$ is an integer, we let $[U]^n$ denote the set of all size-$n$ subsets of~$U$.
-We write $x \getsr U$ to denote sampling an element from~$U$ and assigning this to~$x$, and we extend this notation to randomized algorithms.
-
-\heading{Syntax.}
-Fix a nonempty sets $U,\Sigma$ and integers $k,m,n>0$.  Fix a symbol $\bot \not\in U$.  An $(n,k,m)$-filter (over universe~$U$) is a tuple  $B=(\Hash,\Rep,\Qry)$.
-%
-The randomized \emph{hash-sampling} algorithm~$\Hash$ samples a
-size~$k$  family of functions~$\mathcal{H}=\{h_1,h_2,\ldots,h_k\}$
-where each $h_i \in  \mathrm{Func}(U,[m])$.  We write $\mathcal{H}
-\getsr \Hash$ for this operation.
-%
-The randomized representation algorithm $\Rep\colon [U]^n \rightarrow
-\Sigma^m \times \bits^*$ takes a set~$S$ of~$n$ elements as input, and outputs
-representation~$M$ of length~$m$ along with (possibly empty) side-information~$\tau$.
-%
-The deterministic query algorithm $\Qry\colon \Sigma^m \times \bits^* \times U
-\rightarrow \bits$ takes a representation $M$, side-information~$\tau$, and an element $x \in
-U$, and returns a bit.
-%
-We assume that both $\Rep$ and $\Qry$ have blackbox access to the
-functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$.
-Typically this access will be implicit, but when we need to make it explicit we will write~$\mathcal{H}$ (or the individual hash functions) as superscripts.
-%which we denote by writing~$\mathcal{H}$ as a superscript.
-%Thus, we write $M \gets \Rep^{\mathcal{H}}(S)$ and $b \gets \Qry^{\mathcal{H}}(M,x)$ for the execution of the representation and query algorithms, respectively.
-%
-%We write $M \gets \Rep(S)$ and $b \gets \Qry(M,x)$ for the execution of the representation and query algorithms, respectively.
-For correctness, we demand that for all~$S$ of size~$n$ and all $x
-\in S$, it holds that $\Prob{\mathcal{H}\getsr\Hash;\,(M,\tau)\getsr\Rep(S)\,:\,\Qry(M,\tau,x)=1}=1$, where the
-probability is over the coins of $\Hash$ and~$\Rep$.
-
-%\heading{Discussion.}
-This syntax captures classical Bloom filters by setting~$\Sigma=\bits$,  and defining $\Rep,\Qry$ in the obvious way, with $\tau=\emptystring$.
-We note that even though $\Rep$ may be randomized, it does not have to be; for the classical Bloom filter, it is deterministic.
-
-By allowing $\Rep$ to output side-information, we allow for (say) $\Rep$ and $\Qry$ to share a secret key selected during representation generation.
-\tsnote{Ultimately it might be cleaner to fold the hash functions into the side-information, too.
-But in that case, we will likely want an explicit separation between private side-information (e.g., the key for a secret permutation of the bits of~$M$) and public side-information (e.g., the hash functions used to create~$M$).
-Note that we do see constructions that have \emph{no} ``stand-alone'' hash functions yet use a secret key (e.g., the PRF-based double-hashing construction), and also schemes that employ \emph{both} stand-alone hash functions and a secret key (e.g.
-the record BF from Durham et al.)}  In our security notions, any side-information will be kept secret from the adversary.
-
-Setting $\Sigma=\bits^{\leq L}$ allows one to store a bitstring of length at most~$L$ at each location.
-This allows our syntax to capture the cuckoo-hashing construction from NY, as well as the ``garbled Bloom filter'' from Dong, Chen and Wen~\cite{xxx}, among other things.
-We note that even though this would allow for the storage of counters (say) at each filter location, our restriction that~$\Qry$ returns a bit does not capture functionality typically demanded of Bloom filters that employ counters, e.g., returning a counter value.
-(One could, however, have $\Qry$ compute an arbitrary, fixed predicate.
-For example, ``has~$x$ been seen at least 5 times?''.)
-Our syntax also does not capture filters that are mutable, that is, whose representation may change over time.
-On the other hand, we can state a simple correctness condition for these kinds of filters; this will not be true when we further generalize to capture, properly, counters and mutability.
-
-\heading{FP-security of hash-based filters.} \tsnote{NY give it in
-the private hash setting (sort of); but, intuitively, it should be
-hard to find false-positives even if you know that MD5 or SHA-x are
-the hash functions.  Not totally sure how to capture this intuition
-nicely.} \jnote{Not sure I agree. First of all, if $\epsilon$ is not
-negligible then a random element is a false positive with noticeable
-probability. Beyond that, I think that intuitively it makes sense
-that if you want false positives to be hard to find then you need to
-make the hash functions secret.} \tsnote{I don't think it makes sense
-to talk about asymptotics or negligibility, for exactly the reason you
-state. I think the key point here is: what is ``hard''?   The designer decides what FP rate is
-acceptable for a given application, a given set of efficiency
-constraints, the side-effects of a FP, etc.  For a fixed FP target,
-she optimizes the filter size and/or the number of hash functions for
-her setting. Whether the target FP rate is 0.01 or $2^{-80}$, we should be able to say (in the ROM, at least)
-that it will take this-many hash computations, and this many on-line
-set-membership queries, to find the first FP.  In the standard model,
-with public hash functions, it is clearly more difficult to make
-formal claims.  Even so, in practice I expect it would be quite expensive to
-find a string~$x$ such that $(h_1(x),h_2(x),\ldots,h_k(x))$
-falls in a given set of tuples when $h_i(x)=\mathrm{truncate}(\mathrm{SHA256}(\langle i \rangle
-\concat x), m)$, say. (Even more so if my setting admits relatively
-expensive hash computations, e.g. SCRYPT.)  BTW, your suggestion to
-have a FP notion with secret~$\mathcal{S}$ is interesting here. }
-
-The traditional notion of soundness
-for a Bloom filter captures the difficulty of finding false
-positives when the attacker is non-adaptive. Following NY, we
-consider soundness against adaptive adversaries. But we further
-generalize to allow for settings in which the attacker may have some
-a priori knowledge about the contents of~$S$. (The Niedermaier et
-al.~\cite{xxx} attacks, for example, exploit knowledge about the
-distribution of German last names.)   In particular, our notions
-take as input an explicit distribution $\distr{U}{n}$ over~$[U]^n$.
-
-\jknote{We also want to capture the fact that finding the first
-false positive should not make it any easier to find subsequent
-false positives. This is not really captured by the Naor paper,
-either (at least not directly, though it may end up being implied by
-their definition).} \tsnote{See my comment in the intro.}
-
-In Figure~\ref{fig:fp-filter} we give three distinct notions,
-characterized by what access the adversary has to the underlying
-hash functions used by the filter.  In the top notion, the hash
-functions are secret.  This is the setting addressed by NY, and it
-captures applications in which the hash functions are (say) secretly
-keyed PRFs, and in which no explicit, external interface to these is
-surfaced.
-%
-The bottom notion considers the case that the full code of the hash functions is known to the attacker.
-This is the case, for example, when attacking the Bloom filters used in the Squid proxy~\cite{xxx}.
-%
-The middle notion is a compromise: it makes the hash functions
-public, but assumes that the adversary only accesses them in a
-black-box manner.  That is, the adversary does not exploit
-structural features of the hash functions in its attack.  This
-notion makes it easy to track the query complexity of an attack, and
-also allows us to capture constructions in the random-oracle model.
-\tsnote{I'm not sure this is really useful for anything other than ROM analysis.
-Perhaps for settings in which the hash-functions are secret, but the attack surface expose a way for the adversary to see their outputs?}
-
-For each experiment, we define an associated advantage
-notion.  Namely, given an $(n,k,m)$-filter~$B=(\Hash,\Rep,\Qry)$,
-distribution~$\distr{U}{n}$ and adversary~$A$, we define:
-\begin{align*}
-\AdvFPSecHash{B}{\distr{U}{n},A} &= \Prob{\ExpFPSecHash{B}{\distr{U}{n},A}} \\
-\AdvFPPubHashBB{B}{\distr{U}{n},A} &= \Prob{\ExpFPPubHashBB{B}{\distr{U}{n},A}} \\
-\AdvFPSecHash{B}{\distr{U}{n},A} &= \Prob{\ExpFPPubHash{B}{\distr{U}{n},A}}
-\end{align*}
-The probabilities are over the coins of the indicated experiment,
-and the coins of the adversary.   In all experiments, we track the
-time-complexity~$t$ of~$A$, as well as the number of set-membership
-($\QryOracle$ oracle) queries~$q_{\mathrm{sm}}$ that it makes.   In
-the second, we also track the number of hash-queries
-$q_{\mathrm{h}}$ that the adversary makes.
-
-We note that the distribution~$\distr{U}{n}$ must be independent of the hash functions $h_1,h_2,\ldots,h_k$ that are used to create~$M$.
-Otherwise, when (say) $\Sigma=\bits$, the distribution may only assign positive probability to sets~$S$ that cause an abnormally large number of bits in~$M$ to be set to 1.
-Our security notions enforce this independence.
-
-\jnote{How do we want to define a ``secure'' Bloom filter (even
-informally)? Do we want to say that the probability of finding a
-false positive is negligible? Or that if we set the FP rate to
-$\epsilon$ then the best an attacker can do with $q$ hash queries is
-$1-(1-\epsilon)^q$ plus negligible?} 
-\tsnote{Formally, I don't think we can (and still be rooted in
-  reality.)  Even informally it's hard, since the fact is that the
-  designer decides what is ``secure'' for her setting.  I think we
-  just say something like ``A bloom filter is
-  $(t,q_h,q_m,\epsilon)$-secure if no attacker running in time at
-  most~$t$, asking at most~$q_h$ hash queries and $q_m$ set-membership
-  queries, has probability more than~$\epsilon$ of finding a FP.''  (If
-you like, we can throw a paramter~$n$ in there, for the number of FPs
-it must find.)  Perhaps informally we say that a bloom filter is
-secure if, for ``reasonable'' $t,q_h,q_m$, the value of~$\epsilon$ is
-not ``significantly larger'' than the designer's target.  I guess
-that's not far off from one of your suggestions.}
-
-\jnote{One thing that is nice about the
-NY notion is that you get a ``clean'' definition of security: no
-matter how many FPs the attacker has found so far, the probability
-that it can output a fresh FP is still $\epsilon$.}
-
-\jnote{What parameters are needed to get negligible $\epsilon$? Are
-they reasonable in practice?} \tsnote{Again, I don't think that
-negligible is reasonable in practice :P}
-
-\begin{figure}
-\centering
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpFPSecHash{B}{\distr{U}{n},A}$}\\
-$S \getsr \distr{U}{n}$\\
-$h_1,\ldots,h_k \getsr \Hash$\\
-$\HashOracle = (h_1, \ldots, h_k)$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle}(S)$\\
-if $x \not\in S \wedge \Qry^{\HashOracle}(M,\tau,x)=1$ then\\
-\nudge Ret 1\\
-Ret 0
-}
-%
-{
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
-
-\medskip
-\oracle{$\HashOracle(i,x)$}\\
-Ret $h_i(x)$\\
-}
-}
-%%%%%%%
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpFPPubHashBB{B}{\distr{U}{n}, A}$}\\
-$S \getsr \distr{U}{n}$\\
-$h_1,\ldots,h_k \getsr \Hash$\\
-$\HashOracle = (h_1, \ldots, h_k)$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle,\HashOracle}(S)$\\
-if $x \not\in S \wedge \Qry^{\HashOracle}(M,\tau,x)=1$ then\\
-\nudge Ret 1\\
-Ret 0
-}
-%
-{
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
-
-\medskip
-\oracle{$\HashOracle(i,x)$}\\
-Ret $h_i(x)$\\
-}
-}
-%%%%%%%
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpFPPubHash{B}{\distr{U}{n}, A}$}\\
-$S \getsr \distr{U}{n}$\\
-$h_1,\ldots,h_k \getsr \Hash$\\
-$\HashOracle = (h_1, \ldots, h_k)$\\
-$(M,\tau) \gets \Rep^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle}(S,\{h_1,h_2,\ldots,h_k\})$\\
-if $x \not\in S \wedge \Qry^{\HashOracle}(M,\tau,x)=1$ then\\
-\nudge Ret 1\\
-Ret 0
-}
-%
-{
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
-
-\medskip
-\oracle{$\HashOracle(i,x)$}\\
-Ret $h_i(x)$\\
-} } \caption{False-positive security (soundness) for an
-$(n,k,m)$-filter~$B$ with private hash functions (top), black-box
-queriable hash functions (middle), and public hash functions
-(bottom). \jnote{Could also consider not giving $S$ to the
-adversary.} } \label{fig:fp-filter}
-\end{figure}
-
-%%%%
-% \if{0}
-% \begin{figure}
-% \centering
-% \fpage{.6}{
-% \hpagess{.6}{.35}
-% {
-% \experimentv{$\ExpFPSecHash{S,B}{A}$}\\
-% $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-% $M \gets \Rep^{\HashOracle}(S)$\\
-% $x \getsr A^{\QryOracle}(S)$\\
-% if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
-% \nudge Ret 1\\
-% Ret 0
-% }
-% %
-% {
-% \oracle{$\QryOracle(x)$}\\
-% Ret $\Qry^{\HashOracle}(M,x)$\\
-
-% \medskip
-% \oracle{$\HashOracle(i,x)$}\\
-% Ret $h_i(x)$\\
-% }
-% }
-% %%%%%%%
-% \fpage{.6}{
-% \hpagess{.6}{.35}
-% {
-% \experimentv{$\ExpFPPubHashBB{S,B}{A}$}\\
-% $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-% $M \gets \Rep^{\HashOracle}(S)$\\
-% $x \getsr A^{\QryOracle,\HashOracle}(S)$\\
-% if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
-% \nudge Ret 1\\
-% Ret 0
-% }
-% %
-% {
-% \oracle{$\QryOracle(x)$}\\
-% Ret $\Qry^{\HashOracle}(M,x)$\\
-
-% \medskip
-% \oracle{$\HashOracle(i,x)$}\\
-% Ret $h_i(x)$\\
-% }
-% }
-% %%%%%%%
-% \fpage{.6}{
-% \hpagess{.6}{.35}
-% {
-% \experimentv{$\ExpFPPubHash{S,B}{A}$}\\
-% $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-% $M \gets \Rep^{\HashOracle}(S)$\\
-% $x \getsr A^{\QryOracle}(S,\{h_1,h_2,\ldots,h_k\})$\\
-% if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
-% \nudge Ret 1\\
-% Ret 0
-% }
-% %
-% {
-% \oracle{$\QryOracle(x)$}\\
-% Ret $\Qry^{\HashOracle}(M,x)$\\
-
-% \medskip
-% \oracle{$\HashOracle(i,x)$}\\
-% Ret $h_i(x)$\\
-% }
-% }
-% \caption{False-positive security (soundness) for an $(n,k,m)$-filter~$B$ with private hash functions (top), black-box queriable hash functions (middle), and public hash functions (bottom). }
-% \label{fig:fp-filter}
-% \end{figure}
-%\fi
-%%%%%
-
-\heading{Privacy of hash-based filters.} We now define privacy notions for $(n,k,m)$-filters.
-Informally, the adversary is given the representation~$M$ of a secret set~$S$, and its goal is to guess one of the elements of~$S$.
-Of course, if the distribution~$\distr{U}{n}$ has low min-entropy with respect to any particular element $x \in U$, then it will be relatively easy to guess~$x$.
-To capture this min-entropy, let $p_{\mathrm{max}} = \max_{x \in U} \Prob{S \getsr \distr{U}{n}:\, x \in S}$ and define $\mu = -\log_2 p_{\mathrm{max}}$ to be the (element-wise) min-entropy of distribution $\distr{U}{n}$.
-
-We note that~$S$ must be independent of the hash functions~$h_1,h_2,\ldots,h_k$ used to create the representation of~$S$.  \tsnote{I thought this would be needed, but now I'm not sure it is. }
-
-A weaker notion of privacy would not give~$M$ to the adversary.
-However, this would not capture attacks such as those mounted by Neidermayer et al.\cite{XXX}, and would not speak to settings in which (say) an honest-but-curious third party is given the representation~$M$ in order to carry out some task on behalf of the holder of~$S$.
-
-\begin{figure}
-\centering
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpPrivSecHash{B}{\distr{U}{n}, A}$}\\
-$S \getsr \distr{U}{n}$\\
-$h_1,\ldots,h_k \getsr \Hash$\\
-$\HashOracle = (h_1, \ldots, h_k)$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle}(M)$\\
-if $x\in S$ then Ret 1\\
-Ret 0
-}
-%
-{
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
-
-\medskip
-\oracle{$\HashOracle(i,x)$}\\
-Ret $h_i(x)$\\
-}
-}
-%%%%%%%%%%
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpPrivPubHashBB{B}{\distr{U}{n}, A}$}\\
-$ S \getsr \distr{U}{n}$\\
-$h_1,\ldots,h_k \getsr \Hash$\\
-$\HashOracle = (h_1, \ldots, h_k)$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle,\HashOracle}(M)$\\
-if $x\in S$ then Ret 1\\
-Ret 0\\
-}
-%
-{
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
-
-\medskip
-\oracle{$\HashOracle(i,x)$}\\
-Ret $h_i(x)$\\
-}
-}
-%%%%%%%
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpPrivPubHash{B}{\distr{U}{n}, A}$}\\
-$ S \getsr \distr{U}{n}$\\
-$h_1,\ldots,h_k \getsr \Hash$\\
-$\HashOracle = (h_1, \ldots, h_k)$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle}(M,\{h_1,h_2,\ldots,h_k\})$\\
-if $x\in S$ then Ret 1\\
-Ret 0\\
-}
-%
-{
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
-
-\medskip
-\oracle{$\HashOracle(i,x)$}\\
-Ret $h_i(x)$\\
-}
-}
-\caption{Set-privacy for an $(n,k,m)$-filter~$B$ for private (top), black-box queriable (middle),  and public (bottom) hash functions. \textcolor{cyan}{Revisit when the FP notion settles out.}}
-\label{fig:fp-filter}
-\end{figure}
-
-\heading{Achieving FP-security and privacy.}
+\section{Achieving FP-Security and Privacy}
 \tsnote{Under our current notions, you can never hope to prove privacy bounds that beat the min-entropy of $\distr{U}{n}$.}
@@
 \tsnote{Prove privacy of other suggestions, such as the record-level BF from Durham et al.?}
-
-\heading{Security in multiple-server settings. }  \jnote{What is the
-goal here? If they don't share hash functions, I'm not sure what is
-gained by considering this definition.} \tsnote{Perhaps not the same
-hash functions, but correlated ones.  For example, server~$j$ uses
-hash functions $\tilde{h}_i(x) = h_i(\langle \mathrm{id}_j \rangle \concat x)$ for
-some $h_i$ shared among servers.  The $\mathrm{id}_j$ may or may not
-be public, e.g. in a P2P network your ID might be a nonce learned only
-when you join.  Also, the sets $\mathcal{S_j}$ stored at each server
-might be correlated.} In this section, we consider
-security notions for settings in which there may be multiple
-servers, each holding a filter representation of a set.  To allow
-for each server to embed server-specific information into its
-representation, we abstract the servers as $B_1,B_2,\ldots,B_\ell$
-where each $B_i=(\Hash_i,\Rep_i,\Qry_i)$ is an $(n,k,m)$-filter.
-\tsnote{Still some kinks to be ironed out though.  The current
-notions sample fresh hash functions for each server.  But in (say)
-the Squid setting, the same hash functions are used across all Squid
-instances... maybe it suffices, for that setting, to say that the
-$\Hash_i$ are all the same, and each simply returns a fixed set
-of~$k$ hash functions (i.e., deterministic).} To model insider
-attacks, we give the adversary the ability to corrupt (adaptively)
-instances of the filter.  Such attacks capture P2P settings, in
-which the adversary may join the network as a peer.
-
-\begin{figure}
-\centering
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpFPSecHash{B_1,B_2,\ldots,B_\ell}{\distr{U}{n}, A}$}\\
-$\mathcal{C} \gets \emptyset$\\
-for $i=1$ to $\ell$\\
-\nudge $S_i \getsr \distr{U}{n}$\\
-\nudge $ \mathcal{H}_i \gets \{h^i_1,h^i_2,\ldots,h^i_k\} \getsr \Hash_i$\\
-\nudge $M_i \getsr \Rep_i^{\HashOracle(i,\cdot,\cdot)}(S_i)$\\
-$(i,x) \getsr A^{\QryOracle,\CorruptOracle}(\{S_i\}_{i=1}^{\ell})$\\
-if $i \not\in \mathcal{C} \wedge \Qry_i^{\HashOracle(i,\cdot,\cdot)}(M_i,x)=1$ then \\
-\nudge Ret 1\\
-Ret 0
-}
-%
-{
-\oracle{$\QryOracle(i,x)$}\\
-Ret $\Qry_i^{\HashOracle}(M_i,x)$\\
-
-\medskip
-\oracle{$\HashOracle(i,j,x)$}\\
-Ret $h^i_j(x)$\\
-
-\medskip
-\oracle{$\CorruptOracle(i,x)$}\\
-$\mathcal{C} \gets \mathcal{C} \cup \{i\}$\\
-Ret $M_i,\mathcal{H}_i$\\
-}
-}
-%%%%%%%%%%
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpFPPubHashBB{B_1,B_2,\ldots, B_\ell}{\distr{U}{n}, A}$}\\
-$\mathcal{C} \gets \emptyset$\\
-for $i=1$ to $\ell$\\
-\nudge $S_i \getsr \distr{U}{n}$\\
-\nudge $ \{h^i_1,h^i_2,\ldots,h^i_k\} \getsr \Hash_i$\\
-\nudge $M_i \getsr \Rep_i^{\HashOracle(i,\cdot,\cdot)}(S_i)$\\
-$(i,x) \getsr A^{\QryOracle,\HashOracle,\CorruptOracle}(\{S_i\}_{i=1}^{\ell})$\\
-if $i \not\in \mathcal{C} \wedge \Qry_i^{\HashOracle(i,\cdot,\cdot)}(M_i,x)=1$ then \\
-\nudge Ret 1\\
-Ret 0
-}
-%
-{
-\oracle{$\QryOracle(i,x)$}\\
-Ret $\Qry_i^{\HashOracle}(M_i,x)$\\
-
-\medskip
-\oracle{$\HashOracle(i,j,x)$}\\
-Ret $h^i_j(x)$\\
-
-\medskip
-\oracle{$\CorruptOracle(i,x)$}\\
-$\mathcal{C} \gets \mathcal{C} \cup \{i\}$\\
-Ret $M_i$\\
-}
-}
-%%%%%%%
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpFPPubHash{B_1,B_2,\ldots,B_\ell}{\distr{U}{n}, A}$}\\
-$\mathcal{C} \gets \emptyset$\\
-for $i=1$ to $\ell$\\
-\nudge $S_i \getsr \distr{U}{n}$\\
-\nudge $ \mathcal{H}_i \gets \{h^i_1,h^i_2,\ldots,h^i_k\} \getsr \Hash_i$\\
-\nudge $M_i \getsr \Rep_i^{\HashOracle(i,\cdot,\cdot)}(S_i)$\\
-$(i,x) \getsr A^{\QryOracle,\CorruptOracle}(\{S_i\}_{i=1}^{\ell},\{\mathcal{H}_i\}_{i=1}^{\ell})$\\
-if $i \not\in \mathcal{C} \wedge \Qry_i^{\HashOracle(i,\cdot,\cdot)}(M_i,x)=1$ then \\
-\nudge Ret 1\\
-Ret 0
-}
-%
-{
-\oracle{$\QryOracle(i,x)$}\\
-Ret $\Qry_i^{\HashOracle}(M_i,x)$\\
-
-\medskip
-\oracle{$\HashOracle(i,j,x)$}\\
-Ret $h^i_j(x)$\\
-
-\medskip
-\oracle{$\CorruptOracle(i,x)$}\\
-$\mathcal{C} \gets \mathcal{C} \cup \{i\}$\\
-Ret $M_i$\\
-}
-}
-\caption{False-positive security for an $(n,k,m)$-filter~$B$ in the multiple-server setting.
-(Three variations, depending on access to/knowledge of hash functions.) \textcolor{cyan}{Not clear which of these notions really makes sense.}}
-\label{fig:fp-filter}
-\end{figure}

### 2016-07-06 filters-syntax.tex
restructuring and other updates

--- 2016-07-06 filters.tex
@@
 On the other hand, we can state a simple correctness condition for these kinds of filters; this will not be true when we further generalize to capture, properly, counters and mutability.
-
-\heading{FP-security of hash-based filters.} \tsnote{NY give it in
-the private hash setting (sort of); but, intuitively, it should be
-hard to find false-positives even if you know that MD5 or SHA-x are
-the hash functions.  Not totally sure how to capture this intuition
-nicely.} \jnote{Not sure I agree. First of all, if $\epsilon$ is not
-negligible then a random element is a false positive with noticeable
-probability. Beyond that, I think that intuitively it makes sense
-that if you want false positives to be hard to find then you need to
-make the hash functions secret.} \tsnote{I don't think it makes sense
-to talk about asymptotics or negligibility, for exactly the reason you
-state. I think the key point here is: what is ``hard''?   The designer decides what FP rate is
-acceptable for a given application, a given set of efficiency
-constraints, the side-effects of a FP, etc.  For a fixed FP target,
-she optimizes the filter size and/or the number of hash functions for
-her setting. Whether the target FP rate is 0.01 or $2^{-80}$, we should be able to say (in the ROM, at least)
-that it will take this-many hash computations, and this many on-line
-set-membership queries, to find the first FP.  In the standard model,
-with public hash functions, it is clearly more difficult to make
-formal claims.  Even so, in practice I expect it would be quite expensive to
-find a string~$x$ such that $(h_1(x),h_2(x),\ldots,h_k(x))$
-falls in a given set of tuples when $h_i(x)=\mathrm{truncate}(\mathrm{SHA256}(\langle i \rangle
-\concat x), m)$, say. (Even more so if my setting admits relatively
-expensive hash computations, e.g. SCRYPT.)  BTW, your suggestion to
-have a FP notion with secret~$\mathcal{S}$ is interesting here. }
-
-The traditional notion of soundness
-for a Bloom filter captures the difficulty of finding false
-positives when the attacker is non-adaptive. Following NY, we
-consider soundness against adaptive adversaries. But we further
-generalize to allow for settings in which the attacker may have some
-a priori knowledge about the contents of~$S$. (The Niedermaier et
-al.~\cite{xxx} attacks, for example, exploit knowledge about the
-distribution of German last names.)   In particular, our notions
-take as input an explicit distribution $\distr{U}{n}$ over~$[U]^n$.
-
-\jknote{We also want to capture the fact that finding the first
-false positive should not make it any easier to find subsequent
-false positives. This is not really captured by the Naor paper,
-either (at least not directly, though it may end up being implied by
-their definition).} \tsnote{See my comment in the intro.}
-
-In Figure~\ref{fig:fp-filter} we give three distinct notions,
-characterized by what access the adversary has to the underlying
-hash functions used by the filter.  In the top notion, the hash
-functions are secret.  This is the setting addressed by NY, and it
-captures applications in which the hash functions are (say) secretly
-keyed PRFs, and in which no explicit, external interface to these is
-surfaced.
-%
-The bottom notion considers the case that the full code of the hash functions is known to the attacker.
-This is the case, for example, when attacking the Bloom filters used in the Squid proxy~\cite{xxx}.
-%
-The middle notion is a compromise: it makes the hash functions
-public, but assumes that the adversary only accesses them in a
-black-box manner.  That is, the adversary does not exploit
-structural features of the hash functions in its attack.  This
-notion makes it easy to track the query complexity of an attack, and
-also allows us to capture constructions in the random-oracle model.
-
-For each experiment, we define an associated advantage
-notion.  Namely, given an $(n,k,m)$-filter~$B=(\Hash,\Rep,\Qry)$,
-distribution~$\distr{U}{n}$ and adversary~$A$, we define:
-\begin{align*}
-\AdvFPSecHash{B}{\distr{U}{n},A} &= \Prob{\ExpFPSecHash{B}{\distr{U}{n},A}} \\
-\AdvFPPubHashBB{B}{\distr{U}{n},A} &= \Prob{\ExpFPPubHashBB{B}{\distr{U}{n},A}} \\
-\AdvFPSecHash{B}{\distr{U}{n},A} &= \Prob{\ExpFPPubHash{B}{\distr{U}{n},A}}
-\end{align*}
-The probabilities are over the coins of the indicated experiment,
-and the coins of the adversary.   In all experiments, we track the
-time-complexity~$t$ of~$A$, as well as the number of set-membership
-($\QryOracle$ oracle) queries~$q_{\mathrm{sm}}$ that it makes.   In
-the second, we also track the number of hash-queries
-$q_{\mathrm{h}}$ that the adversary makes.
-
-We note that the distribution~$\distr{U}{n}$ must be independent of the hash functions $h_1,h_2,\ldots,h_k$ that are used to create~$M$.
-Otherwise, when (say) $\Sigma=\bits$, the distribution may only assign positive probability to sets~$S$ that cause an abnormally large number of bits in~$M$ to be set to 1.
-Our security notions enforce this independence.
-
-\jnote{How do we want to define a ``secure'' Bloom filter (even
-informally)? Do we want to say that the probability of finding a
-false positive is negligible? Or that if we set the FP rate to
-$\epsilon$ then the best an attacker can do with $q$ hash queries is
-$1-(1-\epsilon)^q$ plus negligible?} 
-\tsnote{Formally, I don't think we can (and still be rooted in
-  reality.)  Even informally it's hard, since the fact is that the
-  designer decides what is ``secure'' for her setting.  I think we
-  just say something like ``A bloom filter is
-  $(t,q_h,q_m,\epsilon)$-secure if no attacker running in time at
-  most~$t$, asking at most~$q_h$ hash queries and $q_m$ set-membership
-  queries, has probability more than~$\epsilon$ of finding a FP.''  (If
-you like, we can throw a paramter~$n$ in there, for the number of FPs
-it must find.)  Perhaps informally we say that a bloom filter is
-secure if, for ``reasonable'' $t,q_h,q_m$, the value of~$\epsilon$ is
-not ``significantly larger'' than the designer's target.  I guess
-that's not far off from one of your suggestions.}
-
-\jnote{One thing that is nice about the
-NY notion is that you get a ``clean'' definition of security: no
-matter how many FPs the attacker has found so far, the probability
-that it can output a fresh FP is still $\epsilon$.}
-
-\jnote{What parameters are needed to get negligible $\epsilon$? Are
-they reasonable in practice?} \tsnote{Again, I don't think that
-negligible is reasonable in practice :P}
-
-\begin{figure}
-\centering
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpFPSecHash{B}{\distr{U}{n},A}$}\\
-$S \getsr \distr{U}{n}$\\
-$h_1,\ldots,h_k \getsr \Hash$\\
-$\HashOracle = (h_1, \ldots, h_k)$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle}(S)$\\
-if $x \not\in S \wedge \Qry^{\HashOracle}(M,\tau,x)=1$ then\\
-\nudge Ret 1\\
-Ret 0
-}
-%
-{
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
-
-\medskip
-\oracle{$\HashOracle(i,x)$}\\
-Ret $h_i(x)$\\
-}
-}
-%%%%%%%
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpFPPubHashBB{B}{\distr{U}{n}, A}$}\\
-$S \getsr \distr{U}{n}$\\
-$h_1,\ldots,h_k \getsr \Hash$\\
-$\HashOracle = (h_1, \ldots, h_k)$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle,\HashOracle}(S)$\\
-if $x \not\in S \wedge \Qry^{\HashOracle}(M,\tau,x)=1$ then\\
-\nudge Ret 1\\
-Ret 0
-}
-%
-{
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
-
-\medskip
-\oracle{$\HashOracle(i,x)$}\\
-Ret $h_i(x)$\\
-}
-}
-%%%%%%%
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpFPPubHash{B}{\distr{U}{n}, A}$}\\
-$S \getsr \distr{U}{n}$\\
-$h_1,\ldots,h_k \getsr \Hash$\\
-$\HashOracle = (h_1, \ldots, h_k)$\\
-$(M,\tau) \gets \Rep^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle}(S,\{h_1,h_2,\ldots,h_k\})$\\
-if $x \not\in S \wedge \Qry^{\HashOracle}(M,\tau,x)=1$ then\\
-\nudge Ret 1\\
-Ret 0
-}
-%
-{
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
-
-\medskip
-\oracle{$\HashOracle(i,x)$}\\
-Ret $h_i(x)$\\
-} } \caption{False-positive security (soundness) for an
-$(n,k,m)$-filter~$B$ with private hash functions (top), black-box
-queriable hash functions (middle), and public hash functions
-(bottom). \jnote{Could also consider not giving $S$ to the
-adversary.} } \label{fig:fp-filter}
-\end{figure}
-
-%%%%
-% \if{0}
-% \begin{figure}
-% \centering
-% \fpage{.6}{
-% \hpagess{.6}{.35}
-% {
-% \experimentv{$\ExpFPSecHash{S,B}{A}$}\\
-% $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-% $M \gets \Rep^{\HashOracle}(S)$\\
-% $x \getsr A^{\QryOracle}(S)$\\
-% if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
-% \nudge Ret 1\\
-% Ret 0
-% }
-% %
-% {
-% \oracle{$\QryOracle(x)$}\\
-% Ret $\Qry^{\HashOracle}(M,x)$\\
-
-% \medskip
-% \oracle{$\HashOracle(i,x)$}\\
-% Ret $h_i(x)$\\
-% }
-% }
-% %%%%%%%
-% \fpage{.6}{
-% \hpagess{.6}{.35}
-% {
-% \experimentv{$\ExpFPPubHashBB{S,B}{A}$}\\
-% $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-% $M \gets \Rep^{\HashOracle}(S)$\\
-% $x \getsr A^{\QryOracle,\HashOracle}(S)$\\
-% if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
-% \nudge Ret 1\\
-% Ret 0
-% }
-% %
-% {
-% \oracle{$\QryOracle(x)$}\\
-% Ret $\Qry^{\HashOracle}(M,x)$\\
-
-% \medskip
-% \oracle{$\HashOracle(i,x)$}\\
-% Ret $h_i(x)$\\
-% }
-% }
-% %%%%%%%
-% \fpage{.6}{
-% \hpagess{.6}{.35}
-% {
-% \experimentv{$\ExpFPPubHash{S,B}{A}$}\\
-% $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-% $M \gets \Rep^{\HashOracle}(S)$\\
-% $x \getsr A^{\QryOracle}(S,\{h_1,h_2,\ldots,h_k\})$\\
-% if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
-% \nudge Ret 1\\
-% Ret 0
-% }
-% %
-% {
-% \oracle{$\QryOracle(x)$}\\
-% Ret $\Qry^{\HashOracle}(M,x)$\\
-
-% \medskip
-% \oracle{$\HashOracle(i,x)$}\\
-% Ret $h_i(x)$\\
-% }
-% }
-% \caption{False-positive security (soundness) for an $(n,k,m)$-filter~$B$ with private hash functions (top), black-box queriable hash functions (middle), and public hash functions (bottom). }
-% \label{fig:fp-filter}
-% \end{figure}
-%\fi
-%%%%%
-
-\heading{Privacy of hash-based filters.} We now define privacy notions for $(n,k,m)$-filters.
-Informally, the adversary's goal is to guess one of the elements of the set~$S$.
-Of course, if the distribution~$\distr{U}{n}$ has low min-entropy with respect to any particular element $x \in U$, then it will be relatively easy to guess~$x$.
-To capture this min-entropy, let $p_{\mathrm{max}} = \max_{x \in U} \Prob{S \getsr \distr{U}{n}:\, x \in S}$ and define $\mu = -\log_2 p_{\mathrm{max}}$ to be the (element-wise) min-entropy of distribution $\distr{U}{n}$.
-
-We note that~$S$ must be independent of the hash functions~$h_1,h_2,\ldots,h_k$ used to create the representation of~$S$.  \tsnote{I thought this would be needed, but now I'm not sure it is. }
-
-\begin{figure}
-\centering
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpPrivSecHash{B}{\distr{U}{n}, A}$}\\
-$S \getsr \distr{U}{n}$\\
-$h_1,\ldots,h_k \getsr \Hash$\\
-$\HashOracle = (h_1, \ldots, h_k)$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle}()$\\
-if $x\in S$ then Ret 1\\
-Ret 0
-}
-%
-{
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
-
-\medskip
-\oracle{$\HashOracle(i,x)$}\\
-Ret $h_i(x)$\\
-}
-}
-%%%%%%%%%%
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpPrivPubHashBB{B}{\distr{U}{n}, A}$}\\
-$ S \getsr \distr{U}{n}$\\
-$h_1,\ldots,h_k \getsr \Hash$\\
-$\HashOracle = (h_1, \ldots, h_k)$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle,\HashOracle}()$\\
-if $x\in S$ then Ret 1\\
-Ret 0\\
-}
-%
-{
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
-
-\medskip
-\oracle{$\HashOracle(i,x)$}\\
-Ret $h_i(x)$\\
-}
-}
-%%%%%%%
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpPrivPubHash{B}{\distr{U}{n}, A}$}\\
-$ S \getsr \distr{U}{n}$\\
-$h_1,\ldots,h_k \getsr \Hash$\\
-$\HashOracle = (h_1, \ldots, h_k)$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle}(\{h_1,h_2,\ldots,h_k\})$\\
-if $x\in S$ then Ret 1\\
-Ret 0\\
-}
-%
-{
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
-
-\medskip
-\oracle{$\HashOracle(i,x)$}\\
-Ret $h_i(x)$\\
-}
-}
-\caption{Set-privacy for an $(n,k,m)$-filter~$B$ for private (top), black-box queriable (middle),  and public (bottom) hash functions. \textcolor{cyan}{Revisit when the FP notion settles out.}}
-\label{fig:fp-filter}
-\end{figure}
-
-\heading{Security in multiple-server settings. }  \jnote{What is the
-goal here? If they don't share hash functions, I'm not sure what is
-gained by considering this definition.} \tsnote{Perhaps not the same
-hash functions, but correlated ones.  For example, server~$j$ uses
-hash functions $\tilde{h}_i(x) = h_i(\langle \mathrm{id}_j \rangle \concat x)$ for
-some $h_i$ shared among servers.  The $\mathrm{id}_j$ may or may not
-be public, e.g. in a P2P network your ID might be a nonce learned only
-when you join.  Also, the sets $\mathcal{S_j}$ stored at each server
-might be correlated.} In this section, we consider
-security notions for settings in which there may be multiple
-servers, each holding a filter representation of a set.  To allow
-for each server to embed server-specific information into its
-representation, we abstract the servers as $B_1,B_2,\ldots,B_\ell$
-where each $B_i=(\Hash_i,\Rep_i,\Qry_i)$ is an $(n,k,m)$-filter.
-\tsnote{Still some kinks to be ironed out though.  The current
-notions sample fresh hash functions for each server.  But in (say)
-the Squid setting, the same hash functions are used across all Squid
-instances... maybe it suffices, for that setting, to say that the
-$\Hash_i$ are all the same, and each simply returns a fixed set
-of~$k$ hash functions (i.e., deterministic).} To model insider
-attacks, we give the adversary the ability to corrupt (adaptively)
-instances of the filter.  Such attacks capture P2P settings, in
-which the adversary may join the network as a peer.
-
-\begin{figure}
-\centering
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpFPSecHash{B_1,B_2,\ldots,B_\ell}{\distr{U}{n}, A}$}\\
-$\mathcal{C} \gets \emptyset$\\
-for $i=1$ to $\ell$\\
-\nudge $S_i \getsr \distr{U}{n}$\\
-\nudge $ \mathcal{H}_i \gets \{h^i_1,h^i_2,\ldots,h^i_k\} \getsr \Hash_i$\\
-\nudge $M_i \getsr \Rep_i^{\HashOracle(i,\cdot,\cdot)}(S_i)$\\
-$(i,x) \getsr A^{\QryOracle,\CorruptOracle}(\{S_i\}_{i=1}^{\ell})$\\
-if $i \not\in \mathcal{C} \wedge \Qry_i^{\HashOracle(i,\cdot,\cdot)}(M_i,x)=1$ then \\
-\nudge Ret 1\\
-Ret 0
-}
-%
-{
-\oracle{$\QryOracle(i,x)$}\\
-Ret $\Qry_i^{\HashOracle}(M_i,x)$\\
-
-\medskip
-\oracle{$\HashOracle(i,j,x)$}\\
-Ret $h^i_j(x)$\\
-
-\medskip
-\oracle{$\CorruptOracle(i,x)$}\\
-$\mathcal{C} \gets \mathcal{C} \cup \{i\}$\\
-Ret $M_i,\mathcal{H}_i$\\
-}
-}
-%%%%%%%%%%
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpFPPubHashBB{B_1,B_2,\ldots, B_\ell}{\distr{U}{n}, A}$}\\
-$\mathcal{C} \gets \emptyset$\\
-for $i=1$ to $\ell$\\
-\nudge $S_i \getsr \distr{U}{n}$\\
-\nudge $ \{h^i_1,h^i_2,\ldots,h^i_k\} \getsr \Hash_i$\\
-\nudge $M_i \getsr \Rep_i^{\HashOracle(i,\cdot,\cdot)}(S_i)$\\
-$(i,x) \getsr A^{\QryOracle,\HashOracle,\CorruptOracle}(\{S_i\}_{i=1}^{\ell})$\\
-if $i \not\in \mathcal{C} \wedge \Qry_i^{\HashOracle(i,\cdot,\cdot)}(M_i,x)=1$ then \\
-\nudge Ret 1\\
-Ret 0
-}
-%
-{
-\oracle{$\QryOracle(i,x)$}\\
-Ret $\Qry_i^{\HashOracle}(M_i,x)$\\
-
-\medskip
-\oracle{$\HashOracle(i,j,x)$}\\
-Ret $h^i_j(x)$\\
-
-\medskip
-\oracle{$\CorruptOracle(i,x)$}\\
-$\mathcal{C} \gets \mathcal{C} \cup \{i\}$\\
-Ret $M_i$\\
-}
-}
-%%%%%%%
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpFPPubHash{B_1,B_2,\ldots,B_\ell}{\distr{U}{n}, A}$}\\
-$\mathcal{C} \gets \emptyset$\\
-for $i=1$ to $\ell$\\
-\nudge $S_i \getsr \distr{U}{n}$\\
-\nudge $ \mathcal{H}_i \gets \{h^i_1,h^i_2,\ldots,h^i_k\} \getsr \Hash_i$\\
-\nudge $M_i \getsr \Rep_i^{\HashOracle(i,\cdot,\cdot)}(S_i)$\\
-$(i,x) \getsr A^{\QryOracle,\CorruptOracle}(\{S_i\}_{i=1}^{\ell},\{\mathcal{H}_i\}_{i=1}^{\ell})$\\
-if $i \not\in \mathcal{C} \wedge \Qry_i^{\HashOracle(i,\cdot,\cdot)}(M_i,x)=1$ then \\
-\nudge Ret 1\\
-Ret 0
-}
-%
-{
-\oracle{$\QryOracle(i,x)$}\\
-Ret $\Qry_i^{\HashOracle}(M_i,x)$\\
-
-\medskip
-\oracle{$\HashOracle(i,j,x)$}\\
-Ret $h^i_j(x)$\\
-
-\medskip
-\oracle{$\CorruptOracle(i,x)$}\\
-$\mathcal{C} \gets \mathcal{C} \cup \{i\}$\\
-Ret $M_i$\\
-}
-}
-\caption{False-positive security for an $(n,k,m)$-filter~$B$ in the multiple-server setting.
-(Three variations, depending on access to/knowledge of hash functions.) \textcolor{cyan}{Not clear which of these notions really makes sense.}}
-\label{fig:fp-filter}
-\end{figure}

### 2016-07-06 mutable-filters.tex
restructuring and other updates

@@
-\section{Mutuable hash-based filters}
+\section{Mutuable Hash-Based Filters}
 Here we extend the basic Bloom filter syntax to allow for variations on the traditional Bloom filter, e.g.
@@
 %
-The randomized \emph{initial-representation} algorithm $\Init\colon \multiset{U}{n} \rightarrow \left(\bigcup_{m=m_1}^{m_2}\Sigma^m\right)$ takes a multiset~$S$ of size~$n$ as input, and outputs representation~$M$ of length~$m_1 \leq m \leq m_2$.
+The randomized \emph{initial-representation} algorithm $\Init\colon \multiset{U}{n} \rightarrow \left(\bigcup_{m=m_1}^{m_2}\Sigma^m\right) \times \bits^*$ takes a multiset~$S$ of size~$n$ as input, and outputs representation~$M$ of length~$m_1 \leq m \leq m_2$, and side-information~$\tau$.
 %
-The determinisitc query algorithm $\Qry\colon \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right)\times U \rightarrow \bits^*$ takes a representation $M$ and an element $x \in U$ and returns a bitstring.  
+The determinisitc query algorithm $\Qry\colon \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right)\times \bits^* \times U \rightarrow \bits^*$ takes a representation $M$, side-information~$\tau$, and an element $x \in U$ as input, and returns a bitstring.
 %
-The randomized \emph{update} algorithm $\Update\colon \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right)\times \bits^* \rightarrow \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right) \cup \{\bot\}$ takes a representation and an update string, and returns an updated representation or the distinguished symbol~$\bot$.
+The randomized \emph{update} algorithm $\Update\colon \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right)\times \bits^* \times \bits^*\rightarrow \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right) \cup \{\bot\}$ takes a representation~$M$, side-information~$\tau$, and an update string~$\sigma$ as input, and returns an updated representation or the distinguished symbol~$\bot$.
 %
-The deterministic \emph{test} algorithm $\Test \colon \multiset{U}{} \times \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right)\cup\{\bot\} \times U \rightarrow \bits$ takes a multiset~$S$, a representation~$M$ and an element~$x \in U$ and returns a bit.
+The deterministic \emph{test} algorithm $\Test \colon \multiset{U}{} \times \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right)\cup\{\bot\} \times \bits^* \times U \rightarrow \bits$ takes a multiset~$S$, a representation~$M$, side-information~$\tau$, and an element~$x \in U$ as input, and returns a bit.
 \tsnote{The point of $\Test$ is to capture correctness, which is not guaranteed in this setting.
@@
 $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-$M \getsr \Init^{\HashOracle}(S)$\\
+$(M,\tau) \getsr \Init^{\HashOracle}(S)$\\
 $x \getsr A^{\QryOracle,\UpdateOracle}(S)$\\
-if $\Test^{\HashOracle}(S,M,x) \neq 1$ then\\
+if $\Test^{\HashOracle}(S,M,\tau,x) \neq 1$ then\\
 \nudge Ret 1\\
@@
 if $M = \bot$ then Ret $\bot$\\
-Ret $\Qry^{\HashOracle}(M,x)$\\
+Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
 
@@
 $S \gets S \uplus \{\mathrm{val}\}$\\
-$M \getsr \Update^{\HashOracle}(M,\sigma)$\\
+$M \getsr \Update^{\HashOracle}(M,\tau,\sigma)$\\
 
@@
 $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-$M \getsr \Init^{\HashOracle}(S)$\\
+$(M,\tau) \getsr \Init^{\HashOracle}(S)$\\
 $x \getsr A^{\QryOracle,\UpdateOracle,\HashOracle}(S)$\\
-if $\Test^{\HashOracle}(S,M,x) \neq 1$ then Ret 1\\
+if $\Test^{\HashOracle}(S,M,\tau,x) \neq 1$ then Ret 1\\
 Ret 0
@@
 $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-$M \getsr \Init^{\HashOracle}(S)$\\
+$(M,\tau) \getsr \Init^{\HashOracle}(S)$\\
 $x \getsr A^{\QryOracle,\UpdateOracle}(S,\{h_1,h_2,\ldots,h_k\})$\\
-if $\Test^{\HashOracle}(S,M,x) \neq 1$ then Ret 1\\
+if $\Test^{\HashOracle}(S,M,\tau,x) \neq 1$ then Ret 1\\
 Ret 0
@@
 $S \gets S \uplus \{\\mathrm{val}\}$\\
-$M \getsr \Update^{\HashOracle}(M,\sigma)$\\
+$M \getsr \Update^{\HashOracle}(M,\tau,\sigma)$\\
 

### 2016-07-06 filters-notions.tex
removing bogus, mystery line from security experiments
restructuring and adding some tasks

@@
 
-The traditional notion of soundness
-for a Bloom filter captures the difficulty of finding false
-positives when the attacker is non-adaptive. Following NY, we
-consider soundness against adaptive adversaries. But we further
-generalize to allow for settings in which the attacker may have some
-a priori knowledge about the contents of~$S$. (The Niedermaier et
-al.~\cite{xxx} attacks, for example, exploit knowledge about the
-distribution of German last names.)   In particular, our notions
-take as input an explicit distribution $\distr{U}{n}$ over~$[U]^n$.
+The traditional notion of soundness for a Bloom filter captures the difficulty of finding false positives when the attacker is non-adaptive.
+Following NY, we consider soundness against adaptive adversaries.
+But we further generalize to allow for settings in which the attacker may have some a priori knowledge about the contents of~$S$.
+(The Niedermaier et al.~\cite{xxx} attacks, for example, exploit knowledge about the distribution of German last names.) In particular, our notions take as input an explicit distribution $\distr{U}{n}$ over~$[U]^n$.
 
@@
 
-In Figure~\ref{fig:fp-filter} we give three distinct notions,
-characterized by what access the adversary has to the underlying
-hash functions used by the filter.  In the top notion, the hash
-functions are secret.  This is the setting addressed by NY, and it
-captures applications in which the hash functions are (say) secretly
-keyed PRFs, and in which no explicit, external interface to these is
-surfaced.
+In Figure~\ref{fig:fp-filter} we give three distinct notions, characterized by what access the adversary has to the underlying hash functions used by the filter.
+In the top notion, the hash functions are secret.
+This is the setting addressed by NY, and it captures applications in which the hash functions are (say) secretly keyed PRFs, and in which no explicit, external interface to these is surfaced.
 %
@@
 %
-The middle notion is a compromise: it makes the hash functions
-public, but assumes that the adversary only accesses them in a
-black-box manner.  That is, the adversary does not exploit
-structural features of the hash functions in its attack.  This
-notion makes it easy to track the query complexity of an attack, and
-also allows us to capture constructions in the random-oracle model.
-\tsnote{I'm not sure this is really useful for anything other than ROM analysis.
-Perhaps for settings in which the hash-functions are secret, but the attack surface expose a way for the adversary to see their outputs?}
+The middle notion is a compromise: it makes the hash functions public, but assumes that the adversary only accesses them in a black-box manner.
+That is, the adversary does not exploit structural features of the hash functions in its attack.
+This notion makes it easy to track the query complexity of an attack, and also allows us to capture constructions in the random-oracle model.
+\tsnote{This is the setting for the Neidermayer et al.\  attacks.
+It's also the setting for ROM attacks.}
 
@@
 $h_1,\ldots,h_k \getsr \Hash$\\
-$\HashOracle = (h_1, \ldots, h_k)$\\
 $(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
@@
 $h_1,\ldots,h_k \getsr \Hash$\\
-$\HashOracle = (h_1, \ldots, h_k)$\\
 $(M,\tau) \gets \Rep^{\HashOracle}(S)$\\

### 2016-07-06 filters-results.tex
restructuring and adding some tasks

@@
 \tsnote{Under our current notions, you can never hope to prove privacy bounds that beat the min-entropy of $\distr{U}{n}$.}
-\tsnote{We should prove privacy for the bigram/PRF-based double-hashing construction that Neidermayer et al.\ attacks.
+\begin{itemize}
+\item Prove privacy for the bigram/PRF-based double-hashing construction that Neidermayer et al.\ attacks.
 I'm pretty sure the attack is in the public-BB setting, and the provable security bound is considerably worse than the min-entropy because of the way the representation is made.
-(Essentially, the Hamming weight of the representation is a good estimate of the length of the longest surname in filter.)  Note that their attack would allow one to recover \emph{every} name, not just one.}
-\tsnote{Prove that the basic BF, in the ROM, is private.
+(Essentially, the Hamming weight of the representation is a good estimate of the length of the longest surname in filter.)  Note that their attack would allow one to recover \emph{every} name, not just one.
+
+\item Prove that the basic BF, in the ROM, is private.
 This also shows that the basic BF with $h_j(x)=F_K(\langle j,x \rangle)$ is private.
-I believe this also shows that the bigram approach examined by Neidermayer et al.\ is secure when the hash functions are the $h_j(x)$ just described.
+\tsnote{I believe this also shows that the bigram approach examined by Neidermayer et al.\ is secure when the hash functions are the $h_j(x)$ just described.
 }
-\tsnote{Prove privacy of other suggestions, such as the record-level BF from Durham et al.?}
+
+\item Prove privacy of other suggestions, such as the record-level BF from Durham et al.?  This would be a nice pairing with the Neidermayer et al.\ results
+
+\item Attack privacy of Dong, Chen, Wen construction in the BB-hash setting \tsnote{I give the attack in the related work section.
+Copy it here and flesh it out.}  Prove privacy of construction in secret-hash setting
+
+\item \tsnote{...}
+\end{itemize}

### 2016-07-06 filters-results.tex
cheers

@@
 \begin{itemize}
-\item Prove privacy for the bigram/PRF-based double-hashing construction that Neidermayer et al.\ attacks.
-I'm pretty sure the attack is in the public-BB setting, and the provable security bound is considerably worse than the min-entropy because of the way the representation is made.
-(Essentially, the Hamming weight of the representation is a good estimate of the length of the longest surname in filter.)  Note that their attack would allow one to recover \emph{every} name, not just one.
+\item Prove that the basic BF, in the ROM, is private.  \tsnote{Not at all surprising, but it is the first result one would want in this area.}
 
-\item Prove that the basic BF, in the ROM, is private.
-This also shows that the basic BF with $h_j(x)=F_K(\langle j,x \rangle)$ is private.
-\tsnote{I believe this also shows that the bigram approach examined by Neidermayer et al.\ is secure when the hash functions are the $h_j(x)$ just described.
+\item As a simple corrolary, show that the basic BF with $h_j(x)=F_K(\langle j,x \rangle)$ is private.
+\tsnote{I believe this also shows that the bigram/PRF approach examined by Neidermayer et al.\ is secure when the hash functions are the $h_j(x)$ just described.
 }
 
-\item Prove privacy of other suggestions, such as the record-level BF from Durham et al.?  This would be a nice pairing with the Neidermayer et al.\ results
+\item Cast Neidermayer et al.\ attacks on the bigram/PRF-based double-hashing construction (see their paper) into our formalism.
+\tsnote{Note that their attack would allow one to recover \emph{every} name, not just one.} \tsnote{Note that Neidermayer et al.\ suggest ditching the double-hashing construction in favor of independent PRFs, so the previous item basically explores their suggestion.}
 
-\item Attack privacy of Dong, Chen, Wen construction in the BB-hash setting \tsnote{I give the attack in the related work section.
-Copy it here and flesh it out.}  Prove privacy of construction in secret-hash setting
+\item Prove a privacy bound for the bigram/PRF-based double-hashing construction that Neidermayer et al.\ attacks.
+I'm pretty sure the attack is in the public-BB setting, and the provable security bound is considerably worse than the min-entropy because of the way the representation is made.
+(Essentially, the Hamming weight of the representation is a good estimate of the length of the longest surname in filter.)
+
+\item Attack privacy of Dong, Chen, Wen ``garbled Bloom Filter'' construction in the BB-hash setting \tsnote{I give the attack in the related work section.
+Copy it here and flesh it out.}  Prove privacy of construction in secret-hash setting.
+\tsnote{Makes the point that the application setting really matters.}
+
+\item Prove privacy bounds of other suggestions, such as the record-level BF from Durham et al.?  This would be a nice pairing with the Neidermayer et al.\ results
+
+\item Show implications and/or separations between FP and privacy notions.
 

### 2016-07-06 intro.tex
cheers

@@
 \item S\"{a}rell\"{a} et al., ``BloomCasting: Security in Bloom Filter Based Multicast''.
-\item Dong, Chen, Wen, ``When Private Set Intersection Meets Big Data: An Efficient and Scaleable Protocol'' \tsnote{``garbled bloom filters'', which actually store the set element by storing~$k$ xor-shares, one at each of the~$k$ hash indices (with care for reusing shares if hash collisions occur), and``oblivious bloom intersection''}\tsnote{If the filter and the hash functions are public, there is a naive attack that works for some interesting parameters.
+\item Dong, Chen, Wen, ``When Private Set Intersection Meets Big Data: An Efficient and Scaleable Protocol'' \tsnote{``garbled bloom filters'', which actually store the set element by storing~$k$ xor-shares, one at each of the~$k$ hash indices (with care for reusing shares if hash collisions occur); also and``oblivious bloom intersection''}\tsnote{If the filter and the hash functions are public, there is a naive attack that works for some interesting parameters.
 Pick~$k$ positions $i_1,i_2,\ldots,i_k$, xor strings at these positions to get a candidate~$x$.

### 2016-07-08 filters-notions.tex
no message

@@
 
+\jnote{Do our definitions imply the Naor definition? If so, then why do they use a PRP
+in their construction?}
+
 We note that the distribution~$\distr{U}{n}$ must be independent of the hash functions $h_1,h_2,\ldots,h_k$ that are used to create~$M$.
@@
 \tsnote{Formally, I don't think we can (and still be rooted in
-  reality.)  Even informally it's hard, since the fact is that the
+  reality).  Even informally it's hard, since the fact is that the
   designer decides what is ``secure'' for her setting.  I think we
@@
 that it can output a fresh FP is still $\epsilon$.}
-
-\jnote{What parameters are needed to get negligible $\epsilon$? Are
-they reasonable in practice?} \tsnote{Again, I don't think that
-negligible is reasonable in practice :P}
 

### 2016-07-08 intro.tex
no message

@@
 ``Adversarial-resilient Bloom Filter with a steady representation''.
-First, $M \getsr \mathbf{B}_1(\mathcal{S})$. \jnote{Where does the
-set come from? Is it random? Adversarially chosen?}
-\tsnote{In their formalism, it is implicitly an input to the security experiment.
-Security is universally quantified over sets~$\mathcal{S}$.  This
-would seem to be equivalent to letting the adversary
-pick~$\mathcal{S}$ (prior to the hash functions being picked), with
-the time to compute and write out~$\mathcal{S}$ folded into the
-adversary's running time. } 
-Then the
-adversary is given the set~$\mathcal{S}$ and may make queries
-$x_1,x_2,\ldots,x_q$ to an oracle for $\mathbf{B}_2(M,\cdot)$.  At
-the end of its execution, the adversary outputs~$x^*$ and wins the
-game if (1) $x^* \not\in \mathcal{S} \cup \{x_1,x_2,\ldots,x_q\}$,
-and (2) $\mathbf{B}_2(M,x^*)=1$.
+First, $M \getsr \mathbf{B}_1(\mathcal{S})$ for some set
+$\mathcal{S}$ that can be adversarially chosen. Then the adversary
+may make queries $x_1,x_2,\ldots,x_q$ to an oracle for
+$\mathbf{B}_2(M,\cdot)$.  At the end of its execution, the adversary
+outputs~$x^*$ and wins the game if (1) $x^* \not\in \mathcal{S} \cup
+\{x_1,x_2,\ldots,x_q\}$, and (2) $\mathbf{B}_2(M,x^*)=1$.
 
@@
 Second, we note that the NY syntax does not capture the size of~$M$
-as a parameter; 
-\jnote{I think this is also reasonable; typically
-security is defined without regard for efficiency}
-\tsnote{My complaint isn't about efficiency. It's about the fact that,
-by not including $|M|$ in the definition, the trivial scheme I give
-(just below) is allowed, and is secure.  Anyway, as I say at the end
-of this paragraph, this is a small(er) complaint than what follows}. The surrounding
-text does say that $\mathbf{B}_1$ ``outputs a compressed
+as a parameter; \jnote{I think this is also reasonable; typically
+security is defined without regard for efficiency} \tsnote{My
+complaint isn't about efficiency. It's about the fact that, by not
+including $|M|$ in the definition, the trivial scheme I give (just
+below) is allowed, and is secure.  Anyway, as I say at the end of
+this paragraph, this is a small(er) complaint than what follows}.
+\jnote{I would say that the trivial scheme \emph{is} secure!} The
+surrounding text does say that $\mathbf{B}_1$ ``outputs a compressed
 representation [of $\mathcal{S}$] $\mathbf{B}_1(\mathcal{S})=M$''
@@
 \item Naor and Yogev
-\item Eujin Goh, ``Secure Indexes'' \tsnote{A secure index can be used for set membership.
-Builds a secret-key data structure (an Index) that allows searching for keyword~$w$ if one holds the trapdoor $T_w$ for~$w$, where the trapdoor depends on the secret key.
-Main construction uses traditional Bloom filters and a PRF.
-Construction appears quite inefficient, needing a very long secret key, turning a keyword~$w$ into a bunch of PRF outputs, and then storing each of these PRF outputs in the BF.
-Havent read the full analysis; don't know if this was ever published.
-}
+\item Eujin Goh, ``Secure Indexes'' \tsnote{A secure index can
+    be used for set membership.  Builds a secret-key data
+    structure (an Index) that allows searching for keyword~$w$
+    if one holds the trapdoor $T_w$ for~$w$, where the trapdoor
+    depends on the secret key.  Main construction uses
+    traditional Bloom filters and a PRF.  Construction appears
+    quite inefficient, needing a very long secret key, turning a
+    keyword~$w$ into a bunch of PRF outputs, and then storing
+    each of these PRF outputs in the BF.  Havent read the full
+    analysis; don't know if this was ever published. }
+    \jnote{Never published. I think this work uses Bloom filters
+    for encrypted search; I don't remember the paper having much
+    to say about Bloom filters themselves.}
 \end{itemize}
@@
 \begin{itemize}
-\item Bellovin and Cheswick, ``Privacy-Enhanced Searches Using Encrypted Bloom Filters''.
+\item Bellovin and Cheswick, ``Privacy-Enhanced Searches Using
+    Encrypted Bloom Filters''.
 \item Kerschbaum , ``Public-Key Encrypted Bloom Filters with Applications to Supply Chain Integrity''.

### 2016-07-08 intro.tex
no message

@@
 that apply to arbitrary data structures (constructed in arbitrary
-ways) and then only later specialized to hash-based Bloom filters.}
+ways) and then only later specialized to hash-based Bloom filters.
+(Put this in an appendix for now, until we see how things play
+out.)}
 

### 2016-07-08 intro.tex
intro clean up

@@
 \section{Introduction}
-We revisit the formalization of Bloom filters~\cite{xxx} and closely
-related data structures as primitives with explicit security goals.
-Recently, Naor and Yogev~\cite{xxx} (hereafter NY) gave such a
-formalization, providing syntax for a generalized abstraction of
-Bloom filters, as well as casting the classical Bloom filter
-soundness condition as a security experiment admiting adaptive
-adversaries.  To briefly summarize, a Bloom filter is a data
-structure for compactly representing a set~$\mathcal{S}$ in a way
-that supports constant-time responses to set-membership queries. The
-representation of~$\mathcal{S}$ is an bit-array~$M$ of length~$m$,
-all initially set to~0.  To insert $x \in \mathcal{S}$ into~$M$, one
-computes indices $h_1(x),h_2(x),\ldots,h_k(x)$ where each $h_i
-\colon \mathcal{U} \to \{0,1,\ldots m-1\}$ maps from a
-universe~$\mathcal{U}$ (which contains $\mathcal{S}$) to indices
-of~$M$.  The bits at positions $h_1(x),h_2(x),\ldots,h_k(x)$ are set
-to 1; if a bit is already 1, due to inserting some previous element
-of~$\mathcal{S}$, then it is left alone.  After all elements
-of~$\mathcal{S}$ have been inserted, the resulting bit-array~$M$ is
-taken as the representation.  To test if $y \in \mathcal{S}$, one
-checks if \[(M[h_1(y)]=1 \wedge M[h_2(y)]=1 \wedge \cdots \wedge
-M[h_k(y)]=1),\] returning ``yes'' if so, and ``no'' otherwise. Bloom
-filters are correct, in the sense that if $y \in \mathcal{S}$, the
-set-membership test always returns ``yes''.  The classical soundness
-condition asserts that for all $\mathcal{S}$ and any $y
-\notin\mathcal{S}$, we have $\Prob{h_1,h_2,\ldots,h_k \getsr
-\mathrm{Func}(\mathcal{U},[m])\colon M[h_1(y)]=1 \wedge \cdots
-\wedge M[h_k(y)]=1} \leq \epsilon$ where $\epsilon$, the
-false-positive rate, is a parameter of the Bloom filter.  (The
-values of~$\epsilon,m,k$, and $|\mathcal{S}|$ are related in a
-well-known way.) NY recast this soundness condition as a game in
-which an adversary~$A$ is given~$\mathcal{S}$ and an oracle for
-set-membership queries, and it attempts to find a false positive.
-The fact that~$A$ can \emph{adapt} its queries and its output based
-on what it learns from the set-membership oracle (but, as we will see,
-not upon the hash functions) is the key definitional contribution of~NY.
+We revisit the formalization of Bloom filters~\cite{xxx} and closely related data structures as primitives with explicit security goals.
+Recently, Naor and Yogev~\cite{xxx} (hereafter NY) gave such a formalization, providing syntax for a generalized abstraction of Bloom filters, as well as casting the classical Bloom filter soundness condition as a security experiment admiting adaptive adversaries.
+To briefly summarize, a Bloom filter is a data structure for compactly representing a set~$\mathcal{S}$ in a way that supports constant-time responses to set-membership queries.
+The representation of~$\mathcal{S}$ is an bit-array~$M$ of length~$m$, all initially set to~0.
+To insert $x \in \mathcal{S}$ into~$M$, one computes indices $h_1(x),h_2(x),\ldots,h_k(x)$ where each $h_i \colon \mathcal{U} \to \{0,1,\ldots m-1\}$ maps from a universe~$\mathcal{U}$ (which contains $\mathcal{S}$) to indices of~$M$.
+The bits at positions $h_1(x),h_2(x),\ldots,h_k(x)$ are set to 1; if a bit is already 1, due to inserting some previous element of~$\mathcal{S}$, then it is left alone.
+After all elements of~$\mathcal{S}$ have been inserted, the resulting bit-array~$M$ is taken as the representation.
+To test if $y \in \mathcal{S}$, one checks if \[(M[h_1(y)]=1 \wedge M[h_2(y)]=1 \wedge \cdots \wedge M[h_k(y)]=1),\] returning ``yes'' if so, and ``no'' otherwise.
+Bloom filters are correct, in the sense that if $y \in \mathcal{S}$, the set-membership test always returns ``yes''.
+The classical soundness condition asserts that for all $\mathcal{S}$ and any $y \notin\mathcal{S}$, we have $\Prob{h_1,h_2,\ldots,h_k \getsr \mathrm{Func}(\mathcal{U},[m])\colon M[h_1(y)]=1 \wedge \cdots \wedge M[h_k(y)]=1} \leq \epsilon$ where $\epsilon$, the false-positive rate, is a parameter of the Bloom filter.
+(The values of~$\epsilon,m,k$, and $|\mathcal{S}|$ are related in a well-known way.) NY recast this soundness condition as a game in which an adversary~$A$ is given~$\mathcal{S}$ and an oracle for set-membership queries, and it attempts to find a false positive.
+The fact that~$A$ can \emph{adapt} its queries and its output based on what it learns from the set-membership oracle (but, as we will see, not upon the hash functions) is the key definitional contribution of~NY.
 
-Bloom filters have a broad range of practical applications, for
-example, in content-distribution networks, large database query
-processing, routing algorithms for peer-to-peer networks, protocols
-for establishing linkages between medical-record databases, fair
-routing of TCP packets, Bitcoin wallet synchonization. \tsnote{need
-citations}  Given that NY is addressing such a useful real-world
-object, we find their formalism, both the syntax and security
-notions, to be less precise and useful than one would want.  Let us
-explain.
+Bloom filters have a broad range of practical applications, for example, in content-distribution networks, large database query processing, routing algorithms for peer-to-peer networks, protocols for establishing linkages between medical-record databases, fair routing of TCP packets, Bitcoin wallet synchonization.
+\tsnote{need citations} Given that NY is addressing such a useful real-world object, we find their formalism, both the syntax and security notions, to be less precise and useful than one would want.
+Let us explain.
 
-Syntactically, NY says a Bloom filter (with a steady representation)
-is a pair of algorithms $\mathbf{B}=(\mathbf{B}_1, \mathbf{B}_2)$.
-The setup algorithm~$\mathbf{B}_1$ is randomized, and on input a
-set~$\mathcal{S}$ it returns a representation~$M$ (from some
-undefined, implicit set of representations).  The query
-algorithm~$\mathcal{B}_2$ is deterministic, and on input a
-representation~$M$ and an element~$x \in \mathcal{U}$, it returns a
-bit.  For correctness they make the classical demand, that for all
-$x \in \mathcal{S}$ we have
-$\Prob{\mathbf{B}_2(\mathbf{B}_1(\mathcal{S}),x)=1}=1$.  For
-soundness, adversary~$A$ plays the following game,
-``Adversarial-resilient Bloom Filter with a steady representation''.
-First, $M \getsr \mathbf{B}_1(\mathcal{S})$ for some set
-$\mathcal{S}$ that can be adversarially chosen. Then the adversary
-may make queries $x_1,x_2,\ldots,x_q$ to an oracle for
-$\mathbf{B}_2(M,\cdot)$.  At the end of its execution, the adversary
-outputs~$x^*$ and wins the game if (1) $x^* \not\in \mathcal{S} \cup
-\{x_1,x_2,\ldots,x_q\}$, and (2) $\mathbf{B}_2(M,x^*)=1$.
+Syntactically, NY says a Bloom filter (with a steady representation) is a pair of algorithms $\mathbf{B}=(\mathbf{B}_1, \mathbf{B}_2)$.
+The setup algorithm~$\mathbf{B}_1$ is randomized, and on input a set~$\mathcal{S}$ it returns a representation~$M$ (from some undefined, implicit set of representations).
+The query algorithm~$\mathcal{B}_2$ is deterministic, and on input a representation~$M$ and an element~$x \in \mathcal{U}$, it returns a bit.
+For correctness they make the classical demand, that for all $x \in \mathcal{S}$ we have $\Prob{\mathbf{B}_2(\mathbf{B}_1(\mathcal{S}),x)=1}=1$.
+For soundness, adversary~$A$ plays the following game, ``Adversarial-resilient Bloom Filter with a steady representation''.
+First, $M \getsr \mathbf{B}_1(\mathcal{S})$ for some set $\mathcal{S}$ that can be adversarially chosen.
+Then the adversary may make queries $x_1,x_2,\ldots,x_q$ to an oracle for $\mathbf{B}_2(M,\cdot)$.
+At the end of its execution, the adversary outputs~$x^*$ and wins the game if (1) $x^* \not\in \mathcal{S} \cup \{x_1,x_2,\ldots,x_q\}$, and (2) $\mathbf{B}_2(M,x^*)=1$.
 
-First, we note that the security notion forbids~$A$ to win if it
-outputs $x^* \in \{x_1,x_2,\ldots,x_q\}$, even if one of these was a
-false positive.
-\jnote{We discussed this on the phone, but let me
-put it in writing here. I think this is actually a reasonable choice
-because it captures the notion that ``even after finding some false
-positives, it remains hard to find additional false positives.''
-Note that in practice finding false positives is ``easy'' since
-$\epsilon$ might be $1/1000$ rather than negligible.}
-\tsnote{For me the question is: is security violated once the first FP is found, or
-the second?  My answer, which is in line with the traditional
-soundness notion, is that the first FP is a security violation
-even if finding it isn't ``hard'' by cryptographic standards.
-But I do appreciate your point.  A natural goal is to say that, in some sense,
-\emph{adaptivity doesn't make it any easier} to find a FP.  Adapting
-to what, though?  In the traditional notion, $x$~is picked before the
-coins of~$\mathbf{B}_1$ are flipped, i.e., before the hash functions
-are sampled.  The direct non-adaptive generalization is to say that
-$x_1,x_2,\ldots,x_q$ are all picked up front.  The direct
-\emph{adaptive} generalization would allow $x_1,x_2,\ldots,x_q$ to
-depend in the coins of~$\mathbf{B}_1$, i.e., the hash functions.  The
-NY definition captures only indirect dependence: adversaries that can adapt to set-membership queries,
-but \emph{not} (directly) to the input-output behaviors of the hash
-functions.  The three notions I've proposed in Figure 1 cover a
-spectrum of adaptivity: the first is adapting to set-membership queries
-only, the second to those and hash input-output behavior, the third to
-set-membership queries and full knowledge of the hash functions.  Each
-has it's own associated (informal) security interpretation.}
+First, we note that the security notion forbids~$A$ to win if it outputs $x^* \in \{x_1,x_2,\ldots,x_q\}$, even if one of these was a false positive.
+On one hand, this notion is unsatisfying because it would not say that an attacker wins by creating (say) a bogus email address, and then observing that it passes a spam filter that is based on a Bloom filter represention of a whitelist.\footnote{This is one of the motivating examples from NY.}  The attacker is only allowed to win if it finds a false-positive that it has not verified.
+On the other hand, the NY notion does seem to capture the intuition that finding additional false positives does not become easier as more are learned.
+Our notions will address both sides of this discussion.
+%
+%\jnote{We discussed this on the phone, but let me put it in writing here.
+I think this is actually a reasonable choice because it captures the notion that ``even after finding some false positives, it remains hard to find additional false positives.'' Note that in practice finding false positives is ``easy'' since $\epsilon$ might be $1/1000$ rather than negligible.}
+%
+%\tsnote{For me the question is: is security violated once the first FP is found, or the second?
+My answer, which is in line with the traditional soundness notion, is that the first FP is a security violation even if finding it isn't ``hard'' by cryptographic standards.
+But I do appreciate your point.
+A natural goal is to say that, in some sense, \emph{adaptivity doesn't make it any easier} to find a FP.
+Adapting to what, though?
+In the traditional notion, $x$~is picked before the coins of~$\mathbf{B}_1$ are flipped, i.e., before the hash functions are sampled.
+The direct non-adaptive generalization is to say that $x_1,x_2,\ldots,x_q$ are all picked up front.
+The direct \emph{adaptive} generalization would allow $x_1,x_2,\ldots,x_q$ to depend in the coins of~$\mathbf{B}_1$, i.e., the hash functions.
+The NY definition captures only indirect dependence: adversaries that can adapt to set-membership queries, but \emph{not} (directly) to the input-output behaviors of the hash functions.
+The three notions I've proposed in Figure 1 cover a spectrum of adaptivity: the first is adapting to set-membership queries only, the second to those and hash input-output behavior, the third to set-membership queries and full knowledge of the hash functions.
+Each has it's own associated (informal) security interpretation.}
+%\tsnote{Perhaps a more obvious way to capture the idea that ``finding some FPs doesn't help find additional ones'' is to parameterize my notion(s) with a number~$f$, and say that that the adversary wins iff it outputs~$f$ FPs (these may have been previously queried to the set-membership oracle).
+Note that in the ROM (and probably in practice) finding~$f>1$ FPs will require~$f$ times the work.
+Right?}
+%
+%\tsnote{FYI: this is how MAC security against multiple forgeries is defined.  See \texttt{https://eprint.iacr.org/2006/095.pdf} for details.}
 
-\tsnote{Perhaps a more obvious way to capture the idea that ``finding
-  some FPs doesn't help find additional ones'' is to parameterize my notion(s) with a number~$f$, and say
-that that the adversary wins iff it outputs~$f$ FPs (these may have
-been previously queried to the set-membership oracle).
-Note that in the ROM (and probably in practice) finding~$f>1$ FPs will
-require~$f$ times the work.  Right?} \tsnote{FYI: this is how MAC security against multiple forgeries is defined.  See \texttt{https://eprint.iacr.org/2006/095.pdf} for details.}
-%\tsnote{Here's an off-the-wall idea.  What if the basic FP security
-%notion gave the adversary an oracle for set-membership (and the hash functions, depending on the setting), and after interacting with these
-%it is challenged with either $x_0$ or $x_1$, where $x_0$ is a random
-%point from the set of non-FPs, and $x_1$ is a random point from the
-%set of FPs?  (No oracles after being challenged.)  The adversary has
-%to decide which it received.}
+Second, we note that the NY syntax does not capture the size of~$M$ as a parameter; 
+\jnote{I think this is also reasonable; typically security is defined without regard for efficiency} \tsnote{My complaint isn't about efficiency.
+It's about the fact that, by not including $|M|$ in the definition, the trivial scheme I give (just below) is allowed, and is secure.
+Anyway, as I say at the end of
+this paragraph, this is a small(er) complaint than what follows}.
+\jnote{I would say that the trivial scheme \emph{is} secure!} 
+\tsnote{Okay, well then we need some way to ``rule out'' the trivial solution.
+Perhaps just in the text -- yes, the trivial scheme works, but it isn't interesting in practice.
+Also, in the concrete security bounds that we will prove, the size of the representation is going to come up, e.g.\ the number of bits in the BF array directly affect the FP rate.
+Hence it makes sense to say things like ``an $(n,k,m)$-filter...'' where $m$ is the size of the representation.}
+The surrounding text does say that $\mathbf{B}_1$ ``outputs a compressed representation [of $\mathcal{S}$] $\mathbf{B}_1(\mathcal{S})=M$'' but what exactly this means is never addressed.
+The formal syntax admits $\mathbf{B}_1(\mathcal{S})=\mathcal{S}$ and $\mathbf{B}_2(\mathcal{S},x)=1 \Leftrightarrow x \in \mathcal{S}$, which is also trivially secure by their definition.
+These are both small, but important complaints.
+But a larger complaint, and one that is much harder to see, is that that it is not clear that the NY formalism actually captures real world Bloom filters.
 
-Second, we note that the NY syntax does not capture the size of~$M$
-as a parameter; \jnote{I think this is also reasonable; typically
-security is defined without regard for efficiency} \tsnote{My
-complaint isn't about efficiency. It's about the fact that, by not
-including $|M|$ in the definition, the trivial scheme I give (just
-below) is allowed, and is secure.  Anyway, as I say at the end of
-this paragraph, this is a small(er) complaint than what follows}.
-\jnote{I would say that the trivial scheme \emph{is} secure!} The
-surrounding text does say that $\mathbf{B}_1$ ``outputs a compressed
-representation [of $\mathcal{S}$] $\mathbf{B}_1(\mathcal{S})=M$''
-but what exactly this means is never addressed.  The formal syntax
-admits $\mathbf{B}_1(\mathcal{S})=\mathcal{S}$ and
-$\mathbf{B}_2(\mathcal{S},x)=1 \Leftrightarrow x \in \mathcal{S}$,
-which is also trivially secure by their definition.  These are both
-small, but important complaints.  But a larger complaint, and one
-that is much harder to see, is that that it is not clear that the NY
-formalism actually captures real world Bloom filters.
-
-In particular, say we implement a classic Bloom filter.  Then the
-hash functions $h_1, h_2, \ldots, h_k$ are either sampled from some
-family~$\mathcal{H}$ by~$\mathbf{B}_1$ (recall that this algorithm
-is randomized), or they are hard-coded into the description
-of~$\mathbf{B}_1$.  Let's assume the former for the moment.  In
-order for~$\mathbf{B}_2$ to be able to respond to set-membership
-queries, it must have $h_1,h_2,\ldots,h_k$ as well.
-Since~$\mathbf{B}_2$ receives only the representation~$M$ as input,
-it must be the case that $h_1,h_2,\ldots,h_k$ are encoded into~$M$
-somehow.  But the text strongly suggests, in several places,
-that~$M$ does \emph{not} include these.  Both NY and classical
-analysis of Bloom filters speak of the number of bits used to
-represent the set~$\mathcal{S}$: the classical analysis means only
-the number of bits in the actual array, and NY make comparisons
-throughout between the number of bits~$m$ used by their
-instantiations and the classical bounds. Moreover, the Bloom filter
-they construct in one of their main positive results clearly
-\emph{does not} count as part of the representation size the hash
-functions used to indicate array locations.
+In particular, say we implement a classic Bloom filter.
+Then the hash functions $h_1, h_2, \ldots, h_k$ are either sampled from some family~$\mathcal{H}$ by~$\mathbf{B}_1$ (recall that this algorithm is randomized), or they are hard-coded into the description of~$\mathbf{B}_1$.
+Let's assume the former for the moment.
+In order for~$\mathbf{B}_2$ to be able to respond to set-membership queries, it must have $h_1,h_2,\ldots,h_k$ as well.
+Since~$\mathbf{B}_2$ receives only the representation~$M$ as input, it must be the case that $h_1,h_2,\ldots,h_k$ are encoded into~$M$ somehow.
+But the text strongly suggests, in several places, that~$M$ does \emph{not} include these.
+Both NY and classical analysis of Bloom filters speak of the number of bits used to represent the set~$\mathcal{S}$: the classical analysis means only the number of bits in the actual array, and NY make comparisons throughout between the number of bits~$m$ used by their instantiations and the classical bounds.
+Moreover, the Bloom filter they construct in one of their main positive results clearly \emph{does not} count as part of the representation size the hash functions used to indicate array locations.
 %Thus, if we assume that
@@
 
-\jnote{FWIW, I think the classical description of Bloom filters has
-the same problem. I.e., if the hash functions are not fixed, then
-their description should be counted as part of the length of the
-data structure. On the other hand, if they are fixed, then the
-false-positive rate is not well-defined (since there is no
-probability space to speak of). So in that sense, NY just carried
-over the problem from the classical literature.}
-\tsnote{One can suggest that it \emph{should} be counted in the classical
-  description, but the fact is that it isn't :)  And in the 30+ years
-  since the original paper, no one saw fit to correct this?  From an
-  algorithmic perspective, I think the classical approach makes
-  sense.  The questions being answered are: how many bits do I need to
-  store a representation of the set for a given FP rate, and how does this compare to the
-  combinatorially computed lower-bound?  The description length of the
-hash functions may be bigger or smaller, but the number of bits you
-need to hold the set representation is independent of that.  (Imagine
-that you have long random bitstrings in the set~$\mathcal{S}$.  Then
-whether your hash functions simply truncate, or they are random
-oracles, the size of the representation as a function of the target FP
-rate doesn't change.  Yet the description lengths of the hash
-functions are drastically different.)}
+%\jnote{FWIW, I think the classical description of Bloom filters has the same problem.
+I.e., if the hash functions are not fixed, then their description should be counted as part of the length of the data structure.
+On the other hand, if they are fixed, then the false-positive rate is not well-defined (since there is no probability space to speak of).
+So in that sense, NY just carried over the problem from the classical literature.}
+%
+%\tsnote{One can suggest that it \emph{should} be counted in the classical description, but the fact is that it isn't :) And in the 30+ years since the original paper, no one saw fit to correct this?
+From an algorithmic perspective, I think the classical approach makes sense.
+The questions being answered are: how many bits do I need to store a representation of the set for a given FP rate, and how does this compare to the combinatorially computed lower-bound?
+The description length of the hash functions may be bigger or smaller, but the number of bits you need to hold the set representation is independent of that.
+(Imagine that you have long random bitstrings in the set~$\mathcal{S}$.
+Then whether your hash functions simply truncate, or they are random oracles, the size of the representation as a function of the target FP rate doesn't change.
+Yet the description lengths of the hash functions are drastically different.)}
 
-On the other hand, assume the hash functions are implicitly
-hard-coded into~$\mathbf{B}_1$ (and $\mathbf{B}_2$). Then we can
-treat~$\mathbf{B}_1$ as deterministic, since it will simply carry
-out the steps required to populate an array using these hash
-functions, and output the array~$M$ as the representation.  If the
-descriptions of~$\mathbf{B}_1,\mathbf{B}_2$ are known to the
-adversary, who is also provided with~$\mathcal{S}$, then the
-adversary can compute~$M$ itself, as well as test for false
-positives itself. So it isn't clear how the security notion helps to
-reason about difficulty of finding a false-positive. Moreover, NY
-stresses (at least once) that the representation is \emph{not} given
-to the adversary in their notions.  So it seems unlikely that they
-intended for $h_1,h_2,\ldots,h_k$ to be hard-coded into the
-algorithms.
-\jnote{Perhaps it is reasonable to consider a definition
-in which the set is not given to the adversary?}
-\tsnote{A FP security notion?  Yes, perhaps so.  It's probably a more
-  realistic notion anyway -- is a spammer really going to know my
-  whitelist a priori?  (If he does, I probably have bigger problems in
-my system than receiving new spam email.)  Or set of URLs cached by a
-CDN server?}
+On the other hand, assume the hash functions are implicitly hard-coded into~$\mathbf{B}_1$ (and $\mathbf{B}_2$).
+Then we can treat~$\mathbf{B}_1$ as deterministic, since it will simply carry out the steps required to populate an array using these hash functions, and output the array~$M$ as the representation.
+If the descriptions of~$\mathbf{B}_1,\mathbf{B}_2$ are known to the adversary, who is also provided with~$\mathcal{S}$, then the adversary can compute~$M$ itself, as well as test for false positives itself.
+So it isn't clear how the security notion helps to reason about difficulty of finding a false-positive.
+Moreover, NY stresses (at least once) that the representation is \emph{not} given to the adversary in their notions.
+So it seems unlikely that they intended for $h_1,h_2,\ldots,h_k$ to be hard-coded into the algorithms.
+\jnote{Perhaps it is reasonable to consider a definition in which the set is not given to the adversary?}
+\tsnote{A FP security notion?
+Yes, perhaps so.
+It's probably a more realistic notion anyway -- is a spammer really going to know my whitelist a priori?
+(If he does, I probably have bigger problems in my system than receiving new spam email.) Or set of URLs cached by a CDN server?}
 
-Continuing on this point, it seems that the coins of~$\mathbf{B}_1$
-(whatever their use) are intended to be kept secret from the
-adversary.  Thus, to the extent that it addresses real Bloom filters
-at all, the NY security notion only addresses applications in which
-the representation is created using secret coins.  But many
-real-world applications of Bloom filters have no secrets.  NY point
-to web proxies, which use Bloom filters to compactly represent the
-objects they store locally, as motivation for their work.  But real
-web proxies like Squid~\cite{xxx} do \emph{not} use secrets in their
-Bloom filters.  Squid, in particular, uses the basic Bloom filter with four hash
-functions, defined as follows: $h_1(x) =
-\mathrm{MD5}(x)[0,\ldots,31]$,
-$h_2(x)=\mathrm{MD5}(x)[32,\ldots,63]$,
-$h_3(x)=\mathrm{MD5}(x)[64,\ldots,95]$, and
-$h_4(x)=\mathrm{MD5}(x)[96,\ldots,127]$.  Likewise, there are no
-secrets in the Bloom filters used by Google's BigTable~\cite{xxx},
-HBase~\cite{xxx}, \tsnote{make an impressive list.}
+Continuing on this point, it seems that the coins of~$\mathbf{B}_1$ (whatever their use) are intended to be kept secret from the adversary.
+Thus, to the extent that it addresses real Bloom filters at all, the NY security notion only addresses applications in which the representation is created using secret coins.
+But many real-world applications of Bloom filters have no secrets.
+NY point to web proxies, which use Bloom filters to compactly represent the objects they store locally, as motivation for their work.
+But real web proxies like Squid~\cite{xxx} do \emph{not} use secrets in their Bloom filters.
+Squid, in particular, uses the basic Bloom filter with four hash functions, defined as follows: $h_1(x) = \mathrm{MD5}(x)[0,\ldots,31]$, $h_2(x)=\mathrm{MD5}(x)[32,\ldots,63]$, $h_3(x)=\mathrm{MD5}(x)[64,\ldots,95]$, and $h_4(x)=\mathrm{MD5}(x)[96,\ldots,127]$.
+Likewise, there are no secrets in the Bloom filters used by Google's BigTable~\cite{xxx}, HBase~\cite{xxx}, \tsnote{make an impressive list.}
 
-There are applications in which the proposed Bloom filter instantiations do
-use secretly keyed hash functions, e.g. $h_j(x) = (f(K_0,x) + j\cdot
-g(K_1,x))\bmod m$, where $j\in[1,k]$, $m$ is the number of bits in
-the array, and where $f,g$ are PRFs keyed by secrets $K_0,K_1$.
-This particular ``encrypted Bloom filter'' instantiation was
-suggested for use in efficient linking of records across separate
-medical record databases~\cite{xxx}.  (It was subsequently shown not
-to be secure by Niedermeier et al.~\cite{xxx}, where a clever use of
-frequency analysis recovered the last names of patients given access
-only to the Bloom filter array.)
-%\tsnote{This shows that false-positive security and privacy (whatever it is) are orthogonal,
-%since I'm pretty sure this ``encrypted'' bloom filter resists FPs.})
-In any case, it is clear that the NY definition does not capture the
-most widely used applications of Bloom filters, e.g. CDN summary
-caches, P2P network routing algorithms, etc. \tsnote{Could also
-point out that their positive results use constructions that have
-secret keys, and these are unlikely to be of any use in major
-applications like CDNs or P2P networks.  But maybe the horse is
-sufficiently beaten by now...}
+There are applications in which the proposed Bloom filter instantiations do use secretly keyed hash functions, e.g.
+$h_j(x) = (f(K_0,x) + j\cdot g(K_1,x))\bmod m$, where $j\in[1,k]$, $m$ is the number of bits in the array, and where $f,g$ are PRFs keyed by secrets $K_0,K_1$.
+This particular ``encrypted Bloom filter'' instantiation was suggested for use in efficient linking of records across separate medical record databases~\cite{xxx}.
+(It was subsequently shown not to be secure by Niedermeier et al.~\cite{xxx}, where a clever use of frequency analysis recovered the last names of patients given access only to the Bloom filter array.)
+In any case, it is clear that the NY definition does not capture the most widely used applications of Bloom filters, e.g. CDN summary caches, P2P network routing algorithms, etc. 
+%\tsnote{Could also point out that their positive results use constructions that have secret keys, and these are unlikely to be of any use in major applications like CDNs or P2P networks.
+But maybe the horse is sufficiently beaten by now...}
 
@@
 
-We generalize this syntax to hash-based filters that are mutable
-\jnote{I find ``mutable'' a slightly awkward term,  maybe because it
-makes me think of mutability in the context of programming
-languages. In much data structures literature, this is called the
-``dynamic'' case, in contrast to the ``static'' case.} \tsnote{I
-adopted this term after reading it in some bloom filter
-paper(s). Ironically, I liked it for the same reason you think it is
-awkward :)  My PL association to the term is that an immutable object
-is one whose state cannot be modified after it is created, and a
-mutable object is the opposite.  But I don't really care too much.}, in the sense
+We generalize this syntax to hash-based filters that are mutable,
+%\jnote{I find ``mutable'' a slightly awkward term, maybe because it makes me think of mutability in the context of programming languages.
+In much data structures literature, this is called the ``dynamic'' case, in contrast to the ``static'' case.}
+%
+%\tsnote{I adopted this term after reading it in some bloom filter paper(s).
+Ironically, I liked it for the same reason you think it is awkward :) My PL association to the term is that an immutable object is one whose state cannot be modified after it is created, and a mutable object is the opposite.
+But I don't really care too much.}
+in the sense
 that they allow for updating of the representation. This allows us

### 2016-07-08 filters-syntax.tex
no message
cleaning up filter syntax section

@@
 %
-The randomized \emph{hash-sampling} algorithm~$\Hash$ samples a
-size~$k$  family of functions~$\mathcal{H}=\{h_1,h_2,\ldots,h_k\}$
-where each $h_i \in  \mathrm{Func}(U,[m])$.  We write $\mathcal{H}
-\getsr \Hash$ for this operation.
+The randomized \emph{hash-sampling} algorithm~$\Hash$ samples a size~$k$ family of functions~$\mathcal{H}=\{h_1,h_2,\ldots,h_k\}$ where each $h_i \in \mathrm{Func}(U,[m])$.  
+\jnote{This doesn't seem to work super-well with the random oracle model.} 
+\tsnote{Why not?  As we discussed on the phone, this should be fine.  In the ROM, if we ever need to simulate $\Hash$, we just do it by lazy sampling.}
+We write $\mathcal{H} \getsr \Hash$ for this operation.
 %
-The randomized representation algorithm $\Rep\colon [U]^n \rightarrow
-\Sigma^m \times \bits^*$ takes a set~$S$ of~$n$ elements as input, and outputs
-representation~$M$ of length~$m$ along with (possibly empty) side-information~$\tau$.
+The randomized representation algorithm $\Rep\colon [U]^n \rightarrow \Sigma^m \times \bits^*$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m$ along with (possibly empty) side-information~$\tau$.
 %
-The deterministic query algorithm $\Qry\colon \Sigma^m \times \bits^* \times U
-\rightarrow \bits$ takes a representation $M$, side-information~$\tau$, and an element $x \in
-U$, and returns a bit.
+The deterministic query algorithm $\Qry\colon \Sigma^m \times \bits^* \times U \rightarrow \bits$ takes a representation $M$, side-information~$\tau$, and an element $x \in U$, and returns a bit.
 %
-We assume that both $\Rep$ and $\Qry$ have blackbox access to the
-functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$.
+We assume that both $\Rep$ and $\Qry$ have blackbox access to the functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$.
 Typically this access will be implicit, but when we need to make it explicit we will write~$\mathcal{H}$ (or the individual hash functions) as superscripts.
@@
 %We write $M \gets \Rep(S)$ and $b \gets \Qry(M,x)$ for the execution of the representation and query algorithms, respectively.
-For correctness, we demand that for all~$S$ of size~$n$ and all $x
-\in S$, it holds that $\Prob{\mathcal{H}\getsr\Hash;\,(M,\tau)\getsr\Rep(S)\,:\,\Qry(M,\tau,x)=1}=1$, where the
-probability is over the coins of $\Hash$ and~$\Rep$.
+For correctness, we demand that for all~$S$ of size~$n$ and all $x \in S$, it holds that $\Prob{\mathcal{H}\getsr\Hash;\,(M,\tau)\getsr\Rep(S)\,:\,\Qry(M,\tau,x)=1}=1$, where the probability is over the coins of $\Hash$ and~$\Rep$.
 
@@
 By allowing $\Rep$ to output side-information, we allow for (say) $\Rep$ and $\Qry$ to share a secret key selected during representation generation.
+In our security notions, any side-information will be kept secret from the adversary.
 \tsnote{Ultimately it might be cleaner to fold the hash functions into the side-information, too.
@@
 Note that we do see constructions that have \emph{no} ``stand-alone'' hash functions yet use a secret key (e.g., the PRF-based double-hashing construction), and also schemes that employ \emph{both} stand-alone hash functions and a secret key (e.g.
-the record BF from Durham et al.)}  In our security notions, any side-information will be kept secret from the adversary.
-
+the record BF from Durham et al.)}
+%
+\tsnote{Per our phone call 7/8, we're going to leave things as they are for now.
+Jon will create an appendix with more general syntax and notions; we'll see how results play out, and decide later if we want to adopt the change in syntax.}
 Setting $\Sigma=\bits^{\leq L}$ allows one to store a bitstring of length at most~$L$ at each location.
@@
 (One could, however, have $\Qry$ compute an arbitrary, fixed predicate.
-For example, ``has~$x$ been seen at least 5 times?''.)
-Our syntax also does not capture filters that are mutable, that is, whose representation may change over time.
+For example, ``has~$x$ been seen at least 5 times?''.) Our syntax also does not capture filters that are mutable, that is, whose representation may change over time.
 On the other hand, we can state a simple correctness condition for these kinds of filters; this will not be true when we further generalize to capture, properly, counters and mutability.

### 2016-07-08 filters-notions.tex
cheers

@@
 
-\heading{FP-security of hash-based filters.} \tsnote{NY give it in
-the private hash setting (sort of); but, intuitively, it should be
-hard to find false-positives even if you know that MD5 or SHA-x are
-the hash functions.  Not totally sure how to capture this intuition
-nicely.} \jnote{Not sure I agree. First of all, if $\epsilon$ is not
-negligible then a random element is a false positive with noticeable
-probability. Beyond that, I think that intuitively it makes sense
-that if you want false positives to be hard to find then you need to
-make the hash functions secret.} \tsnote{I don't think it makes sense
-to talk about asymptotics or negligibility, for exactly the reason you
-state. I think the key point here is: what is ``hard''?   The designer decides what FP rate is
-acceptable for a given application, a given set of efficiency
-constraints, the side-effects of a FP, etc.  For a fixed FP target,
-she optimizes the filter size and/or the number of hash functions for
-her setting. Whether the target FP rate is 0.01 or $2^{-80}$, we should be able to say (in the ROM, at least)
-that it will take this-many hash computations, and this many on-line
-set-membership queries, to find the first FP.  In the standard model,
-with public hash functions, it is clearly more difficult to make
-formal claims.  Even so, in practice I expect it would be quite expensive to
-find a string~$x$ such that $(h_1(x),h_2(x),\ldots,h_k(x))$
-falls in a given set of tuples when $h_i(x)=\mathrm{truncate}(\mathrm{SHA256}(\langle i \rangle
-\concat x), m)$, say. (Even more so if my setting admits relatively
-expensive hash computations, e.g. SCRYPT.)  BTW, your suggestion to
-have a FP notion with secret~$\mathcal{S}$ is interesting here. }
-
+\heading{FP-security of hash-based filters.}  
+%\tsnote{NY give it in the private hash setting (sort of); but, intuitively, it should be hard to find false-positives even if you know that MD5 or SHA-x are the hash functions.
+Not totally sure how to capture this intuition nicely.}
+%
+%\jnote{Not sure I agree.
+First of all, if $\epsilon$ is not negligible then a random element is a false positive with noticeable probability.
+Beyond that, I think that intuitively it makes sense that if you want false positives to be hard to find then you need to make the hash functions secret.}
+%
+%\tsnote{I don't think it makes sense to talk about asymptotics or negligibility, for exactly the reason you state.
+I think the key point here is: what is ``hard''?
+The designer decides what FP rate is acceptable for a given application, a given set of efficiency constraints, the side-effects of a FP, etc.
+For a fixed FP target, she optimizes the filter size and/or the number of hash functions for her setting.
+Whether the target FP rate is 0.01 or $2^{-80}$, we should be able to say (in the ROM, at least) that it will take this-many hash computations, and this many on-line set-membership queries, to find the first FP.
+In the standard model, with public hash functions, it is clearly more difficult to make formal claims.
+Even so, in practice I expect it would be quite expensive to find a string~$x$ such that $(h_1(x),h_2(x),\ldots,h_k(x))$ falls in a given set of tuples when $h_i(x)=\mathrm{truncate}(\mathrm{SHA256}(\langle i \rangle \concat x), m)$, say.
+(Even more so if my setting admits relatively expensive hash computations, e.g.
+SCRYPT.) BTW, your suggestion to have a FP notion with secret~$\mathcal{S}$ is interesting here.
+}
+%
 The traditional notion of soundness for a Bloom filter captures the difficulty of finding false positives when the attacker is non-adaptive.
 Following NY, we consider soundness against adaptive adversaries.
-But we further generalize to allow for settings in which the attacker may have some a priori knowledge about the contents of~$S$.
+But we further generalize to allow for settings in which the attacker may have some a priori knowledge about the contents of~$\calS$.
 (The Niedermaier et al.~\cite{xxx} attacks, for example, exploit knowledge about the distribution of German last names.) In particular, our notions take as input an explicit distribution $\distr{U}{n}$ over~$[U]^n$.
 
-\jknote{We also want to capture the fact that finding the first
-false positive should not make it any easier to find subsequent
-false positives. This is not really captured by the Naor paper,
-either (at least not directly, though it may end up being implied by
-their definition).} \tsnote{See my comment in the intro.}
+%\jknote{We also want to capture the fact that finding the first false positive should not make it any easier to find subsequent false positives.
+This is not really captured by the Naor paper, either (at least not directly, though it may end up being implied by their definition).}
+%
+%\tsnote{See my comment in the intro.}
 
@@
 
-\jnote{Do our definitions imply the Naor definition? If so, then why do they use a PRP
-in their construction?}
+\jnote{7/8: Do our definitions imply the Naor definition? If so, then why do they use a PRP in their construction?}
 
 We note that the distribution~$\distr{U}{n}$ must be independent of the hash functions $h_1,h_2,\ldots,h_k$ that are used to create~$M$.
-Otherwise, when (say) $\Sigma=\bits$, the distribution may only assign positive probability to sets~$S$ that cause an abnormally large number of bits in~$M$ to be set to 1.
+Otherwise, when (say) $\Sigma=\bits$, the distribution may only assign positive probability to sets~$\calS$ that cause an abnormally large number of bits in~$M$ to be set to 1.
 Our security notions enforce this independence.
 
-\jnote{How do we want to define a ``secure'' Bloom filter (even
-informally)? Do we want to say that the probability of finding a
-false positive is negligible? Or that if we set the FP rate to
-$\epsilon$ then the best an attacker can do with $q$ hash queries is
-$1-(1-\epsilon)^q$ plus negligible?}
-\tsnote{Formally, I don't think we can (and still be rooted in
-  reality).  Even informally it's hard, since the fact is that the
-  designer decides what is ``secure'' for her setting.  I think we
-  just say something like ``A bloom filter is
-  $(t,q_h,q_m,\epsilon)$-secure if no attacker running in time at
-  most~$t$, asking at most~$q_h$ hash queries and $q_m$ set-membership
-  queries, has probability more than~$\epsilon$ of finding a FP.''  (If
-you like, we can throw a paramter~$n$ in there, for the number of FPs
-it must find.)  Perhaps informally we say that a bloom filter is
-secure if, for ``reasonable'' $t,q_h,q_m$, the value of~$\epsilon$ is
-not ``significantly larger'' than the designer's target.  I guess
-that's not far off from one of your suggestions.}
+\jnote{How do we want to define a ``secure'' Bloom filter (even informally)?
+Do we want to say that the probability of finding a false positive is negligible?
+Or that if we set the FP rate to $\epsilon$ then the best an attacker can do with $q$ hash queries is $1-(1-\epsilon)^q$ plus negligible?}
+%
+\tsnote{Formally, I don't think we can (and still be rooted in reality).
+Even informally it's hard, since the fact is that the designer decides what is ``secure'' for her setting.
+I think we just say something like ``A bloom filter is $(t,q_h,q_m,\epsilon)$-secure if no attacker running in time at most~$t$, asking at most~$q_h$ hash queries and $q_m$ set-membership queries, has probability more than~$\epsilon$ of finding a FP.'' (If you like, we can throw a paramter~$n$ in there, for the number of FPs it must find.) Perhaps informally we say that a bloom filter is secure if, for ``reasonable'' $t,q_h,q_m$, the value of~$\epsilon$ is not ``significantly larger'' than the designer's target.
+I guess that's not far off from one of your suggestions.}
 
-\jnote{One thing that is nice about the
-NY notion is that you get a ``clean'' definition of security: no
-matter how many FPs the attacker has found so far, the probability
-that it can output a fresh FP is still $\epsilon$.}
+%\jnote{One thing that is nice about the NY notion is that you get a ``clean'' definition of security: no matter how many FPs the attacker has found so far, the probability that it can output a fresh FP is still $\epsilon$.}
 
@@
 {
-\experimentv{$\ExpFPSecHash{B}{\distr{U}{n},A}$}\\
-$S \getsr \distr{U}{n}$\\
+\experimentv{$\ExpFPSecHash{B,t}{\distr{U}{n},A}$}\\
+$\calS \getsr \distr{U}{n}$\\
 $h_1,\ldots,h_k \getsr \Hash$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle}(S)$\\
-if $x \not\in S \wedge \Qry^{\HashOracle}(M,\tau,x)=1$ then\\
-\nudge Ret 1\\
-Ret 0
+$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
+$\calX \getsr A^{\QryOracle}(\calS)$\\
+if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
+\nudge Ret 0\\
+If $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
+\nudge Ret 0\\
+Ret 1
 }
@@
 \experimentv{$\ExpFPPubHashBB{B}{\distr{U}{n}, A}$}\\
-$S \getsr \distr{U}{n}$\\
+$\calS \getsr \distr{U}{n}$\\
 $h_1,\ldots,h_k \getsr \Hash$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle,\HashOracle}(S)$\\
-if $x \not\in S \wedge \Qry^{\HashOracle}(M,\tau,x)=1$ then\\
-\nudge Ret 1\\
-Ret 0
+$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
+$\calX \getsr A^{\QryOracle,\HashOracle}(\calS)$\\
+if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
+\nudge Ret 0\\
+If $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
+\nudge Ret 0\\
+Ret 1
 }
@@
 \experimentv{$\ExpFPPubHash{B}{\distr{U}{n}, A}$}\\
-$S \getsr \distr{U}{n}$\\
+$\calS \getsr \distr{U}{n}$\\
 $h_1,\ldots,h_k \getsr \Hash$\\
-$(M,\tau) \gets \Rep^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle}(S,\{h_1,h_2,\ldots,h_k\})$\\
-if $x \not\in S \wedge \Qry^{\HashOracle}(M,\tau,x)=1$ then\\
-\nudge Ret 1\\
-Ret 0
+$(M,\tau) \gets \Rep^{\HashOracle}(\calS)$\\
+$\calX \getsr A^{\QryOracle}(S,\{h_1,h_2,\ldots,h_k\})$\\
+if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
+\nudge Ret 0\\
+If $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
+\nudge Ret 0\\
+Ret 1 
 }
@@
 queriable hash functions (middle), and public hash functions
-(bottom). \jnote{Could also consider not giving $S$ to the
+(bottom). \jnote{Could also consider not giving $\calS$ to the
 adversary.} } \label{fig:fp-filter}
@@
 \experimentv{$\ExpPrivSecHash{B}{\distr{U}{n}, A}$}\\
-$S \getsr \distr{U}{n}$\\
+$\calS \getsr \distr{U}{n}$\\
 $h_1,\ldots,h_k \getsr \Hash$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
+$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
 $x \getsr A^{\QryOracle}(M)$\\
-if $x\in S$ then Ret 1\\
+if $x\in \calS$ then Ret 1\\
 Ret 0
@@
 \experimentv{$\ExpPrivPubHashBB{B}{\distr{U}{n}, A}$}\\
-$ S \getsr \distr{U}{n}$\\
+$ \calS \getsr \distr{U}{n}$\\
 $h_1,\ldots,h_k \getsr \Hash$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
+$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
 $x \getsr A^{\QryOracle,\HashOracle}(M)$\\
-if $x\in S$ then Ret 1\\
+if $x\in \calS$ then Ret 1\\
 Ret 0\\
@@
 \experimentv{$\ExpPrivPubHash{B}{\distr{U}{n}, A}$}\\
-$ S \getsr \distr{U}{n}$\\
+$ \calS \getsr \distr{U}{n}$\\
 $h_1,\ldots,h_k \getsr \Hash$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(S)$\\
+$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
 $x \getsr A^{\QryOracle}(M,\{h_1,h_2,\ldots,h_k\})$\\
-if $x\in S$ then Ret 1\\
+if $x\in \calS$ then Ret 1\\
 Ret 0\\

### 2016-07-08 filters-notions.tex
changed FP notions to allow for finding multiple FPs

@@
 \heading{Privacy of hash-based filters.} We now define privacy notions for $(n,k,m)$-filters.
-Informally, the adversary is given the representation~$M$ of a secret set~$S$, and its goal is to guess one of the elements of~$S$.
+Informally, the adversary is given the representation~$M$ of a secret set~$\calS$, and its goal is to guess one of the elements of~$\calS$.
 Of course, if the distribution~$\distr{U}{n}$ has low min-entropy with respect to any particular element $x \in U$, then it will be relatively easy to guess~$x$.
-To capture this min-entropy, let $p_{\mathrm{max}} = \max_{x \in U} \Prob{S \getsr \distr{U}{n}:\, x \in S}$ and define $\mu = -\log_2 p_{\mathrm{max}}$ to be the (element-wise) min-entropy of distribution $\distr{U}{n}$.
+To capture this min-entropy, let $p_{\mathrm{max}} = \max_{x \in U} \Prob{\calS \getsr \distr{U}{n}:\, x \in \calS}$ and define $\mu = -\log_2 p_{\mathrm{max}}$ to be the (element-wise) min-entropy of distribution $\distr{U}{n}$.
 
-We note that~$S$ must be independent of the hash functions~$h_1,h_2,\ldots,h_k$ used to create the representation of~$S$.  \tsnote{I thought this would be needed, but now I'm not sure it is. }
+We note that~$\calS$ must be independent of the hash functions~$h_1,h_2,\ldots,h_k$ used to create the representation of~$\calS$.  \tsnote{I thought this would be needed, but now I'm not sure it is. }
 
 A weaker notion of privacy would not give~$M$ to the adversary.
-However, this would not capture attacks such as those mounted by Neidermayer et al.\cite{XXX}, and would not speak to settings in which (say) an honest-but-curious third party is given the representation~$M$ in order to carry out some task on behalf of the holder of~$S$.
+However, this would not capture attacks such as those mounted by Neidermayer et al.\cite{XXX}, and would not speak to settings in which (say) an honest-but-curious third party is given the representation~$M$ in order to carry out some task on behalf of the holder of~$\calS$.
 

### 2016-07-08 filters-notions.tex
changed FP notions to allow for finding multiple FPs
adding true membership test oracle to privacy experiments
hash oracles now return all values at once

@@
 \medskip
-\oracle{$\HashOracle(i,x)$}\\
-Ret $h_i(x)$\\
+\oracle{$\HashOracle(x)$}\\
+Ret $\left(h_1(x),\ldots,h_k(x)\right)$\\
 }
@@
 {
-\experimentv{$\ExpFPPubHashBB{B}{\distr{U}{n}, A}$}\\
+\experimentv{$\ExpFPPubHashBB{B,t}{\distr{U}{n}, A}$}\\
 $\calS \getsr \distr{U}{n}$\\
@@
 {
-\experimentv{$\ExpFPPubHash{B}{\distr{U}{n}, A}$}\\
+\experimentv{$\ExpFPPubHash{B,t}{\distr{U}{n}, A}$}\\
 $\calS \getsr \distr{U}{n}$\\
@@
 \medskip
-\oracle{$\HashOracle(i,x)$}\\
-Ret $h_i(x)$\\
+\oracle{$\HashOracle(x)$}\\
+Ret $\left(h_1(x),\ldots,h_k(x)\right)$\\
 } } \caption{False-positive security (soundness) for an
@@
 {
+\oracle{$\MemOracle(x)$}\\
+Ret $[x \in \calS]$\\
+
+\medskip
 \oracle{$\QryOracle(x)$}\\

### 2016-07-08 filters-results.tex
adding new tasks

@@
 \section{Achieving FP-Security and Privacy}
+\heading{FP-security. }
+\begin{itemize}
+\item FP-security/attacks on bigram/PRF-based double-hashing construction \tsnote{Animesh is doing this now}
+\item FP-security/attacks on bigram/domain-separated PRF construction (see below, in Privacy section)
+\item FP-security/attacks Dong, Chen, Wen ``garbled Bloom filter''
+\item FP-security/attacks on count-min sketch
+\item ...
+\end{itemize}
+
+\heading{Privacy. }
 \tsnote{Under our current notions, you can never hope to prove privacy bounds that beat the min-entropy of $\distr{U}{n}$.}

### 2016-07-08 filters-results.tex
cheers

--- 2016-07-06 filters-results.tex
@@
 \section{Achieving FP-Security and Privacy}
+\heading{FP-security. }  Here we give security proofs and attacks with respect the the FP-security notions just described.
+\begin{itemize}
+\item FP-security/attacks on bigram/PRF-based double-hashing construction ($h_j(x) = F_{K1}(x) + j\cdot F_{K2}(x) \bmod m$ where the~$x$ are bigrams of names, etc.) \tsnote{Animesh is doing this now}
+\item FP-security/attacks on bigram/domain-separated PRF construction ($h_j(x)=F_K(\langle j,x \rangle) \bmod m$, or just assume range of~$F$ is $[m]$.)
+\item FP-security/attacks Dong, Chen, Wen ``garbled Bloom filter'' construction
+\item ...
+\end{itemize}
+
+\heading{Privacy. } Here we give security proofs and attacks with respect the the FP-security notions just described.
 \tsnote{Under our current notions, you can never hope to prove privacy bounds that beat the min-entropy of $\distr{U}{n}$.}
@@
 }
+
+\item Prove privacy bounds for the constructions from NY
 

### 2016-07-11 Proofs.tex
Proof of Theorem1 correction1
Updated Proof of Theorem 1 as per the changed syntax and some minor corrections

@@
 \begin{theorem}\label{thm}
-Fix $k, m, n > 0$ and define a hash-based filter as in section \ref{sec:hbf}, except the hash functions are defined by $h_j(x) = \left( f_{K_0}(x) + j\cdot g_{K_1}(x)\right) \bmod m$.
-Let $Func(m,m)$ be the set of all functions $\rho \colon \calK \times \bits^m \sends \bits^m$.
-Let $B_1, B_2$ be 2 adversaries attacking the PRF advantage of $F \colon \calK \times \bits^m \sends \bits^m$ and $A$ be another adversary attacking the false positive game of hash-based filters, then
-
+Fix $k, m, n > 0$ and define a hash-based filter as in section \ref{sec:hbf}, except the hash functions are defined by $h_j(x) =  F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$, where $F \colon \calK \times U \sends [m]$ is a PRF.
+Let $Func(U,[m])$ be the set of all functions $\rho \colon \calK \times U \sends [m]$.
+Let $B_1, B_2$ be 2 adversaries attacking the PRF advantage of $F$, and $A$ be another adversary attacking the false positive game of hash-based filters with private hash functions, then
 \begin{equation}
-\AdvFPSecHash{B}{A} = \abs{ \AdvPRF{F}{B_2} - \AdvPRF{F}{B_1}} \pm q \cdot \epsilon
+\AdvFPSecHash{B,t}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} + q \cdot \epsilon
 \end{equation}
@@
 \ref{fig:Game}.
-$\game{0}(A)$ exactly simulates $\ExpFPSecHash{B}{A}$ with hash functions $h_j(x) = \left( f_{K_0}(x) + j\cdot g_{K_1}(x)\right) \bmod m$.
+$\game{0}(A)$ exactly simulates $\ExpFPSecHash{B,t}{A}$ with hash functions $h_j(x) =  F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$.
 So,
 \begin{equation}
-\AdvFPSecHash{B}{A} = \Prob{\game{0}(A)=1}\label{eq:0}
+\AdvFPSecHash{B,t}{A} = \Prob{\game{0}(A)=1}\label{eq:0}
 \end{equation}
- $\game{1}(A)$ and $\game{2}(A)$ attack 2 different filters, $B_1$ and $B_2$, with hash functions 
+ $\game{1}(A)$ and $\game{2}(A)$ attack 2 different filters with hash functions 
 \begin{eqnarray*}
-h_j(x) &=& ( f_{K_0}(x) + j\cdot \rho_2(x)) \bmod m\\
-h_j(x) &=& ( \rho_1(x) + j \cdot \rho_2(x)) \bmod m 
+h_j(x) &=& ( F_{K_0}(x) + j\cdot \rho_2(x)) \bmod m\\
+\mathrm{and,}\nudge h_j(x) &=& ( \rho_1(x) + j \cdot \rho_2(x)) \bmod m 
 \end{eqnarray*}
-Here, $\rho_1$ and $\rho_2$ are random functions sampled from $Func(m,m)$. Let adversary $B_1, B_2$ simulate $\game{1}(A)$ and $\game{2}(A)$ respectively as shown in Fig. \ref{fig:BGame1}.
+
+Here, $\rho_1$ and $\rho_2$ are random functions sampled from $Func(U,[m])$.
+Let adversaries $B_1, B_2$ simulate $\game{1}(A)$ and $\game{2}(A)$ respectively as shown in Fig.
+\ref{fig:BGame1}.
+When $b=1$, $B_1$ and $B_2$ exactly simulate $\game{0}(A)$
+and $\game{1}(A)$. While, for $b=0$, $B_1$ wins, if $\game{1}(A)$ outputs 0, and  $B_2$ wins, if $\game{2}(A)$ returns 0.
+
+\begin{eqnarray}
+\Prob{\ExpPRF{F}{B_1} = 1|b=1} &=& \Prob{\game{0}(A)=1}\label{eq:m1}\\
+\Prob{\ExpPRF{F}{B_2} = 1|b=1} &=& \Prob{\game{1}(A)=1}\label{eq:m2}\\
+\Prob{\ExpPRF{F}{B_1} = 1|b=0} &=& 1-\Prob{\game{1}(A)=1}\label{eq:m3}\\
+\Prob{\ExpPRF{F}{B_2} = 1|b=0} &=& 1-\Prob{\game{2}(A)=1}\label{eq:m4}
+\end{eqnarray}
 
 \par{In a classical Bloom filter, adversary $A^{'}$ is non-adaptive, i.e., for some fixed $x \notin S$, $A^{'}$ targets the false-positive error conditioned on randomness of hash functions.
-But in the $\ExpFPSecHash{B}{A}$ game, $A$ is adaptive, as it can adapt its queries as well as its output based on response of $\QryOracle$ oracle.
-Let $A$ makes $q$ queries $x_1, x_2, ..., x_q$ to the $\QryOracle$ oracle.
+But in the $\ExpFPSecHash{B,t}{A}$ game, $A$ is adaptive, as it can adapt its queries as well as its output based on response of $\QryOracle$ oracle.
+Let $A$ makes $q>t$ queries $x_1, x_2, ..., x_q$ to the $\QryOracle$ oracle.
 $\game{3}(A)$ simulates $fp-error$ game of $A^{'}$ as shown in Fig.
@@
 $S \getsr \distr{U}{n}$\\
-$M \getsr \Rep^{\HashOracle(\cdot, \cdot)}(S)$\\
-$x \getsr A^{\QryOracle(\cdot)}(S)$\\
-if $x \not\in S \wedge \Qry^{\HashOracle(\cdot, \cdot)}(M,x)=1$ then\\
-\nudge Ret 1\\
-Ret 0\\\\
+$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
+$\calX \getsr A^{\QryOracle}(\calS)$\\
+if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
+\nudge Ret 0\\
+if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
+\nudge Ret 0\\
+Ret 1\\\\
 %
 \oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle(\cdot, \cdot)}(M,x)$\\\\
+Ret $\Qry^{\HashOracle}(M,\tau,x)$\\\\
 %
-\oracle{$\HashOracle(i,x)$}\\
-$h_i(x) = F_{K_1}(x)+i \cdot F_{K_2}(x)$\\
-Ret $h_i(x)$
+\oracle{$\HashOracle(x)$}\\
+$h_i(x) = F_{K_1}(x)+i \cdot F_{K_2}(x)$, for $i\in[1,k]$\\
+Ret $\left(h_1(x),\ldots,h_k(x)\right)$
 }
@@
 $K_1 \getsr \calK$\\
-$\rho \getsr Func(m,m)$\\
+$\rho \getsr Func(U,[m])$\\
 $S \getsr \distr{U}{n}$\\
-$M \getsr \Rep^{\HashOracle(\cdot, \cdot)}(S)$\\
-$x \getsr A^{\QryOracle(\cdot)}(S)$\\
-if $x \not\in S \wedge \Qry^{\HashOracle(\cdot, \cdot)}(M,x)=1$ then\\
-\nudge Ret 1\\
-Ret 0\\\\
+$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
+$\calX \getsr A^{\QryOracle}(\calS)$\\
+if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
+\nudge Ret 0\\
+if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
+\nudge Ret 0\\
+Ret 1\\\\
 %
 \oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle(\cdot, \cdot)}(M,x)$\\\\
+Ret $\Qry^{\HashOracle}(M,\tau,x)$\\\\
 %
-\oracle{$\HashOracle(i,x)$}\\
-$h_i(x) = F_{K_1}(x)+i \cdot \rho(x)$\\
-Ret $h_i(x)$
+\oracle{$\HashOracle(x)$}\\
+$h_i(x) = F_{K_1}(x)+i \cdot \rho(x)$, for $i\in[1,k]$\\
+Ret $\left(h_1(x),\ldots,h_k(x)\right)$
 }
@@
 \underline{\game{2}(A)}\\
-$\rho_1,\rho_2 \getsr Func(m,m)$\\
+$\rho_1,\rho_2 \getsr Func(U,[m])$\\
 $S \getsr \distr{U}{n}$\\
-$M \getsr \Rep^{\HashOracle(\cdot, \cdot)}(S)$\\
-$x \getsr A^{\QryOracle(\cdot)}(S)$\\
-if $x \not\in S \wedge \Qry^{\HashOracle(\cdot, \cdot)}(M,x)=1$ then\\
-\nudge Ret 1\\
-Ret 0\\\\
+$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
+$\calX \getsr A^{\QryOracle}(\calS)$\\
+if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
+\nudge Ret 0\\
+if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
+\nudge Ret 0\\
+Ret 1\\\\
 %
 \oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle(\cdot, \cdot)}(M,x)$\\\\
+Ret $\Qry^{\HashOracle}(M,\tau,x)$\\\\
 %
-\oracle{$\HashOracle(i,x)$}\\
-$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$\\
-Ret $h_i(x)$
+\oracle{$\HashOracle(x)$}\\
+$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
+Ret $\left(h_1(x),\ldots,h_k(x)\right)$
 }
@@
 \underline{$\game{3}(A)$}\\
-$t \getsr [q]$, where $[q] = {0,1, \cdots, q-1}$\\
+$\ell \getsr [q]$, where $[q] = {0,1, \cdots, q-1}$\\
 $count = 0$ \\%count will be used to keep track of queries made to $\QryOracle$\\
 $win \gets false$\\
-$\rho_1,\rho_2 \getsr Func(m,m)$\\
+$\rho_1,\rho_2 \getsr Func(U,[m])$\\
 $S \getsr \distr{U}{n}$\\
-$M \getsr \Rep^{\HashOracle(\cdot, \cdot)}(S)$\\
-$x \getsr A^{\QryOracle(\cdot)}(S)$\\
-if $x \not\in S \wedge \Qry^{\HashOracle(\cdot, \cdot)}(M,x)=1$ then\\
-$\nudge $ Ret 1\\
-Ret 0\\\\
+$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
+$\calX \getsr A^{\QryOracle}(\calS)$\\
+if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
+\nudge Ret 0\\
+if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
+\nudge Ret 0\\
+Ret 1\\\\
 %
@@
 $count=count +1$\\
-if $(count == t)$\\
+if $(count == \ell)$\\
 $\nudge win = true$\\
-$\nudge \mathrm{Ret} \nudge \Qry^{\HashOracle(\cdot, \cdot)}(M,x)$\\
+$\nudge \mathrm{Ret} \nudge \Qry^{\HashOracle}(M,\tau,x)$\\
 else \\
@@
 %
-\oracle{$\HashOracle(i,x)$}\\
-$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$\\
-Ret $h_i(x)$
+\oracle{$\HashOracle(x)$}\\
+$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
+Ret $\left(h_1(x),\ldots,h_k(x)\right)$
 }
@@
 $S \getsr \distr{U}{n}$\\
-$M \getsr \Rep^{\HashOracle(\cdot, \cdot)}(S)$\\
+$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
 When $A$ asks $\QryOracle(x)$:\\
-$\nudge$ Ret $\Qry^{\HashOracle(\cdot, \cdot)}(M,x)$\\
-When $A$ halts with output $x^{'}$: \\
-$\nudge$if $x^{'} \not\in S \wedge \Qry^{\HashOracle(\cdot, \cdot)}(M,x^{'})=1$ then\\
-$\nudge$ $\nudge$ Ret 1\\
-$\nudge$ Ret 0\\\\
-\oracle{$\HashOracle(i,x)$}\\
-$ \mathrm{Ret} \nudge F_{K_1}(x) + i\cdot \calO(x)$\\
+$\nudge$ Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
+When $A$ halts with output $\calX^{'}$: \\
+if $|\calX^{'}| < t$ or $\calX^{'} \cap \calS \neq \emptyset$ then \\
+\nudge Ret 0\\
+if $\exists x \in \calX^{'}$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
+\nudge Ret 0\\
+Ret 1\\\\
+\oracle{$\HashOracle(x)$}\\
+$ \mathrm{Ret} \nudge F_{K_1}(x) + i\cdot \calO(x)$, for $i\in[1,k]$\\
 }
@@
 %$d \getsr \bits $\\
-$\rho_2 \getsr Func(m,m)$\\
+$\rho_2 \getsr Func(U,[m])$\\
 $S \getsr \distr{U}{n}$\\
-$M \getsr \Rep^{\HashOracle(\cdot, \cdot)}(S)$\\
+$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
 When $A$ asks $\QryOracle(x)$:\\
-$\nudge$ Ret $\Qry^{\HashOracle(\cdot, \cdot)}(M,x)$\\
-When $A$ halts with output $x^{'}$: \\
-$\nudge$if $x^{'} \not\in S \wedge \Qry^{\HashOracle(\cdot, \cdot)}(M,x^{'})=1$ then\\
-$\nudge$$\nudge$ Ret 1\\
-$\nudge$Ret 0\\\\
-\oracle{$\HashOracle(i,x)$}\\
+$\nudge$ Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
+When $A$ halts with output $\calX^{'}$: \\
+if $|\calX^{'}| < t$ or $\calX^{'} \cap \calS \neq \emptyset$ then \\
+\nudge Ret 0\\
+if $\exists x \in \calX^{'}$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
+\nudge Ret 0\\
+Ret 1\\\\
+\oracle{$\HashOracle(x)$}\\
 %if $d=0$\\
-$\mathrm{Ret} \nudge \calO(x) + i\cdot \rho_2(x)$
+$\mathrm{Ret} \nudge \calO(x) + i\cdot \rho_2(x)$, for $i\in[1,k]$
 }
@@
 
+From eqns. \ref{eq:m1}, \ref{eq:m2}, \ref{eq:m3} and \ref{eq:m4},
 \begin{eqnarray}
 \nonumber \Prob{\ExpPRF{F}{B_1} = 1} &=& .5\Prob{\ExpPRF{F}{B_1}=1|b=0} + .5\Prob{\ExpPRF{F}{B_1} = 1|b=1}\\
-\nonumber (2\Prob{\ExpPRF{F}{B_1} = 1} - 1) + 1 &=& \Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1}\\
- 1 + \AdvPRF{F}{B_1} &=& \Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1} \label{eq:1}\\
+\nonumber 2\Prob{\ExpPRF{F}{B_1} = 1} &=& 1-\Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1}\\
+\nonumber (2\Prob{\ExpPRF{F}{B_1} = 1} - 1)  &=& \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1}\\
+ \AdvPRF{F}{B_1} &=& \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1} \label{eq:1}\\
 \nonumber& &\\
 \nonumber \Prob{\ExpPRF{F}{B_2} = 1} &=& .5\Prob{\ExpPRF{F}{B_2}=1|b=0} + .5\Prob{\ExpPRF{F}{B_2} = 1|b=1}\\
-\nonumber (2\Prob{\ExpPRF{F}{B_2} = 1} - 1) + 1 &=& \Prob{\game{2}(A)=1} + \Prob{\game{1}(A)=1}\\
- 1 + \AdvPRF{F}{B_2} &=& \Prob{\game{2}(A)=1} + \Prob{\game{1}(A)=1}\label{eq:2}
+\nonumber 2\Prob{\ExpPRF{F}{B_2} = 1} &=& 1-\Prob{\game{2}(A)=1} + \Prob{\game{1}(A)=1}\\
+\nonumber (2\Prob{\ExpPRF{F}{B_2} = 1} - 1)  &=& \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1}\\
+ \AdvPRF{F}{B_2} &=& \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1} \label{eq:2}
 \end{eqnarray}
 
-Subtracting \ref{eq:1} from \ref{eq:2}, we have
-\begin{eqnarray}
-\abs{ \AdvPRF{F}{B_2} - \AdvPRF{F}{B_1}} &= \abs{\Prob{\game{2}(A)=1} - \Prob{\game{0}(A)=1}}\label{eq:2a}
-\end{eqnarray}
+Adding eqn. \ref{eq:1} and \ref{eq:2}, we have
+\begin{equation}
+\AdvPRF{F}{B_2} +\AdvPRF{F}{B_1} = \Prob{\game{0}(A)=1} - \Prob{\game{2}(A)=1}\label{eq:2a}
+\end{equation}
 
@@
 \fpage{0.4}{
-$\experimentv{Adversary \nudge A^{{'}\HashOracle(\cdot, \cdot)}:}$\\
-$t \getsr [q]$, where $[q] = {0,1, \cdots, q-1}$\\
+$\experimentv{Adversary \nudge A^{{'}\HashOracle}:}$\\
+$\ell \getsr [q]$, where $[q] = {0,1, \cdots, q-1}$\\
 $count = 0$\\
-$\rho_1,\rho_2 \getsr Func(m,m)$\\
+$\rho_1,\rho_2 \getsr Func(U,[m])$\\
 $S \getsr \distr{U}{n}$\\
-$M \getsr \Rep^{\HashOracle(\cdot, \cdot)}(S)$\\
+$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
 When $A$ asks $\QryOracle(x)$:\\
 $\nudge cnt = cnt + 1$\\
-$\nudge \mathrm{if} \nudge count == t$\\
-$\nudge r \gets \Qry^{\HashOracle(\cdot, \cdot)}(M,x)$\\
-if $r==1$\\
-$\nudge$ $A$ halts with output $x$\\
-$\nudge$ Ret 1\\
-else\\
-$\nudge$ $A$ outputs NULL\\
-$\nudge$ Ret 0\\\\
+\nudge if $count == \ell$\\
+$\nudge$ $\nudge r \gets \Qry^{\HashOracle}(M,\tau,x)$\\
+\nudge else\\
+$\nudge$ $\nudge r = 0$\\
+\nudge Ret $r$\\
+When $A$ halts with output $\calX^{'}$\\
+\nudge if $|\calX^{'}| < t$ or $\calX^{'} \cap \calS \neq \emptyset$ then \\
+\nudge\nudge Ret 0\\
+\nudge if $\exists x \in \calX^{'}$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
+\nudge \nudge Ret 0\\
+\nudge Ret 1\\
 %
-\oracle{$\HashOracle(i,x)$}\\
-$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$\\
-Ret $h_i(x)$
+\oracle{$\HashOracle(x)$}\\
+$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
+Ret $\left(h_1(x),\ldots,h_k(x)\right)$
 }
@@
 \begin{eqnarray}
-\nonumber \abs{ \AdvPRF{F}{B_2} - \AdvPRF{F}{B_1}} &=& \abs{q \cdot \epsilon - \Prob{\ExpFPSecHash{B}{A}=1}}\\
-\AdvFPSecHash{B}{A} &=& \abs{ \AdvPRF{F}{B_2} - \AdvPRF{F}{B_1}} \pm q \cdot \epsilon
+\nonumber \AdvFPSecHash{B,t}{A} &-& \Prob{\game{2}(A)=1} =  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}   \\
+\nonumber \AdvFPSecHash{B,t}{A}  &=&  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} + \Prob{\game{2}(A)=1}  \\
+\AdvFPSecHash{B,t}{A} &\leq&  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  + q \cdot \epsilon
 \end{eqnarray}
 \end{proof}
+
+\clearpage
+\section{Summary of attacks(based on Bloom filter exploit) on Squid}
+\acnote{For reference}\\
+\heading{Crossby and Wallach: Squid Attack on hash tables} 
+\begin{itemize}
+\item A Squid server was ran on a stand-alone machine.
+\item A file containing a list of URL's was prepared.
+\item The URL requests were parsed and served by the Squid server. This completed the set-up phase.
+\item Crossby and Wallach targeted hash collisions in Squid to increase the average URL load time.
+The authors quote ``This attack does not represent a ''smoking gun” for algorithmic complexity attacks, but it does illustrate how common network services may be sensitive to these attacks".
+2 experiments were carried out to illustrate this.
+\item In experiment 1, around 143K random URL's were requested to the proxy server, whereas in experiment 2, same number of carefully chosen URL's that collide with the already present URL's in the hash-table were requested.
+\item Observation: The load time of random URL's was less than the chosen URL's.
+It must be noted that, the authors did not use a brute-force approach to find collisions.
+Rather,  they proposed an efficient method to find hash-collisions.
+The method involves finding a set of elements that hash to the same index and using a combination of those elements to find more elements.
+\end{itemize}
+
+\heading{Gerber et. al. : Squid attack on cache digest:}
+\begin{itemize}
+\item Squid servers follow a hierarchical model, and in this model the peers can exchange summary of their cache using Bloom filters(cache-digest). 
+\item In the set-up phase, the authors configure 2 peer Squid servers for caching and an HTTP server which responds to all queries of the Squid servers. 
+\item Peer 1's cache-digest is polluted using fake URL's. Both the peers exchange their cache-digests 
+\item Client(s) of Peer 2, start making URL requests. The URL's which are not cached by the latter are searched in its neighbors cache-digest and false positives are counted.
+\item Observation: There is a substantial increase in FP's due to pollution as compared to FP's without it.
+\item Reason: Fake URL's increase the Hamming weight of the cache digest of peer 1 and hence increase false positives.
+\end{itemize}

### 2016-07-11 intro.tex
Updated Proof of Theorem 1 as per the changed syntax and some minor corrections

@@
 To briefly summarize, a Bloom filter is a data structure for compactly representing a set~$\mathcal{S}$ in a way that supports constant-time responses to set-membership queries.
-The representation of~$\mathcal{S}$ is an bit-array~$M$ of length~$m$, all initially set to~0.
+The representation of~$\mathcal{S}$ is a bit-array~$M$ of length~$m$, all initially set to~0.
 To insert $x \in \mathcal{S}$ into~$M$, one computes indices $h_1(x),h_2(x),\ldots,h_k(x)$ where each $h_i \colon \mathcal{U} \to \{0,1,\ldots m-1\}$ maps from a universe~$\mathcal{U}$ (which contains $\mathcal{S}$) to indices of~$M$.
@@
 Bloom filters are correct, in the sense that if $y \in \mathcal{S}$, the set-membership test always returns ``yes''.
-The classical soundness condition asserts that for all $\mathcal{S}$ and any $y \notin\mathcal{S}$, we have $\Prob{h_1,h_2,\ldots,h_k \getsr \mathrm{Func}(\mathcal{U},[m])\colon M[h_1(y)]=1 \wedge \cdots \wedge M[h_k(y)]=1} \leq \epsilon$ where $\epsilon$, the false-positive rate, is a parameter of the Bloom filter.
-(The values of~$\epsilon,m,k$, and $|\mathcal{S}|$ are related in a well-known way.) NY recast this soundness condition as a game in which an adversary~$A$ is given~$\mathcal{S}$ and an oracle for set-membership queries, and it attempts to find a false positive.
+The classical soundness condition asserts that for all $\mathcal{S}$ and any $y \notin\mathcal{S}$, we have $\Prob{h_1,h_2,\ldots,h_k \getsr \mathrm{Func}(\mathcal{U},[m])\colon M[h_1(y)]=1 \wedge \cdots \wedge M[h_k(y)]=1} \leq \epsilon$ where $\epsilon$, the false-positive error, is a parameter of the Bloom filter.
+(The values of~$\epsilon,m,k$, and $|\mathcal{S}|$ are related in a well-known way.) NY recast this soundness condition as a game in which an adversary~$A$ is given~$\mathcal{S}$ and an oracle for set-membership queries, and it attempts to find one or more false positives.
 The fact that~$A$ can \emph{adapt} its queries and its output based on what it learns from the set-membership oracle (but, as we will see, not upon the hash functions) is the key definitional contribution of~NY.

### 2016-07-12 Proofs.tex
Proof Theorem2

@@
 \tsnote{Jon: ignore these for now.  This is Animesh's workspace.}
-\begin{theorem}\label{thm}
+\begin{theorem}\label{thm1}
 Fix $k, m, n > 0$ and define a hash-based filter as in section \ref{sec:hbf}, except the hash functions are defined by $h_j(x) =  F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$, where $F \colon \calK \times U \sends [m]$ is a PRF.
@@
 %\caption{Game playing argument}\label{fig:Game}
-\begin{figure}[h]
+\begin{figure}
 \fpage{.95}{
@@
 }
-\caption{Game playing argument}\label{fig:Game}
+\caption{Theorem \ref{thm1}:Game playing argument}\label{fig:Game}
 \end{figure}
@@
 %\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
-\begin{figure}[h]
+\begin{figure}
 \centering
@@
 }
-\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
+\caption{Theorem \ref{thm1}:Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
 \end{figure}
@@
 }
-\caption{Adversary $A^{'}$ simulating $\game{3}(A)$} \label{AGame3}
+\caption{Theorem \ref{thm1}:Adversary $A^{'}$ simulating $\game{3}(A)$} \label{AGame3}
 \end{figure}
@@
 
+\newcommand{\FK}{F_K(\langle j,x \rangle)}
+\newcommand{\rhoK}{\rho(\langle j,x \rangle)}
+\begin{theorem}\label{thm2}
+A hash-based filter with private hash functions $h_j(x) = \FK$ is secure in the false positive game of an adaptive adversary (A) who makes $q$ set-membership queries in time $O(t)$ , if F is PRF secure and the filter has low FP-error($\epsilon$) in the non-adaptive setting.
+Here, adversary $B$ attacks the PRF game in time $O(t)$, makes $q$ oracle queries, and
+\begin{equation}
+\AdvFPSecHash{B,t}{A} \leq  \AdvPRF{F}{B} + q \cdot \epsilon
+\end{equation}
+Note: $\FK$ provides domain separation and hence mutual independence, unlike hash functions in theorem \ref{thm1}
+\end{theorem}
+
+\acnote{Not complete yet}
+\begin{proof}
+We use a game playing argument similar to theorem \ref{thm1} to prove this theorem.
+In \game{0}(A), adversary attacks the FP game with private hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpFPSecHash{B,t}{A}$.
+\begin{equation}
+\AdvFPSecHash{B,t}{A} = \Prob{\game{0}(A)=1}\label{eq:0T2}
+\end{equation}
+\game{1}(A) simulates $\ExpFPSecHash{B,t}{A}$ with a random function $\rho \getsr Func(U,[m])$ used to generate uniformly random  hash-indices with domain separation, of elements $x \in U$.
+Let $A^{'}$ be the non-adaptive friend of $A$.
+\game{2}(A) simulates behavior of $A^{'}$ as closely as possible.
+The three games are shown in Fig.
+\ref{fig:GameT2}.
+
+%\caption{Game playing argument}\label{fig:Game}
+\begin{figure}
+\fpage{.93}{
+\hpagesssl{.3}{.3}{.3}
+{
+\underline{\game{0}(A)}\\
+$K \getsr \calK $\\
+$S \getsr \distr{U}{n}$\\
+$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
+$\calX \getsr A^{\QryOracle}(\calS)$\\
+if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
+\nudge Ret 0\\
+if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
+\nudge Ret 0\\
+Ret 1\\\\
+%
+\oracle{$\QryOracle(x)$}\\
+Ret $\Qry^{\HashOracle}(M,\tau,x)$\\\\
+%
+\oracle{$\HashOracle(x)$}\\
+$h_j(x) = \FK$, for $j\in[1,k]$\\
+Ret $\left(h_1(x),\ldots,h_k(x)\right)$
+}
+{
+\underline{\game{1}(A)}\\
+$\rho \getsr Func(U,[m])$\\
+$S \getsr \distr{U}{n}$\\
+$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
+$\calX \getsr A^{\QryOracle}(\calS)$\\
+if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
+\nudge Ret 0\\
+if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
+\nudge Ret 0\\
+Ret 1\\\\
+%
+\oracle{$\QryOracle(x)$}\\
+Ret $\Qry^{\HashOracle}(M,\tau,x)$\\\\
+%
+\oracle{$\HashOracle(x)$}\\
+$h_j(x) = \rhoK $, for $j\in[1,k]$\\
+Ret $\left(h_1(x),\ldots,h_k(x)\right)$
+}
+{
+\underline{$\game{2}(A)$}\\
+$\ell \getsr [q]$, where $[q] = {0,1, \cdots, q-1}$\\
+$count = 0$ \\%count will be used to keep track of queries made to $\QryOracle$\\
+$win \gets false$\\
+$\rho \getsr Func(U,[m])$\\
+$S \getsr \distr{U}{n}$\\
+$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
+$\calX \getsr A^{\QryOracle}(\calS)$\\
+if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
+\nudge Ret 0\\
+if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
+\nudge Ret 0\\
+Ret 1\\\\
+%
+\oracle{$\QryOracle(x)$}\\
+$count=count +1$\\
+if $(count == \ell)$\\
+$\nudge win = true$\\
+$\nudge \mathrm{Ret} \nudge \Qry^{\HashOracle}(M,\tau,x)$\\
+else \\
+$\nudge \mathrm{Ret}\nudge 0$\\\\
+%
+\oracle{$\HashOracle(x)$}\\
+$h_j(x) = \rhoK$, for $j\in[1,k]$\\
+Ret $\left(h_1(x),\ldots,h_k(x)\right)$
+}
+}
+\caption{Theorem \ref{thm2}:Game playing argument}\label{fig:GameT2}
+\end{figure}
+
+In Fig. \ref{fig:BGame1T2}, adversary $B$ simulates $\game{1}(A)$ and $\game{2}(A)$ for $b=1$ and $b=0$ respectively .
+
+%\caption{Adversary $B$ and $A^{'}$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}
+\begin{figure}
+\centering
+\fpage{0.9}{
+\hpagessl{0.5}{0.5}
+{
+$\experimentv{Adversary \nudge B^{\calO}:}$\\
+$S \getsr \distr{U}{n}$\\
+$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
+When $A$ asks $\QryOracle(x)$:\\
+$\nudge$ Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
+When $A$ halts with output $\calX^{'}$: \\
+if $|\calX^{'}| < t$ or $\calX^{'} \cap \calS \neq \emptyset$ then \\
+\nudge Ret 0\\
+if $\exists x \in \calX^{'}$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
+\nudge Ret 0\\
+Ret 1\\\\
+\oracle{$\HashOracle(x)$}\\
+$ \mathrm{Ret} \nudge \calO(\langle j,x \rangle)$, for $j\in[1,k]$\\
+}
+{
+$\experimentv{Adversary \nudge A^{'\HashOracle}:}$\\
+$\ell \getsr [q]$, where $[q] = {0,1, \cdots, q-1}$\\
+$count = 0$\\
+$\rho \getsr Func(U,[m])$\\
+$S \getsr \distr{U}{n}$\\
+$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
+When $A$ asks $\QryOracle(x)$:\\
+$\nudge cnt = cnt + 1$\\
+\nudge if $count == \ell$\\
+$\nudge$ $\nudge r \gets \Qry^{\HashOracle}(M,\tau,x)$\\
+\nudge else\\
+$\nudge$ $\nudge r = 0$\\
+\nudge Ret $r$\\
+When $A$ halts with output $\calX^{'}$\\
+\nudge if $|\calX^{'}| < t$ or $\calX^{'} \cap \calS \neq \emptyset$ then \\
+\nudge\nudge Ret 0\\
+\nudge if $\exists x \in \calX^{'}$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
+\nudge \nudge Ret 0\\
+\nudge Ret 1\\\\
+%
+\oracle{$\HashOracle(x)$}\\
+$\mathrm{Ret} \nudge \rhoK$, for $j\in[1,k]$
+}
+}
+\caption{Theorem \ref{thm2}:Adversary $B$ and $A^{'}$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively }\label{fig:BGame1T2}
+\end{figure}
+
+\begin{eqnarray}
+\Prob{\ExpPRF{F}{B} = 1|b=1} &=& \Prob{\game{0}(A)=1}\label{eq:m1T2}\\
+\Prob{\ExpPRF{F}{B} = 1|b=0} &=& 1-\Prob{\game{1}(A)=1}\label{eq:m2T2}
+\end{eqnarray}
+
+From eqns. \ref{eq:m1T2}, \ref{eq:m2T2},
+\begin{eqnarray}
+\nonumber \Prob{\ExpPRF{F}{B} = 1} &=& .5\Prob{\ExpPRF{F}{B_1}=1|b=0} + .5\Prob{\ExpPRF{F}{B_1} = 1|b=1}\\
+\nonumber 2\Prob{\ExpPRF{F}{B} = 1} &=& 1-\Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1}\\
+\nonumber (2\Prob{\ExpPRF{F}{B} = 1} - 1)  &=& \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1}\\
+ \AdvPRF{F}{B} &=& \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1} \label{eq:1T2}
+\end{eqnarray}
+
+Following a similar argument from theorem \ref{thm1},
+\begin{equation}
+\Prob{\game{1}(A)=1} \leq q \cdot \Prob{\game{2}(A)=1} = q \cdot \Prob{\game{2}(A)=1|win=true}\label{eq:3T2}
+\end{equation}
+\begin{eqnarray}
+\nonumber \Prob{\game{2}(A)|win=true} &=& \Prob{A^{'} \mathrm{outputs \nudge FP}}\\
+& \leq & \epsilon, \nudge \mathrm{where} \nudge \epsilon = (1-e^{-kn/m})^k\label{eq:4T2}
+\end{eqnarray}
+
+From eqn. \ref{eq:0T2}, \ref{eq:1T2}, \ref{eq:3T2},  and \ref{eq:4T2}: \\
+\begin{eqnarray}
+\nonumber \AdvFPSecHash{B,t}{A} &-& \Prob{\game{1}(A)=1} =  \AdvPRF{F}{B}   \\
+\nonumber \AdvFPSecHash{B,t}{A}  &=&  \AdvPRF{F}{B} + \Prob{\game{1}(A)=1}  \\
+\AdvFPSecHash{B,t}{A} &\leq&  \AdvPRF{F}{B}  + q \cdot \epsilon
+\end{eqnarray}
+
+\end{proof}
 \clearpage

### 2016-07-13 Proofs.tex
Proof Theorem3

--- 2016-07-11 Proofs.tex
@@
 \tsnote{Jon: ignore these for now.  This is Animesh's workspace.}
-\begin{theorem}\label{thm}
-Fix $k, m, n > 0$ and define a hash-based filter as in section \ref{sec:hbf}, except the hash functions are defined by $h_j(x) =  F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$, where $F \colon \calK \times U \sends [m]$ is a PRF.
-Let $Func(U,[m])$ be the set of all functions $\rho \colon \calK \times U \sends [m]$.
-Let $B_1, B_2$ be 2 adversaries attacking the PRF advantage of $F$, and $A$ be another adversary attacking the false positive game of hash-based filters with private hash functions, then
-\begin{equation}
-\AdvFPSecHash{B,t}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} + q \cdot \epsilon
-\end{equation}
-Note: Here, $q$ is the number of queries made to the $\QryOracle$ oracle and $\epsilon$ is the false positive error in the double hashing scheme given by Kirsch and Mitzenmacher.
-$\epsilon \rightarrow 0$, if $m/n \rightarrow \infty$ and/or $k \rightarrow \infty$ \cite{xxx}
-\end{theorem}
+\acnote{I will review for mistakes}
+\input{Theorem1_FP}
+\input{Theorem2_FP}
+\input{Theorem3_priv}
 
-\begin{proof}
-The proof of the theorem will use a game playing argument as shown in Fig.
-\ref{fig:Game}.
-$\game{0}(A)$ exactly simulates $\ExpFPSecHash{B,t}{A}$ with hash functions $h_j(x) =  F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$.
-So,
-\begin{equation}
-\AdvFPSecHash{B,t}{A} = \Prob{\game{0}(A)=1}\label{eq:0}
-\end{equation}
- $\game{1}(A)$ and $\game{2}(A)$ attack 2 different filters with hash functions 
-\begin{eqnarray*}
-h_j(x) &=& ( F_{K_0}(x) + j\cdot \rho_2(x)) \bmod m\\
-\mathrm{and,}\nudge h_j(x) &=& ( \rho_1(x) + j \cdot \rho_2(x)) \bmod m 
-\end{eqnarray*}
-
-Here, $\rho_1$ and $\rho_2$ are random functions sampled from $Func(U,[m])$.
-Let adversaries $B_1, B_2$ simulate $\game{1}(A)$ and $\game{2}(A)$ respectively as shown in Fig.
-\ref{fig:BGame1}.
-When $b=1$, $B_1$ and $B_2$ exactly simulate $\game{0}(A)$
-and $\game{1}(A)$. While, for $b=0$, $B_1$ wins, if $\game{1}(A)$ outputs 0, and  $B_2$ wins, if $\game{2}(A)$ returns 0.
-
-\begin{eqnarray}
-\Prob{\ExpPRF{F}{B_1} = 1|b=1} &=& \Prob{\game{0}(A)=1}\label{eq:m1}\\
-\Prob{\ExpPRF{F}{B_2} = 1|b=1} &=& \Prob{\game{1}(A)=1}\label{eq:m2}\\
-\Prob{\ExpPRF{F}{B_1} = 1|b=0} &=& 1-\Prob{\game{1}(A)=1}\label{eq:m3}\\
-\Prob{\ExpPRF{F}{B_2} = 1|b=0} &=& 1-\Prob{\game{2}(A)=1}\label{eq:m4}
-\end{eqnarray}
-
-\par{In a classical Bloom filter, adversary $A^{'}$ is non-adaptive, i.e., for some fixed $x \notin S$, $A^{'}$ targets the false-positive error conditioned on randomness of hash functions.
-But in the $\ExpFPSecHash{B,t}{A}$ game, $A$ is adaptive, as it can adapt its queries as well as its output based on response of $\QryOracle$ oracle.
-Let $A$ makes $q>t$ queries $x_1, x_2, ..., x_q$ to the $\QryOracle$ oracle.
-$\game{3}(A)$ simulates $fp-error$ game of $A^{'}$ as shown in Fig.
-\ref{fig:Game}.}
-
-%\caption{Game playing argument}\label{fig:Game}
-\begin{figure}[h]
-\fpage{.95}{
-\hpagessd{.5}{.5}
-{
-\underline{\game{0}(A)}\\
-$K_1, K_2 \getsr \calK$\\
-$S \getsr \distr{U}{n}$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
-$\calX \getsr A^{\QryOracle}(\calS)$\\
-if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
-\nudge Ret 0\\
-if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
-\nudge Ret 0\\
-Ret 1\\\\
-%
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\\\
-%
-\oracle{$\HashOracle(x)$}\\
-$h_i(x) = F_{K_1}(x)+i \cdot F_{K_2}(x)$, for $i\in[1,k]$\\
-Ret $\left(h_1(x),\ldots,h_k(x)\right)$
-}
-{
-\underline{\game{1}(A)}\\
-$K_1 \getsr \calK$\\
-$\rho \getsr Func(U,[m])$\\
-$S \getsr \distr{U}{n}$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
-$\calX \getsr A^{\QryOracle}(\calS)$\\
-if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
-\nudge Ret 0\\
-if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
-\nudge Ret 0\\
-Ret 1\\\\
-%
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\\\
-%
-\oracle{$\HashOracle(x)$}\\
-$h_i(x) = F_{K_1}(x)+i \cdot \rho(x)$, for $i\in[1,k]$\\
-Ret $\left(h_1(x),\ldots,h_k(x)\right)$
-}
-{
-\underline{\game{2}(A)}\\
-$\rho_1,\rho_2 \getsr Func(U,[m])$\\
-$S \getsr \distr{U}{n}$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
-$\calX \getsr A^{\QryOracle}(\calS)$\\
-if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
-\nudge Ret 0\\
-if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
-\nudge Ret 0\\
-Ret 1\\\\
-%
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\\\
-%
-\oracle{$\HashOracle(x)$}\\
-$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
-Ret $\left(h_1(x),\ldots,h_k(x)\right)$
-}
-{
-\underline{$\game{3}(A)$}\\
-$\ell \getsr [q]$, where $[q] = {0,1, \cdots, q-1}$\\
-$count = 0$ \\%count will be used to keep track of queries made to $\QryOracle$\\
-$win \gets false$\\
-$\rho_1,\rho_2 \getsr Func(U,[m])$\\
-$S \getsr \distr{U}{n}$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
-$\calX \getsr A^{\QryOracle}(\calS)$\\
-if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
-\nudge Ret 0\\
-if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
-\nudge Ret 0\\
-Ret 1\\\\
-%
-\oracle{$\QryOracle(x)$}\\
-$count=count +1$\\
-if $(count == \ell)$\\
-$\nudge win = true$\\
-$\nudge \mathrm{Ret} \nudge \Qry^{\HashOracle}(M,\tau,x)$\\
-else \\
-$\nudge \mathrm{Ret}\nudge 0$\\\\
-%
-\oracle{$\HashOracle(x)$}\\
-$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
-Ret $\left(h_1(x),\ldots,h_k(x)\right)$
-}
-}
-\caption{Game playing argument}\label{fig:Game}
-\end{figure}
-
-%\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
-\begin{figure}[h]
-\centering
-\fpage{0.9}{
-\hpagessl{0.5}{0.5}
-{
-$\experimentv{Adversary \nudge B_1^{\calO}:}$\\
-$K_1 \getsr \calK $\\
-$S \getsr \distr{U}{n}$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
-When $A$ asks $\QryOracle(x)$:\\
-$\nudge$ Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
-When $A$ halts with output $\calX^{'}$: \\
-if $|\calX^{'}| < t$ or $\calX^{'} \cap \calS \neq \emptyset$ then \\
-\nudge Ret 0\\
-if $\exists x \in \calX^{'}$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
-\nudge Ret 0\\
-Ret 1\\\\
-\oracle{$\HashOracle(x)$}\\
-$ \mathrm{Ret} \nudge F_{K_1}(x) + i\cdot \calO(x)$, for $i\in[1,k]$\\
-}
-{
-$\experimentv{Adversary \nudge B_2^{\calO}:}$\\
-%$d \getsr \bits $\\
-$\rho_2 \getsr Func(U,[m])$\\
-$S \getsr \distr{U}{n}$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
-When $A$ asks $\QryOracle(x)$:\\
-$\nudge$ Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
-When $A$ halts with output $\calX^{'}$: \\
-if $|\calX^{'}| < t$ or $\calX^{'} \cap \calS \neq \emptyset$ then \\
-\nudge Ret 0\\
-if $\exists x \in \calX^{'}$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
-\nudge Ret 0\\
-Ret 1\\\\
-\oracle{$\HashOracle(x)$}\\
-%if $d=0$\\
-$\mathrm{Ret} \nudge \calO(x) + i\cdot \rho_2(x)$, for $i\in[1,k]$
-}
-}
-\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
-\end{figure}
-
-From eqns. \ref{eq:m1}, \ref{eq:m2}, \ref{eq:m3} and \ref{eq:m4},
-\begin{eqnarray}
-\nonumber \Prob{\ExpPRF{F}{B_1} = 1} &=& .5\Prob{\ExpPRF{F}{B_1}=1|b=0} + .5\Prob{\ExpPRF{F}{B_1} = 1|b=1}\\
-\nonumber 2\Prob{\ExpPRF{F}{B_1} = 1} &=& 1-\Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1}\\
-\nonumber (2\Prob{\ExpPRF{F}{B_1} = 1} - 1)  &=& \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1}\\
- \AdvPRF{F}{B_1} &=& \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1} \label{eq:1}\\
-\nonumber& &\\
-\nonumber \Prob{\ExpPRF{F}{B_2} = 1} &=& .5\Prob{\ExpPRF{F}{B_2}=1|b=0} + .5\Prob{\ExpPRF{F}{B_2} = 1|b=1}\\
-\nonumber 2\Prob{\ExpPRF{F}{B_2} = 1} &=& 1-\Prob{\game{2}(A)=1} + \Prob{\game{1}(A)=1}\\
-\nonumber (2\Prob{\ExpPRF{F}{B_2} = 1} - 1)  &=& \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1}\\
- \AdvPRF{F}{B_2} &=& \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1} \label{eq:2}
-\end{eqnarray}
-
-Adding eqn. \ref{eq:1} and \ref{eq:2}, we have
-\begin{equation}
-\AdvPRF{F}{B_2} +\AdvPRF{F}{B_1} = \Prob{\game{0}(A)=1} - \Prob{\game{2}(A)=1}\label{eq:2a}
-\end{equation}
-
-In $\game{3}(A)$, assume, without loss of generality that $A$ halts with output $x$ immediately, if it asks $x$ to $\QryOracle$ and $\QryOracle$ returns $1$.
-Thus, all queries to $\QryOracle$ return 0 until the first one.
-Hence,
-
-\begin{equation}
-\Prob{\game{2}(A)=1} \leq q \cdot \Prob{\game{3}(A)=1} = q \cdot \Prob{\game{3}(A)=1|win=true}\label{eq:3}
-\end{equation}
-
-In Fig. \ref{AGame3}, adversary $A^{'}$ simulates $\game{3}(A)$. Since, adversary $A^{'}$ exactly simulates $\game{3}(A)$ conditioned on $win = true$, 
-\begin{eqnarray}
-\nonumber \Prob{\game{3}(A)|win=true} &=& \Prob{A^{'} \mathrm{outputs \nudge FP}}\\
-& \leq & \epsilon, \nudge \mathrm{where} \nudge \epsilon = (1-e^{-kn/m})^k\label{eq:4}
-\end{eqnarray}
-
-%\caption{Adversary $A^{'}$ simulating $\game{3}(A)$} \label{AGame3}
-\begin{figure}
-\centering
-\fpage{0.4}{
-$\experimentv{Adversary \nudge A^{{'}\HashOracle}:}$\\
-$\ell \getsr [q]$, where $[q] = {0,1, \cdots, q-1}$\\
-$count = 0$\\
-$\rho_1,\rho_2 \getsr Func(U,[m])$\\
-$S \getsr \distr{U}{n}$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
-When $A$ asks $\QryOracle(x)$:\\
-$\nudge cnt = cnt + 1$\\
-\nudge if $count == \ell$\\
-$\nudge$ $\nudge r \gets \Qry^{\HashOracle}(M,\tau,x)$\\
-\nudge else\\
-$\nudge$ $\nudge r = 0$\\
-\nudge Ret $r$\\
-When $A$ halts with output $\calX^{'}$\\
-\nudge if $|\calX^{'}| < t$ or $\calX^{'} \cap \calS \neq \emptyset$ then \\
-\nudge\nudge Ret 0\\
-\nudge if $\exists x \in \calX^{'}$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
-\nudge \nudge Ret 0\\
-\nudge Ret 1\\
-%
-\oracle{$\HashOracle(x)$}\\
-$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
-Ret $\left(h_1(x),\ldots,h_k(x)\right)$
-}
-\caption{Adversary $A^{'}$ simulating $\game{3}(A)$} \label{AGame3}
-\end{figure}
-
-From eqn. \ref{eq:0}, \ref{eq:2a}, \ref{eq:3} and \ref{eq:4}: \\
-\begin{eqnarray}
-\nonumber \AdvFPSecHash{B,t}{A} &-& \Prob{\game{2}(A)=1} =  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}   \\
-\nonumber \AdvFPSecHash{B,t}{A}  &=&  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} + \Prob{\game{2}(A)=1}  \\
-\AdvFPSecHash{B,t}{A} &\leq&  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  + q \cdot \epsilon
-\end{eqnarray}
-\end{proof}
-
-\clearpage
 \section{Summary of attacks(based on Bloom filter exploit) on Squid}

### 2016-07-13 Theorem1_FP.tex
Added missing files

\begin{theorem}\label{thm1}
Fix $k, m, n > 0$ and define a hash-based filter as in section \ref{sec:hbf}, except the hash functions are defined by $h_j(x) =  F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$, where $F \colon \calK \times U \sends [m]$ is a PRF. Let $Func(U,[m])$ be the set of all functions $\rho \colon \calK \times U \sends [m]$. Let $B_1, B_2$ be 2 adversaries attacking the PRF advantage of $F$, and $A$ be another adversary attacking the false positive game of hash-based filters with private hash functions, then 
\begin{equation}
\AdvFPSecHash{B,t}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} + q \cdot \epsilon
\end{equation}
Note: Here, $q$ is the number of queries made to the $\QryOracle$ oracle and $\epsilon$ is the false positive error in the double hashing scheme given by Kirsch and Mitzenmacher. $\epsilon \rightarrow 0$, if $m/n \rightarrow \infty$ and/or $k \rightarrow \infty$ \cite{xxx}
\end{theorem}

\begin{proof}
The proof of the theorem will use a game playing argument as shown in Fig. \ref{fig:Game}. $\game{0}(A)$ exactly simulates $\ExpFPSecHash{B,t}{A}$ with hash functions $h_j(x) =  F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$. So,
\begin{equation}
\AdvFPSecHash{B,t}{A} = \Prob{\game{0}(A)=1}\label{eq:0}
\end{equation}
 $\game{1}(A)$ and $\game{2}(A)$ attack 2 different filters with hash functions 
\begin{eqnarray*}
h_j(x) &=& ( F_{K_0}(x) + j\cdot \rho_2(x)) \bmod m\\
\mathrm{and,}\nudge h_j(x) &=& ( \rho_1(x) + j \cdot \rho_2(x)) \bmod m 
\end{eqnarray*}

Here, $\rho_1$ and $\rho_2$ are random functions sampled from $Func(U,[m])$. Let adversaries $B_1, B_2$ simulate $\game{1}(A)$ and $\game{2}(A)$ respectively as shown in Fig. \ref{fig:BGame1}. When $b=1$, $B_1$ and $B_2$ exactly simulate $\game{0}(A)$
and $\game{1}(A)$. While, for $b=0$, $B_1$ wins, if $\game{1}(A)$ outputs 0, and  $B_2$ wins, if $\game{2}(A)$ returns 0.

\begin{eqnarray}
\Prob{\ExpPRF{F}{B_1} = 1|b=1} &=& \Prob{\game{0}(A)=1}\label{eq:m1}\\
\Prob{\ExpPRF{F}{B_2} = 1|b=1} &=& \Prob{\game{1}(A)=1}\label{eq:m2}\\
\Prob{\ExpPRF{F}{B_1} = 1|b=0} &=& 1-\Prob{\game{1}(A)=1}\label{eq:m3}\\
\Prob{\ExpPRF{F}{B_2} = 1|b=0} &=& 1-\Prob{\game{2}(A)=1}\label{eq:m4}
\end{eqnarray}

\par{In a classical Bloom filter, adversary $A^{'}$ is non-adaptive, i.e., for some fixed $x \notin S$, $A^{'}$ targets the false-positive error conditioned on randomness of hash functions. But in the $\ExpFPSecHash{B,t}{A}$ game, $A$ is adaptive, as it can adapt its queries as well as its output based on response of $\QryOracle$ oracle. Let $A$ makes $q>t$ queries $x_1, x_2, ..., x_q$ to the $\QryOracle$ oracle. $\game{3}(A)$ simulates $fp-error$ game of $A^{'}$ as shown in Fig. \ref{fig:Game}.}

%\caption{Game playing argument}\label{fig:Game}
\begin{figure}
\fpage{.95}{
\hpagessd{.5}{.5}
{
\underline{\game{0}(A)}\\
$K_1, K_2 \getsr \calK$\\
$S \getsr \distr{U}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
$\calX \getsr A^{\QryOracle}(\calS)$\\
if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,\tau,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = F_{K_1}(x)+i \cdot F_{K_2}(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{\game{1}(A)}\\
$K_1 \getsr \calK$\\
$\rho \getsr Func(U,[m])$\\
$S \getsr \distr{U}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
$\calX \getsr A^{\QryOracle}(\calS)$\\
if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,\tau,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = F_{K_1}(x)+i \cdot \rho(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{\game{2}(A)}\\
$\rho_1,\rho_2 \getsr Func(U,[m])$\\
$S \getsr \distr{U}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
$\calX \getsr A^{\QryOracle}(\calS)$\\
if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,\tau,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{$\game{3}(A)$}\\
$\ell \getsr [q]$, where $[q] = {0,1, \cdots, q-1}$\\
$count = 0$ \\%count will be used to keep track of queries made to $\QryOracle$\\
$win \gets false$\\
$\rho_1,\rho_2 \getsr Func(U,[m])$\\
$S \getsr \distr{U}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
$\calX \getsr A^{\QryOracle}(\calS)$\\
if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
$count=count +1$\\
if $(count == \ell)$\\
$\nudge win = true$\\
$\nudge \mathrm{Ret} \nudge \Qry^{\HashOracle}(M,\tau,x)$\\
else \\
$\nudge \mathrm{Ret}\nudge 0$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
}
\caption{Theorem \ref{thm1}:Game playing argument}\label{fig:Game}
\end{figure}

%\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
\begin{figure}
\centering
\fpage{0.9}{
\hpagessl{0.5}{0.5}
{
$\experimentv{Adversary \nudge B_1^{\calO}:}$\\
$K_1 \getsr \calK $\\
$S \getsr \distr{U}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge$ Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
When $A$ halts with output $\calX^{'}$: \\
if $|\calX^{'}| < t$ or $\calX^{'} \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists x \in \calX^{'}$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
\oracle{$\HashOracle(x)$}\\
$ \mathrm{Ret} \nudge F_{K_1}(x) + i\cdot \calO(x)$, for $i\in[1,k]$\\
}
{
$\experimentv{Adversary \nudge B_2^{\calO}:}$\\
%$d \getsr \bits $\\
$\rho_2 \getsr Func(U,[m])$\\
$S \getsr \distr{U}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge$ Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
When $A$ halts with output $\calX^{'}$: \\
if $|\calX^{'}| < t$ or $\calX^{'} \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists x \in \calX^{'}$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
\oracle{$\HashOracle(x)$}\\
%if $d=0$\\
$\mathrm{Ret} \nudge \calO(x) + i\cdot \rho_2(x)$, for $i\in[1,k]$
}
}
\caption{Theorem \ref{thm1}:Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
\end{figure}

From eqns. \ref{eq:m1}, \ref{eq:m2}, \ref{eq:m3} and \ref{eq:m4},
\begin{eqnarray}
\nonumber \Prob{\ExpPRF{F}{B_1} = 1} &=& .5\Prob{\ExpPRF{F}{B_1}=1|b=0} + .5\Prob{\ExpPRF{F}{B_1} = 1|b=1}\\
\nonumber 2\Prob{\ExpPRF{F}{B_1} = 1} &=& 1-\Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1}\\
\nonumber (2\Prob{\ExpPRF{F}{B_1} = 1} - 1)  &=& \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1}\\
 \AdvPRF{F}{B_1} &=& \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1} \label{eq:1}\\
\nonumber& &\\
\nonumber \Prob{\ExpPRF{F}{B_2} = 1} &=& .5\Prob{\ExpPRF{F}{B_2}=1|b=0} + .5\Prob{\ExpPRF{F}{B_2} = 1|b=1}\\
\nonumber 2\Prob{\ExpPRF{F}{B_2} = 1} &=& 1-\Prob{\game{2}(A)=1} + \Prob{\game{1}(A)=1}\\
\nonumber (2\Prob{\ExpPRF{F}{B_2} = 1} - 1)  &=& \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1}\\
 \AdvPRF{F}{B_2} &=& \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1} \label{eq:2}
\end{eqnarray}

Adding eqn. \ref{eq:1} and \ref{eq:2}, we have
\begin{equation}
\AdvPRF{F}{B_2} +\AdvPRF{F}{B_1} = \Prob{\game{0}(A)=1} - \Prob{\game{2}(A)=1}\label{eq:2a}
\end{equation}

In $\game{3}(A)$, assume, without loss of generality that $A$ halts with output $x$ immediately, if it asks $x$ to $\QryOracle$ and $\QryOracle$ returns $1$. Thus, all queries to $\QryOracle$ return 0 until the first one. Hence,

\begin{equation}
\Prob{\game{2}(A)=1} \leq q \cdot \Prob{\game{3}(A)=1} = q \cdot \Prob{\game{3}(A)=1|win=true}\label{eq:3}
\end{equation}

In Fig. \ref{AGame3}, adversary $A^{'}$ simulates $\game{3}(A)$. Since, adversary $A^{'}$ exactly simulates $\game{3}(A)$ conditioned on $win = true$, 
\begin{eqnarray}
\nonumber \Prob{\game{3}(A)|win=true} &=& \Prob{A^{'} \mathrm{outputs \nudge FP}}\\
& \leq & \epsilon, \nudge \mathrm{where} \nudge \epsilon = (1-e^{-kn/m})^k\label{eq:4}
\end{eqnarray}

%\caption{Adversary $A^{'}$ simulating $\game{3}(A)$} \label{AGame3}
\begin{figure}
\centering
\fpage{0.4}{
$\experimentv{Adversary \nudge A^{{'}\HashOracle}:}$\\
$\ell \getsr [q]$, where $[q] = {0,1, \cdots, q-1}$\\
$count = 0$\\
$\rho_1,\rho_2 \getsr Func(U,[m])$\\
$S \getsr \distr{U}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge count = count + 1$\\
\nudge if $count == \ell$\\
$\nudge$ $\nudge r \gets \Qry^{\HashOracle}(M,\tau,x)$\\
\nudge else\\
$\nudge$ $\nudge r = 0$\\
\nudge Ret $r$\\
When $A$ halts with output $\calX^{'}$\\
\nudge if $|\calX^{'}| < t$ or $\calX^{'} \cap \calS \neq \emptyset$ then \\
\nudge\nudge Ret 0\\
\nudge if $\exists x \in \calX^{'}$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge \nudge Ret 0\\
\nudge Ret 1\\
%
\oracle{$\HashOracle(x)$}\\
$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
\caption{Theorem \ref{thm1}:Adversary $A^{'}$ simulating $\game{3}(A)$} \label{AGame3}
\end{figure}

From eqn. \ref{eq:0}, \ref{eq:2a}, \ref{eq:3} and \ref{eq:4}: \\
\begin{eqnarray}
\nonumber \AdvFPSecHash{B,t}{A} &-& \Prob{\game{2}(A)=1} =  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}   \\
\nonumber \AdvFPSecHash{B,t}{A}  &=&  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} + \Prob{\game{2}(A)=1}  \\
\AdvFPSecHash{B,t}{A} &\leq&  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  + q \cdot \epsilon
\end{eqnarray}
\end{proof}

\clearpage

### 2016-07-13 Theorem2_FP.tex
Added missing files

\newcommand{\FK}{F_K(\langle j,x \rangle)}
\newcommand{\rhoK}{\rho(\langle j,x \rangle)}

\begin{theorem}\label{thm2}
A hash-based filter with private hash functions $h_j(x) = \FK$ is secure in the false positive game of an adaptive adversary (A) who makes $q$ set-membership queries in time $O(t)$ , if F is PRF secure and the filter has low FP-error($\epsilon$) in the non-adaptive setting. Here, adversary $B$ attacks the PRF game in time $O(t)$, makes $q$ oracle queries, and 
\begin{equation}
\AdvFPSecHash{B,t}{A} \leq  \AdvPRF{F}{B} + q \cdot \epsilon
\end{equation}
Note: $\FK$ provides domain separation and hence mutual independence, unlike hash functions in theorem \ref{thm1}
\end{theorem}

\begin{proof}
We use a game playing argument similar to theorem \ref{thm1} to prove this theorem. In \game{0}(A), adversary attacks the FP game with private hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpFPSecHash{B,t}{A}$.
\begin{equation}
\AdvFPSecHash{B,t}{A} = \Prob{\game{0}(A)=1}\label{eq:0T2}
\end{equation}
\game{1}(A) simulates $\ExpFPSecHash{B,t}{A}$ with a random function $\rho \getsr Func(U,[m])$ used to generate uniformly random  hash-indices with domain separation, of elements $x \in U$. Let $A^{'}$ be the non-adaptive friend of $A$. \game{2}(A) simulates behavior of $A^{'}$ as closely as possible. The three games are shown in Fig. \ref{fig:GameT2}.

%\caption{Game playing argument}\label{fig:Game}
\begin{figure}
\fpage{.99}{
\hpagesssl{.34}{.34}{.31}
{
\underline{\game{0}(A)}\\
$K \getsr \calK $\\
$S \getsr \distr{U}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
$\calX \getsr A^{\QryOracle}(\calS)$\\
if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,\tau,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_j(x) = \FK$, for $j\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{\game{1}(A)}\\
$\rho \getsr Func(U,[m])$\\
$S \getsr \distr{U}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
$\calX \getsr A^{\QryOracle}(\calS)$\\
if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,\tau,x)$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_j(x) = \rhoK $, for $j\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
{
\underline{$\game{2}(A)$}\\
$\ell \getsr [q]$, where $[q] = {0,1, \cdots, q-1}$\\
$count = 0$ \\%count will be used to keep track of queries made to $\QryOracle$\\
$win \gets false$\\
$\rho \getsr Func(U,[m])$\\
$S \getsr \distr{U}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
$\calX \getsr A^{\QryOracle}(\calS)$\\
if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$\\
\nudge Ret 0\\
Ret 1\\\\
%
\oracle{$\QryOracle(x)$}\\
$count=count +1$\\
if $(count == \ell)$\\
$\nudge win = true$\\
$\nudge \mathrm{Ret} \nudge \Qry^{\HashOracle}(M,\tau,x)$\\
else \\
$\nudge \mathrm{Ret}\nudge 0$\\\\
%
\oracle{$\HashOracle(x)$}\\
$h_j(x) = \rhoK$, for $j\in[1,k]$\\
Ret $\left(h_1(x),\ldots,h_k(x)\right)$
}
}
\caption{Theorem \ref{thm2}:Game playing argument}\label{fig:GameT2}
\end{figure}

In Fig. \ref{fig:BGame1T2}, adversary $B$ simulates $\game{1}(A)$ and $\game{2}(A)$ for $b=1$ and $b=0$ respectively .

%\caption{Adversary $B$ and $A^{'}$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}
\begin{figure}
\centering
\fpage{0.9}{
\hpagessl{0.5}{0.5}
{
$\experimentv{Adversary \nudge B^{\calO}:}$\\
$S \getsr \distr{U}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge$ Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
When $A$ halts with output $\calX^{'}$: \\
if $|\calX^{'}| < t$ or $\calX^{'} \cap \calS \neq \emptyset$ then \\
\nudge Ret 0\\
if $\exists x \in \calX^{'}$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge Ret 0\\
Ret 1\\\\
\oracle{$\HashOracle(x)$}\\
$ \mathrm{Ret} \nudge \calO(\langle j,x \rangle)$, for $j\in[1,k]$\\
}
{
$\experimentv{Adversary \nudge A^{'\HashOracle}:}$\\
$\ell \getsr [q]$, where $[q] = {0,1, \cdots, q-1}$\\
$count = 0$\\
$\rho \getsr Func(U,[m])$\\
$S \getsr \distr{U}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
When $A$ asks $\QryOracle(x)$:\\
$\nudge cnt = cnt + 1$\\
\nudge if $count == \ell$\\
$\nudge$ $\nudge r \gets \Qry^{\HashOracle}(M,\tau,x)$\\
\nudge else\\
$\nudge$ $\nudge r = 0$\\
\nudge Ret $r$\\
When $A$ halts with output $\calX^{'}$\\
\nudge if $|\calX^{'}| < t$ or $\calX^{'} \cap \calS \neq \emptyset$ then \\
\nudge\nudge Ret 0\\
\nudge if $\exists x \in \calX^{'}$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
\nudge \nudge Ret 0\\
\nudge Ret 1\\\\
%
\oracle{$\HashOracle(x)$}\\
$\mathrm{Ret} \nudge \rhoK$, for $j\in[1,k]$
}
}
\caption{Theorem \ref{thm2}:Adversary $B$ and $A^{'}$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively }\label{fig:BGame1T2}
\end{figure}

\begin{eqnarray}
\Prob{\ExpPRF{F}{B} = 1|b=1} &=& \Prob{\game{0}(A)=1}\label{eq:m1T2}\\
\Prob{\ExpPRF{F}{B} = 1|b=0} &=& 1-\Prob{\game{1}(A)=1}\label{eq:m2T2}
\end{eqnarray}

From eqns. \ref{eq:m1T2}, \ref{eq:m2T2},
\begin{eqnarray}
\nonumber \Prob{\ExpPRF{F}{B} = 1} &=& .5\Prob{\ExpPRF{F}{B_1}=1|b=0} + .5\Prob{\ExpPRF{F}{B_1} = 1|b=1}\\
\nonumber 2\Prob{\ExpPRF{F}{B} = 1} &=& 1-\Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1}\\
\nonumber (2\Prob{\ExpPRF{F}{B} = 1} - 1)  &=& \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1}\\
 \AdvPRF{F}{B} &=& \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1} \label{eq:1T2}
\end{eqnarray}

Following a similar argument from theorem \ref{thm1},
\begin{equation}
\Prob{\game{1}(A)=1} \leq q \cdot \Prob{\game{2}(A)=1} = q \cdot \Prob{\game{2}(A)=1|win=true}\label{eq:3T2}
\end{equation}
\begin{eqnarray}
\nonumber \Prob{\game{2}(A)|win=true} &=& \Prob{A^{'} \mathrm{outputs \nudge FP}}\\
& \leq & \epsilon, \nudge \mathrm{where} \nudge \epsilon = (1-e^{-kn/m})^k\label{eq:4T2}
\end{eqnarray}

From eqn. \ref{eq:0T2}, \ref{eq:1T2}, \ref{eq:3T2},  and \ref{eq:4T2}: \\
\begin{eqnarray}
\nonumber \AdvFPSecHash{B,t}{A} &-& \Prob{\game{1}(A)=1} =  \AdvPRF{F}{B}   \\
\nonumber \AdvFPSecHash{B,t}{A}  &=&  \AdvPRF{F}{B} + \Prob{\game{1}(A)=1}  \\
\AdvFPSecHash{B,t}{A} &\leq&  \AdvPRF{F}{B}  + q \cdot \epsilon
\end{eqnarray}

\end{proof}

### 2016-07-13 Theorem3_priv.tex
Added missing files

\begin{theorem}\label{thm3}
A classsic Bloom filter is private in random oracle model(ROM), i.e. an adaptive adversary $A$ has low probability of winning the $\ExpPrivPubHashBB{B}{\distr{U}{n},A}$ game in ROM. For $q$ queries and min-entropy ($\mu$) of $\distr{U}{n}$,

\begin{equation}
\AdvPrivPubHashBB{B}{A} \leq  \frac{q}{2^\mu} + \frac{n}{\abs{U}}
\end{equation}

\end{theorem}

\begin{proof}
As shown in Fig. \ref{fig:GameT3}, $\game{0}(A)$ and $\game{1}(A)$ exactly simulate $\ExpPrivPubHashBB{B}{\distr{U}{n}, A}$ in ROM, except in $\game{1}(A)$, the random oracle always returns $k$ uniformly random values for any $x \in U$.
\begin{equation}
\AdvPrivPubHashBB{B}{A} = \Prob{\game{0}(A)=1}\label{eq:0T3}
\end{equation}
%\caption{Game playing argument}\label{fig:Game}
\begin{figure}
\centering
\fpage{.6}{
\hpagess{.4}{.45}
{
$\game{1}(A)$\\
\fbox{$\game{0}(A)$\\
}
$\\ \calS \getsr \distr{U}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
$x \getsr A^{\MemOracle,\QryOracle,\HashOracle}(M)$\\
if $x\in \calS$ then Ret 1\\
Ret 0
}
%
{
\oracle{$\MemOracle(x)$}\\
Ret $[x \in \calS]$\\

\medskip
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,\tau,x)$\\

\medskip
\oracle{$\HashOracle(x)$}\\
$\rho_i \getsr Func(U,[m]), \mathrm{for} \nudge i \in [1,k]$\\
$z_{i} \gets \rho_i(x), \mathrm{for} \nudge i \in [1,k]$\\
if $T[x] \neq $ undefined\\
\nudge Bad $\gets$ true\\
\fbox{
$z_i \gets T[x], \mathrm{for} \nudge i \in [1,k]$
}
$\\T[x] \gets z_i, \mathrm{for} \nudge i \in [1,k]$\\
Ret $z_i, \mathrm{for} \nudge i \in [1,k]$
}
}
\caption{Theorem \ref{thm3}: Game playing argument}\label{fig:GameT3}
\end{figure}
It is evident from $\game{0}(A)$ and $\game{1}(A)$ that 
\begin{equation}
\Prob{\game{0}(A) : \mathrm{Bad}=\mathrm{true}} = \Prob{\game{1}(A) : \mathrm{Bad}=\mathrm{true}}\label{eq:1T3}
\end{equation}
Using fundamental lemma of game playing argument and eqn. \ref{eq:1T3}
\begin{eqnarray}
\nonumber \Prob{\game{0}(A)=1} & \leq & \Prob{\game{0}(A)=1 | \mathrm{Bad} \neq \mathrm{true}} + \Prob{\game{0}(A) : \mathrm{Bad}=\mathrm{true}}\\
&=& \Prob{\game{1}(A)=1} + \Prob{\game{1}(A) : \mathrm{Bad}=\mathrm{true}}\label{eq:2T3}
\end{eqnarray}

Let the random oracle be modified to output $k$ uniformly random values without setting any Bad flag. Let's call it $\game{2}(A)$ which is shown in Fig. \ref{fig:Game2T3}. It turns out that the  $\QryOracle$ is no more deterministic due to coins of the random oracle. Hence, the results of the $q$ queries by $A$ are mutually independent and random. So, neglecting the output of $A$, the game samples one of the elements queried by $A$, and returns 1/0.

\begin{equation}
\Prob{\game{2}(A)=1} = \frac{q}{2^\mu}\label{eq:3T3}
\end{equation}

\begin{figure}
\centering
\fpage{.6}{
\hpagess{.5}{.5}
{
\underline{$\game{2}(A)$}\\
$\calX \gets \emptyset$\\
$\calS \getsr \distr{U}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
$x^{'} \gets A^{\MemOracle,\QryOracle,\HashOracle}(M)$\\
$x \getsr \calX$\\
if $x\in \calS $ then Ret 1\\
Ret 0
}
%
{
\oracle{$\MemOracle(x)$}\\
Ret $[x \in \calS]$\\

\medskip
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,\tau,x)$\\

\medskip
\oracle{$\HashOracle(x)$}\\
$\calX \gets \calX \cup x$\\ 
$\rho_i \getsr Func(U,[m]), \mathrm{for} \nudge i \in [1,k]$\\
$z_i \gets \rho_i(x), \mathrm{for} \nudge i \in [1,k]$\\
Ret $z_i, \mathrm{for} \nudge i \in [1,k]$
}
}
\caption{Theorem \ref{thm3}: Game playing argument}\label{fig:Game2T3}
\end{figure}

In $\game{1}(A)$, $T[x]\neq$ undefined, if earlier $\Rep$ asked hash-indices of $x$. So,  Bad $\gets$ true if $A$ queries an element present in $\calS$. 
\begin{equation}
\Prob{\game{1}(A):\mathrm{Bad} = \mathrm{true}} = \frac{n}{\abs{U}}\label{eq:4T3}
\end{equation}

From eqn. \ref{eq:0T3}, \ref{eq:1T3}, \ref{eq:2T3}, \ref{eq:3T3} and \ref{eq:4T3}

\begin{equation}
\AdvPrivPubHashBB{B}{A} \leq  \frac{q}{2^\mu} + \frac{n}{\abs{U}}
\end{equation}

\end{proof}

### 2016-07-13 Theorem1_FP.tex
cleaning up theorem 1

@@
+\heading{Linear-PRF construction. }
+Here we consider a hash-based filter that was attacked by Neidermayer et al.
+in~\cite{xxx}.
+Let $B_{\mathrm{lin}}=(\Hash,\Rep,\Qry)$ be defined as follows.
+Fix non-empty sets~$\univ, \univ$ and integers $k,m>0$.
+Let $F\colon\mathcal{K} \times \univ \to [m]$ be a function family.
+The $\Hash$ algorithm samples two keys $K_0,K_1 \getsr \mathcal{K}$ and defines $h_j(x) = F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$ for $j \in [k]$.
+The $\Rep$ and $\Qry$ algorithms are the standard (determinisitic) BF ones.
+\tsnote{Should define these someplace.}  The following result shows, informally, that if~$F$ is a good PRF and the (non-adaptive) FP rate is sufficiently small, then $B_\mathrm{lin}$ is secure against adaptive FP-finding adversaries.
+
 \begin{theorem}\label{thm1}
-Fix $k, m, n > 0$ and define a hash-based filter as in section \ref{sec:hbf}, except the hash functions are defined by $h_j(x) =  F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$, where $F \colon \calK \times U \sends [m]$ is a PRF.
-Let $Func(U,[m])$ be the set of all functions $\rho \colon \calK \times U \sends [m]$.
-Let $B_1, B_2$ be 2 adversaries attacking the PRF advantage of $F$, and $A$ be another adversary attacking the false positive game of hash-based filters with private hash functions, then
-\begin{equation}
-\AdvFPSecHash{B,t}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} + q \cdot \epsilon
-\end{equation}
-Note: Here, $q$ is the number of queries made to the $\QryOracle$ oracle and $\epsilon$ is the false positive error in the double hashing scheme given by Kirsch and Mitzenmacher.
-$\epsilon \rightarrow 0$, if $m/n \rightarrow \infty$ and/or $k \rightarrow \infty$ \cite{xxx}
+Fix $k,m,n>0$, and let $B_\mathrm{lin}=(\Hash,\Rep,\Qry)$ be the hash-based filter just described. 
+Let~$A$ be an adversary, compatible with $\ExpFPSecHash{B_\mathrm{lin},t}{\cdot}$, that asks at most~$q$ queries to its $\QryOracle$ oracle.  Then there exist adversaries~$B_1$ and $B_2$ such that
+\[
+\AdvFPSecHash{B_{\mathrm{lin}},t}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} + q \cdot  (1-e^{-kn/m})^k
+\]
 \end{theorem}
-
-\begin{proof}
+Before giving the proof, we note that  $(1-e^{-kn/m})^k \rightarrow 0$ as the ratio between the bit-length of the representation~$M$ and the size of the represented set~$S$, i.e.,$m/n$ tends to $\infty$.
+\begin{proof}[Theorem~\ref{thm1}]
 The proof of the theorem will use a game playing argument as shown in Fig.
@@
 \begin{equation}
-\AdvFPSecHash{B,t}{A} = \Prob{\game{0}(A)=1}\label{eq:0}
+\AdvFPSecHash{B_{\mathrm{lin}},t}{A} = \Prob{\game{0}(A)=1}\label{eq:0}
 \end{equation}
@@
 
-Here, $\rho_1$ and $\rho_2$ are random functions sampled from $Func(U,[m])$.
+Here, $\rho_1$ and $\rho_2$ are random functions sampled from $Func(\univ,[m])$.
 Let adversaries $B_1, B_2$ simulate $\game{1}(A)$ and $\game{2}(A)$ respectively as shown in Fig.
@@
 $K_1, K_2 \getsr \calK$\\
-$S \getsr \distr{U}{n}$\\
+$S \getsr \distr{\univ}{n}$\\
 $(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
@@
 $K_1 \getsr \calK$\\
-$\rho \getsr Func(U,[m])$\\
-$S \getsr \distr{U}{n}$\\
+$\rho \getsr Func(\univ,[m])$\\
+$S \getsr \distr{\univ}{n}$\\
 $(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
@@
 \underline{\game{2}(A)}\\
-$\rho_1,\rho_2 \getsr Func(U,[m])$\\
-$S \getsr \distr{U}{n}$\\
+$\rho_1,\rho_2 \getsr Func(\univ,[m])$\\
+$S \getsr \distr{\univ}{n}$\\
 $(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
@@
 $win \gets false$\\
-$\rho_1,\rho_2 \getsr Func(U,[m])$\\
-$S \getsr \distr{U}{n}$\\
+$\rho_1,\rho_2 \getsr Func(\univ,[m])$\\
+$S \getsr \distr{\univ}{n}$\\
 $(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
@@
 $K_1 \getsr \calK $\\
-$S \getsr \distr{U}{n}$\\
+$S \getsr \distr{\univ}{n}$\\
 $(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
@@
 %$d \getsr \bits $\\
-$\rho_2 \getsr Func(U,[m])$\\
-$S \getsr \distr{U}{n}$\\
+$\rho_2 \getsr Func(\univ,[m])$\\
+$S \getsr \distr{\univ}{n}$\\
 $(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
@@
 $count = 0$\\
-$\rho_1,\rho_2 \getsr Func(U,[m])$\\
-$S \getsr \distr{U}{n}$\\
+$\rho_1,\rho_2 \getsr Func(\univ,[m])$\\
+$S \getsr \distr{\univ}{n}$\\
 $(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\

### 2016-07-13 filters-syntax.tex
Updated Proof of Theorem 1 as per the changed syntax and some minor corrections
cleaning up theorem 1

@@
 \heading{Preliminaries.}
-When~$U$ is a set and $n>0$ is an integer, we let $[U]^n$ denote the set of all size-$n$ subsets of~$U$.
-We write $x \getsr U$ to denote sampling an element from~$U$ and assigning this to~$x$, and we extend this notation to randomized algorithms.
+When~$\univ$ is a set and $n>0$ is an integer, we let $[\univ]^n$ denote the set of all size-$n$ subsets of~$\univ$.
+We write $x \getsr \univ$ to denote sampling an element from~$\univ$ and assigning this to~$x$, and we extend this notation to randomized algorithms.
 
 \heading{Syntax.}
-Fix a nonempty sets $U,\Sigma$ and integers $k,m,n>0$.  Fix a symbol $\bot \not\in U$. An $(n,k,m)$-filter (over universe~$U$) is a tuple $B=(\Hash,\Rep,\Qry)$.
+Fix nonempty sets $\univ,\Sigma$ and integers $k,m,n>0$.  Fix a symbol $\bot \not\in \univ$. An $(n,k,m)$-filter (over universe~$\univ$) is a tuple $B=(\Hash,\Rep,\Qry)$.
 %
-The randomized \emph{hash-sampling} algorithm~$\Hash$ samples a size~$k$ family of functions~$\mathcal{H}=\{h_1,h_2,\ldots,h_k\}$ where each $h_i \in \mathrm{Func}(U,[m])$.  
+The randomized \emph{hash-sampling} algorithm~$\Hash$ samples a size~$k$ family of functions~$\mathcal{H}=\{h_1,h_2,\ldots,h_k\}$ where each $h_i \in \mathrm{Func}(\univ,[m])$.  
 \jnote{This doesn't seem to work super-well with the random oracle model.} 
@@
 %
-The randomized representation algorithm $\Rep\colon [U]^n \rightarrow \Sigma^m \times \bits^*$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m$ along with (possibly empty) side-information~$\tau$.
+The randomized representation algorithm $\Rep\colon [\univ]^n \rightarrow \Sigma^m \times \bits^*$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m$ along with (possibly empty) side-information~$\tau$.
 %
-The deterministic query algorithm $\Qry\colon \Sigma^m \times \bits^* \times U \rightarrow \bits$ takes a representation $M$, side-information~$\tau$, and an element $x \in U$, and returns a bit.
+The deterministic query algorithm $\Qry\colon \Sigma^m \times \bits^* \times \univ \rightarrow \bits$ takes a representation $M$, side-information~$\tau$, and an element $x \in \univ$, and returns a bit.
 %

### 2016-07-14 Theorem1_FP.tex
cleaning up theorem 1

@@
 Before giving the proof, we note that  $(1-e^{-kn/m})^k \rightarrow 0$ as the ratio between the bit-length of the representation~$M$ and the size of the represented set~$S$, i.e.,$m/n$ tends to $\infty$.
+%
 \begin{proof}[Theorem~\ref{thm1}]
@@
 \begin{eqnarray}
-\Prob{\ExpPRF{F}{B_1} = 1|b=1} &=& \Prob{\game{0}(A)=1}\label{eq:m1}\\
-\Prob{\ExpPRF{F}{B_2} = 1|b=1} &=& \Prob{\game{1}(A)=1}\label{eq:m2}\\
-\Prob{\ExpPRF{F}{B_1} = 1|b=0} &=& 1-\Prob{\game{1}(A)=1}\label{eq:m3}\\
-\Prob{\ExpPRF{F}{B_2} = 1|b=0} &=& 1-\Prob{\game{2}(A)=1}\label{eq:m4}
+\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=1} &=& \Prob{\game{0}(A)=1}\label{eq:m1}\\
+\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=1} &=& \Prob{\game{1}(A)=1}\label{eq:m2}\\
+\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=0} &=& 1-\Prob{\game{1}(A)=1}\label{eq:m3}\\
+\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=0} &=& 1-\Prob{\game{2}(A)=1}\label{eq:m4}
 \end{eqnarray}
@@
 \begin{figure}
-\fpage{.95}{
-\hpagessd{.5}{.5}
+\fpage{.9}{
+\hpagessl{.45}{.5}
 {
@@
 $K_1 \getsr \calK$\\
-$\rho \getsr Func(\univ,[m])$\\
+$\rho \getsr \Func{\univ,[m]}$\\
 $S \getsr \distr{\univ}{n}$\\
@@
 }
+}
+\fpage{.9}{
+\hpagessl{.45}{.5}
 {
 \underline{\game{2}(A)}\\
-$\rho_1,\rho_2 \getsr Func(\univ,[m])$\\
+$\rho_1,\rho_2 \getsr \Func{\univ,[m]}$\\
 $S \getsr \distr{\univ}{n}$\\
@@
 $count = 0$ \\%count will be used to keep track of queries made to $\QryOracle$\\
-$win \gets false$\\
-$\rho_1,\rho_2 \getsr Func(\univ,[m])$\\
+$\win \gets \false$\\
+$\rho_1,\rho_2 \getsr \Func{\univ,[m]}$\\
 $S \getsr \distr{\univ}{n}$\\
@@
 if $(count == \ell)$\\
-$\nudge win = true$\\
+$\nudge \win = \true$\\
 $\nudge \mathrm{Ret} \nudge \Qry^{\HashOracle}(M,\tau,x)$\\
@@
 {
-$\experimentv{Adversary \nudge B_1^{\calO}:}$\\
+$\adversaryv{B_1^{\calO}}$\\
 $K_1 \getsr \calK $\\
@@
 {
-$\experimentv{Adversary \nudge B_2^{\calO}:}$\\
+$\adversaryv{B_2^{\calO}}$\\
 %$d \getsr \bits $\\
-$\rho_2 \getsr Func(\univ,[m])$\\
+$\rho_2 \getsr \Func(\univ,[m])$\\
 $S \getsr \distr{\univ}{n}$\\
@@
 \begin{eqnarray}
-\nonumber \Prob{\ExpPRF{F}{B_1} = 1} &=& .5\Prob{\ExpPRF{F}{B_1}=1|b=0} + .5\Prob{\ExpPRF{F}{B_1} = 1|b=1}\\
+\nonumber \Prob{\ExpPRF{F}{B_1} = 1} &=& .5\Prob{\ExpPRF{F}{B_1}=1\,|\,b=0} + .5\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=1}\\
 \nonumber 2\Prob{\ExpPRF{F}{B_1} = 1} &=& 1-\Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1}\\
@@
 \nonumber& &\\
-\nonumber \Prob{\ExpPRF{F}{B_2} = 1} &=& .5\Prob{\ExpPRF{F}{B_2}=1|b=0} + .5\Prob{\ExpPRF{F}{B_2} = 1|b=1}\\
+\nonumber \Prob{\ExpPRF{F}{B_2} = 1} &=& .5\Prob{\ExpPRF{F}{B_2}=1\,|\,b=0} + .5\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=1}\\
 \nonumber 2\Prob{\ExpPRF{F}{B_2} = 1} &=& 1-\Prob{\game{2}(A)=1} + \Prob{\game{1}(A)=1}\\
@@
 \begin{equation}
-\Prob{\game{2}(A)=1} \leq q \cdot \Prob{\game{3}(A)=1} = q \cdot \Prob{\game{3}(A)=1|win=true}\label{eq:3}
+\Prob{\game{2}(A)=1} \leq q \cdot \Prob{\game{3}(A)=1} = q \cdot \Prob{\game{3}(A)=1\,|\,\win=\true}\label{eq:3}
 \end{equation}
@@
 \begin{eqnarray}
-\nonumber \Prob{\game{3}(A)|win=true} &=& \Prob{A^{'} \mathrm{outputs \nudge FP}}\\
+\nonumber \Prob{\game{3}(A)\,|\,\win=\true} &=& \Prob{A' \mbox{outputs FP}}\\
 & \leq & \epsilon, \nudge \mathrm{where} \nudge \epsilon = (1-e^{-kn/m})^k\label{eq:4}
@@
 \fpage{0.4}{
-$\experimentv{Adversary \nudge A^{{'}\HashOracle}:}$\\
+$\adversaryv{A'^{\HashOracle}}$\\
 $\ell \getsr [q]$, where $[q] = {0,1, \cdots, q-1}$\\
 $count = 0$\\
-$\rho_1,\rho_2 \getsr Func(\univ,[m])$\\
+$\rho_1,\rho_2 \getsr \Func{\univ,[m]}$\\
 $S \getsr \distr{\univ}{n}$\\
@@
 \nudge Ret $r$\\
-When $A$ halts with output $\calX^{'}$\\
-\nudge if $|\calX^{'}| < t$ or $\calX^{'} \cap \calS \neq \emptyset$ then \\
+When $A$ halts with output $\calX'$\\
+\nudge if $|\calX'| < t$ or $\calX' \cap \calS \neq \emptyset$ then \\
 \nudge\nudge Ret 0\\
@@
 }
-\caption{Theorem \ref{thm1}:Adversary $A^{'}$ simulating $\game{3}(A)$} \label{AGame3}
+\caption{Theorem \ref{thm1}:Adversary $A'$ simulating $\game{3}(A)$} \label{AGame3}
 \end{figure}

### 2016-07-14 filters-syntax.tex
New section with generic treatment

--- 2016-07-08 filters-syntax.tex
@@
 \heading{Syntax.}
-Fix a nonempty sets $U,\Sigma$ and integers $k,m,n>0$.  Fix a symbol $\bot \not\in U$. An $(n,k,m)$-filter (over universe~$U$) is a tuple $B=(\Hash,\Rep,\Qry)$.
+Fix nonempty sets $U,\Sigma$ and integers $k,m,n>0$.  Fix a symbol $\bot \not\in U$.
+An $(n,k,m)$-filter (over universe~$U$) is a tuple $B=(\Hash,\Rep,\Qry)$.
 %
-The randomized \emph{hash-sampling} algorithm~$\Hash$ samples a size~$k$ family of functions~$\mathcal{H}=\{h_1,h_2,\ldots,h_k\}$ where each $h_i \in \mathrm{Func}(U,[m])$.  
-\jnote{This doesn't seem to work super-well with the random oracle model.} 
-\tsnote{Why not?  As we discussed on the phone, this should be fine.  In the ROM, if we ever need to simulate $\Hash$, we just do it by lazy sampling.}
-We write $\mathcal{H} \getsr \Hash$ for this operation.
+The randomized \emph{hash-sampling} algorithm~$\Hash$ samples a
+size~$k$ family of functions~$\mathcal{H}=\{h_1,h_2,\ldots,h_k\}$
+where each $h_i \in \mathrm{Func}(U,[m])$. \jnote{This doesn't seem
+to work super-well with the random oracle model.} \tsnote{Why not?
+As we discussed on the phone, this should be fine.  In the ROM, if
+we ever need to simulate $\Hash$, we just do it by lazy sampling.}
+\jnote{True, it just means that $\Hash$ is not an efficient
+algorithm in that case.} We write $\mathcal{H} \getsr \Hash$ for
+this operation.
 %

### 2016-07-14 intro.tex
New section with generic treatment

@@
 \section{Introduction}
-We revisit the formalization of Bloom filters~\cite{xxx} and closely related data structures as primitives with explicit security goals.
-Recently, Naor and Yogev~\cite{xxx} (hereafter NY) gave such a formalization, providing syntax for a generalized abstraction of Bloom filters, as well as casting the classical Bloom filter soundness condition as a security experiment admiting adaptive adversaries.
-To briefly summarize, a Bloom filter is a data structure for compactly representing a set~$\mathcal{S}$ in a way that supports constant-time responses to set-membership queries.
-The representation of~$\mathcal{S}$ is a bit-array~$M$ of length~$m$, all initially set to~0.
-To insert $x \in \mathcal{S}$ into~$M$, one computes indices $h_1(x),h_2(x),\ldots,h_k(x)$ where each $h_i \colon \mathcal{U} \to \{0,1,\ldots m-1\}$ maps from a universe~$\mathcal{U}$ (which contains $\mathcal{S}$) to indices of~$M$.
-The bits at positions $h_1(x),h_2(x),\ldots,h_k(x)$ are set to 1; if a bit is already 1, due to inserting some previous element of~$\mathcal{S}$, then it is left alone.
-After all elements of~$\mathcal{S}$ have been inserted, the resulting bit-array~$M$ is taken as the representation.
-To test if $y \in \mathcal{S}$, one checks if \[(M[h_1(y)]=1 \wedge M[h_2(y)]=1 \wedge \cdots \wedge M[h_k(y)]=1),\] returning ``yes'' if so, and ``no'' otherwise.
-Bloom filters are correct, in the sense that if $y \in \mathcal{S}$, the set-membership test always returns ``yes''.
-The classical soundness condition asserts that for all $\mathcal{S}$ and any $y \notin\mathcal{S}$, we have $\Prob{h_1,h_2,\ldots,h_k \getsr \mathrm{Func}(\mathcal{U},[m])\colon M[h_1(y)]=1 \wedge \cdots \wedge M[h_k(y)]=1} \leq \epsilon$ where $\epsilon$, the false-positive error, is a parameter of the Bloom filter.
-(The values of~$\epsilon,m,k$, and $|\mathcal{S}|$ are related in a well-known way.) NY recast this soundness condition as a game in which an adversary~$A$ is given~$\mathcal{S}$ and an oracle for set-membership queries, and it attempts to find one or more false positives.
-The fact that~$A$ can \emph{adapt} its queries and its output based on what it learns from the set-membership oracle (but, as we will see, not upon the hash functions) is the key definitional contribution of~NY.
+We revisit the formalization of Bloom filters~\cite{xxx} and closely
+related data structures as primitives with explicit security goals.
+Recently, Naor and Yogev~\cite{xxx} (hereafter NY) gave such a
+formalization, providing syntax for a generalized abstraction of
+Bloom filters, as well as casting the classical Bloom filter
+soundness condition as a security experiment admiting adaptive
+adversaries.  To briefly summarize, a Bloom filter is a data
+structure for compactly representing a set~$\mathcal{S}$ in a way
+that supports constant-time responses to set-membership queries. The
+representation of~$\mathcal{S}$ is a bit-array~$M$ of length~$m$,
+all initially set to~0.  To insert $x \in \mathcal{S}$ into~$M$, one
+computes indices $h_1(x),h_2(x),\ldots,h_k(x)$ where each $h_i
+\colon \mathcal{U} \to \{0,1,\ldots m-1\}$ maps from a
+universe~$\mathcal{U}$ (which contains $\mathcal{S}$) to indices
+of~$M$.  The bits at positions $h_1(x),h_2(x),\ldots,h_k(x)$ are set
+to 1; if a bit is already 1, due to inserting some previous element
+of~$\mathcal{S}$, then it is left alone.  After all elements
+of~$\mathcal{S}$ have been inserted, the resulting bit-array~$M$ is
+taken as the representation.  To test if $y \in \mathcal{S}$, one
+checks if \[(M[h_1(y)]=1 \wedge M[h_2(y)]=1 \wedge \cdots \wedge
+M[h_k(y)]=1),\] returning ``yes'' if so, and ``no'' otherwise. Bloom
+filters are correct, in the sense that if $y \in \mathcal{S}$, the
+set-membership test always returns ``yes''.  The classical soundness
+condition asserts that for all $\mathcal{S}$ and any $y
+\notin\mathcal{S}$, we have $\Prob{h_1,h_2,\ldots,h_k \getsr
+\mathrm{Func}(\mathcal{U},[m])\colon M[h_1(y)]=1 \wedge \cdots
+\wedge M[h_k(y)]=1} \leq \epsilon$ where $\epsilon$, the
+false-positive error, is a parameter of the Bloom filter.  (The
+values of~$\epsilon,m,k$, and $|\mathcal{S}|$ are related in a
+well-known way.) NY recast this soundness condition as a game in
+which an adversary~$A$ is given~$\mathcal{S}$ and an oracle for
+set-membership queries, and it attempts to find one or more false
+positives. The fact that~$A$ can \emph{adapt} its queries and its
+output based on what it learns from the set-membership oracle (but,
+as we will see, not upon the hash functions) is the key definitional
+contribution of~NY.
 

### 2016-07-14 Theorem1_FP.tex
cleaning up theorem 1

@@
 
+\fixme{Note: the following theorem is incorrect for $t>1$.  Or, at least, the proof does not cover $t>1$.}
 \begin{theorem}\label{thm1}
@@
  $\game{1}(A)$ and $\game{2}(A)$ attack 2 different filters with hash functions 
-\begin{eqnarray*}
-h_j(x) &=& ( F_{K_0}(x) + j\cdot \rho_2(x)) \bmod m\\
-\mathrm{and,}\nudge h_j(x) &=& ( \rho_1(x) + j \cdot \rho_2(x)) \bmod m 
-\end{eqnarray*}
-
-Here, $\rho_1$ and $\rho_2$ are random functions sampled from $Func(\univ,[m])$.
+$h_j(x) = ( F_{K_0}(x) + j\cdot \rho_2(x)) \bmod m$ and $h_j(x) = ( \rho_1(x) + j \cdot \rho_2(x)) \bmod m$, respectively.
+Here, $\rho_1$ and $\rho_2$ are random functions sampled from $\Func{\univ,[m]}$.
 Let adversaries $B_1, B_2$ simulate $\game{1}(A)$ and $\game{2}(A)$ respectively as shown in Fig.
 \ref{fig:BGame1}.
-When $b=1$, $B_1$ and $B_2$ exactly simulate $\game{0}(A)$
-and $\game{1}(A)$. While, for $b=0$, $B_1$ wins, if $\game{1}(A)$ outputs 0, and  $B_2$ wins, if $\game{2}(A)$ returns 0.
-
+When $b=1$, adversaries $B_1$ and $B_2$ exactly simulate $\game{0}(A)$ and $\game{1}(A)$, respectively.
+When $b=0$, adversary $B_1$ wins if $\game{1}(A)$ outputs 0; adversary $B_2$ wins if $\game{2}(A)$ returns 0.
+Thus we have
 \begin{eqnarray}
@@
 
-\par{In a classical Bloom filter, adversary $A^{'}$ is non-adaptive, i.e., for some fixed $x \notin S$, $A^{'}$ targets the false-positive error conditioned on randomness of hash functions.
-But in the $\ExpFPSecHash{B,t}{A}$ game, $A$ is adaptive, as it can adapt its queries as well as its output based on response of $\QryOracle$ oracle.
+\noindent
+In a classical Bloom filter, adversary $A^{'}$ is non-adaptive, i.e., for some fixed $x \notin S$, $A^{'}$ targets the false-positive error conditioned on randomness of hash functions.
+\tsnote{The classical FP requirement considers only non-adaptive (and information-theoretic) adversaries.
+It suffices to say this.}  But in the $\ExpFPSecHash{B,t}{A}$ game, $A$~is adaptive, as it can adapt its queries as well as its output based on response of $\QryOracle$ oracle.
 Let $A$ makes $q>t$ queries $x_1, x_2, ..., x_q$ to the $\QryOracle$ oracle.
-$\game{3}(A)$ simulates $fp-error$ game of $A^{'}$ as shown in Fig.
-\ref{fig:Game}.}
+$\game{3}(A)$ simulates fp-error\tsnote{?} game of~$A^{'}$ as shown in Fig.
+\ref{fig:Game}.
 
@@
 \underline{$\game{3}(A)$}\\
-$\ell \getsr [q]$, where $[q] = {0,1, \cdots, q-1}$\\
-$count = 0$ \\%count will be used to keep track of queries made to $\QryOracle$\\
+$\ell \getsr [q]$\\
+$c = 0$ \\%count will be used to keep track of queries made to $\QryOracle$\\
 $\win \gets \false$\\
@@
 \oracle{$\QryOracle(x)$}\\
-$count=count +1$\\
-if $(count == \ell)$\\
+$c=c +1$\\
+if $(c == \ell)$\\
 $\nudge \win = \true$\\
@@
 %$d \getsr \bits $\\
-$\rho_2 \getsr \Func(\univ,[m])$\\
+$\rho_2 \getsr \Func(\univ,[m])$ \\
 $S \getsr \distr{\univ}{n}$\\
@@
 
-From eqns. \ref{eq:m1}, \ref{eq:m2}, \ref{eq:m3} and \ref{eq:m4},
+From eqns. \ref{eq:m1}, \ref{eq:m2}, \ref{eq:m3} and \ref{eq:m4}, \tsnote{this can be compacted}
 \begin{eqnarray}
@@
 
+\noindent
 Adding eqn. \ref{eq:1} and \ref{eq:2}, we have
@@
 In $\game{3}(A)$, assume, without loss of generality that $A$ halts with output $x$ immediately, if it asks $x$ to $\QryOracle$ and $\QryOracle$ returns $1$.
-Thus, all queries to $\QryOracle$ return 0 until the first one.
+\fixme{This only works when $t=1$!
+This is where the proof breaks down for the case of $t>1$.} Thus, all queries to $\QryOracle$ return 0 until the first one.
 Hence,
@@
 
-In Fig. \ref{AGame3}, adversary $A^{'}$ simulates $\game{3}(A)$. Since, adversary $A^{'}$ exactly simulates $\game{3}(A)$ conditioned on $win = true$, 
+In Fig. \ref{AGame3}, adversary $A'$ simulates $\game{3}(A)$. Since, adversary $A'$ exactly simulates $\game{3}(A)$ conditioned on $\win = \true$, 
 \begin{eqnarray}
 \nonumber \Prob{\game{3}(A)\,|\,\win=\true} &=& \Prob{A' \mbox{outputs FP}}\\
-& \leq & \epsilon, \nudge \mathrm{where} \nudge \epsilon = (1-e^{-kn/m})^k\label{eq:4}
+& \leq & \epsilon,\mbox{ where } \epsilon = (1-e^{-kn/m})^k\label{eq:4}
 \end{eqnarray}
@@
 \begin{eqnarray}
-\nonumber \AdvFPSecHash{B,t}{A} &-& \Prob{\game{2}(A)=1} =  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}   \\
-\nonumber \AdvFPSecHash{B,t}{A}  &=&  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} + \Prob{\game{2}(A)=1}  \\
-\AdvFPSecHash{B,t}{A} &\leq&  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  + q \cdot \epsilon
+\nonumber \AdvFPSecHash{B_{\mathrm{lin}},t}{A} &-& \Prob{\game{2}(A)=1} =  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}   \\
+\nonumber \AdvFPSecHash{B_{\mathrm{lin}},t}{A}  &=&  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} + \Prob{\game{2}(A)=1}  \\
+\AdvFPSecHash{B_{\mathrm{lin}},t}{A} &\leq&  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  + q \cdot \epsilon
 \end{eqnarray}

### 2016-07-14 filters-syntax.tex

--- 2016-07-13 filters-syntax.tex
@@
 \heading{Syntax.}
-Fix nonempty sets $\univ,\Sigma$ and integers $k,m,n>0$.  Fix a symbol $\bot \not\in \univ$. An $(n,k,m)$-filter (over universe~$\univ$) is a tuple $B=(\Hash,\Rep,\Qry)$.
+
+Fix nonempty sets $U,\Sigma$ and integers $k,m,n>0$.  Fix a symbol $\bot \not\in U$.
+An $(n,k,m)$-filter (over universe~$U$) is a tuple $B=(\Hash,\Rep,\Qry)$.
 %
-The randomized \emph{hash-sampling} algorithm~$\Hash$ samples a size~$k$ family of functions~$\mathcal{H}=\{h_1,h_2,\ldots,h_k\}$ where each $h_i \in \mathrm{Func}(\univ,[m])$.  
-\jnote{This doesn't seem to work super-well with the random oracle model.} 
-\tsnote{Why not?  As we discussed on the phone, this should be fine.  In the ROM, if we ever need to simulate $\Hash$, we just do it by lazy sampling.}
-We write $\mathcal{H} \getsr \Hash$ for this operation.
+The randomized \emph{hash-sampling} algorithm~$\Hash$ samples a
+size~$k$ family of functions~$\mathcal{H}=\{h_1,h_2,\ldots,h_k\}$
+where each $h_i \in \mathrm{Func}(U,[m])$. \jnote{This doesn't seem
+to work super-well with the random oracle model.} \tsnote{Why not?
+As we discussed on the phone, this should be fine.  In the ROM, if
+we ever need to simulate $\Hash$, we just do it by lazy sampling.}
+\jnote{True, it just means that $\Hash$ is not an efficient
+algorithm in that case.} We write $\mathcal{H} \getsr \Hash$ for
+this operation.
 %

### 2016-07-14 generic.tex
Trying again...

\section{Secure Data Structures, Abstractly}
We focus on the case of static data structures only (for now).
\def\pub{{\sf pub}}

\subsection{Syntax}
Fix a universe $U$.

\begin{definition}
A (randomized) \emph{data structure} is a pair of algorithms $(\Rep, \Qry)$
parameterized by a collection $\mathcal{S}$ of subsets of~$U$ and a collection
of supported queries $\mathcal{Q}$ and having the following syntax:
\begin{itemize}
\item $\Rep$ is a randomized algorithm taking as input $S \in \mathcal{S}$,
and outputting a pair of values $(\pub, M)$.
\item $\Qry$ is a deterministic algorithm that takes as input $\pub, M$,
and a query $q\in \mathcal{Q}$, and returns an answer~$a$.
\end{itemize}
A data structure is \emph{$\epsilon$-correct} if for all $S \in \mathcal{S}$ and
all $q \in \mathcal{Q}$ it holds that
\begin{eqnarray}
\Pr[(\pub, M) \leftarrow \Rep(S) : \Qry(\pub, M, q) \neq q(S)] \leq \epsilon, \label{eqn:correctness}
\end{eqnarray}
where $q(S)$ denotes the correct answer to the query $q$ on the set~$S$.
The \emph{size} of a data structure is the maximum length of any~$M$ that can be
output by $\Rep$.
\end{definition}

Our treatment of $\pub, M$ is not symmetric, since we only count $M$ against the size
of the data structure. When we define security
we may give the attacker $\pub$ but not~$M$, and in that case the data structure cannot
trivially make everything part of~$\pub$.

It is not hard to see Bloom filters are one possible instantiation of the above. If we fix some
size bound~$n$, then $\mathcal{S}$ becomes the collection of all subsets of $U$
of size (at most)~$n$. We also fix $\mathcal{Q} = U$, where a query ``$x$'' has
the semantics ``is $x$ in $S$?'' Algorithm $\Rep$, which has values $k, m$ hardwired,
chooses a set of hash functions $h_1, \ldots, h_k$ and computes an $m$-bit
array in the usual way; a natural possibility is to set $\pub = (h_1, \ldots, h_k)$ and
to let $M$ be the bit array.

The above definition can be lifted to the random-oracle model in the natural way
by giving $\Rep, \Qry$ access to a random oracle. In that case,
the probability in Equation~(\ref{eqn:correctness})
is also taken over choice of the random oracle.

\heading{FP security.}
As highlighted by Naor and Yogev,
Equation~(\ref{eqn:correctness}) is a non-adaptive version of correctness;
we are interested in defining an adaptive (i.e., adversarial) notion of correctness.
The general style of the definition is as follows:
first, a set $S$ is chosen according to some distribution over~$\mathcal{S}$ and then
$\Rep(S)$ is run to generate $(\pub, M)$. The attacker $A$ is given $\pub$ and (possibly)~$S$;
in addition, $A$ is given \emph{oracle access} to~$\Qry(\pub, M, \cdot)$.
If $(\Rep, \Qry)$ is defined in the random-oracle model, then
$A$ is given access to the random oracle as well.
$A$ \emph{succeeds} if it outputs $t$ distinct queries $q_1, \ldots, q_t \in \mathcal{Q}$ for which
$\Qry(\pub, M, q_i) \neq q_i(S)$ for all~$i$.
Roughly, we say that a data structure is $(t,\epsilon')$-FP-secure if the probability that
any polynomial-time attacker succeeds is at most~$\epsilon'$. A full definition
would also bound the number of queries to $\Qry$ (and the random oracle) made
be the attacker; it is useful to make the convention that if $A$ outputs
$q_1, \ldots, q_t$ then it must have made those queries to its oracle previously.

The notion of FP-security defined above captures the fp-prv notion for Bloom filters
if we put the hash
functions in $M$ (and thus increase the size of the data structure); it also captures the fp-pub
notion if we put the hash function in~$\pub$. It captures the fp-bb-pub notion in the
random-oracle model.

Note that the security we can hope for is somewhat limited, since there
is always a trivial attack in which
the attacker tries random queries $q_1, q_2, \ldots$ until it finds $t$ queries for which the
data structure returns an incorrect answer.\footnote{This assumes the attacker
knows the true set $S$, which need not be the case.} Roughly speaking,
if the data structure is $\epsilon$-correct then the attacker expects to find a query on which
an incorrect result is returned
every $1/\epsilon$ tries; thus, an
attacker making $t/\epsilon$ queries succeeds with constant probability.

\def\bin{{\sf Bin}}

Actually, it seems worthwhile to formalize this. Let $X_i$ be a random variable indicating
whether the $i$th query of the attacker gives an incorrect result. Then an attacker making $T$
queries can succeed
if $N \stackrel{{\rm def}}{=} \sum_{i=1}^T X_i \geq t$. If we treat the $X_i$ as independent Bernoulli trials with
probability~$\epsilon$, then $N$ follows the well-studied binomial distribution.
Let $\bin(T, \epsilon; t)$ denote the probability that $N \geq t$. So the best security we can
hope for
is that if the data structure is $\epsilon$-correct then for any desired bound $T$
the data structure is $(t, \bin(T,\epsilon; t))$-FP-secure against any attacker making
at most $T$~queries. \jnote{Need to find different terms to use for a query $q \in \mathcal{Q}$
and a query that the attacker makes to its oracle.}

\heading{Comparison to Naor-Yogev definition.}
The style of the Naor-Yogev (NY) definition is slightly different. \jnote{Even if we ignore
all the other issues, chief among them the inconsistent way it treats the hash functions.}
Lifting their definition to our setting, the experiment is similar but the attacker
succeeds only if it outputs a single query $q$ for which $\Qry(\pub, M, q) \neq q(S)$ \emph{subject
to the restriction that it did not query $q$ to its $\Qry$ oracle}.
It will be interesting to understand formally the relation between our definition and theirs.
Here are some observations:
\begin{enumerate}
\item Say a scheme is $\epsilon_{NY}$-secure under the NY definition.
Then we claim it is $(t, T\epsilon_{NY}/t)$-secure against an attacker making $T$ queries. To see
this, assume not. Then there is an attacker $A$ that, with probability $\epsilon'=T\epsilon_{NY}/t$,
issues $T$ queries of which at least $t$ among those give incorrect answers.
If we simply run $A$ and
then choose a random query to output, we succeed with probability at least $\epsilon' \cdot t/T$.
It is unclear whether this is tight.

\item There is a contrived scheme that is $(2, 0)$-FP-secure but not NY-secure at all; the basic idea is
to have a data structure that always has \emph{exactly one} false positive that is easy to find
given the public information.

\item If a scheme is $(1,\epsilon_{FP})$-FP-secure for an attacker making $T$ queries
then it is also $\epsilon_{FP}$-secure under the NY definition, at least for attackers making at most $T-1$
queries.
This is immediate.
\end{enumerate}

### 2016-07-14 filters-notions.tex
hash oracles now return all values at once
cheers
Updated Proof of Theorem 1 as per the changed syntax and some minor corrections
privacy added

@@
 %
-The middle notion is a compromise: it makes the hash functions public, but assumes that the adversary only accesses them in a black-box manner.
-That is, the adversary does not exploit structural features of the hash functions in its attack.
-This notion makes it easy to track the query complexity of an attack, and also allows us to capture constructions in the random-oracle model.
+The middle notion is a compromise: it makes the hash functions
+public, but assumes that the adversary only accesses them in a
+black-box manner.  That is, the adversary does not exploit
+structural features of the hash functions in its attack.  This
+notion makes it easy to track the query complexity of an attack, and
+also allows us to capture constructions in the random-oracle model.
 \tsnote{This is the setting for the Neidermayer et al.\  attacks.
-It's also the setting for ROM attacks.}
+It's also the setting for ROM attacks.} \jnote{I don't think the
+middle notion is interesting. I disagree regarding the attacks of
+Neidermayer et al.: there, the hash functions are secret (though
+they are based on public ``random oracles'' $g$ and $h$). The ROM
+can be handled separately by giving all algorithms access to
+the~RO.}
 
@@
 \begin{align*}
-\AdvFPSecHash{B}{\distr{U}{n},A} &= \Prob{\ExpFPSecHash{B}{\distr{U}{n},A}} \\
-\AdvFPPubHashBB{B}{\distr{U}{n},A} &= \Prob{\ExpFPPubHashBB{B}{\distr{U}{n},A}} \\
-\AdvFPSecHash{B}{\distr{U}{n},A} &= \Prob{\ExpFPPubHash{B}{\distr{U}{n},A}}
+\AdvFPSecHash{B,t}{\distr{U}{n},A} &= \Prob{\ExpFPSecHash{B,t}{\distr{U}{n},A}=1} \\
+\AdvFPPubHashBB{B,t}{\distr{U}{n},A} &= \Prob{\ExpFPPubHashBB{B,t}{\distr{U}{n},A}=1} \\
+\AdvFPSecHash{B,t}{\distr{U}{n},A} &= \Prob{\ExpFPPubHash{B,t}{\distr{U}{n},A}=1}
 \end{align*}
@@
 
-\jnote{7/8: Do our definitions imply the Naor definition? If so, then why do they use a PRP in their construction?}
-
-We note that the distribution~$\distr{U}{n}$ must be independent of the hash functions $h_1,h_2,\ldots,h_k$ that are used to create~$M$.
-Otherwise, when (say) $\Sigma=\bits$, the distribution may only assign positive probability to sets~$\calS$ that cause an abnormally large number of bits in~$M$ to be set to 1.
-Our security notions enforce this independence.
+We note that the distribution~$\distr{U}{n}$ must be independent of
+the hash functions $h_1,h_2,\ldots,h_k$ that are used to create~$M$.
+Otherwise, when (say) $\Sigma=\bits$, the distribution may only
+assign positive probability to sets~$\calS$ that cause an abnormally
+large number of bits in~$M$ to be set to 1.  Our security notions
+enforce this independence.
 
@@
 %
-\tsnote{Formally, I don't think we can (and still be rooted in reality).
-Even informally it's hard, since the fact is that the designer decides what is ``secure'' for her setting.
-I think we just say something like ``A bloom filter is $(t,q_h,q_m,\epsilon)$-secure if no attacker running in time at most~$t$, asking at most~$q_h$ hash queries and $q_m$ set-membership queries, has probability more than~$\epsilon$ of finding a FP.'' (If you like, we can throw a paramter~$n$ in there, for the number of FPs it must find.) Perhaps informally we say that a bloom filter is secure if, for ``reasonable'' $t,q_h,q_m$, the value of~$\epsilon$ is not ``significantly larger'' than the designer's target.
-I guess that's not far off from one of your suggestions.}
+\tsnote{Formally, I don't think we can (and still be rooted in
+reality).  Even informally it's hard, since the fact is that the
+designer decides what is ``secure'' for her setting.  I think we
+just say something like ``A bloom filter is
+$(t,q_h,q_m,\epsilon)$-secure if no attacker running in time at
+most~$t$, asking at most~$q_h$ hash queries and $q_m$ set-membership
+queries, has probability more than~$\epsilon$ of finding a FP.''
+Perhaps informally we say that a bloom filter is secure if, for
+``reasonable'' $t,q_h,q_m$, the value of~$\epsilon$ is not
+``significantly larger'' than the designer's target.  I guess that's
+not far off from one of your suggestions.}
 
@@
 
+\tsnote{Explain need for $\MemOracle$, as a way to disambiguate true positives from false positives.}
+
 We note that~$\calS$ must be independent of the hash functions~$h_1,h_2,\ldots,h_k$ used to create the representation of~$\calS$.  \tsnote{I thought this would be needed, but now I'm not sure it is. }
@@
 $(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
-$x \getsr A^{\QryOracle}(M)$\\
+$x \getsr A^{\MemOracle,\QryOracle}(M)$\\
 if $x\in \calS$ then Ret 1\\
@@
 $(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
-$x \getsr A^{\QryOracle,\HashOracle}(M)$\\
+$x \getsr A^{\MemOracle,\QryOracle,\HashOracle}(M)$\\
 if $x\in \calS$ then Ret 1\\
@@
 $(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
-$x \getsr A^{\QryOracle}(M,\{h_1,h_2,\ldots,h_k\})$\\
+$x \getsr A^{\MemOracle,\QryOracle}(M,\{h_1,h_2,\ldots,h_k\})$\\
 if $x\in \calS$ then Ret 1\\

### 2016-07-14 generic.tex
privacy added

@@
 
+\subsection{Adversarial Soundness}
 \heading{FP security.}
@@
 first, a set $S$ is chosen according to some distribution over~$\mathcal{S}$ and then
-$\Rep(S)$ is run to generate $(\pub, M)$. The attacker $A$ is given $\pub$ and (possibly)~$S$;
+$\Rep(S)$ is run to generate $(\pub, M)$. (Unless stated otherwise, we assume
+security holds for all distributions and thus for all sets $S$.)
+The attacker $A$ is given $\pub$ and (possibly)~$S$;
 in addition, $A$ is given \emph{oracle access} to~$\Qry(\pub, M, \cdot)$.
@@
 
+\jnote{One option is to define the adversary's \emph{advantage} as the difference between
+its success probability and the success probability of the above, trivial attack. Just a thought.}
+
 \heading{Comparison to Naor-Yogev definition.}
@@
 \item If a scheme is $(1,\epsilon_{FP})$-FP-secure for an attacker making $T$ queries
-then it is also $\epsilon_{FP}$-secure under the NY definition, at least for attackers making at most $T-1$
+then it is also $\epsilon_{FP}$-secure under the NY definition,
+at least for attackers making at most $T-1$
 queries.
@@
 \end{enumerate}
+
+\subsection{Privacy}
+One can also consider the orthogonal notion of privacy for a data structure.
+\jnote{Actually, I am now unsure what the right way to define it is. It seems natural
+to give the attacker $\pub$. But if we give them $\pub$ and $M$ then they have everything.
+If $S$ has high min-entropy (element-wise), then it might still be possible to have security here.}
+There are several possible definitions:
+\begin{enumerate}
+\item A ``one-wayness'' definition where $S$ has high min-entropy (element-wise), and we
+give the attacker $\pub$ and either $M$ or oracle access to $\Qry$. The attacker
+succeeds if it can output an element in~$S$.
+
+\item An ``indistinguishability'' definition where either $S_0$ or $S_1$ is used, and the attacker
+must determine which. Here the attacker is given $\pub$ but only oracle access to $\Qry$, and
+it is disallowed from asking any query $q$ for which $q(S_0) \neq q(S_1)$. 
+\end{enumerate}

### 2016-07-14 intro.tex
privacy added

@@
 
-Second, we note that the NY syntax does not capture the size of~$M$ as a parameter;
-\jnote{I think this is also reasonable; typically security is defined without regard for efficiency} \tsnote{My complaint isn't about efficiency.
-It's about the fact that, by not including $|M|$ in the definition, the trivial scheme I give (just below) is allowed, and is secure.
-Anyway, as I say at the end of
+Second, we note that the NY syntax does not capture the size of~$M$
+as a parameter; \jnote{I think this is also reasonable; typically
+security is defined without regard for efficiency} \tsnote{My
+complaint isn't about efficiency. It's about the fact that, by not
+including $|M|$ in the definition, the trivial scheme I give (just
+below) is allowed, and is secure.  Anyway, as I say at the end of
 this paragraph, this is a small(er) complaint than what follows}.
 \jnote{I would say that the trivial scheme \emph{is} secure!}
-\tsnote{Okay, well then we need some way to ``rule out'' the trivial solution.
-Perhaps just in the text -- yes, the trivial scheme works, but it isn't interesting in practice.
-Also, in the concrete security bounds that we will prove, the size of the representation is going to come up, e.g.\ the number of bits in the BF array directly affect the FP rate.
-Hence it makes sense to say things like ``an $(n,k,m)$-filter...'' where $m$ is the size of the representation.}
-The surrounding text does say that $\mathbf{B}_1$ ``outputs a compressed representation [of $\mathcal{S}$] $\mathbf{B}_1(\mathcal{S})=M$'' but what exactly this means is never addressed.
-The formal syntax admits $\mathbf{B}_1(\mathcal{S})=\mathcal{S}$ and $\mathbf{B}_2(\mathcal{S},x)=1 \Leftrightarrow x \in \mathcal{S}$, which is also trivially secure by their definition.
-These are both small, but important complaints.
-But a larger complaint, and one that is much harder to see, is that that it is not clear that the NY formalism actually captures real world Bloom filters.
+\tsnote{Okay, well then we need some way to ``rule out'' the trivial
+solution. Perhaps just in the text -- yes, the trivial scheme works,
+but it isn't interesting in practice. Also, in the concrete security
+bounds that we will prove, the size of the representation is going
+to come up, e.g.\ the number of bits in the BF array directly affect
+the FP rate. Hence it makes sense to say things like ``an
+$(n,k,m)$-filter\ldots'' where $m$ is the size of the
+representation.} \jnote{I still disagree: efficiency is orthogonal
+to functionality and security.} The surrounding text does say that
+$\mathbf{B}_1$ ``outputs a compressed representation [of
+$\mathcal{S}$] $\mathbf{B}_1(\mathcal{S})=M$'' but what exactly this
+means is never addressed. The formal syntax admits
+$\mathbf{B}_1(\mathcal{S})=\mathcal{S}$ and
+$\mathbf{B}_2(\mathcal{S},x)=1 \Leftrightarrow x \in \mathcal{S}$,
+which is also trivially secure by their definition.  These are both
+small, but important complaints. But a larger complaint, and one
+that is much harder to see, is that that it is not clear that the NY
+formalism actually captures real world Bloom filters.
 

### 2016-07-15 intro.tex
cheers

@@
 representation.} \jnote{I still disagree: efficiency is orthogonal
-to functionality and security.} The surrounding text does say that
+to functionality and security.} \fixme{
+Let's discuss this verbally, because I feel like we are talking past each other.}The surrounding text does say that
 $\mathbf{B}_1$ ``outputs a compressed representation [of

### 2016-07-15 filters-syntax.tex
cheers

@@
 \jnote{True, it just means that $\Hash$ is not an efficient
-algorithm in that case.} We write $\mathcal{H} \getsr \Hash$ for
-this operation.
+algorithm in that case.} \tsnote{Agreed.  Just not sure that matters.}
+We write $\mathcal{H} \getsr \Hash$ for this operation.
 %
@@
 This allows our syntax to capture the cuckoo-hashing construction from NY, as well as the ``garbled Bloom filter'' from Dong, Chen and Wen~\cite{xxx}, among other things.
-We note that even though this would allow for the storage of counters (say) at each filter location, our restriction that~$\Qry$ returns a bit does not capture functionality typically demanded of Bloom filters that employ counters, e.g., returning a counter value.
+\fixme{If we change to generalized syntax, let's make sure we still capture all of these constructions.}We note that even though this would allow for the storage of counters (say) at each filter location, our restriction that~$\Qry$ returns a bit does not capture functionality typically demanded of Bloom filters that employ counters, e.g., returning a counter value.
 (One could, however, have $\Qry$ compute an arbitrary, fixed predicate.

### 2016-07-15 filters-notions.tex
cheers

@@
 can be handled separately by giving all algorithms access to
-the~RO.}
+the~RO.}\tsnote{You're correct; I misread some of the text.  It is
+only the setup for the attack that needs access to the hash functions,
+and this is just modeling what is likely to appear in the real
+``encrypted'' BFs.}
 

### 2016-07-15 generic.tex
cheers

@@
 we may give the attacker $\pub$ but not~$M$, and in that case the data structure cannot
-trivially make everything part of~$\pub$.
+trivially make everything part of~$\pub$. \tsnote{Is the idea that
+  anything that is secret is part of~$M$?  For example, if the scheme
+  uses public hash functions to populate a bit-array, and then a
+  secretly-keyed blockcipher to encipher the array; the
+  blockcipher key is encoded in~$M$?  This may cause some issues in
+  the security defintions, i.e.\ whether we can give~$M$ to the
+  attacker or not. } \tsnote{By the way, I'm coming around to the
+  viewpoint that it is fair to include in the ``size'' of the
+  representation any secret information.  In makes more difficult
+  comparisons to classical lower-bounds (which [NY] makes, incorrectly
+IMO), but it does seem fair to say ``this is how many bits of memory
+you need to allocate to represent this set \emph{securely}.''  }
 
@@
 array in the usual way; a natural possibility is to set $\pub = (h_1, \ldots, h_k)$ and
-to let $M$ be the bit array.
+to let $M$ be the bit array.  \tsnote{If $\mathcal{Q}=U$ and we use the
+  semantics you suggest, then isn't Equation~\ref{eqn:correctness}
+  both correctness and soundness?  If so, I don't see how this
+  captures the classical BF, which requires $\epsilon=0$ for one kind
+  of error, but allows $\epsilon>0$ for the other. }
 
@@
 Equation~(\ref{eqn:correctness}) is a non-adaptive version of correctness;
-we are interested in defining an adaptive (i.e., adversarial) notion of correctness.
+we are interested in defining an adaptive (i.e., adversarial) notion
+of correctness. \tsnote{Correctness?  Or soundness?}
 The general style of the definition is as follows:
@@
 functions in $M$ (and thus increase the size of the data structure); it also captures the fp-pub
-notion if we put the hash function in~$\pub$. It captures the fp-bb-pub notion in the
+notion if we put the hash function in~$\pub$. \tsnote{Except that the win condition allows both
+false-positives and false-negatives, given the correctness requirement
+in the syntax.} It captures the fp-bb-pub notion in the
 random-oracle model.
@@
 \jnote{One option is to define the adversary's \emph{advantage} as the difference between
-its success probability and the success probability of the above, trivial attack. Just a thought.}
+its success probability and the success probability of the above,
+trivial attack. Just a thought.}
+\tsnote{Or, perhaps by recasting security
+  as distinguishing between $\Qry(\pub,M,\cdot)$ and an oracle that
+  returns 0,1 according to Bernoulli with paramter~$\epsilon$.}
 
@@
 to give the attacker $\pub$. But if we give them $\pub$ and $M$ then they have everything.
-If $S$ has high min-entropy (element-wise), then it might still be possible to have security here.}
+If $S$ has high min-entropy (element-wise), then it might still be
+possible to have security here.}\tsnote{I think we will always bump up
+against the (element-wise) min-entropy of the distribution over~$S$,
+at least in the ``one-wayness'' style definition that I had been imagining. }
 There are several possible definitions:
@@
 must determine which. Here the attacker is given $\pub$ but only oracle access to $\Qry$, and
-it is disallowed from asking any query $q$ for which $q(S_0) \neq q(S_1)$. 
+it is disallowed from asking any query $q$ for which $q(S_0) \neq
+q(S_1)$. \tsnote{How will the adversary know that a query satisfies
+  this in (say) the case of the classical BF?  We can, of course,
+enforce it in the experiement, but then our resource accounting risks
+overcounting the number of queries.} \tsnote{Also, we need that, in general, $\pub$ itself
+does not leak information about~$S_0$ vs.\ $S_1$. }
 \end{enumerate}

### 2016-07-18 generic.tex
cheers
replies to comments...

@@
 The \emph{size} of a data structure is the maximum length of any~$M$ that can be
-output by $\Rep$.
+output by $\Rep$. \tsnote{How does one define the length of~$M$,
+  without knowing what kind of object it is (or demanding it be
+  bit-length, relative to some implicit encoding into bitstrings)?
+  Also, why take the max?  Why not just the length of~$M$, whatever it
+happens to be?}\jnote{I was assuming that $M$ is a bitstring. One can talk
+about the length of $M$ in some run of the algorithm, but when you want to talk
+about how well the data structure as a whole performs, taking the max is one natural option.}
+\tsnote{What is a ``query''?  A predicate? A
+real-valued function? A (potentially) randomized algorithm?} \jnote{A query is a deterministic
+function.}
 \end{definition}
@@
   blockcipher key is encoded in~$M$?  This may cause some issues in
-  the security defintions, i.e.\ whether we can give~$M$ to the
-  attacker or not. } \tsnote{By the way, I'm coming around to the
+  the security definitions, i.e.\ whether we can give~$M$ to the
+  attacker or not. } \jnote{Yes, anything secret is part of $M$; anything public
+  is part of $\pub$.} \tsnote{By the way, I'm coming around to the
   viewpoint that it is fair to include in the ``size'' of the
@@
 IMO), but it does seem fair to say ``this is how many bits of memory
-you need to allocate to represent this set \emph{securely}.''  }
+you need to allocate to represent this set \emph{securely}.''}
 
@@
   captures the classical BF, which requires $\epsilon=0$ for one kind
-  of error, but allows $\epsilon>0$ for the other. }
+  of error, but allows $\epsilon>0$ for the other. } \jnote{The definition does not distinguish
+  between elements in the set (for which $q(S)=1$) or outside the set (for which
+  $q(S)=0$). But a Bloom filter does satisfy Equation~\ref{eqn:correctness} in either case.}
+  \jnote{In that sense, I am using ``soundness'' and ``correctness'' interchangeably here.}
+  \jnote{I'm not tied to allowing false negatives when we specialize the definition to the case
+  of set-membership queries. But in the abstract definition it seems unclear why one would choose
+  some queries on which error is ok and other queries where error is not allowed. Though if one
+  wanted to be general, one could simply have two (disjoint) sets of queries $\mathcal{Q}_1, \mathcal{Q}_2$
+  where error is allowed on the former but not on the latter.}
 
@@
 false-positives and false-negatives, given the correctness requirement
-in the syntax.} It captures the fp-bb-pub notion in the
+in the syntax.} \jnote{True. But if false negatives cannot occur at all (by design of
+the data structure, not by definition of the primitive), then the attacker cannot hope to win
+by finding a false negative.} It captures the fp-bb-pub notion in the
 random-oracle model.
@@
   this in (say) the case of the classical BF?  We can, of course,
-enforce it in the experiement, but then our resource accounting risks
-overcounting the number of queries.} \tsnote{Also, we need that, in general, $\pub$ itself
-does not leak information about~$S_0$ vs.\ $S_1$. }
+enforce it in the experiment, but then our resource accounting risks
+overcounting the number of queries.} \jnote{I was assuming the attacker knows $S_0, S_1$.}
+\tsnote{Also, we need that, in general, $\pub$ itself
+does not leak information about~$S_0$ vs.\ $S_1$. } \jnote{Sure, this would be implied
+by the definition in this case.}
 \end{enumerate}

### 2016-07-20 Theorem1_FP.tex
Modified proof of Theorem1

@@
 Let $B_{\mathrm{lin}}=(\Hash,\Rep,\Qry)$ be defined as follows.
-Fix non-empty sets~$\univ, \univ$ and integers $k,m>0$.
+Fix non-empty set ~$\univ$ and integers $k,m,n>0$.
 Let $F\colon\mathcal{K} \times \univ \to [m]$ be a function family.
@@
 The $\Rep$ and $\Qry$ algorithms are the standard (determinisitic) BF ones.
-\tsnote{Should define these someplace.}  The following result shows, informally, that if~$F$ is a good PRF and the (non-adaptive) FP rate is sufficiently small, then $B_\mathrm{lin}$ is secure against adaptive FP-finding adversaries.
+\tsnote{Should define these someplace.}\acnote{Deterministic Rep and Qry defined(without side info)} $\Rep\colon [\univ]^n \rightarrow \Sigma^m$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m$.
+$\Qry\colon \Sigma^m \times \univ \rightarrow \bits$ takes a representation $M$ and an element $x \in \univ$, and returns a bit indicating presence/absence of $x$.
+The following result shows, informally, that if~$F$ is a good PRF and the (non-adaptive) FP rate is sufficiently small, then $B_\mathrm{lin}$ is secure against adaptive FP-finding adversaries.
 
@@
 \[
-\AdvFPSecHash{B_{\mathrm{lin}},t}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} + q \cdot  (1-e^{-kn/m})^k
+\AdvFPSecHash{B_{\mathrm{lin}},t}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  + \frac{q}{\dbinom{q}{t}} \times  (1-e^{-kn/m})^k
 \]
@@
 %
-\begin{proof}[Theorem~\ref{thm1}]
-The proof of the theorem will use a game playing argument as shown in Fig.
-\ref{fig:Game}.
-$\game{0}(A)$ exactly simulates $\ExpFPSecHash{B,t}{A}$ with hash functions $h_j(x) =  F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$.
+\begin{proof}[\Cref{thm1}]
+The proof of the theorem will use a game playing argument as shown in \Cref{fig:Game}.
+$\game{0}(A)$ exactly simulates $\ExpFPSecHash{B_\mathrm{lin},t}{A}$ with hash functions $h_j(x) =  F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$.
 So,
@@
 $h_j(x) = ( F_{K_0}(x) + j\cdot \rho_2(x)) \bmod m$ and $h_j(x) = ( \rho_1(x) + j \cdot \rho_2(x)) \bmod m$, respectively.
-Here, $\rho_1$ and $\rho_2$ are random functions sampled from $\Func{\univ,[m]}$.
-Let adversaries $B_1, B_2$ simulate $\game{1}(A)$ and $\game{2}(A)$ respectively as shown in Fig.
-\ref{fig:BGame1}.
-When $b=1$, adversaries $B_1$ and $B_2$ exactly simulate $\game{0}(A)$ and $\game{1}(A)$, respectively.
+Here, $\rho_1$ and $\rho_2$ are random functions sampled from $\Func{\univ,[m]}$. \\
+\noindent
+Let adversaries $B_1, B_2$ simulate $\game{1}(A)$ and $\game{2}(A)$ respectively as shown in \Cref{fig:BGame1}.
+When $b=1$, adversaries $B_1$ and $B_2$ exactly simulate $\game{0}(A)$ and $\game{1}(A)$.
 When $b=0$, adversary $B_1$ wins if $\game{1}(A)$ outputs 0; adversary $B_2$ wins if $\game{2}(A)$ returns 0.
 Thus we have
-\begin{eqnarray}
-\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=1} &=& \Prob{\game{0}(A)=1}\label{eq:m1}\\
-\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=1} &=& \Prob{\game{1}(A)=1}\label{eq:m2}\\
-\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=0} &=& 1-\Prob{\game{1}(A)=1}\label{eq:m3}\\
-\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=0} &=& 1-\Prob{\game{2}(A)=1}\label{eq:m4}
-\end{eqnarray}
 
-\noindent
-In a classical Bloom filter, adversary $A^{'}$ is non-adaptive, i.e., for some fixed $x \notin S$, $A^{'}$ targets the false-positive error conditioned on randomness of hash functions.
-\tsnote{The classical FP requirement considers only non-adaptive (and information-theoretic) adversaries.
-It suffices to say this.}  But in the $\ExpFPSecHash{B,t}{A}$ game, $A$~is adaptive, as it can adapt its queries as well as its output based on response of $\QryOracle$ oracle.
-Let $A$ makes $q>t$ queries $x_1, x_2, ..., x_q$ to the $\QryOracle$ oracle.
-$\game{3}(A)$ simulates fp-error\tsnote{?} game of~$A^{'}$ as shown in Fig.
-\ref{fig:Game}.
+\begin{align}
+\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=1} &= \Prob{\game{0}(A)=1}\label{eq:m1}\\
+\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=1} &= \Prob{\game{1}(A)=1}\label{eq:m2}\\
+\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=0} &= 1-\Prob{\game{1}(A)=1}\label{eq:m3}\\
+\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=0} &= 1-\Prob{\game{2}(A)=1}\label{eq:m4}
+\end{align}
 
@@
 $S \getsr \distr{\univ}{n}$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
-$\calX \getsr A^{\QryOracle}(\calS)$\\
-if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
+$M \getsr \Rep^{\HashOracle}(\calS)$\\
+$\calZ \getsr A^{\QryOracle}(\calS)$\\
+if $|\calZ| < t$ or $\calZ \cap \calS \neq \emptyset$ then \\
 \nudge Ret 0\\
-if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
+if $\exists z \in \calZ$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
 \nudge Ret 0\\
@@
 \oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\\\
+Ret $\Qry^{\HashOracle}(M,x)$\\\\
 %
@@
 \underline{$\game{3}(A)$}\\
-$\ell \getsr [q]$\\
-$c = 0$ \\%count will be used to keep track of queries made to $\QryOracle$\\
-$\win \gets \false$\\
+$\calY \gets \emptyset $\\
 $\rho_1,\rho_2 \getsr \Func{\univ,[m]}$\\
 $S \getsr \distr{\univ}{n}$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
-$\calX \getsr A^{\QryOracle}(\calS)$\\
-if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
-\nudge Ret 0\\
-if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
+$M \getsr \Rep^{\HashOracle}(\calS)$\\
+$\calZ \getsr A^{\QryOracle}(\calS)$\\
+$z_1,\cdots, z_t \getsr \calY $\\
+if $\exists i\in[1,t] \,\Qry^{\HashOracle}(M,z_i)=0$ then\\
 \nudge Ret 0\\
@@
 \oracle{$\QryOracle(x)$}\\
-$c=c +1$\\
-if $(c == \ell)$\\
-$\nudge \win = \true$\\
-$\nudge \mathrm{Ret} \nudge \Qry^{\HashOracle}(M,\tau,x)$\\
-else \\
-$\nudge \mathrm{Ret}\nudge 0$\\\\
+$\calY \gets \calY \cup x$\\
+Ret $\Qry^{\HashOracle}(M,x)$\\
 %
@@
 }
-\caption{Theorem \ref{thm1}:Game playing argument}\label{fig:Game}
+\caption{\Cref{thm1}:Game playing argument}\label{fig:Game}
 \end{figure}
@@
 $S \getsr \distr{\univ}{n}$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
+$M \getsr \Rep^{\HashOracle}(\calS)$\\
 When $A$ asks $\QryOracle(x)$:\\
-$\nudge$ Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
-When $A$ halts with output $\calX^{'}$: \\
-if $|\calX^{'}| < t$ or $\calX^{'} \cap \calS \neq \emptyset$ then \\
+$\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
+When $A$ halts with output $\calZ^{'}$: \\
+if $|\calZ^{'}| < t$ or $\calZ^{'} \cap \calS \neq \emptyset$ then \\
 \nudge Ret 0\\
-if $\exists x \in \calX^{'}$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
+if $\exists z \in \calZ^{'}$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
 \nudge Ret 0\\
@@
 $S \getsr \distr{\univ}{n}$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
+$M \getsr \Rep^{\HashOracle}(\calS)$\\
 When $A$ asks $\QryOracle(x)$:\\
-$\nudge$ Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
-When $A$ halts with output $\calX^{'}$: \\
-if $|\calX^{'}| < t$ or $\calX^{'} \cap \calS \neq \emptyset$ then \\
+$\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
+When $A$ halts with output $\calZ^{'}$: \\
+
+if $|\calZ^{'}| < t$ or $\calZ^{'} \cap \calS \neq \emptyset$ then \\
 \nudge Ret 0\\
-if $\exists x \in \calX^{'}$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
+if $\exists z \in \calZ^{'}$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
 \nudge Ret 0\\
@@
 }
-\caption{Theorem \ref{thm1}:Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
+\caption{\Cref{thm1}:Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
 \end{figure}
-
-From eqns. \ref{eq:m1}, \ref{eq:m2}, \ref{eq:m3} and \ref{eq:m4}, \tsnote{this can be compacted}
-\begin{eqnarray}
-\nonumber \Prob{\ExpPRF{F}{B_1} = 1} &=& .5\Prob{\ExpPRF{F}{B_1}=1\,|\,b=0} + .5\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=1}\\
-\nonumber 2\Prob{\ExpPRF{F}{B_1} = 1} &=& 1-\Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1}\\
-\nonumber (2\Prob{\ExpPRF{F}{B_1} = 1} - 1)  &=& \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1}\\
- \AdvPRF{F}{B_1} &=& \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1} \label{eq:1}\\
+\noindent
+From \Cref{eq:m1,eq:m2,eq:m3,eq:m4}, \acnote{compacted} \tsnote{this can be compacted}
+\begin{align}
+\nonumber \Prob{\ExpPRF{F}{B_1} = 1} &= .5\Prob{\ExpPRF{F}{B_1}=1\,|\,b=0} + .5\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=1}\\
+\nonumber 2\Prob{\ExpPRF{F}{B_1} = 1} &= 1-\Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1}\\
+\nonumber (2\Prob{\ExpPRF{F}{B_1} = 1} - 1)  &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1}\\
+ \AdvPRF{F}{B_1} &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1} \label{eq:1}\\
 \nonumber& &\\
-\nonumber \Prob{\ExpPRF{F}{B_2} = 1} &=& .5\Prob{\ExpPRF{F}{B_2}=1\,|\,b=0} + .5\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=1}\\
-\nonumber 2\Prob{\ExpPRF{F}{B_2} = 1} &=& 1-\Prob{\game{2}(A)=1} + \Prob{\game{1}(A)=1}\\
-\nonumber (2\Prob{\ExpPRF{F}{B_2} = 1} - 1)  &=& \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1}\\
- \AdvPRF{F}{B_2} &=& \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1} \label{eq:2}
-\end{eqnarray}
+\nonumber \Prob{\ExpPRF{F}{B_2} = 1} &= .5\Prob{\ExpPRF{F}{B_2}=1\,|\,b=0} + .5\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=1}\\
+\nonumber 2\Prob{\ExpPRF{F}{B_2} = 1} &= 1-\Prob{\game{2}(A)=1} + \Prob{\game{1}(A)=1}\\
+\nonumber (2\Prob{\ExpPRF{F}{B_2} = 1} - 1)  &= \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1}\\
+ \AdvPRF{F}{B_2} &= \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1} \label{eq:2a}
+\end{align}
 
 \noindent
-Adding eqn. \ref{eq:1} and \ref{eq:2}, we have
+Adding \Cref{eq:1,eq:2a}, we have
 \begin{equation}
-\AdvPRF{F}{B_2} +\AdvPRF{F}{B_1} = \Prob{\game{0}(A)=1} - \Prob{\game{2}(A)=1}\label{eq:2a}
+\AdvPRF{F}{B_2} +\AdvPRF{F}{B_1} = \Prob{\game{0}(A)=1} - \Prob{\game{2}(A)=1}\label{eq:2}
 \end{equation}
 
-In $\game{3}(A)$, assume, without loss of generality that $A$ halts with output $x$ immediately, if it asks $x$ to $\QryOracle$ and $\QryOracle$ returns $1$.
-\fixme{This only works when $t=1$!
-This is where the proof breaks down for the case of $t>1$.} Thus, all queries to $\QryOracle$ return 0 until the first one.
-Hence,
-
+\noindent
+In $\game{3}(A)$, $t$ elements are sampled from the $q$ queries and tested for false positives. The probability of selecting $t$ FP elements from the set of $q$ queries is $1/\dbinom{q}{t}$. So, 
 \begin{equation}
-\Prob{\game{2}(A)=1} \leq q \cdot \Prob{\game{3}(A)=1} = q \cdot \Prob{\game{3}(A)=1\,|\,\win=\true}\label{eq:3}
+\Prob{\game{2}(A)=1} = \frac{1}{\dbinom{q}{t}}\times\Prob{\game{3}(A)=1}\label{eq:3}
 \end{equation}
 
-In Fig. \ref{AGame3}, adversary $A'$ simulates $\game{3}(A)$. Since, adversary $A'$ exactly simulates $\game{3}(A)$ conditioned on $\win = \true$, 
-\begin{eqnarray}
-\nonumber \Prob{\game{3}(A)\,|\,\win=\true} &=& \Prob{A' \mbox{outputs FP}}\\
-& \leq & \epsilon,\mbox{ where } \epsilon = (1-e^{-kn/m})^k\label{eq:4}
-\end{eqnarray}
+\noindent
+The classical FP requirement considers only non-adaptive (and information-theoretic) adversaries and $A'$ is one such adversary simulating $\game{3}(A)$.
+\acnote{changed}\tsnote{The classical FP requirement considers only non-adaptive (and information-theoretic) adversaries.
+It suffices to say this.} From \Cref{fig:AGame3} and $\game{3}(A)$, it is evident that
+\begin{align}
+\nonumber \Prob{\game{3}(A)=1} &= q\Prob{A' \mbox{outputs FP}}\\
+& \leq q\epsilon,\mbox{ where } \epsilon = (1-e^{-kn/m})^k \label{eq:4}
+\end{align}
 
@@
 $\adversaryv{A'^{\HashOracle}}$\\
-$\ell \getsr [q]$, where $[q] = {0,1, \cdots, q-1}$\\
-$count = 0$\\
-$\rho_1,\rho_2 \getsr \Func{\univ,[m]}$\\
-$S \getsr \distr{\univ}{n}$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
+$\calY \gets \emptyset $ \\
+$\ell \getsr [q]$\\
+$c = 0$\\
+$\rho \getsr Func(U,[m])$\\
+$S \getsr \distr{U}{n}$\\
+$M \getsr \Rep^{\HashOracle}(\calS)$\\
 When $A$ asks $\QryOracle(x)$:\\
-$\nudge count = count + 1$\\
-\nudge if $count == \ell$\\
-$\nudge$ $\nudge r \gets \Qry^{\HashOracle}(M,\tau,x)$\\
+$\nudge c = c + 1$\\
+\nudge if $c == \ell$\\
+$\nudge$ $\nudge r \gets \Qry^{\HashOracle}(M,x)$\\
+$\nudge$ $\nudge \calY \gets \calY \cup x$\\
 \nudge else\\
@@
 \nudge Ret $r$\\
-When $A$ halts with output $\calX'$\\
-\nudge if $|\calX'| < t$ or $\calX' \cap \calS \neq \emptyset$ then \\
-\nudge\nudge Ret 0\\
-\nudge if $\exists x \in \calX^{'}$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
+When $A$ halts with output $\calZ^{'}$\\
+\nudge $z \gets \calY$\\
+\nudge if $\Qry^{\HashOracle}(M,z)=0$ then\\
 \nudge \nudge Ret 0\\
-\nudge Ret 1\\
+\nudge Ret 1\\\\
 %
@@
 }
-\caption{Theorem \ref{thm1}:Adversary $A'$ simulating $\game{3}(A)$} \label{AGame3}
+\caption{\Cref{thm1}:Adversary $A'$ simulating $\game{3}(A)$} \label{fig:AGame3}
 \end{figure}
 
-From eqn. \ref{eq:0}, \ref{eq:2a}, \ref{eq:3} and \ref{eq:4}: \\
-\begin{eqnarray}
-\nonumber \AdvFPSecHash{B_{\mathrm{lin}},t}{A} &-& \Prob{\game{2}(A)=1} =  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}   \\
-\nonumber \AdvFPSecHash{B_{\mathrm{lin}},t}{A}  &=&  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} + \Prob{\game{2}(A)=1}  \\
-\AdvFPSecHash{B_{\mathrm{lin}},t}{A} &\leq&  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  + q \cdot \epsilon
-\end{eqnarray}
+\noindent
+From \Cref{eq:0,eq:2,eq:3,eq:4} \\
+\begin{align}
+\nonumber \AdvFPSecHash{B_{\mathrm{lin}},t}{A} &- \Prob{\game{2}(A)=1} =  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}   \\
+\nonumber \AdvFPSecHash{B_{\mathrm{lin}},t}{A}  &=  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} + \Prob{\game{2}(A)=1}  \\
+\nonumber \AdvFPSecHash{B_{\mathrm{lin}},t}{A} &\leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  + \frac{q \cdot \epsilon}{\dbinom{q}{t}}\\
+\AdvFPSecHash{B_{\mathrm{lin}},t}{A} &\leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  + \frac{q}{\dbinom{q}{t}} \times  (1-e^{-kn/m})^k
+\end{align}
 \end{proof}
-
-\clearpage

### 2016-07-20 Theorem1_FP.tex
Modified Proofs

@@
 
-\fixme{Note: the following theorem is incorrect for $t>1$.  Or, at least, the proof does not cover $t>1$.}
+\fixme{Note: the following theorem is incorrect for $t>1$.  Or, at least, the proof does not cover $t>1$.}\acnote{Modified.}
 \begin{theorem}\label{thm1}
@@
 Let adversaries $B_1, B_2$ simulate $\game{1}(A)$ and $\game{2}(A)$ respectively as shown in \Cref{fig:BGame1}.
-When $b=1$, adversaries $B_1$ and $B_2$ exactly simulate $\game{0}(A)$ and $\game{1}(A)$.
-When $b=0$, adversary $B_1$ wins if $\game{1}(A)$ outputs 0; adversary $B_2$ wins if $\game{2}(A)$ returns 0.
-Thus we have
+When $b=0$, $B_1$ wins if $\game{1}(A)$ outputs 0; $B_2$ wins if $\game{2}(A)$ returns 0.
+When $b=1$, $B_1$ and $B_2$ exactly simulate $\game{0}(A)$ and $\game{1}(A)$.
+Thus, we have
 
@@
 $z_1,\cdots, z_t \getsr \calY $\\
-if $\exists i\in[1,t] \,\Qry^{\HashOracle}(M,z_i)=0$ then\\
+if $\exists i\in[1,t] \,\mbox{s.t.} \,\Qry^{\HashOracle}(M,z_i)=0$ then\\
 \nudge Ret 0\\
@@
 $\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
-When $A$ halts with output $\calZ^{'}$: \\
-if $|\calZ^{'}| < t$ or $\calZ^{'} \cap \calS \neq \emptyset$ then \\
+When $A$ halts with output $\calZ'$: \\
+if $|\calZ'| < t$ or $\calZ' \cap \calS \neq \emptyset$ then \\
 \nudge Ret 0\\
-if $\exists z \in \calZ^{'}$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
+if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
 \nudge Ret 0\\
@@
 $\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
-When $A$ halts with output $\calZ^{'}$: \\
+When $A$ halts with output $\calZ'$: \\
 
-if $|\calZ^{'}| < t$ or $\calZ^{'} \cap \calS \neq \emptyset$ then \\
+if $|\calZ'| < t$ or $\calZ' \cap \calS \neq \emptyset$ then \\
 \nudge Ret 0\\
-if $\exists z \in \calZ^{'}$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
+if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
 \nudge Ret 0\\
@@
 \noindent
-In $\game{3}(A)$, $t$ elements are sampled from the $q$ queries and tested for false positives. The probability of selecting $t$ FP elements from the set of $q$ queries is $1/\dbinom{q}{t}$. So, 
+In $\game{3}(A)$, $t$ elements are sampled from the $q$ queries with probability  $1/\dbinom{q}{t}$ and tested for false positives. So, 
 \begin{equation}
@@
 \nonumber \Prob{\game{3}(A)=1} &= q\Prob{A' \mbox{outputs FP}}\\
-& \leq q\epsilon,\mbox{ where } \epsilon = (1-e^{-kn/m})^k \label{eq:4}
+& \leq q\times(1-e^{-kn/m})^k \label{eq:4}
 \end{align}
 
-%\caption{Adversary $A^{'}$ simulating $\game{3}(A)$} \label{AGame3}
+%\caption{Adversary $A'$ simulating $\game{3}(A)$} \label{AGame3}
 \begin{figure}
@@
 \nudge Ret $r$\\
-When $A$ halts with output $\calZ^{'}$\\
+When $A$ halts with output $\calZ'$\\
 \nudge $z \gets \calY$\\
@@
 \nonumber \AdvFPSecHash{B_{\mathrm{lin}},t}{A}  &=  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} + \Prob{\game{2}(A)=1}  \\
-\nonumber \AdvFPSecHash{B_{\mathrm{lin}},t}{A} &\leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  + \frac{q \cdot \epsilon}{\dbinom{q}{t}}\\
 \AdvFPSecHash{B_{\mathrm{lin}},t}{A} &\leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  + \frac{q}{\dbinom{q}{t}} \times  (1-e^{-kn/m})^k

### 2016-07-20 Theorem2_FP.tex
Modified Proofs

@@
 \newcommand{\rhoK}{\rho(\langle j,x \rangle)}
+\fixme{Clean up to match style, language and typesetting (macros,
+  especially) of previous theorem.}\acnote{Modified.}
 
+Let $B_{\mathrm{lin}}=(\Hash,\Rep,\Qry)$ be the hash-based filter defined as earlier, except the private hash functions of the $\HashOracle'$s algorithm are $h_j(x) = \FK, \, j \in [1,k]$.
+Informally, if F is PRF secure and the filter has low FP-error in the non-adaptive setting, then $B_{\mathrm{lin}}$ is secure against adaptive FP-finding adversaries.
 \begin{theorem}\label{thm2}
-A hash-based filter with private hash functions $h_j(x) = \FK$ is secure in the false positive game of an adaptive adversary (A) who makes $q$ set-membership queries in time $O(t)$ , if F is PRF secure and the filter has low FP-error($\epsilon$) in the non-adaptive setting.
-Here, adversary $B$ attacks the PRF game in time $O(t)$, makes $q$ oracle queries, and
+Fix $k,m,n >0$.
+Let $B_{\mathrm{lin}}$ be the hash based filter just described.
+If there exists an adaptive adversary $A$ compatible with $\ExpFPPubHash{B_{\mathrm{lin},t}}{\cdot}$, then there exists an adversary $B$ attacking the PRF game such that
 \begin{equation}
-\AdvFPSecHash{B,t}{A} \leq  \AdvPRF{F}{B} + q \cdot \epsilon
+\AdvFPSecHash{B_\mathrm{lin},t}{A}\leq  \AdvPRF{F}{B}  + \frac{q}{\dbinom{q}{t}} \times  (1-e^{-kn/m})^k
 \end{equation}
-Note: $\FK$ provides domain separation and hence mutual independence, unlike hash functions in theorem \ref{thm1}
+Before giving the proof, it should be noted that $\FK$ provides domain separation and hence mutual independence, unlike hash functions in \Cref{thm1}
 \end{theorem}
 
-\begin{proof}
-We use a game playing argument similar to theorem \ref{thm1} to prove this theorem.
-In \game{0}(A), adversary attacks the FP game with private hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpFPSecHash{B,t}{A}$.
+\begin{proof}[\Cref{thm2}]
+We use a game playing argument similar to \Cref{thm1} to prove this theorem.
+In \game{0}(A), adversary attacks the FP game with private hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpFPSecHash{B_\mathrm{lin},t}{A}$.
 \begin{equation}
-\AdvFPSecHash{B,t}{A} = \Prob{\game{0}(A)=1}\label{eq:0T2}
+\AdvFPSecHash{B_\mathrm{lin},t}{A} = \Prob{\game{0}(A)=1}\label{eq:0T2}
 \end{equation}
-\game{1}(A) simulates $\ExpFPSecHash{B,t}{A}$ with a random function $\rho \getsr Func(U,[m])$ used to generate uniformly random  hash-indices with domain separation, of elements $x \in U$.
-Let $A^{'}$ be the non-adaptive friend of $A$.
-\game{2}(A) simulates behavior of $A^{'}$ as closely as possible.
-The three games are shown in Fig.
-\ref{fig:GameT2}.
+\noindent
+\game{1}(A) simulates $\ExpFPSecHash{B_\mathrm{lin},t}{A}$ with a random function $\rho \getsr Func(\univ,[m])$ used to generate uniformly random  hash-indices with domain separation, of elements $x \in \univ$.
+In $\game{2}(A)$, $t$ elements are sampled from the set of queries and tested for false positives.
+The three games are shown in \Cref{fig:GameT2}.
 
@@
 \underline{\game{0}(A)}\\
-$K \getsr \calK $\\
-$S \getsr \distr{U}{n}$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
-$\calX \getsr A^{\QryOracle}(\calS)$\\
-if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
+$K_1, K_2 \getsr \calK$\\
+$S \getsr \distr{\univ}{n}$\\
+$M \getsr \Rep^{\HashOracle}(\calS)$\\
+$\calZ \getsr A^{\QryOracle}(\calS)$\\
+if $|\calZ| < t$ or $\calZ \cap \calS \neq \emptyset$ then \\
 \nudge Ret 0\\
-if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
+if $\exists z \in \calZ$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
 \nudge Ret 0\\
@@
 \oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\\\
+Ret $\Qry^{\HashOracle}(M,x)$\\\\
 %
 \oracle{$\HashOracle(x)$}\\
-$h_j(x) = \FK$, for $j\in[1,k]$\\
+$h_j(x) = \FK$\\
 Ret $\left(h_1(x),\ldots,h_k(x)\right)$
@@
 \underline{\game{1}(A)}\\
-$\rho \getsr Func(U,[m])$\\
-$S \getsr \distr{U}{n}$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
-$\calX \getsr A^{\QryOracle}(\calS)$\\
-if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
+$\rho \getsr \Func{\univ,[m]}$\\
+$S \getsr \distr{\univ}{n}$\\
+$M \getsr \Rep^{\HashOracle}(\calS)$\\
+$\calZ \getsr A^{\QryOracle}(\calS)$\\
+if $|\calZ| < t$ or $\calZ \cap \calS \neq \emptyset$ then \\
 \nudge Ret 0\\
-if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
+if $\exists z \in \calZ$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
 \nudge Ret 0\\
@@
 \oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\\\
+Ret $\Qry^{\HashOracle}(M,x)$\\\\
 %
 \oracle{$\HashOracle(x)$}\\
-$h_j(x) = \rhoK $, for $j\in[1,k]$\\
+$h_j(x) = \rhoK $\\
 Ret $\left(h_1(x),\ldots,h_k(x)\right)$
@@
 {
-\underline{$\game{2}(A)$}\\
-$\ell \getsr [q]$, where $[q] = {0,1, \cdots, q-1}$\\
-$count = 0$ \\%count will be used to keep track of queries made to $\QryOracle$\\
-$win \gets false$\\
-$\rho \getsr Func(U,[m])$\\
-$S \getsr \distr{U}{n}$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
-$\calX \getsr A^{\QryOracle}(\calS)$\\
-if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
-\nudge Ret 0\\
-if $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$\\
+\underline{\game{2}(A)}\\
+$\calY \gets \emptyset $\\
+$\rho \getsr \Func{\univ,[m]}$\\
+$S \getsr \distr{\univ}{n}$\\
+$M \getsr \Rep^{\HashOracle}(\calS)$\\
+$\calZ \getsr A^{\QryOracle}(\calS)$\\
+$z_1,\cdots, z_t \getsr \calY $\\
+if $\exists i\in[1,t] \, \mbox{s.t.} \,\Qry^{\HashOracle}(M,z_i)=0$ then\\
 \nudge Ret 0\\
@@
 \oracle{$\QryOracle(x)$}\\
-$count=count +1$\\
-if $(count == \ell)$\\
-$\nudge win = true$\\
-$\nudge \mathrm{Ret} \nudge \Qry^{\HashOracle}(M,\tau,x)$\\
-else \\
-$\nudge \mathrm{Ret}\nudge 0$\\\\
+$\calY \gets \calY \cup x$\\
+Ret $\Qry^{\HashOracle}(M,x)$\\
 %
 \oracle{$\HashOracle(x)$}\\
-$h_j(x) = \rhoK$, for $j\in[1,k]$\\
+$h_j(x) = \rhoK$\\
 Ret $\left(h_1(x),\ldots,h_k(x)\right)$
@@
 }
-\caption{Theorem \ref{thm2}:Game playing argument}\label{fig:GameT2}
+\caption{\Cref{thm2}:Game playing argument}\label{fig:GameT2}
 \end{figure}
 
-In Fig. \ref{fig:BGame1T2}, adversary $B$ simulates $\game{1}(A)$ and $\game{2}(A)$ for $b=1$ and $b=0$ respectively .
+\noindent
+In \Cref{fig:BGame1T2}, adversary $B$ simulates $\game{0}(A)$ and $\game{1}(A)$ for $b=1$ and $b=0$ respectively .
 
-%\caption{Adversary $B$ and $A^{'}$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}
+%\caption{Adversary $B$ and $A'$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}
 \begin{figure}
@@
 {
-$\experimentv{Adversary \nudge B^{\calO}:}$\\
-$S \getsr \distr{U}{n}$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
+$\adversaryv{B^{\calO}}$\\
+$K_1 \getsr \calK $\\
+$S \getsr \distr{\univ}{n}$\\
+$M \getsr \Rep^{\HashOracle}(\calS)$\\
 When $A$ asks $\QryOracle(x)$:\\
-$\nudge$ Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
-When $A$ halts with output $\calX^{'}$: \\
-if $|\calX^{'}| < t$ or $\calX^{'} \cap \calS \neq \emptyset$ then \\
+$\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
+When $A$ halts with output $\calZ'$: \\
+if $|\calZ'| < t$ or $\calZ' \cap \calS \neq \emptyset$ then \\
 \nudge Ret 0\\
-if $\exists x \in \calX^{'}$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
+if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
 \nudge Ret 0\\
@@
 {
-$\experimentv{Adversary \nudge A^{'\HashOracle}:}$\\
-$\ell \getsr [q]$, where $[q] = {0,1, \cdots, q-1}$\\
-$count = 0$\\
+$\adversaryv{A'^{\HashOracle}}$\\
+$\calY \gets \emptyset $ \\
+$\ell \getsr [q]$\\
+$c = 0$\\
 $\rho \getsr Func(U,[m])$\\
 $S \getsr \distr{U}{n}$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
+$M \getsr \Rep^{\HashOracle}(\calS)$\\
 When $A$ asks $\QryOracle(x)$:\\
-$\nudge cnt = cnt + 1$\\
-\nudge if $count == \ell$\\
-$\nudge$ $\nudge r \gets \Qry^{\HashOracle}(M,\tau,x)$\\
+$\nudge c = c + 1$\\
+\nudge if $c == \ell$\\
+$\nudge$ $\nudge r \gets \Qry^{\HashOracle}(M,x)$\\
+$\nudge$ $\nudge \calY \gets \calY \cup x$\\
 \nudge else\\
@@
 \nudge Ret $r$\\
-When $A$ halts with output $\calX^{'}$\\
-\nudge if $|\calX^{'}| < t$ or $\calX^{'} \cap \calS \neq \emptyset$ then \\
-\nudge\nudge Ret 0\\
-\nudge if $\exists x \in \calX^{'}$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
+When $A$ halts with output $\calZ'$\\
+\nudge $z \gets \calY$\\
+\nudge if $\Qry^{\HashOracle}(M,z)=0$ then\\
 \nudge \nudge Ret 0\\
@@
 \oracle{$\HashOracle(x)$}\\
-$\mathrm{Ret} \nudge \rhoK$, for $j\in[1,k]$
+$\mathrm{Ret} \nudge \rhoK$
 }
 }
-\caption{Theorem \ref{thm2}:Adversary $B$ and $A^{'}$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively }\label{fig:BGame1T2}
+\caption{\Cref{thm2}:Adversary $B$ and $A'$ simulating $\game{0}(A)$, $\game{1}(A)$ and $\game{2}(A)$ respectively }\label{fig:BGame1T2}
 \end{figure}
 
-\begin{eqnarray}
-\Prob{\ExpPRF{F}{B} = 1|b=1} &=& \Prob{\game{0}(A)=1}\label{eq:m1T2}\\
-\Prob{\ExpPRF{F}{B} = 1|b=0} &=& 1-\Prob{\game{1}(A)=1}\label{eq:m2T2}
-\end{eqnarray}
+\begin{align}
+\Prob{\ExpPRF{F}{B} = 1|b=1} &= \Prob{\game{0}(A)=1}\label{eq:m1T2}\\
+\Prob{\ExpPRF{F}{B} = 1|b=0} &= 1-\Prob{\game{1}(A)=1}\label{eq:m2T2}
+\end{align}
 
-From eqns. \ref{eq:m1T2}, \ref{eq:m2T2},
-\begin{eqnarray}
-\nonumber \Prob{\ExpPRF{F}{B} = 1} &=& .5\Prob{\ExpPRF{F}{B_1}=1|b=0} + .5\Prob{\ExpPRF{F}{B_1} = 1|b=1}\\
-\nonumber 2\Prob{\ExpPRF{F}{B} = 1} &=& 1-\Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1}\\
-\nonumber (2\Prob{\ExpPRF{F}{B} = 1} - 1)  &=& \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1}\\
- \AdvPRF{F}{B} &=& \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1} \label{eq:1T2}
-\end{eqnarray}
+\noindent
+From \Cref{eq:m1T2,eq:m2T2},
+\begin{align}
+\nonumber \Prob{\ExpPRF{F}{B} = 1} &= .5\Prob{\ExpPRF{F}{B_1}=1|b=0} + .5\Prob{\ExpPRF{F}{B_1} = 1|b=1}\\
+\nonumber 2\Prob{\ExpPRF{F}{B} = 1} &= 1-\Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1}\\
+\nonumber (2\Prob{\ExpPRF{F}{B} = 1} - 1)  &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1}\\
+ \AdvPRF{F}{B} &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1} \label{eq:1T2}
+\end{align}
 
-Following a similar argument from theorem \ref{thm1},
+\noindent
+Following a similar argument from \Cref{thm1}\fixme{For $t>1$, proof fails for $t>1$}\acnote{Modified.}
 \begin{equation}
-\Prob{\game{1}(A)=1} \leq q \cdot \Prob{\game{2}(A)=1} = q \cdot \Prob{\game{2}(A)=1|win=true}\label{eq:3T2}
+\Prob{\game{1}(A)=1} = \frac{1}{\dbinom{q}{t}}\times\Prob{\game{2}(A)=1}\label{eq:3T2}
 \end{equation}
-\begin{eqnarray}
-\nonumber \Prob{\game{2}(A)|win=true} &=& \Prob{A^{'} \mathrm{outputs \nudge FP}}\\
-& \leq & \epsilon, \nudge \mathrm{where} \nudge \epsilon = (1-e^{-kn/m})^k\label{eq:4T2}
-\end{eqnarray}
 
-From eqn. \ref{eq:0T2}, \ref{eq:1T2}, \ref{eq:3T2},  and \ref{eq:4T2}: \\
-\begin{eqnarray}
-\nonumber \AdvFPSecHash{B,t}{A} &-& \Prob{\game{1}(A)=1} =  \AdvPRF{F}{B}   \\
-\nonumber \AdvFPSecHash{B,t}{A}  &=&  \AdvPRF{F}{B} + \Prob{\game{1}(A)=1}  \\
-\AdvFPSecHash{B,t}{A} &\leq&  \AdvPRF{F}{B}  + q \cdot \epsilon
-\end{eqnarray}
+\begin{align}
+\nonumber \Prob{\game{2}(A)=1} &= q\Prob{A' \mbox{outputs FP}}\\
+& \leq q \times (1-e^{-kn/m})^k \label{eq:4T2}
+\end{align}
+
+\noindent
+From \Cref{eq:0T2,eq:1T2,eq:3T2,eq:4T2}: \\
+\begin{align}
+\nonumber \AdvFPSecHash{B_\mathrm{lin},t}{A} &- \Prob{\game{1}(A)=1} =  \AdvPRF{F}{B}   \\
+\nonumber \AdvFPSecHash{B_\mathrm{lin},t}{A}  &=  \AdvPRF{F}{B} + \Prob{\game{1}(A)=1}  \\
+\AdvFPSecHash{B_\mathrm{lin},t}{A} &\leq  \AdvPRF{F}{B}  + \frac{q}{\dbinom{q}{t}} \times  (1-e^{-kn/m})^k
+\end{align}
 

### 2016-07-20 Theorem1_FP.tex
clean up to theorem 5.1

@@
 The $\Rep$ and $\Qry$ algorithms are the standard (determinisitic) BF ones.
-\tsnote{Should define these someplace.}\acnote{Deterministic Rep and Qry defined(without side info)} $\Rep\colon [\univ]^n \rightarrow \Sigma^m$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m$.
-$\Qry\colon \Sigma^m \times \univ \rightarrow \bits$ takes a representation $M$ and an element $x \in \univ$, and returns a bit indicating presence/absence of $x$.
 The following result shows, informally, that if~$F$ is a good PRF and the (non-adaptive) FP rate is sufficiently small, then $B_\mathrm{lin}$ is secure against adaptive FP-finding adversaries.
@@
 \[
-\AdvFPSecHash{B_{\mathrm{lin}},t}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  + \frac{q}{\dbinom{q}{t}} \times  (1-e^{-kn/m})^k
+\AdvFPSecHash{B_{\mathrm{lin}},t}{A} \leq  \AdvPRF{F}{B_1} +
+\AdvPRF{F}{B_2}  +{\dbinom{q}{t}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^t
 \]
 \end{theorem}
-Before giving the proof, we note that  $(1-e^{-kn/m})^k \rightarrow 0$ as the ratio between the bit-length of the representation~$M$ and the size of the represented set~$S$, i.e.,$m/n$ tends to $\infty$.
+Before giving the proof, we note that Kirsch and Mitzenmacher~\cite{xxx} show
+that the ($t=1$, non-adaptive) FP-probability for~$B_\mathrm{lin}$ is
+always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
+rate of convergence is faster than~$1/n$.  The factor of $\dbinom{q}{t}$ arises as a result
+of removing adaptivity.  Finally, $\dbinom{q}{t} \leq q^t$ (with
+reasonable tightness when~$t$ is small) in which case the final term in the bound behaves as 
+$(q (1-e^{-kn/m})^k + O(q/n) )^t$; loosely, the bound one expects for
+trying to find a single FP in each of~$t$ independent``rounds'', each round
+consisting of~$q$ attempts.
+%Before giving the proof, we note that  $(1-e^{-kn/m})^k \rightarrow 0$ as the ratio between the bit-length of the representation~$M$ and the size of the represented set~$S$, i.e.,$m/n$ tends to $\infty$.
 %

### 2016-07-20 generic.tex
messing with generic syntax section

--- 2016-07-14 generic.tex
@@
-\section{Secure Data Structures, Abstractly}
-We focus on the case of static data structures only (for now).
+\section{Secure Set Representation, Abstractly}
+We focus on the case of static set-representations only (for now).
 \def\pub{{\sf pub}}
+\def\aux{{\sf aux}}
 
@@
 
-\begin{definition}
-A (randomized) \emph{data structure} is a pair of algorithms $(\Rep, \Qry)$
+\begin{definition} %\tsnote{We need a more descriptive name than ``data structure'' :)}
+A (randomized) \emph{set-representation primitive} is a pair of algorithms $(\Rep, \Qry)$
 parameterized by a collection $\mathcal{S}$ of subsets of~$U$ and a collection
-of supported queries $\mathcal{Q}$ and having the following syntax:
+of supported queries $\mathcal{Q}=\{q \colon \mathcal{S} \to \mathbb{R}\}$, where:
 \begin{itemize}
 \item $\Rep$ is a randomized algorithm taking as input $S \in \mathcal{S}$,
-and outputting a pair of values $(\pub, M)$.
-\item $\Qry$ is a deterministic algorithm that takes as input $\pub, M$,
-and a query $q\in \mathcal{Q}$, and returns an answer~$a$.
+and outputting a pair of values $(M,\aux)$, the \emph{representation} (of~$S$) and the \emph{auxillary information} (of~$M$).
+\item $\Qry$ is a deterministic algorithm that takes as input $M, \aux$,
+and a query $q\in \mathcal{Q}$, and returns value~$a$.
 \end{itemize}
@@
 \begin{eqnarray}
-\Pr[(\pub, M) \leftarrow \Rep(S) : \Qry(\pub, M, q) \neq q(S)] \leq \epsilon, \label{eqn:correctness}
+\Pr[(M,\aux) \getsr \Rep(S) : \Qry(M, \aux, q) \neq q(S)] \leq \epsilon, \label{eqn:correctness}
 \end{eqnarray}
-where $q(S)$ denotes the correct answer to the query $q$ on the set~$S$.
-The \emph{size} of a data structure is the maximum length of any~$M$ that can be
+%where $q(S)$ denotes the correct answer to the query $q$ on the set~$S$.
+The \emph{size} of a data structure is the maximum (bit)length of any~$M$ that can be
 output by $\Rep$.
@@
 
-Our treatment of $\pub, M$ is not symmetric, since we only count $M$ against the size
-of the data structure. When we define security
-we may give the attacker $\pub$ but not~$M$, and in that case the data structure cannot
-trivially make everything part of~$\pub$.
-
-It is not hard to see Bloom filters are one possible instantiation of the above. If we fix some
-size bound~$n$, then $\mathcal{S}$ becomes the collection of all subsets of $U$
-of size (at most)~$n$. We also fix $\mathcal{Q} = U$, where a query ``$x$'' has
-the semantics ``is $x$ in $S$?'' Algorithm $\Rep$, which has values $k, m$ hardwired,
-chooses a set of hash functions $h_1, \ldots, h_k$ and computes an $m$-bit
-array in the usual way; a natural possibility is to set $\pub = (h_1, \ldots, h_k)$ and
-to let $M$ be the bit array.
+Our treatment of $M,\aux$ is not symmetric, since we only count $M$ against the size
+of the set-representation. When we define security
+we may give the attacker $\aux$ but not~$M$, and in that case the set-representation cannot
+trivially make everything part of~$\aux$. \tsnote{Encoding secrets into~$M$ may cause some headaches in
+  the security definitions; we'll see. }
+%\tsnote{By the way, I'm coming around to the
+%  viewpoint that it is fair to include in the ``size'' of the
+%  representation any secret information.  In makes more difficult
+%  comparisons to classical lower-bounds (which [NY] makes, incorrectly
+% IMO), but it does seem fair to say ``this is how many bits of memory
+% you need to allocate to represent this set \emph{securely}.''}
 
@@
 
+\heading{Examples.}
+It is not hard to see Bloom filters are one possible instantiation of the above. If we fix some
+size bound~$n$, then $\mathcal{S}$ becomes the collection of all subsets of $U$
+of size (at most)~$n$. We also fix $\mathcal{Q} = U$, where a query ``$x$'' has
+the semantics ``is $x$ in $S$?'' Algorithm $\Rep$, which has values $k, m$ hardwired,
+chooses a set of hash functions $h_1, \ldots, h_k$ and computes an $m$-bit
+array in the usual way; a natural possibility is to set $\aux = (h_1, \ldots, h_k)$ and
+to let~$M$ be the bit array.  
+%\tsnote{If $\mathcal{Q}=U$ and we use the
+%  semantics you suggest, then isn't Equation~\ref{eqn:correctness}
+%  both correctness and soundness?  If so, I don't see how this
+%  captures the classical BF, which requires $\epsilon=0$ for one kind
+%  of error, but allows $\epsilon>0$ for the other. } 
+%\jnote{The definition does not distinguish
+%  between elements in the set (for which $q(S)=1$) or outside the set (for which
+%  $q(S)=0$). But a Bloom filter does satisfy Equation~\ref{eqn:correctness} in either case.}
+%  \jnote{In that sense, I am using ``soundness'' and ``correctness'' interchangeably here.}
+  \jnote{I'm not tied to allowing false negatives when we specialize the definition to the case
+  of set-membership queries. But in the abstract definition it seems unclear why one would choose
+  some queries on which error is ok and other queries where error is not allowed. Though if one
+  wanted to be general, one could simply have two (disjoint) sets of queries $\mathcal{Q}_1, \mathcal{Q}_2$
+  where error is allowed on the former but not on the latter.}
+
 \subsection{Adversarial Soundness}
@@
 Equation~(\ref{eqn:correctness}) is a non-adaptive version of correctness;
-we are interested in defining an adaptive (i.e., adversarial) notion of correctness.
+we are interested in defining an adaptive (i.e., adversarial) notion
+of correctness. \tsnote{Correctness?  Or soundness?}
 The general style of the definition is as follows:
 first, a set $S$ is chosen according to some distribution over~$\mathcal{S}$ and then
-$\Rep(S)$ is run to generate $(\pub, M)$. (Unless stated otherwise, we assume
+$\Rep(S)$ is run to generate $(\aux, M)$. (Unless stated otherwise, we assume
 security holds for all distributions and thus for all sets $S$.)
-The attacker $A$ is given $\pub$ and (possibly)~$S$;
-in addition, $A$ is given \emph{oracle access} to~$\Qry(\pub, M, \cdot)$.
+The attacker $A$ is given $\aux$ and (possibly)~$S$;
+in addition, $A$ is given \emph{oracle access} to~$\Qry(\aux, M, \cdot)$.
 If $(\Rep, \Qry)$ is defined in the random-oracle model, then
@@
 $A$ \emph{succeeds} if it outputs $t$ distinct queries $q_1, \ldots, q_t \in \mathcal{Q}$ for which
-$\Qry(\pub, M, q_i) \neq q_i(S)$ for all~$i$.
+$\Qry(\aux, M, q_i) \neq q_i(S)$ for all~$i$.
 Roughly, we say that a data structure is $(t,\epsilon')$-FP-secure if the probability that
@@
 functions in $M$ (and thus increase the size of the data structure); it also captures the fp-pub
-notion if we put the hash function in~$\pub$. It captures the fp-bb-pub notion in the
+notion if we put the hash function in~$\aux$. \tsnote{Except that the win condition allows both
+false-positives and false-negatives, given the correctness requirement
+in the syntax.} \jnote{True. But if false negatives cannot occur at all (by design of
+the data structure, not by definition of the primitive), then the attacker cannot hope to win
+by finding a false negative.} It captures the fp-bb-pub notion in the
 random-oracle model.
@@
 \jnote{One option is to define the adversary's \emph{advantage} as the difference between
-its success probability and the success probability of the above, trivial attack. Just a thought.}
+its success probability and the success probability of the above,
+trivial attack. Just a thought.}
+\tsnote{Or, perhaps by recasting security
+  as distinguishing between $\Qry(\aux,M,\cdot)$ and an oracle that
+  returns 0,1 according to Bernoulli with paramter~$\epsilon$.}
 
@@
 Lifting their definition to our setting, the experiment is similar but the attacker
-succeeds only if it outputs a single query $q$ for which $\Qry(\pub, M, q) \neq q(S)$ \emph{subject
+succeeds only if it outputs a single query $q$ for which $\Qry(\aux, M, q) \neq q(S)$ \emph{subject
 to the restriction that it did not query $q$ to its $\Qry$ oracle}.
@@
 \jnote{Actually, I am now unsure what the right way to define it is. It seems natural
-to give the attacker $\pub$. But if we give them $\pub$ and $M$ then they have everything.
-If $S$ has high min-entropy (element-wise), then it might still be possible to have security here.}
+to give the attacker $\aux$. But if we give them $\aux$ and $M$ then they have everything.
+If $S$ has high min-entropy (element-wise), then it might still be
+possible to have security here.}\tsnote{I think we will always bump up
+against the (element-wise) min-entropy of the distribution over~$S$,
+at least in the ``one-wayness'' style definition that I had been imagining. }
 There are several possible definitions:
@@
 \item A ``one-wayness'' definition where $S$ has high min-entropy (element-wise), and we
-give the attacker $\pub$ and either $M$ or oracle access to $\Qry$. The attacker
+give the attacker $\aux$ and either $M$ or oracle access to $\Qry$. The attacker
 succeeds if it can output an element in~$S$.
@@
 \item An ``indistinguishability'' definition where either $S_0$ or $S_1$ is used, and the attacker
-must determine which. Here the attacker is given $\pub$ but only oracle access to $\Qry$, and
-it is disallowed from asking any query $q$ for which $q(S_0) \neq q(S_1)$. 
+must determine which. Here the attacker is given $\aux$ but only oracle access to $\Qry$, and
+it is disallowed from asking any query $q$ for which $q(S_0) \neq
+q(S_1)$. \tsnote{How will the adversary know that a query satisfies
+  this in (say) the case of the classical BF?  We can, of course,
+enforce it in the experiment, but then our resource accounting risks
+overcounting the number of queries.} \jnote{I was assuming the attacker knows $S_0, S_1$.}
+\tsnote{Also, we need that, in general, $\aux$ itself
+does not leak information about~$S_0$ vs.\ $S_1$. } \jnote{Sure, this would be implied
+by the definition in this case.}
 \end{enumerate}

### 2016-07-20 intro.tex
messing with generic syntax section

@@
-\jnote{Are we being too specific by focusing on hash-based
-set-membership only? It would be nice to give general definitions
-that apply to arbitrary data structures (constructed in arbitrary
-ways) and then only later specialized to hash-based Bloom filters.
-(Put this in an appendix for now, until we see how things play
-out.)}
+%\jnote{Are we being too specific by focusing on hash-based
+%set-membership only? It would be nice to give general definitions
+%that apply to arbitrary data structures (constructed in arbitrary
+%ways) and then only later specialized to hash-based Bloom filters.
+%(Put this in an appendix for now, until we see how things play
+%out.)}
 

### 2016-07-20 generic.tex
messing with generic syntax section

@@
 \item $\Rep$ is a randomized algorithm taking as input $S \in \mathcal{S}$,
-and outputting a pair of values $(M,\aux)$, the \emph{representation} (of~$S$) and the \emph{auxillary information} (of~$M$).
+and outputting a pair of strings $(M,\aux)$, the \emph{representation} (of~$S$) and the \emph{auxillary information} (of~$M$).
 \item $\Qry$ is a deterministic algorithm that takes as input $M, \aux$,
@@
 %where $q(S)$ denotes the correct answer to the query $q$ on the set~$S$.
-The \emph{size} of a data structure is the maximum (bit)length of any~$M$ that can be
+The \emph{size} of a data structure is the maximum length of any~$M$ that can be
 output by $\Rep$.
@@
 chooses a set of hash functions $h_1, \ldots, h_k$ and computes an $m$-bit
-array in the usual way; a natural possibility is to set $\aux = (h_1, \ldots, h_k)$ and
+array in the usual way; a natural possibility is to set $\aux = (h_1, \ldots, h_k)$ (encoded as a string) and
 to let~$M$ be the bit array.  

### 2016-07-20 generic.tex
updates to generic.tex

@@
-\section{Secure Set Representation, Abstractly}
-We focus on the case of static set-representations only (for now).
+\section{Secure Multiset Representation}
 \def\pub{{\sf pub}}
@@
 
-\subsection{Syntax}
-Fix a universe $U$.
+\heading{Preliminaries. }
+When~$\univ$ is a set and $n>0$ is an integer, we let $[\univ]^n$ denote the set of all size-$n$ subsets of~$\univ$.
+We write $x \getsr \univ$ to denote sampling an element from~$\univ$ and assigning this to~$x$, and we extend this notation to randomized algorithms.
 
-\begin{definition} %\tsnote{We need a more descriptive name than ``data structure'' :)}
-A (randomized) \emph{set-representation primitive} is a pair of algorithms $(\Rep, \Qry)$
-parameterized by a collection $\mathcal{S}$ of subsets of~$U$ and a collection
+\subsection{Static (Multi)set-representations}
+\begin{definition} %\tsnote{We need a more descriptive name than ``set-representation'' :)}
+\tsnote{I think this generalizes pretty easily to multisets.}
+Fix a universe~$U$ and an alphabet~$\Sigma$.  A \emph{static (multi)set-representation primitive} is a pair of algorithms $(\Rep, \Qry)$
+parameterized by a collection $\mathcal{S}$ of multisets, each consisting of elements from~$U$ and a collection
 of supported queries $\mathcal{Q}=\{q \colon \mathcal{S} \to \mathbb{R}\}$, where:
@@
 \item $\Rep$ is a randomized algorithm taking as input $S \in \mathcal{S}$,
-and outputting a pair of strings $(M,\aux)$, the \emph{representation} (of~$S$) and the \emph{auxillary information} (of~$M$).
+and outputting a pair of strings $(M,\aux)$, the \emph{representation} $M \in \Sigma^*$ (of~$S$) 
+and the \emph{auxillary information} $\aux \in \Sigma^*$ (of~$M$).
 \item $\Qry$ is a deterministic algorithm that takes as input $M, \aux$,
@@
 \end{itemize}
-A data structure is \emph{$\epsilon$-correct} if for all $S \in \mathcal{S}$ and
+A set-representation is \emph{$\epsilon$-correct} if for all $S \in \mathcal{S}$ and
 all $q \in \mathcal{Q}$ it holds that
@@
 %where $q(S)$ denotes the correct answer to the query $q$ on the set~$S$.
-The \emph{size} of a data structure is the maximum length of any~$M$ that can be
+The \emph{size} of a set-representation is the maximum (bit)length of any~$M$ that can be
 output by $\Rep$.
@@
   where error is allowed on the former but not on the latter.}
+We note that while our correctness condition does not distinguish among types of errors, it also does not preclude instantiations (like the classical Bloom filter) that admit only one type of error, e.g.
+false-positives.
+
+Setting $\Sigma=\bits^{\leq L}$ allows one to store a bitstring of length at most~$L$ at each location.
+This allows our syntax to capture the cuckoo-hashing construction from NY, as well as the ``garbled Bloom filter'' from Dong, Chen and Wen~\cite{xxx}, among other things.
+Setting $\Sigma=\mathbb{N}$ would allow for the storage of counters (say) at each position in~$M$, and a query ``$x$'' with the semantics ``what is the multiplicity of~$x$ in~$S$.''  (This does not capture counting Bloom filters, or the like, which do not have static representations.)  \tsnote{I guess this can all be accomplished with $\Sigma=\bits^*$, but it isn't necessarily the ``natural'' way.}
+%Our syntax also does not capture filters that are mutable, that is, whose representation may change over time.
+On the other hand, we can state a simple correctness condition for these kinds of filters; this will not be true when we further generalize to capture, properly, counters and mutability.
 
@@
 $\Qry(\aux, M, q_i) \neq q_i(S)$ for all~$i$.
-Roughly, we say that a data structure is $(t,\epsilon')$-FP-secure if the probability that
+Roughly, we say that a set-representation is $(t,\epsilon')$-FP-secure if the probability that
 any polynomial-time attacker succeeds is at most~$\epsilon'$. A full definition
@@
 if we put the hash
-functions in $M$ (and thus increase the size of the data structure); it also captures the fp-pub
+functions in $M$ (and thus increase the size of the set-representation); it also captures the fp-pub
 notion if we put the hash function in~$\aux$. \tsnote{Except that the win condition allows both
@@
 in the syntax.} \jnote{True. But if false negatives cannot occur at all (by design of
-the data structure, not by definition of the primitive), then the attacker cannot hope to win
+the set-representation, not by definition of the primitive), then the attacker cannot hope to win
 by finding a false negative.} It captures the fp-bb-pub notion in the
@@
 the attacker tries random queries $q_1, q_2, \ldots$ until it finds $t$ queries for which the
-data structure returns an incorrect answer.\footnote{This assumes the attacker
+set-representation returns an incorrect answer.\footnote{This assumes the attacker
 knows the true set $S$, which need not be the case.} Roughly speaking,
-if the data structure is $\epsilon$-correct then the attacker expects to find a query on which
+if the set-representation is $\epsilon$-correct then the attacker expects to find a query on which
 an incorrect result is returned
@@
 hope for
-is that if the data structure is $\epsilon$-correct then for any desired bound $T$
-the data structure is $(t, \bin(T,\epsilon; t))$-FP-secure against any attacker making
+is that if the set-representation is $\epsilon$-correct then for any desired bound $T$
+the set-representation is $(t, \bin(T,\epsilon; t))$-FP-secure against any attacker making
 at most $T$~queries. \jnote{Need to find different terms to use for a query $q \in \mathcal{Q}$
@@
 \item There is a contrived scheme that is $(2, 0)$-FP-secure but not NY-secure at all; the basic idea is
-to have a data structure that always has \emph{exactly one} false positive that is easy to find
+to have a set-representation that always has \emph{exactly one} false positive that is easy to find
 given the public information.
@@
 \subsection{Privacy}
-One can also consider the orthogonal notion of privacy for a data structure.
+One can also consider the orthogonal notion of privacy for a set-representation.
 \jnote{Actually, I am now unsure what the right way to define it is. It seems natural

### 2016-07-21 generic.tex
generic

@@
 
-\subsection{Adversarial Soundness}
+\subsection{Adversarial Correctness}
 \heading{FP security.}
@@
 we are interested in defining an adaptive (i.e., adversarial) notion
-of correctness. \tsnote{Correctness?  Or soundness?}
+of correctness.
+
 The general style of the definition is as follows:
-first, a set $S$ is chosen according to some distribution over~$\mathcal{S}$ and then
-$\Rep(S)$ is run to generate $(\aux, M)$. (Unless stated otherwise, we assume
+first, a set~$S$ is chosen according to some distribution over~$\mathcal{S}$ and then
+$\Rep(S)$ is run to generate $(M,\aux)$. (Unless stated otherwise, we assume
 security holds for all distributions and thus for all sets $S$.)
 The attacker $A$ is given $\aux$ and (possibly)~$S$;
-in addition, $A$ is given \emph{oracle access} to~$\Qry(\aux, M, \cdot)$.
-If $(\Rep, \Qry)$ is defined in the random-oracle model, then
-$A$ is given access to the random oracle as well.
-$A$ \emph{succeeds} if it outputs $t$ distinct queries $q_1, \ldots, q_t \in \mathcal{Q}$ for which
-$\Qry(\aux, M, q_i) \neq q_i(S)$ for all~$i$.
+in addition, $A$ is given \emph{oracle access} to~$\Qry(M,\aux,\cdot)$.
+If $(\Rep, \Qry)$ is defined in the random-oracle model, then~$A$ is given access to the random oracle as well.
+The adversary \emph{succeeds} if it outputs~$t$ distinct queries $q_1, \ldots, q_t \in \mathcal{Q}$ for which
+$\Qry(\aux, M, q_i) \neq q_i(S)$ for all~$i \in [t]$
+\tsnote{I will typeset this into an experiment.}
+
 Roughly, we say that a set-representation is $(t,\epsilon')$-FP-secure if the probability that
-any polynomial-time attacker succeeds is at most~$\epsilon'$. A full definition
-would also bound the number of queries to $\Qry$ (and the random oracle) made
-be the attacker; it is useful to make the convention that if $A$ outputs
+any polynomial-time attacker succeeds is at most~$\epsilon'$. \tsnote{$t$ might be a bad choice, since it looks like ``time''.}
+A full definition would also bound the number of queries to $\Qry$ (and the random oracle) made
+be the attacker; it is useful to make the convention that if~$A$ outputs
 $q_1, \ldots, q_t$ then it must have made those queries to its oracle previously.
 
-The notion of FP-security defined above captures the fp-prv notion for Bloom filters
-if we put the hash
-functions in $M$ (and thus increase the size of the set-representation); it also captures the fp-pub
-notion if we put the hash function in~$\aux$. \tsnote{Except that the win condition allows both
-false-positives and false-negatives, given the correctness requirement
-in the syntax.} \jnote{True. But if false negatives cannot occur at all (by design of
-the set-representation, not by definition of the primitive), then the attacker cannot hope to win
-by finding a false negative.} It captures the fp-bb-pub notion in the
-random-oracle model.
+The notion of security defined above captures the fp-prv notion for Bloom filters
+if we put the hash functions in~$M$ (and thus increase the size of the set-representation); it also captures the fp-pub
+notion if we put the hash function in~$\aux$. 
+%\tsnote{Except that the win condition allows both
+%false-positives and false-negatives, given the correctness requirement
+%in the syntax.} 
+%\jnote{True. But if false negatives cannot occur at all (by design of
+%the set-representation, not by definition of the primitive), then the attacker cannot hope to win
+%by finding a false negative.} 
+It captures the fp-bb-pub notion in the random-oracle model.
 
@@
 is always a trivial attack in which
-the attacker tries random queries $q_1, q_2, \ldots$ until it finds $t$ queries for which the
+the attacker tries random queries $q_1, q_2, \ldots$ until it finds~$t$ queries for which the
 set-representation returns an incorrect answer.\footnote{This assumes the attacker
-knows the true set $S$, which need not be the case.} Roughly speaking,
+knows the true set~$S$, which need not be the case.} Roughly speaking,
 if the set-representation is $\epsilon$-correct then the attacker expects to find a query on which
-an incorrect result is returned
-every $1/\epsilon$ tries; thus, an
-attacker making $t/\epsilon$ queries succeeds with constant probability.
+an incorrect result is returned every $1/\epsilon$ tries; thus, an
+attacker making $O(t/\epsilon)$ queries succeeds with constant probability (almost always).
 
@@
 probability~$\epsilon$, then $N$ follows the well-studied binomial distribution.
-Let $\bin(T, \epsilon; t)$ denote the probability that $N \geq t$. So the best security we can
-hope for
+Let $\bin(T, \epsilon; t)$ denote the probability that $N \geq t$. \tsnote{Viewed another way, we could let~$T$ be a negative binomial RV, and ask how many queries are needed (w.h.p) for $N \geq t$.} 
+So the best security we can hope for
 is that if the set-representation is $\epsilon$-correct then for any desired bound $T$

### 2016-07-21 generic.tex
notes and changes discussed between JK and TS on 7/21

@@
 We write $x \getsr \univ$ to denote sampling an element from~$\univ$ and assigning this to~$x$, and we extend this notation to randomized algorithms.
+When~$X$ is a string over some alphabet~$\Sigma$, we write $|X|$ for the bitlength of~$X$, relative to some fixed encoding.
+When~$X$ is a multiset, we overload the notation so that~$|X|$ is the number of elements in~$X$ (with mutiplicity).
 
@@
 \begin{definition} %\tsnote{We need a more descriptive name than ``set-representation'' :)}
-\tsnote{I think this generalizes pretty easily to multisets.}
+%\tsnote{I think this generalizes pretty easily to multisets.}
 Fix a universe~$U$ and an alphabet~$\Sigma$.  A \emph{static (multi)set-representation primitive} is a pair of algorithms $(\Rep, \Qry)$
@@
 %where $q(S)$ denotes the correct answer to the query $q$ on the set~$S$.
-The \emph{size} of a set-representation is the maximum (bit)length of any~$M$ that can be
-output by $\Rep$.
 \end{definition}
+
+\todo{Readdress issue of representation size.
+A general statement might be something like `` The \emph{size} of a set-representation is the maximum (bit)length of any~$M$ that can be output by $\Rep$.''  But all of the natural constructions will have representation whose size will not depend on the coins of $\Rep$, i.e.
+they depend on $|S|$, number of hash functions, desired error rate.
+}
 
@@
 we may give the attacker $\aux$ but not~$M$, and in that case the set-representation cannot
-trivially make everything part of~$\aux$. \tsnote{Encoding secrets into~$M$ may cause some headaches in
-  the security definitions; we'll see. }
+trivially make everything part of~$\aux$. 
+%\tsnote{Encoding secrets into~$M$ may cause some headaches in the security definitions; we'll see. }
 %\tsnote{By the way, I'm coming around to the
@@
 $\Qry(\aux, M, q_i) \neq q_i(S)$ for all~$i \in [t]$
-\tsnote{I will typeset this into an experiment.}
+\todo{Typeset versions of this notion into experiments.}
 
@@
 \tsnote{Or, perhaps by recasting security
-  as distinguishing between $\Qry(\aux,M,\cdot)$ and an oracle that
+  as distinguishing between $\Qry(M,\aux,\cdot)$ and an oracle that
   returns 0,1 according to Bernoulli with paramter~$\epsilon$.}

### 2016-07-22 Theorem1_FP.tex
Modified proof Theorem1

@@
 $\calZ \getsr A^{\QryOracle}(\calS)$\\
-$z_1,\cdots, z_t \getsr \calY $\\
-if $\exists i\in[1,t] \,\mbox{s.t.} \,\Qry^{\HashOracle}(M,z_i)=0$ then\\
+if $|\calY| < t$ then \\ 
 \nudge Ret 0\\
+for $i=1$ to $t$ \\
+\nudge $z_i \getsr \calY $\\
+\nudge $\calY \gets \calY \setminus \{z_i\}$\\
+\nudge if $\Qry^{\HashOracle}(M,z_i)=0$ then\\
+\nudge \nudge Ret 0\\
 Ret 1\\\\
@@
 \oracle{$\QryOracle(x)$}\\
-$\calY \gets \calY \cup x$\\
-Ret $\Qry^{\HashOracle}(M,x)$\\
+$\calY \gets \calY \cup \{x\}$\\
+Ret $\Qry^{\HashOracle}(M,x)$\\\\
 %
@@
 $K_1 \getsr \calK $\\
-$S \getsr \distr{\univ}{n}$\\
+$\calS \getsr \distr{\univ}{n}$\\
 $M \getsr \Rep^{\HashOracle}(\calS)$\\
@@
 When $A$ halts with output $\calZ'$: \\
-if $|\calZ'| < t$ or $\calZ' \cap \calS \neq \emptyset$ then \\
-\nudge Ret 0\\
-if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
-\nudge Ret 0\\
-Ret 1\\\\
+\nudge if $|\calZ'| < t$ or $\calZ' \cap \calS \neq \emptyset$ then \\
+\nudge \nudge Ret 0\\
+\nudge if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
+\nudge \nudge Ret 0\\
+\nudge Ret 1\\\\
 \oracle{$\HashOracle(x)$}\\
@@
 When $A$ halts with output $\calZ'$: \\
-
-if $|\calZ'| < t$ or $\calZ' \cap \calS \neq \emptyset$ then \\
-\nudge Ret 0\\
-if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
-\nudge Ret 0\\
-Ret 1\\\\
+\nudge if $|\calZ'| < t$ or $\calZ' \cap \calS \neq \emptyset$ then \\
+\nudge \nudge Ret 0\\
+\nudge if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
+\nudge \nudge Ret 0\\
+\nudge Ret 1\\\\
 \oracle{$\HashOracle(x)$}\\
@@
 \end{figure}
+
+%
 \noindent
-From \Cref{eq:m1,eq:m2,eq:m3,eq:m4}, \acnote{compacted} \tsnote{this can be compacted}
+From \Cref{eq:m1,eq:m2,eq:m3,eq:m4}, %\acnote{compacted} \tsnote{this can be compacted}
 \begin{align}
@@
 \begin{equation}
-\AdvPRF{F}{B_2} +\AdvPRF{F}{B_1} = \Prob{\game{0}(A)=1} - \Prob{\game{2}(A)=1}\label{eq:2}
+\AdvPRF{F}{B_1} +\AdvPRF{F}{B_2} = \Prob{\game{0}(A)=1} - \Prob{\game{2}(A)=1}\label{eq:2}
 \end{equation}
@@
 \noindent
-In $\game{3}(A)$, $t$ elements are sampled from the $q$ queries with probability  $1/\dbinom{q}{t}$ and tested for false positives. So, 
+In $\game{3}(A)$, $t$ elements are sampled from the $q$ adaptive queries and tested for false positives.
+This is equivalent to $\game{2}(A)$, as the hash functions of the $\HashOracle$ oracle are random and $A$ wins this  game only if it outputs atleast $t$ FP's.\acnote{I was facing problems in connecting game2(adaptive) and game3(non-adaptive).
+I felt that the probability of  winning both games should be equal as the hash functions in the hash oracle are random(not independent) and adversary in game 2 has no means to output t elements which have higher chance of winning than those in game 3.}
 \begin{equation}
-\Prob{\game{2}(A)=1} = \frac{1}{\dbinom{q}{t}}\times\Prob{\game{3}(A)=1}\label{eq:3}
+\Prob{\game{2}(A)=1} = \Prob{\game{3}(A)=1}\label{eq:3}
 \end{equation}
@@
 \noindent
-The classical FP requirement considers only non-adaptive (and information-theoretic) adversaries and $A'$ is one such adversary simulating $\game{3}(A)$.
-\acnote{changed}\tsnote{The classical FP requirement considers only non-adaptive (and information-theoretic) adversaries.
-It suffices to say this.} From \Cref{fig:AGame3} and $\game{3}(A)$, it is evident that
+The classical FP requirement considers only non-adaptive (and information-theoretic) adversaries, and $D$ is one such adversary simulating $\game{3}(A)$ as closely as possible, whereas $D'$ mimics $D$ for $t=1$.
+$D'$ outputs a FP as in a classic Bloom filter and its FP-error is upperbounded by $[(1-e^{-kn/m})^k +O(1/n)]$ \cite{KirschMitzenmacher}.
+%\acnote{changed}\tsnote{The classical FP requirement considers only non-adaptive (and information-theoretic) adversaries.
+It suffices to say this.}
+From \Cref{fig:AGame3}, it is evident that
 \begin{align}
-\nonumber \Prob{\game{3}(A)=1} &= q\Prob{A' \mbox{outputs FP}}\\
-& \leq q\times(1-e^{-kn/m})^k \label{eq:4}
+\Prob{\game{3}(A)=1} &= \Prob{D \, \mbox{outputs $t$ FP} \,}\label{eq:4a}\\
+\nonumber \Prob{D \, \mbox{outputs t FP} \,} &= \dbinom{q}{t}\times \Big[\Prob{D' \, \mbox{outputs FP} \,}\Big]^t\\
+& \leq \dbinom{q}{t}\times \Big[(1-e^{-kn/m})^k +O(1/n)\Big]^t \label{eq:4b}
 \end{align}
-
-%\caption{Adversary $A'$ simulating $\game{3}(A)$} \label{AGame3}
+From \Cref{eq:4a,eq:4b}
+\begin{equation}
+\Prob{\game{3}(A)=1} \leq \dbinom{q}{t}\times [(1-e^{-kn/m})^k +O(1/n)]^t \label{eq:4}
+\end{equation}
+%\caption{Non-adaptive adversaries simulating $\game{2}(A)$} \label{AGame3}
 \begin{figure}
 \centering
-\fpage{0.4}{
-$\adversaryv{A'^{\HashOracle}}$\\
+\fpage{0.8}{
+\hpagessl{.5}{.4}
+{
+$\adversaryv{D^{\HashOracle}}$\\
+$\calY, \calZ \gets \emptyset $ \\
+$\rho \getsr Func(U,[m])$\\
+$\calS \getsr \distr{U}{n}$\\
+$M \getsr \Rep^{\HashOracle}(\calS)$\\
+When $A$ asks $\QryOracle(x)$:\\
+$\nudge \calY \gets \calY \cup {x}$\\
+$\nudge r \gets \Qry^{\HashOracle}(M,x)$\\
+\nudge Ret $r$\\
+When $A$ halts with output $\calZ'$\\
+\nudge if $|\calZ'|<t \, \mbox{or} \, |\calY| < t$\\
+\nudge \nudge Ret $\emptyset$\\
+\nudge for $i=1$ to $t$ \\
+\nudge \nudge $z_i \getsr \calY $\\
+\nudge \nudge if $\Qry^{\HashOracle}(M,z_i)=0$ then\\
+\nudge \nudge Ret $\emptyset$\\
+\nudge \nudge $\calZ \gets \calZ \cup z_i$\\
+\nudge \nudge $\calY \gets \calY \setminus {z_i}$\\
+\nudge Ret $\calZ $\\\\
+%
+\oracle{$\HashOracle(x)$}\\
+$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
+Ret $\left(h_1(x),\ldots,h_k(x)\right)$
+}
+{
+$\adversaryv{D'^{\HashOracle}}$\\
 $\calY \gets \emptyset $ \\
@@
 $\rho \getsr Func(U,[m])$\\
-$S \getsr \distr{U}{n}$\\
+$\calS \getsr \distr{U}{n}$\\
 $M \getsr \Rep^{\HashOracle}(\calS)$\\
@@
 $\nudge$ $\nudge r \gets \Qry^{\HashOracle}(M,x)$\\
-$\nudge$ $\nudge \calY \gets \calY \cup x$\\
+$\nudge$ $\nudge \calY \gets \calY \cup {x}$\\
 \nudge else\\
@@
 \nudge $z \gets \calY$\\
-\nudge if $\Qry^{\HashOracle}(M,z)=0$ then\\
-\nudge \nudge Ret 0\\
-\nudge Ret 1\\\\
+\nudge if $\Qry^{\HashOracle}(M,z)=1$ then\\
+\nudge \nudge Ret $z$\\\\
 %
@@
 }
-\caption{\Cref{thm1}:Adversary $A'$ simulating $\game{3}(A)$} \label{fig:AGame3}
+}
+\caption{Non-adaptive adversaries simulating $\game{3}(A)$} \label{fig:AGame3}
 \end{figure}
@@
 \nonumber \AdvFPSecHash{B_{\mathrm{lin}},t}{A}  &=  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} + \Prob{\game{2}(A)=1}  \\
-\AdvFPSecHash{B_{\mathrm{lin}},t}{A} &\leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  + \frac{q}{\dbinom{q}{t}} \times  (1-e^{-kn/m})^k
+\AdvFPSecHash{B_{\mathrm{lin}},t}{A} &\leq  \AdvPRF{F}{B_1} +
+\AdvPRF{F}{B_2}  +{\dbinom{q}{t}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^t
 \end{align}

### 2016-07-22 correctness.tex
restructuring

--- 2016-07-15 filters-notions.tex
@@
-\section{Security Notions for Hash-Based Filters}
+\section{Correctness Against Adaptive Adversaries}
+As highlighted by Naor and Yogev,
+Equation~(\ref{eqn:correctness}) is a non-adaptive version of correctness;
+we are interested in defining an adaptive (i.e., adversarial) notion
+of correctness.
 
+The general style of the definition is as follows:
+first, a set~$S$ is chosen according to some distribution over~$\mathcal{S}$ and then
+$\Rep(S)$ is run to generate $(M,\aux)$. (Unless stated otherwise, we assume
+security holds for all distributions and thus for all sets $S$.)
+The attacker $A$ is given $\aux$ and (possibly)~$S$;
+in addition, $A$ is given \emph{oracle access} to~$\Qry(M,\aux,\cdot)$.
+If $(\Rep, \Qry)$ is defined in the random-oracle model, then~$A$ is given access to the random oracle as well.
+The adversary \emph{succeeds} if it outputs~$t$ distinct queries $q_1, \ldots, q_t \in \mathcal{Q}$ for which
+$\Qry(\aux, M, q_i) \neq q_i(S)$ for all~$i \in [t]$
+\todo{Typeset versions of this notion into experiments.}
+
+Roughly, we say that a set-representation is $(t,\epsilon')$-FP-secure if the probability that
+any polynomial-time attacker succeeds is at most~$\epsilon'$. \tsnote{$t$ might be a bad choice, since it looks like ``time''.}
+A full definition would also bound the number of queries to $\Qry$ (and the random oracle) made
+be the attacker; it is useful to make the convention that if~$A$ outputs
+$q_1, \ldots, q_t$ then it must have made those queries to its oracle previously.
+
+The notion of security defined above captures the fp-prv notion for Bloom filters
+if we put the hash functions in~$M$ (and thus increase the size of the set-representation); it also captures the fp-pub
+notion if we put the hash function in~$\aux$. 
+%\tsnote{Except that the win condition allows both
+%false-positives and false-negatives, given the correctness requirement
+%in the syntax.} 
+%\jnote{True. But if false negatives cannot occur at all (by design of
+%the set-representation, not by definition of the primitive), then the attacker cannot hope to win
+%by finding a false negative.} 
+It captures the fp-bb-pub notion in the random-oracle model.
+
+Note that the security we can hope for is somewhat limited, since there
+is always a trivial attack in which
+the attacker tries random queries $q_1, q_2, \ldots$ until it finds~$t$ queries for which the
+set-representation returns an incorrect answer.\footnote{This assumes the attacker
+knows the true set~$S$, which need not be the case.} Roughly speaking,
+if the set-representation is $\epsilon$-correct then the attacker expects to find a query on which
+an incorrect result is returned every $1/\epsilon$ tries; thus, an
+attacker making $O(t/\epsilon)$ queries succeeds with constant probability (almost always).
+
+\def\bin{{\sf Bin}}
+
+Actually, it seems worthwhile to formalize this. Let $X_i$ be a random variable indicating
+whether the $i$th query of the attacker gives an incorrect result. Then an attacker making $T$
+queries can succeed
+if $N \stackrel{{\rm def}}{=} \sum_{i=1}^T X_i \geq t$. If we treat the $X_i$ as independent Bernoulli trials with
+probability~$\epsilon$, then $N$ follows the well-studied binomial distribution.
+Let $\bin(T, \epsilon; t)$ denote the probability that $N \geq t$. \tsnote{Viewed another way, we could let~$T$ be a negative binomial RV, and ask how many queries are needed (w.h.p) for $N \geq t$.} 
+So the best security we can hope for
+is that if the set-representation is $\epsilon$-correct then for any desired bound $T$
+the set-representation is $(t, \bin(T,\epsilon; t))$-FP-secure against any attacker making
+at most $T$~queries. \jnote{Need to find different terms to use for a query $q \in \mathcal{Q}$
+and a query that the attacker makes to its oracle.}
+
+\jnote{One option is to define the adversary's \emph{advantage} as the difference between
+its success probability and the success probability of the above,
+trivial attack. Just a thought.}
+\tsnote{Or, perhaps by recasting security
+  as distinguishing between $\Qry(M,\aux,\cdot)$ and an oracle that
+  returns 0,1 according to Bernoulli with paramter~$\epsilon$.}
+
+\heading{Comparison to Naor-Yogev definition.}
+The style of the Naor-Yogev (NY) definition is slightly different. \jnote{Even if we ignore
+all the other issues, chief among them the inconsistent way it treats the hash functions.}
+Lifting their definition to our setting, the experiment is similar but the attacker
+succeeds only if it outputs a single query $q$ for which $\Qry(\aux, M, q) \neq q(S)$ \emph{subject
+to the restriction that it did not query $q$ to its $\Qry$ oracle}.
+It will be interesting to understand formally the relation between our definition and theirs.
+Here are some observations:
+\begin{enumerate}
+\item Say a scheme is $\epsilon_{NY}$-secure under the NY definition.
+Then we claim it is $(t, T\epsilon_{NY}/t)$-secure against an attacker making $T$ queries. To see
+this, assume not. Then there is an attacker $A$ that, with probability $\epsilon'=T\epsilon_{NY}/t$,
+issues $T$ queries of which at least $t$ among those give incorrect answers.
+If we simply run $A$ and
+then choose a random query to output, we succeed with probability at least $\epsilon' \cdot t/T$.
+It is unclear whether this is tight.
+
+\item There is a contrived scheme that is $(2, 0)$-FP-secure but not NY-secure at all; the basic idea is
+to have a set-representation that always has \emph{exactly one} false positive that is easy to find
+given the public information.
+
+\item If a scheme is $(1,\epsilon_{FP})$-FP-secure for an attacker making $T$ queries
+then it is also $\epsilon_{FP}$-secure under the NY definition,
+at least for attackers making at most $T-1$
+queries.
+This is immediate.
+\end{enumerate}
+
+\if{0}
 \heading{FP-security of hash-based filters.}
@@
 \end{figure}
+
+\fi

### 2016-07-22 generic.tex
restructuring

@@
 \def\pub{{\sf pub}}
-\def\aux{{\sf aux}}
+\def\aux{{\sf pub}}
 
@@
 
-\subsection{Static (Multi)set-representations}
-\begin{definition} %\tsnote{We need a more descriptive name than ``set-representation'' :)}
-%\tsnote{I think this generalizes pretty easily to multisets.}
+heading{{Static (Multi)set-representations. }
+\begin{definition} 
 Fix a universe~$U$ and an alphabet~$\Sigma$.  A \emph{static (multi)set-representation primitive} is a pair of algorithms $(\Rep, \Qry)$
@@
 On the other hand, we can state a simple correctness condition for these kinds of filters; this will not be true when we further generalize to capture, properly, counters and mutability.
-
-\subsection{Adversarial Correctness}
-\heading{FP security.}
-As highlighted by Naor and Yogev,
-Equation~(\ref{eqn:correctness}) is a non-adaptive version of correctness;
-we are interested in defining an adaptive (i.e., adversarial) notion
-of correctness.
-
-The general style of the definition is as follows:
-first, a set~$S$ is chosen according to some distribution over~$\mathcal{S}$ and then
-$\Rep(S)$ is run to generate $(M,\aux)$. (Unless stated otherwise, we assume
-security holds for all distributions and thus for all sets $S$.)
-The attacker $A$ is given $\aux$ and (possibly)~$S$;
-in addition, $A$ is given \emph{oracle access} to~$\Qry(M,\aux,\cdot)$.
-If $(\Rep, \Qry)$ is defined in the random-oracle model, then~$A$ is given access to the random oracle as well.
-The adversary \emph{succeeds} if it outputs~$t$ distinct queries $q_1, \ldots, q_t \in \mathcal{Q}$ for which
-$\Qry(\aux, M, q_i) \neq q_i(S)$ for all~$i \in [t]$
-\todo{Typeset versions of this notion into experiments.}
-
-Roughly, we say that a set-representation is $(t,\epsilon')$-FP-secure if the probability that
-any polynomial-time attacker succeeds is at most~$\epsilon'$. \tsnote{$t$ might be a bad choice, since it looks like ``time''.}
-A full definition would also bound the number of queries to $\Qry$ (and the random oracle) made
-be the attacker; it is useful to make the convention that if~$A$ outputs
-$q_1, \ldots, q_t$ then it must have made those queries to its oracle previously.
-
-The notion of security defined above captures the fp-prv notion for Bloom filters
-if we put the hash functions in~$M$ (and thus increase the size of the set-representation); it also captures the fp-pub
-notion if we put the hash function in~$\aux$. 
-%\tsnote{Except that the win condition allows both
-%false-positives and false-negatives, given the correctness requirement
-%in the syntax.} 
-%\jnote{True. But if false negatives cannot occur at all (by design of
-%the set-representation, not by definition of the primitive), then the attacker cannot hope to win
-%by finding a false negative.} 
-It captures the fp-bb-pub notion in the random-oracle model.
-
-Note that the security we can hope for is somewhat limited, since there
-is always a trivial attack in which
-the attacker tries random queries $q_1, q_2, \ldots$ until it finds~$t$ queries for which the
-set-representation returns an incorrect answer.\footnote{This assumes the attacker
-knows the true set~$S$, which need not be the case.} Roughly speaking,
-if the set-representation is $\epsilon$-correct then the attacker expects to find a query on which
-an incorrect result is returned every $1/\epsilon$ tries; thus, an
-attacker making $O(t/\epsilon)$ queries succeeds with constant probability (almost always).
-
-\def\bin{{\sf Bin}}
-
-Actually, it seems worthwhile to formalize this. Let $X_i$ be a random variable indicating
-whether the $i$th query of the attacker gives an incorrect result. Then an attacker making $T$
-queries can succeed
-if $N \stackrel{{\rm def}}{=} \sum_{i=1}^T X_i \geq t$. If we treat the $X_i$ as independent Bernoulli trials with
-probability~$\epsilon$, then $N$ follows the well-studied binomial distribution.
-Let $\bin(T, \epsilon; t)$ denote the probability that $N \geq t$. \tsnote{Viewed another way, we could let~$T$ be a negative binomial RV, and ask how many queries are needed (w.h.p) for $N \geq t$.} 
-So the best security we can hope for
-is that if the set-representation is $\epsilon$-correct then for any desired bound $T$
-the set-representation is $(t, \bin(T,\epsilon; t))$-FP-secure against any attacker making
-at most $T$~queries. \jnote{Need to find different terms to use for a query $q \in \mathcal{Q}$
-and a query that the attacker makes to its oracle.}
-
-\jnote{One option is to define the adversary's \emph{advantage} as the difference between
-its success probability and the success probability of the above,
-trivial attack. Just a thought.}
-\tsnote{Or, perhaps by recasting security
-  as distinguishing between $\Qry(M,\aux,\cdot)$ and an oracle that
-  returns 0,1 according to Bernoulli with paramter~$\epsilon$.}
-
-\heading{Comparison to Naor-Yogev definition.}
-The style of the Naor-Yogev (NY) definition is slightly different. \jnote{Even if we ignore
-all the other issues, chief among them the inconsistent way it treats the hash functions.}
-Lifting their definition to our setting, the experiment is similar but the attacker
-succeeds only if it outputs a single query $q$ for which $\Qry(\aux, M, q) \neq q(S)$ \emph{subject
-to the restriction that it did not query $q$ to its $\Qry$ oracle}.
-It will be interesting to understand formally the relation between our definition and theirs.
-Here are some observations:
-\begin{enumerate}
-\item Say a scheme is $\epsilon_{NY}$-secure under the NY definition.
-Then we claim it is $(t, T\epsilon_{NY}/t)$-secure against an attacker making $T$ queries. To see
-this, assume not. Then there is an attacker $A$ that, with probability $\epsilon'=T\epsilon_{NY}/t$,
-issues $T$ queries of which at least $t$ among those give incorrect answers.
-If we simply run $A$ and
-then choose a random query to output, we succeed with probability at least $\epsilon' \cdot t/T$.
-It is unclear whether this is tight.
-
-\item There is a contrived scheme that is $(2, 0)$-FP-secure but not NY-secure at all; the basic idea is
-to have a set-representation that always has \emph{exactly one} false positive that is easy to find
-given the public information.
-
-\item If a scheme is $(1,\epsilon_{FP})$-FP-secure for an attacker making $T$ queries
-then it is also $\epsilon_{FP}$-secure under the NY definition,
-at least for attackers making at most $T-1$
-queries.
-This is immediate.
-\end{enumerate}
-
-\subsection{Privacy}
-One can also consider the orthogonal notion of privacy for a set-representation.
-\jnote{Actually, I am now unsure what the right way to define it is. It seems natural
-to give the attacker $\aux$. But if we give them $\aux$ and $M$ then they have everything.
-If $S$ has high min-entropy (element-wise), then it might still be
-possible to have security here.}\tsnote{I think we will always bump up
-against the (element-wise) min-entropy of the distribution over~$S$,
-at least in the ``one-wayness'' style definition that I had been imagining. }
-There are several possible definitions:
-\begin{enumerate}
-\item A ``one-wayness'' definition where $S$ has high min-entropy (element-wise), and we
-give the attacker $\aux$ and either $M$ or oracle access to $\Qry$. The attacker
-succeeds if it can output an element in~$S$.
-
-\item An ``indistinguishability'' definition where either $S_0$ or $S_1$ is used, and the attacker
-must determine which. Here the attacker is given $\aux$ but only oracle access to $\Qry$, and
-it is disallowed from asking any query $q$ for which $q(S_0) \neq
-q(S_1)$. \tsnote{How will the adversary know that a query satisfies
-  this in (say) the case of the classical BF?  We can, of course,
-enforce it in the experiment, but then our resource accounting risks
-overcounting the number of queries.} \jnote{I was assuming the attacker knows $S_0, S_1$.}
-\tsnote{Also, we need that, in general, $\aux$ itself
-does not leak information about~$S_0$ vs.\ $S_1$. } \jnote{Sure, this would be implied
-by the definition in this case.}
-\end{enumerate}

### 2016-07-22 intro.tex
restructuring

--- 2016-07-14 intro.tex
@@
-\jnote{Are we being too specific by focusing on hash-based
-set-membership only? It would be nice to give general definitions
-that apply to arbitrary data structures (constructed in arbitrary
-ways) and then only later specialized to hash-based Bloom filters.
-(Put this in an appendix for now, until we see how things play
-out.)}
-
 \section{Introduction}
+\label{sec:intro}
+\tsnote{Skeleton text from old intro.  (Full version of old intro now
+  in an appendix.}
 We revisit the formalization of Bloom filters~\cite{xxx} and closely
@@
 
-Bloom filters have a broad range of practical applications, for example, in content-distribution networks, large database query processing, routing algorithms for peer-to-peer networks, protocols for establishing linkages between medical-record databases, fair routing of TCP packets, Bitcoin wallet synchonization.
-\tsnote{need citations} Given that NY is addressing such a useful real-world object, we find their formalism, both the syntax and security notions, to be less precise and useful than one would want.
-Let us explain.
-
-Syntactically, NY says a Bloom filter (with a steady representation) is a pair of algorithms $\mathbf{B}=(\mathbf{B}_1, \mathbf{B}_2)$.
-The setup algorithm~$\mathbf{B}_1$ is randomized, and on input a set~$\mathcal{S}$ it returns a representation~$M$ (from some undefined, implicit set of representations).
-The query algorithm~$\mathcal{B}_2$ is deterministic, and on input a representation~$M$ and an element~$x \in \mathcal{U}$, it returns a bit.
-For correctness they make the classical demand, that for all $x \in \mathcal{S}$ we have $\Prob{\mathbf{B}_2(\mathbf{B}_1(\mathcal{S}),x)=1}=1$.
-For soundness, adversary~$A$ plays the following game, ``Adversarial-resilient Bloom Filter with a steady representation''.
-First, $M \getsr \mathbf{B}_1(\mathcal{S})$ for some set $\mathcal{S}$ that can be adversarially chosen.
-Then the adversary may make queries $x_1,x_2,\ldots,x_q$ to an oracle for $\mathbf{B}_2(M,\cdot)$.
-At the end of its execution, the adversary outputs~$x^*$ and wins the game if (1) $x^* \not\in \mathcal{S} \cup \{x_1,x_2,\ldots,x_q\}$, and (2) $\mathbf{B}_2(M,x^*)=1$.
-
-First, we note that the security notion forbids~$A$ to win if it outputs $x^* \in \{x_1,x_2,\ldots,x_q\}$, even if one of these was a false positive.
-On one hand, this notion is unsatisfying because it would not say that an attacker wins by creating (say) a bogus email address, and then observing that it passes a spam filter that is based on a Bloom filter represention of a whitelist.\footnote{This is one of the motivating examples from NY.}  The attacker is only allowed to win if it finds a false-positive that it has not verified.
-On the other hand, the NY notion does seem to capture the intuition that finding additional false positives does not become easier as more are learned.
-Our notions will address both sides of this discussion.
-%
-%\jnote{We discussed this on the phone, but let me put it in writing here.
-I think this is actually a reasonable choice because it captures the notion that ``even after finding some false positives, it remains hard to find additional false positives.'' Note that in practice finding false positives is ``easy'' since $\epsilon$ might be $1/1000$ rather than negligible.}
-%
-%\tsnote{For me the question is: is security violated once the first FP is found, or the second?
-My answer, which is in line with the traditional soundness notion, is that the first FP is a security violation even if finding it isn't ``hard'' by cryptographic standards.
-But I do appreciate your point.
-A natural goal is to say that, in some sense, \emph{adaptivity doesn't make it any easier} to find a FP.
-Adapting to what, though?
-In the traditional notion, $x$~is picked before the coins of~$\mathbf{B}_1$ are flipped, i.e., before the hash functions are sampled.
-The direct non-adaptive generalization is to say that $x_1,x_2,\ldots,x_q$ are all picked up front.
-The direct \emph{adaptive} generalization would allow $x_1,x_2,\ldots,x_q$ to depend in the coins of~$\mathbf{B}_1$, i.e., the hash functions.
-The NY definition captures only indirect dependence: adversaries that can adapt to set-membership queries, but \emph{not} (directly) to the input-output behaviors of the hash functions.
-The three notions I've proposed in Figure 1 cover a spectrum of adaptivity: the first is adapting to set-membership queries only, the second to those and hash input-output behavior, the third to set-membership queries and full knowledge of the hash functions.
-Each has it's own associated (informal) security interpretation.}
-%\tsnote{Perhaps a more obvious way to capture the idea that ``finding some FPs doesn't help find additional ones'' is to parameterize my notion(s) with a number~$f$, and say that that the adversary wins iff it outputs~$f$ FPs (these may have been previously queried to the set-membership oracle).
-Note that in the ROM (and probably in practice) finding~$f>1$ FPs will require~$f$ times the work.
-Right?}
-%
-%\tsnote{FYI: this is how MAC security against multiple forgeries is defined.  See \texttt{https://eprint.iacr.org/2006/095.pdf} for details.}
-
-Second, we note that the NY syntax does not capture the size of~$M$
-as a parameter; \jnote{I think this is also reasonable; typically
-security is defined without regard for efficiency} \tsnote{My
-complaint isn't about efficiency. It's about the fact that, by not
-including $|M|$ in the definition, the trivial scheme I give (just
-below) is allowed, and is secure.  Anyway, as I say at the end of
-this paragraph, this is a small(er) complaint than what follows}.
-\jnote{I would say that the trivial scheme \emph{is} secure!}
-\tsnote{Okay, well then we need some way to ``rule out'' the trivial
-solution. Perhaps just in the text -- yes, the trivial scheme works,
-but it isn't interesting in practice. Also, in the concrete security
-bounds that we will prove, the size of the representation is going
-to come up, e.g.\ the number of bits in the BF array directly affect
-the FP rate. Hence it makes sense to say things like ``an
-$(n,k,m)$-filter\ldots'' where $m$ is the size of the
-representation.} \jnote{I still disagree: efficiency is orthogonal
-to functionality and security.} The surrounding text does say that
-$\mathbf{B}_1$ ``outputs a compressed representation [of
-$\mathcal{S}$] $\mathbf{B}_1(\mathcal{S})=M$'' but what exactly this
-means is never addressed. The formal syntax admits
-$\mathbf{B}_1(\mathcal{S})=\mathcal{S}$ and
-$\mathbf{B}_2(\mathcal{S},x)=1 \Leftrightarrow x \in \mathcal{S}$,
-which is also trivially secure by their definition.  These are both
-small, but important complaints. But a larger complaint, and one
-that is much harder to see, is that that it is not clear that the NY
-formalism actually captures real world Bloom filters.
-
-In particular, say we implement a classic Bloom filter.
-Then the hash functions $h_1, h_2, \ldots, h_k$ are either sampled from some family~$\mathcal{H}$ by~$\mathbf{B}_1$ (recall that this algorithm is randomized), or they are hard-coded into the description of~$\mathbf{B}_1$.
-Let's assume the former for the moment.
-In order for~$\mathbf{B}_2$ to be able to respond to set-membership queries, it must have $h_1,h_2,\ldots,h_k$ as well.
-Since~$\mathbf{B}_2$ receives only the representation~$M$ as input, it must be the case that $h_1,h_2,\ldots,h_k$ are encoded into~$M$ somehow.
-But the text strongly suggests, in several places, that~$M$ does \emph{not} include these.
-Both NY and classical analysis of Bloom filters speak of the number of bits used to represent the set~$\mathcal{S}$: the classical analysis means only the number of bits in the actual array, and NY make comparisons throughout between the number of bits~$m$ used by their instantiations and the classical bounds.
-Moreover, the Bloom filter they construct in one of their main positive results clearly \emph{does not} count as part of the representation size the hash functions used to indicate array locations.
-%Thus, if we assume that
-%$\mathbf{B}_1$ is sampling $h_1,h_2,\ldots,h_k$, it seems that their
-%formalization fails to capture the basic Bloom filter construction;
-%at best, it is hard to see clearly that it does.
-
-%\jnote{FWIW, I think the classical description of Bloom filters has the same problem.
-I.e., if the hash functions are not fixed, then their description should be counted as part of the length of the data structure.
-On the other hand, if they are fixed, then the false-positive rate is not well-defined (since there is no probability space to speak of).
-So in that sense, NY just carried over the problem from the classical literature.}
-%
-%\tsnote{One can suggest that it \emph{should} be counted in the classical description, but the fact is that it isn't :) And in the 30+ years since the original paper, no one saw fit to correct this?
-From an algorithmic perspective, I think the classical approach makes sense.
-The questions being answered are: how many bits do I need to store a representation of the set for a given FP rate, and how does this compare to the combinatorially computed lower-bound?
-The description length of the hash functions may be bigger or smaller, but the number of bits you need to hold the set representation is independent of that.
-(Imagine that you have long random bitstrings in the set~$\mathcal{S}$.
-Then whether your hash functions simply truncate, or they are random oracles, the size of the representation as a function of the target FP rate doesn't change.
-Yet the description lengths of the hash functions are drastically different.)}
-
-On the other hand, assume the hash functions are implicitly hard-coded into~$\mathbf{B}_1$ (and $\mathbf{B}_2$).
-Then we can treat~$\mathbf{B}_1$ as deterministic, since it will simply carry out the steps required to populate an array using these hash functions, and output the array~$M$ as the representation.
-If the descriptions of~$\mathbf{B}_1,\mathbf{B}_2$ are known to the adversary, who is also provided with~$\mathcal{S}$, then the adversary can compute~$M$ itself, as well as test for false positives itself.
-So it isn't clear how the security notion helps to reason about difficulty of finding a false-positive.
-Moreover, NY stresses (at least once) that the representation is \emph{not} given to the adversary in their notions.
-So it seems unlikely that they intended for $h_1,h_2,\ldots,h_k$ to be hard-coded into the algorithms.
-\jnote{Perhaps it is reasonable to consider a definition in which the set is not given to the adversary?}
-\tsnote{A FP security notion?
-Yes, perhaps so.
-It's probably a more realistic notion anyway -- is a spammer really going to know my whitelist a priori?
-(If he does, I probably have bigger problems in my system than receiving new spam email.) Or set of URLs cached by a CDN server?}
-
-Continuing on this point, it seems that the coins of~$\mathbf{B}_1$ (whatever their use) are intended to be kept secret from the adversary.
-Thus, to the extent that it addresses real Bloom filters at all, the NY security notion only addresses applications in which the representation is created using secret coins.
-But many real-world applications of Bloom filters have no secrets.
-NY point to web proxies, which use Bloom filters to compactly represent the objects they store locally, as motivation for their work.
-But real web proxies like Squid~\cite{xxx} do \emph{not} use secrets in their Bloom filters.
-Squid, in particular, uses the basic Bloom filter with four hash functions, defined as follows: $h_1(x) = \mathrm{MD5}(x)[0,\ldots,31]$, $h_2(x)=\mathrm{MD5}(x)[32,\ldots,63]$, $h_3(x)=\mathrm{MD5}(x)[64,\ldots,95]$, and $h_4(x)=\mathrm{MD5}(x)[96,\ldots,127]$.
-Likewise, there are no secrets in the Bloom filters used by Google's BigTable~\cite{xxx}, HBase~\cite{xxx}, \tsnote{make an impressive list.}
-
-There are applications in which the proposed Bloom filter instantiations do use secretly keyed hash functions, e.g.
-$h_j(x) = (f(K_0,x) + j\cdot g(K_1,x))\bmod m$, where $j\in[1,k]$, $m$ is the number of bits in the array, and where $f,g$ are PRFs keyed by secrets $K_0,K_1$.
-This particular ``encrypted Bloom filter'' instantiation was suggested for use in efficient linking of records across separate medical record databases~\cite{xxx}.
-(It was subsequently shown not to be secure by Niedermeier et al.~\cite{xxx}, where a clever use of frequency analysis recovered the last names of patients given access only to the Bloom filter array.)
-In any case, it is clear that the NY definition does not capture the most widely used applications of Bloom filters, e.g. CDN summary caches, P2P network routing algorithms, etc.
-%\tsnote{Could also point out that their positive results use constructions that have secret keys, and these are unlikely to be of any use in major applications like CDNs or P2P networks.
-But maybe the horse is sufficiently beaten by now...}
-
-%\tsnote{What about content-based routing, or whatever that field is calling itself now?  A Bloom filter seems likely to be used there, and you'd want privacy for at least the content-seeker.}
+Bloom filters have a broad range of practical applications, for
+example, in content-distribution networks, large database query
+processing, routing algorithms for peer-to-peer networks, protocols
+for establishing linkages between medical-record databases, fair
+routing of TCP packets, Bitcoin wallet synchonization. \tsnote{need
+  citations}
 
@@
 \end{itemize}
-
-\if{0}
-\paragraph{Basic issues in Naor-Yogev. }
-\begin{itemize}
-\item The NY paper formalizes and investigates a security notion of limited interest
-\item The proposed construction won't scale in common network applications (e.g. large CDN, P2P networks)
-\item The main (im)possibility results are of theoretical interest only
-\item The basic syntax and operation of their Bloom filter formalization is underdefined.
-(This really irritates me.)  It isn’t clear that their Bloom filter formalization actually captures traditional Bloom filters!
-\tsnote{UPDATE (5/20/16): It is clear, now, that it \emph{does not}.} \tsnote{Also, why isn't the size of the representation somehow a part of the syntax or correctness/soundness conditions?
-The fact that the representation is supposed to be small doesn't appear in the syntax anywhere so, syntactically, $B_1(S)=S$ and $B_2(S,x)=1 \Leftrightarrow x \in S$ works just fine, and is trivially secure by their definition!
-}
-\item The ``adversarial-resilient Bloom Filter'' definition does not give the adversary access to the hash functions that created the representation; effectively, they are secret.
-(No matter if the [NY] syntax does or does not allow them to be encoded in the representation.)  This is odd and does not match reality, e.g.
-the popular Squid proxy uses plain MD5, splits the output into four chunks, and defines these as four hash functions.
-Hardly secret.
-\tsnote{I did find a setting where Bloom filters use secret keys: privacy-preserving record linkage.
-Here one wants to know if two databases contain information about the same person (abstractly, a set of record identifiers); you create a Bloom filter for each record, one for each unique identifier in some cases.
-Suggested hash functions are $H_j(x) = g(x) + j\cdot h(x) \bmod m$ for $j=\{0,1,\ldots,k-1\}$, and $g,h$ are (e.g.) HMAC-SHA1 with different keys.
-In practice, apparently the~$x$ are bigrams extracted from string identifiers (e.g.
-``Thomas''); papers show how to break this ``encrypted'' Bloom filter by recovering a large fraction of names, via (roughly) frequency analysis.}
-\item The ``unsteady representation'' does not seem well founded.
-Not sure what Bloom filter-like data structures would have randomized querying procedures.
-They mention the possibility of differential privacy mechanisms being incorporated into the querying procedure.
-But what's the purpose of this, if the security definition gives the adversary the set~$S$?
-(What are you keeping private?)
-\end{itemize}
-
-\paragraph{Discussion. }
-The traditional definition of Bloom filter soundness is information theoretic.
-Effectively, it states that an IT adversary cannot find a false positive with probability more than some small value.
-(That value is a function of the size of the set being represented, the representation size, the size of the universe, and the number of hash functions.)  This paper ([NY]) replaces the traditional IT notion with a computational notion, and casts it as a security experiment/goal.
-Namely: given the set~$S$ that is represented by the Bloom filter, and access to an oracle for Bloom filter set-membership queries, an attacker must find a false positive.
-
-\jknote{Of course, [NY] discusses an info-theoretic notion also. So in some sense what is really new here is consideration of adaptivity...}
-\tsnote{Yes, defining soundness with respect to explicit adversaries, who are also adaptive, does seem to be the novel piece.}
-
-Security relative to this notion appears to have some practical relevance.
-[NY] points to whitelisting spam filters as an example.
-That is, a Bloom filter is populated with set~$S$ of whitelisted email addresses, so a false positive translates to an attacker finding an email address that sneaks through the filter.
-[NY] suggest a second example of content-caching servers that keep a Bloom filter of their own storage contents.
-A false positive causes the server to search its local store, which is slow, only to find nothing.
-\tsnote{Question: in their security notions, the adversary wins by returning an $x^*$ that is not in~$S$ and is not one of the queries it asked to $B_2$; why the latter?
-I understand why you shouldn't get credit for output something in~$S$ when~$S$ is given to you, but what if one of the queries to~$B_2$ is not in~$S$ and is a FP?
-Shouldn't the adversary already win?}
-
-To the first example, I suspect that spam filters are far more sophisticated than simply looking for whitelisted email addresses.
-So the example feels artificial and overblown as practical motivation.
-But more to the point, the security notion proposed by [NY] gives~$S$ ---the set of whitelisted email addresses--- to the adversary.
-In practice, knowledge of these email addresses may be more damaging than creating a false-positive email address!
-(Keep in mind that the attacker wins, in this scenario, by creating any email address that passes the filter, even ones that bear no resemblance to real email addresses.)  From this perspective, the [NY] security definition is narrow in its scope, even assuming it says something useful about spam filtering.
-
-\jknote{Yes, although another way to interpret this is that the adversary cannot find a false positive EVEN IF it had the whitelisted email addresses, even if in practice it does not.}
-\tsnote{Fair enough.
-And this potentially unrealistic attack is preventable by a simple countermeasure.
-That said, I'm not convinced the countermeasure is easy to deploy at scale, or that it meshes well with real deployments.
-(See below.)  } \tsnote{Also, while the adversary is given~$S$ (the whitelisted email addresses), the hash functions used to create the Bloom filter are \emph{secret}.
-I'm not convinced this is realistic.}
-
-I am less critical of the second example, although this is mostly because I feel ignorant of how real CDNs operate.
-However, I believe that the following is common.
-Say I'm a caching server.
-If my Bloom filter tells me that some requested content is not locally stored, then I check the Bloom filters of my network neighbors, these having been shared with me.
-When a neighbor's Bloom filter is positive for the requested content, I contact that neighbor, and that neighbor only.
-(If no neighbor has it, then I have to retrieve it from some slower and more distant source, like the Web.)  Now, the [NY] construction uses a PRP, meaning that a secret key is involved in evaluating the Bloom filter.
-Thus, I need to know the secret keys of my neighbors in order to operate in the way just described.
-This seems troublesome in practice, at CDN-sized scale.
-(Also in P2P networks, where peers are joining/leaving frequently.)  Thus, their solution to a (potentially) real problem seems to be a non-solution.
-
-Note that there is at least one way to avoid this knowledge of secret keys issues.
-Namely, assume that content-caching servers distinguish between Bloom filter queries that originate from outside the CDN (e.g.
-users’ browsers) and those from within (e.g.
-other servers), and that the attacker only makes the former type of queries.
-Then each server could store its neighbors’ Bloom filters in the clear, as normal, and only use the PRP construction when responding to external queries.
-I don’t know how realistic this separation of queries is, in practice, nor how easy it would be to deploy such a strategy.
-I also don’t know if this restricted attack scenario is interesting or plausible.
-
-Moving on, the paper spends too much time asking and answering questions that are interesting to theoreticians, only.
-Specifically, the relationship between the existence of one-way functions and Bloom filters that are secure relative to their definition.
-
-\jknote{Agreed. =)}
-
-Finally, the Bloom filter formalization that is given does not obviously capture traditional Bloom filters!
-Traditionally, both Bloom filter population and querying procedures use hash functions $h_1,h_2,...h_k$ that each map from some universe $U$ to $[m]$, where $m$ is the bit-length of the array $M$ that represents a given set $S$.
-These hash functions are missing from the authors’ definition, apparently swept into the algorithms $B_1$ (population) and $B_2$ (querying).
-I don't really understand how, though.
-They allow $B_1$ to be randomized, which would let $B_1$ pick the hash functions.
-But the security definition provides no way for $B_1$ to share these with $B_2$.
-So how would $B_2$ be able to process set-membership queries?
-(Note: based on how they define the size of the representation $M$, $B_1$ cannot include descriptions of $h_1, h_2, \ldots , h_k$ in $M$.
-They really mean $M$ to be the array that represents the set $S$.)  In general, their formalization of the Bloom filter primitive is badly underdefined.
-
-\jknote{You had me for a minute...but actually I think the representations of the hash functions ARE included in the representation.
-This is not explicit, but is consistent with the way they state their positive result in the computational setting (“...if there is a Bloom filter using $m$ bits of memory, then there is a strongly resilient Bloom filter using $m + \lambda$ bits of memory…”); more importantly, it seems explicit from their treatment of the IT case.}
-
-\tsnote{Perhaps.
-I'm still not convinced.
-If you read the text preceding the statement of Theorem 1.2 (page 4), you'll see their discussion of lower bounds on “memory” required for a given set size and FP rate.
-This bound is the classical one for Bloom filters and speaks only of the (bit)size of the array.
-It says nothing about the description of the hash functions needed to populate the array.
-In fact, this lower bound is for any method of representing set $S$ in a bit array, not only for hashing-based methods.
-%
-Maybe they are defining “memory” differently in this discussion than in their theorems.
-This would be annoying, and I think it isn't the case.
-So for the moment, I'll continue to hold my position on this.
-%
-(I'll also point out that they explicitly say that $B_1$ outputs “compressed representation of [set $S$] $B_1(S)=M$”.
-But it would be easy to have small sets $S$ for which the bitsize of the array is smaller than the total bitsize of $S$, yet the combined bitsize of array + hash functions is larger.)
-%
-But for the sake of argument, say that their representation size~$m$ does include the description of the hash functions.
-To me, this is a clunky way to handle this matter.
-For one thing, it doesn't play well with analysis in the ROM, which is the traditional way to establish results relating FP rate, set size and array size for Bloom filters.
-(I know there are standard model assumptions that suffice, too.)  For another, this way of accounting makes unnecessarily hard to answer the two important operational questions: how big is the array, and how many hash function calls do I need to make per item/query?
-%
-I'll agree that this syntactic issue does not matter for theorem statements such as ``...if there is a Bloom filter using $m$ bits of memory, then there is a strongly resilient Bloom filter using $m + \lambda$ bits of memory…''.
-In fact, this statement would be true for the traditional way of defining Bloom filter memory (array size), since the extra space is basically for a PRP key.}
-
-\tsnote{UPDATE (5/20/16): I'm now convinced that what they call memory size~$m$, when applied to real Bloom filters, is \emph{only} the size of the bit array, and does \emph{not} include a description of the hash functions.
-The memory size comparisons that are made throughout the paper are to classical memory lowerbounds that account only for the bitsize of the array.
-Concretely: in the abstract they say ``...
-we show there exists a Bloom filter for sets of size~$n$ and error~$\epsilon$, that is secure against~$t$ queries and uses only $O(n\log\frac{1}{\varepsilon} + t)$ bits of memory.
-In comparison, $n \log\frac{1}{\varepsilon}$ is the best possible under a non-adaptive adversary.''  The latter bound is the classical one.
-If you look in the paper for this actual result, it's in Theorem 6.2.
-So, we look at the theorem and the construction that proves it.
-It uses a specially constructed function~$g$ and a Cuckoo hashing dictionary~$D$, consisting of two tables~$T_1,T_2$ and two hash functions~$h_1,h_2$.
-Here is a quote from the proof ``The final memory of the Bloom filter is the memory of~$D$ and the representation of~$g$.
-The dictionary~$D$ consists of $O(n)$ cells, each of size $|g(x)|=O(\log\frac{1}{\varepsilon})$ bits and therefore~$D$ and~$g$ together can be represented using $O(n\log\frac{1}{\varepsilon} + t)$ bits'', where earlier they say ``the representation of~$g$ requires $O(t)$ bits''.
-(Note that this~$g$ is only used to determined \emph{what} is stored at the indicated array/table positions, not \emph{where}.)  Thus they are not considering the size of the hash functions~$h_1,h_2$ that are used to indicated which cells of~$D$ need to be altered.
-So, as I said, I'm now convinced that their Bloom filter syntax does not actually capture real Bloom filters.}
-
-Finally, the security definitions do not give the adversary access to the hash functions that created the representation; effectively, they are secret.
-\tsnote{Unless they are assuming that the hash functions are fixed, part of the algorithms $B_1$ and $B_2$?
-In which case, $A$~knows them too; and the security notion gives~$S$ to~$A$, so...}  This strikes me as quite odd, and seems to miss the point that finding a false positive should be hard, in practice, even if you know that the hash functions are, say,  $h_i(X)=\mathrm{SHA256}(\langle i \rangle \concat X)$.
-(If the hash functions are not kept secret, the whole [NY] security notion kind of unravels; the adversary already is given~$S$, so if it knows the hash functions then you might as well just give it the whole Bloom filter data structure.) \tsnote{In the Squid proxy, the hash functions are not secret: you can download the source code, and the docs~\footnote{http://wiki.squid-cache.org/SquidFaq/CacheDigests} (available online even!) tell you that ``The protocol design allows for a variable number of hash functions (k).
-However, Squid employs a very efficient method using a fixed number - four.
-{\bf Rather than computing a number of independent hash functions over a URL Squid uses a 128-bit MD5 hash of the key (actually a combination of the URL and the HTTP retrieval method) and then splits this into four equal chunks.
-Each chunk, modulo the digest size (m), is used as the value for one of the hash functions - i.e.
-an index into the bit array.}  Note: As Squid retrieves objects and stores them in its cache on disk, it adds them to the in-RAM index using a lookup key which is an MD5 hash - the very one discussed above.
-This means that the values for the Cache Digest hash functions are already available and consequently the operations are extremely efficient!''  (``Key'' here just means hash input, as in ``key-value pair''.)}
-
-\paragraph{Obvious Tasks. }
-
-\begin{enumerate}
-\item Get a solid handle on how Bloom filters are used in practice, and what generalizations have gained traction in the academic literature.
-(See wikipedia, a section of which I've pasted in at the end of this doc.) \tsnote{5/23: lots of uses to consider --CDNs/load balancers, peer-to-peer networks, medical record linkage, model checking, etc.
-Might be good to try to characterize by, say, setting (distributed vs.
-local), typical BF instance size (e.g.
-local whitelist of emails = ``small'', CDN server-cache summary = ``large''), security concerns, and estimated severity of security violation (e.g.
-FP at CDN server = ``low'' or ``medium'', deanonymizing medical record = ``high'').
-Just throwing out ideas...}
-\item Work out a proper “cryptographic” syntax for the Bloom filter primitive.  (Possibly something more general, see number 5.)
-\item Establish security notions that are appropriate for broader use cases (e.g.
-privacy of~$S$, privacy of the representation~$M$, authenticity of representation~$M$), single Bloom filter vs.\ multiple Bloom filter settings (e.g.
-attacking a CDN by querying multiple servers)
-\item Develop constructions that are secure and are supported by a practice-informed argument for deployment
-\item Break some stuff :-)
-\item Starting with a secure ``basic'' Bloom filter, develop results for more complicated Bloom filter constructions (e.g. hierarchical Bloom filters, attenuated BFs), and Bloom-filter-based protocols
-\item Expand from Bloom filters to  approximate-set-membership primitives, i.e.
-more general compressed representations (of sets) that admit queries  Note: this should be done only if it makes sense~---i.e.
-it doesn't explode the scope, it doesn't send us off too far into theoryland.
-\item Expand more generally to hash-based approximate set operations, e.g.\ minhash methods for approximating $J(A,B)$ for sets $A,B$.
-Note: this should be done only if it makes sense~---i.e.
-it doesn't explode the scope, it doesn't send us off too far into theoryland.
-\end{enumerate}
-
-\jknote{I think privacy is an interesting question.
-I also thought that both privacy and soundness could be considered both in the setting when the representation is “hidden” from the adversary (as in the paper under discussion) as well as in the setting where the representation is public.
-[Ahh...I see you have some similar thoughts further below.] Some thoughts about this:
-(1) Privacy in the “hidden” setting. Here the idea would be that queries about whether $x \in S$ reveal only the result of the query and nothing else;
-(2) Privacy in the “public” setting.
-Here we could assume the elements of~$S$ have high entropy, and~$S$ has low density, and require that the attacker cannot find~$x \in S$ even when given the representation(!) I see no reason why this should not be achievable in the random oracle model, or possibly even in the standard model;
-(3) Soundness in the “public” setting.
-Note that if the soundness is 0.5 then the attacker can simply guess random elements until it finds a false positive.
-So one way to approach this is to look at negligible soundness error only.
-Or, in the random oracle model, you could count queries to the RO and bound the attacker's success as a function of the number of queries it makes.
-}
-
-\paragraph{From the Wikipedia page...}
-Google BigTable, Apache HBase and Apache Cassandra use Bloom filters to reduce the disk lookups for non-existent rows or columns.
-Avoiding costly disk lookups considerably increases the performance of a database query operation.[7][8]
-The Google Chrome web browser used to use a Bloom filter to identify malicious URLs.
-Any URL was first checked against a local Bloom filter, and only if the Bloom filter returned a positive result was a full check of the URL performed (and the user warned, if that too returned a positive result).[9][10]
-The Squid Web Proxy Cache uses Bloom filters for cache digests.[11]
-Bitcoin uses Bloom filters to speed up wallet synchronization.[12][13]
-The Venti archival storage system uses Bloom filters to detect previously stored data.[14]
-The SPIN model checker uses Bloom filters to track the reachable state space for large verification problems.[15]
-The Cascading analytics framework uses Bloom filters to speed up asymmetric joins, where one of the joined data sets is significantly larger than the other (often called Bloom join[16] in the database literature).[17]
-The Exim mail transfer agent (MTA) uses bloom filters in its rate-limit feature.[18]
-
-\fi

### 2016-07-22 privacy.tex
restructuring

\subsection{Notions of Privacy}
One can also consider the orthogonal notion of privacy for a set-representation.
\jnote{Actually, I am now unsure what the right way to define it is. It seems natural
to give the attacker $\aux$. But if we give them $\aux$ and $M$ then they have everything.
If $S$ has high min-entropy (element-wise), then it might still be
possible to have security here.}\tsnote{I think we will always bump up
against the (element-wise) min-entropy of the distribution over~$S$,
at least in the ``one-wayness'' style definition that I had been imagining. }
There are several possible definitions:
\begin{enumerate}
\item A ``one-wayness'' definition where $S$ has high min-entropy (element-wise), and we
give the attacker $\aux$ and either $M$ or oracle access to $\Qry$. The attacker
succeeds if it can output an element in~$S$.

\item An ``indistinguishability'' definition where either $S_0$ or $S_1$ is used, and the attacker
must determine which. Here the attacker is given $\aux$ but only oracle access to $\Qry$, and
it is disallowed from asking any query $q$ for which $q(S_0) \neq
q(S_1)$. \tsnote{How will the adversary know that a query satisfies
  this in (say) the case of the classical BF?  We can, of course,
enforce it in the experiment, but then our resource accounting risks
overcounting the number of queries.} \jnote{I was assuming the attacker knows $S_0, S_1$.}
\tsnote{Also, we need that, in general, $\aux$ itself
does not leak information about~$S_0$ vs.\ $S_1$. } \jnote{Sure, this would be implied
by the definition in this case.}
\end{enumerate}

### 2016-07-22 results.tex
restructuring

--- 2016-07-06 filters-results.tex
@@
-\section{Achieving FP-Security and Privacy}
+\section{Achieving Security Notions}
+\heading{Correctness. }  Here we give security proofs and attacks with respect to the correctness notions.
+\begin{itemize}
+\item Show Bloom Filter is correct in the ROM %\jnote{Would be good to show that RO-based Bloom filter is FP-secure.}
+\item FP-security/attacks on bigram/PRF-based double-hashing construction ($h_j(x) = F_{K1}(x) + j\cdot F_{K2}(x) \bmod m$ where the~$x$ are bigrams of names, etc.) 
+\item FP-security/attacks on bigram/domain-separated PRF construction ($h_j(x)=F_K(\langle j,x \rangle) \bmod m$, or just assume range of~$F$ is $[m]$.)
+\item FP-security/attacks Dong, Chen, Wen ``garbled Bloom filter'' construction
+\item ...
+\end{itemize}
+
+\heading{Privacy. } Here we give security proofs and attacks with respect to the privacy notions we have defined.
 \tsnote{Under our current notions, you can never hope to prove privacy bounds that beat the min-entropy of $\distr{U}{n}$.}

### 2016-07-22 syntax.tex
typesetting experiments

--- 2016-05-30 syntax.tex
@@
-\newcommand{\Rep}{\mathsc{Rep}}
-\newcommand{\Hash}{\mathsc{Hash}}
-\newcommand{\Qry}{\mathsc{Qry}}
-\newcommand{\Update}{\mathsc{Up}}
-\newcommand{\Init}{\mathsc{Init}}
-\newcommand{\Test}{\mathsc{Test}}
-\newcommand{\multiset}[1]{\mathbb{M}_{#1}}
-\newcommand{\ExpCorrectSecHash}[2]{\mathrm{Exp}^{\mathrm{cor\mbox{-}prv}}_{#1}(#2)}
-\newcommand{\ExpCorrectPubHash}[2]{\mathrm{Exp}^{\mathrm{cor\mbox{-}pub}}_{#1}(#2)}
-\newcommand{\ExpCorrect}[2]{\mathrm{Exp}^{\mathrm{cor}}_{#1}(#2)}
+\section{Secure Multiset Representation}
+\def\pub{{\sf pub}}
+\def\aux{{\sf pub}}
 
-\newcommand{\QryOracle}{\mathsf{Query}}
-\newcommand{\UpdateOracle}{\mathsf{Update}}
-\newcommand{\HashOracle}{\mathsf{Hash}}
+\heading{Preliminaries. }
+When~$\univ$ is a set and $n>0$ is an integer, we let $[\univ]^n$ denote the set of all size-$n$ subsets of~$\univ$.
+We write $x \getsr \univ$ to denote sampling an element from~$\univ$ and assigning this to~$x$, and we extend this notation to randomized algorithms.
+When~$X$ is a string over some alphabet~$\Sigma$, we write $|X|$ for the bitlength of~$X$, relative to some fixed encoding.
+When~$X$ is a multiset, we overload the notation so that~$|X|$ is the number of elements in~$X$ (with mutiplicity).
 
-\section{Hash-based Filters}
-\heading{Preliminaries.}
-When~$U$ is a set and $n>0$ is an integer, we let $[U]^n$ denote the set of all size-$n$ subsets of~$U$.
-We let $\multiset{U}$ denote the set of all finite multisets of~$U$.
-We can denote any multiset~$S$ as $\{(x,\ell) \,|\, x \in U, \ell > 0\}$ where each~$x$ appears exactly once, and each~$\ell$ is an integer.
-We define the multiplicity of~$x$ as $\mu_S(x) = \ell$.
-We write $|S|= \sum_{(x,\ell)\in S}\mu_S(x)$, and let $\multiset{U,n}$ denote the set of multisets~$S$ where $|S|=n$.
+\heading{Static (Multi)set-representations. }
+\begin{definition} 
+Fix a universe~$U$ and an alphabet~$\Sigma$.  A \emph{static (multi)set-representation primitive} is a pair of algorithms $\setprim=(\Rep, \Qry)$
+parameterized by a collection $\mathcal{S}$ of multisets, each consisting of elements from~$U$ and a collection
+of supported queries $\mathcal{Q}=\{q \colon \mathcal{S} \to \mathbb{R}\}$, where:
+\begin{itemize}
+\item $\Rep$ is a randomized algorithm taking as input $S \in \mathcal{S}$,
+and outputting a pair of strings $(M,\aux)$, the \emph{representation} $M \in \Sigma^*$ (of~$S$) 
+and the \emph{auxillary information} $\aux \in \Sigma^*$ (of~$M$).
+\item $\Qry$ is a deterministic algorithm that takes as input $M, \aux$,
+and a query $q\in \mathcal{Q}$, and returns value~$a$.
+\end{itemize}
+A set-representation is \emph{$\epsilon$-correct} if for all $S \in \mathcal{S}$ and
+all $q \in \mathcal{Q}$ it holds that
+\begin{eqnarray}
+\Pr[(M,\aux) \getsr \Rep(S) : \Qry(M, \aux, q) \neq q(S)] \leq \epsilon, \label{eqn:correctness}
+\end{eqnarray}
+%where $q(S)$ denotes the correct answer to the query $q$ on the set~$S$.
+\end{definition}
 
-We write $x \getsr U$ to denote sampling an element from~$U$ and assigning this to~$x$, and we extend this notation to randomized algorithms.
+\todo{Readdress issue of representation size.
+A general statement might be something like `` The \emph{size} of a set-representation is the maximum (bit)length of any~$M$ that can be output by $\Rep$.''  But all of the natural constructions will have representation whose size will not depend on the coins of $\Rep$, i.e.
+they depend on $|S|$, number of hash functions, desired error rate.
+}
 
-\heading{Syntax.}
-Fix a nonempty sets $U,\Sigma$ and integers $k,m,n>0$.  Fix a symbol $\bot \not\in U$.  An $(n,k,m)$-filter (over universe~$U$) is a tuple  $B=(\Hash,\Rep,\Qry)$.   
-%
-The randomized \emph{hash-sampling} algorithm~$\Hash$ samples a size~$k$ family of functions~$\mathcal{H}=\{h_1,h_2,\ldots,h_k\}$ where each $h_i \in  \mathrm{Func}(U,\{0,1,\ldots,m-1\})$.
-We write $\mathcal{H} \getsr \Hash$ for this operation.
-%
-The deterministic representation algorithm $\Rep\colon [U]^n \rightarrow \Sigma^m$ takes a set~$S$ of~$n$ elements as input, and outputs representation~$M$ of length~$m$.
-%
-The determinisitc query algorithm $\Qry\colon \Sigma^m \times U \rightarrow \bits$ takes a representation $M$ and an element $x \in U$ and returns a bit.  
-%
-We assume that both $\Rep$ and $\Qry$ have the following blackbox access to the functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$.
-%which we denote by writing~$\mathcal{H}$ as a superscript.   
-%Thus, we write $M \gets \Rep^{\mathcal{H}}(S)$ and $b \gets \Qry^{\mathcal{H}}(M,x)$ for the execution of the representation and query algorithms, respectively.
-%
-%We write $M \gets \Rep(S)$ and $b \gets \Qry(M,x)$ for the execution of the representation and query algorithms, respectively.
-For correctness, we demand that for all~$S$ of size~$n$, we have that for all $x \in S, \Prob{\Qry(\Rep(S),x)=1}=1$, where the probability is over the coins of $\Hash$.
+Our treatment of $M,\aux$ is not symmetric, since we only count $M$ against the size
+of the set-representation. When we define security
+we may give the attacker $\aux$ but not~$M$, and in that case the set-representation cannot
+trivially make everything part of~$\aux$. 
+%\tsnote{Encoding secrets into~$M$ may cause some headaches in the security definitions; we'll see. }
+%\tsnote{By the way, I'm coming around to the
+%  viewpoint that it is fair to include in the ``size'' of the
+%  representation any secret information.  In makes more difficult
+%  comparisons to classical lower-bounds (which [NY] makes, incorrectly
+% IMO), but it does seem fair to say ``this is how many bits of memory
+% you need to allocate to represent this set \emph{securely}.''}
 
-%\heading{Discusssion.}
-This syntax captures classical Bloom filters by setting~$\Sigma=\bits$,  and defining $\Rep,\Qry$ in the obvious way.
+The above definition can be lifted to the random-oracle model in the natural way
+by giving $\Rep, \Qry$ access to a random oracle. In that case,
+the probability in Equation~(\ref{eqn:correctness})
+is also taken over choice of the random oracle.
+
+\heading{Examples.}
+It is not hard to see Bloom filters are one possible instantiation of the above. If we fix some
+size bound~$n$, then $\mathcal{S}$ becomes the collection of all subsets of $U$
+of size (at most)~$n$. We also fix $\mathcal{Q} = U$, where a query ``$x$'' has
+the semantics ``is $x$ in $S$?'' Algorithm $\Rep$, which has values $k, m$ hardwired,
+chooses a set of hash functions $h_1, \ldots, h_k$ and computes an $m$-bit
+array in the usual way; a natural possibility is to set $\aux = (h_1, \ldots, h_k)$ (encoded as a string) and
+to let~$M$ be the bit array.  
+%\tsnote{If $\mathcal{Q}=U$ and we use the
+%  semantics you suggest, then isn't Equation~\ref{eqn:correctness}
+%  both correctness and soundness?  If so, I don't see how this
+%  captures the classical BF, which requires $\epsilon=0$ for one kind
+%  of error, but allows $\epsilon>0$ for the other. } 
+%\jnote{The definition does not distinguish
+%  between elements in the set (for which $q(S)=1$) or outside the set (for which
+%  $q(S)=0$). But a Bloom filter does satisfy Equation~\ref{eqn:correctness} in either case.}
+%  \jnote{In that sense, I am using ``soundness'' and ``correctness'' interchangeably here.}
+  \jnote{I'm not tied to allowing false negatives when we specialize the definition to the case
+  of set-membership queries. But in the abstract definition it seems unclear why one would choose
+  some queries on which error is ok and other queries where error is not allowed. Though if one
+  wanted to be general, one could simply have two (disjoint) sets of queries $\mathcal{Q}_1, \mathcal{Q}_2$
+  where error is allowed on the former but not on the latter.}
+We note that while our correctness condition does not distinguish among types of errors, it also does not preclude instantiations (like the classical Bloom filter) that admit only one type of error, e.g.
+false-positives.
+
 Setting $\Sigma=\bits^{\leq L}$ allows one to store a bitstring of length at most~$L$ at each location.
-\tsnote{Would let us capture a construction from NY, among other things.}  We note that even though this would allow for the storage of counters (say) at each filter location, our restriction that~$\Qry$ returns a bit does not capture functionality typically demanded of Bloom filters that employ counters, e.g., returning a counter value.
-(One could, however, have $\Qry$ compute an arbitrary, fixed predicate.
-For example, ``has~$x$ been seen at least 5 times?''.)
-Our syntax also does not capture filters that are mutable, that is, whose representation may change over time. 
+This allows our syntax to capture the cuckoo-hashing construction from NY, as well as the ``garbled Bloom filter'' from Dong, Chen and Wen~\cite{xxx}, among other things.
+Setting $\Sigma=\mathbb{N}$ would allow for the storage of counters (say) at each position in~$M$, and a query ``$x$'' with the semantics ``what is the multiplicity of~$x$ in~$S$.''  (This does not capture counting Bloom filters, or the like, which do not have static representations.)  \tsnote{I guess this can all be accomplished with $\Sigma=\bits^*$, but it isn't necessarily the ``natural'' way.}
+%Our syntax also does not capture filters that are mutable, that is, whose representation may change over time.
 On the other hand, we can state a simple correctness condition for these kinds of filters; this will not be true when we further generalize to capture, properly, counters and mutability.
-
-\heading{Soundness of hash-based filters.} \tsnote{To do.
-Note that it makes sense to consider soundness both in the public and private hash setting.
-NY give it in the private hash setting (sort of); but, intuitively, it should be hard to find false-positives even if you know that MD5 or SHA-x are the hash functions  It might be interesting to run some experiments, e.g.
-set up a bloom filter of URLs or IP/port information, and then open up a network tap and see how many false positives we observe.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Mutuable hash-based filters}
-Here we extend the basic Bloom filter syntax to allow for variations on the traditional Bloom filter, e.g.
-counting Bloom filters~\cite{xxx}, spectral Bloom filters~\cite{xxx}, count-min sketches~\cite{xxx}, stable Bloom filters~\cite{xxx}, etc.
-Before giving it, let us briefly describe what is formalized.
-Our syntax captures settings in which there is some (potentially empty) initial set~$S$, whose representation~$M$ may undergo updates over time.
-Effectively, this allows for expansion of~$S$ to a larger set, or even a multiset, as new elements ``arrive''.
-The update algorithm is responsible for altering the current representation.
-We allow it to take in a string that encodes inputs needed to carry out the updating.
-For example, counting Bloom filters may receive update strings that encode $(x,c)$ where $x \in U$ is the element whose representation should be incremented, and $c \in \mathbb{N}$ is the amount of the increment.
-Network applications, such as looking for heavy-hitters across TCP/IP streams seen by a router, may have $x = (\mathrm{IP_{src}},\mathrm{IP_{dst}})$, the source and destintation address of a packet, and~$c$ the number of bytes in the packet payload.
-When necessary we will specify what is encoded in the update string, but will assume some implicit and fixed encoding scheme.
-Note that our syntax allows for randomized updating.
-This accommodates stable Bloom filters, for example, which has a randomized ``forgetting'' feature as part of its update.
-
-\heading{Syntax. }
-Fix nonempty sets $U,\Sigma$ and integers $k,m_1,m_2,n>0$ with $m_1 \leq m_2$.
-Fix a symbol $\bot \not\in U$.
-An $(n,k,[m_1,m_2])$-filter (over universe~$U$) is a tuple  $B=(\Hash,\Init,\Qry,\Update, \Test)$.
-%
-The randomized \emph{hash-sampling} algorithm~$\Hash$ samples a size~$k$ family of functions~$\mathcal{H}=\{h_1,h_2,\ldots,h_k\}$ where each $h_i \in  \mathrm{Func}(U,\{0,1,\ldots,m_2-1\})$.
-We write $\mathcal{H} \getsr \Hash$ for this operation.
-%
-The deterministic \emph{initial-representation} algorithm $\Init\colon \multiset{U,n} \rightarrow \left(\bigcup_{m=m_1}^{m_2}\Sigma^m\right)$ takes a multiset~$S$ of size~$n$ as input, and outputs representation~$M$ of length~$m_1 \leq m \leq m_2$.
-%
-The determinisitc query algorithm $\Qry\colon \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right)\times U \rightarrow \bits^*$ takes a representation $M$ and an element $x \in U$ and returns a bitstring.  
-%
-The randomized \emph{update} algorithm $\Update\colon \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right)\times \bits^* \rightarrow \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right) \cup \{\bot\}$ takes a representation and an update string, and returns an updated representation or the distinguished symbol~$\bot$.
-%
-The deterministic \emph{test} algorithm $\Test \colon \multiset{U}\times \left(\bigcup_{m=m_1}^{m_2}\Sigma^m \right)\cup\{\bot\} \times U \rightarrow \bits$ takes a multiset~$S$, a representation~$M$ and an element~$x \in U$ and returns a bit.
-%
-%We assume that all $\Init,\Qry,\Update,\Test$ all have blackbox access to the functions $h_1,h_2,\ldots,h_k \in \mathcal{H}$, which we denote by writing~$\mathcal{H}$ as a superscript.
-
-\heading{Correctness.
-} The kind of filters we capture, here, can have \emph{two-sided} error.
-That is, they may result in false-negatives as well as false-positives.
-We captures two versions of correctness in Figure~\ref{fig:correctness-mutable}, corresponding to whether or not the adversary is given access to the hash functions used to create and update the multiset representation.
-
-\begin{figure}
-\centering
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpCorrectSecHash{S,B}{A}$}\\
-$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-$M \gets \Init^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle,\UpdateOracle}(S)$\\
-if $\Test^{\HashOracle}(S,M,x) \neq 1$ then Ret 1\\
-Ret 0\\
-
-\medskip
-\experimentv{$\ExpCorrectPubHash{S,B}{A}$}\\
-$ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-$M \gets \Init^{\HashOracle}(S)$\\
-$x \getsr A^{\QryOracle,\UpdateOracle,\HashOracle}(S)$\\
-if $\Test^{\HashOracle}(S,M,x) \neq 1$ then Ret 1\\
-Ret 0
-}
-%
-{
-\oracle{$\QryOracle(x)$}\\
-if $M = \bot$ then Ret $\bot$\\
-Ret $\Qry^{\HashOracle}(M,x)$\\
-
-\medskip
-\oracle{$\UpdateOracle(\sigma)$}\\
-if $M = \bot$ then Ret $\bot$ \\
-$S \gets S \uplus \{\sigma\}$\\
-$M \getsr \Update^{\HashOracle}(M,\sigma)$\\
-
-\medskip
-\oracle{$\HashOracle(i,x)$}\\
-Ret $h_i(x)$\\
-}
-}
-\caption{Trying to define correctness for an $(n,k,[m_1,m_2])$-filter~$B$.}
-\label{fig:correctness-mutable}
-\end{figure}
-
-\heading{Soundness for mutable hash-based filters. } \tsnote{To do.  Same comments as for the simple case, only it's more complicated here what it means to violate soundness.}
-
-\if{0}
-\heading{Multiset-oriented hash-based filters. }
-\tsnote{Commented out, but in the source: an alternative way to formalize mutable hash-based filters.
-This way directly address the inputs as multisets, instead of starting with a set and then updating the represenation a step at a time.
-Not sure which is cleaner and more easily applied to real problems, yet.}
-
-Let $\mathbb{M}_\mathcal{U}$ be the set of multisets over~$\mathcal{U}$.
-We can denote any multiset as $\{(x,\ell) \,|\, x \in \mathcal{U}, \ell \in \mathbb{N}\}$, and for a particular multiset~$S$ we define the multiplicity of~$x$ as $\mu_S(x) = \ell$ where $(x,\ell)\in S$.
-
-An $(n,k,[m_1,m_2])$-filter with operations is a tuple  $B=(\Hash,\Rep,\Qry, \mathcal{F})$.  
-The set $\mathcal{F}$ is the finite collection of allowable operations.  All operations are of the form 
-$f: \mathbb{M}_{\mathcal{U}} \times \mathbb{M}_{\mathcal{U}} \rightarrow \mathbb{M}_{\mathcal{U}} \cup \{\bot\}$.  
-%
-The deterministic representation algorithm $\Rep\colon \mathbb{M}_\mathcal{U} \rightarrow \bigcup_{m=m_1}^{m_2}\Sigma^m$ takes a multiset~$S$, and outputs representation~$M$ of length~$m_1 \leq m \leq m_2$, or the distinguished symbol~$\bot$.
-We assume that if the multiset~$S=\{(x_1,\ell_1),(x_2,\ell_2),\ldots,(x_t,\ell_t)\}$ is such that $n < \sum_{i=1}^t \ell_i$ then $\Rep(S)=\bot$.
-%
-The randomized hash-sampling algorithm~$\Hash$ is as before.
-%
-The determinisitic query algorithm $\Qry$... \tsnote{Not sure how to define this!  See my comment, below...}
-
-%Correctness is defined as follows.
-Let $S,T$ be arbitrary multisets and let~$f$ be an arbitrary operation in $\mathcal{F}$.
-If $f(S,T) = S'\neq \bot$, then for all $x \in S'$ we demand that $\Qry(\Rep(S'),x)=1$.
-\tsnote{might need a stronger condition that this holds for any sequence of operations that do not result in $\bot$.}
-
-Let us see how this syntax captures various kinds of Bloom filters.
-First, let $\Sigma = \mathbb{N}$ and define $f_{\mathrm{add}}(S,T)=\{(x,\mu_S(x)+\mu_T(x)) \,|\, x \in \mathcal{U}\}$ and $f_\mathrm{del}(S,T) = \{(x,\min\{0,\mu_S(x)-\mu_T(x)\}) \,|\, x \in \mathcal{U} \}$.
-Define $\Rep(S')$ as follows: for each $(x,\ell)\in S'$ and $j\in\{1,2,\ldots,k\}$, set $M[h_j(x)]=\ell$.
-Finally, define $\Qry(M,x) = 1 \Leftrightarrow \forall j \in \{1,2,\ldots,k\},\; M[h_j(x)] > 0$.
-This allows us to capture counting Bloom filters.
-\tsnote{Does it?
-Acutally, you might want $\Qry(M,x)$ to return a number, i.e., a counter value.
-How do you define correctness then?}
-
-\tsnote{There are more direct ways to formalize counting Bloom filters, like the syntax above.
-But this less direct way will allow us to capture other kinds ``advanced'' Bloom filters proposed in the literature or (more importantly) used in practice.
-For example, $f_{\mathrm{setify}}(S,T)=\{(x,1) \,|\, x \in \mathcal{U} \mbox{s.t.
-} \mu_S(x)>0, \mu_T(x)>0\}$.
-On the other hand, we may end up deciding it is overkill...
-}
-\fi

### 2016-07-22 correctness.tex
typesetting experiments
rewriting/fleshing out syntax section

@@
 \section{Correctness Against Adaptive Adversaries}
-As highlighted by Naor and Yogev,
-Equation~(\ref{eqn:correctness}) is a non-adaptive version of correctness;
+As highlighted by Naor and Yogev, Equation~(\ref{eqn:correctness}) is a non-adaptive version of correctness;
 we are interested in defining an adaptive (i.e., adversarial) notion
-of correctness.
+of correctness.   Figure~\ref{fig:correctness} describes a security
+experiment that captures such a notion.
+First, a set~$S$ is chosen according to some
+distribution~$\distr{\calS}{}$ over the collection of multisets
+$\mathcal{S}$ associated to~$\Pi=(\Rep,\Qry)$, and then
+$\Rep(S)$ is run to generate $(M,\aux)$.
+%(Unless stated otherwise, we assume security holds for all distributions and thus for all sets $S$.)
+Adversary~$A$ is given~$\aux$ and (possibly) $\calS$~as input; it is
+provided an oracle~$\TestOracle$ that, on input a query~$q \in \calQ$,
+computes (and returns) the result of $\Qry(M,\aux,q)$, and increments
+a counter if this result is in error.  The adversary wins if it
+manages to cause at least~$r>0$ such errors among its queries.
 
-The general style of the definition is as follows:
-first, a set~$S$ is chosen according to some distribution over~$\mathcal{S}$ and then
-$\Rep(S)$ is run to generate $(M,\aux)$. (Unless stated otherwise, we assume
-security holds for all distributions and thus for all sets $S$.)
-The attacker $A$ is given $\aux$ and (possibly)~$S$;
-in addition, $A$ is given \emph{oracle access} to~$\Qry(M,\aux,\cdot)$.
-If $(\Rep, \Qry)$ is defined in the random-oracle model, then~$A$ is given access to the random oracle as well.
-The adversary \emph{succeeds} if it outputs~$t$ distinct queries $q_1, \ldots, q_t \in \mathcal{Q}$ for which
-$\Qry(\aux, M, q_i) \neq q_i(S)$ for all~$i \in [t]$
+The adversary \emph{succeeds} if it outputs~$r$ distinct queries $q_1, \ldots, q_r \in \mathcal{Q}$ for which
+$\Qry(\aux, M, q_i) \neq q_i(S)$ for all~$i \in [r]$
 \todo{Typeset versions of this notion into experiments.}
 
-Roughly, we say that a set-representation is $(t,\epsilon')$-FP-secure if the probability that
-any polynomial-time attacker succeeds is at most~$\epsilon'$. \tsnote{$t$ might be a bad choice, since it looks like ``time''.}
-A full definition would also bound the number of queries to $\Qry$ (and the random oracle) made
-be the attacker; it is useful to make the convention that if~$A$ outputs
-$q_1, \ldots, q_t$ then it must have made those queries to its oracle previously.
+\begin{figure}
+\centering
+\fpage{.6}{
+\hpagess{.6}{.35}
+{
+\experimentv{$\ExpCorrect{\setprim,r}{\distr{\calS}{},A}$}\\
+$S \getsr \distr{\calS}{}$\\
+$\mathrm{err}\gets 0$\\
+$(M,\aux) \getsr \Rep(S)$\\
+$z \getsr A^{\TestOracle}(S,\aux)$\\
+if $\mathrm{err} < r$ then Return 0\\
+Return 1
+}
+%
+{
+\oracle{$\TestOracle(q)$}\\
+$a \gets \Qry(M,\aux,q)$\\
+if $a \neq q(S)$ then \\
+\nudge $\mathrm{err}\gets\mathrm{err}+1$\\
+Return~$a$
+}
+}
+\caption{} 
+\label{fig:fp-filter}
+\label{fig:correctness}
+\end{figure}
 
-The notion of security defined above captures the fp-prv notion for Bloom filters
-if we put the hash functions in~$M$ (and thus increase the size of the set-representation); it also captures the fp-pub
-notion if we put the hash function in~$\aux$. 
-%\tsnote{Except that the win condition allows both
-%false-positives and false-negatives, given the correctness requirement
-%in the syntax.} 
-%\jnote{True. But if false negatives cannot occur at all (by design of
-%the set-representation, not by definition of the primitive), then the attacker cannot hope to win
-%by finding a false negative.} 
-It captures the fp-bb-pub notion in the random-oracle model.
+If $(\Rep, \Qry)$ is defined in the random-oracle model, then~$A$ is given access to the random oracle as well.
+
+Roughly, we say that a set-representation~$\Pi$ is $(r,\epsilon',t)$-FP-secure if the probability that
+any $t$-time attacker succeeds is at most~$\epsilon'$. 
+(A full definition would also bound the number of queries to $\Qry$ (and the random oracle) made
+be the attacker.)
 
@@
 \end{enumerate}
+
+\begin{figure}
+\centering
+\fpage{.6}{
+\hpagess{.6}{.35}
+{
+\experimentv{$\ExpCorrect{\setprim,t}{\distr{\calS}{},A}$}\\
+$\calS \getsr \distr{U}{n}$\\
+$(M,\aux) \getsr \Rep^{\HashOracle}(\calS)$\\
+$\calX \getsr A^{\QryOracle}(\calS,\aux)$\\
+if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
+\nudge Ret 0\\
+If $\exists x \in \calX$ s.t. $\Qry(M,\aux,x)=0$ then\\
+\nudge Ret 0\\
+Ret 1
+}
+%
+{
+\oracle{$\QryOracle(x)$}\\
+Ret $\Qry(M,\aux,x)$\\
+}
+}
+\caption{} 
+\label{fig:fp-filter}
+\label{fig:correctness}
+\end{figure}
 

### 2016-07-22 syntax.tex
rewriting/fleshing out syntax section

@@
 \def\pub{{\sf pub}}
-\def\aux{{\sf pub}}
+\def\aux{{\sf aux}}
 
@@
 
-\heading{Static (Multi)set-representations. }
+Algorithms may be provided black-box access to one or more oracles, which we write as superscripts, e.g., $F^{O_1,O_2,\ldots}$.  An \emph{adversary} is a randomized algorithm
+
+\heading{Static (Multi)set-representations.
+}  We being by defining a general primitive that produces a representation of a given multiset, and provides a mechanism to answer a specified collection of questions about that multiset.
+Informally, the representation should serve as a good approximation of the multiset, at least with respect to the allowed questions.
 \begin{definition} 
-Fix a universe~$U$ and an alphabet~$\Sigma$.  A \emph{static (multi)set-representation primitive} is a pair of algorithms $\setprim=(\Rep, \Qry)$
+Fix a universe~$\univ$ and an alphabet~$\Sigma$.  A \emph{static (multi)set-representation primitive} (or just set-representation) is a pair of algorithms $\setprim=(\Rep, \Qry)$
 parameterized by a collection $\mathcal{S}$ of multisets, each consisting of elements from~$U$ and a collection
@@
 and outputting a pair of strings $(M,\aux)$, the \emph{representation} $M \in \Sigma^*$ (of~$S$) 
-and the \emph{auxillary information} $\aux \in \Sigma^*$ (of~$M$).
+and the \emph{auxilliary information} $\aux \in \bits^*$ (of~$M$).
 \item $\Qry$ is a deterministic algorithm that takes as input $M, \aux$,
@@
 \end{itemize}
-A set-representation is \emph{$\epsilon$-correct} if for all $S \in \mathcal{S}$ and
-all $q \in \mathcal{Q}$ it holds that
+A set-representation is \emph{$\epsilon$-correct} if, for all $S \in \mathcal{S}$ and
+all $q \in \mathcal{Q}$, it holds that
 \begin{eqnarray}
@@
 
-\todo{Readdress issue of representation size.
+\noindent
+The definition can be lifted to the random-oracle model
+by giving $\Rep, \Qry$ access to a random oracle. In that case,
+the probability in Equation~(\ref{eqn:correctness}) is also taken over choice of the random oracle.
+
+All of the constructions of set-representations that we will consider have the property that~$|M|$ does not depend on the coins of~$\Rep$.
+Thus we assume that~$|M|$ depends only on~$|S|$.
+In general this need not be true, but the assumption does not restrict our syntax from capturing natural constructions (e.g., those seen in practice), and it makes it easier to state our security notions.
+%
+%\todo{Readdress issue of representation size.
 A general statement might be something like `` The \emph{size} of a set-representation is the maximum (bit)length of any~$M$ that can be output by $\Rep$.''  But all of the natural constructions will have representation whose size will not depend on the coins of $\Rep$, i.e.
@@
 
-Our treatment of $M,\aux$ is not symmetric, since we only count $M$ against the size
-of the set-representation. When we define security
-we may give the attacker $\aux$ but not~$M$, and in that case the set-representation cannot
-trivially make everything part of~$\aux$. 
+%Our treatment of $M,\aux$ is not symmetric, since we only count $M$ against the size
+%of the set-representation. When we define security
+%we may give the attacker $\aux$ but not~$M$, and in that case the set-representation cannot
+%trivially make everything part of~$\aux$. 
 %\tsnote{Encoding secrets into~$M$ may cause some headaches in the security definitions; we'll see. }
@@
 
-The above definition can be lifted to the random-oracle model in the natural way
-by giving $\Rep, \Qry$ access to a random oracle. In that case,
-the probability in Equation~(\ref{eqn:correctness})
-is also taken over choice of the random oracle.
-
 \heading{Examples.}
-It is not hard to see Bloom filters are one possible instantiation of the above. If we fix some
-size bound~$n$, then $\mathcal{S}$ becomes the collection of all subsets of $U$
-of size (at most)~$n$. We also fix $\mathcal{Q} = U$, where a query ``$x$'' has
-the semantics ``is $x$ in $S$?'' Algorithm $\Rep$, which has values $k, m$ hardwired,
-chooses a set of hash functions $h_1, \ldots, h_k$ and computes an $m$-bit
-array in the usual way; a natural possibility is to set $\aux = (h_1, \ldots, h_k)$ (encoded as a string) and
-to let~$M$ be the bit array.  
+It is not hard to see Bloom filters are one possible instantiation a set-representation primitive.
+Fix an $n \geq 0$, let $\mathcal{S}=[\univ]^n$, and fix $\Sigma=\bits$.  
+Next, let $\calQ$ be a set of predicates $q_x$, one for each $x \in \univ$,
+such that $q_x(S)=1$ iff $x \in S$.
+Define algorithm~$\Rep$, with integers $k, m > 0$ and a description of a hash function family~$\mathcal{H}=\{h \colon \univ \to \{1,2,\ldots,m\}\}$ hardwared into it, to sample hash functions $h_1, \ldots, h_k$ from~$\mathcal{H}$ and then computes an $m$-bit array in the standard way.
+It sets $\aux = (h_1, \ldots, h_k)$ and $M$ to be the bit array, and returns these.
+The algorithm~$\Qry$ is defined so that, on input $(M,\aux,q_x)$, it returns 1 iff $M[h_1(x)]=1 \wedge M[h_2(x)]=1 \wedge \cdots \wedge M[h_k(x)]=1$ holds.
   %\tsnote{If $\mathcal{Q}=U$ and we use the
@@
 %  \jnote{In that sense, I am using ``soundness'' and ``correctness'' interchangeably here.}
-  \jnote{I'm not tied to allowing false negatives when we specialize the definition to the case
-  of set-membership queries. But in the abstract definition it seems unclear why one would choose
-  some queries on which error is ok and other queries where error is not allowed. Though if one
-  wanted to be general, one could simply have two (disjoint) sets of queries $\mathcal{Q}_1, \mathcal{Q}_2$
-  where error is allowed on the former but not on the latter.}
+%  \jnote{I'm not tied to allowing false negatives when we specialize the definition to the case
+%  of set-membership queries. But in the abstract definition it seems unclear why one would choose
+%  some queries on which error is ok and other queries where error is not allowed. Though if one
+%  wanted to be general, one could simply have two (disjoint) sets of queries $\mathcal{Q}_1, \mathcal{Q}_2$
+%  where error is allowed on the former but not on the latter.}
 We note that while our correctness condition does not distinguish among types of errors, it also does not preclude instantiations (like the classical Bloom filter) that admit only one type of error, e.g.
@@
 
-Setting $\Sigma=\bits^{\leq L}$ allows one to store a bitstring of length at most~$L$ at each location.
-This allows our syntax to capture the cuckoo-hashing construction from NY, as well as the ``garbled Bloom filter'' from Dong, Chen and Wen~\cite{xxx}, among other things.
-Setting $\Sigma=\mathbb{N}$ would allow for the storage of counters (say) at each position in~$M$, and a query ``$x$'' with the semantics ``what is the multiplicity of~$x$ in~$S$.''  (This does not capture counting Bloom filters, or the like, which do not have static representations.)  \tsnote{I guess this can all be accomplished with $\Sigma=\bits^*$, but it isn't necessarily the ``natural'' way.}
-%Our syntax also does not capture filters that are mutable, that is, whose representation may change over time.
-On the other hand, we can state a simple correctness condition for these kinds of filters; this will not be true when we further generalize to capture, properly, counters and mutability.
+The so-called ``garbled Bloom filter'' due to Dong, Chen and Wen~\cite{xxx}, which stores xor-shares of bitstring~$x \in S$ at positions $h_1(x),h_2(x),\ldots,h_k(x)$ in an array, can be captured by letting~$\Sigma=\bits^L$ for a specified integer~$L>0$.
+Similarly, one can capture the cuckoo-hashing construction from NY, which (loosely speaking) stores a hash $g(x)$ at positions determined by $h_1(x),h_2(x),\ldots,h_k(x)$.
+\tsnote{Check this, I forget the exact details now.}
+
+Expanding beyond queries that are predicates, consider $\Sigma=\bits^L$ and a scheme that stores $L$-bit counters at each position in an array.
+In particular, for each~$x \in S$ the $\Rep$~algorithm increments the counters stored at $h_1(x),h_2(x),\ldots,h_k(x)$, returns the final array of counters as~$M$.
+This representation naturally supports a set of queries $\calQ$ where $q_x$ has the semantics ``what is the multiplicity of~$x$ in~$S$.''   Such a construction gives a static version of a counting Bloom filter~\cite{xxx}.
+(We will capture dynamic versions, as well as count-min sketches, scalable Bloom filters, etc., in a later section.)

### 2016-07-22 syntax.tex
rewriting/fleshing out syntax section

@@
 
-The so-called ``garbled Bloom filter'' due to Dong, Chen and Wen~\cite{xxx}, which stores xor-shares of bitstring~$x \in S$ at positions $h_1(x),h_2(x),\ldots,h_k(x)$ in an array, can be captured by letting~$\Sigma=\bits^L$ for a specified integer~$L>0$.
-Similarly, one can capture the cuckoo-hashing construction from NY, which (loosely speaking) stores a hash $g(x)$ at positions determined by $h_1(x),h_2(x),\ldots,h_k(x)$.
+A Bloom filter with secret hash functions is captured by appending to~$M$ appropriate encodings of $h_1,h_2,\ldots,h_k$, and setting $\aux=\emptystring$.
+Related constructions that use a secret key~$K$, but not for hashing are captured in analogous ways.
+
+The so-called ``garbled Bloom filter'' due to Dong, Chen and Wen~\cite{xxx}, which stores xor-shares of bitstring~$x \in S$ at positions $h_1(x),h_2(x),\ldots,h_k(x)$ in an array, falls within our syntax by letting~$\Sigma=\bits^L$ for a specified integer~$L>0$.
+Similarly the cuckoo-hashing construction from NY, which (loosely speaking) stores a hash $g(x)$ at positions determined by $h_1(x),h_2(x),\ldots,h_k(x)$.
 \tsnote{Check this, I forget the exact details now.}

### 2016-07-22 correctness.tex
cheers

--- 2016-07-15 filters-notions.tex
@@
-\section{Security Notions for Hash-Based Filters}
+\section{Correctness Against Adaptive Adversaries}
+As highlighted by Naor and Yogev, Equation~(\ref{eqn:correctness}) is a non-adaptive version of correctness;
+we are interested in defining an adaptive (i.e., adversarial) notion
+of correctness.   Figure~\ref{fig:correctness} describes a security
+experiment that captures such a notion.
 
+First, a set~$S$ is chosen according to some
+distribution~$\distr{\calS}{}$ over the collection of multisets
+$\mathcal{S}$ associated to~$\Pi=(\Rep,\Qry)$, and then
+$\Rep(S)$ is run to generate $(M,\aux)$.
+%(Unless stated otherwise, we assume security holds for all distributions and thus for all sets $S$.)
+Adversary~$A$ is given~$\calS$ and $\aux$~as input; it is
+provided an oracle~$\TestOracle$ that, on input a query~$q \in \calQ$,
+computes (and returns) the result of $\Qry(M,\aux,q)$, and increments
+a counter if this result is in error.  The adversary wins if it
+manages to cause at least~$r>0$ such errors among its queries.
+
+The notion is lifted to the random-oracle model by providing
+$\Rep,\Qry$ and the adversary~$A$ with oracle access to the
+random-oracle(s).
+
+\begin{figure}[htp]
+\centering
+\fpage{.6}{
+\hpagess{.6}{.35}
+{
+\experimentv{$\ExpCorrect{\setprim,r}{\distr{\calS}{},A}$}\\
+$S \getsr \distr{\calS}{}$\\
+$\mathrm{err}\gets 0$\\
+$(M,\aux) \getsr \Rep(S)$\\
+$z \getsr A^{\TestOracle}(S,\aux)$\\
+if $\mathrm{err} < r$ then Return 0\\
+Return 1
+}
+%
+{
+\oracle{$\TestOracle(q)$}\\
+$a \gets \Qry(M,\aux,q)$\\
+if $a \neq q(S)$ then \\
+\nudge $\mathrm{err}\gets\mathrm{err}+1$\\
+Return~$a$
+}
+}
+\caption{Correctness of~$\Pi$ against (adaptive) adversary~$A$, when
+  the target multiset~$S$ is sampled from~$\calS$ according to distribution~$\distr{\calS}{}$.} 
+\label{fig:correctness}
+\end{figure}
+
+In this experiment we track the time-complexity (relative to some
+implied model of computation) and query-complexity (i.e., number of
+queries) of the adversary~$A$.  Roughly, we say that a
+set-representation~$\Pi$ is $(t,q,r,\epsilon')$-correct if the
+probability that any adversary with time-complexity~$t$ and
+query-complexity~$q$ causes~$r$ errors with probability at
+most~$\epsilon'$.  \tsnote{Maybe not... revisit.}
+
+\def\bin{{\sf Bin}}
+\heading{Defining adversarial advantage. } 
+For any scheme~$\Pi$ there is a trivial,
+\emph{non-adaptive} attack against this that wins a noticible fraction of the time.  In
+particular, let $q_1,q_2,\ldots,q_T$ be uniform samples from~$\calQ$.
+%The expected number of random queries needed to
+%find a error is $1/\epsilon$ tries; thus, an attacker making $O(t/\epsilon)$ queries succeeds with constant probability (almost always).
+%Actually, it seems worthwhile to formalize this. 
+Let $X_i$ be a random variable indicating the event $Qry(M,\aux,q_i)\neq q_i(S)$.  
+If~$\Pi$ is $\epsilon$-correct, then the probability that $X_i=1$ is at most~$\epsilon$.
+And if the experiment requires the adversary to induce~$r$ errors, the attack wins iff
+$N \stackrel{{\rm def}}{=} \sum_{i=1}^T X_i \geq r$.  Modelling the $X_i$ as independent Bernoulli trials with
+probability~$\epsilon$ gives $N$ a binomial distribution.  \fixme{Something feels wrong with this...}  
+Writing $\bin(T, \epsilon; r)$ for the probability that $N \geq r$,
+we conclude that the \emph{best} correctness we can hope for against adversaries making~$T$ queries is  $\bin(T,\epsilon; t))$.
+%\jnote{Need to find different terms to use for a query $q \in \mathcal{Q}$
+%and a query that the attacker makes to its oracle.}
+\tsnote{Viewed another way, we could let~$T$ be a negative binomial RV, and ask how many queries are needed (w.h.p) for $N \geq t$.}
+
+\jnote{One option is to define the adversary's \emph{advantage} as the difference between
+its success probability and the success probability of the above,
+trivial attack. Just a thought.}
+\tsnote{Or, perhaps by recasting security
+  as distinguishing between $\Qry(M,\aux,\cdot)$ and an oracle that
+  returns 0,1 according to Bernoulli with paramter~$\epsilon$.}
+
+\heading{Comparison to Naor-Yogev definition.}
+The style of the Naor-Yogev (NY) definition is slightly different. \jnote{Even if we ignore
+all the other issues, chief among them the inconsistent way it treats the hash functions.}
+Lifting their definition to our setting, the experiment is similar but the attacker
+succeeds only if it outputs a single query $q$ for which $\Qry( M,
+\aux, q) \neq q(S)$  \emph{subject to the restriction that it did not query $q$ to its $\Qry$ oracle}.
+It will be interesting to understand formally the relation between our definition and theirs.
+Here are some observations:
+\begin{enumerate}
+\item Say a scheme is $\epsilon_{NY}$-secure under the NY definition.
+Then we claim it is $(t,q, r, q\epsilon_{NY}/r)$-correct. To see
+this, assume not. Then there is a $t$-time attacker~$A$ that, with
+probability at least $\epsilon'=q\epsilon_{NY}/r$,
+issues~$q$ Test-queries of which at least~$r$ cause errors. If we simply run~$A$ and then choose a random Test-query to
+output, we succeed with probability at least $\epsilon' \cdot r/q$. It is unclear whether this is tight.
+
+\item There is a contrived scheme that is $(t, q, 2, 0)$-correct but not NY-secure at all; the basic idea is
+to have a set-representation that always has \emph{exactly one} false positive that is easy to find
+given the public information.
+
+\item If a scheme is $(t,q,1,\epsilon)$-correct, then it is also $\epsilon$-secure under the NY definition,
+at least for attackers making at most $q-1$ queries.
+This is immediate.
+\end{enumerate}
+
+\if{0}
 \heading{FP-security of hash-based filters.}

### 2016-07-25 correctness.tex
cheers
revamping section on trivial attacks

@@
 {
-\experimentv{$\ExpCorrect{\setprim,r}{\distr{\calS}{},A}$}\\
+\experimentv{$\ExpCorrect{\setprim,\distr{\calS}{},r}{A}$}\\
 $S \getsr \distr{\calS}{}$\\
@@
 implied model of computation) and query-complexity (i.e., number of
-queries) of the adversary~$A$.  Roughly, we say that a
-set-representation~$\Pi$ is $(t,q,r,\epsilon')$-correct if the
-probability that any adversary with time-complexity~$t$ and
-query-complexity~$q$ causes~$r$ errors with probability at
-most~$\epsilon'$.  \tsnote{Maybe not... revisit.}
+queries) of the adversary~$A$.  
+We define the advantage of adversary~$A$ in the correctness experiment as 
+\[
+\AdvCorrect{\Pi,\distr{\calS}{},r}{A} = \Prob{\ExpCorrect{\Pi,\distr{\calS}{}, r,}{A}}.
+\]
+and, overloading notation, we write $\AdvCorrect{\Pi,\distr{\calS}{},r}{t,q}$ for the maximum over all~$t$-time adversaries that ask at most~$q$ queries. Roughly, we say that a
+set-representation~$\Pi$ is $(t,q,r,\epsilon')$-correct if $\AdvCorrect{\Pi,\distr{\calS}{},r}{t,q} \leq \epsilon'$.
 
 \def\bin{{\sf Bin}}
-\heading{Defining adversarial advantage. } 
-For any scheme~$\Pi$ there is a trivial,
-\emph{non-adaptive} attack against this that wins a noticible fraction of the time.  In
-particular, let $q_1,q_2,\ldots,q_T$ be uniform samples from~$\calQ$.
+\heading{Observations on trivial attacks. } 
+Let~$\Pi$ be a scheme that is $\epsilon$-correct, and consider an attack that 
+asks random queries $q_1,q_2,\ldots,q_T$, i.e., uniform samples from~$\calQ$.
 %The expected number of random queries needed to
@@
 %Actually, it seems worthwhile to formalize this. 
-Let $X_i$ be a random variable indicating the event $Qry(M,\aux,q_i)\neq q_i(S)$.  
-If~$\Pi$ is $\epsilon$-correct, then the probability that $X_i=1$ is at most~$\epsilon$.
-And if the experiment requires the adversary to induce~$r$ errors, the attack wins iff
-$N \stackrel{{\rm def}}{=} \sum_{i=1}^T X_i \geq r$.  Modelling the $X_i$ as independent Bernoulli trials with
-probability~$\epsilon$ gives $N$ a binomial distribution.  \fixme{Something feels wrong with this...}  
-Writing $\bin(T, \epsilon; r)$ for the probability that $N \geq r$,
-we conclude that the \emph{best} correctness we can hope for against adversaries making~$T$ queries is  $\bin(T,\epsilon; t))$.
+Let $X_i$ be a random variable indicating the event $\Qry(M,\aux,q_i)\neq q_i(S)$.  
+The $\epsilon$-correctness of~$\Pi$ guarantees that the probability that $X_i=1$ is at most~$\epsilon$, 
+and it is tempting to model the~$X_i$ as i.i.d. Bernoulli trials with success probability~$\epsilon$.
+However, a moment's reflection shows that this is not the case.
+Consider the following scheme.
+Fix $|S|=n$ for all $S \in \calS$, where $n \ll |\univ|$.
+For the queries, let $\calQ = \{q_x\colon \calS \to \bits \,|\, \forall x \in \univ\}$ where $\forall S \in \calS$ the predicate $q_x(S)=1 \Leftrightarrow x \in S$.
+Let $\Rep(S)$ pick a random element~$s \in S$, and return $M = S \setminus \{s\}$ and $\aux = \emptystring$.
+To respond to queries, let~$\Qry(M,\aux,q_x)=1$ iff $x \in M$.
+It is easy to see that this scheme is $1/n$-correct; for any fixed~$S$, there are exactly~$n$ queries~$q_x$ that have probability~$1/n$  (over the coins of~$\Rep$) of causing a correctness error.
+Moreover, once the coins of~$\Rep$ are fixed, there is exactly \emph{one} query that will cause an error.
+Thus $\Prob{X_i=1}=1/|\univ| \ll 1/n = \epsilon$.
+
+This example is contrived, but the point is that $\epsilon$-correctness is measured over the coins of~$\Rep$, for a fixed~$S$ and query~$q$; once the coins of~$\Rep$ are fixed, it is not straightforward how to connect~$\epsilon$ to events that depend on other sources of randomness.
+\tsnote{Not sure if there's more to say in this section, or if what's here is already too much.}
+
+%
+%And if the experiment requires the adversary to induce~$r$ errors, the attack wins iff
+%$N \stackrel{{\rm def}}{=} \sum_{i=1}^T X_i \geq r$.  Modelling the $X_i$ as independent Bernoulli trials with
+%probability~$\epsilon$ gives $N$ a binomial distribution.  \fixme{Something feels wrong with this...}  
+%Writing $\bin(T, \epsilon; r)$ for the probability that $N \geq r$,
+%we conclude that the \emph{best} correctness we can hope for against adversaries making~$T$ queries is  $\bin(T,\epsilon; t))$.
 %\jnote{Need to find different terms to use for a query $q \in \mathcal{Q}$
 %and a query that the attacker makes to its oracle.}
-\tsnote{Viewed another way, we could let~$T$ be a negative binomial RV, and ask how many queries are needed (w.h.p) for $N \geq t$.}
-
-\jnote{One option is to define the adversary's \emph{advantage} as the difference between
-its success probability and the success probability of the above,
-trivial attack. Just a thought.}
-\tsnote{Or, perhaps by recasting security
-  as distinguishing between $\Qry(M,\aux,\cdot)$ and an oracle that
-  returns 0,1 according to Bernoulli with paramter~$\epsilon$.}
+%\tsnote{Viewed another way, we could let~$T$ be a negative binomial RV, and ask how many queries are needed (w.h.p) for $N \geq t$.} 
+%
+%\jnote{One option is to define the adversary's \emph{advantage} as the difference between
+%its success probability and the success probability of the above,
+%trivial attack. Just a thought.}
+%\tsnote{Or, perhaps by recasting security
+%  as distinguishing between $\Qry(M,\aux,\cdot)$ and an oracle that
+%  returns 0,1 according to Bernoulli with paramter~$\epsilon$.}
+%\fixme{Not clear this attack is generically applicable enough to serve as a reference/baseline.
+(See email discusssion 7/23.)  Might be worth pointing out that this intuition, between non-adaptive error-probability and the expected number of queries to find an error, can be quite misleading.}
 

### 2016-07-25 correctness.tex
revamping section on trivial attacks

@@
 We define the advantage of adversary~$A$ in the correctness experiment as 
-\[
-\AdvCorrect{\Pi,\distr{\calS}{},r}{A} = \Prob{\ExpCorrect{\Pi,\distr{\calS}{}, r,}{A}}.
-\]
-and, overloading notation, we write $\AdvCorrect{\Pi,\distr{\calS}{},r}{t,q}$ for the maximum over all~$t$-time adversaries that ask at most~$q$ queries. Roughly, we say that a
+$\AdvCorrect{\Pi,\distr{\calS}{},r}{A} = \Prob{\ExpCorrect{\Pi,\distr{\calS}{}, r,}{A}=1}$.
+Overloading notation, we write $\AdvCorrect{\Pi,\distr{\calS}{},r}{t,q}$ for the maximum over all~$t$-time adversaries that ask at most~$q$ queries. Roughly, we say that a
 set-representation~$\Pi$ is $(t,q,r,\epsilon')$-correct if $\AdvCorrect{\Pi,\distr{\calS}{},r}{t,q} \leq \epsilon'$.

### 2016-07-25 Theorem1_FP.tex
more clean up of Animesh's Theorem 1

@@
 
-\fixme{Note: the following theorem is incorrect for $t>1$.  Or, at least, the proof does not cover $t>1$.}\acnote{Modified.}
+\fixme{Note: the following theorem is incorrect for $r>1$.  Or, at least, the proof does not cover $t>1$.}\acnote{Modified.}
 \begin{theorem}\label{thm1}
 Fix $k,m,n>0$, and let $B_\mathrm{lin}=(\Hash,\Rep,\Qry)$ be the hash-based filter just described. 
-Let~$A$ be an adversary, compatible with $\ExpFPSecHash{B_\mathrm{lin},t}{\cdot}$, that asks at most~$q$ queries to its $\QryOracle$ oracle.  Then there exist adversaries~$B_1$ and $B_2$ such that
+Let~$A$ be an adversary, compatible with $\ExpFPSecHash{B_\mathrm{lin},r}{\cdot}$, that asks at most~$q$ queries to its $\QryOracle$ oracle.  Then 
 \[
-\AdvFPSecHash{B_{\mathrm{lin}},t}{A} \leq  \AdvPRF{F}{B_1} +
-\AdvPRF{F}{B_2}  +{\dbinom{q}{t}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^t
+\AdvFPSecHash{B_{\mathrm{lin}},r}{A} \leq  \AdvPRF{F}{B_1} +
+\AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
 \]
+for PRF-adversaries~$B_1$ and $B_2$ given explicitly in the proof of
+this theorem.  \tsnote{Statement about resources of these reductions.}
 \end{theorem}
 Before giving the proof, we note that Kirsch and Mitzenmacher~\cite{xxx} show
-that the ($t=1$, non-adaptive) FP-probability for~$B_\mathrm{lin}$ is
+that the ($r=1$, non-adaptive) FP-probability for~$B_\mathrm{lin}$ is
 always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
-rate of convergence is faster than~$1/n$.  The factor of $\dbinom{q}{t}$ arises as a result
-of removing adaptivity.  Finally, $\dbinom{q}{t} \leq q^t$ (with
+rate of convergence is faster than~$1/n$.  The factor of $\dbinom{q}{r}$ arises as a result
+of removing adaptivity.  Finally, $\dbinom{q}{r} \leq q^r$ (with
 reasonable tightness when~$t$ is small) in which case the final term in the bound behaves as 
-$(q (1-e^{-kn/m})^k + O(q/n) )^t$; loosely, the bound one expects for
+$(q (1-e^{-kn/m})^k + O(q/n) )^r$; loosely, the bound one expects for
 trying to find a single FP in each of~$t$ independent``rounds'', each round
@@
 The proof of the theorem will use a game playing argument as shown in \Cref{fig:Game}.
-$\game{0}(A)$ exactly simulates $\ExpFPSecHash{B_\mathrm{lin},t}{A}$ with hash functions $h_j(x) =  F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$.
+$\game{0}(A)$ exactly simulates $\ExpFPSecHash{B_\mathrm{lin},r}{A}$ with hash functions $h_j(x) =  F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$.
 So,
 \begin{equation}
-\AdvFPSecHash{B_{\mathrm{lin}},t}{A} = \Prob{\game{0}(A)=1}\label{eq:0}
+\AdvFPSecHash{B_{\mathrm{lin}},r}{A} = \Prob{\game{0}(A)=1}\label{eq:0}
 \end{equation}
@@
 Here, $\rho_1$ and $\rho_2$ are random functions sampled from $\Func{\univ,[m]}$. \\
-\noindent
-Let adversaries $B_1, B_2$ simulate $\game{1}(A)$ and $\game{2}(A)$ respectively as shown in \Cref{fig:BGame1}.
-When $b=0$, $B_1$ wins if $\game{1}(A)$ outputs 0; $B_2$ wins if $\game{2}(A)$ returns 0.
-When $b=1$, $B_1$ and $B_2$ exactly simulate $\game{0}(A)$ and $\game{1}(A)$.
-Thus, we have
 
+\tsnote{The PRF experiment has not be defined yet, so strictly
+  speaking these claims make no sense. }
+Let adversaries $B_1, B_2$ be as shown in Figures~\ref{xxx}.  By
+construction, these simulate $\game{1}(A)$ and $\game{2}(A)$,
+respectively. When $b=0$, $B_1$ wins if $\game{1}(A)$ outputs 0; $B_2$
+wins if $\game{2}(A)$ returns 0. When $b=1$, $B_1$ and $B_2$ exactly
+simulate $\game{0}(A)$ and $\game{1}(A)$.  \tsnote{What is~$b$?} Thus, we have
 \begin{align}
@@
 $\calZ \getsr A^{\QryOracle}(\calS)$\\
-if $|\calZ| < t$ or $\calZ \cap \calS \neq \emptyset$ then \\
+if $|\calZ| < r$ or $\calZ \cap \calS \neq \emptyset$ then \\
 \nudge Ret 0\\
@@
 \oracle{$\HashOracle(x)$}\\
-$h_i(x) = F_{K_1}(x)+i \cdot F_{K_2}(x)$, for $i\in[1,k]$\\
+$h_i(x) = F_{K_1}(x)+i \cdot F_{K_2}(x) \bmod m$, for $i\in[1,k]$\\
 Ret $\left(h_1(x),\ldots,h_k(x)\right)$
@@
 \oracle{$\HashOracle(x)$}\\
-$h_i(x) = F_{K_1}(x)+i \cdot \rho(x)$, for $i\in[1,k]$\\
+$h_i(x) = F_{K_1}(x)+i \cdot \rho(x) \bmod m$, for $i\in[1,k]$\\
 Ret $\left(h_1(x),\ldots,h_k(x)\right)$
@@
 \oracle{$\HashOracle(x)$}\\
-$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
+$h_i(x) = \rho_1(x)+i \cdot \rho_2(x) \bmod m$, for $i\in[1,k]$\\
 Ret $\left(h_1(x),\ldots,h_k(x)\right)$
@@
 {
-\underline{$\game{3}(A)$}\\
-$\calY \gets \emptyset $\\
-$\rho_1,\rho_2 \getsr \Func{\univ,[m]}$\\
+\underline{{$\game{3}(A)$},\fbox{$\game{4}(A)$}}\\
+$c \gets 0$\\
+$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
+%$\calY \gets \emptyset $\\
+%$\rho_1,\rho_2 \getsr \Func{\univ,[m]}$\\
 $S \getsr \distr{\univ}{n}$\\
@@
 $\calZ \getsr A^{\QryOracle}(\calS)$\\
-if $|\calY| < t$ then \\ 
-\nudge Ret 0\\
-for $i=1$ to $t$ \\
-\nudge $z_i \getsr \calY $\\
-\nudge $\calY \gets \calY \setminus \{z_i\}$\\
-\nudge if $\Qry^{\HashOracle}(M,z_i)=0$ then\\
-\nudge \nudge Ret 0\\
-Ret 1\\\\
+if $|\calZ| < r$ or $\calZ \cap \calS \neq \emptyset$ then Ret 0\\
+if $\forall z \in \calZ,\,\Qry^{\HashOracle}(M,z)=1$ then \\
+\nudge if $\bad=\true$ then \fbox{Ret 0}\\
+\nudge Ret 1\\
+Ret 0\\\\
+%if $|\calY| < t$ then \\ 
+%\nudge Ret 0\\
+%for $i=1$ to $t$ \\
+%\nudge $z_i \getsr \calY $\\
+%\nudge $\calY \gets \calY \setminus \{z_i\}$\\
+%\nudge if $\Qry^{\HashOracle}(M,z_i)=0$ then\\
+%\nudge \nudge Ret 0\\
+%Ret 1\\\\
 %
 \oracle{$\QryOracle(x)$}\\
-$\calY \gets \calY \cup \{x\}$\\
-Ret $\Qry^{\HashOracle}(M,x)$\\\\
+%$\calY \gets \calY \cup \{x\}$\\
+$c \gets c+1$\\
+$v \gets \Qry^{\HashOracle}(M,x)$\\
+if $c \in \mathcal{I}$ and $v\neq 1$ then\\
+\nudge $\bad \gets \true$ \\
+%\nudge \fbox{Ret 1} \\
+if $c \not\in \mathcal{I}$ and $v\neq 0$ then\\
+\nudge $\bad \gets \true$\\
+%\nudge \fbox{Ret 0}\\
+Ret~$v$\\\\
 %
 \oracle{$\HashOracle(x)$}\\
-$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
-Ret $\left(h_1(x),\ldots,h_k(x)\right)$
+$a,b \getsr [m]$\\
+for $i = 1$ to~$k$, $v_i = a+i \cdot b \bmod m$\\
+Ret $\left(v_1,\ldots,v_k\right)$
 }
@@
 \noindent
-In $\game{3}(A)$, $t$ elements are sampled from the $q$ adaptive queries and tested for false positives.
-This is equivalent to $\game{2}(A)$, as the hash functions of the $\HashOracle$ oracle are random and $A$ wins this  game only if it outputs atleast $t$ FP's.\acnote{I was facing problems in connecting game2(adaptive) and game3(non-adaptive).
-I felt that the probability of  winning both games should be equal as the hash functions in the hash oracle are random(not independent) and adversary in game 2 has no means to output t elements which have higher chance of winning than those in game 3.}
+In $\game{3}(A)$, $t$ elements are sampled from the $q$ adaptive
+queries and tested for false positives. This is equivalent to
+$\game{2}(A)$, as the hash functions of the $\HashOracle$ oracle are
+random and $A$ wins this  game only if it outputs atleast $t$
+FP's.\acnote{I was facing problems in connecting game2(adaptive) and
+  game3(non-adaptive). I felt that the probability of  winning both
+  games should be equal as the hash functions in the hash oracle are
+  random(not independent) and adversary in game 2 has no means to
+  output t elements which have higher chance of winning than those in
+  game 3.} \tsnote{I have rewritten game $\game{3}(A)$ and added
+  $\game{4}(A)$.  It should be that
+  $\Prob{\game{2}(A)}=\Prob{\game{3}(A)=1}$. Moreover
+  $\Prob{\game{4}(A)=1} = \Prob{\game{3}(A)=1 \wedge \neg\bad} =
+  \Prob{\game{3}(A)=1}\Prob{\game{3}{A}:\,\neg\bad} =
+  \Prob{\game{3}(A)=1}\frac{1}{\dbinom{q}{r}}$. Finally the event
+  $\game{4}(A)=1$ happens iff $\bad \neq \true$.  That means there is
+  a non-adaptive adversary that runs~$A$, simulates $\QryOracle$ by
+  simply returning 1 iff $c \in \mathcal{I}$, and uses the queries
+  with indices in $\mathcal{I}$ as its non-adaptive FPs.  To be
+  totally clear, you might want to add a $\game{5}(A)$ that has this
+  $\QryOracle$ behavior, and then give the non-adaptive FP-adversary~$A'$ that
+simulates~$\game{5}(A)$, and so on. }\fixme{Clean up everything after this.}
 \begin{equation}
@@
 \Prob{\game{3}(A)=1} &= \Prob{D \, \mbox{outputs $t$ FP} \,}\label{eq:4a}\\
-\nonumber \Prob{D \, \mbox{outputs t FP} \,} &= \dbinom{q}{t}\times \Big[\Prob{D' \, \mbox{outputs FP} \,}\Big]^t\\
-& \leq \dbinom{q}{t}\times \Big[(1-e^{-kn/m})^k +O(1/n)\Big]^t \label{eq:4b}
+\nonumber \Prob{D \, \mbox{outputs t FP} \,} &= \dbinom{q}{r}\times \Big[\Prob{D' \, \mbox{outputs FP} \,}\Big]^r\\
+& \leq \dbinom{q}{r}\times \Big[(1-e^{-kn/m})^k +O(1/n)\Big]^r \label{eq:4b}
 \end{align}
@@
 \begin{equation}
-\Prob{\game{3}(A)=1} \leq \dbinom{q}{t}\times [(1-e^{-kn/m})^k +O(1/n)]^t \label{eq:4}
+\Prob{\game{3}(A)=1} \leq \dbinom{q}{r}\times [(1-e^{-kn/m})^k +O(1/n)]^r \label{eq:4}
 \end{equation}
@@
 \end{figure}	
-
+\fixme{These adversaries are incorrect.  They are FP adversaries, so
+  they get~$S$ as input.  They also do not sample random functions;
+  use lazy sampling (a la game $\game{3}(A)$.  Please clean things up.)}
 \noindent

### 2016-07-25 correctness.tex
cheers

@@
 However, a moment's reflection shows that this is not the case.
-Consider the following scheme.
+Concretely, consider the following scheme.
 Fix $|S|=n$ for all $S \in \calS$, where $n \ll |\univ|$.
@@
 To respond to queries, let~$\Qry(M,\aux,q_x)=1$ iff $x \in M$.
-It is easy to see that this scheme is $1/n$-correct; for any fixed~$S$, there are exactly~$n$ queries~$q_x$ that have probability~$1/n$  (over the coins of~$\Rep$) of causing a correctness error.
+It is easy to see that this scheme is $1/n$-correct; for any fixed~$S$, there are exactly~$n$ queries~$q_x$ that have probability~$1/n$  (over the coins of~$\Rep$) of causing a correctness error, and the remaining $|\univ|-n$ queries have probability zero of causing an error.
 Moreover, once the coins of~$\Rep$ are fixed, there is exactly \emph{one} query that will cause an error.
-Thus $\Prob{X_i=1}=1/|\univ| \ll 1/n = \epsilon$.
+Thus for random queries from~$Q$, for all~$i\in[T]$ we have $\Prob{X_i=1}=1/|\univ| \ll 1/n = \epsilon$.
 

### 2016-07-25 privacy.tex
adding privacy experiments
questions about 'indistinguishability' privacy notion

@@
 it is disallowed from asking any query $q$ for which $q(S_0) \neq
-q(S_1)$. \tsnote{How will the adversary know that a query satisfies
-  this in (say) the case of the classical BF?  We can, of course,
-enforce it in the experiment, but then our resource accounting risks
-overcounting the number of queries.} \jnote{I was assuming the attacker knows $S_0, S_1$.}
-\tsnote{Also, we need that, in general, $\aux$ itself
-does not leak information about~$S_0$ vs.\ $S_1$. } \jnote{Sure, this would be implied
-by the definition in this case.}
+q(S_1)$. \tsnote{I'm not convinced this is the right restriction.
+  This says that security is required \emph{only} for properties that are
+  true of both sets.  So a scheme with $M=S$ will be trivially secure
+  against set membership queries.  } \tsnote{Do you mean to
+  assume that the attacker does not ask~$q$ such that $q(S_0)=q(S_1)$
+  because these are pointless?}
+%\tsnote{How will the adversary know that a query satisfies
+%  this in (say) the case of the classical BF?  We can, of course,
+%enforce it in the experiment, but then our resource accounting risks
+%overcounting the number of queries.} \jnote{I was assuming the attacker knows $S_0, S_1$.}
+%\tsnote{Also, we need that, in general, $\aux$ itself
+%does not leak information about~$S_0$ vs.\ $S_1$. } \jnote{Sure, this would be implied
+%by the definition in this case.}
 \end{enumerate}
+
+\begin{figure}[htp]
+\centering
+\hfpages{.45}{
+\hpagess{.5}{.45}
+{
+\experimentv{$\ExpWPriv{\setprim,\distr{\calS}{}}{A}$}\\
+$S \getsr \distr{\calS}{}$\\
+$(M,\aux) \getsr \Rep(S)$\\
+$z \getsr A^{\TestOracle}(\aux)$\\
+if $z \in S$ then Return 1\\
+Return 0
+
+\medskip
+\experimentv{$\ExpPriv{\setprim,\distr{\calS}{}}{A}$}\\
+$S \getsr \distr{\calS}{}$\\
+$(M,\aux) \getsr \Rep(S)$\\
+$z \getsr A(M,\aux)$\\
+if $z \in S$ then Return 1\\
+Return 0
+}
+%
+{
+\oracle{$\TestOracle(q)$}\\
+$a \gets \Qry(M,\aux,q)$\\
+Return~$a$
+}
+}
+%
+{
+\hpagess{.5}{.45}
+{
+\experimentv{$\ExpPriv{\setprim}{A}$}\\
+$b \getsr \bits$\\
+$z \getsr A^{\RepOracle,\TestOracle}()$\\
+if $z = b$ then Return 1\\
+Return 0
+}
+%
+{
+\oracle{$\RepOracle(S_0,S_1)$}\\
+if $\mathrm{used}=\true$ then \\
+\nudge Ret $\bot$\\
+$\mathrm{used}=\true$\\
+$(M,\aux) \getsr \Rep(S_b)$\\
+Return $\aux$\\
+
+\medskip
+\oracle{$\TestOracle(q)$}\\
+$a \gets \Qry(M,\aux,q)$\\
+Return~$a$
+}
+}
+\caption{Privacy notions. (Still playing...)} 
+\label{fig:privacy}
+\end{figure}

### 2016-07-25 privacy.tex
questions about 'indistinguishability' privacy notion
cheers

@@
   assume that the attacker does not ask~$q$ such that $q(S_0)=q(S_1)$
-  because these are pointless?}
+  because these are pointless?  Otherwise, I don't see a need for restrictions.}
 %\tsnote{How will the adversary know that a query satisfies
@@
 if $z \in S$ then Return 1\\
-Return 0
+Return 0\\
 }
@@
 if $z = b$ then Return 1\\
-Return 0
+Return 0\\
 }
@@
 if $\mathrm{used}=\true$ then \\
+\nudge Ret $\bot$\\
+if $|S_0|\neq|S_1|$ then \\
 \nudge Ret $\bot$\\
@@
 $a \gets \Qry(M,\aux,q)$\\
-Return~$a$
+Return~$a$\\
 }
 }
-\caption{Privacy notions. (Still playing...)} 
+\caption{Privacy notions. {\bf Left:} ``One-wayness'' style
+  definitions. The top is a weaker notion, because the representation
+  is hidden from the adversary. {\bf Right:} An
+  ``indistinguishability'' style notion. (Still playing...)} 
 \label{fig:privacy}

### 2016-07-25 syntax.tex
cheers

@@
 such that $q_x(S)=1$ iff $x \in S$.
-Define algorithm~$\Rep$, with integers $k, m > 0$ and a description of a hash function family~$\mathcal{H}=\{h \colon \univ \to \{1,2,\ldots,m\}\}$ hardwared into it, to sample hash functions $h_1, \ldots, h_k$ from~$\mathcal{H}$ and then computes an $m$-bit array in the standard way.
+Define algorithm~$\Rep$, with functions $k=k(|S|), m=m(|S|)$ and a description of a hash function family~$\mathcal{H}=\{h \colon \univ \to \{1,2,\ldots,m\}\}$ hardwired into it, to sample hash functions $h_1, \ldots, h_k$ from~$\mathcal{H}$ and then computes an $m$-bit array in the standard way.
 It sets $\aux = (h_1, \ldots, h_k)$ and $M$ to be the bit array, and returns these.

### 2016-07-26 notions.tex
cheers

--- 2016-07-25 correctness.tex
@@
-\section{Correctness Against Adaptive Adversaries}
+\section{Security Notions}
+\tsnote{intro text}
+
+\subsection{Correctness Against Adaptive Adversaries}
 As highlighted by Naor and Yogev, Equation~(\ref{eqn:correctness}) is a non-adaptive version of correctness;
@@
 
-\if{0}
-\heading{FP-security of hash-based filters.}
-%\tsnote{NY give it in the private hash setting (sort of); but, intuitively, it should be hard to find false-positives even if you know that MD5 or SHA-x are the hash functions.
-Not totally sure how to capture this intuition nicely.}
-%
-%\jnote{Not sure I agree.
-First of all, if $\epsilon$ is not negligible then a random element is a false positive with noticeable probability.
-Beyond that, I think that intuitively it makes sense that if you want false positives to be hard to find then you need to make the hash functions secret.}
-%
-%\tsnote{I don't think it makes sense to talk about asymptotics or negligibility, for exactly the reason you state.
-I think the key point here is: what is ``hard''?
-The designer decides what FP rate is acceptable for a given application, a given set of efficiency constraints, the side-effects of a FP, etc.
-For a fixed FP target, she optimizes the filter size and/or the number of hash functions for her setting.
-Whether the target FP rate is 0.01 or $2^{-80}$, we should be able to say (in the ROM, at least) that it will take this-many hash computations, and this many on-line set-membership queries, to find the first FP.
-In the standard model, with public hash functions, it is clearly more difficult to make formal claims.
-Even so, in practice I expect it would be quite expensive to find a string~$x$ such that $(h_1(x),h_2(x),\ldots,h_k(x))$ falls in a given set of tuples when $h_i(x)=\mathrm{truncate}(\mathrm{SHA256}(\langle i \rangle \concat x), m)$, say.
-(Even more so if my setting admits relatively expensive hash computations, e.g.
-SCRYPT.) BTW, your suggestion to have a FP notion with secret~$\mathcal{S}$ is interesting here.
-}
-%
-The traditional notion of soundness for a Bloom filter captures the difficulty of finding false positives when the attacker is non-adaptive.
-Following NY, we consider soundness against adaptive adversaries.
-But we further generalize to allow for settings in which the attacker may have some a priori knowledge about the contents of~$\calS$.
-(The Niedermaier et al.~\cite{xxx} attacks, for example, exploit knowledge about the distribution of German last names.) In particular, our notions take as input an explicit distribution $\distr{U}{n}$ over~$[U]^n$.
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
-%\jknote{We also want to capture the fact that finding the first false positive should not make it any easier to find subsequent false positives.
-This is not really captured by the Naor paper, either (at least not directly, though it may end up being implied by their definition).}
-%
-%\tsnote{See my comment in the intro.}
+\subsection{Notions of Privacy}
+One can also consider the orthogonal notion of privacy for a set-representation.
+\jnote{Actually, I am now unsure what the right way to define it is. It seems natural
+to give the attacker $\aux$. But if we give them $\aux$ and $M$ then they have everything.
+If $S$ has high min-entropy (element-wise), then it might still be
+possible to have security here.}\tsnote{I think we will always bump up
+against the (element-wise) min-entropy of the distribution over~$S$,
+at least in the ``one-wayness'' style definition that I had been imagining. }
+There are several possible definitions:
+\begin{enumerate}
+\item A ``one-wayness'' definition where $S$ has high min-entropy (element-wise), and we
+give the attacker $\aux$ and either $M$ or oracle access to $\Qry$. The attacker
+succeeds if it can output an element in~$S$.
 
-In Figure~\ref{fig:fp-filter} we give three distinct notions, characterized by what access the adversary has to the underlying hash functions used by the filter.
-In the top notion, the hash functions are secret.
-This is the setting addressed by NY, and it captures applications in which the hash functions are (say) secretly keyed PRFs, and in which no explicit, external interface to these is surfaced.
-%
-The bottom notion considers the case that the full code of the hash functions is known to the attacker.
-This is the case, for example, when attacking the Bloom filters used in the Squid proxy~\cite{xxx}.
-%
-The middle notion is a compromise: it makes the hash functions
-public, but assumes that the adversary only accesses them in a
-black-box manner.  That is, the adversary does not exploit
-structural features of the hash functions in its attack.  This
-notion makes it easy to track the query complexity of an attack, and
-also allows us to capture constructions in the random-oracle model.
-\tsnote{This is the setting for the Neidermayer et al.\  attacks.
-It's also the setting for ROM attacks.} \jnote{I don't think the
-middle notion is interesting. I disagree regarding the attacks of
-Neidermayer et al.: there, the hash functions are secret (though
-they are based on public ``random oracles'' $g$ and $h$). The ROM
-can be handled separately by giving all algorithms access to
-the~RO.}\tsnote{You're correct; I misread some of the text.  It is
-only the setup for the attack that needs access to the hash functions,
-and this is just modeling what is likely to appear in the real
-``encrypted'' BFs.}
+\item An ``indistinguishability'' definition where either $S_0$ or $S_1$ is used, and the attacker
+must determine which. Here the attacker is given $\aux$ but only oracle access to $\Qry$, and
+it is disallowed from asking any query $q$ for which $q(S_0) \neq
+q(S_1)$. \tsnote{I'm not convinced this is the right restriction.
+  This says that security is required \emph{only} for properties that are
+  true of both sets.  So a scheme with $M=S$ will be trivially secure
+  against set membership queries.  } \tsnote{Do you mean to
+  assume that the attacker does not ask~$q$ such that $q(S_0)=q(S_1)$
+  because these are pointless?  Otherwise, I don't see a need for restrictions.}
+%\tsnote{How will the adversary know that a query satisfies
+%  this in (say) the case of the classical BF?  We can, of course,
+%enforce it in the experiment, but then our resource accounting risks
+%overcounting the number of queries.} \jnote{I was assuming the attacker knows $S_0, S_1$.}
+%\tsnote{Also, we need that, in general, $\aux$ itself
+%does not leak information about~$S_0$ vs.\ $S_1$. } \jnote{Sure, this would be implied
+%by the definition in this case.}
+\end{enumerate}
 
-For each experiment, we define an associated advantage
-notion.  Namely, given an $(n,k,m)$-filter~$B=(\Hash,\Rep,\Qry)$,
-distribution~$\distr{U}{n}$ and adversary~$A$, we define:
-\begin{align*}
-\AdvFPSecHash{B,t}{\distr{U}{n},A} &= \Prob{\ExpFPSecHash{B,t}{\distr{U}{n},A}=1} \\
-\AdvFPPubHashBB{B,t}{\distr{U}{n},A} &= \Prob{\ExpFPPubHashBB{B,t}{\distr{U}{n},A}=1} \\
-\AdvFPSecHash{B,t}{\distr{U}{n},A} &= \Prob{\ExpFPPubHash{B,t}{\distr{U}{n},A}=1}
-\end{align*}
-The probabilities are over the coins of the indicated experiment,
-and the coins of the adversary.   In all experiments, we track the
-time-complexity~$t$ of~$A$, as well as the number of set-membership
-($\QryOracle$ oracle) queries~$q_{\mathrm{sm}}$ that it makes.   In
-the second, we also track the number of hash-queries
-$q_{\mathrm{h}}$ that the adversary makes.
+\begin{figure}[htp]
+\centering
+\hfpages{.45}{
+\hpagess{.5}{.45}
+{
+\experimentv{$\ExpWPriv{\setprim,\distr{\calS}{}}{A}$}\\
+$S \getsr \distr{\calS}{}$\\
+$(M,\aux) \getsr \Rep(S)$\\
+$z \getsr A^{\TestOracle}(\aux)$\\
+if $z \in S$ then Return 1\\
+Return 0
 
-We note that the distribution~$\distr{U}{n}$ must be independent of
-the hash functions $h_1,h_2,\ldots,h_k$ that are used to create~$M$.
-Otherwise, when (say) $\Sigma=\bits$, the distribution may only
-assign positive probability to sets~$\calS$ that cause an abnormally
-large number of bits in~$M$ to be set to 1.  Our security notions
-enforce this independence.
-
-\jnote{How do we want to define a ``secure'' Bloom filter (even informally)?
-Do we want to say that the probability of finding a false positive is negligible?
-Or that if we set the FP rate to $\epsilon$ then the best an attacker can do with $q$ hash queries is $1-(1-\epsilon)^q$ plus negligible?}
-%
-\tsnote{Formally, I don't think we can (and still be rooted in
-reality).  Even informally it's hard, since the fact is that the
-designer decides what is ``secure'' for her setting.  I think we
-just say something like ``A bloom filter is
-$(t,q_h,q_m,\epsilon)$-secure if no attacker running in time at
-most~$t$, asking at most~$q_h$ hash queries and $q_m$ set-membership
-queries, has probability more than~$\epsilon$ of finding a FP.''
-Perhaps informally we say that a bloom filter is secure if, for
-``reasonable'' $t,q_h,q_m$, the value of~$\epsilon$ is not
-``significantly larger'' than the designer's target.  I guess that's
-not far off from one of your suggestions.}
-
-%\jnote{One thing that is nice about the NY notion is that you get a ``clean'' definition of security: no matter how many FPs the attacker has found so far, the probability that it can output a fresh FP is still $\epsilon$.}
-
-\begin{figure}
-\centering
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpFPSecHash{B,t}{\distr{U}{n},A}$}\\
-$\calS \getsr \distr{U}{n}$\\
-$h_1,\ldots,h_k \getsr \Hash$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
-$\calX \getsr A^{\QryOracle}(\calS)$\\
-if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
-\nudge Ret 0\\
-If $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
-\nudge Ret 0\\
-Ret 1
+\medskip
+\experimentv{$\ExpPriv{\setprim,\distr{\calS}{}}{A}$}\\
+$S \getsr \distr{\calS}{}$\\
+$(M,\aux) \getsr \Rep(S)$\\
+$z \getsr A(M,\aux)$\\
+if $z \in S$ then Return 1\\
+Return 0\\
 }
@@
 {
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
-
-\medskip
-\oracle{$\HashOracle(x)$}\\
-Ret $\left(h_1(x),\ldots,h_k(x)\right)$\\
+\oracle{$\TestOracle(q)$}\\
+$a \gets \Qry(M,\aux,q)$\\
+Return~$a$
 }
-}
-%%%%%%%
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpFPPubHashBB{B,t}{\distr{U}{n}, A}$}\\
-$\calS \getsr \distr{U}{n}$\\
-$h_1,\ldots,h_k \getsr \Hash$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
-$\calX \getsr A^{\QryOracle,\HashOracle}(\calS)$\\
-if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
-\nudge Ret 0\\
-If $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
-\nudge Ret 0\\
-Ret 1
 }
@@
 {
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
-
-\medskip
-\oracle{$\HashOracle(x)$}\\
-Ret $\left(h_1(x),\ldots,h_k(x)\right)$\\
-}
-}
-%%%%%%%
-\fpage{.6}{
-\hpagess{.6}{.35}
+\hpagess{.5}{.45}
 {
-\experimentv{$\ExpFPPubHash{B,t}{\distr{U}{n}, A}$}\\
-$\calS \getsr \distr{U}{n}$\\
-$h_1,\ldots,h_k \getsr \Hash$\\
-$(M,\tau) \gets \Rep^{\HashOracle}(\calS)$\\
-$\calX \getsr A^{\QryOracle}(S,\{h_1,h_2,\ldots,h_k\})$\\
-if $|\calX| < t$ or $\calX \cap \calS \neq \emptyset$ then \\
-\nudge Ret 0\\
-If $\exists x \in \calX$ s.t. $\Qry^{\HashOracle}(M,\tau,x)=0$ then\\
-\nudge Ret 0\\
-Ret 1
+\experimentv{$\ExpPrivInd{\setprim}{A}$}\\
+$b \getsr \bits$\\
+$z \getsr A^{\RepOracle,\TestOracle}()$\\
+if $z = b$ then Return 1\\
+Return 0\\
 }
@@
 {
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
+\oracle{$\RepOracle(S_0,S_1)$}\\
+if $\mathrm{used}=\true$ then \\
+\nudge Ret $\bot$\\
+if $|S_0|\neq|S_1|$ then \\
+\nudge Ret $\bot$\\
+$\mathrm{used}=\true$\\
+$(M,\aux) \getsr \Rep(S_b)$\\
+Return $\aux$\\
 
 \medskip
-\oracle{$\HashOracle(x)$}\\
-Ret $\left(h_1(x),\ldots,h_k(x)\right)$\\
-} } \caption{False-positive security (soundness) for an
-$(n,k,m)$-filter~$B$ with private hash functions (top), black-box
-queriable hash functions (middle), and public hash functions
-(bottom). \jnote{Could also consider not giving $\calS$ to the
-adversary.} } \label{fig:fp-filter}
-\end{figure}
-
-%%%%
-% \if{0}
-% \begin{figure}
-% \centering
-% \fpage{.6}{
-% \hpagess{.6}{.35}
-% {
-% \experimentv{$\ExpFPSecHash{S,B}{A}$}\\
-% $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-% $M \gets \Rep^{\HashOracle}(S)$\\
-% $x \getsr A^{\QryOracle}(S)$\\
-% if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
-% \nudge Ret 1\\
-% Ret 0
-% }
-% %
-% {
-% \oracle{$\QryOracle(x)$}\\
-% Ret $\Qry^{\HashOracle}(M,x)$\\
-
-% \medskip
-% \oracle{$\HashOracle(i,x)$}\\
-% Ret $h_i(x)$\\
-% }
-% }
-% %%%%%%%
-% \fpage{.6}{
-% \hpagess{.6}{.35}
-% {
-% \experimentv{$\ExpFPPubHashBB{S,B}{A}$}\\
-% $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-% $M \gets \Rep^{\HashOracle}(S)$\\
-% $x \getsr A^{\QryOracle,\HashOracle}(S)$\\
-% if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
-% \nudge Ret 1\\
-% Ret 0
-% }
-% %
-% {
-% \oracle{$\QryOracle(x)$}\\
-% Ret $\Qry^{\HashOracle}(M,x)$\\
-
-% \medskip
-% \oracle{$\HashOracle(i,x)$}\\
-% Ret $h_i(x)$\\
-% }
-% }
-% %%%%%%%
-% \fpage{.6}{
-% \hpagess{.6}{.35}
-% {
-% \experimentv{$\ExpFPPubHash{S,B}{A}$}\\
-% $ \{h_1,h_2,\ldots,h_k\} \getsr \Hash$\\
-% $M \gets \Rep^{\HashOracle}(S)$\\
-% $x \getsr A^{\QryOracle}(S,\{h_1,h_2,\ldots,h_k\})$\\
-% if $x \not\in S \wedge \Qry^{\HashOracle}(M,x)=1$ then\\
-% \nudge Ret 1\\
-% Ret 0
-% }
-% %
-% {
-% \oracle{$\QryOracle(x)$}\\
-% Ret $\Qry^{\HashOracle}(M,x)$\\
-
-% \medskip
-% \oracle{$\HashOracle(i,x)$}\\
-% Ret $h_i(x)$\\
-% }
-% }
-% \caption{False-positive security (soundness) for an $(n,k,m)$-filter~$B$ with private hash functions (top), black-box queriable hash functions (middle), and public hash functions (bottom). }
-% \label{fig:fp-filter}
-% \end{figure}
-%\fi
-%%%%%
-
-\heading{Privacy of hash-based filters.} We now define privacy notions for $(n,k,m)$-filters.
-Informally, the adversary is given the representation~$M$ of a secret set~$\calS$, and its goal is to guess one of the elements of~$\calS$.
-Of course, if the distribution~$\distr{U}{n}$ has low min-entropy with respect to any particular element $x \in U$, then it will be relatively easy to guess~$x$.
-To capture this min-entropy, let $p_{\mathrm{max}} = \max_{x \in U} \Prob{\calS \getsr \distr{U}{n}:\, x \in \calS}$ and define $\mu = -\log_2 p_{\mathrm{max}}$ to be the (element-wise) min-entropy of distribution $\distr{U}{n}$.
-
-\tsnote{Explain need for $\MemOracle$, as a way to disambiguate true positives from false positives.}
-
-We note that~$\calS$ must be independent of the hash functions~$h_1,h_2,\ldots,h_k$ used to create the representation of~$\calS$.  \tsnote{I thought this would be needed, but now I'm not sure it is. }
-
-A weaker notion of privacy would not give~$M$ to the adversary.
-However, this would not capture attacks such as those mounted by Neidermayer et al.\cite{XXX}, and would not speak to settings in which (say) an honest-but-curious third party is given the representation~$M$ in order to carry out some task on behalf of the holder of~$\calS$.
-
-\begin{figure}
-\centering
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpPrivSecHash{B}{\distr{U}{n}, A}$}\\
-$\calS \getsr \distr{U}{n}$\\
-$h_1,\ldots,h_k \getsr \Hash$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
-$x \getsr A^{\MemOracle,\QryOracle}(M)$\\
-if $x\in \calS$ then Ret 1\\
-Ret 0
-}
-%
-{
-\oracle{$\MemOracle(x)$}\\
-Ret $[x \in \calS]$\\
-
-\medskip
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
-
-\medskip
-\oracle{$\HashOracle(x)$}\\
-Ret $\left(h_1(x),\ldots,h_k(x)\right)$\\
+\oracle{$\TestOracle(q)$}\\
+$a \gets \Qry(M,\aux,q)$\\
+Return~$a$\\
 }
 }
-%%%%%%%%%%
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpPrivPubHashBB{B}{\distr{U}{n}, A}$}\\
-$ \calS \getsr \distr{U}{n}$\\
-$h_1,\ldots,h_k \getsr \Hash$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
-$x \getsr A^{\MemOracle,\QryOracle,\HashOracle}(M)$\\
-if $x\in \calS$ then Ret 1\\
-Ret 0\\
-}
-%
-{
-\oracle{$\MemOracle(x)$}\\
-Ret $[x \in \calS]$\\
-
-\medskip
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
-
-\medskip
-\oracle{$\HashOracle(x)$}\\
-Ret $\left(h_1(x),\ldots,h_k(x)\right)$\\
-}
-}
-%%%%%%%
-\fpage{.6}{
-\hpagess{.6}{.35}
-{
-\experimentv{$\ExpPrivPubHash{B}{\distr{U}{n}, A}$}\\
-$ \calS \getsr \distr{U}{n}$\\
-$h_1,\ldots,h_k \getsr \Hash$\\
-$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
-$x \getsr A^{\MemOracle,\QryOracle}(M,\{h_1,h_2,\ldots,h_k\})$\\
-if $x\in \calS$ then Ret 1\\
-Ret 0\\
-}
-%
-{
-\oracle{$\MemOracle(x)$}\\
-Ret $[x \in \calS]$\\
-
-\medskip
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,\tau,x)$\\
-
-\medskip
-\oracle{$\HashOracle(x)$}\\
-Ret $\left(h_1(x),\ldots,h_k(x)\right)$\\
-}
-}
-\caption{Set-privacy for an $(n,k,m)$-filter~$B$ for private (top), black-box queriable (middle),  and public (bottom) hash functions. \textcolor{cyan}{Revisit when the FP notion settles out.}}
-\label{fig:fp-filter}
+\caption{Privacy notions. {\bf Left:} ``One-wayness'' style
+  definitions. The top is a weaker notion, because the representation
+  is hidden from the adversary. {\bf Right:} An
+  ``indistinguishability'' style notion. (Still playing...)} 
+\label{fig:privacy}
 \end{figure}
-
-\fi

### 2016-07-26 notions.tex
restructuring
cheers

@@
 \section{Security Notions}
+\label{sec:security-notions}
 \tsnote{intro text}
+As highlighted by Naor and Yogev, Equation~(\ref{eqn:correctness}) is a non-adaptive version of correctness;
+we are interested in defining an adaptive (i.e., adversarial) notion
+of correctness.   Figure~\ref{fig:correctness} describes a security experiment 
+that captures such a notion.
+
+In addition to correctness, we establish notions of privacy for set-representations.
+We explore two notions.
+The first has the flavor of a one-wayness game, in which the adversary is given the auxiliary information~$\aux$ and, either the representation~$M$ or the abillity to call an oracle that evaluates $\Qry(M,\aux,q)$ on queries~$q$ of its choosing.
+At the end of this game, the adversary must output some point in the set represented by~$M$.
+In the second privacy notion, the adversary presents two sets~$S_0$ and $S_1$ (of equal size), and is given $(M,\aux)$ where~$M$ represents $S_b$ for a uniform bit~$b$.
+In this game, the adversary must determine which set~$M$ represents.
 
 \subsection{Correctness Against Adaptive Adversaries}
-As highlighted by Naor and Yogev, Equation~(\ref{eqn:correctness}) is a non-adaptive version of correctness;
-we are interested in defining an adaptive (i.e., adversarial) notion
-of correctness.   Figure~\ref{fig:correctness} describes a security
-experiment that captures such a notion.
 

### 2016-07-26 notions.tex
cheers
comments on relationships between correctness and privacy notions

@@
 \end{figure}
+
+\heading{Relationships among notions.}
+\tsnote{Seems that correctness and privacy are orthogonal?  Not sure about relationship between different notions of privacy.}
+\tsnote{Not even clear how to reduce correctness to the stronger version of one-wayness.
+In the correctness experiment, you get~$(S,\aux)$ but not~$M$; whereas in the stronger version of one-wayness, the adversary expects~$(M,\aux)$ as input.}
+\tsnote{Reducing correctness to the weaker version is syntactically possible, but not clear how to connect the success events.
+In the one-wayness game, you win by outputing an element of~$S$; but how does this lead to finding an error-inducing query?
+Maybe the one-wayness attacker makes no queries, and just outputs a point~$z$.
+Then the correctness attacker does what?
+Ask some query~$q_z$ related to~$z$ (remember, queries are not syntactically restricted to set membership!) and see if the oracle returns the true value $q_z(S)$?
+This is pretty complicated...
+Note that any query~$q$ the one-wayness adversary asks can be checked locally against the true value~$q(S)$ by the correctness adversary.
+But still, it's not clear how to do a quality reduction.
+}
+\tsnote{Likewise the other way: the one-wayness adversary does not get~$S$, and yet needs to provide this to the correctness adversary.}

### 2016-07-26 notions.tex
comments on relationships between correctness and privacy notions
cheers

@@
   assume that the attacker does not ask~$q$ such that $q(S_0)=q(S_1)$
-  because these are pointless?  Otherwise, I don't see a need for restrictions.}
+  because these are pointless?
+Otherwise, I don't see a need for restrictions.} \tsnote{Maybe we restrict from queries~$q$ that would have the same value for all sets~$S \in \calS$?
+(Or all sets of the same size, or...?)}
 %\tsnote{How will the adversary know that a query satisfies
@@
   is hidden from the adversary. {\bf Right:} An
-  ``indistinguishability'' style notion. (Still playing...)} 
+  ``indistinguishability'' style notion. (Still playing...) \textcolor{red}{on the right, should $S_0,S_1$ be sampled from $\distr{\calS}{}$ instead?  This would be in line with the other notions}} 
 \label{fig:privacy}

### 2016-07-26 notions.tex
cheers
slight change to correctness experiment

@@
 \nudge $\mathrm{err}\gets\mathrm{err}+1$\\
-Return~$a$
+Return~$(a,\mathrm{err})$
 }
@@
 \heading{Relationships among notions.}
-\tsnote{Seems that correctness and privacy are orthogonal?  Not sure about relationship between different notions of privacy.}
-\tsnote{Not even clear how to reduce correctness to the stronger version of one-wayness.
-In the correctness experiment, you get~$(S,\aux)$ but not~$M$; whereas in the stronger version of one-wayness, the adversary expects~$(M,\aux)$ as input.}
-\tsnote{Reducing correctness to the weaker version is syntactically possible, but not clear how to connect the success events.
+If we allow for trivial schemes, e.g.
+$M=S$, then correctness and the stronger version of one-wayness privacy (Priv) are clearly orthogonal.\tsnote{In general, it isn't clear how to reduce correctness to the Priv notion.
+In the correctness experiment, you get~$(S,\aux)$ but not~$M$; whereas in the Priv-notion, the adversary expects~$(M,\aux)$ as input.}
+Curiously, $M=S$ does seem to be both correct and private (up to the element-wise min-entropy of~$S$) in the weaker version of one-wayness privacy (wPriv).
+\tsnote{Reducing correctness to the weaker version, wPriv, is syntactically possible, but not clear how to connect the success events.
 In the one-wayness game, you win by outputing an element of~$S$; but how does this lead to finding an error-inducing query?
@@
 }
+
 \tsnote{Likewise the other way: the one-wayness adversary does not get~$S$, and yet needs to provide this to the correctness adversary.}

### 2016-07-26 notions.tex
slight change to correctness experiment

@@
 Then the correctness attacker does what?
-Ask some query~$q_z$ related to~$z$ (remember, queries are not syntactically restricted to set membership!) and see if the oracle returns the true value $q_z(S)$?
+Ask some query~$q_z$ related to~$z$ ---remember, queries are not syntactically restricted to set membership!--- and see if the oracle returns the true value $q_z(S)$?
 This is pretty complicated...
-Note that any query~$q$ the one-wayness adversary asks can be checked locally against the true value~$q(S)$ by the correctness adversary.
-But still, it's not clear how to do a quality reduction.
+and it's not clear how to do a quality reduction.
 }

### 2016-07-26 notions.tex
comments about privacy

@@
   true of both sets.  So a scheme with $M=S$ will be trivially secure
-  against set membership queries.  } \tsnote{Do you mean to
+  against set membership queries. Do you mean to
   assume that the attacker does not ask~$q$ such that $q(S_0)=q(S_1)$
   because these are pointless?
-Otherwise, I don't see a need for restrictions.} \tsnote{Maybe we restrict from queries~$q$ that would have the same value for all sets~$S \in \calS$?
+Otherwise, I don't see a need for restrictions.
+Maybe we restrict from queries~$q$ that would have the same value for all sets~$S \in \calS$?
 (Or all sets of the same size, or...?)}
+
+\tsnote{Is this the right kind of indistinguishability anyway?
+It seems to me that we want to say that a representation~$M$ and the public info~$\aux$ tell you nothing (non-trivial) about the set being represented.
+To me, this game would be more like, you are handed $(M,\aux)$ and you need to output a query~$q$ such that $q(S_0) \neq q(S_1)$...
+I don't know, this is tricky.}
 %\tsnote{How will the adversary know that a query satisfies
@@
 $b \getsr \bits$\\
-$z \getsr A^{\RepOracle,\TestOracle}()$\\
+$z \getsr A^{\RepOracle,\TestOracle}$\\
 if $z = b$ then Return 1\\
@@
 $M=S$, then correctness and the stronger version of one-wayness privacy (Priv) are clearly orthogonal.\tsnote{In general, it isn't clear how to reduce correctness to the Priv notion.
-In the correctness experiment, you get~$(S,\aux)$ but not~$M$; whereas in the Priv-notion, the adversary expects~$(M,\aux)$ as input.}
+In the correctness experiment, you get~$(S,\aux)$ but not~$M$; whereas in the Priv-notion, the adversary expects~$(M,\aux)$ as input.
+Unless the coins of Rep are effectively leaked in~$\aux$, you can't reliably produce~$M$ given~$(S,\aux)$.}
 Curiously, $M=S$ does seem to be both correct and private (up to the element-wise min-entropy of~$S$) in the weaker version of one-wayness privacy (wPriv).

### 2016-07-26 notions.tex
comments about privacy

@@
   true of both sets.  So a scheme with $M=S$ will be trivially secure
-  against set membership queries. Do you mean to
-  assume that the attacker does not ask~$q$ such that $q(S_0)=q(S_1)$
-  because these are pointless?
-Otherwise, I don't see a need for restrictions.
-Maybe we restrict from queries~$q$ that would have the same value for all sets~$S \in \calS$?
-(Or all sets of the same size, or...?)}
+  against set membership queries.
+Maybe we restrict from queries~$q$ that are a priori known to have the same value for all sets~$S \in \calS$, or all~$S$ of a given size, etc., as these might be pointless?)}
 
@@
 It seems to me that we want to say that a representation~$M$ and the public info~$\aux$ tell you nothing (non-trivial) about the set being represented.
-To me, this game would be more like, you are handed $(M,\aux)$ and you need to output a query~$q$ such that $q(S_0) \neq q(S_1)$...
-I don't know, this is tricky.}
+One way to capture this would be indistinguishability with respect to the query set~$\calQ$: you are handed $(M,\aux)$ and you need to output a query~$q\in\calQ$ such that $q(S_0) \neq q(S_1)$.
+But this doesn't really capture that $(M,\aux)$ on their \emph{own} do not leak information about the set.
+(Classical BFs, by the way, essentially leak the number of elements in the set by looking at the Hamming weight of the array.)  I don't know, this is tricky...
+How do you handle the fact that, under our current syntax, $M$~may contain secrets, e.g.
+a PRP key?}
 %\tsnote{How will the adversary know that a query satisfies

### 2016-07-26 notions.tex
comments about privacy

@@
 But this doesn't really capture that $(M,\aux)$ on their \emph{own} do not leak information about the set.
-(Classical BFs, by the way, essentially leak the number of elements in the set by looking at the Hamming weight of the array.)  I don't know, this is tricky...
+(Classical BFs, by the way, essentially leak the number of elements in the set by looking at the number of 0-bits in the array.)  I don't know, this is tricky...
 How do you handle the fact that, under our current syntax, $M$~may contain secrets, e.g.

### 2016-07-26 notions.tex
comments about privacy

@@
 At the end of this game, the adversary must output some point in the set represented by~$M$.
-In the second privacy notion, the adversary presents two sets~$S_0$ and $S_1$ (of equal size), and is given $(M,\aux)$ where~$M$ represents $S_b$ for a uniform bit~$b$.
-In this game, the adversary must determine which set~$M$ represents.
+In the second privacy notion, the adversary presents two sets~$S_0$ and $S_1$ (of equal size) and a representation~$M$ is created for one of these two.
+Then the adversary is given $\aux$ and oracle access to $\Qry(M,\aux,q)$, and it must decide which set~$M$ represents.
 
@@
 \tsnote{Is this the right kind of indistinguishability anyway?
-It seems to me that we want to say that a representation~$M$ and the public info~$\aux$ tell you nothing (non-trivial) about the set being represented.
-One way to capture this would be indistinguishability with respect to the query set~$\calQ$: you are handed $(M,\aux)$ and you need to output a query~$q\in\calQ$ such that $q(S_0) \neq q(S_1)$.
-But this doesn't really capture that $(M,\aux)$ on their \emph{own} do not leak information about the set.
+This current notion says, in effect, that $S_0$ and $S_1$ are indistinguishable \emph{with respect to the allowed queries} (assuming that $\aux$ doesn't stupidly leak information.)  But why not try to formalize the intution that a representation~$M$ and the public info~$\aux$ tell you nothing (non-trivial) about the set being represented, period?
 (Classical BFs, by the way, essentially leak the number of elements in the set by looking at the number of 0-bits in the array.)   I don't know, this is tricky...
-How do you handle the fact that, under our current syntax, $M$~may contain secrets, e.g.
-a PRP key?}
+Also, if you give~$M$ to the adversary, how do you handle the fact that, under our current syntax, $M$~may contain secret keys, etc.?}
 %\tsnote{How will the adversary know that a query satisfies

### 2016-07-26 notions.tex
comments about privacy

@@
 This current notion says, in effect, that $S_0$ and $S_1$ are indistinguishable \emph{with respect to the allowed queries} (assuming that $\aux$ doesn't stupidly leak information.)  But why not try to formalize the intution that a representation~$M$ and the public info~$\aux$ tell you nothing (non-trivial) about the set being represented, period?
-(Classical BFs, by the way, essentially leak the number of elements in the set by looking at the number of 0-bits in the array.)   I don't know, this is tricky...
+(Classical BFs, by the way, essentially leak the number of elements in the set by looking at the number of 0-bits in the array.)   That's tricky to define...
 Also, if you give~$M$ to the adversary, how do you handle the fact that, under our current syntax, $M$~may contain secret keys, etc.?}

### 2016-07-26 notions.tex
messing with privacy notion
privacy

@@
 {
-\hpagess{.5}{.45}
+\hpagess{.5}{.475}
 {
-\experimentv{$\ExpPrivInd{\setprim}{A}$}\\
+\experimentv{$\ExpPrivInd{\setprim,\distr{\calS}{}}{A}$}\\
 $b \getsr \bits$\\
@@
 {
-\oracle{$\RepOracle(S_0,S_1)$}\\
-if $\mathrm{used}=\true$ then \\
-\nudge Ret $\bot$\\
-if $|S_0|\neq|S_1|$ then \\
-\nudge Ret $\bot$\\
+%\oracle{$\RepOracle(S_0,S_1)$}\\
+\oracle{$\RepOracle()$}\\
+if $\mathrm{used}=\true$ then Ret $\bot$\\
+%if $|S_0|\neq|S_1|$ then \\
+%\nudge Ret $\bot$\\
+$S_0,S_1 \getsr \distr{\calS}{}$\\
 $\mathrm{used}=\true$\\
 $(M,\aux) \getsr \Rep(S_b)$\\
-Return $\aux$\\
+Return $(S_0,S_1,\aux)$\\
 
@@
   is hidden from the adversary. {\bf Right:} An
-  ``indistinguishability'' style notion. (Still playing...) \textcolor{red}{on the right, should $S_0,S_1$ be sampled from $\distr{\calS}{}$ instead?  This would be in line with the other notions}} 
+  ``indistinguishability'' style notion. (Still playing...)} 
 \label{fig:privacy}
@@
 
-\heading{Relationships among notions.}
+\subsection{Relationships Among Notions}
 If we allow for trivial schemes, e.g.

### 2016-07-27 syntax.tex
updating syntax of data structures, and adding set-multiplicity data structures

@@
-\section{Secure Multiset Representation}
+\section{Secure Data Structures}
 \def\pub{{\sf pub}}
@@
 
-\heading{Static (Multi)set-representations.
-}  We being by defining a general primitive that produces a representation of a given multiset, and provides a mechanism to answer a specified collection of questions about that multiset.
+\heading{(Set-multiplicity) Data Structures.}  We being by defining a general primitive that produces a representation of a given multiset, and provides a mechanism to answer a specified collection of questions about that multiset.
 Informally, the representation should serve as a good approximation of the multiset, at least with respect to the allowed questions.
 \begin{definition} 
-Fix a universe~$\univ$ and an alphabet~$\Sigma$.  A \emph{static (multi)set-representation primitive} (or just set-representation) is a pair of algorithms $\setprim=(\Rep, \Qry)$
-parameterized by a collection $\mathcal{S}$ of multisets, each consisting of elements from~$U$ and a collection
-of supported queries $\mathcal{Q}=\{q \colon \mathcal{S} \to \mathbb{R}\}$, where:
+Fix a non-empty set~$\univ$. A \emph{static data structure} (over universe~$\univ$)
+is a tuple $\setprim=(\Sigma,\Gamma,\calS,\calQ,\Rep, \Qry)$ where:
 \begin{itemize}
-\item $\Rep$ is a randomized algorithm taking as input $S \in \mathcal{S}$,
-and outputting a pair of strings $(M,\aux)$, the \emph{representation} $M \in \Sigma^*$ (of~$S$) 
-and the \emph{auxilliary information} $\aux \in \bits^*$ (of~$M$).
-\item $\Qry$ is a deterministic algorithm that takes as input $M, \aux$,
-and a query $q\in \mathcal{Q}$, and returns value~$a$.
+\item $\Sigma$ is the \emph{representation alphabet}
+\item $\Gamma$ is the set of possible \emph{query answers}
+\item $\calS$ is a set  of multisets over universe~$\univ$
+\item $\mathcal{Q}=\{q \colon \mathcal{S} \to \Gamma\}$ is a set of supported \emph{queries}
+\item $\Rep \colon \mathcal{S} \to \Sigma^* \times \bits^*$ is a randomized \emph{representation algorithm}, taking as input $S \in \mathcal{S}$, and outputting a \emph{representation} $M \in \Sigma^*$ and some \emph{auxilliary information} $\aux \in \bits^*$
+\item $\Qry\colon \Sigma^* \times \bits^* \times \calQ \to \Gamma$ is a deterministic \emph{query-evaluation} algorithm, taking as input $M, \aux, q$, and returns \emph{answer} $a \in \Gamma$.
 \end{itemize}
-A set-representation is \emph{$\epsilon$-correct} if, for all $S \in \mathcal{S}$ and
-all $q \in \mathcal{Q}$, it holds that
-\begin{eqnarray}
-\Pr[(M,\aux) \getsr \Rep(S) : \Qry(M, \aux, q) \neq q(S)] \leq \epsilon, \label{eqn:correctness}
-\end{eqnarray}
-%where $q(S)$ denotes the correct answer to the query $q$ on the set~$S$.
+Let $\mathrm{Err}(S,q,M,\aux)$ be a predicate that is true iff $\Qry(M, \aux, q) \neq q(S)$.  Then a data structure
+\emph{$\epsilon$-correct}, or has (worst-case) error probability $\epsilon$, if
+\[
+\max_{S,q}\Pr[(M,\aux) \getsr \Rep(S) : \mathrm{Err}(S,q,M,\aux)=1 ] \leq \epsilon, \label{eqn:correctness}
+\]
+where the maximum is over $S \in \mathcal{S}$ and $q \in \mathcal{Q}$.  Relatedly, it has \emph{error rate} $\tilde{\epsilon}$ if
+\[
+\max_{S}\Pr[(M,\aux) \getsr \Rep(S);\, q \getsr \calQ : \mathrm{Err}(S,q,M,\aux)=1] \leq \tilde{\epsilon} \label{eqn:error_rate}
+\]
 \end{definition}
@@
 
-All of the constructions of set-representations that we will consider have the property that~$|M|$ does not depend on the coins of~$\Rep$.
+All of the data structures that we will consider have the property that~$|M|$ does not depend on the coins of~$\Rep$.
 Thus we assume that~$|M|$ depends only on~$|S|$.
 In general this need not be true, but the assumption does not restrict our syntax from capturing natural constructions (e.g., those seen in practice), and it makes it easier to state our security notions.
+
+Our particular focus will be on data structures that support multiplicity queries, of which set-membership queries are a special case.  
+\begin{definition} A \emph{set-multipicity data structure} is a data structure with $D=\mathbb{N}$ and where $\calQ=\{q_x \,|\, x \in \univ\}$ where $q_x(S)$ is defined to be the multiplicity of~$x$ in the multiset~$S$.
+\end{definition}
 %
@@
 \heading{Examples.}
-It is not hard to see Bloom filters are one possible instantiation a set-representation primitive.
-Fix an $n \geq 0$, let $\mathcal{S}=[\univ]^n$, and fix $\Sigma=\bits$.  
-Next, let $\calQ$ be a set of predicates $q_x$, one for each $x \in \univ$,
+It is not hard to see Bloom filters are one possible instantiation a set-multiplicity data structure.
+Fix an $n \geq 0$, let $\mathcal{S}=[\univ]^n$, and let $\Sigma=\Gamma\bits$.  
+Let $\calQ$ be a set of predicates $q_x$, one for each $x \in \univ$,
 such that $q_x(S)=1$ iff $x \in S$.

### 2016-07-27 syntax.tex
updating syntax of data structures, and adding set-multiplicity data structures

@@
 
-\heading{(Set-multiplicity) Data Structures.}  We being by defining a general primitive that produces a representation of a given multiset, and provides a mechanism to answer a specified collection of questions about that multiset.
+\heading{Data Structures.}  We being by defining a general primitive that produces a representation of a given multiset, and provides a mechanism to answer a specified collection of questions about that multiset.
 Informally, the representation should serve as a good approximation of the multiset, at least with respect to the allowed questions.
-\begin{definition} 
+\begin{definition} \rm
 Fix a non-empty set~$\univ$. A \emph{static data structure} (over universe~$\univ$)
@@
 Let $\mathrm{Err}(S,q,M,\aux)$ be a predicate that is true iff $\Qry(M, \aux, q) \neq q(S)$.  Then a data structure
-\emph{$\epsilon$-correct}, or has (worst-case) error probability $\epsilon$, if
-\[
-\max_{S,q}\Pr[(M,\aux) \getsr \Rep(S) : \mathrm{Err}(S,q,M,\aux)=1 ] \leq \epsilon, \label{eqn:correctness}
-\]
-where the maximum is over $S \in \mathcal{S}$ and $q \in \mathcal{Q}$.  Relatedly, it has \emph{error rate} $\tilde{\epsilon}$ if
-\[
-\max_{S}\Pr[(M,\aux) \getsr \Rep(S);\, q \getsr \calQ : \mathrm{Err}(S,q,M,\aux)=1] \leq \tilde{\epsilon} \label{eqn:error_rate}
-\]
+has \emph{error-probability} $\epsilon$, if
+$\max_{S,q}\Pr[(M,\aux) \getsr \Rep(S) : \mathrm{Err}(S,q,M,\aux)=1 ] \leq \epsilon$,
+where the maximum is over $S \in \mathcal{S}$ and $q \in \mathcal{Q}$.  Relatedly, it has \emph{error-rate} $\tilde{\epsilon}$ if
+$\max_{S}\Pr[(M,\aux) \getsr \Rep(S);\, q \getsr \calQ : \mathrm{Err}(S,q,M,\aux)=1] \leq \tilde{\epsilon}$.
 \end{definition}
@@
 by giving $\Rep, \Qry$ access to a random oracle. In that case,
-the probability in Equation~(\ref{eqn:correctness}) is also taken over choice of the random oracle.
+the probabilities defining the error-probability and error-rate are also taken over choice of the random oracle.
 
@@
 
+We will sometimes say that a data structure is $(1-\epsilon)$-correct, meaning it has error-probability~$\epsilon$.
+Note that $1-\epsilon$ is a worst-case lower bound on the correctness of the data structure.
+
+\heading{Set-multiplicity Data Structures. }
 Our particular focus will be on data structures that support multiplicity queries, of which set-membership queries are a special case.  
@@
 The algorithm~$\Qry$ is defined so that, on input $(M,\aux,q_x)$, it returns 1 iff $M[h_1(x)]=1 \wedge M[h_2(x)]=1 \wedge \cdots \wedge M[h_k(x)]=1$ holds.
-  %\tsnote{If $\mathcal{Q}=U$ and we use the
-%  semantics you suggest, then isn't Equation~\ref{eqn:correctness}
-%  both correctness and soundness?  If so, I don't see how this
-%  captures the classical BF, which requires $\epsilon=0$ for one kind
-%  of error, but allows $\epsilon>0$ for the other. } 
-%\jnote{The definition does not distinguish
-%  between elements in the set (for which $q(S)=1$) or outside the set (for which
-%  $q(S)=0$). But a Bloom filter does satisfy Equation~\ref{eqn:correctness} in either case.}
-%  \jnote{In that sense, I am using ``soundness'' and ``correctness'' interchangeably here.}
-%  \jnote{I'm not tied to allowing false negatives when we specialize the definition to the case
-%  of set-membership queries. But in the abstract definition it seems unclear why one would choose
-%  some queries on which error is ok and other queries where error is not allowed. Though if one
-%  wanted to be general, one could simply have two (disjoint) sets of queries $\mathcal{Q}_1, \mathcal{Q}_2$
-%  where error is allowed on the former but not on the latter.}
-We note that while our correctness condition does not distinguish among types of errors, it also does not preclude instantiations (like the classical Bloom filter) that admit only one type of error, e.g.
+
+We note that, while our measure of error~$\epsilon$ does not distinguish among ``types'' of errors, it also does not preclude instantiations (like the classical Bloom filter) that admit only one type of error, e.g.
 false-positives.

### 2016-07-27 syntax.tex
updating syntax of data structures, and adding set-multiplicity data structures

@@
-\section{Secure Data Structures}
+\section{(Set-multiplicity) Data Structures}
 \def\pub{{\sf pub}}
@@
 
+\todo{Add discussion of just how broad the syntax is, in general.}
+
 \heading{Set-multiplicity Data Structures. }
@@
 
-\heading{Examples.}
+\heading{Bloom Filters and Related Data Structures. }
 It is not hard to see Bloom filters are one possible instantiation a set-multiplicity data structure.
-Fix an $n \geq 0$, let $\mathcal{S}=[\univ]^n$, and let $\Sigma=\Gamma\bits$.  
-Let $\calQ$ be a set of predicates $q_x$, one for each $x \in \univ$,
-such that $q_x(S)=1$ iff $x \in S$.
-Define algorithm~$\Rep$, with functions $k=k(|S|), m=m(|S|)$ and a description of a hash function family~$\mathcal{H}=\{h \colon \univ \to \{1,2,\ldots,m\}\}$ hardwired into it, to sample hash functions $h_1, \ldots, h_k$ from~$\mathcal{H}$ and then computes an $m$-bit array in the standard way.
+Fix an $n \geq 0$, let $\mathcal{S}=[\univ]^n$, and let $\Sigma=\Gamma=\bits$.  
+Define the queries so that $q_x(S)=1$ if $x \in S$, and 0 otherwise.
+Define algorithm~$\Rep$, with functions $k=k(|S|), m=m(|S|)$ and a description of a hash function family~$\mathcal{H}=\{h \colon \univ \to \{1,2,\ldots,m\}\}$ hardwired into it, to sample hash functions $h_1, \ldots, h_k$ from~$\mathcal{H}$ and then compute an $m$-bit array in the standard way.
 It sets $\aux = (h_1, \ldots, h_k)$ and $M$ to be the bit array, and returns these.
-The algorithm~$\Qry$ is defined so that, on input $(M,\aux,q_x)$, it returns 1 iff $M[h_1(x)]=1 \wedge M[h_2(x)]=1 \wedge \cdots \wedge M[h_k(x)]=1$ holds.
-
-We note that, while our measure of error~$\epsilon$ does not distinguish among ``types'' of errors, it also does not preclude instantiations (like the classical Bloom filter) that admit only one type of error, e.g.
+The algorithm~$\Qry$ is defined so that, on input $(M,\aux,q_x)$, it returns the minimum of the values (either 0 or 1) held at $M[h_1(x)],\ldots,M[h_k(x)]$.
+We note that, while our error-probability and error-rate do not distinguish among ``types'' of errors, they also do not preclude instantiations (like the classical Bloom filter) that admit only one type of error, e.g.
 false-positives.
 
+As a simple extension, consider $\Sigma=\mathbb{N}$ and a scheme that stores counters at each position in an array.
+In particular, for each~$x \in S$ the $\Rep$~algorithm increments the counters stored at positions $h_1(x), h_2(x), \ldots, h_k(x)$, returns the final array of counters as~$M$.
+The $\Qry$-algorithm remains the same.
+Such a construction gives a static version of a counting Bloom filter~\cite{xxx}.
+We will capture dynamic versions, as well as count-min sketches, scalable Bloom filters, etc., in a later section.
+
 A Bloom filter with secret hash functions is captured by appending to~$M$ appropriate encodings of $h_1,h_2,\ldots,h_k$, and setting $\aux=\emptystring$.
-Related constructions that use a secret key~$K$, but not for hashing are captured in analogous ways.
+Related constructions \tsnote{Name them?} that use a secret key~$K$, but not for hashing, are captured by appending~$K$ to~$M$ and setting $\aux=((h_1, \ldots, h_k)$.
 
@@
 Similarly the cuckoo-hashing construction from NY, which (loosely speaking) stores a hash $g(x)$ at positions determined by $h_1(x),h_2(x),\ldots,h_k(x)$.
-\tsnote{Check this, I forget the exact details now.}
-
-Expanding beyond queries that are predicates, consider $\Sigma=\bits^L$ and a scheme that stores $L$-bit counters at each position in an array.
-In particular, for each~$x \in S$ the $\Rep$~algorithm increments the counters stored at $h_1(x),h_2(x),\ldots,h_k(x)$, returns the final array of counters as~$M$.
-This representation naturally supports a set of queries $\calQ$ where $q_x$ has the semantics ``what is the multiplicity of~$x$ in~$S$.''   Such a construction gives a static version of a counting Bloom filter~\cite{xxx}.
-(We will capture dynamic versions, as well as count-min sketches, scalable Bloom filters, etc., in a later section.)
+\tsnote{Check the correctness of this claim.}

### 2016-07-27 syntax.tex
updating syntax of data structures, and adding set-multiplicity data structures
cheers

@@
 
-\heading{Bloom Filters and Related Data Structures. }
+%\heading{Bloom Filters and Related Data Structures. }
 It is not hard to see Bloom filters are one possible instantiation a set-multiplicity data structure.
@@
 Such a construction gives a static version of a counting Bloom filter~\cite{xxx}.
-We will capture dynamic versions, as well as count-min sketches, scalable Bloom filters, etc., in a later section.
+We will capture dynamic versions, as well as count-min sketches~\cite{xxx}, scalable Bloom filters~\cite{xxx}, etc., in a later section.
 

### 2016-07-27 syntax.tex
cheers

@@
 Let $\mathrm{Err}(S,q,M,\aux)$ be a predicate that is true iff $\Qry(M, \aux, q) \neq q(S)$.  Then a data structure
-has \emph{error-probability} $\epsilon$, if
-$\max_{S,q}\Pr[(M,\aux) \getsr \Rep(S) : \mathrm{Err}(S,q,M,\aux)=1 ] \leq \epsilon$,
+has \emph{error-probability} $\epsilon$ if
+\[
+\max_{S,q}\Pr[(M,\aux) \getsr \Rep(S) : \mathrm{Err}(S,q,M,\aux)=1 ] \leq \epsilon
+\]
 where the maximum is over $S \in \mathcal{S}$ and $q \in \mathcal{Q}$.  Relatedly, it has \emph{error-rate} $\tilde{\epsilon}$ if
-$\max_{S}\Pr[(M,\aux) \getsr \Rep(S);\, q \getsr \calQ : \mathrm{Err}(S,q,M,\aux)=1] \leq \tilde{\epsilon}$.
+\[
+\max_{S}\Pr[(M,\aux) \getsr \Rep(S);\, q \getsr \calQ : \mathrm{Err}(S,q,M,\aux)=1] \leq \tilde{\epsilon}.
+\]
 \end{definition}

### 2016-07-27 notions.tex
privacy
cheers

@@
 \tsnote{intro text}
-As highlighted by Naor and Yogev, Equation~(\ref{eqn:correctness}) is a non-adaptive version of correctness;
-we are interested in defining an adaptive (i.e., adversarial) notion
-of correctness.   Figure~\ref{fig:correctness} describes a security experiment 
+Following NY, we are interested in defining an adaptive (i.e.,
+adversarial) notion of correctness.   Figure~\ref{fig:correctness} describes a security experiment 
 that captures such a notion.
@@
 distribution~$\distr{\calS}{}$ over the collection of multisets
-$\mathcal{S}$ associated to~$\Pi=(\Rep,\Qry)$, and then
+$\mathcal{S}$ associated to~$\Pi$, and then
 $\Rep(S)$ is run to generate $(M,\aux)$.
@@
 \heading{Observations on trivial attacks. } 
-Let~$\Pi$ be a scheme that is $\epsilon$-correct, and consider an attack that 
+Let~$\Pi$ be a scheme that is $(1-\epsilon)$-correct, and consider an attack that 
 asks random queries $q_1,q_2,\ldots,q_T$, i.e., uniform samples from~$\calQ$.
@@
 %Actually, it seems worthwhile to formalize this. 
-Let $X_i$ be a random variable indicating the event $\Qry(M,\aux,q_i)\neq q_i(S)$.  
-The $\epsilon$-correctness of~$\Pi$ guarantees that the probability that $X_i=1$ is at most~$\epsilon$, 
-and it is tempting to model the~$X_i$ as i.i.d. Bernoulli trials with success probability~$\epsilon$.
+Let $\mathrm{Err}_i$ be a random variable indicating the event $\Qry(M,\aux,q_i)\neq q_i(S)$.  
+The $(1-\epsilon)$-correctness of~$\Pi$ guarantees that the probability that $\mathrm{Err}_i=1$ is at most~$\epsilon$, 
+and it is tempting to model the~$\mathrm{Err}_i$ as i.i.d. Bernoulli trials with success probability~$\epsilon$.
 However, a moment's reflection shows that this is not the case.
@@
 Moreover, once the coins of~$\Rep$ are fixed, there is exactly \emph{one} query that will cause an error.
-Thus for random queries from~$Q$, for all~$i\in[T]$ we have $\Prob{X_i=1}=1/|\univ| \ll 1/n = \epsilon$.
+Thus for random queries from~$Q$, for all~$i\in[T]$ we have $\Prob{\mathrm{Err}_i=1}=1/|\univ| \ll 1/n = \epsilon$.
 
-This example is contrived, but the point is that $\epsilon$-correctness is measured over the coins of~$\Rep$, for a fixed~$S$ and query~$q$; once the coins of~$\Rep$ are fixed, it is not straightforward how to connect~$\epsilon$ to events that depend on other sources of randomness.
-\tsnote{Not sure if there's more to say in this section, or if what's here is already too much.}
+This example is contrived, but it highlights the important difference
+between error-probability and error-rate.  In particular, the
+error-probability~$\epsilon$ is measured only over the coins
+of~$\Rep$, for a fixed~$S$ and query~$q$.
+Once the coins of~$\Rep$ are fixed, it is not straightforward how to
+connect~$\epsilon$ to events that depend on other sources of
+randomness. \tsnote{Not sure if there's more to say in this section, or if what's here is already too much.}
 
@@
 succeeds if it can output an element in~$S$.
+\tsnote{Neither of these seems to capture the Neidermeier et al.
+attack.
+Giving the adversary~$M$ is closest, but our syntax would put the hash function secret keys into~$M$, which the Neidermeier attack doesn't get.}
 
@@
 
-\begin{figure}[htp]
+\begin{figure}[htbp]
 \centering
-\hfpages{.45}{
+\hfpages{.495}{
 \hpagess{.5}{.45}
@@
 if $z \in S$ then Return 1\\
-Return 0
+Return 0\\
 
@@
 {
-\hpagess{.5}{.475}
+\hpagess{.485}{.5}
 {
@@
 $b \getsr \bits$\\
-$z \getsr A^{\RepOracle,\TestOracle}$\\
-if $z = b$ then Return 1\\
+$S_0,S_1 \getsr \distr{\calS}{}$\\
+$(M,\aux) \getsr \Rep(S_b)$\\
+$b' \getsr A^{\TestOracle}(S_0,S_1,\aux)$\\
+if $b' = b$ then Return 1\\
 Return 0\\
@@
 {
-%\oracle{$\RepOracle(S_0,S_1)$}\\
-\oracle{$\RepOracle()$}\\
-if $\mathrm{used}=\true$ then Ret $\bot$\\
+\oracle{$\TestOracle(q)$}\\
+$a \gets \Qry(M,\aux,q)$\\
+Return~$a$\\
+
+\medskip
+\oracle{$\RepOracle(S_0,S_1)$}\\
+if $\mathrm{used}=\true$ then Return $\bot$\\
 %if $|S_0|\neq|S_1|$ then \\
@@
 
-\medskip
-\oracle{$\TestOracle(q)$}\\
-$a \gets \Qry(M,\aux,q)$\\
-Return~$a$\\
 }
@@
   is hidden from the adversary. {\bf Right:} An
-  ``indistinguishability'' style notion. (Still playing...)} 
+  ``indistinguishability'' style notion. (Still playing... ignore unused oracles)} 
 \label{fig:privacy}

### 2016-07-27 syntax.tex
cheers

--- 2016-07-27 syntax.tex
@@
 Informally, the representation should serve as a good approximation of the multiset, at least with respect to the allowed questions.
-\begin{definition} \rm
+\begin{definition}[Data Structure] \rm
 Fix a non-empty set~$\univ$. A \emph{static data structure} (over universe~$\univ$)
@@
 \end{itemize}
+\hfill\dqed
+\end{definition}
+
+All of the data structures that we will consider have the property that~$|M|$ does not depend on the coins of~$\Rep$.
+Thus we assume that~$|M|$ depends only on~$|S|$.
+In general this need not be true, but the assumption does not restrict our syntax from capturing natural constructions (e.g., those seen in practice), and it makes it easier to state our security notions.
+
+\begin{definition}[Error probability and rate] \rm
+Fix a data structure $\setprim=(\Sigma,\Gamma,\calS,\calQ,\Rep, \Qry)$.
 Let $\mathrm{Err}(S,q,M,\aux)$ be a predicate that is true iff $\Qry(M, \aux, q) \neq q(S)$.  Then a data structure
-has \emph{error-probability} $\epsilon$, if
-$\max_{S,q}\Pr[(M,\aux) \getsr \Rep(S) : \mathrm{Err}(S,q,M,\aux)=1 ] \leq \epsilon$,
-where the maximum is over $S \in \mathcal{S}$ and $q \in \mathcal{Q}$.  Relatedly, it has \emph{error-rate} $\tilde{\epsilon}$ if
+has \emph{error-probability} $\epsilon$ if
+$\max_{S,q}\Pr[(M,\aux) \getsr \Rep(S) : \mathrm{Err}(S,q,M,\aux)=1 ] \leq \epsilon$
+where the maximum is over $S \in \mathcal{S}$ and $q \in \mathcal{Q}$.
+
+Relatedly, it has \emph{error-rate} $\tilde{\epsilon}$ if
 $\max_{S}\Pr[(M,\aux) \getsr \Rep(S);\, q \getsr \calQ : \mathrm{Err}(S,q,M,\aux)=1] \leq \tilde{\epsilon}$.
+\hfill\dqed
 \end{definition}
@@
 the probabilities defining the error-probability and error-rate are also taken over choice of the random oracle.
-
-All of the data structures that we will consider have the property that~$|M|$ does not depend on the coins of~$\Rep$.
-Thus we assume that~$|M|$ depends only on~$|S|$.
-In general this need not be true, but the assumption does not restrict our syntax from capturing natural constructions (e.g., those seen in practice), and it makes it easier to state our security notions.
 
@@
 \begin{definition} A \emph{set-multipicity data structure} is a data structure with $D=\mathbb{N}$ and where $\calQ=\{q_x \,|\, x \in \univ\}$ where $q_x(S)$ is defined to be the multiplicity of~$x$ in the multiset~$S$.
+\hfill\dqed
 \end{definition}

### 2016-07-27 notions.tex
cheers

@@
 Following NY, we are interested in defining an adaptive (i.e.,
-adversarial) notion of correctness.   Figure~\ref{fig:correctness} describes a security experiment 
-that captures such a notion.
-
-In addition to correctness, we establish notions of privacy for set-representations.
-We explore two notions.
-The first has the flavor of a one-wayness game, in which the adversary is given the auxiliary information~$\aux$ and, either the representation~$M$ or the abillity to call an oracle that evaluates $\Qry(M,\aux,q)$ on queries~$q$ of its choosing.
+adversarial) notion of correctness.   
+In addition to correctness, we establish three notions of privacy for
+set-representations.
+The first two have the flavor of a one-wayness game, in which the adversary is given the auxiliary information~$\aux$ and, either the representation~$M$ or the abillity to call an oracle that evaluates $\Qry(M,\aux,q)$ on queries~$q$ of its choosing.
 At the end of this game, the adversary must output some point in the set represented by~$M$.

### 2016-07-27 notions.tex
cheers

@@
 set-representation~$\Pi$ is $(t,q,r,\epsilon')$-correct if $\AdvCorrect{\Pi,\distr{\calS}{},r}{t,q} \leq \epsilon'$.
-
-\def\bin{{\sf Bin}}
-\heading{Observations on trivial attacks. } 
-Let~$\Pi$ be a scheme that is $(1-\epsilon)$-correct, and consider an attack that 
-asks random queries $q_1,q_2,\ldots,q_T$, i.e., uniform samples from~$\calQ$.
-%The expected number of random queries needed to
-%find a error is $1/\epsilon$ tries; thus, an attacker making $O(t/\epsilon)$ queries succeeds with constant probability (almost always).
-%Actually, it seems worthwhile to formalize this. 
-Let $\mathrm{Err}_i$ be a random variable indicating the event $\Qry(M,\aux,q_i)\neq q_i(S)$.  
-The $(1-\epsilon)$-correctness of~$\Pi$ guarantees that the probability that $\mathrm{Err}_i=1$ is at most~$\epsilon$, 
-and it is tempting to model the~$\mathrm{Err}_i$ as i.i.d. Bernoulli trials with success probability~$\epsilon$.
-However, a moment's reflection shows that this is not the case.
-Concretely, consider the following scheme.
-Fix $|S|=n$ for all $S \in \calS$, where $n \ll |\univ|$.
-For the queries, let $\calQ = \{q_x\colon \calS \to \bits \,|\, \forall x \in \univ\}$ where $\forall S \in \calS$ the predicate $q_x(S)=1 \Leftrightarrow x \in S$.
-Let $\Rep(S)$ pick a random element~$s \in S$, and return $M = S \setminus \{s\}$ and $\aux = \emptystring$.
-To respond to queries, let~$\Qry(M,\aux,q_x)=1$ iff $x \in M$.
-It is easy to see that this scheme is $1/n$-correct; for any fixed~$S$, there are exactly~$n$ queries~$q_x$ that have probability~$1/n$  (over the coins of~$\Rep$) of causing a correctness error, and the remaining $|\univ|-n$ queries have probability zero of causing an error.
-Moreover, once the coins of~$\Rep$ are fixed, there is exactly \emph{one} query that will cause an error.
-Thus for random queries from~$Q$, for all~$i\in[T]$ we have $\Prob{\mathrm{Err}_i=1}=1/|\univ| \ll 1/n = \epsilon$.
-
-This example is contrived, but it highlights the important difference
-between error-probability and error-rate.  In particular, the
-error-probability~$\epsilon$ is measured only over the coins
-of~$\Rep$, for a fixed~$S$ and query~$q$.
-Once the coins of~$\Rep$ are fixed, it is not straightforward how to
-connect~$\epsilon$ to events that depend on other sources of
-randomness. \tsnote{Not sure if there's more to say in this section, or if what's here is already too much.}
 

### 2016-07-27 syntax.tex
cheers

@@
 
+\def\bin{{\sf Bin}}
+\heading{Trivial attacks, and error-probability vs.\ error-rate. } 
+Let~$\Pi$ be a scheme that is $(1-\epsilon)$-correct, and consider an attack that 
+asks random queries $q_1,q_2,\ldots,q_T$, i.e., uniform samples from~$\calQ$.
+%The expected number of random queries needed to
+%find a error is $1/\epsilon$ tries; thus, an attacker making $O(t/\epsilon)$ queries succeeds with constant probability (almost always).
+%Actually, it seems worthwhile to formalize this. 
+Let $\mathrm{Err}_i$ be a random variable indicating the event $\Qry(M,\aux,q_i)\neq q_i(S)$.  
+The $(1-\epsilon)$-correctness of~$\Pi$ guarantees that the probability that $\mathrm{Err}_i=1$ is at most~$\epsilon$, 
+and it is tempting to model the~$\mathrm{Err}_i$ as i.i.d. Bernoulli trials with success probability~$\epsilon$.
+However, a moment's reflection shows that this is not the case.
+Concretely, consider the following scheme.
+Fix $|S|=n$ for all $S \in \calS$, where $n \ll |\univ|$.
+For the queries, let $\calQ = \{q_x\colon \calS \to \bits \,|\, \forall x \in \univ\}$ where $\forall S \in \calS$ the predicate $q_x(S)=1 \Leftrightarrow x \in S$.
+Let $\Rep(S)$ pick a random element~$s \in S$, and return $M = S \setminus \{s\}$ and $\aux = \emptystring$.
+To respond to queries, let~$\Qry(M,\aux,q_x)=1$ iff $x \in M$.
+It is easy to see that this scheme is $1/n$-correct; for any fixed~$S$, there are exactly~$n$ queries~$q_x$ that have probability~$1/n$  (over the coins of~$\Rep$) of causing a correctness error, and the remaining $|\univ|-n$ queries have probability zero of causing an error.
+Moreover, once the coins of~$\Rep$ are fixed, there is exactly \emph{one} query that will cause an error.
+Thus for random queries from~$Q$, for all~$i\in[T]$ we have $\Prob{\mathrm{Err}_i=1}=1/|\univ| \ll 1/n = \epsilon$.
+
+This example is contrived, but it highlights the important difference
+between error-probability and error-rate.  In particular, the
+error-probability~$\epsilon$ is measured only over the coins
+of~$\Rep$, for a fixed~$S$ and query~$q$.
+Once the coins of~$\Rep$ are fixed, it is not straightforward how to
+connect~$\epsilon$ to events that depend on other sources of
+randomness. \tsnote{Not sure if there's more to say in this section, or if what's here is already too much.}
 \heading{Set-multiplicity Data Structures. }

### 2016-07-28 Theorem1_FP.tex
more clean up of Animesh's Theorem 1
Theorem 1 proof in old syntax

@@
 
-\fixme{Note: the following theorem is incorrect for $r>1$.  Or, at least, the proof does not cover $t>1$.}\acnote{Modified.}
+\fixme{Note: the following theorem is incorrect for $r>1$.  Or, at least, the proof does not cover $r>1$.}\acnote{Modified.}
 \begin{theorem}\label{thm1}
 Fix $k,m,n>0$, and let $B_\mathrm{lin}=(\Hash,\Rep,\Qry)$ be the hash-based filter just described. 
-Let~$A$ be an adversary, compatible with $\ExpFPSecHash{B_\mathrm{lin},r}{\cdot}$, that asks at most~$q$ queries to its $\QryOracle$ oracle.  Then 
+Let~$A$ be an adversary, compatible with $\ExpFPSecHash{B_\mathrm{lin},r}{\cdot}$, that asks at most~$q$ queries in time $t$ to its $\QryOracle$ oracle.  Then 
 \[
@@
 for PRF-adversaries~$B_1$ and $B_2$ given explicitly in the proof of
-this theorem.  \tsnote{Statement about resources of these reductions.}
+this theorem. Here, $B_1$ and $B_2$, each ask $q$ oracle queries in time O(t). \tsnote{Statement about resources of these reductions.}
 \end{theorem}
@@
 $(q (1-e^{-kn/m})^k + O(q/n) )^r$; loosely, the bound one expects for
-trying to find a single FP in each of~$t$ independent``rounds'', each round
+trying to find a single FP in each of~$r$ independent``rounds'', each round
 consisting of~$q$ attempts.
@@
 So,
+
 \begin{equation}
@@
 \end{equation}
+
 $\game{1}(A)$ and $\game{2}(A)$ attack 2 different filters with hash functions 
@@
 
+In $\game{3}(A)$, $r$ random integers are chosen and the $\QryOracle$ oracle sets a $\bad$ flag if query response for any of the $r$ queries is false or any of the $q-r$ queries return true.
+Also, the hash functions are linear combinations of two random points in $[m]$, similar to $\game{2}(A)$.
+So, both have equal probability of returning 1.
+
+\begin{equation}
+\Prob{\game{2}(A)=1} = \Prob{\game{3}(A)=1}\label{eq:3}
+\end{equation}
+
+The probability of winning  $\game{3}(A)$ is same as $\game{4}(A)$, except $\game{4}(A)$ outputs 0 if $\bad$ flag is set.
+In short, $\game{3}(A)$ and $\game{4}(A)$ are identical untill $\bad =true$.
+On the  other hand, $\game{5}(A)$ simulates the non-adaptive counterpart of $\game{4}(A)$.
+ \tsnote{I have rewritten game $\game{3}(A)$ and added
+  $\game{4}(A)$.  It should be that
+  $\Prob{\game{2}(A)}=\Prob{\game{3}(A)=1}$. Moreover
+  $\Prob{\game{4}(A)=1} = \Prob{\game{3}(A)=1 \wedge \neg\bad} =
+  \Prob{\game{3}(A)=1}\Prob{\game{3}{A}:\,\neg\bad} =
+  \Prob{\game{3}(A)=1}\frac{1}{\dbinom{q}{r}}$. Finally the event
+  $\game{4}(A)=1$ happens iff $\bad \neq \true$.  That means there is
+  a non-adaptive adversary that runs~$A$, simulates $\QryOracle$ by
+  simply returning 1 iff $c \in \mathcal{I}$, and uses the queries
+  with indices in $\mathcal{I}$ as its non-adaptive FPs.  To be
+  totally clear, you might want to add a $\game{5}(A)$ that has this
+  $\QryOracle$ behavior, and then give the non-adaptive FP-adversary~$A'$ that
+simulates~$\game{5}(A)$, and so on. }\fixme{Clean up everything after this.}
+
+\begin{align}
+\nonumber \Prob{\game{4}(A)=1} &= \Prob{\game{3}(A)=1 \wedge \neg\bad}\\ 
+\nonumber & = \Prob{\game{3}(A)=1}\Prob{\game{3}(A):\,\neg\bad}\\
+& = \Prob{\game{3}(A)=1}\frac{1}{\dbinom{q}{r}}\label{eq:3a}\\
+\Prob{\game{5}(A)=1} &= \Prob{\game{4}(A)=1}\label{eq:3b}
+\end{align}
+
+From  \Cref{eq:3,eq:3a,eq:3b}:
+\begin{equation}
+\Prob{\game{5}(A)=1} = \Prob{\game{2}(A)=1}\frac{1}{\dbinom{q}{r}}\label{eq:3c}
+\end{equation}
+
 \tsnote{The PRF experiment has not be defined yet, so strictly
   speaking these claims make no sense. }
-Let adversaries $B_1, B_2$ be as shown in Figures~\ref{xxx}.  By
-construction, these simulate $\game{1}(A)$ and $\game{2}(A)$,
-respectively. When $b=0$, $B_1$ wins if $\game{1}(A)$ outputs 0; $B_2$
-wins if $\game{2}(A)$ returns 0. When $b=1$, $B_1$ and $B_2$ exactly
-simulate $\game{0}(A)$ and $\game{1}(A)$.  \tsnote{What is~$b$?} Thus, we have
+The PRF game of $F$ is shown in \Cref{fig:prf}. Let prf-adversaries $B_1, B_2$ be as shown in \Cref{fig:BGame1}.  By
+construction, these simulate $\game{1}(A)$ and $\game{2}(A)$, respectively.
+When $b=0$, $B_1$ wins if $\game{1}(A)$ outputs 0; $B_2$ wins if $\game{2}(A)$ returns 0.
+When $b=1$, $B_1$ and $B_2$ exactly simulate $\game{0}(A)$ and $\game{1}(A)$.
+So,
 \begin{align}
@@
 \oracle{$\HashOracle(x)$}\\
-$h_i(x) = F_{K_1}(x)+i \cdot F_{K_2}(x) \bmod m$, for $i\in[1,k]$\\
+for $i = 1$ to $k$\\
+\nudge $h_i(x) = F_{K_1}(x)+i \cdot F_{K_2}(x) \bmod m$\\
 Ret $\left(h_1(x),\ldots,h_k(x)\right)$
@@
 \oracle{$\HashOracle(x)$}\\
-$h_i(x) = F_{K_1}(x)+i \cdot \rho(x) \bmod m$, for $i\in[1,k]$\\
+for $i=1$ to $k$\\
+\nudge $h_i(x) = F_{K_1}(x)+i \cdot \rho(x) \bmod m$\\
 Ret $\left(h_1(x),\ldots,h_k(x)\right)$
@@
 \oracle{$\HashOracle(x)$}\\
-$h_i(x) = \rho_1(x)+i \cdot \rho_2(x) \bmod m$, for $i\in[1,k]$\\
+for $i=1$ to $k$\\
+\nudge $h_i(x) = \rho_1(x)+i \cdot \rho_2(x) \bmod m$\\
 Ret $\left(h_1(x),\ldots,h_k(x)\right)$
@@
 $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
+$\bad \gets \false$\\
 %$\calY \gets \emptyset $\\
@@
 $a,b \getsr [m]$\\
-for $i = 1$ to~$k$, $v_i = a+i \cdot b \bmod m$\\
+for $i = 1$ to~$k$\\
+\nudge $v_i = a+i \cdot b \bmod m$\\
 Ret $\left(v_1,\ldots,v_k\right)$
@@
 \caption{\Cref{thm1}:Game playing argument}\label{fig:Game}
+\end{figure}
+
+%\caption{$\Cref{thm1}:\game{5}(A)$ in game playing argument}\label{fig:game5}
+\begin{figure}
+\centering
+\fpage{0.8}
+{
+\hpagess{0.5}{0.4}{
+\underline{$\game{5}(A)$}\\
+$c \gets 0$\\
+$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
+$\calY \gets \emptyset$\\
+$S \getsr \distr{\univ}{n}$\\
+$M \getsr \Rep^{\HashOracle}(\calS)$\\
+$\calZ \getsr A^{\QryOracle}(\calS)$\\
+if $|\calY| < r$ or $\calY \cap \calS \neq \emptyset$ then\\
+\nudge Ret 0\\
+if $\forall y \in \calY,\,\Qry^{\HashOracle}(M,y)=1$ then \\
+\nudge Ret 1\\
+Ret 0
+}
+%
+{
+\oracle{$\QryOracle(x)$}\\
+$c \gets c+1$\\
+if $c \in \mathcal{I}$ then\\
+\nudge $\calY \gets \calY \cup {x}$\\
+\nudge Ret~$1$\\\\
+%
+\oracle{$\HashOracle(x)$}\\
+$a,b \getsr [m]$\\
+for $i = 1$ to~$k$\\
+\nudge $v_i = a+i \cdot b \bmod m$\\
+Ret $\left(v_1,\ldots,v_k\right)$
+}
+}
+\caption{$\Cref{thm1}:\game{5}(A)$ in game playing argument}\label{fig:game5}
+\end{figure}
+
+%\caption{PRF game}\label{fig:prf}
+\begin{figure}
+\centering
+\fpage{0.45}{
+\hpagess{0.4}{0.35}
+{
+$\experimentv{\ExpPRF{F}{B}}$\\
+$K \getsr \calK $\\
+$\rho \getsr Func(\univ,[m])$\\
+$b \getsr \bits$\\
+$b' \getsr B^\calO$\\
+Ret $[b = b']$\\
+}
+{
+$\oracle{\calO \smallskip(x)}$\\
+if $ b = 1$ then\\
+\nudge Ret $F_K(x)$\\
+Ret $\rho(x)$\\
+}
+}
+\caption{PRF game}\label{fig:prf}
 \end{figure}
@@
 When $A$ halts with output $\calZ'$: \\
-\nudge if $|\calZ'| < t$ or $\calZ' \cap \calS \neq \emptyset$ then \\
+\nudge if $|\calZ'| < r$ or $\calZ' \cap \calS \neq \emptyset$ then \\
 \nudge \nudge Ret 0\\
@@
 \caption{\Cref{thm1}:Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
+\end{figure}
+
+%\caption{Non-adaptive adversaries simulating $\game{2}(A)$} \label{AGame3}
+\begin{figure}
+\centering
+\fpage{0.8}{
+\hpagessl{.5}{.4}
+{
+$\adversaryv{D^{\HashOracle}}$\\
+$c \gets 0$\\
+$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
+$\calY, \calZ \gets \emptyset $ \\
+When $A$ asks $\QryOracle(x)$:\\
+\nudge $c \gets c+1$\\
+\nudge if $c \in \mathcal{I}$ then\\
+\nudge \nudge $\calY \gets \calY \cup {x}$\\
+\nudge \nudge Ret~$1$\\
+\nudge else \\
+\nudge  \nudge Ret~$0$\\
+When $A$ halts with output $\calZ'$\\
+\nudge if $|\calZ'|<r \, \mbox{or} \, |\calY| < r$\\
+\nudge \nudge Ret $\emptyset$\\
+\nudge if $\forall y \in \calY,\,\Qry^{\HashOracle}(M,y)=1$ then \\
+\nudge \nudge Ret $\calY$\\
+\nudge Ret $\emptyset$\\\\
+%
+\oracle{$\HashOracle(x)$}\\
+$a,b \getsr [m]$\\
+for $i = 1$ to~$k$\\
+\nudge $v_i = a+i \cdot b \bmod m$\\
+Ret $\left(v_1,\ldots,v_k\right)$
+}
+{
+$\adversaryv{D'^{\HashOracle}}$\\
+$c \gets 0$\\
+$\ell \getsr [q]$\\
+%$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
+$\calY \gets \emptyset$\\
+When $A$ asks $\QryOracle(x)$:\\
+$\nudge c \gets c + 1$\\
+\nudge if $c == \ell$\\
+$\nudge$ $\nudge r \gets \Qry^{\HashOracle}(M,x)$\\
+$\nudge$ $\nudge \calY \gets \calY \cup {x}$\\
+\nudge else\\
+$\nudge$ $\nudge r \gets 0$\\
+\nudge Ret $r$\\
+When $A$ halts with output $\calZ'$\\
+\nudge $z \gets \calY$\\
+\nudge if $\Qry^{\HashOracle}(M,z)=1$ then\\
+\nudge \nudge Ret $z$\\
+\nudge else\\
+\nudge \nudge Ret Null\\\\
+%
+\oracle{$\HashOracle(x)$}\\
+$a,b \getsr [m]$\\
+for $i = 1$ to~$k$\\
+\nudge $v_i = a+i \cdot b \bmod m$\\
+Ret $\left(v_1,\ldots,v_k\right)$
+}
+}
+\caption{Non-adaptive adversaries simulating $\game{3}(A)$} \label{fig:AGame3}
 \end{figure}
@@
 
+The classical FP requirement considers only non-adaptive (and information-theoretic) adversaries, and $D$ is one such adversary simulating $\game{5}(A)$ as closely as possible, whereas $D'$ mimics $D$ for $r=1$.
+$D'$ outputs a FP as in a classic Bloom filter and its FP-error is upperbounded by $[(1-e^{-kn/m})^k +O(1/n)]$ \cite{KirschMitzenmacher}.
+%\acnote{changed}\tsnote{The classical FP requirement considers only non-adaptive (and information-theoretic) adversaries.
+It suffices to say this.}
 \noindent
-In $\game{3}(A)$, $t$ elements are sampled from the $q$ adaptive
-queries and tested for false positives. This is equivalent to
-$\game{2}(A)$, as the hash functions of the $\HashOracle$ oracle are
-random and $A$ wins this  game only if it outputs atleast $t$
-FP's.\acnote{I was facing problems in connecting game2(adaptive) and
-  game3(non-adaptive). I felt that the probability of  winning both
-  games should be equal as the hash functions in the hash oracle are
-  random(not independent) and adversary in game 2 has no means to
-  output t elements which have higher chance of winning than those in
-  game 3.} \tsnote{I have rewritten game $\game{3}(A)$ and added
-  $\game{4}(A)$.  It should be that
-  $\Prob{\game{2}(A)}=\Prob{\game{3}(A)=1}$. Moreover
-  $\Prob{\game{4}(A)=1} = \Prob{\game{3}(A)=1 \wedge \neg\bad} =
-  \Prob{\game{3}(A)=1}\Prob{\game{3}{A}:\,\neg\bad} =
-  \Prob{\game{3}(A)=1}\frac{1}{\dbinom{q}{r}}$. Finally the event
-  $\game{4}(A)=1$ happens iff $\bad \neq \true$.  That means there is
-  a non-adaptive adversary that runs~$A$, simulates $\QryOracle$ by
-  simply returning 1 iff $c \in \mathcal{I}$, and uses the queries
-  with indices in $\mathcal{I}$ as its non-adaptive FPs.  To be
-  totally clear, you might want to add a $\game{5}(A)$ that has this
-  $\QryOracle$ behavior, and then give the non-adaptive FP-adversary~$A'$ that
-simulates~$\game{5}(A)$, and so on. }\fixme{Clean up everything after this.}
+From \Cref{fig:AGame3}, it is evident that
+\begin{align}
+\Prob{\game{5}(A)=1} &= \Prob{D \, \mbox{outputs $r$ FP} \,}\label{eq:4a}\\
+\nonumber \Prob{D \, \mbox{outputs r FP} \,} &=  \Big[\Prob{D' \, \mbox{outputs FP} \,}\Big]^r\\
+& \leq \Big[(1-e^{-kn/m})^k +O(1/n)\Big]^r \label{eq:4b}
+\end{align}
+\noindent
+From \Cref{eq:4a,eq:4b}
 \begin{equation}
-\Prob{\game{2}(A)=1} = \Prob{\game{3}(A)=1}\label{eq:3}
+\Prob{\game{5}(A)=1} \leq [(1-e^{-kn/m})^k +O(1/n)]^r \label{eq:4}
 \end{equation}
@@
 \noindent
-The classical FP requirement considers only non-adaptive (and information-theoretic) adversaries, and $D$ is one such adversary simulating $\game{3}(A)$ as closely as possible, whereas $D'$ mimics $D$ for $t=1$.
-$D'$ outputs a FP as in a classic Bloom filter and its FP-error is upperbounded by $[(1-e^{-kn/m})^k +O(1/n)]$ \cite{KirschMitzenmacher}.
-%\acnote{changed}\tsnote{The classical FP requirement considers only non-adaptive (and information-theoretic) adversaries.
-It suffices to say this.}
-From \Cref{fig:AGame3}, it is evident that
+Using \ref{eq:4} in \ref{eq:3c}:
 \begin{align}
-\Prob{\game{3}(A)=1} &= \Prob{D \, \mbox{outputs $t$ FP} \,}\label{eq:4a}\\
-\nonumber \Prob{D \, \mbox{outputs t FP} \,} &= \dbinom{q}{r}\times \Big[\Prob{D' \, \mbox{outputs FP} \,}\Big]^r\\
-& \leq \dbinom{q}{r}\times \Big[(1-e^{-kn/m})^k +O(1/n)\Big]^r \label{eq:4b}
+\nonumber \Prob{\game{2}(A)=1}\frac{1}{\dbinom{q}{r}}  &\leq [(1-e^{-kn/m})^k +O(1/n)]^r\\
+ \Prob{\game{2}(A)=1}  & \leq \dbinom{q}{r}[(1-e^{-kn/m})^k +O(1/n)]^r\label{eq:5}
 \end{align}
-From \Cref{eq:4a,eq:4b}
-\begin{equation}
-\Prob{\game{3}(A)=1} \leq \dbinom{q}{r}\times [(1-e^{-kn/m})^k +O(1/n)]^r \label{eq:4}
-\end{equation}
-%\caption{Non-adaptive adversaries simulating $\game{2}(A)$} \label{AGame3}
-\begin{figure}
-\centering
-\fpage{0.8}{
-\hpagessl{.5}{.4}
-{
-$\adversaryv{D^{\HashOracle}}$\\
-$\calY, \calZ \gets \emptyset $ \\
-$\rho \getsr Func(U,[m])$\\
-$\calS \getsr \distr{U}{n}$\\
-$M \getsr \Rep^{\HashOracle}(\calS)$\\
-When $A$ asks $\QryOracle(x)$:\\
-$\nudge \calY \gets \calY \cup {x}$\\
-$\nudge r \gets \Qry^{\HashOracle}(M,x)$\\
-\nudge Ret $r$\\
-When $A$ halts with output $\calZ'$\\
-\nudge if $|\calZ'|<t \, \mbox{or} \, |\calY| < t$\\
-\nudge \nudge Ret $\emptyset$\\
-\nudge for $i=1$ to $t$ \\
-\nudge \nudge $z_i \getsr \calY $\\
-\nudge \nudge if $\Qry^{\HashOracle}(M,z_i)=0$ then\\
-\nudge \nudge Ret $\emptyset$\\
-\nudge \nudge $\calZ \gets \calZ \cup z_i$\\
-\nudge \nudge $\calY \gets \calY \setminus {z_i}$\\
-\nudge Ret $\calZ $\\\\
-%
-\oracle{$\HashOracle(x)$}\\
-$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
-Ret $\left(h_1(x),\ldots,h_k(x)\right)$
-}
-{
-$\adversaryv{D'^{\HashOracle}}$\\
-$\calY \gets \emptyset $ \\
-$\ell \getsr [q]$\\
-$c = 0$\\
-$\rho \getsr Func(U,[m])$\\
-$\calS \getsr \distr{U}{n}$\\
-$M \getsr \Rep^{\HashOracle}(\calS)$\\
-When $A$ asks $\QryOracle(x)$:\\
-$\nudge c = c + 1$\\
-\nudge if $c == \ell$\\
-$\nudge$ $\nudge r \gets \Qry^{\HashOracle}(M,x)$\\
-$\nudge$ $\nudge \calY \gets \calY \cup {x}$\\
-\nudge else\\
-$\nudge$ $\nudge r = 0$\\
-\nudge Ret $r$\\
-When $A$ halts with output $\calZ'$\\
-\nudge $z \gets \calY$\\
-\nudge if $\Qry^{\HashOracle}(M,z)=1$ then\\
-\nudge \nudge Ret $z$\\\\
-%
-\oracle{$\HashOracle(x)$}\\
-$h_i(x) = \rho_1(x)+i \cdot \rho_2(x)$, for $i\in[1,k]$\\
-Ret $\left(h_1(x),\ldots,h_k(x)\right)$
-}
-}
-\caption{Non-adaptive adversaries simulating $\game{3}(A)$} \label{fig:AGame3}
-\end{figure}	
+
 \fixme{These adversaries are incorrect.  They are FP adversaries, so
@@
 \noindent
-From \Cref{eq:0,eq:2,eq:3,eq:4} \\
+
+From \Cref{eq:0,eq:2,eq:5} \\
 \begin{align}
-\nonumber \AdvFPSecHash{B_{\mathrm{lin}},t}{A} &- \Prob{\game{2}(A)=1} =  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}   \\
-\nonumber \AdvFPSecHash{B_{\mathrm{lin}},t}{A}  &=  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} + \Prob{\game{2}(A)=1}  \\
-\AdvFPSecHash{B_{\mathrm{lin}},t}{A} &\leq  \AdvPRF{F}{B_1} +
-\AdvPRF{F}{B_2}  +{\dbinom{q}{t}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^t
+\nonumber \AdvFPSecHash{B_{\mathrm{lin}},r}{A} &- \Prob{\game{2}(A)=1} =  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}   \\
+\nonumber \AdvFPSecHash{B_{\mathrm{lin}},r}{A}  &=  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} + \Prob{\game{2}(A)=1}  \\
+\AdvFPSecHash{B_{\mathrm{lin}},r}{A} &\leq  \AdvPRF{F}{B_1} +
+\AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
 \end{align}
+
 \end{proof}

### 2016-07-28 Theorem1_FP.tex
Corrections Proof1

@@
 Let $F\colon\mathcal{K} \times \univ \to [m]$ be a function family.
-The $\Hash$ algorithm samples two keys $K_0,K_1 \getsr \mathcal{K}$ and defines $h_j(x) = F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$ for $j \in [k]$.
+The $\Hash$ algorithm samples two keys $K_0,K_1 \getsr \mathcal{K}$ and defines $h_j(x) = F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$ for $j \in [1,k]$.
 The $\Rep$ and $\Qry$ algorithms are the standard (determinisitic) BF ones.
@@
 \[
-\AdvFPSecHash{B_{\mathrm{lin}},r}{A} \leq  \AdvPRF{F}{B_1} +
-\AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
+\AdvFPSecHash{B_{\mathrm{lin}},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
 \]
@@
 of removing adaptivity.  Finally, $\dbinom{q}{r} \leq q^r$ (with
-reasonable tightness when~$t$ is small) in which case the final term in the bound behaves as 
+reasonable tightness when~$r$ is small) in which case the final term in the bound behaves as 
 $(q (1-e^{-kn/m})^k + O(q/n) )^r$; loosely, the bound one expects for
@@
 \nudge $\calY \gets \calY \cup {x}$\\
-\nudge Ret~$1$\\\\
+\nudge Ret 1\\
+else\\
+\nudge Ret 0 \\\\
 %
@@
 }
-\caption{$\Cref{thm1}:\game{5}(A)$ in game playing argument}\label{fig:game5}
+\caption{\Cref{thm1}:$\game{5}(A)$ in game playing argument}\label{fig:game5}
 \end{figure}
@@
 \nudge else\\
-\nudge \nudge Ret Null\\\\
+\nudge \nudge Ret $\lambda$\\\\
 %

### 2016-07-29 Theorem1_FP.tex
Theorem1 resource accounting modified

@@
 Fix $k,m,n>0$, and let $B_\mathrm{lin}=(\Hash,\Rep,\Qry)$ be the hash-based filter just described. 
-Let~$A$ be an adversary, compatible with $\ExpFPSecHash{B_\mathrm{lin},r}{\cdot}$, that asks at most~$q$ queries in time $t$ to its $\QryOracle$ oracle.  Then 
+Let~$A$ be an adversary, compatible with $\ExpFPSecHash{B_\mathrm{lin},r}{\cdot}$, that asks at most~$q \times r$ queries in time $t$ to its $\QryOracle$ oracle.  Then 
 \[
@@
 for PRF-adversaries~$B_1$ and $B_2$ given explicitly in the proof of
-this theorem. Here, $B_1$ and $B_2$, each ask $q$ oracle queries in time O(t). \tsnote{Statement about resources of these reductions.}
+this theorem. Here, $B_1$ and $B_2$, each ask $q \times r$ oracle queries in time O(t). \tsnote{Statement about resources of these reductions.}
 \end{theorem}
@@
 \begin{equation}
-\Prob{\game{5}(A)=1} \leq [(1-e^{-kn/m})^k +O(1/n)]^r \label{eq:4}
+\Prob{\game{5}(A)=1} \leq [(1-e^{-kn/m})^k + O(1/n)]^r \label{eq:4}
 \end{equation}

### 2016-07-29 Theorem1_FP.tex
Theorem 2 proof in old syntax

@@
 %$d \getsr \bits $\\
-$\rho_2 \getsr \Func(\univ,[m])$ \\
+$\rho_2 \getsr Func(\univ, [m])$ \\
 $S \getsr \distr{\univ}{n}$\\

### 2016-07-29 Theorem2_FP.tex
Theorem 2 proof in old syntax

@@
 \newcommand{\rhoK}{\rho(\langle j,x \rangle)}
+
 \fixme{Clean up to match style, language and typesetting (macros,
-  especially) of previous theorem.}\acnote{Modified.}
+  especially) of previous theorem.}
 
-Let $B_{\mathrm{lin}}=(\Hash,\Rep,\Qry)$ be the hash-based filter defined as earlier, except the private hash functions of the $\HashOracle'$s algorithm are $h_j(x) = \FK, \, j \in [1,k]$.
-Informally, if F is PRF secure and the filter has low FP-error in the non-adaptive setting, then $B_{\mathrm{lin}}$ is secure against adaptive FP-finding adversaries.
+Let $B_{\mathrm{ds}}=(\Hash,\Rep,\Qry)$ be the hash-based filter defined as earlier, except the hash functions are defined as $h_j(x) = \FK, \, j \in [1,k]$.
+Informally, the following result shows, if F is PRF secure and the filter has low FP-error in the non-adaptive setting, then $B_{\mathrm{ds}}$ is secure against adaptive FP-finding adversaries.
+
 \begin{theorem}\label{thm2}
 Fix $k,m,n >0$.
-Let $B_{\mathrm{lin}}$ be the hash based filter just described.
-If there exists an adaptive adversary $A$ compatible with $\ExpFPPubHash{B_{\mathrm{lin},t}}{\cdot}$, then there exists an adversary $B$ attacking the PRF game such that
+Let $B_{\mathrm{ds}}$ be the hash based filter described earlier.
+If there exists an adaptive adversary $A$ compatible with $\ExpFPPubHash{B_{\mathrm{ds},t}}{\cdot}$ asking $q \times r$ queries in $t$ time, then there exists an adversary $B$ attacking the PRF game in time $O(t)$ and asking same number of queries as $A$ such that
 \begin{equation}
-\AdvFPSecHash{B_\mathrm{lin},t}{A}\leq  \AdvPRF{F}{B}  + \frac{q}{\dbinom{q}{t}} \times  (1-e^{-kn/m})^k
+\AdvFPSecHash{B_\mathrm{ds},t}{A}\leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
 \end{equation}
-Before giving the proof, it should be noted that $\FK$ provides domain separation and hence mutual independence, unlike hash functions in \Cref{thm1}
 \end{theorem}
 
+\acnote{I think we should give a proof of the non-adaptive FP-error bound $(1-e^{-kn/m})^k + O(1/n) $.
+This bound which we picked from KM's theorem 6.2, is a particular case (double hashing scheme).
+Theorem 6.1, on the other hand holds good for any hashing scheme that satisfies Lemma 4.1.
+\\
+ I tried to give the FP-bound as a Lemma. 
+\begin{lemma}\label{lemma1}
+Fix $k,m,n >0$. The FP-error of hash-based filter $B_{\mathrm{ds}}$ with hash functions $h_j(x) = \FK, \, j \in [k]$ is upperbounded by $(1-e^{-kn/m})^k + O(1/n)$.
+\end{lemma}
+}
+\acnote{As I had told you earlier, I was not able to understand the proofs of KM paper and now I am stuck in this proof. 
+\begin{proof}($Lemma$ \ref{lemma1})
+In \ref{KM}, $Theorem \,6.1$ gives the upperbound of FP error of any hashing scheme satisfying the 5 conditions enlisted in Lemma 4.1, and all these conditions are satisfied by $B_{\mathrm{ds}}$ as shown below.\\
+Since the hash functions of $B_{\mathrm{ds}}$ provide randomness with domain separation and the number of hash functions are controlled by parameter $j$, condition 1 and 2 are trivially satisfied.
+The last condition is also trivial, since size of $B_{\mathrm{ds}}$ will be some constant multiple of size of $S$, as in the classical bloom filter.\\
+The satisfiability of remaining 2 conditions is non-trivial ...
+\end{proof}}
+%
 \begin{proof}[\Cref{thm2}]
 We use a game playing argument similar to \Cref{thm1} to prove this theorem.
-In \game{0}(A), adversary attacks the FP game with private hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpFPSecHash{B_\mathrm{lin},t}{A}$.
+In \game{0}(A), adversary attacks the FP game with  hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpFPSecHash{B_\mathrm{ds},r}{A}$.
 \begin{equation}
-\AdvFPSecHash{B_\mathrm{lin},t}{A} = \Prob{\game{0}(A)=1}\label{eq:0T2}
+\AdvFPSecHash{B_\mathrm{ds},r}{A} = \Prob{\game{0}(A)=1}\label{eq:0T2}
 \end{equation}
 \noindent
-\game{1}(A) simulates $\ExpFPSecHash{B_\mathrm{lin},t}{A}$ with a random function $\rho \getsr Func(\univ,[m])$ used to generate uniformly random  hash-indices with domain separation, of elements $x \in \univ$.
-In $\game{2}(A)$, $t$ elements are sampled from the set of queries and tested for false positives.
-The three games are shown in \Cref{fig:GameT2}.
+\game{1}(A), \game{2}(A), and \game{3}(A) are same as in the previous theorem, except the hash-functions are distinct random functions.
+The non-adaptive counterparts of $B_\mathrm{ds}$ as well as the prf adversary are  identical to those of $B_\mathrm{lin}$.
+As shown in \game{1}(A) and \game{2}(A), the $\HashOracle$ oracle returns distinct random values in these simulations.
+$B$, on the other hand uses its oracle to generate random values (for $b=0$) in the following way, $h_j(x) = \calO(\langle j,x \rangle)$.
 
@@
 \begin{figure}
-\fpage{.99}{
-\hpagesssl{.34}{.34}{.31}
+\fpage{.9}{
+\hpagessl{.45}{.5}
 {
@@
 }
+}
+\fpage{.9}{
+\hpagessl{.45}{.5}
 {
-\underline{\game{2}(A)}\\
-$\calY \gets \emptyset $\\
-$\rho \getsr \Func{\univ,[m]}$\\
+\underline{{$\game{2}(A)$},\fbox{$\game{3}(A)$}}\\
+$c \gets 0$\\
+$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
+$\bad \gets \false$\\
 $S \getsr \distr{\univ}{n}$\\
@@
 $\calZ \getsr A^{\QryOracle}(\calS)$\\
-$z_1,\cdots, z_t \getsr \calY $\\
-if $\exists i\in[1,t] \, \mbox{s.t.} \,\Qry^{\HashOracle}(M,z_i)=0$ then\\
-\nudge Ret 0\\
-Ret 1\\\\
+if $|\calZ| < r$ or $\calZ \cap \calS \neq \emptyset$ then Ret 0\\
+if $\forall z \in \calZ,\,\Qry^{\HashOracle}(M,z)=1$ then \\
+\nudge if $\bad=\true$ then \fbox{Ret 0}\\
+\nudge Ret 1\\
+Ret 0\\\\
 %
 \oracle{$\QryOracle(x)$}\\
-$\calY \gets \calY \cup x$\\
-Ret $\Qry^{\HashOracle}(M,x)$\\
+%$\calY \gets \calY \cup \{x\}$\\
+$c \gets c+1$\\
+$v \gets \Qry^{\HashOracle}(M,x)$\\
+if $c \in \mathcal{I}$ and $v\neq 1$ then\\
+\nudge $\bad \gets \true$ \\
+%\nudge \fbox{Ret 1} \\
+if $c \not\in \mathcal{I}$ and $v\neq 0$ then\\
+\nudge $\bad \gets \true$\\
+%\nudge \fbox{Ret 0}\\
+Ret~$v$\\\\
 %
 \oracle{$\HashOracle(x)$}\\
-$h_j(x) = \rhoK$\\
-Ret $\left(h_1(x),\ldots,h_k(x)\right)$
+for $i = 1$ to~$k$\\
+\nudge $v_i  \getsr [m]$\\
+Ret $\left(v_1,\ldots,v_k\right)$
+}
+{
+\underline{$\game{4}(A)$}\\
+$c \gets 0$\\
+$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
+$\calY \gets \emptyset$\\
+$S \getsr \distr{\univ}{n}$\\
+$M \getsr \Rep^{\HashOracle}(\calS)$\\
+$\calZ \getsr A^{\QryOracle}(\calS)$\\
+if $|\calY| < r$ or $\calY \cap \calS \neq \emptyset$ then\\
+\nudge Ret 0\\
+if $\forall y \in \calY,\,\Qry^{\HashOracle}(M,y)=1$ then \\
+\nudge Ret 1\\
+Ret 0\\\\
+%
+\oracle{$\QryOracle(x)$}\\
+$c \gets c+1$\\
+if $c \in \mathcal{I}$ then\\
+\nudge $\calY \gets \calY \cup {x}$\\
+\nudge Ret 1\\
+else\\
+\nudge Ret 0 \\\\
+%
+\oracle{$\HashOracle(x)$}\\
+for $i = 1$ to~$k$\\
+\nudge $v_i  \getsr [m]$\\
+Ret $\left(v_1,\ldots,v_k\right)$
 }
 }
-\caption{\Cref{thm2}:Game playing argument}\label{fig:GameT2}
+\caption{\Cref{thm2}: Game playing argument}\label{fig:GameT2}
 \end{figure}
-
 \noindent
-In \Cref{fig:BGame1T2}, adversary $B$ simulates $\game{0}(A)$ and $\game{1}(A)$ for $b=1$ and $b=0$ respectively .
-
-%\caption{Adversary $B$ and $A'$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}
-\begin{figure}
-\centering
-\fpage{0.9}{
-\hpagessl{0.5}{0.5}
-{
-$\adversaryv{B^{\calO}}$\\
-$K_1 \getsr \calK $\\
-$S \getsr \distr{\univ}{n}$\\
-$M \getsr \Rep^{\HashOracle}(\calS)$\\
-When $A$ asks $\QryOracle(x)$:\\
-$\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
-When $A$ halts with output $\calZ'$: \\
-if $|\calZ'| < t$ or $\calZ' \cap \calS \neq \emptyset$ then \\
-\nudge Ret 0\\
-if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
-\nudge Ret 0\\
-Ret 1\\\\
-\oracle{$\HashOracle(x)$}\\
-$ \mathrm{Ret} \nudge \calO(\langle j,x \rangle)$, for $j\in[1,k]$\\
-}
-{
-$\adversaryv{A'^{\HashOracle}}$\\
-$\calY \gets \emptyset $ \\
-$\ell \getsr [q]$\\
-$c = 0$\\
-$\rho \getsr Func(U,[m])$\\
-$S \getsr \distr{U}{n}$\\
-$M \getsr \Rep^{\HashOracle}(\calS)$\\
-When $A$ asks $\QryOracle(x)$:\\
-$\nudge c = c + 1$\\
-\nudge if $c == \ell$\\
-$\nudge$ $\nudge r \gets \Qry^{\HashOracle}(M,x)$\\
-$\nudge$ $\nudge \calY \gets \calY \cup x$\\
-\nudge else\\
-$\nudge$ $\nudge r = 0$\\
-\nudge Ret $r$\\
-When $A$ halts with output $\calZ'$\\
-\nudge $z \gets \calY$\\
-\nudge if $\Qry^{\HashOracle}(M,z)=0$ then\\
-\nudge \nudge Ret 0\\
-\nudge Ret 1\\\\
-%
-\oracle{$\HashOracle(x)$}\\
-$\mathrm{Ret} \nudge \rhoK$
-}
-}
-\caption{\Cref{thm2}:Adversary $B$ and $A'$ simulating $\game{0}(A)$, $\game{1}(A)$ and $\game{2}(A)$ respectively }\label{fig:BGame1T2}
-\end{figure}
-
-\begin{align}
-\Prob{\ExpPRF{F}{B} = 1|b=1} &= \Prob{\game{0}(A)=1}\label{eq:m1T2}\\
-\Prob{\ExpPRF{F}{B} = 1|b=0} &= 1-\Prob{\game{1}(A)=1}\label{eq:m2T2}
+Using analysis of previous theorem and \Cref{lemma1}\acnote{change if lemma1 not required}, we have
+\begin{align}\label{eq:1T2}
+\AdvPRF{F}{B} &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1} \\
+\Prob{\game{1}(A)=1} &= \Prob{\game{2}(A)=1}\\
+\Prob{\game{3}(A)=1} &= \frac{1}{\dbinom{q}{r}}\Prob{\game{2}(A)=1}\\
+\Prob{\game{4}(A)=1} &= \Prob{\game{3}(A)=1}\\
+\Prob{\game{4}(A)=1} & \leq \Big[(1-e^{-kn/m})^k +O(1/n)\Big]^r
 \end{align}
@@
 \noindent
-From \Cref{eq:m1T2,eq:m2T2},
+From \Cref{eq:0T2,eq:1T2}
 \begin{align}
-\nonumber \Prob{\ExpPRF{F}{B} = 1} &= .5\Prob{\ExpPRF{F}{B_1}=1|b=0} + .5\Prob{\ExpPRF{F}{B_1} = 1|b=1}\\
-\nonumber 2\Prob{\ExpPRF{F}{B} = 1} &= 1-\Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1}\\
-\nonumber (2\Prob{\ExpPRF{F}{B} = 1} - 1)  &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1}\\
- \AdvPRF{F}{B} &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1} \label{eq:1T2}
-\end{align}
-
-\noindent
-Following a similar argument from \Cref{thm1}\fixme{For $t>1$, proof fails for $t>1$}\acnote{Modified.}
-\begin{equation}
-\Prob{\game{1}(A)=1} = \frac{1}{\dbinom{q}{t}}\times\Prob{\game{2}(A)=1}\label{eq:3T2}
-\end{equation}
-
-\begin{align}
-\nonumber \Prob{\game{2}(A)=1} &= q\Prob{A' \mbox{outputs FP}}\\
-& \leq q \times (1-e^{-kn/m})^k \label{eq:4T2}
-\end{align}
-
-\noindent
-From \Cref{eq:0T2,eq:1T2,eq:3T2,eq:4T2}: \\
-\begin{align}
-\nonumber \AdvFPSecHash{B_\mathrm{lin},t}{A} &- \Prob{\game{1}(A)=1} =  \AdvPRF{F}{B}   \\
-\nonumber \AdvFPSecHash{B_\mathrm{lin},t}{A}  &=  \AdvPRF{F}{B} + \Prob{\game{1}(A)=1}  \\
-\AdvFPSecHash{B_\mathrm{lin},t}{A} &\leq  \AdvPRF{F}{B}  + \frac{q}{\dbinom{q}{t}} \times  (1-e^{-kn/m})^k
+\nonumber \AdvPRF{F}{B} &= \AdvFPSecHash{B_\mathrm{ds},r}{A} - \frac{1}{\dbinom{q}{r}}\Prob{\game{2}(A)=1}\\
+\nonumber \AdvFPSecHash{B_\mathrm{ds},r}{A} &= \AdvPRF{F}{B} + \frac{1}{\dbinom{q}{r}}\Prob{\game{2}(A)=1}\\
+\nonumber \AdvFPSecHash{B_\mathrm{ds},r}{A} &= \AdvPRF{F}{B} +  \dbinom{q}{r}\Prob{\game{4}(A)=1}\\
+\AdvFPSecHash{B_\mathrm{ds},r}{A} &= \AdvPRF{F}{B} +  \dbinom{q}{r}\Big[(1-e^{-kn/m})^k +O(1/n)\Big]^r
 \end{align}

### 2016-08-02 Theorem1_FP.tex
edits to theorem 1 and proof

@@
 
-\fixme{Note: the following theorem is incorrect for $r>1$.  Or, at least, the proof does not cover $r>1$.}\acnote{Modified.}
 \begin{theorem}\label{thm1}
-Fix $k,m,n>0$, and let $B_\mathrm{lin}=(\Hash,\Rep,\Qry)$ be the hash-based filter just described. 
-Let~$A$ be an adversary, compatible with $\ExpFPSecHash{B_\mathrm{lin},r}{\cdot}$, that asks at most~$q \times r$ queries in time $t$ to its $\QryOracle$ oracle.  Then 
+Fix $k,m,n,r>0$, and let $B_\mathrm{lin}=(\Hash,\Rep,\Qry)$ be the hash-based filter just described. 
+For any adversary~$A$ that makes a total of~$q$ queries to its oracle
+and has time-complexity~$t$,
+there exist adversaries~$B_1,B_2$ (explicitly constructed in the proof of this theorem) such that
 \[
-\AdvFPSecHash{B_{\mathrm{lin}},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
+\AdvFPSecHash{B_{\mathrm{lin}},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
 \]
-for PRF-adversaries~$B_1$ and $B_2$ given explicitly in the proof of
-this theorem. Here, $B_1$ and $B_2$, each ask $q \times r$ oracle queries in time O(t). \tsnote{Statement about resources of these reductions.}
+Here, $B_1$ and $B_2$, each ask~$q$ oracle queries and have time complexity~$O(t+qm)$.
 \end{theorem}
@@
 
-In $\game{3}(A)$, $r$ random integers are chosen and the $\QryOracle$ oracle sets a $\bad$ flag if query response for any of the $r$ queries is false or any of the $q-r$ queries return true.
-Also, the hash functions are linear combinations of two random points in $[m]$, similar to $\game{2}(A)$.
-So, both have equal probability of returning 1.
+\tsnote{I'll need to rewrite all below here.  The current text is too hand-wavy and fast.}
+In $\game{3}(A)$, the hash functions are linear combinations of two random points
+in $[m]$, similar to $\game{2}(A)$. 
+\tsnote{`In transitioning from $\game{2}$ to $\game{3}$ we
+  replace the all-at-once sampling of random functions~$\rho_1,\rho_2$
+with lazying sampling in the $\HashOracle$, which is the only place
+these random functions are used.  This does not alter the input-output
+behavior of the $\HashOracle$.''  Why do we do this?}
+We also sample $r$~distinct random integers are chosen \tsnote{why?
+  What are we setting up?} and the $\QryOracle$ oracle sets a $\bad$
+flag if query response for any of the $r$ queries is false or any of
+the $q-r$ queries return true. \tsnote{We
+  set $\bad$ to $\true$ if the queries indexed by the
+  set~$\mathcal{I}$ fail to be false-positives, or if any of the
+  remaining queries \emph{are} false-positives.  Again, why are we
+  doing this?  }
 
+So, both have equal probability of returning 1.  \tsnote{``The value
+  of~$\bad$ does not affect the value returned by~$\game{3}$. Thus we
+  conclude that...'' }
 \begin{equation}
@@
 
-The probability of winning  $\game{3}(A)$ is same as $\game{4}(A)$, except $\game{4}(A)$ outputs 0 if $\bad$ flag is set.
-In short, $\game{3}(A)$ and $\game{4}(A)$ are identical untill $\bad =true$.
-On the  other hand, $\game{5}(A)$ simulates the non-adaptive counterpart of $\game{4}(A)$.
- \tsnote{I have rewritten game $\game{3}(A)$ and added
-  $\game{4}(A)$.  It should be that
-  $\Prob{\game{2}(A)}=\Prob{\game{3}(A)=1}$. Moreover
-  $\Prob{\game{4}(A)=1} = \Prob{\game{3}(A)=1 \wedge \neg\bad} =
-  \Prob{\game{3}(A)=1}\Prob{\game{3}{A}:\,\neg\bad} =
-  \Prob{\game{3}(A)=1}\frac{1}{\dbinom{q}{r}}$. Finally the event
-  $\game{4}(A)=1$ happens iff $\bad \neq \true$.  That means there is
-  a non-adaptive adversary that runs~$A$, simulates $\QryOracle$ by
-  simply returning 1 iff $c \in \mathcal{I}$, and uses the queries
-  with indices in $\mathcal{I}$ as its non-adaptive FPs.  To be
-  totally clear, you might want to add a $\game{5}(A)$ that has this
-  $\QryOracle$ behavior, and then give the non-adaptive FP-adversary~$A'$ that
-simulates~$\game{5}(A)$, and so on. }\fixme{Clean up everything after this.}
+The probability of winning  $\game{3}(A)$ is same as $\game{4}(A)$,
+except $\game{4}(A)$ outputs 0 if $\bad$ flag is
+set.\tsnote{I don't understand this sentence.  What you mean to say is
+  something like this: ``By construction, $\game{3}$ and $\game{4}$
+  are identical-until-bad.  In addition, $\game{4}$ returning 1
+  implies that $\bad$ is never set to~$\true$.  From these two
+  observations, we can conclude that $\Prob{\game{4}(A)=1} =
+  \Prob{\game{3}(A)=1 \wedge \neg\bad}$.'' }
+In short, $\game{3}(A)$ and $\game{4}(A)$ are identical untill $\bad
+=true$.  On the  other hand, $\game{5}(A)$ simulates the non-adaptive
+counterpart of $\game{4}(A)$.  \tsnote{This statement is unjustified.
+(See my comments below.) Actually it's meaningless, because games are
+not not adaptive or non-adaptive.  Adversaries are.}
 
+\tsnote{You need to just justify these next lines better. For example,
+why is the event $\neg \bad$ independent of the event $\game{3}(A)=1$?}
 \begin{align}
@@
 \end{align}
+\tsnote{How does the last line follow from the games?  I mean, it
+  isn't obvious to me that your $\game{5}$ is equivalent to $\game{4}$.  The
+  latter looks at the adversary's output~$\mathcal{Z}$, but the former
+ignores this and looks at this new set~$\mathcal{Y}$.  Why are these
+equivalent with respect to the events $\game{4}(A)=1$ and
+$\game{5}(A)=1$?  Just looking at the $\QryOracle$ in the two games,
+it appears that they have pretty different behaviors. I mean, in
+$\game{4}$ the oracle still returns what it is supposed to, even if
+$\bad\gets\true$.  But in $\game{5}$ the oracle returns fixed values,
+no matter if the query is or is not a FP.  You have to explain why
+these changes are okay.  Also, why is this new set~$\mathcal{Y}$
+necessary?  }
+\tsnote{The point that needs to be made about the relationship between
+  $\game{4}$ and $\game{5}$ is this.  $\game{4}$ returns 1 only if
+  $\bad=\false$ at the end of the game.  In turn, this implies that
+  the game managed to ``guess'', prior to the execution of~$A$, which
+  of its queries would result in false-positives.  (By the way, we
+  need to state an assumption here: that~$A$ halts and
+  outputs~$\mathcal{Z}$ (of size~$r$) as soon as its queries
+  reveal~$r$ false positives.  This is without loss of generality; say
+why.  I guess you also need to assume that every point in
+the~$\mathcal{Z}$ output by~$A$ has already been queried
+to~$\QryOracle$.  Strictly speaking this is not without loss of
+generality, but would be easily enforced (in the original
+  security definitions) by counting as part of the number of
+  queries~$q$ the points in~$\mathcal{Z}$.  Without these assumptions,
+things don't quite work.)  Hence, if $\game{4}(A)=1$ there is a
+non-adaptive adversary~$D$ that finds~$r$ false positives against
+$\tilde{B}_{\mathrm{lin}}$, which is $B_{\mathrm{lin}}$ but
+with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$,
+respectively.  (Note, this is \emph{not} the adversary~$D$ that you
+give, because the one you give simulates things that it would be given
+in the FP game, e.g. the set~$S$.)  That is, $\Prob{\game{4}(A)=1} =
+\AdvFPSecHash{\tilde{B}_{\mathrm{lin}},r}{D}$.  (So I guess there's no
+need for $\game{5}$.)  Now argue that this advantage is upperbounded
+by what the theorem claims, i.e. the KM bound raised to~$r$.}
 
@@
 
-\tsnote{The PRF experiment has not be defined yet, so strictly
-  speaking these claims make no sense. }
-The PRF game of $F$ is shown in \Cref{fig:prf}. Let prf-adversaries $B_1, B_2$ be as shown in \Cref{fig:BGame1}.  By
+%\tsnote{The PRF experiment has not be defined yet, so strictly
+% speaking these claims make no sense. }
+The PRF game of $F$ is shown in \Cref{fig:prf}. Let prf-adversaries
+$B_1, B_2$ be as shown in \Cref{fig:BGame1}. \tsnote{Why is $B_2$
+  sampling a random function?  This ruins the tightness of security
+  bound w.r.t.\ resources.  Please have~$B_2$ carry out lazy sampling
+  of~$\rho_2$.  Also, please use the macro for Func.}  By
 construction, these simulate $\game{1}(A)$ and $\game{2}(A)$, respectively.
@@
 }
-\caption{PRF game}\label{fig:prf}
+\caption{The PRF experiment for a function family $F \colon \calK
+  \times \calX \to [m]$. }\label{fig:prf}
 \end{figure}
@@
 
-The classical FP requirement considers only non-adaptive (and information-theoretic) adversaries, and $D$ is one such adversary simulating $\game{5}(A)$ as closely as possible, whereas $D'$ mimics $D$ for $r=1$.
+\tsnote{This proof jumps around too much.  The games should be
+  addressed in order, as much as possible.}  
+The classical FP requirement considers only non-adaptive (and information-theoretic) adversaries, and~$D$ is one such adversary simulating $\game{5}(A)$ as closely as possible, whereas $D'$ mimics $D$ for $r=1$.
 $D'$ outputs a FP as in a classic Bloom filter and its FP-error is upperbounded by $[(1-e^{-kn/m})^k +O(1/n)]$ \cite{KirschMitzenmacher}.
@@
 \noindent
-From \Cref{fig:AGame3}, it is evident that
+From \Cref{fig:AGame3}, it is evident that \tsnote{Where is the
+  set~$S$ in $D$ and $D'$?  Make sure to give it to~$A$.  Why is this
+  extra set~$\mathcal{Y}$ needed?}
 \begin{align}
@@
 \end{align}
+\tsnote{How does the second line follow?  You're claiming independence
+  somehow, but you haven't justified it.}
 \noindent

### 2016-08-02 Theorem2_FP.tex
comments on theorem 2

@@
 
-\fixme{Clean up to match style, language and typesetting (macros,
-  especially) of previous theorem.}
+Let $B_{\mathrm{ds}}=(\Hash,\Rep,\Qry)$ be the hash-based filter defined as earlier, except the hash functions are defined as $h_j(x) = \FK, \, j \in [1,k]$.
+Informally, the following result shows, if~$F$ is PRF secure and the filter has low FP-error in the non-adaptive setting, then $B_{\mathrm{ds}}$ is secure against adaptive FP-finding adversaries.
 
-Let $B_{\mathrm{ds}}=(\Hash,\Rep,\Qry)$ be the hash-based filter defined as earlier, except the hash functions are defined as $h_j(x) = \FK, \, j \in [1,k]$.
-Informally, the following result shows, if F is PRF secure and the filter has low FP-error in the non-adaptive setting, then $B_{\mathrm{ds}}$ is secure against adaptive FP-finding adversaries.
-
+\tsnote{Clean up so it looks like the previous theorem.}
 \begin{theorem}\label{thm2}
@@
 
+\tsnote{I don't see why this is necessary.  Doesn't it follow from the
+standard bounds on Bloom filters (go look them up and adjust the
+theorem accordingly) which assume that the hash functions are random
+functions?  Whatever argument you use in Theorem 1 to justify
+independence, i.e. turning one non-adaptive FP into~$r$ non-adaptive
+FPs, should apply here, too.}
 \acnote{I think we should give a proof of the non-adaptive FP-error bound $(1-e^{-kn/m})^k + O(1/n) $.

### 2016-08-02 Theorem2_FP.tex
comments on theorem 2

@@
 independence, i.e. turning one non-adaptive FP into~$r$ non-adaptive
-FPs, should apply here, too.}
+FPs, should apply here, too.  You don't need to understand the KM
+results deeply for this argument, by the way.  You just need to
+understand why you get independence, i.e. why it is that, after the
+set~$S$ has been hashed (hence the bits in~$M$ are set), then the
+probabilities that distinct $x_1,\ldots,x_r$ are each FPs are
+independent.  This really is pretty immediate from the fact that
+$\rho_1,\rho_2$ are random functions and the $x_i$ are distinct.}
+\tsnote{I guess if you want, you could give a 1-to-$r$ lemma for the hash
+  functions (with random functions $\rho1,\rho_2$ used in Theorem 1, prove it, and use that lemma in the
+  proof of Theorem 1.  Then do the parallel thing here, for Theorem 2.}
 \acnote{I think we should give a proof of the non-adaptive FP-error bound $(1-e^{-kn/m})^k + O(1/n) $.

### 2016-08-03 notions.tex
comment on syntax, output of Rep

@@
 One can also consider the orthogonal notion of privacy for a set-representation.
-\jnote{Actually, I am now unsure what the right way to define it is. It seems natural
-to give the attacker $\aux$. But if we give them $\aux$ and $M$ then they have everything.
-If $S$ has high min-entropy (element-wise), then it might still be
-possible to have security here.}\tsnote{I think we will always bump up
-against the (element-wise) min-entropy of the distribution over~$S$,
-at least in the ``one-wayness'' style definition that I had been imagining. }
+%\jnote{Actually, I am now unsure what the right way to define it is. It seems natural
+%to give the attacker $\aux$. But if we give them $\aux$ and $M$ then they have everything.
+%If $S$ has high min-entropy (element-wise), then it might still be
+%possible to have security here.}\tsnote{I think we will always bump up
+%against the (element-wise) min-entropy of the distribution over~$S$,
+%at least in the ``one-wayness'' style definition that I had been imagining. }
 There are several possible definitions:
@@
 
-\medskip
-\oracle{$\RepOracle(S_0,S_1)$}\\
-if $\mathrm{used}=\true$ then Return $\bot$\\
-%if $|S_0|\neq|S_1|$ then \\
-%\nudge Ret $\bot$\\
-$S_0,S_1 \getsr \distr{\calS}{}$\\
-$\mathrm{used}=\true$\\
-$(M,\aux) \getsr \Rep(S_b)$\\
-Return $(S_0,S_1,\aux)$\\
+%\medskip
+%\oracle{$\RepOracle(S_0,S_1)$}\\
+%f $\mathrm{used}=\true$ then Return $\bot$\\
+%%if $|S_0|\neq|S_1|$ then \\
+%%\nudge Ret $\bot$\\
+%$S_0,S_1 \getsr \distr{\calS}{}$\\
+%$\mathrm{used}=\true$\\
+%$(M,\aux) \getsr \Rep(S_b)$\\
+%Return $(S_0,S_1,\aux)$\\
 
@@
   is hidden from the adversary. {\bf Right:} An
-  ``indistinguishability'' style notion. (Still playing... ignore unused oracles)} 
+  ``indistinguishability'' style notion. (Still playing...)} 
 \label{fig:privacy}

### 2016-08-03 syntax.tex
cheers
comment on syntax, output of Rep

@@
 \end{definition}
-
+\tsnote{I'm now leaning towards having $\Rep$ output~$M$ and explicit pubic/private auxillary data.
+Pushing secrets into~$M$ makes it more difficult to capture (for example) the Neidermeier et al.\ attacks in our privacy notions; see Figure~\ref{fig:privacy}.
+In those attacks, the adversary would get the bitarray (which one naturally thinks of as~$M$) but not the secret keys for the PRFs/hash functions.
+You could say that the bitarray is put in $\aux$ and that~$M$ \emph{only} contains the secret keys, but this is unnatural.}
 All of the data structures that we will consider have the property that~$|M|$ does not depend on the coins of~$\Rep$.
@@
 where the maximum is over $S \in \mathcal{S}$ and $q \in \mathcal{Q}$.  
-
+%
 Relatedly, it has \emph{error-rate} $\tilde{\epsilon}$ if
@@
 randomness. \tsnote{Not sure if there's more to say in this section, or if what's here is already too much.}
+
 \heading{Set-multiplicity Data Structures. }

### 2016-08-03 notions.tex
messing with privacy notions again

@@
 Return 0\\
+
+\medskip
+\experimentv{$\ExpPrivSS{\setprim,\distr{\calS}{}}{A}$}\\
+$S \getsr \distr{\calS}{}$\\
+$(M,\aux) \getsr \Rep(S)$\\
+$f \getsr A(M,\aux)$\\
+$S' \getsr \distr{\calS}{}$\\
+if $f(S) \neq f(S')$ then\\
+\nudge Return 1\\
+Return 0\\
 }
@@
   is hidden from the adversary. {\bf Right:} An
-  ``indistinguishability'' style notion. (Still playing...)} 
+  ``indistinguishability'' style notion and a semantic-security style notion. (Still playing...)} 
 \label{fig:privacy}
@@
 \subsection{Relationships Among Notions}
-If we allow for trivial schemes, e.g.
-$M=S$, then correctness and the stronger version of one-wayness privacy (Priv) are clearly orthogonal.\tsnote{In general, it isn't clear how to reduce correctness to the Priv notion.
-In the correctness experiment, you get~$(S,\aux)$ but not~$M$; whereas in the Priv-notion, the adversary expects~$(M,\aux)$ as input.
-Unless the coins of Rep are effectively leaked in~$\aux$, you can't reliably produce~$M$ given~$(S,\aux)$.}
+If we allow for trivial schemes, e.g. $M=S$, then correctness and the stronger version of one-wayness privacy (Priv) are clearly orthogonal.
+\tsnote{My $M=S\setminus\{x\}$ for a random $x \in S$ construction is less trivial (it compresses), but also serves to separate correctness from Priv.}
+\tsnote{In general, it isn't clear how to reduce
+correctness to the Priv notion.  In the correctness experiment, you
+  get~$(S,\aux)$ but not~$M$; whereas in the Priv-notion, the
+  adversary expects~$(M,\aux)$ as input.  Unless the coins of Rep are
+  effectively leaked in~$\aux$, you can't reliably produce~$M$
+  given~$(S,\aux)$.} 
 Curiously, $M=S$ does seem to be both correct and private (up to the element-wise min-entropy of~$S$) in the weaker version of one-wayness privacy (wPriv).

### 2016-08-05 syntax.tex
cheers
changing syntax so that Rep returns public and private aux info

@@
 \section{(Set-multiplicity) Data Structures}
-\def\pub{{\sf pub}}
-\def\aux{{\sf aux}}
 
@@
 \item $\mathcal{Q}=\{q \colon \mathcal{S} \to \Gamma\}$ is a set of supported \emph{queries}
-\item $\Rep \colon \mathcal{S} \to \Sigma^* \times \bits^*$ is a randomized \emph{representation algorithm}, taking as input $S \in \mathcal{S}$, and outputting a \emph{representation} $M \in \Sigma^*$ and some \emph{auxilliary information} $\aux \in \bits^*$
-\item $\Qry\colon \Sigma^* \times \bits^* \times \calQ \to \Gamma$ is a deterministic \emph{query-evaluation} algorithm, taking as input $M, \aux, q$, and returns \emph{answer} $a \in \Gamma$.
+\item $\Rep \colon \mathcal{S} \to \Sigma^* \times \bits^* \times \bits^*$ is a randomized \emph{representation algorithm}, taking as input $S \in \mathcal{S}$, and outputting a \emph{representation} $M \in \Sigma^*$, \emph{private side-information} $\privaux \in \bits^*$, and \emph{public side-information} $\pubaux \in \bits^*$
+\item $\Qry\colon \Sigma^* \times \bits^* \times \calQ \to \Gamma$ is a deterministic \emph{query-evaluation} algorithm, taking as input $M, \privaux, q$, and returns \emph{answer} $a \in \Gamma$.
 \end{itemize}
@@
 \end{definition}
-\tsnote{I'm now leaning towards having $\Rep$ output~$M$ and explicit pubic/private auxillary data.
+\tsnote{I implemented this change.}\tsnote{I'm now leaning towards having $\Rep$ output~$M$ and explicit pubic/private auxillary data.
 Pushing secrets into~$M$ makes it more difficult to capture (for example) the Neidermeier et al.\ attacks in our privacy notions; see Figure~\ref{fig:privacy}.
@@
 Fix a data structure $\setprim=(\Sigma,\Gamma,\calS,\calQ,\Rep, \Qry)$.
-Let $\mathrm{Err}(S,q,M,\aux)$ be a predicate that is true iff $\Qry(M, \aux, q) \neq q(S)$.  Then a data structure
+Let $\mathrm{Err}(S,q,M,\privaux)$ be a predicate that is true iff $\Qry(M, \privaux, q) \neq q(S)$.  Then a data structure
 has \emph{error-probability} $\epsilon$ if
-$\max_{S,q}\Pr[(M,\aux) \getsr \Rep(S) : \mathrm{Err}(S,q,M,\aux)=1 ] \leq \epsilon$
+$\max_{S,q}\Pr[(M,\pubaux,\privaux) \getsr \Rep(S) : \mathrm{Err}(S,q,M,\privaux)=1 ] \leq \epsilon$
 where the maximum is over $S \in \mathcal{S}$ and $q \in \mathcal{Q}$.  
@@
 Relatedly, it has \emph{error-rate} $\tilde{\epsilon}$ if
-$\max_{S}\Pr[(M,\aux) \getsr \Rep(S);\, q \getsr \calQ : \mathrm{Err}(S,q,M,\aux)=1] \leq \tilde{\epsilon}$.
+$\max_{S}\Pr[(M,\pubaux,\privaux) \getsr \Rep(S);\, q \getsr \calQ : \mathrm{Err}(S,q,M,\privaux)=1] \leq \tilde{\epsilon}$.
 \hfill\dqed
@@
 %Actually, it seems worthwhile to formalize this. 
-Let $\mathrm{Err}_i$ be a random variable indicating the event $\Qry(M,\aux,q_i)\neq q_i(S)$.  
+Let $\mathrm{Err}_i$ be a random variable indicating the event $\Qry(M,\privaux,q_i)\neq q_i(S)$.  
 The $(1-\epsilon)$-correctness of~$\Pi$ guarantees that the probability that $\mathrm{Err}_i=1$ is at most~$\epsilon$, 
@@
 For the queries, let $\calQ = \{q_x\colon \calS \to \bits \,|\, \forall x \in \univ\}$ where $\forall S \in \calS$ the predicate $q_x(S)=1 \Leftrightarrow x \in S$.
-Let $\Rep(S)$ pick a random element~$s \in S$, and return $M = S \setminus \{s\}$ and $\aux = \emptystring$.
-To respond to queries, let~$\Qry(M,\aux,q_x)=1$ iff $x \in M$.
+Let $\Rep(S)$ pick a random element~$s \in S$, and return $M = S \setminus \{s\}$ and $\privaux = \emptystring$.
+To respond to queries, let~$\Qry(M,\privaux,q_x)=1$ iff $x \in M$.
 It is easy to see that this scheme is $1/n$-correct; for any fixed~$S$, there are exactly~$n$ queries~$q_x$ that have probability~$1/n$  (over the coins of~$\Rep$) of causing a correctness error, and the remaining $|\univ|-n$ queries have probability zero of causing an error.
@@
 
-%Our treatment of $M,\aux$ is not symmetric, since we only count $M$ against the size
+%Our treatment of $M,\privaux$ is not symmetric, since we only count $M$ against the size
 %of the set-representation. When we define security
-%we may give the attacker $\aux$ but not~$M$, and in that case the set-representation cannot
-%trivially make everything part of~$\aux$. 
+%we may give the attacker $\privaux$ but not~$M$, and in that case the set-representation cannot
+%trivially make everything part of~$\privaux$. 
 %\tsnote{Encoding secrets into~$M$ may cause some headaches in the security definitions; we'll see. }
@@
 Define algorithm~$\Rep$, with functions $k=k(|S|), m=m(|S|)$ and a description of a hash function family~$\mathcal{H}=\{h \colon \univ \to \{1,2,\ldots,m\}\}$ hardwired into it, to sample hash functions $h_1, \ldots, h_k$ from~$\mathcal{H}$ and then compute an $m$-bit array in the standard way.
-It sets $\aux = (h_1, \ldots, h_k)$ and $M$ to be the bit array, and returns these.
-The algorithm~$\Qry$ is defined so that, on input $(M,\aux,q_x)$, it returns the minimum of the values (either 0 or 1) held at $M[h_1(x)],\ldots,M[h_k(x)]$.
+It sets $\privaux=\pubaux = (h_1, \ldots, h_k)$ and~$M$ to be the bit array, and returns these.
+The algorithm~$\Qry$ is defined so that, on input $(M,\privaux,q_x)$, it returns the minimum of the values (either 0 or 1) held at $M[h_1(x)],\ldots,M[h_k(x)]$.
 We note that, while our error-probability and error-rate do not distinguish among ``types'' of errors, they also do not preclude instantiations (like the classical Bloom filter) that admit only one type of error, e.g.
@@
 
-As a simple extension, consider $\Sigma=\mathbb{N}$ and a scheme that stores counters at each position in an array.
+As a simple extension, consider $\Sigma=\mathbb{N}$ and modify the basic Bloom filter so that it that stores counters, rather than bits, at each position in an array.
 In particular, for each~$x \in S$ the $\Rep$~algorithm increments the counters stored at positions $h_1(x), h_2(x), \ldots, h_k(x)$, returns the final array of counters as~$M$.
@@
 
-A Bloom filter with secret hash functions is captured by appending to~$M$ appropriate encodings of $h_1,h_2,\ldots,h_k$, and setting $\aux=\emptystring$.
-Related constructions \tsnote{Name them?} that use a secret key~$K$, but not for hashing, are captured by appending~$K$ to~$M$ and setting $\aux=((h_1, \ldots, h_k)$.
+A Bloom filter with secret hash functions is captured by setting $\privaux=(h_1,h_2,\ldots,h_k)$, and setting $\pubaux=\emptystring$.
+Related constructions \tsnote{Name them?} that use a secret key~$K$, but not for hashing, are captured setting $\privaux=K, \pubaux=((h_1, \ldots, h_k)$.
 

### 2016-08-05 notions.tex
cheers

@@
 set-representations.
-The first two have the flavor of a one-wayness game, in which the adversary is given the auxiliary information~$\aux$ and, either the representation~$M$ or the abillity to call an oracle that evaluates $\Qry(M,\aux,q)$ on queries~$q$ of its choosing.
+The first two have the flavor of a one-wayness game, in which the adversary is given the auxiliary information~$\pubaux$ and, either the representation~$M$ or the abillity to call an oracle that evaluates $\Qry(M,\privaux,q)$ on queries~$q$ of its choosing.
 At the end of this game, the adversary must output some point in the set represented by~$M$.
 In the second privacy notion, the adversary presents two sets~$S_0$ and $S_1$ (of equal size) and a representation~$M$ is created for one of these two.
-Then the adversary is given $\aux$ and oracle access to $\Qry(M,\aux,q)$, and it must decide which set~$M$ represents.
+Then the adversary is given $\pubaux$ and oracle access to $\Qry(M,\privaux,q)$, and it must decide which set~$M$ represents.
 
@@
 $\mathcal{S}$ associated to~$\Pi$, and then
-$\Rep(S)$ is run to generate $(M,\aux)$.
+$\Rep(S)$ is run to generate $(M,\pubaux,\privaux)$.
 %(Unless stated otherwise, we assume security holds for all distributions and thus for all sets $S$.)
-Adversary~$A$ is given~$\calS$ and $\aux$~as input; it is
+Adversary~$A$ is given~$\calS$ and $\pubaux$~as input; it is
 provided an oracle~$\TestOracle$ that, on input a query~$q \in \calQ$,
-computes (and returns) the result of $\Qry(M,\aux,q)$, and increments
+computes (and returns) the result of $\Qry(M,\privaux,q)$, and increments
 a counter if this result is in error.  The adversary wins if it
@@
 $\mathrm{err}\gets 0$\\
-$(M,\aux) \getsr \Rep(S)$\\
-$z \getsr A^{\TestOracle}(S,\aux)$\\
+$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
+$z \getsr A^{\TestOracle}(S,\pubaux)$\\
 if $\mathrm{err} < r$ then Return 0\\
@@
 \oracle{$\TestOracle(q)$}\\
-$a \gets \Qry(M,\aux,q)$\\
+$a \gets \Qry(M,\privaux,q)$\\
 if $a \neq q(S)$ then \\
@@
 \item A ``one-wayness'' definition where $S$ has high min-entropy (element-wise), and we
-give the attacker $\aux$ and either $M$ or oracle access to $\Qry$. The attacker
-succeeds if it can output an element in~$S$.
-\tsnote{Neither of these seems to capture the Neidermeier et al.
+give the attacker $\pubaux$ and either $M$ or oracle access to $\Qry$. The attacker
+succeeds if it can output an element in~$S$. \tsnote{fixed by
+  changing syntax.}\tsnote{Neither of these seems to capture the Neidermeier et al.
 attack.
@@
 \item An ``indistinguishability'' definition where either $S_0$ or $S_1$ is used, and the attacker
-must determine which. Here the attacker is given $\aux$ but only oracle access to $\Qry$, and
+must determine which. Here the attacker is given $\pubaux$ but only oracle access to $\Qry$, and
 it is disallowed from asking any query $q$ for which $q(S_0) \neq
@@
 \tsnote{Is this the right kind of indistinguishability anyway?
-This current notion says, in effect, that $S_0$ and $S_1$ are indistinguishable \emph{with respect to the allowed queries} (assuming that $\aux$ doesn't stupidly leak information.)  But why not try to formalize the intution that a representation~$M$ and the public info~$\aux$ tell you nothing (non-trivial) about the set being represented, period?
+This current notion says, in effect, that $S_0$ and $S_1$ are indistinguishable \emph{with respect to the allowed queries} (assuming that $\pubaux$ doesn't stupidly leak information.)  But why not try to formalize the intution that a representation~$M$ and the public info~$\pubaux$ tell you nothing (non-trivial) about the set being represented, period?
 (Classical BFs, by the way, essentially leak the number of elements in the set by looking at the number of 0-bits in the array.)   That's tricky to define...
@@
 $S \getsr \distr{\calS}{}$\\
-$(M,\aux) \getsr \Rep(S)$\\
-$z \getsr A^{\TestOracle}(\aux)$\\
+$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
+$z \getsr A^{\TestOracle}(\pubaux)$\\
 if $z \in S$ then Return 1\\
@@
 $S \getsr \distr{\calS}{}$\\
-$(M,\aux) \getsr \Rep(S)$\\
-$z \getsr A(M,\aux)$\\
+$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
+$z \getsr A(M,\pubaux)$\\
 if $z \in S$ then Return 1\\
@@
 $S_0,S_1 \getsr \distr{\calS}{}$\\
-$(M,\aux) \getsr \Rep(S_b)$\\
-$b' \getsr A^{\TestOracle}(S_0,S_1,\aux)$\\
+$(M,\pubaux,\privaux) \getsr \Rep(S_b)$\\
+$b' \getsr A^{\TestOracle}(S_0,S_1,\pubaux)$\\
 if $b' = b$ then Return 1\\
@@
 $S \getsr \distr{\calS}{}$\\
-$(M,\aux) \getsr \Rep(S)$\\
-$f \getsr A(M,\aux)$\\
+$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
+$f \getsr A(M,\pubaux)$\\
 $S' \getsr \distr{\calS}{}$\\
@@
 \oracle{$\TestOracle(q)$}\\
-$a \gets \Qry(M,\aux,q)$\\
+$a \gets \Qry(M,\privaux,q)$\\
 Return~$a$\\

### 2016-08-05 syntax.tex
cheers

@@
 A Bloom filter with secret hash functions is captured by setting $\privaux=(h_1,h_2,\ldots,h_k)$, and setting $\pubaux=\emptystring$.
-Related constructions \tsnote{Name them?} that use a secret key~$K$, but not for hashing, are captured setting $\privaux=K, \pubaux=((h_1, \ldots, h_k)$.
+Related constructions \tsnote{Name them?} that use a secret key~$K$, but not for hashing, are captured setting $\privaux=K, \pubaux=(h_1, \ldots, h_k)$.
 

### 2016-08-05 notions.tex
cheers
playing with notions again

@@
 
-\tsnote{Is this the right kind of indistinguishability anyway?
-This current notion says, in effect, that $S_0$ and $S_1$ are indistinguishable \emph{with respect to the allowed queries} (assuming that $\pubaux$ doesn't stupidly leak information.)  But why not try to formalize the intution that a representation~$M$ and the public info~$\pubaux$ tell you nothing (non-trivial) about the set being represented, period?
-(Classical BFs, by the way, essentially leak the number of elements in the set by looking at the number of 0-bits in the array.)   That's tricky to define...
-Also, if you give~$M$ to the adversary, how do you handle the fact that, under our current syntax, $M$~may contain secret keys, etc.?}
+\tsnote{Is this the right kind of indistinguishability anyway?  This
+  current notion says, in effect, that $S_0$ and $S_1$ are
+  indistinguishable \emph{with respect to the allowed queries}
+  (assuming that $\pubaux$ doesn't stupidly leak information.)  But
+  why not try to formalize the intution that a representation~$M$ and
+  the public info~$\pubaux$ tell you nothing (non-trivial) about the
+  set being represented, period?  (Classical BFs, by the way,
+  essentially leak the number of elements in the set by looking at the
+  number of 0-bits in the array.)   That's tricky to define... I'll
+  take a shot at it.}
 %\tsnote{How will the adversary know that a query satisfies
@@
 {
+\experimentv{$\ExpPriv{\setprim,\distr{\calS}{}}{A}$}\\
+$S \getsr \distr{\calS}{}$\\
+$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
+$z \getsr A^{\TestOracle}(M,\pubaux)$\\
+if $z \in S$ then Return 1\\
+Return 0\\
+
+\medskip
 \experimentv{$\ExpWPriv{\setprim,\distr{\calS}{}}{A}$}\\
@@
 Return 0\\
-
-\medskip
-\experimentv{$\ExpPriv{\setprim,\distr{\calS}{}}{A}$}\\
-$S \getsr \distr{\calS}{}$\\
-$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
-$z \getsr A(M,\pubaux)$\\
-if $z \in S$ then Return 1\\
-Return 0\\
 }
@@
 \oracle{$\TestOracle(q)$}\\
-$a \gets \Qry(M,\aux,q)$\\
+$a \gets \Qry(M,\privaux,q)$\\
 Return~$a$
@@
 $(M,\pubaux,\privaux) \getsr \Rep(S_b)$\\
-$b' \getsr A^{\TestOracle}(S_0,S_1,\pubaux)$\\
+$b' \getsr A^{\TestOracle}(M,\pubaux)$\\
 if $b' = b$ then Return 1\\
@@
 \experimentv{$\ExpPrivSS{\setprim,\distr{\calS}{}}{A}$}\\
-$S \getsr \distr{\calS}{}$\\
+$S\getsr \distr{\calS}{}$\\
 $(M,\pubaux,\privaux) \getsr \Rep(S)$\\
-$f \getsr A(M,\pubaux)$\\
+$f \getsr A(M,\pubaux,\privaux)$\\
 $S' \getsr \distr{\calS}{}$\\
@@
 %\oracle{$\RepOracle(S_0,S_1)$}\\
-%f $\mathrm{used}=\true$ then Return $\bot$\\
+%if $\mathrm{used}=\true$ then Return $\bot$\\
 %%if $|S_0|\neq|S_1|$ then \\
@@
 \caption{Privacy notions. {\bf Left:} ``One-wayness'' style
-  definitions. The top is a weaker notion, because the representation
+  definitions. The bottom is a weaker notion, because the representation
   is hidden from the adversary. {\bf Right:} An

### 2016-08-05 notions.tex
writing up text for privacy notions

@@
 \subsection{Notions of Privacy}
-One can also consider the orthogonal notion of privacy for a set-representation.
+One can also consider the orthogonal notion of privacy for a
+set-representation.   There are various ways to formalize privacy, and
+we give some of these in Figure~\ref{fig:privacy}.  
 %\jnote{Actually, I am now unsure what the right way to define it is. It seems natural
@@
 %at least in the ``one-wayness'' style definition that I had been imagining. }
+On the left side of this figure, we give two ``one-wayness''
+definitions, in which the adversary must output an element of the
+set~$S$ represented by~$M$.  The first version (priv) gives the
+adversary~$(M,\pubaux)$ as input; the second (wpriv) gives
+only~$\pubaux$.  The wpriv-notion captures leakage about the elements
+of~$S$ that results from observing the results of allowed queries.
+The stronger priv-notion captures what is jointly leaked, by the
+representation~$M$ and the allowed queries, about set elements.
+
+On the right side of the figure, we give two ``indistinguishability''
+notions of privacy.  The first version (ind-qry) captures more
+generally what~$M$ and the allowed queries leak about the set that is
+represented.  In particular, two sets~$S_0,S_1$ are sampled according
+to distribution~$\distr{\calS}{}$, one of these is picked at random to
+be represented.  The adversary is provided the resulting~$M,\pubaux$
+and allowed to make queries~$q \in \calQ$; it must determine which
+of~$S_0$ or~$S_1$ was actually represented.  We call this notion
+indistinguishabilty (of sets) under a (adaptively chosen) query
+attack.
+%
+The second version is inspired by the semantic security notion for
+encryption schemes, and we refer to it as semantic-security (of sets)
+with respect to the full representation (ss-rep).  In this experiment,
+a set~$\calS$ is sample according to distribution~$\distr{\calS}{}$,
+and the adversary is given the full ouput of running $\Rep(S)$,
+i.e. $(M,\pubaux,\privaux)$.  The adversary must output a
+function~$f\colon\calS \to \bits^*$ such that $f(S)$ differs from
+$f(S')$ for a set~$S'$ that is subsequently sampled according to~$\distr{\calS}{}$.
+
+\if{0}
 There are several possible definitions:
@@
 \end{enumerate}
+\fi
 

### 2016-08-05 notions.tex
cheers

@@
 \subsection{Relationships Among Notions}
+
+\heading{Privacy notions. }
+Clearly we have priv $\Rightarrow$ wpriv, tightly and by a simple
+reduction.  We should be able to show
+\begin{itemize}
+\item ss-rep $\Rightarrow$ ind-qry
+\item ind-qry $\Rightarrow$ ss-rep \tsnote{Not sure about this separation...}
+\item ind-qry $\Rightarrow$ priv \emph{for set-multiplicity data
+    structures} \tsnote{but probably not in general}
+\item \{w\}priv $\not\Rightarrow$ ind-qry
+\item wpriv $\not\Rightarrow$ priv \tsnote{$M=S$, or my
+    $M=S\setminus \{x\}$ for a random $x\in S$, if you want something
+    a bit less trivial. I'm sure there are more natural schemes that
+    will separate, too.}
+\end{itemize}
+
+\heading{Correctness vs.\ Privacy. }
 If we allow for trivial schemes, e.g. $M=S$, then correctness and the stronger version of one-wayness privacy (Priv) are clearly orthogonal.

### 2016-08-09 Theorem1_FP.tex
edits to theorem 1 and proof
Proof 1

@@
+\acnote{I am moving comments to end of the proof in tex file and commenting them as the labels are getting mangled}
 \heading{Linear-PRF construction. }
@@
 Let $B_{\mathrm{lin}}=(\Hash,\Rep,\Qry)$ be defined as follows.
-Fix non-empty set ~$\univ$ and integers $k,m,n>0$.
+Fix non-empty sets ~$\univ$, $\calK$ and integers $k,m,n>0$.
 Let $F\colon\mathcal{K} \times \univ \to [m]$ be a function family.
@@
 
-$\game{1}(A)$ and $\game{2}(A)$ attack 2 different filters with hash functions 
-$h_j(x) = ( F_{K_0}(x) + j\cdot \rho_2(x)) \bmod m$ and $h_j(x) = ( \rho_1(x) + j \cdot \rho_2(x)) \bmod m$, respectively.
-Here, $\rho_1$ and $\rho_2$ are random functions sampled from $\Func{\univ,[m]}$. \\
-
-\tsnote{I'll need to rewrite all below here.  The current text is too hand-wavy and fast.}
-In $\game{3}(A)$, the hash functions are linear combinations of two random points
-in $[m]$, similar to $\game{2}(A)$. 
-\tsnote{`In transitioning from $\game{2}$ to $\game{3}$ we
-  replace the all-at-once sampling of random functions~$\rho_1,\rho_2$
-with lazying sampling in the $\HashOracle$, which is the only place
-these random functions are used.  This does not alter the input-output
-behavior of the $\HashOracle$.''  Why do we do this?}
-We also sample $r$~distinct random integers are chosen \tsnote{why?
-  What are we setting up?} and the $\QryOracle$ oracle sets a $\bad$
-flag if query response for any of the $r$ queries is false or any of
-the $q-r$ queries return true. \tsnote{We
-  set $\bad$ to $\true$ if the queries indexed by the
-  set~$\mathcal{I}$ fail to be false-positives, or if any of the
-  remaining queries \emph{are} false-positives.  Again, why are we
-  doing this?  }
-
-So, both have equal probability of returning 1.  \tsnote{``The value
-  of~$\bad$ does not affect the value returned by~$\game{3}$. Thus we
-  conclude that...'' }
+$\game{1}(A)$ and $\game{2}(A)$ attack 2 different filters.
+In $\game{1}(A)$, $F_{K_1}$ is replaced by a random function, whereas in $\game{2}(A)$, both $F_{K_0}$ and $F_{K_1}$ are replaced by random functions as shown below.
+Here, $\rho_1$ and $\rho_2$ are random functions sampled from $\Func{\univ,[m]}$.
+\begin{align*}
+\game{1}(A)\, : \, h_j(x) &= ( F_{K_0}(x) + j\cdot \rho_2(x)) \bmod m\\
+\game{2}(A)\, : \, h_j(x) &= ( \rho_1(x) + j \cdot \rho_2(x)) \bmod m
+\end{align*}
+In $\game{3}(A)$, we replace the hash functions of $\HashOracle$ (in $\game{2}(A)$) with lazy sampling of elements from $[m]$.
+This brings us close to the classic Bloom filter's soundness condition, as now the hash indices sampled during a query are random points in $[m]$, and are independent of the hash indices used by the $\Rep$.
+As mentioned in \acnote{ref :{sec:intro}}, the soundness condition of a classic bloom filter is given as  $\Prob{h_1,h_2,\ldots,h_k \getsr \mathrm{Func}(\univ,[m])\colon M[h_1(y)]=1 \wedge \cdots \wedge M[h_k(y)]=1} \leq \epsilon$.
+Also, the $\QryOracle$ now sets $\bad$ to $\true$ if the queries indexed by the set $\mathcal{I}$ fail to be false-positives, or if any of the remaining queries are false-positives.
+It can be observed that the $\bad$ flag has no impact on the output of the $\QryOracle$, nor does it affect  the value returned by~$\game{3}$.
+Rather it lays foundation for $\game{4}(A)$.
+From these observations,
+\begin{align}
+\Prob{\game{3}(A)=1 \wedge \neg\bad} &= \Prob{\game{3}(A)=1} \Prob{\game{3}(A) : \neg\bad}\label{eq:1} \\
+\Prob{\game{2}(A)=1} &= \Prob{\game{3}(A)=1}\label{eq:2}
+\end{align}
+$\game{4}(A)$ is identical to $\game{3}(A)$ except it returns 0 if $\bad$ is set to true.
+So, by construction $\game{4}(A)$ and $\game{3}(A)$ are identical-untill-$\bad$.
+In addition, $\game{4}(A)$ returning 1 implies that bad is never set to true.
+Therefore,
 \begin{equation}
-\Prob{\game{2}(A)=1} = \Prob{\game{3}(A)=1}\label{eq:3}
+\Prob{\game{4}(A)=1} = \Prob{\game{3}(A)=1 \wedge \neg\bad}\label{eq:3}
 \end{equation}
-
-The probability of winning  $\game{3}(A)$ is same as $\game{4}(A)$,
-except $\game{4}(A)$ outputs 0 if $\bad$ flag is
-set.\tsnote{I don't understand this sentence.  What you mean to say is
-  something like this: ``By construction, $\game{3}$ and $\game{4}$
-  are identical-until-bad.  In addition, $\game{4}$ returning 1
-  implies that $\bad$ is never set to~$\true$.  From these two
-  observations, we can conclude that $\Prob{\game{4}(A)=1} =
-  \Prob{\game{3}(A)=1 \wedge \neg\bad}$.'' }
-In short, $\game{3}(A)$ and $\game{4}(A)$ are identical untill $\bad
-=true$.  On the  other hand, $\game{5}(A)$ simulates the non-adaptive
-counterpart of $\game{4}(A)$.  \tsnote{This statement is unjustified.
-(See my comments below.) Actually it's meaningless, because games are
-not not adaptive or non-adaptive.  Adversaries are.}
-
-\tsnote{You need to just justify these next lines better. For example,
-why is the event $\neg \bad$ independent of the event $\game{3}(A)=1$?}
+From \Cref{eq:1,eq:2,eq:3}
+\begin{equation}
+\Prob{\game{4}(A)=1} =  \Prob{\game{2}(A)=1} \Prob{\game{3}(A) : \neg\bad} \label{eq:4}
+\end{equation}
+Since, probability of any set of $r$ queries indexed by set $\calI$ to be not false positives are equally likely to any other set sampled from $[\{1,2,\ldots,q\}]^r$, we have
+\begin{equation}
+\Prob{\game{3}(A) : \neg\bad} = \frac{1}{\dbinom{q}{r}}\label{eq:555}
+\end{equation}
+From \Cref{eq:4,eq:555}
+\begin{equation}
+\Prob{\game{4}(A)=1} = \Prob{\game{2}(A)=1}\frac{1}{\dbinom{q}{r}}\label{eq:6}
+\end{equation}
+In $\game{4}(A)$, $A$ wins $\ExpFPSecHash{B_{\mathrm{lin}},r}{A}$ after finding $r$ false positives indexed by $\calI$.
+Therefore, without loss of generality, it can be assumed that $A$ halts just after it finds the $r$ false positives, and outputs $\calZ$(of size $r$).
+Further, we can also assume that every point in $\calZ$ has already been queried to $\QryOracle$.
+This assumption can be  easily enforced (in the original security definitions) by counting as part of the number of queries~$q$, the points in $\mathcal{Z}$.
+Hence, if $\game{4}(A)=1$, there is a non-adaptive adversary~$D$ that finds~$r$ false positives against $\tilde{B}_{\mathrm{lin}}$, which is $B_{\mathrm{lin}}$ but with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$, respectively as shown in \Cref{fig:D}.
+So,
 \begin{align}
-\nonumber \Prob{\game{4}(A)=1} &= \Prob{\game{3}(A)=1 \wedge \neg\bad}\\ 
-\nonumber & = \Prob{\game{3}(A)=1}\Prob{\game{3}(A):\,\neg\bad}\\
-& = \Prob{\game{3}(A)=1}\frac{1}{\dbinom{q}{r}}\label{eq:3a}\\
-\Prob{\game{5}(A)=1} &= \Prob{\game{4}(A)=1}\label{eq:3b}
+\nonumber \Prob{\ExpFPSecHash{\tilde{B}_{\mathrm{lin}},r}{D} = 1} &= \Prob{\game{4}(A) = 1}\\
+\mathrm{or} \nudge \AdvFPSecHash{\tilde{B}_{\mathrm{lin}},r}{D} &= \Prob{\game{4}(A) = 1}\label{eq:7}
 \end{align}
-\tsnote{How does the last line follow from the games?  I mean, it
-  isn't obvious to me that your $\game{5}$ is equivalent to $\game{4}$.  The
-  latter looks at the adversary's output~$\mathcal{Z}$, but the former
-ignores this and looks at this new set~$\mathcal{Y}$.  Why are these
-equivalent with respect to the events $\game{4}(A)=1$ and
-$\game{5}(A)=1$?  Just looking at the $\QryOracle$ in the two games,
-it appears that they have pretty different behaviors. I mean, in
-$\game{4}$ the oracle still returns what it is supposed to, even if
-$\bad\gets\true$.  But in $\game{5}$ the oracle returns fixed values,
-no matter if the query is or is not a FP.  You have to explain why
-these changes are okay.  Also, why is this new set~$\mathcal{Y}$
-necessary?  }
-\tsnote{The point that needs to be made about the relationship between
-  $\game{4}$ and $\game{5}$ is this.  $\game{4}$ returns 1 only if
-  $\bad=\false$ at the end of the game.  In turn, this implies that
-  the game managed to ``guess'', prior to the execution of~$A$, which
-  of its queries would result in false-positives.  (By the way, we
-  need to state an assumption here: that~$A$ halts and
-  outputs~$\mathcal{Z}$ (of size~$r$) as soon as its queries
-  reveal~$r$ false positives.  This is without loss of generality; say
-why.  I guess you also need to assume that every point in
-the~$\mathcal{Z}$ output by~$A$ has already been queried
-to~$\QryOracle$.  Strictly speaking this is not without loss of
-generality, but would be easily enforced (in the original
-  security definitions) by counting as part of the number of
-  queries~$q$ the points in~$\mathcal{Z}$.  Without these assumptions,
-things don't quite work.)  Hence, if $\game{4}(A)=1$ there is a
-non-adaptive adversary~$D$ that finds~$r$ false positives against
-$\tilde{B}_{\mathrm{lin}}$, which is $B_{\mathrm{lin}}$ but
-with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$,
-respectively.  (Note, this is \emph{not} the adversary~$D$ that you
-give, because the one you give simulates things that it would be given
-in the FP game, e.g. the set~$S$.)  That is, $\Prob{\game{4}(A)=1} =
-\AdvFPSecHash{\tilde{B}_{\mathrm{lin}},r}{D}$.  (So I guess there's no
-need for $\game{5}$.)  Now argue that this advantage is upperbounded
-by what the theorem claims, i.e. the KM bound raised to~$r$.}
-
-From  \Cref{eq:3,eq:3a,eq:3b}:
+Let $\calF$ be the event of getting a false positive in a classic Bloom filter.
+Since, $D$ is a non-adaptive adversary, for $r=1$, it exactly simulates the classic Bloom filter game.
+Also, as the elements of $\calI$ are randomly sampled from $[\{1,2,\ldots,q\}]^r$, the event of any query indexed by $\calI$ being a false positive is mutually independent of any other query indexed by the same set.
+Hence,
+\begin{align}
+\nonumber \AdvFPSecHash{\tilde{B}_{\mathrm{lin}},r}{D} &= [\Prob{\calF}]^r\\
+&\leq \left( (1-e^{-kn/m})^k + O(1/n) \right)^r \label{eq:8}
+\end{align}
+Here, $\left( (1-e^{-kn/m})^k + O(1/n) \right)$ is the upper bound of $\calF$, as given by Kirsch et. al.\ref{KM}.
+From \Cref{eq:7,eq:8},
 \begin{equation}
-\Prob{\game{5}(A)=1} = \Prob{\game{2}(A)=1}\frac{1}{\dbinom{q}{r}}\label{eq:3c}
+\Prob{\game{4}(A)=1} \leq  \left( (1-e^{-kn/m})^k + O(1/n) \right)^r \label{eq:9}
 \end{equation}
-
-%\tsnote{The PRF experiment has not be defined yet, so strictly
-% speaking these claims make no sense. }
-The PRF game of $F$ is shown in \Cref{fig:prf}. Let prf-adversaries
-$B_1, B_2$ be as shown in \Cref{fig:BGame1}. \tsnote{Why is $B_2$
-  sampling a random function?  This ruins the tightness of security
-  bound w.r.t.\ resources.  Please have~$B_2$ carry out lazy sampling
-  of~$\rho_2$.  Also, please use the macro for Func.}  By
+Using \Cref{eq:6} in \Cref{eq:9}
+\begin{align}
+\Prob{\game{2}(A)=1}\frac{1}{\dbinom{q}{r}} & \leq  \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\\
+\Prob{\game{2}(A)=1} &\leq \dbinom{q}{r}\left( (1-e^{-kn/m})^k + O(1/n) \right)^r\label{eq:10}
+\end{align}
+The PRF game of $F$ is shown in \Cref{fig:prf}. Let prf-adversaries $B_1, B_2$ be as shown in \Cref{fig:BGame1}.  By
 construction, these simulate $\game{1}(A)$ and $\game{2}(A)$, respectively.
@@
 %\caption{$\Cref{thm1}:\game{5}(A)$ in game playing argument}\label{fig:game5}
-\begin{figure}
-\centering
-\fpage{0.8}
-{
-\hpagess{0.5}{0.4}{
-\underline{$\game{5}(A)$}\\
-$c \gets 0$\\
-$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
-$\calY \gets \emptyset$\\
-$S \getsr \distr{\univ}{n}$\\
-$M \getsr \Rep^{\HashOracle}(\calS)$\\
-$\calZ \getsr A^{\QryOracle}(\calS)$\\
-if $|\calY| < r$ or $\calY \cap \calS \neq \emptyset$ then\\
-\nudge Ret 0\\
-if $\forall y \in \calY,\,\Qry^{\HashOracle}(M,y)=1$ then \\
-\nudge Ret 1\\
-Ret 0
-}
+%\begin{figure}
+%\centering
+%\fpage{0.8}
+%{
+%\hpagess{0.5}{0.4}{
+%\underline{$\game{5}(A)$}\\
+%$c \gets 0$\\
+%$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
+%$\calY \gets \emptyset$\\
+%$S \getsr \distr{\univ}{n}$\\
+%$M \getsr \Rep^{\HashOracle}(\calS)$\\
+%$\calZ \getsr A^{\QryOracle}(\calS)$\\
+%if $|\calY| < r$ or $\calY \cap \calS \neq \emptyset$ then\\
+%\nudge Ret 0\\
+%if $\forall y \in \calY,\,\Qry^{\HashOracle}(M,y)=1$ then \\
+%\nudge Ret 1\\
+%Ret 0
+%}
 %
-{
-\oracle{$\QryOracle(x)$}\\
-$c \gets c+1$\\
-if $c \in \mathcal{I}$ then\\
-\nudge $\calY \gets \calY \cup {x}$\\
-\nudge Ret 1\\
-else\\
-\nudge Ret 0 \\\\
+%{
+%\oracle{$\QryOracle(x)$}\\
+%$c \gets c+1$\\
+%if $c \in \mathcal{I}$ then\\
+%\nudge $\calY \gets \calY \cup {x}$\\
+%\nudge Ret 1\\
+%else\\
+%\nudge Ret 0 \\\\
 %
-\oracle{$\HashOracle(x)$}\\
-$a,b \getsr [m]$\\
-for $i = 1$ to~$k$\\
-\nudge $v_i = a+i \cdot b \bmod m$\\
-Ret $\left(v_1,\ldots,v_k\right)$
-}
-}
-\caption{\Cref{thm1}:$\game{5}(A)$ in game playing argument}\label{fig:game5}
-\end{figure}
+%\oracle{$\HashOracle(x)$}\\
+%$a,b \getsr [m]$\\
+%for $i = 1$ to~$k$\\
+%\nudge $v_i = a+i \cdot b \bmod m$\\
+%Ret $\left(v_1,\ldots,v_k\right)$
+%}
+%}
+%\caption{\Cref{thm1}:$\game{5}(A)$ in game playing argument}\label{fig:game5}
+%\end{figure}
 
@@
 %$d \getsr \bits $\\
-$\rho_2 \getsr Func(\univ, [m])$ \\
+%$\rho_2 \getsr Func(\univ, [m])$ \\
 $S \getsr \distr{\univ}{n}$\\
@@
 %if $d=0$\\
-$\mathrm{Ret} \nudge \calO(x) + i\cdot \rho_2(x)$, for $i\in[1,k]$
+$a \getsr [m]$\\
+if $T[x] \neq \undefined$\\
+\nudge $a \gets T[x]$\\
+$T[x] \gets a$\\
+$\mathrm{Ret} \nudge \calO(x) + i\cdot a$, for $i\in[1,k]$
 }
@@
 
-%\caption{Non-adaptive adversaries simulating $\game{2}(A)$} \label{AGame3}
+%\caption{Non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:D}
 \begin{figure}
 \centering
-\fpage{0.8}{
-\hpagessl{.5}{.4}
+\fpage{0.7}{
+\hpagess{0.55}{0.4}
 {
-$\adversaryv{D^{\HashOracle}}$\\
+$\adversaryv{D^{\QryOracle, \calS}}$\\
 $c \gets 0$\\
 $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
-$\calY, \calZ \gets \emptyset $ \\
 When $A$ asks $\QryOracle(x)$:\\
 \nudge $c \gets c+1$\\
-\nudge if $c \in \mathcal{I}$ then\\
-\nudge \nudge $\calY \gets \calY \cup {x}$\\
-\nudge \nudge Ret~$1$\\
-\nudge else \\
-\nudge  \nudge Ret~$0$\\
-When $A$ halts with output $\calZ'$\\
-\nudge if $|\calZ'|<r \, \mbox{or} \, |\calY| < r$\\
-\nudge \nudge Ret $\emptyset$\\
-\nudge if $\forall y \in \calY,\,\Qry^{\HashOracle}(M,y)=1$ then \\
-\nudge \nudge Ret $\calY$\\
-\nudge Ret $\emptyset$\\\\
+\nudge $r \gets 0$\\
+\nudge if $c \in \mathcal{I}$\\
+\nudge \nudge $r \gets \QryOracle(x)$\\
+\nudge Ret $r$\\
+When $A$ halts with output $\calZ$\\
+\nudge Ret $\calZ$
+}
+{
+\oracle{$\QryOracle(x)$}\\
+ Ret $\Qry^{\HashOracle}(M,x)$\\\\
 %
 \oracle{$\HashOracle(x)$}\\
-$a,b \getsr [m]$\\
 for $i = 1$ to~$k$\\
-\nudge $v_i = a+i \cdot b \bmod m$\\
-Ret $\left(v_1,\ldots,v_k\right)$
-}
-{
-$\adversaryv{D'^{\HashOracle}}$\\
-$c \gets 0$\\
-$\ell \getsr [q]$\\
-%$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
-$\calY \gets \emptyset$\\
-When $A$ asks $\QryOracle(x)$:\\
-$\nudge c \gets c + 1$\\
-\nudge if $c == \ell$\\
-$\nudge$ $\nudge r \gets \Qry^{\HashOracle}(M,x)$\\
-$\nudge$ $\nudge \calY \gets \calY \cup {x}$\\
-\nudge else\\
-$\nudge$ $\nudge r \gets 0$\\
-\nudge Ret $r$\\
-When $A$ halts with output $\calZ'$\\
-\nudge $z \gets \calY$\\
-\nudge if $\Qry^{\HashOracle}(M,z)=1$ then\\
-\nudge \nudge Ret $z$\\
-\nudge else\\
-\nudge \nudge Ret $\lambda$\\\\
-%
-\oracle{$\HashOracle(x)$}\\
-$a,b \getsr [m]$\\
-for $i = 1$ to~$k$\\
-\nudge $v_i = a+i \cdot b \bmod m$\\
+\nudge $v_i = \rho_1(x)+i \cdot \rho_2(x) \bmod m$\\
 Ret $\left(v_1,\ldots,v_k\right)$
@@
 }
-\caption{Non-adaptive adversaries simulating $\game{3}(A)$} \label{fig:AGame3}
+\caption{Non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:D}
 \end{figure}
@@
 \noindent
-From \Cref{eq:m1,eq:m2,eq:m3,eq:m4}, %\acnote{compacted} \tsnote{this can be compacted}
+From \Cref{eq:m1,eq:m2,eq:m3,eq:m4},
 \begin{align}
@@
 \nonumber (2\Prob{\ExpPRF{F}{B_1} = 1} - 1)  &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1}\\
- \AdvPRF{F}{B_1} &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1} \label{eq:1}\\
+ \AdvPRF{F}{B_1} &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1} \label{eq:11}\\
 \nonumber& &\\
@@
 \nonumber (2\Prob{\ExpPRF{F}{B_2} = 1} - 1)  &= \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1}\\
- \AdvPRF{F}{B_2} &= \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1} \label{eq:2a}
+ \AdvPRF{F}{B_2} &= \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1} \label{eq:12}
 \end{align}
@@
 \noindent
-Adding \Cref{eq:1,eq:2a}, we have
+Adding \Cref{eq:11,eq:12}, we have
 \begin{equation}
-\AdvPRF{F}{B_1} +\AdvPRF{F}{B_2} = \Prob{\game{0}(A)=1} - \Prob{\game{2}(A)=1}\label{eq:2}
+\AdvPRF{F}{B_1} +\AdvPRF{F}{B_2} = \Prob{\game{0}(A)=1} - \Prob{\game{2}(A)=1}\label{eq:13}
 \end{equation}
+
+From \Cref{eq:0,eq:10,eq:13} \\
+\begin{align}
+\nonumber \AdvFPSecHash{B_{\mathrm{lin}},r}{A} &- \Prob{\game{2}(A)=1} =  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}   \\
+\nonumber \AdvFPSecHash{B_{\mathrm{lin}},r}{A}  &=  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} + \Prob{\game{2}(A)=1}  \\
+\AdvFPSecHash{B_{\mathrm{lin}},r}{A} &\leq  \AdvPRF{F}{B_1} +
+\AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
+\end{align}
+
+\iffalse
+%Comments
+\tsnote{I'll need to rewrite all below here.  The current text is too hand-wavy and fast.}
+\tsnote{`In transitioning from $\game{2}$ to $\game{3}$ we
+  replace the all-at-once sampling of random functions~$\rho_1,\rho_2$
+with lazying sampling in the $\HashOracle$, which is the only place
+these random functions are used.  This does not alter the input-output
+behavior of the $\HashOracle$.''  Why do we do this?}
+We also sample $r$~distinct random integers are chosen \tsnote{why?
+  What are we setting up?} and the $\QryOracle$ oracle sets a $\bad$
+flag if query response for any of the $r$ queries is false or any of
+the $q-r$ queries return true. \tsnote{We
+  set $\bad$ to $\true$ if the queries indexed by the
+  set~$\mathcal{I}$ fail to be false-positives, or if any of the
+  remaining queries \emph{are} false-positives.  Again, why are we
+  doing this?  }
+\tsnote{How does the last line follow from the games?  I mean, it
+  isn't obvious to me that your $\game{5}$ is equivalent to $\game{4}$.  The
+  latter looks at the adversary's output~$\mathcal{Z}$, but the former
+ignores this and looks at this new set~$\mathcal{Y}$.  Why are these
+equivalent with respect to the events $\game{4}(A)=1$ and
+$\game{5}(A)=1$?  Just looking at the $\QryOracle$ in the two games,
+it appears that they have pretty different behaviors. I mean, in
+$\game{4}$ the oracle still returns what it is supposed to, even if
+$\bad\gets\true$.  But in $\game{5}$ the oracle returns fixed values,
+no matter if the query is or is not a FP.  You have to explain why
+these changes are okay.  Also, why is this new set~$\mathcal{Y}$
+necessary?  }
+\tsnote{The point that needs to be made about the relationship between
+  $\game{4}$ and $\game{5}$ is this.  $\game{4}$ returns 1 only if
+  $\bad=\false$ at the end of the game.  In turn, this implies that
+  the game managed to ``guess'', prior to the execution of~$A$, which
+  of its queries would result in false-positives.  (By the way, we
+  need to state an assumption here: that~$A$ halts and
+  outputs~$\mathcal{Z}$ (of size~$r$) as soon as its queries
+  reveal~$r$ false positives.  This is without loss of generality; say
+why.  I guess you also need to assume that every point in
+the~$\mathcal{Z}$ output by~$A$ has already been queried
+to~$\QryOracle$.  Strictly speaking this is not without loss of
+generality, but would be easily enforced (in the original
+  security definitions) by counting as part of the number of
+  queries~$q$ the points in~$\mathcal{Z}$.  Without these assumptions,
+things don't quite work.)  Hence, if $\game{4}(A)=1$ there is a
+non-adaptive adversary~$D$ that finds~$r$ false positives against
+$\tilde{B}_{\mathrm{lin}}$, which is $B_{\mathrm{lin}}$ but
+with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$,
+respectively.  (Note, this is \emph{not} the adversary~$D$ that you
+give, because the one you give simulates things that it would be given
+in the FP game, e.g. the set~$S$.)  That is, $\Prob{\game{4}(A)=1} =
+\AdvFPSecHash{\tilde{B}_{\mathrm{lin}},r}{D}$.  (So I guess there's no
+need for $\game{5}$.)  Now argue that this advantage is upperbounded
+	by what the theorem claims, i.e. the KM bound raised to~$r$.}
+
+In $\game{3}(A)$, the hash functions are linear combinations of two random points
+in $[m]$, similar to $\game{2}(A)$.
+
+So, both have equal probability of returning 1.  \tsnote{``The value
+  of~$\bad$ does not affect the value returned by~$\game{3}$. Thus we
+  conclude that...'' }
+\begin{equation}
+\Prob{\game{2}(A)=1} = \Prob{\game{3}(A)=1}\label{eq:3}
+\end{equation}
+
+The probability of winning  $\game{3}(A)$ is same as $\game{4}(A)$,
+except $\game{4}(A)$ outputs 0 if $\bad$ flag is
+set.\tsnote{I don't understand this sentence.  What you mean to say is
+  something like this: ``By construction, $\game{3}$ and $\game{4}$
+  are identical-until-bad.  In addition, $\game{4}$ returning 1
+  implies that $\bad$ is never set to~$\true$.  From these two
+  observations, we can conclude that $\Prob{\game{4}(A)=1} =
+  \Prob{\game{3}(A)=1 \wedge \neg\bad}$.'' }
+In short, $\game{3}(A)$ and $\game{4}(A)$ are identical untill $\bad
+=true$.  On the  other hand, $\game{5}(A)$ simulates the non-adaptive
+counterpart of $\game{4}(A)$.  \tsnote{This statement is unjustified.
+(See my comments below.) Actually it's meaningless, because games are
+not not adaptive or non-adaptive.  Adversaries are.}
+
+\tsnote{You need to just justify these next lines better. For example,
+why is the event $\neg \bad$ independent of the event $\game{3}(A)=1$?}
+\begin{align}
+\nonumber \Prob{\game{4}(A)=1} &= \Prob{\game{3}(A)=1 \wedge \neg\bad}\\ 
+\nonumber & = \Prob{\game{3}(A)=1}\Prob{\game{3}(A):\,\neg\bad}\\
+& = \Prob{\game{3}(A)=1}\frac{1}{\dbinom{q}{r}}\label{eq:3a}\\
+\Prob{\game{5}(A)=1} &= \Prob{\game{4}(A)=1}\label{eq:3b}
+\end{align}
+
+\tsnote{Why is $B_2$
+  sampling a random function?  This ruins the tightness of security
+  bound w.r.t.\ resources.  Please have~$B_2$ carry out lazy sampling
+  of~$\rho_2$.  Also, please use the macro for Func.}
 
@@
   set~$S$ in $D$ and $D'$?  Make sure to give it to~$A$.  Why is this
-  extra set~$\mathcal{Y}$ needed?}
+  extra set~$\mathcal{Y}$ needed?  What is the point of~$D'$? }
 \begin{align}
@@
 
-From \Cref{eq:0,eq:2,eq:5} \\
-\begin{align}
-\nonumber \AdvFPSecHash{B_{\mathrm{lin}},r}{A} &- \Prob{\game{2}(A)=1} =  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}   \\
-\nonumber \AdvFPSecHash{B_{\mathrm{lin}},r}{A}  &=  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} + \Prob{\game{2}(A)=1}  \\
-\AdvFPSecHash{B_{\mathrm{lin}},r}{A} &\leq  \AdvPRF{F}{B_1} +
-\AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
-\end{align}
-
+\fi
 \end{proof}

### 2016-08-13 Theorem1_FP.tex
Proofs

@@
 For any adversary~$A$ that makes a total of~$q$ queries to its oracle
-and has time-complexity~$t$,
+and has time-complexity~$O(t)$,
 there exist adversaries~$B_1,B_2$ (explicitly constructed in the proof of this theorem) such that
@@
 \end{align}
-Here, $\left( (1-e^{-kn/m})^k + O(1/n) \right)$ is the upper bound of $\calF$, as given by Kirsch et. al.\ref{KM}.
+Here, $\left( (1-e^{-kn/m})^k + O(1/n) \right)$ is the upper bound of $\calF$, as given by Kirsch et. al.\ref{KM}.\\
 From \Cref{eq:7,eq:8},

### 2016-08-13 Theorem1_FP.tex
further cleaning up of Theorem 1

--- 2016-08-09 Theorem1_FP.tex
@@
 
-$\game{1}(A)$ and $\game{2}(A)$ attack 2 different filters.
  In $\game{1}(A)$, $F_{K_1}$ is replaced by a random function, whereas in $\game{2}(A)$, both $F_{K_0}$ and $F_{K_1}$ are replaced by random functions as shown below.
 Here, $\rho_1$ and $\rho_2$ are random functions sampled from $\Func{\univ,[m]}$.
+%\begin{align*}
+%\game{1}(A)\, : \, h_j(x) &= ( F_{K_0}(x) + j\cdot \rho_2(x)) \bmod m\\
+%\game{2}(A)\, : \, h_j(x) &= ( \rho_1(x) + j \cdot \rho_2(x)) \bmod m
+%\end{align*}
+
+\begin{figure}
+\centering
+\fpage{0.9}{
+\hpagessl{0.5}{0.5}
+{
+$\adversaryv{B_1^{\calO}}$\\
+$K_1 \getsr \calK $\\
+$\calS \getsr \distr{\univ}{n}$\\
+$M \getsr \Rep^{\HashOracle}(\calS)$\\
+When $A$ asks $\QryOracle(x)$:\\
+$\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
+When $A$ halts with output $\calZ'$: \\
+\nudge if $|\calZ'| < r$ or $\calZ' \cap \calS \neq \emptyset$ then \\
+\nudge \nudge Ret 0\\
+\nudge if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
+\nudge \nudge Ret 0\\
+\nudge Ret 1\\\\
+\oracle{$\HashOracle(x)$}\\
+$ \mathrm{Ret} \nudge F_{K_1}(x) + i\cdot \calO(x)$, for $i\in[1,k]$\\
+}
+{
+$\adversaryv{B_2^{\calO}}$\\
+%$d \getsr \bits $\\
+%$\rho_2 \getsr Func(\univ, [m])$ \\
+$S \getsr \distr{\univ}{n}$\\
+$M \getsr \Rep^{\HashOracle}(\calS)$\\
+When $A$ asks $\QryOracle(x)$:\\
+$\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
+When $A$ halts with output $\calZ'$: \\
+\nudge if $|\calZ'| < r$ or $\calZ' \cap \calS \neq \emptyset$ then \\
+\nudge \nudge Ret 0\\
+\nudge if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
+\nudge \nudge Ret 0\\
+\nudge Ret 1\\\\
+\oracle{$\HashOracle(x)$}\\
+%if $d=0$\\
+$a \getsr [m]$\\
+if $T[x] \neq \undefined$\\
+\nudge $a \gets T[x]$\\
+$T[x] \gets a$\\
+$\mathrm{Ret} \nudge \calO(x) + i\cdot a$, for $i\in[1,k]$
+}
+}
+\caption{\Cref{thm1}:Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
+\end{figure}
+
+The PRF security notion is shown in \Cref{fig:prf}. Let
+prf-adversaries $B_1, B_2$ be as shown in \Cref{fig:BGame1}.
+Adversary~$B_1$ is constructed so that, if its challenge bit~$b=1$,
+then it exactly simulates $\game{0}$ for~$A$; if $b=0$, it
+simulates~$\game{1}$.  Similarly, adversary~$B_2$ simulates~$\game{1}$
+if its challenge bit~$b=1$, and $\game{2}$ otherwise.  We can conclude
+that 
 \begin{align*}
-\game{1}(A)\, : \, h_j(x) &= ( F_{K_0}(x) + j\cdot \rho_2(x)) \bmod m\\
-\game{2}(A)\, : \, h_j(x) &= ( \rho_1(x) + j \cdot \rho_2(x)) \bmod m
+\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=1} &= \Prob{\game{0}(A)=1} \\%\label{eq:m1}\\
+\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=0} &= 1-\Prob{\game{1}(A)=1} \\%\label{eq:m3}\\
+\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=1} &= \Prob{\game{1}(A)=1} \\%\label{eq:m2}\\
+\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=0} &= 1-\Prob{\game{2}(A)=1} \\%\label{eq:m4}
 \end{align*}
-In $\game{3}(A)$, we replace the hash functions of $\HashOracle$ (in $\game{2}(A)$) with lazy sampling of elements from $[m]$.
-This brings us close to the classic Bloom filter's soundness condition, as now the hash indices sampled during a query are random points in $[m]$, and are independent of the hash indices used by the $\Rep$.
-As mentioned in \acnote{ref :{sec:intro}}, the soundness condition of a classic bloom filter is given as  $\Prob{h_1,h_2,\ldots,h_k \getsr \mathrm{Func}(\univ,[m])\colon M[h_1(y)]=1 \wedge \cdots \wedge M[h_k(y)]=1} \leq \epsilon$.
-Also, the $\QryOracle$ now sets $\bad$ to $\true$ if the queries indexed by the set $\mathcal{I}$ fail to be false-positives, or if any of the remaining queries are false-positives.
-It can be observed that the $\bad$ flag has no impact on the output of the $\QryOracle$, nor does it affect  the value returned by~$\game{3}$.
-Rather it lays foundation for $\game{4}(A)$.
-From these observations,
-\begin{align}
-\Prob{\game{3}(A)=1 \wedge \neg\bad} &= \Prob{\game{3}(A)=1} \Prob{\game{3}(A) : \neg\bad}\label{eq:1} \\
-\Prob{\game{2}(A)=1} &= \Prob{\game{3}(A)=1}\label{eq:2}
-\end{align}
-$\game{4}(A)$ is identical to $\game{3}(A)$ except it returns 0 if $\bad$ is set to true.
-So, by construction $\game{4}(A)$ and $\game{3}(A)$ are identical-untill-$\bad$.
-In addition, $\game{4}(A)$ returning 1 implies that bad is never set to true.
-Therefore,
-\begin{equation}
-\Prob{\game{4}(A)=1} = \Prob{\game{3}(A)=1 \wedge \neg\bad}\label{eq:3}
-\end{equation}
-From \Cref{eq:1,eq:2,eq:3}
-\begin{equation}
-\Prob{\game{4}(A)=1} =  \Prob{\game{2}(A)=1} \Prob{\game{3}(A) : \neg\bad} \label{eq:4}
-\end{equation}
-Since, probability of any set of $r$ queries indexed by set $\calI$ to be not false positives are equally likely to any other set sampled from $[\{1,2,\ldots,q\}]^r$, we have
-\begin{equation}
-\Prob{\game{3}(A) : \neg\bad} = \frac{1}{\dbinom{q}{r}}\label{eq:555}
-\end{equation}
-From \Cref{eq:4,eq:555}
-\begin{equation}
-\Prob{\game{4}(A)=1} = \Prob{\game{2}(A)=1}\frac{1}{\dbinom{q}{r}}\label{eq:6}
-\end{equation}
-In $\game{4}(A)$, $A$ wins $\ExpFPSecHash{B_{\mathrm{lin}},r}{A}$ after finding $r$ false positives indexed by $\calI$.
+%
+\noindent
+By a standard conditioning of the PRF advantage, we have 
+%From \Cref{eq:m1,eq:m2,eq:m3,eq:m4},
+%\begin{align}
+%\nonumber \Prob{\ExpPRF{F}{B_1} = 1} &= .5\Prob{\ExpPRF{F}{B_1}=1\,|\,b=0} + .5\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=1}\\
+%\nonumber 2\Prob{\ExpPRF{F}{B_1} = 1} &= 1-\Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1}\\
+%\nonumber (2\Prob{\ExpPRF{F}{B_1} = 1} - 1)  &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1}\\
+% \AdvPRF{F}{B_1} &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1} \label{eq:11}\\
+%\nonumber& &\\
+%\nonumber \Prob{\ExpPRF{F}{B_2} = 1} &= .5\Prob{\ExpPRF{F}{B_2}=1\,|\,b=0} + .5\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=1}\\
+%\nonumber 2\Prob{\ExpPRF{F}{B_2} = 1} &= 1-\Prob{\game{2}(A)=1} + \Prob{\game{1}(A)=1}\\
+%\nonumber (2\Prob{\ExpPRF{F}{B_2} = 1} - 1)  &= \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1}\\
+% \AdvPRF{F}{B_2} &= \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1} \label{eq:12}
+%\end{align}
+%\noindent
+%Adding \Cref{eq:11,eq:12}, we have
+\begin{equation*}
+\Prob{\game{0}(A)=1} = \AdvPRF{F}{B_1} +\AdvPRF{F}{B_2} + \Prob{\game{2}(A)=1}%\label{eq:13}
+\end{equation*}
+
+In $\game{3}(A)$, we replace the random functions used in
+$\HashOracle$ (in $\game{2}(A)$) with lazy sampling of elements from
+$[m]$.  This change does not alter the behavior of the oracle, as the
+random functions are (by the no-pointless-queries assumption on~$A$) always called on a new
+value of~$x$.
+%
+Also, the $\QryOracle$ oracle now sets $\bad$ to $\true$ if the
+queries indexed by the set $\mathcal{I}$ fail to be false-positives,
+or if any of the remaining queries are false-positives. It can be
+observed that the $\bad$ flag has no impact on the output of the
+$\QryOracle$, nor does it affect  the value returned
+by~$\game{3}$. Thus we have $\Prob{\game{2}(A)=1} =
+\Prob{\game{3}(A)=1}$ and
+\[
+\Prob{\game{3}(A)=1 \wedge \game{3}(A): \neg\bad} = \Prob{\game{3}(A)=1} \Prob{\game{3}(A) : \neg\bad}%\label{eq:1} \\
+\]
+
+We note that $\game{3}$ and $\game{4}$ are
+``identical-untill-$\bad$''~\cite{BeRo-gameplaying}.  In particular,
+in $\game{4}$ returns 0 when $\game{3}$ would have returned 1 (i.e.,
+the adversary outputs~$r$ false-positives) but $\bad=\true$.  
+Moreover,  $\game{4}(A)$ returning 1 implies that $\bad$ is never set to $\true$. Therefore,
+$\Prob{\game{4}(A)=1} = \Prob{\game{3}(A)=1 \wedge \neg\bad} =
+\Prob{\game{3}(A)=1} \Prob{\game{3}(A) : \neg\bad}$, by our previous observation.
+
+Before continuing the proof, a bit of intuition for the introduction
+of the $\bad$-flag in games~$\game{3},\game{4}$.   Intuitively, if the index
+set~$\mathcal{I}$ exactly predicts which of the $\QryOracle$ will be
+false-positives (and, conversely, which will not be), then a
+non-adaptive FP-finding adversary can ``guess'' which of~$A$'s queries require it
+to return 1 when simulating the $\QryOracle$, and which require it to
+return 0.  In this way, no queries ever actually need to be made.
+Moving to a non-adaptive setting will allow us to connect to classical
+results on the FP-rate of Bloom filters; more in a moment.
+
+Now, consider $\Prob{\game{3}(A) : \neg\bad}$.  The indicated event
+happens iff the $r$-set~$\calI$ contains exactly the indices of
+$\QryOracle$-queries that are false-positives.  Since the value
+of~$\bad$ does not alter the responses of~$\QryOracle$, the
+set~$\mathcal{Z}$ output by~$A$ and the set~$\calI$ are independent.
+Thus $\bad$ remains $\false$ after~$A$ halts with probability
+$1/\dbinom{q}{r}$, and we have 
+\begin{equation*}
+\Prob{\game{3}(A)=1} = \frac{1}{\dbinom{q}{r}}\Prob{\game{4}(A)=1}
+\end{equation*}
+
+\fixme{Tom is here in rewriting the proof.}
+Moving on $\game{4}(A)$, $A$ wins $\ExpFPSecHash{B_{\mathrm{lin}},r}{A}$ after finding $r$ false positives indexed by $\calI$.
 Therefore, without loss of generality, it can be assumed that $A$ halts just after it finds the $r$ false positives, and outputs $\calZ$(of size $r$).
@@
 \Prob{\game{2}(A)=1} &\leq \dbinom{q}{r}\left( (1-e^{-kn/m})^k + O(1/n) \right)^r\label{eq:10}
-\end{align}
-The PRF game of $F$ is shown in \Cref{fig:prf}. Let prf-adversaries $B_1, B_2$ be as shown in \Cref{fig:BGame1}.  By
-construction, these simulate $\game{1}(A)$ and $\game{2}(A)$, respectively.
-When $b=0$, $B_1$ wins if $\game{1}(A)$ outputs 0; $B_2$ wins if $\game{2}(A)$ returns 0.
-When $b=1$, $B_1$ and $B_2$ exactly simulate $\game{0}(A)$ and $\game{1}(A)$.
-So,
-\begin{align}
-\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=1} &= \Prob{\game{0}(A)=1}\label{eq:m1}\\
-\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=1} &= \Prob{\game{1}(A)=1}\label{eq:m2}\\
-\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=0} &= 1-\Prob{\game{1}(A)=1}\label{eq:m3}\\
-\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=0} &= 1-\Prob{\game{2}(A)=1}\label{eq:m4}
 \end{align}
@@
 \underline{{$\game{3}(A)$},\fbox{$\game{4}(A)$}}\\
-$c \gets 0$\\
+$c\gets 0$, $\bad\gets\false$\\
 $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
-$\bad \gets \false$\\
-%$\calY \gets \emptyset $\\
-%$\rho_1,\rho_2 \getsr \Func{\univ,[m]}$\\
 $S \getsr \distr{\univ}{n}$\\
@@
 Ret 0\\\\
-%if $|\calY| < t$ then \\ 
-%\nudge Ret 0\\
-%for $i=1$ to $t$ \\
-%\nudge $z_i \getsr \calY $\\
-%\nudge $\calY \gets \calY \setminus \{z_i\}$\\
-%\nudge if $\Qry^{\HashOracle}(M,z_i)=0$ then\\
-%\nudge \nudge Ret 0\\
-%Ret 1\\\\
-%
+
 \oracle{$\QryOracle(x)$}\\
-%$\calY \gets \calY \cup \{x\}$\\
 $c \gets c+1$\\
@@
 \nudge $\bad \gets \true$ \\
-%\nudge \fbox{Ret 1} \\
 if $c \not\in \mathcal{I}$ and $v\neq 0$ then\\
 \nudge $\bad \gets \true$\\
-%\nudge \fbox{Ret 0}\\
 Ret~$v$\\\\
@@
 %\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
-\begin{figure}
-\centering
-\fpage{0.9}{
-\hpagessl{0.5}{0.5}
-{
-$\adversaryv{B_1^{\calO}}$\\
-$K_1 \getsr \calK $\\
-$\calS \getsr \distr{\univ}{n}$\\
-$M \getsr \Rep^{\HashOracle}(\calS)$\\
-When $A$ asks $\QryOracle(x)$:\\
-$\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
-When $A$ halts with output $\calZ'$: \\
-\nudge if $|\calZ'| < r$ or $\calZ' \cap \calS \neq \emptyset$ then \\
-\nudge \nudge Ret 0\\
-\nudge if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
-\nudge \nudge Ret 0\\
-\nudge Ret 1\\\\
-\oracle{$\HashOracle(x)$}\\
-$ \mathrm{Ret} \nudge F_{K_1}(x) + i\cdot \calO(x)$, for $i\in[1,k]$\\
-}
-{
-$\adversaryv{B_2^{\calO}}$\\
-%$d \getsr \bits $\\
-%$\rho_2 \getsr Func(\univ, [m])$ \\
-$S \getsr \distr{\univ}{n}$\\
-$M \getsr \Rep^{\HashOracle}(\calS)$\\
-When $A$ asks $\QryOracle(x)$:\\
-$\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
-When $A$ halts with output $\calZ'$: \\
-\nudge if $|\calZ'| < r$ or $\calZ' \cap \calS \neq \emptyset$ then \\
-\nudge \nudge Ret 0\\
-\nudge if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
-\nudge \nudge Ret 0\\
-\nudge Ret 1\\\\
-\oracle{$\HashOracle(x)$}\\
-%if $d=0$\\
-$a \getsr [m]$\\
-if $T[x] \neq \undefined$\\
-\nudge $a \gets T[x]$\\
-$T[x] \gets a$\\
-$\mathrm{Ret} \nudge \calO(x) + i\cdot a$, for $i\in[1,k]$
-}
-}
-\caption{\Cref{thm1}:Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
-\end{figure}
 
@@
 \end{figure}
-
-%
-\noindent
-From \Cref{eq:m1,eq:m2,eq:m3,eq:m4},
-\begin{align}
-\nonumber \Prob{\ExpPRF{F}{B_1} = 1} &= .5\Prob{\ExpPRF{F}{B_1}=1\,|\,b=0} + .5\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=1}\\
-\nonumber 2\Prob{\ExpPRF{F}{B_1} = 1} &= 1-\Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1}\\
-\nonumber (2\Prob{\ExpPRF{F}{B_1} = 1} - 1)  &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1}\\
- \AdvPRF{F}{B_1} &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1} \label{eq:11}\\
-\nonumber& &\\
-\nonumber \Prob{\ExpPRF{F}{B_2} = 1} &= .5\Prob{\ExpPRF{F}{B_2}=1\,|\,b=0} + .5\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=1}\\
-\nonumber 2\Prob{\ExpPRF{F}{B_2} = 1} &= 1-\Prob{\game{2}(A)=1} + \Prob{\game{1}(A)=1}\\
-\nonumber (2\Prob{\ExpPRF{F}{B_2} = 1} - 1)  &= \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1}\\
- \AdvPRF{F}{B_2} &= \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1} \label{eq:12}
-\end{align}
-
-\noindent
-Adding \Cref{eq:11,eq:12}, we have
-\begin{equation}
-\AdvPRF{F}{B_1} +\AdvPRF{F}{B_2} = \Prob{\game{0}(A)=1} - \Prob{\game{2}(A)=1}\label{eq:13}
-\end{equation}
 

### 2016-08-14 Theorem2_FP.tex

@@
 \newcommand{\rhoK}{\rho(\langle j,x \rangle)}
+\newcommand{\OK}{\calO(\langle j,x \rangle)}
 
-Let $B_{\mathrm{ds}}=(\Hash,\Rep,\Qry)$ be the hash-based filter defined as earlier, except the hash functions are defined as $h_j(x) = \FK, \, j \in [1,k]$.
+\heading{Construction of PRF with domain separation.}
+Let $B_{\mathrm{ds}}=(\Hash,\Rep,\Qry)$ be a hash-based filter defined as follows.
+Fix non-empty sets ~$\univ$, $\calK$ and integers $k,m,n>0$.
+Let $F\colon\mathcal{K} \times \univ \to [m]$ be a function family.
+The $\Hash$ algorithm provides randomness with domain separation, as it samples key $K \getsr \mathcal{K}$ and defines $h_j(x) = \FK $ for $j \in [1,k]$.
+The $\Rep$ and $\Qry$ algorithms are the standard (determinisitic) BF ones.
 Informally, the following result shows, if~$F$ is PRF secure and the filter has low FP-error in the non-adaptive setting, then $B_{\mathrm{ds}}$ is secure against adaptive FP-finding adversaries.
 
-\tsnote{Clean up so it looks like the previous theorem.}
 \begin{theorem}\label{thm2}
-Fix $k,m,n >0$.
-Let $B_{\mathrm{ds}}$ be the hash based filter described earlier.
-If there exists an adaptive adversary $A$ compatible with $\ExpFPPubHash{B_{\mathrm{ds},t}}{\cdot}$ asking $q \times r$ queries in $t$ time, then there exists an adversary $B$ attacking the PRF game in time $O(t)$ and asking same number of queries as $A$ such that
-\begin{equation}
-\AdvFPSecHash{B_\mathrm{ds},t}{A}\leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
-\end{equation}
+Fix $k,m,n,r >0$.
+Let $B_{\mathrm{ds}}$ be the hash based filter just described.
+If there exists an adaptive adversary, $A$ compatible with $\ExpFPSecHash{B_{\mathrm{ds},r}}{\cdot}$ asking $q$ queries, and has time complexity O(t), then there exists an adversary $B$ (explicitly constructed in the proof of this theorem), such that
+\[
+\AdvFPSecHash{B_\mathrm{ds},t}{A} =  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k  \right)^r
+\]
+Here, $B$ asks $q$ queries, and has time complexity $O(t+qm)$.
 \end{theorem}
 
-\tsnote{I don't see why this is necessary.  Doesn't it follow from the
-standard bounds on Bloom filters (go look them up and adjust the
-theorem accordingly) which assume that the hash functions are random
-functions?  Whatever argument you use in Theorem 1 to justify
-independence, i.e. turning one non-adaptive FP into~$r$ non-adaptive
-FPs, should apply here, too.  You don't need to understand the KM
-results deeply for this argument, by the way.  You just need to
-understand why you get independence, i.e. why it is that, after the
-set~$S$ has been hashed (hence the bits in~$M$ are set), then the
-probabilities that distinct $x_1,\ldots,x_r$ are each FPs are
-independent.  This really is pretty immediate from the fact that
-$\rho_1,\rho_2$ are random functions and the $x_i$ are distinct.}
-\tsnote{I guess if you want, you could give a 1-to-$r$ lemma for the hash
-  functions (with random functions $\rho1,\rho_2$ used in Theorem 1, prove it, and use that lemma in the
-  proof of Theorem 1.  Then do the parallel thing here, for Theorem 2.}
-\acnote{I think we should give a proof of the non-adaptive FP-error bound $(1-e^{-kn/m})^k + O(1/n) $.
-This bound which we picked from KM's theorem 6.2, is a particular case (double hashing scheme).
-Theorem 6.1, on the other hand holds good for any hashing scheme that satisfies Lemma 4.1.
-\\
- I tried to give the FP-bound as a Lemma. 
-\begin{lemma}\label{lemma1}
-Fix $k,m,n >0$. The FP-error of hash-based filter $B_{\mathrm{ds}}$ with hash functions $h_j(x) = \FK, \, j \in [k]$ is upperbounded by $(1-e^{-kn/m})^k + O(1/n)$.
-\end{lemma}
-}
-\acnote{As I had told you earlier, I was not able to understand the proofs of KM paper and now I am stuck in this proof. 
-\begin{proof}($Lemma$ \ref{lemma1})
-In \ref{KM}, $Theorem \,6.1$ gives the upperbound of FP error of any hashing scheme satisfying the 5 conditions enlisted in Lemma 4.1, and all these conditions are satisfied by $B_{\mathrm{ds}}$ as shown below.\\
-Since the hash functions of $B_{\mathrm{ds}}$ provide randomness with domain separation and the number of hash functions are controlled by parameter $j$, condition 1 and 2 are trivially satisfied.
-The last condition is also trivial, since size of $B_{\mathrm{ds}}$ will be some constant multiple of size of $S$, as in the classical bloom filter.\\
-The satisfiability of remaining 2 conditions is non-trivial ...
-\end{proof}}
-%
 \begin{proof}[\Cref{thm2}]
@@
 \begin{equation}
-\AdvFPSecHash{B_\mathrm{ds},r}{A} = \Prob{\game{0}(A)=1}\label{eq:0T2}
+\AdvFPSecHash{B_\mathrm{ds},r}{A} = \Prob{\game{0}(A)=1}\label{eq:2T0}
 \end{equation}
 \noindent
-\game{1}(A), \game{2}(A), and \game{3}(A) are same as in the previous theorem, except the hash-functions are distinct random functions.
-The non-adaptive counterparts of $B_\mathrm{ds}$ as well as the prf adversary are  identical to those of $B_\mathrm{lin}$.
-As shown in \game{1}(A) and \game{2}(A), the $\HashOracle$ oracle returns distinct random values in these simulations.
-$B$, on the other hand uses its oracle to generate random values (for $b=0$) in the following way, $h_j(x) = \calO(\langle j,x \rangle)$.
+In $\game{1}(A)$, $A$ attacks a different filter $\tilde{B}_\mathrm{ds}$, in which $F_K$ is replaced by a random function $\rho$ sampled from $\Func{\univ,[m]}$.
+$\game{2}(A)$ and $\game{3}(A)$ on the other hand use lazy sampling in $\Hash$ to select random values from $[m]$.
+This makes $\game{2}(A)$ and $\game{3}(A)$ identical to $\game{3}(A)$ and $\game{4}(A)$ of previous theorem, and hence the analysis and results of \Cref{thm1} apply to this theorem as well.
+Therefore,
+\begin{align}
+\Prob{\game{2}(A)=1 \wedge \neg\bad} &= \Prob{\game{2}(A)=1}\Prob{\game{2}(A) : \neg\bad}\label{eq:2T1} \\
+\Prob{\game{1}(A)=1} &= \Prob{\game{2}(A)=1}\label{eq:2T2}
+\end{align}
+From \Cref{eq:2T1,eq:2T2}
+\begin{equation}
+\Prob{\game{2}(A)=1 \wedge \neg\bad} = \Prob{\game{1}(A)=1}\Prob{\game{2}(A) : \neg\bad}\label{eq:2T3}
+\end{equation}
+\noindent
+Also,
+\begin{equation}
+\Prob{\game{3}(A)=1} = \Prob{\game{2}(A)=1 \wedge \neg\bad}\label{eq:2T4}
+\end{equation}
+\noindent
+Using \Cref{eq:2T3} in \Cref{eq:2T4}
+\begin{equation}
+\Prob{\game{3}(A)=1} = \Prob{\game{1}(A)=1}\Prob{\game{2}(A) : \neg\bad}\label{eq:2T5}
+\end{equation}
+\begin{equation}
+\Prob{\game{2}(A) : \neg\bad} = \frac{1}{\dbinom{q}{r}}\label{eq:2T6}
+\end{equation}
+\noindent
+From \Cref{eq:2T5,eq:2T6}
+\begin{align}
+\nonumber \Prob{\game{3}(A)=1} &= \Prob{\game{1}(A)=1}\frac{1}{\dbinom{q}{r}}\\
+\Prob{\game{1}(A)=1} &= \dbinom{q}{r} \times \Prob{\game{3}(A)=1} \label{eq:2T7}
+\end{align}
+
+Let $D$ be a non-adaptive adversary (shown in \Cref{fig:2TD}) that finds ~$r$ false positives against $\tilde{B}_{\mathrm{ds}}$.
+As discussed in the previous theorem, if $A$ wins $\game{3}(\cdot)$, then $D$ wins $\ExpFPSecHash{\tilde{B}_{\mathrm{ds}},r}{\cdot}$ game.
+So,
+\begin{equation}
+\AdvFPSecHash{\tilde{B}_{\mathrm{ds}},r}{D} = \Prob{\game{3}(A) = 1}\label{eq:2T8}
+\end{equation}
+Since, $D's$ $\HashOracle$ returns $k$ random values which are mutually independent of each other, for $r=1$, $\AdvFPSecHash{\tilde{B}_{\mathrm{ds}},1}{D}$ is same as the false positive probability ($(1-e^{-kn/m})^k$) of a classic Bloom filter.
+Also, as discussed in the previous theorem, for $r \neq 1$, the event of getting a false positive is independent of the index of the query for a non-adaptive adversary.
+So,
+\begin{equation}
+\AdvFPSecHash{\tilde{B}_{\mathrm{ds}},r}{D} =   \left( (1-e^{-kn/m})^k  \right)^r \label{eq:2T8a}
+\end{equation}
+\noindent
+From \Cref{eq:2T7,eq:2T8,eq:2T8a}
+\begin{equation}
+\Prob{\game{1}(A)=1} = \dbinom{q}{r} \times \left( (1-e^{-kn/m})^k  \right)^r \label{eq:2T8b}
+\end{equation}
 
@@
 \underline{\game{0}(A)}\\
-$K_1, K_2 \getsr \calK$\\
+$K \getsr \calK$\\
 $S \getsr \distr{\univ}{n}$\\
@@
 \oracle{$\HashOracle(x)$}\\
-$h_j(x) = \FK$\\
+for $j = 1$ to $k$\\
+\nudge $h_j(x) =\FK $\\
 Ret $\left(h_1(x),\ldots,h_k(x)\right)$
@@
 \oracle{$\HashOracle(x)$}\\
-$h_j(x) = \rhoK $\\
+for $j=1$ to $k$\\
+\nudge $h_j(x) = \rhoK $\\
 Ret $\left(h_1(x),\ldots,h_k(x)\right)$
@@
 \fpage{.9}{
-\hpagessl{.45}{.5}
+\hpagessl{.55}{.3}
 {
@@
 $\calZ \getsr A^{\QryOracle}(\calS)$\\
-if $|\calZ| < r$ or $\calZ \cap \calS \neq \emptyset$ then Ret 0\\
+if $|\calZ| < r$ or $\calZ \cap \calS \neq \emptyset$ then\\
+\nudge Ret 0\\
 if $\forall z \in \calZ,\,\Qry^{\HashOracle}(M,z)=1$ then \\
@@
 \nudge Ret 1\\
-Ret 0\\\\
-%
+Ret 0
+}
+{
 \oracle{$\QryOracle(x)$}\\
@@
 \oracle{$\HashOracle(x)$}\\
-for $i = 1$ to~$k$\\
-\nudge $v_i  \getsr [m]$\\
-Ret $\left(v_1,\ldots,v_k\right)$
-}
-{
-\underline{$\game{4}(A)$}\\
-$c \gets 0$\\
-$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
-$\calY \gets \emptyset$\\
-$S \getsr \distr{\univ}{n}$\\
-$M \getsr \Rep^{\HashOracle}(\calS)$\\
-$\calZ \getsr A^{\QryOracle}(\calS)$\\
-if $|\calY| < r$ or $\calY \cap \calS \neq \emptyset$ then\\
-\nudge Ret 0\\
-if $\forall y \in \calY,\,\Qry^{\HashOracle}(M,y)=1$ then \\
-\nudge Ret 1\\
-Ret 0\\\\
-%
-\oracle{$\QryOracle(x)$}\\
-$c \gets c+1$\\
-if $c \in \mathcal{I}$ then\\
-\nudge $\calY \gets \calY \cup {x}$\\
-\nudge Ret 1\\
-else\\
-\nudge Ret 0 \\\\
-%
-\oracle{$\HashOracle(x)$}\\
-for $i = 1$ to~$k$\\
-\nudge $v_i  \getsr [m]$\\
+$a \getsr [m]$\\
+for $j = 1$ to~$k$\\
+\nudge $v_j = a$\\
 Ret $\left(v_1,\ldots,v_k\right)$
@@
 }
-\caption{\Cref{thm2}: Game playing argument}\label{fig:GameT2}
+\caption{\Cref{thm2}:Game playing argument}\label{fig:Game}
 \end{figure}
+
+%\caption{PRF adversary $B$ simulating $\game{1}(A)$ and $\game{2}(A)$, and non-adaptive adversary $D$ simulating $\game{4}(A)$} 
+\begin{figure}
+\centering
+\fpage{0.9}{
+\hpagessl{0.5}{0.5}
+{
+$\adversaryv{B^{\calO}}$\\
+$\calS \getsr \distr{\univ}{n}$\\
+$M \getsr \Rep^{\HashOracle}(\calS)$\\
+When $A$ asks $\QryOracle(x)$:\\
+$\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
+When $A$ halts with output $\calZ'$: \\
+\nudge if $|\calZ'| < r$ or $\calZ' \cap \calS \neq \emptyset$ then \\
+\nudge \nudge Ret 0\\
+\nudge if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
+\nudge \nudge Ret 0\\
+\nudge Ret 1\\\\
+\oracle{$\HashOracle(x)$}\\
+\nudge Ret $\OK$, for $j\in[1,k]$\\
+}
+{
+$\adversaryv{D^{\QryOracle, \calS}}$\\
+$c \gets 0$\\
+$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
+When $A$ asks $\QryOracle(x)$:\\
+\nudge $c \gets c+1$\\
+\nudge $r \gets 0$\\
+\nudge if $c \in \mathcal{I}$\\
+\nudge \nudge $r \gets \QryOracle(x)$\\
+\nudge Ret $r$\\
+When $A$ halts with output $\calZ$\\
+\nudge Ret $\calZ$\\\\
+%
+\oracle{$\QryOracle(x)$}\\
+ Ret $\Qry^{\HashOracle}(M,x)$\\\\
+%
+\oracle{$\HashOracle(x)$}\\
+for $j = 1$ to~$k$\\
+\nudge $v_j = \rhoK $\\
+Ret $\left(v_1,\ldots,v_k\right)$
+}
+}
+\caption{PRF adversary $B$ simulating $\game{1}(A)$ and $\game{2}(A)$, and non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:2TD}
+\end{figure}
+
+Let adversary $B$ be as  shown in \Cref{fig:2TD}.
+It can be observed that, by construction $B$ simulates $\game{0}(A)$ and $\game{1}(A)$ respectively.
+For $b=1$, $B$ wins, if $A$ wins $\game{0}(\cdot)$.
+While for $b = 0$, if $A$ wins $\game{1}(\cdot)$, $B$ wins by returning 0.
+Therefore,
+\begin{align}
+\Prob{\ExpPRF{F}{B} = 1\,|\,b=1} &= \Prob{\game{0}(A)=1}\label{eq:2T9}\\
+\Prob{\ExpPRF{F}{B} = 1\,|\,b=0} &= 1-\Prob{\game{1}(A)=1}\label{eq:2T10}
+\end{align}
 \noindent
-Using analysis of previous theorem and \Cref{lemma1}\acnote{change if lemma1 not required}, we have
-\begin{align}\label{eq:1T2}
-\AdvPRF{F}{B} &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1} \\
-\Prob{\game{1}(A)=1} &= \Prob{\game{2}(A)=1}\\
-\Prob{\game{3}(A)=1} &= \frac{1}{\dbinom{q}{r}}\Prob{\game{2}(A)=1}\\
-\Prob{\game{4}(A)=1} &= \Prob{\game{3}(A)=1}\\
-\Prob{\game{4}(A)=1} & \leq \Big[(1-e^{-kn/m})^k +O(1/n)\Big]^r
+From \Cref{eq:2T9,eq:2T10}
+\begin{align}
+\nonumber \Prob{\ExpPRF{F}{B} = 1} &= .5\Prob{\ExpPRF{F}{B}=1\,|\,b=0} + .5\Prob{\ExpPRF{F}{B} = 1\,|\,b=1}\\
+\nonumber 2\Prob{\ExpPRF{F}{B} = 1} &= 1-\Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1}\\
+\nonumber (2\Prob{\ExpPRF{F}{B} = 1} - 1)  &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1}\\
+ \AdvPRF{F}{B} &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1} \label{eq:2T11}
 \end{align}
+\noindent
+Using \Cref{eq:2T0,eq:2T8b} in \Cref{eq:2T11}
+\begin{align}
+ \nonumber \AdvPRF{F}{B} &= \AdvFPSecHash{B_\mathrm{ds},r}{A} - \dbinom{q}{r} \times \left( (1-e^{-kn/m})^k  \right)^r \\
+\AdvFPSecHash{B_\mathrm{ds},r}{A} &= \AdvPRF{F}{B} + \dbinom{q}{r} \times \left( (1-e^{-kn/m})^k  \right)^r\label{eq:2T12}
+\end{align}
+\end{proof}
 
-\noindent
-From \Cref{eq:0T2,eq:1T2}
-\begin{align}
-\nonumber \AdvPRF{F}{B} &= \AdvFPSecHash{B_\mathrm{ds},r}{A} - \frac{1}{\dbinom{q}{r}}\Prob{\game{2}(A)=1}\\
-\nonumber \AdvFPSecHash{B_\mathrm{ds},r}{A} &= \AdvPRF{F}{B} + \frac{1}{\dbinom{q}{r}}\Prob{\game{2}(A)=1}\\
-\nonumber \AdvFPSecHash{B_\mathrm{ds},r}{A} &= \AdvPRF{F}{B} +  \dbinom{q}{r}\Prob{\game{4}(A)=1}\\
-\AdvFPSecHash{B_\mathrm{ds},r}{A} &= \AdvPRF{F}{B} +  \dbinom{q}{r}\Big[(1-e^{-kn/m})^k +O(1/n)\Big]^r
-\end{align}
-
-\end{proof}
+\iffalse
+\acnote{I think we should give a proof of the non-adaptive FP-error bound $(1-e^{-kn/m})^k + O(1/n) $.
+This bound which we picked from KM's theorem 6.2, is a particular case (double hashing scheme).
+Theorem 6.1, on the other hand holds good for any hashing scheme that satisfies Lemma 4.1.
+\\
+ I tried to give the FP-bound as a Lemma. 
+\begin{lemma}\label{lemma1}
+Fix $k,m,n >0$. The FP-error of hash-based filter $B_{\mathrm{ds}}$ with hash functions $h_j(x) = \FK, \, j \in [k]$ is upperbounded by $(1-e^{-kn/m})^k + O(1/n)$.
+\end{lemma}
+}
+\acnote{As I had told you earlier, I was not able to understand the proofs of KM paper and now I am stuck in this proof. 
+\begin{proof}($Lemma$ \ref{lemma1})
+In \ref{KM}, $Theorem \,6.1$ gives the upperbound of FP error of any hashing scheme satisfying the 5 conditions enlisted in Lemma 4.1, and all these conditions are satisfied by $B_{\mathrm{ds}}$ as shown below.\\
+Since the hash functions of $B_{\mathrm{ds}}$ provide randomness with domain separation and the number of hash functions are controlled by parameter $j$, condition 1 and 2 are trivially satisfied.
+The last condition is also trivial, since size of $B_{\mathrm{ds}}$ will be some constant multiple of size of $S$, as in the classical bloom filter.\\
+The satisfiability of remaining 2 conditions is non-trivial ...
+\end{proof}}
+%
+\tsnote{Clean up so it looks like the previous theorem.}
+\tsnote{I don't see why this is necessary.  Doesn't it follow from the
+standard bounds on Bloom filters (go look them up and adjust the
+theorem accordingly) which assume that the hash functions are random
+functions?  Whatever argument you use in Theorem 1 to justify
+independence, i.e. turning one non-adaptive FP into~$r$ non-adaptive
+FPs, should apply here, too.  You don't need to understand the KM
+results deeply for this argument, by the way.  You just need to
+understand why you get independence, i.e. why it is that, after the
+set~$S$ has been hashed (hence the bits in~$M$ are set), then the
+probabilities that distinct $x_1,\ldots,x_r$ are each FPs are
+independent.  This really is pretty immediate from the fact that
+$\rho_1,\rho_2$ are random functions and the $x_i$ are distinct.}
+\tsnote{I guess if you want, you could give a 1-to-$r$ lemma for the hash
+  functions (with random functions $\rho1,\rho_2$ used in Theorem 1, prove it, and use that lemma in the
+  proof of Theorem 1.  Then do the parallel thing here, for Theorem 2.}
+\fi

### 2016-08-14 Proofs.tex
Added missing files
Theorem 1 proof in old syntax
Theorem 2 proof in old syntax
Proof 1
Proofs
rewriting proof of Theorem 1

@@
 \tsnote{Jon: ignore these for now.  This is Animesh's workspace.}
-\acnote{I will review for mistakes}
-\input{Theorem1_FP}
+\input{Theorem1_FP_unmerged}
 \input{Theorem2_FP}
-\input{Theorem3_priv}
+%\input{Theorem3_priv}
 
+\iffalse
 \section{Summary of attacks(based on Bloom filter exploit) on Squid}
@@
 \item Crossby and Wallach targeted hash collisions in Squid to increase the average URL load time.
-The authors quote ``This attack does not represent a ''smoking gun” for algorithmic complexity attacks, but it does illustrate how common network services may be sensitive to these attacks".
+The authors quote ``This attack does not represent a ''smoking gun'' for algorithmic complexity attacks, but it does illustrate how common network services may be sensitive to these attacks".
 2 experiments were carried out to illustrate this.
@@
 \end{itemize}
+
+\fi

### 2016-08-15 Theorem1_FP.tex
finished cleaning up Theorem 1

@@
 $K_1 \getsr \calK $\\
-$\calS \getsr \distr{\univ}{n}$\\
-$M \getsr \Rep^{\HashOracle}(\calS)$\\
+$S \getsr \distr{\univ}{n}$\\
+$M \getsr \Rep^{\HashOracle}(S)$\\
+Run~$A(S)$\\
 When $A$ asks $\QryOracle(x)$:\\
@@
 $M \getsr \Rep^{\HashOracle}(\calS)$\\
+Run $A(S)$\\
 When $A$ asks $\QryOracle(x)$:\\
@@
 
-\fixme{Tom is here in rewriting the proof.}
-Moving on $\game{4}(A)$, $A$ wins $\ExpFPSecHash{B_{\mathrm{lin}},r}{A}$ after finding $r$ false positives indexed by $\calI$.
-Therefore, without loss of generality, it can be assumed that $A$ halts just after it finds the $r$ false positives, and outputs $\calZ$(of size $r$).
-Further, we can also assume that every point in $\calZ$ has already been queried to $\QryOracle$.
-This assumption can be  easily enforced (in the original security definitions) by counting as part of the number of queries~$q$, the points in $\mathcal{Z}$.
-Hence, if $\game{4}(A)=1$, there is a non-adaptive adversary~$D$ that finds~$r$ false positives against $\tilde{B}_{\mathrm{lin}}$, which is $B_{\mathrm{lin}}$ but with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$, respectively as shown in \Cref{fig:D}.
-So,
-\begin{align}
-\nonumber \Prob{\ExpFPSecHash{\tilde{B}_{\mathrm{lin}},r}{D} = 1} &= \Prob{\game{4}(A) = 1}\\
-\mathrm{or} \nudge \AdvFPSecHash{\tilde{B}_{\mathrm{lin}},r}{D} &= \Prob{\game{4}(A) = 1}\label{eq:7}
-\end{align}
-Let $\calF$ be the event of getting a false positive in a classic Bloom filter.
-Since, $D$ is a non-adaptive adversary, for $r=1$, it exactly simulates the classic Bloom filter game.
-Also, as the elements of $\calI$ are randomly sampled from $[\{1,2,\ldots,q\}]^r$, the event of any query indexed by $\calI$ being a false positive is mutually independent of any other query indexed by the same set.
-Hence,
-\begin{align}
-\nonumber \AdvFPSecHash{\tilde{B}_{\mathrm{lin}},r}{D} &= [\Prob{\calF}]^r\\
-&\leq \left( (1-e^{-kn/m})^k + O(1/n) \right)^r \label{eq:8}
-\end{align}
-Here, $\left( (1-e^{-kn/m})^k + O(1/n) \right)$ is the upper bound of $\calF$, as given by Kirsch et. al.\ref{KM}.\\
-From \Cref{eq:7,eq:8},
-\begin{equation}
-\Prob{\game{4}(A)=1} \leq  \left( (1-e^{-kn/m})^k + O(1/n) \right)^r \label{eq:9}
-\end{equation}
-Using \Cref{eq:6} in \Cref{eq:9}
-\begin{align}
-\Prob{\game{2}(A)=1}\frac{1}{\dbinom{q}{r}} & \leq  \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\\
-\Prob{\game{2}(A)=1} &\leq \dbinom{q}{r}\left( (1-e^{-kn/m})^k + O(1/n) \right)^r\label{eq:10}
-\end{align}
+Recall that adversary~$A$ wins $\ExpFPSecHash{B_{\mathrm{lin}},r}{}$ by finding~$r$ false positives.
+We can assume, without loss of generality,  that~$A$ halts immediately upon finding its $r$-th false positive.
+We can also assume that every point in $\calZ$ has already been queried to $\QryOracle$.
+This latter assumption is not without loss, but can be  easily enforced (in the original security definitions) by counting as part of the number of queries~$q$, the points in $\mathcal{Z}$.
+%
+Under these assumptions, if $\game{4}(A)=1$, then there is a non-adaptive adversary~$D$ that finds~$r$ false positives against $\tilde{B}_{\mathrm{lin}}$, which is $B_{\mathrm{lin}}$ but with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$, respectively.
+We give this~$D$ in \Cref{fig:D}.
+Intuitively, adversary~$D$ guesses which~$r$ of~$A$'s queries will be the false positives; it simulates the~$\QryOracle$ by returning 1 on the guessed queries, and 0 otherwise; and it halts by outputting the set of guessed queries.
+Thus we have
+$\Prob{\game{4}(A)=1} =\Prob{\ExpFPSecHash{\tilde{B}_{\mathrm{lin}},r}{D} = 1}$.
+
+Note that $\tilde{B}_{\mathrm{lin}}$ is the scheme that is analyzed in the classical Bloom filter literature ---the hash functions are modeled as independent random functions, and the parameters $k,m,n$  are set to achieve a target maximum false-positive probability (or rate).
+Kirsch and Mitzenmacher~\cite{KM} show that the upperbound on false-positive probability for a non-adaptive adversary and $r=1$ is $\left( (1-e^{-kn/m})^k + O(1/n) \right)$.
+For $r>1$, we observe that~$A$'s queries are distinct and not elements of the original set~$S$, since we assume no pointless queries.
+Hence, so are the points $x_1,x_2,\ldots,x_r$ returned by~$D$.
+Let $\calF_i$ be the event that~$x_i$ is a false positive.
+Since $\game{4}$ (equivalently $\tilde{B}_{\mathrm{lin}}$) use independent random functions, the events $\calF_1,\calF_2,\ldots,\calF_r$ are independent.
+\[
+\Prob{\ExpFPSecHash{\tilde{B}_{\mathrm{lin}},r}{D} = 1}\leq \left( (1-e^{-kn/m})^k + O(1/n) \right)^r 
+\]
+
+To summarize, we have 
+\[
+\AdvFPSecHash{B_{\mathrm{lin}},r}{A}  \leq  \AdvPRF{F}{B_1} +\AdvPRF{F}{B_2} +\dbinom{q}{r}\left( (1-e^{-kn/m})^k + O(1/n) \right)^r
+\]
+which is the bound claimed in the theorem statement. \hfill \qed
 
@@
 $K \getsr \calK $\\
-$\rho \getsr Func(\univ,[m])$\\
+$\rho \getsr \Func(\univ,[m])$\\
 $b \getsr \bits$\\
@@
 \centering
-\fpage{0.7}{
-\hpagess{0.55}{0.4}
+\fpage{0.35}
 {
-$\adversaryv{D^{\QryOracle, \calS}}$\\
-$c \gets 0$\\
+$\adversaryv{D(S)}$\\[4pt]
+$c \gets 0$, $\calX \gets \emptyset$\\
 $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
+Run $A(S)$\\
 When $A$ asks $\QryOracle(x)$:\\
@@
 \nudge if $c \in \mathcal{I}$\\
-\nudge \nudge $r \gets \QryOracle(x)$\\
+\nudge \nudge $\calX \gets \calX \cup \{x\}$\\
+\nudge \nudge $r \gets 1$\\
 \nudge Ret $r$\\
-When $A$ halts with output $\calZ$\\
-\nudge Ret $\calZ$
-}
-{
-\oracle{$\QryOracle(x)$}\\
- Ret $\Qry^{\HashOracle}(M,x)$\\\\
-%
-\oracle{$\HashOracle(x)$}\\
-for $i = 1$ to~$k$\\
-\nudge $v_i = \rho_1(x)+i \cdot \rho_2(x) \bmod m$\\
-Ret $\left(v_1,\ldots,v_k\right)$
-}
+When $A$ halts:\\
+\nudge Ret $\calX$
 }
@@
 \end{figure}
-
-From \Cref{eq:0,eq:10,eq:13} \\
-\begin{align}
-\nonumber \AdvFPSecHash{B_{\mathrm{lin}},r}{A} &- \Prob{\game{2}(A)=1} =  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}   \\
-\nonumber \AdvFPSecHash{B_{\mathrm{lin}},r}{A}  &=  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} + \Prob{\game{2}(A)=1}  \\
-\AdvFPSecHash{B_{\mathrm{lin}},r}{A} &\leq  \AdvPRF{F}{B_1} +
-\AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
-\end{align}
 

### 2016-08-16 intro.tex
rewriting/fleshing out syntax section
notes

@@
 \tsnote{Skeleton text from old intro.  (Full version of old intro now
-  in an appendix.}
+  in an appendix.} \jnote{Too focused on Bloom filters for my
+  taste.}
 We revisit the formalization of Bloom filters~\cite{xxx} and closely
@@
 Bloom filters, as well as casting the classical Bloom filter
-soundness condition as a security experiment admiting adaptive
+soundness condition as a security experiment admitting adaptive
 adversaries.  To briefly summarize, a Bloom filter is a data
@@
 taken as the representation.  To test if $y \in \mathcal{S}$, one
-checks if \[(M[h_1(y)]=1 \wedge M[h_2(y)]=1 \wedge \cdots \wedge
-M[h_k(y)]=1),\] returning ``yes'' if so, and ``no'' otherwise. Bloom
+checks if
+\[
+(M[h_1(y)]=1 \wedge M[h_2(y)]=1 \wedge \cdots \wedge M[h_k(y)]=1),
+\]
+returning ``yes'' if so, and ``no'' otherwise. Bloom
 filters are correct, in the sense that if $y \in \mathcal{S}$, the

### 2016-08-16 syntax.tex
notes

@@
-\section{(Set-multiplicity) Data Structures}
+\section{(Multiset) Data Structures}
 
-\heading{Preliminaries. }
-When~$\univ$ is a set and $n>0$ is an integer, we let $[\univ]^n$ denote the set of all size-$n$ subsets of~$\univ$.
-We write $x \getsr \univ$ to denote sampling an element from~$\univ$ and assigning this to~$x$, and we extend this notation to randomized algorithms.
-When~$X$ is a string over some alphabet~$\Sigma$, we write $|X|$ for the bitlength of~$X$, relative to some fixed encoding.
-When~$X$ is a multiset, we overload the notation so that~$|X|$ is the number of elements in~$X$ (with mutiplicity).
+\heading{Preliminaries. } When~$\univ$ is a set and $n>0$ is an
+integer, we let $[\univ]^n$ denote the set of all size-$n$ subsets
+\jnote{Multisets?} of~$\univ$. We write $x \getsr \univ$ to denote
+sampling an element from~$\univ$ and assigning this to~$x$, and we
+extend this notation to randomized algorithms.  When~$X$ is a string
+over some alphabet~$\Sigma$, we write $|X|$ for the bitlength
+of~$X$, relative to some fixed encoding.  When~$X$ is a multiset, we
+overload the notation so that~$|X|$ is the number of elements in~$X$
+(with mutiplicity).
 
@@
 
-\heading{Data Structures.}  We being by defining a general primitive that produces a representation of a given multiset, and provides a mechanism to answer a specified collection of questions about that multiset.
-Informally, the representation should serve as a good approximation of the multiset, at least with respect to the allowed questions.
-\begin{definition}[Data Structure] \rm
+\heading{Data structures.}  We being by defining a general primitive
+that produces a representation of a given multiset, and provides a
+mechanism to answer a specified collection of questions about that
+multiset.  Informally, the representation should serve as a good
+approximation of the multiset, at least with respect to the allowed
+questions.
+\begin{definition}[Data structure] \rm
 Fix a non-empty set~$\univ$. A \emph{static data structure} (over universe~$\univ$)
@@
 \begin{itemize}
-\item $\Sigma$ is the \emph{representation alphabet}
-\item $\Gamma$ is the set of possible \emph{query answers}
-\item $\calS$ is a set  of multisets over universe~$\univ$
-\item $\mathcal{Q}=\{q \colon \mathcal{S} \to \Gamma\}$ is a set of supported \emph{queries}
-\item $\Rep \colon \mathcal{S} \to \Sigma^* \times \bits^* \times \bits^*$ is a randomized \emph{representation algorithm}, taking as input $S \in \mathcal{S}$, and outputting a \emph{representation} $M \in \Sigma^*$, \emph{private side-information} $\privaux \in \bits^*$, and \emph{public side-information} $\pubaux \in \bits^*$
-\item $\Qry\colon \Sigma^* \times \bits^* \times \calQ \to \Gamma$ is a deterministic \emph{query-evaluation} algorithm, taking as input $M, \privaux, q$, and returns \emph{answer} $a \in \Gamma$.
+\item $\Sigma$ is the \emph{representation alphabet}. \jnote{Is
+    there any reason not to simply fix this to $\{0,1\}$?}
+\item $\Gamma$ is the set of possible \emph{query answers}.
+    \jnote{Do we need this for any reason?}
+\item $\calS$ is a set  of multisets over universe~$\univ$.
+\item $\mathcal{Q}=\{q \colon \mathcal{S} \to \Gamma\}$ is a set
+    of supported \emph{queries}.
+\item $\Rep \colon \mathcal{S} \to \Sigma^* \times \bits^*
+    \times \bits^*$ is a randomized \emph{representation
+    algorithm}, taking as input $S \in \mathcal{S}$, and
+    outputting a \emph{representation} $M \in \Sigma^*$,
+    \emph{private side information} $\privaux \in \bits^*$, and
+    \emph{public side information} $\pubaux \in \bits^*$.
+\item $\Qry\colon \Sigma^* \times \bits^* \times \calQ \to
+    \Gamma$ is a deterministic \emph{query-evaluation}
+    algorithm, taking as input $M, \privaux, q$, and returns
+    \emph{answer} $a \in \Gamma$. \jnote{Should take $\pubaux$
+    as input also.}
 \end{itemize}
@@
 \end{definition}
-\tsnote{I implemented this change.}\tsnote{I'm now leaning towards having $\Rep$ output~$M$ and explicit pubic/private auxillary data.
-Pushing secrets into~$M$ makes it more difficult to capture (for example) the Neidermeier et al.\ attacks in our privacy notions; see Figure~\ref{fig:privacy}.
-In those attacks, the adversary would get the bitarray (which one naturally thinks of as~$M$) but not the secret keys for the PRFs/hash functions.
-You could say that the bitarray is put in $\aux$ and that~$M$ \emph{only} contains the secret keys, but this is unnatural.}
-All of the data structures that we will consider have the property that~$|M|$ does not depend on the coins of~$\Rep$.
-Thus we assume that~$|M|$ depends only on~$|S|$.
-In general this need not be true, but the assumption does not restrict our syntax from capturing natural constructions (e.g., those seen in practice), and it makes it easier to state our security notions.
+\tsnote{I implemented this change.}\tsnote{I'm now leaning towards
+having $\Rep$ output~$M$ and explicit pubic/private auxillary data.
+Pushing secrets into~$M$ makes it more difficult to capture (for
+example) the Neidermeier et al.\ attacks in our privacy notions; see
+Figure~\ref{fig:privacy}.  In those attacks, the adversary would get
+the bitarray (which one naturally thinks of as~$M$) but not the
+secret keys for the PRFs/hash functions.  You could say that the
+bitarray is put in $\aux$ and that~$M$ \emph{only} contains the
+secret keys, but this is unnatural.} All of the data structures that
+we will consider have the property that~$|M|$ does not depend on the
+coins of~$\Rep$. Thus we assume that~$|M|$ depends only on~$|S|$. In
+general this need not be true, but the assumption does not restrict
+our syntax from capturing natural constructions (e.g., those used in
+practice), and it makes it easier to state our security notions.
 
 \begin{definition}[Error probability and rate] \rm
-Fix a data structure $\setprim=(\Sigma,\Gamma,\calS,\calQ,\Rep, \Qry)$.
-Let $\mathrm{Err}(S,q,M,\privaux)$ be a predicate that is true iff $\Qry(M, \privaux, q) \neq q(S)$.  Then a data structure
-has \emph{error-probability} $\epsilon$ if
-$\max_{S,q}\Pr[(M,\pubaux,\privaux) \getsr \Rep(S) : \mathrm{Err}(S,q,M,\privaux)=1 ] \leq \epsilon$
-where the maximum is over $S \in \mathcal{S}$ and $q \in \mathcal{Q}$.  
+Fix a data structure $\setprim=(\Sigma,\Gamma,\calS,\calQ,\Rep,
+\Qry)$. Let $\mathrm{Err}(S,q,M,\privaux)$ be a predicate that is
+true iff $\Qry(M, \privaux, q) \neq q(S)$.  Then a data structure
+has \emph{error probability} $\epsilon$ if
+$\max_{S,q}\Pr[(M,\pubaux,\privaux) \getsr \Rep(S) :
+\mathrm{Err}(S,q,M,\privaux)=1 ] \leq \epsilon$.
 %
-Relatedly, it has \emph{error-rate} $\tilde{\epsilon}$ if
-$\max_{S}\Pr[(M,\pubaux,\privaux) \getsr \Rep(S);\, q \getsr \calQ : \mathrm{Err}(S,q,M,\privaux)=1] \leq \tilde{\epsilon}$.
-\hfill\dqed
+It has \emph{error rate} $\tilde{\epsilon}$ if
+$\max_{S}\Pr[(M,\pubaux,\privaux) \getsr \Rep(S);\, q \getsr \calQ :
+\mathrm{Err}(S,q,M,\privaux)=1] \leq \tilde{\epsilon}$. \hfill\dqed
 \end{definition}
 
-\noindent
-The definition can be lifted to the random-oracle model
-by giving $\Rep, \Qry$ access to a random oracle. In that case,
-the probabilities defining the error-probability and error-rate are also taken over choice of the random oracle.
+\noindent The definition can be lifted to the random-oracle model by
+giving $\Rep, \Qry$ access to a random oracle. In that case, the
+probabilities defining the error probability and error rate are also
+taken over choice of the random oracle.
 
-We will sometimes say that a data structure is $(1-\epsilon)$-correct, meaning it has error-probability~$\epsilon$.
-Note that $1-\epsilon$ is a worst-case lower bound on the correctness of the data structure.
+We will sometimes say that a data structure is
+$(1-\epsilon)$-correct, meaning it has error probability~$\epsilon$.
+Note that $1-\epsilon$ is a worst-case lower bound on the
+correctness of the data structure.
 
@@
 \def\bin{{\sf Bin}}
-\heading{Trivial attacks, and error-probability vs.\ error-rate. } 
-Let~$\Pi$ be a scheme that is $(1-\epsilon)$-correct, and consider an attack that 
-asks random queries $q_1,q_2,\ldots,q_T$, i.e., uniform samples from~$\calQ$.
+\heading{Trivial attacks, and error probability vs.\ error rate. }
+Let~$\Pi$ be a scheme that is $(1-\epsilon)$-correct, and consider
+an attack that asks random queries $q_1,q_2,\ldots,q_T$, i.e.,
+uniform samples from~$\calQ$.
 %The expected number of random queries needed to
@@
 
-This example is contrived, but it highlights the important difference
-between error-probability and error-rate.  In particular, the
-error-probability~$\epsilon$ is measured only over the coins
-of~$\Rep$, for a fixed~$S$ and query~$q$.
-Once the coins of~$\Rep$ are fixed, it is not straightforward how to
-connect~$\epsilon$ to events that depend on other sources of
-randomness. \tsnote{Not sure if there's more to say in this section, or if what's here is already too much.}
+This example is contrived, but it highlights the important
+difference between error probability and error rate.  In particular,
+the error probability~$\epsilon$ is measured only over the coins
+of~$\Rep$, for a fixed~$S$ and query~$q$. Once the coins of~$\Rep$
+are fixed, it is not straightforward how to connect~$\epsilon$ to
+events that depend on other sources of randomness. \tsnote{Not sure
+if there's more to say in this section, or if what's here is already
+too much.}
 
-\heading{Set-multiplicity Data Structures. }
-Our particular focus will be on data structures that support multiplicity queries, of which set-membership queries are a special case.  
-\begin{definition} A \emph{set-multipicity data structure} is a data structure with $D=\mathbb{N}$ and where $\calQ=\{q_x \,|\, x \in \univ\}$ where $q_x(S)$ is defined to be the multiplicity of~$x$ in the multiset~$S$.
-\hfill\dqed
+\heading{Set-multiplicity Data Structures. } Our particular focus
+will be on data structures that support multiplicity queries, of
+which set-membership queries are a special case.
+\begin{definition} A \emph{set-multiplicity data structure} is a data
+structure with $D=\mathbb{N}$ \jnote{Notation. (Anyway, I don't
+think we need an explicit symbol for the range of queries.)} and
+where $\calQ=\{q_x \,|\, x \in \univ\}$ where $q_x(S)$ is defined to
+be the multiplicity of~$x$ in the multiset~$S$. \hfill\dqed
 \end{definition}
@@
 %\heading{Bloom Filters and Related Data Structures. }
-It is not hard to see Bloom filters are one possible instantiation a set-multiplicity data structure.
-Fix an $n \geq 0$, let $\mathcal{S}=[\univ]^n$, and let $\Sigma=\Gamma=\bits$.  
-Define the queries so that $q_x(S)=1$ if $x \in S$, and 0 otherwise.
-Define algorithm~$\Rep$, with functions $k=k(|S|), m=m(|S|)$ and a description of a hash function family~$\mathcal{H}=\{h \colon \univ \to \{1,2,\ldots,m\}\}$ hardwired into it, to sample hash functions $h_1, \ldots, h_k$ from~$\mathcal{H}$ and then compute an $m$-bit array in the standard way.
-It sets $\privaux=\pubaux = (h_1, \ldots, h_k)$ and~$M$ to be the bit array, and returns these.
-The algorithm~$\Qry$ is defined so that, on input $(M,\privaux,q_x)$, it returns the minimum of the values (either 0 or 1) held at $M[h_1(x)],\ldots,M[h_k(x)]$.
-We note that, while our error-probability and error-rate do not distinguish among ``types'' of errors, they also do not preclude instantiations (like the classical Bloom filter) that admit only one type of error, e.g.
+It is not hard to see Bloom filters are one possible instantiation a
+set-multiplicity data structure. Fix an $n \geq 0$, let
+$\mathcal{S}=[\univ]^n$, and let $\Sigma=\Gamma=\bits$. Define the
+queries so that $q_x(S)=1$ if $x \in S$, and 0 otherwise.  Define
+algorithm~$\Rep$, with functions $k=k(|S|), m=m(|S|)$ and a
+description of a hash function family~$\mathcal{H}=\{h \colon \univ
+\to \{1,2,\ldots,m\}\}$ hardwired into it, to sample hash functions
+$h_1, \ldots, h_k$ from~$\mathcal{H}$ and then compute an $m$-bit
+array in the standard way.  It sets $\privaux=\pubaux = (h_1,
+\ldots, h_k)$ and~$M$ to be the bit array, and returns these.  The
+algorithm~$\Qry$ is defined so that, on input $(M,\privaux,q_x)$, it
+returns the AND of the values (either 0 or 1) held at
+$M[h_1(x)],\ldots,M[h_k(x)]$.  We note that, while our error
+probability and error rate do not distinguish among ``types'' of
+errors, they also do not preclude instantiations (like the classical
+Bloom filter) that admit only one type of error, e.g.
 false-positives.
 
-As a simple extension, consider $\Sigma=\mathbb{N}$ and modify the basic Bloom filter so that it that stores counters, rather than bits, at each position in an array.
-In particular, for each~$x \in S$ the $\Rep$~algorithm increments the counters stored at positions $h_1(x), h_2(x), \ldots, h_k(x)$, returns the final array of counters as~$M$.
-The $\Qry$-algorithm remains the same.
-Such a construction gives a static version of a counting Bloom filter~\cite{xxx}.
-We will capture dynamic versions, as well as count-min sketches~\cite{xxx}, scalable Bloom filters~\cite{xxx}, etc., in a later section.
+As a simple extension, consider $\Sigma=\mathbb{N}$ and modify the
+basic Bloom filter so that it that stores counters, rather than
+bits, at each position in an array.  In particular, for each~$x \in
+S$ the $\Rep$~algorithm increments the counters stored at positions
+$h_1(x), h_2(x), \ldots, h_k(x)$, returns the final array of
+counters as~$M$.  The $\Qry$-algorithm remains the same. Such a
+construction gives a static version of a counting Bloom
+filter~\cite{xxx}.  We will capture dynamic versions, as well as
+count-min sketches~\cite{xxx}, scalable Bloom filters~\cite{xxx},
+etc., in a later section.
 

### 2016-08-17 Theorem1_FP.tex
finished cleaning up Theorem 1
Proof 2 in old syntax, Proof 1 in new syntax(not complete)

@@
-\acnote{I am moving comments to end of the proof in tex file and commenting them as the labels are getting mangled}
+%\acnote{I am moving comments to end of the proof in tex file and commenting them as the labels are getting mangled}
 \heading{Linear-PRF construction. }
@@
 consisting of~$q$ attempts.
-%Before giving the proof, we note that  $(1-e^{-kn/m})^k \rightarrow 0$ as the ratio between the bit-length of the representation~$M$ and the size of the represented set~$S$, i.e.,$m/n$ tends to $\infty$.
-%
+
 \begin{proof}[\Cref{thm1}]
@@
 
- In $\game{1}(A)$, $F_{K_1}$ is replaced by a random function, whereas in $\game{2}(A)$, both $F_{K_0}$ and $F_{K_1}$ are replaced by random functions as shown below.
-Here, $\rho_1$ and $\rho_2$ are random functions sampled from $\Func{\univ,[m]}$.
-%\begin{align*}
-%\game{1}(A)\, : \, h_j(x) &= ( F_{K_0}(x) + j\cdot \rho_2(x)) \bmod m\\
-%\game{2}(A)\, : \, h_j(x) &= ( \rho_1(x) + j \cdot \rho_2(x)) \bmod m
-%\end{align*}
+ In $\game{1}(A)$, $F_{K_1}$ is replaced by a random function, whereas in $\game{2}(A)$, both $F_{K_0}$ and $F_{K_1}$ are replaced by random functions.
 
@@
 $\adversaryv{B_1^{\calO}}$\\
-$K_1 \getsr \calK $\\
-$S \getsr \distr{\univ}{n}$\\
-$M \getsr \Rep^{\HashOracle}(S)$\\
-Run~$A(S)$\\
-When $A$ asks $\QryOracle(x)$:\\
-$\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
-When $A$ halts with output $\calZ'$: \\
-\nudge if $|\calZ'| < r$ or $\calZ' \cap \calS \neq \emptyset$ then \\
-\nudge \nudge Ret 0\\
-\nudge if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
-\nudge \nudge Ret 0\\
-\nudge Ret 1\\\\
+$S \getsr \distr{\calS}{}$\\
+$\err \gets 0$\\
+$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+Run~$A(S, \pubaux)$\\
+When $A$ asks $\TestOracle(q)$:\\
+\nudge $a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
+\nudge if $a \neq q(S)$ then \\
+\nudge \nudge $\err \gets \err +1$\\
+Return~$(a,\err )$
+When $A$ halts: \\
+if $\err  < r$ then Return 0\\
+Return 1\\\\
+%
 \oracle{$\HashOracle(x)$}\\
@@
 $\adversaryv{B_2^{\calO}}$\\
-%$d \getsr \bits $\\
-%$\rho_2 \getsr Func(\univ, [m])$ \\
-$S \getsr \distr{\univ}{n}$\\
-$M \getsr \Rep^{\HashOracle}(\calS)$\\
-Run $A(S)$\\
-When $A$ asks $\QryOracle(x)$:\\
-$\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
-When $A$ halts with output $\calZ'$: \\
-\nudge if $|\calZ'| < r$ or $\calZ' \cap \calS \neq \emptyset$ then \\
-\nudge \nudge Ret 0\\
-\nudge if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
-\nudge \nudge Ret 0\\
-\nudge Ret 1\\\\
+$S \getsr \distr{\calS}{}$\\
+$\err \gets 0$\\
+$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+Run~$A(S, \pubaux)$\\
+When $A$ asks $\TestOracle(q)$:\\
+\nudge $a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
+\nudge if $a \neq q(S)$ then \\
+\nudge \nudge $\err \gets\err +1$\\
+Return~$(a,\err )$
+When $A$ halts: \\
+if $\err  < r$ then Return 0\\
+Return 1\\\\
 \oracle{$\HashOracle(x)$}\\
-%if $d=0$\\
 $a \getsr [m]$\\
@@
 $T[x] \gets a$\\
-$\mathrm{Ret} \nudge \calO(x) + i\cdot a$, for $i\in[1,k]$
+Ret  $\calO(x) + i\cdot a$, for $i\in[1,k]$
 }
@@
 By a standard conditioning of the PRF advantage, we have 
-%From \Cref{eq:m1,eq:m2,eq:m3,eq:m4},
-%\begin{align}
-%\nonumber \Prob{\ExpPRF{F}{B_1} = 1} &= .5\Prob{\ExpPRF{F}{B_1}=1\,|\,b=0} + .5\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=1}\\
-%\nonumber 2\Prob{\ExpPRF{F}{B_1} = 1} &= 1-\Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1}\\
-%\nonumber (2\Prob{\ExpPRF{F}{B_1} = 1} - 1)  &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1}\\
-% \AdvPRF{F}{B_1} &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1} \label{eq:11}\\
-%\nonumber& &\\
-%\nonumber \Prob{\ExpPRF{F}{B_2} = 1} &= .5\Prob{\ExpPRF{F}{B_2}=1\,|\,b=0} + .5\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=1}\\
-%\nonumber 2\Prob{\ExpPRF{F}{B_2} = 1} &= 1-\Prob{\game{2}(A)=1} + \Prob{\game{1}(A)=1}\\
-%\nonumber (2\Prob{\ExpPRF{F}{B_2} = 1} - 1)  &= \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1}\\
-% \AdvPRF{F}{B_2} &= \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1} \label{eq:12}
-%\end{align}
-%\noindent
-%Adding \Cref{eq:11,eq:12}, we have
 \begin{equation*}
@@
 ``identical-untill-$\bad$''~\cite{BeRo-gameplaying}.  In particular,
-in $\game{4}$ returns 0 when $\game{3}$ would have returned 1 (i.e.,
-the adversary outputs~$r$ false-positives) but $\bad=\true$.  
+in $\game{4}$, $A$ returns 0 when $\game{3}$ would have returned 1 (i.e.,
+the adversary outputs~$r$ false-positives, but $\bad=\true$).  
 Moreover,  $\game{4}(A)$ returning 1 implies that $\bad$ is never set to $\true$. Therefore,
@@
 \begin{equation*}
-\Prob{\game{3}(A)=1} = \frac{1}{\dbinom{q}{r}}\Prob{\game{4}(A)=1}
+\Prob{\game{4}(A)=1} = \frac{1}{\dbinom{q}{r}}\Prob{\game{3}(A)=1}
 \end{equation*}
@@
 \underline{\game{0}(A)}\\
-$K_1, K_2 \getsr \calK$\\
-$S \getsr \distr{\univ}{n}$\\
-$M \getsr \Rep^{\HashOracle}(\calS)$\\
-$\calZ \getsr A^{\QryOracle}(\calS)$\\
-if $|\calZ| < r$ or $\calZ \cap \calS \neq \emptyset$ then \\
-\nudge Ret 0\\
-if $\exists z \in \calZ$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
-\nudge Ret 0\\
-Ret 1\\\\
+$S \getsr \distr{\calS}{}$\\
+$\err \gets 0$\\
+$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+$z \getsr A^{\TestOracle}(S,\pubaux)$\\
+if $\err  < r$ then Return 0\\
+Return 1\\\\
 %
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,x)$\\\\
+\oracle{$\TestOracle(q)$}\\
+$a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
+if $a \neq q(S)$ then \\
+\nudge $\err \gets\err +1$\\
+Return~$(a,\err )$
 %
@@
 \underline{\game{1}(A)}\\
-$K_1 \getsr \calK$\\
 $\rho \getsr \Func{\univ,[m]}$\\
-$S \getsr \distr{\univ}{n}$\\
-$M \getsr \Rep^{\HashOracle}(\calS)$\\
-$\calZ \getsr A^{\QryOracle}(\calS)$\\
-if $|\calZ| < r$ or $\calZ \cap \calS \neq \emptyset$ then \\
-\nudge Ret 0\\
-if $\exists z \in \calZ$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
-\nudge Ret 0\\
-Ret 1\\\\
+$S \getsr \distr{\calS}{}$\\
+$\err \gets 0$\\
+$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+$z \getsr A^{\TestOracle}(S,\pubaux)$\\
+if $\err  < r$ then Return 0\\
+Return 1\\\\
 %
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,x)$\\\\
+\oracle{$\TestOracle(q)$}\\
+$a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
+if $a \neq q(S)$ then \\
+\nudge $\err \gets\err +1$\\
+Return~$(a,\err )$
 %
@@
 $\rho_1,\rho_2 \getsr \Func{\univ,[m]}$\\
-$S \getsr \distr{\univ}{n}$\\
-$M \getsr \Rep^{\HashOracle}(\calS)$\\
-$\calZ \getsr A^{\QryOracle}(\calS)$\\
-if $|\calZ| < r$ or $\calZ \cap \calS \neq \emptyset$ then \\
-\nudge Ret 0\\
-if $\exists z \in \calZ$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
-\nudge Ret 0\\
-Ret 1\\\\
+$S \getsr \distr{\calS}{}$\\
+$\err \gets 0$\\
+$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+$z \getsr A^{\TestOracle}(S,\pubaux)$\\
+if $\err  < r$ then Return 0\\
+Return 1\\\\
 %
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,x)$\\\\
+\oracle{$\TestOracle(q)$}\\
+$a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
+if $a \neq q(S)$ then \\
+\nudge $\err \gets\err +1$\\
+Return~$(a,\err )$
 %
@@
 \underline{{$\game{3}(A)$},\fbox{$\game{4}(A)$}}\\
-$c\gets 0$, $\bad\gets\false$\\
+$c\gets 0$, $\bad \gets \false$\\
 $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
-$S \getsr \distr{\univ}{n}$\\
-$M \getsr \Rep^{\HashOracle}(\calS)$\\
-$\calZ \getsr A^{\QryOracle}(\calS)$\\
-if $|\calZ| < r$ or $\calZ \cap \calS \neq \emptyset$ then Ret 0\\
-if $\forall z \in \calZ,\,\Qry^{\HashOracle}(M,z)=1$ then \\
-\nudge if $\bad=\true$ then \fbox{Ret 0}\\
-\nudge Ret 1\\
-Ret 0\\\\
-
-\oracle{$\QryOracle(x)$}\\
+$S \getsr \distr{\calS}{}$\\
+$\err \gets 0$\\
+$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+$z \getsr A^{\TestOracle}(S,\pubaux)$\\
+if $\err  < r$ then Return 0\\
+Return 1\\\\
+%
+\oracle{$\TestOracle(q)$}\\
 $c \gets c+1$\\
-$v \gets \Qry^{\HashOracle}(M,x)$\\
-if $c \in \mathcal{I}$ and $v\neq 1$ then\\
+$v \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
+if $c \in \mathcal{I}$ and $a \neq q(S)$ then \\
 \nudge $\bad \gets \true$ \\
-if $c \not\in \mathcal{I}$ and $v\neq 0$ then\\
+if $c \not\in \mathcal{I}$ and $a \neq q(S)$ then \\
 \nudge $\bad \gets \true$\\
-Ret~$v$\\\\
+\nudge $\err \gets\err +1$\\
+Return~$(v,\err )$
 %
@@
 
-%\caption{$\Cref{thm1}:\game{5}(A)$ in game playing argument}\label{fig:game5}
-%\begin{figure}
-%\centering
-%\fpage{0.8}
-%{
-%\hpagess{0.5}{0.4}{
-%\underline{$\game{5}(A)$}\\
-%$c \gets 0$\\
-%$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
-%$\calY \gets \emptyset$\\
-%$S \getsr \distr{\univ}{n}$\\
-%$M \getsr \Rep^{\HashOracle}(\calS)$\\
-%$\calZ \getsr A^{\QryOracle}(\calS)$\\
-%if $|\calY| < r$ or $\calY \cap \calS \neq \emptyset$ then\\
-%\nudge Ret 0\\
-%if $\forall y \in \calY,\,\Qry^{\HashOracle}(M,y)=1$ then \\
-%\nudge Ret 1\\
-%Ret 0
-%}
-%
-%{
-%\oracle{$\QryOracle(x)$}\\
-%$c \gets c+1$\\
-%if $c \in \mathcal{I}$ then\\
-%\nudge $\calY \gets \calY \cup {x}$\\
-%\nudge Ret 1\\
-%else\\
-%\nudge Ret 0 \\\\
-%
-%\oracle{$\HashOracle(x)$}\\
-%$a,b \getsr [m]$\\
-%for $i = 1$ to~$k$\\
-%\nudge $v_i = a+i \cdot b \bmod m$\\
-%Ret $\left(v_1,\ldots,v_k\right)$
-%}
-%}
-%\caption{\Cref{thm1}:$\game{5}(A)$ in game playing argument}\label{fig:game5}
-%\end{figure}
-
 %\caption{PRF game}\label{fig:prf}
@@
 $K \getsr \calK $\\
-$\rho \getsr \Func(\univ,[m])$\\
+$\rho \getsr \Func{\univ,[m]}$\\
 $b \getsr \bits$\\
@@
 }
-\caption{The PRF experiment for a function family $F \colon \calK
-  \times \calX \to [m]$. }\label{fig:prf}
+\caption{PRF security notion}\label{fig:prf}
 \end{figure}
@@
 $c \gets 0$, $\calX \gets \emptyset$\\
+$\err \gets 0$\\
 $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
@@
 \nudge \nudge $r \gets 1$\\
-\nudge Ret $r$\\
+\nudge \nudge $\err \gets \err + 1$\\
+\nudge Ret $(r,\err )$\\
 When $A$ halts:\\
@@
 \noindent
+%\caption{$\Cref{thm1}:\game{5}(A)$ in game playing argument}\label{fig:game5}
+%\begin{figure}
+%\centering
+%\fpage{0.8}
+%{
+%\hpagess{0.5}{0.4}{
+%\underline{$\game{5}(A)$}\\
+%$c \gets 0$\\
+%$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
+%$\calY \gets \emptyset$\\
+%$S \getsr \distr{\univ}{n}$\\
+%$M \getsr \Rep^{\HashOracle}(\calS)$\\
+%$\calZ \getsr A^{\QryOracle}(\calS)$\\
+%if $|\calY| < r$ or $\calY \cap \calS \neq \emptyset$ then\\
+%\nudge Ret 0\\
+%if $\forall y \in \calY,\,\Qry^{\HashOracle}(M,y)=1$ then \\
+%\nudge Ret 1\\
+%Ret 0
+%}
+%
+%{
+%\oracle{$\QryOracle(x)$}\\
+%$c \gets c+1$\\
+%if $c \in \mathcal{I}$ then\\
+%\nudge $\calY \gets \calY \cup {x}$\\
+%\nudge Ret 1\\
+%else\\
+%\nudge Ret 0 \\\\
+%
+%\oracle{$\HashOracle(x)$}\\
+%$a,b \getsr [m]$\\
+%for $i = 1$ to~$k$\\
+%\nudge $v_i = a+i \cdot b \bmod m$\\
+%Ret $\left(v_1,\ldots,v_k\right)$
+%}
+%}
+%\caption{\Cref{thm1}:$\game{5}(A)$ in game playing argument}\label{fig:game5}
+%\end{figure}
+
+%From \Cref{eq:m1,eq:m2,eq:m3,eq:m4},
+%\begin{align}
+%\nonumber \Prob{\ExpPRF{F}{B_1} = 1} &= .5\Prob{\ExpPRF{F}{B_1}=1\,|\,b=0} + .5\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=1}\\
+%\nonumber 2\Prob{\ExpPRF{F}{B_1} = 1} &= 1-\Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1}\\
+%\nonumber (2\Prob{\ExpPRF{F}{B_1} = 1} - 1)  &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1}\\
+% \AdvPRF{F}{B_1} &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1} \label{eq:11}\\
+%\nonumber& &\\
+%\nonumber \Prob{\ExpPRF{F}{B_2} = 1} &= .5\Prob{\ExpPRF{F}{B_2}=1\,|\,b=0} + .5\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=1}\\
+%\nonumber 2\Prob{\ExpPRF{F}{B_2} = 1} &= 1-\Prob{\game{2}(A)=1} + \Prob{\game{1}(A)=1}\\
+%\nonumber (2\Prob{\ExpPRF{F}{B_2} = 1} - 1)  &= \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1}\\
+% \AdvPRF{F}{B_2} &= \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1} \label{eq:12}
+%\end{align}
+%\noindent
+%Adding \Cref{eq:11,eq:12}, we have
+%Before giving the proof, we note that  $(1-e^{-kn/m})^k \rightarrow 0$ as the ratio between the bit-length of the representation~$M$ and the size of the represented set~$S$, i.e.,$m/n$ tends to $\infty$.
+%
+%\begin{align*}
+%\game{1}(A)\, : \, h_j(x) &= ( F_{K_0}(x) + j\cdot \rho_2(x)) \bmod m\\
+%\game{2}(A)\, : \, h_j(x) &= ( \rho_1(x) + j \cdot \rho_2(x)) \bmod m
+%\end{align*}
 

### 2016-08-17 Theorem2_FP.tex
Proof 2 in old syntax, Proof 1 in new syntax(not complete)

@@
 \[
-\AdvFPSecHash{B_\mathrm{ds},t}{A} =  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k  \right)^r
+\AdvFPSecHash{B_\mathrm{ds},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
 \]
@@
 \end{equation}
-\noindent
-In $\game{1}(A)$, $A$ attacks a different filter $\tilde{B}_\mathrm{ds}$, in which $F_K$ is replaced by a random function $\rho$ sampled from $\Func{\univ,[m]}$.
-$\game{2}(A)$ and $\game{3}(A)$ on the other hand use lazy sampling in $\Hash$ to select random values from $[m]$.
-This makes $\game{2}(A)$ and $\game{3}(A)$ identical to $\game{3}(A)$ and $\game{4}(A)$ of previous theorem, and hence the analysis and results of \Cref{thm1} apply to this theorem as well.
+
+Let $B$ be a prf-adversary as shown in \Cref{fig:2TD}. Based on its challenge bit $b$, it exactly simulates $\game{0}$ or $\game{1}$. So,
+\begin{align*}
+\Prob{\ExpPRF{F}{B} = 1\,|\,b=1} &= \Prob{\game{0}(A)=1} \\%\label{eq:m1}\\
+\Prob{\ExpPRF{F}{B} = 1\,|\,b=0} &= 1-\Prob{\game{1}(A)=1}
+\end{align*}
+
+By a standard conditioning of PRF advantage, we have
+
+\begin{equation*}
+\Prob{\game{0}(A)=1} = \AdvPRF{F}{B} + \Prob{\game{1}(A)=1}%\label{eq:13}
+\end{equation*}
+
+In $\game{1}$, $A$ attacks a different filter $\tilde{B}_\mathrm{ds}$, in which $F_K$ is replaced by a random function.
+$\game{2}$ and $\game{3}$ on the other hand use lazy sampling in $\Hash$ to select random values from $[m]$.
+This makes $\game{2}$ and $\game{3}$ identical to $\game{3}$ and $\game{4}$ of previous theorem, and hence the analysis and results of \Cref{thm1} apply to this theorem as well.
 Therefore,
-\begin{align}
-\Prob{\game{2}(A)=1 \wedge \neg\bad} &= \Prob{\game{2}(A)=1}\Prob{\game{2}(A) : \neg\bad}\label{eq:2T1} \\
-\Prob{\game{1}(A)=1} &= \Prob{\game{2}(A)=1}\label{eq:2T2}
-\end{align}
-From \Cref{eq:2T1,eq:2T2}
-\begin{equation}
-\Prob{\game{2}(A)=1 \wedge \neg\bad} = \Prob{\game{1}(A)=1}\Prob{\game{2}(A) : \neg\bad}\label{eq:2T3}
-\end{equation}
-\noindent
-Also,
-\begin{equation}
-\Prob{\game{3}(A)=1} = \Prob{\game{2}(A)=1 \wedge \neg\bad}\label{eq:2T4}
-\end{equation}
-\noindent
-Using \Cref{eq:2T3} in \Cref{eq:2T4}
-\begin{equation}
-\Prob{\game{3}(A)=1} = \Prob{\game{1}(A)=1}\Prob{\game{2}(A) : \neg\bad}\label{eq:2T5}
-\end{equation}
-\begin{equation}
-\Prob{\game{2}(A) : \neg\bad} = \frac{1}{\dbinom{q}{r}}\label{eq:2T6}
-\end{equation}
-\noindent
-From \Cref{eq:2T5,eq:2T6}
-\begin{align}
-\nonumber \Prob{\game{3}(A)=1} &= \Prob{\game{1}(A)=1}\frac{1}{\dbinom{q}{r}}\\
-\Prob{\game{1}(A)=1} &= \dbinom{q}{r} \times \Prob{\game{3}(A)=1} \label{eq:2T7}
-\end{align}
+\begin{align*}
+\Prob{\game{1}(A)=1} = \Prob{\game{2}(A)=1}\\
+\Prob{\game{3}(A)=1} = \frac{1}{\dbinom{q}{r}}\Prob{\game{2}(A)=1}
+\end{align*}
 
 Let $D$ be a non-adaptive adversary (shown in \Cref{fig:2TD}) that finds ~$r$ false positives against $\tilde{B}_{\mathrm{ds}}$.
-As discussed in the previous theorem, if $A$ wins $\game{3}(\cdot)$, then $D$ wins $\ExpFPSecHash{\tilde{B}_{\mathrm{ds}},r}{\cdot}$ game.
+As discussed in the previous theorem, if $A$ wins $\game{3}$, then $D$ wins $\ExpFPSecHash{\tilde{B}_{\mathrm{ds}},r}{\cdot}$ game.
 So,
-\begin{equation}
+\begin{equation*}
 \AdvFPSecHash{\tilde{B}_{\mathrm{ds}},r}{D} = \Prob{\game{3}(A) = 1}\label{eq:2T8}
-\end{equation}
-Since, $D's$ $\HashOracle$ returns $k$ random values which are mutually independent of each other, for $r=1$, $\AdvFPSecHash{\tilde{B}_{\mathrm{ds}},1}{D}$ is same as the false positive probability ($(1-e^{-kn/m})^k$) of a classic Bloom filter.
-Also, as discussed in the previous theorem, for $r \neq 1$, the event of getting a false positive is independent of the index of the query for a non-adaptive adversary.
+\end{equation*}
+Note that like $\tilde{B}_{\mathrm{lin}}$, $\tilde{B}_{\mathrm{ds}}$ is the scheme that is analyzed in the classical Bloom filter literature.
+So, for a non-adaptive adversary $D$ and $r=1$, the upper bound on false-positive probability of a classical Bloom filter applies to $\tilde{B}_{\mathrm{ds}}$ as well.
+For $r > 1$, based on the assumption that $A$ makes no pointless queries, the queries made by $A$ as well as the elements returned by $D$ are distinct and not elements of the original set $S$.
+Also, since $\game{3}$ uses independent random functions, the event of getting a false positive is independent of the index of the query.
 So,
-\begin{equation}
-\AdvFPSecHash{\tilde{B}_{\mathrm{ds}},r}{D} =   \left( (1-e^{-kn/m})^k  \right)^r \label{eq:2T8a}
-\end{equation}
+\begin{equation*}
+\AdvFPSecHash{\tilde{B}_{\mathrm{ds}},r}{D} =   {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
+\end{equation*}
 \noindent
-From \Cref{eq:2T7,eq:2T8,eq:2T8a}
-\begin{equation}
-\Prob{\game{1}(A)=1} = \dbinom{q}{r} \times \left( (1-e^{-kn/m})^k  \right)^r \label{eq:2T8b}
-\end{equation}
+To summarize, we have
+\[
+\AdvFPSecHash{B_\mathrm{ds},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
+\]
+which is the bound claimed in the theorem statement. \hfill \qed
 
@@
 }
-\caption{\Cref{thm2}:Game playing argument}\label{fig:Game}
+\caption{\Cref{thm2}: Game playing argument}\label{fig:Game}
 \end{figure}
@@
 $c \gets 0$\\
+$\calX \gets \emptyset$\\
 $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
+Run $A(S)$\\
 When $A$ asks $\QryOracle(x)$:\\
@@
 \nudge if $c \in \mathcal{I}$\\
-\nudge \nudge $r \gets \QryOracle(x)$\\
+\nudge \nudge $\calX \gets \calX \cup \{x\}$\\
+\nudge \nudge $r \gets 1$\\
 \nudge Ret $r$\\
-When $A$ halts with output $\calZ$\\
-\nudge Ret $\calZ$\\\\
+When $A$ halts:\\
+\nudge Ret $\calX$\\\\
 %
-\oracle{$\QryOracle(x)$}\\
- Ret $\Qry^{\HashOracle}(M,x)$\\\\
+%\oracle{$\QryOracle(x)$}\\
+% Ret $\Qry^{\HashOracle}(M,x)$\\\\
 %
-\oracle{$\HashOracle(x)$}\\
-for $j = 1$ to~$k$\\
-\nudge $v_j = \rhoK $\\
-Ret $\left(v_1,\ldots,v_k\right)$
+%\oracle{$\HashOracle(x)$}\\
+%for $j = 1$ to~$k$\\
+%\nudge $v_j = \rhoK $\\
+%Ret $\left(v_1,\ldots,v_k\right)$
 }
 }
-\caption{PRF adversary $B$ simulating $\game{1}(A)$ and $\game{2}(A)$, and non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:2TD}
+\caption{\Cref{thm2}: \emph{Left}:PRF adversary $B$ simulating $\game{1}(A)$ and $\game{2}(A)$.\emph{Right}: Non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:2TD}
 \end{figure}
 
-Let adversary $B$ be as  shown in \Cref{fig:2TD}.
-It can be observed that, by construction $B$ simulates $\game{0}(A)$ and $\game{1}(A)$ respectively.
-For $b=1$, $B$ wins, if $A$ wins $\game{0}(\cdot)$.
-While for $b = 0$, if $A$ wins $\game{1}(\cdot)$, $B$ wins by returning 0.
-Therefore,
-\begin{align}
-\Prob{\ExpPRF{F}{B} = 1\,|\,b=1} &= \Prob{\game{0}(A)=1}\label{eq:2T9}\\
-\Prob{\ExpPRF{F}{B} = 1\,|\,b=0} &= 1-\Prob{\game{1}(A)=1}\label{eq:2T10}
-\end{align}
-\noindent
-From \Cref{eq:2T9,eq:2T10}
-\begin{align}
-\nonumber \Prob{\ExpPRF{F}{B} = 1} &= .5\Prob{\ExpPRF{F}{B}=1\,|\,b=0} + .5\Prob{\ExpPRF{F}{B} = 1\,|\,b=1}\\
-\nonumber 2\Prob{\ExpPRF{F}{B} = 1} &= 1-\Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1}\\
-\nonumber (2\Prob{\ExpPRF{F}{B} = 1} - 1)  &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1}\\
- \AdvPRF{F}{B} &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1} \label{eq:2T11}
-\end{align}
-\noindent
-Using \Cref{eq:2T0,eq:2T8b} in \Cref{eq:2T11}
-\begin{align}
- \nonumber \AdvPRF{F}{B} &= \AdvFPSecHash{B_\mathrm{ds},r}{A} - \dbinom{q}{r} \times \left( (1-e^{-kn/m})^k  \right)^r \\
-\AdvFPSecHash{B_\mathrm{ds},r}{A} &= \AdvPRF{F}{B} + \dbinom{q}{r} \times \left( (1-e^{-kn/m})^k  \right)^r\label{eq:2T12}
-\end{align}
 \end{proof}
-
-\iffalse
-\acnote{I think we should give a proof of the non-adaptive FP-error bound $(1-e^{-kn/m})^k + O(1/n) $.
-This bound which we picked from KM's theorem 6.2, is a particular case (double hashing scheme).
-Theorem 6.1, on the other hand holds good for any hashing scheme that satisfies Lemma 4.1.
-\\
- I tried to give the FP-bound as a Lemma. 
-\begin{lemma}\label{lemma1}
-Fix $k,m,n >0$. The FP-error of hash-based filter $B_{\mathrm{ds}}$ with hash functions $h_j(x) = \FK, \, j \in [k]$ is upperbounded by $(1-e^{-kn/m})^k + O(1/n)$.
-\end{lemma}
-}
-\acnote{As I had told you earlier, I was not able to understand the proofs of KM paper and now I am stuck in this proof. 
-\begin{proof}($Lemma$ \ref{lemma1})
-In \ref{KM}, $Theorem \,6.1$ gives the upperbound of FP error of any hashing scheme satisfying the 5 conditions enlisted in Lemma 4.1, and all these conditions are satisfied by $B_{\mathrm{ds}}$ as shown below.\\
-Since the hash functions of $B_{\mathrm{ds}}$ provide randomness with domain separation and the number of hash functions are controlled by parameter $j$, condition 1 and 2 are trivially satisfied.
-The last condition is also trivial, since size of $B_{\mathrm{ds}}$ will be some constant multiple of size of $S$, as in the classical bloom filter.\\
-The satisfiability of remaining 2 conditions is non-trivial ...
-\end{proof}}
-%
-\tsnote{Clean up so it looks like the previous theorem.}
-\tsnote{I don't see why this is necessary.  Doesn't it follow from the
-standard bounds on Bloom filters (go look them up and adjust the
-theorem accordingly) which assume that the hash functions are random
-functions?  Whatever argument you use in Theorem 1 to justify
-independence, i.e. turning one non-adaptive FP into~$r$ non-adaptive
-FPs, should apply here, too.  You don't need to understand the KM
-results deeply for this argument, by the way.  You just need to
-understand why you get independence, i.e. why it is that, after the
-set~$S$ has been hashed (hence the bits in~$M$ are set), then the
-probabilities that distinct $x_1,\ldots,x_r$ are each FPs are
-independent.  This really is pretty immediate from the fact that
-$\rho_1,\rho_2$ are random functions and the $x_i$ are distinct.}
-\tsnote{I guess if you want, you could give a 1-to-$r$ lemma for the hash
-  functions (with random functions $\rho1,\rho_2$ used in Theorem 1, prove it, and use that lemma in the
-  proof of Theorem 1.  Then do the parallel thing here, for Theorem 2.}
-\fi

### 2016-08-17 Theorem1_FP.tex
Proof1 new syntax

@@
 Let $B_{\mathrm{lin}}=(\Hash,\Rep,\Qry)$ be defined as follows.
-Fix non-empty sets ~$\univ$, $\calK$ and integers $k,m,n>0$.
+Fix non-empty sets ~$\calK$, $\univ$ and integers $k,m,n>0$.
 Let $F\colon\mathcal{K} \times \univ \to [m]$ be a function family.
@@
 The $\Rep$ and $\Qry$ algorithms are the standard (determinisitic) BF ones.
-The following result shows, informally, that if~$F$ is a good PRF and the (non-adaptive) FP rate is sufficiently small, then $B_\mathrm{lin}$ is secure against adaptive FP-finding adversaries.
+$B_{\mathrm{lin}}$ is in fact one instantiation of a set-multiplicity data structure.
+It must be noted that $B_{\mathrm{lin}}$ admits errors in form of false-positives only.
+So, error rate of $B_{\mathrm{lin}}$ is same as the (non-adaptive) FP rate.
+The following result shows, informally, that if~$F$ is a good PRF and the error rate is sufficiently small, then $B_\mathrm{lin}$ is correct against adaptive error-finding adversaries.
+Henceforth, we refer errors and error-rate in $B_{\mathrm{lin}}$ as false-positives and false-positive(FP) rate, respectively.
 
@@
 \[
-\AdvFPSecHash{B_{\mathrm{lin}},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\AdvCorrect{B_{\mathrm{lin}},\distr{\calS}{},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
 \]
@@
 The proof of the theorem will use a game playing argument as shown in \Cref{fig:Game}.
-$\game{0}(A)$ exactly simulates $\ExpFPSecHash{B_\mathrm{lin},r}{A}$ with hash functions $h_j(x) =  F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$.
+$\game{0}(A)$ exactly simulates $\ExpCorrect{B_\mathrm{lin},\distr{\calS}{},r}{A}$ with hash functions $h_j(x) =  F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$.
 So,
@@
 \begin{equation}
-\AdvFPSecHash{B_{\mathrm{lin}},r}{A} = \Prob{\game{0}(A)=1}\label{eq:0}
+\AdvCorrect{B_{\mathrm{lin}},\distr{\calS}{},r}{A} = \Prob{\game{0}(A)=1}\label{eq:0}
 \end{equation}
@@
 \nudge \nudge $\err \gets \err +1$\\
-Return~$(a,\err )$
+Return~$(a,\err )$\\
 When $A$ halts: \\
-if $\err  < r$ then Return 0\\
-Return 1\\\\
+\nudge if $\err  < r$ then Return 0\\
+\nudge Return 1\\\\
 %
@@
 \nudge \nudge $\err \gets\err +1$\\
-Return~$(a,\err )$
+Return~$(a,\err )$\\
 When $A$ halts: \\
-if $\err  < r$ then Return 0\\
-Return 1\\\\
+\nudge if $\err  < r$ then Return 0\\
+\nudge Return 1\\\\
 \oracle{$\HashOracle(x)$}\\
@@
 
-Recall that adversary~$A$ wins $\ExpFPSecHash{B_{\mathrm{lin}},r}{}$ by finding~$r$ false positives.
+Recall that adversary~$A$ wins $\ExpCorrect{B_{\mathrm{lin}},\distr{\calS}{},r}{}$ by finding~$r$ false positives.
 We can assume, without loss of generality,  that~$A$ halts immediately upon finding its $r$-th false positive.
@@
 Thus we have
-$\Prob{\game{4}(A)=1} =\Prob{\ExpFPSecHash{\tilde{B}_{\mathrm{lin}},r}{D} = 1}$.
+$\Prob{\game{4}(A)=1} =\Prob{\ExpCorrect{\tilde{B}_{\mathrm{lin}},\distr{\calS}{},r}{D} = 1}$.
 
@@
 \[
-\Prob{\ExpFPSecHash{\tilde{B}_{\mathrm{lin}},r}{D} = 1}\leq \left( (1-e^{-kn/m})^k + O(1/n) \right)^r 
+\Prob{\ExpCorrect{\tilde{B}_{\mathrm{lin}},\distr{\calS}{},r}{D} = 1}\leq \left( (1-e^{-kn/m})^k + O(1/n) \right)^r 
 \]
@@
 \[
-\AdvFPSecHash{B_{\mathrm{lin}},r}{A}  \leq  \AdvPRF{F}{B_1} +\AdvPRF{F}{B_2} +\dbinom{q}{r}\left( (1-e^{-kn/m})^k + O(1/n) \right)^r
+\AdvCorrect{B_{\mathrm{lin}},\distr{\calS}{},r}{A}  \leq  \AdvPRF{F}{B_1} +\AdvPRF{F}{B_2} +\dbinom{q}{r}\left( (1-e^{-kn/m})^k + O(1/n) \right)^r
 \]
@@
 \nudge $\err \gets\err +1$\\
-Return~$(a,\err )$
+Return~$(a,\err )$\\\\
 %
@@
 \nudge $\err \gets\err +1$\\
-Return~$(v,\err )$
+Return~$(v,\err )$\\\\
 %
@@
 }
-\caption{Non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:D}
+\caption{\Cref{thm1}: Non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:D}
 \end{figure}
 
-\iffalse
-%Comments
-\tsnote{I'll need to rewrite all below here.  The current text is too hand-wavy and fast.}
-\tsnote{`In transitioning from $\game{2}$ to $\game{3}$ we
-  replace the all-at-once sampling of random functions~$\rho_1,\rho_2$
-with lazying sampling in the $\HashOracle$, which is the only place
-these random functions are used.  This does not alter the input-output
-behavior of the $\HashOracle$.''  Why do we do this?}
-We also sample $r$~distinct random integers are chosen \tsnote{why?
-  What are we setting up?} and the $\QryOracle$ oracle sets a $\bad$
-flag if query response for any of the $r$ queries is false or any of
-the $q-r$ queries return true. \tsnote{We
-  set $\bad$ to $\true$ if the queries indexed by the
-  set~$\mathcal{I}$ fail to be false-positives, or if any of the
-  remaining queries \emph{are} false-positives.  Again, why are we
-  doing this?  }
-\tsnote{How does the last line follow from the games?  I mean, it
-  isn't obvious to me that your $\game{5}$ is equivalent to $\game{4}$.  The
-  latter looks at the adversary's output~$\mathcal{Z}$, but the former
-ignores this and looks at this new set~$\mathcal{Y}$.  Why are these
-equivalent with respect to the events $\game{4}(A)=1$ and
-$\game{5}(A)=1$?  Just looking at the $\QryOracle$ in the two games,
-it appears that they have pretty different behaviors. I mean, in
-$\game{4}$ the oracle still returns what it is supposed to, even if
-$\bad\gets\true$.  But in $\game{5}$ the oracle returns fixed values,
-no matter if the query is or is not a FP.  You have to explain why
-these changes are okay.  Also, why is this new set~$\mathcal{Y}$
-necessary?  }
-\tsnote{The point that needs to be made about the relationship between
-  $\game{4}$ and $\game{5}$ is this.  $\game{4}$ returns 1 only if
-  $\bad=\false$ at the end of the game.  In turn, this implies that
-  the game managed to ``guess'', prior to the execution of~$A$, which
-  of its queries would result in false-positives.  (By the way, we
-  need to state an assumption here: that~$A$ halts and
-  outputs~$\mathcal{Z}$ (of size~$r$) as soon as its queries
-  reveal~$r$ false positives.  This is without loss of generality; say
-why.  I guess you also need to assume that every point in
-the~$\mathcal{Z}$ output by~$A$ has already been queried
-to~$\QryOracle$.  Strictly speaking this is not without loss of
-generality, but would be easily enforced (in the original
-  security definitions) by counting as part of the number of
-  queries~$q$ the points in~$\mathcal{Z}$.  Without these assumptions,
-things don't quite work.)  Hence, if $\game{4}(A)=1$ there is a
-non-adaptive adversary~$D$ that finds~$r$ false positives against
-$\tilde{B}_{\mathrm{lin}}$, which is $B_{\mathrm{lin}}$ but
-with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$,
-respectively.  (Note, this is \emph{not} the adversary~$D$ that you
-give, because the one you give simulates things that it would be given
-in the FP game, e.g. the set~$S$.)  That is, $\Prob{\game{4}(A)=1} =
-\AdvFPSecHash{\tilde{B}_{\mathrm{lin}},r}{D}$.  (So I guess there's no
-need for $\game{5}$.)  Now argue that this advantage is upperbounded
-	by what the theorem claims, i.e. the KM bound raised to~$r$.}
-
-In $\game{3}(A)$, the hash functions are linear combinations of two random points
-in $[m]$, similar to $\game{2}(A)$.
-
-So, both have equal probability of returning 1.  \tsnote{``The value
-  of~$\bad$ does not affect the value returned by~$\game{3}$. Thus we
-  conclude that...'' }
-\begin{equation}
-\Prob{\game{2}(A)=1} = \Prob{\game{3}(A)=1}\label{eq:3}
-\end{equation}
-
-The probability of winning  $\game{3}(A)$ is same as $\game{4}(A)$,
-except $\game{4}(A)$ outputs 0 if $\bad$ flag is
-set.\tsnote{I don't understand this sentence.  What you mean to say is
-  something like this: ``By construction, $\game{3}$ and $\game{4}$
-  are identical-until-bad.  In addition, $\game{4}$ returning 1
-  implies that $\bad$ is never set to~$\true$.  From these two
-  observations, we can conclude that $\Prob{\game{4}(A)=1} =
-  \Prob{\game{3}(A)=1 \wedge \neg\bad}$.'' }
-In short, $\game{3}(A)$ and $\game{4}(A)$ are identical untill $\bad
-=true$.  On the  other hand, $\game{5}(A)$ simulates the non-adaptive
-counterpart of $\game{4}(A)$.  \tsnote{This statement is unjustified.
-(See my comments below.) Actually it's meaningless, because games are
-not not adaptive or non-adaptive.  Adversaries are.}
-
-\tsnote{You need to just justify these next lines better. For example,
-why is the event $\neg \bad$ independent of the event $\game{3}(A)=1$?}
-\begin{align}
-\nonumber \Prob{\game{4}(A)=1} &= \Prob{\game{3}(A)=1 \wedge \neg\bad}\\ 
-\nonumber & = \Prob{\game{3}(A)=1}\Prob{\game{3}(A):\,\neg\bad}\\
-& = \Prob{\game{3}(A)=1}\frac{1}{\dbinom{q}{r}}\label{eq:3a}\\
-\Prob{\game{5}(A)=1} &= \Prob{\game{4}(A)=1}\label{eq:3b}
-\end{align}
-
-\tsnote{Why is $B_2$
-  sampling a random function?  This ruins the tightness of security
-  bound w.r.t.\ resources.  Please have~$B_2$ carry out lazy sampling
-  of~$\rho_2$.  Also, please use the macro for Func.}
-
-\tsnote{This proof jumps around too much.  The games should be
-  addressed in order, as much as possible.}  
-The classical FP requirement considers only non-adaptive (and information-theoretic) adversaries, and~$D$ is one such adversary simulating $\game{5}(A)$ as closely as possible, whereas $D'$ mimics $D$ for $r=1$.
-$D'$ outputs a FP as in a classic Bloom filter and its FP-error is upperbounded by $[(1-e^{-kn/m})^k +O(1/n)]$ \cite{KirschMitzenmacher}.
-%\acnote{changed}\tsnote{The classical FP requirement considers only non-adaptive (and information-theoretic) adversaries.
-It suffices to say this.}
-\noindent
-From \Cref{fig:AGame3}, it is evident that \tsnote{Where is the
-  set~$S$ in $D$ and $D'$?  Make sure to give it to~$A$.  Why is this
-  extra set~$\mathcal{Y}$ needed?  What is the point of~$D'$? }
-\begin{align}
-\Prob{\game{5}(A)=1} &= \Prob{D \, \mbox{outputs $r$ FP} \,}\label{eq:4a}\\
-\nonumber \Prob{D \, \mbox{outputs r FP} \,} &=  \Big[\Prob{D' \, \mbox{outputs FP} \,}\Big]^r\\
-& \leq \Big[(1-e^{-kn/m})^k +O(1/n)\Big]^r \label{eq:4b}
-\end{align}
-\tsnote{How does the second line follow?  You're claiming independence
-  somehow, but you haven't justified it.}
-\noindent
-From \Cref{eq:4a,eq:4b}
-\begin{equation}
-\Prob{\game{5}(A)=1} \leq [(1-e^{-kn/m})^k + O(1/n)]^r \label{eq:4}
-\end{equation}
-
-\noindent
-Using \ref{eq:4} in \ref{eq:3c}:
-\begin{align}
-\nonumber \Prob{\game{2}(A)=1}\frac{1}{\dbinom{q}{r}}  &\leq [(1-e^{-kn/m})^k +O(1/n)]^r\\
- \Prob{\game{2}(A)=1}  & \leq \dbinom{q}{r}[(1-e^{-kn/m})^k +O(1/n)]^r\label{eq:5}
-\end{align}
-
-\fixme{These adversaries are incorrect.  They are FP adversaries, so
-  they get~$S$ as input.  They also do not sample random functions;
-  use lazy sampling (a la game $\game{3}(A)$.  Please clean things up.)}
-\noindent
-%\caption{$\Cref{thm1}:\game{5}(A)$ in game playing argument}\label{fig:game5}
-%\begin{figure}
-%\centering
-%\fpage{0.8}
-%{
-%\hpagess{0.5}{0.4}{
-%\underline{$\game{5}(A)$}\\
-%$c \gets 0$\\
-%$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
-%$\calY \gets \emptyset$\\
-%$S \getsr \distr{\univ}{n}$\\
-%$M \getsr \Rep^{\HashOracle}(\calS)$\\
-%$\calZ \getsr A^{\QryOracle}(\calS)$\\
-%if $|\calY| < r$ or $\calY \cap \calS \neq \emptyset$ then\\
-%\nudge Ret 0\\
-%if $\forall y \in \calY,\,\Qry^{\HashOracle}(M,y)=1$ then \\
-%\nudge Ret 1\\
-%Ret 0
-%}
-%
-%{
-%\oracle{$\QryOracle(x)$}\\
-%$c \gets c+1$\\
-%if $c \in \mathcal{I}$ then\\
-%\nudge $\calY \gets \calY \cup {x}$\\
-%\nudge Ret 1\\
-%else\\
-%\nudge Ret 0 \\\\
-%
-%\oracle{$\HashOracle(x)$}\\
-%$a,b \getsr [m]$\\
-%for $i = 1$ to~$k$\\
-%\nudge $v_i = a+i \cdot b \bmod m$\\
-%Ret $\left(v_1,\ldots,v_k\right)$
-%}
-%}
-%\caption{\Cref{thm1}:$\game{5}(A)$ in game playing argument}\label{fig:game5}
-%\end{figure}
-
-%From \Cref{eq:m1,eq:m2,eq:m3,eq:m4},
-%\begin{align}
-%\nonumber \Prob{\ExpPRF{F}{B_1} = 1} &= .5\Prob{\ExpPRF{F}{B_1}=1\,|\,b=0} + .5\Prob{\ExpPRF{F}{B_1} = 1\,|\,b=1}\\
-%\nonumber 2\Prob{\ExpPRF{F}{B_1} = 1} &= 1-\Prob{\game{1}(A)=1} + \Prob{\game{0}(A)=1}\\
-%\nonumber (2\Prob{\ExpPRF{F}{B_1} = 1} - 1)  &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1}\\
-% \AdvPRF{F}{B_1} &= \Prob{\game{0}(A)=1} - \Prob{\game{1}(A)=1} \label{eq:11}\\
-%\nonumber& &\\
-%\nonumber \Prob{\ExpPRF{F}{B_2} = 1} &= .5\Prob{\ExpPRF{F}{B_2}=1\,|\,b=0} + .5\Prob{\ExpPRF{F}{B_2} = 1\,|\,b=1}\\
-%\nonumber 2\Prob{\ExpPRF{F}{B_2} = 1} &= 1-\Prob{\game{2}(A)=1} + \Prob{\game{1}(A)=1}\\
-%\nonumber (2\Prob{\ExpPRF{F}{B_2} = 1} - 1)  &= \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1}\\
-% \AdvPRF{F}{B_2} &= \Prob{\game{1}(A)=1} - \Prob{\game{2}(A)=1} \label{eq:12}
-%\end{align}
-%\noindent
-%Adding \Cref{eq:11,eq:12}, we have
-%Before giving the proof, we note that  $(1-e^{-kn/m})^k \rightarrow 0$ as the ratio between the bit-length of the representation~$M$ and the size of the represented set~$S$, i.e.,$m/n$ tends to $\infty$.
-%
-%\begin{align*}
-%\game{1}(A)\, : \, h_j(x) &= ( F_{K_0}(x) + j\cdot \rho_2(x)) \bmod m\\
-%\game{2}(A)\, : \, h_j(x) &= ( \rho_1(x) + j \cdot \rho_2(x)) \bmod m
-%\end{align*}
-
-\fi
 \end{proof}

### 2016-08-19 Theorem1_FP.tex
Proof1 Proof2 new syntax

@@
 $B_{\mathrm{lin}}$ is in fact one instantiation of a set-multiplicity data structure.
-It must be noted that $B_{\mathrm{lin}}$ admits errors in form of false-positives only.
+It must be noted that $B_{\mathrm{lin}}$ admits errors in form of false-positives(FP) only.
 So, error rate of $B_{\mathrm{lin}}$ is same as the (non-adaptive) FP rate.
 The following result shows, informally, that if~$F$ is a good PRF and the error rate is sufficiently small, then $B_\mathrm{lin}$ is correct against adaptive error-finding adversaries.
-Henceforth, we refer errors and error-rate in $B_{\mathrm{lin}}$ as false-positives and false-positive(FP) rate, respectively.
+Henceforth, we refer errors and error-rate in $B_{\mathrm{lin}}$ as FP's and FP rate, respectively.
 
@@
 \nudge \nudge $\err \gets \err +1$\\
-Return~$(a,\err )$\\
+\nudge Return~$(a,\err )$\\
 When $A$ halts: \\
@@
 \nudge \nudge $\err \gets\err +1$\\
-Return~$(a,\err )$\\
+\nudge Return~$(a,\err )$\\
 When $A$ halts: \\

### 2016-08-19 Theorem2_FP.tex
Proof1 Proof2 new syntax

@@
 The $\Rep$ and $\Qry$ algorithms are the standard (determinisitic) BF ones.
-Informally, the following result shows, if~$F$ is PRF secure and the filter has low FP-error in the non-adaptive setting, then $B_{\mathrm{ds}}$ is secure against adaptive FP-finding adversaries.
+$B_{\mathrm{ds}}$ is another instantiation of the set-multiplicity data structure.
+Like $B_{\mathrm{lin}}$, $B_{\mathrm{ds}}$ admits errors in form of false positives only.
+Informally, the following result shows, if~$F$ is PRF secure and the filter has low error rate in the non-adaptive setting, then $B_{\mathrm{ds}}$ is correct against adaptive error finding adversaries.
+Hereafter, we refer errors and error-rate in $B_{\mathrm{ds}}$ as false-positives and false-positive rate, respectively.
 
@@
 Let $B_{\mathrm{ds}}$ be the hash based filter just described.
-If there exists an adaptive adversary, $A$ compatible with $\ExpFPSecHash{B_{\mathrm{ds},r}}{\cdot}$ asking $q$ queries, and has time complexity O(t), then there exists an adversary $B$ (explicitly constructed in the proof of this theorem), such that
+If there exists an adaptive adversary, $A$ compatible with $\ExpCorrect{B_{\mathrm{ds}},\distr{\calS}{},r}{\cdot}$ asking $q$ queries, and has time complexity O(t), then there exists an adversary $B$ (explicitly constructed in the proof of this theorem), such that
 \[
-\AdvFPSecHash{B_\mathrm{ds},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\AdvCorrect{B_{\mathrm{ds}},\distr{\calS}{},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
 \]
@@
 We use a game playing argument similar to \Cref{thm1} to prove this theorem.
-In \game{0}(A), adversary attacks the FP game with  hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpFPSecHash{B_\mathrm{ds},r}{A}$.
+In \game{0}(A), adversary attacks the FP game with  hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpCorrect{B_{\mathrm{ds}},\distr{\calS}{},r}{A}$.
 \begin{equation}
-\AdvFPSecHash{B_\mathrm{ds},r}{A} = \Prob{\game{0}(A)=1}\label{eq:2T0}
+\AdvCorrect{B_{\mathrm{ds}},\distr{\calS}{},r}{A} = \Prob{\game{0}(A)=1}\label{eq:2T0}
 \end{equation}
@@
 $\game{2}$ and $\game{3}$ on the other hand use lazy sampling in $\Hash$ to select random values from $[m]$.
-This makes $\game{2}$ and $\game{3}$ identical to $\game{3}$ and $\game{4}$ of previous theorem, and hence the analysis and results of \Cref{thm1} apply to this theorem as well.
+It can be observed that, except  $\Hash$, $\game{2}$ and $\game{3}$ are identical to $\game{3}$ and $\game{4}$ of previous theorem.
+Since, $\Hash$ in all of these games returns random values, the analysis and results of \Cref{thm1} apply to this theorem as well.
 Therefore,
@@
 Let $D$ be a non-adaptive adversary (shown in \Cref{fig:2TD}) that finds ~$r$ false positives against $\tilde{B}_{\mathrm{ds}}$.
-As discussed in the previous theorem, if $A$ wins $\game{3}$, then $D$ wins $\ExpFPSecHash{\tilde{B}_{\mathrm{ds}},r}{\cdot}$ game.
+As discussed in the previous theorem, if $A$ wins $\game{3}$, then $D$ wins $\ExpCorrect{\tilde{B}_{\mathrm{ds}},\distr{\calS}{},r}{\cdot}$ game.
 So,
 \begin{equation*}
-\AdvFPSecHash{\tilde{B}_{\mathrm{ds}},r}{D} = \Prob{\game{3}(A) = 1}\label{eq:2T8}
+\AdvCorrect{\tilde{B}_{\mathrm{ds}},\distr{\calS}{},r}{D} = \Prob{\game{3}(A) = 1}\label{eq:2T8}
 \end{equation*}
@@
 \begin{equation*}
-\AdvFPSecHash{\tilde{B}_{\mathrm{ds}},r}{D} =   {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
+\AdvCorrect{\tilde{B}_{\mathrm{ds}},\distr{\calS}{},r}{D} =   {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
 \end{equation*}
@@
 \[
-\AdvFPSecHash{B_\mathrm{ds},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
+\AdvCorrect{B_{\mathrm{ds}},\distr{\calS}{},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
 \]
@@
 \underline{\game{0}(A)}\\
-$K \getsr \calK$\\
-$S \getsr \distr{\univ}{n}$\\
-$M \getsr \Rep^{\HashOracle}(\calS)$\\
-$\calZ \getsr A^{\QryOracle}(\calS)$\\
-if $|\calZ| < r$ or $\calZ \cap \calS \neq \emptyset$ then \\
-\nudge Ret 0\\
-if $\exists z \in \calZ$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
-\nudge Ret 0\\
-Ret 1\\\\
+$S \getsr \distr{\calS}{}$\\
+$\err \gets 0$\\
+$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+$z \getsr A^{\TestOracle}(S,\pubaux)$\\
+if $\err  < r$ then Return 0\\
+Return 1\\\\
 %
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,x)$\\\\
+\oracle{$\TestOracle(q)$}\\
+$a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
+if $a \neq q(S)$ then \\
+\nudge $\err \gets\err +1$\\
+Return~$(a,\err )$\\\\
 %
@@
 $\rho \getsr \Func{\univ,[m]}$\\
-$S \getsr \distr{\univ}{n}$\\
-$M \getsr \Rep^{\HashOracle}(\calS)$\\
-$\calZ \getsr A^{\QryOracle}(\calS)$\\
-if $|\calZ| < r$ or $\calZ \cap \calS \neq \emptyset$ then \\
-\nudge Ret 0\\
-if $\exists z \in \calZ$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
-\nudge Ret 0\\
-Ret 1\\\\
+$S \getsr \distr{\calS}{}$\\
+$\err \gets 0$\\
+$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+$z \getsr A^{\TestOracle}(S,\pubaux)$\\
+if $\err  < r$ then Return 0\\
+Return 1\\\\
 %
-\oracle{$\QryOracle(x)$}\\
-Ret $\Qry^{\HashOracle}(M,x)$\\\\
+\oracle{$\TestOracle(q)$}\\
+$a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
+if $a \neq q(S)$ then \\
+\nudge $\err \gets\err +1$\\
+Return~$(a,\err )$\\\\
 %
@@
 \underline{{$\game{2}(A)$},\fbox{$\game{3}(A)$}}\\
-$c \gets 0$\\
+$c\gets 0$, $\bad \gets \false$\\
 $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
-$\bad \gets \false$\\
-$S \getsr \distr{\univ}{n}$\\
-$M \getsr \Rep^{\HashOracle}(\calS)$\\
-$\calZ \getsr A^{\QryOracle}(\calS)$\\
-if $|\calZ| < r$ or $\calZ \cap \calS \neq \emptyset$ then\\
-\nudge Ret 0\\
-if $\forall z \in \calZ,\,\Qry^{\HashOracle}(M,z)=1$ then \\
-\nudge if $\bad=\true$ then \fbox{Ret 0}\\
-\nudge Ret 1\\
-Ret 0
+$S \getsr \distr{\calS}{}$\\
+$\err \gets 0$\\
+$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+$z \getsr A^{\TestOracle}(S,\pubaux)$\\
+if $\err  < r$ then Return 0\\
+Return 1
 }
+%
 {
-\oracle{$\QryOracle(x)$}\\
-%$\calY \gets \calY \cup \{x\}$\\
+\oracle{$\TestOracle(q)$}\\
 $c \gets c+1$\\
-$v \gets \Qry^{\HashOracle}(M,x)$\\
-if $c \in \mathcal{I}$ and $v\neq 1$ then\\
+$v \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
+if $c \in \mathcal{I}$ and $a \neq q(S)$ then \\
 \nudge $\bad \gets \true$ \\
-%\nudge \fbox{Ret 1} \\
-if $c \not\in \mathcal{I}$ and $v\neq 0$ then\\
+if $c \not\in \mathcal{I}$ and $a \neq q(S)$ then \\
 \nudge $\bad \gets \true$\\
-%\nudge \fbox{Ret 0}\\
-Ret~$v$\\\\
+\nudge $\err \gets\err +1$\\
+Return~$(v,\err )$\\\\
 %
@@
 $\adversaryv{B^{\calO}}$\\
-$\calS \getsr \distr{\univ}{n}$\\
-$M \getsr \Rep^{\HashOracle}(\calS)$\\
-When $A$ asks $\QryOracle(x)$:\\
-$\nudge$ Ret $\Qry^{\HashOracle}(M,x)$\\
-When $A$ halts with output $\calZ'$: \\
-\nudge if $|\calZ'| < r$ or $\calZ' \cap \calS \neq \emptyset$ then \\
-\nudge \nudge Ret 0\\
-\nudge if $\exists z \in \calZ'$ s.t. $\Qry^{\HashOracle}(M,z)=0$ then\\
-\nudge \nudge Ret 0\\
-\nudge Ret 1\\\\
+$S \getsr \distr{\calS}{}$\\
+$\err \gets 0$\\
+$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+Run~$A(S, \pubaux)$\\
+When $A$ asks $\TestOracle(q)$:\\
+\nudge $a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
+\nudge if $a \neq q(S)$ then \\
+\nudge \nudge $\err \gets \err +1$\\
+\nudge Return~$(a,\err )$\\
+When $A$ halts: \\
+\nudge if $\err  < r$ then Return 0\\
+\nudge Return 1\\\\
+%
+%
 \oracle{$\HashOracle(x)$}\\
@@
 $\adversaryv{D^{\QryOracle, \calS}}$\\
-$c \gets 0$\\
-$\calX \gets \emptyset$\\
+$c \gets 0$, $\calX \gets \emptyset$\\
+$\err \gets 0$\\
 $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
@@
 \nudge \nudge $r \gets 1$\\
-\nudge Ret $r$\\
+\nudge \nudge $\err \gets \err + 1$\\
+\nudge Ret $(r,\err )$\\
 When $A$ halts:\\
-\nudge Ret $\calX$\\\\
+\nudge Ret $\calX $
+}
 %
@@
 }
-}
-\caption{\Cref{thm2}: \emph{Left}:PRF adversary $B$ simulating $\game{1}(A)$ and $\game{2}(A)$.\emph{Right}: Non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:2TD}
+\caption{\Cref{thm2}: \bf{Left}:PRF adversary $B$ simulating $\game{1}(A)$ and $\game{2}(A)$.\bf{Right}: Non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:2TD}
 \end{figure}

### 2016-08-19 Theorem1_FP.tex
Proof 1,2 update

@@
 %
-Also, the $\QryOracle$ oracle now sets $\bad$ to $\true$ if the
+Also, the $\Test$ oracle now sets $\bad$ to $\true$ if the
 queries indexed by the set $\mathcal{I}$ fail to be false-positives,
@@
 observed that the $\bad$ flag has no impact on the output of the
-$\QryOracle$, nor does it affect  the value returned
+$\Test$, nor does it affect  the value returned
 by~$\game{3}$. Thus we have $\Prob{\game{2}(A)=1} =
@@
 of the $\bad$-flag in games~$\game{3},\game{4}$.   Intuitively, if the index
-set~$\mathcal{I}$ exactly predicts which of the $\QryOracle$ will be
+set~$\mathcal{I}$ exactly predicts which of the $\Test$ queries will be
 false-positives (and, conversely, which will not be), then a
 non-adaptive FP-finding adversary can ``guess'' which of~$A$'s queries require it
-to return 1 when simulating the $\QryOracle$, and which require it to
+to return 1 when simulating the $\Test$, and which require it to
 return 0.  In this way, no queries ever actually need to be made.
@@
 happens iff the $r$-set~$\calI$ contains exactly the indices of
-$\QryOracle$-queries that are false-positives.  Since the value
-of~$\bad$ does not alter the responses of~$\QryOracle$, the
-set~$\mathcal{Z}$ output by~$A$ and the set~$\calI$ are independent.
+$\Test$-queries that are false-positives.  Since the value
+of~$\bad$ does not alter the responses of~$\Test$, $\err$'s update
+and the set~$\calI$ are independent.
 Thus $\bad$ remains $\false$ after~$A$ halts with probability
@@
 We can assume, without loss of generality,  that~$A$ halts immediately upon finding its $r$-th false positive.
-We can also assume that every point in $\calZ$ has already been queried to $\QryOracle$.
+% We can also assume that every point in $\calZ$ has already been queried to $\Test$.
 This latter assumption is not without loss, but can be  easily enforced (in the original security definitions) by counting as part of the number of queries~$q$, the points in $\mathcal{Z}$.
 %
-Under these assumptions, if $\game{4}(A)=1$, then there is a non-adaptive adversary~$D$ that finds~$r$ false positives against $\tilde{B}_{\mathrm{lin}}$, which is $B_{\mathrm{lin}}$ but with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$, respectively.
+%Under these assumptions,
+So, if $\game{4}(A)=1$, then there is a non-adaptive adversary~$D$ that finds~$r$ false positives against $\tilde{B}_{\mathrm{lin}}$, which is $B_{\mathrm{lin}}$ but with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$, respectively.
 We give this~$D$ in \Cref{fig:D}.
-Intuitively, adversary~$D$ guesses which~$r$ of~$A$'s queries will be the false positives; it simulates the~$\QryOracle$ by returning 1 on the guessed queries, and 0 otherwise; and it halts by outputting the set of guessed queries.
+Intuitively, adversary~$D$ guesses which~$r$ of~$A$'s queries will be false positives; it simulates the~$\Test$ oracle by returning 1 on the guessed queries, and 0 otherwise; and it halts after finding $r$ FP's.
 Thus we have
@@
 Kirsch and Mitzenmacher~\cite{KM} show that the upperbound on false-positive probability for a non-adaptive adversary and $r=1$ is $\left( (1-e^{-kn/m})^k + O(1/n) \right)$.
-For $r>1$, we observe that~$A$'s queries are distinct and not elements of the original set~$S$, since we assume no pointless queries.
-Hence, so are the points $x_1,x_2,\ldots,x_r$ returned by~$D$.
-Let $\calF_i$ be the event that~$x_i$ is a false positive.
+For $r>1$, we observe that~$A$'s queries $x_1,x_2,\ldots,x_q$ are distinct and not elements of the original set~$S$, since we assume no pointless queries.
+Let $\calF_i$ be the event that~$x_i(i \in \mathcal{I}$ is a false positive.
 Since $\game{4}$ (equivalently $\tilde{B}_{\mathrm{lin}}$) use independent random functions, the events $\calF_1,\calF_2,\ldots,\calF_r$ are independent.
@@
 $v \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
-if $c \in \mathcal{I}$ and $a \neq q(S)$ then \\
+if $c \in \mathcal{I}$ and $v = q(S)$ then \\
 \nudge $\bad \gets \true$ \\
-if $c \not\in \mathcal{I}$ and $a \neq q(S)$ then \\
+if $c \not\in \mathcal{I}$ and $v \neq q(S)$ then \\
 \nudge $\bad \gets \true$\\
+if $v \neq q(S)$\\
 \nudge $\err \gets\err +1$\\
@@
 $\adversaryv{D(S)}$\\[4pt]
-$c \gets 0$, $\calX \gets \emptyset$\\
+$c \gets 0$\\%, $\calX \gets \emptyset$\\
 $\err \gets 0$\\
@@
 Run $A(S)$\\
-When $A$ asks $\QryOracle(x)$:\\
+When $A$ asks $\Test(x)$:\\
 \nudge $c \gets c+1$\\
@@
 \nudge if $c \in \mathcal{I}$\\
-\nudge \nudge $\calX \gets \calX \cup \{x\}$\\
+%\nudge \nudge $\calX \gets \calX \cup \{x\}$\\
 \nudge \nudge $r \gets 1$\\
@@
 When $A$ halts:\\
-\nudge Ret $\calX$
+\nudge Ret 1
 }

### 2016-08-19 Theorem2_FP.tex
Proof 1,2 update

@@
 \begin{proof}[\Cref{thm2}]
-We use a game playing argument similar to \Cref{thm1} to prove this theorem.
+We use a game playing argument (shown in \Cref{fig:2TGame}) similar to \Cref{thm1} to prove this theorem.
 In \game{0}(A), adversary attacks the FP game with  hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpCorrect{B_{\mathrm{ds}},\distr{\calS}{},r}{A}$.
@@
 So, for a non-adaptive adversary $D$ and $r=1$, the upper bound on false-positive probability of a classical Bloom filter applies to $\tilde{B}_{\mathrm{ds}}$ as well.
-For $r > 1$, based on the assumption that $A$ makes no pointless queries, the queries made by $A$ as well as the elements returned by $D$ are distinct and not elements of the original set $S$.
+For $r > 1$, based on the assumption that $A$ makes no pointless queries, the queries made by $A$ are distinct and not elements of the original set $S$.
 Also, since $\game{3}$ uses independent random functions, the event of getting a false positive is independent of the index of the query.
@@
 }
-\caption{\Cref{thm2}: Game playing argument}\label{fig:Game}
+\caption{\Cref{thm2}: Game playing argument}\label{fig:2TGame}
 \end{figure}
@@
 {
-$\adversaryv{D^{\QryOracle, \calS}}$\\
-$c \gets 0$, $\calX \gets \emptyset$\\
+$\adversaryv{D^{\TestOracle, \calS}}$\\
+$c \gets 0$\\%, $\calX \gets \emptyset$\\
 $\err \gets 0$\\
@@
 Run $A(S)$\\
-When $A$ asks $\QryOracle(x)$:\\
+When $A$ asks $\TestOracle(x)$:\\
 \nudge $c \gets c+1$\\
@@
 When $A$ halts:\\
-\nudge Ret $\calX $
+\nudge Ret 1
 }
 %
-%\oracle{$\QryOracle(x)$}\\
+%\oracle{$\TestOracle(x)$}\\
 % Ret $\Qry^{\HashOracle}(M,x)$\\\\

### 2016-08-19 Theorem2_FP.tex
Proof 1,2 typos fix

@@
 }
-\caption{\Cref{thm2}: \bf{Left}:PRF adversary $B$ simulating $\game{1}(A)$ and $\game{2}(A)$.\bf{Right}: Non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:2TD}
+\caption{\Cref{thm2}: \textbf{Left}: PRF adversary $B$ simulating $\game{1}(A)$ and $\game{2}(A)$. \textbf{Right}: Non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:2TD}
 \end{figure}

### 2016-08-23 notions.tex
cheers

@@
 
-On the right side of the figure, we give two ``indistinguishability''
-notions of privacy.  The first version (ind-qry) captures more
-generally what~$M$ and the allowed queries leak about the set that is
-represented.  In particular, two sets~$S_0,S_1$ are sampled according
-to distribution~$\distr{\calS}{}$, one of these is picked at random to
-be represented.  The adversary is provided the resulting~$M,\pubaux$
-and allowed to make queries~$q \in \calQ$; it must determine which
-of~$S_0$ or~$S_1$ was actually represented.  We call this notion
-indistinguishabilty (of sets) under a (adaptively chosen) query
-attack.
+%On the right side of the figure, we give two ``indistinguishability''
+%notions of privacy.  The first version (ind-qry) captures more
+%generally what~$M$ and the allowed queries leak about the set that is
+%represented.  In particular, two sets~$S_0,S_1$ are sampled according
+%to distribution~$\distr{\calS}{}$, one of these is picked at random to
+%be represented.  The adversary is provided the resulting~$M,\pubaux$
+%and allowed to make queries~$q \in \calQ$; it must determine which
+%of~$S_0$ or~$S_1$ was actually represented.  We call this notion
+%indistinguishabilty (of sets) under a (adaptively chosen) query
+%attack.
 %
-The second version is inspired by the semantic security notion for
-encryption schemes, and we refer to it as semantic-security (of sets)
+On the right side of the figure, we give a definition
+inspired by the semantic security notion for
+encryption schemes.  We refer to it as semantic-security (of sets)
 with respect to the full representation (ss-rep).  In this experiment,
@@
 \oracle{$\TestOracle(q)$}\\
-$a \gets \Qry(M,\privaux,q)$\\
+$a \gets \Qry(M,\pubaux,\privaux,q)$\\
 Return~$a$
@@
 {
-\experimentv{$\ExpPrivInd{\setprim,\distr{\calS}{}}{A}$}\\
-$b \getsr \bits$\\
-$S_0,S_1 \getsr \distr{\calS}{}$\\
-$(M,\pubaux,\privaux) \getsr \Rep(S_b)$\\
-$b' \getsr A^{\TestOracle}(M,\pubaux)$\\
-if $b' = b$ then Return 1\\
-Return 0\\
-
-\medskip
+%\experimentv{$\ExpPrivInd{\setprim,\distr{\calS}{}}{A}$}\\
+%$b \getsr \bits$\\
+%$S_0,S_1 \getsr \distr{\calS}{}$\\
+%$(M,\pubaux,\privaux) \getsr \Rep(S_b)$\\
+%$b' \getsr A^{\TestOracle}(M,\pubaux)$\\
+%if $b' = b$ then Return 1\\
+%Return 0\\
+%
+%\medskip
 \experimentv{$\ExpPrivSS{\setprim,\distr{\calS}{}}{A}$}\\
@@
 \oracle{$\TestOracle(q)$}\\
-$a \gets \Qry(M,\privaux,q)$\\
+$a \gets \Qry(M,\pubaux,\privaux,q)$\\
 Return~$a$\\
@@
 \begin{itemize}
-\item ss-rep $\Rightarrow$ ind-qry
-\item ind-qry $\Rightarrow$ ss-rep \tsnote{Not sure about this separation...}
-\item ind-qry $\Rightarrow$ priv \emph{for set-multiplicity data
+%\item ss-rep $\Rightarrow$ ind-qry
+%\item ind-qry $\Rightarrow$ ss-rep \tsnote{Not sure about this separation...}
+\item ss-rep $\Rightarrow$ priv \emph{for set-multiplicity data
     structures} \tsnote{but probably not in general}
-\item \{w\}priv $\not\Rightarrow$ ind-qry
+\item \{w\}priv $\not\Rightarrow$ ss-rep
 \item wpriv $\not\Rightarrow$ priv \tsnote{$M=S$, or my

### 2016-08-23 syntax.tex
cheers

@@
     \Gamma$ is a deterministic \emph{query-evaluation}
-    algorithm, taking as input $M, \privaux, q$, and returns
-    \emph{answer} $a \in \Gamma$. \jnote{Should take $\pubaux$
-    as input also.}
+    algorithm, taking as input $M, \pubaux,\privaux, q$, and returns
+    \emph{answer} $a \in \Gamma$. 
 \end{itemize}
@@
 \end{definition}
-\tsnote{I implemented this change.}\tsnote{I'm now leaning towards
-having $\Rep$ output~$M$ and explicit pubic/private auxillary data.
-Pushing secrets into~$M$ makes it more difficult to capture (for
-example) the Neidermeier et al.\ attacks in our privacy notions; see
-Figure~\ref{fig:privacy}.  In those attacks, the adversary would get
-the bitarray (which one naturally thinks of as~$M$) but not the
-secret keys for the PRFs/hash functions.  You could say that the
-bitarray is put in $\aux$ and that~$M$ \emph{only} contains the
-secret keys, but this is unnatural.} All of the data structures that
+%\tsnote{I implemented this change.}\tsnote{I'm now leaning towards
+%having $\Rep$ output~$M$ and explicit pubic/private auxillary data.
+%Pushing secrets into~$M$ makes it more difficult to capture (for
+%example) the Neidermeier et al.\ attacks in our privacy notions; see
+%Figure~\ref{fig:privacy}.  In those attacks, the adversary would get
+%the bitarray (which one naturally thinks of as~$M$) but not the
+%secret keys for the PRFs/hash functions.  You could say that the
+%bitarray is put in $\aux$ and that~$M$ \emph{only} contains the
+%secret keys, but this is unnatural.} 
+All of the data structures that
 we will consider have the property that~$|M|$ does not depend on the

### 2016-08-23 notions.tex
trying to sort out privacy notions, post-crypto chat

@@
 One can also consider the orthogonal notion of privacy for a
-set-representation.   There are various ways to formalize privacy, and
-we give some of these in Figure~\ref{fig:privacy}.  
+set-representation.  We formalize two types of privacy notions. One
+type captures a kind of one-wayness of the representation~$M$,
+relative to the allowed queries.  Informally, that given the
+representation and the public information, it is hard to guess any
+value in the represented set~$S$.  The other type captures a kind of
+semantic security, essentially requiring that $(M,\pub)$ and th
+allowed queries do not leak any (non-trivial) information about the set~$S$.
 %\jnote{Actually, I am now unsure what the right way to define it is. It seems natural
@@
 %at least in the ``one-wayness'' style definition that I had been imagining. }
-On the left side of this figure, we give two ``one-wayness''
+
+In Figure~\ref{fig:privacy-ow} we give two ``one-wayness''
 definitions, in which the adversary must output an element of the
@@
 The stronger priv-notion captures what is jointly leaked, by the
-representation~$M$ and the allowed queries, about set elements.
+representation~$M$ and the allowed queries, about set elements.  We
+define advantage measures $\AdvPriv{\Pi,\distr{\calS}{}}{A} =
+\Prob{\ExpPriv{\Pi,\distr{\calS}{}}{A}=1}$ and $\AdvWPriv{\Pi,\distr{\calS}{}}{A} =
+\Prob{\ExpWPriv{\Pi,\distr{\calS}{}}{A}=1}$; in both we track the
+time-complexity~$t$ and number of oracle queries~$q$ made by the adversary.
 
-%On the right side of the figure, we give two ``indistinguishability''
-%notions of privacy.  The first version (ind-qry) captures more
-%generally what~$M$ and the allowed queries leak about the set that is
-%represented.  In particular, two sets~$S_0,S_1$ are sampled according
-%to distribution~$\distr{\calS}{}$, one of these is picked at random to
-%be represented.  The adversary is provided the resulting~$M,\pubaux$
-%and allowed to make queries~$q \in \calQ$; it must determine which
-%of~$S_0$ or~$S_1$ was actually represented.  We call this notion
-%indistinguishabilty (of sets) under a (adaptively chosen) query
-%attack.
-%
-On the right side of the figure, we give a definition
-inspired by the semantic security notion for
-encryption schemes.  We refer to it as semantic-security (of sets)
-with respect to the full representation (ss-rep).  In this experiment,
-a set~$\calS$ is sample according to distribution~$\distr{\calS}{}$,
-and the adversary is given the full ouput of running $\Rep(S)$,
-i.e. $(M,\pubaux,\privaux)$.  The adversary must output a
-function~$f\colon\calS \to \bits^*$ such that $f(S)$ differs from
-$f(S')$ for a set~$S'$ that is subsequently sampled according to~$\distr{\calS}{}$.
-
-\if{0}
-There are several possible definitions:
-\begin{enumerate}
-\item A ``one-wayness'' definition where $S$ has high min-entropy (element-wise), and we
-give the attacker $\pubaux$ and either $M$ or oracle access to $\Qry$. The attacker
-succeeds if it can output an element in~$S$. \tsnote{fixed by
-  changing syntax.}\tsnote{Neither of these seems to capture the Neidermeier et al.
-attack.
-Giving the adversary~$M$ is closest, but our syntax would put the hash function secret keys into~$M$, which the Neidermeier attack doesn't get.}
-
-\item An ``indistinguishability'' definition where either $S_0$ or $S_1$ is used, and the attacker
-must determine which. Here the attacker is given $\pubaux$ but only oracle access to $\Qry$, and
-it is disallowed from asking any query $q$ for which $q(S_0) \neq
-q(S_1)$. \tsnote{I'm not convinced this is the right restriction.
-  This says that security is required \emph{only} for properties that are
-  true of both sets.  So a scheme with $M=S$ will be trivially secure
-  against set membership queries.
-Maybe we restrict from queries~$q$ that are a priori known to have the same value for all sets~$S \in \calS$, or all~$S$ of a given size, etc., as these might be pointless?)}
-
-\tsnote{Is this the right kind of indistinguishability anyway?  This
-  current notion says, in effect, that $S_0$ and $S_1$ are
-  indistinguishable \emph{with respect to the allowed queries}
-  (assuming that $\pubaux$ doesn't stupidly leak information.)  But
-  why not try to formalize the intution that a representation~$M$ and
-  the public info~$\pubaux$ tell you nothing (non-trivial) about the
-  set being represented, period?  (Classical BFs, by the way,
-  essentially leak the number of elements in the set by looking at the
-  number of 0-bits in the array.)   That's tricky to define... I'll
-  take a shot at it.}
-%\tsnote{How will the adversary know that a query satisfies
-%  this in (say) the case of the classical BF?  We can, of course,
-%enforce it in the experiment, but then our resource accounting risks
-%overcounting the number of queries.} \jnote{I was assuming the attacker knows $S_0, S_1$.}
-%\tsnote{Also, we need that, in general, $\aux$ itself
-%does not leak information about~$S_0$ vs.\ $S_1$. } \jnote{Sure, this would be implied
-%by the definition in this case.}
-\end{enumerate}
-\fi
+\tsnote{Still messing about here, and in the figure.}
+In Figure~\ref{fig:privacy-ss} we give a definition capturing semantic-security (of sets)
+with respect to the full representation (ss-rep).  In the ``real''
+setting (ss-rep-1), a set~$S$ is sampled according to distribution~$\distr{\calS}{}$,
+and the adversary is given the~$M,\pubaux$ that result from running
+$\Rep(S)$.  It is also provided oracle access to $\QryOracle$.
+The adversary must output a function~$f\colon\calS \to \bits^*$ and a
+string~$v$ such that $f(S)=v$.  In the ``fake'' setting (ss-rep-0) a
+predictor~$P$ is given $\pubaux$ only, and no $\QryOracle$ access.  It
+also outputs an $f,v$ pair such that $f(S)=v$.  The advantage of~$A$ (over~$P$)
+is $\AdvPrivSS{\Pi,\distr{\calS}{}}{A,P} =
+\Prob{\ExpPrivSSreal{\Pi,\distr{\calS}{}}{A}=1} -
+\Prob{\ExpPrivSSsim{\Pi,\distr{\calS}{}}{P}=1}$.  To prevent trivial wins
+for~$A$, e.g. $f(S)=M$, we forbid~$A$ from outputting~$f$
+such that $f(S)=f(S')$ for all $S,S'$ in the support of $\distr{\calS}{}$.
 
@@
 \centering
-\hfpages{.495}{
+\fpage{.495}{
 \hpagess{.5}{.45}
@@
 }
+\caption{``One-wayness'' style privacy
+  definitions. The bottom is a weaker notion, because the representation
+  is hidden from the adversary.} 
+\label{fig:privacy-ow}
+\end{figure}
+
 %
+\begin{figure}[htbp]
+\centering
+\hfpages{.495}
 {
-\hpagess{.485}{.5}
+\hpagess{.49}{.49}
 {
-%\experimentv{$\ExpPrivInd{\setprim,\distr{\calS}{}}{A}$}\\
-%$b \getsr \bits$\\
-%$S_0,S_1 \getsr \distr{\calS}{}$\\
-%$(M,\pubaux,\privaux) \getsr \Rep(S_b)$\\
-%$b' \getsr A^{\TestOracle}(M,\pubaux)$\\
-%if $b' = b$ then Return 1\\
-%Return 0\\
-%
-%\medskip
-\experimentv{$\ExpPrivSS{\setprim,\distr{\calS}{}}{A}$}\\
+
+\experimentv{$\ExpPrivSSreal{\setprim,\distr{\calS}{}}{A}$}\\
 $S\getsr \distr{\calS}{}$\\
 $(M,\pubaux,\privaux) \getsr \Rep(S)$\\
-$f \getsr A(M,\pubaux,\privaux)$\\
-$S' \getsr \distr{\calS}{}$\\
-if $f(S) \neq f(S')$ then\\
+$(f,v) \getsr A^{\TestOracle}(M,\pubaux)$\\
+if $f(S)=v$ then\\
+\nudge Return 1\\
+Return 0\\
+
+\medskip
+\experimentv{$\ExpPrivSSsim{\setprim,\distr{\calS}{}}{P}$}\\
+$S\getsr \distr{\calS}{}$\\
+$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
+$(f,v) \getsr P(\pubaux)$\\
+if $f(S)=v$ then\\
 \nudge Return 1\\
@@
 Return~$a$\\
-
-%\medskip
-%\oracle{$\RepOracle(S_0,S_1)$}\\
-%if $\mathrm{used}=\true$ then Return $\bot$\\
-%%if $|S_0|\neq|S_1|$ then \\
-%%\nudge Ret $\bot$\\
-%$S_0,S_1 \getsr \distr{\calS}{}$\\
-%$\mathrm{used}=\true$\\
-%$(M,\aux) \getsr \Rep(S_b)$\\
-%Return $(S_0,S_1,\aux)$\\
-
 }
 }
-\caption{Privacy notions. {\bf Left:} ``One-wayness'' style
-  definitions. The bottom is a weaker notion, because the representation
-  is hidden from the adversary. {\bf Right:} An
-  ``indistinguishability'' style notion and a semantic-security style notion. (Still playing...)} 
-\label{fig:privacy}
+{
+\hpagess{.49}{.49}
+{
+\experimentv{$\ExpPrivSS{\setprim,\distr{\calS}{},P}{A}$}\\
+$S\getsr \distr{\calS}{}$\\
+$b \getsr \bits$\\
+%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
+$(M_1,\pubaux,\privaux) \getsr \Rep(S)$\\
+$M_0 \getsr P(\pubaux)$\\
+%$(f,v) \getsr \getsr A^{\TestOracle}(M,\pubaux)$\\
+$b' \getsr A^{\TestOracle}(M_b,\pubaux)$\\
+%if $f(S)=v$ then\\
+if $b'=b$ then\\
+\nudge Return 1\\
+Return 0\\
+%
+%\medskip
+%\experimentv{$\ExpPrivSSsim{\setprim,\distr{\calS}{}}{P}$}\\
+%$S\getsr \distr{\calS}{}$\\
+%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
+%$(f,v) \getsr P(\pubaux)$\\
+%if $f(S)=v$ then\\
+%\nudge Return 1\\
+%Return 0\\
+}
+%
+{
+\oracle{$\TestOracle(q)$}\\
+$a \gets \Qry(M_1,\pubaux,\privaux,q)$\\
+Return~$a$\\
+}
+}
+\caption{Semantic-security style privacy definitions. } 
+\label{fig:privacy-ss}
 \end{figure}
-
 \subsection{Relationships Among Notions}

### 2016-08-23 notions.tex
trying to sort out privacy notions, post-crypto chat

@@
 and the adversary is given the~$M,\pubaux$ that result from running
-$\Rep(S)$.  It is also provided oracle access to $\QryOracle$.
+$\Rep(S)$.  It is also provided oracle access to $\TestOracle$.
 The adversary must output a function~$f\colon\calS \to \bits^*$ and a
 string~$v$ such that $f(S)=v$.  In the ``fake'' setting (ss-rep-0) a
-predictor~$P$ is given $\pubaux$ only, and no $\QryOracle$ access.  It
+predictor~$P$ is given $\pubaux$ only, and no $\TestOracle$ access.  It
 also outputs an $f,v$ pair such that $f(S)=v$.  The advantage of~$A$ (over~$P$)
@@
 }
-\caption{Semantic-security style privacy definitions. } 
+\caption{Semantic-security style privacy
+  definitions. \textcolor{red}{On the left, need to protect against
+    adversary outputting
+    things like $f(S)=M$.  One idea is to forbid~$f$ such that
+    $f(S)=f(S')$ for all $S,S'$ in the support of $\distr{\calS}{}$.}
+    } 
 \label{fig:privacy-ss}

### 2016-08-23 syntax.tex
syntax

@@
 integer, we let $[\univ]^n$ denote the set of all size-$n$ subsets
-\jnote{Multisets?} of~$\univ$. We write $x \getsr \univ$ to denote
+%\jnote{Multisets?} 
+of~$\univ$. We write $x \getsr \univ$ to denote
 sampling an element from~$\univ$ and assigning this to~$x$, and we
@@
 \begin{definition} A \emph{set-multiplicity data structure} is a data
-structure with $D=\mathbb{N}$ \jnote{Notation. (Anyway, I don't
-think we need an explicit symbol for the range of queries.)} and
+structure with $\Gamma=\mathbb{N}$ and
 where $\calQ=\{q_x \,|\, x \in \univ\}$ where $q_x(S)$ is defined to
@@
 It is not hard to see Bloom filters are one possible instantiation a
-set-multiplicity data structure. Fix an $n \geq 0$, let
-$\mathcal{S}=[\univ]^n$, and let $\Sigma=\Gamma=\bits$. Define the
-queries so that $q_x(S)=1$ if $x \in S$, and 0 otherwise.  Define
+set-multiplicity data structure.  Fix $\Sigma=\Gamma=\bits$.  Define
 algorithm~$\Rep$, with functions $k=k(|S|), m=m(|S|)$ and a

### 2016-08-23 syntax.tex
syntax

@@
 Fix a data structure $\setprim=(\Sigma,\Gamma,\calS,\calQ,\Rep,
-\Qry)$. Let $\mathrm{Err}(S,q,M,\privaux)$ be a predicate that is
-true iff $\Qry(M, \privaux, q) \neq q(S)$.  Then a data structure
+\Qry)$. Let $\mathrm{Err}(S,q,M,\pubaux,\privaux)$ be a predicate that is
+true iff $\Qry(M, \pubaux,\privaux, q) \neq q(S)$.  Then a data structure
 has \emph{error probability} $\epsilon$ if
 $\max_{S,q}\Pr[(M,\pubaux,\privaux) \getsr \Rep(S) :
-\mathrm{Err}(S,q,M,\privaux)=1 ] \leq \epsilon$.
+\mathrm{Err}(S,q,M,\pubaux,\privaux)=1 ] \leq \epsilon$.
 %
@@
 $\max_{S}\Pr[(M,\pubaux,\privaux) \getsr \Rep(S);\, q \getsr \calQ :
-\mathrm{Err}(S,q,M,\privaux)=1] \leq \tilde{\epsilon}$. \hfill\dqed
+\mathrm{Err}(S,q,M,\pubaux,\privaux)=1] \leq \tilde{\epsilon}$. \hfill\dqed
 \end{definition}
@@
 \def\bin{{\sf Bin}}
-\heading{Trivial attacks, and error probability vs.\ error rate. }
+\heading{``Trivial'' attacks, and error probability vs.\ error rate. }
 Let~$\Pi$ be a scheme that is $(1-\epsilon)$-correct, and consider
@@
 %Actually, it seems worthwhile to formalize this.
-Let $\mathrm{Err}_i$ be a random variable indicating the event $\Qry(M,\privaux,q_i)\neq q_i(S)$.
+Let $\mathrm{Err}_i$ be a random variable indicating the event $\Qry(M,\pubaux,\privaux,q_i)\neq q_i(S)$.
 The $(1-\epsilon)$-correctness of~$\Pi$ guarantees that the probability that $\mathrm{Err}_i=1$ is at most~$\epsilon$,
@@
 Let $\Rep(S)$ pick a random element~$s \in S$, and return $M = S \setminus \{s\}$ and $\privaux = \emptystring$.
-To respond to queries, let~$\Qry(M,\privaux,q_x)=1$ iff $x \in M$.
+To respond to queries, let~$\Qry(M,\pubaux,\privaux,q_x)=1$ iff $x \in M$.
 It is easy to see that this scheme is $1/n$-correct; for any fixed~$S$, there are exactly~$n$ queries~$q_x$ that have probability~$1/n$  (over the coins of~$\Rep$) of causing a correctness error, and the remaining $|\univ|-n$ queries have probability zero of causing an error.
@@
 events that depend on other sources of randomness. \tsnote{Not sure
-if there's more to say in this section, or if what's here is already
-too much.}
+if there's more to say in this section.}
 
@@
 $h_1, \ldots, h_k$ from~$\mathcal{H}$ and then compute an $m$-bit
-array in the standard way.  It sets $\privaux=\pubaux = (h_1,
-\ldots, h_k)$ and~$M$ to be the bit array, and returns these.  The
-algorithm~$\Qry$ is defined so that, on input $(M,\privaux,q_x)$, it
-returns the AND of the values (either 0 or 1) held at
-$M[h_1(x)],\ldots,M[h_k(x)]$.  We note that, while our error
+array~$M$ (intialized to 0 everywhere) by setting $M[h_i(x)]=1$ for
+all $i\in [k]$ and $x \in S$.  Finally, $\Rep$ returns
+$\privaux=\emptystring$, $\pubaux = (h_1,\ldots, h_k)$, and~$M$ as the
+representation.  
+%
+The algorithm~$\Qry$ is defined so that, on input $(M,\pubaux,\privaux,q_x)$, it
+returns the minimum of the values $M[h_1(x)],\ldots,M[h_k(x)]$.  We note that, while our error
 probability and error rate do not distinguish among ``types'' of

### 2016-08-23 syntax.tex
syntax

@@
 %\jnote{Multisets?} 
-of~$\univ$. We write $x \getsr \univ$ to denote
+of~$\univ$, and $[[\univ]]^n$ for the set of all multisets
+over~$\univ$ with total multiplicity~$n$. We write $x \getsr \univ$ to denote
 sampling an element from~$\univ$ and assigning this to~$x$, and we
@@
 of~$X$, relative to some fixed encoding.  When~$X$ is a multiset, we
-overload the notation so that~$|X|$ is the number of elements in~$X$
-(with mutiplicity).
+overload the notation so that~$|X|$ is the total multiplicity of~$X$.
 
@@
 \begin{definition}[Data structure] \rm
-Fix a non-empty set~$\univ$. A \emph{static data structure} (over universe~$\univ$)
+Fix a non-empty set~$\univ$. A \emph{data structure} (over universe~$\univ$)
 is a tuple $\setprim=(\Sigma,\Gamma,\calS,\calQ,\Rep, \Qry)$ where:
 \begin{itemize}
-\item $\Sigma$ is the \emph{representation alphabet}. \jnote{Is
-    there any reason not to simply fix this to $\{0,1\}$?}
+\item $\Sigma$ is the \emph{representation alphabet}.
+%\jnote{Is there any reason not to simply fix this to $\{0,1\}$?}
 \item $\Gamma$ is the set of possible \emph{query answers}.
-    \jnote{Do we need this for any reason?}
+%\jnote{Do we need this for any reason?}
 \item $\calS$ is a set  of multisets over universe~$\univ$.
@@
     \emph{private side information} $\privaux \in \bits^*$, and
-    \emph{public side information} $\pubaux \in \bits^*$.
-\item $\Qry\colon \Sigma^* \times \bits^* \times \calQ \to
+    \emph{public side information} $\pubaux \in \bits^*$.  We write
+    $(M,\pubaux,\privaux \getsr \Rep(S)$ as shorthand for this execution.
+\item $\Qry\colon \Sigma^* \times \bits^* \times \bits^* \times \calQ \to
     \Gamma$ is a deterministic \emph{query-evaluation}
-    algorithm, taking as input $M, \pubaux,\privaux, q$, and returns
-    \emph{answer} $a \in \Gamma$. 
+    algorithm, taking as input $M\in\Sigma^*$, $\pubaux,\privaux \in
+    \bits^*$ and $q \in \calQ$, and outputting
+    an \emph{answer} $a \in \Gamma$.  We write $a \gets
+    \Qry(M,\pubaux,\privaux,q)$ for this execution.
 \end{itemize}
@@
 Note that $1-\epsilon$ is a worst-case lower bound on the
-correctness of the data structure.
+correctness of the data structure. \tsnote{Don't know if this will be necessary.}
 
@@
 uniform samples from~$\calQ$.
-%The expected number of random queries needed to
-%find a error is $1/\epsilon$ tries; thus, an attacker making $O(t/\epsilon)$ queries succeeds with constant probability (almost always).
-%Actually, it seems worthwhile to formalize this.
 Let $\mathrm{Err}_i$ be a random variable indicating the event $\Qry(M,\pubaux,\privaux,q_i)\neq q_i(S)$.
@@
 \end{definition}
-%
-%\todo{Readdress issue of representation size.
-A general statement might be something like `` The \emph{size} of a set-representation is the maximum (bit)length of any~$M$ that can be output by $\Rep$.''  But all of the natural constructions will have representation whose size will not depend on the coins of $\Rep$, i.e.
-they depend on $|S|$, number of hash functions, desired error rate.
-}
 
-%Our treatment of $M,\privaux$ is not symmetric, since we only count $M$ against the size
-%of the set-representation. When we define security
-%we may give the attacker $\privaux$ but not~$M$, and in that case the set-representation cannot
-%trivially make everything part of~$\privaux$.
-%\tsnote{Encoding secrets into~$M$ may cause some headaches in the security definitions; we'll see. }
-%\tsnote{By the way, I'm coming around to the
-%  viewpoint that it is fair to include in the ``size'' of the
-%  representation any secret information.  In makes more difficult
-%  comparisons to classical lower-bounds (which [NY] makes, incorrectly
-% IMO), but it does seem fair to say ``this is how many bits of memory
-% you need to allocate to represent this set \emph{securely}.''}
-
-%\heading{Bloom Filters and Related Data Structures. }
-It is not hard to see Bloom filters are one possible instantiation a
+It is not hard to see Bloom filters are an instantiation a
 set-multiplicity data structure.  Fix $\Sigma=\Gamma=\bits$.  Define

### 2016-08-23 syntax.tex
syntax

@@
 integer, we let $[\univ]^n$ denote the set of all size-$n$ subsets
-%\jnote{Multisets?} 
 of~$\univ$, and $[[\univ]]^n$ for the set of all multisets
-over~$\univ$ with total multiplicity~$n$. We write $x \getsr \univ$ to denote
+over~$\univ$ with total multiplicity~$n$. \tsnote{We may not need all
+  of that.} We write $x \getsr \univ$ to denote
 sampling an element from~$\univ$ and assigning this to~$x$, and we
@@
 mechanism to answer a specified collection of questions about that
-multiset.  Informally, the representation should serve as a good
-approximation of the multiset, at least with respect to the allowed
-questions.
+multiset. 
+%Informally, the representation should serve as a good
+%approximation of the multiset, at least with respect to the allowed queries.
 \begin{definition}[Data structure] \rm
@@
     \emph{public side information} $\pubaux \in \bits^*$.  We write
-    $(M,\pubaux,\privaux \getsr \Rep(S)$ as shorthand for this execution.
+    $(M,\pubaux,\privaux) \getsr \Rep(S)$ as shorthand for this execution.
 \item $\Qry\colon \Sigma^* \times \bits^* \times \bits^* \times \calQ \to
@@
 
-\heading{Set-multiplicity Data Structures. } Our particular focus
+\heading{Data Structures for Set-Multiplicity Queries. } Our particular focus
 will be on data structures that support multiplicity queries, of
@@
 count-min sketches~\cite{xxx}, scalable Bloom filters~\cite{xxx},
-etc., in a later section.
+etc., in a later section.\tsnote{If we ultimately do!}
 
-A Bloom filter with secret hash functions is captured by setting $\privaux=(h_1,h_2,\ldots,h_k)$, and setting $\pubaux=\emptystring$.
-Related constructions \tsnote{Name them?} that use a secret key~$K$, but not for hashing, are captured setting $\privaux=K, \pubaux=(h_1, \ldots, h_k)$.
+A Bloom filter with secret hash functions is captured by setting
+$\privaux=(h_1,h_2,\ldots,h_k)$, and setting $\pubaux=\emptystring$.
+Related constructions that use a secret key~$K$, but not for hashing (e.g. the PRP-based
+construction from NY), are captured setting $\privaux=K, \pubaux=(h_1, \ldots, h_k)$.
 

### 2016-08-23 syntax.tex
syntax

@@
 $\privaux=(h_1,h_2,\ldots,h_k)$, and setting $\pubaux=\emptystring$.
-Related constructions that use a secret key~$K$, but not for hashing (e.g. the PRP-based
+Related constructions that use a secret key~$K$, but not for hashing (e.g.\ the PRP-based
 construction from NY), are captured setting $\privaux=K, \pubaux=(h_1, \ldots, h_k)$.
 
-The so-called ``garbled Bloom filter'' due to Dong, Chen and Wen~\cite{xxx}, which stores xor-shares of bitstring~$x \in S$ at positions $h_1(x),h_2(x),\ldots,h_k(x)$ in an array, falls within our syntax by letting~$\Sigma=\bits^L$ for a specified integer~$L>0$.
-Similarly the cuckoo-hashing construction from NY, which (loosely speaking) stores a hash $g(x)$ at positions determined by $h_1(x),h_2(x),\ldots,h_k(x)$.
-\tsnote{Check the correctness of this claim.}
+By setting $\Sigma=\bits^L$ for a specified $L>0$, we capture he
+so-called ``garbled Bloom filter'' due to Dong, Chen and
+Wen~\cite{xxx}.  This stores xor-shares of bitstring~$x \in S$ at
+positions $h_1(x),h_2(x),\ldots,h_k(x)$ in an array.  Similarly, the
+cuckoo-hashing construction from NY, which (loosely speaking) stores a
+hash $g(x)$ at positions determined by $h_1(x),h_2(x),\ldots,h_k(x)$,
+is captured when $L=|g(x)|$. \tsnote{Check the correctness of this claim.}

### 2016-08-23 notions.tex
syntax

@@
 set-representations.
-The first two have the flavor of a one-wayness game, in which the adversary is given the auxiliary information~$\pubaux$ and, either the representation~$M$ or the abillity to call an oracle that evaluates $\Qry(M,\privaux,q)$ on queries~$q$ of its choosing.
+The first two have the flavor of a one-wayness game, in which the adversary is given the auxiliary information~$\pubaux$ and, either the representation~$M$ or the abillity to call an oracle that evaluates $\Qry(M,\pubaux,\privaux,q)$ on queries~$q$ of its choosing.
 At the end of this game, the adversary must output some point in the set represented by~$M$.
 In the second privacy notion, the adversary presents two sets~$S_0$ and $S_1$ (of equal size) and a representation~$M$ is created for one of these two.
-Then the adversary is given $\pubaux$ and oracle access to $\Qry(M,\privaux,q)$, and it must decide which set~$M$ represents.
+Then the adversary is given $\pubaux$ and oracle access to $\Qry(M,\pubaux,\privaux,q)$, and it must decide which set~$M$ represents.
 
@@
 \oracle{$\TestOracle(q)$}\\
-$a \gets \Qry(M,\privaux,q)$\\
+$a \gets \Qry(M,\pubaux,\privaux,q)$\\
 if $a \neq q(S)$ then \\

### 2016-08-23 notions.tex
slight notational change, removing explicit subscript \calS from distribution

@@
 First, a set~$S$ is chosen according to some
-distribution~$\distr{\calS}{}$ over the collection of multisets
+distribution~$\distr{}{}$ over the collection of multisets
 $\mathcal{S}$ associated to~$\Pi$, and then
@@
 {
-\experimentv{$\ExpCorrect{\setprim,\distr{\calS}{},r}{A}$}\\
-$S \getsr \distr{\calS}{}$\\
+\experimentv{$\ExpCorrect{\setprim,\distr{}{},r}{A}$}\\
+$S \getsr \distr{}{}$\\
 $\mathrm{err}\gets 0$\\
@@
 \caption{Correctness of~$\Pi$ against (adaptive) adversary~$A$, when
-  the target multiset~$S$ is sampled from~$\calS$ according to distribution~$\distr{\calS}{}$.} 
+  the target multiset~$S$ is sampled from~$\calS$ according to distribution~$\distr{}{}$.} 
 \label{fig:correctness}
@@
 We define the advantage of adversary~$A$ in the correctness experiment as 
-$\AdvCorrect{\Pi,\distr{\calS}{},r}{A} = \Prob{\ExpCorrect{\Pi,\distr{\calS}{}, r,}{A}=1}$.
-Overloading notation, we write $\AdvCorrect{\Pi,\distr{\calS}{},r}{t,q}$ for the maximum over all~$t$-time adversaries that ask at most~$q$ queries. Roughly, we say that a
-set-representation~$\Pi$ is $(t,q,r,\epsilon')$-correct if $\AdvCorrect{\Pi,\distr{\calS}{},r}{t,q} \leq \epsilon'$.
+$\AdvCorrect{\Pi,\distr{}{},r}{A} = \Prob{\ExpCorrect{\Pi,\distr{}{}, r,}{A}=1}$.
+Overloading notation, we write $\AdvCorrect{\Pi,\distr{}{},r}{t,q}$ for the maximum over all~$t$-time adversaries that ask at most~$q$ queries. Roughly, we say that a
+set-representation~$\Pi$ is $(t,q,r,\epsilon')$-correct if $\AdvCorrect{\Pi,\distr{}{},r}{t,q} \leq \epsilon'$.
 
@@
 representation~$M$ and the allowed queries, about set elements.  We
-define advantage measures $\AdvPriv{\Pi,\distr{\calS}{}}{A} =
-\Prob{\ExpPriv{\Pi,\distr{\calS}{}}{A}=1}$ and $\AdvWPriv{\Pi,\distr{\calS}{}}{A} =
-\Prob{\ExpWPriv{\Pi,\distr{\calS}{}}{A}=1}$; in both we track the
+define advantage measures $\AdvPriv{\Pi,\distr{}{}}{A} =
+\Prob{\ExpPriv{\Pi,\distr{}{}}{A}=1}$ and $\AdvWPriv{\Pi,\distr{}{}}{A} =
+\Prob{\ExpWPriv{\Pi,\distr{}{}}{A}=1}$; in both we track the
 time-complexity~$t$ and number of oracle queries~$q$ made by the adversary.
@@
 with respect to the full representation (ss-rep).  In the ``real''
-setting (ss-rep-1), a set~$S$ is sampled according to distribution~$\distr{\calS}{}$,
+setting (ss-rep-1), a set~$S$ is sampled according to distribution~$\distr{}{}$,
 and the adversary is given the~$M,\pubaux$ that result from running
@@
 also outputs an $f,v$ pair such that $f(S)=v$.  The advantage of~$A$ (over~$P$)
-is $\AdvPrivSS{\Pi,\distr{\calS}{}}{A,P} =
-\Prob{\ExpPrivSSreal{\Pi,\distr{\calS}{}}{A}=1} -
-\Prob{\ExpPrivSSsim{\Pi,\distr{\calS}{}}{P}=1}$.  To prevent trivial wins
+is $\AdvPrivSS{\Pi,\distr{}{}}{A,P} =
+\Prob{\ExpPrivSSreal{\Pi,\distr{}{}}{A}=1} -
+\Prob{\ExpPrivSSsim{\Pi,\distr{}{}}{P}=1}$.  To prevent trivial wins
 for~$A$, e.g. $f(S)=M$, we forbid~$A$ from outputting~$f$
-such that $f(S)=f(S')$ for all $S,S'$ in the support of $\distr{\calS}{}$.
+such that $f(S)=f(S')$ for all $S,S'$ in the support of $\distr{}{}$.
 
@@
 {
-\experimentv{$\ExpPriv{\setprim,\distr{\calS}{}}{A}$}\\
-$S \getsr \distr{\calS}{}$\\
+\experimentv{$\ExpPriv{\setprim,\distr{}{}}{A}$}\\
+$S \getsr \distr{}{}$\\
 $(M,\pubaux,\privaux) \getsr \Rep(S)$\\
@@
 \medskip
-\experimentv{$\ExpWPriv{\setprim,\distr{\calS}{}}{A}$}\\
-$S \getsr \distr{\calS}{}$\\
+\experimentv{$\ExpWPriv{\setprim,\distr{}{}}{A}$}\\
+$S \getsr \distr{}{}$\\
 $(M,\pubaux,\privaux) \getsr \Rep(S)$\\
@@
 
-\experimentv{$\ExpPrivSSreal{\setprim,\distr{\calS}{}}{A}$}\\
-$S\getsr \distr{\calS}{}$\\
+\experimentv{$\ExpPrivSSreal{\setprim,\distr{}{}}{A}$}\\
+$S\getsr \distr{}{}$\\
 $(M,\pubaux,\privaux) \getsr \Rep(S)$\\
@@
 \medskip
-\experimentv{$\ExpPrivSSsim{\setprim,\distr{\calS}{}}{P}$}\\
-$S\getsr \distr{\calS}{}$\\
+\experimentv{$\ExpPrivSSsim{\setprim,\distr{}{}}{P}$}\\
+$S\getsr \distr{}{}$\\
 $(M,\pubaux,\privaux) \getsr \Rep(S)$\\
@@
 {
-\experimentv{$\ExpPrivSS{\setprim,\distr{\calS}{},P}{A}$}\\
-$S\getsr \distr{\calS}{}$\\
+\experimentv{$\ExpPrivSS{\setprim,\distr{}{},P}{A}$}\\
+$S\getsr \distr{}{}$\\
 $b \getsr \bits$\\
@@
 %\medskip
-%\experimentv{$\ExpPrivSSsim{\setprim,\distr{\calS}{}}{P}$}\\
-%$S\getsr \distr{\calS}{}$\\
+%\experimentv{$\ExpPrivSSsim{\setprim,\distr{}{}}{P}$}\\
+%$S\getsr \distr{}{}$\\
 %$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
@@
     things like $f(S)=M$.  One idea is to forbid~$f$ such that
-    $f(S)=f(S')$ for all $S,S'$ in the support of $\distr{\calS}{}$.}
+    $f(S)=f(S')$ for all $S,S'$ in the support of $\distr{}{}$.}
     } 

### 2016-08-23 notions.tex
cheers

@@
 \label{sec:security-notions}
-\tsnote{intro text}
 Following NY, we are interested in defining an adaptive (i.e.,
@@
 \caption{Correctness of~$\Pi$ against (adaptive) adversary~$A$, when
-  the target multiset~$S$ is sampled from~$\calS$ according to distribution~$\distr{}{}$.} 
+  the represented multiset~$S$ is sampled according to distribution~$\distr{}{}$.} 
 \label{fig:correctness}
@@
 set-representation~$\Pi$ is $(t,q,r,\epsilon')$-correct if $\AdvCorrect{\Pi,\distr{}{},r}{t,q} \leq \epsilon'$.
-
-%
-%And if the experiment requires the adversary to induce~$r$ errors, the attack wins iff
-%$N \stackrel{{\rm def}}{=} \sum_{i=1}^T X_i \geq r$.  Modelling the $X_i$ as independent Bernoulli trials with
-%probability~$\epsilon$ gives $N$ a binomial distribution.  \fixme{Something feels wrong with this...}  
-%Writing $\bin(T, \epsilon; r)$ for the probability that $N \geq r$,
-%we conclude that the \emph{best} correctness we can hope for against adversaries making~$T$ queries is  $\bin(T,\epsilon; t))$.
-%\jnote{Need to find different terms to use for a query $q \in \mathcal{Q}$
-%and a query that the attacker makes to its oracle.}
-%\tsnote{Viewed another way, we could let~$T$ be a negative binomial RV, and ask how many queries are needed (w.h.p) for $N \geq t$.} 
-%
-%\jnote{One option is to define the adversary's \emph{advantage} as the difference between
-%its success probability and the success probability of the above,
-%trivial attack. Just a thought.}
-%\tsnote{Or, perhaps by recasting security
-%  as distinguishing between $\Qry(M,\aux,\cdot)$ and an oracle that
-%  returns 0,1 according to Bernoulli with paramter~$\epsilon$.}
-%\fixme{Not clear this attack is generically applicable enough to serve as a reference/baseline.
-(See email discusssion 7/23.)  Might be worth pointing out that this intuition, between non-adaptive error-probability and the expected number of queries to find an error, can be quite misleading.}
 
@@
 
-\tsnote{Still messing about here, and in the figure.}
+\tsnote{Wet paint...}
 In Figure~\ref{fig:privacy-ss} we give a definition capturing semantic-security (of sets)
@@
 for~$A$, e.g. $f(S)=M$, we forbid~$A$ from outputting~$f$
-such that $f(S)=f(S')$ for all $S,S'$ in the support of $\distr{}{}$.
+such that $f(S)=f(S')$ for all $S,S'$ in the support of the
+distribution $\distr{}{}$.
 
@@
 \end{figure}
-\subsection{Relationships Among Notions}
 
-\heading{Privacy notions. }
-Clearly we have priv $\Rightarrow$ wpriv, tightly and by a simple
-reduction.  We should be able to show
-\begin{itemize}
-%\item ss-rep $\Rightarrow$ ind-qry
-%\item ind-qry $\Rightarrow$ ss-rep \tsnote{Not sure about this separation...}
-\item ss-rep $\Rightarrow$ priv \emph{for set-multiplicity data
-    structures} \tsnote{but probably not in general}
-\item \{w\}priv $\not\Rightarrow$ ss-rep
-\item wpriv $\not\Rightarrow$ priv \tsnote{$M=S$, or my
-    $M=S\setminus \{x\}$ for a random $x\in S$, if you want something
-    a bit less trivial. I'm sure there are more natural schemes that
-    will separate, too.}
-\end{itemize}
+\subsection{Relationships Among Notions}\todo{Decide which of these
+  statements should have formal theorems and proofs.}
+Clearly we have priv $\Rightarrow$ wpriv, tightly and by an obvious
+reduction.  The converse is not true, however: consider the previous
+construction in which $M = S \setminus \{x\}$ for a random $x \in S$,
+and $\pubaux=\privaux=\emptystring$.  We note that this construction
+also serves to separate the priv notion from our notion of
+correctness.  (It is $1-(1/|S|)$ correct, but has no priv-security.)
 
-\heading{Correctness vs.\ Privacy. }
-If we allow for trivial schemes, e.g. $M=S$, then correctness and the stronger version of one-wayness privacy (Priv) are clearly orthogonal.
-\tsnote{My $M=S\setminus\{x\}$ for a random $x \in S$ construction is less trivial (it compresses), but also serves to separate correctness from Priv.}
-\tsnote{In general, it isn't clear how to reduce
-correctness to the Priv notion.  In the correctness experiment, you
-  get~$(S,\aux)$ but not~$M$; whereas in the Priv-notion, the
-  adversary expects~$(M,\aux)$ as input.  Unless the coins of Rep are
-  effectively leaked in~$\aux$, you can't reliably produce~$M$
-  given~$(S,\aux)$.} 
-Curiously, $M=S$ does seem to be both correct and private (up to the element-wise min-entropy of~$S$) in the weaker version of one-wayness privacy (wPriv).
-\tsnote{Reducing correctness to the weaker version, wPriv, is syntactically possible, but not clear how to connect the success events.
+Curiously, the trivial scheme that sets $M=S$, $\pubaux=\privaux=\emptystring$ does seem to be both correct and wpriv-secure (up to the element-wise min-entropy of~$S$).
+\tsnote{In general, reducing correctness to wPriv is syntactically possible, but not clear how to connect the success events.
 In the one-wayness game, you win by outputing an element of~$S$; but how does this lead to finding an error-inducing query?
@@
 }
+\tsnote{Likewise the other way: the one-wayness adversary does not get~$S$, and yet needs to provide this to the correctness adversary.}
 
-\tsnote{Likewise the other way: the one-wayness adversary does not get~$S$, and yet needs to provide this to the correctness adversary.}
+We should be able to show
+\begin{itemize}
+\item ss-rep $\Rightarrow$ priv \emph{for set-multiplicity data
+    structures} \tsnote{but probably not in general}
+\item \{w\}priv $\not\Rightarrow$ ss-rep
+\end{itemize}

### 2016-08-23 results.tex
cheers

@@
 \section{Achieving Security Notions}
+\todo{Below are two lists of things that we should show.}
+
 \heading{Correctness. }  Here we give security proofs and attacks with respect to the correctness notions.
@@
 \item Show Bloom Filter is correct in the ROM %\jnote{Would be good to show that RO-based Bloom filter is FP-secure.}
-\item FP-security/attacks on bigram/PRF-based double-hashing construction ($h_j(x) = F_{K1}(x) + j\cdot F_{K2}(x) \bmod m$ where the~$x$ are bigrams of names, etc.) 
-\item FP-security/attacks on bigram/domain-separated PRF construction ($h_j(x)=F_K(\langle j,x \rangle) \bmod m$, or just assume range of~$F$ is $[m]$.)
-\item FP-security/attacks Dong, Chen, Wen ``garbled Bloom filter'' construction
+\item correctness security/attacks on bigram/PRF-based double-hashing construction ($h_j(x) = F_{K1}(x) + j\cdot F_{K2}(x) \bmod m$ where the~$x$ are bigrams of names, etc.) 
+\item correctness-security/attacks on bigram/domain-separated PRF construction ($h_j(x)=F_K(\langle j,x \rangle) \bmod m$, or just assume range of~$F$ is $[m]$.)
+\item correctness-security/attacks Dong, Chen, Wen ``garbled Bloom filter'' construction
 \item ...
@@
 \heading{Privacy. } Here we give security proofs and attacks with respect to the privacy notions we have defined.
-\tsnote{Under our current notions, you can never hope to prove privacy bounds that beat the min-entropy of $\distr{U}{n}$.}
+\tsnote{Under our current notions, you can never hope to prove privacy bounds that beat the element wise min-entropy of $\distr{}{}$.}
 \begin{itemize}
-\item Prove that the basic BF, in the ROM, is private.  \tsnote{Not at all surprising, but it is the first result one would want in this area.}
+\item Prove that the basic BF, in the ROM, is private.  \tsnote{Relative the strongest notion for which this is true.  If it isn't true for all, then give the attack(s).}
 
@@
 \tsnote{I believe this also shows that the bigram/PRF approach examined by Neidermayer et al.\ is secure when the hash functions are the $h_j(x)$ just described.
+This was, in fact, one of the countermeasures they proposed.
 }
@@
 \item Cast Neidermayer et al.\ attacks on the bigram/PRF-based double-hashing construction (see their paper) into our formalism.
-\tsnote{Note that their attack would allow one to recover \emph{every} name, not just one.} \tsnote{Note that Neidermayer et al.\ suggest ditching the double-hashing construction in favor of independent PRFs, so the previous item basically explores their suggestion.}
+\tsnote{Note that their attack would allow one to recover \emph{every} name, not just one.}
 
@@
 
-\item Show implications and/or separations between FP and privacy notions.
+\item Show implications and/or separations between FP and privacy notions. \tsnote{Belongs in previous section.}
 

### 2016-08-23 results.tex
cheers

@@
 \begin{itemize}
-\item Show Bloom Filter is correct in the ROM %\jnote{Would be good to show that RO-based Bloom filter is FP-secure.}
+\item Show Bloom Filter is correct in the ROM 
 \item correctness security/attacks on bigram/PRF-based double-hashing construction ($h_j(x) = F_{K1}(x) + j\cdot F_{K2}(x) \bmod m$ where the~$x$ are bigrams of names, etc.) 
@@
 \item correctness-security/attacks Dong, Chen, Wen ``garbled Bloom filter'' construction
-\item ...
+
 \end{itemize}
@@
 \item Prove a privacy bound for the bigram/PRF-based double-hashing construction that Neidermayer et al.\ attacks.
-I'm pretty sure the attack is in the public-BB setting, and the provable security bound is considerably worse than the min-entropy because of the way the representation is made.
+I expect that the provable security bound is considerably worse than the min-entropy because of the way the representation is made.
 (Essentially, the Hamming weight of the representation is a good estimate of the length of the longest surname in filter.)
 
-\item Attack privacy of Dong, Chen, Wen ``garbled Bloom Filter'' construction in the BB-hash setting \tsnote{I give the attack in the related work section.
-Copy it here and flesh it out.}  Prove privacy of construction in secret-hash setting.
+\item Attack priv-security of Dong, Chen, Wen ``garbled Bloom Filter'' construction when the hash functions are public.\tsnote{I give the attack in the related work section.
+Copy it here and flesh it out.}  Prove priv-security privacy of construction when hash functions are secret.
 \tsnote{Makes the point that the application setting really matters.}
@@
 
-\item Show implications and/or separations between FP and privacy notions. \tsnote{Belongs in previous section.}
-
-\item \tsnote{...}
+\item ...
 \end{itemize}

### 2016-08-23 notions.tex
cheers

@@
 In addition to correctness, we establish three notions of privacy for
-set-representations.
-The first two have the flavor of a one-wayness game, in which the adversary is given the auxiliary information~$\pubaux$ and, either the representation~$M$ or the abillity to call an oracle that evaluates $\Qry(M,\pubaux,\privaux,q)$ on queries~$q$ of its choosing.
-At the end of this game, the adversary must output some point in the set represented by~$M$.
-In the second privacy notion, the adversary presents two sets~$S_0$ and $S_1$ (of equal size) and a representation~$M$ is created for one of these two.
-Then the adversary is given $\pubaux$ and oracle access to $\Qry(M,\pubaux,\privaux,q)$, and it must decide which set~$M$ represents.
+set-representations. The first two have the flavor of a one-wayness
+game, in which the adversary seeks to return an element of the
+represented set~$S$.  The final notion is reminiscent of
+semantic-security for encryption schemes, and attempts to capture the
+intuition that the representation~$M$ and the public
+information~$\pubaux$ should not leak any efficiently computable
+information about~$S$.
+
+\tsnote{flesh out}
 
@@
 
-We should be able to show
+\todo{We should be able to show...}
 \begin{itemize}

### 2016-08-23 results.tex
Theorem1,2 modified and moved to section4

@@
 \section{Achieving Security Notions}
+\heading{Linear-PRF construction. }
+Here we consider a set-multiplicity data structure that was attacked by Neidermayer et al.
+in~\cite{xxx}.
+Let $\Pi_{\mathrm{lin}}= (\Sigma,\Gamma,\calS,\calQ,\Rep, \Qry)$ be defined as follows.
+Fix an $n \geq 0$, let $\mathcal{S}=[\univ]^n$, and let $\Sigma=\Gamma=\bits$.
+The queries are defined so that $q_x(S)=1$ if $x \in S$, and 0 otherwise.
+Fix non-empty sets ~$\calK$, $\univ$ and integers $k,m,n>0$.
+Let $F\colon\mathcal{K} \times \univ \to [m]$ be a function family.
+Define $\Hash$ as an algorithm that samples two keys $K_0,K_1 \getsr \mathcal{K}$ and defines $h_j(x) = F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$ for $j \in [1,k]$.
+$\Rep$ uses $\Hash$ to set $\privaux=\pubaux = (h_1, \ldots, h_k)$, computes an $m$ bit array, $M$ in the standard way and returns $(M,\pubaux,\privaux)$.
+The $\Qry$ algorithm gets $(M,\privaux, q_x)$ as input, and returns the AND of values at $M[h_1(x)],\ldots,M[h_k(x)]$.
+It must be noted that $\Pi_{\mathrm{lin}}$ admits errors in form of false-positives(FP) only.
+So, error rate of $\Pi_{\mathrm{lin}}$ is same as the (non-adaptive) FP rate.
+The following result shows, informally, that if~$F$ is a good PRF and the error rate is sufficiently small, then $\Pi_\mathrm{lin}$ is correct against adaptive error-finding adversaries.
+Henceforth, we refer errors and error-rate in $\Pi_{\mathrm{lin}}$ as FP's and FP rate, respectively.
+
+\begin{theorem}\label{thm1}
+Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{lin}}= (\Sigma,\Gamma,\calS,\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described.
+For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exist prf-adversaries~$B_1,B_2$ (explicitly constructed in the proof of this theorem) such that
+\[
+\AdvCorrect{\Pi_{\mathrm{lin}},\distr{\calS}{},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\]
+Here, $B_1$ and $B_2$, each ask~$q$ oracle queries and have time complexity~$O(t+qm)$.
+\end{theorem}
+Before giving the proof, we note that Kirsch and Mitzenmacher~\cite{xxx} show
+that the ($r=1$, non-adaptive) FP-probability for~$\Pi_\mathrm{lin}$ is
+always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
+rate of convergence is faster than~$1/n$.  The factor of $\dbinom{q}{r}$ arises as a result
+of removing adaptivity.  Finally, $\dbinom{q}{r} \leq q^r$ (with
+reasonable tightness when~$r$ is small) in which case the final term in the bound behaves as 
+$(q (1-e^{-kn/m})^k + O(q/n) )^r$; loosely, the bound one expects for
+trying to find a single FP in each of~$r$ independent``rounds'', each round
+consisting of~$q$ attempts.
+
+\heading{Construction of PRF with domain separation.}
+Let $\Pi_{\mathrm{ds}}= (\Sigma,\Gamma,\calS,\calQ,\Rep, \Qry)$ be a set-multiplicity data structure identical to $\Pi_{\mathrm{lin}}$, except the $Hash$ algorithm, which is defined as follows.
+Fix non-empty sets ~$\calK$, $\univ$ and integers $k,m,n>0$.
+Let $F\colon\mathcal{K} \times \univ \to [m]$ be a function family.
+The $\Hash$ algorithm provides randomness with domain separation, as it samples key $K \getsr \mathcal{K}$ and defines $h_j(x) = F_K(\langle j,x \rangle) $ for $j \in [1,k]$.
+Like $\Pi_{\mathrm{lin}}$, $\Pi_{\mathrm{ds}}$ admits errors in form of false positives only.
+Informally, the following result shows, if~$F$ is PRF secure and the data structure has low error rate in the non-adaptive setting, then $\Pi_{\mathrm{ds}}$ is correct against adaptive error finding adversaries.
+Hereafter, we refer errors and error-rate in $\Pi_{\mathrm{ds}}$ as false-positives and false-positive rate, respectively.
+
+\begin{theorem}\label{thm2}
+Fix $k,m,n,r >0$.
+Let $\Pi_{\mathrm{ds}}$ be the set-multiplicity data structure just described.
+If there exists an adaptive adversary, $A$ compatible with $\ExpCorrect{\Pi_{\mathrm{ds}},\distr{\calS}{},r}{\cdot}$ asking $q$ queries, and has time complexity O(t), then there exists a prf-adversary $B$ (explicitly constructed in the proof of this theorem), such that
+\[
+\AdvCorrect{\Pi_{\mathrm{ds}},\distr{\calS}{},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\]
+Here, $B$ asks $q$ queries, and has time complexity $O(t+qm)$.
+\end{theorem}
+
 \todo{Below are two lists of things that we should show.}

### 2016-08-23 Theorem1_FP.tex
Proof 1,2 typos fix
Proof1,2 modified

@@
-%\acnote{I am moving comments to end of the proof in tex file and commenting them as the labels are getting mangled}
-\heading{Linear-PRF construction. }
-Here we consider a hash-based filter that was attacked by Neidermayer et al.
+%\heading{Linear-PRF construction. }
+%Here we consider a set-multiplicity data structure that was attacked by Neidermayer et al.
 in~\cite{xxx}.
-Let $B_{\mathrm{lin}}=(\Hash,\Rep,\Qry)$ be defined as follows.
+Let $\Pi_{\mathrm{lin}}= (\Sigma,\Gamma,\calS,\calQ,\Rep, \Qry)$ be defined as follows.
+Fix an $n \geq 0$, let $\mathcal{S}=[\univ]^n$, and let $\Sigma=\Gamma=\bits$.
+The queries are defined so that $q_x(S)=1$ if $x \in S$, and 0 otherwise.
 Fix non-empty sets ~$\calK$, $\univ$ and integers $k,m,n>0$.
 Let $F\colon\mathcal{K} \times \univ \to [m]$ be a function family.
-The $\Hash$ algorithm samples two keys $K_0,K_1 \getsr \mathcal{K}$ and defines $h_j(x) = F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$ for $j \in [1,k]$.
-The $\Rep$ and $\Qry$ algorithms are the standard (determinisitic) BF ones.
-$B_{\mathrm{lin}}$ is in fact one instantiation of a set-multiplicity data structure.
-It must be noted that $B_{\mathrm{lin}}$ admits errors in form of false-positives(FP) only.
-So, error rate of $B_{\mathrm{lin}}$ is same as the (non-adaptive) FP rate.
-The following result shows, informally, that if~$F$ is a good PRF and the error rate is sufficiently small, then $B_\mathrm{lin}$ is correct against adaptive error-finding adversaries.
-Henceforth, we refer errors and error-rate in $B_{\mathrm{lin}}$ as FP's and FP rate, respectively.
-
-\begin{theorem}\label{thm1}
-Fix $k,m,n,r>0$, and let $B_\mathrm{lin}=(\Hash,\Rep,\Qry)$ be the hash-based filter just described. 
-For any adversary~$A$ that makes a total of~$q$ queries to its oracle
-and has time-complexity~$O(t)$,
-there exist adversaries~$B_1,B_2$ (explicitly constructed in the proof of this theorem) such that
-\[
-\AdvCorrect{B_{\mathrm{lin}},\distr{\calS}{},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
-\]
-Here, $B_1$ and $B_2$, each ask~$q$ oracle queries and have time complexity~$O(t+qm)$.
-\end{theorem}
-Before giving the proof, we note that Kirsch and Mitzenmacher~\cite{xxx} show
-that the ($r=1$, non-adaptive) FP-probability for~$B_\mathrm{lin}$ is
-always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
-rate of convergence is faster than~$1/n$.  The factor of $\dbinom{q}{r}$ arises as a result
-of removing adaptivity.  Finally, $\dbinom{q}{r} \leq q^r$ (with
-reasonable tightness when~$r$ is small) in which case the final term in the bound behaves as 
-$(q (1-e^{-kn/m})^k + O(q/n) )^r$; loosely, the bound one expects for
-trying to find a single FP in each of~$r$ independent``rounds'', each round
-consisting of~$q$ attempts.
+Define $\Hash$ as an algorithm that samples two keys $K_0,K_1 \getsr \mathcal{K}$ and defines $h_j(x) = F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$ for $j \in [1,k]$.
+$\Rep$ uses $\Hash$ to set $\privaux=\pubaux = (h_1, \ldots, h_k)$, and computes an $m$ bit array, $M$ in the standard way and returns $(M,\pubaux,\privaux)$.
+The $\Qry$ algorithm gets $(M,\privaux, q_x)$ as input, and returns the AND of values at $M[h_1(x)],\ldots,M[h_k(x)]$.
+It must be noted that $\Pi_{\mathrm{lin}}$ admits errors in form of false-positives(FP) only.
+So, error rate of $\Pi_{\mathrm{lin}}$ is same as the (non-adaptive) FP rate.
+The following result shows, informally, that if~$F$ is a good PRF and the error rate is sufficiently small, then $\Pi_\mathrm{lin}$ is correct against adaptive error-finding adversaries.
+Henceforth, we refer errors and error-rate in $\Pi_{\mathrm{lin}}$ as FP's and FP rate, respectively.
+%
+%\begin{theorem}\label{thm1}
+%Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{lin}}= (\Sigma,\Gamma,\calS,\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described.
+For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exist adversaries~$B_1,B_2$ (explicitly constructed in the proof of this theorem) such that
+%\[
+%\AdvCorrect{\Pi_{\mathrm{lin}},\distr{\calS}{},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+%\]
+%Here, $B_1$ and $B_2$, each ask~$q$ oracle queries and have time complexity~$O(t+qm)$.
+%\end{theorem}
+%Before giving the proof, we note that Kirsch and Mitzenmacher~\cite{xxx} show
+%that the ($r=1$, non-adaptive) FP-probability for~$\Pi_\mathrm{lin}$ is
+%always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
+%rate of convergence is faster than~$1/n$.  The factor of $\dbinom{q}{r}$ arises as a result
+%of removing adaptivity.  Finally, $\dbinom{q}{r} \leq q^r$ (with
+%reasonable tightness when~$r$ is small) in which case the final term in the bound behaves as 
+%$(q (1-e^{-kn/m})^k + O(q/n) )^r$; loosely, the bound one expects for
+%trying to find a single FP in each of~$r$ independent``rounds'', each round
+%consisting of~$q$ attempts.
 
@@
 The proof of the theorem will use a game playing argument as shown in \Cref{fig:Game}.
-$\game{0}(A)$ exactly simulates $\ExpCorrect{B_\mathrm{lin},\distr{\calS}{},r}{A}$ with hash functions $h_j(x) =  F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$.
+$\game{0}(A)$ exactly simulates $\ExpCorrect{\Pi_\mathrm{lin},\distr{\calS}{},r}{A}$ with hash functions $h_j(x) =  F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$.
 So,
@@
 \begin{equation}
-\AdvCorrect{B_{\mathrm{lin}},\distr{\calS}{},r}{A} = \Prob{\game{0}(A)=1}\label{eq:0}
+\AdvCorrect{\Pi_{\mathrm{lin}},\distr{\calS}{},r}{A} = \Prob{\game{0}(A)=1}\label{eq:0}
 \end{equation}
@@
 
-Recall that adversary~$A$ wins $\ExpCorrect{B_{\mathrm{lin}},\distr{\calS}{},r}{}$ by finding~$r$ false positives.
+Recall that adversary~$A$ wins $\ExpCorrect{\Pi_{\mathrm{lin}},\distr{\calS}{},r}{}$ by finding~$r$ false positives.
 We can assume, without loss of generality,  that~$A$ halts immediately upon finding its $r$-th false positive.
@@
 %Under these assumptions,
-So, if $\game{4}(A)=1$, then there is a non-adaptive adversary~$D$ that finds~$r$ false positives against $\tilde{B}_{\mathrm{lin}}$, which is $B_{\mathrm{lin}}$ but with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$, respectively.
+So, if $\game{4}(A)=1$, then there is a non-adaptive adversary~$D$ that finds~$r$ false positives against $\tilde{\Pi}_{\mathrm{lin}}$, which is $\Pi_{\mathrm{lin}}$ but with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$, respectively.
 We give this~$D$ in \Cref{fig:D}.
@@
 Thus we have
-$\Prob{\game{4}(A)=1} =\Prob{\ExpCorrect{\tilde{B}_{\mathrm{lin}},\distr{\calS}{},r}{D} = 1}$.
+$\Prob{\game{4}(A)=1} =\Prob{\ExpCorrect{\tilde{\Pi}_{\mathrm{lin}},\distr{\calS}{},r}{D} = 1}$.
 
-Note that $\tilde{B}_{\mathrm{lin}}$ is the scheme that is analyzed in the classical Bloom filter literature ---the hash functions are modeled as independent random functions, and the parameters $k,m,n$  are set to achieve a target maximum false-positive probability (or rate).
+Note that $\tilde{\Pi}_{\mathrm{lin}}$ is the scheme that is analyzed in the classical Bloom filter literature ---the hash functions are modeled as independent random functions, and the parameters $k,m,n$  are set to achieve a target maximum false-positive probability (or rate).
 Kirsch and Mitzenmacher~\cite{KM} show that the upperbound on false-positive probability for a non-adaptive adversary and $r=1$ is $\left( (1-e^{-kn/m})^k + O(1/n) \right)$.
 For $r>1$, we observe that~$A$'s queries $x_1,x_2,\ldots,x_q$ are distinct and not elements of the original set~$S$, since we assume no pointless queries.
-Let $\calF_i$ be the event that~$x_i(i \in \mathcal{I}$ is a false positive.
-Since $\game{4}$ (equivalently $\tilde{B}_{\mathrm{lin}}$) use independent random functions, the events $\calF_1,\calF_2,\ldots,\calF_r$ are independent.
+Let $\calF_i$ be the event that~$x_i(i \in \mathcal{I})$ is a false positive.
+Since $\game{4}$ (equivalently $\tilde{\Pi}_{\mathrm{lin}}$) use independent random functions, the events $\calF_1,\calF_2,\ldots,\calF_r$ are independent.
 \[
-\Prob{\ExpCorrect{\tilde{B}_{\mathrm{lin}},\distr{\calS}{},r}{D} = 1}\leq \left( (1-e^{-kn/m})^k + O(1/n) \right)^r 
+\Prob{\ExpCorrect{\tilde{\Pi}_{\mathrm{lin}},\distr{\calS}{},r}{D} = 1}\leq \left( (1-e^{-kn/m})^k + O(1/n) \right)^r 
 \]
@@
 \[
-\AdvCorrect{B_{\mathrm{lin}},\distr{\calS}{},r}{A}  \leq  \AdvPRF{F}{B_1} +\AdvPRF{F}{B_2} +\dbinom{q}{r}\left( (1-e^{-kn/m})^k + O(1/n) \right)^r
+\AdvCorrect{\Pi_{\mathrm{lin}},\distr{\calS}{},r}{A}  \leq  \AdvPRF{F}{B_1} +\AdvPRF{F}{B_2} +\dbinom{q}{r}\left( (1-e^{-kn/m})^k + O(1/n) \right)^r
 \]

### 2016-08-23 Theorem2_FP.tex
Proof1,2 modified

@@
 
-\heading{Construction of PRF with domain separation.}
-Let $B_{\mathrm{ds}}=(\Hash,\Rep,\Qry)$ be a hash-based filter defined as follows.
+%\heading{Construction of PRF with domain separation.}
+%Let $\Pi_{\mathrm{ds}}= (\Sigma,\Gamma,\calS,\calQ,\Rep, \Qry)$ be a set-multiplicity data structure identical to $\Pi_{\mathrm{lin}}, except the $Hash$ algorithm which is defined as follows.
 Fix non-empty sets ~$\univ$, $\calK$ and integers $k,m,n>0$.
 Let $F\colon\mathcal{K} \times \univ \to [m]$ be a function family.
-The $\Hash$ algorithm provides randomness with domain separation, as it samples key $K \getsr \mathcal{K}$ and defines $h_j(x) = \FK $ for $j \in [1,k]$.
-The $\Rep$ and $\Qry$ algorithms are the standard (determinisitic) BF ones.
-$B_{\mathrm{ds}}$ is another instantiation of the set-multiplicity data structure.
-Like $B_{\mathrm{lin}}$, $B_{\mathrm{ds}}$ admits errors in form of false positives only.
-Informally, the following result shows, if~$F$ is PRF secure and the filter has low error rate in the non-adaptive setting, then $B_{\mathrm{ds}}$ is correct against adaptive error finding adversaries.
-Hereafter, we refer errors and error-rate in $B_{\mathrm{ds}}$ as false-positives and false-positive rate, respectively.
-
-\begin{theorem}\label{thm2}
-Fix $k,m,n,r >0$.
-Let $B_{\mathrm{ds}}$ be the hash based filter just described.
-If there exists an adaptive adversary, $A$ compatible with $\ExpCorrect{B_{\mathrm{ds}},\distr{\calS}{},r}{\cdot}$ asking $q$ queries, and has time complexity O(t), then there exists an adversary $B$ (explicitly constructed in the proof of this theorem), such that
-\[
-\AdvCorrect{B_{\mathrm{ds}},\distr{\calS}{},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
-\]
-Here, $B$ asks $q$ queries, and has time complexity $O(t+qm)$.
-\end{theorem}
+The $\Hash$ algorithm provides randomness with domain separation, as it samples key $K \getsr \mathcal{K}$ and defines $h_j(x) = F_K(\langle j,x \rangle) $ for $j \in [1,k]$.
+Like $\Pi_{\mathrm{lin}}$, $\Pi_{\mathrm{ds}}$ admits errors in form of false positives only.
+Informally, the following result shows, if~$F$ is PRF secure and the filter has low error rate in the non-adaptive setting, then $\Pi_{\mathrm{ds}}$ is correct against adaptive error finding adversaries.
+Hereafter, we refer errors and error-rate in $\Pi_{\mathrm{ds}}$ as false-positives and false-positive rate, respectively.
+%
+%\begin{theorem}\label{thm2}
+%Fix $k,m,n,r >0$.
+Let $\Pi_{\mathrm{ds}}$ be the hash based filter just described.
+If there exists an adaptive adversary, $A$ compatible with $\ExpCorrect{\Pi_{\mathrm{ds}},\distr{\calS}{},r}{\cdot}$ asking $q$ queries, and has time complexity O(t), then there exists an adversary $B$ (explicitly constructed in the proof of this theorem), such that
+%\[
+%\AdvCorrect{\Pi_{\mathrm{ds}},\distr{\calS}{},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+%\]
+%Here, $B$ asks $q$ queries, and has time complexity $O(t+qm)$.
+%\end{theorem}
 
@@
 We use a game playing argument (shown in \Cref{fig:2TGame}) similar to \Cref{thm1} to prove this theorem.
-In \game{0}(A), adversary attacks the FP game with  hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpCorrect{B_{\mathrm{ds}},\distr{\calS}{},r}{A}$.
+In \game{0}(A), adversary attacks the FP game with  hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpCorrect{\Pi_{\mathrm{ds}},\distr{\calS}{},r}{A}$.
 \begin{equation}
-\AdvCorrect{B_{\mathrm{ds}},\distr{\calS}{},r}{A} = \Prob{\game{0}(A)=1}\label{eq:2T0}
+\AdvCorrect{\Pi_{\mathrm{ds}},\distr{\calS}{},r}{A} = \Prob{\game{0}(A)=1}\label{eq:2T0}
 \end{equation}
@@
 
-In $\game{1}$, $A$ attacks a different filter $\tilde{B}_\mathrm{ds}$, in which $F_K$ is replaced by a random function.
+In $\game{1}$, $A$ attacks a different filter $\tilde{\Pi}_\mathrm{ds}$, in which $F_K$ is replaced by a random function.
 $\game{2}$ and $\game{3}$ on the other hand use lazy sampling in $\Hash$ to select random values from $[m]$.
@@
 
-Let $D$ be a non-adaptive adversary (shown in \Cref{fig:2TD}) that finds ~$r$ false positives against $\tilde{B}_{\mathrm{ds}}$.
-As discussed in the previous theorem, if $A$ wins $\game{3}$, then $D$ wins $\ExpCorrect{\tilde{B}_{\mathrm{ds}},\distr{\calS}{},r}{\cdot}$ game.
+Let $D$ be a non-adaptive adversary (shown in \Cref{fig:2TD}) that finds ~$r$ false positives against $\tilde{\Pi}_{\mathrm{ds}}$.
+As discussed in the previous theorem, if $A$ wins $\game{3}$, then $D$ wins $\ExpCorrect{\tilde{\Pi}_{\mathrm{ds}},\distr{\calS}{},r}{\cdot}$ game.
 So,
 \begin{equation*}
-\AdvCorrect{\tilde{B}_{\mathrm{ds}},\distr{\calS}{},r}{D} = \Prob{\game{3}(A) = 1}\label{eq:2T8}
+\AdvCorrect{\tilde{\Pi}_{\mathrm{ds}},\distr{\calS}{},r}{D} = \Prob{\game{3}(A) = 1}\label{eq:2T8}
 \end{equation*}
-Note that like $\tilde{B}_{\mathrm{lin}}$, $\tilde{B}_{\mathrm{ds}}$ is the scheme that is analyzed in the classical Bloom filter literature.
-So, for a non-adaptive adversary $D$ and $r=1$, the upper bound on false-positive probability of a classical Bloom filter applies to $\tilde{B}_{\mathrm{ds}}$ as well.
+Note that like $\tilde{\Pi}_{\mathrm{lin}}$, $\tilde{\Pi}_{\mathrm{ds}}$ is the scheme that is analyzed in the classical Bloom filter literature.
+So, for a non-adaptive adversary $D$ and $r=1$, the upper bound on false-positive probability of a classical Bloom filter applies to $\tilde{\Pi}_{\mathrm{ds}}$ as well.
 For $r > 1$, based on the assumption that $A$ makes no pointless queries, the queries made by $A$ are distinct and not elements of the original set $S$.
@@
 \begin{equation*}
-\AdvCorrect{\tilde{B}_{\mathrm{ds}},\distr{\calS}{},r}{D} =   {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
+\AdvCorrect{\tilde{\Pi}_{\mathrm{ds}},\distr{\calS}{},r}{D} =   {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
 \end{equation*}
@@
 \[
-\AdvCorrect{B_{\mathrm{ds}},\distr{\calS}{},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
+\AdvCorrect{\Pi_{\mathrm{ds}},\distr{\calS}{},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
 \]

### 2016-08-25 notions.tex
updated privacy defs

@@
 One can also consider the orthogonal notion of privacy for a
-set-representation.  We formalize two types of privacy notions. One
-type captures a kind of one-wayness of the representation~$M$,
-relative to the allowed queries.  Informally, that given the
-representation and the public information, it is hard to guess any
-value in the represented set~$S$.  The other type captures a kind of
-semantic security, essentially requiring that $(M,\pub)$ and th
-allowed queries do not leak any (non-trivial) information about the set~$S$.
+data structure. \jnote{I am still hoping that we can treat data structures
+at an even more general level than set-representation data structures.}
+We formalize two types of privacy notions. The first captures
+a ``one-wayness'' property, which (informally) requires that an attacker
+cannot learn any value in a set $S$ given its
+representation $M$ along with the public information~$\pub$.  The second definition
+captures a flavor of semantic security, essentially requiring that $M$ and $\pub$ do
+not leak any (non-trivial) information about the set~$S$ they represent.
 %\jnote{Actually, I am now unsure what the right way to define it is. It seems natural
@@
 
-In Figure~\ref{fig:privacy-ow} we give two ``one-wayness''
-definitions, in which the adversary must output an element of the
-set~$S$ represented by~$M$.  The first version (priv) gives the
-adversary~$(M,\pubaux)$ as input; the second (wpriv) gives
-only~$\pubaux$.  The wpriv-notion captures leakage about the elements
-of~$S$ that results from observing the results of allowed queries.
-The stronger priv-notion captures what is jointly leaked, by the
-representation~$M$ and the allowed queries, about set elements.  We
-define advantage measures $\AdvPriv{\Pi,\distr{}{}}{A} =
-\Prob{\ExpPriv{\Pi,\distr{}{}}{A}=1}$ and $\AdvWPriv{\Pi,\distr{}{}}{A} =
-\Prob{\ExpWPriv{\Pi,\distr{}{}}{A}=1}$; in both we track the
+\jnote{OK, from here on I specialize to set-representation data structures\ldots}
+The one-wayness definition (see
+Figure~\ref{fig:privacy-ow}) is parameterized by a distribution $\distr{}{}$ over
+sets. \jnote{I got rid of the weaker definition, since it seems unnatural to me.}
+A set $S$ is chosen from this distribution, and a representation
+$(M,\pubaux,\privaux)$ of that set is computed.
+In one experiment ($\ExpPriv{\Pi,\distr{}{}}$), the attacker is given $M, \pubaux$;
+in a second experiment (${\bf Exp}^{\rm null}_{\Pi,\distr{}{}}$), it is not.
+In both cases, the attacker is given
+access to an oracle via which it can
+issue queries and obtain the corresponding responses.
+For a given $\distr{}{}$ and $A$, we define the advantage measure
+$\AdvPriv{\Pi,\distr{}{}}{A} \bydef
+\left| \Prob{\ExpPriv{\Pi,\distr{}{}}{A}=1} - \Prob{{\bf Exp}^{\rm null}_{\Pi,\distr{}{}}(A)=1} \right|$.
+We track the
 time-complexity~$t$ and number of oracle queries~$q$ made by the adversary.
 
-\tsnote{Wet paint...}
-In Figure~\ref{fig:privacy-ss} we give a definition capturing semantic-security (of sets)
-with respect to the full representation (ss-rep).  In the ``real''
-setting (ss-rep-1), a set~$S$ is sampled according to distribution~$\distr{}{}$,
-and the adversary is given the~$M,\pubaux$ that result from running
-$\Rep(S)$.  It is also provided oracle access to $\TestOracle$.
-The adversary must output a function~$f\colon\calS \to \bits^*$ and a
-string~$v$ such that $f(S)=v$.  In the ``fake'' setting (ss-rep-0) a
-predictor~$P$ is given $\pubaux$ only, and no $\TestOracle$ access.  It
-also outputs an $f,v$ pair such that $f(S)=v$.  The advantage of~$A$ (over~$P$)
-is $\AdvPrivSS{\Pi,\distr{}{}}{A,P} =
-\Prob{\ExpPrivSSreal{\Pi,\distr{}{}}{A}=1} -
-\Prob{\ExpPrivSSsim{\Pi,\distr{}{}}{P}=1}$.  To prevent trivial wins
-for~$A$, e.g. $f(S)=M$, we forbid~$A$ from outputting~$f$
-such that $f(S)=f(S')$ for all $S,S'$ in the support of the
-distribution $\distr{}{}$.
-
-\begin{figure}[htbp]
+\begin{figure}[hbtp]
 \centering
-\fpage{.495}{
+\fpage{.6}{
 \hpagess{.5}{.45}
@@
 $z \getsr A^{\TestOracle}(M,\pubaux)$\\
-if $z \in S$ then Return 1\\
-Return 0\\
+if $z \in S$ then return 1\\
+return 0\\
 
 \medskip
-\experimentv{$\ExpWPriv{\setprim,\distr{}{}}{A}$}\\
+\experimentv{${\bf Exp}^{\rm null}_{\Pi, \distr{}{}}(A)$} \\
 $S \getsr \distr{}{}$\\
 $(M,\pubaux,\privaux) \getsr \Rep(S)$\\
-$z \getsr A^{\TestOracle}(\pubaux)$\\
-if $z \in S$ then Return 1\\
-Return 0\\
+$z \getsr A^{\TestOracle}()$\\
+if $z \in S$ then return 1\\
+return 0\\
+%\medskip
+%\experimentv{$\ExpWPriv{\setprim,\distr{}{}}{A}$}\\
+%$S \getsr \distr{}{}$\\
+%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
+%$z \getsr A^{\TestOracle}(\pubaux)$\\
+%if $z \in S$ then Return 1\\
+%Return 0\\
 }
@@
 $a \gets \Qry(M,\pubaux,\privaux,q)$\\
-Return~$a$
+return~$a$
 }
 }
-\caption{``One-wayness'' style privacy
-  definitions. The bottom is a weaker notion, because the representation
-  is hidden from the adversary.} 
+\caption{Experiments for a ``one-wayness'' style privacy
+  definition.}
 \label{fig:privacy-ow}
@@
 
-%
-\begin{figure}[htbp]
+\jnote{I'm not sure whether we want to limit consideration to ``high-entropy''
+distributions
+and require the probability of finding an element to be low,
+or whether we want to allow arbitrary distributions but compare the attacker's
+success probability when given $(M, \pub)$ to its success probability when given nothing.
+The latter seems cleaner, so I took that approach here.}
+
+\jnote{Actually, I am unsure whether a one-wayness definition is independently
+interesting if we have (and can achieve) a semantic-security definition.}
+
+Our semantic-secure definition is simulation-based (see
+Figure~\ref{fig:privacy-ss}).
+In this definition we compare the probabilities with which an attacker $A$ outputs~1
+in two experiments: one ``real'' and one ``simulated.''
+In the real experiment (ss-rep-1), $A$ outputs a set $S$ and is given the
+$M,\pubaux$ that result from running $\Rep(S)$.
+In the simulated experiment (ss-rep-0), $A$ outputs $S$ and is given $M, \pubaux$ output
+by a simulator $\calS$ that is only given ${\sf leak}(S)$. \jnote{Note
+there is no need for a query oracle here, since the attacker knows the set. Interestingly,
+if we provide a query oracle in the real world and an oracle that returns the correct
+answer in the simulated world, then this definition seems to imply correctness also.}
+For a given function ${\sf leak}$, adversary $A$, and simulator~$\calS$,
+we define the advantage measure
+$\AdvPrivSS{\Pi,{\sf leak}}{A,\calS} \bydef
+\left| \Prob{\ExpPrivSSreal{\Pi}{A}=1} -
+\Prob{\ExpPrivSSsim{\Pi,{\sf leak}}{A, \calS}=1} \right|$.
+Informally, a scheme $\Pi$ is secure with respect to some leakage ${\sf leak}$
+if there is a simulator $\calS$ such that $\AdvPrivSS{\Pi,{\sf leak}}{A,\calS}$ is small
+for all~$A$. Intuitively, this means that the public portion
+$M, \pubaux$ of the representation of a set~$S$ leaks only ${\sf leak}(S)$.
+
+\begin{figure}[hbtp]
 \centering
-\hfpages{.495}
+\fpage{.6}{
+\hpagess{.5}{.45}
 {
-\hpagess{.49}{.49}
-{
-
-\experimentv{$\ExpPrivSSreal{\setprim,\distr{}{}}{A}$}\\
-$S\getsr \distr{}{}$\\
+\experimentv{${\bf Exp}^{\rm ss\mbox{-}rep\mbox{-}1}_{\Pi}(A)$}\\
+$S \gets A()$ \\
 $(M,\pubaux,\privaux) \getsr \Rep(S)$\\
-$(f,v) \getsr A^{\TestOracle}(M,\pubaux)$\\
-if $f(S)=v$ then\\
-\nudge Return 1\\
-Return 0\\
+return $A(M,\pubaux)$\\
 
 \medskip
-\experimentv{$\ExpPrivSSsim{\setprim,\distr{}{}}{P}$}\\
-$S\getsr \distr{}{}$\\
-$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
-$(f,v) \getsr P(\pubaux)$\\
-if $f(S)=v$ then\\
-\nudge Return 1\\
-Return 0\\
+\experimentv{${\bf Exp}^{\rm ss\mbox{-}rep\mbox{-}0}_{\Pi, {\sf leak}}(A, \calS)$}\\
+$S \gets A()$\\
+$(M,\pubaux) \getsr \calS({\sf info}(S))$ \\
+return $A(M,\pubaux)$\\
+%\medskip
+%\experimentv{$\ExpWPriv{\setprim,\distr{}{}}{A}$}\\
+%$S \getsr \distr{}{}$\\
+%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
+%$z \getsr A^{\TestOracle}(\pubaux)$\\
+%if $z \in S$ then Return 1\\
+%Return 0\\
 }
 %
-{
-\oracle{$\TestOracle(q)$}\\
-$a \gets \Qry(M,\pubaux,\privaux,q)$\\
-Return~$a$\\
+{}
 }
-}
-{
-\hpagess{.49}{.49}
-{
-\experimentv{$\ExpPrivSS{\setprim,\distr{}{},P}{A}$}\\
-$S\getsr \distr{}{}$\\
-$b \getsr \bits$\\
+\caption{Experiments for a ``semantic-security'' style privacy
+  definition.}
+\label{fig:privacy-ss}
+\end{figure}
+
+%
+%\begin{figure}[htbp]
+%\centering
+%\hfpages{.495}
+%{
+%\hpagess{.49}{.49}
+%{
+%
+%\experimentv{$\ExpPrivSSreal{\setprim,\distr{}{}}{A}$}\\
+%$S\getsr \distr{}{}$\\
 %$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
-$(M_1,\pubaux,\privaux) \getsr \Rep(S)$\\
-$M_0 \getsr P(\pubaux)$\\
-%$(f,v) \getsr \getsr A^{\TestOracle}(M,\pubaux)$\\
-$b' \getsr A^{\TestOracle}(M_b,\pubaux)$\\
+%$(f,v) \getsr A^{\TestOracle}(M,\pubaux)$\\
 %if $f(S)=v$ then\\
-if $b'=b$ then\\
-\nudge Return 1\\
-Return 0\\
+%\nudge Return 1\\
+%Return 0\\
 %
@@
 %Return 0\\
-}
-%
-{
-\oracle{$\TestOracle(q)$}\\
-$a \gets \Qry(M_1,\pubaux,\privaux,q)$\\
-Return~$a$\\
-}
-}
-\caption{Semantic-security style privacy
-  definitions. \textcolor{red}{On the left, need to protect against
-    adversary outputting
-    things like $f(S)=M$.  One idea is to forbid~$f$ such that
-    $f(S)=f(S')$ for all $S,S'$ in the support of $\distr{}{}$.}
-    } 
-\label{fig:privacy-ss}
-\end{figure}
+%}
+%%
+%{
+%\oracle{$\TestOracle(q)$}\\
+%$a \gets \Qry(M,\pubaux,\privaux,q)$\\
+%Return~$a$\\
+%}
+%}
+%{
+%\hpagess{.49}{.49}
+%{
+%\experimentv{$\ExpPrivSS{\setprim,\distr{}{},P}{A}$}\\
+%$S\getsr \distr{}{}$\\
+%$b \getsr \bits$\\
+%%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
+%$(M_1,\pubaux,\privaux) \getsr \Rep(S)$\\
+%$M_0 \getsr P(\pubaux)$\\
+%%$(f,v) \getsr \getsr A^{\TestOracle}(M,\pubaux)$\\
+%$b' \getsr A^{\TestOracle}(M_b,\pubaux)$\\
+%%if $f(S)=v$ then\\
+%if $b'=b$ then\\
+%\nudge Return 1\\
+%Return 0\\
+%%
+%%\medskip
+%%\experimentv{$\ExpPrivSSsim{\setprim,\distr{}{}}{P}$}\\
+%%$S\getsr \distr{}{}$\\
+%%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
+%%$(f,v) \getsr P(\pubaux)$\\
+%%if $f(S)=v$ then\\
+%%\nudge Return 1\\
+%%Return 0\\
+%}
+%%
+%{
+%\oracle{$\TestOracle(q)$}\\
+%$a \gets \Qry(M_1,\pubaux,\privaux,q)$\\
+%Return~$a$\\
+%}
+%}
+%\caption{Semantic-security style privacy
+%  definitions. \textcolor{red}{On the left, need to protect against
+%    adversary outputting
+%    things like $f(S)=M$.  One idea is to forbid~$f$ such that
+%    $f(S)=f(S')$ for all $S,S'$ in the support of $\distr{}{}$.}
+%    }
+%\label{fig:privacy-ss}
+%\end{figure}
 

### 2016-08-25 intro.tex
Bibliography

@@
   taste.}
-We revisit the formalization of Bloom filters~\cite{xxx} and closely
+We revisit the formalization of Bloom filters~\cite{bloom1970space} and closely
 related data structures as primitives with explicit security goals.
-Recently, Naor and Yogev~\cite{xxx} (hereafter NY) gave such a
+Recently, Naor and Yogev~\cite{naor2015bloom} (hereafter NY) gave such a
 formalization, providing syntax for a generalized abstraction of
@@
 for establishing linkages between medical-record databases, fair
-routing of TCP packets, Bitcoin wallet synchonization. \tsnote{need
+routing of TCP packets, Bitcoin wallet synchonization~\cite{schnell2011novel,niedermeyer2014cryptanalysis,gervais2014privacy,nojima2009cryptographically,feng2001stochastic,reynolds2003efficient,byers2002informed,broder2004network}.
+\tsnote{need
   citations}

### 2016-08-26 intro.tex
cheers

@@
 \label{sec:intro}
-\tsnote{Skeleton text from old intro.  (Full version of old intro now
-  in an appendix.} \jnote{Too focused on Bloom filters for my
-  taste.}
+\jnote{Too focused on Bloom filters for my taste.}
+\tsnote{Yep, it's just a placeholder, with most of the NY-bashing cut out.  Doesn't reflect our updated/current level of generality.}
 We revisit the formalization of Bloom filters~\cite{bloom1970space} and closely

### 2016-08-26 notions.tex
cheers

@@
 \fpage{.6}{
-\hpagess{.6}{.35}
+\hpagess{.5}{.45}
 {
@@
 In one experiment ($\ExpPriv{\Pi,\distr{}{}}$), the attacker is given $M, \pubaux$;
-in a second experiment (${\bf Exp}^{\rm null}_{\Pi,\distr{}{}}$), it is not.
+in a second experiment ($\ExpPrivNull{\Pi,\distr{}{}}{}$), it is not.
 In both cases, the attacker is given
@@
 $\AdvPriv{\Pi,\distr{}{}}{A} \bydef
-\left| \Prob{\ExpPriv{\Pi,\distr{}{}}{A}=1} - \Prob{{\bf Exp}^{\rm null}_{\Pi,\distr{}{}}(A)=1} \right|$.
+\left| \Prob{\ExpPriv{\Pi,\distr{}{}}{A}=1} - \Prob{\ExpPrivNull{\Pi,\distr{}{}}{A}=1} \right|$.
 We track the
@@
 \medskip
-\experimentv{${\bf Exp}^{\rm null}_{\Pi, \distr{}{}}(A)$} \\
+\experimentv{$\ExpPrivNull{\Pi, \distr{}{}}{A}$} \\
 $S \getsr \distr{}{}$\\
 $(M,\pubaux,\privaux) \getsr \Rep(S)$\\
-$z \getsr A^{\TestOracle}()$\\
+$z \getsr A^{\TestOracle}(\emptystring,\emptystring)$\\
 if $z \in S$ then return 1\\
@@
 {
-\experimentv{${\bf Exp}^{\rm ss\mbox{-}rep\mbox{-}1}_{\Pi}(A)$}\\
+\experimentv{$\ExpPrivSSreal{\Pi}{A}$}\\
 $S \gets A()$ \\
@@
 \medskip
-\experimentv{${\bf Exp}^{\rm ss\mbox{-}rep\mbox{-}0}_{\Pi, {\sf leak}}(A, \calS)$}\\
+\experimentv{$\ExpPrivSSsim{\Pi, {\sf leak}}{A, \calS}$}\\
 $S \gets A()$\\
-$(M,\pubaux) \getsr \calS({\sf info}(S))$ \\
+$(M,\pubaux) \getsr \calS({\sf leak}(S))$ \\
 return $A(M,\pubaux)$\\

### 2016-08-26 notions.tex
cheers

@@
 if we provide a query oracle in the real world and an oracle that returns the correct
-answer in the simulated world, then this definition seems to imply correctness also.}
+answer in the simulated world, then this definition seems to imply
+correctness also.}
+\tsnote{Need to pass state between stages if you want~$A$ to know the
+  set it previously sampled, right?}
 For a given function ${\sf leak}$, adversary $A$, and simulator~$\calS$,
@@
 \experimentv{$\ExpPrivSSreal{\Pi}{A}$}\\
-$S \gets A()$ \\
+$S \getsr A()$ \\
 $(M,\pubaux,\privaux) \getsr \Rep(S)$\\
+return $A(M,\pubaux)$\\
+}
+%
+{
+\experimentv{$\ExpPrivSSsim{\Pi, {\sf leak}}{A, \calS}$}\\
+$S \getsr A()$\\
+$(M,\pubaux) \getsr \calS({\sf leak}(S))$ \\
 return $A(M,\pubaux)$\\
@@
 \medskip
-\experimentv{$\ExpPrivSSsim{\Pi, {\sf leak}}{A, \calS}$}\\
+\experimentv{$\ExpPrivSSsim{\Pi}{A, \calS}$}\\
 $S \gets A()$\\
-$(M,\pubaux) \getsr \calS({\sf leak}(S))$ \\
-return $A(M,\pubaux)$\\
-%\medskip
-%\experimentv{$\ExpWPriv{\setprim,\distr{}{}}{A}$}\\
-%$S \getsr \distr{}{}$\\
-%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
-%$z \getsr A^{\TestOracle}(\pubaux)$\\
-%if $z \in S$ then Return 1\\
-%Return 0\\
+$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
+$(M',\pubaux) \gets \calS(\pubaux)$ \\
+return $A(M',\pubaux)$\\
 }
-%
-{}
 }

### 2016-08-26 notions.tex
comments

@@
 Figure~\ref{fig:privacy-ow}) is parameterized by a distribution $\distr{}{}$ over
-sets. \jnote{I got rid of the weaker definition, since it seems unnatural to me.}
+sets. \jnote{I got rid of the weaker definition, since it seems
+  unnatural to me.}\tsnote{Why? It captures things like the Squid
+  summary cache -- hash functions are public (in the code, in the
+  literature), but you would need to corrupt the HTTP proxy-server to
+  get the representation.}
 A set $S$ is chosen from this distribution, and a representation
@@
 success probability when given $(M, \pub)$ to its success probability when given nothing.
-The latter seems cleaner, so I took that approach here.}
+The latter seems cleaner, so I took that approach here.}\tsnote{I
+guess I prefer the former.  Security bounds will always surface the (elementwise)
+min-entropy of~$\distr{}{}$.  In any case, it's not clear to me that
+the null experiment captures reference/trivial attacks, which is what
+I think you are trying to capture with it.  I mean, why not give the
+public information? }
 
@@
 interesting if we have (and can achieve) a semantic-security definition.}
-
+\tsnote{Depends on what information we decide is okay to leak.  A
+  classical BF gives an~$M$ that leaks a good approximation of $|S|$.
+Do we want that to be considered semantically secure?  On the other
+hand, a classical BF is one-way in the ROM, up to the min-entropy of
+the distribution over~$S$.  So that may already give an interesting
+example that fits in the gap.}
 Our semantic-secure definition is simulation-based (see

### 2016-08-26 notions.tex
notes from phone call

@@
 set-representation~$\Pi$ is $(t,q,r,\epsilon')$-correct if $\AdvCorrect{\Pi,\distr{}{},r}{t,q} \leq \epsilon'$.
+\jnote{Note that test includes err because we don't want to penalize
+the adversary's resources for computing $q(S)$.}
 
@@
 \end{enumerate}
+\jnote{Case of $r=1$ does not necessarily imply anything for $r>1$: can have a scheme
+where finding the first false positive is hard but then the rest are easy; can have
+a scheme where finding one false positive is easy but there do not exist
+any more false positives.}
 
@@
   literature), but you would need to corrupt the HTTP proxy-server to
-  get the representation.}
+  get the representation.} \jnote{We can include the weaker definition, or perhaps
+  it is cleaner to just have the syntax output $(\pub, \privaux)$ with $\pub$ always
+  public and $\privaux$ always private; a scheme can then choose whether $M$ is in $\pub$
+  or $\privaux$. If we do this, then need to be careful how to define size.}
 A set $S$ is chosen from this distribution, and a representation
@@
 $\AdvPriv{\Pi,\distr{}{}}{A} \bydef
-\left| \Prob{\ExpPriv{\Pi,\distr{}{}}{A}=1} - \Prob{\ExpPrivNull{\Pi,\distr{}{}}{A}=1} \right|$.
+\left| \Prob{\ExpPriv{\Pi,\distr{}{}}{A}=1} - \Prob{\ExpPrivNull{\Pi,\distr{}{}}{P}=1} \right|$.
 We track the
 time-complexity~$t$ and number of oracle queries~$q$ made by the adversary.
+\jnote{Change. Compare $A$ in the 1-world to $P$ in the 0-world. Security means
+there exists a $P$
+such that for all~$A$ the following holds: $A$ in the 1-world does not do much better than
+$P$ in the 0-world. Note that there is a canonical $P$ that does best, information-theoretically.}
 
@@
 \medskip
-\experimentv{$\ExpPrivNull{\Pi, \distr{}{}}{A}$} \\
+\experimentv{$\ExpPrivNull{\Pi, \distr{}{}}{P}$} \\
 $S \getsr \distr{}{}$\\
-$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
-$z \getsr A^{\TestOracle}(\emptystring,\emptystring)$\\
+%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
+$z \getsr P()$\\
 if $z \in S$ then return 1\\
@@
 the distribution over~$S$.  So that may already give an interesting
-example that fits in the gap.}
+example that fits in the gap.} \jnote{Yes. Semantic security
+is parameterized by the leakage function, and so might or might not imply
+one-wayness.}
 Our semantic-secure definition is simulation-based (see
@@
 In the simulated experiment (ss-rep-0), $A$ outputs $S$ and is given $M, \pubaux$ output
-by a simulator $\calS$ that is only given ${\sf leak}(S)$. \jnote{Note
+by a simulator $\calS$ that is only given ${\sf leak}(S)$. \jnote{${\sf leak}$ can
+be randomized.} \jnote{Note
 there is no need for a query oracle here, since the attacker knows the set. Interestingly,
@@
 \tsnote{Need to pass state between stages if you want~$A$ to know the
-  set it previously sampled, right?}
+  set it previously sampled, right?} \jnote{Yes, unless by convention all algorithms
+  are stateful. (smiley face).}
 For a given function ${\sf leak}$, adversary $A$, and simulator~$\calS$,
@@
 
-\medskip
-\experimentv{$\ExpPrivSSsim{\Pi}{A, \calS}$}\\
-$S \gets A()$\\
-$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
-$(M',\pubaux) \gets \calS(\pubaux)$ \\
-return $A(M',\pubaux)$\\
+%\medskip
+%\experimentv{$\ExpPrivSSsim{\Pi}{A, \calS}$}\\
+%$S \gets A()$\\
+%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
+%$(M',\pubaux) \gets \calS(\pubaux)$ \\
+%return $A(M',\pubaux)$\\
 }

### 2016-08-26 results.tex
notes from phone call

@@
 \section{Achieving Security Notions}
+
+\jnote{Outline:
+}
+
 \heading{Linear-PRF construction. }
@@
 \begin{itemize}
-\item Show Bloom Filter is correct in the ROM 
-\item correctness security/attacks on bigram/PRF-based double-hashing construction ($h_j(x) = F_{K1}(x) + j\cdot F_{K2}(x) \bmod m$ where the~$x$ are bigrams of names, etc.) 
-\item correctness-security/attacks on bigram/domain-separated PRF construction ($h_j(x)=F_K(\langle j,x \rangle) \bmod m$, or just assume range of~$F$ is $[m]$.)
+\item Show Bloom Filter is correct in the ROM. \jnote{Should follow along the lines
+of Theorem~2, but taking into account adversary's oracle queries.}
+\item correctness security/attacks on the bigram/PRF-based double-hashing construction ($h_j(x) = F_{K1}(x) + j\cdot F_{K2}(x) \bmod m$ where the~$x$ are bigrams of names, etc.)
+\jnote{Done}
+\item correctness-security/attacks on the bigram/domain-separated PRF construction ($h_j(x)=F_K(\langle j,x \rangle) \bmod m$, or just assume range of~$F$ is $[m]$.) \jnote{Done}
 \item correctness-security/attacks Dong, Chen, Wen ``garbled Bloom filter'' construction
@@
 
-\item Prove privacy bounds for the constructions from NY
+\item Prove privacy bounds for the constructions from NY. \jnote{Is this interesting?}
 
@@
 (Essentially, the Hamming weight of the representation is a good estimate of the length of the longest surname in filter.)
+\jnote{Maybe tailor leakage function appropriately, i.e., so that
+it only leaks the number of bigrams?}
 

### 2016-08-29 notions.tex
privacy definitions

--- 2016-08-26 notions.tex
@@
 adversarial) notion of correctness.
-In addition to correctness, we establish three notions of privacy for
-set-representations. The first two have the flavor of a one-wayness
-game, in which the adversary seeks to return an element of the
-represented set~$S$.  The final notion is reminiscent of
-semantic-security for encryption schemes, and attempts to capture the
-intuition that the representation~$M$ and the public
-information~$\pubaux$ should not leak any efficiently computable
-information about~$S$.
+In addition to correctness, we establish notions of privacy for
+set-representations.
 
@@
 We formalize two types of privacy notions. The first captures
-a ``one-wayness'' property, which (informally) requires that an attacker
-cannot learn any value in a set $S$ given its
-representation $M$ along with the public information~$\pub$.  The second definition
+a ``one-wayness'' property that (informally) requires that
+the representation of some set~$S$ does not make it any easier for an attacker
+to learn an element of~$S$.
+The second definition
 captures a flavor of semantic security, essentially requiring that $M$ and $\pub$ do
-not leak any (non-trivial) information about the set~$S$ they represent.
-%\jnote{Actually, I am now unsure what the right way to define it is. It seems natural
-%to give the attacker $\aux$. But if we give them $\aux$ and $M$ then they have everything.
-%If $S$ has high min-entropy (element-wise), then it might still be
-%possible to have security here.}\tsnote{I think we will always bump up
-%against the (element-wise) min-entropy of the distribution over~$S$,
-%at least in the ``one-wayness'' style definition that I had been imagining. }
+not leak any information about the set~$S$ they represent beyond
+what is captured in some explicit leakage function.
 
 \jnote{OK, from here on I specialize to set-representation data structures\ldots}
-The one-wayness definition (see
-Figure~\ref{fig:privacy-ow}) is parameterized by a distribution $\distr{}{}$ over
-sets. \jnote{I got rid of the weaker definition, since it seems unnatural to me.}
-A set $S$ is chosen from this distribution, and a representation
-$(M,\pubaux,\privaux)$ of that set is computed.
-In one experiment ($\ExpPriv{\Pi,\distr{}{}}$), the attacker is given $M, \pubaux$;
-in a second experiment ($\ExpPrivNull{\Pi,\distr{}{}}{}$), it is not.
-In both cases, the attacker is given
-access to an oracle via which it can
-issue queries and obtain the corresponding responses.
-For a given $\distr{}{}$ and $A$, we define the advantage measure
-$\AdvPriv{\Pi,\distr{}{}}{A} \bydef
-\left| \Prob{\ExpPriv{\Pi,\distr{}{}}{A}=1} - \Prob{\ExpPrivNull{\Pi,\distr{}{}}{A}=1} \right|$.
-We track the
-time-complexity~$t$ and number of oracle queries~$q$ made by the adversary.
 
-\begin{figure}[hbtp]
-\centering
-\fpage{.6}{
-\hpagess{.5}{.45}
-{
-\experimentv{$\ExpPriv{\setprim,\distr{}{}}{A}$}\\
-$S \getsr \distr{}{}$\\
-$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
-$z \getsr A^{\TestOracle}(M,\pubaux)$\\
-if $z \in S$ then return 1\\
-return 0\\
+\jnote{I don't know if I like the one-wayness definition any more; it seems a bit
+ad hoc. And why do we care about one-wayness, anyway? Instead, I give
+two versions of semantic security.}
 
-\medskip
-\experimentv{$\ExpPrivNull{\Pi, \distr{}{}}{A}$} \\
-$S \getsr \distr{}{}$\\
-$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
-$z \getsr A^{\TestOracle}(\emptystring,\emptystring)$\\
-if $z \in S$ then return 1\\
-return 0\\
-%\medskip
-%\experimentv{$\ExpWPriv{\setprim,\distr{}{}}{A}$}\\
+%The one-wayness definition (see
+%Figure~\ref{fig:privacy-ow}) is parameterized by a distribution $\distr{}{}$ over
+%sets. A set $S$ is chosen from this distribution, and a representation
+%$(\pubaux,\privaux)$ of that set is computed.
+%In one experiment ($\ExpPriv{\Pi,\distr{}{}}$), an attacker~$A$ is given $\pubaux$;
+%in a second experiment ($\ExpPrivNull{\Pi,\distr{}{}}{}$), it is not.
+%For a given $\distr{}{}$ and $A$, we define the advantage measure
+%$\AdvPriv{\Pi,\distr{}{}}{A} \bydef
+%\left| \Prob{\ExpPriv{\Pi,\distr{}{}}{A}=1} - \Prob{\ExpPrivNull{\Pi,\distr{}{}}{P}=1} \right|$.
+%We track the
+%time-complexity~$t$ and number of oracle queries~$q$ made by the adversary.
+%\jnote{Change. Compare $A$ in the 1-world to $P$ in the 0-world. Security means
+%there exists a $P$
+%such that for all~$A$ the following holds: $A$ in the 1-world does not do much better than
+%$P$ in the 0-world. Note that there is a canonical $P$ that does best, information-theoretically.}
+%\jnote{I now wonder whether we should allow test queries in both worlds.}
+%
+%\begin{figure}[hbtp]
+%\centering
+%\fpage{.6}{
+%\hpagess{.5}{.45}
+%{
+%\experimentv{$\ExpPriv{\setprim,\distr{}{}}{A}$}\\
 %$S \getsr \distr{}{}$\\
 %$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
-%$z \getsr A^{\TestOracle}(\pubaux)$\\
-%if $z \in S$ then Return 1\\
-%Return 0\\
-}
+%$z \getsr A^{\TestOracle}(M,\pubaux)$\\
+%if $z \in S$ then return 1\\
+%return 0\\
 %
-{
-\oracle{$\TestOracle(q)$}\\
-$a \gets \Qry(M,\pubaux,\privaux,q)$\\
-return~$a$
-}
-}
-\caption{Experiments for a ``one-wayness'' style privacy
-  definition.}
-\label{fig:privacy-ow}
-\end{figure}
+%\medskip
+%\experimentv{$\ExpPrivNull{\Pi, \distr{}{}}{P}$} \\
+%$S \getsr \distr{}{}$\\
+%%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
+%$z \getsr P()$\\
+%if $z \in S$ then return 1\\
+%return 0\\
+%%\medskip
+%%\experimentv{$\ExpWPriv{\setprim,\distr{}{}}{A}$}\\
+%%$S \getsr \distr{}{}$\\
+%%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
+%%$z \getsr A^{\TestOracle}(\pubaux)$\\
+%%if $z \in S$ then Return 1\\
+%%Return 0\\
+%}
+%%
+%{
+%\oracle{$\TestOracle(q)$}\\
+%$a \gets \Qry(M,\pubaux,\privaux,q)$\\
+%return~$a$
+%}
+%}
+%\caption{Experiments for a ``one-wayness'' style privacy
+%  definition.}
+%\label{fig:privacy-ow}
+%\end{figure}
 
-\jnote{I'm not sure whether we want to limit consideration to ``high-entropy''
-distributions
-and require the probability of finding an element to be low,
-or whether we want to allow arbitrary distributions but compare the attacker's
-success probability when given $(M, \pub)$ to its success probability when given nothing.
-The latter seems cleaner, so I took that approach here.}
-
-\jnote{Actually, I am unsure whether a one-wayness definition is independently
-interesting if we have (and can achieve) a semantic-security definition.}
-
+%\jnote{Actually, I am unsure whether a one-wayness definition is independently
+%interesting if we have (and can achieve) a semantic-security definition.}
+%\tsnote{Depends on what information we decide is okay to leak.  A
+%  classical BF gives an~$M$ that leaks a good approximation of $|S|$.
+%Do we want that to be considered semantically secure?  On the other
+%hand, a classical BF is one-way in the ROM, up to the min-entropy of
+%the distribution over~$S$.  So that may already give an interesting
+%example that fits in the gap.} \jnote{Yes. Semantic security
+%is parameterized by the leakage function, and so might or might not imply
+%one-wayness.}
 Our semantic-secure definition is simulation-based (see
@@
 In the real experiment (ss-rep-1), $A$ outputs a set $S$ and is given the
-$M,\pubaux$ that result from running $\Rep(S)$.
-In the simulated experiment (ss-rep-0), $A$ outputs $S$ and is given $M, \pubaux$ output
-by a simulator $\calS$ that is only given ${\sf leak}(S)$. \jnote{Note
-there is no need for a query oracle here, since the attacker knows the set. Interestingly,
-if we provide a query oracle in the real world and an oracle that returns the correct
-answer in the simulated world, then this definition seems to imply
-correctness also.}
+public information $\pubaux$ that results from running $\Rep(S)$.\footnote{We do not give $A$ an oracle for
+issuing queries; since $A$ knows the set~$S$, such an oracle would be superfluous.
+\jnote{Interestingly,
+if we provided a query oracle in the real world and an oracle that returns the correct
+answer in the simulated world, then the definition seems to imply
+correctness also.}}
+In the simulated experiment (ss-rep-0), $A$ outputs $S$ and is given $\pubaux$ output
+by a simulator $\Sim$ that is only given ${\sf leak}(S)$ for some (possibly randomized)
+function~${\sf leak}$.
 \tsnote{Need to pass state between stages if you want~$A$ to know the
-  set it previously sampled, right?}
-For a given function ${\sf leak}$, adversary $A$, and simulator~$\calS$,
+  set it previously sampled, right?} \jnote{Yes, unless by convention all algorithms
+  are stateful. (smiley face). Whatever you prefer is fine with me.}
+For a given function ${\sf leak}$, adversary $A$, and simulator~$\Sim$,
 we define the advantage measure
-$\AdvPrivSS{\Pi,{\sf leak}}{A,\calS} \bydef
+$\AdvPrivSS{\Pi,{\sf leak}}{A,\Sim} \bydef
 \left| \Prob{\ExpPrivSSreal{\Pi}{A}=1} -
-\Prob{\ExpPrivSSsim{\Pi,{\sf leak}}{A, \calS}=1} \right|$.
-Informally, a scheme $\Pi$ is secure with respect to some leakage ${\sf leak}$
-if there is a simulator $\calS$ such that $\AdvPrivSS{\Pi,{\sf leak}}{A,\calS}$ is small
+\Prob{\ExpPrivSSsim{\Pi,{\sf leak}}{A, \Sim}=1} \right|$.
+Informally, a scheme $\Pi$ is secure with respect to some leakage function ${\sf leak}$
+if there is a simulator $\Sim$ such that $\AdvPrivSS{\Pi,{\sf leak}}{A,\Sim}$ is small
 for all~$A$. Intuitively, this means that the public portion
-$M, \pubaux$ of the representation of a set~$S$ leaks only ${\sf leak}(S)$.
+$\pubaux$ of the representation of a set~$S$ leaks~${\sf leak}(S)$ and nothing more.
 
@@
 {
-\experimentv{$\ExpPrivSSsim{\Pi, {\sf leak}}{A, \calS}$}\\
+\experimentv{$\ExpPrivSSsim{\Pi, {\sf leak}}{A, \Sim}$}\\
 $S \getsr A()$\\
-$(M,\pubaux) \getsr \calS({\sf leak}(S))$ \\
+$(M,\pubaux) \getsr \Sim({\sf leak}(S))$ \\
 return $A(M,\pubaux)$\\
 
-\medskip
-\experimentv{$\ExpPrivSSsim{\Pi}{A, \calS}$}\\
-$S \gets A()$\\
-$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
-$(M',\pubaux) \gets \calS(\pubaux)$ \\
-return $A(M',\pubaux)$\\
+%\medskip
+%\experimentv{$\ExpPrivSSsim{\Pi}{A, \calS}$}\\
+%$S \gets A()$\\
+%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
+%$(M',\pubaux) \gets \calS(\pubaux)$ \\
+%return $A(M',\pubaux)$\\
 }

### 2016-08-29 syntax.tex
privacy definitions

@@
 practice), and it makes it easier to state our security notions.
+
+\jnote{I think we agreed to just have the syntax output $(\pub, \privaux)$, with
+the semantics being that in our definitions $\pub$ is always
+  public and $\privaux$ is always private.
+  Different schemes can then choose whether $M$ is in $\pub$
+  or $\privaux$. If we do this, then need to be careful how to define size, though
+  I don't think we ever explicitly care about size for any of our results.}
 

### 2016-08-29 Theorem1_FP.tex
Correction in Figures

@@
 $z \getsr A^{\TestOracle}(S,\pubaux)$\\
+if $\bad = \true$ then \fbox{Return 0}\\
 if $\err  < r$ then Return 0\\

### 2016-08-30 Theorem1_FP.tex
Proof1,2 formatting

--- 2016-08-23 Theorem1_FP.tex
@@
 if $\err  < r$ then Return 0\\
-Return 1\\\\
+Return 1\\
 %
@@
 \nudge $\err \gets\err +1$\\
-Return~$(a,\err )$\\\\
+Return~$(a,\err )$\\
 %
@@
 \underline{{$\game{3}(A)$},\fbox{$\game{4}(A)$}}\\
-$c\gets 0$, $\bad \gets \false$\\
+$c\gets 0$, $\bad \gets \false$, $\err \gets 0$\\
 $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
 $S \getsr \distr{\calS}{}$\\
-$\err \gets 0$\\
 $(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
 $z \getsr A^{\TestOracle}(S,\pubaux)$\\
+if $\bad = \true$ then \fbox{Return 0}\\
 if $\err  < r$ then Return 0\\
-Return 1\\\\
+Return 1\\
 %
@@
 \nudge $\err \gets\err +1$\\
-Return~$(v,\err )$\\\\
+Return~$(v,\err )$\\
 %

### 2016-08-30 Theorem3_FP.tex
Theorem3 (in appendix)

\acnote{To be verified before moving the theorem to section 4}
\heading{Classical Bloom filter in random oracle model (ROM). }
As discussed earlier, the classical Bloom filter (BF) is an instantiation of a set multiplicity data structure and admits errors in form of false  positives (FP) only. In the ROM, $\Rep$ queries the random oracle to get the hash indices of elements of set $S$. It then computes the $m$-bit array, $M$ and outputs $\privaux=\emptystring$, $\pubaux = \emptystring$ and $M$ as the representation of
the Bloom filter. The $\Qry$ oracle uses the random oracle in a similar way. For any query $q$, it gets the hash indices $h_1, \ldots, h_k$ from the random oracle and returns 1 if $M[h_i(x)]=1$ for all $i\in [k]$, and 0 otherwise.
\begin{theorem}\label{thm3}
Fix $k,m,n,r>0$. Let $A$ be an adaptive adversary (for attacking BF) asking $q_\mathsf{A}$ queries to the random oracle. Let $t_\mathsf{A}$ be the running time of $A$ given these queries. Then there is a prf-adversary  $B$ (explicitly given in the proof) such that
\[
\AdvCorrect{{BF},\distr{\calS}{},r}{A} \leq  \AdvPRF{F}{B}  +{\dbinom{q_\mathsf{A}}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
Here, $B$ asks~$O(q_\mathsf{A})$ oracle queries and has time complexity~$O(t_A+q_\mathsf{A}m)$.
\end{theorem}

\begin{proof}[\Cref{thm3}]
The proof of this theorem will follow along the lines of \Cref{thm2} with the following alterations. In $\game{0}$, the $\Hash$ oracle does lazy sampling to mimic a random oracle; in rest of the games, it returns $k$ random elements for each query. We get rid of $\game{1}$, and $\Rep$, $\Qry$ and adversary $A$ are given access to the random oracle in all the games. 
\end{proof}

### 2016-08-31 syntax.tex
making the data structure synatax more succinct

@@
 \begin{definition}[Data structure] \rm
-Fix a non-empty set~$\univ$. A \emph{data structure} (over universe~$\univ$)
-is a tuple $\setprim=(\Sigma,\Gamma,\calS,\calQ,\Rep, \Qry)$ where:
+Fix a non-empty set~$\univ$, and a set of multisets~$\calS$ over
+$\univ$. 
+A \emph{data structure} (for $\calS$) is a tuple $\setprim=(\calQ,\Rep, \Qry)$ where:
 \begin{itemize}
-\item $\Sigma$ is the \emph{representation alphabet}.
-%\jnote{Is there any reason not to simply fix this to $\{0,1\}$?}
-\item $\Gamma$ is the set of possible \emph{query answers}.
-%\jnote{Do we need this for any reason?}
-\item $\calS$ is a set  of multisets over universe~$\univ$.
 \item $\mathcal{Q}=\{q \colon \mathcal{S} \to \Gamma\}$ is a set
-    of supported \emph{queries}.
-\item $\Rep \colon \mathcal{S} \to \Sigma^* \times \bits^*
+    of supported \emph{queries}, where $\Gamma$ is the set of query \emph{answers}.
+\item $\Rep \colon \mathcal{S} \to \bits^*
     \times \bits^*$ is a randomized \emph{representation

### 2016-08-31 syntax.tex
syntax

@@
     \times \bits^*$ is a randomized \emph{representation
-    algorithm}, taking as input $S \in \mathcal{S}$, and
-    outputting a \emph{representation} $M \in \Sigma^*$,
-    \emph{private side information} $\privaux \in \bits^*$, and
-    \emph{public side information} $\pubaux \in \bits^*$.  We write
-    $(M,\pubaux,\privaux) \getsr \Rep(S)$ as shorthand for this execution.
+    algorithm}, taking as input $S \in \mathcal{S}$, and outputting %a \emph{representation} $M \in \Sigma^*$,
+    \emph{private representation data} $\privaux \in \bits^*$, and
+    \emph{public representation data} $\pubaux \in \bits^*$.  We write
+    $(\pubaux,\privaux) \getsr \Rep(S)$ as shorthand for this execution.
 \item $\Qry\colon \Sigma^* \times \bits^* \times \bits^* \times \calQ \to
     \Gamma$ is a deterministic \emph{query-evaluation}
-    algorithm, taking as input $M\in\Sigma^*$, $\pubaux,\privaux \in
+    algorithm, taking as input $\pubaux,\privaux \in
     \bits^*$ and $q \in \calQ$, and outputting
     an \emph{answer} $a \in \Gamma$.  We write $a \gets
-    \Qry(M,\pubaux,\privaux,q)$ for this execution.
+    \Qry(\pubaux,\privaux,q)$ for this execution.
 \end{itemize}
@@
 \end{definition}
+
+\todo{Insert discussion of syntax, if needed.  If we think it is
+  helpful to discuss the size of the representation, we can declare it
+as $|\pubaux|+|\privaux|$ and comment that if one wants to compare to
+classical size bounds, a more fine-grained separation of the output of
+$\Rep$ would allow this.}
 %\tsnote{I implemented this change.}\tsnote{I'm now leaning towards
@@
 %secret keys, but this is unnatural.}
-All of the data structures that
-we will consider have the property that~$|M|$ does not depend on the
-coins of~$\Rep$. Thus we assume that~$|M|$ depends only on~$|S|$. In
-general this need not be true, but the assumption does not restrict
-our syntax from capturing natural constructions (e.g., those used in
-practice), and it makes it easier to state our security notions.
 
-\jnote{I think we agreed to just have the syntax output $(\pub, \privaux)$, with
-the semantics being that in our definitions $\pub$ is always
-  public and $\privaux$ is always private.
-  Different schemes can then choose whether $M$ is in $\pub$
-  or $\privaux$. If we do this, then need to be careful how to define size, though
-  I don't think we ever explicitly care about size for any of our results.}
+%All of the data structures that we will consider have the property that~$|M|$ does not depend on the
+%coins of~$\Rep$. Thus we assume that~$|M|$ depends only on~$|S|$. In
+%general this need not be true, but the assumption does not restrict
+%our syntax from capturing natural constructions (e.g., those used in
+%practice), and it makes it easier to state our security notions.
+
+%\jnote{I think we agreed to just have the syntax output $(\pub, \privaux)$, with
+%the semantics being that in our definitions $\pub$ is always
+%  public and $\privaux$ is always private.
+%  Different schemes can then choose whether $M$ is in $\pub$
+%  or $\privaux$. If we do this, then need to be careful how to define size, though
+%  I don't think we ever explicitly care about size for any of our results.}
 

### 2016-08-31 notions.tex
dropping M throughout

@@
 $\mathcal{S}$ associated to~$\Pi$, and then
-$\Rep(S)$ is run to generate $(M,\pubaux,\privaux)$.
+$\Rep(S)$ is run to generate $(\pubaux,\privaux)$.
 %(Unless stated otherwise, we assume security holds for all distributions and thus for all sets $S$.)
@@
 provided an oracle~$\TestOracle$ that, on input a query~$q \in \calQ$,
-computes (and returns) the result of $\Qry(M,\privaux,q)$, and increments
+computes (and returns) the result of $\Qry(\pubaux,\privaux,q)$, and increments
 a counter if this result is in error.  The adversary wins if it
@@
 $\mathrm{err}\gets 0$\\
-$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
+$(\pubaux,\privaux) \getsr \Rep(S)$\\
 $z \getsr A^{\TestOracle}(S,\pubaux)$\\
@@
 \oracle{$\TestOracle(q)$}\\
-$a \gets \Qry(M,\pubaux,\privaux,q)$\\
+$a \gets \Qry(\pubaux,\privaux,q)$\\
 if $a \neq q(S)$ then \\

### 2016-08-31 notions.tex
no message

--- 2016-08-29 notions.tex
@@
 correctness also.}}
-In the simulated experiment (ss-rep-0), $A$ outputs $S$ and is given $\pubaux$ output
-by a simulator $\Sim$ that is only given ${\sf leak}(S)$ for some (possibly randomized)
-function~${\sf leak}$.
 \tsnote{Need to pass state between stages if you want~$A$ to know the
@@
   are stateful. (smiley face). Whatever you prefer is fine with me.}
+In the simulated experiment (ss-rep-0), $A$ outputs $S$ and is given $\pubaux$ output
+by a simulator $\Sim$ that is only given ${\sf leak}(S)$ for some (possibly randomized)
+function~${\sf leak}$. \jnote{Could also give $\Sim$ a membership oracle.}
 For a given function ${\sf leak}$, adversary $A$, and simulator~$\Sim$,
@@
 Informally, a scheme $\Pi$ is secure with respect to some leakage function ${\sf leak}$
-if there is a simulator $\Sim$ such that $\AdvPrivSS{\Pi,{\sf leak}}{A,\Sim}$ is small
-for all~$A$. Intuitively, this means that the public portion
+if for all $A$ there is a simulator $\Sim$ such that
+$\AdvPrivSS{\Pi,{\sf leak}}{A,\Sim}$ is small.
+Intuitively, this means that the public portion
 $\pubaux$ of the representation of a set~$S$ leaks~${\sf leak}(S)$ and nothing more.
+\jnote{Need to relate running time of $\Sim$ to running time of~$A$.}
 

### 2016-08-31 notions.tex
no message

@@
 
-\subsection{Notions of Privacy}
-One can also consider the orthogonal notion of privacy for a
+\subsection{Privacy}
+\jnote{Define appropriate notion of min-entropy for our setting.
+Define one-wayness.}
+
+One can also consider the orthogonal notion of \emph{privacy} for a
 data structure. \jnote{I am still hoping that we can treat data structures
@@
 
-\jnote{I don't know if I like the one-wayness definition any more; it seems a bit
-ad hoc. And why do we care about one-wayness, anyway? Instead, I give
-two versions of semantic security.}
+%\jnote{I don't know if I like the one-wayness definition any more; it seems a bit
+%ad hoc. And why do we care about one-wayness, anyway? Instead, I give
+%two versions of semantic security.}
 

### 2016-08-31 Theorem2_FP.tex
Proof1,2 formatting
Proofs

@@
 
-Let $B$ be a prf-adversary as shown in \Cref{fig:2TD}. Based on its challenge bit $b$, it exactly simulates $\game{0}$ or $\game{1}$. So,
+Let $B$ be a prf-adversary as shown in \Cref{fig:D}. Based on its challenge bit $b$, it exactly simulates $\game{0}$ or $\game{1}$. So,
 \begin{align*}
@@
 Let $D$ be a non-adaptive adversary (shown in \Cref{fig:2TD}) that finds ~$r$ false positives against $\tilde{\Pi}_{\mathrm{ds}}$.
-As discussed in the previous theorem, if $A$ wins $\game{3}$, then $D$ wins $\ExpCorrect{\tilde{\Pi}_{\mathrm{ds}},\distr{\calS}{},r}{\cdot}$ game.
+Using explanations from previous theorem, if $A$ wins $\game{3}$, then $D$ wins $\ExpCorrect{\tilde{\Pi}_{\mathrm{ds}},\distr{\calS}{},r}{\cdot}$ game.
 So,
@@
 \]
-which is the bound claimed in the theorem statement. \hfill \qed
+which is the bound claimed in the theorem statement. %\hfill \qed
 
@@
 \fpage{.9}{
-\hpagessl{.55}{.3}
+\hpagessl{.45}{.5}
 {
@@
 \oracle{$\HashOracle(x)$}\\
-$a \getsr [m]$\\
 for $j = 1$ to~$k$\\
-\nudge $v_j = a$\\
+\nudge $v_j \getsr [m]$\\
 Ret $\left(v_1,\ldots,v_k\right)$
@@
 
-%\caption{PRF adversary $B$ simulating $\game{1}(A)$ and $\game{2}(A)$, and non-adaptive adversary $D$ simulating $\game{4}(A)$} 
+%\caption{PRF adversary $B$ simulating $\game{1}(A)$ and $\game{2}(A)$
 \begin{figure}
 \centering
-\fpage{0.9}{
-\hpagessl{0.5}{0.5}
-{
+\fpage{0.5}{
 $\adversaryv{B^{\calO}}$\\
@@
 }
-{
-$\adversaryv{D^{\TestOracle, \calS}}$\\
-$c \gets 0$\\%, $\calX \gets \emptyset$\\
-$\err \gets 0$\\
-$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
-Run $A(S)$\\
-When $A$ asks $\TestOracle(x)$:\\
-\nudge $c \gets c+1$\\
-\nudge $r \gets 0$\\
-\nudge if $c \in \mathcal{I}$\\
-%\nudge \nudge $\calX \gets \calX \cup \{x\}$\\
-\nudge \nudge $r \gets 1$\\
-\nudge \nudge $\err \gets \err + 1$\\
-\nudge Ret $(r,\err )$\\
-When $A$ halts:\\
-\nudge Ret 1
-}
-%
-%\oracle{$\TestOracle(x)$}\\
-% Ret $\Qry^{\HashOracle}(M,x)$\\\\
-%
-%\oracle{$\HashOracle(x)$}\\
-%for $j = 1$ to~$k$\\
-%\nudge $v_j = \rhoK $\\
-%Ret $\left(v_1,\ldots,v_k\right)$
-}
-\caption{\Cref{thm2}: \textbf{Left}: PRF adversary $B$ simulating $\game{1}(A)$ and $\game{2}(A)$. \textbf{Right}: Non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:2TD}
+\caption{\Cref{thm2}: PRF adversary $B$ simulating $\game{1}(A)$ and $\game{2}(A)$} \label{fig:2TD}
 \end{figure}

### 2016-08-31 Theorem3_FP.tex
Proofs

@@
 \begin{theorem}\label{thm3}
-Fix $k,m,n,r>0$.
-Let $A$ be an adaptive adversary (for attacking BF) asking $q_\mathsf{A}$ queries to the random oracle.
-Let $t_\mathsf{A}$ be the running time of $A$ given these queries.
-Then there is a prf-adversary  $B$ (explicitly given in the proof) such that
+Fix $k,m,n,r>0$. Let $A$ be an adaptive adversary (for attacking BF) asking $q$ queries to the random oracle. Let $t$ be the running time of $A$ given these queries. Then, 
 \[
-\AdvCorrect{{BF},\distr{\calS}{},r}{A} \leq  \AdvPRF{F}{B}  +{\dbinom{q_\mathsf{A}}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\AdvCorrect{{BF},\distr{\calS}{},r}{A} \leq  {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
 \]
-Here, $B$ asks~$O(q_\mathsf{A})$ oracle queries and has time complexity~$O(t_A+q_\mathsf{A}m)$.
 \end{theorem}
@@
 \begin{proof}[\Cref{thm3}]
-The proof of this theorem will follow along the lines of \Cref{thm2} with the following alterations.
-In $\game{0}$, the $\Hash$ oracle does lazy sampling to mimic a random oracle; in rest of the games, it returns $k$ random elements for each query.
-We get rid of $\game{1}$, and $\Rep$, $\Qry$ and adversary $A$ are given access to the random oracle in all the games.
+The proof of this theorem will follow along the lines of \Cref{thm2}.
 \end{proof}

### 2016-08-31 Theorem2_FP.tex
Proofs

@@
 We use a game playing argument (shown in \Cref{fig:2TGame}) similar to \Cref{thm1} to prove this theorem.
-In \game{0}(A), adversary attacks the FP game with  hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpCorrect{\Pi_{\mathrm{ds}},\distr{\calS}{},r}{A}$.
+In \game{0}, adversary attacks the correctness game with  hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpCorrect{\Pi_{\mathrm{ds}},\distr{\calS}{},r}{A}$.
 \begin{equation}
@@
 
-Let $B$ be a prf-adversary as shown in \Cref{fig:D}. Based on its challenge bit $b$, it exactly simulates $\game{0}$ or $\game{1}$. So,
+Let $B$ be a prf-adversary as shown in \Cref{fig:2TD}. Based on its challenge bit $b$, it exactly simulates $\game{0}$ or $\game{1}$. So,
 \begin{align*}
@@
 It can be observed that, except  $\Hash$, $\game{2}$ and $\game{3}$ are identical to $\game{3}$ and $\game{4}$ of previous theorem.
-Since, $\Hash$ in all of these games returns random values, the analysis and results of \Cref{thm1} apply to this theorem as well.
+Since, $\Hash$ in all of these games returns random values, the analyses and intermediate results of \Cref{thm1} apply to this theorem as well.
 Therefore,
@@
 
-Let $D$ be a non-adaptive adversary (shown in \Cref{fig:2TD}) that finds ~$r$ false positives against $\tilde{\Pi}_{\mathrm{ds}}$.
+Let $D$ be a non-adaptive adversary (shown in \Cref{fig:D}) that finds ~$r$ false positives against $\tilde{\Pi}_{\mathrm{ds}}$.
 Using explanations from previous theorem, if $A$ wins $\game{3}$, then $D$ wins $\ExpCorrect{\tilde{\Pi}_{\mathrm{ds}},\distr{\calS}{},r}{\cdot}$ game.

### 2016-09-02 notions.tex
cheers

--- 2016-08-31 notions.tex
@@
 Lifting their definition to our setting, the experiment is similar but the attacker
-succeeds only if it outputs a single query $q$ for which $\Qry( M,
-\aux, q) \neq q(S)$  \emph{subject to the restriction that it did not query $q$ to its $\Qry$ oracle}.
+succeeds only if it outputs a single query $q$ for which $\Qry(\pubaux,\privaux, q) \neq q(S)$  \emph{subject to the restriction that it did not query $q$ to its $\Qry$ oracle}.
 It will be interesting to understand formally the relation between our definition and theirs.
@@
 %one-wayness.}
-Our semantic-secure definition is simulation-based (see
-Figure~\ref{fig:privacy-ss}).
+Our semantic-secure definition is simulation-based (see Figure~\ref{fig:privacy-ss}).
 In this definition we compare the probabilities with which an attacker $A$ outputs~1
@@
 In the real experiment (ss-rep-1), $A$ outputs a set $S$  and is given the
-public information $\pubaux$ that results from running $\Rep(S)$.\footnote{We do not give $A$ an oracle for
-issuing queries; since $A$ knows the set~$S$, such an oracle would be superfluous.
+public information $\pubaux$ that results from running $\Rep(S)$.
+\footnote{We do not give $A$ an oracle for issuing queries; 
+since $A$ knows the set~$S$, such an oracle would be superfluous.
 \jnote{Interestingly,
@@
 correctness also.}}
-\tsnote{Need to pass state between stages if you want~$A$ to know the
-  set it previously sampled, right?} \jnote{Yes, unless by convention all algorithms
-  are stateful. (smiley face). Whatever you prefer is fine with me.}
 In the simulated experiment (ss-rep-0), $A$ outputs $S$ and is given $\pubaux$ output
 by a simulator $\Sim$ that is only given ${\sf leak}(S)$ for some (possibly randomized)
-function~${\sf leak}$. \jnote{Could also give $\Sim$ a membership oracle.}
+function~${\sf leak}$.
+%\tsnote{Need to pass state between stages if you want~$A$ to know the
+%  set it previously sampled, right?} \jnote{Yes, unless by convention all algorithms
+%  are stateful. (smiley face). Whatever you prefer is fine with me.}
 For a given function ${\sf leak}$, adversary $A$, and simulator~$\Sim$,
@@
 Informally, a scheme $\Pi$ is secure with respect to some leakage function ${\sf leak}$
-if for all $A$ there is a simulator $\Sim$ such that
-$\AdvPrivSS{\Pi,{\sf leak}}{A,\Sim}$ is small.
-Intuitively, this means that the public portion
+if there is a simulator $\Sim$ such that $\AdvPrivSS{\Pi,{\sf leak}}{A,\Sim}$ is small
+for all~$A$. Intuitively, this means that the public portion
 $\pubaux$ of the representation of a set~$S$ leaks~${\sf leak}(S)$ and nothing more.
-\jnote{Need to relate running time of $\Sim$ to running time of~$A$.}
 
@@
 \experimentv{$\ExpPrivSSreal{\Pi}{A}$}\\
-$S \getsr A()$ \\
-$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
-return $A(M,\pubaux)$\\
+$(S,\st) \getsr A()$ \\
+$(\pubaux,\privaux) \getsr \Rep(S)$\\
+return $A(\st,\pubaux)$\\
 }
@@
 \experimentv{$\ExpPrivSSsim{\Pi, {\sf leak}}{A, \Sim}$}\\
-$S \getsr A()$\\
-$(M,\pubaux) \getsr \Sim({\sf leak}(S))$ \\
-return $A(M,\pubaux)$\\
+$(S,\st) \getsr A()$\\
+$(\st,\pubaux) \getsr \Sim({\sf leak}(S))$ \\
+return $A(\st,\pubaux)$\\
 

### 2016-09-02 Theorem3_FP.tex

@@
 \heading{Classical Bloom filter in random oracle model (ROM). }
-As discussed earlier, the classical Bloom filter (BF) is an instantiation of a set multiplicity data structure and admits errors in form of false  positives (FP) only.
+As discussed earlier, the classical Bloom filter (BF) is an instantiation of a set multiplicity data structure and admits errors in form of false-positives(FPs) only.
 In the ROM, $\Rep$ queries the random oracle to get the hash indices of elements of set $S$.
@@
 The proof of this theorem will follow along the lines of \Cref{thm2}.
+As in previous proofs, we use a game playing argument to prove this theorem as well.
+In $\game{0}$, the $\HashOracle$ does lazy sampling of elements from $[m]$ to mimic a random oracle(RO).
+It can be observed that, $\game{0}$ exactly simulates the BF's correctness game attacked by an adaptive adversary.
+So, $\AdvCorrect{{BF},\distr{\calS}{},r}{A} = \Prob{\game{0}(A) = 1}$.
+%
+In $\game{1}$, assuming $A$ does not make any pointless queries, $\HashOracle$ is modified to sample random elements from $[m]$.
+In addition, $\Test$ sets $\bad$ to $\true$ if queries indexed by set $\calI$ fail to be FPs, or if any of the remaining queries are FPs.
+$\game{2}$, on the other hand is exactly same as $\game{1}$ except it returns 0, if $\bad$ is set to $\true$.
+It can be easily seen that, $\game{1}$ and $\game{2}$ are exactly same as $\game{2}$ and $\game{3}$ of \Cref{thm2}'s game playing argument.
+So,
+\begin{align*}
+\Prob{\game{1}(A)=1} = \Prob{\game{0}(A)=1}\\
+\Prob{\game{2}(A)=1} = \frac{1}{\dbinom{q}{r}}\Prob{\game{1}(A)=1}
+\end{align*}
+\Cref{fig:D} shows non-adaptive adversary, $D$ that finds $r$ FPs against the standard BF. Using a similar explanation from previous proofs,
+\begin{align*}
+\AdvCorrect{{BF},\distr{\calS}{},r}{D} &= \Prob{\game{2}(A) = 1}\\
+\AdvCorrect{{BF},\distr{\calS}{},r}{D} &\leq \left( (1-e^{-kn/m})^k + O(1/n) \right)^r \,.
+\end{align*}
+To summarize, we have
+\[
+\AdvCorrect{{BF},\distr{\calS}{},r}{A} \leq  {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\]
+
+\begin{figure}
+\fpage{.9}{
+\hpagessl{.45}{.5}
+{
+\underline{\game{0}(A)}\\
+$S \getsr \distr{\calS}{}$\\
+$\err \gets 0$\\
+$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+$z \getsr A^{\TestOracle}(S,\pubaux)$\\
+if $\err  < r$ then Return 0\\
+Return 1\\\\
+%
+\oracle{$\TestOracle(q)$}\\
+$a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
+if $a \neq q(S)$ then \\
+\nudge $\err \gets\err +1$\\
+Return~$(a,\err )$\\\\
+%
+\oracle{$\HashOracle(x)$}\\
+for $j = 1$ to $k$\\
+\nudge $v_j \getsr [m]$\\
+\nudge if $T_j[x] \neq \undefined$\\
+\nudge \nudge $v_j \gets T_j[x]$\\
+\nudge $T_j[x] \gets v_j$\\
+Ret $\left(v_1,\ldots,v_k\right)$
+}
+{
+\underline{{$\game{1}(A)$},\fbox{$\game{2}(A)$}}\\
+$c\gets 0$, $\bad \gets \false$\\
+$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
+$S \getsr \distr{\calS}{}$\\
+$\err \gets 0$\\
+$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+$z \getsr A^{\TestOracle}(S,\pubaux)$\\
+if $\bad = \true$ then \fbox{Return 0}\\
+if $\err  < r$ then Return 0\\
+Return 1\\ 
+%
+\oracle{$\TestOracle(q)$}\\
+$c \gets c+1$\\
+$v \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
+if $c \in \mathcal{I}$ and $v = q(S)$ then \\
+\nudge $\bad \gets \true$ \\
+if $c \not\in \mathcal{I}$ and $v \neq q(S)$ then \\
+\nudge $\bad \gets \true$\\
+if $v \neq q(S)$\\
+\nudge $\err \gets\err +1$\\
+Return~$(v,\err )$\\\\
+%
+\oracle{$\HashOracle(x)$}\\
+for $j = 1$ to~$k$\\
+\nudge $v_j \getsr [m]$\\
+Ret $\left(v_1,\ldots,v_k\right)$
+}
+}
+\caption{\Cref{thm3}: Game playing argument}\label{fig:3TGame}
+\end{figure}
+
 \end{proof}

### 2016-09-02 results.tex
no message

@@
 
-\jnote{Outline:
+\jnote{Organize by scheme, not by security notions.
 }
@@
 \heading{Construction of PRF with domain separation.}
-Let $\Pi_{\mathrm{ds}}= (\Sigma,\Gamma,\calS,\calQ,\Rep, \Qry)$ be a set-multiplicity data structure identical to $\Pi_{\mathrm{lin}}$, except the $Hash$ algorithm, which is defined as follows.
+Let $\Pi_{\mathrm{ds}}= (\Sigma,\Gamma,\calS,\calQ,\Rep, \Qry)$ be a set-multiplicity data structure identical to $\Pi_{\mathrm{lin}}$, except the $\Hash$ oracle, which is defined as follows.
 Fix non-empty sets ~$\calK$, $\univ$ and integers $k,m,n>0$.

### 2016-09-02 notions.tex
OW notion returns
cleaning up privacy section

@@
 
-%\jnote{I don't know if I like the one-wayness definition any more; it seems a bit
-%ad hoc. And why do we care about one-wayness, anyway? Instead, I give
-%two versions of semantic security.}
-
-%The one-wayness definition (see
-%Figure~\ref{fig:privacy-ow}) is parameterized by a distribution $\distr{}{}$ over
-%sets. A set $S$ is chosen from this distribution, and a representation
-%$(\pubaux,\privaux)$ of that set is computed.
-%In one experiment ($\ExpPriv{\Pi,\distr{}{}}$), an attacker~$A$ is given $\pubaux$;
-%in a second experiment ($\ExpPrivNull{\Pi,\distr{}{}}{}$), it is not.
-%For a given $\distr{}{}$ and $A$, we define the advantage measure
-%$\AdvPriv{\Pi,\distr{}{}}{A} \bydef
-%\left| \Prob{\ExpPriv{\Pi,\distr{}{}}{A}=1} - \Prob{\ExpPrivNull{\Pi,\distr{}{}}{P}=1} \right|$.
-%We track the
-%time-complexity~$t$ and number of oracle queries~$q$ made by the adversary.
-%\jnote{Change. Compare $A$ in the 1-world to $P$ in the 0-world. Security means
-%there exists a $P$
-%such that for all~$A$ the following holds: $A$ in the 1-world does not do much better than
-%$P$ in the 0-world. Note that there is a canonical $P$ that does best, information-theoretically.}
-%\jnote{I now wonder whether we should allow test queries in both worlds.}
-%
-%\begin{figure}[hbtp]
-%\centering
-%\fpage{.6}{
-%\hpagess{.5}{.45}
-%{
-%\experimentv{$\ExpPriv{\setprim,\distr{}{}}{A}$}\\
-%$S \getsr \distr{}{}$\\
-%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
-%$z \getsr A^{\TestOracle}(M,\pubaux)$\\
-%if $z \in S$ then return 1\\
-%return 0\\
-%
-%\medskip
-%\experimentv{$\ExpPrivNull{\Pi, \distr{}{}}{P}$} \\
-%$S \getsr \distr{}{}$\\
-%%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
-%$z \getsr P()$\\
-%if $z \in S$ then return 1\\
-%return 0\\
-%%\medskip
-%%\experimentv{$\ExpWPriv{\setprim,\distr{}{}}{A}$}\\
-%%$S \getsr \distr{}{}$\\
-%%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
-%%$z \getsr A^{\TestOracle}(\pubaux)$\\
-%%if $z \in S$ then Return 1\\
-%%Return 0\\
-%}
-%%
-%{
-%\oracle{$\TestOracle(q)$}\\
-%$a \gets \Qry(M,\pubaux,\privaux,q)$\\
-%return~$a$
-%}
-%}
-%\caption{Experiments for a ``one-wayness'' style privacy
-%  definition.}
-%\label{fig:privacy-ow}
-%\end{figure}
-
-%\jnote{Actually, I am unsure whether a one-wayness definition is independently
-%interesting if we have (and can achieve) a semantic-security definition.}
-%\tsnote{Depends on what information we decide is okay to leak.  A
-%  classical BF gives an~$M$ that leaks a good approximation of $|S|$.
-%Do we want that to be considered semantically secure?  On the other
-%hand, a classical BF is one-way in the ROM, up to the min-entropy of
-%the distribution over~$S$.  So that may already give an interesting
-%example that fits in the gap.} \jnote{Yes. Semantic security
-%is parameterized by the leakage function, and so might or might not imply
-%one-wayness.}
 Our semantic-secure definition is simulation-based (see Figure~\ref{fig:privacy-ss}).
@@
 function~${\sf leak}$.
-%\tsnote{Need to pass state between stages if you want~$A$ to know the
-%  set it previously sampled, right?} \jnote{Yes, unless by convention all algorithms
-%  are stateful. (smiley face). Whatever you prefer is fine with me.}
 For a given function ${\sf leak}$, adversary $A$, and simulator~$\Sim$,
@@
 \jnote{Need to relate running time of $\Sim$ to running time of~$A$.}
-
+\todo{Introduce OW notion, if we keep it}
 \begin{figure}[hbtp]
@@
 return $A(\st,\pubaux)$\\
-
-%\medskip
-%\experimentv{$\ExpPrivSSsim{\Pi}{A, \calS}$}\\
-%$S \gets A()$\\
-%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
-%$(M',\pubaux) \gets \calS(\pubaux)$ \\
-%return $A(M',\pubaux)$\\
 }
@@
 \label{fig:privacy-ss}
+\end{figure}
+
+\begin{figure}[hbtp]
+\centering
+\fpage{.6}{
+\hpagess{.5}{.45}
+{
+\experimentv{$\ExpPrivOW{\setprim,\distr{}{}}{A}$}\\
+$S \getsr \distr{}{}$\\
+$(\pubaux,\privaux) \getsr \Rep(S)$\\
+$z \getsr A^{\TestOracle}(\pubaux)$\\
+if $z \in S$ then return 1\\
+return 0\\
+}
+{
+\oracle{$\TestOracle(q)$}\\
+eturn $\Qry(\pubaux,\privaux,q)$
+}
+}
+\caption{Experiments for a ``one-way'' style privacy
+  definition.}
+\label{fig:privacy-ow}
 \end{figure}
@@
 
-\subsection{Relationships Among Notions}\todo{Decide which of these
-  statements should have formal theorems and proofs.}
-Clearly we have priv $\Rightarrow$ wpriv, tightly and by an obvious
-reduction.  The converse is not true, however: consider the previous
-construction in which $M = S \setminus \{x\}$ for a random $x \in S$,
-and $\pubaux=\privaux=\emptystring$.  We note that this construction
-also serves to separate the priv notion from our notion of
-correctness.  (It is $1-(1/|S|)$ correct, but has no priv-security.)
-
-Curiously, the trivial scheme that sets $M=S$, $\pubaux=\privaux=\emptystring$ does seem to be both correct and wpriv-secure (up to the element-wise min-entropy of~$S$).
-\tsnote{In general, reducing correctness to wPriv is syntactically possible, but not clear how to connect the success events.
-In the one-wayness game, you win by outputing an element of~$S$; but how does this lead to finding an error-inducing query?
-Maybe the one-wayness attacker makes no queries, and just outputs a point~$z$.
-Then the correctness attacker does what?
-Ask some query~$q_z$ related to~$z$ ---remember, queries are not syntactically restricted to set membership!--- and see if the oracle returns the true value $q_z(S)$?
-This is pretty complicated...
-and it's not clear how to do a quality reduction.
-}
-\tsnote{Likewise the other way: the one-wayness adversary does not get~$S$, and yet needs to provide this to the correctness adversary.}
-
-\todo{We should be able to show...}
-\begin{itemize}
-\item ss-rep $\Rightarrow$ priv \emph{for set-multiplicity data
-    structures} \tsnote{but probably not in general}
-\item \{w\}priv $\not\Rightarrow$ ss-rep
-\end{itemize}
+\heading{Relationships Among Notions.} \todo{SS$\Rightarrow$OW?
+  (Probably not in general, but perhaps for set-multiplicity data
+  structures that satisfy certain assumptions on the query set.)
+  SS$\not\Rightarrow$ correctness; the converse is already shown by
+  the example I gave earlier, i.e. $M=S\setminus\{x\}$ for random $x
+  \in S$.}

### 2016-09-05 results.tex
adding scheme descriptions and updating text

@@
 }
+\include{scheme-descriptions}
 
@@
 in~\cite{xxx}.
-Let $\Pi_{\mathrm{lin}}= (\Sigma,\Gamma,\calS,\calQ,\Rep, \Qry)$ be defined as follows.
-Fix an $n \geq 0$, let $\mathcal{S}=[\univ]^n$, and let $\Sigma=\Gamma=\bits$.
-The queries are defined so that $q_x(S)=1$ if $x \in S$, and 0 otherwise.
-Fix non-empty sets ~$\calK$, $\univ$ and integers $k,m,n>0$.
-Let $F\colon\mathcal{K} \times \univ \to [m]$ be a function family.
-Define $\Hash$ as an algorithm that samples two keys $K_0,K_1 \getsr \mathcal{K}$ and defines $h_j(x) = F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$ for $j \in [1,k]$.
-$\Rep$ uses $\Hash$ to set $\privaux=\pubaux = (h_1, \ldots, h_k)$, computes an $m$ bit array, $M$ in the standard way and returns $(M,\pubaux,\privaux)$.
-The $\Qry$ algorithm gets $(M,\privaux, q_x)$ as input, and returns the AND of values at $M[h_1(x)],\ldots,M[h_k(x)]$.
-It must be noted that $\Pi_{\mathrm{lin}}$ admits errors in form of false-positives(FP) only.
-So, error rate of $\Pi_{\mathrm{lin}}$ is same as the (non-adaptive) FP rate.
-The following result shows, informally, that if~$F$ is a good PRF and the error rate is sufficiently small, then $\Pi_\mathrm{lin}$ is correct against adaptive error-finding adversaries.
-Henceforth, we refer errors and error-rate in $\Pi_{\mathrm{lin}}$ as FP's and FP rate, respectively.
+Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.
+Then $\Pi_{\mathrm{lin}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:lin-and-ds} (left side).
+The following result shows, informally, that if~$F$ is a good PRF, then $\Pi_\mathrm{lin}$ is correct against adaptive error-finding adversaries.
 

### 2016-09-05 syntax.tex
adding scheme descriptions and updating text

@@
     algorithm}, taking as input $S \in \mathcal{S}$, and outputting %a \emph{representation} $M \in \Sigma^*$,
-    \emph{private representation data} $\privaux \in \bits^*$, and
-    \emph{public representation data} $\pubaux \in \bits^*$.  We write
+    \emph{public representation data} $\pubaux \in \bits^*$ and
+    \emph{private representation data} $\privaux \in \bits^*$. We write
     $(\pubaux,\privaux) \getsr \Rep(S)$ as shorthand for this execution.
@@
 Fix a data structure $\setprim=(\Sigma,\Gamma,\calS,\calQ,\Rep,
-\Qry)$. Let $\mathrm{Err}(S,q,M,\pubaux,\privaux)$ be a predicate that is
-true iff $\Qry(M, \pubaux,\privaux, q) \neq q(S)$.  Then a data structure
+\Qry)$. Let $\mathrm{Err}(S,q,\pubaux,\privaux)$ be a predicate that is
+true iff $\Qry(\pubaux,\privaux, q) \neq q(S)$.  Then a data structure
 has \emph{error probability} $\epsilon$ if
-$\max_{S,q}\Pr[(M,\pubaux,\privaux) \getsr \Rep(S) :
-\mathrm{Err}(S,q,M,\pubaux,\privaux)=1 ] \leq \epsilon$.
+$\max_{S,q}\Pr[(\pubaux,\privaux) \getsr \Rep(S) :
+\mathrm{Err}(S,q,\pubaux,\privaux)=1 ] \leq \epsilon$.
 %
 It has \emph{error rate} $\tilde{\epsilon}$ if
-$\max_{S}\Pr[(M,\pubaux,\privaux) \getsr \Rep(S);\, q \getsr \calQ :
-\mathrm{Err}(S,q,M,\pubaux,\privaux)=1] \leq \tilde{\epsilon}$. \hfill\dqed
+$\max_{S}\Pr[(\pubaux,\privaux) \getsr \Rep(S);\, q \getsr \calQ :
+\mathrm{Err}(S,q,\pubaux,\privaux)=1] \leq \tilde{\epsilon}$. \hfill\dqed
 \end{definition}
@@
 correctness of the data structure. \tsnote{Don't know if this will be necessary.}
-
-\todo{Add discussion of just how broad the syntax is, in general.}
 

### 2016-09-05 results.tex
cheers

@@
 Before giving the proof, we note that Kirsch and Mitzenmacher~\cite{xxx} show
-that the ($r=1$, non-adaptive) FP-probability for~$\Pi_\mathrm{lin}$ is
+that the ($r=1$, zero-query) FP-probability for~$\Pi_\mathrm{lin}$ is
 always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
 rate of convergence is faster than~$1/n$.  The factor of $\dbinom{q}{r}$ arises as a result
-of removing adaptivity.  Finally, $\dbinom{q}{r} \leq q^r$ (with
+of moving from the adaptive to the zero-query setting.  Finally, $\dbinom{q}{r} \leq q^r$ (with
 reasonable tightness when~$r$ is small) in which case the final term in the bound behaves as
@@
 \heading{Construction of PRF with domain separation.}
-Let $\Pi_{\mathrm{ds}}= (\Sigma,\Gamma,\calS,\calQ,\Rep, \Qry)$ be a set-multiplicity data structure identical to $\Pi_{\mathrm{lin}}$, except the $\Hash$ oracle, which is defined as follows.
-Fix non-empty sets ~$\calK$, $\univ$ and integers $k,m,n>0$.
-Let $F\colon\mathcal{K} \times \univ \to [m]$ be a function family.
-The $\Hash$ algorithm provides randomness with domain separation, as it samples key $K \getsr \mathcal{K}$ and defines $h_j(x) = F_K(\langle j,x \rangle) $ for $j \in [1,k]$.
-Like $\Pi_{\mathrm{lin}}$, $\Pi_{\mathrm{ds}}$ admits errors in form of false positives only.
-Informally, the following result shows, if~$F$ is PRF secure and the data structure has low error rate in the non-adaptive setting, then $\Pi_{\mathrm{ds}}$ is correct against adaptive error finding adversaries.
-Hereafter, we refer errors and error-rate in $\Pi_{\mathrm{ds}}$ as false-positives and false-positive rate, respectively.
+Let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be a set-multiplicity data structure defined on the right-side of Figure~\ref{fig:lin-and-ds}.
+As with the preceding theorem, the following says (informally) that if~$F$ is a secure PRF, then this domain-separated PRF construction is correct against adaptive adversaries.
 
+\fixme{Make look like the previous theorem}
 \begin{theorem}\label{thm2}

### 2016-09-05 Proofs.tex
cheers
Theorem3 (in appendix)
Syntax consistence

--- 2016-07-13 Proofs.tex
@@
 \section{Proofs}
+\input{Theorem1_FP}
+
 \tsnote{Jon: ignore these for now.  This is Animesh's workspace.}
-\acnote{I will review for mistakes}
-\input{Theorem1_FP}
 \input{Theorem2_FP}
-\input{Theorem3_priv}
-
-\section{Summary of attacks(based on Bloom filter exploit) on Squid}
-\acnote{For reference}\\
-\heading{Crossby and Wallach: Squid Attack on hash tables} 
-\begin{itemize}
-\item A Squid server was ran on a stand-alone machine.
-\item A file containing a list of URL's was prepared.
-\item The URL requests were parsed and served by the Squid server. This completed the set-up phase.
-\item Crossby and Wallach targeted hash collisions in Squid to increase the average URL load time.
-The authors quote ``This attack does not represent a ''smoking gun” for algorithmic complexity attacks, but it does illustrate how common network services may be sensitive to these attacks".
-2 experiments were carried out to illustrate this.
-\item In experiment 1, around 143K random URL's were requested to the proxy server, whereas in experiment 2, same number of carefully chosen URL's that collide with the already present URL's in the hash-table were requested.
-\item Observation: The load time of random URL's was less than the chosen URL's.
-It must be noted that, the authors did not use a brute-force approach to find collisions.
-Rather,  they proposed an efficient method to find hash-collisions.
-The method involves finding a set of elements that hash to the same index and using a combination of those elements to find more elements.
-\end{itemize}
-
-\heading{Gerber et. al. : Squid attack on cache digest:}
-\begin{itemize}
-\item Squid servers follow a hierarchical model, and in this model the peers can exchange summary of their cache using Bloom filters(cache-digest). 
-\item In the set-up phase, the authors configure 2 peer Squid servers for caching and an HTTP server which responds to all queries of the Squid servers. 
-\item Peer 1's cache-digest is polluted using fake URL's. Both the peers exchange their cache-digests 
-\item Client(s) of Peer 2, start making URL requests. The URL's which are not cached by the latter are searched in its neighbors cache-digest and false positives are counted.
-\item Observation: There is a substantial increase in FP's due to pollution as compared to FP's without it.
-\item Reason: Fake URL's increase the Hamming weight of the cache digest of peer 1 and hence increase false positives.
-\end{itemize}
+\input{Theorem3_FP}

### 2016-09-05 Theorem1_FP.tex
Theorem3 (in appendix)
Proofs
Syntax consistence

@@
-%\heading{Linear-PRF construction. }
-%Here we consider a set-multiplicity data structure that was attacked by Neidermayer et al.
-in~\cite{xxx}.
-Let $\Pi_{\mathrm{lin}}= (\Sigma,\Gamma,\calS,\calQ,\Rep, \Qry)$ be defined as follows.
-Fix an $n \geq 0$, let $\mathcal{S}=[\univ]^n$, and let $\Sigma=\Gamma=\bits$.
-The queries are defined so that $q_x(S)=1$ if $x \in S$, and 0 otherwise.
-Fix non-empty sets ~$\calK$, $\univ$ and integers $k,m,n>0$.
-Let $F\colon\mathcal{K} \times \univ \to [m]$ be a function family.
-Define $\Hash$ as an algorithm that samples two keys $K_0,K_1 \getsr \mathcal{K}$ and defines $h_j(x) = F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$ for $j \in [1,k]$.
-$\Rep$ uses $\Hash$ to set $\privaux=\pubaux = (h_1, \ldots, h_k)$, and computes an $m$ bit array, $M$ in the standard way and returns $(M,\pubaux,\privaux)$.
-The $\Qry$ algorithm gets $(M,\privaux, q_x)$ as input, and returns the AND of values at $M[h_1(x)],\ldots,M[h_k(x)]$.
-It must be noted that $\Pi_{\mathrm{lin}}$ admits errors in form of false-positives(FP) only.
-So, error rate of $\Pi_{\mathrm{lin}}$ is same as the (non-adaptive) FP rate.
-The following result shows, informally, that if~$F$ is a good PRF and the error rate is sufficiently small, then $\Pi_\mathrm{lin}$ is correct against adaptive error-finding adversaries.
-Henceforth, we refer errors and error-rate in $\Pi_{\mathrm{lin}}$ as FP's and FP rate, respectively.
-%
-%\begin{theorem}\label{thm1}
-%Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{lin}}= (\Sigma,\Gamma,\calS,\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described.
-For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exist adversaries~$B_1,B_2$ (explicitly constructed in the proof of this theorem) such that
-%\[
-%\AdvCorrect{\Pi_{\mathrm{lin}},\distr{\calS}{},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
-%\]
-%Here, $B_1$ and $B_2$, each ask~$q$ oracle queries and have time complexity~$O(t+qm)$.
-%\end{theorem}
-%Before giving the proof, we note that Kirsch and Mitzenmacher~\cite{xxx} show
-%that the ($r=1$, non-adaptive) FP-probability for~$\Pi_\mathrm{lin}$ is
-%always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
-%rate of convergence is faster than~$1/n$.  The factor of $\dbinom{q}{r}$ arises as a result
-%of removing adaptivity.  Finally, $\dbinom{q}{r} \leq q^r$ (with
-%reasonable tightness when~$r$ is small) in which case the final term in the bound behaves as 
-%$(q (1-e^{-kn/m})^k + O(q/n) )^r$; loosely, the bound one expects for
-%trying to find a single FP in each of~$r$ independent``rounds'', each round
-%consisting of~$q$ attempts.
-
 \begin{proof}[\Cref{thm1}]
@@
 
+%\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
 \begin{figure}
-\centering
 \fpage{0.9}{
@@
 $\err \gets 0$\\
-$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
 Run~$A(S, \pubaux)$\\
-When $A$ asks $\TestOracle(q)$:\\
-\nudge $a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
-\nudge if $a \neq q(S)$ then \\
+When $A$ asks $\TestOracle(q_x)$:\\
+\nudge $a \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
+\nudge if $a \neq q_x(S)$ then \\
 \nudge \nudge $\err \gets \err +1$\\
@@
 $\err \gets 0$\\
-$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
 Run~$A(S, \pubaux)$\\
-When $A$ asks $\TestOracle(q)$:\\
-\nudge $a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
-\nudge if $a \neq q(S)$ then \\
+When $A$ asks $\TestOracle(q_x)$:\\
+\nudge $a \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
+\nudge if $a \neq q_x(S)$ then \\
 \nudge \nudge $\err \gets\err +1$\\
@@
 false-positives (and, conversely, which will not be), then a
-non-adaptive FP-finding adversary can ``guess'' which of~$A$'s queries require it
+zero-query FP-finding adversary can ``guess'' which of~$A$'s queries require it
 to return 1 when simulating the $\Test$, and which require it to
 return 0.  In this way, no queries ever actually need to be made.
-Moving to a non-adaptive setting will allow us to connect to classical
+Moving to a zero-query setting will allow us to connect to classical
 results on the FP-rate of Bloom filters; more in a moment.
@@
 %Under these assumptions,
-So, if $\game{4}(A)=1$, then there is a non-adaptive adversary~$D$ that finds~$r$ false positives against $\tilde{\Pi}_{\mathrm{lin}}$, which is $\Pi_{\mathrm{lin}}$ but with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$, respectively.
+So, if $\game{4}(A)=1$, then there is a zero-query adversary~$D$ that finds~$r$ false positives against $\tilde{\Pi}_{\mathrm{lin}}$, which is $\Pi_{\mathrm{lin}}$ but with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$, respectively.
 We give this~$D$ in \Cref{fig:D}.
 Intuitively, adversary~$D$ guesses which~$r$ of~$A$'s queries will be false positives; it simulates the~$\Test$ oracle by returning 1 on the guessed queries, and 0 otherwise; and it halts after finding $r$ FP's.
+It must be noted that, by the no-pointless queries assumption and the fact that the hash functions in $D$ are instantiated with random functions, $\pubaux$ is information theoretically independent of elements not in $S$.
 Thus we have
@@
 Note that $\tilde{\Pi}_{\mathrm{lin}}$ is the scheme that is analyzed in the classical Bloom filter literature ---the hash functions are modeled as independent random functions, and the parameters $k,m,n$  are set to achieve a target maximum false-positive probability (or rate).
-Kirsch and Mitzenmacher~\cite{KM} show that the upperbound on false-positive probability for a non-adaptive adversary and $r=1$ is $\left( (1-e^{-kn/m})^k + O(1/n) \right)$.
+Kirsch and Mitzenmacher~\cite{KM} show that the upperbound on false-positive probability for a zero-query adversary and $r=1$ is $\left( (1-e^{-kn/m})^k + O(1/n) \right)$.
 For $r>1$, we observe that~$A$'s queries $x_1,x_2,\ldots,x_q$ are distinct and not elements of the original set~$S$, since we assume no pointless queries.
@@
 $\err \gets 0$\\
-$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
 $z \getsr A^{\TestOracle}(S,\pubaux)$\\
@@
 %
-\oracle{$\TestOracle(q)$}\\
-$a \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
-if $a \neq q(S)$ then \\
+\oracle{$\TestOracle(q_x)$}\\
+$a \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
+if $a \neq q_x(S)$ then \\
 \nudge $\err \gets\err +1$\\
@@
 $S \getsr \distr{\calS}{}$\\
-$(M,\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
 $z \getsr A^{\TestOracle}(S,\pubaux)$\\
@@
 %
-\oracle{$\TestOracle(q)$}\\
+\oracle{$\TestOracle(q_x)$}\\
 $c \gets c+1$\\
-$v \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
-if $c \in \mathcal{I}$ and $v = q(S)$ then \\
+$v \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
+if $c \in \mathcal{I}$ and $v = q_x(S)$ then \\
 \nudge $\bad \gets \true$ \\
-if $c \not\in \mathcal{I}$ and $v \neq q(S)$ then \\
+if $c \not\in \mathcal{I}$ and $v \neq q_x(S)$ then \\
 \nudge $\bad \gets \true$\\
-if $v \neq q(S)$\\
+if $v \neq q_x(S)$\\
 \nudge $\err \gets\err +1$\\
@@
 
-%\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
-
 %\caption{Non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:D}
@@
 {
-$\adversaryv{D(S)}$\\[4pt]
+$\adversaryv{D(S, \pubaux)}$\\[4pt]
 $c \gets 0$\\%, $\calX \gets \emptyset$\\
@@
 $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
-Run $A(S)$\\
+Run $A(S, \pubaux)$\\
 When $A$ asks $\Test(x)$:\\
@@
 }
-\caption{\Cref{thm1}: Non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:D}
+\caption{Zero-query adversary $D$} \label{fig:D}
 \end{figure}

### 2016-09-05 Theorem2_FP.tex
Syntax consistence

@@
 \newcommand{\OK}{\calO(\langle j,x \rangle)}
-
-%\heading{Construction of PRF with domain separation.}
-%Let $\Pi_{\mathrm{ds}}= (\Sigma,\Gamma,\calS,\calQ,\Rep, \Qry)$ be a set-multiplicity data structure identical to $\Pi_{\mathrm{lin}}, except the $Hash$ algorithm which is defined as follows.
-Fix non-empty sets ~$\univ$, $\calK$ and integers $k,m,n>0$.
-Let $F\colon\mathcal{K} \times \univ \to [m]$ be a function family.
-The $\Hash$ algorithm provides randomness with domain separation, as it samples key $K \getsr \mathcal{K}$ and defines $h_j(x) = F_K(\langle j,x \rangle) $ for $j \in [1,k]$.
-Like $\Pi_{\mathrm{lin}}$, $\Pi_{\mathrm{ds}}$ admits errors in form of false positives only.
-Informally, the following result shows, if~$F$ is PRF secure and the filter has low error rate in the non-adaptive setting, then $\Pi_{\mathrm{ds}}$ is correct against adaptive error finding adversaries.
-Hereafter, we refer errors and error-rate in $\Pi_{\mathrm{ds}}$ as false-positives and false-positive rate, respectively.
-%
-%\begin{theorem}\label{thm2}
-%Fix $k,m,n,r >0$.
-Let $\Pi_{\mathrm{ds}}$ be the hash based filter just described.
-If there exists an adaptive adversary, $A$ compatible with $\ExpCorrect{\Pi_{\mathrm{ds}},\distr{\calS}{},r}{\cdot}$ asking $q$ queries, and has time complexity O(t), then there exists an adversary $B$ (explicitly constructed in the proof of this theorem), such that
-%\[
-%\AdvCorrect{\Pi_{\mathrm{ds}},\distr{\calS}{},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
-%\]
-%Here, $B$ asks $q$ queries, and has time complexity $O(t+qm)$.
-%\end{theorem}
 
@@
 
-Let $D$ be a non-adaptive adversary (shown in \Cref{fig:D}) that finds ~$r$ false positives against $\tilde{\Pi}_{\mathrm{ds}}$.
+Let $D$ be a zero-query adversary (shown in \Cref{fig:D}) that finds ~$r$ false positives against $\tilde{\Pi}_{\mathrm{ds}}$.
 Using explanations from previous theorem, if $A$ wins $\game{3}$, then $D$ wins $\ExpCorrect{\tilde{\Pi}_{\mathrm{ds}},\distr{\calS}{},r}{\cdot}$ game.
@@
 \end{equation*}
+
 Note that like $\tilde{\Pi}_{\mathrm{lin}}$, $\tilde{\Pi}_{\mathrm{ds}}$ is the scheme that is analyzed in the classical Bloom filter literature.
-So, for a non-adaptive adversary $D$ and $r=1$, the upper bound on false-positive probability of a classical Bloom filter applies to $\tilde{\Pi}_{\mathrm{ds}}$ as well.
+So, for a zero-query adversary $D$ and $r=1$, the upper bound on false-positive probability of a classical Bloom filter applies to $\tilde{\Pi}_{\mathrm{ds}}$ as well.
 For $r > 1$, based on the assumption that $A$ makes no pointless queries, the queries made by $A$ are distinct and not elements of the original set $S$.
@@
 {
-\oracle{$\TestOracle(q)$}\\
+\oracle{$\TestOracle(q_x)$}\\
 $c \gets c+1$\\
-$v \gets \Qry^{\HashOracle}(M,\privaux,q)$\\
-if $c \in \mathcal{I}$ and $v = q(S)$ then \\
+$v \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
+if $c \in \mathcal{I}$ and $v = q_x(S)$ then \\
 \nudge $\bad \gets \true$ \\
-if $c \not\in \mathcal{I}$ and $v \neq q(S)$ then \\
+if $c \not\in \mathcal{I}$ and $v \neq q_x(S)$ then \\
 \nudge $\bad \gets \true$\\
-if $v \neq q(S)$\\
+if $v \neq q_x(S)$\\
 \nudge $\err \gets\err +1$\\

### 2016-09-05 results.tex
Syntax consistence

@@
 \begin{theorem}\label{thm1}
-Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{lin}}= (\Sigma,\Gamma,\calS,\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described.
+Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{lin}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described.
 For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exist prf-adversaries~$B_1,B_2$ (explicitly constructed in the proof of this theorem) such that
@@
 \begin{theorem}\label{thm2}
-Fix $k,m,n,r >0$.
-Let $\Pi_{\mathrm{ds}}$ be the set-multiplicity data structure just described.
-If there exists an adaptive adversary, $A$ compatible with $\ExpCorrect{\Pi_{\mathrm{ds}},\distr{\calS}{},r}{\cdot}$ asking $q$ queries, and has time complexity O(t), then there exists a prf-adversary $B$ (explicitly constructed in the proof of this theorem), such that
+Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described.
+For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exists a prf-adversary ~$B$ (explicitly constructed in the proof of this theorem) such that
 \[

### 2016-09-05 syntax.tex
Syntax consistence

@@
 
-\heading{Data structures.}  We being by defining a general primitive
+\heading{Data structures.}  We begin by defining a general primitive
 that produces a representation of a given multiset, and provides a
@@
 \begin{definition}[Error probability and rate] \rm
-Fix a data structure $\setprim=(\Sigma,\Gamma,\calS,\calQ,\Rep,
-\Qry)$. Let $\mathrm{Err}(S,q,\pubaux,\privaux)$ be a predicate that is
+Fix a data structure $\setprim=(\calQ,\Rep, \Qry)$. Let $\mathrm{Err}(S,q,\pubaux,\privaux)$ be a predicate that is
 true iff $\Qry(\pubaux,\privaux, q) \neq q(S)$.  Then a data structure
@@
 uniform samples from~$\calQ$.
-Let $\mathrm{Err}_i$ be a random variable indicating the event $\Qry(M,\pubaux,\privaux,q_i)\neq q_i(S)$.
+Let $\mathrm{Err}_i$ be a random variable indicating the event $\Qry(\pubaux,\privaux,q_i)\neq q_i(S)$.
 The $(1-\epsilon)$-correctness of~$\Pi$ guarantees that the probability that $\mathrm{Err}_i=1$ is at most~$\epsilon$,
@@
 Let $\Rep(S)$ pick a random element~$s \in S$, and return $M = S \setminus \{s\}$ and $\privaux = \emptystring$.
-To respond to queries, let~$\Qry(M,\pubaux,\privaux,q_x)=1$ iff $x \in M$.
+To respond to queries, let~$\Qry(\pubaux,\privaux,q_x)=1$ iff $x \in M$.
 It is easy to see that this scheme is $1/n$-correct; for any fixed~$S$, there are exactly~$n$ queries~$q_x$ that have probability~$1/n$  (over the coins of~$\Rep$) of causing a correctness error, and the remaining $|\univ|-n$ queries have probability zero of causing an error.
@@
 
-It is not hard to see Bloom filters are an instantiation a
+It is not hard to see Bloom filters are an instantiation of a
 set-multiplicity data structure.  Fix $\Sigma=\Gamma=\bits$.  Define
@@
 all $i\in [k]$ and $x \in S$.  Finally, $\Rep$ returns
-$\privaux=\emptystring$, $\pubaux = (h_1,\ldots, h_k)$, and~$M$ as the
+$\privaux=\emptystring$ and $\pubaux = M$ as the
 representation.
 %
-The algorithm~$\Qry$ is defined so that, on input $(M,\pubaux,\privaux,q_x)$, it
+The algorithm~$\Qry$ is defined so that, on input $(\pubaux,\privaux,q_x)$, it
 returns the minimum of the values $M[h_1(x)],\ldots,M[h_k(x)]$.  We note that, while our error
@@
 As a simple extension, consider $\Sigma=\mathbb{N}$ and modify the
-basic Bloom filter so that it that stores counters, rather than
+basic Bloom filter so that it stores counters, rather than
 bits, at each position in an array.  In particular, for each~$x \in
@@
 A Bloom filter with secret hash functions is captured by setting
-$\privaux=(h_1,h_2,\ldots,h_k)$, and setting $\pubaux=\emptystring$.
+$\privaux=(h_1,h_2,\ldots,h_k)$, and setting $\pubaux=M$.
 Related constructions that use a secret key~$K$, but not for hashing (e.g.\ the PRP-based
-construction from NY), are captured setting $\privaux=K, \pubaux=(h_1, \ldots, h_k)$.
+construction from NY), are captured setting $\privaux=K, \pubaux=M$.
 
-By setting $\Sigma=\bits^L$ for a specified $L>0$, we capture he
+By setting $\Sigma=\bits^L$ for a specified $L>0$, we capture the
 so-called ``garbled Bloom filter'' due to Dong, Chen and

### 2016-09-06 results.tex
cheers

@@
 \begin{theorem}\label{thm1}
-Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{lin}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described.
+Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{lin}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
+Let $\distr{}{}$ be a distribution over~$\mathcal{S}$.
 For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exist prf-adversaries~$B_1,B_2$ (explicitly constructed in the proof of this theorem) such that
@@
 
-\fixme{Make look like the previous theorem}
 \begin{theorem}\label{thm2}
-Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described.
+Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure in Figure~\ref{fig:lin-and-ds}.
+Let $\distr{}{}$ be a distribution over~$\mathcal{S}$.
 For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exists a prf-adversary ~$B$ (explicitly constructed in the proof of this theorem) such that

### 2016-09-06 notions.tex
minor edits

@@
 In addition to correctness, we establish notions of privacy for
-set-representations.
+set-multiplicity data structures.
 
@@
 distribution~$\distr{}{}$ over the collection of multisets
-$\mathcal{S}$ associated to~$\Pi$, and then
-$\Rep(S)$ is run to generate $(\pubaux,\privaux)$.
+$\mathcal{S}$ associated with~$\Pi$, and then
+$\Rep(S)$ is run to generate $(\pubaux,\privaux)$. \jnote{I thought we were going to let
+the adversary choose~$S$?}
 %(Unless stated otherwise, we assume security holds for all distributions and thus for all sets $S$.)
-Adversary~$A$ is given~$\calS$ and $\pubaux$~as input; it is
-provided an oracle~$\TestOracle$ that, on input a query~$q \in \calQ$,
-computes (and returns) the result of $\Qry(\pubaux,\privaux,q)$, and increments
+Adversary~$A$ is given~$\pubaux$~as input; it is also
+provided with access to an oracle~$\TestOracle$ that, on input a query~$q \in \calQ$,
+returns $\Qry(\pubaux,\privaux,q)$ and increments
 a counter if this result is in error.  The adversary wins if it
@@
 set-representation~$\Pi$ is $(t,q,r,\epsilon')$-correct if $\AdvCorrect{\Pi,\distr{}{},r}{t,q} \leq \epsilon'$.
-\jnote{Note that test includes err because we don't want to penalize
-the adversary's resources for computing $q(S)$.}
+\jnote{Note~$q$ is overloaded here.}
+%\jnote{Note that test includes err because we don't want to penalize
+%the adversary's resources for computing $q(S)$.}
 
@@
 Lifting their definition to our setting, the experiment is similar but the attacker
-succeeds only if it outputs a single query $q$ for which $\Qry(\pubaux,\privaux, q) \neq q(S)$  \emph{subject to the restriction that it did not query $q$ to its $\Qry$ oracle}.
-It will be interesting to understand formally the relation between our definition and theirs.
+succeeds only if it outputs a single query $q$ for which
+$\Qry(\pubaux,\privaux, q) \neq q(S)$  \emph{subject to the restriction that it did not
+query $q$ to its $\TestOracle$ oracle}.
+It will be interesting to understand formally the relation between our
+definition and theirs.
 Here are some observations:

### 2016-09-06 ds-ss-proof.tex
starting to typeset ss proof for domain-separated PRF construction

\begin{theorem}
Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.  For any set~$S$, let $\leak(S)=|S|$.  For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exists a simulator~$\Sim$ and a prf-adversary ~$B$ (both explicitly constructed in the proof of this theorem) such that
$
\AdvPrivSS{\Pi_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}.
$
\end{theorem}

### 2016-09-06 notions.tex
starting to typeset ss proof for domain-separated PRF construction
no message

@@
 manages to cause at least~$r>0$ such errors among its queries.
+\jnote{If we are specializing the set-multiplicity data structures then we
+may as well have the attacker query $x$ which gets translated to query $q_x$. If
+we are trying to be more general then we should be consistent.} \jnote{Why does $A$ output
+anything at all?}
 
@@
 }
-\caption{Correctness of~$\Pi$ against (adaptive) adversary~$A$, when
+\caption{Correctness of~$\Pi$ against an (adaptive) adversary~$A$, when
   the represented multiset~$S$ is sampled according to distribution~$\distr{}{}$.}
@@
 
-In this experiment we track the time-complexity (relative to some
-implied model of computation) and query-complexity (i.e., number of
-queries) of the adversary~$A$.
+In this experiment we track the time complexity (relative to some
+model of computation) and query complexity (i.e., number of
+queries to $\TestOracle$) of~$A$.
 We define the advantage of adversary~$A$ in the correctness experiment as
 $\AdvCorrect{\Pi,\distr{}{},r}{A} = \Prob{\ExpCorrect{\Pi,\distr{}{}, r,}{A}=1}$.
-Overloading notation, we write $\AdvCorrect{\Pi,\distr{}{},r}{t,q}$ for the maximum over all~$t$-time adversaries that ask at most~$q$ queries. Roughly, we say that a
-set-representation~$\Pi$ is $(t,q,r,\epsilon')$-correct if $\AdvCorrect{\Pi,\distr{}{},r}{t,q} \leq \epsilon'$.
+Overloading notation, we write $\AdvCorrect{\Pi,\distr{}{},r}{t,q}$ for the maximum over
+all~$t$-time adversaries that ask at most~$q$ queries. We say that a
+set-representation data structure~$\Pi$ is $(t,q,r,\epsilon')$-correct if $\AdvCorrect{\Pi,\distr{}{},r}{t,q} \leq \epsilon'$.
 \jnote{Note~$q$ is overloaded here.}
@@
 \heading{Comparison to Naor-Yogev definition.}
-The style of the Naor-Yogev (NY) definition is slightly different. \jnote{Even if we ignore
-all the other issues, chief among them the inconsistent way it treats the hash functions.}
-Lifting their definition to our setting, the experiment is similar but the attacker
-succeeds only if it outputs a single query $q$ for which
+The style of the Naor-Yogev definition is different from ours.
+Lifting their definition\footnote{They focus specifically on set-representation data structures
+with no false negatives, and consider worst-case choice of~$S$. Their data-structure syntax
+also does not distinguish public and private portions of the representation. Nevertheless, it is straightforward
+to extend their definition to more closely match ours.}
+to our setting,
+the experiment is similar but the attacker
+succeeds only if it outputs a (single) query $q$ for which
 $\Qry(\pubaux,\privaux, q) \neq q(S)$  \emph{subject to the restriction that it did not
-query $q$ to its $\TestOracle$ oracle}.
+previously query $q$ to its $\TestOracle$ oracle} (see Figure~\ref{fig:NYcorrectness}).
+
+\begin{figure}[htp]
+\centering
+\fpage{.6}{
+\hpagess{.5}{.45}
+{
+\experimentv{$\ExpCorrect{\setprim,\distr{}{},r}{A}$}\\
+$S \getsr \distr{}{}$\\
+$\mathcal{Q} \gets \emptyset$\\
+%$\mathrm{err}\gets 0$\\
+$(\pubaux,\privaux) \getsr \Rep(S)$\\
+$q \getsr A^{\TestOracle}(S,\pubaux)$\\
+if $\left(q \not \in \mathcal{Q}\right.$ and \\
+\nudge $\left.\Qry(\pubaux,\privaux,q) \neq q(S)\right)$ \\
+\nudge \nudge then Return 1\\
+Return 0
+}
+%
+{
+\oracle{$\TestOracle(q)$}\\
+$a \gets \Qry(\pubaux,\privaux,q)$\\
+$\mathcal{Q} \gets \mathcal{Q} \cup \{q\}$ \\
+%\nudge $\mathrm{err}\gets\mathrm{err}+1$\\
+Return~$(a,q(S))$
+}
+}
+\caption{The Naor-Yogev definition of
+correctness, adapted to our setting.}
+\label{fig:NYcorrectness}
+\end{figure}
+
 It will be interesting to understand formally the relation between our

### 2016-09-06 ds-ss-proof.tex
proof sketch for ss-security of domain-sep PRF constuction

@@
 \begin{theorem}
-Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
+Fix $k,m,n>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
 For any set~$S$, let $\leak(S)=|S|$.
-For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exists a simulator~$\Sim$ and a prf-adversary ~$B$ (both explicitly constructed in the proof of this theorem) such that
-$
-\AdvPrivSS{\Pi_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}.
-$
+There exists a simulator~$\Sim$ such that, for any adversary~$A$
+\[
+\AdvPrivSS{\Pi_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
+\]
+where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.) 
 \end{theorem}
+\begin{proof}[Proof (sketch). ]
+Adversary~$B^{f}$ simulates the steps of $\ExpPrivSSreal{\Pi_{\mathrm{ds}}}{A}$, using its oracle to simuate~$\Rep(S)$.
+When~$f=F_K$ then the simulation is perfect.
+When~$f=\rho$ then~$B$ simulates $\ExpPrivSSreal{\tilde{\Pi}_{\mathrm{ds}}}{A}$ where $\tilde{\Rep}$ effectively uses~$k$ independent random functions as the hash functions.
+But the $\pub$ produced by $\tilde{\Rep}$ has a distribution that depends only on the size of~$S$ ($n$) and the other public parameters~$m,k$.
+Thus, a simulator~$\Sim$ given only $\leak(S)=|S|=n$ can produce a correct~$\pub$ as follows: starting with an all-zeros array~$M$ of length~$m$, uniformly sample (with replacement)~$nk$ integers in~$[m]$ and set the resulting positions of~$M$ to 1.
+\end{proof}

### 2016-09-07 notions.tex
no message

@@
 $\Rep(S)$ is run to generate $(\pubaux,\privaux)$. \jnote{I thought we were going to let
-the adversary choose~$S$?}
+the adversary choose~$S$?} \jnote{If instead we choose $S$ from ${\cal D}$, then
+is it clear we want to give $S$ to~$A$?}
 %(Unless stated otherwise, we assume security holds for all distributions and thus for all sets $S$.)
@@
 
+\jnote{I changed $\TestOracle$ so that it outputs $(a, q(S))$ rather
+than $(a,\mathrm{err})$. Note that the latter can be computed from the former,
+and in the general case I think the former is what we want.} \jnote{I also changed
+the definition so the adversary has to find $r$ {\bf unique} inputs on which
+there is an error.}
+
 \begin{figure}[htp]
 \centering
-\fpage{.6}{
+\fpage{.65}{
 \hpagess{.5}{.45}
@@
 $S \getsr \distr{}{}$\\
+$\mathcal{Q} \gets \emptyset$ \\
 $\mathrm{err}\gets 0$\\
@@
 $a \gets \Qry(\pubaux,\privaux,q)$\\
-if $a \neq q(S)$ then \\
+if ($a \neq q(S)$ and $q \not \in \mathcal{Q}$) then \\
 \nudge $\mathrm{err}\gets\mathrm{err}+1$\\
-Return~$(a,\mathrm{err})$
+$\mathcal{Q} \gets \mathcal{Q} \cup \{q\}$ \\
+Return~$(a,q(S))$
 }
@@
 We define the advantage of adversary~$A$ in the correctness experiment as
-$\AdvCorrect{\Pi,\distr{}{},r}{A} = \Prob{\ExpCorrect{\Pi,\distr{}{}, r,}{A}=1}$.
+$\AdvCorrect{\Pi,\distr{}{},r}{A} = \Prob{\ExpCorrect{\Pi,\distr{}{}, r}{A}=1}$.
 Overloading notation, we write $\AdvCorrect{\Pi,\distr{}{},r}{t,q}$ for the maximum over
@@
 
-\heading{Comparison to Naor-Yogev definition.}
-The style of the Naor-Yogev definition is different from ours.
+\heading{Comparison to the Naor-Yogev definition.}
+The structure of the Naor-Yogev definition is different from ours.
 Lifting their definition\footnote{They focus specifically on set-representation data structures
@@
 $\Qry(\pubaux,\privaux, q) \neq q(S)$  \emph{subject to the restriction that it did not
-previously query $q$ to its $\TestOracle$ oracle} (see Figure~\ref{fig:NYcorrectness}).
+previously query $q$ to its $\TestOracle$ oracle}. We refer to
+Figure~\ref{fig:NYcorrectness} for a definition of the relevant experiment.
+We define the advantage of adversary~$A$ as
+$\NYAdvCorrect{\Pi,\distr{}{}}{A} = \Prob{\NYExpCorrect{\Pi,\distr{}{}}{A}=1}$,
+and write $\NYAdvCorrect{\Pi,\distr{}{},r}{t,q}$ for the maximum over
+all~$t$-time adversaries that ask at most~$q$ queries. We say that a
+set-representation data structure~$\Pi$ is $(t,q,\epsilon')$-NY-correct if
+$\NYAdvCorrect{\Pi,\distr{}{}}{t,q} \leq \epsilon'$. \jnote{This should all probably
+move to an appendix; it's a lot of notation to digest for something we never use again
+in the paper.}
+
+\jnote{Just noticed something (else) odd about the NY definition: we cannot assume w.l.o.g.\
+that $A$ makes exactly $q$ queries, and in fact it is possible to have cases where increasing
+the number of queries the attacker makes can decrease its advantage! This seems like
+another drawback of the definition.}
 
@@
 {
-\experimentv{$\ExpCorrect{\setprim,\distr{}{},r}{A}$}\\
+\experimentv{$\ExpCorrect{\setprim,\distr{}{}}{A}$}\\
 $S \getsr \distr{}{}$\\
@@
 
-It will be interesting to understand formally the relation between our
-definition and theirs.
-Here are some observations:
+With the above in place we can now relate their definition to ours.
+
+\jnote{There's something ``morally wrong'' with the follow theorem statement:
+if we increase $q$ then the assumption about the NY-correctness of $\Pi$ (presumably)
+gets stronger---even if formally that is not true---but the conclusion of the theorem
+becomes weaker.}
+
+\begin{theorem}
+If $\Pi$ is $(t,q,\epsilon')$-NY-correct, then it is also
+$(t, q', r, q'\epsilon'/r)$-correct for any $q' \leq q+1$ and $r\geq 1$.
+\end{theorem}
+\begin{proof}
+Let $\Pi$ be a set-representation data structure that is $(t,q,\epsilon')$-NY-correct,
+and assume that for some $q' \leq q+1$ and $r \geq 1$
+there is an adversary $A$ running in time~$t$
+and making $q'$ oracle queries (note that without loss of generality
+we may assume $A$ always makes exactly $q'$ queries) such that
+$\AdvCorrect{\Pi,\distr{}{},r}{A} > q'\epsilon'/r$.
+With probability at least
+$q'\epsilon'/r$ in an execution of $\ExpCorrect{\Pi,\distr{}{},r}{A}$, we have that
+$A$ makes at least $r$ distinct queries to $\TestOracle$ for which
+an incorrect answer is returned. Let $A'$ be the algorithm that simply
+runs~$A$, but chooses
+uniformly one of the $q'$ queries of $A$ to its $\TestOracle$ oracle and outputs that query
+as its final output. Then with probability at least $r/q' \cdot (q'\epsilon'/r)=\epsilon'$
+the query chosen by $A'$
+leads to an incorrect answer, and was not previously asked to the $\TestOracle$ oracle.
+Since the running time of $A'$ is at most $t$, and it makes at most $q'-1 \leq q$ queries
+to its oracle, this is a contradiction.
+\end{proof}
+
+\jnote{It is unclear whether the above is tight, but it is also unclear whether
+that is something worth thinking about. }
+
 \begin{enumerate}
@@
 probability at least $\epsilon'=q\epsilon_{NY}/r$,
-issues~$q$ Test-queries of which at least~$r$ cause errors. If we simply run~$A$ and then choose a random Test-query to
-output, we succeed with probability at least $\epsilon' \cdot r/q$. It is unclear whether this is tight.
+issues~$q$ Test-queries of which at least~$r$ cause errors.
+If we simply run~$A$ and then choose a random Test-query to
+output, we succeed with probability at least $\epsilon' \cdot r/q$.
+It is unclear whether this is tight.
 

### 2016-09-07 notions.tex
no message

@@
 Let $\Pi$ be a set-representation data structure that is $(t,q,\epsilon')$-NY-correct,
-and assume that for some $q' \leq q+1$ and $r \geq 1$
+and assume that for some distribution $\distr{}{}$, some $q' \leq q+1$, and
+some $r \geq 1$
 there is an adversary $A$ running in time~$t$
-and making $q'$ oracle queries (note that without loss of generality
-we may assume $A$ always makes exactly $q'$ queries) such that
+and making $q'$ oracle queries such that
 $\AdvCorrect{\Pi,\distr{}{},r}{A} > q'\epsilon'/r$.
+(Note that
+we may assume $A$ always makes exactly $q'$ queries without loss of generality.)
 With probability at least
@@
 \jnote{It is unclear whether the above is tight, but it is also unclear whether
-that is something worth thinking about. }
+that is something worth thinking about.}
+\jnote{I guess the most interesting(?)\@ case for comparison purposes
+is when $r=1$. Then one can have a scheme, say, where every query is independently
+answered incorrectly with probability~$\epsilon$. Such a
+scheme will be $(t,q,\epsilon)$-NY-correct
+for any $t, q$, however an adversary making $q=1/\epsilon$ queries has constant advantage
+under our correctness definition (for $r=1$). So the theorem is tight for $r=1$.}
 

### 2016-09-07 Theorem3_FP.tex

--- 2016-08-31 Theorem3_FP.tex
@@
-\acnote{To be verified before moving the theorem to section 4}
+\acnote{INCOMPLETE. To be verified before moving the theorem to section 4}
 \heading{Classical Bloom filter in random oracle model (ROM). }
-As discussed earlier, the classical Bloom filter (BF) is an instantiation of a set multiplicity data structure and admits errors in form of false  positives (FP) only.
-In the ROM, $\Rep$ queries the random oracle to get the hash indices of elements of set $S$.
-It then computes the $m$-bit array, $M$ and outputs $\privaux=\emptystring$, $\pubaux = \emptystring$ and $M$ as the representation of
-the Bloom filter.
-The $\Qry$ oracle uses the random oracle in a similar way.
-For any query $q$, it gets the hash indices $h_1, \ldots, h_k$ from the random oracle and returns 1 if $M[h_i(x)]=1$ for all $i\in [k]$, and 0 otherwise.
+Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.  Then $\Pi_{\mathrm{Bloom}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-garbled-bf} (left side).  The following result shows,
 \begin{theorem}\label{thm3}
-Fix $k,m,n,r>0$. Let $A$ be an adaptive adversary (for attacking BF) asking $q$ queries to the random oracle. Let $t$ be the running time of $A$ given these queries. Then, 
+Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{Bloom}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described.
+For any adversary~$A$ that makes a total of~$q$ queries to the oracle and has time-complexity~$O(t)$, there exist prf-adversaries~$B_1,B_2$ (explicitly constructed in the proof of this theorem) such that
 \[
-\AdvCorrect{{BF},\distr{\calS}{},r}{A} \leq  {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\AdvCorrect{\Pi_{\mathrm{Bloom}},\distr{\calS}{},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
 \]
@@
 \begin{proof}[\Cref{thm3}]
-The proof of this theorem will follow along the lines of \Cref{thm2}.
+We use a game playing argument to prove this theorem in the ROM.
+In $\game{0}$, the $\HashOracle$ does lazy sampling of elements from $[m]$ to mimic a random oracle(RO).
+For every distinct query, $\Hash$ returns a random value sampled from $[m]$.
+Here, the adversary $A$, along with $\Rep$ and $\Qry$ are given access to $\Hash$.
+It can be seen that, $\game{0}$ exactly simulates the correctness game of $\Pi_{\mathrm{Bloom}}$.
+So, $\AdvCorrect{\Pi_{\mathrm{Bloom}},\distr{\calS}{},r}{A} = \Prob{\game{0}(A) = 1}$.
+
+\begin{figure}
+\fpage{.9}{
+\hpagessl{.45}{.5}
+{
+\underline{\game{0}(A)}\\
+$S \getsr \distr{\calS}{}$, $\err \gets 0$\\
+$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+$z \getsr A^{\TestOracle, \HashOracle}(S,\pubaux)$\\
+if $\err  < r$ then Return 0\\
+Return 1\\
+%
+\oracle{$\TestOracle(q_x)$}\\
+$a \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
+if $a \neq q_x(S)$ then \\
+\nudge $\err \gets\err +1$\\
+Return~$(a,\err )$\\
+%
+\oracle{$\HashOracle(i,q_y)$}\\
+$v \getsr [m]$\\
+if $T[i,q_y] \neq \undefined$\\
+\nudge $v \gets T[i,q_y]$\\
+$T[i,q_y] \gets v$\\
+Ret $v$
+}
+{
+\underline{$\game{1}(A)$}\\
+$S \getsr \distr{\calS}{}$, $\err \gets 0$\\
+$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+$z \getsr A^{\TestOracle, \HashOracle}(S,\pubaux)$\\
+if $\err  < r$ then Return 0\\
+Return 1\\ 
+%
+\oracle{$\TestOracle(q_x)$}\\
+$M \gets\pubaux$\\
+for $j \in \{1,2,\ldots,k\}$\\
+\nudge $h_j \gets \HashOracle(j,q_x)$\\
+\nudge if $M[h_j] \neq 1$ then Return $(0, \err)$\\
+$\err \gets \err +1$\\
+Return~$(1,\err )$\\
+%
+\oracle{$\HashOracle(i,q_y)$}\\
+$v \getsr [m]$\\
+if $T[i,q_y] \neq \undefined$\\
+\nudge $v \gets T[i,q_y]$\\
+$T[i,q_y] \gets v$\\
+Ret $v$
+}
+}
+\fpage{.9}{
+\hpagessl{.45}{.5}
+{
+\underline{$\game{2}(A)$}\\
+$S \getsr \distr{\calS}{}$, $\err \gets 0$\\
+$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+$z \getsr A^{\TestOracle, \HashOracle}(S,\pubaux)$\\
+if $\err  < r$ then Return 0\\
+Return 1\\ 
+%
+\oracle{$\TestOracle(q_x)$}\\
+$M \gets\pubaux$\\
+for $j \in \{1,2,\ldots,k\}$\\
+\nudge $h_j \gets \HashOracle(j,q_x)$\\
+\nudge if $M[h_j] \neq 1$\\
+\nudge \nudge if $j = 1$ then Return $(0, \err, \emptystring)$\\
+\nudge \nudge Return $(0, \err, (h_1, \ldots, h_{j-1}))$\\
+$\err \gets \err +1$\\
+Return~$(1,\err, (h_1, \ldots, h_{k}) )$\\
+%
+\oracle{$\HashOracle(i,q_y)$}\\
+$v \getsr [m]$\\
+if $T[i,q_y] \neq \undefined$\\
+\nudge $v \gets T[i,q_y]$\\
+$T[i,q_y] \gets v$\\
+Ret $v$
+}
+{
+\underline{$\game{3}(A)$}\\
+$S \getsr \distr{\calS}{}$, $\err \gets 0$\\
+$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+$z \getsr A^{\TestOracle, \HashOracle}(S,\pubaux)$\\
+if $\err  < r$ then Return 0\\
+Return 1\\ 
+%
+\oracle{$\TestOracle(q_x)$}\\
+$M \gets\pubaux $\\
+$(h_1, \ldots, h_{k}) \gets \HashOracle(q_x)$\\
+for $j \in \{1,2,\ldots,k\}$\\
+\nudge if $M[h_j] \neq 1$ then \\
+\nudge \nudge Return~$(0,\err, (h_1, \ldots, h_{k}) )$\\
+$\err \gets \err +1$\\
+Return~$(1,\err, (h_1, \ldots, h_{k}) )$\\
+%
+\oracle{$\HashOracle(q_y)$}\\
+$v_j \getsr [m]$\\
+for $j \in \{1,2,\ldots,k\}$\\
+\nudge if $T[j,q_y] \neq \undefined$\\
+\nudge \nudge $v_j \gets T[j,q_y]$\\
+\nudge $T[j,q_y] \gets v_j$\\
+Ret $\left(v_1,\ldots,v_k\right)$
+}
+}
+\caption{\Cref{thm3}: Game playing argument}\label{fig:3TGame}
+\end{figure}
+\begin{figure}
+\fpage{.9}{
+\hpagessl{.45}{.5}
+{
+\underline{\game{4}(A)\fbox{\game{5}(A)}}\\
+$S \getsr \distr{\calS}{}$\\
+$\err \gets 0$, $\Ans \gets \emptyset$\\
+$c \gets 0$, $\bad \gets \false$\\
+$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
+$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+$z \getsr A^{\TestOracle, \HashOracle}(S,\pubaux)$\\
+if $\bad = \true$ then \fbox{Return 0}\\
+if $\err  < r$ then Return 0\\
+Return 1\\
+%
+\oracle{$\TestOracle(q_x)$}\\
+if $\Ans[x] \neq \undefined$\\
+\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(q_x)$\\
+Return $\Ans[x]$\\
+%
+}
+{
+\oracle{$\HashOracle(q_y)$}\\
+$c \gets c + 1$\\
+$v_j \getsr [m]$\\
+for $j \in \{1,2,\ldots,k\}$\\
+\nudge if $T[j,x] \neq \undefined$\\
+\nudge \nudge $v_j \gets T[j,q_y]$\\
+\nudge $T[j,q_y] \gets h_j$\\
+%
+$M \gets\pubaux$\\
+for $j \in \{1,2,\ldots,k\}$\\
+\nudge if $M[v_j] \neq 1$ then \\
+\nudge \nudge $\Ans[q_y] \gets (0,\err, (v_1, \ldots, v_{k}) )$\\
+\nudge \nudge if $c \in \calI$ then $\bad \gets \true$\\
+\nudge \nudge $\Break$\\
+if $c \notin \calI$ then $\bad \gets \true$\\
+$\err \gets \err +1$\\
+$\Ans[q_y] \gets (0,\err, (v_1, \ldots, v_{k}))$\\
+Ret $\left(v_1,\ldots,v_k\right)$
+}
+}
+\caption{\Cref{thm3}: Game playing argument}\label{fig:3TGame}
+\end{figure}
+
+%The proof of this theorem will follow along the lines of \Cref{thm2}.
+As in previous proofs, we use a game playing argument to prove this theorem as well.
+In $\game{0}$, the $\HashOracle$ does lazy sampling of elements from $[m]$ to mimic a random oracle(RO).
+It can be observed that, $\game{0}$ exactly simulates the BF's correctness game attacked by an adaptive adversary.
+So, $\AdvCorrect{{BF},\distr{\calS}{},r}{A} = \Prob{\game{0}(A) = 1}$.
+%
+%In $\game{1}$, assuming $A$ does not make any pointless queries, $\HashOracle$ is modified to sample random elements from $[m]$.
+In addition, $\Test$ sets $\bad$ to $\true$ if queries indexed by set $\calI$ fail to be FPs, or if any of the remaining queries are FPs.
+$\game{2}$, on the other hand is exactly same as $\game{1}$ except it returns 0, if $\bad$ is set to $\true$.
+It can be easily seen that, $\game{1}$ and $\game{2}$ are exactly same as $\game{2}$ and $\game{3}$ of \Cref{thm2}'s game playing argument.
+So,
+%\begin{align*}
+%\Prob{\game{1}(A)=1} = \Prob{\game{0}(A)=1}\\
+%\Prob{\game{2}(A)=1} = \frac{1}{\dbinom{q}{r}}\Prob{\game{1}(A)=1}
+%\end{align*}
+%\Cref{fig:D} shows non-adaptive adversary, $D$ that finds $r$ FPs against the standard BF. Using a similar explanation from previous proofs,
+%\begin{align*}
+%\AdvCorrect{{BF},\distr{\calS}{},r}{D} &= \Prob{\game{2}(A) = 1}\\
+%\AdvCorrect{{BF},\distr{\calS}{},r}{D} &\leq \left( (1-e^{-kn/m})^k + O(1/n) \right)^r \,.
+%\end{align*}
+%To summarize, we have
+%\[
+%\AdvCorrect{{BF},\distr{\calS}{},r}{A} \leq  {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+%\]
+
 \end{proof}

### 2016-09-07 syntax.tex

@@
 of~$\univ$, and $[[\univ]]^n$ for the set of all multisets
-over~$\univ$ with total multiplicity~$n$. \tsnote{We may not need all
+over~$\univ$ with total multiplicity~$n$. \jnote{I guess we are
+viewing sets as a special case of multisets, so maybe just say
+that.} \tsnote{We may not need all
   of that.} We write $x \getsr \univ$ to denote
-sampling an element from~$\univ$ and assigning this to~$x$, and we
-extend this notation to randomized algorithms.  When~$X$ is a string
-over some alphabet~$\Sigma$, we write $|X|$ for the bitlength
+sampling an element uniformly from~$\univ$ and assigning it to~$x$,
+and we extend this notation to randomized algorithms. When~$X$ is a
+string over some alphabet~$\Sigma$, we write $|X|$ for the bitlength
 of~$X$, relative to some fixed encoding.  When~$X$ is a multiset, we
-overload the notation so that~$|X|$ is the total multiplicity of~$X$.
+overload the notation so that~$|X|$ is the total multiplicity
+of~$X$.
 
-Algorithms may be provided black-box access to one or more oracles, which we write as superscripts, e.g., $F^{O_1,O_2,\ldots}$.  An \emph{adversary} is a randomized algorithm
+Algorithms may be provided black-box access to one or more oracles,
+which we write as superscripts, e.g., $F^{O_1,O_2,\ldots}$.  An \emph{adversary} is a randomized algorithm.
 
@@
 \begin{definition}[Data structure] \rm
-Fix a non-empty set~$\univ$, and a set of multisets~$\calS$ over
-$\univ$. 
-A \emph{data structure} (for $\calS$) is a tuple $\setprim=(\calQ,\Rep, \Qry)$ where:
+Fix a non-empty set~$\univ$, and a collection of (multi)sets~$\calS$
+over $\univ$. A \emph{data structure} (for $\calS$) is a tuple
+$\setprim=(\calQ,\Rep, \Qry)$ where:
 \begin{itemize}
@@
     \times \bits^*$ is a randomized \emph{representation
-    algorithm}, taking as input $S \in \mathcal{S}$, and outputting %a \emph{representation} $M \in \Sigma^*$,
+    algorithm}, taking as input a (multi)set $S \in \mathcal{S}$, and outputting %a \emph{representation} $M \in \Sigma^*$,
     \emph{public representation data} $\pubaux \in \bits^*$ and
@@
     $(\pubaux,\privaux) \getsr \Rep(S)$ as shorthand for this execution.
-\item $\Qry\colon \Sigma^* \times \bits^* \times \bits^* \times \calQ \to
+\item $\Qry\colon \bits^* \times \bits^* \times \calQ \to
     \Gamma$ is a deterministic \emph{query-evaluation}
-    algorithm, taking as input $\pubaux,\privaux \in
-    \bits^*$ and $q \in \calQ$, and outputting
-    an \emph{answer} $a \in \Gamma$.  We write $a \gets
-    \Qry(\pubaux,\privaux,q)$ for this execution.
+    algorithm, taking as input $\pubaux,\privaux \in \bits^*$
+    and a query $q \in \calQ$, and outputting an \emph{answer}
+    $a \in \Gamma$.  We write $a \gets \Qry(\pubaux,\privaux,q)$
+    for this execution.
 \end{itemize}
@@
 \begin{definition}[Error probability and rate] \rm
-Fix a data structure $\setprim=(\calQ,\Rep, \Qry)$. Let $\mathrm{Err}(S,q,\pubaux,\privaux)$ be a predicate that is
-true iff $\Qry(\pubaux,\privaux, q) \neq q(S)$.  Then a data structure
-has \emph{error probability} $\epsilon$ if
-$\max_{S,q}\Pr[(\pubaux,\privaux) \getsr \Rep(S) :
-\mathrm{Err}(S,q,\pubaux,\privaux)=1 ] \leq \epsilon$.
+For a given data structure $\setprim=(\calQ,\Rep, \Qry)$, let
+$\mathrm{Err}(S,q,\pubaux,\privaux)$ be a predicate that is true iff
+$\Qry(\pubaux,\privaux, q) \neq q(S)$.  Then $\Pi$ has \emph{error
+probability} $\epsilon$ if $\max_{S,q}\Pr[(\pubaux,\privaux) \getsr
+\Rep(S) : \mathrm{Err}(S,q,\pubaux,\privaux)=1 ] \leq \epsilon$.
 %
@@
 
-\noindent The definition can be lifted to the random-oracle model by
-giving $\Rep, \Qry$ access to a random oracle. In that case, the
-probabilities defining the error probability and error rate are also
-taken over choice of the random oracle.
+\noindent The definitions above can be lifted to the random-oracle
+model by giving $\Rep, \Qry$ access to a random oracle. In that
+case, the probabilities defining the error probability and error
+rate are also taken over choice of the random oracle.
 
@@
 
+We note that, while our error probability and error rate do not
+distinguish among ``types'' of errors, they also do not preclude
+instantiations (like the classical Bloom filter) that admit only one
+type of error, e.g., false positives.
+
 \def\bin{{\sf Bin}}
-\heading{``Trivial'' attacks, and error probability vs.\ error rate. }
-Let~$\Pi$ be a scheme that is $(1-\epsilon)$-correct, and consider
-an attack that asks random queries $q_1,q_2,\ldots,q_T$, i.e.,
-uniform samples from~$\calQ$.
-Let $\mathrm{Err}_i$ be a random variable indicating the event $\Qry(\pubaux,\privaux,q_i)\neq q_i(S)$.
-The $(1-\epsilon)$-correctness of~$\Pi$ guarantees that the probability that $\mathrm{Err}_i=1$ is at most~$\epsilon$,
-and it is tempting to model the~$\mathrm{Err}_i$ as i.i.d. Bernoulli trials with success probability~$\epsilon$.
-However, a moment's reflection shows that this is not the case.
-Concretely, consider the following scheme.
-Fix $|S|=n$ for all $S \in \calS$, where $n \ll |\univ|$.
-For the queries, let $\calQ = \{q_x\colon \calS \to \bits \,|\, \forall x \in \univ\}$ where $\forall S \in \calS$ the predicate $q_x(S)=1 \Leftrightarrow x \in S$.
-Let $\Rep(S)$ pick a random element~$s \in S$, and return $M = S \setminus \{s\}$ and $\privaux = \emptystring$.
-To respond to queries, let~$\Qry(\pubaux,\privaux,q_x)=1$ iff $x \in M$.
-It is easy to see that this scheme is $1/n$-correct; for any fixed~$S$, there are exactly~$n$ queries~$q_x$ that have probability~$1/n$  (over the coins of~$\Rep$) of causing a correctness error, and the remaining $|\univ|-n$ queries have probability zero of causing an error.
-Moreover, once the coins of~$\Rep$ are fixed, there is exactly \emph{one} query that will cause an error.
-Thus for random queries from~$Q$, for all~$i\in[T]$ we have $\Prob{\mathrm{Err}_i=1}=1/|\univ| \ll 1/n = \epsilon$.
+\heading{``Trivial'' attacks, and error probability vs.\ error
+rate.} \jnote{Not sure this belongs here. I'd rather move any
+discussion of ``attacks'' (trivial or not) to later. But if we just
+want to highlight the difference between error and error rate we
+could do that here.} Let~$\Pi$ be a scheme that is
+$(1-\epsilon)$-correct, and consider an attack that asks random
+queries $q_1,q_2,\ldots,q_T$, i.e., uniform samples from~$\calQ$.
+Let $\mathrm{Err}_i$ be a random variable indicating the event
+$\Qry(\pubaux,\privaux,q_i)\neq q_i(S)$. The
+$(1-\epsilon)$-correctness of~$\Pi$ guarantees that the probability
+that $\mathrm{Err}_i=1$ is at most~$\epsilon$, and it is tempting to
+model the~$\mathrm{Err}_i$ as i.i.d. Bernoulli trials with success
+probability~$\epsilon$. However, a moment's reflection shows that
+this is not the case.  Concretely, consider the following scheme.
+Fix $|S|=n$ for all $S \in \calS$, where $n \ll |\univ|$. For the
+queries, let $\calQ = \{q_x\colon \calS \to \bits \,|\, \forall x
+\in \univ\}$ where $\forall S \in \calS$ the predicate $q_x(S)=1
+\Leftrightarrow x \in S$.  Let $\Rep(S)$ pick a random element~$s
+\in S$, and return $M = S \setminus \{s\}$ and $\privaux =
+\emptystring$.  To respond to queries,
+let~$\Qry(\pubaux,\privaux,q_x)=1$ iff $x \in M$.  It is easy to see
+that this scheme is $1/n$-correct; for any fixed~$S$, there are
+exactly~$n$ queries~$q_x$ that have probability~$1/n$  (over the
+coins of~$\Rep$) of causing a correctness error, and the remaining
+$|\univ|-n$ queries have probability zero of causing an error.
+Moreover, once the coins of~$\Rep$ are fixed, there is exactly
+\emph{one} query that will cause an error.  Thus for random queries
+from~$Q$, for all~$i\in[T]$ we have
+$\Prob{\mathrm{Err}_i=1}=1/|\univ| \ll 1/n = \epsilon$.
 
@@
 
-\heading{Data Structures for Set-Multiplicity Queries. } Our particular focus
-will be on data structures that support multiplicity queries, of
-which set-membership queries are a special case.
-\begin{definition} A \emph{set-multiplicity data structure} is a data
-structure with $\Gamma=\mathbb{N}$ and
-where $\calQ=\{q_x \,|\, x \in \univ\}$ where $q_x(S)$ is defined to
-be the multiplicity of~$x$ in the multiset~$S$. \hfill\dqed
+\heading{Data structures for set-multiplicity queries.} Our
+particular focus will be on data structures that support
+multiplicity queries, of which set-membership queries are a special
+case.
+\begin{definition} \rm
+A \emph{set-multiplicity data structure} is a data structure with
+$\Gamma=\mathbb{N}$ and $\calQ=\{q_x\}_{x \in \univ}$, where
+$q_x(S)$ is defined to be the multiplicity of~$x$ in the
+multiset~$S$. \hfill\dqed
 \end{definition}
 
-It is not hard to see Bloom filters are an instantiation of a
-set-multiplicity data structure.  Fix $\Sigma=\Gamma=\bits$.  Define
-algorithm~$\Rep$, with functions $k=k(|S|), m=m(|S|)$ and a
-description of a hash function family~$\mathcal{H}=\{h \colon \univ
-\to \{1,2,\ldots,m\}\}$ hardwired into it, to sample hash functions
-$h_1, \ldots, h_k$ from~$\mathcal{H}$ and then compute an $m$-bit
-array~$M$ (intialized to 0 everywhere) by setting $M[h_i(x)]=1$ for
-all $i\in [k]$ and $x \in S$.  Finally, $\Rep$ returns
-$\privaux=\emptystring$ and $\pubaux = M$ as the
+We illustrate our notation by casting Bloom filters as a particular
+example of a set-multiplicity data structure. \jnote{Only handles
+sets, not multisets.} Let $\Gamma=\bits$, and fix functions
+$k(\cdot)$ and $m(\cdot)$ parameterizing the scheme. Algorithm
+$\Rep$, on input a set~$S$, computes $k=k(|S|)$ and $m=m(|S|)$ and
+then chooses $k$ functions $h_1, \ldots, h_k \in \mathcal{H}$ for
+some function family $\mathcal{H}=\{h \colon \univ \to
+\{1,2,\ldots,m\}\}$. \jnote{Note depends on $m$. It might be easier
+(especially since we talk about error) to already let the hash
+functions be independent random oracles.} It then computes an
+$m$-bit array~$M$ (initialized to 0 everywhere) by setting
+$M[h_i(x)]=1$ for all $i\in [k]$ and $x \in S$.  Finally, $\Rep$
+returns $\privaux=\emptystring$ and $\pubaux = M$ as the
 representation.
 %
-The algorithm~$\Qry$ is defined so that, on input $(\pubaux,\privaux,q_x)$, it
-returns the minimum of the values $M[h_1(x)],\ldots,M[h_k(x)]$.  We note that, while our error
-probability and error rate do not distinguish among ``types'' of
-errors, they also do not preclude instantiations (like the classical
-Bloom filter) that admit only one type of error, e.g.
-false-positives.
+Algorithm~$\Qry$ is defined so that, on input
+$(\pubaux,\privaux,q_x)$, it returns the minimum of the values
+$M[h_1(x)],\ldots,M[h_k(x)]$. \jnote{How does $\Qry$ know the hash
+functions?}
 
-As a simple extension, consider $\Sigma=\mathbb{N}$ and modify the
-basic Bloom filter so that it stores counters, rather than
-bits, at each position in an array.  In particular, for each~$x \in
-S$ the $\Rep$~algorithm increments the counters stored at positions
+As a simple extension, consider $\Gamma=\mathbb{N}$ and modify the
+basic Bloom filter so that it stores counters, rather than bits, at
+each position in an array.  In particular, for each~$x \in S$ the
+$\Rep$~algorithm increments the counters stored at positions
 $h_1(x), h_2(x), \ldots, h_k(x)$, returns the final array of
@@
 
-By setting $\Sigma=\bits^L$ for a specified $L>0$, we capture the
-so-called ``garbled Bloom filter'' due to Dong, Chen and
-Wen~\cite{xxx}.  This stores xor-shares of bitstring~$x \in S$ at
-positions $h_1(x),h_2(x),\ldots,h_k(x)$ in an array.  Similarly, the
-cuckoo-hashing construction from NY, which (loosely speaking) stores a
-hash $g(x)$ at positions determined by $h_1(x),h_2(x),\ldots,h_k(x)$,
-is captured when $L=|g(x)|$. \tsnote{Check the correctness of this claim.}
+By setting $\Sigma=\bits^L$ for a specified $L>0$, we can capture
+the so-called ``garbled Bloom filter'' due to Dong, Chen and
+Wen~\cite{xxx}. \jnote{Details have to be filled in.} This stores
+xor-shares of bitstring~$x \in S$ at positions
+$h_1(x),h_2(x),\ldots,h_k(x)$ in an array. Similarly, the
+cuckoo-hashing construction from NY, which (loosely speaking) stores
+a hash $g(x)$ at positions determined by
+$h_1(x),h_2(x),\ldots,h_k(x)$, is captured when $L=|g(x)|$.
+\tsnote{Check the correctness of this claim.}

### 2016-09-07 notions.tex
Theorems comparing our definition to NY definition

--- 2016-09-07 notions.tex
@@
 all~$t$-time adversaries that ask at most~$q$ queries. We say that a
-set-representation data structure~$\Pi$ is $(t,q,r,\epsilon')$-correct if $\AdvCorrect{\Pi,\distr{}{},r}{t,q} \leq \epsilon'$.
+set-representation data structure~$\Pi$ is $(t,q,r,\epsilon)$-correct if $\AdvCorrect{\Pi,\distr{}{},r}{t,q} \leq \epsilon$.
 \jnote{Note~$q$ is overloaded here.}
@@
 all~$t$-time adversaries that ask at most~$q$ queries. We say that a
-set-representation data structure~$\Pi$ is $(t,q,\epsilon')$-NY-correct if
-$\NYAdvCorrect{\Pi,\distr{}{}}{t,q} \leq \epsilon'$. \jnote{This should all probably
+set-representation data structure~$\Pi$ is $(t,q,\epsilon)$-NY-correct if
+$\NYAdvCorrect{\Pi,\distr{}{}}{t,q} \leq \epsilon$. \jnote{This should all probably
 move to an appendix; it's a lot of notation to digest for something we never use again
@@
 
-\jnote{There's something ``morally wrong'' with the follow theorem statement:
-if we increase $q$ then the assumption about the NY-correctness of $\Pi$ (presumably)
-gets stronger---even if formally that is not true---but the conclusion of the theorem
-becomes weaker.}
+\jnote{Do we have a compelling example of why the definition in Figure~\ref{fig:correctness}
+is ``better'' than the definition in Figure~\ref{fig:NYcorrectness}?}
 
 \begin{theorem}
-If $\Pi$ is $(t,q,\epsilon')$-NY-correct, then it is also
-$(t, q', r, q'\epsilon'/r)$-correct for any $q' \leq q+1$ and $r\geq 1$.
+If $\Pi$ is $(t,q,\epsilon)$-NY-correct, then it is also
+$(t, q', r, q'\epsilon/r)$-correct for any $q' \leq q+1$ and $r\geq 1$.
 \end{theorem}
 \begin{proof}
-Let $\Pi$ be a set-representation data structure that is $(t,q,\epsilon')$-NY-correct,
-and assume that for some $q' \leq q+1$ and $r \geq 1$
+Let $\Pi$ be a set-representation data structure that is $(t,q,\epsilon)$-NY-correct,
+and assume that for some distribution $\distr{}{}$, some $q' \leq q+1$, and
+some $r \geq 1$
 there is an adversary $A$ running in time~$t$
-and making $q'$ oracle queries (note that without loss of generality
-we may assume $A$ always makes exactly $q'$ queries) such that
-$\AdvCorrect{\Pi,\distr{}{},r}{A} > q'\epsilon'/r$.
+and making $q'$ oracle queries such that
+$\AdvCorrect{\Pi,\distr{}{},r}{A} > q'\epsilon/r$.
+(Note that
+we may assume $A$ always makes exactly $q'$ queries without loss of generality.)
 With probability at least
-$q'\epsilon'/r$ in an execution of $\ExpCorrect{\Pi,\distr{}{},r}{A}$, we have that
+$q'\epsilon/r$ in an execution of $\ExpCorrect{\Pi,\distr{}{},r}{A}$, we have that
 $A$ makes at least $r$ distinct queries to $\TestOracle$ for which
@@
 uniformly one of the $q'$ queries of $A$ to its $\TestOracle$ oracle and outputs that query
-as its final output. Then with probability at least $r/q' \cdot (q'\epsilon'/r)=\epsilon'$
+as its final output. Then with probability at least $r/q' \cdot (q'\epsilon/r)=\epsilon$
 the query chosen by $A'$
@@
 
-\jnote{It is unclear whether the above is tight, but it is also unclear whether
-that is something worth thinking about. }
+\jnote{The above is tight, at least for $r=1$. Specifically, consider a scheme
+in which every query is independently
+answered incorrectly with probability~$\epsilon$. Such a
+scheme will be $(t,q,\epsilon)$-NY-correct
+for any $t, q$, however an adversary making $q=1/\epsilon$ queries has constant advantage
+under our correctness definition (for $r=1$).}
 
-\begin{enumerate}
-\item Say a scheme is $\epsilon_{NY}$-secure under the NY definition.
-Then we claim it is $(t,q, r, q\epsilon_{NY}/r)$-correct. To see
-this, assume not. Then there is a $t$-time attacker~$A$ that, with
-probability at least $\epsilon'=q\epsilon_{NY}/r$,
-issues~$q$ Test-queries of which at least~$r$ cause errors.
-If we simply run~$A$ and then choose a random Test-query to
-output, we succeed with probability at least $\epsilon' \cdot r/q$.
-It is unclear whether this is tight.
+\begin{theorem}
+If $\Pi$ is $(t, q, 1, \epsilon)$-correct, then it is also $(t, q-1, \epsilon)$-NY-correct.
+\end{theorem}
+\begin{proof}
+Let $\Pi$ be a set-representation data structure that is $(t,q,1,\epsilon)$-correct,
+and assume that for some distribution $\distr{}{}$
+there is an adversary $A$ running in time~$t$
+and making at most $q-1$ oracle queries such that
+$\NYAdvCorrect{\Pi,\distr{}{}}{A} > \epsilon$.
+Let $A'$ be the algorithm that simply
+runs~$A$, passing the oracle queries of $A$ to its own oracle, until $A$ terminates
+with output~$q$; then, $A'$ sends $q$ to $\TestOracle$. \jnote{$q$ is (still)
+overloaded!} It is immediate that $A'$ makes at most $q$ oracle queries, and
+$\AdvCorrect{\Pi,\distr{}{},1}{A'} \geq \NYAdvCorrect{\Pi,\distr{}{}}{A}$, a contradiction.
+\end{proof}
 
-\item There is a contrived scheme that is $(t, q, 2, 0)$-correct but not NY-secure at all; the basic idea is
-to have a set-representation that always has \emph{exactly one} false positive that is easy to find
-given the public information.
+\begin{theorem}
+There exists a set-representation data structure $\Pi$ that
+is $(t, q, 2, 0)$-correct, but is not $(t, 0, \epsilon)$-NY-correct
+for any $\epsilon<1$.
+\end{theorem}
+\begin{proof}
+We prove the theorem for set-membership data structures.
+Let $x \in {\cal X}$ be an arbitrary element of the universe, and
+let $\Pi$ be the data structure in which $\Rep(S)$ outputs $\pubaux=\privaux=S$, and
+$\Qry(S, S, q_y)$ outputs $q_y(S)$ if $y \neq x$ but outputs $1-q_x(S)$ otherwise. This
+scheme always answers incorrectly for a single, fixed query, and answers
+correctly for every other query. The theorem follows.
+\end{proof}
 
-\item If a scheme is $(t,q,1,\epsilon)$-correct, then it is also $\epsilon$-secure under the NY definition,
-at least for attackers making at most $q-1$ queries.
-This is immediate.
-\end{enumerate}
+\jnote{I'm not sure what to conclude from any of the results above. The proofs
+are also all trivial.}
+
 \jnote{Case of $r=1$ does not necessarily imply anything for $r>1$: can have a scheme
 where finding the first false positive is hard but then the rest are easy; can have
-a scheme where finding one false positive is easy but there do not exist
-any more false positives.}
+a scheme where finding one false positive is easy finding more is hard (e.g.,
+because there do not exist
+any more).}
 

### 2016-09-07 notions.tex
no message

@@
 %the adversary's resources for computing $q(S)$.}
+
+\jnote{Case of $r=1$ does not necessarily imply anything for $r>1$: can have a scheme
+where finding the first false positive is hard but then the rest are easy; can have
+a scheme where finding one false positive is easy finding more is hard (e.g.,
+because there do not exist
+any more).}
 
@@
 
-\jnote{Case of $r=1$ does not necessarily imply anything for $r>1$: can have a scheme
-where finding the first false positive is hard but then the rest are easy; can have
-a scheme where finding one false positive is easy finding more is hard (e.g.,
-because there do not exist
-any more).}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 Define one-wayness.}
+
+In this section we specialize to the case of set-membership data structures, and
+focus on sets rather than multisets.
+Before continuing, it will be useful to define a notion of ``point-wise min-entropy.''
+Let ${\cal D}$ be
+a distribution on sets over some universe ${\cal X}$. Then the \emph{point-wise
+min-entropy} of ${\cal D}$ is defined as
+\[H_\infty({\cal D}) \bydef -\log \max_{x \in {\cal X}} \Pr[S \getsr {\cal D} : x \in S].\]
 

### 2016-09-07 syntax.tex
updates to syntax.tex

@@
 
-\noindent The definitions above can be lifted to the random-oracle
+%We will sometimes say that a data structure is
+%$(1-\epsilon)$-correct, meaning it has error probability~$\epsilon$.
+%Note that $1-\epsilon$ is a worst-case lower bound on the
+%correctness of the data structure. \tsnote{Don't know if this will be necessary.}
+
+These definitions, and those that follow, can be lifted to the random-oracle
 model by giving $\Rep, \Qry$ access to a random oracle. In that
@@
 rate are also taken over choice of the random oracle.
-
-We will sometimes say that a data structure is
-$(1-\epsilon)$-correct, meaning it has error probability~$\epsilon$.
-Note that $1-\epsilon$ is a worst-case lower bound on the
-correctness of the data structure. \tsnote{Don't know if this will be necessary.}
 
@@
 \def\bin{{\sf Bin}}
-\heading{``Trivial'' attacks, and error probability vs.\ error
-rate.} \jnote{Not sure this belongs here. I'd rather move any
-discussion of ``attacks'' (trivial or not) to later. But if we just
-want to highlight the difference between error and error rate we
-could do that here.} Let~$\Pi$ be a scheme that is
-$(1-\epsilon)$-correct, and consider an attack that asks random
+\heading{Error probability vs.\ error rate. }
+We pause to highlight an important
+difference between error probability and error rate.  In particular,
+the error probability~$\epsilon$ is measured only over the coins
+of~$\Rep$, for a fixed~$S$ and query~$q$. Once the coins of~$\Rep$
+are fixed, it is not straightforward how to connect~$\epsilon$ to
+events that depend on other sources of randomness.   We illustrate how
+this surfaces with the following example.
+
+Let~$\Pi$ be a data structure that has error-probability $\epsilon$,
+and consider a correctness-violating attack that asks random
 queries $q_1,q_2,\ldots,q_T$, i.e., uniform samples from~$\calQ$.
 Let $\mathrm{Err}_i$ be a random variable indicating the event
-$\Qry(\pubaux,\privaux,q_i)\neq q_i(S)$. The
-$(1-\epsilon)$-correctness of~$\Pi$ guarantees that the probability
+$\Qry(\pubaux,\privaux,q_i)\neq q_i(S)$.  We know that the probability
 that $\mathrm{Err}_i=1$ is at most~$\epsilon$, and it is tempting to
@@
 
-This example is contrived, but it highlights the important
-difference between error probability and error rate.  In particular,
-the error probability~$\epsilon$ is measured only over the coins
-of~$\Rep$, for a fixed~$S$ and query~$q$. Once the coins of~$\Rep$
-are fixed, it is not straightforward how to connect~$\epsilon$ to
-events that depend on other sources of randomness. \tsnote{Not sure
-if there's more to say in this section.}
-
 \heading{Data structures for set-multiplicity queries.} Our
 particular focus will be on data structures that support
-multiplicity queries, of which set-membership queries are a special
-case.
+multiplicity queries.
+
 \begin{definition} \rm
@@
 
-We illustrate our notation by casting Bloom filters as a particular
-example of a set-multiplicity data structure. \jnote{Only handles
-sets, not multisets.} Let $\Gamma=\bits$, and fix functions
+The classical Bloom filter is a special case of a set-multiplicity
+data structure, as set-membership query is a type of
+set-multiplicity query.  Specifically, 
+%\jnote{Only handles sets, not multisets.} 
+let $\Gamma=\bits$, and fix functions
 $k(\cdot)$ and $m(\cdot)$ parameterizing the scheme. Algorithm
@@
 (especially since we talk about error) to already let the hash
-functions be independent random oracles.} It then computes an
-$m$-bit array~$M$ (initialized to 0 everywhere) by setting
+functions be independent random oracles.} \tsnote{I don't see the
+problem.  $\Rep$ knows~$m$, so any function (whose range admits at
+least~$m$ values) can be effectively treated as having range~$[m]$.
+But I added a sentence at the end of this paragraph, too.  See if that
+helps.} 
+It then computes an $m$-bit array~$M$ (initialized to 0 everywhere) by setting
 $M[h_i(x)]=1$ for all $i\in [k]$ and $x \in S$.  Finally, $\Rep$
-returns $\privaux=\emptystring$ and $\pubaux = M$ as the
+returns $\privaux=\emptystring$ and $\pubaux = \langle M,h_1,h_2,\ldots,h_k\rangle$ as the
 representation.
@@
 $(\pubaux,\privaux,q_x)$, it returns the minimum of the values
-$M[h_1(x)],\ldots,M[h_k(x)]$. \jnote{How does $\Qry$ know the hash
-functions?}
+$M[h_1(x)],\ldots,M[h_k(x)]$.  We note that the standard Bloom filter
+analysis treats $h_1,h_2,\ldots,h_k$ as independent random functions,
+which we may capture in the ROM with some simple adjustments to the above.
 
 As a simple extension, consider $\Gamma=\mathbb{N}$ and modify the
-basic Bloom filter so that it stores counters, rather than bits, at
+classical Bloom filter so that it stores counters, rather than bits, at
 each position in an array.  In particular, for each~$x \in S$ the
@@
 count-min sketches~\cite{xxx}, scalable Bloom filters~\cite{xxx},
-etc., in a later section.\tsnote{If we ultimately do!}
+etc., in future work.\tsnote{?}
 
@@
 $h_1(x),h_2(x),\ldots,h_k(x)$, is captured when $L=|g(x)|$.
-\tsnote{Check the correctness of this claim.}
+\todo{Check the correctness of this claim.}

### 2016-09-07 notions.tex
beginning to address JK's comments in notions.tex

@@
 $\Rep(S)$ is run to generate $(\pubaux,\privaux)$. \jnote{I thought we were going to let
-the adversary choose~$S$?} \jnote{If instead we choose $S$ from ${\cal D}$, then
-is it clear we want to give $S$ to~$A$?}
+the adversary choose~$S$?} \tsnote{Email discussion.} \jnote{If instead we choose $S$ from ${\cal D}$, then
+is it clear we want to give $S$ to~$A$?} \tsnote{For \emph{correctness},
+yes, if for no other reason than to allow~$A$ to know when it asking
+a pointless query.  But also it will make no difference to the
+provable correctness of the constructions we consider.}
 %(Unless stated otherwise, we assume security holds for all distributions and thus for all sets $S$.)
@@
 may as well have the attacker query $x$ which gets translated to query $q_x$. If
-we are trying to be more general then we should be consistent.} \jnote{Why does $A$ output
-anything at all?}
+we are trying to be more general then we should be consistent.}
+\tsnote{I don't see how this correctness notion is specialized to
+  set-multiplicity data structures.  I don't think we actually
+  specialize notions in any way until, maybe, the OW privacy notion.
+  It is true that we only deliver concrete results for set-multiplicty
+data structures, however.}\jnote{Why does $A$ output
+anything at all?}\tsnote{To signify it is finished execution.  Matter
+of taste, I'm not hardover about it.}
 
@@
 than $(a,\mathrm{err})$. Note that the latter can be computed from the former,
-and in the general case I think the former is what we want.} \jnote{I also changed
-the definition so the adversary has to find $r$ {\bf unique} inputs on which
-there is an error.}
+and in the general case I think the former is what we
+want.}\tsnote{This may have implications for the efficiency of
+reductions, I'm not sure. The reason I introduced the $\mathrm{err}$
+counter and returned this was to avoid~$A$ be forced to evalutate
+queries of unknown computational cost.} 
+%\jnote{I also changedthe definition so the adversary has to find $r$
+% {\bf unique} inputs on which there is an error.}
 
@@
 $S \getsr \distr{}{}$\\
-$\mathcal{Q} \gets \emptyset$ \\
-$\mathrm{err}\gets 0$\\
+$\mathcal{C} \gets \emptyset$; $\mathrm{err}\gets 0$\\
 $(\pubaux,\privaux) \getsr \Rep(S)$\\
@@
 \oracle{$\TestOracle(q)$}\\
+if $q \in \mathcal{C}$ then Return $\bot$\\
 $a \gets \Qry(\pubaux,\privaux,q)$\\
-if ($a \neq q(S)$ and $q \not \in \mathcal{Q}$) then \\
+if $a \neq q(S)$ then \\
 \nudge $\mathrm{err}\gets\mathrm{err}+1$\\
-$\mathcal{Q} \gets \mathcal{Q} \cup \{q\}$ \\
+$\mathcal{C} \gets \mathcal{C} \cup \{q\}$ \\
 Return~$(a,q(S))$
@@
 
+\newcommand{\leak}{{\sf leak}}
 \subsection{Privacy}

### 2016-09-07 notions.tex
cheers

@@
 $\Rep(S)$ is run to generate $(\pubaux,\privaux)$. \jnote{I thought we were going to let
-the adversary choose~$S$?} \tsnote{Email discussion.} \jnote{If instead we choose $S$ from ${\cal D}$, then
+the adversary choose~$S$?} \tsnote{Email discussion. At this point,
+I'm happy just making~$S$ part of the experiment ``name'', the
+way~$\distr{}{}$ is now.  The distribution seems not to matter for
+correctness, at least for the schemes we consdier.} \jnote{If instead we choose $S$ from ${\cal D}$, then
 is it clear we want to give $S$ to~$A$?} \tsnote{For \emph{correctness},
@@
 set-representation data structure~$\Pi$ is $(t,q,r,\epsilon)$-correct if $\AdvCorrect{\Pi,\distr{}{},r}{t,q} \leq \epsilon$.
-\jnote{Note~$q$ is overloaded here.}
+\jnote{Note~$q$ is overloaded here.}\tsnote{True, and do we even need
+  it, other than for making a compact statements of comparison with
+  NY?  Why not just have explict advantage bounding statements, as we
+  do for our other results, relating our notion to NY's?  (And,
+  probably, moving all of that to an appendix, as you later suggest.)}
 %\jnote{Note that test includes err because we don't want to penalize
@@
 
-\jnote{Case of $r=1$ does not necessarily imply anything for $r>1$: can have a scheme
+\todo{Explain that the case of $r=1$ does not necessarily imply anything for $r>1$: can have a scheme
 where finding the first false positive is hard but then the rest are easy; can have
@@
 the number of queries the attacker makes can decrease its advantage! This seems like
-another drawback of the definition.}
+another drawback of the definition.}\tsnote{Really?  That seems worth
+pointing out, as part of our list of complaints.}
 
@@
 {
-\experimentv{$\ExpCorrect{\setprim,\distr{}{}}{A}$}\\
+\experimentv{$\NYExpCorrect{\setprim,\distr{}{}}{A}$}\\
 $S \getsr \distr{}{}$\\
-$\mathcal{Q} \gets \emptyset$\\
+$\mathcal{C} \gets \emptyset$\\
 %$\mathrm{err}\gets 0$\\
@@
 $a \gets \Qry(\pubaux,\privaux,q)$\\
-$\mathcal{Q} \gets \mathcal{Q} \cup \{q\}$ \\
+$\mathcal{C} \gets \mathcal{C} \cup \{q\}$ \\
 %\nudge $\mathrm{err}\gets\mathrm{err}+1$\\
@@
 \jnote{Do we have a compelling example of why the definition in Figure~\ref{fig:correctness}
-is ``better'' than the definition in Figure~\ref{fig:NYcorrectness}?}
+is ``better'' than the definition in
+Figure~\ref{fig:NYcorrectness}?}\tsnote{I don't know, but we do seem
+to have a compelling list of shortcomings of their notion, which ours
+doesn't seem to suffer. Anyway, it's a bit of an unfair comparison, in
+their favor.  You're lifting their notion to ours, which is more
+general.  And by the time we get to that, we have already done them
+the favor of cleaning up the syntax, so that their ``lifted'' notion
+looks better than it was.}
 
@@
 If $\Pi$ is $(t,q,\epsilon)$-NY-correct, then it is also
-$(t, q', r, q'\epsilon/r)$-correct for any $q' \leq q+1$ and $r\geq 1$.
+$(t, q', r, q'\epsilon/r)$-correct for any $q' \leq q+1$ and $r\geq
+1$.
+\tsnote{this could easily be written, albeit less compactly, without
+introducing the resource-parameterized notation; likewise the others.}
 \end{theorem}
@@
 \end{theorem}
+
 \begin{proof}
@@
 \jnote{I'm not sure what to conclude from any of the results above. The proofs
-are also all trivial.}
+are also all trivial.} \tsnote{Trivial or not, it's all part of the
+overall contribution, which is putting this topic on a solid
+foundation.  We can move it all to an appendix, but I still see it as
+very worthwhile.}
 
@@
 
-\jnote{OK, from here on I specialize to set-representation data structures\ldots}
+\jnote{OK, from here on I specialize to set-representation data
+  structures\ldots} \tsnote{I don't understand this comment.  That's
+  what our syntax supports anyway, so how is this specializing?}
 

### 2016-09-07 results.tex
starting to typeset ss proof for domain-separated PRF construction
cheers

@@
 \[
-\AdvCorrect{\Pi_{\mathrm{lin}},\distr{\calS}{},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\AdvCorrect{\Pi_{\mathrm{lin}},\distr{}{},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
 \]
@@
 As with the preceding theorem, the following says (informally) that if~$F$ is a secure PRF, then this domain-separated PRF construction is correct against adaptive adversaries.
+We note that Neidermayer et al.
+in~\cite{xxx} suggest replacing the linear-PRF hash functions in the previous construction with independently keyed PRFs as a way to thwart their attacks.
+The construction we consider now achieves the same end, albeit via explict domain separation rather than separate keys.
 
@@
 \[
-\AdvCorrect{\Pi_{\mathrm{ds}},\distr{\calS}{},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\AdvCorrect{\Pi_{\mathrm{ds}},\distr{}{},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
 \]
@@
 \end{theorem}
+
+%%%%%%%%%%
+\input{ds-ss-proof}
+%%%%%%%%%%
 

### 2016-09-07 results.tex
cheers

@@
 %%%%%%%%%%
-\input{ds-ss-proof}
+\begin{theorem}
+Fix $k,m,n>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
+For any set~$S$, let $\leak(S)=|S|$.
+There exists a simulator~$\Sim$ such that, for any adversary~$A$
+\[
+\AdvPrivSS{\Pi_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
+\]
+where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.) 
+\end{theorem}
+\begin{proof}[Proof (sketch). ]
+Adversary~$B^{f}$ simulates the steps of $\ExpPrivSSreal{\Pi_{\mathrm{ds}}}{A}$, using its oracle to simuate~$\Rep(S)$.
+When~$f=F_K$ then the simulation is perfect.
+When~$f=\rho$ then~$B$ simulates $\ExpPrivSSreal{\overline{\Pi}_{\mathrm{ds}}}{A}$ where $\overline{\Rep}$ effectively uses~$k$ independent random functions as the hash functions.
+But the $\pub$ produced by $\overline{\Rep}$ has a distribution that depends only~$|S|=n$, not the specific elements of~$S$, and the other public parameters~$m,k$.
+Thus, a simulator~$\Sim$ given only $\leak(S)=|S|$ can produce a correct~$\pub$ as follows: starting with an all-zeros array~$M$ of length~$m$, uniformly sample (with replacement)~$nk$ integers in~$[m]$ and set the resulting positions of~$M$ to 1.
+\end{proof}
 %%%%%%%%%%

### 2016-09-07 results.tex
cheers

@@
 \include{scheme-descriptions}
+
+%%%%%%%%%%%%%%%%% LINEAR-PRF %%%%%%%%%%%%%%%%%%%%
 
@@
 
-\begin{theorem}\label{thm1}
+\begin{theorem}\label{thm1}\label{thm:lin-correctness}
 Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{lin}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
@@
 \end{theorem}
-Before giving the proof, we note that Kirsch and Mitzenmacher~\cite{xxx} show
+The proof appears in Appendix~\ref{app:xxx}.  We note that Kirsch and Mitzenmacher~\cite{xxx} show
 that the ($r=1$, zero-query) FP-probability for~$\Pi_\mathrm{lin}$ is
@@
 
+\begin{theorem}\label{thm:lin-ss}
+Fix $k,m,n>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
+For any set~$S$, let $\leak(S)=|S|$.
+There exists a simulator~$\Sim$ such that, for any adversary~$A$
+\[
+\AdvPrivSS{\Pi_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B} + \mbox{[TBD]}
+\]
+where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.) 
+\end{theorem}
+\begin{proof}[Proof (sketch). ]
+\end{proof}
+
+%%%%%%%%%%%%%%%%% DOMAIN-SEPARATED PRF %%%%%%%%%%%%%%%%%%%%
+
 \heading{Construction of PRF with domain separation.}
@@
 
-\begin{theorem}\label{thm2}
+\begin{theorem}\label{thm2}\label{thm:ds-correctness}
 Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure in Figure~\ref{fig:lin-and-ds}.
@@
 %%%%%%%%%%
-\begin{theorem}
+\begin{theorem}\label{thm:ds-ss}
 Fix $k,m,n>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.

### 2016-09-07 notions.tex
comments on the comments

@@
 way~$\distr{}{}$ is now.  The distribution seems not to matter for
-correctness, at least for the schemes we consdier.} \jnote{If instead we choose $S$ from ${\cal D}$, then
+correctness, at least for the schemes we consider.} \jnote{If instead we choose $S$ from ${\cal D}$, then
 is it clear we want to give $S$ to~$A$?} \tsnote{For \emph{correctness},
@@
 provable correctness of the constructions we consider.}
+\jnote{OK, I think I would just change the definitions so that the attacker
+chooses $S$.}
 %(Unless stated otherwise, we assume security holds for all distributions and thus for all sets $S$.)
@@
   It is true that we only deliver concrete results for set-multiplicty
-data structures, however.}\jnote{Why does $A$ output
-anything at all?}\tsnote{To signify it is finished execution.  Matter
-of taste, I'm not hardover about it.}
+data structures, however.}
 
@@
 reductions, I'm not sure. The reason I introduced the $\mathrm{err}$
-counter and returned this was to avoid~$A$ be forced to evalutate
-queries of unknown computational cost.} 
-%\jnote{I also changedthe definition so the adversary has to find $r$
-% {\bf unique} inputs on which there is an error.}
+counter and returned this was to avoid~$A$ be forced to evaluate
+queries of unknown computational cost.} \jnote{Not sure what you mean. If the
+oracle returns $q(S)$ then $A$ doesn't have to evaluate it. All $A$ has to do
+is an equality check to see if $a=q(S)$ or not.}
 
@@
   it, other than for making a compact statements of comparison with
-  NY?  Why not just have explict advantage bounding statements, as we
+  NY?  Why not just have explicit advantage bounding statements, as we
   do for our other results, relating our notion to NY's?  (And,
   probably, moving all of that to an appendix, as you later suggest.)}
-%\jnote{Note that test includes err because we don't want to penalize
-%the adversary's resources for computing $q(S)$.}
+\jnote{Not sure what you mean. I was pointing out that we use $q$ both for a particular
+query, as well as for the bound on the number of attacker's queries. Don't we want to
+keep track of the query bound?}
 
@@
 the favor of cleaning up the syntax, so that their ``lifted'' notion
-looks better than it was.}
+looks better than it was.} \jnote{I agree, it's just that once we have ``lifted'' it
+appropriately, it's not clear what's wrong with it and why we introduce a different
+style of definition.}
 
@@
 \tsnote{this could easily be written, albeit less compactly, without
-introducing the resource-parameterized notation; likewise the others.}
+introducing the resource-parameterized notation; likewise the others.} \jnote{How?}
 \end{theorem}
@@
 foundation.  We can move it all to an appendix, but I still see it as
-very worthwhile.}
+very worthwhile.} \jnote{It's worth having for completeness, I'm just not sure
+what we (or the reader) is supposed to do with it. It's not like we can draw
+any simple conclusions like ``our definition implies theirs'' or anything.}
 
@@
 \subsection{Privacy}
-\jnote{Define appropriate notion of min-entropy for our setting.
-Define one-wayness.}
 
@@
 One can also consider the orthogonal notion of \emph{privacy} for a
-data structure. \jnote{I am still hoping that we can treat data structures
-at an even more general level than set-representation data structures.}
+data structure.
 We formalize two types of privacy notions. The first captures
@@
 what is captured in some explicit leakage function.
-
-\jnote{OK, from here on I specialize to set-representation data
-  structures\ldots} \tsnote{I don't understand this comment.  That's
-  what our syntax supports anyway, so how is this specializing?}
 

### 2016-09-07 syntax.tex
beginning to address JK's comments in notions.tex
comments on the comments

@@
 The classical Bloom filter is a special case of a set-multiplicity
-data structure, as set-membership query is a type of
+data structure, as set-membership queries are a type of
 set-multiplicity query.  Specifically,
 %\jnote{Only handles sets, not multisets.}
-let $\Gamma=\bits$, and fix functions
-$k(\cdot)$ and $m(\cdot)$ parameterizing the scheme. Algorithm
-$\Rep$, on input a set~$S$, computes $k=k(|S|)$ and $m=m(|S|)$ and
-then chooses $k$ functions $h_1, \ldots, h_k \in \mathcal{H}$ for
-some function family $\mathcal{H}=\{h \colon \univ \to
-\{1,2,\ldots,m\}\}$. \jnote{Note depends on $m$. It might be easier
-(especially since we talk about error) to already let the hash
-functions be independent random oracles.} \tsnote{I don't see the
-problem.  $\Rep$ knows~$m$, so any function (whose range admits at
-least~$m$ values) can be effectively treated as having range~$[m]$.
-But I added a sentence at the end of this paragraph, too.  See if that
-helps.} 
-It then computes an $m$-bit array~$M$ (initialized to 0 everywhere) by setting
-$M[h_i(x)]=1$ for all $i\in [k]$ and $x \in S$.  Finally, $\Rep$
-returns $\privaux=\emptystring$ and $\pubaux = \langle M,h_1,h_2,\ldots,h_k\rangle$ as the
-representation.
+let $\Gamma=\bits$, and fix functions $k(\cdot)$ and $m(\cdot)$
+parameterizing the scheme. Algorithm $\Rep$, on input a set~$S$,
+computes $k=k(|S|)$ and $m=m(|S|)$ and then chooses $k$ functions
+$h_1, \ldots, h_k \in \mathcal{H}$ for some function family
+$\mathcal{H}=\{h \colon \univ \to \{1,2,\ldots,m\}\}$. \jnote{Note
+depends on $m$. It might be easier (especially since we talk about
+error) to already let the hash functions be independent random
+oracles.} \tsnote{I don't see the problem.  $\Rep$ knows~$m$, so any
+function (whose range admits at least~$m$ values) can be effectively
+treated as having range~$[m]$. But I added a sentence at the end of
+this paragraph, too.  See if that helps.} \jnote{$\Rep$ knows $m$,
+but $m$ can take any value so we need an $\mathcal{H}$ that is
+defined for every possible~$m$.} It then computes an $m$-bit
+array~$M$ (initialized to 0 everywhere) by setting $M[h_i(x)]=1$ for
+all $i\in [k]$ and $x \in S$.  Finally, $\Rep$ returns
+$\privaux=\emptystring$ and $\pubaux = \langle
+M,h_1,h_2,\ldots,h_k\rangle$ as the representation.
 %
@@
 the so-called ``garbled Bloom filter'' due to Dong, Chen and
-Wen~\cite{xxx}. \jnote{Details have to be filled in.} This stores
+Wen~\cite{xxx}. \todo{Details have to be filled in.} This stores
 xor-shares of bitstring~$x \in S$ at positions

### 2016-09-08 Theorem3_FP.tex
Proof3

@@
-\acnote{INCOMPLETE. To be verified before moving the theorem to section 4}
 \heading{Classical Bloom filter in random oracle model (ROM). }
@@
 Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{Bloom}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described.
-For any adversary~$A$ that makes a total of~$q$ queries to the oracle and has time-complexity~$O(t)$, there exist prf-adversaries~$B_1,B_2$ (explicitly constructed in the proof of this theorem) such that
+For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$, then
 \[
-\AdvCorrect{\Pi_{\mathrm{Bloom}},\distr{\calS}{},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\AdvCorrect{\Pi_{\mathrm{Bloom}},\distr{\calS}{},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
 \]
@@
 We use a game playing argument to prove this theorem in the ROM.
-In $\game{0}$, the $\HashOracle$ does lazy sampling of elements from $[m]$ to mimic a random oracle(RO).
+In $\game{0}$, the $\Hash$ does lazy sampling of elements from $[m]$ to mimic a random oracle(RO).
 For every distinct query, $\Hash$ returns a random value sampled from $[m]$.
@@
 
+$\game{1}$ is exactly same as $\game{0}$ except the $\Qry$ oracle is replaced by the code of $\Qry$, whereas in $\game{2}$, the $\Test$ oracle returns the hash values back to the adversary along with value of $\err$ and output of the $\Qry$ oracle.
+$\game{3}$ on the other hand, returns all the $k$ hash values for any query.
+This results in adversary getting $(k-1)$ hash values for free corresponding to each query, whereas we charge the adversary for a single query.
+Since $k$ is likely to be very small compared to the number of queries the adversary makes, this does not change the dynamics significantly.
+Also, in real world, RO will be a hash function, and hence the adversary can perform local computations to get the hash values.
+It can be easily seen that the output of all the games will be same.
+Hence, $\Prob{\game{0}(A) = 1} = \Prob{\game{1}(A) = 1} = \Prob{\game{2}(A) = 1} = \Prob{\game{3}(A) = 1}$.
+
+In $\game{4}$, we offload all of $\Test$'s computations to $\Hash$, which now maintains an $\Ans$ table to compute and save answers for each query.
+For any query, $q$, the $\Test$ oracle returns answer stored at $\Ans[q]$.
+We also introduce the $\bad$ flag in this game.
+Like in the earlier proofs,  $\bad$ is set to true, if queries indexed by the r-set $\calI$ fail to be false positives, or the other queries are false-positives.
+$\bad$ in fact does not affect the output of $\Hash$ or the game.
+So, $\Prob{\game{4}(A) = 1} = \Prob{\game{3}(A) = 1}$.
+$\game{5}$ is exactly same as $\game{4}$, but returns 0, if $\bad$ is set to true.
+It can be observed that, the total queries made to the $\Hash$ oracle by the adversary(in both games) is the sum of queries($q_T$) made by the $\Test$ oracle, and adversary's direct queries($q_H$).
+Using analyses and intermediate results of previous proofs, $\Prob{\game{5}(A)=1} = \frac{1}{\dbinom{q}{r}}\Prob{\game{4}(A)=1}$.
+
+To summarize, 
+\[
+\AdvCorrect{\Pi_{\mathrm{Bloom}},\distr{\calS}{},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\]
+which is the bound claimed in the theorem statement.
 \begin{figure}
@@
 \nudge \nudge if $j = 1$ then Return $(0, \err, \emptystring)$\\
-\nudge \nudge Return $(0, \err, (h_1, \ldots, h_{j-1}))$\\
+\nudge \nudge Return $(0, \err, (h_1, \ldots, h_j))$\\
 $\err \gets \err +1$\\
@@
 \nudge \nudge $v_j \gets T[j,q_y]$\\
-\nudge $T[j,q_y] \gets h_j$\\
+\nudge $T[j,q_y] \gets v_j$\\
 %
@@
 $\err \gets \err +1$\\
-$\Ans[q_y] \gets (0,\err, (v_1, \ldots, v_{k}))$\\
+$\Ans[q_y] \gets (1,\err, (v_1, \ldots, v_{k}))$\\
 Ret $\left(v_1,\ldots,v_k\right)$
@@
 }
-\caption{\Cref{thm3}: Game playing argument}\label{fig:3TGame}
+\caption{\Cref{thm3}: $\game{4}$ and $\game{5}$ of game playing argument}\label{fig:3TGame}
 \end{figure}

### 2016-09-08 syntax.tex
cheers

@@
 viewing sets as a special case of multisets, so maybe just say
-that.} \tsnote{We may not need all
-  of that.} We write $x \getsr \univ$ to denote
+that.}  We write $x \getsr \univ$ to denote
 sampling an element uniformly from~$\univ$ and assigning it to~$x$,
@@
 $h_1, \ldots, h_k \in \mathcal{H}$ for some function family
-$\mathcal{H}=\{h \colon \univ \to \{1,2,\ldots,m\}\}$. \jnote{Note
-depends on $m$. It might be easier (especially since we talk about
-error) to already let the hash functions be independent random
-oracles.} \tsnote{I don't see the problem.  $\Rep$ knows~$m$, so any
-function (whose range admits at least~$m$ values) can be effectively
-treated as having range~$[m]$. But I added a sentence at the end of
-this paragraph, too.  See if that helps.} \jnote{$\Rep$ knows $m$,
-but $m$ can take any value so we need an $\mathcal{H}$ that is
-defined for every possible~$m$.} It then computes an $m$-bit
+$\mathcal{H}=\{h \colon \univ \to \mathbb{N}\}$.\footnote{For this
+  example, we are implicitly assuming that the range of the hash
+  functions admits a natural mapping to $[m]$.  In practice, this
+  could be enforced in various ways, including allowing $\Rep$ to
+  return an indication of error. }
+It then computes an $m$-bit
 array~$M$ (initialized to 0 everywhere) by setting $M[h_i(x)]=1$ for

### 2016-09-09 Theorem3_FP.tex
Proof3 update

@@
-\heading{Classical Bloom filter in random oracle model (ROM). }
-Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.  Then $\Pi_{\mathrm{Bloom}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-garbled-bf} (left side).  The following result shows,
-\begin{theorem}\label{thm3}
-Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{Bloom}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described.
-For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$, then
-\[
-\AdvCorrect{\Pi_{\mathrm{Bloom}},\distr{\calS}{},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
-\]
-\end{theorem}
-
 \begin{proof}[\Cref{thm3}]
@@
 
-$\game{1}$ is exactly same as $\game{0}$ except the $\Qry$ oracle is replaced by the code of $\Qry$, whereas in $\game{2}$, the $\Test$ oracle returns the hash values back to the adversary along with value of $\err$ and output of the $\Qry$ oracle.
+$\game{1}$ is exactly same as $\game{0}$ except the $\Qry$ oracle is replaced by the code of $\Qry$, whereas in $\game{2}$, the $\Test$ oracle returns the hash values back to the adversary along with $q_x(S)$ and output of the $\Qry$ oracle.
 $\game{3}$ on the other hand, returns all the $k$ hash values for any query.
-This results in adversary getting $(k-1)$ hash values for free corresponding to each query, whereas we charge the adversary for a single query.
-Since $k$ is likely to be very small compared to the number of queries the adversary makes, this does not change the dynamics significantly.
-Also, in real world, RO will be a hash function, and hence the adversary can perform local computations to get the hash values.
+This results in adversary getting $(k-1)$ hash values for free as we charge the adversary for a single query.
+Since $k$ is likely to be very small compared to the number of queries the adversary makes, this would not affect the analysis in any significant manner.
+Also, in real world, RO will be a hash function; hence the adversary can perform local computations to get the hash values.
 It can be easily seen that the output of all the games will be same.
-Hence, $\Prob{\game{0}(A) = 1} = \Prob{\game{1}(A) = 1} = \Prob{\game{2}(A) = 1} = \Prob{\game{3}(A) = 1}$.
+So, $\Prob{\game{0}(A) = 1} = \Prob{\game{1}(A) = 1} = \Prob{\game{2}(A) = 1} = \Prob{\game{3}(A) = 1}$.
 
-In $\game{4}$, we offload all of $\Test$'s computations to $\Hash$, which now maintains an $\Ans$ table to compute and save answers for each query.
+In $\game{4}$, assuming $A$ does not make any pointless queries, $\Hash$ returns $k$ random values (for each query) sampled from $[m]$.
+Also, we offload all of $\Test$'s computations to $\Hash$, which now maintains an $\Ans$ table to compute and save answers for each query.
 For any query, $q$, the $\Test$ oracle returns answer stored at $\Ans[q]$.
@@
 So, $\Prob{\game{4}(A) = 1} = \Prob{\game{3}(A) = 1}$.
+
 $\game{5}$ is exactly same as $\game{4}$, but returns 0, if $\bad$ is set to true.
-It can be observed that, the total queries made to the $\Hash$ oracle by the adversary(in both games) is the sum of queries($q_T$) made by the $\Test$ oracle, and adversary's direct queries($q_H$).
-Using analyses and intermediate results of previous proofs, $\Prob{\game{5}(A)=1} = \frac{1}{\dbinom{q}{r}}\Prob{\game{4}(A)=1}$.
+It can be observed that, the total queries made to the $\Hash$ oracle by the adversary is the sum of queries($q_T$) made by the $\Test$ oracle, and adversary's direct queries($q_H$).
+Using analyses and intermediate results of previous proofs, $\Prob{\game{5}(A)=1} = \frac{1}{\dbinom{q_T + q_H}{r}}\Prob{\game{4}(A)=1}$.
+
+For $r=1$, $\game{5}$ exactly simulates the classical Bloom filter.
+Since, $\Hash$ returns random values for each query, the event of getting a false-positive is independent of the index of the query.
+Using Kirsch and Mitzenmacher's upper bound on false positive probability of a classical Bloom filter, we have  $\Prob{\game{5}(A)=1} = \left( (1-e^{-kn/m})^k + O(1/n) \right)^r$.
 
@@
 \nudge $\err \gets\err +1$\\
-Return~$(a,\err )$\\
+Return~$(a,q_x(S) )$\\
 %
@@
 \nudge $h_j \gets \HashOracle(j,q_x)$\\
-\nudge if $M[h_j] \neq 1$ then Return $(0, \err)$\\
+\nudge if $M[h_j] \neq 1$ then Return $(0, q_x(S))$\\
 $\err \gets \err +1$\\
-Return~$(1,\err )$\\
+Return~$(1,q_x(S))$\\
 %
@@
 \nudge if $M[h_j] \neq 1$\\
-\nudge \nudge if $j = 1$ then Return $(0, \err, \emptystring)$\\
-\nudge \nudge Return $(0, \err, (h_1, \ldots, h_j))$\\
+%\nudge \nudge if $j = 1$ then Return $(0, \err, \emptystring)$\\
+\nudge \nudge Return $(0, q_x(S), (h_1, \ldots, h_j))$\\
 $\err \gets \err +1$\\
-Return~$(1,\err, (h_1, \ldots, h_{k}) )$\\
+Return~$(1,q_x(S), (h_1, \ldots, h_{k}) )$\\
 %
@@
 \nudge if $M[h_j] \neq 1$ then \\
-\nudge \nudge Return~$(0,\err, (h_1, \ldots, h_{k}) )$\\
+\nudge \nudge Return~$(0,q_x(S), (h_1, \ldots, h_{k}) )$\\
 $\err \gets \err +1$\\
-Return~$(1,\err, (h_1, \ldots, h_{k}) )$\\
+Return~$(1,q_x(S), (h_1, \ldots, h_{k}) )$\\
 %
 \oracle{$\HashOracle(q_y)$}\\
-$v_j \getsr [m]$\\
 for $j \in \{1,2,\ldots,k\}$\\
+\nudge $v_j \getsr [m]$\\
 \nudge if $T[j,q_y] \neq \undefined$\\
@@
 $c \gets c + 1$\\
-$v_j \getsr [m]$\\
 for $j \in \{1,2,\ldots,k\}$\\
-\nudge if $T[j,x] \neq \undefined$\\
-\nudge \nudge $v_j \gets T[j,q_y]$\\
-\nudge $T[j,q_y] \gets v_j$\\
+\nudge $v_j \getsr [m]$\\
 %
@@
 \nudge if $M[v_j] \neq 1$ then \\
-\nudge \nudge $\Ans[q_y] \gets (0,\err, (v_1, \ldots, v_{k}) )$\\
+\nudge \nudge $\Ans[q_y] \gets (0, q_y(S), (v_1, \ldots, v_{k}) )$\\
 \nudge \nudge if $c \in \calI$ then $\bad \gets \true$\\
@@
 $\err \gets \err +1$\\
-$\Ans[q_y] \gets (1,\err, (v_1, \ldots, v_{k}))$\\
+$\Ans[q_y] \gets (1, q_y(S), (v_1, \ldots, v_{k}))$\\
 Ret $\left(v_1,\ldots,v_k\right)$
@@
 
-%The proof of this theorem will follow along the lines of \Cref{thm2}.
-As in previous proofs, we use a game playing argument to prove this theorem as well.
-In $\game{0}$, the $\HashOracle$ does lazy sampling of elements from $[m]$ to mimic a random oracle(RO).
-It can be observed that, $\game{0}$ exactly simulates the BF's correctness game attacked by an adaptive adversary.
-So, $\AdvCorrect{{BF},\distr{\calS}{},r}{A} = \Prob{\game{0}(A) = 1}$.
-%
-%In $\game{1}$, assuming $A$ does not make any pointless queries, $\HashOracle$ is modified to sample random elements from $[m]$.
-In addition, $\Test$ sets $\bad$ to $\true$ if queries indexed by set $\calI$ fail to be FPs, or if any of the remaining queries are FPs.
-$\game{2}$, on the other hand is exactly same as $\game{1}$ except it returns 0, if $\bad$ is set to $\true$.
-It can be easily seen that, $\game{1}$ and $\game{2}$ are exactly same as $\game{2}$ and $\game{3}$ of \Cref{thm2}'s game playing argument.
-So,
-%\begin{align*}
-%\Prob{\game{1}(A)=1} = \Prob{\game{0}(A)=1}\\
-%\Prob{\game{2}(A)=1} = \frac{1}{\dbinom{q}{r}}\Prob{\game{1}(A)=1}
-%\end{align*}
-%\Cref{fig:D} shows non-adaptive adversary, $D$ that finds $r$ FPs against the standard BF. Using a similar explanation from previous proofs,
-%\begin{align*}
-%\AdvCorrect{{BF},\distr{\calS}{},r}{D} &= \Prob{\game{2}(A) = 1}\\
-%\AdvCorrect{{BF},\distr{\calS}{},r}{D} &\leq \left( (1-e^{-kn/m})^k + O(1/n) \right)^r \,.
-%\end{align*}
-%To summarize, we have
-%\[
-%\AdvCorrect{{BF},\distr{\calS}{},r}{A} \leq  {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
-%\]
-
 \end{proof}

### 2016-09-09 results.tex
Proof3 update

@@
 
+%%%%%%%%%%%%%%%%% CLASSICAL BLOOM FILTER IN ROM %%%%%%%%%%%%%%%%%%%%
+
+\heading{Classical Bloom filter in random oracle model (ROM). }
+Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.  Then $\Pi_{\mathrm{Bloom}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-garbled-bf} (left side).  The following result shows,
+
+\begin{theorem}\label{thm3}\label{thm:bf-correctness}
+Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{Bloom}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described.
+For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
+\[
+\AdvCorrect{\Pi_{\mathrm{Bloom}},\distr{\calS}{},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\]
+\end{theorem}
+
+\input{Theorem3_FP}
+
 \todo{Below are two lists of things that we should show.}

### 2016-09-12 notions.tex
no message

@@
 
-First, a set~$S$ is chosen according to some
-distribution~$\distr{}{}$ over the collection of multisets
-$\mathcal{S}$ associated with~$\Pi$, and then
-$\Rep(S)$ is run to generate $(\pubaux,\privaux)$. \jnote{I thought we were going to let
-the adversary choose~$S$?} \tsnote{Email discussion. At this point,
-I'm happy just making~$S$ part of the experiment ``name'', the
-way~$\distr{}{}$ is now.  The distribution seems not to matter for
-correctness, at least for the schemes we consider.} \jnote{If instead we choose $S$ from ${\cal D}$, then
-is it clear we want to give $S$ to~$A$?} \tsnote{For \emph{correctness},
-yes, if for no other reason than to allow~$A$ to know when it asking
-a pointless query.  But also it will make no difference to the
-provable correctness of the constructions we consider.}
-\jnote{OK, I think I would just change the definitions so that the attacker
-chooses $S$.}
+First, the adversary $A$ outputs a set $S$ from among those supported by
+the data structure. Then,
+$\Rep(S)$ is run to generate $(\pubaux,\privaux)$.
+%\jnote{I thought we were going to let
+%the adversary choose~$S$?} \tsnote{Email discussion. At this point,
+%I'm happy just making~$S$ part of the experiment ``name'', the
+%way~$\distr{}{}$ is now.  The distribution seems not to matter for
+%correctness, at least for the schemes we consider.} \jnote{If instead we choose $S$ from ${\cal D}$, then
+%is it clear we want to give $S$ to~$A$?} \tsnote{For \emph{correctness},
+%yes, if for no other reason than to allow~$A$ to know when it asking
+%a pointless query.  But also it will make no difference to the
+%provable correctness of the constructions we consider.}
+%\jnote{OK, I think I would just change the definitions so that the attacker
+%chooses $S$.}
 %(Unless stated otherwise, we assume security holds for all distributions and thus for all sets $S$.)

### 2016-09-12 notions.tex
no message

@@
 set-multiplicity data structures.
+All adversaries are stateful by default.
 
@@
 manages to cause at least~$r>0$ such errors among its queries.
-\jnote{If we are specializing the set-multiplicity data structures then we
-may as well have the attacker query $x$ which gets translated to query $q_x$. If
-we are trying to be more general then we should be consistent.}
-\tsnote{I don't see how this correctness notion is specialized to
-  set-multiplicity data structures.  I don't think we actually
-  specialize notions in any way until, maybe, the OW privacy notion.
-  It is true that we only deliver concrete results for set-multiplicty
-data structures, however.}
-
-The notion is lifted to the random-oracle model by providing
+The notion can be lifted to the random-oracle model by providing
 $\Rep,\Qry$ and the adversary~$A$ with oracle access to the
@@
 
-\jnote{I changed $\TestOracle$ so that it outputs $(a, q(S))$ rather
-than $(a,\mathrm{err})$. Note that the latter can be computed from the former,
-and in the general case I think the former is what we
-want.}\tsnote{This may have implications for the efficiency of
-reductions, I'm not sure. The reason I introduced the $\mathrm{err}$
-counter and returned this was to avoid~$A$ be forced to evaluate
-queries of unknown computational cost.} \jnote{Not sure what you mean. If the
-oracle returns $q(S)$ then $A$ doesn't have to evaluate it. All $A$ has to do
-is an equality check to see if $a=q(S)$ or not.}
+%\jnote{I changed $\TestOracle$ so that it outputs $(a, q(S))$ rather
+%than $(a,\mathrm{err})$. Note that the latter can be computed from the former,
+%and in the general case I think the former is what we
+%want.}\tsnote{This may have implications for the efficiency of
+%reductions, I'm not sure. The reason I introduced the $\mathrm{err}$
+%counter and returned this was to avoid~$A$ be forced to evaluate
+%queries of unknown computational cost.} \jnote{Not sure what you mean. If the
+%oracle returns $q(S)$ then $A$ doesn't have to evaluate it. All $A$ has to do
+%is an equality check to see if $a=q(S)$ or not.}
 
@@
 {
-\experimentv{$\ExpCorrect{\setprim,\distr{}{},r}{A}$}\\
-$S \getsr \distr{}{}$\\
+\experimentv{$\ExpCorrect{\setprim,r}{A}$}\\
+$S \getsr A$\\
 $\mathcal{C} \gets \emptyset$; $\mathrm{err}\gets 0$\\
@@
 $\mathcal{C} \gets \mathcal{C} \cup \{q\}$ \\
-Return~$(a,q(S))$
+Return~$a$
 }
 }
-\caption{Correctness of~$\Pi$ against an (adaptive) adversary~$A$, when
-  the represented multiset~$S$ is sampled according to distribution~$\distr{}{}$.}
+\caption{Correctness of~$\Pi$ against an (adaptive) adversary~$A$.}
 \label{fig:correctness}
@@
 The structure of the Naor-Yogev definition is different from ours.
-Lifting their definition\footnote{They focus specifically on set-representation data structures
-with no false negatives, and consider worst-case choice of~$S$. Their data-structure syntax
-also does not distinguish public and private portions of the representation. Nevertheless, it is straightforward
+Lifting their definition\footnote{They focus specifically on set-representation data
+structures
+with no false negatives, and their data-structure syntax
+does not distinguish public and private portions of the representation. Nevertheless, it is straightforward
 to extend their definition to more closely match ours.}
@@
 \experimentv{$\NYExpCorrect{\setprim,\distr{}{}}{A}$}\\
-$S \getsr \distr{}{}$\\
+$S \getsr A$\\
 $\mathcal{C} \gets \emptyset$\\
@@
 %\nudge $\mathrm{err}\gets\mathrm{err}+1$\\
-Return~$(a,q(S))$
+Return~$a$
 }

### 2016-09-13 notions.tex
no message

@@
 We define the advantage of adversary~$A$ in the correctness experiment as
-$\AdvCorrect{\Pi,\distr{}{},r}{A} = \Prob{\ExpCorrect{\Pi,\distr{}{}, r}{A}=1}$.
-Overloading notation, we write $\AdvCorrect{\Pi,\distr{}{},r}{t,q}$ for the maximum over
-all~$t$-time adversaries that ask at most~$q$ queries. We say that a
-set-representation data structure~$\Pi$ is $(t,q,r,\epsilon)$-correct if $\AdvCorrect{\Pi,\distr{}{},r}{t,q} \leq \epsilon$.
+$\AdvCorrect{\Pi,r}{A} = \Prob{\ExpCorrect{\Pi,r}{A}=1}$.
+Overloading notation, we write $\AdvCorrect{\Pi,r}{t,q}$ for the maximum over
+all~$t$-time adversaries that ask at most~$q$ queries. We say a
+data structure~$\Pi$ is $(t,q,r,\epsilon)$-correct if $\AdvCorrect{\Pi,r}{t,q} \leq \epsilon$.
 \jnote{Note~$q$ is overloaded here.}\tsnote{True, and do we even need
@@
 We define the advantage of adversary~$A$ as
-$\NYAdvCorrect{\Pi,\distr{}{}}{A} = \Prob{\NYExpCorrect{\Pi,\distr{}{}}{A}=1}$,
-and write $\NYAdvCorrect{\Pi,\distr{}{},r}{t,q}$ for the maximum over
+$\NYAdvCorrect{\Pi}{A} = \Prob{\NYExpCorrect{\Pi}{A}=1}$,
+and write $\NYAdvCorrect{\Pi,r}{t,q}$ for the maximum over
 all~$t$-time adversaries that ask at most~$q$ queries. We say that a
-set-representation data structure~$\Pi$ is $(t,q,\epsilon)$-NY-correct if
-$\NYAdvCorrect{\Pi,\distr{}{}}{t,q} \leq \epsilon$. \jnote{This should all probably
+data structure~$\Pi$ is $(t,q,\epsilon)$-NY-correct if
+$\NYAdvCorrect{\Pi}{t,q} \leq \epsilon$. \jnote{This should all probably
 move to an appendix; it's a lot of notation to digest for something we never use again
@@
 {
-\experimentv{$\NYExpCorrect{\setprim,\distr{}{}}{A}$}\\
+\experimentv{$\NYExpCorrect{\setprim}{A}$}\\
 $S \getsr A$\\
@@
 \begin{proof}
-Let $\Pi$ be a set-representation data structure that is $(t,q,\epsilon)$-NY-correct,
-and assume that for some distribution $\distr{}{}$, some $q' \leq q+1$, and
-some $r \geq 1$
+Let $\Pi$ be a data structure that is $(t,q,\epsilon)$-NY-correct,
+and assume that for some $q' \leq q+1$ and
+$r \geq 1$
 there is an adversary $A$ running in time~$t$
 and making $q'$ oracle queries such that
-$\AdvCorrect{\Pi,\distr{}{},r}{A} > q'\epsilon/r$.
+$\AdvCorrect{\Pi,r}{A} > q'\epsilon/r$.
 (Note that
@@
 With probability at least
-$q'\epsilon/r$ in an execution of $\ExpCorrect{\Pi,\distr{}{},r}{A}$, we have that
+$q'\epsilon/r$ in an execution of $\ExpCorrect{\Pi,r}{A}$, we have that
 $A$ makes at least $r$ distinct queries to $\TestOracle$ for which
@@
 \begin{proof}
-Let $\Pi$ be a set-representation data structure that is $(t,q,1,\epsilon)$-correct,
-and assume that for some distribution $\distr{}{}$
+Let $\Pi$ be a data structure that is $(t,q,1,\epsilon)$-correct,
+and assume
 there is an adversary $A$ running in time~$t$
 and making at most $q-1$ oracle queries such that
-$\NYAdvCorrect{\Pi,\distr{}{}}{A} > \epsilon$.
+$\NYAdvCorrect{\Pi}{A} > \epsilon$.
 Let $A'$ be the algorithm that simply
@@
 overloaded!} It is immediate that $A'$ makes at most $q$ oracle queries, and
-$\AdvCorrect{\Pi,\distr{}{},1}{A'} \geq \NYAdvCorrect{\Pi,\distr{}{}}{A}$, a contradiction.
+$\AdvCorrect{\Pi,1}{A'} \geq \NYAdvCorrect{\Pi}{A}$, a contradiction.
 \end{proof}
@@
 \begin{theorem}
-There exists a set-representation data structure $\Pi$ that
+There exists a data structure $\Pi$ that
 is $(t, q, 2, 0)$-correct, but is not $(t, 0, \epsilon)$-NY-correct
@@
 \begin{proof}
-We prove the theorem for set-membership data structures.
-Let $x \in {\cal X}$ be an arbitrary element of the universe, and
-let $\Pi$ be the data structure in which $\Rep(S)$ outputs $\pubaux=\privaux=S$, and
-$\Qry(S, S, q_y)$ outputs $q_y(S)$ if $y \neq x$ but outputs $1-q_x(S)$ otherwise. This
+Let $\Pi$ be the set-membership data structure in which $\Rep(S)$ outputs
+$\pubaux=\privaux=S$, and
+$\Qry(S, S, q_y)$ outputs $q_y(S)$ if $y \neq x$ but outputs $1-q_x(S)$ otherwise,
+where $x \in {\cal X}$ is a fixed element of the universe. This
 scheme always answers incorrectly for a single, fixed query, and answers

### 2016-09-15 notions.tex
privacy defs; semantic security implies one-wayness

@@
 $(\pubaux,\privaux) \getsr \Rep(S)$\\
-$z \getsr A^{\TestOracle}(S,\pubaux)$\\
+$\perp \getsr A^{\TestOracle}(\pubaux)$\\
 if $\mathrm{err} < r$ then Return 0\\
@@
 data structure~$\Pi$ is $(t,q,r,\epsilon)$-correct if $\AdvCorrect{\Pi,r}{t,q} \leq \epsilon$.
+
 \jnote{Note~$q$ is overloaded here.}\tsnote{True, and do we even need
@@
 $(\pubaux,\privaux) \getsr \Rep(S)$\\
-$q \getsr A^{\TestOracle}(S,\pubaux)$\\
-if $\left(q \not \in \mathcal{Q}\right.$ and \\
+$q \getsr A^{\TestOracle}(\pubaux)$\\
+if $\left(q \not \in \mathcal{C}\right.$ and \\
 \nudge $\left.\Qry(\pubaux,\privaux,q) \neq q(S)\right)$ \\
@@
 
-In this section we specialize to the case of set-membership data structures, and
+One can also consider the orthogonal notion of \emph{privacy} for a
+data structure.
+We specialize to the case of set-membership data structures, and
 focus on sets rather than multisets.
@@
 Let ${\cal D}$ be
-a distribution on sets over some universe ${\cal X}$. Then the \emph{point-wise
+a distribution over subsets of some universe ${\cal X}$. The \emph{point-wise
 min-entropy} of ${\cal D}$ is defined as
@@
 
-One can also consider the orthogonal notion of \emph{privacy} for a
-data structure.
 We formalize two types of privacy notions. The first captures
 a ``one-wayness'' property that (informally) requires that
-the representation of some set~$S$ does not make it any easier for an attacker
-to learn an element of~$S$.
+the public representation of a set~$S$ does not make it any easier for an attacker
+to learn elements of~$S$.
 The second definition
-captures a flavor of semantic security, essentially requiring that $M$ and $\pub$ do
-not leak any information about the set~$S$ they represent beyond
-what is captured in some explicit leakage function.
+captures a flavor of semantic security, essentially requiring that $\pub$ does
+not leak any information about the set~$S$ it represents beyond
+what is captured by some explicit leakage function.
+
+Our one-wayness notion is defined in Figure~\ref{fig:privacy-ow}.
+The relevant experiment begins by first sampling a set $S$ according to a distribution
+${\cal D}$. Then $\Rep(S)$ is run to obtain $\pubaux,\privaux$, and the attacker~$A$ is given
+$\pubaux$. The attacker succeeds if it is able to output an element of~$S$.
+We define the advantage of adversary~$A$ in this experiment\footnote{We
+remark that one could consider augmenting experiment $\ExpPrivOW{\Pi,{\cal D}}{A}$ by additionally
+giving $A$ access to an oracle for testing membership in~$S$. However, it is not hard
+to see that allowing $q$ such queries can increase $A$'s advantage by at most a factor of~$q$.} as
+$\AdvPrivOW{\Pi,\mathcal{D}}{A} = \Prob{\ExpPrivOW{\Pi,{\cal D}}{A}=1}$ and,
+overloading notation, we write $\AdvPrivOW{\Pi,{\cal D}}{t}$ for the maximum of this value over
+all~$t$-time adversaries.
+Noting that an attacker can trivially succeed with probability
+$2^{-H_\infty({\cal D})}$ by outputting the element most likely to be in~$S$,
+we say a
+set-representation data structure~$\Pi$ is $(t,\epsilon)$-ow-private if for all ${\cal D}$
+we have $\AdvPrivOW{\Pi,{\cal D}}{t} - 2^{-H_\infty({\cal D})} \leq \epsilon$.
+\jnote{Not sure I'm completely happy with the definition.}
+
+\begin{figure}[hbtp]
+\centering
+\fpage{.25}{
+%\hpagess{.5}{.45}
+%{
+\experimentv{$\ExpPrivOW{\setprim,\distr{}{}}{A}$}\\
+$S \getsr \distr{}{}$\\
+$(\pubaux,\privaux) \getsr \Rep(S)$\\
+$z \getsr A(\pubaux)$\\
+if $z \in S$ then return 1\\
+return 0
+%}
+%{
+%\oracle{$\TestOracle(q)$}\\
+%Return $\Qry(\pubaux,\privaux,q)$
+%}
+}
+\caption{Experiment for a ``one-way'' style privacy
+  definition.}
+\label{fig:privacy-ow}
+\end{figure}
 
@@
 public information $\pubaux$ that results from running $\Rep(S)$.
-\footnote{We do not give $A$ an oracle for issuing queries;
-since $A$ knows the set~$S$, such an oracle would be superfluous.
-\jnote{Interestingly,
-if we provided a query oracle in the real world and an oracle that returns the correct
-answer in the simulated world, then the definition seems to imply
-correctness also.}}
+%\footnote{We do not give $A$ an oracle for issuing queries;
+%since $A$ knows the set~$S$, such an oracle would be superfluous.
+%\jnote{Interestingly,
+%if we provided a query oracle in the real world and an oracle that returns the correct
+%answer in the simulated world, then the definition seems to imply
+%correctness also.}}
 In the simulated experiment (ss-rep-0), $A$ outputs $S$ and is given $\pubaux$ output
@@
 For a given function ${\sf leak}$, adversary $A$, and simulator~$\Sim$,
-we define the advantage measure
+we define the advantage
 $\AdvPrivSS{\Pi,{\sf leak}}{A,\Sim} \bydef
@@
 $\pubaux$ of the representation of a set~$S$ leaks~${\sf leak}(S)$ and nothing more.
-\jnote{Need to relate running time of $\Sim$ to running time of~$A$.}
-\todo{Introduce OW notion, if we keep it}
+\jnote{Need to relate running time of $\Sim$ to running time of~$A$. Also, the definition
+as stated does not really work well in the presence of (programmable) random oracles.}
+
 \begin{figure}[hbtp]
@@
 \experimentv{$\ExpPrivSSreal{\Pi}{A}$}\\
-$(S,\st) \getsr A()$ \\
+$S \getsr A$ \\
 $(\pubaux,\privaux) \getsr \Rep(S)$\\
-return $A(\st,\pubaux)$\\
+return $A(\pubaux)$\\
 }
@@
 \experimentv{$\ExpPrivSSsim{\Pi, {\sf leak}}{A, \Sim}$}\\
-$(S,\st) \getsr A()$\\
-$(\st,\pubaux) \getsr \Sim({\sf leak}(S))$ \\
-return $A(\st,\pubaux)$\\
+$S \getsr A$\\
+$\pubaux \getsr \Sim({\sf leak}(S))$ \\
+return $A(\pubaux)$\\
 }
@@
 \label{fig:privacy-ss}
-\end{figure}
-
-\begin{figure}[hbtp]
-\centering
-\fpage{.6}{
-\hpagess{.5}{.45}
-{
-\experimentv{$\ExpPrivOW{\setprim,\distr{}{}}{A}$}\\
-$S \getsr \distr{}{}$\\
-$(\pubaux,\privaux) \getsr \Rep(S)$\\
-$z \getsr A^{\TestOracle}(\pubaux)$\\
-if $z \in S$ then return 1\\
-return 0\\
-}
-{
-\oracle{$\TestOracle(q)$}\\
-eturn $\Qry(\pubaux,\privaux,q)$
-}
-}
-\caption{Experiments for a ``one-way'' style privacy
-  definition.}
-\label{fig:privacy-ow}
 \end{figure}
@@
 
-\heading{Relationships Among Notions.} \todo{SS$\Rightarrow$OW?
-  (Probably not in general, but perhaps for set-multiplicity data
-  structures that satisfy certain assumptions on the query set.)
-  SS$\not\Rightarrow$ correctness; the converse is already shown by
-  the example I gave earlier, i.e. $M=S\setminus\{x\}$ for random $x
-  \in S$.}
+\heading{Relationships between the notions.}
+Our intuition is that semantic security implies one-wayness. And, indeed, this is
+the case---provided one is careful with the technical details.
+For a distribution ${\cal D}$
+over subsets of some universe ${\cal X}$, define
+\[\tilde H_\infty({\cal D} \mid {\sf leak}) \bydef -\log \sum_{r \in R} \Pr_{S \getsr {\cal D}}[{\sf leak}(S)=r] \cdot
+\max_{x \in {\cal X}} \Pr_{S \getsr {\cal D}}[x \in S \mid {\sf leak}(S)=r].\]
+
+\begin{theorem}
+Let $\Pi$ be a set-representation data structure that is $(t, \epsilon)$-semantically secure
+with respect to leakage ${\sf leak}:2^{\cal X} \rightarrow R$.
+Then $\AdvPrivOW{\Pi,\mathcal{D}}{t} \leq \tilde H_\infty({\cal D} \mid {\sf leak}) + \epsilon$.
+\end{theorem}
+\begin{proof}
+Fix a distribution ${\cal D}$ and an attacker
+$A$ running in time $t$, and let $\delta \bydef \AdvPrivOW{\Pi,\mathcal{D}}{A}$.
+Define an attacker $A'$ who behaves as follows: first, it samples a set $S$ according to
+distribution~${\cal D}$. Then, given $\pubaux$, it runs $A(\pubaux)$ to obtain an element~$z$.
+Finally, it outputs~1 if and only if $z \in S$.
+
+It is immediate that $\Pr[\ExpPrivSSreal{\Pi}{A'}=1] = \delta$. Semantic
+security of $\Pi$ implies that there exists a simulator $\Sim$ for which
+$\ExpPrivSSsim{\Pi, {\sf leak}}{A', \Sim} \geq \delta - \epsilon$. However,
+the only information
+that $\Sim$
+and $A'$ jointly have about the set~$S$ that was sampled is ${\sf leak}(S)$; thus,
+we must have $\ExpPrivSSsim{\Pi, {\sf leak}}{A', \Sim} \leq H_\infty({\cal D} \mid {\sf leak})$.
+This implies
+$\delta \leq \tilde H_\infty({\cal D} \mid {\sf leak})+\epsilon$ as desired.
+\end{proof}
+
+%\todo{SS$\Rightarrow$OW?
+%  (Probably not in general, but perhaps for set-multiplicity data
+%  structures that satisfy certain assumptions on the query set.)
+%  SS$\not\Rightarrow$ correctness; the converse is already shown by
+%  the example I gave earlier, i.e. $M=S\setminus\{x\}$ for random $x
+%  \in S$.} \jnote{Since we can set $\pubaux$ to be the emptystring, I think
+%  it is trivial to see that privacy does not imply correctness.}

### 2016-09-15 syntax.tex
Citations

@@
 construction gives a static version of a counting Bloom
-filter~\cite{xxx}.  We will capture dynamic versions, as well as
-count-min sketches~\cite{xxx}, scalable Bloom filters~\cite{xxx},
+filter~\cite{fan2000summary}.  We will capture dynamic versions, as well as
+count-min sketches~\cite{cormode2005improved}, scalable Bloom filters~\cite{almeida2007scalable},
 etc., in future work.\tsnote{?}
@@
 the so-called ``garbled Bloom filter'' due to Dong, Chen and
-Wen~\cite{xxx}. \todo{Details have to be filled in.} This stores
+Wen~\cite{dong2013private}. \todo{Details have to be filled in.} This stores
 xor-shares of bitstring~$x \in S$ at positions

### 2016-09-15 Theorem1_FP.tex
Proofs syntax update
Proof5 updated as per changed syntax

@@
 $S \getsr \distr{\calS}{}$\\
-$\err \gets 0$\\
+$\calC \gets \emptyset$; $\err \gets 0$\\
 $(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
@@
 When $A$ asks $\TestOracle(q_x)$:\\
+\nudge if $q_x \in \mathcal{C}$ then Return $\bot$\\
 \nudge $a \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
 \nudge if $a \neq q_x(S)$ then \\
-\nudge \nudge $\err \gets \err +1$\\
-\nudge Return~$(a,\err )$\\
+\nudge \nudge $\err \gets \err + 1$\\
+\nudge \nudge  $\calC \gets \calC \cup \{q_x\}$\\
+\nudge Return~$a$\\
 When $A$ halts: \\
@@
 \oracle{$\HashOracle(x)$}\\
-$ \mathrm{Ret} \nudge F_{K_1}(x) + i\cdot \calO(x)$, for $i\in[1,k]$\\
+Return $F_{K_1}(x) + i\cdot \calO(x)$, for $i\in[1,k]$\\
 }
@@
 When $A$ asks $\TestOracle(q_x)$:\\
+\nudge if $q_x \in \mathcal{C}$ then Return $\bot$\\
 \nudge $a \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
 \nudge if $a \neq q_x(S)$ then \\
-\nudge \nudge $\err \gets\err +1$\\
-\nudge Return~$(a,\err )$\\
+\nudge \nudge $\err \gets \err +1$\\
+\nudge \nudge $\calC \gets \calC \cup \{q_x\}$\\
+\nudge Return~$a$\\
 When $A$ halts: \\
@@
 $T[x] \gets a$\\
-Ret  $\calO(x) + i\cdot a$, for $i\in[1,k]$
+Return  $\calO(x) + i\cdot a$, for $i\in[1,k]$
 }
@@
 \underline{\game{0}(A)}\\
-$S \getsr \distr{\calS}{}$\\
-$\err \gets 0$\\
+$S \getsr \distr{\calS}{}$; $\calC \gets \emptyset$; $\err \gets 0$\\
 $(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
-$z \getsr A^{\TestOracle}(S,\pubaux)$\\
+$\bot \getsr A^{\TestOracle}(S,\pubaux)$\\
 if $\err  < r$ then Return 0\\
@@
 \oracle{$\TestOracle(q_x)$}\\
+if $q_x \in \mathcal{C}$ then Return $\bot$\\
 $a \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
 if $a \neq q_x(S)$ then \\
-\nudge $\err \gets\err +1$\\
-Return~$(a,\err )$\\
+\nudge $\err \gets \err + 1$; $\calC \gets \calC \cup \{q_x\}$\\
+Return~$a$\\
 %
@@
 $\rho \getsr \Func{\univ,[m]}$\\
-$S \getsr \distr{\calS}{}$\\
-$\err \gets 0$\\
+$S \getsr \distr{\calS}{}$; $\calC \gets \emptyset$; $\err \gets 0$\\
 $(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
-$z \getsr A^{\TestOracle}(S,\pubaux)$\\
+$\bot \getsr A^{\TestOracle}(S,\pubaux)$\\
 if $\err  < r$ then Return 0\\
@@
 $\rho_1,\rho_2 \getsr \Func{\univ,[m]}$\\
-$S \getsr \distr{\calS}{}$\\
-$\err \gets 0$\\
+$S \getsr \distr{\calS}{}$; $\calC \gets \emptyset$; $\err \gets 0$\\
 $(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
-$z \getsr A^{\TestOracle}(S,\pubaux)$\\
+$\bot \getsr A^{\TestOracle}(S,\pubaux)$\\
 if $\err  < r$ then Return 0\\
@@
 \oracle{$\TestOracle(q_x)$}\\
+if $q_x \in \mathcal{C}$ then Return $\bot$\\
 $a \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
 if $a \neq q_x(S)$ then \\
-\nudge $\err \gets\err +1$\\
-Return~$(a,\err )$\\\\
+\nudge $\err \gets \err + 1$; $\calC \gets \calC \cup \{q_x\}$\\
+Return~$a$\\\\
 %
@@
 \underline{{$\game{3}(A)$},\fbox{$\game{4}(A)$}}\\
-$c\gets 0$, $\bad \gets \false$, $\err \gets 0$\\
-$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
-$S \getsr \distr{\calS}{}$\\
+$c\gets 0$, $\bad \gets \false$, $\err \gets 0$;  $\calC \gets \emptyset$\\
+$S \getsr \distr{\calS}{}$; $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
 $(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
-$z \getsr A^{\TestOracle}(S,\pubaux)$\\
+$\bot \getsr A^{\TestOracle}(S,\pubaux)$\\
 if $\bad = \true$ then \fbox{Return 0}\\
@@
 \oracle{$\TestOracle(q_x)$}\\
+if $q_x \in \mathcal{C}$ then Return $\bot$\\
 $c \gets c+1$\\
@@
 if $v \neq q_x(S)$\\
-\nudge $\err \gets\err +1$\\
-Return~$(v,\err )$\\
+\nudge $\err \gets \err +1$; $\calC \gets \calC \cup \{q_x\}$\\
+Return~$v$\\
 %
@@
 \nudge $v_i = a+i \cdot b \bmod m$\\
-Ret $\left(v_1,\ldots,v_k\right)$
+Return $\left(v_1,\ldots,v_k\right)$
 }
@@
 $b' \getsr B^\calO$\\
-Ret $[b = b']$\\
+Return $[b = b']$\\
 }
@@
 if $ b = 1$ then\\
-\nudge Ret $F_K(x)$\\
-Ret $\rho(x)$\\
+\nudge Return $F_K(x)$\\
+Return $\rho(x)$\\
 }
@@
 $c \gets 0$\\%, $\calX \gets \emptyset$\\
-$\err \gets 0$\\
+$\calC \gets \emptyset$; $\err \gets 0$\\
 $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
 Run $A(S, \pubaux)$\\
-When $A$ asks $\Test(x)$:\\
+When $A$ asks $\TestOracle(q_x)$:\\
+if $q_x \in \mathcal{C}$ then Return $\bot$\\
 \nudge $c \gets c+1$\\
@@
 \nudge if $c \in \mathcal{I}$\\
-%\nudge \nudge $\calX \gets \calX \cup \{x\}$\\
 \nudge \nudge $r \gets 1$\\
 \nudge \nudge $\err \gets \err + 1$\\
-\nudge Ret $(r,\err )$\\
+\nudge \nudge $\calC \gets \calC \cup \{q_x\}$\\
+\nudge Return $r$\\
 When $A$ halts:\\
-\nudge Ret 1
+\nudge Return $\bot$
 }

### 2016-09-15 Theorem2_FP.tex
Proofs syntax update
Proof7 updated as per changed syntax

@@
 \nudge $h_j(x) =\FK $\\
-Ret $\left(h_1(x),\ldots,h_k(x)\right)$
+Return $\left(h_1(x),\ldots,h_k(x)\right)$
 }
@@
 \nudge $h_j(x) = \rhoK $\\
-Ret $\left(h_1(x),\ldots,h_k(x)\right)$
+Return $\left(h_1(x),\ldots,h_k(x)\right)$
 }
@@
 {
-\underline{{$\game{2}(A)$},\fbox{$\game{3}(A)$}}\\
-$c\gets 0$, $\bad \gets \false$\\
-$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
-$S \getsr \distr{\calS}{}$\\
-$\err \gets 0$\\
+\underline{\game{2}(A)\fbox{\game{3}(A)}}\\
+$c\gets 0$, $\bad \gets \false$, $\err \gets 0$;  $\calC \gets \emptyset$\\
+$S \getsr \distr{\calS}{}$; $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
 $(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
-$z \getsr A^{\TestOracle}(S,\pubaux)$\\
+$\bot \getsr A^{\TestOracle}(S,\pubaux)$\\
 if $\bad = \true$ then \fbox{Return 0}\\
@@
 if $v \neq q_x(S)$\\
-\nudge $\err \gets\err +1$\\
-Return~$(v,\err )$\\\\
+\nudge $\err \gets \err +1$; $\calC \gets \calC \cup \{q_x\}$\\
+Return~$v$\\\\
 %
@@
 \nudge $v_j \getsr [m]$\\
-Ret $\left(v_1,\ldots,v_k\right)$
+Return $\left(v_1,\ldots,v_k\right)$
 }
@@
 When $A$ asks $\TestOracle(q_x)$:\\
+\nudge if $q_x \in \mathcal{C}$ then Return $\bot$\\
 \nudge $a \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
@@
 \nudge \nudge $\err \gets \err +1$\\
-\nudge Return~$(a,\err )$\\
+\nudge \nudge  $\calC \gets \calC \cup \{q_x\}$\\
+\nudge Return~$a$\\
 When $A$ halts: \\
@@
 \oracle{$\HashOracle(x)$}\\
-\nudge Ret $\OK$, for $j\in[1,k]$\\
+\nudge Return $\OK$, for $j\in[1,k]$\\
 }

### 2016-09-15 Theorem1_FP.tex
Small update

@@
 \nudge if $q_x \in \mathcal{C}$ then Return $\bot$\\
+\nudge $\calC \gets \calC \cup \{q_x\}$\\
 \nudge $a \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
@@
 \nudge \nudge $\err \gets \err + 1$\\
-\nudge \nudge  $\calC \gets \calC \cup \{q_x\}$\\
 \nudge Return~$a$\\
@@
 \nudge \nudge $\err \gets \err +1$\\
-\nudge \nudge $\calC \gets \calC \cup \{q_x\}$\\
 \nudge Return~$a$\\
@@
 if $q_x \in \mathcal{C}$ then Return $\bot$\\
+$\calC \gets \calC \cup \{q_x\}$\\
 $a \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
-if $a \neq q_x(S)$ then \\
-\nudge $\err \gets \err + 1$; $\calC \gets \calC \cup \{q_x\}$\\
+if $a \neq q_x(S)$ then $\err \gets \err + 1$\\
 Return~$a$\\
@@
 if $q_x \in \mathcal{C}$ then Return $\bot$\\
+$\calC \gets \calC \cup \{q_x\}$\\
 $a \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
-if $a \neq q_x(S)$ then \\
-\nudge $\err \gets \err + 1$; $\calC \gets \calC \cup \{q_x\}$\\
+if $a \neq q_x(S)$ then $\err \gets \err + 1$\\
 Return~$a$\\\\
@@
 if $q_x \in \mathcal{C}$ then Return $\bot$\\
+$\calC \gets \calC \cup \{q_x\}$\\
 $c \gets c+1$\\
@@
 \nudge $\bad \gets \true$\\
-if $v \neq q_x(S)$\\
-\nudge $\err \gets \err +1$; $\calC \gets \calC \cup \{q_x\}$\\
+if $v \neq q_x(S)$ then $\err \gets \err +1$\\
 Return~$v$\\
@@
 }
-\caption{\Cref{thm1}:Game playing argument}\label{fig:Game}
+\caption{\Cref{thm1}: Game playing argument}\label{fig:Game}
 \end{figure}
@@
 When $A$ asks $\TestOracle(q_x)$:\\
-if $q_x \in \mathcal{C}$ then Return $\bot$\\
+\nudge if $q_x \in \mathcal{C}$ then Return $\bot$\\
+\nudge $\calC \gets \calC \cup \{q_x\}$\\
 \nudge $c \gets c+1$\\
@@
 \nudge \nudge $\err \gets \err + 1$\\
-\nudge \nudge $\calC \gets \calC \cup \{q_x\}$\\
 \nudge Return $r$\\

### 2016-09-15 Theorem2_FP.tex
Small update

@@
 \nudge $\bad \gets \true$\\
-if $v \neq q_x(S)$\\
-\nudge $\err \gets \err +1$; $\calC \gets \calC \cup \{q_x\}$\\
+if $v \neq q_x(S)$ then $\err \gets \err +1$\\
 Return~$v$\\\\
@@
 \nudge \nudge $\err \gets \err +1$\\
-\nudge \nudge  $\calC \gets \calC \cup \{q_x\}$\\
 \nudge Return~$a$\\

### 2016-09-16 notions.tex
no message

@@
 $\pubaux$ of the representation of a set~$S$ leaks~${\sf leak}(S)$ and nothing more.
-\jnote{Need to relate running time of $\Sim$ to running time of~$A$. Also, the definition
+\jnote{The definition
 as stated does not really work well in the presence of (programmable) random oracles.}
@@
 with respect to leakage ${\sf leak}:2^{\cal X} \rightarrow R$.
-Then $\AdvPrivOW{\Pi,\mathcal{D}}{t} \leq \tilde H_\infty({\cal D} \mid {\sf leak}) + \epsilon$.
+Then $\AdvPrivOW{\Pi,\mathcal{D}}{t} \leq 2^{-\tilde H_\infty({\cal D} \mid {\sf leak})} + \epsilon$.
 \end{theorem}
@@
 and $A'$ jointly have about the set~$S$ that was sampled is ${\sf leak}(S)$; thus,
-we must have $\ExpPrivSSsim{\Pi, {\sf leak}}{A', \Sim} \leq H_\infty({\cal D} \mid {\sf leak})$.
+we must have $\ExpPrivSSsim{\Pi, {\sf leak}}{A', \Sim} \leq 2^{-\tilde H_\infty({\cal D} \mid {\sf leak})}$.
 This implies
-$\delta \leq \tilde H_\infty({\cal D} \mid {\sf leak})+\epsilon$ as desired.
+$\delta \leq 2^{-\tilde H_\infty({\cal D} \mid {\sf leak})}+\epsilon$ as desired.
 \end{proof}

### 2016-09-21 notions.tex
replacing q with \qry macro for generic name of queries

@@
 Adversary~$A$ is given~$\pubaux$~as input; it is also
-provided with access to an oracle~$\TestOracle$ that, on input a query~$q \in \calQ$,
+provided with access to an oracle~$\TestOracle$ that, on input a query~$\qry \in \calQ$,
 returns $\Qry(\pubaux,\privaux,q)$ and increments
@@
 {
-\oracle{$\TestOracle(q)$}\\
-if $q \in \mathcal{C}$ then Return $\bot$\\
-$a \gets \Qry(\pubaux,\privaux,q)$\\
-if $a \neq q(S)$ then \\
+\oracle{$\TestOracle(\qry)$}\\
+if $\qry \in \mathcal{C}$ then Return $\bot$\\
+$a \gets \Qry(\pubaux,\privaux,\qry)$\\
+if $a \neq \qry(S)$ then \\
 \nudge $\mathrm{err}\gets\mathrm{err}+1$\\
-$\mathcal{C} \gets \mathcal{C} \cup \{q\}$ \\
+$\mathcal{C} \gets \mathcal{C} \cup \{\qry\}$ \\
 Return~$a$
@@
 
-\jnote{Note~$q$ is overloaded here.}\tsnote{True, and do we even need
-  it, other than for making a compact statements of comparison with
-  NY?  Why not just have explicit advantage bounding statements, as we
-  do for our other results, relating our notion to NY's?  (And,
-  probably, moving all of that to an appendix, as you later suggest.)}
-\jnote{Not sure what you mean. I was pointing out that we use $q$ both for a particular
-query, as well as for the bound on the number of attacker's queries. Don't we want to
-keep track of the query bound?}
+\jnote{Note~$q$ is overloaded here.}
 
@@
 the experiment is similar but the attacker
-succeeds only if it outputs a (single) query $q$ for which
-$\Qry(\pubaux,\privaux, q) \neq q(S)$  \emph{subject to the restriction that it did not
-previously query $q$ to its $\TestOracle$ oracle}. We refer to
+succeeds only if it outputs a (single) query $\qry$ for which
+$\Qry(\pubaux,\privaux, \qry) \neq \qry(S)$  \emph{subject to the restriction that it did not
+previously query $\qry$ to its $\TestOracle$ oracle}. We refer to
 Figure~\ref{fig:NYcorrectness} for a definition of the relevant experiment.
@@
 $(\pubaux,\privaux) \getsr \Rep(S)$\\
-$q \getsr A^{\TestOracle}(\pubaux)$\\
-if $\left(q \not \in \mathcal{C}\right.$ and \\
-\nudge $\left.\Qry(\pubaux,\privaux,q) \neq q(S)\right)$ \\
+$\qry \getsr A^{\TestOracle}(\pubaux)$\\
+if $\left(\qry \not \in \mathcal{C}\right.$ and \\
+\nudge $\left.\Qry(\pubaux,\privaux,\qry) \neq \qry(S)\right)$ \\
 \nudge \nudge then Return 1\\
@@
 1$.
-\tsnote{this could easily be written, albeit less compactly, without
-introducing the resource-parameterized notation; likewise the others.} \jnote{How?}
 \end{theorem}
@@
 Let $A'$ be the algorithm that simply
-runs~$A$, passing the oracle queries of $A$ to its own oracle, until $A$ terminates
-with output~$q$; then, $A'$ sends $q$ to $\TestOracle$. \jnote{$q$ is (still)
-overloaded!} It is immediate that $A'$ makes at most $q$ oracle queries, and
+runs~$A$, passing the oracle queries of~$A$ to its own oracle, until~$A$ terminates
+with output~$\qry$; then, $A'$ sends~$\qry$ to $\TestOracle$. It is immediate that $A'$ makes at most $q$ oracle queries, and
 $\AdvCorrect{\Pi,1}{A'} \geq \NYAdvCorrect{\Pi}{A}$, a contradiction.
@@
 $\pubaux=\privaux=S$, and
-$\Qry(S, S, q_y)$ outputs $q_y(S)$ if $y \neq x$ but outputs $1-q_x(S)$ otherwise,
+$\Qry(S, S, \qry_y)$ outputs $\qry_y(S)$ if $y \neq x$ but outputs $1-\qry_x(S)$ otherwise,
 where $x \in {\cal X}$ is a fixed element of the universe. This
@@
 %  (Probably not in general, but perhaps for set-multiplicity data
-%  structures that satisfy certain assumptions on the query set.)
+%  structures that satisfy certain assumptions on the qnuery set.)
 %  SS$\not\Rightarrow$ correctness; the converse is already shown by

### 2016-09-21 syntax.tex
replacing q with \qry macro for generic name of queries

@@
+\newcommand{\qry}{\mathsf{qry}}
 \section{(Multiset) Data Structures}
@@
 \begin{itemize}
-\item $\mathcal{Q}=\{q \colon \mathcal{S} \to \Gamma\}$ is a set
+\item $\mathcal{Q}=\{\qry \colon \mathcal{S} \to \Gamma\}$ is a set
     of supported \emph{queries}, where $\Gamma$ is the set of query \emph{answers}.
@@
     algorithm, taking as input $\pubaux,\privaux \in \bits^*$
-    and a query $q \in \calQ$, and outputting an \emph{answer}
-    $a \in \Gamma$.  We write $a \gets \Qry(\pubaux,\privaux,q)$
+    and a query $\qry \in \calQ$, and outputting an \emph{answer}
+    $a \in \Gamma$.  We write $a \gets \Qry(\pubaux,\privaux,\qry)$
     for this execution.
@@
 $\Rep$ would allow this.}
-%\tsnote{I implemented this change.}\tsnote{I'm now leaning towards
-%having $\Rep$ output~$M$ and explicit pubic/private auxillary data.
-%Pushing secrets into~$M$ makes it more difficult to capture (for
-%example) the Neidermeier et al.\ attacks in our privacy notions; see
-%Figure~\ref{fig:privacy}.  In those attacks, the adversary would get
-%the bitarray (which one naturally thinks of as~$M$) but not the
-%secret keys for the PRFs/hash functions.  You could say that the
-%bitarray is put in $\aux$ and that~$M$ \emph{only} contains the
-%secret keys, but this is unnatural.}
-
-%All of the data structures that we will consider have the property that~$|M|$ does not depend on the
-%coins of~$\Rep$. Thus we assume that~$|M|$ depends only on~$|S|$. In
-%general this need not be true, but the assumption does not restrict
-%our syntax from capturing natural constructions (e.g., those used in
-%practice), and it makes it easier to state our security notions.
-
-%\jnote{I think we agreed to just have the syntax output $(\pub, \privaux)$, with
-%the semantics being that in our definitions $\pub$ is always
-%  public and $\privaux$ is always private.
-%  Different schemes can then choose whether $M$ is in $\pub$
-%  or $\privaux$. If we do this, then need to be careful how to define size, though
-%  I don't think we ever explicitly care about size for any of our results.}
 
@@
 For a given data structure $\setprim=(\calQ,\Rep, \Qry)$, let
-$\mathrm{Err}(S,q,\pubaux,\privaux)$ be a predicate that is true iff
-$\Qry(\pubaux,\privaux, q) \neq q(S)$.  Then $\Pi$ has \emph{error
-probability} $\epsilon$ if $\max_{S,q}\Pr[(\pubaux,\privaux) \getsr
-\Rep(S) : \mathrm{Err}(S,q,\pubaux,\privaux)=1 ] \leq \epsilon$.
+$\mathrm{Err}(S,\qry,\pubaux,\privaux)$ be a predicate that is true iff
+$\Qry(\pubaux,\privaux, \qry) \neq \qry(S)$.  Then $\Pi$ has \emph{error
+probability} $\epsilon$ if $\max_{S,\qry}\Pr[(\pubaux,\privaux) \getsr
+\Rep(S) : \mathrm{Err}(S,\qry,\pubaux,\privaux)=1 ] \leq \epsilon$.
 %
 It has \emph{error rate} $\tilde{\epsilon}$ if
-$\max_{S}\Pr[(\pubaux,\privaux) \getsr \Rep(S);\, q \getsr \calQ :
-\mathrm{Err}(S,q,\pubaux,\privaux)=1] \leq \tilde{\epsilon}$. \hfill\dqed
+$\max_{S}\Pr[(\pubaux,\privaux) \getsr \Rep(S);\, \qry \getsr \calQ :
+\mathrm{Err}(S,\qry,\pubaux,\privaux)=1] \leq \tilde{\epsilon}$. \hfill\dqed
 \end{definition}
@@
 the error probability~$\epsilon$ is measured only over the coins
-of~$\Rep$, for a fixed~$S$ and query~$q$. Once the coins of~$\Rep$
+of~$\Rep$, for a fixed~$S$ and query~$\qry$. Once the coins of~$\Rep$
 are fixed, it is not straightforward how to connect~$\epsilon$ to
@@
 and consider a correctness-violating attack that asks random
-queries $q_1,q_2,\ldots,q_T$, i.e., uniform samples from~$\calQ$.
+queries $\qry_1,\qry_2,\ldots,\qry_T$, i.e., uniform samples from~$\calQ$.
 Let $\mathrm{Err}_i$ be a random variable indicating the event
-$\Qry(\pubaux,\privaux,q_i)\neq q_i(S)$.  We know that the probability
+$\Qry(\pubaux,\privaux,\qry_i)\neq \qry_i(S)$.  We know that the probability
 that $\mathrm{Err}_i=1$ is at most~$\epsilon$, and it is tempting to
@@
 Fix $|S|=n$ for all $S \in \calS$, where $n \ll |\univ|$. For the
-queries, let $\calQ = \{q_x\colon \calS \to \bits \,|\, \forall x
-\in \univ\}$ where $\forall S \in \calS$ the predicate $q_x(S)=1
+queries, let $\calQ = \{\qry_x\colon \calS \to \bits \,|\, \forall x
+\in \univ\}$ where $\forall S \in \calS$ the predicate $\qry_x(S)=1
 \Leftrightarrow x \in S$.  Let $\Rep(S)$ pick a random element~$s
@@
 \emptystring$.  To respond to queries,
-let~$\Qry(\pubaux,\privaux,q_x)=1$ iff $x \in M$.  It is easy to see
+let~$\Qry(\pubaux,\privaux,\qry_x)=1$ iff $x \in M$.  It is easy to see
 that this scheme is $1/n$-correct; for any fixed~$S$, there are
-exactly~$n$ queries~$q_x$ that have probability~$1/n$  (over the
+exactly~$n$ queries~$\qry_x$ that have probability~$1/n$  (over the
 coins of~$\Rep$) of causing a correctness error, and the remaining
@@
 A \emph{set-multiplicity data structure} is a data structure with
-$\Gamma=\mathbb{N}$ and $\calQ=\{q_x\}_{x \in \univ}$, where
-$q_x(S)$ is defined to be the multiplicity of~$x$ in the
+$\Gamma=\mathbb{N}$ and $\calQ=\{\qry_x\}_{x \in \univ}$, where
+$\qry_x(S)$ is defined to be the multiplicity of~$x$ in the
 multiset~$S$. \hfill\dqed
@@
 Algorithm~$\Qry$ is defined so that, on input
-$(\pubaux,\privaux,q_x)$, it returns the minimum of the values
+$(\pubaux,\privaux,\qry_x)$, it returns the minimum of the values
 $M[h_1(x)],\ldots,M[h_k(x)]$.  We note that the standard Bloom filter

### 2016-09-21 notions.tex
no message

@@
 focus on sets rather than multisets.
-Before continuing, it will be useful to define a notion of ``point-wise min-entropy.''
+Before continuing, it will be useful to define a notion that captures the difficulty
+of guessing an element in a set chosen from some distribution.
 Let ${\cal D}$ be
@@
 
-Our semantic-secure definition is simulation-based (see Figure~\ref{fig:privacy-ss}).
+Our semantic-security definition is based on the simulation paradigm (see Figure~\ref{fig:privacy-ss}).
+\jnote{Here it would not be hard to write the definition for general data structures, not
+specifically set-multiplicity data structures.}
 In this definition we compare the probabilities with which an attacker $A$ outputs~1
@@
 Informally, a scheme $\Pi$ is secure with respect to some leakage function ${\sf leak}$
-if for all $A$ there is a simulator $\Sim$ such that
-$\AdvPrivSS{\Pi,{\sf leak}}{A,\Sim}$ is small.
+if for all efficient $A$ there is a simulator $\Sim$ such that
+$\AdvPrivSS{\Pi,{\sf leak}}{A,\Sim}$ is small. \jnote{Do we want to
+write a formal $t, \epsilon$-style definition?}
 Intuitively, this means that the public portion
@@
 as stated does not really work well in the presence of (programmable) random oracles.}
+\jnote{In the current definition there is (intentionally) no bound on the simulator's
+running time.}
 
@@
 \heading{Relationships between the notions.}
-Our intuition is that semantic security implies one-wayness. And, indeed, this is
+Intuition suggests that semantic security should imply one-wayness. And, indeed, this is
 the case---provided one is careful with the technical details.

### 2016-09-21 results.tex
no message

@@
 
-\jnote{Organize by scheme, not by security notions.
-}
+\subsection{A Meta-Theorem for Privacy}
+Here we prove a result that can be used to show that a large class of ``canonical''
+data structures are semantically secure, with respect to leakage of the size of the set.
+\jnote{It would not be too hard to generalize this to arbitrary data structures over
+arbitrary objects, so long as the number of distinct queries to the PRF made by $\Rep$
+depends only on ${\sf leak}$.}
+
+We first define what we mean by ``canonical.''
+
+\def\bool{\{0,1\}}
+
+\begin{definition}
+A set-multiplicity data structure $(\Rep, \Qry)$ is {\sf canonical} if
+there exist algorithms $\Rep_1, \Rep_2$, and a function
+$F: \bool^n \times \bool^{\ell_{in}} \rightarrow \bool^{\ell_{out}}$
+such that the following hold:
+\begin{itemize}
+\item $\Rep_1$ takes as input a set $S$ and outputs distinct values $x_1, \ldots, x_t \in \bool^{\ell_{in}}$,
+where $t$ depends only on~$|S|$.
+\item $\Rep_2$ takes as input $|S|$ and $y_1, \ldots, y_t \in \bool^{\ell_{out}}$, and outputs
+$\pubaux$.
+\item For any $S$, the distribution on $\pubaux$ output by $\Rep(S)$ is identical to the distribution
+on $\pubaux$ computing as follows:
+\begin{enumerate}
+\item $x_1, \ldots, x_t \getsr \Rep_1(S)$.
+\item $k \getsr \bool^n$.
+\item $\pubaux \getsr \Rep_2(|S|, F_k(x_1), \ldots, F_k(x_t))$.
+\end{enumerate}
+\end{itemize}
+In this case, we say that $(\Rep_1, \Rep_2, F)$ is the {\sf canonical representation}
+of~$\Rep$.
+\end{definition}
+\jnote{Not sure how general to make the above. Need to verify that it is general enough
+to prove security of all the constructions we care about.}
+
+We next show that any canonical data structure in which $F$ is a pseudorandom function is
+semantically secure with respect to leakage consisting of the size of the set.
+
+\begin{theorem}
+Let $\Pi=(\Rep, \Qry)$ be a canonical set-multiplicity data structure for which $\Rep$ has canonical representation
+$(\Rep_1, \Rep_2, F)$. If $F$ is a pseudorandom function, then $\Pi$
+is semantically secure with respect to leakage function ${\sf leak}(S) = |S|$.
+\end{theorem}
+\begin{proof}
+We define the following simulator $\Sim$: on input $n$, define $S^*=\{x_1, \ldots, x_n\}$
+(for distinct elements $x_1, \ldots, x_n$). Then compute
+\begin{enumerate}
+\item $x_1, \ldots, x_t \getsr \Rep_1(S^*)$,
+\item $k \getsr \bool^n$,
+\item $\pubaux \getsr \Rep_2(|S|, F_k(x_1), \ldots, F_k(x_t))$,
+\end{enumerate}
+and output $\pubaux$.
+
+For a given set $S$, define distribution $\mbox{{\sc Real}}_S$ as follows:
+\[ \{ (\pubaux, \privaux) \getsr \Rep(S) : \pubaux\},\]
+and define distribution $\mbox{{\sf Ideal}}_S$ as
+\[ \{ \pubaux \getsr \Sim(|S|) : \pubaux \}.\]
+Our goal is to show that
+
+\end{proof}
+
+%Here is a proof sketch:
+%The simulator, given n=|S|, runs the honest scheme on inputs x_1, ...,
+%x_n and outputs the public portion of the result.
+%
+%To see that this is indistinguishable from the real public portion on
+%the actual set S, consider the following hybrids:
+%H0: The real pub produced from the real set S={s_1, ..., s_n}
+%H1: Run the representation algorithm on S, but using random functions
+%in place of PRFs, and output pub.
+%H2: Run the representation algorithm on {x_1, ..., x_n}, still using
+%random functions in place of PRFs, and output pub. The claim is that
+%this is identically distributed to H1. The main observation is that
+%since we are using random functions, the inputs to the random
+%functions don't matter, subject to the technical condition that the
+%number of distinct inputs to the random functions does not change.
+%(Here is where we rely on the fact that |S|=n is known, as well as an
+%appropriate definition of "natural.")
+%H3: Run the representation algorithm on {x_1, ..., x_n}, using the
+%real Rep (with PRFs).
+
+\jnote{Organize by scheme, not by security notions.}
+
 \include{scheme-descriptions}

### 2016-09-21 syntax.tex
no message

@@
 mechanism to answer a specified collection of questions about that
-multiset.
+multiset. \jnote{I still think we should be more general, and deal
+with objects other than multisets. Actually, I think we should
+either specialize to sets or talk generically about data structures
+for arbitrary objects; talking about multisets seems to make the
+definitions more cumbersome while not adding very much in terms of
+generality.}
 %Informally, the representation should serve as a good
@@
 over $\univ$. A \emph{data structure} (for $\calS$) is a tuple
-$\setprim=(\calQ,\Rep, \Qry)$ where:
+$\setprim=(\calQ,\Rep, \Qry)$ where \jnote{I would prefer moving
+$\calQ$ out of the tuple, and instead calling it a ``data structure
+for $\calQ$ over $\calS$.''}:
 \begin{itemize}

### 2016-09-21 results.tex
proof of semantic security for "canonical" representations

@@
 Let $\Pi=(\Rep, \Qry)$ be a canonical set-multiplicity data structure for which $\Rep$ has canonical representation
-$(\Rep_1, \Rep_2, F)$. If $F$ is a pseudorandom function, then $\Pi$
+$(\Rep_1, \Rep_2, F)$. If $F$ is a $(t, \epsilon)$-pseudorandom function, then $\Pi$
 is semantically secure with respect to leakage function ${\sf leak}(S) = |S|$.
@@
 \begin{proof}
-We define the following simulator $\Sim$: on input $n$, define $S^*=\{x_1, \ldots, x_n\}$
-(for distinct elements $x_1, \ldots, x_n$). Then compute
+We define the following simulator $\Sim$: on input $n$, define $S^*=\{e_1, \ldots, e_n\}$
+(for distinct elements $e_1, \ldots, e_n$). Then compute
 \begin{enumerate}
@@
 
-For a given set $S$, define distribution $\mbox{{\sc Real}}_S$ as follows:
+\def\hyb{\mbox{{\sc Hyb}}}
+
+For a given set $S$, define distribution $\mbox{{\sc Real}}_S$ as
 \[ \{ (\pubaux, \privaux) \getsr \Rep(S) : \pubaux\},\]
@@
 \[ \{ \pubaux \getsr \Sim(|S|) : \pubaux \}.\]
-Our goal is to show that
+Our goal is to show that $\mbox{{\sc Real}}_S$ and $\mbox{{\sf Ideal}}_S$ are computationally
+indistinguishable for any set~$S$. \jnote{I'm not quite sure how to elegantly do a proof
+like this in the concrete setting.}
+To do so, first note that we can express $\mbox{{\sc Real}}_S$ as the outcome of
+the following experiment:
+\begin{enumerate}
+\item $x_1, \ldots, x_t \getsr \Rep_1(S)$.
+\item $k \getsr \bool^n$.
+\item $\pubaux \getsr \Rep_2(|S|, F_k(x_1), \ldots, F_k(x_t))$.
+\item Return $\pubaux$.
+\end{enumerate}
 
+Now, consider a hybrid distribution $\hyb_S$ computed as follows:
+\begin{enumerate}
+\item $x_1, \ldots, x_t \getsr \Rep_1(S)$.
+\item $y_1, \ldots, y_t \leftarrow \bool^{\ell_{out}}$
+\item $\pubaux \getsr \Rep_2(|S|, y_1, \ldots, y_t)$.
+\item Return $\pubaux$.
+\end{enumerate}
+It follows immediately from the fact that $F$ is a pseudorandom function (and efficiency
+of $\Rep_2$) that $\hyb_S$ is computationally indistinguishable from $\mbox{{\sc Real}}_S$.
+
+Next, consider the following distribution $\hyb'_S$:
+\begin{enumerate}
+\item $S^* := \{e_1, \ldots, e_n\}$, where $n = |S|$.
+\item $x_1, \ldots, x_{t^*} \getsr \Rep_1(S^*)$.
+\item $y_1, \ldots, y_{t^*} \leftarrow \bool^{\ell_{out}}$
+\item $\pubaux \getsr \Rep_2(|S|, y_1, \ldots, y_{t^*})$.
+\item Return $\pubaux$.
+\end{enumerate}
+We claim that $\hyb'_S$ is identically distributed to $\hyb_S$. The follows immediately from the
+observation that the distribution on $t$ (in $\hyb_S$) is identical to the distribution on~$t^*$
+(in $\hyb'_S$) by definition
+of what it means to be canonical.
+
+To complete the proof, we simply note that $\hyb'_S$ and $\mbox{{\sf Ideal}}_S$
+are computationally indistinguishable, again relying on pseudorandomness of~$F$.
 \end{proof}

### 2016-09-22 TheoremGBF_correctness.tex
GBF proof 1st draft

\heading{Garbled Bloom filter in random oracle model (ROM). }
Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.  Then $\Pi_{\mathrm{garb}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-garbled-bf} (right side).  The following result shows,

\begin{figure}[pt]
\centering
\fpage{0.95}{
\hpagessl{.4}{.55}
{
\algorithmv{$\Rep^H(S)$}\\
$M \gets 0^m$\\
for $x \in S$\\
\nudge for $j \in \{1,2,\ldots,k\}$\\
\nudge\nudge $h_j \gets H(j,x)$\\
\nudge\nudge $M[h_j] \gets 1$\\
$\pubaux \gets M$, $\privaux \gets \emptystring$\\
Return $(\pubaux,\privaux)$\\

\medskip
\algorithmv{$\Qry^H(\pubaux,\privaux,q_x)$}\\
$M\gets\pubaux$\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $h_j \gets H(j,x)$\\
\nudge if $M[h_j] \neq 1$ then Return 0\\
Return 1
}
{
\algorithmv{$\Rep^H(S)$}\\
$M \gets \mathrm{null}^m$; $\lambda \gets \calK$\\
for $x \in S$\\
\nudge $\finalshare \gets 0^\lambda$; $\emptyslot \gets -1$\\
\nudge for $j \in \{1,2,\ldots, k\}$\\
\nudge \nudge $h_j \gets H(j,x)$\\
\nudge \nudge if $M[h_j] \neq \mathrm{null}$ then\\
\nudge \nudge \nudge $\finalshare \gets \finalshare \xor M[h_j]$\\
\nudge \nudge else if $\emptyslot = -1$ then\\
\nudge \nudge \nudge $\emptyslot \gets h_j$\\
\nudge \nudge else\\
\nudge \nudge \nudge $M[h_j] \gets \bits^\lambda$\\
\nudge \nudge \nudge $\finalshare \gets \finalshare \xor M[h_j]$\\
\nudge $M[\emptyslot] \gets \finalshare \xor x$\\
for $i \in \{1,2,\ldots, m\}$\\
\nudge if $M[i] = \null$ then\\
\nudge \nudge  $M[i] \gets \bits^\lambda$\\
$\pubaux \gets M$; $\privaux \gets \lambda$\\

\medskip
\algorithmv{$\Qry(\pubaux,\privaux,q_x)$}\\
$M \gets \pubaux$, $\lambda \gets \privaux$, $x \gets 0^\lambda$\\
for $j \in \{1,2,\dots,k\}$\\
\nudge $h_j \gets H(j,x)$\\
\nudge $x \gets x \xor M[h_j]$\\
if $x = q_x$ then Return 1\\
Return 0
}
}
\caption{{\bf Left:} $\Rep$ and $\Qry$ algorithms for classic Bloom
  filter $\Pi_{\mathrm{Bloom}}$ in the ROM for a hash function $H\colon \mathbb{N} \times
  \univ \to [m]$. {\bf Right:} $\Rep$ and $\Qry$ algorithms for garbled Bloom
  filter $\Pi_{\mathrm{garbled}}$ in the ROM for a hash function $H\colon \mathbb{N} \times \calK
 \times \univ \to [m]$. For both, the query set is $\calQ=\{q_x\colon
  \univ \to \bits\}$ where $q_x(S)=1 \Leftrightarrow x \in S$.  }
\label{fig:bf-and-garbled-bf}
\end{figure}

\begin{theorem}\label{thm:gbf-correctness}
Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{garb}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described. For any adversary~$A$ that makes a total of~$q$ queries to the RO, and has time-complexity~$O(t)$,
\[
\AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A} \leq  \epsilon +  \max\left(\dfrac{1}{\dbinom{m}{k}-(q-1)}\left(1-\dfrac{n}{2^\lambda}\right), \dbinom{q}{r}\left(\dfrac{1}{2^\lambda}\right)^r \right).
\]
Here, $\epsilon$ is the collision error(described in proof).\acnote{1)Upperbound of $\epsilon$ is loosely equal to the FP upperbound in a classical BF. 2) Recommended values of $\lambda$ in GBF paper = 80 or 256. 3) For time being, number of queries to RO is assumed to include queries to $\Test$.}
\end{theorem}
\begin{proof}[\Cref{thm:gbf-correctness}]
Define an adaptive attacker $A'$ that has the following behavior. It lazily samples ~$k$ positions $i_1,i_2,\ldots,i_k$ from $[m]$, xor shares($\lambda$-bit strings) at these positions in ($M$) to get a candidate~$x$.  If $h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots \wedge h_k(x) = i_k$, then either $x \in S$ or~$x$ is a false-positive. If $x$ is not a false-positive, it repeats the attack for a different set of $k$ positions. Let $A'$ make $q$ queries to the RO; assume RO returns all $k$ hash values of each query at one go.

Let $\calF_1$ be the event that $x$ is a false-positive(in above attack).
 $$\Prob{\calF_1} = \Prob{h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots \wedge h_k(x) = i_k : x \notin S}.\Prob{x \notin S}.$$
 The probability that $x$ is not one of the $n$ $\lambda$-bit strings is $1-\dfrac{n}{2^\lambda}$, and $ \Prob{h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots \wedge\\ h_k(x) = i_k} = \dfrac{1}{\dbinom{m}{k}-(q-1)}$. It must be noted that the factor $q-1$ is due to lazy sampling of the $k$ positions. Putting together, $\Prob{\calF_1} =  \dfrac{1}{\dbinom{m}{k}-(q-1)} . \Big(1-\dfrac{n}{2^\lambda}\Big)$.  If adversary $A'$ makes $q = \dbinom{m}{k}$ queries, it has very high chance of winning(assuming $\lambda$ is large) the correctness game for $r=1$.  Let $q = (r+1) \times q_r$. For $r > 1$, if adversary $A'$ makes $q_r = \dbinom{m}{k}$ queries to find a single false-positive, and repeats this for $r$ times, it has high probability of winning the correctness game. The total queries that $A'$ makes is $(r+1)\dbinom{m}{k} = O\Big(\dbinom{m}{k}\Big)$.

% Let $A$ be an adaptive adversary(different from $A'$)\acnote{this attacker is similar to the adaptive attackers of previous proofs, where there is no known weakness of the filter in general} attacking $\Pi_{\mathrm{garb}}$, and
Suppose $A'$ also finds false-positives without exploiting the inherent weakness of $\Pi_{\mathrm{garb}}$. For this case, let $D$ be the corresponding  zero-query adversary equivalent of $A'$(shown in \ref{Fig.(xxx)}). Dong et. al. \cite{dong2013private} show that the upperbound on false-positive probability in a garbled Bloom filter for a zero-query adversary and $r=1$ is $\dfrac{1}{2^\lambda}$.   Using analyses from previous proofs, the probability that $A'$ finds $r$ false-positives is $\dbinom{q}{r}\left(\dfrac{1}{2^\lambda}\right)^r$.

Let $\calF$ be the event of finding $r$ false-positives in $\Pi_{\mathrm{garb}}$. From above analysis, we have
\begin{align*}
\Prob{\calF} =  \max\left(\dfrac{1}{\dbinom{m}{k}-(q-1)}\left(1-\dfrac{n}{2^\lambda}\right), \dbinom{q}{r}\left(\dfrac{1}{2^\lambda}\right)^r \right)
\end{align*}

A collison in a garbled Bloom filter occurs when two or more elements in a set have the same set of hash values. A collision results in false-negatives as only one of the elements is captured in the representation, and hence $\Qry$ returns 1 for this element, and 0 for others. Let $\epsilon$ be the probability of finding a false-negative in a garbled Bloom filter. As per Dong et. al. \cite{dong2013private}, the upper bound of $\epsilon$  is loosely same as the upper bound of false-positive probability of the classical Bloom filter. Since, the set $S$ is fixed at the start of the game, $\epsilon$ is more or less a contant.

Let $\calE$ be the event of finding $r$ errors in $\Pi_{\mathrm{garb}}$. Then $\Prob{\calE}$ is sum of the false-positive and false-negative probabilities. Also, $\Prob{\calE} = \AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A}$ So, 
\begin{align*}
\AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A} = \epsilon +  \max\left(\dfrac{1}{\dbinom{m}{k}-(q-1)}\left(1-\dfrac{n}{2^\lambda}\right), \dbinom{q}{r}\left(\dfrac{1}{2^\lambda}\right)^r \right)
\end{align*}

It can be observed that,
\begin{align*}
\AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A} & \leq \epsilon + \max\left(\dfrac{1}{\dbinom{m}{k}-(q-1)}, \dbinom{q}{r}\left(\dfrac{1}{2^\lambda}\right)^r \right)\\
\AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A} & \geq \epsilon + \max\left(\dfrac{1}{\dbinom{m}{k}-(q-1)}\left(1-\dfrac{n}{2^\lambda}\right), \dbinom{q}{r}\left(\frac{1}{2^\lambda}\right)^r \right)
\end{align*}
\end{proof}

### 2016-09-22 results.tex

@@
 \heading{Linear-PRF construction. }
-Here we consider a set-multiplicity data structure that was attacked by Neidermayer et al.
-in~\cite{xxx}.
-Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.
+Here we consider a set-multiplicity data structure that was attacked
+by Neidermayer et al. in~\cite{xxx}. \todo{Not actually a true
+  statement, because $\Rep$ isn't correct.
+Needs fixing.} Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.
 Then $\Pi_{\mathrm{lin}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:lin-and-ds} (left side).
@@
 
-\begin{theorem}\label{thm:lin-ss}
-Fix $k,m,n>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
-For any set~$S$, let $\leak(S)=|S|$.
+\todo{Privacy theorem for the ``plain'' linear-PRF scheme.  Should follow from Jon's general result(?)}
+
+%%%%%%%%%%%%%%%%% BIGRAM LINEAR-PRF (AKA "NEIDERMAYER")  %%%%%%%%%%%%%%%%%%%%
+\heading{Bigram Linear-PRF construction (``Neidermayer''). }
+\todo{Correctness theorem for this scheme.  Should follow pretty closely the one for ``plain'' linear-PRF.}
+
+Next we consider the privacy of this construction, relative to a leakage function that behaves as follows.
+On input a set $S=\{x_1,x_2,\ldots,x_n\}$, it computes $B_i \gets \mathsf{bigram}(x_i)$ for each $i \in [n]$.
+Then, for all $1 \leq c \leq p$, and all size-$c$ subsets $\{j_1,j_2,\ldots,j_c\} \subseteq p$, it computes $L{j_1,j_2,\ldots,j_c}=|B_{j_1} \cap B_{j_2} \cap \ldots \cap B_{j_c}|$.
+That is, it computes all of the $c$-way intersections.
+It returns $|S|=n$ and all of the $2^p -1$ intersection sizes as the leakage.
+\todo{Explain why this is plausibly leaked by $\pubaux$ for this construction.} \tsnote{This is exponential in size, so that means a simulator that reads the entire leakage will also be exponential-time in~$p$.
+} \tsnote{Should we be considering smaller, but less realistic leakage, like $\mathsf{leak}(S)=S\setminus\{x\}$.}
+
+\begin{theorem}\label{thm:bi-lin-ss}
+Fix $k,m,n>0$, and let $\Pi_{\mathrm{bi-lin}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig: neidermayer}.
+Let $\leak(S)$ be as just described.
 There exists a simulator~$\Sim$ such that, for any adversary~$A$
 \[
-\AdvPrivSS{\Pi_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B} + \mbox{[TBD]}
+\AdvPrivSS{\Pi_{\mathrm{bi-lin}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2} \mbox{[TBD]}
 \]
@@
 \end{theorem}
-\begin{proof}[Proof (sketch). ]
+\begin{proof}[Proof (sketch).
+] Adversary~$B_1^{f}$ simulates the steps of $\ExpPrivSSreal{\Pi_{\mathrm{bi-lin}}}{A}$, using its oracle to simulate~$\Rep(S)$.
+Specificially, to compute each $M_x$ index~$i$, it computes $i \gets f(b)+j\cdot F_{K_2}(b) \bmod m$ for a key~$K_2$ that it chooses.
+When~$f=F_{K_1}$ then the simulation is perfect.
+When~$f=\rho_1$ for a random function~$\rho_1$, then~$B_1$ simulates $\ExpPrivSSreal{\overline{\Pi}_{\mathrm{bi-lin}}}{A}$ where $\overline{\Rep}$ computes $i \gets \rho_1(b)+j\cdot F_{K_2}(b) \bmod m$.
+Adversary $B_2^{g}$ simulates $\ExpPrivSSreal{\overline{\Pi}_{\mathrm{bi-lin}}}{A}$, using it's oracle to compute $i \gets \rho_1(b) + j\cdot g(b) \bmod m$, where $\rho_1$ is a (lazily sampled) random function.
+When $g=F_{K_2}$ the simulation is perfect; when $g=\rho_2$ is a random function, adversary~$B_2$ simulates $\ExpPrivSSreal{\widetilde{\Pi}_{\mathrm{bi-lin}}}{A}$, where $\widetilde{\Rep}$ computes $i \gets \rho_1(b)+j\cdot\rho_2(b) \bmod m$.
+
+Our simulator $\Sim$ receives the leakage $\leak(S)$ described earlier.  With this, it simulates $\widetilde{\Rep}$ as follows.
+
+But the $\pub$ produced by $\overline{\Rep}$ has a distribution that depends only~$|S|=n$, not the specific elements of~$S$, and the other public parameters~$m,k$.
+Thus, a simulator~$\Sim$ given only $\leak(S)=|S|$ can produce a correct~$\pub$ as follows: starting with an all-zeros array~$M$ of length~$m$, uniformly sample (with replacement)~$nk$ integers in~$[m]$ and set the resulting positions of~$M$ to 1.
 \end{proof}

### 2016-09-23 results.tex
counterexample for SS-privacy of bigram linear

--- 2016-09-21 results.tex
@@
 
-\begin{theorem}\label{thm:lin-ss}
-Fix $k,m,n>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
-For any set~$S$, let $\leak(S)=|S|$.
-There exists a simulator~$\Sim$ such that, for any adversary~$A$
-\[
-\AdvPrivSS{\Pi_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B} + \mbox{[TBD]}
-\]
-where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
+\todo{Privacy theorem for the ``plain'' linear-PRF scheme.  Should follow from Jon's general result(?)}
+
+%%%%%%%%%%%%%%%%% BIGRAM LINEAR-PRF (AKA "NEIDERMAYER")  %%%%%%%%%%%%%%%%%%%%
+\heading{Bigram Linear-PRF construction (``Neidermayer''). }
+\todo{Correctness theorem for this scheme.  Should follow pretty closely the one for ``plain'' linear-PRF.}
+
+%Next we consider the privacy of this construction, relative to a leakage function that behaves as follows.
+On input a set $S=\{x_1,x_2,\ldots,x_n\}$, it computes $B_i \gets \mathsf{bigram}(x_i)$ for each $i \in [n]$.
+Then, for all $1 \leq c \leq p$, and all size-$c$ subsets $\{j_1,j_2,\ldots,j_c\} \subseteq p$, it computes $L{j_1,j_2,\ldots,j_c}=|B_{j_1} \cap B_{j_2} \cap \ldots \cap B_{j_c}|$.
+That is, it computes all of the $c$-way intersections.
+It returns $|S|=n$ and all of the $2^p -1$ intersection sizes as the leakage.
+\todo{Explain why this is plausibly leaked by $\pubaux$ for this construction.} \tsnote{This is exponential in size, so that means a simulator that reads the entire leakage will also be exponential-time in~$p$.
+} \tsnote{Should we be considering smaller, but less realistic leakage, like $\mathsf{leak}(S)=S\setminus\{x\}$.}
+
+Next we exhibit an efficient SS-privacy attack even when simulator is provided nearly the entire set.
+Consider the following leakage function.
+On input a set~$S=\{x_1,x_2,\ldots,x_n\}$, it assigns $x'_n \gets x_n[1:|x_n|-1]$ and returns $\mathsf{leak}(S)=\{x_1,x_2,\ldots,x'_n\}$.
+
+\begin{figure}
+\centering
+\fpage{.5}
+{
+\adversaryv{A}\\
+On input $\emptystring$:\\
+\nudge $x_1 \gets \mathrm{cab}$\\
+\nudge $x_2 \gets \mathrm{bab}$\\
+\nudge $z \getsr \bits$\\
+\nudge if $z=1$ then $x_3 \gets \mathrm{caba}$\\
+\nudge else $x_3 \gets \mathrm{cabc}$\\
+\nudge Return $S=\{x_1,x_2,x_3\}$\\
+On input $\pub \neq \emptystring$:\\
+\nudge $M_1,M_2,M_3 \gets \pub$\\
+\nudge $M_{1,2} \gets M_1 \vee M_2$\\
+\nudge if $z=1 \wedge \left(\mathsf{hamming}(M_{1,2} \wedge M_3) = 4k\right)$ then \\
+\nudge\nudge Return 1 \\
+\nudge if $z=0 \wedge \left(\mathsf{hamming}(M_{1,2} \wedge M_3) = 3k\right)$ then \\
+\nudge\nudge Return 1 \\
+\nudge Return 0
+}
+\caption{Adversary for Theorem~\ref{thm:bi-lin-ss}}
+\label{fig:adv-bi-lin-ss}
+\end{figure}
+
+\begin{theorem}\label{thm:bi-lin-ss}
+Let $\Pi_{\mathrm{bi-lin}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig: neidermayer}, but instantiated with $F_{K_1},F_{K_2}$ replaced by independent random functions~$\rho_1,\rho_2$ (respectively).
+Let $\leak$ be the leakage function just described.
+Let~$\univ=\{\mathrm{a,b,c}\}^*$.
+Let $n=3$,  $m=3\alpha $ for integer $\alpha >> 1$, and let, $k = \lceil \ln(2) \alpha \rceil$.\tsnote{This value of~$k$ is from the classical analysis for minimizing the FP rate for a Bloom filter, and is set this way for compatibility with classical results.
+It isn't used in any essential way in the proof sketch.}  Let~$A$ be the adversary in Figure~\ref{fig:adv-bi-lin-ss}.
+Then for any simulator $\Sim$,
+the advantage $\AdvPrivSS{\Pi_{\mathrm{bi-lin}},\leak}{A,\Sim}$ can be made arbitrarily close to $1/2$ by choice of~$\alpha$.
+
 \end{theorem}
-\begin{proof}[Proof (sketch). ]
+\begin{proof}(Sketch.)
+On input the set~$S$ produced by~$A$, the $\Rep$ algorithm turns $x_1=$'cab', $x_2=$'bab' and $x_3$ into their respective bigram sets: $B_{x_1}=\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{b}\sqcup\}$, $B_{x_2}=\{\sqcup\mathrm{b},\mathrm{ba},\mathrm{ab}, \mathrm{b}\sqcup \}$; the set $B_{x_3}$ will be either $\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{ba}, \mathrm{a}\sqcup\}$, or $\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{bc}, \mathrm{c}\sqcup\}$, each with probability 1/2.
+It then produces $alpha$-bit arrays $M_1, M_2, M_3$ by hashing the corresponding bigram sets using the hash functions $h_j(s)=\rho_1(s)+ j\rho_2(s) \bmod m$.
+Note that for sufficiently large~$m$, each of $M_1,M_2$ will contain exactly $4k$ positions set to 1; this is with overwhelming probability (up to collisions in the hash functions for different bigrams within a given bigram set).
+Likewise, $M_{1,2}=M_1 \vee M_2$ will have exactly $6k$ positions set to 1, because $B_{x_1}$ and $B_{x_2}$ share $\mathrm{ab}$ and $\mathrm{a}\sqcup$.
+
+In the case that $B_{x_3}=\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{ba}, \mathrm{a}\sqcup\}$, only one of its elements ($\mathrm{a}\sqcup$) is not in either of $B_{x_1},B_{x_2}$.
+Hence, the hamming weight of $M_{1,2}\wedge M_3$ will be $4k$.
+On the other hand, when $B_{x_3} = \{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{bc}, \mathrm{c}\sqcup\}$, two of its elements ($\mathrm{bc}, \mathrm{c}\sqcup$) are not covered by $B_{x_1},B_{x_2}$.
+In this case, the hamming weight of $M_{1,2} \wedge M_3$ will be $3k$.
+Thus $\ExpPrivSSreal{\Pi_{\mathrm{bi-lin}}}{A}=1$ with overwhelming probability.
+
+On the other hand, the simulator~$\Sim$ is given 'cab','bab','cab' as input.
+It can perfectly simulate $M_1,M_2$ by lazily sampling random functions~$\rho_1,\rho_2$ itself.
+However, it has no information about the bit~$z$, so at best it can cause~$A$ to output 1 with probabilility~$1/2$.
 \end{proof}

### 2016-09-23 results.tex
counterexample for SS-privacy of bigram linear

@@
 On input the set~$S$ produced by~$A$, the $\Rep$ algorithm turns $x_1=$'cab', $x_2=$'bab' and $x_3$ into their respective bigram sets: $B_{x_1}=\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{b}\sqcup\}$, $B_{x_2}=\{\sqcup\mathrm{b},\mathrm{ba},\mathrm{ab}, \mathrm{b}\sqcup \}$; the set $B_{x_3}$ will be either $\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{ba}, \mathrm{a}\sqcup\}$, or $\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{bc}, \mathrm{c}\sqcup\}$, each with probability 1/2.
-It then produces $alpha$-bit arrays $M_1, M_2, M_3$ by hashing the corresponding bigram sets using the hash functions $h_j(s)=\rho_1(s)+ j\rho_2(s) \bmod m$.
+It then produces $\alpha$-bit arrays $M_1, M_2, M_3$ by hashing the corresponding bigram sets using the hash functions $h_j(s)=\rho_1(s)+ j\rho_2(s) \bmod m$.
 Note that for sufficiently large~$m$, each of $M_1,M_2$ will contain exactly $4k$ positions set to 1; this is with overwhelming probability (up to collisions in the hash functions for different bigrams within a given bigram set).

### 2016-09-24 notions.tex
moving NY comparison to its own file, and placing in an appendix

@@
 
-\jnote{Note~$q$ is overloaded here.}
-
 \todo{Explain that the case of $r=1$ does not necessarily imply anything for $r>1$: can have a scheme
@@
 any more).}
-
-\heading{Comparison to the Naor-Yogev definition.}
-The structure of the Naor-Yogev definition is different from ours.
-Lifting their definition\footnote{They focus specifically on set-representation data
-structures
-with no false negatives, and their data-structure syntax
-does not distinguish public and private portions of the representation. Nevertheless, it is straightforward
-to extend their definition to more closely match ours.}
-to our setting,
-the experiment is similar but the attacker
-succeeds only if it outputs a (single) query $\qry$ for which
-$\Qry(\pubaux,\privaux, \qry) \neq \qry(S)$  \emph{subject to the restriction that it did not
-previously query $\qry$ to its $\TestOracle$ oracle}. We refer to
-Figure~\ref{fig:NYcorrectness} for a definition of the relevant experiment.
-We define the advantage of adversary~$A$ as
-$\NYAdvCorrect{\Pi}{A} = \Prob{\NYExpCorrect{\Pi}{A}=1}$,
-and write $\NYAdvCorrect{\Pi,r}{t,q}$ for the maximum over
-all~$t$-time adversaries that ask at most~$q$ queries. We say that a
-data structure~$\Pi$ is $(t,q,\epsilon)$-NY-correct if
-$\NYAdvCorrect{\Pi}{t,q} \leq \epsilon$. \jnote{This should all probably
-move to an appendix; it's a lot of notation to digest for something we never use again
-in the paper.}
-
-\jnote{Just noticed something (else) odd about the NY definition: we cannot assume w.l.o.g.\
-that $A$ makes exactly $q$ queries, and in fact it is possible to have cases where increasing
-the number of queries the attacker makes can decrease its advantage! This seems like
-another drawback of the definition.}\tsnote{Really?  That seems worth
-pointing out, as part of our list of complaints.}
-
-\begin{figure}[htp]
-\centering
-\fpage{.6}{
-\hpagess{.5}{.45}
-{
-\experimentv{$\NYExpCorrect{\setprim}{A}$}\\
-$S \getsr A$\\
-$\mathcal{C} \gets \emptyset$\\
-%$\mathrm{err}\gets 0$\\
-$(\pubaux,\privaux) \getsr \Rep(S)$\\
-$\qry \getsr A^{\TestOracle}(\pubaux)$\\
-if $\left(\qry \not \in \mathcal{C}\right.$ and \\
-\nudge $\left.\Qry(\pubaux,\privaux,\qry) \neq \qry(S)\right)$ \\
-\nudge \nudge then Return 1\\
-Return 0
-}
-%
-{
-\oracle{$\TestOracle(q)$}\\
-$a \gets \Qry(\pubaux,\privaux,q)$\\
-$\mathcal{C} \gets \mathcal{C} \cup \{q\}$ \\
-%\nudge $\mathrm{err}\gets\mathrm{err}+1$\\
-Return~$a$
-}
-}
-\caption{The Naor-Yogev definition of
-correctness, adapted to our setting.}
-\label{fig:NYcorrectness}
-\end{figure}
-
-With the above in place we can now relate their definition to ours.
-
-\jnote{Do we have a compelling example of why the definition in Figure~\ref{fig:correctness}
-is ``better'' than the definition in
-Figure~\ref{fig:NYcorrectness}?}\tsnote{I don't know, but we do seem
-to have a compelling list of shortcomings of their notion, which ours
-doesn't seem to suffer. Anyway, it's a bit of an unfair comparison, in
-their favor.  You're lifting their notion to ours, which is more
-general.  And by the time we get to that, we have already done them
-the favor of cleaning up the syntax, so that their ``lifted'' notion
-looks better than it was.} \jnote{I agree, it's just that once we have ``lifted'' it
-appropriately, it's not clear what's wrong with it and why we introduce a different
-style of definition.}
-
-\begin{theorem}
-If $\Pi$ is $(t,q,\epsilon)$-NY-correct, then it is also
-$(t, q', r, q'\epsilon/r)$-correct for any $q' \leq q+1$ and $r\geq
-1$.
-\end{theorem}
-\begin{proof}
-Let $\Pi$ be a data structure that is $(t,q,\epsilon)$-NY-correct,
-and assume that for some $q' \leq q+1$ and
-$r \geq 1$
-there is an adversary $A$ running in time~$t$
-and making $q'$ oracle queries such that
-$\AdvCorrect{\Pi,r}{A} > q'\epsilon/r$.
-(Note that
-we may assume $A$ always makes exactly $q'$ queries without loss of generality.)
-With probability at least
-$q'\epsilon/r$ in an execution of $\ExpCorrect{\Pi,r}{A}$, we have that
-$A$ makes at least $r$ distinct queries to $\TestOracle$ for which
-an incorrect answer is returned. Let $A'$ be the algorithm that simply
-runs~$A$, but chooses
-uniformly one of the $q'$ queries of $A$ to its $\TestOracle$ oracle and outputs that query
-as its final output. Then with probability at least $r/q' \cdot (q'\epsilon/r)=\epsilon$
-the query chosen by $A'$
-leads to an incorrect answer, and was not previously asked to the $\TestOracle$ oracle.
-Since the running time of $A'$ is at most $t$, and it makes at most $q'-1 \leq q$ queries
-to its oracle, this is a contradiction.
-\end{proof}
-
-\jnote{The above is tight, at least for $r=1$. Specifically, consider a scheme
-in which every query is independently
-answered incorrectly with probability~$\epsilon$. Such a
-scheme will be $(t,q,\epsilon)$-NY-correct
-for any $t, q$, however an adversary making $q=1/\epsilon$ queries has constant advantage
-under our correctness definition (for $r=1$).}
-
-\begin{theorem}
-If $\Pi$ is $(t, q, 1, \epsilon)$-correct, then it is also $(t, q-1, \epsilon)$-NY-correct.
-\end{theorem}
-
-\begin{proof}
-Let $\Pi$ be a data structure that is $(t,q,1,\epsilon)$-correct,
-and assume
-there is an adversary $A$ running in time~$t$
-and making at most $q-1$ oracle queries such that
-$\NYAdvCorrect{\Pi}{A} > \epsilon$.
-Let $A'$ be the algorithm that simply
-runs~$A$, passing the oracle queries of~$A$ to its own oracle, until~$A$ terminates
-with output~$\qry$; then, $A'$ sends~$\qry$ to $\TestOracle$. It is immediate that $A'$ makes at most $q$ oracle queries, and
-$\AdvCorrect{\Pi,1}{A'} \geq \NYAdvCorrect{\Pi}{A}$, a contradiction.
-\end{proof}
-
-\begin{theorem}
-There exists a data structure $\Pi$ that
-is $(t, q, 2, 0)$-correct, but is not $(t, 0, \epsilon)$-NY-correct
-for any $\epsilon<1$.
-\end{theorem}
-\begin{proof}
-Let $\Pi$ be the set-membership data structure in which $\Rep(S)$ outputs
-$\pubaux=\privaux=S$, and
-$\Qry(S, S, \qry_y)$ outputs $\qry_y(S)$ if $y \neq x$ but outputs $1-\qry_x(S)$ otherwise,
-where $x \in {\cal X}$ is a fixed element of the universe. This
-scheme always answers incorrectly for a single, fixed query, and answers
-correctly for every other query. The theorem follows.
-\end{proof}
-
-\jnote{I'm not sure what to conclude from any of the results above. The proofs
-are also all trivial.} \tsnote{Trivial or not, it's all part of the
-overall contribution, which is putting this topic on a solid
-foundation.  We can move it all to an appendix, but I still see it as
-very worthwhile.} \jnote{It's worth having for completeness, I'm just not sure
-what we (or the reader) is supposed to do with it. It's not like we can draw
-any simple conclusions like ``our definition implies theirs'' or anything.}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 

### 2016-09-24 ny-def-comparison.tex
moving NY comparison to its own file, and placing in an appendix

\section{Comparison to the Naor-Yogev definition.}
The structure of the Naor-Yogev definition is different from ours.
Lifting their definition\footnote{They focus specifically on set-representation data
structures
with no false negatives, and their data-structure syntax
does not distinguish public and private portions of the representation. Nevertheless, it is straightforward
to extend their definition to more closely match ours.}
to our setting,
the experiment is similar but the attacker
succeeds only if it outputs a (single) query $\qry$ for which
$\Qry(\pubaux,\privaux, \qry) \neq \qry(S)$  \emph{subject to the restriction that it did not
previously query $\qry$ to its $\TestOracle$ oracle}. We refer to
Figure~\ref{fig:NYcorrectness} for a definition of the relevant experiment.
We define the advantage of adversary~$A$ as
$\NYAdvCorrect{\Pi}{A} = \Prob{\NYExpCorrect{\Pi}{A}=1}$,
and write $\NYAdvCorrect{\Pi,r}{t,q}$ for the maximum over
all~$t$-time adversaries that ask at most~$q$ queries. We say that a
data structure~$\Pi$ is $(t,q,\epsilon)$-NY-correct if
$\NYAdvCorrect{\Pi}{t,q} \leq \epsilon$. \jnote{This should all probably
move to an appendix; it's a lot of notation to digest for something we never use again
in the paper.}

\jnote{Just noticed something (else) odd about the NY definition: we cannot assume w.l.o.g.\
that $A$ makes exactly $q$ queries, and in fact it is possible to have cases where increasing
the number of queries the attacker makes can decrease its advantage! This seems like
another drawback of the definition.}\tsnote{Really?  That seems worth
pointing out, as part of our list of complaints.}

\begin{figure}[htp]
\centering
\fpage{.6}{
\hpagess{.5}{.45}
{
\experimentv{$\NYExpCorrect{\setprim}{A}$}\\
$S \getsr A$\\
$\mathcal{C} \gets \emptyset$\\
%$\mathrm{err}\gets 0$\\
$(\pubaux,\privaux) \getsr \Rep(S)$\\
$\qry \getsr A^{\TestOracle}(\pubaux)$\\
if $\left(\qry \not \in \mathcal{C}\right.$ and \\
\nudge $\left.\Qry(\pubaux,\privaux,\qry) \neq \qry(S)\right)$ \\
\nudge \nudge then Return 1\\
Return 0
}
%
{
\oracle{$\TestOracle(\qry)$}\\
$a \gets \Qry(\pubaux,\privaux,\qry)$\\
$\mathcal{C} \gets \mathcal{C} \cup \{\qry\}$ \\
%\nudge $\mathrm{err}\gets\mathrm{err}+1$\\
Return~$a$
}
}
\caption{The Naor-Yogev definition of
correctness, adapted to our setting.}
\label{fig:NYcorrectness}
\end{figure}

With the above in place we can now relate their definition to ours.

\jnote{Do we have a compelling example of why the definition in Figure~\ref{fig:correctness}
is ``better'' than the definition in
Figure~\ref{fig:NYcorrectness}?}\tsnote{I don't know, but we do seem
to have a compelling list of shortcomings of their notion, which ours
doesn't seem to suffer. Anyway, it's a bit of an unfair comparison, in
their favor.  You're lifting their notion to ours, which is more
general.  And by the time we get to that, we have already done them
the favor of cleaning up the syntax, so that their ``lifted'' notion
looks better than it was.} \jnote{I agree, it's just that once we have ``lifted'' it
appropriately, it's not clear what's wrong with it and why we introduce a different
style of definition.}

\begin{theorem}
If $\Pi$ is $(t,q,\epsilon)$-NY-correct, then it is also
$(t, q', r, q'\epsilon/r)$-correct for any $q' \leq q+1$ and $r\geq
1$.
\end{theorem}
\begin{proof}
Let $\Pi$ be a data structure that is $(t,q,\epsilon)$-NY-correct,
and assume that for some $q' \leq q+1$ and
$r \geq 1$
there is an adversary $A$ running in time~$t$
and making $q'$ oracle queries such that
$\AdvCorrect{\Pi,r}{A} > q'\epsilon/r$.
(Note that
we may assume $A$ always makes exactly $q'$ queries without loss of generality.)
With probability at least
$q'\epsilon/r$ in an execution of $\ExpCorrect{\Pi,r}{A}$, we have that
$A$ makes at least $r$ distinct queries to $\TestOracle$ for which
an incorrect answer is returned. Let $A'$ be the algorithm that simply
runs~$A$, but chooses
uniformly one of the $q'$ queries of $A$ to its $\TestOracle$ oracle and outputs that query
as its final output. Then with probability at least $r/q' \cdot (q'\epsilon/r)=\epsilon$
the query chosen by $A'$
leads to an incorrect answer, and was not previously asked to the $\TestOracle$ oracle.
Since the running time of $A'$ is at most $t$, and it makes at most $q'-1 \leq q$ queries
to its oracle, this is a contradiction.
\end{proof}

\jnote{The above is tight, at least for $r=1$. Specifically, consider a scheme
in which every query is independently
answered incorrectly with probability~$\epsilon$. Such a
scheme will be $(t,q,\epsilon)$-NY-correct
for any $t, q$, however an adversary making $q=1/\epsilon$ queries has constant advantage
under our correctness definition (for $r=1$).}

\begin{theorem}
If $\Pi$ is $(t, q, 1, \epsilon)$-correct, then it is also $(t, q-1, \epsilon)$-NY-correct.
\end{theorem}

\begin{proof}
Let $\Pi$ be a data structure that is $(t,q,1,\epsilon)$-correct,
and assume
there is an adversary $A$ running in time~$t$
and making at most $q-1$ oracle queries such that
$\NYAdvCorrect{\Pi}{A} > \epsilon$.
Let $A'$ be the algorithm that simply
runs~$A$, passing the oracle queries of~$A$ to its own oracle, until~$A$ terminates
with output~$\qry$; then, $A'$ sends~$\qry$ to $\TestOracle$. It is immediate that $A'$ makes at most $q$ oracle queries, and
$\AdvCorrect{\Pi,1}{A'} \geq \NYAdvCorrect{\Pi}{A}$, a contradiction.
\end{proof}

\begin{theorem}
There exists a data structure $\Pi$ that
is $(t, q, 2, 0)$-correct, but is not $(t, 0, \epsilon)$-NY-correct
for any $\epsilon<1$.
\end{theorem}
\begin{proof}
Let $\Pi$ be the set-membership data structure in which $\Rep(S)$ outputs
$\pubaux=\privaux=S$, and
$\Qry(S, S, \qry_y)$ outputs $\qry_y(S)$ if $y \neq x$ but outputs $1-\qry_x(S)$ otherwise,
where $x \in {\cal X}$ is a fixed element of the universe. This
scheme always answers incorrectly for a single, fixed query, and answers
correctly for every other query. The theorem follows.
\end{proof}

\jnote{I'm not sure what to conclude from any of the results above. The proofs
are also all trivial.} \tsnote{Trivial or not, it's all part of the
overall contribution, which is putting this topic on a solid
foundation.  We can move it all to an appendix, but I still see it as
very worthwhile.} \jnote{It's worth having for completeness, I'm just not sure
what we (or the reader) is supposed to do with it. It's not like we can draw
any simple conclusions like ``our definition implies theirs'' or anything.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-09-24 syntax.tex
moving NY comparison to its own file, and placing in an appendix

@@
 $\calQ$ out of the tuple, and instead calling it a ``data structure
-for $\calQ$ over $\calS$.''}:
+for $\calQ$ over $\calS$.''}\tsnote{But $\Qry$ really is tied to
+$\calQ$, as those are the only queries upon which $\Qry$ is defined to
+operate.  So, if anything, I would support removing $\calQ$ from the
+high-level API, and just explaining what it is as part of the
+description of $\Qry$}:
 \begin{itemize}
@@
 
+\tsnote{needs updating, since $\Sigma$ is gone, and the range of
+  $\Rep$ is just $\bits^*$ with implicit encoding of whatever is the
+  ``natural'' way to think about $\pubaux$ (e.g. counters, xor-shares)}
 By setting $\Sigma=\bits^L$ for a specified $L>0$, we can capture

### 2016-09-25 results.tex
commenting on Jon's meta-theorem

@@
 
-\def\bool{\{0,1\}}
+\def\bits{\{0,1\}}
 
@@
 there exist algorithms $\Rep_1, \Rep_2$, and a function
-$F: \bool^n \times \bool^{\ell_{in}} \rightarrow \bool^{\ell_{out}}$
+$F: \calK \times \bits^{\ell_{in}} \rightarrow \bits^{\ell_{out}}$
 such that the following hold:
 \begin{itemize}
-\item $\Rep_1$ takes as input a set $S$ and outputs distinct values $x_1, \ldots, x_t \in \bool^{\ell_{in}}$,
-where $t$ depends only on~$|S|$.
-\item $\Rep_2$ takes as input $|S|$ and $y_1, \ldots, y_t \in \bool^{\ell_{out}}$, and outputs
+\item $\Rep_1$ takes as input a set $S=\{x_1,\ldots,x_n\}$ and outputs distinct values $s_1, \ldots, s_t \in \bits^{\ell_{in}}$,
+where $t$ depends only on~$n$.
+\item $\Rep_2$ takes as input $n$ and $y_1, \ldots, y_t \in \bits^{\ell_{out}}$, and outputs
 $\pubaux$.
@@
 \begin{enumerate}
-\item $x_1, \ldots, x_t \getsr \Rep_1(S)$.
-\item $k \getsr \bool^n$.
-\item $\pubaux \getsr \Rep_2(|S|, F_k(x_1), \ldots, F_k(x_t))$.
+\item $s_1, \ldots, s_t \getsr \Rep_1(S)$.
+\item $K \getsr \calK$.
+\item $\pubaux \getsr \Rep_2(n, F_K(s_1), \ldots,F_K(s_t))$. 
 \end{enumerate}
@@
 In this case, we say that $(\Rep_1, \Rep_2, F)$ is the {\sf canonical representation}
-of~$\Rep$.
+of~$\Rep$. \tsnote{Seems odd to call it this without explaining how
+  this canonical representation handles $\privaux$, too.  }
 \end{definition}
@@
 to prove security of all the constructions we care about.}
-
+\tsnote{Would be good to give an example or two of the schemes this
+  covers.  Domain-separated PRF BF, for example.  I think it covers
+  classical BF, too, if $F_K(s)=s$ for all $K \in \calK$, $\Rep_1$
+  simply returns the elements of~$S$, and $\Rep_2$ actually picks hash
+  functions and does the hashing. It does not cover
+  linear-PRF or Neidermayer. }
 We next show that any canonical data structure in which $F$ is a pseudorandom function is
@@
 Let $\Pi=(\Rep, \Qry)$ be a canonical set-multiplicity data structure for which $\Rep$ has canonical representation
-$(\Rep_1, \Rep_2, F)$. If $F$ is a $(t, \epsilon)$-pseudorandom function, then $\Pi$
-is semantically secure with respect to leakage function ${\sf leak}(S) = |S|$.
+$(\Rep_1, \Rep_2, F)$. If $F$ is a $(t, \epsilon)$-pseudorandom
+function \tsnote{overloading~$t$}, then $\Pi$ is semantically secure
+with respect to leakage function ${\sf leak}(S) = |S|$.
+\tsnote{We have a mixture of styles of theorem statements, resource-parameterized statements vs.\ ``verbose'' concrete statements.  We
+  need to make things uniform.}
 \end{theorem}
@@
 \begin{enumerate}
-\item $x_1, \ldots, x_t \getsr \Rep_1(S^*)$,
-\item $k \getsr \bool^n$,
-\item $\pubaux \getsr \Rep_2(|S|, F_k(x_1), \ldots, F_k(x_t))$,
+\item $s_1, \ldots, s_t \getsr \Rep_1(S^*)$,
+\item $K \getsr \calK$,
+\item $\pubaux \getsr \Rep_2(|S|, F_K(s_1), \ldots, F_K(s_t))$,
 \end{enumerate}
@@
 indistinguishable for any set~$S$. \jnote{I'm not quite sure how to elegantly do a proof
-like this in the concrete setting.}
+like this in the concrete setting.}\tsnote{I think you just follow the
+sketch that I typeset for the Domain-Separated PRF scheme. (I'll embed
+notes below, too.) The bound will be exactly what is there, shoudl be able to just cut-and-paste,
+basically.  All that's needed, I think, is to do resource accounting
+for $\Sim$ and the PRF-adversary~$B$.}
 To do so, first note that we can express $\mbox{{\sc Real}}_S$ as the outcome of
-the following experiment:
+the following experiment: \tsnote{I'd call this ``Game $G0$''...}
 \begin{enumerate}
-\item $x_1, \ldots, x_t \getsr \Rep_1(S)$.
-\item $k \getsr \bool^n$.
-\item $\pubaux \getsr \Rep_2(|S|, F_k(x_1), \ldots, F_k(x_t))$.
+\item $s_1, \ldots, s_t \getsr \Rep_1(S)$.
+\item $K \getsr \bits^n$.
+\item $\pubaux \getsr \Rep_2(|S|, F_k(s_1), \ldots, F_k(s_t))$.
 \item Return $\pubaux$.
@@
 Now, consider a hybrid distribution $\hyb_S$ computed as follows:
+\tsnote{...and this ``Game $G1$''...}
 \begin{enumerate}
-\item $x_1, \ldots, x_t \getsr \Rep_1(S)$.
-\item $y_1, \ldots, y_t \leftarrow \bool^{\ell_{out}}$
+\item $s_1, \ldots, s_t \getsr \Rep_1(S)$.
+\item $y_1, \ldots, y_t \leftarrow \bits^{\ell_{out}}$
 \item $\pubaux \getsr \Rep_2(|S|, y_1, \ldots, y_t)$.
@@
 of $\Rep_2$) that $\hyb_S$ is computationally indistinguishable from $\mbox{{\sc Real}}_S$.
-
+\tsnote{...and then it's clear that the difference between the
+  probability of $G0 \outputs 1$ and $G1 \outputs 1$ is exactly the
+  PRF advantage of~$B$, who simply uses it's oracle to simulate calls
+  to $F_K$ prior to running $\Rep_2$...}
 Next, consider the following distribution $\hyb'_S$:
@@
 \item $S^* := \{e_1, \ldots, e_n\}$, where $n = |S|$.
-\item $x_1, \ldots, x_{t^*} \getsr \Rep_1(S^*)$.
-\item $y_1, \ldots, y_{t^*} \leftarrow \bool^{\ell_{out}}$
+\item $s_1, \ldots, s_{t^*} \getsr \Rep_1(S^*)$.
+\item $y_1, \ldots, y_{t^*} \leftarrow \bits^{\ell_{out}}$
 \item $\pubaux \getsr \Rep_2(|S|, y_1, \ldots, y_{t^*})$.
@@
 of what it means to be canonical.
+\tsnote{...and it is clear that the distriubtion of everything is the
+  same as in Game $G1$, so we are done. }
 
@@
 
-\jnote{Organize by scheme, not by security notions.}
+%\jnote{Organize by scheme, not by security notions.}
 
@@
 
-\todo{Privacy theorem for the ``plain'' linear-PRF scheme.  Should follow from Jon's general result(?)}
+\todo{Privacy theorem for the ``plain'' linear-PRF scheme. Does not
+  follow from Jon's general theorem.}
 

### 2016-09-25 results.tex
comments on Jon's meta-theorem, and instructions added to DS privacy result on how to handle in light of Jon's result

@@
 
-%%%%%%%%%%
 \begin{theorem}\label{thm:ds-ss}
@@
 \end{theorem}
-\begin{proof}[Proof (sketch). ]
+\begin{proof}[Proof (sketch). ] \todo{Move this sketch to be a proof
+    of Jon's meta-result. Downgrade theorem to be a corollary of that
+    result, the proof simply being a description of how $\Rep$
+    decomposes into $\Rep_1$ and $\Rep_2$.}
 Adversary~$B^{f}$ simulates the steps of $\ExpPrivSSreal{\Pi_{\mathrm{ds}}}{A}$, using its oracle to simuate~$\Rep(S)$.
@@
 \end{proof}
-%%%%%%%%%%
 

### 2016-09-25 results.tex
comments on Jon's meta-theorem, and instructions added to DS privacy result on how to handle in light of Jon's result
starting to generalize canonical representation def to multiple PRF keys

@@
 \begin{enumerate}
-\item $s_1, \ldots, s_t \getsr \Rep_1(S)$.
-\item $K \getsr \calK$.
-\item $\pubaux \getsr \Rep_2(n, F_K(s_1), \ldots,F_K(s_t))$. 
+\item $s_1, \ldots, s_t \getsr \Rep_1(S)$;
+\item $K_1,K_2,\ldots,K_p \getsr \calK$ for some fixed number of keys~$p$;
+\item $\pubaux \getsr \Rep_2(n, \{F_{K_j}(s_1), \ldots,F_{K_j}(s_t)\}_{j\in[p]})$. 
 \end{enumerate}
@@
   simply returns the elements of~$S$, and $\Rep_2$ actually picks hash
-  functions and does the hashing. It does not cover
+  functions and does the hashing. (Although the following theorem does
+  not work in this case, of course.) It does not cover
   linear-PRF or Neidermayer. }
-We next show that any canonical data structure in which $F$ is a pseudorandom function is
+We next show that any canonical data structure in which~$F$ is a pseudorandom function is
 semantically secure with respect to leakage consisting of the size of the set.

### 2016-09-25 TheoremGBF_correctness.tex
GBF proof in appendix

@@
 Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.  Then $\Pi_{\mathrm{garb}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-garbled-bf} (right side).  The following result shows,
-
-\begin{figure}[pt]
-\centering
-\fpage{0.95}{
-\hpagessl{.4}{.55}
-{
-\algorithmv{$\Rep^H(S)$}\\
-$M \gets 0^m$\\
-for $x \in S$\\
-\nudge for $j \in \{1,2,\ldots,k\}$\\
-\nudge\nudge $h_j \gets H(j,x)$\\
-\nudge\nudge $M[h_j] \gets 1$\\
-$\pubaux \gets M$, $\privaux \gets \emptystring$\\
-Return $(\pubaux,\privaux)$\\
-
-\medskip
-\algorithmv{$\Qry^H(\pubaux,\privaux,q_x)$}\\
-$M\gets\pubaux$\\
-for $j \in \{1,2,\ldots,k\}$\\
-\nudge $h_j \gets H(j,x)$\\
-\nudge if $M[h_j] \neq 1$ then Return 0\\
-Return 1
-}
-{
-\algorithmv{$\Rep^H(S)$}\\
-$M \gets \mathrm{null}^m$; $\lambda \gets \calK$\\
-for $x \in S$\\
-\nudge $\finalshare \gets 0^\lambda$; $\emptyslot \gets -1$\\
-\nudge for $j \in \{1,2,\ldots, k\}$\\
-\nudge \nudge $h_j \gets H(j,x)$\\
-\nudge \nudge if $M[h_j] \neq \mathrm{null}$ then\\
-\nudge \nudge \nudge $\finalshare \gets \finalshare \xor M[h_j]$\\
-\nudge \nudge else if $\emptyslot = -1$ then\\
-\nudge \nudge \nudge $\emptyslot \gets h_j$\\
-\nudge \nudge else\\
-\nudge \nudge \nudge $M[h_j] \gets \bits^\lambda$\\
-\nudge \nudge \nudge $\finalshare \gets \finalshare \xor M[h_j]$\\
-\nudge $M[\emptyslot] \gets \finalshare \xor x$\\
-for $i \in \{1,2,\ldots, m\}$\\
-\nudge if $M[i] = \null$ then\\
-\nudge \nudge  $M[i] \gets \bits^\lambda$\\
-$\pubaux \gets M$; $\privaux \gets \lambda$\\
-
-\medskip
-\algorithmv{$\Qry(\pubaux,\privaux,q_x)$}\\
-$M \gets \pubaux$, $\lambda \gets \privaux$, $x \gets 0^\lambda$\\
-for $j \in \{1,2,\dots,k\}$\\
-\nudge $h_j \gets H(j,x)$\\
-\nudge $x \gets x \xor M[h_j]$\\
-if $x = q_x$ then Return 1\\
-Return 0
-}
-}
-\caption{{\bf Left:} $\Rep$ and $\Qry$ algorithms for classic Bloom
-  filter $\Pi_{\mathrm{Bloom}}$ in the ROM for a hash function $H\colon \mathbb{N} \times
-  \univ \to [m]$. {\bf Right:} $\Rep$ and $\Qry$ algorithms for garbled Bloom
-  filter $\Pi_{\mathrm{garbled}}$ in the ROM for a hash function $H\colon \mathbb{N} \times \calK
- \times \univ \to [m]$. For both, the query set is $\calQ=\{q_x\colon
-  \univ \to \bits\}$ where $q_x(S)=1 \Leftrightarrow x \in S$.  }
-\label{fig:bf-and-garbled-bf}
-\end{figure}
 
@@
 3) For time being, number of queries to RO is assumed to include queries to $\Test$.}
+It can be observed that, if $\dbinom{m}{k} << 2^\lambda$, and $2^\lambda >> n$
+\begin{align*}
+\AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A} & \geq \epsilon + \left(\dfrac{1}{\dbinom{m}{k}-(q-1)}\right)
+\end{align*}
+Also, if $\dbinom{m}{k} >> 1$, and $2^\lambda >> n$
+\begin{align*}
+\AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A} & \leq \epsilon + \max\left(\dfrac{1}{\dbinom{m}{k}-(q-1)}, \dbinom{q}{r}\left(\dfrac{1}{2^\lambda}\right)^r \right)
+\end{align*}
 \end{theorem}
-\begin{proof}[\Cref{thm:gbf-correctness}]
+\begin{proof}%[\Cref{thm:gbf-correctness}]
 Define an adaptive attacker $A'$ that has the following behavior.
@@
 \cite{dong2013private} show that the upperbound on false-positive probability in a garbled Bloom filter for a zero-query adversary and $r=1$ is $\dfrac{1}{2^\lambda}$.
-Using analyses from previous proofs, the probability that $A'$ finds $r$ false-positives is $\dbinom{q}{r}\left(\dfrac{1}{2^\lambda}\right)^r$.
+Using analyses from previous proofs, the probability that $A'$ finds $r$ false-positives is upperbounded by  $\dbinom{q}{r}\left(\dfrac{1}{2^\lambda}\right)^r$.
 
@@
 \begin{align*}
-\Prob{\calF} =  \max\left(\dfrac{1}{\dbinom{m}{k}-(q-1)}\left(1-\dfrac{n}{2^\lambda}\right), \dbinom{q}{r}\left(\dfrac{1}{2^\lambda}\right)^r \right)
+\Prob{\calF} \leq  \max\left(\dfrac{1}{\dbinom{m}{k}-(q-1)}\left(1-\dfrac{n}{2^\lambda}\right), \dbinom{q}{r}\left(\dfrac{1}{2^\lambda}\right)^r \right)
 \end{align*}
 
-A collison in a garbled Bloom filter occurs when two or more elements in a set have the same set of hash values.
+A collison in a garbled Bloom filter occurs when two or more distinct elements in a set have the same set of hash values.
 A collision results in false-negatives as only one of the elements is captured in the representation, and hence $\Qry$ returns 1 for this element, and 0 for others.
@@
 \begin{align*}
-\AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A} = \epsilon +  \max\left(\dfrac{1}{\dbinom{m}{k}-(q-1)}\left(1-\dfrac{n}{2^\lambda}\right), \dbinom{q}{r}\left(\dfrac{1}{2^\lambda}\right)^r \right)
+\AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A} \leq \epsilon +  \max\left(\dfrac{1}{\dbinom{m}{k}-(q-1)}\left(1-\dfrac{n}{2^\lambda}\right), \dbinom{q}{r}\left(\dfrac{1}{2^\lambda}\right)^r \right)
 \end{align*}
 
-It can be observed that,
-\begin{align*}
-\AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A} & \leq \epsilon + \max\left(\dfrac{1}{\dbinom{m}{k}-(q-1)}, \dbinom{q}{r}\left(\dfrac{1}{2^\lambda}\right)^r \right)\\
-\AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A} & \geq \epsilon + \max\left(\dfrac{1}{\dbinom{m}{k}-(q-1)}\left(1-\dfrac{n}{2^\lambda}\right), \dbinom{q}{r}\left(\frac{1}{2^\lambda}\right)^r \right)
-\end{align*}
 \end{proof}

### 2016-09-26 results.tex
changing back
cheers

@@
 on $\pubaux$ computing as follows: 
-\begin{enumerate}
-\item $s_1, \ldots, s_t \getsr \Rep_1(S)$;
-\item $K_1,K_2,\ldots,K_p \getsr \calK$ for some fixed number of keys~$p$;
-\item $\pubaux \getsr \Rep_2(n, \{F_{K_j}(s_1), \ldots,F_{K_j}(s_t)\}_{j\in[p]})$. 
-\end{enumerate}
+(1) $s_1, \ldots, s_t \getsr \Rep_1(S)$;
+(2) $K \getsr \calK$;
+(3) $\pubaux \getsr \Rep_2(n, F_{K}(s_1), \ldots,F_{K}(s_t))$. 
+%\item $K_1,K_2,\ldots,K_p \getsr \calK$ for some fixed number of keys~$p$;
+%\item $\pubaux \getsr \Rep_2(n, \{F_{K_j}(s_1),
+%\ldots,F_{K_j}(s_t)\}_{j\in[p]})$. 
 \end{itemize}
@@
 \begin{proof}
-We define the following simulator $\Sim$: on input $n$, define $S^*=\{e_1, \ldots, e_n\}$
-(for distinct elements $e_1, \ldots, e_n$). Then compute
-\begin{enumerate}
-\item $s_1, \ldots, s_t \getsr \Rep_1(S^*)$,
-\item $K \getsr \calK$,
-\item $\pubaux \getsr \Rep_2(|S|, F_K(s_1), \ldots, F_K(s_t))$,
-\end{enumerate}
-and output $\pubaux$.
+We define a simulator $\Sim$ as follows. On input $n$, $\Sim$ fixes a
+set $S^*=\{e_1, \ldots, e_n\}$. In then computes:
+(1) $s_1, \ldots, s_t \getsr \Rep_1(S^*)$;
+(2) $K \getsr \calK$;
+(3) $\pubaux \getsr \Rep_2(|S|, F_K(s_1), \ldots, F_K(s_t))$, and
+finally returns $\pubaux$.
 

### 2016-09-26 TheoremGBF_correctness.tex
GBF Proof update

@@
 \]
+\[
+\AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A}  \geq \epsilon + \left(\dfrac{1}{\dbinom{m}{k}-(q-1)}\right)
+\]
 Here, $\epsilon$ is the collision error(described in proof).\acnote{1)Upperbound of $\epsilon$ is loosely equal to the FP upperbound in a classical BF.
 2) Recommended values of $\lambda$ in GBF paper = 80 or 256.
-3) For time being, number of queries to RO is assumed to include queries to $\Test$.}
-It can be observed that, if $\dbinom{m}{k} << 2^\lambda$, and $2^\lambda >> n$
-\begin{align*}
-\AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A} & \geq \epsilon + \left(\dfrac{1}{\dbinom{m}{k}-(q-1)}\right)
-\end{align*}
-Also, if $\dbinom{m}{k} >> 1$, and $2^\lambda >> n$
-\begin{align*}
-\AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A} & \leq \epsilon + \max\left(\dfrac{1}{\dbinom{m}{k}-(q-1)}, \dbinom{q}{r}\left(\dfrac{1}{2^\lambda}\right)^r \right)
-\end{align*}
-\end{theorem}
+3) For time being, number of queries to RO is assumed to include queries to $\Test$.}\end{theorem}
+
 \begin{proof}%[\Cref{thm:gbf-correctness}]
-Define an adaptive attacker $A'$ that has the following behavior.
+Define an adaptive attacker $A$ that has the following behavior.
 It lazily samples ~$k$ positions $i_1,i_2,\ldots,i_k$ from $[m]$, xor shares($\lambda$-bit strings) at these positions in ($M$) to get a candidate~$x$.
@@
 If $x$ is not a false-positive, it repeats the attack for a different set of $k$ positions.
-Let $A'$ make $q$ queries to the RO; assume RO returns all $k$ hash values of each query at one go.
+Let $A$ make $q$ queries to the RO; assume RO returns all $k$ hash values of each query at one go.
 
@@
 \Big(1-\dfrac{n}{2^\lambda}\Big)$.
-If adversary $A'$ makes $q = \dbinom{m}{k}$ queries, it has very high chance of winning(assuming $\lambda$ is large) the correctness game for $r=1$.
+If adversary $A$ makes $q = \dbinom{m}{k}$ queries, it has very high chance of winning(assuming $\lambda$ is large) the correctness game for $r=1$.
 Let $q = (r+1) \times q_r$.
-For $r > 1$, if adversary $A'$ makes $q_r = \dbinom{m}{k}$ queries to find a single false-positive, and repeats this for $r$ times, it has high probability of winning the correctness game.
-The total queries that $A'$ makes is $(r+1)\dbinom{m}{k} = O\Big(\dbinom{m}{k}\Big)$.
+For $r > 1$, if adversary $A$ makes $q_r = \dbinom{m}{k}$ queries to find a single false-positive, and repeats this for $r$ times, it has high probability of winning the correctness game.
+The total queries that $A$ makes is $(r+1)\dbinom{m}{k} = O\Big(\dbinom{m}{k}\Big)$.
 
-% Let $A$ be an adaptive adversary(different from $A'$)\acnote{this attacker is similar to the adaptive attackers of previous proofs, where there is no known weakness of the filter in general} attacking $\Pi_{\mathrm{garb}}$, and
-Suppose $A'$ also finds false-positives without exploiting the inherent weakness of $\Pi_{\mathrm{garb}}$.
-For this case, let $D$ be the corresponding  zero-query adversary equivalent of $A'$(shown in \ref{Fig.(xxx)}).
+% Let $A$ be an adaptive adversary(different from $A$)\acnote{this attacker is similar to the adaptive attackers of previous proofs, where there is no known weakness of the filter in general} attacking $\Pi_{\mathrm{garb}}$, and
+Suppose $A$ also finds false-positives without exploiting the inherent weakness of $\Pi_{\mathrm{garb}}$.
+For this case, let $D$ be the corresponding  zero-query adversary equivalent of $A$(shown in \Cref{fig:D}).
 Dong et.
@@
 \cite{dong2013private} show that the upperbound on false-positive probability in a garbled Bloom filter for a zero-query adversary and $r=1$ is $\dfrac{1}{2^\lambda}$.
-Using analyses from previous proofs, the probability that $A'$ finds $r$ false-positives is upperbounded by  $\dbinom{q}{r}\left(\dfrac{1}{2^\lambda}\right)^r$.
+Using analyses from previous proofs, the probability that $A$ finds $r$ false-positives is upperbounded by  $\dbinom{q}{r}\left(\dfrac{1}{2^\lambda}\right)^r$.
 
@@
 \end{align*}
+and,
+\begin{align*}
+\AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A} & \geq \epsilon + \left(\dfrac{1}{\dbinom{m}{k}-(q-1)}\right)
+\end{align*}
 

### 2016-09-26 results.tex
modified DS privacy proof so that it follows from Jon's meta result

@@
 
-\todo{Privacy theorem for the ``plain'' linear-PRF scheme. Does not
-  follow from Jon's general theorem.}
+\todo{Privacy theorem for the ``plain'' linear-PRF scheme.  Follows from Jon's general theorem.}
 
@@
 \heading{Construction of PRF with domain separation.}
-Let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be a set-multiplicity data structure defined on the right-side of Figure~\ref{fig:lin-and-ds}.
-As with the preceding theorem, the following says (informally) that if~$F$ is a secure PRF, then this domain-separated PRF construction is correct against adaptive adversaries.
-We note that Neidermayer et al.
-in~\cite{xxx} suggest replacing the linear-PRF hash functions in the previous construction with independently keyed PRFs as a way to thwart their attacks.
-The construction we consider now achieves the same end, albeit via explict domain separation rather than separate keys.
+Let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be a set-multiplicity data
+structure defined on the right-side of Figure~\ref{fig:lin-and-ds}.
+As with the preceding theorem, the following says (informally) that
+if~$F$ is a secure PRF, then this domain-separated PRF construction is
+correct against adaptive adversaries.  We note that Neidermayer et
+al. in~\cite{xxx} suggest replacing the linear-PRF hash functions in
+the previous construction with independently keyed PRFs as a way to
+thwart their attacks.  The construction we consider now achieves the
+same end, albeit via explict domain separation rather than separate
+keys.
 
@@
 
+The privacy of $\Pi_{\mathrm{ds}}$ follows directly from our general
+result, Theorem~\ref{thm:xxx}.
+
+\begin{theorem}\label{thm:ds-ss}
+Fix $k,m,n>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
+For any set~$S$, let $\leak(S)=|S|$.
+There exists a simulator~$\Sim$ such that, for any adversary~$A$
+\[
+\AdvPrivSS{\Pi_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
+\]
+where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
+\end{theorem}
+\begin{proof}
+The decompose $\Rep$ into $\Rep_1$ and $\Rep_2$ as follows.  On input
+$S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, \ldots, s_k\langle k,x_1\rangle, s_{k+1}=\langle 1,x_2\rangle, \ldots, s_{2k}=\langle k,x_2\rangle, \ldots ,s_{kn+1}=\langle 1,x_n\rangle, \ldots, s_{kn}=\langle k,x_n \rangle$.
+On input $n,F_K(s_1),\ldots,F_K(s_{kn})$, algorithm $\Rep_2$ simply initializes an all-zero array~$M$ of~$m$-bits, and sets the positions $M[F_K(s_i)]$ to 1.
+It returns~$M$ as $\pubaux$.
+\end{proof}
+
+\fixme{The following is left only for cut-and-paste value.}
 \begin{theorem}\label{thm:ds-ss}
@@
 \end{proof}
+\fixme{The above is left only for cut-and-paste value.}
 

### 2016-09-26 results.tex
adjusting scheme descriptions for linear/DS to match theorem statemetns resulting from Jon's general result

@@
 
-\heading{Linear-PRF construction. }
+\subsection{Linear PRF-hash construction }
+%\heading{Linear-PRF construction. }
 Here we consider a set-multiplicity data structure that was attacked
@@
 %%%%%%%%%%%%%%%%% BIGRAM LINEAR-PRF (AKA "NEIDERMAYER")  %%%%%%%%%%%%%%%%%%%%
-\heading{Bigram Linear-PRF construction (``Neidermayer''). }
+\subsection{Bigram Linear-PRF construction}
+%\heading{Bigram Linear-PRF construction (``Neidermayer''). }
 \todo{Correctness theorem for this scheme.  Should follow pretty closely the one for ``plain'' linear-PRF.}
@@
 
+\todo{OW privacy proof?}
+
 %%%%%%%%%%%%%%%%% DOMAIN-SEPARATED PRF %%%%%%%%%%%%%%%%%%%%
 
-\heading{Construction of PRF with domain separation.}
+\subsection{Domain-separated PRF-Hash}
+%\heading{Construction of PRF with domain separation.}
 Let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be a set-multiplicity data
@@
 
-\fixme{The following is left only for cut-and-paste value.}
+\fixme{ ----The following is left only for cut-and-paste value---- }
 \begin{theorem}\label{thm:ds-ss}
@@
 \end{proof}
-\fixme{The above is left only for cut-and-paste value.}
+\fixme{ ----The above is left only for cut-and-paste value---- }
 
@@
 \heading{Classical Bloom filter in random oracle model (ROM). }
-Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.  Then $\Pi_{\mathrm{Bloom}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-garbled-bf} (left side).  The following result shows,
+Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.
+Then $\Pi_{\mathrm{Bloom}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-garbled-bf} (left side).
+The following theorem proves correctness for this construction.
+Again, we stress that this correctness is with respect to adaptive adversaries, aiming to find $r \geq 1$ errors (in this case, false-positives), and with public hash functions.
 
@@
 \input{Theorem3_FP}
+
+\todo{Explain why classical BF in the ROM does not meet our SS-privacy notion, and why this is intuitive/supports our definition.}
+
+\todo{OW privacy proof for classic BF in the ROM}
 

### 2016-09-26 results.tex
making a pass through the results section, especially the lin, bi-lin, ds constructions

@@
 to prove security of all the constructions we care about.}
-\tsnote{Would be good to give an example or two of the schemes this
+\tsnote{Point out an example or two of the schemes this
   covers.  Domain-separated PRF BF, for example.  I think it covers
@@
   functions and does the hashing. (Although the following theorem does
-  not work in this case, of course.) It does not cover
-  linear-PRF or Neidermayer. }
+  not work in this case, of course.) It does not cover Neidermayer because there's no guarantee of distinct $s_1,\ldots,s_t$. }
 We next show that any canonical data structure in which~$F$ is a pseudorandom function is
@@
 
-\subsection{Linear PRF-hash construction }
+\subsection{Linear PRF-hash Bloom Filter }
 %\heading{Linear-PRF construction. }
-Here we consider a set-multiplicity data structure that was attacked
-by Neidermayer et al. in~\cite{xxx}. \todo{Not actually a true
-  statement, because $\Rep$ isn't correct.
-Needs fixing.} Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.
+The domain-separated PRF-hash requires~$k$ PRF evaluations per set-membership query, and this may be unattractive in certain use cases.
+Kirsch and Mitzenmacher~\cite{xxx} have shown that two PRF evaluations suffices, defining the hash functions to be $h_i(x)=F_K(\langle 1,x \rangle) + j\cdot F_K(\langle 2,x \rangle) \bmod m$, where~$m$ is the bitlength of the Bloom filter.\footnote{Actually, they define $h_i(x)=F_{K_1}(x)  + j\cdot F_{K_2}(x) \bmod m$, using distinct keys instead of domain-separation, but the constructions are equivalent with respect to security.} We call this the \emph{linear PRF-hash} Bloom Filter.
+In this section, we show that this scheme is both correct and private with respect to our SS notion.
+
+Looking ahead to the next section, we will analyze a closely related construction, which was attacked by Neidermayer et al.~\cite{xxx} in the context of private medical-record linkage.
+It uses the same linear-PRF hash functions, but has a $\Rep$ algorithm that that does not ensure that the hash functions are called on \emph{distinct} values.
+We show that this is \emph{not} private with respect to our SS notion for a leakage function that leaks nearly the entire set~$S$.
+\todo{It would be better, perhaps, to show that it is not OW secure, since this implies it isn't SS secure, and OW security is what Neidermayer et al.
+violate.}
+
+Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.
 Then $\Pi_{\mathrm{lin}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:lin-and-ds} (left side).
@@
 \begin{theorem}\label{thm:bi-lin-ss}
-Let $\Pi_{\mathrm{bi-lin}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig: neidermayer}, but instantiated with $F_{K_1},F_{K_2}$ replaced by independent random functions~$\rho_1,\rho_2$ (respectively).
+Let $\Pi_{\mathrm{bi-lin}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig: neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.
 Let $\leak$ be the leakage function just described.
@@
 On the other hand, the simulator~$\Sim$ is given 'cab','bab','cab' as input.
-It can perfectly simulate $M_1,M_2$ by lazily sampling random functions~$\rho_1,\rho_2$ itself.
+It can perfectly simulate $M_1,M_2$ by lazily sampling random function~$\rho$ itself.
 However, it has no information about the bit~$z$, so at best it can cause~$A$ to output 1 with probabilility~$1/2$.

### 2016-09-26 results.tex
cheers

@@
 
-Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.
+Taken together, the results of this section and the next highlight how sensitive the privacy of linear PRF-hash constructions is to usage.
+
+For now, let $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.
 Then $\Pi_{\mathrm{lin}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:lin-and-ds} (left side).
@@
 
-\todo{Privacy theorem for the ``plain'' linear-PRF scheme.  Follows from Jon's general theorem.}
+\todo{Privacy theorem.  Follows from Jon's general theorem.}
 
@@
 
-\todo{Explain why classical BF in the ROM does not meet our SS-privacy notion, and why this is intuitive/supports our definition.}
+Turning to privacy, we note immediately that the classical BF, in the ROM, does not meet our SS-privacy notion when the leakage function fails to reveal the entire set~$S$.
+This is because the set~$S$ is adversarially chosen, and the adversary has access to the random oracle, i.e.
+the hash functions used to make~$\pubaux$.
+Thus the adversary can simply check that the $\pubaux$ it receives is correct.
+Thus, unless $m,k,n$ are such that the false-positive rate is large, the simulator needs to call the random oracle\tsnote{I assume the simulator gets access to the RO?} on the points in~$S$ in order to ``fool'' the adversary.
+\tsnote{I'm still not completely comfortable with this.
+It isn't explicit in our SS notion, but I assume that~$A$ is stateful and so knows~$S$ in its second stage?
+If so, I wonder if the classic BF in the ROM would be secure relative to a weaker notion (but still stronger than OW) in which the second stage does not know~$S$?
+This seems likely to me.}
 
@@
 \item Show Bloom Filter is correct in the ROM. \jnote{Should follow along the lines
-of Theorem~2, but taking into account adversary's oracle queries.}
+of Theorem~2, but taking into account adversary's oracle queries.} [DONE]
 \item correctness security/attacks on the bigram/PRF-based double-hashing construction ($h_j(x) = F_{K1}(x) + j\cdot F_{K2}(x) \bmod m$ where the~$x$ are bigrams of names, etc.)
-\jnote{Done}
-\item correctness-security/attacks on the bigram/domain-separated PRF construction ($h_j(x)=F_K(\langle j,x \rangle) \bmod m$, or just assume range of~$F$ is $[m]$.) \jnote{Done}
+\item correctness-security/attacks on the bigram/domain-separated PRF construction ($h_j(x)=F_K(\langle j,x \rangle) \bmod m$, or just assume range of~$F$ is $[m]$.) 
 \item correctness-security/attacks Dong, Chen, Wen ``garbled Bloom filter'' construction
@@
 
-\heading{Privacy. } Here we give security proofs and attacks with respect to the privacy notions we have defined.
-\tsnote{Under our current notions, you can never hope to prove privacy bounds that beat the element wise min-entropy of $\distr{}{}$.}
+\heading{Privacy. } 
 \begin{itemize}
-\item Prove that the basic BF, in the ROM, is private.  \tsnote{Relative the strongest notion for which this is true.  If it isn't true for all, then give the attack(s).}
-
-\item As a simple corrolary, show that the basic BF with $h_j(x)=F_K(\langle j,x \rangle)$ is private.
-\tsnote{I believe this also shows that the bigram/PRF approach examined by Neidermayer et al.\ is secure when the hash functions are the $h_j(x)$ just described.
-This was, in fact, one of the countermeasures they proposed.
-}
-
-\item Prove privacy bounds for the constructions from NY. \jnote{Is this interesting?}
+\item Prove that the basic BF, in the ROM, is private.  \tsnote{Not SS, should be OW}
+\item Show that the bigram DS-PRF construction is SS \tsnote{Shows Neidermayer's suggested countermeasure works}
+\item Show that the basic BF DS-PRF construction is SS [DONE]
+\item Prove privacy bounds for the constructions from NY \tsnote{Follows from Jon's meta-theorem}
 
@@
 (Essentially, the Hamming weight of the representation is a good estimate of the length of the longest surname in filter.)
-\jnote{Maybe tailor leakage function appropriately, i.e., so that
-it only leaks the number of bigrams?}
+\jnote{Maybe tailor leakage function appropriately, i.e., so that it only leaks the number of bigrams?}
 
@@
 
-\item Prove privacy bounds of other suggestions, such as the record-level BF from Durham et al.?  This would be a nice pairing with the Neidermayer et al.\ results
+\item Prove privacy bounds of other suggestions, such as the record-level BF from Durham et al.?  This would be a nice pairing with the Neidermayer et al.\ results \tsnote{No time.}
 
-\item ...
 \end{itemize}

### 2016-09-26 notions.tex
making a pass through the results section, especially the lin, bi-lin, ds constructions
notes

@@
 
-One can also consider the orthogonal notion of \emph{privacy} for a
-data structure.
+One can also consider the orthogonal notion of \emph{privacy} for a data structure.
 We specialize to the case of set-membership data structures, and
-focus on sets rather than multisets.
-Before continuing, it will be useful to define a notion that captures the difficulty
+focus on sets rather than multisets. Before continuing, it will be useful to define a notion that captures the difficulty
 of guessing an element in a set chosen from some distribution.
-Let ${\cal D}$ be
-a distribution over subsets of some universe ${\cal X}$. The \emph{point-wise
+Let ${\cal D}$ be a distribution over subsets of some universe ${\cal X}$. The \emph{point-wise
 min-entropy} of ${\cal D}$ is defined as
@@
 
+\tsnote{I think we should switch the order of presentation, since we
+  use the SS notion much more. }
 We formalize two types of privacy notions. The first captures
@@
 the public representation of a set~$S$ does not make it any easier for an attacker
-to learn elements of~$S$.
-The second definition
+to learn elements of~$S$.  The second definition
 captures a flavor of semantic security, essentially requiring that $\pub$ does
@@
 all~$t$-time adversaries.
-Noting that an attacker can trivially succeed with probability
-$2^{-H_\infty({\cal D})}$ by outputting the element most likely to be in~$S$,
-we say a
-set-representation data structure~$\Pi$ is $(t,\epsilon)$-ow-private if for all ${\cal D}$
-we have $\AdvPrivOW{\Pi,{\cal D}}{t} - 2^{-H_\infty({\cal D})} \leq \epsilon$.
-\jnote{Not sure I'm completely happy with the definition.}
+We remark that an attacker can trivially achieve advantage
+$2^{-H_\infty({\cal D})}$ by outputting the element most likely to be in~$S$.
 
@@
 if for all efficient $A$ there is a simulator $\Sim$ such that
-$\AdvPrivSS{\Pi,{\sf leak}}{A,\Sim}$ is small. \jnote{Do we want to
-write a formal $t, \epsilon$-style definition?}
+$\AdvPrivSS{\Pi,{\sf leak}}{A,\Sim}$ is small.
 Intuitively, this means that the public portion
@@
 
-%
-%\begin{figure}[htbp]
-%\centering
-%\hfpages{.495}
-%{
-%\hpagess{.49}{.49}
-%{
-%
-%\experimentv{$\ExpPrivSSreal{\setprim,\distr{}{}}{A}$}\\
-%$S\getsr \distr{}{}$\\
-%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
-%$(f,v) \getsr A^{\TestOracle}(M,\pubaux)$\\
-%if $f(S)=v$ then\\
-%\nudge Return 1\\
-%Return 0\\
-%
-%\medskip
-%\experimentv{$\ExpPrivSSsim{\setprim,\distr{}{}}{P}$}\\
-%$S\getsr \distr{}{}$\\
-%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
-%$(f,v) \getsr P(\pubaux)$\\
-%if $f(S)=v$ then\\
-%\nudge Return 1\\
-%Return 0\\
-%}
-%%
-%{
-%\oracle{$\TestOracle(q)$}\\
-%$a \gets \Qry(M,\pubaux,\privaux,q)$\\
-%Return~$a$\\
-%}
-%}
-%{
-%\hpagess{.49}{.49}
-%{
-%\experimentv{$\ExpPrivSS{\setprim,\distr{}{},P}{A}$}\\
-%$S\getsr \distr{}{}$\\
-%$b \getsr \bits$\\
-%%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
-%$(M_1,\pubaux,\privaux) \getsr \Rep(S)$\\
-%$M_0 \getsr P(\pubaux)$\\
-%%$(f,v) \getsr \getsr A^{\TestOracle}(M,\pubaux)$\\
-%$b' \getsr A^{\TestOracle}(M_b,\pubaux)$\\
-%%if $f(S)=v$ then\\
-%if $b'=b$ then\\
-%\nudge Return 1\\
-%Return 0\\
-%%
-%%\medskip
-%%\experimentv{$\ExpPrivSSsim{\setprim,\distr{}{}}{P}$}\\
-%%$S\getsr \distr{}{}$\\
-%%$(M,\pubaux,\privaux) \getsr \Rep(S)$\\
-%%$(f,v) \getsr P(\pubaux)$\\
-%%if $f(S)=v$ then\\
-%%\nudge Return 1\\
-%%Return 0\\
-%}
-%%
-%{
-%\oracle{$\TestOracle(q)$}\\
-%$a \gets \Qry(M_1,\pubaux,\privaux,q)$\\
-%Return~$a$\\
-%}
-%}
-%\caption{Semantic-security style privacy
-%  definitions. \textcolor{red}{On the left, need to protect against
-%    adversary outputting
-%    things like $f(S)=M$.  One idea is to forbid~$f$ such that
-%    $f(S)=f(S')$ for all $S,S'$ in the support of $\distr{}{}$.}
-%    }
-%\label{fig:privacy-ss}
-%\end{figure}
-
 \heading{Relationships between the notions.}
@@
 \max_{x \in {\cal X}} \Pr_{S \getsr {\cal D}}[x \in S \mid {\sf leak}(S)=r].\]
+
+\jnote{Make theorem statements consistent -- get rid of $(t, \epsilon)$-style.}
 

### 2016-09-26 results.tex
restructuring results.tex

@@
 
-\subsection{A Meta-Theorem for Privacy}
+%%%%%%%%%%%%%%%%% CLASSICAL BLOOM FILTER IN ROM %%%%%%%%%%%%%%%%%%%%
+
+\subsection{Classical Bloom filter in random oracle model (ROM). }
+Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.
+Then $\Pi_{\mathrm{Bloom}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-garbled-bf} (left side).
+The following theorem proves correctness for this construction.
+Again, we stress that this correctness is with respect to adaptive adversaries, aiming to find $r \geq 1$ errors (in this case, false-positives), and with public hash functions.
+
+\begin{theorem}\label{thm3}\label{thm:bf-correctness}
+Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{Bloom}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described.
+For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
+\[
+\AdvCorrect{\Pi_{\mathrm{Bloom}},\distr{\calS}{},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\]
+\end{theorem}
+
+\input{Theorem3_FP}
+
+Turning to privacy, we note immediately that the classical BF, in the ROM, does not meet our SS-privacy notion when the leakage function fails to reveal the entire set~$S$.
+This is because the set~$S$ is adversarially chosen, and the adversary has access to the random oracle, i.e.
+the hash functions used to make~$\pubaux$.
+Thus the adversary can simply check that the $\pubaux$ it receives is correct.
+Thus, unless $m,k,n$ are such that the false-positive rate is large, the simulator needs to call the random oracle\tsnote{I assume the simulator gets access to the RO?} on the points in~$S$ in order to ``fool'' the adversary.
+\tsnote{I'm still not completely comfortable with this.
+It isn't explicit in our SS notion, but I assume that~$A$ is stateful and so knows~$S$ in its second stage?
+If so, I wonder if the classic BF in the ROM would be secure relative to a weaker notion (but still stronger than OW) in which the second stage does not know~$S$?
+This seems likely to me.}
+
+\todo{distributional-SS or OW privacy proof for classic BF in the ROM}
+
+\subsection{Privacy of Secretly Keyed Canonical Data Structures}
 Here we prove a result that can be used to show that a large class of ``canonical''
@@
 
+The SS-privacy of the linear-PRF hash construction follows directly from~Theorem~\ref{thm:xxx}.
 \todo{Privacy theorem.  Follows from Jon's general theorem.}
+\begin{theorem}\label{thm:lin-privacy}
+Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{lin}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
+For any set~$S$, let $\leak(S)=|S|$.
+There exists a simulator~$\Sim$ such that, for any adversary~$A$
+\[
+\AdvPrivSS{\Pi_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
+\]
+where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
+\end{theorem}
+\begin{proof}
+It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
+On input a set of distinct elements
+$S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, s_3 = \langle 1,x_2\rangle, s_4=\langle 2,x_2 \rangle,\ldots,s_{2n-1}=\langle 1,x_n \rangle, s_{2n}=\langle 2,x_n \rangle$.
+
+On input $n,F_K(s_1),F_K(s_2),\ldots,F_K(s_{2n-1}) , F_K(s_{2n})$, algorithm $\Rep_2$ initializes an all-zero array~$M$ of~$m$-bits, and sets the positions $M[F_K(s_i)+j\cdot F_K(s_{i+1})\bmod m]$ to 1, for each $j \in [k]$.
+It returns~$M$ as $\pubaux$.
+\end{proof}
 
@@
 if~$F$ is a secure PRF, then this domain-separated PRF construction is
-correct against adaptive adversaries.  We note that Neidermayer et
+correct against adaptive adversaries.  
+\tsnote{Not really appropriate to say this next thing; I'll add a new section that addresses bigram DS-PRF hash.}
+We note that Neidermayer et
 al. in~\cite{xxx} suggest replacing the linear-PRF hash functions in
@@
 \begin{proof}
-The decompose $\Rep$ into $\Rep_1$ and $\Rep_2$ as follows.  On input
-$S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, \ldots, s_k\langle k,x_1\rangle, s_{k+1}=\langle 1,x_2\rangle, \ldots, s_{2k}=\langle k,x_2\rangle, \ldots ,s_{kn+1}=\langle 1,x_n\rangle, \ldots, s_{kn}=\langle k,x_n \rangle$.
+It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
+On input a set of distinct elements $S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, \ldots, s_k\langle k,x_1\rangle, s_{k+1}=\langle 1,x_2\rangle, \ldots, s_{2k}=\langle k,x_2\rangle, \ldots ,s_{kn+1}=\langle 1,x_n\rangle, \ldots, s_{kn}=\langle k,x_n \rangle$.
 On input $n,F_K(s_1),\ldots,F_K(s_{kn})$, algorithm $\Rep_2$ simply initializes an all-zero array~$M$ of~$m$-bits, and sets the positions $M[F_K(s_i)]$ to 1.
@@
 
-%%%%%%%%%%%%%%%%% CLASSICAL BLOOM FILTER IN ROM %%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%% Bigram DOMAIN-SEPARATED PRF %%%%%%%%%%%%%%%%%%%%
 
-\heading{Classical Bloom filter in random oracle model (ROM). }
-Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.
-Then $\Pi_{\mathrm{Bloom}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-garbled-bf} (left side).
-The following theorem proves correctness for this construction.
-Again, we stress that this correctness is with respect to adaptive adversaries, aiming to find $r \geq 1$ errors (in this case, false-positives), and with public hash functions.
-
-\begin{theorem}\label{thm3}\label{thm:bf-correctness}
-Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{Bloom}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described.
-For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
-\[
-\AdvCorrect{\Pi_{\mathrm{Bloom}},\distr{\calS}{},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
-\]
-\end{theorem}
-
-\input{Theorem3_FP}
-
-Turning to privacy, we note immediately that the classical BF, in the ROM, does not meet our SS-privacy notion when the leakage function fails to reveal the entire set~$S$.
-This is because the set~$S$ is adversarially chosen, and the adversary has access to the random oracle, i.e.
-the hash functions used to make~$\pubaux$.
-Thus the adversary can simply check that the $\pubaux$ it receives is correct.
-Thus, unless $m,k,n$ are such that the false-positive rate is large, the simulator needs to call the random oracle\tsnote{I assume the simulator gets access to the RO?} on the points in~$S$ in order to ``fool'' the adversary.
-\tsnote{I'm still not completely comfortable with this.
-It isn't explicit in our SS notion, but I assume that~$A$ is stateful and so knows~$S$ in its second stage?
-If so, I wonder if the classic BF in the ROM would be secure relative to a weaker notion (but still stronger than OW) in which the second stage does not know~$S$?
-This seems likely to me.}
-
-\todo{OW privacy proof for classic BF in the ROM}
+\subsection{Domain-separated PRF-Hash}
+%\heading{Construction of PRF with domain separation.}
+Let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be a set-multiplicity data
+structure defined on the right-side of Figure~\ref{fig:lin-and-ds}.
+As with the preceding theorem, the following says (informally) that
+if~$F$ is a secure PRF, then this domain-separated PRF construction is
+correct against adaptive adversaries.  
+\tsnote{Not really appropriate to say this next thing; I'll add a new section that addresses bigram DS-PRF hash.}
+We note that Neidermayer et
+al. in~\cite{xxx} suggest replacing the linear-PRF hash functions in
+the previous construction with independently keyed PRFs as a way to
+thwart their attacks.  The construction we consider now achieves the
+same end, albeit via explict domain separation rather than separate
+keys.
 

### 2016-09-26 results.tex
restructuring

@@
 \subsection{Classical Bloom filter in random oracle model (ROM). }
+
+\heading{Correctness. }
 Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.
@@
 
+\heading{Privacy. }
 Turning to privacy, we note immediately that the classical BF, in the ROM, does not meet our SS-privacy notion when the leakage function fails to reveal the entire set~$S$.
@@
 
+\heading{Correctness. }
 For now, let $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.
@@
 
+\heading{Privacy. }
 The SS-privacy of the linear-PRF hash construction follows directly from~Theorem~\ref{thm:xxx}.
-\todo{Privacy theorem.  Follows from Jon's general theorem.}
 \begin{theorem}\label{thm:lin-privacy}
@@
 %\heading{Bigram Linear-PRF construction (``Neidermayer''). }
-\todo{Correctness theorem for this scheme.  Should follow pretty closely the one for ``plain'' linear-PRF.}
+\heading{Correctness.} 
+\todo{Correctness theorem for this scheme.
+Should follow pretty closely the one for ``plain'' linear-PRF.}\tsnote{Actually not sure this is that interesting, but for parallel structure one would want to give it.}
 
@@
 
+\heading{Privacy. }
 Next we exhibit an efficient SS-privacy attack even when simulator is provided nearly the entire set.
@@
 %\heading{Construction of PRF with domain separation.}
+\heading{Correctness. }
 Let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be a set-multiplicity data
@@
 
+\heading{Privacy. }
 The privacy of $\Pi_{\mathrm{ds}}$ follows directly from our general
@@
 
-\subsection{Domain-separated PRF-Hash}
-%\heading{Construction of PRF with domain separation.}
-Let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be a set-multiplicity data
-structure defined on the right-side of Figure~\ref{fig:lin-and-ds}.
-As with the preceding theorem, the following says (informally) that
-if~$F$ is a secure PRF, then this domain-separated PRF construction is
-correct against adaptive adversaries.  
-\tsnote{Not really appropriate to say this next thing; I'll add a new section that addresses bigram DS-PRF hash.}
-We note that Neidermayer et
-al. in~\cite{xxx} suggest replacing the linear-PRF hash functions in
+\subsection{Bigram Domain-Separated PRF-Hash}
+We note that Neidermayer et al. in~\cite{xxx} suggest replacing the linear-PRF hash functions in
 the previous construction with independently keyed PRFs as a way to
 thwart their attacks.  The construction we consider now achieves the
-same end, albeit via explict domain separation rather than separate
-keys.
+same end, albeit via explict domain separation rather than separate keys.
+\todo{Privacy proof, at a minimum... if it is actually secure.}
+
+\begin{verbatim}
+%------------------------------------%
+\end{verbatim}
 

### 2016-09-26 results.tex
restructuring results.tex

@@
 
+%%%%%%%%%%%%%%%%% DOMAIN-SEPARATED PRF %%%%%%%%%%%%%%%%%%%%
+
+\subsection{Domain-separated PRF-Hash}
+%\heading{Construction of PRF with domain separation.}
+\heading{Correctness. }
+Let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be a set-multiplicity data
+structure defined on the right-side of Figure~\ref{fig:lin-and-ds}.
+As with the preceding theorem, the following says (informally) that
+if~$F$ is a secure PRF, then this domain-separated PRF construction is
+correct against adaptive adversaries.  
+\tsnote{Not really appropriate to say this next thing; I'll add a new section that addresses bigram DS-PRF hash.}
+We note that Neidermayer et
+al. in~\cite{xxx} suggest replacing the linear-PRF hash functions in
+the previous construction with independently keyed PRFs as a way to
+thwart their attacks.  The construction we consider now achieves the
+same end, albeit via explict domain separation rather than separate
+keys.
+
+\begin{theorem}\label{thm2}\label{thm:ds-correctness}
+Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure in Figure~\ref{fig:lin-and-ds}.
+Let $\distr{}{}$ be a distribution over~$\mathcal{S}$.
+For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exists a prf-adversary ~$B$ (explicitly constructed in the proof of this theorem) such that
+\[
+\AdvCorrect{\Pi_{\mathrm{ds}},\distr{}{},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\]
+Here, $B$ asks $q$ queries, and has time complexity $O(t+qm)$.
+\end{theorem}
+
+\heading{Privacy. }
+The privacy of $\Pi_{\mathrm{ds}}$ follows directly from our general
+result, Theorem~\ref{thm:xxx}.
+
+\begin{theorem}\label{thm:ds-ss}
+Fix $k,m,n>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
+For any set~$S$, let $\leak(S)=|S|$.
+There exists a simulator~$\Sim$ such that, for any adversary~$A$
+\[
+\AdvPrivSS{\Pi_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
+\]
+where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
+\end{theorem}
+\begin{proof}
+It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
+On input a set of distinct elements $S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, \ldots, s_k\langle k,x_1\rangle, s_{k+1}=\langle 1,x_2\rangle, \ldots, s_{2k}=\langle k,x_2\rangle, \ldots ,s_{kn+1}=\langle 1,x_n\rangle, \ldots, s_{kn}=\langle k,x_n \rangle$.
+On input $n,F_K(s_1),\ldots,F_K(s_{kn})$, algorithm $\Rep_2$ simply initializes an all-zero array~$M$ of~$m$-bits, and sets the positions $M[F_K(s_i)]$ to 1.
+It returns~$M$ as $\pubaux$.
+\end{proof}
+
+\fixme{ ----The following is left only for cut-and-paste value---- }
+\begin{theorem}\label{thm:ds-ss}
+Fix $k,m,n>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
+For any set~$S$, let $\leak(S)=|S|$.
+There exists a simulator~$\Sim$ such that, for any adversary~$A$
+\[
+\AdvPrivSS{\Pi_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
+\]
+where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
+\end{theorem}
+\begin{proof}[Proof (sketch). ] \todo{Move this sketch to be a proof
+    of Jon's meta-result. Downgrade theorem to be a corollary of that
+    result, the proof simply being a description of how $\Rep$
+    decomposes into $\Rep_1$ and $\Rep_2$.}
+Adversary~$B^{f}$ simulates the steps of $\ExpPrivSSreal{\Pi_{\mathrm{ds}}}{A}$, using its oracle to simuate~$\Rep(S)$.
+When~$f=F_K$ then the simulation is perfect.
+When~$f=\rho$ then~$B$ simulates $\ExpPrivSSreal{\overline{\Pi}_{\mathrm{ds}}}{A}$ where $\overline{\Rep}$ effectively uses~$k$ independent random functions as the hash functions.
+But the $\pub$ produced by $\overline{\Rep}$ has a distribution that depends only~$|S|=n$, not the specific elements of~$S$, and the other public parameters~$m,k$.
+Thus, a simulator~$\Sim$ given only $\leak(S)=|S|$ can produce a correct~$\pub$ as follows: starting with an all-zeros array~$M$ of length~$m$, uniformly sample (with replacement)~$nk$ integers in~$[m]$ and set the resulting positions of~$M$ to 1.
+\end{proof}
+\fixme{ ----The above is left only for cut-and-paste value---- }
+
 %%%%%%%%%%%%%%%%% LINEAR-PRF %%%%%%%%%%%%%%%%%%%%
@@
 }
-\caption{Adversary for Theorem~\ref{thm:bi-lin-ss}}
+\caption{Adversary for Theorem~\ref{thm:bi-lin-ss}.  The function $\mathsf{hamming}(M)$ returns the hamming weight of~$M$}
 \label{fig:adv-bi-lin-ss}
@@
 \begin{theorem}\label{thm:bi-lin-ss}
-Let $\Pi_{\mathrm{bi-lin}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig: neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.
+Let $\Pi_{\bilin}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig: neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.
 Let $\leak$ be the leakage function just described.
@@
 Then for any simulator $\Sim$,
-the advantage $\AdvPrivSS{\Pi_{\mathrm{bi-lin}},\leak}{A,\Sim}$ can be made arbitrarily close to $1/2$ by choice of~$\alpha$.
+the advantage $\AdvPrivSS{\Pi_{\bilin},\leak}{A,\Sim}$ can be made arbitrarily close to $1/2$ by choice of~$\alpha$.
 
@@
 In this case, the hamming weight of $M_{1,2} \wedge M_3$ will be $3k$.
-Thus $\ExpPrivSSreal{\Pi_{\mathrm{bi-lin}}}{A}=1$ with overwhelming probability.
+Thus $\ExpPrivSSreal{\Pi_{\bilin}}{A}=1$ with overwhelming probability.
 
@@
 \todo{OW privacy proof?}
-
-%%%%%%%%%%%%%%%%% DOMAIN-SEPARATED PRF %%%%%%%%%%%%%%%%%%%%
-
-\subsection{Domain-separated PRF-Hash}
-%\heading{Construction of PRF with domain separation.}
-\heading{Correctness. }
-Let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be a set-multiplicity data
-structure defined on the right-side of Figure~\ref{fig:lin-and-ds}.
-As with the preceding theorem, the following says (informally) that
-if~$F$ is a secure PRF, then this domain-separated PRF construction is
-correct against adaptive adversaries.  
-\tsnote{Not really appropriate to say this next thing; I'll add a new section that addresses bigram DS-PRF hash.}
-We note that Neidermayer et
-al. in~\cite{xxx} suggest replacing the linear-PRF hash functions in
-the previous construction with independently keyed PRFs as a way to
-thwart their attacks.  The construction we consider now achieves the
-same end, albeit via explict domain separation rather than separate
-keys.
-
-\begin{theorem}\label{thm2}\label{thm:ds-correctness}
-Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure in Figure~\ref{fig:lin-and-ds}.
-Let $\distr{}{}$ be a distribution over~$\mathcal{S}$.
-For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exists a prf-adversary ~$B$ (explicitly constructed in the proof of this theorem) such that
-\[
-\AdvCorrect{\Pi_{\mathrm{ds}},\distr{}{},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
-\]
-Here, $B$ asks $q$ queries, and has time complexity $O(t+qm)$.
-\end{theorem}
-
-\heading{Privacy. }
-The privacy of $\Pi_{\mathrm{ds}}$ follows directly from our general
-result, Theorem~\ref{thm:xxx}.
-
-\begin{theorem}\label{thm:ds-ss}
-Fix $k,m,n>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
-For any set~$S$, let $\leak(S)=|S|$.
-There exists a simulator~$\Sim$ such that, for any adversary~$A$
-\[
-\AdvPrivSS{\Pi_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
-\]
-where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
-\end{theorem}
-\begin{proof}
-It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
-On input a set of distinct elements $S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, \ldots, s_k\langle k,x_1\rangle, s_{k+1}=\langle 1,x_2\rangle, \ldots, s_{2k}=\langle k,x_2\rangle, \ldots ,s_{kn+1}=\langle 1,x_n\rangle, \ldots, s_{kn}=\langle k,x_n \rangle$.
-On input $n,F_K(s_1),\ldots,F_K(s_{kn})$, algorithm $\Rep_2$ simply initializes an all-zero array~$M$ of~$m$-bits, and sets the positions $M[F_K(s_i)]$ to 1.
-It returns~$M$ as $\pubaux$.
-\end{proof}
-
-\fixme{ ----The following is left only for cut-and-paste value---- }
-\begin{theorem}\label{thm:ds-ss}
-Fix $k,m,n>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
-For any set~$S$, let $\leak(S)=|S|$.
-There exists a simulator~$\Sim$ such that, for any adversary~$A$
-\[
-\AdvPrivSS{\Pi_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
-\]
-where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
-\end{theorem}
-\begin{proof}[Proof (sketch). ] \todo{Move this sketch to be a proof
-    of Jon's meta-result. Downgrade theorem to be a corollary of that
-    result, the proof simply being a description of how $\Rep$
-    decomposes into $\Rep_1$ and $\Rep_2$.}
-Adversary~$B^{f}$ simulates the steps of $\ExpPrivSSreal{\Pi_{\mathrm{ds}}}{A}$, using its oracle to simuate~$\Rep(S)$.
-When~$f=F_K$ then the simulation is perfect.
-When~$f=\rho$ then~$B$ simulates $\ExpPrivSSreal{\overline{\Pi}_{\mathrm{ds}}}{A}$ where $\overline{\Rep}$ effectively uses~$k$ independent random functions as the hash functions.
-But the $\pub$ produced by $\overline{\Rep}$ has a distribution that depends only~$|S|=n$, not the specific elements of~$S$, and the other public parameters~$m,k$.
-Thus, a simulator~$\Sim$ given only $\leak(S)=|S|$ can produce a correct~$\pub$ as follows: starting with an all-zeros array~$M$ of length~$m$, uniformly sample (with replacement)~$nk$ integers in~$[m]$ and set the resulting positions of~$M$ to 1.
-\end{proof}
-\fixme{ ----The above is left only for cut-and-paste value---- }
 

### 2016-09-26 TheoremGBF_correctness.tex
GBF proof updated

@@
 \begin{theorem}\label{thm:gbf-correctness}
-Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{garb}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described.
-For any adversary~$A$ that makes a total of~$q$ queries to the RO, and has time-complexity~$O(t)$,
+Fix $r=1$, $k,m,n>0$, and let $\Pi_{\mathrm{garb}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described.
+For any adversary~$A$ that makes a maximum of~$\dbinom{m}{k}$ queries to the RO, and has time-complexity~$O(t)$,
 \[
-\AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A} \leq  \epsilon +  \max\left(\dfrac{1}{\dbinom{m}{k}-(q-1)}\left(1-\dfrac{n}{2^\lambda}\right), \dbinom{q}{r}\left(\dfrac{1}{2^\lambda}\right)^r \right).
+\AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A}  \geq   \left(1 - e^{-n/m^k}\right)^{nr} + \dfrac{1}{\dbinom{m}{k}-n-(q-1)} . \Big(1-\dfrac{n}{2^\lambda}\Big)
 \]
-\[
-\AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A}  \geq \epsilon + \left(\dfrac{1}{\dbinom{m}{k}-(q-1)}\right)
-\]
-Here, $\epsilon$ is the collision error(described in proof).\acnote{1)Upperbound of $\epsilon$ is loosely equal to the FP upperbound in a classical BF.
-2) Recommended values of $\lambda$ in GBF paper = 80 or 256.
-3) For time being, number of queries to RO is assumed to include queries to $\Test$.}\end{theorem}
+
+The RHS of above expression contains 2 components, $\Prob{\epsilon_{fn}}$(false-negative probability) and $\Prob{\epsilon_{fp}}$(false-positive probability).
+For large values of $m$ and $n$, $\Prob{\epsilon_{fn}} \approx 0$.
+On the other hand, $A$ finds one false-positive with $\Prob{\epsilon_{fp}} \approx 1$ by making $\dbinom{m}{k} - n$ queries.
+
+\end{theorem}
 
 \begin{proof}%[\Cref{thm:gbf-correctness}]
+A collison in a garbled Bloom filter occurs when two or more distinct elements in a set have the same set of hash values.
+A collision results in false-negatives as only one of the elements is captured in the representation, and hence $\Qry$ returns 1 for this element, and 0 for others.
+Let $\epsilon_{fn}'$ be the event of finding a false-negative in a garbled Bloom filter.
+Let $x_1,x_2,\ldots,x_n$ be the elements in $S$.
+The probability that the hash values of $x_2,x_3,\ldots,x_n$ are not same as that of $x_1$ is $p = \left( 1-\dfrac{1}{\dbinom{m}{k}} \right)^{n-1}$.
+For $n >> 0$, $p \approx  e^{-n/m^k}$.
+The probability that $x_2,x_3,\ldots,x_n$ are false-negatives corresponding to $x_1$, i.e., $\Qry$ returns 1 for $x_1$, and 0 for others is $1-p$.
+% Similarly, the probability that remaining $n-1$ elements are false negatives of $x_2,x_3,\ldots,x_n$ respectively is also $1-p$
+.
+For $i \neq j$, the event of finding false-negatives of $x_i$ is independent of the event of finding false-negatives of $x_j$.
+Hence, $\Prob{\epsilon_{fn}} = \left( 1-p \right)^n$.
+Let $\epsilon_{fn}$ be the event of finding $r$ false-negatives.
+$\Prob{\epsilon_{fn}} = \Prob{\epsilon_{fn}'}^{r} = \left( 1-p \right)^{nr}$.
+
 Define an adaptive attacker $A$ that has the following behavior.
-It lazily samples ~$k$ positions $i_1,i_2,\ldots,i_k$ from $[m]$, xor shares($\lambda$-bit strings) at these positions in ($M$) to get a candidate~$x$.
+It makes $n$ queries to find $r=1$ false-negatives.
+It halts if it finds 1 false-negative.
+Otherwise it does lazy sampling of ~$k$ positions $i_1,i_2,\ldots,i_k$ from $[m]$, xor shares($\lambda$-bit strings) at these positions in ($M$) to get a candidate~$x$.
 If $h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots \wedge h_k(x) = i_k$, then either $x \in S$ or~$x$ is a false-positive.
 If $x$ is not a false-positive, it repeats the attack for a different set of $k$ positions.
-Let $A$ make $q$ queries to the RO; assume RO returns all $k$ hash values of each query at one go.
+Assume $A$ stops after finding 1 false-positive.
+If $A$ make $q_n$ queries to the RO, then $\max{q_n} = \dbinom{m}{k}$.
+Assume RO returns all $k$ hash values of each query at one go.
 
-Let $\calF_1$ be the event that $x$ is a false-positive(in above attack).
- $$\Prob{\calF_1} = \Prob{h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots \wedge h_k(x) = i_k : x \notin S}.\Prob{x \notin S}.$$
- The probability that $x$ is not one of the $n$ $\lambda$-bit strings is $1-\dfrac{n}{2^\lambda}$, and $ \Prob{h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots \wedge\\ h_k(x) = i_k} = \dfrac{1}{\dbinom{m}{k}-(q-1)}$.
-It must be noted that the factor $q-1$ is due to lazy sampling of the $k$ positions.
-Putting together, $\Prob{\calF_1} =  \dfrac{1}{\dbinom{m}{k}-(q-1)} .
+Let $\epsilon_{fp}$ be the event that $A$ finds one false-positive. 
+ $$\Prob{\epsilon_{fp}} = \Prob{h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots \wedge h_k(x) = i_k : x \notin S}.\Prob{x \notin S}.$$
+ The probability that $x$ is not one of the $n$ $\lambda$-bit strings is $1-\dfrac{n}{2^\lambda}$, and $ \Prob{h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots \wedge\\ h_k(x) = i_k} = \dfrac{1}{\dbinom{m}{k}-n-(q-1)}$.
+It must be noted that the factor $q-1$ is due to lazy sampling of the $k$ positions; n is the set of hash indices corresponding to the elements of set, S.
+Putting together, $\Prob{\epsilon_{fp}} =  \dfrac{1}{\dbinom{m}{k}-n-(q-1)} .
 \Big(1-\dfrac{n}{2^\lambda}\Big)$.
-If adversary $A$ makes $q = \dbinom{m}{k}$ queries, it has very high chance of winning(assuming $\lambda$ is large) the correctness game for $r=1$.
-Let $q = (r+1) \times q_r$.
-For $r > 1$, if adversary $A$ makes $q_r = \dbinom{m}{k}$ queries to find a single false-positive, and repeats this for $r$ times, it has high probability of winning the correctness game.
-The total queries that $A$ makes is $(r+1)\dbinom{m}{k} = O\Big(\dbinom{m}{k}\Big)$.
 
-% Let $A$ be an adaptive adversary(different from $A$)\acnote{this attacker is similar to the adaptive attackers of previous proofs, where there is no known weakness of the filter in general} attacking $\Pi_{\mathrm{garb}}$, and
-Suppose $A$ also finds false-positives without exploiting the inherent weakness of $\Pi_{\mathrm{garb}}$.
-For this case, let $D$ be the corresponding  zero-query adversary equivalent of $A$(shown in \Cref{fig:D}).
-Dong et.
-al.
-\cite{dong2013private} show that the upperbound on false-positive probability in a garbled Bloom filter for a zero-query adversary and $r=1$ is $\dfrac{1}{2^\lambda}$.
-Using analyses from previous proofs, the probability that $A$ finds $r$ false-positives is upperbounded by  $\dbinom{q}{r}\left(\dfrac{1}{2^\lambda}\right)^r$.
-
-Let $\calF$ be the event of finding $r$ false-positives in $\Pi_{\mathrm{garb}}$. From above analysis, we have
-\begin{align*}
-\Prob{\calF} \leq  \max\left(\dfrac{1}{\dbinom{m}{k}-(q-1)}\left(1-\dfrac{n}{2^\lambda}\right), \dbinom{q}{r}\left(\dfrac{1}{2^\lambda}\right)^r \right)
-\end{align*}
-
-A collison in a garbled Bloom filter occurs when two or more distinct elements in a set have the same set of hash values.
-A collision results in false-negatives as only one of the elements is captured in the representation, and hence $\Qry$ returns 1 for this element, and 0 for others.
-Let $\epsilon$ be the probability of finding a false-negative in a garbled Bloom filter.
-As per Dong et.
-al.
-\cite{dong2013private}, the upper bound of $\epsilon$  is loosely same as the upper bound of false-positive probability of the classical Bloom filter.
-Since, the set $S$ is fixed at the start of the game, $\epsilon$ is more or less a contant.
-
-Let $\calE$ be the event of finding $r$ errors in $\Pi_{\mathrm{garb}}$.
-Then $\Prob{\calE}$ is sum of the false-positive and false-negative probabilities.
-Also, $\Prob{\calE} = \AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A}$ So,
-\begin{align*}
-\AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A} \leq \epsilon +  \max\left(\dfrac{1}{\dbinom{m}{k}-(q-1)}\left(1-\dfrac{n}{2^\lambda}\right), \dbinom{q}{r}\left(\dfrac{1}{2^\lambda}\right)^r \right)
-\end{align*}
-and,
-\begin{align*}
-\AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A} & \geq \epsilon + \left(\dfrac{1}{\dbinom{m}{k}-(q-1)}\right)
-\end{align*}
+If $\epsilon$ is the event of finding $r$ errors, $\Prob{\epsilon} = \Prob{\epsilon_{fn}} + \Prob{\epsilon_{fp}}$, and hence 
+\[
+\AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A}  \geq \left(1 - e^{-n/m^k}\right)^{nr} + \dfrac{1}{\dbinom{m}{k}-n-(q-1)} . \Big(1-\dfrac{n}{2^\lambda}\Big)
+\]
 

### 2016-09-27 intro.tex
notes from phone call
cheers
no message
First pass at intro, some cleanup in Section 2

--- 2016-08-16 intro.tex
@@
 \label{sec:intro}
-\tsnote{Skeleton text from old intro.  (Full version of old intro now
-  in an appendix.} \jnote{Too focused on Bloom filters for my
-  taste.}
-We revisit the formalization of Bloom filters~\cite{xxx} and closely
-related data structures as primitives with explicit security goals.
-Recently, Naor and Yogev~\cite{xxx} (hereafter NY) gave such a
-formalization, providing syntax for a generalized abstraction of
-Bloom filters, as well as casting the classical Bloom filter
-soundness condition as a security experiment admitting adaptive
-adversaries.  To briefly summarize, a Bloom filter is a data
-structure for compactly representing a set~$\mathcal{S}$ in a way
-that supports constant-time responses to set-membership queries. The
-representation of~$\mathcal{S}$ is a bit-array~$M$ of length~$m$,
-all initially set to~0.  To insert $x \in \mathcal{S}$ into~$M$, one
-computes indices $h_1(x),h_2(x),\ldots,h_k(x)$ where each $h_i
-\colon \mathcal{U} \to \{0,1,\ldots m-1\}$ maps from a
-universe~$\mathcal{U}$ (which contains $\mathcal{S}$) to indices
-of~$M$.  The bits at positions $h_1(x),h_2(x),\ldots,h_k(x)$ are set
-to 1; if a bit is already 1, due to inserting some previous element
-of~$\mathcal{S}$, then it is left alone.  After all elements
-of~$\mathcal{S}$ have been inserted, the resulting bit-array~$M$ is
-taken as the representation.  To test if $y \in \mathcal{S}$, one
-checks if
-\[
-(M[h_1(y)]=1 \wedge M[h_2(y)]=1 \wedge \cdots \wedge M[h_k(y)]=1),
-\]
-returning ``yes'' if so, and ``no'' otherwise. Bloom
-filters are correct, in the sense that if $y \in \mathcal{S}$, the
-set-membership test always returns ``yes''.  The classical soundness
-condition asserts that for all $\mathcal{S}$ and any $y
-\notin\mathcal{S}$, we have $\Prob{h_1,h_2,\ldots,h_k \getsr
-\mathrm{Func}(\mathcal{U},[m])\colon M[h_1(y)]=1 \wedge \cdots
-\wedge M[h_k(y)]=1} \leq \epsilon$ where $\epsilon$, the
-false-positive error, is a parameter of the Bloom filter.  (The
-values of~$\epsilon,m,k$, and $|\mathcal{S}|$ are related in a
-well-known way.) NY recast this soundness condition as a game in
-which an adversary~$A$ is given~$\mathcal{S}$ and an oracle for
-set-membership queries, and it attempts to find one or more false
-positives. The fact that~$A$ can \emph{adapt} its queries and its
-output based on what it learns from the set-membership oracle (but,
-as we will see, not upon the hash functions) is the key definitional
-contribution of~NY.
 
-Bloom filters have a broad range of practical applications, for
-example, in content-distribution networks, large database query
-processing, routing algorithms for peer-to-peer networks, protocols
-for establishing linkages between medical-record databases, fair
-routing of TCP packets, Bitcoin wallet synchonization. \tsnote{need
-  citations}
+Data structures are a fundamental tool used throughout computer
+science. Typically, when the behavior of a data structure (e.g., its
+running time or its error probability) is analyzed, the analysis is
+performed under the assumption that the input/queries to the data
+structure are chosen independently of the data structure itself, and
+in particular independent of any internal randomness used by the
+data structure. But, as recently highlighted by Naor and
+Yogev~\cite{naor2015bloom}, there are many natural scenarios in
+which the input/queries may be chosen \emph{adversarially} and
+\emph{adaptively} based on partial information and/or prior
+observations about the data structure.
 
-\heading{Our contributions. }
-Given these shortcomings and the prevalent use of Bloom filters in practice, we revisit the matter of formalizing them as primitives with explicit security goals, these goals being abstracted from the attack surface they expose in practice.
-We begin by giving a new syntax for hash-based filters, which more clearly captures Bloom filters...
+In addition, standard applications of data structures assume that
+the party querying the data structure is fully trusted, and hence
+privacy concerns do not arise. In some scenarios, however, it may be
+desirable to allow some party to pose (certain types of) queries to
+a data structure, but unacceptable to leak the data in its entirety
+to that same party. Existing definitions do not address this at~all.
 
-We generalize this syntax to hash-based filters that are mutable,
-%\jnote{I find ``mutable'' a slightly awkward term, maybe because it makes me think of mutability in the context of programming languages.
-In much data structures literature, this is called the ``dynamic'' case, in contrast to the ``static'' case.}
-%
-%\tsnote{I adopted this term after reading it in some bloom filter paper(s).
-Ironically, I liked it for the same reason you think it is awkward :) My PL association to the term is that an immutable object is one whose state cannot be modified after it is created, and a mutable object is the opposite.
-But I don't really care too much.}
-in the sense
-that they allow for updating of the representation. This allows us
-to capture counting Bloom filters, spectral Bloom filters, stable
-Bloom filters, count-min sketches, and other compact set
-representation data structures...
+The concerns outlined above motivate a careful treatment of data
+structures in an adversarial setting, where both \emph{soundness}
+\jnote{I like soundness better than correctness, but I won't
+insist.} and \emph{correctness} are considered. In this work we
+initiate such a treatment for abstract data structures, and also
+explore the security of several specific data structures---that can
+all be viewed as generalizations of Bloom
+filters~\cite{bloom1970space}---supporting (approximate)
+set-membership queries. Specifically, we show \ldots
 
-We provide various security notions for these primitives...
-FP with private, public representation coins; set privacy with private, public representation coins; FP/set privacy in the multi-representation setting (outsider attack, think CDNs); FP/set privacy in the multi-representation setting with corruptions (insider attack, think P2P networks) \tsnote{Those are just the ones that come to mind now.
-Could also consider authenicity of representations, think CDN or P2P settings.}
+\heading{Comparison to~\cite{naor2015bloom}.} Naor and
+Yogev~\cite{naor2015bloom} recently considered the problem of
+adversarial soundness for (variants of) Bloom filters and, indeed,
+their worked served as inspiration for our own. Our work extends
+their work significantly in several directions. For starters, we
+consider abstract data structures (rather than only the case of
+set-membership data structures), and consider privacy in addition to
+soundness. Even with respect to the specific case of soundness for
+set-membership data structures, our work offers several advantages
+to the Naor-Yogev treatment:
+\begin{itemize}
+\item We explicitly distinguish between public and private
+    portions of a data structure, something that was left
+    ambiguous in~\cite{naor2015bloom}. This allows us, for
+    example, to distinguish between the hash-function keys and
+    the bit array when discussing classical Bloom filters.
+\item The Naor-Yogev definition of soundness allows the
+    adversary to make several set-membership queries, some of
+    which may produce incorrect results, and the attacker then
+    succeeds if it can output a \emph{fresh} query which leads
+    to an error. We propose instead what we find to be a more
+    natural definition in which the attacker succeeds if it can
+    cause a certain number of incorrect results.
+\item Naor and Yogev analyze a new Bloom-filter construction of
+    their own design. In contrast, we are interested in
+    analyzing practical constructions that have been proposed in
+    prior work to understand how secure they are. In particular,
+    we analyze Bloom filters in the random-oracle model.
+    \jnote{Do we? Perhaps we want to explicitly adapt some of
+    our definitions to the ROM?}
+\end{itemize}
 
-We show that...
+%false-positive error, is a parameter of the Bloom filter.  (The
+%values of~$\epsilon,m,k$, and $|\mathcal{S}|$ are related in a
+%well-known way.) NY recast this soundness condition as a game in
+%which an adversary~$A$ is given~$\mathcal{S}$ and an oracle for
+%set-membership queries, and it attempts to find one or more false
+%positives. The fact that~$A$ can \emph{adapt} its queries and its
+%output based on what it learns from the set-membership oracle (but,
+%as we will see, not upon the hash functions) is the key definitional
+%contribution of~NY.
 
-\heading{Related work: attacks}
+%Bloom filters have a broad range of practical applications, for
+%example, in content-distribution networks, large database query
+%processing, routing algorithms for peer-to-peer networks, protocols
+%for establishing linkages between medical-record databases, fair
+%routing of TCP packets, Bitcoin wallet synchonization~\cite{schnell2011novel,niedermeyer2014cryptanalysis,gervais2014privacy,nojima2009cryptographically,feng2001stochastic,reynolds2003efficient,byers2002informed,broder2004network}.
+
+\ignore{We provide various security notions for these primitives...
+FP with private, public representation coins; set privacy with
+private, public representation coins; FP/set privacy in the
+multi-representation setting (outsider attack, think CDNs); FP/set
+privacy in the multi-representation setting with corruptions
+(insider attack, think P2P networks) \tsnote{Those are just the ones
+that come to mind now.  Could also consider authenticity of
+representations, think CDN or P2P settings.}}
+
+\heading{Related work.} \jnote{See the discussion of related work in
+Naor-Yogev. We should cite [LN93]. I can't tell how relevant [MNS11]
+is. [HW13] seems relevant, though I don't think it is captured by
+our current definitions.}
+
+\jnote{Discuss use of BFs and BF variants in a security-oriented
+setting. Also some prior work formalizing BFs in an adversarial
+environment. See commented out portion of the .tex}
+
+\ignore{\heading{Related work: attacks}
 \begin{itemize}
@@
 \tsnote{Journal of Privacy and Confidentiality, 2014}
-\item Gerbet, Kumar and Lauradoux, ``The power of evil choices in bloom filters''.  \tsnote{DSN'15: Looks like a real goldmine of related work!}
+\item Gerbet, Kumar and Lauradoux, ``The power of evil choices in bloom filters''.
+\tsnote{DSN'15: Looks like a real goldmine of related work!}
 \item Crosby and Wallach, ``Denial of Service via Algorithmic Complexity Attacks'' \tsnote{Gives attacks on Squid}
 \item Gao et al., ``Internet Cache Pollution Attacks and Countermeasures''
-\end{itemize}
+\end{itemize}}
 
-\heading{Related work: definitions(?)}
+\ignore{\heading{Related work: definitions(?)}
 \begin{itemize}
 \item Nojima and Kadobayashi, ``Cryptographically Secure Bloom Filters''.
-\tsnote{Gives some security definitions for privacy.
-Quick scan, not super clear what they achieve.
-The definition of client-privacy (Definition 1) for example, makes no sense to me.
-Actually, likewise for server-privacy (Definition 2).
-Both seem vague and thoroughly underspecified.}
+\tsnote{Gives some security definitions for privacy. Quick scan, not super
+clear what they achieve. The definition of client-privacy
+ (Definition 1) for example, makes no sense to me.  Actually,
+ likewise for server-privacy (Definition 2).  Both seem vague
+ and thoroughly underspecified.}
 \item Naor and Yogev
@@
 \end{itemize}
+}

### 2016-09-27 ny-def-comparison.tex
First pass at intro, some cleanup in Section 2

@@
 
-\jnote{Just noticed something (else) odd about the NY definition: we cannot assume w.l.o.g.\
-that $A$ makes exactly $q$ queries, and in fact it is possible to have cases where increasing
-the number of queries the attacker makes can decrease its advantage! This seems like
-another drawback of the definition.}\tsnote{Really?  That seems worth
-pointing out, as part of our list of complaints.}
+%\jnote{Just noticed something (else) odd about the NY definition: we cannot assume w.l.o.g.\
+%that $A$ makes exactly $q$ queries, and in fact it is possible to have cases where increasing
+%the number of queries the attacker makes can decrease its advantage! This seems like
+%another drawback of the definition.}\tsnote{Really?  That seems worth
+%pointing out, as part of our list of complaints.}
 

### 2016-09-27 syntax.tex
notes
my changes to syntax
First pass at intro, some cleanup in Section 2

--- 2016-09-21 syntax.tex
@@
 \newcommand{\qry}{\mathsf{qry}}
-\section{(Multiset) Data Structures}
+\section{Preliminaries}
 
-\heading{Preliminaries. } When~$\univ$ is a set and $n>0$ is an
-integer, we let $[\univ]^n$ denote the set of all size-$n$ subsets
-of~$\univ$, and $[[\univ]]^n$ for the set of all multisets
-over~$\univ$ with total multiplicity~$n$. \jnote{I guess we are
-viewing sets as a special case of multisets, so maybe just say
-that.}  We write $x \getsr \univ$ to denote
-sampling an element uniformly from~$\univ$ and assigning it to~$x$,
-and we extend this notation to randomized algorithms. When~$X$ is a
-string over some alphabet~$\Sigma$, we write $|X|$ for the bitlength
-of~$X$, relative to some fixed encoding.  When~$X$ is a multiset, we
-overload the notation so that~$|X|$ is the total multiplicity
-of~$X$.
+When~$\univ$ is a set, we write $x \getsr \univ$ to denote sampling
+an element uniformly from~$\univ$ and assigning it to~$x$. We extend
+this notation to randomized algorithms, so $x \getsr A(y)$ denotes
+that (randomized) algorithm $A$ is run on input~$y$, and the output
+of the algorithm is assigned to~$x$. Algorithms may be provided
+black-box access to one or more oracles, which we write as
+superscripts, e.g., $F^{O_1,O_2,\ldots}$.
 
-Algorithms may be provided black-box access to one or more oracles,
-which we write as superscripts, e.g., $F^{O_1,O_2,\ldots}$.  An \emph{adversary} is a randomized algorithm.
+\subsection{Data Structures}
 
-\heading{Data structures.}  We begin by defining a general primitive
-that produces a representation of a given multiset, and provides a
-mechanism to answer a specified collection of questions about that
-multiset.
+We consider an abstract notion of data structures.
+
 %Informally, the representation should serve as a good
@@
 \begin{definition}[Data structure] \rm
-Fix a non-empty set~$\univ$, and a collection of (multi)sets~$\calS$
-over $\univ$. A \emph{data structure} (for $\calS$) is a tuple
-$\setprim=(\calQ,\Rep, \Qry)$ where:
+Fix sets~${\cal U}, \Gamma$, and $\calQ$, where $\calQ = \{\qry
+\colon {\cal U} \to \Gamma\}$. A \emph{data structure} (supporting
+queries $\calQ$ over universe ${\cal U}$) is a tuple
+$\setprim=(\Rep, \Qry)$ where:
 \begin{itemize}
-\item $\mathcal{Q}=\{\qry \colon \mathcal{S} \to \Gamma\}$ is a set
-    of supported \emph{queries}, where $\Gamma$ is the set of query \emph{answers}.
-\item $\Rep \colon \mathcal{S} \to \bits^*
-    \times \bits^*$ is a randomized \emph{representation
-    algorithm}, taking as input a (multi)set $S \in \mathcal{S}$, and outputting %a \emph{representation} $M \in \Sigma^*$,
+\item $\Rep \colon {\cal U} \to \bits^* \times \bits^*$ is a
+    randomized \emph{representation algorithm}, taking as input
+    an element $S \in \mathcal{U}$,
+    and outputting %a \emph{representation} $M \in \Sigma^*$,
     \emph{public representation data} $\pubaux \in \bits^*$ and
-    \emph{private representation data} $\privaux \in \bits^*$. We write
-    $(\pubaux,\privaux) \getsr \Rep(S)$ as shorthand for this execution.
+    \emph{private representation data} $\privaux \in \bits^*$.
+    We write $(\pubaux,\privaux) \getsr \Rep(S)$ as shorthand
+    for this execution.
 \item $\Qry\colon \bits^* \times \bits^* \times \calQ \to
@@
     algorithm, taking as input $\pubaux,\privaux \in \bits^*$
-    and a query $\qry \in \calQ$, and outputting an \emph{answer}
-    $a \in \Gamma$.  We write $a \gets \Qry(\pubaux,\privaux,\qry)$
-    for this execution.
+    and a query $\qry \in \calQ$, and outputting an
+    \emph{answer} $a \in \Gamma$.  We write $a \gets
+    \Qry(\pubaux,\privaux,\qry)$ for this execution. \hfill\dqed
 \end{itemize}
-\hfill\dqed
 \end{definition}
@@
 \begin{definition}[Error probability and rate] \rm
-For a given data structure $\setprim=(\calQ,\Rep, \Qry)$, let
-$\mathrm{Err}(S,\qry,\pubaux,\privaux)$ be a predicate that is true iff
-$\Qry(\pubaux,\privaux, \qry) \neq \qry(S)$.  Then $\Pi$ has \emph{error
-probability} $\epsilon$ if $\max_{S,\qry}\Pr[(\pubaux,\privaux) \getsr
-\Rep(S) : \mathrm{Err}(S,\qry,\pubaux,\privaux)=1 ] \leq \epsilon$.
+For a data structure $\setprim=(\Rep, \Qry)$ supporting queries
+${\cal Q}$ over universe ${\cal U}$, let
+$\mathrm{Err}(S,\qry,\pubaux,\privaux)$ be  true iff
+$\Qry(\pubaux,\privaux, \qry) \neq \qry(S)$.  Then $\Pi$ has
+\emph{error probability} $\epsilon$ if
+$\max_{S,\qry}\Pr[(\pubaux,\privaux) \getsr \Rep(S) :
+\mathrm{Err}(S,\qry,\pubaux,\privaux)=1 ] \leq \epsilon$.
 %
@@
 
+\jnote{The following may need to be updated to fit the new syntax.}
 Let~$\Pi$ be a data structure that has error-probability $\epsilon$,
-and consider a correctness-violating attack that asks random
-queries $\qry_1,\qry_2,\ldots,\qry_T$, i.e., uniform samples from~$\calQ$.
+and consider a correctness-violating attack that asks random queries
+$\qry_1,\qry_2,\ldots,\qry_T$, i.e., uniform samples from~$\calQ$.
 Let $\mathrm{Err}_i$ be a random variable indicating the event
-$\Qry(\pubaux,\privaux,\qry_i)\neq \qry_i(S)$.  We know that the probability
-that $\mathrm{Err}_i=1$ is at most~$\epsilon$, and it is tempting to
-model the~$\mathrm{Err}_i$ as i.i.d. Bernoulli trials with success
-probability~$\epsilon$. However, a moment's reflection shows that
-this is not the case.  Concretely, consider the following scheme.
-Fix $|S|=n$ for all $S \in \calS$, where $n \ll |\univ|$. For the
-queries, let $\calQ = \{\qry_x\colon \calS \to \bits \,|\, \forall x
-\in \univ\}$ where $\forall S \in \calS$ the predicate $\qry_x(S)=1
-\Leftrightarrow x \in S$.  Let $\Rep(S)$ pick a random element~$s
-\in S$, and return $M = S \setminus \{s\}$ and $\privaux =
-\emptystring$.  To respond to queries,
-let~$\Qry(\pubaux,\privaux,\qry_x)=1$ iff $x \in M$.  It is easy to see
-that this scheme is $1/n$-correct; for any fixed~$S$, there are
+$\Qry(\pubaux,\privaux,\qry_i)\neq \qry_i(S)$.  We know that the
+probability that $\mathrm{Err}_i=1$ is at most~$\epsilon$, and it is
+tempting to model the~$\mathrm{Err}_i$ as i.i.d. Bernoulli trials
+with success probability~$\epsilon$. However, a moment's reflection
+shows that this is not the case. Concretely, consider the following
+scheme. Fix $|S|=n$ for all $S \in \calS$, where $n \ll |\univ|$.
+For the queries, let $\calQ = \{\qry_x\colon \calS \to \bits \,|\,
+\forall x \in \univ\}$ where $\forall S \in \calS$ the predicate
+$\qry_x(S)=1 \Leftrightarrow x \in S$.  Let $\Rep(S)$ pick a random
+element~$s \in S$, and return $M = S \setminus \{s\}$ and $\privaux
+= \emptystring$.  To respond to queries,
+let~$\Qry(\pubaux,\privaux,\qry_x)=1$ iff $x \in M$.  It is easy to
+see that this scheme is $1/n$-correct; for any fixed~$S$, there are
 exactly~$n$ queries~$\qry_x$ that have probability~$1/n$ (over the
@@
 
-\heading{Data structures for set-multiplicity queries.} Our
-particular focus will be on data structures that support
-multiplicity queries.
+\heading{Data structures for set-membership queries.} Our particular
+focus will be on data structures that support membership queries.
+\jnote{I changed this from multiplicity to membership.}
 
 \begin{definition} \rm
-A \emph{set-multiplicity data structure} is a data structure with
-$\Gamma=\mathbb{N}$ and $\calQ=\{\qry_x\}_{x \in \univ}$, where
-$\qry_x(S)$ is defined to be the multiplicity of~$x$ in the
-multiset~$S$. \hfill\dqed
+A \emph{set-membership data structure over $\univ$} is a data
+structure with ${\cal U} \subseteq 2^\univ$, $\Gamma=\{0,1\}$, and
+$\calQ=\{\qry_x\}_{x \in \univ}$, where $\qry_x(S)$ is true iff $x
+\in S$. \hfill\dqed
 \end{definition}
+
+\jnote{Clean up the following, because we discuss BFs later.}
 

### 2016-09-27 results.tex
cheers
changed to LNCS format

@@
 \]
-where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
+where~$B$ is constructed from~$A$.  
+%(Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
 \end{theorem}
@@
 %%%%%%%%%%%%%%%%% BIGRAM LINEAR-PRF (AKA "NEIDERMAYER")  %%%%%%%%%%%%%%%%%%%%
-\subsection{Bigram Linear-PRF construction}
+\subsection{Bigram Linear-PRF Construction}
 %\heading{Bigram Linear-PRF construction (``Neidermayer''). }
-\heading{Correctness.} 
-\todo{Correctness theorem for this scheme.
+%\heading{Correctness.} 
+%\todo{Correctness theorem for this scheme.
 Should follow pretty closely the one for ``plain'' linear-PRF.}\tsnote{Actually not sure this is that interesting, but for parallel structure one would want to give it.}
-
-%Next we consider the privacy of this construction, relative to a leakage function that behaves as follows.
-On input a set $S=\{x_1,x_2,\ldots,x_n\}$, it computes $B_i \gets \mathsf{bigram}(x_i)$ for each $i \in [n]$.
-Then, for all $1 \leq c \leq p$, and all size-$c$ subsets $\{j_1,j_2,\ldots,j_c\} \subseteq p$, it computes $L{j_1,j_2,\ldots,j_c}=|B_{j_1} \cap B_{j_2} \cap \ldots \cap B_{j_c}|$.
-That is, it computes all of the $c$-way intersections.
-It returns $|S|=n$ and all of the $2^p -1$ intersection sizes as the leakage.
-\todo{Explain why this is plausibly leaked by $\pubaux$ for this construction.} \tsnote{This is exponential in size, so that means a simulator that reads the entire leakage will also be exponential-time in~$p$.
-} \tsnote{Should we be considering smaller, but less realistic leakage, like $\mathsf{leak}(S)=S\setminus\{x\}$.}
-
 \heading{Privacy. }
-Next we exhibit an efficient SS-privacy attack even when simulator is provided nearly the entire set.
+We only address the privacy of this construction, as the correctness follows immediately from the correctness of the Linear-PRF contruction.
+The privacy, however, does not.
+Here we exhibit an efficient SS-privacy attack even when simulator is provided nearly the entire set.
 Consider the following leakage function.
@@
 \centering
-\fpage{.5}
+\fpage{.55}
 {
@@
 \nudge $M_{1,2} \gets M_1 \vee M_2$\\
-\nudge if $z=1 \wedge \left(\mathsf{hamming}(M_{1,2} \wedge M_3) = 4k\right)$ then \\
+\nudge if $z=1 \wedge \left(3k < \mathsf{hamming}(M_{1,2} \wedge M_3) = 4k\right)$ then \\
 \nudge\nudge Return 1 \\
-\nudge if $z=0 \wedge \left(\mathsf{hamming}(M_{1,2} \wedge M_3) = 3k\right)$ then \\
+\nudge if $z=0 \wedge \left(\mathsf{hamming}(M_{1,2} \wedge M_3) \leq 3k\right)$ then \\
 \nudge\nudge Return 1 \\
@@
 }
-\caption{Adversary for Theorem~\ref{thm:bi-lin-ss}.  The function $\mathsf{hamming}(M)$ returns the hamming weight of~$M$}
+\caption{Adversary for Theorem~\ref{thm:bi-lin-ss}. The function $\mathsf{hamming}(M)$ returns the hamming weight of~$M$.}
 \label{fig:adv-bi-lin-ss}
@@
 It isn't used in any essential way in the proof sketch.}  Let~$A$ be the adversary in Figure~\ref{fig:adv-bi-lin-ss}.
-Then for any simulator $\Sim$,
-the advantage $\AdvPrivSS{\Pi_{\bilin},\leak}{A,\Sim}$ can be made arbitrarily close to $1/2$ by choice of~$\alpha$.
+Then for any simulator $\Sim$, the advantage $\AdvPrivSS{\Pi_{\bilin},\leak}{A,\Sim}$ can be made arbitrarily close to $1/2$ by choice of~$\alpha$.
 
@@
 It then produces $\alpha$-bit arrays $M_1, M_2, M_3$ by hashing the corresponding bigram sets using the hash functions $h_j(s)=\rho_1(s)+ j\rho_2(s) \bmod m$.
-Note that for sufficiently large~$m$, each of $M_1,M_2$ will contain exactly $4k$ positions set to 1; this is with overwhelming probability (up to collisions in the hash functions for different bigrams within a given bigram set).
+Note that for sufficiently large~$m$, each of $M_1,M_2$ will contain exactly $4k$ positions set to 1; this is with overwhelming probability, up to collisions in the hash functions for different bigrams within a given bigram set.
 Likewise, $M_{1,2}=M_1 \vee M_2$ will have exactly $6k$ positions set to 1, because $B_{x_1}$ and $B_{x_2}$ share $\mathrm{ab}$ and $\mathrm{a}\sqcup$.
@@
 
-On the other hand, the simulator~$\Sim$ is given 'cab','bab','cab' as input.
-It can perfectly simulate $M_1,M_2$ by lazily sampling random function~$\rho$ itself.
-However, it has no information about the bit~$z$, so at best it can cause~$A$ to output 1 with probabilility~$1/2$.
+On the other hand, the simulator~$\Sim$ is given 'cab','bab','cab' as
+input.  It can perfectly simulate $M_1,M_2$ by lazily sampling random
+function~$\rho$ itself.  However, it has no information about the
+bit~$z$, so at best it can cause~$A$ to output 1 with
+probabilility~$1/2$.  That is $\ExpPrivSSsim{\Pi_{\bilin}}{A,\Sim} \leq 1/2$.
 \end{proof}
 
-\todo{OW privacy proof?}
+\todo{OW privacy proof?
+Or just some text that says that Neidermayer et al show something stronger~---OW-privacy violation---~albeit with $n=10000, m=10000\alpha$ for an $\alpha$ that I need to look up.}
 
 %%%%%%%%%%%%%%%%% Bigram DOMAIN-SEPARATED PRF %%%%%%%%%%%%%%%%%%%%
+\subsection{Bigram Domain-Separated PRF-Hash}
+We note that Neidermayer et al.
+in~\cite{xxx} suggest replacing the linear-PRF hash functions in the previous construction with independently keyed PRFs as a countermeasure to their attack.
+In terms of SS-privacy, however, this change offers no help.
+The following theorem is proved via a nearly identical argument as Theorem~\ref{thm:bi-lin-ss}
 
-\subsection{Bigram Domain-Separated PRF-Hash}
-We note that Neidermayer et al. in~\cite{xxx} suggest replacing the linear-PRF hash functions in
-the previous construction with independently keyed PRFs as a way to
-thwart their attacks.  The construction we consider now achieves the
-same end, albeit via explict domain separation rather than separate keys.
-\todo{Privacy proof, at a minimum... if it is actually secure.}
+\begin{theorem}\label{thm:bi-lin-ss}
+Let $\Pi_{\bilin}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig: neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.
+Let $\leak$ be the leakage function described just prior to Theorem~\ref{thm:bi-lin-ss}.
+Let~$\univ=\{\mathrm{a,b,c}\}^*$.
+Let $n=3$,  $m=3\alpha $ for integer $\alpha >> 1$, and let, $k = \lceil \ln(2) \alpha \rceil$.\tsnote{This value of~$k$ is from the classical analysis for minimizing the FP rate for a Bloom filter, and is set this way for compatibility with classical results.
+It isn't used in any essential way in the proof sketch.}  Let~$A$ be the adversary in Figure~\ref{fig:adv-bi-lin-ss}.
+Then for any simulator $\Sim$,
+the advantage $\AdvPrivSS{\Pi_{\mathrm{ds}},\leak}{A,\Sim}$ can be made arbitrarily close to $1/2$ by choice of~$\alpha$.
+\end{theorem}
+
+\todo{OW privacy proof?  Distributional SS privacy proof?}
 

### 2016-09-27 TheoremGBF_correctness.tex
GBF proofs

@@
 
-The RHS of above expression contains 2 components, $\Prob{\epsilon_{fn}}$(false-negative probability) and $\Prob{\epsilon_{fp}}$(false-positive probability).
-For large values of $m$ and $n$, $\Prob{\epsilon_{fn}} \approx 0$.
-On the other hand, $A$ finds one false-positive with $\Prob{\epsilon_{fp}} \approx 1$ by making $\dbinom{m}{k} - n$ queries.
+The RHS of above expression contains 2 components, $\Prob{\epsilon_{\fn}}$(false-negative probability) and $\Prob{\epsilon_{\fp}}$(false-positive probability).
+For large values of $m$ and $n$, $\Prob{\epsilon_{\fn}} \approx 0$.
+On the other hand, $A$ finds one false-positive with $\Prob{\epsilon_{\fp}} \approx 1$ by making $\dbinom{m}{k} - n$ queries at maximum.
 
@@
 A collision results in false-negatives as only one of the elements is captured in the representation, and hence $\Qry$ returns 1 for this element, and 0 for others.
-Let $\epsilon_{fn}'$ be the event of finding a false-negative in a garbled Bloom filter.
+Let $\epsilon_{\fn}'$ be the event of finding a false-negative in a garbled Bloom filter.
 Let $x_1,x_2,\ldots,x_n$ be the elements in $S$.
@@
 For $n >> 0$, $p \approx  e^{-n/m^k}$.
-The probability that $x_2,x_3,\ldots,x_n$ are false-negatives corresponding to $x_1$, i.e., $\Qry$ returns 1 for $x_1$, and 0 for others is $1-p$.
+The probability that $x_2,x_3,\ldots,x_n$ are false-negatives corresponding to $x_1$( $\Qry$ returns 1 for $x_1$, and 0 for others) is $1-p$.
 % Similarly, the probability that remaining $n-1$ elements are false negatives of $x_2,x_3,\ldots,x_n$ respectively is also $1-p$
@@
 For $i \neq j$, the event of finding false-negatives of $x_i$ is independent of the event of finding false-negatives of $x_j$.
-Hence, $\Prob{\epsilon_{fn}} = \left( 1-p \right)^n$.
-Let $\epsilon_{fn}$ be the event of finding $r$ false-negatives.
-$\Prob{\epsilon_{fn}} = \Prob{\epsilon_{fn}'}^{r} = \left( 1-p \right)^{nr}$.
+Hence, $\Prob{\epsilon_{\fn}'} = \left( 1-p \right)^n$.
+Let $\epsilon_{\fn}$ be the event of finding $r$ false-negatives.
+Since $\epsilon_{\fn}'$ is independent of the index of a query, $\Prob{\epsilon_{\fn}} = \Prob{\epsilon_{\fn}'}^{r} = \left( 1-p \right)^{nr}$.
 
 Define an adaptive attacker $A$ that has the following behavior.
-It makes $n$ queries to find $r=1$ false-negatives.
+It makes $n$ queries to find $r=1$ false-negative.
 It halts if it finds 1 false-negative.
@@
 Assume $A$ stops after finding 1 false-positive.
-If $A$ make $q_n$ queries to the RO, then $\max{q_n} = \dbinom{m}{k}$.
+If $A$ make $q_n$ queries to the RO, then $\max\left(q_n\right) = \dbinom{m}{k}$.
 Assume RO returns all $k$ hash values of each query at one go.
 
-Let $\epsilon_{fp}$ be the event that $A$ finds one false-positive. 
- $$\Prob{\epsilon_{fp}} = \Prob{h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots \wedge h_k(x) = i_k : x \notin S}.\Prob{x \notin S}.$$
+Let $\epsilon_{\fp}$ be the event that $A$ finds one false-positive. 
+ $$\Prob{\epsilon_{\fp}} = \Prob{h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots \wedge h_k(x) = i_k : x \notin S}.\Prob{x \notin S}.$$
  The probability that $x$ is not one of the $n$ $\lambda$-bit strings is $1-\dfrac{n}{2^\lambda}$, and $ \Prob{h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots \wedge\\ h_k(x) = i_k} = \dfrac{1}{\dbinom{m}{k}-n-(q-1)}$.
 It must be noted that the factor $q-1$ is due to lazy sampling of the $k$ positions; n is the set of hash indices corresponding to the elements of set, S.
-Putting together, $\Prob{\epsilon_{fp}} =  \dfrac{1}{\dbinom{m}{k}-n-(q-1)} .
+Putting together, $\Prob{\epsilon_{\fp}} =  \dfrac{1}{\dbinom{m}{k}-n-(q-1)} .
 \Big(1-\dfrac{n}{2^\lambda}\Big)$.
 
-If $\epsilon$ is the event of finding $r$ errors, $\Prob{\epsilon} = \Prob{\epsilon_{fn}} + \Prob{\epsilon_{fp}}$, and hence 
+If $\epsilon$ is the event of finding $r=1$ error, $\Prob{\epsilon} = \AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A} =  \Prob{\epsilon_{\fn}} + \Prob{\epsilon_{\fp}}$($\epsilon_{\fn}$ and $\epsilon_{\fp}$ are mutually independent) and hence
 \[

### 2016-09-27 TheoremGBF_correctnessUB.tex
GBF proofs

\begin{theorem}\label{thm:gbf-correctnessUB}
Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{garb}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described. For any adversary~$A$ that makes a total of $q$ queries to the RO, and has time-complexity~$O(t)$,
\[
\AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A}  \leq \left(1 - e^{-n/m^k}\right)^{nr} + \dbinom{q}{r}\left(\dfrac{1}{2^\lambda}\right)^r
\]
\end{theorem}

\begin{proof}
Let $\epsilon_{\fn}$, $\epsilon_{\fp}$ be the events of finding $r$ false-negatives, and $r$ false-positives respectively in a garbled Bloom filter. Dong et al.\cite{dong2013private}, show that for a zero-query adversary and $r=1$, the upper bound on false-positive probability in a garbled Bloom filter is $\left(\dfrac{1}{2^\lambda}\right)$. Using analyses and results from  previous proofs, $\Prob{\epsilon_{\fp}} \leq \dbinom{q}{r}\left(\dfrac{1}{2^\lambda}\right)^r$.

In an earlier proof, we found a tight bound on $\epsilon_{\fn}$, i.e. $\Prob{\epsilon_{\fn}} = \left( 1-p \right)^{nr}$, where $p = \left( 1-\dfrac{1}{\dbinom{m}{k}} \right)^{n-1}$. For $n >> 0$, $p \approx  e^{-n/m^k}$. Since, $\epsilon_{\fp}$ and $\epsilon_{\fn}$ are mutually independent events, The probability that $A$ wins the correctness game is upper-bounded by $\Prob{\epsilon_{\fn}} + \Prob{\epsilon_{\fp}}$. Hence,
\[
\AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A}  \leq \left(1 - e^{-n/m^k}\right)^{nr} + \dbinom{q}{r}\left(\dfrac{1}{2^\lambda}\right)^r
\]
\end{proof}

### 2016-09-27 syntax.tex

@@
 \begin{definition}[Data structure] \rm
-Fix sets~${\cal U}, \Gamma$, and $\calQ$, where $\calQ = \{\qry
-\colon {\cal U} \to \Gamma\}$. A \emph{data structure} (supporting
-queries $\calQ$ over universe ${\cal U}$) is a tuple
-$\setprim=(\Rep, \Qry)$ where:
+Fix sets~${\cal U}, \Gamma$, and $\calQ = \{\qry \colon {\cal U} \to
+\Gamma\}$. A \emph{data structure} (supporting queries $\calQ$ over
+universe ${\cal U}$) is a tuple $\setprim=(\Rep, \Qry)$ where:
 \begin{itemize}
@@
 \begin{definition}[Error probability and rate] \rm
-For a data structure $\setprim=(\Rep, \Qry)$ supporting queries
-${\cal Q}$ over universe ${\cal U}$, let
+For a specific data structure $\setprim=(\Rep, \Qry)$ supporting
+queries ${\cal Q}$ over universe ${\cal U}$, let
 $\mathrm{Err}(S,\qry,\pubaux,\privaux)$ be  true iff
-$\Qry(\pubaux,\privaux, \qry) \neq \qry(S)$.  Then $\Pi$ has
-\emph{error probability} $\epsilon$ if
-$\max_{S,\qry}\Pr[(\pubaux,\privaux) \getsr \Rep(S) :
-\mathrm{Err}(S,\qry,\pubaux,\privaux)=1 ] \leq \epsilon$.
+$\Qry(\pubaux,\privaux, \qry) \neq \qry(S)$.  Then we say that $\Pi$
+has \emph{error probability}~$\epsilon$ if
+\[\max_{S,\qry}\Pr[(\pubaux,\privaux) \getsr \Rep(S) :
+\mathrm{Err}(S,\qry,\pubaux,\privaux)=1 ] \leq \epsilon.\]
 %
-It has \emph{error rate} $\tilde{\epsilon}$ if
-$\max_{S}\Pr[(\pubaux,\privaux) \getsr \Rep(S);\, \qry \getsr \calQ :
-\mathrm{Err}(S,\qry,\pubaux,\privaux)=1] \leq \tilde{\epsilon}$. \hfill\dqed
+We say it has \emph{error rate} $\tilde{\epsilon}$ if
+\[{\textstyle \max_{S}\Pr[(\pubaux,\privaux) \getsr \Rep(S);\, \qry \getsr \calQ :
+\mathrm{Err}(S,\qry,\pubaux,\privaux)=1]} \leq \tilde{\epsilon}. \]
+%\hfill\dqed
 \end{definition}
@@
 
-These definitions, and those that follow, can be lifted to the random-oracle
-model by giving $\Rep, \Qry$ access to a random oracle. In that
-case, the probabilities defining the error probability and error
-rate are also taken over choice of the random oracle.
-
-We note that, while our error probability and error rate do not
+The above definition can be lifted to the random-oracle model by
+giving $\Rep, \Qry$ access to a random oracle. In that case, the
+probabilities are also taken over choice of the random oracle. We
+remark that, while our error probability and error rate do not
 distinguish among ``types'' of errors, they also do not preclude
@@
 \def\bin{{\sf Bin}}
-\heading{Error probability vs.\ error rate. }
-We pause to highlight an important
-difference between error probability and error rate.  In particular,
-the error probability~$\epsilon$ is measured only over the coins
-of~$\Rep$, for a fixed~$S$ and query~$\qry$. Once the coins of~$\Rep$
-are fixed, it is not straightforward how to connect~$\epsilon$ to
-events that depend on other sources of randomness.   We illustrate how
-this surfaces with the following example.
+\ignore{
+\heading{Error probability vs.\ error rate. } We pause to
+highlight an important difference between error probability and
+error rate.  In particular, the error probability~$\epsilon$ is
+measured only over the coins of~$\Rep$, for a fixed~$S$ and
+query~$\qry$. Once the coins of~$\Rep$ are fixed, it is not
+straightforward how to connect~$\epsilon$ to events that depend on
+other sources of randomness.   We illustrate how this surfaces with
+the following example.
 
@@
 from~$Q$, for all~$i\in[T]$ we have
-$\Prob{\mathrm{Err}_i=1}=1/|\univ| \ll 1/n = \epsilon$.
+$\Prob{\mathrm{Err}_i=1}=1/|\univ| \ll 1/n = \epsilon$.}
 
-\heading{Data structures for set-membership queries.} Our particular
-focus will be on data structures that support membership queries.
-\jnote{I changed this from multiplicity to membership.}
+\heading{Data structures for set-membership queries.} An important
+special case is a data structure that supports set-membership
+queries. \jnote{I changed this from multiplicity to membership.}
 
@@
 
-\jnote{Clean up the following, because we discuss BFs later.}
+Note that we do not require ${\cal U} = 2^\univ$ since, e.g., a
+set-membership data structure may only be defined for sets up to
+some bounded size.
 
-The classical Bloom filter is a special case of a set-multiplicity
-data structure, as set-membership queries are a type of
-set-multiplicity query.  Specifically,
+\ignore{ \jnote{Below needs to change.} For concreteness, we note
+that a classical Bloom filter is a particular example of a
+set-membership data structure. Specifically,
 %\jnote{Only handles sets, not multisets.}
@@
 the so-called ``garbled Bloom filter'' due to Dong, Chen and
-Wen~\cite{dong2013private}. \todo{Details have to be filled in.} This stores
-xor-shares of bitstring~$x \in S$ at positions
+Wen~\cite{dong2013private}. \todo{Details have to be filled in.}
+This stores xor-shares of bitstring~$x \in S$ at positions
 $h_1(x),h_2(x),\ldots,h_k(x)$ in an array. Similarly, the
@@
 $h_1(x),h_2(x),\ldots,h_k(x)$, is captured when $L=|g(x)|$.
-\todo{Check the correctness of this claim.}
+\todo{Check the correctness of this claim.} }

### 2016-09-27 TheoremGBF_correctness.tex
minor update GBF proof

@@
 
-The RHS of above expression contains 2 components, $\Prob{\epsilon_{\fn}}$(false-negative probability) and $\Prob{\epsilon_{\fp}}$(false-positive probability).
+The RHS of above expression contains 2 components, $\Prob{\epsilon_{\fn}}= \left(1 - e^{-n/m^k}\right)^{nr}$ (false-negative probability), and $\Prob{\epsilon_{\fp}}=\dfrac{1}{\dbinom{m}{k}-n-(q-1)} .
+\Big(1-\dfrac{n}{2^\lambda}\Big)$ (false-positive probability).
 For large values of $m$ and $n$, $\Prob{\epsilon_{\fn}} \approx 0$.
@@
  $$\Prob{\epsilon_{\fp}} = \Prob{h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots \wedge h_k(x) = i_k : x \notin S}.\Prob{x \notin S}.$$
- The probability that $x$ is not one of the $n$ $\lambda$-bit strings is $1-\dfrac{n}{2^\lambda}$, and $ \Prob{h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots \wedge\\ h_k(x) = i_k} = \dfrac{1}{\dbinom{m}{k}-n-(q-1)}$.
+ The probability that $x$ is not one of the $n$ $\lambda$-bit strings is $1-\dfrac{n}{2^\lambda}$, and $ \mathrm{Pr}[h_{1}(x)=i_1$ $\wedge h_2(x)=i_2 \wedge \cdots \wedge h_k(x) = i_k] = \dfrac{1}{\dbinom{m}{k}-n-(q-1)}$.
 It must be noted that the factor $q-1$ is due to lazy sampling of the $k$ positions; n is the set of hash indices corresponding to the elements of set, S.

### 2016-09-27 notions.tex
small changes

@@
 $\AdvCorrect{\Pi,r}{A} = \Prob{\ExpCorrect{\Pi,r}{A}=1}$.
-Overloading notation, we write $\AdvCorrect{\Pi,r}{t,q}$ for the maximum over
+\tsnote{drop} Overloading notation, we write $\AdvCorrect{\Pi,r}{t,q}$ for the maximum over
 all~$t$-time adversaries that ask at most~$q$ queries. We say a
@@
 }
-\caption{Experiments for a ``semantic-security'' style privacy
+\caption{Experiments for the ``semantic-security'' privacy
   definition.}
 \label{fig:privacy-ss}
+
+\end{figure}
+\begin{figure}[hbtp]
+\centering
+\fpage{.6}{
+\hpagess{.5}{.45}
+{
+\experimentv{$\ExpPrivSSreal{\Pi,\distr{}{}}{A}$}\\
+$S \getsr \distr{}{}$ \\
+$(\pubaux,\privaux) \getsr \Rep(S)$\\
+return $A(S,\pubaux)$\\
+}
+%
+{
+\experimentv{$\ExpPrivSSsim{\Pi, {\sf leak}, \distr{}{}}{A, \Sim}$}\\
+$S \getsr \distr{}{}$\\
+$\pubaux \getsr \Sim({\sf leak}(S))$ \\
+return $A(S,\pubaux)$\\
+}
+}
+\caption{Experiments for the ``distibutional semantic-security'' privacy
+  definition.}
+\label{fig:privacy-dss}
 \end{figure}

### 2016-09-28 results.tex
restructuring section 4, dropping scheme-descriptions.tex and moving schemes in-line

@@
 %%%%%%%%%%%%%%%%% CLASSICAL BLOOM FILTER IN ROM %%%%%%%%%%%%%%%%%%%%
+
+\begin{figure}[tp]
+\centering
+\hfpagess{.4}{.55}
+{
+\algorithmv{$\Rep^H(S)$}\\
+$M \gets 0^m$\\
+for $x \in S$\\
+\nudge for $j \in \{1,2,\ldots,k\}$\\
+\nudge\nudge $h_j \gets H(j,x)$\\
+\nudge\nudge $M[h_j] \gets 1$\\
+$\pubaux \gets M$, $\privaux \gets \emptystring$\\
+Return $(\pubaux,\privaux)$\\
+
+\medskip
+\algorithmv{$\Qry^H(\pubaux,\privaux,q_x)$}\\
+$M\gets\pubaux$\\
+for $j \in \{1,2,\ldots,k\}$\\
+\nudge $h_j \gets H(j,x)$\\
+\nudge if $M[h_j] \neq 1$ then Return 0\\
+Return 1
+}
+{
+\algorithmv{$\Rep(S)$}\\
+$M \gets 0^m$; $K \getsr \calK$\\
+for $x \in S$\\
+\nudge for $j \in \{1,2,\ldots,k\}$\\
+\nudge\nudge $h_j \gets F_{K}(j,x) $\\
+\nudge\nudge $M[h_j] \gets 1$\\
+$\pubaux \gets M$, $\privaux \gets \langle K \rangle$\\
+Return $(\pubaux,\privaux)$\\
+
+\medskip
+\algorithmv{$\Qry(\pubaux,\privaux,q_x)$}\\
+$M\gets\pubaux$, $K \gets \privaux$\\
+for $j \in \{1,2,\ldots,k\}$\\
+\nudge $h_j \gets F_{K}(\langle j,x \rangle) $\\
+\nudge if $M[h_j] \neq 1$ then Return 0\\
+Return 1
+}
+\caption{{\bf Left:} $\Rep$ and $\Qry$ algorithms for classic Bloom
+  filter $\Pi_{\mathrm{Bloom}}$ in the ROM for a hash function $H\colon \mathbb{N} \times
+  \univ \to [m]$. {\bf Right:} [[ $\Rep$ and $\Qry$
+  algorithms for the domain-separated PRF data structure
+  $\Pi_{\mathrm{ds}}$, using function family $F \colon
+  \calK \times \univ \to [m]$.  Both constructions have query set is $\calQ=\{q_x\colon
+  \univ \to \bits\}$ where $q_x(S)=1 \Leftrightarrow x \in S$.  }
+\label{fig:bf-and-lin}
+\end{figure}
 
@@
 Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.
-Then $\Pi_{\mathrm{Bloom}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-garbled-bf} (left side).
+Then $\Pi_{\mathrm{Bloom}}= (\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-garbled-bf} (left side).
 The following theorem proves correctness for this construction.
@@
 \begin{theorem}\label{thm3}\label{thm:bf-correctness}
-Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{Bloom}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described.
+Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{Bloom}}= (\Rep, \Qry)$ be the set-multiplicity data structure just described.
 For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
@@
 \heading{Privacy. }
-Turning to privacy, we note immediately that the classical BF, in the ROM, does not meet our SS-privacy notion when the leakage function fails to reveal the entire set~$S$.
-This is because the set~$S$ is adversarially chosen, and the adversary has access to the random oracle, i.e.
-the hash functions used to make~$\pubaux$.
-Thus the adversary can simply check that the $\pubaux$ it receives is correct.
-Thus, unless $m,k,n$ are such that the false-positive rate is large, the simulator needs to call the random oracle\tsnote{I assume the simulator gets access to the RO?} on the points in~$S$ in order to ``fool'' the adversary.
-\tsnote{I'm still not completely comfortable with this.
+Turning to privacy, we observe immediately that the classical BF, in the
+ROM, does not meet our SS-privacy notion when the leakage function
+fails to reveal the entire set~$S$.  This is because the set~$S$ is
+adversarially chosen, and the adversary has access to the random
+oracle, i.e. the hash functions used to make~$\pubaux$.  Thus the
+adversary can simply check that the $\pubaux$ it receives is correct.
+Thus, unless $m,k,n$ are such that the false-positive rate is large,
+the simulator needs to call the random oracle on the points in~$S$ in order to ``fool'' the adversary.
+%\tsnote{I'm still not completely comfortable with this.
 It isn't explicit in our SS notion, but I assume that~$A$ is stateful and so knows~$S$ in its second stage?
@@
 This seems likely to me.}
+
+We note that this will be true for \emph{any} data structure that returns an empty $\privaux$, because this implies that $\pubaux$ alone suffices to evaluate $\Qry(\pubaux,\privaux,\cdot)$.
+
+\begin{theorem}\label{thm3}\label{thm:bf-ow}
+Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{Bloom}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described.
+For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
+\[
+\AdvCorrect{\Pi_{\mathrm{Bloom}},\distr{\calS}{},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\]
+\end{theorem}
 
@@
 
-\include{scheme-descriptions}
-
 %%%%%%%%%%%%%%%%% DOMAIN-SEPARATED PRF %%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%% LINEAR-PRF %%%%%%%%%%%%%%%%%%%%
+\begin{figure}[tp]
+\centering
+\hfpagess{.5}{.5}
+{
+\algorithmv{$\Rep(S)$}\\
+$M \gets 0^m$; $K \getsr \calK$\\
+for $x \in S$\\
+\jnote{Fix}\tsnote{Fix what?}\\
+\nudge for $j \in \{1,2,\ldots,k\}$\\
+\nudge\nudge $h_j \gets F_{K}(\langle 1,x \rangle) + j\cdot F_{K}(\langle 2,x \rangle) \bmod m$\\
+\nudge\nudge $M[h_j] \gets 1$\\
+$\pubaux \gets M$, $\privaux \gets \langle K \rangle$\\
+Return $(\pubaux,\privaux)$\\
+
+\medskip
+\algorithmv{$\Qry(\pubaux,\privaux,q_x)$}\\
+$M\gets\pubaux$, $K \gets \privaux$\\
+\jnote{Fix}\tsnote{Fix what?} \\
+for $j \in \{1,2,\ldots,k\}$\\
+\nudge $h_j \gets F_{K}(\langle 1,x \rangle) + j\cdot F_{K}(\langle 2,x\rangle) \bmod m$\\
+\nudge if $M[h_j] \neq 1$ then Return 0\\
+Return 1
+}
+{
+\algorithmv{$\Rep(S)$}\\
+$\pubaux \gets \emptystring$\\
+$K_1,K_2, \getsr \calK$\\
+for each $x \in S$\\
+\nudge $M_x \gets 0^m$\\
+\nudge $B_x \gets \mathsf{bigram}(x)$\\
+\nudge for each $b \in B_x$\\
+\nudge\nudge for $j \in [k]$\\
+\nudge\nudge\nudge $i \gets F_{K}(\langle 1, b\rangle)+j\cdot
+F_{K}(\langle b  \rangle) \bmod m$\\
+\nudge\nudge\nudge $M_x[i] \gets 1$\\
+\nudge $\pubaux \gets \langle\pubaux, M_x \rangle$\\
+$\privaux \gets \langle K_1,K_2 \rangle$\\
+Return $(\pubaux,\privaux)$\\
+
+\medskip
+\algorithmv{$\Qry(\pubaux,\privaux,q_x)$}\\
+$B \gets \mathsf{bigram}(x)$\\
+$\overline{M} \gets 0^m$\\
+for each $b \in B$\\
+\nudge for $j \in [k]$\\
+\nudge\nudge $i \gets F_{K}(\langle 1,b \rangle)+j\cdot F_{K}(\langle2,b \rangle) \bmod m$\\
+\nudge\nudge $\overline{M}[i] \gets 1$\\
+if $M \in \pubaux$ then Return 1 \\
+Return 0
+}
+\caption{{\bf Left:} $\Rep$ and $\Qry$ algorithms for the linear-PRF
+  data structure $\Pi_{\mathrm{lin}}$ {\bf Right:}
+The scheme from Neidermayer et al.\cite{xxx}, $\Pi_{\bilin}$. The $\mathsf{bigram}$
+algorithm takes a string~$x=x_1,x_2,\ldots,x_\ell$ as input, and
+returns the set of bigrams for the left- and right-padded string
+$\sqcup x \sqcup$, i.e. $\{\sqcup x_1, x_1x_2,\ldots,x_\ell\sqcup\}$.
+}
+\label{fig:lin-and-bi-lin}
+\end{figure}
 
@@
 
+%%%%%%%%%%%%%%%%% GARBLED BF  %%%%%%%%%%%%%%%%%%%%
+\subsection{Garbled Bloom Filter}
+\begin{figure}
+\centering
+\fpage{.525}
+{
+\algorithmv{$\Rep^H(S)$}\\
+$M \gets \mathrm{null}^m$; $\lambda \gets \calK$\\
+for $x \in S$\\
+\nudge $\finalshare \gets 0^\lambda$; $\emptyslot \gets -1$\\
+\nudge for $j \in \{1,2,\ldots, k\}$\\
+\nudge \nudge $h_j \gets H(j,x)$\\
+\nudge \nudge if $M[h_j] \neq \mathrm{null}$ then\\
+\nudge \nudge \nudge $\finalshare \gets \finalshare \xor M[h_j]$\\
+\nudge \nudge else if $\emptyslot = -1$ then\\
+\nudge \nudge \nudge $\emptyslot \gets h_j$\\
+\nudge \nudge else\\
+\nudge \nudge \nudge $M[h_j] \gets \bits^\lambda$\\
+\nudge \nudge \nudge $\finalshare \gets \finalshare \xor M[h_j]$\\
+\nudge $M[\emptyslot] \gets \finalshare \xor x$\\
+for $i \in \{1,2,\ldots, m\}$\\
+\nudge if $M[i] = \undefined$ then\\
+\nudge \nudge  $M[i] \gets \bits^\lambda$\\
+$\pubaux \gets M$; $\privaux \gets \lambda$\\
+
+\medskip
+\algorithmv{$\Qry(\pubaux,\privaux,q_x)$}\\
+$M \gets \pubaux$, $\lambda \gets \privaux$, $x \gets 0^\lambda$\\
+for $j \in \{1,2,\dots,k\}$\\
+\nudge $h_j \gets H(j,x)$\\
+\nudge $x \gets x \xor M[h_j]$\\
+if $x = q_x$ then Return 1\\
+Return 0
+}
+\caption{ $\Rep$ and $\Qry$ algorithms for garbled Bloom
+  filter $\Pi_{\mathrm{garbled}}$ in the ROM for a hash function $H\colon \mathbb{N} \times \calK
+ \times \univ \to [m]$. The query set is $\calQ=\{q_x\colon
+  \univ \to \bits\}$ where $q_x(S)=1 \Leftrightarrow x \in S$.}
+
+\end{figure}
+
 \begin{verbatim}

### 2016-09-28 results.tex
cleaning up in Section 4, prior to adding new material

@@
   filter $\Pi_{\mathrm{Bloom}}$ in the ROM for a hash function $H\colon \mathbb{N} \times
-  \univ \to [m]$. {\bf Right:} [[ $\Rep$ and $\Qry$
+  \univ \to [m]$. {\bf Right:} $\Rep$ and $\Qry$
   algorithms for the domain-separated PRF data structure
@@
 Again, we stress that this correctness is with respect to adaptive adversaries, aiming to find $r \geq 1$ errors (in this case, false-positives), and with public hash functions.
+The proof appears in Appendix~\ref{sec:thm3_fp}.
 
@@
 \[
-\AdvCorrect{\Pi_{\mathrm{Bloom}},\distr{\calS}{},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\AdvCorrect{\Pi_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
 \]
@@
 
-\input{Theorem3_FP}
+%\input{Theorem3_FP}
 
@@
 
-\def\bits{\{0,1\}}
+%\def\bits{\{0,1\}}
 
@@
 \end{definition}
-\jnote{Not sure how general to make the above. Need to verify that it is general enough
-to prove security of all the constructions we care about.}
+%\jnote{Not sure how general to make the above. Need to verify that it is general enough
+%to prove security of all the constructions we care about.}
 \tsnote{Point out an example or two of the schemes this
@@
 \heading{Correctness. }
-Let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be a set-multiplicity data
+Let $\Pi_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-membership data
 structure defined on the right-side of Figure~\ref{fig:lin-and-ds}.
@@
 correct against adaptive adversaries.  
-\tsnote{Not really appropriate to say this next thing; I'll add a new section that addresses bigram DS-PRF hash.}
-We note that Neidermayer et
-al. in~\cite{xxx} suggest replacing the linear-PRF hash functions in
-the previous construction with independently keyed PRFs as a way to
-thwart their attacks.  The construction we consider now achieves the
-same end, albeit via explict domain separation rather than separate
-keys.
+% \tsnote{Not really appropriate to say this next thing; I'll add a new section that addresses bigram DS-PRF hash.}
+% We note that Neidermayer et
+% al. in~\cite{xxx} suggest replacing the linear-PRF hash functions in
+% the previous construction with independently keyed PRFs as a way to
+% thwart their attacks.  The construction we consider now achieves the
+% same end, albeit via explict domain separation rather than separate
+% keys.
 
 \begin{theorem}\label{thm2}\label{thm:ds-correctness}
-Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure in Figure~\ref{fig:lin-and-ds}.
-Let $\distr{}{}$ be a distribution over~$\mathcal{S}$.
+Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-multiplicity data structure in Figure~\ref{fig:lin-and-ds}.
 For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exists a prf-adversary ~$B$ (explicitly constructed in the proof of this theorem) such that
 \[
-\AdvCorrect{\Pi_{\mathrm{ds}},\distr{}{},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\AdvCorrect{\Pi_{\mathrm{ds}},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
 \]
@@
 \heading{Privacy. }
-The privacy of $\Pi_{\mathrm{ds}}$ follows directly from our general
-result, Theorem~\ref{thm:xxx}.
+The privacy of $\Pi_{\mathrm{ds}}$ follows directly from our general result, Theorem~\ref{thm:xxx}.
 
@@
 \label{fig:lin-and-bi-lin}
+\label{fig:neidermayer}
 \end{figure}
@@
 Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{lin}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
-Let $\distr{}{}$ be a distribution over~$\mathcal{S}$.
 For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exist prf-adversaries~$B_1,B_2$ (explicitly constructed in the proof of this theorem) such that
 \[
-\AdvCorrect{\Pi_{\mathrm{lin}},\distr{}{},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\AdvCorrect{\Pi_{\mathrm{lin}},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
 \]
@@
 \begin{theorem}\label{thm:lin-privacy}
-Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{lin}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
+Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
 For any set~$S$, let $\leak(S)=|S|$.
@@
 \begin{theorem}\label{thm:bi-lin-ss}
-Let $\Pi_{\bilin}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig: neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.
+Let $\Pi_{\bilin}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig: neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.
 Let $\leak$ be the leakage function just described.
@@
 \begin{theorem}\label{thm:bi-lin-ss}
-Let $\Pi_{\bilin}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig: neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.
+Let $\Pi_{\bilin}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig: neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.
 Let $\leak$ be the leakage function described just prior to Theorem~\ref{thm:bi-lin-ss}.

### 2016-09-28 results.tex
cleaning up in Section 4, prior to adding new material

@@
 
-\begin{theorem}\label{thm3}\label{thm:bf-ow}
-Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{Bloom}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described.
-For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
+\begin{theorem}\label{thm3}\label{thm:bf-ow} \todo{Finish typesetting.  Result is on chalkboard.}
+Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{Bloom}}= (\Rep, \Qry)$ be the set-multiplicity data structure just described.
+Let $\distr{}{}$ be a distribution over subsets of universe~$\univ$, where $\mu = H_\infty(\distr{}{})$.
+For any adversary~$A$ that makes $q$~queries to its oracle
 \[
-\AdvCorrect{\Pi_{\mathrm{Bloom}},\distr{\calS}{},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\AdvPrivOW{\Pi_{\mathrm{Bloom}},\distr{}{},r}{A} \leq  \frac{(kqn+n)}{2^{\mu}}
 \]
 \end{theorem}
-
-\todo{distributional-SS or OW privacy proof for classic BF in the ROM}
 

### 2016-09-28 Theorem3_FP.tex
Proofs syntax update
Proof3 update
Proof9 updated as per changed syntax
cleaning up in Section 4, prior to adding new material
Complying proof with current syntax

@@
+\section{Proof of \Cref{thm3}}
+\label{sec:thm3_fp}
 \begin{proof}[\Cref{thm3}]
@@
 
-$\game{1}$ is exactly same as $\game{0}$ except the $\Qry$ oracle is replaced by the code of $\Qry$, whereas in $\game{2}$, the $\Test$ oracle returns the hash values back to the adversary along with $q_x(S)$ and output of the $\Qry$ oracle.
+$\game{1}$ is exactly same as $\game{0}$ except the $\Qry$ oracle is replaced by the code of $\Qry$, whereas in $\game{2}$, the $\Test$ oracle returns the hash values back to the adversary along with output of the $\Qry$ oracle.
 $\game{3}$ on the other hand, returns all the $k$ hash values for any query.
@@
 Also, we offload all of $\Test$'s computations to $\Hash$, which now maintains an $\Ans$ table to compute and save answers for each query.
-For any query, $q$, the $\Test$ oracle returns answer stored at $\Ans[q]$.
+For any query, $\qry$, the $\Test$ oracle returns answer stored at $\Ans[\qry]$.
 We also introduce the $\bad$ flag in this game.
@@
 $\game{5}$ is exactly same as $\game{4}$, but returns 0, if $\bad$ is set to true.
-It can be observed that, the total queries made to the $\Hash$ oracle by the adversary is the sum of queries($q_T$) made by the $\Test$ oracle, and adversary's direct queries($q_H$).
-Using analyses and intermediate results of previous proofs, $\Prob{\game{5}(A)=1} = \frac{1}{\dbinom{q_T + q_H}{r}}\Prob{\game{4}(A)=1}$.
+It can be observed that, the total queries made to the $\Hash$ oracle by the adversary is the sum of queries($q_T$) made by the $\Test$ oracle, and adversary's direct queries($q_H$) to the RO.
+Using analyses and intermediate results of previous proofs, $\Prob{\game{5}(A)=1} = \dfrac{1}{\dbinom{q_T + q_H}{r}}\Prob{\game{4}(A)=1}$.
 
@@
 \underline{\game{0}(A)}\\
-$S \getsr \distr{\calS}{}$, $\err \gets 0$\\
+$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
 $(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
-$z \getsr A^{\TestOracle, \HashOracle}(S,\pubaux)$\\
+$\bot \getsr A^{\TestOracle}(\pubaux)$\\
 if $\err  < r$ then Return 0\\
@@
 %
-\oracle{$\TestOracle(q_x)$}\\
-$a \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
-if $a \neq q_x(S)$ then \\
-\nudge $\err \gets\err +1$\\
-Return~$(a,q_x(S) )$\\
+\oracle{$\TestOracle(\qry_x)$}\\
+if $\qry_x \in \mathcal{C}$ then Return $\bot$\\
+$\calC \gets \calC \cup \{\qry_x\}$\\
+$a \gets \Qry^{\HashOracle}(\pubaux,\privaux,\qry_x)$\\
+if $a \neq \qry_x(S)$ then \\
+\nudge $\err \gets \err + 1$\\
+Return~$a$\\
 %
-\oracle{$\HashOracle(i,q_y)$}\\
+\oracle{$\HashOracle(i,\qry_y)$}\\
 $v \getsr [m]$\\
-if $T[i,q_y] \neq \undefined$\\
-\nudge $v \gets T[i,q_y]$\\
-$T[i,q_y] \gets v$\\
+if $T[i,\qry_y] \neq \undefined$\\
+\nudge $v \gets T[i,\qry_y]$\\
+$T[i,\qry_y] \gets v$\\
 Ret $v$
@@
 \underline{$\game{1}(A)$}\\
-$S \getsr \distr{\calS}{}$, $\err \gets 0$\\
+$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
 $(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
-$z \getsr A^{\TestOracle, \HashOracle}(S,\pubaux)$\\
+$\bot \getsr A^{\TestOracle}(\pubaux)$\\
 if $\err  < r$ then Return 0\\
@@
 %
-\oracle{$\TestOracle(q_x)$}\\
-$M \gets\pubaux$\\
+\oracle{$\TestOracle(\qry_x)$}\\
+if $\qry_x \in \mathcal{C}$ then Return $\bot$\\
+$\calC \gets \calC \cup \{\qry_x\}$; $M \gets\pubaux$\\
 for $j \in \{1,2,\ldots,k\}$\\
-\nudge $h_j \gets \HashOracle(j,q_x)$\\
-\nudge if $M[h_j] \neq 1$ then Return $(0, q_x(S))$\\
-$\err \gets \err +1$\\
-Return~$(1,q_x(S))$\\
+\nudge $h_j \gets \HashOracle(j,\qry_x)$\\
+\nudge if $M[h_j] \neq 1$ then Return 0\\
+$\err \gets \err + 1$\\
+Return 1\\
 %
-\oracle{$\HashOracle(i,q_y)$}\\
+\oracle{$\HashOracle(i,\qry_y)$}\\
 $v \getsr [m]$\\
-if $T[i,q_y] \neq \undefined$\\
-\nudge $v \gets T[i,q_y]$\\
-$T[i,q_y] \gets v$\\
+if $T[i,\qry_y] \neq \undefined$\\
+\nudge $v \gets T[i,\qry_y]$\\
+$T[i,\qry_y] \gets v$\\
 Ret $v$
@@
 \underline{$\game{2}(A)$}\\
-$S \getsr \distr{\calS}{}$, $\err \gets 0$\\
+$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
 $(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
-$z \getsr A^{\TestOracle, \HashOracle}(S,\pubaux)$\\
+$\bot \getsr A^{\TestOracle}(\pubaux)$\\
 if $\err  < r$ then Return 0\\
@@
 %
-\oracle{$\TestOracle(q_x)$}\\
-$M \gets\pubaux$\\
+\oracle{$\TestOracle(\qry_x)$}\\
+if $\qry_x \in \mathcal{C}$ then Return $\bot$\\
+$\calC \gets \calC \cup \{\qry_x\}$; $M \gets\pubaux$\\
 for $j \in \{1,2,\ldots,k\}$\\
-\nudge $h_j \gets \HashOracle(j,q_x)$\\
+\nudge $h_j \gets \HashOracle(j,\qry_x)$\\
 \nudge if $M[h_j] \neq 1$\\
-%\nudge \nudge if $j = 1$ then Return $(0, \err, \emptystring)$\\
-\nudge \nudge Return $(0, q_x(S), (h_1, \ldots, h_j))$\\
+\nudge \nudge Return $(0, (h_1, \ldots, h_j))$\\
 $\err \gets \err +1$\\
-Return~$(1,q_x(S), (h_1, \ldots, h_{k}) )$\\
+Return~$(1, (h_1, \ldots, h_{k}) )$\\
 %
-\oracle{$\HashOracle(i,q_y)$}\\
+\oracle{$\HashOracle(i,\qry_y)$}\\
 $v \getsr [m]$\\
-if $T[i,q_y] \neq \undefined$\\
-\nudge $v \gets T[i,q_y]$\\
-$T[i,q_y] \gets v$\\
+if $T[i,\qry_y] \neq \undefined$\\
+\nudge $v \gets T[i,\qry_y]$\\
+$T[i,\qry_y] \gets v$\\
 Ret $v$
@@
 \underline{$\game{3}(A)$}\\
-$S \getsr \distr{\calS}{}$, $\err \gets 0$\\
+$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
 $(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
-$z \getsr A^{\TestOracle, \HashOracle}(S,\pubaux)$\\
+$\bot \getsr A^{\TestOracle}(\pubaux)$\\
 if $\err  < r$ then Return 0\\
@@
 %
-\oracle{$\TestOracle(q_x)$}\\
-$M \gets\pubaux $\\
-$(h_1, \ldots, h_{k}) \gets \HashOracle(q_x)$\\
+\oracle{$\TestOracle(\qry_x)$}\\
+if $\qry_x \in \mathcal{C}$ then Return $\bot$\\
+$\calC \gets \calC \cup \{\qry_x\}$; $M \gets\pubaux$\\
+$(h_1, \ldots, h_{k}) \gets \HashOracle(\qry_x)$\\
 for $j \in \{1,2,\ldots,k\}$\\
 \nudge if $M[h_j] \neq 1$ then \\
-\nudge \nudge Return~$(0,q_x(S), (h_1, \ldots, h_{k}) )$\\
+\nudge \nudge Return~$(0, (h_1, \ldots, h_{k}) )$\\
 $\err \gets \err +1$\\
-Return~$(1,q_x(S), (h_1, \ldots, h_{k}) )$\\
+Return~$(1, (h_1, \ldots, h_{k}) )$\\
 %
-\oracle{$\HashOracle(q_y)$}\\
+\oracle{$\HashOracle(\qry_y)$}\\
 for $j \in \{1,2,\ldots,k\}$\\
 \nudge $v_j \getsr [m]$\\
-\nudge if $T[j,q_y] \neq \undefined$\\
-\nudge \nudge $v_j \gets T[j,q_y]$\\
-\nudge $T[j,q_y] \gets v_j$\\
+\nudge if $T[j,\qry_y] \neq \undefined$\\
+\nudge \nudge $v_j \gets T[j,\qry_y]$\\
+\nudge $T[j,\qry_y] \gets v_j$\\
 Ret $\left(v_1,\ldots,v_k\right)$
@@
 \underline{\game{4}(A)\fbox{\game{5}(A)}}\\
-$S \getsr \distr{\calS}{}$\\
-$\err \gets 0$, $\Ans \gets \emptyset$\\
-$c \gets 0$, $\bad \gets \false$\\
-$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
+$c\gets 0$, $\bad \gets \false$, $\err \gets 0$;  $\calC \gets \emptyset$\\
+$S \getsr A$; $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
 $(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
-$z \getsr A^{\TestOracle, \HashOracle}(S,\pubaux)$\\
+$\bot \getsr A^{\TestOracle}(\pubaux)$\\
 if $\bad = \true$ then \fbox{Return 0}\\
@@
 %
-\oracle{$\TestOracle(q_x)$}\\
+\oracle{$\TestOracle(\qry_x)$}\\
+if $\qry_x \in \mathcal{C}$ then Return $\bot$\\
+$\calC \gets \calC \cup \{\qry_x\}$\\
 if $\Ans[x] \neq \undefined$\\
-\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(q_x)$\\
+\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(\qry_x)$\\
 Return $\Ans[x]$\\
@@
 {
-\oracle{$\HashOracle(q_y)$}\\
+\oracle{$\HashOracle(\qry_y)$}\\
 $c \gets c + 1$\\
@@
 \nudge if $M[v_j] \neq 1$ then \\
-\nudge \nudge $\Ans[q_y] \gets (0, q_y(S), (v_1, \ldots, v_{k}) )$\\
+\nudge \nudge $\Ans[\qry_y] \gets (0, (v_1, \ldots, v_{k}) )$\\
 \nudge \nudge if $c \in \calI$ then $\bad \gets \true$\\
 \nudge \nudge $\Break$\\
+if $j < k$ then Return $\left(v_1,\ldots,v_k\right)$\\
 if $c \notin \calI$ then $\bad \gets \true$\\
 $\err \gets \err +1$\\
-$\Ans[q_y] \gets (1, q_y(S), (v_1, \ldots, v_{k}))$\\
-Ret $\left(v_1,\ldots,v_k\right)$
+$\Ans[\qry_y] \gets (1, (v_1, \ldots, v_{k}))$\\
+Return $\left(v_1,\ldots,v_k\right)$
 }

### 2016-09-28 results.tex
cleaning section 4

@@
 \nudge\nudge\nudge $i \gets F_{K}(\langle 1, b\rangle)+j\cdot
-F_{K}(\langle b  \rangle) \bmod m$\\
+F_{K}(\langle 2, b  \rangle) \bmod m$\\
 \nudge\nudge\nudge $M_x[i] \gets 1$\\
@@
 \nudge for $j \in [k]$\\
-\nudge\nudge $i \gets F_{K}(\langle 1,b \rangle)+j\cdot F_{K}(\langle2,b \rangle) \bmod m$\\
+\nudge\nudge $i \gets F_{K}(\langle 1,b \rangle)+j\cdot F_{K}(\langle 2,b \rangle) \bmod m$\\
 \nudge\nudge $\overline{M}[i] \gets 1$\\
@@
 \begin{theorem}\label{thm1}\label{thm:lin-correctness}
-Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{lin}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
+Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{lin}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-bin-lin}.
 For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exist prf-adversaries~$B_1,B_2$ (explicitly constructed in the proof of this theorem) such that
@@
 \begin{theorem}\label{thm:lin-privacy}
-Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
+Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-bin-lin}.
 For any set~$S$, let $\leak(S)=|S|$.
@@
 \begin{theorem}\label{thm:bi-lin-ss}
-Let $\Pi_{\bilin}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig: neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.
+Let $\Pi_{\bilin}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.
 Let $\leak$ be the leakage function just described.
@@
 
-\begin{theorem}\label{thm:bi-lin-ss}
-Let $\Pi_{\bilin}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig: neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.
+\begin{theorem}\label{thm:bi-ds-ss}
+Let $\Pi_{\bilin}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.
 Let $\leak$ be the leakage function described just prior to Theorem~\ref{thm:bi-lin-ss}.

### 2016-09-28 results.tex
starting to rewrite GBF results
rewriting GBF material

@@
 {
-\adversaryv{A}\\
+\adversaryv{$A$}\\
 On input $\emptystring$:\\
@@
 {
-\algorithmv{$\Rep^H(S)$}\\
-$M \gets \mathrm{null}^m$; $\lambda \gets \calK$\\
+\algorithmv{$\Rep(S)$}\\
+$M \gets (\bot)^m$\\
+$K_1,K_2,\ldots, K_k \getsr \calK$\\
 for $x \in S$\\
@@
 \nudge for $j \in \{1,2,\ldots, k\}$\\
-\nudge \nudge $h_j \gets H(j,x)$\\
-\nudge \nudge if $M[h_j] \neq \mathrm{null}$ then\\
+\nudge \nudge $h_j \gets H_{K_j}(x)$\\
+\nudge \nudge if $M[h_j] \neq \bot$ then\\
 \nudge \nudge \nudge $\finalshare \gets \finalshare \xor M[h_j]$\\
@@
 \nudge \nudge else\\
-\nudge \nudge \nudge $M[h_j] \gets \bits^\lambda$\\
+\nudge \nudge \nudge $M[h_j] \getsr \bits^\lambda$\\
 \nudge \nudge \nudge $\finalshare \gets \finalshare \xor M[h_j]$\\
@@
 \nudge if $M[i] = \undefined$ then\\
-\nudge \nudge  $M[i] \gets \bits^\lambda$\\
-$\pubaux \gets M$; $\privaux \gets \lambda$\\
+\nudge \nudge  $M[i] \getsr \bits^\lambda$\\
+$\pubaux \gets M$; $\privaux \gets $???\\
 
 \medskip
-\algorithmv{$\Qry(\pubaux,\privaux,q_x)$}\\
-$M \gets \pubaux$, $\lambda \gets \privaux$, $x \gets 0^\lambda$\\
+\algorithmv{$\Qry(\pubaux,\privaux,\qry_x)$}\\
+$M \gets \pubaux$, ??? $\gets \privaux$\\
+$x' \gets 0^\lambda$\\
 for $j \in \{1,2,\dots,k\}$\\
-\nudge $h_j \gets H(j,x)$\\
-\nudge $x \gets x \xor M[h_j]$\\
-if $x = q_x$ then Return 1\\
+\nudge $h_j \gets H_{K_j}(x)$\\
+\nudge $x' \gets x' \xor M[h_j]$\\
+if $x' =x $ then Return 1\\
 Return 0
@@
 \caption{ $\Rep$ and $\Qry$ algorithms for garbled Bloom
-  filter $\Pi_{\mathrm{garbled}}$ in the ROM for a hash function $H\colon \mathbb{N} \times \calK
- \times \univ \to [m]$. The query set is $\calQ=\{q_x\colon
-  \univ \to \bits\}$ where $q_x(S)=1 \Leftrightarrow x \in S$.}
+  filter $\Pi_{\mathrm{garbled}}$ in the ROM for a hash function $H\colon \calK \times \mathbb{N} \times 
+ \univ \to [m]$. The query set is $\calQ=\{\qry_x\colon
+  \univ \to \bits\}$ where $\qry_x(S)=1 \Leftrightarrow x \in S$.}
 
+\end{figure}
+
+\begin{figure}
+\centering
+\hfpagess{.45}{.5}
+{
+\adversaryv{$A^{\TestOracle}(\pubaux)$}\\
+$M \gets \pubaux$\\
+for $1 \leq i_1 < i_2 < \cdots < i_k \leq m$\\
+\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
+\nudge if $\TestOracle(x)=1$ then Return $\bot$
+}
+{
+\adversaryv{$A^{\TestOracle,H}(\pubaux)$}\\
+$M \gets \pubaux$\\
+for $1 \leq i_1 < i_2 < \cdots < i_k \leq m$\\
+\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
+\nudge $x' \gets H(1,x) \xor H(2,x) \xor \cdots \xor H(k,x)$\\
+\nudge if $x=x'$ then\\
+\nudge\nudge $\TestOracle(x)$\\
+\nudge\nudge Return $\bot$\\
+}
+
+\caption{Adversary for Theorem~\ref{thm:xxx}.}
+\label{fig:adv-bi-lin-ss}
 \end{figure}

### 2016-09-28 results.tex
rewriting GBF

@@
 \centering
-\fpage{.525}
+\fpage{.75}
 {
@@
 \nudge \nudge  $M[i] \getsr \bits^\lambda$\\
-$\pubaux \gets M$; $\privaux \gets $???\\
+$\pubaux \gets M$; $\privaux \gets \langle K_1,K_2,\ldots,K_k \rangle$ \mbox{ (if secret hash version)}\\
+$\pubaux \gets \langle M,K_1,K_2,\ldots,K_k \rangle$; $\privaux \gets \emptystring$ \mbox{(if public hash version)}\\
 
@@
 \algorithmv{$\Qry(\pubaux,\privaux,\qry_x)$}\\
-$M \gets \pubaux$, ??? $\gets \privaux$\\
+if $\privaux \neq \emptystring$ then\\
+\nudge $M \gets \pubaux$, $K_1,K_2,\ldots,K_k \gets \privaux$\\
+else\\
+\nudge $M,K_1,K_2,\ldots,K_k \gets \pubaux$\\
 $x' \gets 0^\lambda$\\
@@
 \caption{ $\Rep$ and $\Qry$ algorithms for garbled Bloom
-  filter $\Pi_{\mathrm{garbled}}$ in the ROM for a hash function $H\colon \calK \times \mathbb{N} \times 
+  filter $\Pi_{\mathrm{garbled}}$ in the ROM for a hash function $H\colon \calK \times 
  \univ \to [m]$. The query set is $\calQ=\{\qry_x\colon
@@
 {
-\adversaryv{$A^{\TestOracle,H}(\pubaux)$}\\
-$M \gets \pubaux$\\
+\adversaryv{$A^{\TestOracle}(\pubaux)$}\\
+$M,K_1,K_2,\ldots,K_k \gets \pubaux$\\
 for $1 \leq i_1 < i_2 < \cdots < i_k \leq m$\\
@@
 
-\caption{Adversary for Theorem~\ref{thm:xxx}.}
+\caption{Adversary for Theorem~\ref{thm:xxx}.  \textbf{Left:} secret hash case, \textbf{Right:} public hash case.}
 \label{fig:adv-bi-lin-ss}

### 2016-09-28 syntax.tex
note about error probability/error rate definition

@@
 
+\tsnote{Do we ever use this definition?  I guess it is a mapping of
+  classical notions to our syntax, but I don't know if we use it.
+  Anyway,  it looks a bit weird sitting here on its own.  It made more
+  sense when supported by the intuition-building example, now
+  commented out. }
 \begin{definition}[Error probability and rate] \rm
@@
 from~$Q$, for all~$i\in[T]$ we have
-$\Prob{\mathrm{Err}_i=1}=1/|\univ| \ll 1/n = \epsilon$.}
+$\Prob{\mathrm{Err}_i=1}=1/|\univ| \ll 1/n = \epsilon$.
+}
 

### 2016-09-28 results.tex
cheers

@@
 \nudge for $j \in \{1,2,\ldots,k\}$\\
-\nudge\nudge $h_j \gets F_{K}(j,x) $\\
+\nudge\nudge $h_j \gets F_{K}(\langle j,x \rangle) $\\
 \nudge\nudge $M[h_j] \gets 1$\\
@@
 \heading{Correctness. }
-Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.
-Then $\Pi_{\mathrm{Bloom}}= (\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-garbled-bf} (left side).
-The following theorem proves correctness for this construction.
-Again, we stress that this correctness is with respect to adaptive adversaries, aiming to find $r \geq 1$ errors (in this case, false-positives), and with public hash functions.
+Fix $n,k,m \geq 0$, and fix a universe~$\univ$.
+Then $\Pi_{\mathrm{Bloom}}= (\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-lin} (left side).
+We define~$\Pi_{\mathrm{Bloom}}$ in the random oracle model, as the traditional analysis of Bloom filter correctness (as a function of $n,k,m$) is done in this model.\footnote{The standard model version would have $\Rep$ choose $H_1,H_2,\ldots,H_k$ from a hash function family, compute $h_j$ using these, and placing their description in $\pubaux$.}  The following theorem proves that the Bloom filter meets our correctness notion in the ROM.
+Again, we stress that this correctness is with respect to adaptive adversaries, aiming to find $r \geq 1$ errors (in this case, false-positives).
 The proof appears in Appendix~\ref{sec:thm3_fp}.

### 2016-09-28 syntax.tex
cheers
cleaning notation and syntax

@@
 black-box access to one or more oracles, which we write as
-superscripts, e.g., $F^{O_1,O_2,\ldots}$.
+superscripts, e.g., $F^{O_1,O_2,\ldots}$.  We write $\langle
+x,y,\ldots \rangle$ for the encoding of values $x,y,\ldots$ as a
+single bitstring, for some implicit and invertible encoding method.
+When $x$ is a string, we write $x[i]$ for the $i$-th element in that string.
 
@@
 \begin{definition}[Data structure] \rm
-Fix sets~${\cal U}, \Gamma$, and $\calQ = \{\qry \colon {\cal U} \to
+Fix sets~$\univ, \Gamma$, and $\calQ = \{\qry \colon \univ \to
 \Gamma\}$. A \emph{data structure} (supporting queries $\calQ$ over
-universe ${\cal U}$) is a tuple $\setprim=(\Rep, \Qry)$ where:
+universe $\univ$) is a tuple $\setprim=(\Rep, \Qry)$ where:
 \begin{itemize}
-\item $\Rep \colon {\cal U} \to \bits^* \times \bits^*$ is a
+\item $\Rep \colon \univ \to \bits^* \times \bits^*$ is a
     randomized \emph{representation algorithm}, taking as input
-    an element $S \in \mathcal{U}$,
+    an element $S \in \univ$,
     and outputting %a \emph{representation} $M \in \Sigma^*$,
@@
 For a specific data structure $\setprim=(\Rep, \Qry)$ supporting
-queries ${\cal Q}$ over universe ${\cal U}$, let
+queries $\calQ$ over universe $\univ$, let
 $\mathrm{Err}(S,\qry,\pubaux,\privaux)$ be  true iff
@@
 
-\heading{Data structures for set-membership queries.} An important
-special case is a data structure that supports set-membership
+%\heading{Data structures for set-membership queries.} 
+An important special case is a data structure that supports set-membership
 queries. \jnote{I changed this from multiplicity to membership.}
@@
 A \emph{set-membership data structure over $\univ$} is a data
-structure with ${\cal U} \subseteq 2^\univ$, $\Gamma=\{0,1\}$, and
+structure with $\univ \subseteq 2^\elts$, $\Gamma=\{0,1\}$, and
 $\calQ=\{\qry_x\}_{x \in \univ}$, where $\qry_x(S)$ is true iff $x
@@
 
-Note that we do not require ${\cal U} = 2^\univ$ since, e.g., a
+Note that we do not require $\univ = 2^\elts$ since, e.g., a
 set-membership data structure may only be defined for sets up to

### 2016-09-28 syntax.tex
cleaning

@@
 
-\tsnote{Do we ever use this definition?  I guess it is a mapping of
+\tsnote{Do we ever use this next definition?  I guess it is a mapping of
   classical notions to our syntax, but I don't know if we use it.
@@
 \begin{definition} \rm
-A \emph{set-membership data structure over $\univ$} is a data
+A \emph{set-membership data structure over $\elts$} is a data
 structure with $\univ \subseteq 2^\elts$, $\Gamma=\{0,1\}$, and

### 2016-09-28 notions.tex
removing distributional ss notion
cleaning

--- 2016-09-26 notions.tex
@@
 
-\begin{figure}[htp]
+\begin{figure}[tp]
 \centering
@@
 }
-\caption{Correctness of~$\Pi$ against an (adaptive) adversary~$A$.}
+\caption{Correctness of~$\setprim$ against an (adaptive) adversary~$A$.}
 \label{fig:correctness}
@@
 We define the advantage of adversary~$A$ in the correctness experiment as
-$\AdvCorrect{\Pi,r}{A} = \Prob{\ExpCorrect{\Pi,r}{A}=1}$.
-Overloading notation, we write $\AdvCorrect{\Pi,r}{t,q}$ for the maximum over
+$\AdvCorrect{\setprim,r}{A} = \Prob{\ExpCorrect{\setprim,r}{A}=1}$.
+\tsnote{drop} Overloading notation, we write $\AdvCorrect{\setprim,r}{t,q}$ for the maximum over
 all~$t$-time adversaries that ask at most~$q$ queries. We say a
-data structure~$\Pi$ is $(t,q,r,\epsilon)$-correct if $\AdvCorrect{\Pi,r}{t,q} \leq \epsilon$.
+data structure~$\setprim$ is $(t,q,r,\epsilon)$-correct if $\AdvCorrect{\setprim,r}{t,q} \leq \epsilon$.
 
@@
 
-\newcommand{\leak}{{\sf leak}}
 \subsection{Privacy}
@@
 We define the advantage of adversary~$A$ in this experiment\footnote{We
-remark that one could consider augmenting experiment $\ExpPrivOW{\Pi,{\cal D}}{A}$ by additionally
+remark that one could consider augmenting experiment $\ExpPrivOW{\setprim,{\cal D}}{A}$ by additionally
 giving $A$ access to an oracle for testing membership in~$S$. However, it is not hard
 to see that allowing $q$ such queries can increase $A$'s advantage by at most a factor of~$q$.} as
-$\AdvPrivOW{\Pi,\mathcal{D}}{A} = \Prob{\ExpPrivOW{\Pi,{\cal D}}{A}=1}$ and,
-overloading notation, we write $\AdvPrivOW{\Pi,{\cal D}}{t}$ for the maximum of this value over
+$\AdvPrivOW{\setprim,\mathcal{D}}{A} = \Prob{\ExpPrivOW{\setprim,{\cal D}}{A}=1}$ and,
+overloading notation, we write $\AdvPrivOW{\setprim,{\cal D}}{t}$ for the maximum of this value over
 all~$t$-time adversaries.
@@
 
-\begin{figure}[hbtp]
+\begin{figure}[tp]
 \centering
@@
 we define the advantage
-$\AdvPrivSS{\Pi,{\sf leak}}{A,\Sim} \bydef
-\left| \Prob{\ExpPrivSSreal{\Pi}{A}=1} -
-\Prob{\ExpPrivSSsim{\Pi,{\sf leak}}{A, \Sim}=1} \right|$.
-Informally, a scheme $\Pi$ is secure with respect to some leakage function ${\sf leak}$
+$\AdvPrivSS{\setprim,{\sf leak}}{A,\Sim} \bydef
+\left| \Prob{\ExpPrivSSreal{\setprim}{A}=1} -
+\Prob{\ExpPrivSSsim{\setprim,{\sf leak}}{A, \Sim}=1} \right|$.
+Informally, a scheme $\setprim$ is secure with respect to some leakage function ${\sf leak}$
 if for all efficient $A$ there is a simulator $\Sim$ such that
-$\AdvPrivSS{\Pi,{\sf leak}}{A,\Sim}$ is small.
+$\AdvPrivSS{\setprim,{\sf leak}}{A,\Sim}$ is small.
 Intuitively, this means that the public portion
@@
 {
-\experimentv{$\ExpPrivSSreal{\Pi}{A}$}\\
+\experimentv{$\ExpPrivSSreal{\setprim}{A}$}\\
 $S \getsr A$ \\
@@
 {
-\experimentv{$\ExpPrivSSsim{\Pi, {\sf leak}}{A, \Sim}$}\\
+\experimentv{$\ExpPrivSSsim{\setprim, {\sf leak}}{A, \Sim}$}\\
 $S \getsr A$\\
@@
 }
-\caption{Experiments for a ``semantic-security'' style privacy
+\caption{Experiments for the ``semantic-security'' privacy
   definition.}
@@
 \end{figure}
+
+%\begin{figure}[hbtp]
+%\centering
+%\fpage{.6}{
+%\hpagess{.5}{.45}
+%{
+%\experimentv{$\ExpPrivSSreal{\setprim,\distr{}{}}{A}$}\\
+%$S \getsr \distr{}{}$ \\
+%$(\pubaux,\privaux) \getsr \Rep(S)$\\
+%return $A(S,\pubaux)$\\
+%}
+%%
+%{
+%\experimentv{$\ExpPrivSSsim{\setprim, {\sf leak}, \distr{}{}}{A, \Sim}$}\\
+%$S \getsr \distr{}{}$\\
+%$\pubaux \getsr \Sim({\sf leak}(S))$ \\
+%return $A(S,\pubaux)$\\
+%}
+%}
+%\caption{Experiments for the ``distibutional semantic-security'' privacy
+%  definition.}
+%\label{fig:privacy-dss}
+%\end{figure}
 
@@
 \begin{theorem}
-Let $\Pi$ be a set-representation data structure that is $(t, \epsilon)$-semantically secure
+Let $\setprim$ be a set-representation data structure that is $(t, \epsilon)$-semantically secure
 with respect to leakage ${\sf leak}:2^{\cal X} \rightarrow R$.
-Then $\AdvPrivOW{\Pi,\mathcal{D}}{t} \leq 2^{-\tilde H_\infty({\cal D} \mid {\sf leak})} + \epsilon$.
+Then $\AdvPrivOW{\setprim,\mathcal{D}}{t} \leq 2^{-\tilde H_\infty({\cal D} \mid {\sf leak})} + \epsilon$.
 \end{theorem}
@@
 Fix a distribution ${\cal D}$ and an attacker
-$A$ running in time $t$, and let $\delta \bydef \AdvPrivOW{\Pi,\mathcal{D}}{A}$.
+$A$ running in time $t$, and let $\delta \bydef \AdvPrivOW{\setprim,\mathcal{D}}{A}$.
 Define an attacker $A'$ who behaves as follows: first, it samples a set $S$ according to
@@
 
-It is immediate that $\Pr[\ExpPrivSSreal{\Pi}{A'}=1] = \delta$. Semantic
-security of $\Pi$ implies that there exists a simulator $\Sim$ for which
-$\ExpPrivSSsim{\Pi, {\sf leak}}{A', \Sim} \geq \delta - \epsilon$. However,
+It is immediate that $\Pr[\ExpPrivSSreal{\setprim}{A'}=1] = \delta$. Semantic
+security of $\setprim$ implies that there exists a simulator $\Sim$ for which
+$\ExpPrivSSsim{\setprim, {\sf leak}}{A', \Sim} \geq \delta - \epsilon$. However,
 the only information
@@
 and $A'$ jointly have about the set~$S$ that was sampled is ${\sf leak}(S)$; thus,
-we must have $\ExpPrivSSsim{\Pi, {\sf leak}}{A', \Sim} \leq 2^{-\tilde H_\infty({\cal D} \mid {\sf leak})}$.
+we must have $\ExpPrivSSsim{\setprim, {\sf leak}}{A', \Sim} \leq 2^{-\tilde H_\infty({\cal D} \mid {\sf leak})}$.
 This implies

### 2016-09-28 results.tex
cleaning

@@
 \caption{{\bf Left:} $\Rep$ and $\Qry$ algorithms for classic Bloom
-  filter $\Pi_{\mathrm{Bloom}}$ in the ROM for a hash function $H\colon \mathbb{N} \times
+  filter $\setprim_{\mathrm{Bloom}}$ in the ROM for a hash function $H\colon \mathbb{N} \times
   \univ \to [m]$. {\bf Right:} $\Rep$ and $\Qry$
   algorithms for the domain-separated PRF data structure
-  $\Pi_{\mathrm{ds}}$, using function family $F \colon
-  \calK \times \univ \to [m]$.  Both constructions have query set is $\calQ=\{q_x\colon
+  $\setprim_{\mathrm{ds}}$, using function family $F \colon
+  \calK \times \elts \to [m]$.  Both constructions have query set is $\calQ=\{q_x\colon
   \univ \to \bits\}$ where $q_x(S)=1 \Leftrightarrow x \in S$.  }
@@
 Fix $n,k,m \geq 0$, and fix a universe~$\univ$.
-Then $\Pi_{\mathrm{Bloom}}= (\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-lin} (left side).
-We define~$\Pi_{\mathrm{Bloom}}$ in the random oracle model, as the traditional analysis of Bloom filter correctness (as a function of $n,k,m$) is done in this model.\footnote{The standard model version would have $\Rep$ choose $H_1,H_2,\ldots,H_k$ from a hash function family, compute $h_j$ using these, and placing their description in $\pubaux$.}  The following theorem proves that the Bloom filter meets our correctness notion in the ROM.
+Then $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-lin} (left side).
+We define~$\setprim_{\mathrm{Bloom}}$ in the random oracle model, as the traditional analysis of Bloom filter correctness (as a function of $n,k,m$) is done in this model.\footnote{The standard model version would have $\Rep$ choose $H_1,H_2,\ldots,H_k$ from a hash function family, compute $h_j$ using these, and placing their description in $\pubaux$.}  The following theorem proves that the Bloom filter meets our correctness notion in the ROM.
 Again, we stress that this correctness is with respect to adaptive adversaries, aiming to find $r \geq 1$ errors (in this case, false-positives).
@@
 \begin{theorem}\label{thm3}\label{thm:bf-correctness}
-Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{Bloom}}= (\Rep, \Qry)$ be the set-multiplicity data structure just described.
+Fix $k,m,n,r>0$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be the set-multiplicity data structure just described.
 For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
 \[
-\AdvCorrect{\Pi_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
 \]
@@
 \begin{theorem}\label{thm3}\label{thm:bf-ow} \todo{Finish typesetting.  Result is on chalkboard.}
-Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{Bloom}}= (\Rep, \Qry)$ be the set-multiplicity data structure just described.
+Fix $k,m,n,r>0$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be the set-multiplicity data structure just described.
 Let $\distr{}{}$ be a distribution over subsets of universe~$\univ$, where $\mu = H_\infty(\distr{}{})$.
@@
 \[
-\AdvPrivOW{\Pi_{\mathrm{Bloom}},\distr{}{},r}{A} \leq  \frac{(kqn+n)}{2^{\mu}}
+\AdvPrivOW{\setprim_{\mathrm{Bloom}},\distr{}{},r}{A} \leq  \frac{(kqn+n)}{2^{\mu}}
 \]
@@
 \begin{theorem}
-Let $\Pi=(\Rep, \Qry)$ be a canonical set-multiplicity data structure for which $\Rep$ has canonical representation
+Let $\setprim=(\Rep, \Qry)$ be a canonical set-multiplicity data structure for which $\Rep$ has canonical representation
 $(\Rep_1, \Rep_2, F)$. If $F$ is a $(t, \epsilon)$-pseudorandom
-function \tsnote{overloading~$t$}, then $\Pi$ is semantically secure
+function \tsnote{overloading~$t$}, then $\setprim$ is semantically secure
 with respect to leakage function ${\sf leak}(S) = |S|$.
@@
 \heading{Correctness. }
-Let $\Pi_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-membership data
+Let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-membership data
 structure defined on the right-side of Figure~\ref{fig:lin-and-ds}.
@@
 \begin{theorem}\label{thm2}\label{thm:ds-correctness}
-Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-multiplicity data structure in Figure~\ref{fig:lin-and-ds}.
+Fix $k,m,n,r>0$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-multiplicity data structure in Figure~\ref{fig:lin-and-ds}.
 For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exists a prf-adversary ~$B$ (explicitly constructed in the proof of this theorem) such that
 \[
-\AdvCorrect{\Pi_{\mathrm{ds}},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\AdvCorrect{\setprim_{\mathrm{ds}},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
 \]
@@
 \heading{Privacy. }
-The privacy of $\Pi_{\mathrm{ds}}$ follows directly from our general result, Theorem~\ref{thm:xxx}.
-
+The privacy of $\setprim_{\mathrm{ds}}$ follows directly from our general result, Theorem~\ref{thm:xxx}.
 \begin{theorem}\label{thm:ds-ss}
-Fix $k,m,n>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
+Fix $k,m,n>0$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
 For any set~$S$, let $\leak(S)=|S|$.
@@
 \[
-\AdvPrivSS{\Pi_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
+\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
 \]
@@
 \begin{theorem}\label{thm:ds-ss}
-Fix $k,m,n>0$, and let $\Pi_{\mathrm{ds}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
+Fix $k,m,n>0$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
 For any set~$S$, let $\leak(S)=|S|$.
@@
     decomposes into $\Rep_1$ and $\Rep_2$.}
-Adversary~$B^{f}$ simulates the steps of $\ExpPrivSSreal{\Pi_{\mathrm{ds}}}{A}$, using its oracle to simuate~$\Rep(S)$.
+Adversary~$B^{f}$ simulates the steps of $\ExpPrivSSreal{\setprim_{\mathrm{ds}}}{A}$, using its oracle to simuate~$\Rep(S)$.
 When~$f=F_K$ then the simulation is perfect.
-When~$f=\rho$ then~$B$ simulates $\ExpPrivSSreal{\overline{\Pi}_{\mathrm{ds}}}{A}$ where $\overline{\Rep}$ effectively uses~$k$ independent random functions as the hash functions.
+When~$f=\rho$ then~$B$ simulates $\ExpPrivSSreal{\overline{\setprim}_{\mathrm{ds}}}{A}$ where $\overline{\Rep}$ effectively uses~$k$ independent random functions as the hash functions.
 But the $\pub$ produced by $\overline{\Rep}$ has a distribution that depends only~$|S|=n$, not the specific elements of~$S$, and the other public parameters~$m,k$.
@@
 \caption{{\bf Left:} $\Rep$ and $\Qry$ algorithms for the linear-PRF
-  data structure $\Pi_{\mathrm{lin}}$ {\bf Right:}
-The scheme from Neidermayer et al.\cite{xxx}, $\Pi_{\bilin}$. The $\mathsf{bigram}$
+  data structure $\setprim_{\mathrm{lin}}$ {\bf Right:}
+The scheme from Neidermayer et al.\cite{xxx}, $\setprim_{\bilin}$. The $\mathsf{bigram}$
 algorithm takes a string~$x=x_1,x_2,\ldots,x_\ell$ as input, and
@@
 For now, let $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.
-Then $\Pi_{\mathrm{lin}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:lin-and-ds} (left side).
-The following result shows, informally, that if~$F$ is a good PRF, then $\Pi_\mathrm{lin}$ is correct against adaptive error-finding adversaries.
+Then $\setprim_{\mathrm{lin}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:lin-and-ds} (left side).
+The following result shows, informally, that if~$F$ is a good PRF, then $\setprim_\mathrm{lin}$ is correct against adaptive error-finding adversaries.
 
 \begin{theorem}\label{thm1}\label{thm:lin-correctness}
-Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{lin}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-bin-lin}.
+Fix $k,m,n,r>0$, and let $\setprim_{\mathrm{lin}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-bin-lin}.
 For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exist prf-adversaries~$B_1,B_2$ (explicitly constructed in the proof of this theorem) such that
 \[
-\AdvCorrect{\Pi_{\mathrm{lin}},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\AdvCorrect{\setprim_{\mathrm{lin}},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
 \]
@@
 The proof appears in Appendix~\ref{app:xxx}.  We note that Kirsch and Mitzenmacher~\cite{xxx} show
-that the ($r=1$, zero-query) FP-probability for~$\Pi_\mathrm{lin}$ is
+that the ($r=1$, zero-query) FP-probability for~$\setprim_\mathrm{lin}$ is
 always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
@@
 \begin{theorem}\label{thm:lin-privacy}
-Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-bin-lin}.
+Fix $k,m,n,r>0$, and let $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-bin-lin}.
 For any set~$S$, let $\leak(S)=|S|$.
@@
 \begin{theorem}\label{thm:bi-lin-ss}
-Let $\Pi_{\bilin}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.
+Let $\setprim_{\bilin}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.
 Let $\leak$ be the leakage function just described.
@@
 It isn't used in any essential way in the proof sketch.}  Let~$A$ be the adversary in Figure~\ref{fig:adv-bi-lin-ss}.
-Then for any simulator $\Sim$, the advantage $\AdvPrivSS{\Pi_{\bilin},\leak}{A,\Sim}$ can be made arbitrarily close to $1/2$ by choice of~$\alpha$.
+Then for any simulator $\Sim$, the advantage $\AdvPrivSS{\setprim_{\bilin},\leak}{A,\Sim}$ can be made arbitrarily close to $1/2$ by choice of~$\alpha$.
 
@@
 In this case, the hamming weight of $M_{1,2} \wedge M_3$ will be $3k$.
-Thus $\ExpPrivSSreal{\Pi_{\bilin}}{A}=1$ with overwhelming probability.
+Thus $\ExpPrivSSreal{\setprim_{\bilin}}{A}=1$ with overwhelming probability.
 
@@
 bit~$z$, so at best it can cause~$A$ to output 1 with
-probabilility~$1/2$.  That is $\ExpPrivSSsim{\Pi_{\bilin}}{A,\Sim} \leq 1/2$.
+probabilility~$1/2$.  That is $\ExpPrivSSsim{\setprim_{\bilin}}{A,\Sim} \leq 1/2$.
 \end{proof}
@@
 \begin{theorem}\label{thm:bi-ds-ss}
-Let $\Pi_{\bilin}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.
+Let $\setprim_{\bilin}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.
 Let $\leak$ be the leakage function described just prior to Theorem~\ref{thm:bi-lin-ss}.
@@
 Then for any simulator $\Sim$,
-the advantage $\AdvPrivSS{\Pi_{\mathrm{ds}},\leak}{A,\Sim}$ can be made arbitrarily close to $1/2$ by choice of~$\alpha$.
+the advantage $\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim}$ can be made arbitrarily close to $1/2$ by choice of~$\alpha$.
 \end{theorem}
@@
 \caption{ $\Rep$ and $\Qry$ algorithms for garbled Bloom
-  filter $\Pi_{\mathrm{garbled}}$ in the ROM for a hash function $H\colon \calK \times 
+  filter $\setprim_{\mathrm{garbled}}$ in the ROM for a hash function $H\colon \calK \times 
  \univ \to [m]$. The query set is $\calQ=\{\qry_x\colon

### 2016-09-28 syntax.tex
cleaning

@@
 $\mathrm{Err}(S,\qry,\pubaux,\privaux)$ be  true iff
-$\Qry(\pubaux,\privaux, \qry) \neq \qry(S)$.  Then we say that $\Pi$
+$\Qry(\pubaux,\privaux, \qry) \neq \qry(S)$.  Then we say that $\setprim$
 has \emph{error probability}~$\epsilon$ if
@@
 \jnote{The following may need to be updated to fit the new syntax.}
-Let~$\Pi$ be a data structure that has error-probability $\epsilon$,
+Let~$\setprim$ be a data structure that has error-probability $\epsilon$,
 and consider a correctness-violating attack that asks random queries

### 2016-09-28 notions.tex
cheers

@@
 min-entropy} of ${\cal D}$ is defined as
-\[H_\infty({\cal D}) \bydef -\log \max_{x \in {\cal X}} \Pr[S \getsr {\cal D} : x \in S].\]
+$H_\infty({\cal D}) \bydef -\log \max_{x \in {\cal X}} \Pr[S \getsr {\cal D} : x \in S]$.
 
@@
 
-\begin{theorem}
+\begin{theorem}\todo{rewrite}
 Let $\setprim$ be a set-representation data structure that is $(t, \epsilon)$-semantically secure

### 2016-09-28 results.tex
cheers

@@
   filter $\setprim_{\mathrm{Bloom}}$ in the ROM for a hash function $H\colon \mathbb{N} \times
-  \univ \to [m]$. {\bf Right:} $\Rep$ and $\Qry$
+  \elts \to [m]$. {\bf Right:} $\Rep$ and $\Qry$
   algorithms for the domain-separated PRF data structure
@@
 \heading{Correctness. }
-Fix $n,k,m \geq 0$, and fix a universe~$\univ$.
-Then $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-lin} (left side).
+Fix $n,k,m \geq 0$, and fix a set $\elts$.
+Then the classical Bloom filter set-membership data structure $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-lin} (left side).
 We define~$\setprim_{\mathrm{Bloom}}$ in the random oracle model, as the traditional analysis of Bloom filter correctness (as a function of $n,k,m$) is done in this model.\footnote{The standard model version would have $\Rep$ choose $H_1,H_2,\ldots,H_k$ from a hash function family, compute $h_j$ using these, and placing their description in $\pubaux$.}  The following theorem proves that the Bloom filter meets our correctness notion in the ROM.
@@
 \begin{theorem}\label{thm3}\label{thm:bf-correctness}
-Fix $k,m,n,r>0$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be the set-multiplicity data structure just described.
+Fix $k,m,n,r>0$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be classical Bloom filter set-membership data structure.
 For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
@@
 
-\begin{theorem}\label{thm3}\label{thm:bf-ow} \todo{Finish typesetting.  Result is on chalkboard.}
+\begin{theorem}\label{thm3}\label{thm:bf-ow} 
 Fix $k,m,n,r>0$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be the set-multiplicity data structure just described.
@@
 \end{theorem}
+\todo{Typeset simple proof.  Result is on chalkboard.}
 
-\subsection{Privacy of Secretly Keyed Canonical Data Structures}
-Here we prove a result that can be used to show that a large class of ``canonical''
-data structures are semantically secure, with respect to leakage of the size of the set.
+\subsection{Privacy of Secretly-Keyed ``Canonical'' Data Structures}
+Here we prove a result that can be used to show that a large class of canonical
+data structures are SS-secure, with respect to leakage of the size of the set.
 \jnote{It would not be too hard to generalize this to arbitrary data structures over
@@
 depends only on ${\sf leak}$.}
-
 We first define what we mean by ``canonical.''
@@
 \begin{definition}
-A set-multiplicity data structure $(\Rep, \Qry)$ is {\sf canonical} if
+A data structure $(\Rep, \Qry)$ is {\sf canonical} if
 there exist algorithms $\Rep_1, \Rep_2$, and a function
@@
 \end{itemize}
-In this case, we say that $(\Rep_1, \Rep_2, F)$ is the {\sf canonical representation}
-of~$\Rep$. \tsnote{Seems odd to call it this without explaining how
+We say that $(\Rep_1, \Rep_2, F)$ is the {\sf canonical representation}
+of~$\Rep$. \hfill\dqed \tsnote{Seems odd to call it this without explaining how
   this canonical representation handles $\privaux$, too.  }
@@
 
-\begin{theorem}
-Let $\setprim=(\Rep, \Qry)$ be a canonical set-multiplicity data structure for which $\Rep$ has canonical representation
+\begin{theorem}\todo{Rewrite to match old DS-PRF proof}
+Let $\setprim=(\Rep, \Qry)$ be a canonical data structure for which $\Rep$ has canonical representation
 $(\Rep_1, \Rep_2, F)$. If $F$ is a $(t, \epsilon)$-pseudorandom
@@
 with respect to leakage function ${\sf leak}(S) = |S|$.
-\tsnote{We have a mixture of styles of theorem statements, resource-parameterized statements vs.\ ``verbose'' concrete statements.  We
-  need to make things uniform.}
 \end{theorem}
@@
 For any set~$S$, let $\leak(S)=|S|$.
-There exists a simulator~$\Sim$ such that, for any adversary~$A$
+There exists a simulator~$\Sim$ and adversary~$B$ such that, for any adversary~$A$
 \[
@@
 \]
-where~$B$ is constructed from~$A$.  
 %(Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
@@
 For any set~$S$, let $\leak(S)=|S|$.
-There exists a simulator~$\Sim$ such that, for any adversary~$A$
+There exists a simulator~$\Sim$ and an adversary~$B$ such that, for any adversary~$A$
 \[
@@
   filter $\setprim_{\mathrm{garbled}}$ in the ROM for a hash function $H\colon \calK \times 
- \univ \to [m]$. The query set is $\calQ=\{\qry_x\colon
+ \elts \to [m]$. The query set is $\calQ=\{\qry_x\colon
   \univ \to \bits\}$ where $\qry_x(S)=1 \Leftrightarrow x \in S$.}

### 2016-09-28 results.tex
cheers

@@
 \nudge\nudge $\overline{M}[i] \gets 1$\\
-if $M \in \pubaux$ then Return 1 \\
+if $\overline{M} \in \pubaux$ then Return 1 \\
 Return 0
@@
 \heading{Correctness. }
-For now, let $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.
-Then $\setprim_{\mathrm{lin}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:lin-and-ds} (left side).
-The following result shows, informally, that if~$F$ is a good PRF, then $\setprim_\mathrm{lin}$ is correct against adaptive error-finding adversaries.
+For now, let $n,k,m \geq 0$.
+Then $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ is defined as in Figure~\ref{fig:lin-and-ds} (left side).
+The following result shows, informally, that if~$F$ is a good PRF, then $\setprim_{\mathrm{lin}}$ is correct against adaptive error-finding adversaries.
 
 \begin{theorem}\label{thm1}\label{thm:lin-correctness}
-Fix $k,m,n,r>0$, and let $\setprim_{\mathrm{lin}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-bin-lin}.
+Fix $k,m,n,r>0$, and let $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-bin-lin}.
 For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exist prf-adversaries~$B_1,B_2$ (explicitly constructed in the proof of this theorem) such that

### 2016-09-28 Theorem1_FP.tex
Syntax consistency of proof1

@@
+%F_{K}(\langle 1,x \rangle) + j\cdot F_{K}(\langle 2,x \rangle) \bmod m
 \begin{proof}[\Cref{thm1}]
 The proof of the theorem will use a game playing argument as shown in \Cref{fig:Game}.
-$\game{0}(A)$ exactly simulates $\ExpCorrect{\Pi_\mathrm{lin},\distr{\calS}{},r}{A}$ with hash functions $h_j(x) =  F_{K_0}(x) + j\cdot F_{K_1}(x) \bmod m$.
+$\game{0}(A)$ exactly simulates $\ExpCorrect{\Pi_\mathrm{lin},\distr{\calS}{},r}{A}$ with hash functions $h_j(x) =  F_{K}(\langle 1,x \rangle) + j\cdot F_{K}(\langle 2,x \rangle) \bmod m$.
 So,
@@
 
- In $\game{1}(A)$, $F_{K_1}$ is replaced by a random function, whereas in $\game{2}(A)$, both $F_{K_0}$ and $F_{K_1}$ are replaced by random functions.
+ In $\game{1}(A)$, $F_{K}(\langle 1,\cdot \rangle)$ is replaced by a random function, whereas in $\game{2}(A)$, both $F_{K}(\langle 1,\cdot \rangle)$ and $F_{K}(\langle 2, \cdot \rangle)$ are replaced by random functions.
 
@@
 {
-$\adversaryv{B_1^{\calO}}$\\
-$S \getsr \distr{\calS}{}$\\
+$\adversaryv{B_1^{\calO}(S, \pubaux)}$\\
+%$S \getsr A$\\
 $\calC \gets \emptyset$; $\err \gets 0$\\
-$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
-Run~$A(S, \pubaux)$\\
-When $A$ asks $\TestOracle(q_x)$:\\
-\nudge if $q_x \in \mathcal{C}$ then Return $\bot$\\
-\nudge $\calC \gets \calC \cup \{q_x\}$\\
-\nudge $a \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
-\nudge if $a \neq q_x(S)$ then \\
+%$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+Run~$A(\pubaux)$\\
+When $A$ asks $\TestOracle(\qry_x)$:\\
+\nudge if $x \in \mathcal{C}$ then Return $\bot$\\
+\nudge $\calC \gets \calC \cup x$\\
+\nudge $a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
+\nudge if $a \neq \qry_x(S)$ then \\
 \nudge \nudge $\err \gets \err + 1$\\
@@
 \oracle{$\HashOracle(x)$}\\
-Return $F_{K_1}(x) + i\cdot \calO(x)$, for $i\in[1,k]$\\
+for $i \in \{1,2,\ldots,k\}$\\
+\nudge $v_i \gets F_{K}(\langle 1,x \rangle) + i \cdot \calO(\langle 2,x \rangle) \bmod m$\\
+Return ${v_1,v_2,\ldots,v_k}$
 }
 {
-$\adversaryv{B_2^{\calO}}$\\
-$S \getsr \distr{\calS}{}$\\
+$\adversaryv{B_2^{\calO}(S, \pubaux)}$\\
+%$S \getsr A$\\
 $\calC \gets \emptyset$; $\err \gets 0$\\
-$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
-Run~$A(S, \pubaux)$\\
-When $A$ asks $\TestOracle(q_x)$:\\
-\nudge if $q_x \in \mathcal{C}$ then Return $\bot$\\
-\nudge $\calC \gets \calC \cup \{q_x\}$\\
-\nudge $a \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
-\nudge if $a \neq q_x(S)$ then \\
+%$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+Run~$A(\pubaux)$\\
+When $A$ asks $\TestOracle(\qry_x)$:\\
+\nudge if $x \in \mathcal{C}$ then Return $\bot$\\
+\nudge $\calC \gets \calC \cup x$\\
+\nudge $a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
+\nudge if $a \neq \qry_x(S)$ then \\
 \nudge \nudge $\err \gets \err +1$\\
@@
 \nudge Return 1\\\\
+%
 \oracle{$\HashOracle(x)$}\\
@@
 $T[x] \gets a$\\
-Return  $\calO(x) + i\cdot a$, for $i\in[1,k]$
+for $i \in \{1,2,\ldots,k\}$\\
+\nudge $v_i \gets \calO(\langle 1,x \rangle) + i\cdot a$\\
+Return ${v_1,v_2,\ldots,v_k}$
 }
@@
 \begin{figure}
-\fpage{.9}{
-\hpagessl{.45}{.5}
+\fpage{.99}{
+\hpagessl{.52}{.5}
 {
 \underline{\game{0}(A)}\\
-$S \getsr \distr{\calS}{}$; $\calC \gets \emptyset$; $\err \gets 0$\\
+$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
 $(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
-$\bot \getsr A^{\TestOracle}(S,\pubaux)$\\
+$\bot \getsr A^{\TestOracle}(\pubaux)$\\
 if $\err  < r$ then Return 0\\
@@
 %
-\oracle{$\TestOracle(q_x)$}\\
-if $q_x \in \mathcal{C}$ then Return $\bot$\\
-$\calC \gets \calC \cup \{q_x\}$\\
-$a \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
-if $a \neq q_x(S)$ then $\err \gets \err + 1$\\
+\oracle{$\TestOracle(\qry_x)$}\\
+if $x \in \mathcal{C}$ then Return $\bot$\\
+$\calC \gets \calC \cup x$\\
+$a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
+if $a \neq \qry_x(S)$ then $\err \gets \err + 1$\\
 Return~$a$\\
@@
 for $i = 1$ to $k$\\
-\nudge $h_i(x) = F_{K_1}(x)+i \cdot F_{K_2}(x) \bmod m$\\
+\nudge $h_i(x) = F_{K}(\langle 1,x \rangle) + i\cdot F_{K}(\langle 2,x \rangle) \bmod m$\\
 Ret $\left(h_1(x),\ldots,h_k(x)\right)$
@@
 \underline{\game{1}(A)}\\
-$\rho \getsr \Func{\univ,[m]}$\\
-$S \getsr \distr{\calS}{}$; $\calC \gets \emptyset$; $\err \gets 0$\\
+$K \getsr \calK$, $\rho \getsr \Func{\univ,[m]}$\\
+$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
 $(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
-$\bot \getsr A^{\TestOracle}(S,\pubaux)$\\
+$\bot \getsr A^{\TestOracle}(\pubaux)$\\
 if $\err  < r$ then Return 0\\
@@
 for $i=1$ to $k$\\
-\nudge $h_i(x) = F_{K_1}(x)+i \cdot \rho(x) \bmod m$\\
+\nudge $h_i(x) = F_{K}(\langle 1,x \rangle) + i \cdot \rho(x) \bmod m$\\
 Ret $\left(h_1(x),\ldots,h_k(x)\right)$
@@
 }
-\fpage{.9}{
-\hpagessl{.45}{.5}
+\fpage{.99}{
+\hpagessl{.52}{.5}
 {
@@
 $\rho_1,\rho_2 \getsr \Func{\univ,[m]}$\\
-$S \getsr \distr{\calS}{}$; $\calC \gets \emptyset$; $\err \gets 0$\\
+$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
 $(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
-$\bot \getsr A^{\TestOracle}(S,\pubaux)$\\
+$\bot \getsr A^{\TestOracle}(\pubaux)$\\
 if $\err  < r$ then Return 0\\
@@
 %
-\oracle{$\TestOracle(q_x)$}\\
-if $q_x \in \mathcal{C}$ then Return $\bot$\\
-$\calC \gets \calC \cup \{q_x\}$\\
-$a \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
-if $a \neq q_x(S)$ then $\err \gets \err + 1$\\
+\oracle{$\TestOracle(\qry_x)$}\\
+if $x \in \mathcal{C}$ then Return $\bot$\\
+$\calC \gets \calC \cup x$\\
+$a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
+if $a \neq \qry_x(S)$ then $\err \gets \err + 1$\\
 Return~$a$\\\\
@@
 for $i=1$ to $k$\\
-\nudge $h_i(x) = \rho_1(x)+i \cdot \rho_2(x) \bmod m$\\
+\nudge $h_i(x) = \rho_1(x) + i \cdot \rho_2(x) \bmod m$\\
 Ret $\left(h_1(x),\ldots,h_k(x)\right)$
@@
 $c\gets 0$, $\bad \gets \false$, $\err \gets 0$;  $\calC \gets \emptyset$\\
-$S \getsr \distr{\calS}{}$; $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
+$S \getsr A$; $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
 $(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
-$\bot \getsr A^{\TestOracle}(S,\pubaux)$\\
+$\bot \getsr A^{\TestOracle}(\pubaux)$\\
 if $\bad = \true$ then \fbox{Return 0}\\
@@
 %
-\oracle{$\TestOracle(q_x)$}\\
-if $q_x \in \mathcal{C}$ then Return $\bot$\\
-$\calC \gets \calC \cup \{q_x\}$\\
+\oracle{$\TestOracle(\qry_x)$}\\
+if $x \in \mathcal{C}$ then Return $\bot$\\
+$\calC \gets \calC \cup x$\\
 $c \gets c+1$\\
-$v \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
-if $c \in \mathcal{I}$ and $v = q_x(S)$ then \\
+$v \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
+if $c \in \mathcal{I}$ and $v = \qry_x(S)$ then \\
 \nudge $\bad \gets \true$ \\
-if $c \not\in \mathcal{I}$ and $v \neq q_x(S)$ then \\
+if $c \not\in \mathcal{I}$ and $v \neq \qry_x(S)$ then \\
 \nudge $\bad \gets \true$\\
-if $v \neq q_x(S)$ then $\err \gets \err +1$\\
+if $v \neq \qry_x(S)$ then $\err \gets \err +1$\\
 Return~$v$\\
@@
 \centering
-\fpage{0.45}{
-\hpagess{0.4}{0.35}
+\fpage{0.55}{
+\hpagess{0.5}{0.35}
 {
@@
 $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
-Run $A(S, \pubaux)$\\
-When $A$ asks $\TestOracle(q_x)$:\\
-\nudge if $q_x \in \mathcal{C}$ then Return $\bot$\\
-\nudge $\calC \gets \calC \cup \{q_x\}$\\
+Run $A(\pubaux)$\\
+When $A$ asks $\TestOracle(\qry_x)$:\\
+\nudge if $x \in \mathcal{C}$ then Return $\bot$\\
+\nudge $\calC \gets \calC \cup x$\\
 \nudge $c \gets c+1$\\

### 2016-09-28 intro.tex
comments in intro

@@
 Yogev~\cite{naor2015bloom} recently considered the problem of
-adversarial soundness for (variants of) Bloom filters and, indeed,
+adversarial soundness for Bloom filters and, indeed,
 their worked served as inspiration for our own. Our work extends
@@
 \end{itemize}
+\tsnote{I think we can say a bit more here about what they show, and
+  why their presentation is lacking, certainly as a work that anchors
+  an important area of study.  This feels a bit weak, at the moment.
+  For example, at the opening of this section we say they consider
+  ``adversarial soundness for Bloom filters'', but I assert that it
+  isn't clear that their syntax allows them to study Bloom filters at all.}
+We give a more detailed comparison to, and criticism of~\cite{naor2015bloom} in Appendix~\ref{sec:xxx}.
 
+\todo{Describe the BF variants we consider, and briefly why they are
+  natural/interesting.}
+\todo{Surface contribution of setting the stage for a bunch of future
+  work: dynamic data-structures (including counting BFs, stable BFs,
+  hierachical BFs, count-min-sketches, etc.); security of common
+  usages of BF and related data structrues (e.g. CDNs and other
+  distributed storage, find more); more generally bringing to the
+  attention of the community the need to give proper cryptographic
+  treatment to data structures (which may not have been conceived with
+  security-critical applications in mind but have been co-opted for
+  them (like BFs).}
 %false-positive error, is a parameter of the Bloom filter.  (The

### 2016-09-28 results.tex
comments in intro

@@
 \begin{theorem}\label{thm3}\label{thm:bf-correctness}
-Fix $k,m,n,r>0$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be classical Bloom filter set-membership data structure.
+Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be classical Bloom filter (set-membership) data structure.
 For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
@@
 \end{theorem}
-
+The proof appears in Appendix~\ref{app:xxx}.  We note that Kirsch and Mitzenmacher~\cite{xxx} show
+that the ($r=1$, zero-query) FP-probability for~$\setprim_\mathrm{Bloom}$ is
+always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
+rate of convergence is faster than~$1/n$.  The multiplicative (``hybrid'') term arises as a result
+of moving from the adaptive to the zero-query setting.  
+Finally, $\dbinom{q_T+q_H}{r} \leq (q_T+q_H)^r$ (with reasonable tightness when~$r$ is small) in 
+which case the final term in the bound behaves as
+$((q_T+q_H) (1-e^{-kn/m})^k + O(q/n) )^r$; loosely, this is the bound one expects for
+trying to find a single FP in each of~$r$ independent``rounds'', each round
+consisting of~$(q_T+q_H)$ attempts.
 %\input{Theorem3_FP}
@@
 \begin{theorem}\label{thm3}\label{thm:bf-ow} 
-Fix $k,m,n,r>0$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be the set-multiplicity data structure just described.
-Let $\distr{}{}$ be a distribution over subsets of universe~$\univ$, where $\mu = H_\infty(\distr{}{})$.
+Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be the classical Bloom filter data structure just described.
+Let $\distr{}{}$ be a distribution over subsets of universe~$\univ=2^\elts$, where $\mu = H_\infty(\distr{}{})$.
 For any adversary~$A$ that makes $q$~queries to its oracle
@@
 \begin{theorem}\label{thm2}\label{thm:ds-correctness}
-Fix $k,m,n,r>0$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-multiplicity data structure in Figure~\ref{fig:lin-and-ds}.
+Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-membership data structure in Figure~\ref{fig:lin-and-ds}.
 For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exists a prf-adversary ~$B$ (explicitly constructed in the proof of this theorem) such that
@@
 \begin{theorem}\label{thm:ds-ss}
-Fix $k,m,n>0$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
-For any set~$S$, let $\leak(S)=|S|$.
+Fix $k,m,n>0$, a set~$\elts$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-membership data structure described in Figure~\ref{fig:lin-and-ds}.
+For any set~$S \in 2^\elts$, let $\leak(S)=|S|$.
 There exists a simulator~$\Sim$ and adversary~$B$ such that, for any adversary~$A$
@@
 Fix $k,m,n>0$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
-For any set~$S$, let $\leak(S)=|S|$.
+For any set~$S \in 2^\elts$, let $\leak(S)=|S|$.
 There exists a simulator~$\Sim$ such that, for any adversary~$A$
@@
 returns the set of bigrams for the left- and right-padded string
-$\sqcup x \sqcup$, i.e. $\{\sqcup x_1, x_1x_2,\ldots,x_\ell\sqcup\}$.
+$\sqcup x \sqcup$, i.e. $\{\sqcup x_1, x_1x_2,\ldots,x_{\ell-1}x_\ell,x_\ell\sqcup\}$.
 }
@@
 \begin{theorem}\label{thm1}\label{thm:lin-correctness}
-Fix $k,m,n,r>0$, and let $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-bin-lin}.
+Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-membership data structure described in Figure~\ref{fig:lin-and-bin-lin}.
 For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exist prf-adversaries~$B_1,B_2$ (explicitly constructed in the proof of this theorem) such that
@@
 always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
-rate of convergence is faster than~$1/n$.  The factor of $\dbinom{q}{r}$ arises as a result
-of moving from the adaptive to the zero-query setting.  Finally, $\dbinom{q}{r} \leq q^r$ (with
-reasonable tightness when~$r$ is small) in which case the final term in the bound behaves as
-$(q (1-e^{-kn/m})^k + O(q/n) )^r$; loosely, the bound one expects for
-trying to find a single FP in each of~$r$ independent``rounds'', each round
-consisting of~$q$ attempts.
+rate of convergence is faster than~$1/n$.   As in previous cases, the multiplicative term $\dbinom{q}{r}$ arises when switching from the adaptive to zero-query settings.
 
@@
 \begin{theorem}\label{thm:lin-privacy}
-Fix $k,m,n,r>0$, and let $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-bin-lin}.
+Fix $k,m,n,r>0$, a set $\elts$, and let $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-membership data structure described in Figure~\ref{fig:lin-and-bin-lin}.
 For any set~$S$, let $\leak(S)=|S|$.
@@
 \heading{Privacy. }
+Consider the set-membership data structure given in Figure~\ref{fig:lin-and-bi-lin} (right side), which we call the \emph{bigram linear-PRF} construction.
+This construction is of practical interest, as it has been suggested as a way to address the privacy-preserving record-linkage problem, in particular for linking common records in medical databases~\cite{neidermayer,xxx}.
 We only address the privacy of this construction, as the correctness follows immediately from the correctness of the Linear-PRF contruction.
@@
 On input a set~$S=\{x_1,x_2,\ldots,x_n\}$, it assigns $x'_n \gets x_n[1:|x_n|-1]$ and returns $\mathsf{leak}(S)=\{x_1,x_2,\ldots,x'_n\}$.
+\todo{OW privacy proof?
+Or just some text that says that Neidermayer et al show something stronger~---OW-privacy violation---~albeit with $n=10000, m=10000\alpha$ for an $\alpha$ that I need to look up.}
 
@@
 \centering
-\fpage{.55}
+\fpage{.65}
 {
@@
 Let $\leak$ be the leakage function just described.
-Let~$\univ=\{\mathrm{a,b,c}\}^*$.
+Let~$\elts=\{\mathrm{a,b,c}\}^*$.
 Let $n=3$,  $m=3\alpha $ for integer $\alpha >> 1$, and let, $k = \lceil \ln(2) \alpha \rceil$.\tsnote{This value of~$k$ is from the classical analysis for minimizing the FP rate for a Bloom filter, and is set this way for compatibility with classical results.
@@
 Then for any simulator $\Sim$, the advantage $\AdvPrivSS{\setprim_{\bilin},\leak}{A,\Sim}$ can be made arbitrarily close to $1/2$ by choice of~$\alpha$.
-
 \end{theorem}
@@
 
-\todo{OW privacy proof?
-Or just some text that says that Neidermayer et al show something stronger~---OW-privacy violation---~albeit with $n=10000, m=10000\alpha$ for an $\alpha$ that I need to look up.}
-
 %%%%%%%%%%%%%%%%% Bigram DOMAIN-SEPARATED PRF %%%%%%%%%%%%%%%%%%%%
@@
 Let $\leak$ be the leakage function described just prior to Theorem~\ref{thm:bi-lin-ss}.
-Let~$\univ=\{\mathrm{a,b,c}\}^*$.
+Let~$\elts=\{\mathrm{a,b,c}\}^*$.
 Let $n=3$,  $m=3\alpha $ for integer $\alpha >> 1$, and let, $k = \lceil \ln(2) \alpha \rceil$.\tsnote{This value of~$k$ is from the classical analysis for minimizing the FP rate for a Bloom filter, and is set this way for compatibility with classical results.

### 2016-09-28 results.tex
cleaning

@@
 \centering
-\hfpagess{.4}{.55}
+\hfpagess{.4}{.4}
 {
@@
 Fix $n,k,m \geq 0$, and fix a set $\elts$.
-Then the classical Bloom filter set-membership data structure $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-lin} (left side).
+Then the classical Bloom filter set-membership data structure $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ over~$\elts$ is defined as in Figure~\ref{fig:bf-and-lin} (left side).
 We define~$\setprim_{\mathrm{Bloom}}$ in the random oracle model, as the traditional analysis of Bloom filter correctness (as a function of $n,k,m$) is done in this model.\footnote{The standard model version would have $\Rep$ choose $H_1,H_2,\ldots,H_k$ from a hash function family, compute $h_j$ using these, and placing their description in $\pubaux$.}  The following theorem proves that the Bloom filter meets our correctness notion in the ROM.
@@
 \begin{theorem}\label{thm3}\label{thm:bf-correctness}
-Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be classical Bloom filter (set-membership) data structure.
+Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be classical Bloom filter (set-membership) data structure over~$\elts$.
 For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
@@
 \begin{theorem}\label{thm3}\label{thm:bf-ow} 
-Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be the classical Bloom filter data structure just described.
+Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be the classical Bloom filter data structure over~$\elts$.
 Let $\distr{}{}$ be a distribution over subsets of universe~$\univ=2^\elts$, where $\mu = H_\infty(\distr{}{})$.
@@
 \begin{theorem}\label{thm2}\label{thm:ds-correctness}
-Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-membership data structure in Figure~\ref{fig:lin-and-ds}.
+Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-membership data structure (over~$\elts$) in Figure~\ref{fig:lin-and-ds}.
 For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exists a prf-adversary ~$B$ (explicitly constructed in the proof of this theorem) such that
@@
 \begin{theorem}\label{thm1}\label{thm:lin-correctness}
-Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-membership data structure described in Figure~\ref{fig:lin-and-bin-lin}.
+Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-membership data structure (over~$\elts$) described in Figure~\ref{fig:lin-and-bin-lin}.
 For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exist prf-adversaries~$B_1,B_2$ (explicitly constructed in the proof of this theorem) such that
@@
 \begin{theorem}\label{thm:lin-privacy}
-Fix $k,m,n,r>0$, a set $\elts$, and let $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-membership data structure described in Figure~\ref{fig:lin-and-bin-lin}.
-For any set~$S$, let $\leak(S)=|S|$.
+Fix $k,m,n,r>0$, a set $\elts$, and let $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-membership data structure (over~$\elts$) described in Figure~\ref{fig:lin-and-bin-lin}.
+For any set~$S \in 2^{\elts}$, let $\leak(S)=|S|$.
 There exists a simulator~$\Sim$ and an adversary~$B$ such that, for any adversary~$A$
@@
 Here we exhibit an efficient SS-privacy attack even when simulator is provided nearly the entire set.
-Consider the following leakage function.
-On input a set~$S=\{x_1,x_2,\ldots,x_n\}$, it assigns $x'_n \gets x_n[1:|x_n|-1]$ and returns $\mathsf{leak}(S)=\{x_1,x_2,\ldots,x'_n\}$.
+Consider the following ``all-but-last'' leakage function.
+On input a set~$S=\{x_1,x_2,\ldots,x_n\}$, it assigns $x'_n \gets x_n[1:|x_n|-1]$ and returns $\mathsf{leak_{abl}}(S)=\{x_1,x_2,\ldots,x'_n\}$.
 \todo{OW privacy proof?
@@
 \begin{theorem}\label{thm:bi-lin-ss}
-Let $\setprim_{\bilin}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.
-Let $\leak$ be the leakage function just described.
+Let $\setprim_{\bilin}= (\Rep, \Qry)$ be the set-membership data structure described in Figure~\ref{fig:neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.
+Let $\leak_{\mathsf{abl}}$ be the leakage function just described.
 Let~$\elts=\{\mathrm{a,b,c}\}^*$.
@@
 It isn't used in any essential way in the proof sketch.}  Let~$A$ be the adversary in Figure~\ref{fig:adv-bi-lin-ss}.
-Then for any simulator $\Sim$, the advantage $\AdvPrivSS{\setprim_{\bilin},\leak}{A,\Sim}$ can be made arbitrarily close to $1/2$ by choice of~$\alpha$.
+Then for any simulator $\Sim$, the advantage $\AdvPrivSS{\setprim_{\bilin},\leak_{\mathsf{abl}}}{A,\Sim}$ can be made arbitrarily close to $1/2$ by choice of~$\alpha$.
 \end{theorem}
@@
 \begin{theorem}\label{thm:bi-ds-ss}
-Let $\setprim_{\bilin}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.
+Let $\setprim_{\bilin}= (\Rep, \Qry)$ be the set-membership data structure described in Figure~\ref{fig:neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.
 Let $\leak$ be the leakage function described just prior to Theorem~\ref{thm:bi-lin-ss}.

### 2016-09-28 intro.tex
cleaning

@@
 set-membership queries. Specifically, we show \ldots
+\todo{highlight that we are able surface ways in which constructions
+  are sensitive to use cases, i.e. schemes secure with secret hash
+  functions but not with public hash functions}
+\todo{Somewhere in the intro, might what to face the ``nothing hard''
+  criticism head on.  Perhaps mention that many of the results follow
+  a common pattern (which, for privacy, we tease out in a general
+  theorem), and that often the most technically difficult part is
+  connnecting the adaptive setting to the zero-query setting.}
 

### 2016-09-29 Theorem2_FP.tex

@@
 \underline{\game{0}(A)}\\
-$S \getsr \distr{\calS}{}$; $\calC \gets \emptyset$; $\err \gets 0$\\
+$K \getsr \calK $\\
+$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
 $(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
-$\bot \getsr A^{\TestOracle}(S,\pubaux)$\\
+$\bot \getsr A^{\TestOracle}(\pubaux)$\\
 if $\err  < r$ then Return 0\\
@@
 $(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
-$\bot \getsr A^{\TestOracle}(S,\pubaux)$\\
+$\bot \getsr A^{\TestOracle}(\pubaux)$\\
 if $\err  < r$ then Return 0\\
@@
 $(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
-$\bot \getsr A^{\TestOracle}(S,\pubaux)$\\
+$\bot \getsr A^{\TestOracle}(\pubaux)$\\
 if $\bad = \true$ then \fbox{Return 0}\\
@@
 {
-\oracle{$\TestOracle(q_x)$}\\
-if $q_x \in \mathcal{C}$ then Return $\bot$\\
-$\calC \gets \calC \cup \{q_x\}$\\
+\oracle{$\TestOracle(\qry_x)$}\\
+if $x \in \mathcal{C}$ then Return $\bot$\\
+$\calC \gets \calC \cup x$\\
 $c \gets c+1$\\
-$v \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
-if $c \in \mathcal{I}$ and $v = q_x(S)$ then \\
+$v \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
+if $c \in \mathcal{I}$ and $v = \qry_x(S)$ then \\
 \nudge $\bad \gets \true$ \\
-if $c \not\in \mathcal{I}$ and $v \neq q_x(S)$ then \\
+if $c \not\in \mathcal{I}$ and $v \neq \qry_x(S)$ then \\
 \nudge $\bad \gets \true$\\
-if $v \neq q_x(S)$ then $\err \gets \err +1$\\
+if $v \neq \qry_x(S)$ then $\err \gets \err +1$\\
 Return~$v$\\\\
@@
 \fpage{0.5}{
-$\adversaryv{B^{\calO}}$\\
-$S \getsr \distr{\calS}{}$\\
+$\adversaryv{B^{\calO}(S, \pubaux)}$\\
+%$S \getsr A$\\
 $\calC \gets \emptyset$; $\err \gets 0$\\
-$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
-Run~$A(S, \pubaux)$\\
-When $A$ asks $\TestOracle(q_x)$:\\
-\nudge if $q_x \in \mathcal{C}$ then Return $\bot$\\
-\nudge $\calC \gets \calC \cup \{q_x\}$\\
-\nudge $a \gets \Qry^{\HashOracle}(\pubaux,\privaux,q_x)$\\
-\nudge if $a \neq q_x(S)$ then \\
+%$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+Run~$A(\pubaux)$\\
+When $A$ asks $\TestOracle(\qry_x)$:\\
+\nudge if $x \in \mathcal{C}$ then Return $\bot$\\
+\nudge $\calC \gets \calC \cup x$\\
+\nudge $a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
+\nudge if $a \neq \qry_x(S)$ then \\
 \nudge \nudge $\err \gets \err +1$\\

### 2016-09-29 ny-def-comparison.tex

@@
 \section{Comparison to the Naor-Yogev definition.}
+\fixme{Uses $(t,q,\epsilon)$-style notion and theorem statements.  May
+be okay because this is a self contained appendix, but better if
+consistent with the rest of the document.}
 The structure of the Naor-Yogev definition is different from ours.

### 2016-09-29 intro.tex
no message

@@
 a data structure, but unacceptable to leak the data in its entirety
-to that same party. Existing definitions do not address this at~all.
+to that same party. Existing definitions do not address privacy in
+this sense at~all.
 
@@
 structures in an adversarial setting, where both \emph{soundness}
-\jnote{I like soundness better than correctness, but I won't
-insist.} and \emph{correctness} are considered. In this work we
-initiate such a treatment for abstract data structures, and also
-explore the security of several specific data structures---that can
-all be viewed as generalizations of Bloom
+\jnote{I like ``soundness'' better than ``correctness,'' but I won't
+insist.} and \emph{privacy} are considered. In this work we initiate
+such a treatment for abstract data structures, and also explore the
+security of several specific data structures---that can all be
+viewed as generalizations of Bloom
 filters~\cite{bloom1970space}---supporting (approximate)
-set-membership queries. Specifically, we show \ldots
-\todo{highlight that we are able surface ways in which constructions
+set-membership queries. Specifically, we show \ldots \todo{highlight
+that we are able surface ways in which constructions
   are sensitive to use cases, i.e. schemes secure with secret hash
@@
     we analyze Bloom filters in the random-oracle model.
-    \jnote{Do we? Perhaps we want to explicitly adapt some of
-    our definitions to the ROM?}
+    \jnote{Which are widely used?}
 \end{itemize}
@@
   isn't clear that their syntax allows them to study Bloom filters at all.}
-We give a more detailed comparison to, and criticism of~\cite{naor2015bloom} in Appendix~\ref{sec:xxx}.
+  \jnote{I'm a little concerned about walking the line between
+  criticizing them and offending them. I also wouldn't say ``their
+  syntax doesn't allow them to study Bloom filters''; is that
+  because they don't deal with random oracles?}
+We give a more detailed comparison to, and criticism
+of~\cite{naor2015bloom} in Appendix~\ref{sec:xxx}. \jnote{Any
+comparison/criticism should be in the Intro. The Appendix is just a
+technical comparison of different styles of definition.}
 
@@
   work: dynamic data-structures (including counting BFs, stable BFs,
-  hierachical BFs, count-min-sketches, etc.); security of common
+  hierarchical BFs, count-min-sketches, etc.); security of common
   usages of BF and related data structrues (e.g. CDNs and other

### 2016-09-29 notions.tex
cleaning
no message

@@
 set-multiplicity data structures.
-All adversaries are stateful by default.
+\jnote{I would call it ``soundness'' rather than ``correctness.'' But if you disagree,
+just remove this comment and we'll go with correctness.}
 
@@
 where finding the first false positive is hard but then the rest are easy; can have
-a scheme where finding one false positive is easy finding more is hard (e.g.,
+a scheme where finding one false positive is easy but finding more is hard (e.g.,
 because there do not exist
-any more).}
+any more). Note that the [NY15] definition does not capture this at all.}
 
@@
 %\end{figure}
+\todo{A simple theorem that says if $\privaux=\emptystring$ then
+  SS-privacy is unachievable for any leakage other than $\leak(S)=S$?
+It's at least worth a highlighted remark, I think.  Currently it is a
+remark in the classical BF section, but it seems worth ``pulling up''.} \jnote{Yes, agreed.}
 

### 2016-09-29 results.tex
no message

@@
-\section{Achieving Security Notions}
+\section{Case Studies}
+Here we explore various set-membership data structures that have been proposed
+in the literature with respect to our definitions.
 
@@
 
-\subsection{Classical Bloom filter in random oracle model (ROM). }
+\subsection{Classical Bloom Filter in the Random-Oracle Model}
 
-\heading{Correctness. }
-Fix $n,k,m \geq 0$, and fix a set $\elts$.
-Then the classical Bloom filter set-membership data structure $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ over~$\elts$ is defined as in Figure~\ref{fig:bf-and-lin} (left side).
-We define~$\setprim_{\mathrm{Bloom}}$ in the random oracle model, as the traditional analysis of Bloom filter correctness (as a function of $n,k,m$) is done in this model.\footnote{The standard model version would have $\Rep$ choose $H_1,H_2,\ldots,H_k$ from a hash function family, compute $h_j$ using these, and placing their description in $\pubaux$.}  The following theorem proves that the Bloom filter meets our correctness notion in the ROM.
-Again, we stress that this correctness is with respect to adaptive adversaries, aiming to find $r \geq 1$ errors (in this case, false-positives).
+Fix $n,k,m \geq 0$, and fix a set $\elts$.  Then the classical Bloom
+filter set-membership data structure $\setprim_{\mathrm{Bloom}}=
+(\Rep, \Qry)$ over~$\elts$ is defined as in
+Figure~\ref{fig:bf-and-lin} (left side).  We
+define~$\setprim_{\mathrm{Bloom}}$ in the random-oracle model
+(ROM), as the traditional analysis of Bloom filter correctness (as a
+function of $n,k,m$) is done in this model.\footnote{The standard
+model version would have $\Rep$ choose $H_1,H_2,\ldots,H_k$ from a
+hash function family, compute $h_j$ using these, and placing their
+description in $\pubaux$.}
+
+\heading{Correctness. } The following theorem proves that the Bloom
+filter meets our correctness notion in the ROM.  Again, we stress
+that this correctness is with respect to adaptive adversaries,
+aiming to find $r \geq 1$ errors (in this case, false-positives).
 The proof appears in Appendix~\ref{sec:thm3_fp}.
@@
 \subsection{Privacy of Secretly-Keyed ``Canonical'' Data Structures}
+\jnote{Maybe this should be moved to Section~3.2?}
+
 Here we prove a result that can be used to show that a large class of canonical
@@
 of~$\Rep$. \hfill\dqed \tsnote{Seems odd to call it this without explaining how
-  this canonical representation handles $\privaux$, too.  }
+  this canonical representation handles $\privaux$, too.} \jnote{It
+  doesn't matter what priv is.}
 \end{definition}
@@
   not work in this case, of course.) It does not cover Neidermayer because there's no guarantee of distinct $s_1,\ldots,s_t$. }
+  \jnote{I say we state the general theorem in Section~3.2 and just
+  promise that applications will come in Section~4.}
 We next show that any canonical data structure in which~$F$ is a pseudorandom function is
@@
 \begin{proof}
-We define a simulator $\Sim$ as follows. On input $n$, $\Sim$ fixes a
-set $S^*=\{e_1, \ldots, e_n\}$. In then computes:
-(1) $s_1, \ldots, s_t \getsr \Rep_1(S^*)$;
-(2) $K \getsr \calK$;
-(3) $\pubaux \getsr \Rep_2(|S|, F_K(s_1), \ldots, F_K(s_t))$, and
-finally returns $\pubaux$.
+We define a simulator $\Sim$ as follows. On input $n$, $\Sim$ fixes
+a set $S^*=\{e_1, \ldots, e_n\}$. In then computes: (1)~$s_1,
+\ldots, s_t \getsr \Rep_1(S^*)$; (2)~$K \getsr \calK$; (3)~$\pubaux
+\getsr \Rep_2(|S|, F_K(s_1), \ldots, F_K(s_t))$, and finally returns
+$\pubaux$.
 
@@
 \end{proof}
+\fixme{ ----The following is left only for cut-and-paste value---- }
+\begin{theorem}\label{thm:ds-ss}
+Fix $k,m,n>0$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
+For any set~$S \in 2^\elts$, let $\leak(S)=|S|$.
+There exists a simulator~$\Sim$ such that, for any adversary~$A$
+\[
+\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
+\]
+where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
+\end{theorem}
+\begin{proof}[Proof (sketch). ] \todo{Move this sketch to be a proof
+    of Jon's meta-result. Downgrade theorem to be a corollary of that
+    result, the proof simply being a description of how $\Rep$
+    decomposes into $\Rep_1$ and $\Rep_2$.}
+Adversary~$B^{f}$ simulates the steps of $\ExpPrivSSreal{\setprim_{\mathrm{ds}}}{A}$, using its oracle to simuate~$\Rep(S)$.
+When~$f=F_K$ then the simulation is perfect.
+When~$f=\rho$ then~$B$ simulates $\ExpPrivSSreal{\overline{\setprim}_{\mathrm{ds}}}{A}$ where $\overline{\Rep}$ effectively uses~$k$ independent random functions as the hash functions.
+But the $\pub$ produced by $\overline{\Rep}$ has a distribution that depends only~$|S|=n$, not the specific elements of~$S$, and the other public parameters~$m,k$.
+Thus, a simulator~$\Sim$ given only $\leak(S)=|S|$ can produce a correct~$\pub$ as follows: starting with an all-zeros array~$M$ of length~$m$, uniformly sample (with replacement)~$nk$ integers in~$[m]$ and set the resulting positions of~$M$ to 1.
+\end{proof}
+\fixme{ ----The above is left only for cut-and-paste value---- }
 
@@
 \end{proof}
-
-\fixme{ ----The following is left only for cut-and-paste value---- }
-\begin{theorem}\label{thm:ds-ss}
-Fix $k,m,n>0$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
-For any set~$S \in 2^\elts$, let $\leak(S)=|S|$.
-There exists a simulator~$\Sim$ such that, for any adversary~$A$
-\[
-\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
-\]
-where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
-\end{theorem}
-\begin{proof}[Proof (sketch). ] \todo{Move this sketch to be a proof
-    of Jon's meta-result. Downgrade theorem to be a corollary of that
-    result, the proof simply being a description of how $\Rep$
-    decomposes into $\Rep_1$ and $\Rep_2$.}
-Adversary~$B^{f}$ simulates the steps of $\ExpPrivSSreal{\setprim_{\mathrm{ds}}}{A}$, using its oracle to simuate~$\Rep(S)$.
-When~$f=F_K$ then the simulation is perfect.
-When~$f=\rho$ then~$B$ simulates $\ExpPrivSSreal{\overline{\setprim}_{\mathrm{ds}}}{A}$ where $\overline{\Rep}$ effectively uses~$k$ independent random functions as the hash functions.
-But the $\pub$ produced by $\overline{\Rep}$ has a distribution that depends only~$|S|=n$, not the specific elements of~$S$, and the other public parameters~$m,k$.
-Thus, a simulator~$\Sim$ given only $\leak(S)=|S|$ can produce a correct~$\pub$ as follows: starting with an all-zeros array~$M$ of length~$m$, uniformly sample (with replacement)~$nk$ integers in~$[m]$ and set the resulting positions of~$M$ to 1.
-\end{proof}
-\fixme{ ----The above is left only for cut-and-paste value---- }
 

### 2016-09-29 syntax.tex
cheers
no message

@@
 black-box access to one or more oracles, which we write as
-superscripts, e.g., $F^{O_1,O_2,\ldots}$.  We write $\langle
-x,y,\ldots \rangle$ for the encoding of values $x,y,\ldots$ as a
-single bitstring, for some implicit and invertible encoding method.
-When $x$ is a string, we write $x[i]$ for the $i$-th element in that string.
+superscripts, e.g., $F^{O_1,O_2,\ldots}$.  All algorithms (and, in
+particular, all adversaries) are stateful by default. We write
+$\langle x,y,\ldots \rangle$ for the encoding of values $x,y,\ldots$
+as a single bitstring, for some implicit and invertible encoding
+method. When $x$ is a string, we write $x[i]$ for the $i$-th element
+in that string, and $x[i:j]$ for the substring $x[i]x[i+1]\cdots
+x[j]$.
 
@@
   sense when supported by the intuition-building example, now
-  commented out. }
+  commented out. } \jnote{I don't think we do ever use it, but maybe
+  we should? E.g., we can compare the (normal) error probability to
+  the adversarial soundness probability.}
+
 \begin{definition}[Error probability and rate] \rm
@@
 \mathrm{Err}(S,\qry,\pubaux,\privaux)=1]} \leq \tilde{\epsilon}. \]
-%\hfill\dqed
+\hfill\dqed
 \end{definition}

### 2016-09-29 syntax.tex
no message

@@
 Note that we do not require $\univ = 2^\elts$ since, e.g., a
-set-membership data structure may only be defined for sets up to
-some bounded size.
+particular set-membership data structure might only be defined for
+sets up to some bounded size.
 

### 2016-09-29 results.tex
no message
added skeleton of SS-proof for GBF

@@
 aiming to find $r \geq 1$ errors (in this case, false-positives).
-The proof appears in Appendix~\ref{sec:thm3_fp}.
+The proof appears in Appendix~\ref{sec:thm3_fp}. \jnote{We seem to
+have plenty of space, so maybe start moving things from the appendix
+to the main body?}
 
@@
 
+\heading{Privacy. }
+The SS-privacy of the garbled Bloom filter construction follows directly from~Theorem~\ref{thm:xxx}.
+\begin{theorem}\label{thm:lin-privacy} \fixme{Fill out the proof}
+Fix $k,m,n,r>0$, a set $\elts$, and let $\setprim_{\mathrm{gbf}}= (\Rep, \Qry)$ be the set-membership data structure (over~$\elts$) described in Figure~\ref{fig:gbf}.
+For any set~$S \in 2^{\elts}$, let $\leak(S)=|S|$.
+There exists a simulator~$\Sim$ and an adversary~$B$ such that, for any adversary~$A$
+\[
+\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
+\]
+%(Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
+\end{theorem}
+\begin{proof}
+It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
+On input a set of distinct elements
+$S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, s_3 = \langle 1,x_2\rangle, s_4=\langle 2,x_2 \rangle,\ldots,s_{2n-1}=\langle 1,x_n \rangle, s_{2n}=\langle 2,x_n \rangle$.
+
+On input $n,F_K(s_1),F_K(s_2),\ldots,F_K(s_{2n-1}) , F_K(s_{2n})$, algorithm $\Rep_2$ initializes an all-zero array~$M$ of~$m$-bits, and sets the positions $M[F_K(s_i)+j\cdot F_K(s_{i+1})\bmod m]$ to 1, for each $j \in [k]$.
+It returns~$M$ as $\pubaux$.
+\end{proof}
+
 \begin{verbatim}

### 2016-09-29 results.tex
working on GBF section

@@
   \univ \to \bits\}$ where $\qry_x(S)=1 \Leftrightarrow x \in S$.}
-
+\label{fig:gbf}
 \end{figure}
@@
 \end{figure}
+\heading{Correctness.}
+Dong, Chen and Wen~\cite{xxx} introduce a set-membership data
+structure called a \emph{garbled Bloom filter}.  We give the
+pseudocode for it in Figure~\ref{fig:gbf}
+
+If the filter and the hash functions are public, there is a naive
+attack that works for some interesting parameters.  Pick~$k$ positions
+$i_1,i_2,\ldots,i_k$, xor strings at these positions to get a
+candidate~$x$.  If $h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots
+\wedge h_k(x) = i_k$ then either $x \in S$ or~$x$ is a
+false-positive. (You don't have to do all~$k$ hashes, you can stop as
+soon as one fails to match the index.) Say you have a 1000-position
+filter ($m=1000$) and a 100-element set ($n=100$), and you are willing
+to tolerate a 1\% FP rate.  Then you'd set $k=4$ (a la Squid).  There
+are roughly $2^{35}$ subsets of 4 indices to consider, which is
+reasonable on a laptop these days.  (Also, since $n=100$ the expected
+number of trials is roughly $2^{28}$.) With the FP rate of 1\%, if you
+find a winner then almost certainly it is in the set.  Granted, this
+attack is naive, but notice that you \emph{cannot} mount it against a
+standard Bloom filter. Also notice that this attack might be
+significantly more efficient than brute force guessing over the
+universe of inputs (imagine that $U=\bits^{64}$), even if you know
+that the distribution deviates significantly from uniform.
 

### 2016-09-29 results.tex
GBF

@@
 {
-\adversaryv{$A$}\\
+\adversaryv{$A$}\\[1ex]
 On input $\emptystring$:\\
@@
 {
-\algorithmv{$\Rep(S)$}\\
+\algorithmv{$\Rep^H(S)$}\\
 $M \gets (\bot)^m$\\
-$K_1,K_2,\ldots, K_k \getsr \calK$\\
+%$K_1,K_2,\ldots, K_k \getsr \calK$\\
 for $x \in S$\\
@@
 \nudge for $j \in \{1,2,\ldots, k\}$\\
-\nudge \nudge $h_j \gets H_{K_j}(x)$\\
+\nudge \nudge $h_j \gets H(j,x)$\\
 \nudge \nudge if $M[h_j] \neq \bot$ then\\
@@
 \nudge \nudge  $M[i] \getsr \bits^\lambda$\\
-$\pubaux \gets M$; $\privaux \gets \langle K_1,K_2,\ldots,K_k \rangle$ \mbox{ (if secret hash version)}\\
-$\pubaux \gets \langle M,K_1,K_2,\ldots,K_k \rangle$; $\privaux \gets \emptystring$ \mbox{(if public hash version)}\\
+$\pubaux \gets \emptystring$; $\privaux \gets \langle M\rangle$ \mbox{ (if private~$M$)}\\
+$\pubaux \gets \langle M \rangle$; $\privaux \gets \emptystring$ \mbox{(if public~$M$)}\\
 
@@
 \algorithmv{$\Qry(\pubaux,\privaux,\qry_x)$}\\
-if $\privaux \neq \emptystring$ then\\
-\nudge $M \gets \pubaux$, $K_1,K_2,\ldots,K_k \gets \privaux$\\
-else\\
-\nudge $M,K_1,K_2,\ldots,K_k \gets \pubaux$\\
+if $\privaux \neq \emptystring$ then $M \gets \privaux$\\
+else $M\gets \pubaux$\\
 $x' \gets 0^\lambda$\\
 for $j \in \{1,2,\dots,k\}$\\
-\nudge $h_j \gets H_{K_j}(x)$\\
+\nudge $h_j \gets H(j,x)$\\
 \nudge $x' \gets x' \xor M[h_j]$\\
@@
 \caption{ $\Rep$ and $\Qry$ algorithms for garbled Bloom
-  filter $\setprim_{\mathrm{garbled}}$ in the ROM for a hash function $H\colon \calK \times
+  filter $\setprim_{\mathrm{garbled}}$ in the ROM.hash function $H\colon \calK \times
  \elts \to [m]$. The query set is $\calQ=\{\qry_x\colon
@@
 \centering
-\hfpagess{.45}{.5}
+\hfpagess{.425}{.425}
 {
-\adversaryv{$A^{\TestOracle}(\pubaux)$}\\
+\adversaryv{$A^{\TestOracle}(\pubaux)$}\\[1ex]
+$M,K_1,K_2,\ldots,K_k \gets \pubaux$\\
+for $1 \leq i_1 < i_2 < \cdots < i_k \leq m$\\
+\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
+\nudge if  $\bigwedge_{j=1}^k H(j,x)=i_j$ then \\
+\nudge\nudge $a\gets\TestOracle(x)$\\
+\nudge\nudge Return $\bot$\\
+}
+{
+\adversaryv{$A^{\TestOracle}(\pubaux)$}\\[1ex]
 $M \gets \pubaux$\\
@@
 }
-{
-\adversaryv{$A^{\TestOracle}(\pubaux)$}\\
-$M,K_1,K_2,\ldots,K_k \gets \pubaux$\\
-for $1 \leq i_1 < i_2 < \cdots < i_k \leq m$\\
-\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
-\nudge $x' \gets H(1,x) \xor H(2,x) \xor \cdots \xor H(k,x)$\\
-\nudge if $x=x'$ then\\
-\nudge\nudge $\TestOracle(x)$\\
-\nudge\nudge Return $\bot$\\
-}
-
-\caption{Adversary for Theorem~\ref{thm:xxx}.  \textbf{Left:} secret hash case, \textbf{Right:} public hash case.}
+\caption{Adversary for Theorem~\ref{thm:xxx}.  \textbf{Left:} public hash case, \textbf{Right:} private hash case.}
 \label{fig:adv-bi-lin-ss}
@@
 Dong, Chen and Wen~\cite{xxx} introduce a set-membership data
-structure called a \emph{garbled Bloom filter}.  We give the
-pseudocode for it in Figure~\ref{fig:gbf}
+structure called a \emph{garbled Bloom filter} (GBF).   Modulo some implementation
+details, a GBF is like a classical Bloom filter, but
+rather than storing a bit 1 at the indices determined by $H_j(x)$, the
+GBF stores xor-shares of~$x$.  Thus, if $x \in S$, then hashing~$x$
+and xoring together the strings stored at the indicated positions
+recovers~$x$. We give the pseudocode for the GBF $\Rep$ and $\Qry$
+algorithms in Figure~\ref{fig:gbf}.
+
+In~\cite{xxx} the GBF is a central piece of a private set-intersection
+scheme
+
+The authors note that the GBF is of general interest, so we consider
+its correctness and
+
+The pseudocode captures
+two version, one in which the
 

### 2016-09-29 results.tex
GBF

@@
 \centering
-\fpage{.75}
+\fpage{.8}{
+\hpagess{.55}{.45}
 {
@@
 $\pubaux \gets \langle M \rangle$; $\privaux \gets \emptystring$ \mbox{(if public~$M$)}\\
-
-\medskip
+}
+{
 \algorithmv{$\Qry(\pubaux,\privaux,\qry_x)$}\\
@@
 }
+}
 \caption{ $\Rep$ and $\Qry$ algorithms for garbled Bloom
@@
 \centering
-\hfpagess{.425}{.425}
-{
-\adversaryv{$A^{\TestOracle}(\pubaux)$}\\[1ex]
-$M,K_1,K_2,\ldots,K_k \gets \pubaux$\\
-for $1 \leq i_1 < i_2 < \cdots < i_k \leq m$\\
-\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
-\nudge if  $\bigwedge_{j=1}^k H(j,x)=i_j$ then \\
-\nudge\nudge $a\gets\TestOracle(x)$\\
-\nudge\nudge Return $\bot$\\
-}
+\fpage{.425}
 {
@@
 \nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
-\nudge if $\TestOracle(x)=1$ then Return $\bot$
+\nudge if  $x \not\in S \wedge \left(\bigwedge_{j=1}^k H(j,x)=i_j \right)$ then \\
+\nudge\nudge $a\gets\TestOracle(x)$\\
+\nudge\nudge Return $\bot$\\
 }
-\caption{Adversary for Theorem~\ref{thm:xxx}.  \textbf{Left:} public hash case, \textbf{Right:} private hash case.}
-\label{fig:adv-bi-lin-ss}
+%{
+%\adversaryv{$A^{\TestOracle}(\pubaux)$}\\[1ex]
+%$M \gets \pubaux$\\
+%for $1 \leq i_1 < i_2 < \cdots < i_k \leq m$\\
+%\nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
+%\nudge if $\TestOracle(x)=1$ then Return $\bot$
+%}
+%\caption{Adversary for Theorem~\ref{thm:xxx}.  \textbf{Left:} public hash case, \textbf{Right:} private hash case.}
+\caption{Adversary for Theorem~\ref{thm:xxx}. }
+\label{fig:adv-gbf}
 \end{figure}
@@
 \heading{Privacy. }
-The SS-privacy of the garbled Bloom filter construction follows directly from~Theorem~\ref{thm:xxx}.
-\begin{theorem}\label{thm:lin-privacy} \fixme{Fill out the proof}
-Fix $k,m,n,r>0$, a set $\elts$, and let $\setprim_{\mathrm{gbf}}= (\Rep, \Qry)$ be the set-membership data structure (over~$\elts$) described in Figure~\ref{fig:gbf}.
-For any set~$S \in 2^{\elts}$, let $\leak(S)=|S|$.
-There exists a simulator~$\Sim$ and an adversary~$B$ such that, for any adversary~$A$
-\[
-\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
-\]
-%(Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
-\end{theorem}
-\begin{proof}
-It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
-On input a set of distinct elements
-$S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, s_3 = \langle 1,x_2\rangle, s_4=\langle 2,x_2 \rangle,\ldots,s_{2n-1}=\langle 1,x_n \rangle, s_{2n}=\langle 2,x_n \rangle$.
-
-On input $n,F_K(s_1),F_K(s_2),\ldots,F_K(s_{2n-1}) , F_K(s_{2n})$, algorithm $\Rep_2$ initializes an all-zero array~$M$ of~$m$-bits, and sets the positions $M[F_K(s_i)+j\cdot F_K(s_{i+1})\bmod m]$ to 1, for each $j \in [k]$.
-It returns~$M$ as $\pubaux$.
-\end{proof}
 

### 2016-09-29 results.tex
GBF

@@
 of moving from the adaptive to the zero-query setting.
-Finally, $\dbinom{q_T+q_H}{r} \leq (q_T+q_H)^r$ (with reasonable tightness when~$r$ is small) in
+Finally, $\binom{q_T+q_H}{r} \leq (q_T+q_H)^r$ (with reasonable tightness when~$r$ is small) in
 which case the final term in the bound behaves as
@@
 In~\cite{xxx} the GBF is a central piece of a private set-intersection
-scheme
+scheme, in which the client computes a classical BF over its
+set~$S_1$, the server computes a GBF over its set~$S_2$, and then an
+oblivious transfer protocol is carried out, at the end of which the
+client obtains a GBF for $S_1 \cap S_2$ (the server learns nothing).
+The authors note that the GBF is a new set-membership data strucure
+that may be of general interest, so we explore its correctness and
+privacy with respect to use case that may or may not make the
+representation~$M$ public. The pseudocode in Figure~\ref{fig:gbf}
+covers both possibilities.
 
-The authors note that the GBF is of general interest, so we consider
-its correctness and
+We note that~\cite{xxx} provides error-rate analysis, i.e., the
+probability of finding a single false-positive in a non-adaptive
+attack.  When $\lambda$ is the bit-length of the xor-shares, they
+argue that the error-rate is at most $2^{-\lambda}$, roughly because
+the xor-shares stored in~$M$ are random strings.  (Note that
+  this is independent of~$k,m,n$; although $k>1$ is required for the
+  xor shares.)  However, this analysis implicilty assumes that the potential false-positive string~$x$ is fixed
+\emph{before}~$M$ is determined.  We will see that this carries over
+\tsnote{I think?} to the case in which~$M$ is private (i.e.,
+$\pubaux=\emptystring,\privaux=\langle M \rangle$), but when~$M$ is
+public things are different.
 
-The pseudocode captures
-two version, one in which the
+Consider the adversary described in Figure~\ref{fig:adv-gbf}.  In one
+round of the for-loop, it pics~$k$ positions $i_1,i_2,\ldots,i_k$, and
+xors the strings at these positions to get a candidate~$x$.   If $x
+\in S$, which the adversary knows in the correctness experiment, then
+it moves on to a new set of positions.  If $x \not\in S$ and 
+$h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots \wedge h_k(x) = i_k$,
+then it \emph{must be} that $x$ is a false-positive.   Indeed, note
+that the probability of this (in the ROM) is precisely the
+false-positive rate of a classical BF using the same $(k,m,n)$ as the GBF.
 
-If the filter and the hash functions are public, there is a naive
-attack that works for some interesting parameters.  Pick~$k$ positions
-$i_1,i_2,\ldots,i_k$, xor strings at these positions to get a
-candidate~$x$.  If $h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots
-\wedge h_k(x) = i_k$ then either $x \in S$ or~$x$ is a
-false-positive. (You don't have to do all~$k$ hashes, you can stop as
-soon as one fails to match the index.) Say you have a 1000-position
-filter ($m=1000$) and a 100-element set ($n=100$), and you are willing
-to tolerate a 1\% FP rate.  Then you'd set $k=4$ (a la Squid).  There
-are roughly $2^{35}$ subsets of 4 indices to consider, which is
-reasonable on a laptop these days.  (Also, since $n=100$ the expected
-number of trials is roughly $2^{28}$.) With the FP rate of 1\%, if you
-find a winner then almost certainly it is in the set.  Granted, this
-attack is naive, but notice that you \emph{cannot} mount it against a
-standard Bloom filter. Also notice that this attack might be
-significantly more efficient than brute force guessing over the
-universe of inputs (imagine that $U=\bits^{64}$), even if you know
-that the distribution deviates significantly from uniform.
+Now, this adversary will find a false positive, if there is one, but in the worst case it will consider
+$\binom{m}{k} \approx m^k$ $k$-tuples of positions.  If both~$m$
+and~$k$ are large this is infeasible.  In~\cite{xxx} they suggest to
+set~$k=\lambda$, and test with $\lambda=80$.  Making 80 hash calls per
+set-membership query would be laughable in many applications, and a
+$2^{-80}$ false-postive rate would be considered overkill.\footnote{Note
+that, as described in~\cite{xxx}, $\lambda$ must be at least the
+bitlength of the longest element $x \in S$. \tsnote{This could be
+  handled with a slight change to the set membership test, by checking
+if the $\lambda$-bit shares xor to, say, the $\lambda$-bit truncation
+of~$x$.}}
+Let us consider a practically interesting set of parameters. Say you have a 1000-position
+filter, $m=1000$, and a 100-element set, $n=100$,  and $k=4$ hash
+functions (a la Squid\cite{squid}).  This results in a false-positive rate of
+approximately 1\% in a classical BF.  There are roughly $2^{35}$
+subsets of four indices to consider, which is reasonable on a laptop
+these days.  Moreover, with $n=100$ the expected
+number of trials is roughly $2^{28}$.   
+Note that the attack is easily extended to find $r>1$ false positives.
+
+We admit that attack is not particularly sophisticated, yet it might
+be significantly more efficient than brute force guessing over the
+universe of inputs (imagine that $\elts=\bits^{128}$), even if you know
+that the distribution deviates significantly from uniform. Notice,
+too, that you \emph{cannot} mount it against a standard Bloom
+filter.
+
+\todo{Insert correctness theorem for \emph{private}~$M$ in the ROM.}
+\begin{theorem}
+Fix $k,m,n,r,\lambda>0$, a set~$\elts$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the garbled Bloom filter (set membership) data structure over~$\elts$.
+For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
+\[
+\AdvCorrect{\setprim_{\mathrm{gbf}},r}{A} \leq  [...]
+\]
+\end{theorem}
 

### 2016-09-29 results.tex
gbf

@@
 
+Switching now to the case of a \emph{private}~$M$ GBF, we have the following correctness bound.
 \todo{Insert correctness theorem for \emph{private}~$M$ in the ROM.}
 \begin{theorem}
-Fix $k,m,n,r,\lambda>0$, a set~$\elts$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the garbled Bloom filter (set membership) data structure over~$\elts$.
+Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the private~$M$ GBF.
 For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,

### 2016-09-29 results.tex
gbf

@@
 {
-\algorithmv{$\Qry(\pubaux,\privaux,\qry_x)$}\\
+\algorithmv{$\Qry^H(\pubaux,\privaux,\qry_x)$}\\
 if $\privaux \neq \emptystring$ then $M \gets \privaux$\\
@@
 \end{figure}
-\heading{Correctness.}
 Dong, Chen and Wen~\cite{xxx} introduce a set-membership data
@@
 
+\heading{Correctness.}
 We note that~\cite{xxx} provides error-rate analysis, i.e., the

### 2016-09-29 notions.tex
Moved meta-theorem to Section 3

@@
 %  it is trivial to see that privacy does not imply correctness.}
+
+\heading{Privacy of ``canonical'' data structures. }
+Here we prove a result that can be used to show that a large class of canonical
+data structures are SS-secure, with respect to leakage of the size of the set.
+\jnote{It would not be too hard to generalize this to arbitrary data structures over
+arbitrary objects, so long as the number of distinct queries to the PRF made by $\Rep$
+depends only on ${\sf leak}$.}
+We first define what we mean by ``canonical.''
+
+%\def\bits{\{0,1\}}
+
+\begin{definition}
+A data structure $(\Rep, \Qry)$ is {\sf canonical} if
+there exist algorithms $\Rep_1, \Rep_2$, and a function
+$F: \calK \times \bits^{\ell_{in}} \rightarrow \bits^{\ell_{out}}$
+such that the following hold:
+\begin{itemize}
+\item $\Rep_1$ takes as input a set $S=\{x_1,\ldots,x_n\}$ and outputs distinct values $s_1, \ldots, s_t \in \bits^{\ell_{in}}$,
+where $t$ depends only on~$n$.
+\item $\Rep_2$ takes as input $n$ and $y_1, \ldots, y_t \in \bits^{\ell_{out}}$, and outputs
+$\pubaux$.
+\item For any $S$, the distribution on $\pubaux$ output by $\Rep(S)$ is identical to the distribution
+on $\pubaux$ computing as follows:
+(1) $s_1, \ldots, s_t \getsr \Rep_1(S)$;
+(2) $K \getsr \calK$;
+(3) $\pubaux \getsr \Rep_2(n, F_{K}(s_1), \ldots,F_{K}(s_t))$.
+%\item $K_1,K_2,\ldots,K_p \getsr \calK$ for some fixed number of keys~$p$;
+%\item $\pubaux \getsr \Rep_2(n, \{F_{K_j}(s_1),
+%\ldots,F_{K_j}(s_t)\}_{j\in[p]})$.
+\end{itemize}
+We say that $(\Rep_1, \Rep_2, F)$ is the {\sf canonical representation}
+of~$\Rep$. \hfill\dqed \tsnote{Seems odd to call it this without explaining how
+  this canonical representation handles $\privaux$, too.} \jnote{It
+  doesn't matter what priv is.}
+\end{definition}
+%\jnote{Not sure how general to make the above. Need to verify that it is general enough
+%to prove security of all the constructions we care about.}
+\tsnote{Point out an example or two of the schemes this
+  covers.  Domain-separated PRF BF, for example.  I think it covers
+  classical BF, too, if $F_K(s)=s$ for all $K \in \calK$, $\Rep_1$
+  simply returns the elements of~$S$, and $\Rep_2$ actually picks hash
+  functions and does the hashing. (Although the following theorem does
+  not work in this case, of course.) It does not cover Neidermayer because there's no guarantee of distinct $s_1,\ldots,s_t$. }
+  \jnote{I say we state the general theorem in Section~3.2 and just
+  promise that applications will come in Section~4.}
+We next show that any canonical data structure in which~$F$ is a pseudorandom function is
+semantically secure with respect to leakage consisting of the size of the set.
+
+\begin{theorem}\todo{Rewrite to match old DS-PRF proof}
+Let $\setprim=(\Rep, \Qry)$ be a canonical data structure for which $\Rep$ has canonical representation
+$(\Rep_1, \Rep_2, F)$. If $F$ is a $(t, \epsilon)$-pseudorandom
+function \tsnote{overloading~$t$}, then $\setprim$ is semantically secure
+with respect to leakage function ${\sf leak}(S) = |S|$.
+\end{theorem}
+\begin{proof}
+We define a simulator $\Sim$ as follows. On input $n$, $\Sim$ fixes
+a set $S^*=\{e_1, \ldots, e_n\}$. In then computes: (1)~$s_1,
+\ldots, s_t \getsr \Rep_1(S^*)$; (2)~$K \getsr \calK$; (3)~$\pubaux
+\getsr \Rep_2(|S|, F_K(s_1), \ldots, F_K(s_t))$, and finally returns
+$\pubaux$.
+
+\def\hyb{\mbox{{\sc Hyb}}}
+
+For a given set $S$, define distribution $\mbox{{\sc Real}}_S$ as
+\[ \{ (\pubaux, \privaux) \getsr \Rep(S) : \pubaux\},\]
+and define distribution $\mbox{{\sf Ideal}}_S$ as
+\[ \{ \pubaux \getsr \Sim(|S|) : \pubaux \}.\]
+Our goal is to show that $\mbox{{\sc Real}}_S$ and $\mbox{{\sf Ideal}}_S$ are computationally
+indistinguishable for any set~$S$. \jnote{I'm not quite sure how to elegantly do a proof
+like this in the concrete setting.}\tsnote{I think you just follow the
+sketch that I typeset for the Domain-Separated PRF scheme. (I'll embed
+notes below, too.) The bound will be exactly what is there, shoudl be able to just cut-and-paste,
+basically.  All that's needed, I think, is to do resource accounting
+for $\Sim$ and the PRF-adversary~$B$.}
+To do so, first note that we can express $\mbox{{\sc Real}}_S$ as the outcome of
+the following experiment: \tsnote{I'd call this ``Game $G0$''...}
+\begin{enumerate}
+\item $s_1, \ldots, s_t \getsr \Rep_1(S)$.
+\item $K \getsr \bits^n$.
+\item $\pubaux \getsr \Rep_2(|S|, F_k(s_1), \ldots, F_k(s_t))$.
+\item Return $\pubaux$.
+\end{enumerate}
+
+Now, consider a hybrid distribution $\hyb_S$ computed as follows:
+\tsnote{...and this ``Game $G1$''...}
+\begin{enumerate}
+\item $s_1, \ldots, s_t \getsr \Rep_1(S)$.
+\item $y_1, \ldots, y_t \leftarrow \bits^{\ell_{out}}$
+\item $\pubaux \getsr \Rep_2(|S|, y_1, \ldots, y_t)$.
+\item Return $\pubaux$.
+\end{enumerate}
+It follows immediately from the fact that $F$ is a pseudorandom function (and efficiency
+of $\Rep_2$) that $\hyb_S$ is computationally indistinguishable from $\mbox{{\sc Real}}_S$.
+\tsnote{...and then it's clear that the difference between the
+  probability of $G0 \outputs 1$ and $G1 \outputs 1$ is exactly the
+  PRF advantage of~$B$, who simply uses it's oracle to simulate calls
+  to $F_K$ prior to running $\Rep_2$...}
+Next, consider the following distribution $\hyb'_S$:
+\begin{enumerate}
+\item $S^* := \{e_1, \ldots, e_n\}$, where $n = |S|$.
+\item $s_1, \ldots, s_{t^*} \getsr \Rep_1(S^*)$.
+\item $y_1, \ldots, y_{t^*} \leftarrow \bits^{\ell_{out}}$
+\item $\pubaux \getsr \Rep_2(|S|, y_1, \ldots, y_{t^*})$.
+\item Return $\pubaux$.
+\end{enumerate}
+We claim that $\hyb'_S$ is identically distributed to $\hyb_S$. The follows immediately from the
+observation that the distribution on $t$ (in $\hyb_S$) is identical to the distribution on~$t^*$
+(in $\hyb'_S$) by definition
+of what it means to be canonical.
+\tsnote{...and it is clear that the distribution of everything is the
+  same as in Game $G1$, so we are done. }
+
+To complete the proof, we simply note that $\hyb'_S$ and $\mbox{{\sf Ideal}}_S$
+are computationally indistinguishable, again relying on pseudorandomness of~$F$.
+\end{proof}
+\fixme{ ----The following is left only for cut-and-paste value---- }
+\begin{theorem}\label{thm:ds-ss}
+Fix $k,m,n>0$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
+For any set~$S \in 2^\elts$, let $\leak(S)=|S|$.
+There exists a simulator~$\Sim$ such that, for any adversary~$A$
+\[
+\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
+\]
+where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
+\end{theorem}
+\begin{proof}[Proof (sketch). ] \todo{Move this sketch to be a proof
+    of Jon's meta-result. Downgrade theorem to be a corollary of that
+    result, the proof simply being a description of how $\Rep$
+    decomposes into $\Rep_1$ and $\Rep_2$.}
+Adversary~$B^{f}$ simulates the steps of $\ExpPrivSSreal{\setprim_{\mathrm{ds}}}{A}$, using its oracle to simuate~$\Rep(S)$.
+When~$f=F_K$ then the simulation is perfect.
+When~$f=\rho$ then~$B$ simulates $\ExpPrivSSreal{\overline{\setprim}_{\mathrm{ds}}}{A}$ where $\overline{\Rep}$ effectively uses~$k$ independent random functions as the hash functions.
+But the $\pub$ produced by $\overline{\Rep}$ has a distribution that depends only~$|S|=n$, not the specific elements of~$S$, and the other public parameters~$m,k$.
+Thus, a simulator~$\Sim$ given only $\leak(S)=|S|$ can produce a correct~$\pub$ as follows: starting with an all-zeros array~$M$ of length~$m$, uniformly sample (with replacement)~$nk$ integers in~$[m]$ and set the resulting positions of~$M$ to 1.
+\end{proof}
+\fixme{ ----The above is left only for cut-and-paste value---- }

### 2016-09-29 results.tex
Moved meta-theorem to Section 3

@@
 \todo{Typeset simple proof.  Result is on chalkboard.}
-
-\subsection{Privacy of Secretly-Keyed ``Canonical'' Data Structures}
-\jnote{Maybe this should be moved to Section~3.2?}
-
-Here we prove a result that can be used to show that a large class of canonical
-data structures are SS-secure, with respect to leakage of the size of the set.
-\jnote{It would not be too hard to generalize this to arbitrary data structures over
-arbitrary objects, so long as the number of distinct queries to the PRF made by $\Rep$
-depends only on ${\sf leak}$.}
-We first define what we mean by ``canonical.''
-
-%\def\bits{\{0,1\}}
-
-\begin{definition}
-A data structure $(\Rep, \Qry)$ is {\sf canonical} if
-there exist algorithms $\Rep_1, \Rep_2$, and a function
-$F: \calK \times \bits^{\ell_{in}} \rightarrow \bits^{\ell_{out}}$
-such that the following hold:
-\begin{itemize}
-\item $\Rep_1$ takes as input a set $S=\{x_1,\ldots,x_n\}$ and outputs distinct values $s_1, \ldots, s_t \in \bits^{\ell_{in}}$,
-where $t$ depends only on~$n$.
-\item $\Rep_2$ takes as input $n$ and $y_1, \ldots, y_t \in \bits^{\ell_{out}}$, and outputs
-$\pubaux$.
-\item For any $S$, the distribution on $\pubaux$ output by $\Rep(S)$ is identical to the distribution
-on $\pubaux$ computing as follows:
-(1) $s_1, \ldots, s_t \getsr \Rep_1(S)$;
-(2) $K \getsr \calK$;
-(3) $\pubaux \getsr \Rep_2(n, F_{K}(s_1), \ldots,F_{K}(s_t))$.
-%\item $K_1,K_2,\ldots,K_p \getsr \calK$ for some fixed number of keys~$p$;
-%\item $\pubaux \getsr \Rep_2(n, \{F_{K_j}(s_1),
-%\ldots,F_{K_j}(s_t)\}_{j\in[p]})$.
-\end{itemize}
-We say that $(\Rep_1, \Rep_2, F)$ is the {\sf canonical representation}
-of~$\Rep$. \hfill\dqed \tsnote{Seems odd to call it this without explaining how
-  this canonical representation handles $\privaux$, too.} \jnote{It
-  doesn't matter what priv is.}
-\end{definition}
-%\jnote{Not sure how general to make the above. Need to verify that it is general enough
-%to prove security of all the constructions we care about.}
-\tsnote{Point out an example or two of the schemes this
-  covers.  Domain-separated PRF BF, for example.  I think it covers
-  classical BF, too, if $F_K(s)=s$ for all $K \in \calK$, $\Rep_1$
-  simply returns the elements of~$S$, and $\Rep_2$ actually picks hash
-  functions and does the hashing. (Although the following theorem does
-  not work in this case, of course.) It does not cover Neidermayer because there's no guarantee of distinct $s_1,\ldots,s_t$. }
-  \jnote{I say we state the general theorem in Section~3.2 and just
-  promise that applications will come in Section~4.}
-We next show that any canonical data structure in which~$F$ is a pseudorandom function is
-semantically secure with respect to leakage consisting of the size of the set.
-
-\begin{theorem}\todo{Rewrite to match old DS-PRF proof}
-Let $\setprim=(\Rep, \Qry)$ be a canonical data structure for which $\Rep$ has canonical representation
-$(\Rep_1, \Rep_2, F)$. If $F$ is a $(t, \epsilon)$-pseudorandom
-function \tsnote{overloading~$t$}, then $\setprim$ is semantically secure
-with respect to leakage function ${\sf leak}(S) = |S|$.
-\end{theorem}
-\begin{proof}
-We define a simulator $\Sim$ as follows. On input $n$, $\Sim$ fixes
-a set $S^*=\{e_1, \ldots, e_n\}$. In then computes: (1)~$s_1,
-\ldots, s_t \getsr \Rep_1(S^*)$; (2)~$K \getsr \calK$; (3)~$\pubaux
-\getsr \Rep_2(|S|, F_K(s_1), \ldots, F_K(s_t))$, and finally returns
-$\pubaux$.
-
-\def\hyb{\mbox{{\sc Hyb}}}
-
-For a given set $S$, define distribution $\mbox{{\sc Real}}_S$ as
-\[ \{ (\pubaux, \privaux) \getsr \Rep(S) : \pubaux\},\]
-and define distribution $\mbox{{\sf Ideal}}_S$ as
-\[ \{ \pubaux \getsr \Sim(|S|) : \pubaux \}.\]
-Our goal is to show that $\mbox{{\sc Real}}_S$ and $\mbox{{\sf Ideal}}_S$ are computationally
-indistinguishable for any set~$S$. \jnote{I'm not quite sure how to elegantly do a proof
-like this in the concrete setting.}\tsnote{I think you just follow the
-sketch that I typeset for the Domain-Separated PRF scheme. (I'll embed
-notes below, too.) The bound will be exactly what is there, shoudl be able to just cut-and-paste,
-basically.  All that's needed, I think, is to do resource accounting
-for $\Sim$ and the PRF-adversary~$B$.}
-To do so, first note that we can express $\mbox{{\sc Real}}_S$ as the outcome of
-the following experiment: \tsnote{I'd call this ``Game $G0$''...}
-\begin{enumerate}
-\item $s_1, \ldots, s_t \getsr \Rep_1(S)$.
-\item $K \getsr \bits^n$.
-\item $\pubaux \getsr \Rep_2(|S|, F_k(s_1), \ldots, F_k(s_t))$.
-\item Return $\pubaux$.
-\end{enumerate}
-
-Now, consider a hybrid distribution $\hyb_S$ computed as follows:
-\tsnote{...and this ``Game $G1$''...}
-\begin{enumerate}
-\item $s_1, \ldots, s_t \getsr \Rep_1(S)$.
-\item $y_1, \ldots, y_t \leftarrow \bits^{\ell_{out}}$
-\item $\pubaux \getsr \Rep_2(|S|, y_1, \ldots, y_t)$.
-\item Return $\pubaux$.
-\end{enumerate}
-It follows immediately from the fact that $F$ is a pseudorandom function (and efficiency
-of $\Rep_2$) that $\hyb_S$ is computationally indistinguishable from $\mbox{{\sc Real}}_S$.
-\tsnote{...and then it's clear that the difference between the
-  probability of $G0 \outputs 1$ and $G1 \outputs 1$ is exactly the
-  PRF advantage of~$B$, who simply uses it's oracle to simulate calls
-  to $F_K$ prior to running $\Rep_2$...}
-Next, consider the following distribution $\hyb'_S$:
-\begin{enumerate}
-\item $S^* := \{e_1, \ldots, e_n\}$, where $n = |S|$.
-\item $s_1, \ldots, s_{t^*} \getsr \Rep_1(S^*)$.
-\item $y_1, \ldots, y_{t^*} \leftarrow \bits^{\ell_{out}}$
-\item $\pubaux \getsr \Rep_2(|S|, y_1, \ldots, y_{t^*})$.
-\item Return $\pubaux$.
-\end{enumerate}
-We claim that $\hyb'_S$ is identically distributed to $\hyb_S$. The follows immediately from the
-observation that the distribution on $t$ (in $\hyb_S$) is identical to the distribution on~$t^*$
-(in $\hyb'_S$) by definition
-of what it means to be canonical.
-\tsnote{...and it is clear that the distriubtion of everything is the
-  same as in Game $G1$, so we are done. }
-
-To complete the proof, we simply note that $\hyb'_S$ and $\mbox{{\sf Ideal}}_S$
-are computationally indistinguishable, again relying on pseudorandomness of~$F$.
-\end{proof}
-\fixme{ ----The following is left only for cut-and-paste value---- }
-\begin{theorem}\label{thm:ds-ss}
-Fix $k,m,n>0$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
-For any set~$S \in 2^\elts$, let $\leak(S)=|S|$.
-There exists a simulator~$\Sim$ such that, for any adversary~$A$
-\[
-\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
-\]
-where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
-\end{theorem}
-\begin{proof}[Proof (sketch). ] \todo{Move this sketch to be a proof
-    of Jon's meta-result. Downgrade theorem to be a corollary of that
-    result, the proof simply being a description of how $\Rep$
-    decomposes into $\Rep_1$ and $\Rep_2$.}
-Adversary~$B^{f}$ simulates the steps of $\ExpPrivSSreal{\setprim_{\mathrm{ds}}}{A}$, using its oracle to simuate~$\Rep(S)$.
-When~$f=F_K$ then the simulation is perfect.
-When~$f=\rho$ then~$B$ simulates $\ExpPrivSSreal{\overline{\setprim}_{\mathrm{ds}}}{A}$ where $\overline{\Rep}$ effectively uses~$k$ independent random functions as the hash functions.
-But the $\pub$ produced by $\overline{\Rep}$ has a distribution that depends only~$|S|=n$, not the specific elements of~$S$, and the other public parameters~$m,k$.
-Thus, a simulator~$\Sim$ given only $\leak(S)=|S|$ can produce a correct~$\pub$ as follows: starting with an all-zeros array~$M$ of length~$m$, uniformly sample (with replacement)~$nk$ integers in~$[m]$ and set the resulting positions of~$M$ to 1.
-\end{proof}
-\fixme{ ----The above is left only for cut-and-paste value---- }
-
-%Here is a proof sketch:
-%The simulator, given n=|S|, runs the honest scheme on inputs x_1, ...,
-%x_n and outputs the public portion of the result.
-%
-%To see that this is indistinguishable from the real public portion on
-%the actual set S, consider the following hybrids:
-%H0: The real pub produced from the real set S={s_1, ..., s_n}
-%H1: Run the representation algorithm on S, but using random functions
-%in place of PRFs, and output pub.
-%H2: Run the representation algorithm on {x_1, ..., x_n}, still using
-%random functions in place of PRFs, and output pub. The claim is that
-%this is identically distributed to H1. The main observation is that
-%since we are using random functions, the inputs to the random
-%functions don't matter, subject to the technical condition that the
-%number of distinct inputs to the random functions does not change.
-%(Here is where we rely on the fact that |S|=n is known, as well as an
-%appropriate definition of "natural.")
-%H3: Run the representation algorithm on {x_1, ..., x_n}, using the
-%real Rep (with PRFs).
 

### 2016-09-29 syntax.tex
no message
fixed formatting of definition 2
cheers

@@
 
-\tsnote{Do we ever use this next definition?  I guess it is a mapping of
-  classical notions to our syntax, but I don't know if we use it.
-  Anyway,  it looks a bit weird sitting here on its own.  It made more
-  sense when supported by the intuition-building example, now
-  commented out. } \jnote{I don't think we do ever use it, but maybe
-  we should? E.g., we can compare the (normal) error probability to
-  the adversarial soundness probability.}
+\todo{Words :)  Can compare the (normal) error probability to
+  the adversarial soundness probability.  Perhaps pull back some of
+  the previous example for building intuition about the difference
+  between the two.}
 
@@
 $\mathrm{Err}(S,\qry,\pubaux,\privaux)$ be  true iff
-$\Qry(\pubaux,\privaux, \qry) \neq \qry(S)$.  Then we say that $\setprim$
-has \emph{error probability}~$\epsilon$ if
-\[\max_{S,\qry}\Pr[(\pubaux,\privaux) \getsr \Rep(S) :
-\mathrm{Err}(S,\qry,\pubaux,\privaux)=1 ] \leq \epsilon.\]
+$\Qry(\pubaux,\privaux, \qry) \neq \qry(S)$.  Then we define for
+$\setprim$ the quantities
+\begin{align*}
+&\max_{S,\qry}\Prob{(\pubaux,\privaux) \getsr \Rep(S) :
+\mathrm{Err}(S,\qry,\pubaux,\privaux)=1 } &\\
+&\max_{S}\Prob{(\pubaux,\privaux) \getsr \Rep(S);\, \qry \getsr \calQ :
+\mathrm{Err}(S,\qry,\pubaux,\privaux)=1} &
+\end{align*}
+which are the \emph{error probability} and \emph{error rate}, respectively.
 %
-We say it has \emph{error rate} $\tilde{\epsilon}$ if
-\[{\textstyle \max_{S}\Pr[(\pubaux,\privaux) \getsr \Rep(S);\, \qry \getsr \calQ :
-\mathrm{Err}(S,\qry,\pubaux,\privaux)=1]} \leq \tilde{\epsilon}. \]
+%We say it has \emph{error rate} $\tilde{\epsilon}$ if
+%\[{\textstyle \max_{S}\Pr[(\pubaux,\privaux) \getsr \Rep(S);\, \qry \getsr \calQ :
+%\mathrm{Err}(S,\qry,\pubaux,\privaux)=1]} \leq \tilde{\epsilon}. \]
 \hfill\dqed

### 2016-09-29 results.tex
GBF
cheers

@@
 
-\todo{OW privacy proof?  Distributional SS privacy proof?}
+\todo{OW privacy proof? [JON]}
 
@@
 
-\begin{figure}
+\begin{figure}[t]
 \centering
@@
 %\caption{Adversary for Theorem~\ref{thm:xxx}.  \textbf{Left:} public hash case, \textbf{Right:} private hash case.}
-\caption{Adversary for Theorem~\ref{thm:xxx}. }
+\caption{Attack for garbled Bloom filters with public~$M$. }
 \label{fig:adv-gbf}
@@
 approximately 1\% in a classical BF.  There are roughly $2^{35}$
-subsets of four indices to consider, which is reasonable on a laptop
-these days.  Moreover, with $n=100$ the expected
+subsets of four indices to consider, which is reasonable on a
+commodity laptop.  Moreover, with $n=100$ the expected
 number of trials is roughly $2^{28}$.
@@
 
+\todo{Public M, ROM (no, empty priv)}\tsnote{one-wayness suffers the same
+  attack as correctness, I think?}
+
+\todo{Public M, PRF hash (follows from meta-theorem)}
+
+\todo{Private M (trivial!)}
+
 \begin{verbatim}
@@
 \item Prove that the basic BF, in the ROM, is private.  \tsnote{Not SS, should be OW}
-\item Show that the bigram DS-PRF construction is SS \tsnote{Shows Neidermayer's suggested countermeasure works}
+\item Show that the bigram DS-PRF construction is/isn't SS [DONE]
 \item Show that the basic BF DS-PRF construction is SS [DONE]
@@
 
-\item Attack priv-security of Dong, Chen, Wen ``garbled Bloom Filter'' construction when the hash functions are public.\tsnote{I give the attack in the related work section.
+\item Attack correctness of Dong, Chen, Wen ``garbled Bloom Filter'' construction when the hash functions are public.\tsnote{I give the attack in the related work section.
 Copy it here and flesh it out.}  Prove priv-security privacy of construction when hash functions are secret.

### 2016-09-29 results.tex
cheers

@@
 
-Switching now to the case of a \emph{private}~$M$ GBF, we have the following correctness bound.
+Finally, we observe that a similar version of the correctness attack
+works outside of the ROM, say, when we hash via $H(j,x)=F_K(\langle
+j,x \rangle)$ and assume~$F_K$ is a secure PRF.  Here, $\privaux=K$.  Now,
+however, the work switches from offline hash evaluations (i.e., random
+oracle calls) to online set-membership (i.e., $\TestOracle$) queries.
+
+Switching now to the case of a \emph{private}~$M$ GBF, we have the
+following correctness bound.
+
 \todo{Insert correctness theorem for \emph{private}~$M$ in the ROM.}
@@
 \heading{Privacy. }
-
+We observe i
 \todo{Public M, ROM (no, empty priv)}\tsnote{one-wayness suffers the same

### 2016-09-30 notions.tex
cheers

@@
 \jnote{I would call it ``soundness'' rather than ``correctness.'' But if you disagree,
-just remove this comment and we'll go with correctness.}
+just remove this comment and we'll go with correctness.}\tsnote{I
+think stick with correctness, since that's the what's used in NY and
+in classical literature on BFs.  Or something entirely different, but
+I don't know what.  But using ``soundness'' would seem to overload yet
+another term, no?}
 
-\tsnote{flesh out}
+\fixme{Do we say that all notions can be extended to the ROM by giving
+all all algorithms to a RO~$H$?  Is this true for the SS-privacy
+notion?  (It seems to make sense elsewhere.)}
+
+\todo{flesh out opening text}
 
@@
 
-In this experiment we track the time complexity (relative to some
-model of computation) and query complexity (i.e., number of
+In this experiment we track the time complexity~$t$ (relative to some
+model of computation) and query complexity~$q$ (i.e., number of
 queries to $\TestOracle$) of~$A$.
@@
 $\AdvCorrect{\setprim,r}{A} = \Prob{\ExpCorrect{\setprim,r}{A}=1}$.
-\tsnote{drop} Overloading notation, we write $\AdvCorrect{\setprim,r}{t,q}$ for the maximum over
-all~$t$-time adversaries that ask at most~$q$ queries. We say a
-data structure~$\setprim$ is $(t,q,r,\epsilon)$-correct if $\AdvCorrect{\setprim,r}{t,q} \leq \epsilon$.
+%\tsnote{drop} Overloading notation, we write $\AdvCorrect{\setprim,r}{t,q}$ for the maximum over
+%all~$t$-time adversaries that ask at most~$q$ queries. We say a
+%data structure~$\setprim$ is $(t,q,r,\epsilon)$-correct if $\AdvCorrect{\setprim,r}{t,q} \leq \epsilon$.
 
-\todo{Explain that the case of $r=1$ does not necessarily imply anything for $r>1$: can have a scheme
+\todo{[JON] Explain that the case of $r=1$ does not necessarily imply anything for $r>1$: can have a scheme
 where finding the first false positive is hard but then the rest are easy; can have
@@
 running time.}
-
+\todo{Mention why giving a Test oracle to A doesn't seem to help.}
 \begin{figure}[tp]
@@
 remark in the classical BF section, but it seems worth ``pulling up''.} \jnote{Yes, agreed.}
-
+\todo{Since we mention what happens with $\privaux=\emptystring$, also
+mention what happens with $\pubaux=\emptystring$ :)}
 \heading{Relationships between the notions.}

### 2016-09-30 results.tex
cheers

@@
 %\caption{Adversary for Theorem~\ref{thm:xxx}.  \textbf{Left:} public hash case, \textbf{Right:} private hash case.}
-\caption{Attack for garbled Bloom filters with public~$M$. }
+\caption{Correctness attack for garbled Bloom filters with public~$M$. }
 \label{fig:adv-gbf}
@@
 \heading{Privacy. }
-We observe i
+We observe immediately that when~$\pubaux=\langle M \rangle$ the GBF cannot be SS-private (in the ROM) because $\privaux=\emptystring$.
+In fact, it is easy to see that the correctness attack just given works as a privacy attack, too, with small modifications.
+In particular, the attacker cannot check that the reconstructed $x \not\in S$.
+
 \todo{Public M, ROM (no, empty priv)}\tsnote{one-wayness suffers the same

### 2016-09-30 notions.tex
cheers

@@
 Our semantic-security definition is based on the simulation paradigm (see Figure~\ref{fig:privacy-ss}).
-\jnote{Here it would not be hard to write the definition for general data structures, not
-specifically set-multiplicity data structures.}
+%\jnote{Here it would not be hard to write the definition for general data structures, not
+%specifically set-multiplicity data structures.}
 In this definition we compare the probabilities with which an attacker $A$ outputs~1
@@
 
-%\begin{figure}[hbtp]
-%\centering
-%\fpage{.6}{
-%\hpagess{.5}{.45}
-%{
-%\experimentv{$\ExpPrivSSreal{\setprim,\distr{}{}}{A}$}\\
-%$S \getsr \distr{}{}$ \\
-%$(\pubaux,\privaux) \getsr \Rep(S)$\\
-%return $A(S,\pubaux)$\\
-%}
-%%
-%{
-%\experimentv{$\ExpPrivSSsim{\setprim, {\sf leak}, \distr{}{}}{A, \Sim}$}\\
-%$S \getsr \distr{}{}$\\
-%$\pubaux \getsr \Sim({\sf leak}(S))$ \\
-%return $A(S,\pubaux)$\\
-%}
-%}
-%\caption{Experiments for the ``distibutional semantic-security'' privacy
-%  definition.}
-%\label{fig:privacy-dss}
-%\end{figure}
 \todo{A simple theorem that says if $\privaux=\emptystring$ then
@@
 mention what happens with $\pubaux=\emptystring$ :)}
+
 \heading{Relationships between the notions.}
@@
 
-\jnote{Make theorem statements consistent -- get rid of $(t, \epsilon)$-style.}
+\fixme{Make theorem statements consistent -- get rid of $(t, \epsilon)$-style.}
 
@@
 arbitrary objects, so long as the number of distinct queries to the PRF made by $\Rep$
-depends only on ${\sf leak}$.}
+depends only on ${\sf leak}$.}\fixme{Action? Or remove comment?}
 We first define what we mean by ``canonical.''
@@
 We say that $(\Rep_1, \Rep_2, F)$ is the {\sf canonical representation}
-of~$\Rep$. \hfill\dqed \tsnote{Seems odd to call it this without explaining how
-  this canonical representation handles $\privaux$, too.} \jnote{It
-  doesn't matter what priv is.}
+of~$\Rep$. \hfill\dqed 
 \end{definition}
-%\jnote{Not sure how general to make the above. Need to verify that it is general enough
-%to prove security of all the constructions we care about.}
 \tsnote{Point out an example or two of the schemes this
@@
   \jnote{I say we state the general theorem in Section~3.2 and just
-  promise that applications will come in Section~4.}
+  promise that applications will come in Section~4.}\tsnote{Yes.}
 We next show that any canonical data structure in which~$F$ is a pseudorandom function is

### 2016-09-30 notions.tex
no message

--- 2016-09-29 notions.tex
@@
 Following NY, we are interested in defining an adaptive (i.e.,
-adversarial) notion of correctness.
+adversarial) notion of correctness. \jnote{I would call it ``soundness'' rather than ``correctness.'' But if you disagree,
+just remove this comment and we'll go with correctness.}
 In addition to correctness, we establish notions of privacy for
-set-multiplicity data structures.
-\jnote{I would call it ``soundness'' rather than ``correctness.'' But if you disagree,
-just remove this comment and we'll go with correctness.}
+set-membership data structures.
 
@@
 
-First, the adversary $A$ outputs a set $S$ from among those supported by
-the data structure. Then,
-$\Rep(S)$ is run to generate $(\pubaux,\privaux)$.
+\jnote{Entirely general, only specializing to set-membership data structures when needed.}
+
+We first define a notion of correctness for a data structure~$\Pi$. Our definition
+considers an adversary $A$ who may have full information about the data~$S$ being stored (and, indeed,
+may even choose~$S$) but does not know or control the randomness used by the representation
+algorithm~$\Rep$. Nevertheless, $A$ may learn some partial information about that randomness from
+two sources: first, $A$ is given the public portion of the representation output
+by~$\Rep$; second, we allow $A$ to adaptively query the $\Qry$ algorithm on inputs
+of its choice.
+
+In contrast to the style of definition considered by Naor and Yogev (and in addition
+to other differences between our definitions as discussed in the Introduction), we consider
+a more fine-grained definition parameterized by a value~$r$. The goal of the attacker
+is to find $r$ (distinct) points on which the generated representation errs.
+Implications of this choice are discussed further below.
+
+Formally, our definition is specified by an experiment called $\ExpCorrect{\setprim,r}{A}$
+given in Figure~\ref{fig:correctness}.
+Following an initialization step,
+the experiment begins by having the attacker $A$ outputs data $S \in \univ$.
+Then, $\Rep(S)$ is run to generate a representation $(\pubaux,\privaux)$ for that data.
 %\jnote{I thought we were going to let
@@
 %(Unless stated otherwise, we assume security holds for all distributions and thus for all sets $S$.)
-Adversary~$A$ is given~$\pubaux$~as input; it is also
+The adversary~$A$ is given~$\pubaux$, and is also
 provided with access to an oracle~$\TestOracle$ that, on input a query~$\qry \in \calQ$,
-returns $\Qry(\pubaux,\privaux,q)$ and increments
-a counter if this result is in error.  The adversary wins if it
+returns $\Qry(\pubaux,\privaux,\qry)$ to $A$ and also increments
+a counter if this result is incorrect (and if $\qry$ is new).  The adversary succeeds if it
 manages to cause at least~$r>0$ such errors among its queries.
-The notion can be lifted to the random-oracle model by providing
-$\Rep,\Qry$ and the adversary~$A$ with oracle access to the
-random-oracle(s).
+The definition can be lifted to the random-oracle model by providing
+all algorithms (namely, $\Rep,\Qry$, and the adversary~$A$) with access to the
+random oracle.
 
@@
 
-\begin{figure}[tp]
+\begin{figure}[bt]
 \centering
@@
 \experimentv{$\ExpCorrect{\setprim,r}{A}$}\\
+$\mathcal{C} \gets \emptyset$; $\mathrm{err}\gets 0$\\
 $S \getsr A$\\
-$\mathcal{C} \gets \emptyset$; $\mathrm{err}\gets 0$\\
 $(\pubaux,\privaux) \getsr \Rep(S)$\\
@@
 
-In this experiment we track the time complexity (relative to some
+In the experiment we track the time complexity (relative to some
 model of computation) and query complexity (i.e., number of
 queries to $\TestOracle$) of~$A$.
-We define the advantage of adversary~$A$ in the correctness experiment as
+We define the advantage of adversary~$A$ in this experiment as
 $\AdvCorrect{\setprim,r}{A} = \Prob{\ExpCorrect{\setprim,r}{A}=1}$.
-\tsnote{drop} Overloading notation, we write $\AdvCorrect{\setprim,r}{t,q}$ for the maximum over
-all~$t$-time adversaries that ask at most~$q$ queries. We say a
-data structure~$\setprim$ is $(t,q,r,\epsilon)$-correct if $\AdvCorrect{\setprim,r}{t,q} \leq \epsilon$.
+We write $\AdvCorrect{\setprim,r}{t,q}$ for the maximum of this value, taken over
+all~$t$-time adversaries that ask at most~$q$ queries.
+%We say a
+%data structure~$\setprim$ is $(t,q,r,\epsilon)$-correct if $\AdvCorrect{\setprim,r}{t,q} \leq \epsilon$.
 
-\todo{Explain that the case of $r=1$ does not necessarily imply anything for $r>1$: can have a scheme
-where finding the first false positive is hard but then the rest are easy; can have
-a scheme where finding one false positive is easy but finding more is hard (e.g.,
-because there do not exist
-any more). Note that the [NY15] definition does not capture this at all.}
+\heading{The effect of $r$. }
+We observe that there is no definitive relation between
+values of $\AdvCorrect{\setprim,r}{t,q}$ for different values of~$r$ (beyond
+the trivial observation that the advantage can only possibly decrease as $r$ increases.)
+In particular, for any $r$ it is not hard to construct a data structure
+for which
+\[0 < \AdvCorrect{\setprim,1}{t,q} = \AdvCorrect{\setprim,r}{t,q}.\]
+(Consider a data structure in which finding the first query $\qry$ that causes an error
+is ``hard,'' but for which---having found $\qry$---it is easy to find
+many correlated queries that also cause errors.)
+At the other extreme, for any $r$ there also exists a data structure
+with $\AdvCorrect{\setprim,r}{t,r}=1$ but  $\AdvCorrect{\setprim,r+1}{t,\infty}=0$;
+any data structure that always ensures that there are exactly $r$ (easy to find)
+queries that cause an error will~do. \jnote{Not sure if it is worthwhile being more formal.}
+We remark that the Naor-Yogev definition does not capture such distinctions
+at all.
+
+In Appendix~\ref{sec:compare-defs} we provide further comparison between our
+definition and a variant of the Naor-Yogev definition adapted to our syntax.
+
+\def\bool{\{0,1\}}
+
+%\begin{theorem}
+%For any $r$, there is a data structure $\setprim$ for which
+%\[0 < \AdvCorrect{\setprim,1}{t,q} = \AdvCorrect{\setprim,r}{t,q}.\]
+%\end{theorem}
+%\begin{proof}
+%Let $\Pi'=(\Rep', \Qry')$ be a data structure supporting boolean
+%queries $\{\qry : \univ \rightarrow \bool\}$
+%over universe~$\univ$, and for which $\AdvCorrect{\setprim',1}{t,q} > 0$.
+%\end{proof}
 
@@
 
-One can also consider the orthogonal notion of \emph{privacy} for a data structure.
-We specialize to the case of set-membership data structures, and
-focus on sets rather than multisets. Before continuing, it will be useful to define a notion that captures the difficulty
-of guessing an element in a set chosen from some distribution.
-Let ${\cal D}$ be a distribution over subsets of some universe ${\cal X}$. The \emph{point-wise
-min-entropy} of ${\cal D}$ is defined as
-$H_\infty({\cal D}) \bydef -\log \max_{x \in {\cal X}} \Pr[S \getsr {\cal D} : x \in S]$.
+We also initiate a consideration of the orthogonal notion of \emph{privacy} for a data structure.
+We introduce two notions of privacy: a simulation-based, ``semantic-security''-style
+definition that is, in some sense, the strongest notion of privacy one could hope for.
+We also consider the weaker definition of ``one-wayness,'' specialized to the case
+of set-membership data structures, which requires that the public portion
+of the representation of some set should not allow an attacker to deduce any element of that set
+(better than what the attacker could have done without the public representation).
+This may suffice for many practical applications.
 
-\tsnote{I think we should switch the order of presentation, since we
-  use the SS notion much more. }
-We formalize two types of privacy notions. The first captures
-a ``one-wayness'' property that (informally) requires that
-the public representation of a set~$S$ does not make it any easier for an attacker
-to learn elements of~$S$.  The second definition
-captures a flavor of semantic security, essentially requiring that $\pub$ does
-not leak any information about the set~$S$ it represents beyond
-what is captured by some explicit leakage function.
+\subsubsection{A Simulation-Based Definition }
 
+\jnote{I like ``simulation-based security'' rather than ``semantic security.''}
+
+Our simulation-based definition is given in
+Figure~\ref{fig:privacy-ss}.
+In this definition we compare the probabilities with which an attacker $A$ outputs~1
+in two experiments: one ``real'' and one ``simulated.''
+In the real experiment (ss-rep-1), $A$ outputs data $S$  and is given the
+public information $\pubaux$ that results from running $\Rep(S)$.
+%\footnote{We do not give $A$ an oracle for issuing queries;
+%since $A$ knows the set~$S$, such an oracle would be superfluous.
+%\jnote{Interestingly,
+%if we provided a query oracle in the real world and an oracle that returns the correct
+%answer in the simulated world, then the definition seems to imply
+%correctness also.}}
+In the simulated experiment (ss-rep-0), $A$ outputs $S$ and is given $\pubaux$ output
+by a simulator $\Sim$ that is only given ${\sf leak}(S)$ for a (possibly randomized)
+function~${\sf leak}$. (This leakage function is meant to capture what is leaked
+by the public representation in the real world.)
+For a given function ${\sf leak}$ and adversary $A$,
+define
+\begin{eqnarray*}
+\lefteqn{\AdvPrivSS{\setprim,{\sf leak}}{A}} \\
+& \bydef & \min_{\Sim} \left\{
+\left| \Prob{\ExpPrivSSreal{\setprim}{A}=1} -
+\Prob{\ExpPrivSSsim{\setprim,{\sf leak}}{A, \Sim}=1} \right|\right\}.\end{eqnarray*}
+Informally, a scheme $\setprim$ is secure with respect to some leakage function ${\sf leak}$
+if for all efficient $A$ there is a simulator $\Sim$ such that
+$\AdvPrivSS{\setprim,{\sf leak}}{A}$ is small.
+Intuitively, this means that the public portion
+$\pubaux$ of the representation of a set~$S$ leaks~${\sf leak}(S)$ and nothing more.
+
+\begin{figure}[tb]
+\centering
+\fpage{.6}{
+\hpagess{.5}{.45}
+{
+\experimentv{$\ExpPrivSSreal{\setprim}{A}$}\\
+$S \getsr A$ \\
+$(\pubaux,\privaux) \getsr \Rep(S)$\\
+return $A(\pubaux)$\\
+}
+%
+{
+\experimentv{$\ExpPrivSSsim{\setprim, {\sf leak}}{A, \Sim}$}\\
+$S \getsr A$\\
+$\pubaux \getsr \Sim({\sf leak}(S))$ \\
+return $A(\pubaux)$\\
+}
+}
+\caption{Experiments for the ``semantic-security'' privacy
+  definition.}
+\label{fig:privacy-ss}
+\end{figure}
+
+\heading{Remarks on the definition. }
+For completeness, we include here a few observations about the definition.
+First, our definition does not place any limits on the simulator $\Sim$, and indeed
+the simulator may be unbounded. This is only potentially a concern in settings
+where $\leak(S)$ allows reconstruction of (information about) $S$ in an information-theoretic
+sense, but not in a computationally efficient fashion. Since this setting does not arise
+in this paper, allowing unbounded-time simulators is suitable for our purposes. Nevertheless,
+in some applications (and in an asymptotic-security treatment) one may also want to limit consideration
+to simulators running in some bounded time.
+
+Second, we observe that our definition could be extended by also giving $A$ access to a $\Qry$
+oracle in the real world (as in the correctness experiment), while possibly modifying the
+ideal world as well. But note that
+$A$ knows $S$ and so can compute answers $\qry(S)$ on its own (i.e., without a $\Qry$ oracle);
+thus, the only way the $\Qry$ oracle can possibly help $A$ is if $A$ finds queries
+that lead to an error.
+We have chosen not to provide $A$ with
+access to a $\Qry$ oracle so as to cleanly separate considerations
+of correctness and privacy.
+
+Finally, it is worth noting that the ``minimal'' leakage we consider in this work
+is leakage of the size of the data. (I.e., when $S$ is a set then we would
+consider ${\sf leak}(S)=|S|$ as minimal leakage.) This is by analogy with encryption.
+which generally leaks the length of the message being encrypted.
+
+\subsubsection{``One-wayness''}
+
+Here we specialize to the case of set-membership data structures.
 Our one-wayness notion is defined in Figure~\ref{fig:privacy-ow}.
@@
 $\pubaux$. The attacker succeeds if it is able to output an element of~$S$.
-We define the advantage of adversary~$A$ in this experiment\footnote{We
-remark that one could consider augmenting experiment $\ExpPrivOW{\setprim,{\cal D}}{A}$ by additionally
-giving $A$ access to an oracle for testing membership in~$S$. However, it is not hard
-to see that allowing $q$ such queries can increase $A$'s advantage by at most a factor of~$q$.} as
-$\AdvPrivOW{\setprim,\mathcal{D}}{A} = \Prob{\ExpPrivOW{\setprim,{\cal D}}{A}=1}$ and,
-overloading notation, we write $\AdvPrivOW{\setprim,{\cal D}}{t}$ for the maximum of this value over
-all~$t$-time adversaries.
-We remark that an attacker can trivially achieve advantage
-$2^{-H_\infty({\cal D})}$ by outputting the element most likely to be in~$S$.
+We define the advantage of adversary~$A$ in this experiment
+%\footnote{We
+%remark that one could consider augmenting experiment $\ExpPrivOW{\setprim,{\cal D}}{A}$ by additionally
+%giving $A$ access to an oracle for testing membership in~$S$. However, it is not hard
+%to see that allowing $q$ such queries can increase $A$'s advantage by at most a factor of~$q$.}
+as $\AdvPrivOW{\setprim,\mathcal{D}}{A} = \Prob{\ExpPrivOW{\setprim,{\cal D}}{A}=1}$.
+% and,
+%overloading notation, we write $\AdvPrivOW{\setprim,{\cal D}}{t}$ for the maximum of this value over
+%all~$t$-time adversaries.
 
-\begin{figure}[tp]
+\begin{figure}[tbh]
 \centering
@@
 
-Our semantic-security definition is based on the simulation paradigm (see Figure~\ref{fig:privacy-ss}).
-\jnote{Here it would not be hard to write the definition for general data structures, not
-specifically set-multiplicity data structures.}
-In this definition we compare the probabilities with which an attacker $A$ outputs~1
-in two experiments: one ``real'' and one ``simulated.''
-In the real experiment (ss-rep-1), $A$ outputs a set $S$  and is given the
-public information $\pubaux$ that results from running $\Rep(S)$.
-%\footnote{We do not give $A$ an oracle for issuing queries;
-%since $A$ knows the set~$S$, such an oracle would be superfluous.
-%\jnote{Interestingly,
-%if we provided a query oracle in the real world and an oracle that returns the correct
-%answer in the simulated world, then the definition seems to imply
-%correctness also.}}
-In the simulated experiment (ss-rep-0), $A$ outputs $S$ and is given $\pubaux$ output
-by a simulator $\Sim$ that is only given ${\sf leak}(S)$ for some (possibly randomized)
-function~${\sf leak}$.
-For a given function ${\sf leak}$, adversary $A$, and simulator~$\Sim$,
-we define the advantage
-$\AdvPrivSS{\setprim,{\sf leak}}{A,\Sim} \bydef
-\left| \Prob{\ExpPrivSSreal{\setprim}{A}=1} -
-\Prob{\ExpPrivSSsim{\setprim,{\sf leak}}{A, \Sim}=1} \right|$.
-Informally, a scheme $\setprim$ is secure with respect to some leakage function ${\sf leak}$
-if for all efficient $A$ there is a simulator $\Sim$ such that
-$\AdvPrivSS{\setprim,{\sf leak}}{A,\Sim}$ is small.
-Intuitively, this means that the public portion
-$\pubaux$ of the representation of a set~$S$ leaks~${\sf leak}(S)$ and nothing more.
-\jnote{The definition
-as stated does not really work well in the presence of (programmable) random oracles.}
-\jnote{In the current definition there is (intentionally) no bound on the simulator's
-running time.}
-
-\begin{figure}[tp]
-\centering
-\fpage{.6}{
-\hpagess{.5}{.45}
-{
-\experimentv{$\ExpPrivSSreal{\setprim}{A}$}\\
-$S \getsr A$ \\
-$(\pubaux,\privaux) \getsr \Rep(S)$\\
-return $A(\pubaux)$\\
-}
-%
-{
-\experimentv{$\ExpPrivSSsim{\setprim, {\sf leak}}{A, \Sim}$}\\
-$S \getsr A$\\
-$\pubaux \getsr \Sim({\sf leak}(S))$ \\
-return $A(\pubaux)$\\
-}
-}
-\caption{Experiments for the ``semantic-security'' privacy
-  definition.}
-\label{fig:privacy-ss}
-\end{figure}
+Before continuing, it will be useful to define a notion that captures the difficulty
+of guessing an element in a set chosen from some distribution.
+Let ${\cal D}$ be a distribution over subsets of some universe ${\cal X}$. The \emph{point-wise
+min-entropy} of ${\cal D}$ is defined as
+$H_\infty({\cal D}) \bydef -\log \max_{x \in {\cal X}} \Pr[S \getsr {\cal D} : x \in S]$.
+Note that an attacker can trivially achieve advantage
+$\AdvPrivOW{\setprim,\mathcal{D}}{A}=2^{-H_\infty({\cal D})}$ by outputting the element most likely to be in~$S$,
+so an attack is only interesting if it performs better than this.
 
@@
 remark in the classical BF section, but it seems worth ``pulling up''.} \jnote{Yes, agreed.}
+\todo{Since we mention what happens with $\privaux=\emptystring$, also
+mention what happens with $\pubaux=\emptystring$ :)}
 
@@
 \[\tilde H_\infty({\cal D} \mid {\sf leak}) \bydef -\log \sum_{r \in R} \Pr_{S \getsr {\cal D}}[{\sf leak}(S)=r] \cdot
-\max_{x \in {\cal X}} \Pr_{S \getsr {\cal D}}[x \in S \mid {\sf leak}(S)=r].\]
+\max_{x \in {\cal X}} \Pr_{S \getsr {\cal D}}[x \in S \mid {\sf leak}(S)=r];\]
+this merely extends the notion of pointwise min-entropy to condition on some
+observed information ${\sf leak}(S)$ about the set in question.
 
-\jnote{Make theorem statements consistent -- get rid of $(t, \epsilon)$-style.}
-
-\begin{theorem}\todo{rewrite}
-Let $\setprim$ be a set-representation data structure that is $(t, \epsilon)$-semantically secure
-with respect to leakage ${\sf leak}:2^{\cal X} \rightarrow R$.
-Then $\AdvPrivOW{\setprim,\mathcal{D}}{t} \leq 2^{-\tilde H_\infty({\cal D} \mid {\sf leak})} + \epsilon$.
+\begin{theorem}
+Let $\setprim$ be a set-membership data structure. For any distribution ${\cal D}$ and
+attacker~$A$, there is an attacker $A'$ running in about the same time with %JK
+\[\AdvPrivOW{\setprim,\mathcal{D}}{A} \leq \AdvPrivSS{\setprim,{\sf leak}}{A'} + 2^{-\tilde H_\infty({\cal D} \mid {\sf leak})}.\]
+%Let $\setprim$ be a set-representation data structure that is $(t, \epsilon)$-semantically secure
+%with respect to leakage ${\sf leak}:2^{\cal X} \rightarrow R$.
+%Then $\AdvPrivOW{\setprim,\mathcal{D}}{t} \leq 2^{-\tilde H_\infty({\cal D} \mid {\sf leak})} + \epsilon$.
 \end{theorem}
 \begin{proof}
-Fix a distribution ${\cal D}$ and an attacker
-$A$ running in time $t$, and let $\delta \bydef \AdvPrivOW{\setprim,\mathcal{D}}{A}$.
-Define an attacker $A'$ who behaves as follows: first, it samples a set $S$ according to
+%Fix a  and an attacker
+%$A$ running in time $t$, and let $\delta \bydef \AdvPrivOW{\setprim,\mathcal{D}}{A}$.
+Define $A'$ as follows: first, it samples a set $S$ according to
 distribution~${\cal D}$. Then, given $\pubaux$, it runs $A(\pubaux)$ to obtain an element~$z$.
@@
 
-It is immediate that $\Pr[\ExpPrivSSreal{\setprim}{A'}=1] = \delta$. Semantic
-security of $\setprim$ implies that there exists a simulator $\Sim$ for which
-$\ExpPrivSSsim{\setprim, {\sf leak}}{A', \Sim} \geq \delta - \epsilon$. However,
+It is immediate that $\Pr[\ExpPrivSSreal{\setprim}{A'}=1] = \AdvPrivOW{\setprim,\mathcal{D}}{A}$.
+But for any simulator $\Sim$,
 the only information
 that $\Sim$
-and $A'$ jointly have about the set~$S$ that was sampled is ${\sf leak}(S)$; thus,
-we must have $\ExpPrivSSsim{\setprim, {\sf leak}}{A', \Sim} \leq 2^{-\tilde H_\infty({\cal D} \mid {\sf leak})}$.
-This implies
-$\delta \leq 2^{-\tilde H_\infty({\cal D} \mid {\sf leak})}+\epsilon$ as desired.
+and $A'$ jointly have in the ideal world
+about the set~$S$ that was sampled is ${\sf leak}(S)$; thus,
+\[\Prob{\ExpPrivSSsim{\setprim,{\sf leak}}{A, \Sim}=1} \leq
+2^{-\tilde H_\infty({\cal D} \mid {\sf leak})}.\]
+The theorem follows.
 \end{proof}
@@
 
-\heading{Privacy of ``canonical'' data structures. }
-Here we prove a result that can be used to show that a large class of canonical
-data structures are SS-secure, with respect to leakage of the size of the set.
+\subsubsection{Privacy of ``Canonical'' Data Structures }
+Here we prove a result that will be used in the next section
+to show that a large class of
+set-membership
+data structures satisfy our simulation-based notion of security
+(with respect to leakage of the size of the set). Specifically, we prove that
+all such data structures of a certain type are private. We refer to such data structures
+as ``canonical,'' a term we define next.
+
 \jnote{It would not be too hard to generalize this to arbitrary data structures over
@@
 depends only on ${\sf leak}$.}
-We first define what we mean by ``canonical.''
 
@@
 \begin{definition}
-A data structure $(\Rep, \Qry)$ is {\sf canonical} if
+A set-membership data structure $(\Rep, \Qry)$ is {\sf canonical} if
 there exist algorithms $\Rep_1, \Rep_2$, and a function
@@
 \begin{itemize}
-\item $\Rep_1$ takes as input a set $S=\{x_1,\ldots,x_n\}$ and outputs distinct values $s_1, \ldots, s_t \in \bits^{\ell_{in}}$,
-where $t$ depends only on~$n$.
-\item $\Rep_2$ takes as input $n$ and $y_1, \ldots, y_t \in \bits^{\ell_{out}}$, and outputs
+\item $\Rep_1$ takes as input a set $S$ and outputs distinct values $s_1, \ldots, s_t \in \bits^{\ell_{in}}$,
+where $t$ depends only on~$|S|$.
+\item $\Rep_2$ takes as input $|S|$ and $y_1, \ldots, y_t \in \bits^{\ell_{out}}$, and outputs
 $\pubaux$.
@@
 (2) $K \getsr \calK$;
-(3) $\pubaux \getsr \Rep_2(n, F_{K}(s_1), \ldots,F_{K}(s_t))$.
+(3) $\pubaux \getsr \Rep_2(|S|, F_{K}(s_1), \ldots,F_{K}(s_t))$.
 %\item $K_1,K_2,\ldots,K_p \getsr \calK$ for some fixed number of keys~$p$;
@@
 \end{itemize}
-We say that $(\Rep_1, \Rep_2, F)$ is the {\sf canonical representation}
-of~$\Rep$. \hfill\dqed \tsnote{Seems odd to call it this without explaining how
-  this canonical representation handles $\privaux$, too.} \jnote{It
-  doesn't matter what priv is.}
+We call $(\Rep_1, \Rep_2, F)$ the {\sf canonical representation}
+of algorithm~$\Rep$. \hfill\dqed
 \end{definition}
+
 %\jnote{Not sure how general to make the above. Need to verify that it is general enough
 %to prove security of all the constructions we care about.}
-\tsnote{Point out an example or two of the schemes this
-  covers.  Domain-separated PRF BF, for example.  I think it covers
-  classical BF, too, if $F_K(s)=s$ for all $K \in \calK$, $\Rep_1$
-  simply returns the elements of~$S$, and $\Rep_2$ actually picks hash
-  functions and does the hashing. (Although the following theorem does
-  not work in this case, of course.) It does not cover Neidermayer because there's no guarantee of distinct $s_1,\ldots,s_t$. }
-  \jnote{I say we state the general theorem in Section~3.2 and just
-  promise that applications will come in Section~4.}
+%\tsnote{Point out an example or two of the schemes this
+%  covers.  Domain-separated PRF BF, for example.  I think it covers
+%  classical BF, too, if $F_K(s)=s$ for all $K \in \calK$, $\Rep_1$
+%  simply returns the elements of~$S$, and $\Rep_2$ actually picks hash
+%  functions and does the hashing. (Although the following theorem does
+%  not work in this case, of course.) It does not cover Neidermayer because there's no guarantee of distinct $s_1,\ldots,s_t$. }
+%  \jnote{I say we state the general theorem in Section~3.2 and just
+%  promise that applications will come in Section~4.}
 We next show that any canonical data structure in which~$F$ is a pseudorandom function is
 semantically secure with respect to leakage consisting of the size of the set.
+\jnote{Need notation for the advantage in the PRF experiment.}
 
-\begin{theorem}\todo{Rewrite to match old DS-PRF proof}
-Let $\setprim=(\Rep, \Qry)$ be a canonical data structure for which $\Rep$ has canonical representation
-$(\Rep_1, \Rep_2, F)$. If $F$ is a $(t, \epsilon)$-pseudorandom
+\begin{theorem}
+Let $\setprim=(\Rep, \Qry)$ be a canonical data structure for which $\Rep$
+has canonical representation
+$(\Rep_1, \Rep_2, F)$. Then
+\[\AdvPrivSS{\setprim,{\sf leak}}{A} \leq
+
+For ${\sf leak}(S) = |S|$,
+
+If $F$ is a $(t, \epsilon)$-pseudorandom
 function \tsnote{overloading~$t$}, then $\setprim$ is semantically secure
-with respect to leakage function ${\sf leak}(S) = |S|$.
+with respect to leakage function
+
+.
 \end{theorem}

### 2016-09-30 results.tex

@@
 
-Switching now to the case of a \emph{private}~$M$ GBF, we have the
+Switching now to the case of a \emph{private}~$M$ GBF, i.e., $\pubaux=\emptystring, \privaux=\langle M \rangle$, we have the
 following correctness bound.
-
-\todo{Insert correctness theorem for \emph{private}~$M$ in the ROM.}
+\fixme{Insert correctness theorem for \emph{private}~$M$ in the ROM.}
 \begin{theorem}
-Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the private~$M$ GBF.
+Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the private~$M$ garbled Bloom filter.
 For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
@@
 In fact, it is easy to see that the correctness attack just given works as a privacy attack, too, with small modifications.
-In particular, the attacker cannot check that the reconstructed $x \not\in S$.
+In particular, the attacker cannot check that the reconstructed $x \not\in S$, nor query a~$\TestOracle$.
+Thus the efficacy of the attack depends on the false positive rate.
+\todo{Either work out a proof for this case, or punt and make the attack more formal.}
 
-\todo{Public M, ROM (no, empty priv)}\tsnote{one-wayness suffers the same
-  attack as correctness, I think?}
+If instantiated with hash functions $H_j(x) = F_K(\langle j,x \rangle)$ and $\privaux = \langle K \rangle$, the SS-privacy of the GBF follows directly from~Theorem~\ref{thm:xxx}.
+\begin{theorem}\label{thm:lin-privacy}
+Fix $k,m,n,r,\lambda>0$ and a function family~$F\colon \calK \times \bits^* \to [m]$.
+Let $\setprim_{\mathrm{gbf}}= (\Rep, \Qry)$ be the garbled Bloom filter with hash functions $H_j(x)=F_K(\langle j,x \rangle)$ and $\privaux=langle K \rangle$.
+For any set~$S$, let $\leak(S)=|S|$.
+There exists a simulator~$\Sim$ and an adversary~$B$ such that, for any adversary~$A$
+\[
+\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
+\]
+%(Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
+\end{theorem}
+\begin{proof}
+It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
+On input a set of distinct elements \fixme{ANIMESH: make this correct}
+$S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, s_3 = \langle 1,x_2\rangle, s_4=\langle 2,x_2 \rangle,\ldots,s_{2n-1}=\langle 1,x_n \rangle, s_{2n}=\langle 2,x_n \rangle$.
 
-\todo{Public M, PRF hash (follows from meta-theorem)}
-
-\todo{Private M (trivial!)}
+On input $n,F_K(s_1),F_K(s_2),\ldots,F_K(s_{2n-1}) , F_K(s_{2n})$, algorithm $\Rep_2$ initializes an all-zero array~$M$ of~$m$-bits, and sets the positions $M[F_K(s_i)+j\cdot F_K(s_{i+1})\bmod m]$ to 1, for each $j \in [k]$.
+It returns~$M$ as $\pubaux$.
+\end{proof}
 

### 2016-09-30 results.tex

@@
 \centering
-\fpage{.425}
+\hfpagess{.45}{.45}
 {
-\adversaryv{$A^{\TestOracle}(\pubaux)$}\\[1ex]
-$M \gets \pubaux$\\
-for $1 \leq i_1 < i_2 < \cdots < i_k \leq m$\\
+\adversaryv{$A^{\TestOracle,H}(\pubaux)$}\\[1ex]
+$M \gets \pubaux$; $L \gets \binom{m}{k}$
+for $\ell=1$ to $L$\\
+$i_1,i_2,\ldots,i_k \gets \mathcal{I}_L$\\
 \nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
@@
 \nudge\nudge Return $\bot$\\
+}
+{
+\adversaryv{$A^{H}(\pubaux)$}\\[1ex]
+$M \gets \pubaux$
+for $x \in X_1,X_2,\ldots,X_q$\\
+\nudge for $j=1$ to $k$ \\
+\nudge \nudge $i_j \gets H(j,x)$
+\nudge $x' \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
+\nudge if $x' = x$ then Return $x$\\
+Return~$X_q$
 }
@@
 %\caption{Adversary for Theorem~\ref{thm:xxx}.  \textbf{Left:} public hash case, \textbf{Right:} private hash case.}
-\caption{Correctness attack for garbled Bloom filters with public~$M$. }
+\caption{Correctness attack for garbled Bloom filters with public~$M$.
+The sequence $\mathcal{I}_1,\mathcal{I}_2,\ldots,\mathcal{I}_L$ is some implicit enumeration of~$k$-tuples of indices over $[m]$.
+}
 \label{fig:adv-gbf}
@@
 We admit that attack is not particularly sophisticated, yet it might
-be significantly more efficient than brute force guessing over the
-universe of inputs (imagine that $\elts=\bits^{128}$), even if you know
-that the distribution deviates significantly from uniform. Notice,
-too, that you \emph{cannot} mount it against a standard Bloom
-filter.
+be significantly more efficient than brute force guessing.  When $k,m,n$ are as in the example just given, and $\elts=\bits^{128}$, 
+this attack will be considerably faster even if the attacker knows that the distribution deviates significantly from uniform.
+Note that in the ROM, the order in which $k$-tuples are considered is largely irrelevant, especially when $2^\lambda \gg \binom{m}{k}$.
+%Notice,too, that you \emph{cannot} mount it against a standard Bloom filter.
 
@@
 We observe immediately that when~$\pubaux=\langle M \rangle$ the GBF cannot be SS-private (in the ROM) because $\privaux=\emptystring$.
-In fact, it is easy to see that the correctness attack just given works as a privacy attack, too, with small modifications.
-In particular, the attacker cannot check that the reconstructed $x \not\in S$, nor query a~$\TestOracle$.
-Thus the efficacy of the attack depends on the false positive rate.
-\todo{Either work out a proof for this case, or punt and make the attack more formal.}
+In fact, it is easy to see that the correctness attack given in Figure~\ref{fig:adv-gbf} works as a one-wayness attack, too, with small modifications: remove the check for $x \not\in S$, and the call to $\TestOracle$.
+To maximize the efficiency of the attack
+
+ Thus the efficacy of the attack depends on the false positive rate. \todo{Either work out a proof for this case, or punt and make the attack more formal.}
 
 If instantiated with hash functions $H_j(x) = F_K(\langle j,x \rangle)$ and $\privaux = \langle K \rangle$, the SS-privacy of the GBF follows directly from~Theorem~\ref{thm:xxx}.
-\begin{theorem}\label{thm:lin-privacy}
+\begin{theorem}\label{thm:gbf-prf-privacy}
 Fix $k,m,n,r,\lambda>0$ and a function family~$F\colon \calK \times \bits^* \to [m]$.
-Let $\setprim_{\mathrm{gbf}}= (\Rep, \Qry)$ be the garbled Bloom filter with hash functions $H_j(x)=F_K(\langle j,x \rangle)$ and $\privaux=langle K \rangle$.
+Let $\setprim_{\mathrm{gbf\mbox{-}prf}}= (\Rep, \Qry)$ be the garbled Bloom filter with hash functions $H_j(x)=F_K(\langle j,x \rangle)$ and $\privaux=\langle K \rangle$.
 For any set~$S$, let $\leak(S)=|S|$.
@@
 \[
-\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
+\AdvPrivSS{\setprim_{\mathrm{gbf\mbox{-}prf}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
 \]
@@
 It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
-On input a set of distinct elements \fixme{ANIMESH: make this correct}
-$S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, s_3 = \langle 1,x_2\rangle, s_4=\langle 2,x_2 \rangle,\ldots,s_{2n-1}=\langle 1,x_n \rangle, s_{2n}=\langle 2,x_n \rangle$.
-
-On input $n,F_K(s_1),F_K(s_2),\ldots,F_K(s_{2n-1}) , F_K(s_{2n})$, algorithm $\Rep_2$ initializes an all-zero array~$M$ of~$m$-bits, and sets the positions $M[F_K(s_i)+j\cdot F_K(s_{i+1})\bmod m]$ to 1, for each $j \in [k]$.
+On input a set of distinct elements $S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, \ldots, s_k\langle k,x_1\rangle, s_{k+1}=\langle 1,x_2\rangle, \ldots, s_{2k}=\langle k,x_2\rangle, \ldots ,s_{kn+1}=\langle 1,x_n\rangle, \ldots, s_{kn}=\langle k,x_n \rangle$.
+On input $n,F_K(s_1),\ldots,F_K(s_{kn})$, algorithm $\Rep_2$ carries out the pseudocode of~$\Rep$ in Figure~\ref{fig:gbf}, making use of $F_K(s_1),\ldots,F_K(s_{kn})$ in the obvious way.
 It returns~$M$ as $\pubaux$.
@@
 
+\ignore{
 \begin{verbatim}
-%------------------------------------%
+%----- LEFT HERE FOR REMINDERS, AND FOR MENTIONING OPEN PROBLEMS IN INTRO-------------------------------%
 \end{verbatim}

### 2016-09-30 results.tex
adding OW attack for GBF

@@
 \adversaryv{$A^{\TestOracle,H}(\pubaux)$}\\[1ex]
-$M \gets \pubaux$; $L \gets \binom{m}{k}$
-for $\ell=1$ to $L$\\
-$i_1,i_2,\ldots,i_k \gets \mathcal{I}_L$\\
+$M \gets \pubaux$\\
+for $\ell=1$ to $\binom{m}{k}$\\
+\nudge $i_1,i_2,\ldots,i_k \gets \mathcal{I}_\ell$\\
 \nudge $x \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
@@
 \adversaryv{$A^{H}(\pubaux)$}\\[1ex]
-$M \gets \pubaux$
+$M \gets \pubaux$\\
 for $x \in X_1,X_2,\ldots,X_q$\\
 \nudge for $j=1$ to $k$ \\
-\nudge \nudge $i_j \gets H(j,x)$
+\nudge \nudge \nudge $i_j \gets H(j,x)$\\
 \nudge $x' \gets M[i_1] \xor M[i_2] \xor \cdots \xor M[i_k]$\\
 \nudge if $x' = x$ then Return $x$\\
-Return~$X_q$
+Return~$X_{q+1}$
 }
@@
 %\caption{Adversary for Theorem~\ref{thm:xxx}.  \textbf{Left:} public hash case, \textbf{Right:} private hash case.}
-\caption{Correctness attack for garbled Bloom filters with public~$M$.
-The sequence $\mathcal{I}_1,\mathcal{I}_2,\ldots,\mathcal{I}_L$ is some implicit enumeration of~$k$-tuples of indices over $[m]$.
+\caption{{\bf Left:} Correctness attack for garbled Bloom filters with public~$M$.  The sequence $\mathcal{I}_1,\mathcal{I}_2,\ldots$ is some implicit enumeration of~$k$-tuples of indices over $[m]$.
+{\bf Right:} One-wayness attack for garbled Bloom filters with public~$M$.
+The sequence $X_1,X_2,\ldots,X_q,X_{q+1}$ are the $q+1$ most probable points in the support of~$\distr{}{}$ in decreasing order.
 }

### 2016-09-30 notions.tex

@@
 Following NY, we are interested in defining an adaptive (i.e.,
-adversarial) notion of correctness. \jnote{I would call it ``soundness'' rather than ``correctness.'' But if you disagree,
-just remove this comment and we'll go with correctness.}
+adversarial) notion of correctness.
 In addition to correctness, we establish notions of privacy for
-set-membership data structures.
+set-multiplicity data structures.
 
-\tsnote{flesh out}
+\fixme{Do we say that all notions can be extended to the ROM by giving
+all all algorithms to a RO~$H$?  Is this true for the SS-privacy
+notion?  (It seems to make sense elsewhere.)}
+
+\todo{flesh out opening text}
 
@@
 
-In the experiment we track the time complexity (relative to some
-model of computation) and query complexity (i.e., number of
+In this experiment we track the time complexity~$t$ (relative to some
+model of computation) and query complexity~$q$ (i.e., number of
 queries to $\TestOracle$) of~$A$.
@@
 %\end{proof}
+
+%\tsnote{drop} Overloading notation, we write $\AdvCorrect{\setprim,r}{t,q}$ for the maximum over
+%all~$t$-time adversaries that ask at most~$q$ queries. We say a
+%data structure~$\setprim$ is $(t,q,r,\epsilon)$-correct if $\AdvCorrect{\setprim,r}{t,q} \leq \epsilon$.
 
@@
 Let $\setprim$ be a set-membership data structure. For any distribution ${\cal D}$ and
-attacker~$A$, there is an attacker $A'$ running in about the same time with %JK
+attacker~$A$, there is an attacker $A'$ running in about the same time with
 \[\AdvPrivOW{\setprim,\mathcal{D}}{A} \leq \AdvPrivSS{\setprim,{\sf leak}}{A'} + 2^{-\tilde H_\infty({\cal D} \mid {\sf leak})}.\]
@@
 %Then $\AdvPrivOW{\setprim,\mathcal{D}}{t} \leq 2^{-\tilde H_\infty({\cal D} \mid {\sf leak})} + \epsilon$.
+\begin{theorem}\todo{rewrite}
+Let $\setprim$ be a set-representation data structure that is $(t, \epsilon)$-semantically secure
+with respect to leakage ${\sf leak}:2^{\cal X} \rightarrow R$.
+Then $\AdvPrivOW{\setprim,\mathcal{D}}{t} \leq 2^{-\tilde H_\infty({\cal D} \mid {\sf leak})} + \epsilon$.
 \end{theorem}
@@
 
-\jnote{It would not be too hard to generalize this to arbitrary data structures over
-arbitrary objects, so long as the number of distinct queries to the PRF made by $\Rep$
-depends only on ${\sf leak}$.}
+%\jnote{It would not be too hard to generalize this to arbitrary data structures over
+%arbitrary objects, so long as the number of distinct queries to the PRF made by $\Rep$
+%depends only on ${\sf leak}$.}
 
@@
 %  promise that applications will come in Section~4.}
+We say that $(\Rep_1, \Rep_2, F)$ is the {\sf canonical representation}
+of~$\Rep$. \hfill\dqed
+\end{definition}
+%\tsnote{Point out an example or two of the schemes this
+%  covers.  Domain-separated PRF BF, for example.  I think it covers
+%  classical BF, too, if $F_K(s)=s$ for all $K \in \calK$, $\Rep_1$
+%  simply returns the elements of~$S$, and $\Rep_2$ actually picks hash
+%  functions and does the hashing. (Although the following theorem does
+%  not work in this case, of course.) It does not cover Neidermayer because there's no guarantee of distinct $s_1,\ldots,s_t$. }
+%  \jnote{I say we state the general theorem in Section~3.2 and just
+%  promise that applications will come in Section~4.}\tsnote{Yes.}
 We next show that any canonical data structure in which~$F$ is a pseudorandom function is

### 2016-09-30 intro.tex
no message

@@
 structures in an adversarial setting, where both \emph{soundness}
-\jnote{I like ``soundness'' better than ``correctness,'' but I won't
-insist.} and \emph{privacy} are considered. In this work we initiate
-such a treatment for abstract data structures, and also explore the
+and \emph{privacy} are considered. In this work we initiate such a
+treatment for abstract data structures, and also explore the
 security of several specific data structures---that can all be

### 2016-09-30 notions.tex
no message

@@
 all all algorithms to a RO~$H$?  Is this true for the SS-privacy
-notion?  (It seems to make sense elsewhere.)}
+notion?  (It seems to make sense elsewhere.)} \jnote{I think there are subtleties for the SS notion.}
 
@@
 \subsection{Correctness Against Adaptive Adversaries}
-
-\jnote{Entirely general, only specializing to set-membership data structures when needed.}
 
@@
 %Then $\AdvPrivOW{\setprim,\mathcal{D}}{t} \leq 2^{-\tilde H_\infty({\cal D} \mid {\sf leak})} + \epsilon$.
-\begin{theorem}\todo{rewrite}
-Let $\setprim$ be a set-representation data structure that is $(t, \epsilon)$-semantically secure
-with respect to leakage ${\sf leak}:2^{\cal X} \rightarrow R$.
-Then $\AdvPrivOW{\setprim,\mathcal{D}}{t} \leq 2^{-\tilde H_\infty({\cal D} \mid {\sf leak})} + \epsilon$.
 \end{theorem}
@@
 about the set~$S$ that was sampled is ${\sf leak}(S)$; thus,
-\[\Prob{\ExpPrivSSsim{\setprim,{\sf leak}}{A, \Sim}=1} \leq
+\[\Prob{\ExpPrivSSsim{\setprim,{\sf leak}}{A', \Sim}=1} \leq
 2^{-\tilde H_\infty({\cal D} \mid {\sf leak})}.\]
@@
 %  promise that applications will come in Section~4.}
-We say that $(\Rep_1, \Rep_2, F)$ is the {\sf canonical representation}
-of~$\Rep$. \hfill\dqed
-\end{definition}
-%\tsnote{Point out an example or two of the schemes this
-%  covers.  Domain-separated PRF BF, for example.  I think it covers
-%  classical BF, too, if $F_K(s)=s$ for all $K \in \calK$, $\Rep_1$
-%  simply returns the elements of~$S$, and $\Rep_2$ actually picks hash
-%  functions and does the hashing. (Although the following theorem does
-%  not work in this case, of course.) It does not cover Neidermayer because there's no guarantee of distinct $s_1,\ldots,s_t$. }
-%  \jnote{I say we state the general theorem in Section~3.2 and just
-%  promise that applications will come in Section~4.}\tsnote{Yes.}
+
 We next show that any canonical data structure in which~$F$ is a pseudorandom function is
@@
 has canonical representation
-$(\Rep_1, \Rep_2, F)$. Then
-\[\AdvPrivSS{\setprim,{\sf leak}}{A} \leq
-
-For ${\sf leak}(S) = |S|$,
-
-If $F$ is a $(t, \epsilon)$-pseudorandom
-function \tsnote{overloading~$t$}, then $\setprim$ is semantically secure
-with respect to leakage function
-
-.
+$(\Rep_1, \Rep_2, F)$. Then for ${\sf leak}(S) = |S|$ and
+any attacker $A$, there is an attacker
+$A'$ running in about the same time for which
+\[\AdvPrivSS{\setprim,{\sf leak}}{A} \leq {\sf Adv}_F^{\rm PRF}(A'). \]
 \end{theorem}
@@
 We define a simulator $\Sim$ as follows. On input $n$, $\Sim$ fixes
-a set $S^*=\{e_1, \ldots, e_n\}$. In then computes: (1)~$s_1,
-\ldots, s_t \getsr \Rep_1(S^*)$; (2)~$K \getsr \calK$; (3)~$\pubaux
+a set $S^*=\{e_1, \ldots, e_n\}$. It then computes $s_1,
+\ldots, s_t \getsr \Rep_1(S^*)$, chooses a uniform key
+$K \getsr \calK$, runs $\pubaux
 \getsr \Rep_2(|S|, F_K(s_1), \ldots, F_K(s_t))$, and finally returns

### 2016-09-30 notions.tex
proof of meta-theorem done

@@
 a set $S^*=\{e_1, \ldots, e_n\}$. It then computes $s_1,
-\ldots, s_t \getsr \Rep_1(S^*)$, chooses a uniform key
-$K \getsr \calK$, runs $\pubaux
-\getsr \Rep_2(|S|, F_K(s_1), \ldots, F_K(s_t))$, and finally returns
-$\pubaux$.
+\ldots, s_t \getsr \Rep_1(S^*)$, chooses uniform values $y_1, \ldots, y_t \getsr \bool^{\ell_{out}}$,
+and returns $\pubaux
+\getsr \Rep_2(|S|, y_1, \ldots, y_t)$.
 
@@
 
-For a given set $S$, define distribution $\mbox{{\sc Real}}_S$ as
-\[ \{ (\pubaux, \privaux) \getsr \Rep(S) : \pubaux\},\]
-and define distribution $\mbox{{\sf Ideal}}_S$ as
-\[ \{ \pubaux \getsr \Sim(|S|) : \pubaux \}.\]
-Our goal is to show that $\mbox{{\sc Real}}_S$ and $\mbox{{\sf Ideal}}_S$ are computationally
-indistinguishable for any set~$S$. \jnote{I'm not quite sure how to elegantly do a proof
-like this in the concrete setting.}\tsnote{I think you just follow the
-sketch that I typeset for the Domain-Separated PRF scheme. (I'll embed
-notes below, too.) The bound will be exactly what is there, shoudl be able to just cut-and-paste,
-basically.  All that's needed, I think, is to do resource accounting
-for $\Sim$ and the PRF-adversary~$B$.}
-To do so, first note that we can express $\mbox{{\sc Real}}_S$ as the outcome of
-the following experiment: \tsnote{I'd call this ``Game $G0$''...}
+Note that we can express $\Prob{\ExpPrivSSreal{\setprim}{A}=1}$ as the probability that $A$
+outputs~1 in
+the following experiment~$G0$: \jnote{BTW, in class when I do this stuff I usually
+say ``game'' and then correct myself and say ``\ldots but if you want to get funded,
+call it an experiment.'' (Some light humor while you work.)}
 \begin{enumerate}
+\item $S \getsr A$.
 \item $s_1, \ldots, s_t \getsr \Rep_1(S)$.
@@
 \item $\pubaux \getsr \Rep_2(|S|, F_k(s_1), \ldots, F_k(s_t))$.
-\item Return $\pubaux$.
+\item Return $A(\pubaux)$.
 \end{enumerate}
 
-Now, consider a hybrid distribution $\hyb_S$ computed as follows:
-\tsnote{...and this ``Game $G1$''...}
+Now, consider an experiment $G1$ in which computation is done as follows:
 \begin{enumerate}
+\item $S \getsr A$.
 \item $s_1, \ldots, s_t \getsr \Rep_1(S)$.
@@
 \item $\pubaux \getsr \Rep_2(|S|, y_1, \ldots, y_t)$.
-\item Return $\pubaux$.
+\item Return $A(\pubaux)$.
 \end{enumerate}
-It follows immediately from the fact that $F$ is a pseudorandom function (and efficiency
-of $\Rep_2$) that $\hyb_S$ is computationally indistinguishable from $\mbox{{\sc Real}}_S$.
-\tsnote{...and then it's clear that the difference between the
-  probability of $G0 \outputs 1$ and $G1 \outputs 1$ is exactly the
-  PRF advantage of~$B$, who simply uses it's oracle to simulate calls
-  to $F_K$ prior to running $\Rep_2$...}
-Next, consider the following distribution $\hyb'_S$:
+It is immediate that the difference between the probability that $A$ outputs~1 in
+$G1$ and the probability that it outputs~1 in
+$G0$ is bounded by ${\sf Adv}_F^{\rm PRF}(A')$, where $A'$ performs the
+obvious simulation.
+
+Next, consider the following experiment $G2$:
 \begin{enumerate}
+\item $S \getsr A$.
 \item $S^* := \{e_1, \ldots, e_n\}$, where $n = |S|$.
@@
 \item $\pubaux \getsr \Rep_2(|S|, y_1, \ldots, y_{t^*})$.
-\item Return $\pubaux$.
+\item Return $A(\pubaux)$.
 \end{enumerate}
-We claim that $\hyb'_S$ is identically distributed to $\hyb_S$. The follows immediately from the
-observation that the distribution on $t$ (in $\hyb_S$) is identical to the distribution on~$t^*$
-(in $\hyb'_S$) by definition
-of what it means to be canonical.
-\tsnote{...and it is clear that the distribution of everything is the
-  same as in Game $G1$, so we are done. }
+We claim that the probability with which $A$ outputs~1 in $G2$ is \emph{identical} to the
+probability with which it outputs~1 in $G1$.
+The follows immediately from the
+observation that the distribution on $t$ (in $G1$) is identical to the distribution on~$t^*$
+(in $G2$) by definition
+of what it means to be canonical, and it is clear that the distributions of everything
+else are the same as well.
 
-To complete the proof, we simply note that $\hyb'_S$ and $\mbox{{\sf Ideal}}_S$
-are computationally indistinguishable, again relying on pseudorandomness of~$F$.
+One can observe that $G2$ is identical to the following experiment:
+\begin{enumerate}
+\item $S \getsr A$.
+\item $\pubaux \getsr \Sim(|S|)$.
+\item Return $A(\pubaux)$.
+\end{enumerate}
+Moreover, the probability with which $A$ outputs~1 in this experiment is
+precisely $\Prob{\ExpPrivSSsim{\setprim,{\sf leak}}{A, \Sim}=1}$.
+This completes the proof.
 \end{proof}
-\fixme{ ----The following is left only for cut-and-paste value---- }
-\begin{theorem}\label{thm:ds-ss}
-Fix $k,m,n>0$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
+
+%\fixme{ ----The following is left only for cut-and-paste value---- }
+%\begin{theorem}\label{thm:ds-ss}
+%Fix $k,m,n>0$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-multiplicity data structure described in Figure~\ref{fig:lin-and-ds}.
 For any set~$S \in 2^\elts$, let $\leak(S)=|S|$.
 There exists a simulator~$\Sim$ such that, for any adversary~$A$
-\[
-\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
-\]
-where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
-\end{theorem}
-\begin{proof}[Proof (sketch). ] \todo{Move this sketch to be a proof
-    of Jon's meta-result. Downgrade theorem to be a corollary of that
-    result, the proof simply being a description of how $\Rep$
-    decomposes into $\Rep_1$ and $\Rep_2$.}
-Adversary~$B^{f}$ simulates the steps of $\ExpPrivSSreal{\setprim_{\mathrm{ds}}}{A}$, using its oracle to simuate~$\Rep(S)$.
+%\[
+%\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
+%\]
+%where~$B$ is constructed from~$A$.  (Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
+%\end{theorem}
+%\begin{proof}[Proof (sketch). ] \todo{Move this sketch to be a proof
+%    of Jon's meta-result. Downgrade theorem to be a corollary of that
+%    result, the proof simply being a description of how $\Rep$
+%    decomposes into $\Rep_1$ and $\Rep_2$.}
+%Adversary~$B^{f}$ simulates the steps of $\ExpPrivSSreal{\setprim_{\mathrm{ds}}}{A}$, using its oracle to simuate~$\Rep(S)$.
 When~$f=F_K$ then the simulation is perfect.
@@
 Thus, a simulator~$\Sim$ given only $\leak(S)=|S|$ can produce a correct~$\pub$ as follows: starting with an all-zeros array~$M$ of length~$m$, uniformly sample (with replacement)~$nk$ integers in~$[m]$ and set the resulting positions of~$M$ to 1.
-\end{proof}
-\fixme{ ----The above is left only for cut-and-paste value---- }
+%\end{proof}
+%\fixme{ ----The above is left only for cut-and-paste value---- }

### 2016-09-30 notions.tex
no message

@@
 \Prob{\ExpPrivSSsim{\setprim,{\sf leak}}{A, \Sim}=1} \right|\right\}.\end{eqnarray*}
+The definition can be lifted to the random-oracle model by providing
+all algorithms with access to the
+random oracle.
 Informally, a scheme $\setprim$ is secure with respect to some leakage function ${\sf leak}$
@@
 %all~$t$-time adversaries.
+The definition can be lifted to the random-oracle model by providing
+all algorithms (namely, $\Rep,\Qry$, and the adversary~$A$) with access to the
+random oracle.
 

### 2016-09-30 results.tex
gbf

@@
 {
-\adversaryv{$A^{\TestOracle,H}(\pubaux)$}\\[1ex]
+\adversaryv{$A_{\mathrm{ss}}^{\TestOracle,H}(\pubaux)$}\\[1ex]
 $M \gets \pubaux$\\
@@
 {
-\adversaryv{$A^{H}(\pubaux)$}\\[1ex]
+\adversaryv{$A_{\mathrm{ow}}^{H}(\pubaux)$}\\[1ex]
 $M \gets \pubaux$\\
@@
 
-Consider the adversary described in Figure~\ref{fig:adv-gbf}.  In one
+Consider the adversary described in the left half of Figure~\ref{fig:adv-gbf}.  In one
 round of the for-loop, it pics~$k$ positions $i_1,i_2,\ldots,i_k$, and
@@
 We observe immediately that when~$\pubaux=\langle M \rangle$ the GBF cannot be SS-private (in the ROM) because $\privaux=\emptystring$.
-In fact, it is easy to see that the correctness attack given in Figure~\ref{fig:adv-gbf} works as a one-wayness attack, too, with small modifications: remove the check for $x \not\in S$, and the call to $\TestOracle$.
-To maximize the efficiency of the attack
+In fact, the correctness attack given above suggests a one-wayness attack in the ROM, too; see the right half of Figure~\ref{fig:adv-gbf}.
+The naive attack would simply output the most probable element in the support of the distribution $\distr{}{}$ used in the one-wayness experiment to sample~$S$.
+But when~$M$ and the hash functions are available to the attacker, it can carry out set-membership tests for itself.
+Thus the adversary on the right of Figure~\ref{fig:adv-gbf} tries the~$q$ most probable points, in order, halting with its output as soon as the set-membership test is successful.
+If none of these points are yield a successful test, then the next most probable point is output.
+The probabilty that $A_{ow}$ fails to win the one-wayness experiment is
+\begin{eqnarray*}
+\AdvPrivOW{\setprim_{\mathrm{gbf}},\distr{}{}}{A_{\mathrm{ow}}} &= 1 - \Prob{X_1 \not\in S \wedge X_2 \not\in S \wedge \cdots \wedge X_{q+1}\not\in S} \\
+& = 1 - \prod_{i=1}^{q+1} \Prob{X_i \not\in S \,|\, X_{i-1} \not\in S \wedge \cdots X_1 \not\in S}\Prob{X_1 \not\in S}\\
+\end{eqnarray*}
 

### 2016-09-30 results.tex
gbf

@@
 $M \gets \pubaux$\\
-for $x \in X_1,X_2,\ldots,X_q$\\
+for $x \in X_1,X_2,\ldots,X_{q-1}$\\
 \nudge for $j=1$ to $k$ \\
@@
 \nudge if $x' = x$ then Return $x$\\
-Return~$X_{q+1}$
+Return~$X_{q}$
 }
@@
 \caption{{\bf Left:} Correctness attack for garbled Bloom filters with public~$M$.  The sequence $\mathcal{I}_1,\mathcal{I}_2,\ldots$ is some implicit enumeration of~$k$-tuples of indices over $[m]$.
-{\bf Right:} One-wayness attack for garbled Bloom filters with public~$M$.
-The sequence $X_1,X_2,\ldots,X_q,X_{q+1}$ are the $q+1$ most probable points in the support of~$\distr{}{}$ in decreasing order.
-}
+{\bf Right:} One-wayness attack for garbled Bloom filters with public~$M$.  The sequence $X_1,X_2,\ldots,X_q,$ are the~$q$ most probable points in the support of~$\distr{}{}$ in decreasing order.  }
 \label{fig:adv-gbf}
@@
 But when~$M$ and the hash functions are available to the attacker, it can carry out set-membership tests for itself.
-Thus the adversary on the right of Figure~\ref{fig:adv-gbf} tries the~$q$ most probable points, in order, halting with its output as soon as the set-membership test is successful.
+Thus the adversary on the right of Figure~\ref{fig:adv-gbf} tries the~$q-1$ most probable points, in order, halting with its output as soon as the set-membership test is successful.
 If none of these points are yield a successful test, then the next most probable point is output.
-The probabilty that $A_{ow}$ fails to win the one-wayness experiment is
-\begin{eqnarray*}
-\AdvPrivOW{\setprim_{\mathrm{gbf}},\distr{}{}}{A_{\mathrm{ow}}} &= 1 - \Prob{X_1 \not\in S \wedge X_2 \not\in S \wedge \cdots \wedge X_{q+1}\not\in S} \\
-& = 1 - \prod_{i=1}^{q+1} \Prob{X_i \not\in S \,|\, X_{i-1} \not\in S \wedge \cdots X_1 \not\in S}\Prob{X_1 \not\in S}\\
-\end{eqnarray*}
+It is not hard to conclude the following theorem.
 
- Thus the efficacy of the attack depends on the false positive rate. \todo{Either work out a proof for this case, or punt and make the attack more formal.}
+\begin{theorem}
+Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the public~$M$ garbled Bloom filter, in the random-oracle model for~$H$.  Then 
+\[
+\AdvPrivOW{\setprim_{\mathrm{gbf}},\distr{}{}}{A_{\mathrm{ow}}} \geq 1 - (1-1/2^{\mu})^{q}
+\]
+ where $\mu = H_\infty(\distr{}{})$ is the pointwise min-entropy of~$\distr{}{}$, and $A_{\mathrm{ow}}$ makes $kq$ random-oracle queries.
+\end{theorem}
+%\begin{eqnarray*}
+%\AdvPrivOW{\setprim_{\mathrm{gbf}},\distr{}{}}{A_{\mathrm{ow}}} &=& 1 - \Prob{X_1 \not\in S \wedge X_2 \not\in S \wedge \cdots \wedge X_{q+1}\not\in S} \\
+%&=& 1 - \prod_{i=1}^{q+1} \Prob{X_i \not\in S \,|\, X_{i-1} \not\in S \wedge \cdots X_1 \not\in S}\Prob{X_1 \not\in S}\\
+%\end{eqnarray*}
 

### 2016-09-30 results.tex
added OW attack and theorem for gbf

@@
 
-\todo{OW privacy proof? [JON]}
+\todo{OW privacy proof? Attack? [JON]}
 
@@
 following correctness bound.
-\fixme{Insert correctness theorem for \emph{private}~$M$ in the ROM.}
-\begin{theorem}
+
+\begin{theorem}\fixme{FINISH! (Animesh?)}
 Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the private~$M$ garbled Bloom filter.
@@
 \[
-\AdvPrivOW{\setprim_{\mathrm{gbf}},\distr{}{}}{A_{\mathrm{ow}}} \geq 1 - (1-1/2^{\mu})^{q}
+\AdvPrivOW{\setprim_{\mathrm{gbf}},\distr{}{}}{A_{\mathrm{ow}}} \geq 1 - \left(1-\frac{1}{2^{\mu}} \right)^{q} \geq 1 - e^{-q/2^\mu}
 \]
@@
 \end{theorem}
-%\begin{eqnarray*}
-%\AdvPrivOW{\setprim_{\mathrm{gbf}},\distr{}{}}{A_{\mathrm{ow}}} &=& 1 - \Prob{X_1 \not\in S \wedge X_2 \not\in S \wedge \cdots \wedge X_{q+1}\not\in S} \\
-%&=& 1 - \prod_{i=1}^{q+1} \Prob{X_i \not\in S \,|\, X_{i-1} \not\in S \wedge \cdots X_1 \not\in S}\Prob{X_1 \not\in S}\\
-%\end{eqnarray*}
+
+\todo{If time:  would be great to have an upperbound on onewayness for this construction!}
 

### 2016-09-30 TheoremGBF_correctness_privM.tex
GBF correctness for private M

%\begin{theorem}\label{thm:gbf-correctness-privM}
%Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the private~$M$ garbled Bloom filter. For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
%\[
%\AdvCorrect{\setprim_{\mathrm{garb}},r}{A} \leq  {\dbinom{q_T}{r}} \left( \dfrac{1}{2^{\lambda}} \right)^r\,.
%\]
%\end{theorem}
\begin{proof}[\Cref{thm:gbf-correctness-privM}]
We use a game playing argument to prove this theorem. Here, $\Rep$, $\Qry$ and $A$ are given access to $\Hash$ which uses lazy sampling to mimic a RO. $\game{0}$, exactly simulates the correctness game of a garbled Bloom filter for private $M$. Assuming $A$ does not make any pointless queries, the $\Hash$ returns random values sampled from $[m]$ in $\game{1}$. In order to account for queries to RO in $\Test$, the latter returns the $k$ hash values for each query along with the answer. It should be noted that the $\Qry$ oracle returns xor of shares at $k$ random positions in this game.

In $\game{2}$, the $\Test$ does what $\Qry$ is supposed to do. It picks $k$-subset of random indices, xor them to get the estimated final share, and checks whether the final share is equal to the queried element. Finally, it returns the $k$ hash values along with the answer and the \textbf{final share}. Since, prescribed value of $\lambda$ is 80 or 256, there is a very high probability that the final share is a random string(one or more shares that were xor-ed were random shares), and hence the adversary gains very little advantage in knowing the value of the final share. In $\game{3}$, $\Test$ picks up a random $\lambda$-bit string as the final share. The adversary wins if it finds $r$ queries which are same as the received final shares.

$\game{4}$ is identical to \game{3}, except $\bad$ is set to $\true$ if queries indexed by $r$-set $\calI$ fail to be false-positives, or queries indexed by set $\calI$ are false-positives. In $\game{4}$, $\bad$ does not affect the output of the game; $\game{5}$ on the other hand returns 0 if $\bad$ is set to $\true$. The probability of winning $\game{1}$, $\game{2}$, $\game{3}$, and $\game{4}$ are equal. Dong et al. \cite{Dong} showed that the false-positive probability is upper bounded by $2^{-\lambda}$ in case of a zero-query adversary, and $r=1$.  Using results and analyses of previous proofs, $\Prob{\game{5}(A)=1} = \dfrac{1}{\dbinom{q_T}{r}}\Prob{\game{4}(A)=1}$, and $\Prob{\game{5}(A) = 1} = \left( \dfrac{1}{2^{\lambda}} \right)^r$.

To summarize,
\[
\AdvCorrect{\setprim_{\mathrm{garb}},r}{A} \leq  {\dbinom{q_T}{r}} \left( \dfrac{1}{2^{\lambda}} \right)^r\,
\]

\begin{figure}
\fpage{.99}{
\hpagessl{.55}{.5}
{
\underline{\game{0}(A)}\\
$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\

\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
$a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
if $a \neq \qry_x(S)$ then \\
\nudge $\err \gets \err + 1$\\
Return~$a$\\

\oracle{$\HashOracle(\qry_y)$}\\
for $j \in \{1,2,\ldots,k\}$\\
\nudge $v_j \getsr [m]$\\
\nudge if $T[j,y] \neq \undefined$\\
\nudge \nudge $v_j \gets T[j,y]$\\
\nudge $T[j,y] \gets v_j$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
{
\underline{$\game{1}(A)$}\\
$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\

\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
$(h_1,\ldots,h_k \getsr [m]$\\
$a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
if $a \neq \qry_x(S)$ then \\
\nudge $\err \gets \err + 1$\\
Return~$a, h_1,\ldots,h_k $\\

\oracle{$\HashOracle(\qry_y)$}\\
$(v_1,\ldots,v_k \getsr [m]$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\fpage{.99}{
\hpagessl{.55}{.5}
{
\underline{$\game{2}(A)$}\\
$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\

\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
$M \gets \privaux$\\
$(h_1, \ldots, h_{k}) \gets \HashOracle(x)$\\
$\finalshare \gets M[h_1(x)] \xor \ldots M[h_k(x)]$\\
$a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
if $a \neq \qry_x(S)$ then \\
\nudge $\err \gets \err + 1$\\
Return~$a, \finalshare, h_1, \ldots, h_{k}$\\

\oracle{$\HashOracle(\qry_y)$}\\
$(v_1,\ldots,v_k \getsr [m]$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
{
\underline{$\game{3}(A)$}\\
$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\err  < r$ then Return 0\\
Return 1\\

\oracle{$\TestOracle(\qry_x)$}\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
$h_1,\ldots,h_k \gets \HashOracle(x)$\\
$\finalshare \getsr \bits^{\lambda}$\\
$a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
if $a \neq \qry_x(S)$ then \\
\nudge $\err \gets \err + 1$\\
Return~$(a, \finalshare, h_1,\ldots,h_k)$\\

\oracle{$\HashOracle(\qry_y)$}\\
$(v_1,\ldots,v_k \getsr [m]$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
}
\caption{\Cref{thm:gbf-correctness-privM}: Game playing argument}\label{fig:GBFprivMGame}
\end{figure}

\begin{figure}
\fpage{.99}{
\hpagessl{.45}{.55}
{
\underline{\game{4}(A)\fbox{\game{5}(A)}}\\
$c\gets 0$, $\bad \gets \false$, $\err \gets 0$;  $\calC \gets \emptyset$\\
$S \getsr A$; $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
$\bot \getsr A^{\TestOracle}(\pubaux)$\\
if $\bad = \true$ then \fbox{Return 0}\\
if $\err  < r$ then Return 0\\
Return 1\\\\

\oracle{$\HashOracle(\qry_y)$}\\
$(v_1,\ldots,v_k \getsr [m]$\\
Ret $\left(v_1,\ldots,v_k\right)$
}
{
\oracle{$\TestOracle(\qry_x)$}\\
$c \gets c + 1$\\
if $x \in \mathcal{C}$ then Return $\bot$\\
$\calC \gets \calC \cup x$\\
$M \gets \privaux$\\
$(h_1, \ldots, h_{k}) \gets \HashOracle(x)$\\
$\finalshare \gets M[h_1(x)] \xor \ldots M[h_k(x)]$\\
$a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
if $a \neq \qry_x(S)$ then \\
\nudge $\err \gets \err + 1$\\
\nudge if $c \notin \calI$ then $\bad \gets \true$\\
else if $c \in \calI$ then $\bad \gets \true$\\
Return~$a, \finalshare, h_1, \ldots, h_{k}$\\
}
}
\caption{\Cref{thm:gbf-correctness-privM}: $\game{4}$ and $\game{5}$ of game playing argument}\label{fig:GBFprivMGame1}
\end{figure}

\end{proof}

### 2016-09-30 Theorem1_FP.tex
Syntax consistency of proofs 1 and 2
Syntax consistency

@@
 The proof of the theorem will use a game playing argument as shown in \Cref{fig:Game}.
-$\game{0}(A)$ exactly simulates $\ExpCorrect{\Pi_\mathrm{lin},\distr{\calS}{},r}{A}$ with hash functions $h_j(x) =  F_{K}(\langle 1,x \rangle) + j\cdot F_{K}(\langle 2,x \rangle) \bmod m$.
+$\game{0}(A)$ exactly simulates $\ExpCorrect{\setprim_\mathrm{lin},r}{A}$ with hash functions $h_j(x) =  F_{K}(\langle 1,x \rangle) + j\cdot F_{K}(\langle 2,x \rangle) \bmod m$.
 So,
@@
 \begin{equation}
-\AdvCorrect{\Pi_{\mathrm{lin}},\distr{\calS}{},r}{A} = \Prob{\game{0}(A)=1}\label{eq:0}
+\AdvCorrect{\setprim_{\mathrm{lin}},r}{A} = \Prob{\game{0}(A)=1}\label{eq:0}
 \end{equation}
@@
 
-Recall that adversary~$A$ wins $\ExpCorrect{\Pi_{\mathrm{lin}},\distr{\calS}{},r}{}$ by finding~$r$ false positives.
+Recall that adversary~$A$ wins $\ExpCorrect{\setprim_{\mathrm{lin}},r}{}$ by finding~$r$ false positives.
 We can assume, without loss of generality,  that~$A$ halts immediately upon finding its $r$-th false positive.
@@
 %Under these assumptions,
-So, if $\game{4}(A)=1$, then there is a zero-query adversary~$D$ that finds~$r$ false positives against $\tilde{\Pi}_{\mathrm{lin}}$, which is $\Pi_{\mathrm{lin}}$ but with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$, respectively.
+So, if $\game{4}(A)=1$, then there is a zero-query adversary~$D$ that finds~$r$ false positives against $\tilde{\setprim}_{\mathrm{lin}}$, which is $\setprim_{\mathrm{lin}}$ but with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$, respectively.
 We give this~$D$ in \Cref{fig:D}.
@@
 Thus we have
-$\Prob{\game{4}(A)=1} =\Prob{\ExpCorrect{\tilde{\Pi}_{\mathrm{lin}},\distr{\calS}{},r}{D} = 1}$.
+$\Prob{\game{4}(A)=1} =\Prob{\ExpCorrect{\tilde{\setprim}_{\mathrm{lin}},r}{D} = 1}$.
 
-Note that $\tilde{\Pi}_{\mathrm{lin}}$ is the scheme that is analyzed in the classical Bloom filter literature ---the hash functions are modeled as independent random functions, and the parameters $k,m,n$  are set to achieve a target maximum false-positive probability (or rate).
+Note that $\tilde{\setprim}_{\mathrm{lin}}$ is the scheme that is analyzed in the classical Bloom filter literature ---the hash functions are modeled as independent random functions, and the parameters $k,m,n$  are set to achieve a target maximum false-positive probability (or rate).
 Kirsch and Mitzenmacher~\cite{KM} show that the upperbound on false-positive probability for a zero-query adversary and $r=1$ is $\left( (1-e^{-kn/m})^k + O(1/n) \right)$.
@@
 Let $\calF_i$ be the event that~$x_i(i \in \mathcal{I})$ is a false positive.
-Since $\game{4}$ (equivalently $\tilde{\Pi}_{\mathrm{lin}}$) use independent random functions, the events $\calF_1,\calF_2,\ldots,\calF_r$ are independent.
+Since $\game{4}$ (equivalently $\tilde{\setprim}_{\mathrm{lin}}$) use independent random functions, the events $\calF_1,\calF_2,\ldots,\calF_r$ are independent.
 \[
-\Prob{\ExpCorrect{\tilde{\Pi}_{\mathrm{lin}},\distr{\calS}{},r}{D} = 1}\leq \left( (1-e^{-kn/m})^k + O(1/n) \right)^r 
+\Prob{\ExpCorrect{\tilde{\setprim}_{\mathrm{lin}},r}{D} = 1}\leq \left( (1-e^{-kn/m})^k + O(1/n) \right)^r 
 \]
@@
 \[
-\AdvCorrect{\Pi_{\mathrm{lin}},\distr{\calS}{},r}{A}  \leq  \AdvPRF{F}{B_1} +\AdvPRF{F}{B_2} +\dbinom{q}{r}\left( (1-e^{-kn/m})^k + O(1/n) \right)^r
+\AdvCorrect{\setprim_{\mathrm{lin}},r}{A}  \leq  \AdvPRF{F}{B_1} +\AdvPRF{F}{B_2} +\dbinom{q}{r}\left( (1-e^{-kn/m})^k + O(1/n) \right)^r
 \]
@@
 \underline{\game{0}(A)}\\
+$K \getsr \calK $\\
 $S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
@@
 \underline{\game{1}(A)}\\
-$K \getsr \calK$, $\rho \getsr \Func{\univ,[m]}$\\
+$K \getsr \calK $, $\rho \getsr \Func{\univ,[m]}$\\
 $S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\

### 2016-09-30 Theorem2_FP.tex
Syntax consistency

@@
 We use a game playing argument (shown in \Cref{fig:2TGame}) similar to \Cref{thm1} to prove this theorem.
-In \game{0}, adversary attacks the correctness game with  hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpCorrect{\Pi_{\mathrm{ds}},\distr{\calS}{},r}{A}$.
+In \game{0}, adversary attacks the correctness game with  hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpCorrect{\setprim_{\mathrm{ds}},r}{A}$.
 \begin{equation}
-\AdvCorrect{\Pi_{\mathrm{ds}},\distr{\calS}{},r}{A} = \Prob{\game{0}(A)=1}\label{eq:2T0}
+\AdvCorrect{\setprim_{\mathrm{ds}},r}{A} = \Prob{\game{0}(A)=1}\label{eq:2T0}
 \end{equation}
@@
 
-In $\game{1}$, $A$ attacks a different filter $\tilde{\Pi}_\mathrm{ds}$, in which $F_K$ is replaced by a random function.
+In $\game{1}$, $A$ attacks a different filter $\tilde{\setprim}_\mathrm{ds}$, in which $F_K$ is replaced by a random function.
 $\game{2}$ and $\game{3}$ on the other hand use lazy sampling in $\Hash$ to select random values from $[m]$.
@@
 
-Let $D$ be a zero-query adversary (shown in \Cref{fig:D}) that finds ~$r$ false positives against $\tilde{\Pi}_{\mathrm{ds}}$.
-Using explanations from previous theorem, if $A$ wins $\game{3}$, then $D$ wins $\ExpCorrect{\tilde{\Pi}_{\mathrm{ds}},\distr{\calS}{},r}{\cdot}$ game.
+Let $D$ be a zero-query adversary (shown in \Cref{fig:D}) that finds ~$r$ false positives against $\tilde{\setprim}_{\mathrm{ds}}$.
+Using explanations from previous theorem, if $A$ wins $\game{3}$, then $D$ wins $\ExpCorrect{\tilde{\setprim}_{\mathrm{ds}},r}{\cdot}$ game.
 So,
 \begin{equation*}
-\AdvCorrect{\tilde{\Pi}_{\mathrm{ds}},\distr{\calS}{},r}{D} = \Prob{\game{3}(A) = 1}\label{eq:2T8}
+\AdvCorrect{\tilde{\setprim}_{\mathrm{ds}},r}{D} = \Prob{\game{3}(A) = 1}\label{eq:2T8}
 \end{equation*}
 
-Note that like $\tilde{\Pi}_{\mathrm{lin}}$, $\tilde{\Pi}_{\mathrm{ds}}$ is the scheme that is analyzed in the classical Bloom filter literature.
-So, for a zero-query adversary $D$ and $r=1$, the upper bound on false-positive probability of a classical Bloom filter applies to $\tilde{\Pi}_{\mathrm{ds}}$ as well.
+Note that like $\tilde{\setprim}_{\mathrm{lin}}$, $\tilde{\setprim}_{\mathrm{ds}}$ is the scheme that is analyzed in the classical Bloom filter literature.
+So, for a zero-query adversary $D$ and $r=1$, the upper bound on false-positive probability of a classical Bloom filter applies to $\tilde{\setprim}_{\mathrm{ds}}$ as well.
 For $r > 1$, based on the assumption that $A$ makes no pointless queries, the queries made by $A$ are distinct and not elements of the original set $S$.
@@
 \begin{equation*}
-\AdvCorrect{\tilde{\Pi}_{\mathrm{ds}},\distr{\calS}{},r}{D} =   {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
+\AdvCorrect{\tilde{\setprim}_{\mathrm{ds}},r}{D} =   {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
 \end{equation*}
@@
 \[
-\AdvCorrect{\Pi_{\mathrm{ds}},\distr{\calS}{},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
+\AdvCorrect{\setprim_{\mathrm{ds}},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
 \]

### 2016-09-30 TheoremGBF_correctness.tex
Syntax consistency

@@
 \heading{Garbled Bloom filter in random oracle model (ROM). }
-Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.  Then $\Pi_{\mathrm{garb}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-garbled-bf} (right side).  The following result shows,
+Fix $n,k,m \geq 0$ and let $\mathcal{S}=[\univ]^n$.  Then $\setprim_{\mathrm{garb}}= (\calQ,\Rep, \Qry)$ is defined as in Figure~\ref{fig:bf-and-garbled-bf} (right side).  The following result shows,
 
 \begin{theorem}\label{thm:gbf-correctness}
-Fix $r=1$, $k,m,n>0$, and let $\Pi_{\mathrm{garb}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described.
+Fix $r=1$, $k,m,n>0$, and let $\setprim_{\mathrm{garb}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described.
 For any adversary~$A$ that makes a maximum of~$\dbinom{m}{k}$ queries to the RO, and has time-complexity~$O(t)$,
 \[
-\AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A}  \geq   \left(1 - e^{-n/m^k}\right)^{nr} + \dfrac{1}{\dbinom{m}{k}-n-(q-1)} . \Big(1-\dfrac{n}{2^\lambda}\Big)
+\AdvCorrect{\setprim_{\mathrm{garb}},r}{A}  \geq   \left(1 - e^{-n/m^k}\right)^{nr} + \dfrac{1}{\dbinom{m}{k}-n-(q-1)} . \Big(1-\dfrac{n}{2^\lambda}\Big)
 \]
@@
 
-If $\epsilon$ is the event of finding $r=1$ error, $\Prob{\epsilon} = \AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A} =  \Prob{\epsilon_{\fn}} + \Prob{\epsilon_{\fp}}$($\epsilon_{\fn}$ and $\epsilon_{\fp}$ are mutually independent) and hence
+If $\epsilon$ is the event of finding $r=1$ error, $\Prob{\epsilon} = \AdvCorrect{\setprim_{\mathrm{garb}},r}{A} =  \Prob{\epsilon_{\fn}} + \Prob{\epsilon_{\fp}}$($\epsilon_{\fn}$ and $\epsilon_{\fp}$ are mutually independent) and hence
 \[
-\AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A}  \geq \left(1 - e^{-n/m^k}\right)^{nr} + \dfrac{1}{\dbinom{m}{k}-n-(q-1)} . \Big(1-\dfrac{n}{2^\lambda}\Big)
+\AdvCorrect{\setprim_{\mathrm{garb}},r}{A}  \geq \left(1 - e^{-n/m^k}\right)^{nr} + \dfrac{1}{\dbinom{m}{k}-n-(q-1)} . \Big(1-\dfrac{n}{2^\lambda}\Big)
 \]

### 2016-09-30 notions.tex
GBF, adding descriptive names to theorem statements in Section 4

@@
 attacker~$A$, there is an attacker $A'$ running in about the same time with
-\[\AdvPrivOW{\setprim,\mathcal{D}}{A} \leq \AdvPrivSS{\setprim,{\sf leak}}{A'} + 2^{-\tilde H_\infty({\cal D} \mid {\sf leak})}.\]
+\[\AdvPrivOW{\setprim,\mathcal{D}}{A} \leq \AdvPrivSS{\setprim,{\sf
+    leak}}{A'} + 2^{-\tilde H_\infty({\cal D} \mid {\sf leak})}.\] 
 %Let $\setprim$ be a set-representation data structure that is $(t, \epsilon)$-semantically secure
@@
 2^{-\tilde H_\infty({\cal D} \mid {\sf leak})}.\]
-The theorem follows.
+The theorem follows. \hfill\qed
 \end{proof}
@@
 outputs~1 in
-the following experiment~$G0$: \jnote{BTW, in class when I do this stuff I usually
-say ``game'' and then correct myself and say ``\ldots but if you want to get funded,
-call it an experiment.'' (Some light humor while you work.)}
+the following experiment~$G0$: 
+%\jnote{BTW, in class when I do this stuff I usually
+%say ``game'' and then correct myself and say ``\ldots but if you want to get funded,
+%call it an experiment.'' (Some light humor while you work.)}
 \begin{enumerate}
@@
 $G1$ and the probability that it outputs~1 in
-$G0$ is bounded by ${\sf Adv}_F^{\rm PRF}(A')$, where $A'$ performs the
+$G0$ is bounded by $\AdvPRF{F}{A'}$, where $A'$ performs the
 obvious simulation.
@@
 precisely $\Prob{\ExpPrivSSsim{\setprim,{\sf leak}}{A, \Sim}=1}$.
-This completes the proof.
+This completes the proof. \hfill\qed
 \end{proof}

### 2016-09-30 results.tex
cheers
GBF correctness for private M
GBF, adding descriptive names to theorem statements in Section 4

@@
 
-\begin{theorem}\label{thm3}\label{thm:bf-ow}
+\begin{theorem}[{\rm OW-privacy of classic BF in the ROM}]\label{thm3}\label{thm:bf-ow}
 Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be the classical Bloom filter data structure over~$\elts$.
@@
 
-\begin{theorem}\label{thm2}\label{thm:ds-correctness}
+\begin{theorem}[{\rm Correctness of DS-PRF}]\label{thm2}\label{thm:ds-correctness}
 Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-membership data structure (over~$\elts$) in Figure~\ref{fig:lin-and-ds}.
@@
 The privacy of $\setprim_{\mathrm{ds}}$ follows directly from our general result, Theorem~\ref{thm:xxx}.
-\begin{theorem}\label{thm:ds-ss}
+\begin{theorem}[\rm{SS-privacy of DS PRF}]\label{thm:ds-ss}
 Fix $k,m,n>0$, a set~$\elts$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-membership data structure described in Figure~\ref{fig:lin-and-ds}.
@@
 
-\begin{theorem}\label{thm1}\label{thm:lin-correctness}
+\begin{theorem}[{\rm Correctness of linear-PRF}]\label{thm1}\label{thm:lin-correctness}
 Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-membership data structure (over~$\elts$) described in Figure~\ref{fig:lin-and-bin-lin}.
@@
 The SS-privacy of the linear-PRF hash construction follows directly from~Theorem~\ref{thm:xxx}.
-\begin{theorem}\label{thm:lin-privacy}
+\begin{theorem}[{\rm SS-privacy of linear-PRF}]\label{thm:lin-privacy}
 Fix $k,m,n,r>0$, a set $\elts$, and let $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-membership data structure (over~$\elts$) described in Figure~\ref{fig:lin-and-bin-lin}.
@@
 
-\begin{theorem}\label{thm:bi-lin-ss}
+\begin{theorem}[{\rm SS-privacy of bigram linear-PRF}]\label{thm:bi-lin-ss}
 Let $\setprim_{\bilin}= (\Rep, \Qry)$ be the set-membership data structure described in Figure~\ref{fig:neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.
@@
 \end{theorem}
-\begin{proof}(Sketch.)
+\begin{proof}\tsnote{still a bit sketchy but believable}
 On input the set~$S$ produced by~$A$, the $\Rep$ algorithm turns $x_1=$'cab', $x_2=$'bab' and $x_3$ into their respective bigram sets: $B_{x_1}=\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{b}\sqcup\}$, $B_{x_2}=\{\sqcup\mathrm{b},\mathrm{ba},\mathrm{ab}, \mathrm{b}\sqcup \}$; the set $B_{x_3}$ will be either $\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{ba}, \mathrm{a}\sqcup\}$, or $\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{bc}, \mathrm{c}\sqcup\}$, each with probability 1/2.
@@
 
-\begin{theorem}\label{thm:bi-ds-ss}
+\begin{theorem}[{\rm SS-privacy of bigram DS PRF-hash}]\label{thm:bi-ds-ss}
 Let $\setprim_{\bilin}= (\Rep, \Qry)$ be the set-membership data structure described in Figure~\ref{fig:neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.
@@
 works outside of the ROM, say, when we hash via $H(j,x)=F_K(\langle
-j,x \rangle)$ and assume~$F_K$ is a secure PRF.  Here, $\privaux=K$.  Now,
+j,x \rangle)$ and assume~$F_K$ is a secure PRF.  Here,
+$\privaux=\langle K \rangle$.  Now,
 however, the work switches from offline hash evaluations (i.e., random
@@
 
-Switching now to the case of a \emph{private}~$M$ GBF, i.e., $\pubaux=\emptystring, \privaux=\langle M \rangle$, we have the
+Switching now to the case of a \emph{private}-$M$ GBF, i.e., $\pubaux=\emptystring, \privaux=\langle M \rangle$, we have the
 following correctness bound.
 
-\begin{theorem}\fixme{FINISH! (Animesh?)}
-Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the private~$M$ garbled Bloom filter.
+\begin{theorem}[{\rm Correctness of private-$M$ GBF in the ROM}]\fixme{FINISH! (Animesh?)}
+Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the private-$M$ garbled Bloom filter.
 For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
 \[
-\AdvCorrect{\setprim_{\mathrm{gbf}},r}{A} \leq  [...]
+\AdvCorrect{\setprim_{\mathrm{gbf}},r}{A} \leq  {\dbinom{q_T}{r}} \left( \dfrac{1}{2^{\lambda}} \right)^r\,.
 \]
@@
 
-\begin{theorem}
-Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the public~$M$ garbled Bloom filter, in the random-oracle model for~$H$.  Then 
+\begin{theorem}[{\rm OW-privacy of public-$M$ GBF}]
+Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the public-$M$ garbled Bloom filter, in the random-oracle model for~$H$.
+Then \fixme{This probability might not be correct...
+verify when less tired.}
 \[
-\AdvPrivOW{\setprim_{\mathrm{gbf}},\distr{}{}}{A_{\mathrm{ow}}} \geq 1 - \left(1-\frac{1}{2^{\mu}} \right)^{q} \geq 1 - e^{-q/2^\mu}
+\AdvPrivOW{\setprim_{\mathrm{gbf}},\distr{}{}}{A_{\mathrm{ow}}} \geq 1 - \left(1-\frac{n}{2^{\mu}} \right)^{q} \geq 1 - e^{-nq/2^\mu}
 \]
@@
 \end{theorem}
-
-\todo{If time:  would be great to have an upperbound on onewayness for this construction!}
+\noindent
+We conjecture that this is the optimal attack on the GBF in this setting.
 
 If instantiated with hash functions $H_j(x) = F_K(\langle j,x \rangle)$ and $\privaux = \langle K \rangle$, the SS-privacy of the GBF follows directly from~Theorem~\ref{thm:xxx}.
-\begin{theorem}\label{thm:gbf-prf-privacy}
+\begin{theorem}[{\rm SS-privacy of GBF with secret hash functions}]
+\label{thm:gbf-prf-privacy}
 Fix $k,m,n,r,\lambda>0$ and a function family~$F\colon \calK \times \bits^* \to [m]$.

### 2016-09-30 notions.tex
fixing linebreaks and other cleaning

@@
 any attacker $A$, there is an attacker
-$A'$ running in about the same time for which
-\[\AdvPrivSS{\setprim,{\sf leak}}{A} \leq {\sf Adv}_F^{\rm PRF}(A'). \]
+$B$ running in about the same time for which
+\[\AdvPrivSS{\setprim,{\sf leak}}{A} \leq {\sf Adv}_F^{\rm PRF}(B). \]
 \end{theorem}
@@
 $G1$ and the probability that it outputs~1 in
-$G0$ is bounded by $\AdvPRF{F}{A'}$, where $A'$ performs the
+$G0$ is bounded by $\AdvPRF{F}{B}$, where $B$ performs the
 obvious simulation.

### 2016-09-30 results.tex
fixing linebreaks and other cleaning

@@
 \end{theorem}
+\todo{move proof back in-line.}
 The proof appears in Appendix~\ref{app:xxx}.  We note that Kirsch and Mitzenmacher~\cite{xxx} show
@@
 \[
-\AdvPrivOW{\setprim_{\mathrm{Bloom}},\distr{}{},r}{A} \leq  \frac{(kqn+n)}{2^{\mu}}
+\AdvPrivOW{\setprim_{\mathrm{Bloom}},\distr{}{},r}{A} \leq  \frac{(kqn+n)}{2^{\mu}}\;.
 \]
@@
 \end{theorem}
+\todo{some form of proof ---at least a proof sketch in the text--- needs to appear here!}
 
@@
 \[
-\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
+\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}\;.
 \]
@@
 It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
-On input a set of distinct elements $S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, \ldots, s_k\langle k,x_1\rangle, s_{k+1}=\langle 1,x_2\rangle, \ldots, s_{2k}=\langle k,x_2\rangle, \ldots ,s_{kn+1}=\langle 1,x_n\rangle, \ldots, s_{kn}=\langle k,x_n \rangle$.
-On input $n,F_K(s_1),\ldots,F_K(s_{kn})$, algorithm $\Rep_2$ simply initializes an all-zero array~$M$ of~$m$-bits, and sets the positions $M[F_K(s_i)]$ to 1.
+On input a set of distinct elements $S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, \ldots, s_k\langle k,x_1\rangle, s_{k+1}=\langle 1,x_2\rangle, \ldots,\linebreak s_{2k}=\langle k,x_2\rangle, \ldots ,s_{kn+1}=\langle 1,x_n\rangle, \ldots, s_{kn}=\langle k,x_n \rangle$.
+On input $n,F_K(s_1),\ldots,\linebreak F_K(s_{kn})$, algorithm $\Rep_2$ simply initializes an all-zero array~$M$ of~$m$-bits, and sets the positions $M[F_K(s_i)]$ to 1.
 It returns~$M$ as $\pubaux$.
+\hfill\qed
 \end{proof}
@@
 On input a set of distinct elements
-$S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, s_3 = \langle 1,x_2\rangle, s_4=\langle 2,x_2 \rangle,\ldots,s_{2n-1}=\langle 1,x_n \rangle, s_{2n}=\langle 2,x_n \rangle$.
+$S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, s_3 = \langle 1,x_2\rangle, s_4=\langle 2,x_2 \rangle,\ldots,\linebreak s_{2n-1}=\langle 1,x_n \rangle, s_{2n}=\langle 2,x_n \rangle$.
 
@@
 It returns~$M$ as $\pubaux$.
+\hfill\qed
 \end{proof}
@@
 bit~$z$, so at best it can cause~$A$ to output 1 with
-probabilility~$1/2$.  That is $\ExpPrivSSsim{\setprim_{\bilin}}{A,\Sim} \leq 1/2$.
+probabilility~$1/2$.  That is $\ExpPrivSSsim{\setprim_{\bilin}}{A,\Sim} \leq 1/2$. \hfill\qed
 \end{proof}
@@
 set~$k=\lambda$, and test with $\lambda=80$.  Making 80 hash calls per
-set-membership query would be laughable in many applications, and a
-$2^{-80}$ false-postive rate would be considered overkill.\footnote{Note
+set-membership query would be prohibitive in many applications, and a
+$2^{-80}$ false-postive rate would be typically considered overkill in
+practice.\footnote{Note
 that, as described in~\cite{xxx}, $\lambda$ must be at least the
@@
 \[
-\AdvPrivSS{\setprim_{\mathrm{gbf\mbox{-}prf}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
+\AdvPrivSS{\setprim_{\mathrm{gbf\mbox{-}prf}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}\;.
 \]
@@
 It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
-On input a set of distinct elements $S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, \ldots, s_k\langle k,x_1\rangle, s_{k+1}=\langle 1,x_2\rangle, \ldots, s_{2k}=\langle k,x_2\rangle, \ldots ,s_{kn+1}=\langle 1,x_n\rangle, \ldots, s_{kn}=\langle k,x_n \rangle$.
-On input $n,F_K(s_1),\ldots,F_K(s_{kn})$, algorithm $\Rep_2$ carries out the pseudocode of~$\Rep$ in Figure~\ref{fig:gbf}, making use of $F_K(s_1),\ldots,F_K(s_{kn})$ in the obvious way.
-It returns~$M$ as $\pubaux$.
+On input a set of distinct elements $S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, \ldots, s_k\langle k,x_1\rangle, s_{k+1}=\langle 1,x_2\rangle, \ldots,\linebreak s_{2k}=\langle k,x_2\rangle, \ldots ,s_{kn+1}=\langle 1,x_n\rangle, \ldots, s_{kn}=\langle k,x_n \rangle$.
+On input $n,F_K(s_1),\ldots,\linebreak F_K(s_{kn})$, algorithm $\Rep_2$ carries out the pseudocode of~$\Rep$ in Figure~\ref{fig:gbf}, making use of $F_K(s_1),\ldots,F_K(s_{kn})$ in the obvious way.
+It returns~$M$ as $\pubaux$.\hfill\qed
 \end{proof}

### 2016-09-30 BF_correctness.tex
moving files to better names

--- 2016-09-28 Theorem3_FP.tex
@@
-\section{Proof of \Cref{thm3}}
+\section{Proof of Theorem~\ref{thm:thm:bf-correctness}
 \label{sec:thm3_fp}
-\begin{proof}[\Cref{thm3}]
+\begin{proof}[\ref{thm:thm:bf-correctness}]
 We use a game playing argument to prove this theorem in the ROM.
@@
 Here, the adversary $A$, along with $\Rep$ and $\Qry$ are given access to $\Hash$.
-It can be seen that, $\game{0}$ exactly simulates the correctness game of $\Pi_{\mathrm{Bloom}}$.
-So, $\AdvCorrect{\Pi_{\mathrm{Bloom}},\distr{\calS}{},r}{A} = \Prob{\game{0}(A) = 1}$.
+It can be seen that, $\game{0}$ exactly simulates the correctness game of $\setprim_{\mathrm{Bloom}}$.
+So, $\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} = \Prob{\game{0}(A) = 1}$.
 
@@
 \[
-\AdvCorrect{\Pi_{\mathrm{Bloom}},\distr{\calS}{},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
 \]
@@
 \oracle{$\TestOracle(\qry_x)$}\\
-if $\qry_x \in \mathcal{C}$ then Return $\bot$\\
-$\calC \gets \calC \cup \{\qry_x\}$\\
-$a \gets \Qry^{\HashOracle}(\pubaux,\privaux,\qry_x)$\\
+if $x \in \mathcal{C}$ then Return $\bot$\\
+$\calC \gets \calC \cup x$\\
+$a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
 if $a \neq \qry_x(S)$ then \\
@@
 $v \getsr [m]$\\
-if $T[i,\qry_y] \neq \undefined$\\
-\nudge $v \gets T[i,\qry_y]$\\
-$T[i,\qry_y] \gets v$\\
+if $T[i,y] \neq \undefined$\\
+\nudge $v \gets T[i,y]$\\
+$T[i,y] \gets v$\\
 Ret $v$
@@
 \oracle{$\TestOracle(\qry_x)$}\\
-if $\qry_x \in \mathcal{C}$ then Return $\bot$\\
-$\calC \gets \calC \cup \{\qry_x\}$; $M \gets\pubaux$\\
+if $x \in \mathcal{C}$ then Return $\bot$\\
+$\calC \gets \calC \cup x$; $M \gets\pubaux$\\
 for $j \in \{1,2,\ldots,k\}$\\
-\nudge $h_j \gets \HashOracle(j,\qry_x)$\\
+\nudge $h_j \gets \HashOracle(j, x)$\\
 \nudge if $M[h_j] \neq 1$ then Return 0\\
@@
 \oracle{$\TestOracle(\qry_x)$}\\
-if $\qry_x \in \mathcal{C}$ then Return $\bot$\\
-$\calC \gets \calC \cup \{\qry_x\}$; $M \gets\pubaux$\\
+if $x \in \mathcal{C}$ then Return $\bot$\\
+$\calC \gets \calC \cup x$; $M \gets\pubaux$\\
 for $j \in \{1,2,\ldots,k\}$\\
-\nudge $h_j \gets \HashOracle(j,\qry_x)$\\
+\nudge $h_j \gets \HashOracle(j, x)$\\
 \nudge if $M[h_j] \neq 1$\\
@@
 \oracle{$\TestOracle(\qry_x)$}\\
-if $\qry_x \in \mathcal{C}$ then Return $\bot$\\
-$\calC \gets \calC \cup \{\qry_x\}$; $M \gets\pubaux$\\
-$(h_1, \ldots, h_{k}) \gets \HashOracle(\qry_x)$\\
+if $x \in \mathcal{C}$ then Return $\bot$\\
+$\calC \gets \calC \cup x$; $M \gets\pubaux$\\
+$(h_1, \ldots, h_{k}) \gets \HashOracle(x)$\\
 for $j \in \{1,2,\ldots,k\}$\\
@@
 \nudge $v_j \getsr [m]$\\
-\nudge if $T[j,\qry_y] \neq \undefined$\\
-\nudge \nudge $v_j \gets T[j,\qry_y]$\\
-\nudge $T[j,\qry_y] \gets v_j$\\
+\nudge if $T[j,y] \neq \undefined$\\
+\nudge \nudge $v_j \gets T[j,y]$\\
+\nudge $T[j,y] \gets v_j$\\
 Ret $\left(v_1,\ldots,v_k\right)$
@@
 \oracle{$\TestOracle(\qry_x)$}\\
-if $\qry_x \in \mathcal{C}$ then Return $\bot$\\
-$\calC \gets \calC \cup \{\qry_x\}$\\
+if $x \in \mathcal{C}$ then Return $\bot$\\
+$\calC \gets \calC \cup x$\\
 if $\Ans[x] \neq \undefined$\\
-\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(\qry_x)$\\
+\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(x)$\\
 Return $\Ans[x]$\\
@@
 \nudge if $M[v_j] \neq 1$ then \\
-\nudge \nudge $\Ans[\qry_y] \gets (0, (v_1, \ldots, v_{k}) )$\\
+\nudge \nudge $\Ans[y] \gets (0, (v_1, \ldots, v_{k}) )$\\
 \nudge \nudge if $c \in \calI$ then $\bad \gets \true$\\
@@
 $\err \gets \err +1$\\
-$\Ans[\qry_y] \gets (1, (v_1, \ldots, v_{k}))$\\
+$\Ans[y] \gets (1, (v_1, \ldots, v_{k}))$\\
 Return $\left(v_1,\ldots,v_k\right)$

### 2016-09-30 BF_correctness.tex
moving files to better names

@@
-\section{Proof of Theorem~\ref{thm:thm:bf-correctness}
+\section{Proof of Theorem~\ref{thm:bf-correctness}}
 \label{sec:thm3_fp}
-\begin{proof}[\ref{thm:thm:bf-correctness}]
+\begin{proof}[\ref{thm:bf-correctness}]
 We use a game playing argument to prove this theorem in the ROM.

### 2016-09-30 BF_correctness.tex
moving bf-correctness proof back in line

@@
-\section{Proof of Theorem~\ref{thm:bf-correctness}}
-\label{sec:thm3_fp}
-\begin{proof}[\ref{thm:bf-correctness}]
-We use a game playing argument to prove this theorem in the ROM.
+%\section{Proof of Theorem~\ref{thm:bf-correctness}}
+%\label{sec:thm3_fp}
+\begin{proof}[Theorem~\ref{thm:bf-correctness}]
+We use a game playing argument, please refer to Figures~\ref{fig:bf-correctness-games1} and~\ref{fig:bf-correctness-games2}.
 In $\game{0}$, the $\Hash$ does lazy sampling of elements from $[m]$ to mimic a random oracle(RO).
@@
 It can be observed that, the total queries made to the $\Hash$ oracle by the adversary is the sum of queries($q_T$) made by the $\Test$ oracle, and adversary's direct queries($q_H$) to the RO.
-Using analyses and intermediate results of previous proofs, $\Prob{\game{5}(A)=1} = \dfrac{1}{\dbinom{q_T + q_H}{r}}\Prob{\game{4}(A)=1}$.
+Using analyses and intermediate results of previous proofs, $\Prob{\game{5}(A)=1} = \dfrac{1}{\binom{q_T + q_H}{r}}\Prob{\game{4}(A)=1}$.
 
@@
 which is the bound claimed in the theorem statement.
-\begin{figure}
+\begin{figure}[tp]
 \fpage{.9}{
@@
 }
-\caption{\Cref{thm3}: Game playing argument}\label{fig:3TGame}
+\caption{\ref{thm:bf-correctness}: Game playing argument}
+\label{fig:bf-correctness-games1}
 \end{figure}
-\begin{figure}
+\begin{figure}[tp]
 \fpage{.9}{
@@
 }
-\caption{\Cref{thm3}: $\game{4}$ and $\game{5}$ of game playing argument}\label{fig:3TGame}
+\caption{\ref{thm:bf-correctness}: $\game{4}$ and $\game{5}$ of game
+  playing argument}
+\label{fig:bf-correctness-games2}
 \end{figure}
-
+\hfill\qed
 \end{proof}

### 2016-09-30 results.tex
moving bf-correctness proof back in line

@@
 \end{theorem}
-\todo{move proof back in-line.}
-The proof appears in Appendix~\ref{app:xxx}.  We note that Kirsch and Mitzenmacher~\cite{xxx} show
+We note that Kirsch and Mitzenmacher~\cite{xxx} show
 that the ($r=1$, zero-query) FP-probability for~$\setprim_\mathrm{Bloom}$ is
@@
 consisting of~$(q_T+q_H)$ attempts.
-%\input{Theorem3_FP}
+\input{BF_correctness}
 

### 2016-09-30 results.tex
cleaning up section 4

@@
 We note that Kirsch and Mitzenmacher~\cite{xxx} show
-that the ($r=1$, zero-query) FP-probability for~$\setprim_\mathrm{Bloom}$ is
+that the ($r=1$, zero-query) error-probability for~$\setprim_\mathrm{Bloom}$ is
 always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
@@
 $((q_T+q_H) (1-e^{-kn/m})^k + O(q/n) )^r$; loosely, this is the bound one expects for
-trying to find a single FP in each of~$r$ independent``rounds'', each round
+trying to find a single correctness error (in this case, a false positive) in each of~$r$ independent``rounds'', each round
 consisting of~$(q_T+q_H)$ attempts.
@@
 The proof appears in Appendix~\ref{app:xxx}.  We note that Kirsch and Mitzenmacher~\cite{xxx} show
-that the ($r=1$, zero-query) FP-probability for~$\setprim_\mathrm{lin}$ is
+that the ($r=1$, zero-query) error-probability for~$\setprim_\mathrm{lin}$ is
 always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic

### 2016-09-30 results.tex
cheers

@@
   data structure $\setprim_{\mathrm{lin}}$ {\bf Right:}
-The scheme from Neidermayer et al.\cite{xxx}, $\setprim_{\bilin}$. The $\mathsf{bigram}$
+The scheme from Niedermeyer et al.\cite{xxx}, $\setprim_{\bilin}$. The $\mathsf{bigram}$
 algorithm takes a string~$x=x_1,x_2,\ldots,x_\ell$ as input, and
@@
 \label{fig:lin-and-bi-lin}
-\label{fig:neidermayer}
+\label{fig:niedermeyer}
 \end{figure}
@@
 
-Looking ahead to the next section, we will analyze a closely related construction, which was attacked by Neidermayer et al.~\cite{xxx} in the context of private medical-record linkage.
+Looking ahead to the next section, we will analyze a closely related construction, which was attacked by Niedermeyer et al.~\cite{xxx} in the context of private medical-record linkage.
 It uses the same linear-PRF hash functions, but has a $\Rep$ algorithm that that does not ensure that the hash functions are called on \emph{distinct} values.
 We show that this is \emph{not} private with respect to our SS notion for a leakage function that leaks nearly the entire set~$S$.
-\todo{It would be better, perhaps, to show that it is not OW secure, since this implies it isn't SS secure, and OW security is what Neidermayer et al.
+\todo{It would be better, perhaps, to show that it is not OW secure, since this implies it isn't SS secure, and OW security is what Niedermeyer et al.
 violate.}
@@
 \todo{OW privacy proof?
-Or just some text that says that Neidermayer et al show something stronger~---OW-privacy violation---~albeit with $n=10000, m=10000\alpha$ for an $\alpha$ that I need to look up.}
+Or just some text that says that Niedermeyer et al show something stronger~---OW-privacy violation---~albeit with $n=10000, m=10000\alpha$ for an $\alpha$ that I need to look up.}
 
@@
 \subsection{Bigram Domain-Separated PRF-Hash}
-We note that Neidermayer et al.
+We note that Niedermeyer et al.
 in~\cite{xxx} suggest replacing the linear-PRF hash functions in the previous construction with independently keyed PRFs as a countermeasure to their attack.
@@
 \begin{theorem}[{\rm SS-privacy of bigram DS PRF-hash}]\label{thm:bi-ds-ss}
-Let $\setprim_{\bilin}= (\Rep, \Qry)$ be the set-membership data structure described in Figure~\ref{fig:neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.
+Let $\setprim_{\bilin}= (\Rep, \Qry)$ be the set-membership data structure described in Figure~\ref{fig:niedermeyer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.
 Let $\leak$ be the leakage function described just prior to Theorem~\ref{thm:bi-lin-ss}.

### 2016-09-30 lin-correctness.tex
moving files to better names

--- 2016-09-30 Theorem1_FP.tex
@@
 %F_{K}(\langle 1,x \rangle) + j\cdot F_{K}(\langle 2,x \rangle) \bmod m
-\begin{proof}[\Cref{thm1}]
+\begin{proof}[Theorem~\ref{thm:xxx}]
 The proof of the theorem will use a game playing argument as shown in \Cref{fig:Game}.
@@
 %\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
-\begin{figure}
+\begin{figure}[tp]
 \fpage{0.9}{
@@
 }
-\caption{\Cref{thm1}:Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
+\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
+\fixme{fix caption and Crefs}
 \end{figure}
@@
 %\caption{Game playing argument}\label{fig:Game}
-\begin{figure}
+\begin{figure}[tp]
 \fpage{.99}{
@@
 \caption{\Cref{thm1}: Game playing argument}\label{fig:Game}
+\fixme{fix caption and Crefs}
 \end{figure}
@@
 %\caption{PRF game}\label{fig:prf}
-\begin{figure}
+\begin{figure}[tp]
 \centering
@@
 \caption{Zero-query adversary $D$} \label{fig:D}
+\fixme{For what theorem?}
 \end{figure}

### 2016-09-30 results.tex
moving files to better names
moving files, moving proofs inline

@@
 \end{theorem}
-\todo{some form of proof ---at least a proof sketch in the text--- needs to appear here!}
+We note that Kirsch and Mitzenmacher~\cite{xxx} show
+that the ($r=1$, zero-query) error-probability for~$\setprim_\mathrm{ds}$ is
+always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
+rate of convergence is faster than~$1/n$.   As before, the multiplicative term $\dbinom{q}{r}$ arises when switching from the adaptive to zero-query settings.
+\input{ds-correctness}
 
@@
 \end{theorem}
-The proof appears in Appendix~\ref{app:xxx}.  We note that Kirsch and Mitzenmacher~\cite{xxx} show
+Again, Kirsch and Mitzenmacher~\cite{xxx} show
 that the ($r=1$, zero-query) error-probability for~$\setprim_\mathrm{lin}$ is
 always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
-rate of convergence is faster than~$1/n$.   As in previous cases, the multiplicative term $\dbinom{q}{r}$ arises when switching from the adaptive to zero-query settings.
+rate of convergence is faster than~$1/n$.   
+the multiplicative term $\dbinom{q}{r}$ arises when switching from the adaptive to zero-query settings.
+\input{lin-correctness}
 
@@
 
-\begin{figure}
+\begin{figure}[tp]
 \centering
@@
 In terms of SS-privacy, however, this change offers no help.
-The following theorem is proved via a nearly identical argument as Theorem~\ref{thm:bi-lin-ss}
+The following theorem is proved via a nearly identical argument as Theorem~\ref{thm:bi-lin-ss}.
 
@@
 \subsection{Garbled Bloom Filter}
-\begin{figure}
+\begin{figure}[tp]
 \centering
@@
 
-\begin{figure}[t]
+\begin{figure}[tp]
 \centering

### 2016-09-30 ds-correctness.tex
cheers

--- 2016-09-30 Theorem2_FP.tex
@@
 
-\begin{proof}[\Cref{thm2}]
+\begin{proof}[Theorem~\ref{thm:xxx}]
+\fixme{Animesh: remove these Cref things and replace with references
+  like I have them in the text.}
 We use a game playing argument (shown in \Cref{fig:2TGame}) similar to \Cref{thm1} to prove this theorem.
@@
 %\caption{Game playing argument}\label{fig:Game}
-\begin{figure}
+\begin{figure}[tp]
 \fpage{.9}{
@@
 \caption{\Cref{thm2}: Game playing argument}\label{fig:2TGame}
+\fixme{Animesh: remove Crefs, fix captions to look like the classical
+  BF games captions}
 \end{figure}
@@
 }
-\caption{\Cref{thm2}: PRF adversary $B$ simulating $\game{1}(A)$ and $\game{2}(A)$} \label{fig:2TD}
+\caption{\Cref{thm2}: PRF adversary $B$ simulating $\game{1}(A)$ and
+  $\game{2}(A)$} \label{fig:2TD}
+\fixme{Animesh: remove Crefs, make caption refer to correct theorem}
 \end{figure}

### 2016-09-30 results.tex
cheers

@@
 always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
-rate of convergence is faster than~$1/n$.   As before, the multiplicative term $\dbinom{q}{r}$ arises when switching from the adaptive to zero-query settings.
+rate of convergence is faster than~$1/n$.   As before, the multiplicative term $\binom{q}{r}$ arises when switching from the adaptive to zero-query settings.
 \input{ds-correctness}
@@
 rate of convergence is faster than~$1/n$.   
-the multiplicative term $\dbinom{q}{r}$ arises when switching from the adaptive to zero-query settings.
+the multiplicative term $\binom{q}{r}$ arises when switching from the adaptive to zero-query settings.
 \input{lin-correctness}

### 2016-09-30 results.tex
cheers

@@
 \end{theorem}
+\fixme{This result is pretty intutitive following the classic BF correctness result. Probably fine to just explain it and push an appendix, or even drop from camera ready if out of space.}
 We note that Kirsch and Mitzenmacher~\cite{xxx} show

### 2016-09-30 TheoremGBF_correctness_privM.tex
cheers

@@
 %\end{theorem}
-\begin{proof}[\Cref{thm:gbf-correctness-privM}]
+\begin{proof}[Theorem~\ref{thm:gbf-correctness-privM}]
 We use a game playing argument to prove this theorem.
 Here, $\Rep$, $\Qry$ and $A$ are given access to $\Hash$ which uses lazy sampling to mimic a RO.
-$\game{0}$, exactly simulates the correctness game of a garbled Bloom filter for private $M$.
-Assuming $A$ does not make any pointless queries, the $\Hash$ returns random values sampled from $[m]$ in $\game{1}$.
+Game $\game{0}$ exactly simulates the correctness game of a private-$M$ garbled Bloom filter in the ROM.
+\tsnote{No, the hash oracle is different because it returns~$k$ values at once.}
+
+Game~$\game{1}$ is equivalent to game~$\game{0}$ under the assumption that~$A$ does not make any pointless random-oracle queries, the $\Hash$ returns random values sampled from $[m]$ in $\game{1}$.
 In order to account for queries to RO in $\Test$, the latter returns the $k$ hash values for each query along with the answer.
 It should be noted that the $\Qry$ oracle returns xor of shares at $k$ random positions in this game.
+\tsnote{No, $\Qry$ just returns the answer~$a$.}
 
@@
 {
-\underline{\game{0}(A)}\\
+\underline{$\game{0}(A)$}\\
 $S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
@@
 $\calC \gets \calC \cup x$\\
-$(h_1,\ldots,h_k \getsr [m]$\\
 $a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
@@
 \nudge $\err \gets \err + 1$\\
+$h_1,\ldots,h_k \gets \HashOracle(\qry_x)$\\
 Return~$a, h_1,\ldots,h_k $\\
@@
 \oracle{$\HashOracle(\qry_y)$}\\
-$(v_1,\ldots,v_k \getsr [m]$\\
+$v_1,\ldots,v_k \getsr [m]$\\
 Ret $\left(v_1,\ldots,v_k\right)$

### 2016-09-30 GBF-correctness-private-M.tex
adding new proof of correctness for private-M GBF in the ROM

--- 2016-09-30 BF_correctness.tex
@@
 \begin{figure}[tp]
-\fpage{.9}{
-\hpagessl{.45}{.5}
+\fpage{.95}{
+\hpagessl{.5}{.5}
 {
-\underline{\game{0}(A)}\\
+\underline{$\game{0}(A)$}\\
 $S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
@@
 Return 1\\
-%
+
 \oracle{$\TestOracle(\qry_x)$}\\
@@
 Return~$a$\\
-%
+
 \oracle{$\HashOracle(i,\qry_y)$}\\
@@
 Return 1\\
-%
+
 \oracle{$\TestOracle(\qry_x)$}\\
 if $x \in \mathcal{C}$ then Return $\bot$\\
-$\calC \gets \calC \cup x$; $M \gets\pubaux$\\
+$\calC \gets \calC \cup x$; $M \gets\privaux$\\
 for $j \in \{1,2,\ldots,k\}$\\
 \nudge $h_j \gets \HashOracle(j, x)$\\
-\nudge if $M[h_j] \neq 1$ then Return 0\\
+$x' \gets M[h_1] \xor M[h_2] \xor \ldots \xor M[h_k]$\\
+if $x' \neq x$ then Return 0\\
 $\err \gets \err + 1$\\
 Return 1\\
-%
+
 \oracle{$\HashOracle(i,\qry_y)$}\\
@@
 }
-\fpage{.9}{
-\hpagessl{.45}{.5}
+\fpage{.95}{
+\hpagessl{.5}{.5}
 {
@@
 Return 1\\
-%
+
 \oracle{$\TestOracle(\qry_x)$}\\
 if $x \in \mathcal{C}$ then Return $\bot$\\
-$\calC \gets \calC \cup x$; $M \gets\pubaux$\\
+$\calC \gets \calC \cup x$; $M \gets\privaux$\\
 for $j \in \{1,2,\ldots,k\}$\\
 \nudge $h_j \gets \HashOracle(j, x)$\\
-\nudge if $M[h_j] \neq 1$\\
-\nudge \nudge Return $(0, (h_1, \ldots, h_j))$\\
-$\err \gets \err +1$\\
-Return~$(1, (h_1, \ldots, h_{k}) )$\\
-%
+$x' \gets M[h_1] \xor M[h_2] \xor \ldots \xor M[h_k]$\\
+if $x' \neq x$ then Return $(0, (h_1, \ldots, h_j))$ \\
+$\err \gets \err + 1$\\
+Return $(1, (h_1, \ldots, h_{k}) )$ \\
+
 \oracle{$\HashOracle(i,\qry_y)$}\\
@@
 Return 1\\
-%
+
 \oracle{$\TestOracle(\qry_x)$}\\
 if $x \in \mathcal{C}$ then Return $\bot$\\
-$\calC \gets \calC \cup x$; $M \gets\pubaux$\\
+$\calC \gets \calC \cup x$; $M \gets\privaux$\\
 $(h_1, \ldots, h_{k}) \gets \HashOracle(x)$\\
-for $j \in \{1,2,\ldots,k\}$\\
-\nudge if $M[h_j] \neq 1$ then \\
-\nudge \nudge Return~$(0, (h_1, \ldots, h_{k}) )$\\
-$\err \gets \err +1$\\
-Return~$(1, (h_1, \ldots, h_{k}) )$\\
-%
+$x' \gets M[h_1] \xor M[h_2] \xor \ldots \xor M[h_k]$\\
+if $x' \neq x$ then Return $(0, (h_1, \ldots, h_j))$ \\
+$\err \gets \err + 1$\\
+Return $(1, (h_1, \ldots, h_{k}) )$ \\
+
 \oracle{$\HashOracle(\qry_y)$}\\
@@
 }
-\caption{\ref{thm:bf-correctness}: Game playing argument}
-\label{fig:bf-correctness-games1}
+\caption{Games $\game{0}$-$\game{3}$ for the
+proof of Theorem~\ref{thm:gbf-correctness}.}
+\label{fig:gbf-correctness-games1}
 \end{figure}
 \begin{figure}[tp]
-\fpage{.9}{
-\hpagessl{.45}{.5}
+\fpage{.95}{
+\hpagessl{.4}{.5}
 {
 \underline{\game{4}(A)\fbox{\game{5}(A)}}\\
-$c\gets 0$, $\bad \gets \false$, $\err \gets 0$;  $\calC \gets \emptyset$\\
-$S \getsr A$; $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
+$c\gets 0$, $\bad \gets \false$\\
+$\err \gets 0$;  $\calC \gets \emptyset$\\
+$S \getsr A$\\
+$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
 $(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
@@
 Return $\Ans[x]$\\
-%
+
 }
@@
 %
-$M \gets\pubaux$\\
-for $j \in \{1,2,\ldots,k\}$\\
-\nudge if $M[v_j] \neq 1$ then \\
-\nudge \nudge $\Ans[y] \gets (0, (v_1, \ldots, v_{k}) )$\\
-\nudge \nudge if $c \in \calI$ then $\bad \gets \true$\\
-\nudge \nudge $\Break$\\
-if $j < k$ then Return $\left(v_1,\ldots,v_k\right)$\\
+$M \gets\privaux$\\
+$y' \gets M[v_1] \xor M[v_2] \xor \ldots \xor M[v_k]$\\
+if $y' \neq y$ then \\
+\nudge $\Ans[y] \gets (0, (v_1, \ldots, v_{k}) )$\\
+\nudge if $c \in \calI$ then $\bad \gets \true$\\
+\nudge Return $\left(v_1,\ldots,v_k\right)$\\
 if $c \notin \calI$ then $\bad \gets \true$\\
@@
 }
-\caption{\ref{thm:bf-correctness}: $\game{4}$ and $\game{5}$ of game
-  playing argument}
-\label{fig:bf-correctness-games2}
+\caption{Games $\game{4}$-$\game{5}$ for the
+proof of Theorem~\ref{thm:gbf-correctness}.}
+\label{fig:gbf-correctness-games2}
 \end{figure}

### 2016-09-30 GBF-correctness-private-M.tex
added note for Jon about RO usage in the correctness game

@@
 %\label{sec:thm3_fp}
-\begin{proof}[Theorem~\ref{thm:bf-correctness}]
-We use a game playing argument, please refer to Figures~\ref{fig:bf-correctness-games1} and~\ref{fig:bf-correctness-games2}.
-In $\game{0}$, the $\Hash$ does lazy sampling of elements from $[m]$ to mimic a random oracle(RO).
+\begin{proof}[Theorem~\ref{thm:gbf-correctness}]
+We use a game playing argument, please refer to Figures~\ref{fig:gbf-correctness-games1} and~\ref{gfig:bf-correctness-games2}.
+In game $\game{0}$, the $\Hash$ oracle performs lazy sampling of elements from $[m]$ to mimic a random oracle (RO).
 For every distinct query, $\Hash$ returns a random value sampled from $[m]$.
-Here, the adversary $A$, along with $\Rep$ and $\Qry$ are given access to $\Hash$.
-It can be seen that, $\game{0}$ exactly simulates the correctness game of $\setprim_{\mathrm{Bloom}}$.
-So, $\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} = \Prob{\game{0}(A) = 1}$.
+It can be seen that, game $\game{0}$ exactly simulates the correctness game of $\setprim_{\mathrm{gbf}}$.
+So, $\AdvCorrect{\setprim_{\mathrm{gbf}},r}{A} = \Prob{\game{0}(A) = 1}$.
 
-$\game{1}$ is exactly same as $\game{0}$ except the $\Qry$ oracle is replaced by the code of $\Qry$, whereas in $\game{2}$, the $\Test$ oracle returns the hash values back to the adversary along with output of the $\Qry$ oracle.
-$\game{3}$ on the other hand, returns all the $k$ hash values for any query.
-This results in adversary getting $(k-1)$ hash values for free as we charge the adversary for a single query.
-Since $k$ is likely to be very small compared to the number of queries the adversary makes, this would not affect the analysis in any significant manner.
-Also, in real world, RO will be a hash function; hence the adversary can perform local computations to get the hash values.
-It can be easily seen that the output of all the games will be same.
-So, $\Prob{\game{0}(A) = 1} = \Prob{\game{1}(A) = 1} = \Prob{\game{2}(A) = 1} = \Prob{\game{3}(A) = 1}$.
+Game $\game{1}$ is exactly same as game $\game{0}$ except the $\Qry$ call (inside the $\TestOracle$ oracle) is replaced by the code of $\Qry$.
+Hence, $\Prob{\game{0}(A) = 1} = \Prob{\game{1}(A) = 1}$.
+
+In game $\game{2}$, the $\Test$ oracle is altered to return the hash values~$h_1,h_2,\ldots, h_k$ in addition to the result of executing the code of $\Qry$.
+As this only provides additional information to the adversary, $\Prob{\game{1}(A) = 1} \leq \Prob{\game{2}(A) = 1}$.
+
+In $\game{3}$, we modify the $\HashOracle$ oracle so that on query~$\qry_x$ it returns all of the~$k$ values that previously would have required calls $\HashOracle(1,\qry_y),\HashOracle(2,\qry_y),\ldots,\HashOracle(k,\qry_y)$.
+This results in adversary getting $(k-1)$ hash values ``for free'', as we charge the adversary only for a single query.
+We alter the $\TestOracle$ oracle accordingly, so that it makes a single call $\Hash(\qry_x)$ rather than~$k$ such calls.
+
+%tom here
 
@@
 \[
-\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\AdvCorrect{\setprim_{\mathrm{gbf}},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
 \]
@@
 $(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
-$\bot \getsr A^{\TestOracle}(\pubaux)$\\
+$\bot \getsr A^{\TestOracle,\HashOracle}(\pubaux)$\\
 if $\err  < r$ then Return 0\\
@@
 $\calC \gets \calC \cup x$\\
-$a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
+$a \gets \Qry^{\HashOracle,\HashOracle}(\pubaux,\privaux, x)$\\
 if $a \neq \qry_x(S)$ then \\
@@
 for $j \in \{1,2,\ldots,k\}$\\
-\nudge $h_j \gets \HashOracle(j, x)$\\
+\nudge $h_j \gets \HashOracle(j, \qry_x)$\\
 $x' \gets M[h_1] \xor M[h_2] \xor \ldots \xor M[h_k]$\\
@@
 $\calC \gets \calC \cup x$; $M \gets\privaux$\\
-$(h_1, \ldots, h_{k}) \gets \HashOracle(x)$\\
+$(h_1, \ldots, h_{k}) \gets \HashOracle(\qry_x)$\\
 $x' \gets M[h_1] \xor M[h_2] \xor \ldots \xor M[h_k]$\\
@@
 if $\Ans[x] \neq \undefined$\\
-\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(x)$\\
+\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(\qry_x)$\\
 Return $\Ans[x]$\\

### 2016-09-30 notions.tex
fixing linebreaks and other cleaning
added note for Jon about RO usage in the correctness game

@@
 adversarial) notion of correctness.
-In addition to correctness, we establish notions of privacy for
-set-multiplicity data structures.
+In addition to correctness, we establish notions of privacy for data structures.
 
-\fixme{Do we say that all notions can be extended to the ROM by giving
-all all algorithms to a RO~$H$?  Is this true for the SS-privacy
-notion?  (It seems to make sense elsewhere.)} \jnote{I think there are subtleties for the SS notion.}
+%\fixme{Do we say that all notions can be extended to the ROM by giving
+%all all algorithms to a RO~$H$?  Is this true for the SS-privacy
+%notion?  (It seems to make sense elsewhere.)} \jnote{I think there are subtleties for the SS notion.}
 
@@
 all algorithms (namely, $\Rep,\Qry$, and the adversary~$A$) with access to the
-random oracle.
+random oracle. \fixme{I think we should *not* allow $S$ to depend on
+  the RO.  That's like letting $S$ depend on $\pub$ in the standard
+  model, but $\pub$ hasn't been fixed yet.  }
 
@@
 semantically secure with respect to leakage consisting of the size of the set.
-\jnote{Need notation for the advantage in the PRF experiment.}
+\jnote{Need notation for the advantage in the PRF
+  experiment.}\tsnote{Currently typeset in an appendix}
 

### 2016-09-30 notions.tex
citations

@@
 
-\begin{theorem}
+\begin{theorem}\label{thm:priv-ss}
 Let $\setprim=(\Rep, \Qry)$ be a canonical data structure for which $\Rep$

### 2016-09-30 results.tex
starting to write ow proof for classic BF in rom
adding new proof of correctness for private-M GBF in the ROM
citations

--- 2016-09-30 results.tex
@@
   \univ \to \bits\}$ where $q_x(S)=1 \Leftrightarrow x \in S$.  }
-\label{fig:bf-and-lin}
+\label{fig:bf-and-ds}
 \end{figure}
@@
 (\Rep, \Qry)$ over~$\elts$ is defined as in
-Figure~\ref{fig:bf-and-lin} (left side).  We
+Figure~\ref{fig:bf-and-ds} (left side).  We
 define~$\setprim_{\mathrm{Bloom}}$ in the random-oracle model
@@
 \end{theorem}
-We note that Kirsch and Mitzenmacher~\cite{xxx} show
+We note that Kirsch and Mitzenmacher~\cite{kirsch2006less} show
 that the ($r=1$, zero-query) error-probability for~$\setprim_\mathrm{Bloom}$ is
@@
 \todo{Typeset simple proof.  Result is on chalkboard.}
+\begin{proof}
+\begin{figure}[tp]
+\hfpagess{.45}{.45}
+{\underline{\game{0}($A$)}\\
+$S \getsr \distr{}{}$\\
+$(\pubaux,\privaux) \getsr \Rep(S)$\\
+$z \getsr A(\pubaux)$\\
+if $z \in S$ then return 1\\
+return 0\\
+
+\medskip
+\oracle{$\HashOracle(\qry_x)$}\\
+}
+{
+}
+\end{figure}
+\end{proof}
 
@@
 Let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-membership data
-structure defined on the right-side of Figure~\ref{fig:lin-and-ds}.
+structure defined on the right-side of Figure~\ref{fig:bf-and-ds}.
 As with the preceding theorem, the following says (informally) that
@@
 \begin{theorem}[{\rm Correctness of DS-PRF}]\label{thm2}\label{thm:ds-correctness}
-Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-membership data structure (over~$\elts$) in Figure~\ref{fig:lin-and-ds}.
+Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-membership data structure (over~$\elts$) in Figure~\ref{fig:bf-and-ds}.
 For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exists a prf-adversary ~$B$ (explicitly constructed in the proof of this theorem) such that
@@
 \end{theorem}
-We note that Kirsch and Mitzenmacher~\cite{xxx} show
+\fixme{This result is pretty intutitive following the classic BF correctness result. Probably fine to just explain it and push an appendix, or even drop from camera ready if out of space.}
+We note that Kirsch and Mitzenmacher~\cite{kirsch2006less} show
 that the ($r=1$, zero-query) error-probability for~$\setprim_\mathrm{ds}$ is
@@
 \heading{Privacy. }
-The privacy of $\setprim_{\mathrm{ds}}$ follows directly from our general result, Theorem~\ref{thm:xxx}.
+The privacy of $\setprim_{\mathrm{ds}}$ follows directly from our general result, Theorem~\ref{thm:priv-ss}.
 \begin{theorem}[\rm{SS-privacy of DS PRF}]\label{thm:ds-ss}
-Fix $k,m,n>0$, a set~$\elts$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-membership data structure described in Figure~\ref{fig:lin-and-ds}.
+Fix $k,m,n>0$, a set~$\elts$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-membership data structure described in Figure~\ref{fig:bf-and-ds}.
 For any set~$S \in 2^\elts$, let $\leak(S)=|S|$.
@@
 \begin{proof}
-It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
+It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:priv-ss}.
 On input a set of distinct elements $S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, \ldots, s_k\langle k,x_1\rangle, s_{k+1}=\langle 1,x_2\rangle, \ldots,\linebreak s_{2k}=\langle k,x_2\rangle, \ldots ,s_{kn+1}=\langle 1,x_n\rangle, \ldots, s_{kn}=\langle k,x_n \rangle$.
@@
 The domain-separated PRF-hash requires~$k$ PRF evaluations per set-membership query, and this may be unattractive in certain use cases.
-Kirsch and Mitzenmacher~\cite{xxx} have shown that two PRF evaluations suffices, defining the hash functions to be $h_i(x)=F_K(\langle 1,x \rangle) + j\cdot F_K(\langle 2,x \rangle) \bmod m$, where~$m$ is the bitlength of the Bloom filter.\footnote{Actually, they define $h_i(x)=F_{K_1}(x)  + j\cdot F_{K_2}(x) \bmod m$, using distinct keys instead of domain-separation, but the constructions are equivalent with respect to security.} We call this the \emph{linear PRF-hash} Bloom Filter.
+Kirsch and Mitzenmacher~\cite{kirsch2006less} have shown that two PRF evaluations suffices, defining the hash functions to be $h_i(x)=F_K(\langle 1,x \rangle) + j\cdot F_K(\langle 2,x \rangle) \bmod m$, where~$m$ is the bitlength of the Bloom filter.\footnote{Actually, they define $h_i(x)=F_{K_1}(x)  + j\cdot F_{K_2}(x) \bmod m$, using distinct keys instead of domain-separation, but the constructions are equivalent with respect to security.} We call this the \emph{linear PRF-hash} Bloom Filter.
 In this section, we show that this scheme is both correct and private with respect to our SS notion.
 
-Looking ahead to the next section, we will analyze a closely related construction, which was attacked by Niedermeyer et al.~\cite{xxx} in the context of private medical-record linkage.
+Looking ahead to the next section, we will analyze a closely related construction, which was attacked by Niedermeyer et al.~\cite{niedermeyer2014cryptanalysis} in the context of private medical-record linkage.
 It uses the same linear-PRF hash functions, but has a $\Rep$ algorithm that that does not ensure that the hash functions are called on \emph{distinct} values.
@@
 For now, let $n,k,m \geq 0$.
-Then $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ is defined as in Figure~\ref{fig:lin-and-ds} (left side).
+Then $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ is defined as in Figure~\ref{fig:lin-and-bi-lin} (left side).
 The following result shows, informally, that if~$F$ is a good PRF, then $\setprim_{\mathrm{lin}}$ is correct against adaptive error-finding adversaries.
@@
 \begin{theorem}[{\rm Correctness of linear-PRF}]\label{thm1}\label{thm:lin-correctness}
-Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-membership data structure (over~$\elts$) described in Figure~\ref{fig:lin-and-bin-lin}.
+Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-membership data structure (over~$\elts$) described in Figure~\ref{fig:lin-and-bi-lin}.
 For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exist prf-adversaries~$B_1,B_2$ (explicitly constructed in the proof of this theorem) such that
@@
 \end{theorem}
-Again, Kirsch and Mitzenmacher~\cite{xxx} show
+Again, Kirsch and Mitzenmacher~\cite{kirsch2006less} show
 that the ($r=1$, zero-query) error-probability for~$\setprim_\mathrm{lin}$ is
@@
 \heading{Privacy. }
-The SS-privacy of the linear-PRF hash construction follows directly from~Theorem~\ref{thm:xxx}.
+The SS-privacy of the linear-PRF hash construction follows directly from~Theorem~\ref{thm:priv-ss}.
 \begin{theorem}[{\rm SS-privacy of linear-PRF}]\label{thm:lin-privacy}
-Fix $k,m,n,r>0$, a set $\elts$, and let $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-membership data structure (over~$\elts$) described in Figure~\ref{fig:lin-and-bin-lin}.
+Fix $k,m,n,r>0$, a set $\elts$, and let $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-membership data structure (over~$\elts$) described in Figure~\ref{fig:lin-and-bi-lin}.
 For any set~$S \in 2^{\elts}$, let $\leak(S)=|S|$.
@@
 \begin{proof}
-It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
+It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:priv-ss}.
 On input a set of distinct elements
@@
 Consider the set-membership data structure given in Figure~\ref{fig:lin-and-bi-lin} (right side), which we call the \emph{bigram linear-PRF} construction.
-This construction is of practical interest, as it has been suggested as a way to address the privacy-preserving record-linkage problem, in particular for linking common records in medical databases~\cite{neidermayer,xxx}.
+This construction is of practical interest, as it has been suggested as a way to address the privacy-preserving record-linkage problem, in particular for linking common records in medical databases~\cite{niedermeyer2014cryptanalysis,schnell2011novel}.
 We only address the privacy of this construction, as the correctness follows immediately from the correctness of the Linear-PRF contruction.
@@
 We note that Niedermeyer et al.
-in~\cite{xxx} suggest replacing the linear-PRF hash functions in the previous construction with independently keyed PRFs as a countermeasure to their attack.
+in~\cite{niedermeyer2014cryptanalysis} suggest replacing the linear-PRF hash functions in the previous construction with independently keyed PRFs as a countermeasure to their attack.
 In terms of SS-privacy, however, this change offers no help.
@@
 \begin{theorem}[{\rm SS-privacy of bigram DS PRF-hash}]\label{thm:bi-ds-ss}
-Let $\setprim_{\bilin}= (\Rep, \Qry)$ be the set-membership data structure described in Figure~\ref{fig:niedermeyer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.
+Let $\setprim_{\bilin}= (\Rep, \Qry)$ be the set-membership data structure described in Figure~\ref{fig:lin-and-bi-lin}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.
 Let $\leak$ be the leakage function described just prior to Theorem~\ref{thm:bi-lin-ss}.
@@
 \end{figure}
-Dong, Chen and Wen~\cite{xxx} introduce a set-membership data
+Dong, Chen and Wen~\cite{dong2013private} introduce a set-membership data
 structure called a \emph{garbled Bloom filter} (GBF).   Modulo some implementation
@@
 
-In~\cite{xxx} the GBF is a central piece of a private set-intersection
+In~\cite{dong2013private} the GBF is a central piece of a private set-intersection
 scheme, in which the client computes a classical BF over its
@@
 \heading{Correctness.}
-We note that~\cite{xxx} provides error-rate analysis, i.e., the
+We note that~\cite{dong2013private} provides error-rate analysis, i.e., the
 probability of finding a single false-positive in a non-adaptive
@@
 $\binom{m}{k} \approx m^k$ $k$-tuples of positions.  If both~$m$
-and~$k$ are large this is infeasible.  In~\cite{xxx} they suggest to
+and~$k$ are large this is infeasible.  In~\cite{dong2013private} they suggest to
 set~$k=\lambda$, and test with $\lambda=80$.  Making 80 hash calls per
@@
 filter, $m=1000$, and a 100-element set, $n=100$,  and $k=4$ hash
-functions (a la Squid\cite{squid}).  This results in a false-positive rate of
+functions (a la Squid\cite{fan2000summary}).  This results in a false-positive rate of
 approximately 1\% in a classical BF.  There are roughly $2^{35}$
@@
 
-\begin{theorem}[{\rm Correctness of private-$M$ GBF in the ROM}]\fixme{FINISH! (Animesh?)}
+\begin{theorem}[{\rm Correctness of private-$M$ GBF in the ROM}]\fixme{FINISH! (Animesh?)}\label{thm:gbf-correctness}
 Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the private-$M$ garbled Bloom filter.
@@
 
-If instantiated with hash functions $H_j(x) = F_K(\langle j,x \rangle)$ and $\privaux = \langle K \rangle$, the SS-privacy of the GBF follows directly from~Theorem~\ref{thm:xxx}.
+If instantiated with hash functions $H_j(x) = F_K(\langle j,x \rangle)$ and $\privaux = \langle K \rangle$, the SS-privacy of the GBF follows directly from~Theorem~\ref{thm:priv-ss}.
 \begin{theorem}[{\rm SS-privacy of GBF with secret hash functions}]

### 2016-09-30 results.tex
no message

--- 2016-09-30 results.tex
@@
 \begin{theorem}\label{thm3}\label{thm:bf-correctness}
-Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be classical Bloom filter (set-membership) data structure over~$\elts$.
-For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
+Fix $k,m,n,r>0$ and a set~$\elts$, and let
+$\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be the classical Bloom
+filter (set-membership) data structure over~$\elts$. For any
+adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$
+oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
 \[
@@
 
-\subsection{Domain-separated PRF-Hash}
+\subsection{Domain-Separated PRF-Hash}
+\jnote{Give English-language description of scheme before turning to
+analysis of correctness.}
+
 %\heading{Construction of PRF with domain separation.}
-\heading{Correctness. }
-Let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-membership data
-structure defined on the right-side of Figure~\ref{fig:lin-and-ds}.
-As with the preceding theorem, the following says (informally) that
-if~$F$ is a secure PRF, then this domain-separated PRF construction is
-correct against adaptive adversaries.
+\heading{Correctness. } Let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$
+be the set-membership data structure defined on the right-side of
+Figure~\ref{fig:lin-and-ds}. As in the preceding theorem, the
+following says (informally) that if~$F$ is a secure PRF, then this
+domain-separated PRF construction is correct against adaptive
+adversaries.
 % \tsnote{Not really appropriate to say this next thing; I'll add a new section that addresses bigram DS-PRF hash.}
@@
 \begin{theorem}[{\rm SS-privacy of bigram linear-PRF}]\label{thm:bi-lin-ss}
-Let $\setprim_{\bilin}= (\Rep, \Qry)$ be the set-membership data structure described in Figure~\ref{fig:neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.
-Let $\leak_{\mathsf{abl}}$ be the leakage function just described.
-Let~$\elts=\{\mathrm{a,b,c}\}^*$.
-Let $n=3$,  $m=3\alpha $ for integer $\alpha >> 1$, and let, $k = \lceil \ln(2) \alpha \rceil$.\tsnote{This value of~$k$ is from the classical analysis for minimizing the FP rate for a Bloom filter, and is set this way for compatibility with classical results.
-It isn't used in any essential way in the proof sketch.}  Let~$A$ be the adversary in Figure~\ref{fig:adv-bi-lin-ss}.
-Then for any simulator $\Sim$, the advantage $\AdvPrivSS{\setprim_{\bilin},\leak_{\mathsf{abl}}}{A,\Sim}$ can be made arbitrarily close to $1/2$ by choice of~$\alpha$.
+Let $\setprim_{\bilin}= (\Rep, \Qry)$ be the set-membership data
+structure described in Figure~\ref{fig:neidermayer}, but with
+$F_{K}$ replaced by a random function~$\rho$. Let
+$\leak_{\mathsf{abl}}$ be the leakage function just described.
+Let~$\elts=\{\mathrm{a,b,c}\}^*$. Let $n=3$,  $m=3\alpha $ for
+integer $\alpha >> 1$, and let, $k = \lceil \ln(2) \alpha
+\rceil$.\tsnote{This value of~$k$ is from the classical analysis for
+minimizing the FP rate for a Bloom filter, and is set this way for
+compatibility with classical results.  It isn't used in any
+essential way in the proof sketch.}  Let~$A$ be the adversary in
+Figure~\ref{fig:adv-bi-lin-ss}.  Then for any simulator $\Sim$, the
+advantage
+$\AdvPrivSS{\setprim_{\bilin},\leak_{\mathsf{abl}}}{A,\Sim}$ can be
+made arbitrarily close to $1/2$ by choice of~$\alpha$.
 \end{theorem}

### 2016-09-30 results.tex

--- 2016-09-30 results.tex
@@
 
-\subsection{Domain-separated PRF-Hash}
+\subsection{Domain-Separated PRF-Hash}
+\jnote{Give English-language description of scheme before turning to
+analysis of correctness.}
+
 %\heading{Construction of PRF with domain separation.}
-\heading{Correctness. }
-Let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-membership data
-structure defined on the right-side of Figure~\ref{fig:bf-and-ds}.
-As with the preceding theorem, the following says (informally) that
-if~$F$ is a secure PRF, then this domain-separated PRF construction is
-correct against adaptive adversaries.
+\heading{Correctness. } Let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$
+be the set-membership data structure defined on the right-hand side
+of Figure~\ref{fig:lin-and-ds}. As in the preceding theorem, the
+following says (informally) that if~$F$ is a secure PRF, then this
+domain-separated PRF construction is correct against adaptive
+adversaries.
+
 % \tsnote{Not really appropriate to say this next thing; I'll add a new section that addresses bigram DS-PRF hash.}

### 2016-09-30 GBF-correctness-private-M.tex
changes to GBF and BF

@@
 
-In $\game{3}$, we modify the $\HashOracle$ oracle so that on query~$\qry_x$ it returns all of the~$k$ values that previously would have required calls $\HashOracle(1,\qry_y),\HashOracle(2,\qry_y),\ldots,\HashOracle(k,\qry_y)$.
+In $\game{3}$, we modify the $\HashOracle$ oracle so that on query~$\qry_x$ it returns all of the~$k$ values that previously would have required calls $\HashOracle(1,\qry_y),\HashOracle(2,\qry_y),\ldots,\linebreak\HashOracle(k,\qry_y)$.
 This results in adversary getting $(k-1)$ hash values ``for free'', as we charge the adversary only for a single query.
 We alter the $\TestOracle$ oracle accordingly, so that it makes a single call $\Hash(\qry_x)$ rather than~$k$ such calls.
+We do this so that we can assume that a call~$\HashOracle(\qry_x)$ is pointless after a~$\TestOracle(\qry_x)$ call, and this will aid us in subsequent games.
+\fixme{for BF proof, this actually does more, it makes a hash query as good as a test query, because~$M$ is public.}  Thus, $\Prob{\game{2}(A) = 1} \leq \Prob{\game{3}(A) = 1}$.
 
 %tom here
+Game~$\game{4}$ contains some important changes from game~$\game{3}$, but we will argue that $\Prob{\game{3}(A) = 1} \leq \Prob{\game{4}(A) = 1}$.
+To begin, in game~$\game{4}$ we sample an $r$-subset of indices from~$\{1,2,\ldots,q_H+q_T\}$.
+(We will see why, shortly.)  Next, the $\TestOracle$ oracle on input~$\qry_x$ no longer computes its answer directly, but instead refers to a new table~$\mathrm{Ans}[x]$ which is populated upon calls to the $\HashOracle$ oracle.
+In particular, if $\mathrm{Ans}[x]$ is undefined, $\TestOracle$ makes a $\HashOracle(\qry_x)$ call; otherwise, it returns the contents of~$\mathrm{Ans}[x]$, which contains exactly the values that~$\TestOracle(\qry_x)$ would have returned in the previous game.
+The $\HashOracle$ oracle, on input~$\qry_y$ computes the random values~$v_1,v_2,\ldots,v_k$ as in $\game{3}$.
+We no longer need to maintain the table~$T$ because hash values are only determined by~$\HashOracle$ calls.
 
@@
 $S \getsr A$\\
-$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
+$\mathcal{I}\getsr [\{1,2,\ldots,q_T + q_H\}]^r$\\
 $(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
@@
 $\calC \gets \calC \cup x$\\
-if $\Ans[x] \neq \undefined$\\
+if $\Ans[x] = \undefined$\\
 \nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(\qry_x)$\\

### 2016-09-30 lin-correctness.tex
cheers
lin correctness proof fixes

@@
 %F_{K}(\langle 1,x \rangle) + j\cdot F_{K}(\langle 2,x \rangle) \bmod m
-\begin{proof}[Theorem~\ref{thm:xxx}]
-The proof of the theorem will use a game playing argument as shown in \Cref{fig:Game}.
+\begin{proof}[Theorem~\ref{thm:lin-correctness}]
+The proof of the theorem will use a game playing argument as shown in  Figure~\ref{fig:lin-correctness-games}.
 $\game{0}(A)$ exactly simulates $\ExpCorrect{\setprim_\mathrm{lin},r}{A}$ with hash functions $h_j(x) =  F_{K}(\langle 1,x \rangle) + j\cdot F_{K}(\langle 2,x \rangle) \bmod m$.
@@
 
-%\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
+%\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:lin-correctness-adv}
 \begin{figure}[tp]
@@
 }
-\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively}\label{fig:BGame1}
+\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively for the
+proof of Theorem~\ref{thm:lin-correctness}.}\label{fig:lin-correctness-adv}
 \fixme{fix caption and Crefs}
@@
 
-The PRF security notion is shown in \Cref{fig:prf}. Let
-prf-adversaries $B_1, B_2$ be as shown in \Cref{fig:BGame1}.
+The PRF security notion is shown in Figure~\ref{fig:prf}. Let
+prf-adversaries $B_1, B_2$ be as shown in Figure~\ref{fig:lin-correctness-adv}.
 Adversary~$B_1$ is constructed so that, if its challenge bit~$b=1$,
@@
 We note that $\game{3}$ and $\game{4}$ are
-``identical-untill-$\bad$''~\cite{BeRo-gameplaying}.  In particular,
+``identical-untill-$\bad$''~\cite{bellare2004game}.  In particular,
 in $\game{4}$, $A$ returns 0 when $\game{3}$ would have returned 1 (i.e.,
@@
 Thus $\bad$ remains $\false$ after~$A$ halts with probability
-$1/\dbinom{q}{r}$, and we have 
+$1/\binom{q}{r}$, and we have 
 \begin{equation*}
@@
 So, if $\game{4}(A)=1$, then there is a zero-query adversary~$D$ that finds~$r$ false positives against $\tilde{\setprim}_{\mathrm{lin}}$, which is $\setprim_{\mathrm{lin}}$ but with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$, respectively.
-We give this~$D$ in \Cref{fig:D}.
+We give this~$D$ in Figure~\ref{fig:lin-correctness-zq-adv}.
 Intuitively, adversary~$D$ guesses which~$r$ of~$A$'s queries will be false positives; it simulates the~$\Test$ oracle by returning 1 on the guessed queries, and 0 otherwise; and it halts after finding $r$ FP's.
@@
 Note that $\tilde{\setprim}_{\mathrm{lin}}$ is the scheme that is analyzed in the classical Bloom filter literature ---the hash functions are modeled as independent random functions, and the parameters $k,m,n$  are set to achieve a target maximum false-positive probability (or rate).
-Kirsch and Mitzenmacher~\cite{KM} show that the upperbound on false-positive probability for a zero-query adversary and $r=1$ is $\left( (1-e^{-kn/m})^k + O(1/n) \right)$.
+Kirsch and Mitzenmacher~\cite{kirsch2006less} show that the upperbound on false-positive probability for a zero-query adversary and $r=1$ is $\left( (1-e^{-kn/m})^k + O(1/n) \right)$.
 For $r>1$, we observe that~$A$'s queries $x_1,x_2,\ldots,x_q$ are distinct and not elements of the original set~$S$, since we assume no pointless queries.
@@
 }
-\caption{\Cref{thm1}: Game playing argument}\label{fig:Game}
+\caption{Games $\game{0}$-$\game{4}$ for the
+proof of Theorem~\ref{thm:lin-correctness}.}
+\label{fig:lin-correctness-games}
 \fixme{fix caption and Crefs}
@@
 }
-\caption{Zero-query adversary $D$} \label{fig:D}
+\caption{Zero-query adversary $D$ for Theorem~\ref{thm:lin-correctness}.} \label{fig:lin-correctness-zq-adv}
 \fixme{For what theorem?}

### 2016-09-30 BF_correctness.tex
cleaning up section 4
cheers
added note for Jon about RO usage in the correctness game
changes to GBF and BF
cleaning bf and gbf still

@@
 We use a game playing argument, please refer to Figures~\ref{fig:bf-correctness-games1} and~\ref{fig:bf-correctness-games2}.
-In $\game{0}$, the $\Hash$ does lazy sampling of elements from $[m]$ to mimic a random oracle(RO).
+In game $\game{0}$, the $\Hash$ oracle performs lazy sampling of elements from $[m]$ to mimic a random oracle (RO).
 For every distinct query, $\Hash$ returns a random value sampled from $[m]$.
-Here, the adversary $A$, along with $\Rep$ and $\Qry$ are given access to $\Hash$.
-It can be seen that, $\game{0}$ exactly simulates the correctness game of $\setprim_{\mathrm{Bloom}}$.
-So, $\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} = \Prob{\game{0}(A) = 1}$.
+It can be seen that, game $\game{0}$ exactly simulates the correctness game of $\setprim_{\mathrm{gbf}}$.
+So, $\AdvCorrect{\setprim_{\mathrm{gbf}},r}{A} = \Prob{\game{0}(A) = 1}$.
 
-$\game{1}$ is exactly same as $\game{0}$ except the $\Qry$ oracle is replaced by the code of $\Qry$, whereas in $\game{2}$, the $\Test$ oracle returns the hash values back to the adversary along with output of the $\Qry$ oracle.
-$\game{3}$ on the other hand, returns all the $k$ hash values for any query.
-This results in adversary getting $(k-1)$ hash values for free as we charge the adversary for a single query.
-Since $k$ is likely to be very small compared to the number of queries the adversary makes, this would not affect the analysis in any significant manner.
-Also, in real world, RO will be a hash function; hence the adversary can perform local computations to get the hash values.
-It can be easily seen that the output of all the games will be same.
-So, $\Prob{\game{0}(A) = 1} = \Prob{\game{1}(A) = 1} = \Prob{\game{2}(A) = 1} = \Prob{\game{3}(A) = 1}$.
+Game $\game{1}$ is exactly same as game $\game{0}$ except the $\Qry$ call (inside the $\TestOracle$ oracle) is replaced by the code of $\Qry$.
+Hence, $\Prob{\game{0}(A) = 1} = \Prob{\game{1}(A) = 1}$.
 
-In $\game{4}$, assuming $A$ does not make any pointless queries, $\Hash$ returns $k$ random values (for each query) sampled from $[m]$.
-Also, we offload all of $\Test$'s computations to $\Hash$, which now maintains an $\Ans$ table to compute and save answers for each query.
-For any query, $\qry$, the $\Test$ oracle returns answer stored at $\Ans[\qry]$.
-We also introduce the $\bad$ flag in this game.
-Like in the earlier proofs,  $\bad$ is set to true, if queries indexed by the r-set $\calI$ fail to be false positives, or the other queries are false-positives.
-$\bad$ in fact does not affect the output of $\Hash$ or the game.
-So, $\Prob{\game{4}(A) = 1} = \Prob{\game{3}(A) = 1}$.
+In game $\game{2}$, the $\Test$ oracle is altered to return the hash values~$h_1,h_2,\ldots, h_k$ in addition to the result of executing the code of $\Qry$.
+As this only provides additional information to the adversary, $\Prob{\game{1}(A) = 1} \leq \Prob{\game{2}(A) = 1}$.
 
-$\game{5}$ is exactly same as $\game{4}$, but returns 0, if $\bad$ is set to true.
-It can be observed that, the total queries made to the $\Hash$ oracle by the adversary is the sum of queries($q_T$) made by the $\Test$ oracle, and adversary's direct queries($q_H$) to the RO.
-Using analyses and intermediate results of previous proofs, $\Prob{\game{5}(A)=1} = \dfrac{1}{\binom{q_T + q_H}{r}}\Prob{\game{4}(A)=1}$.
+In $\game{3}$, we modify the $\HashOracle$ oracle so that on query~$\qry_x$ it returns all of the~$k$ values that previously would have required calls $\HashOracle(1,\qry_y),\HashOracle(2,\qry_y),\ldots,\linebreak\HashOracle(k,\qry_y)$.
+This results in adversary getting $(k-1)$ hash values ``for free'', as we charge the adversary only for a single query.
+We alter the $\TestOracle$ oracle accordingly, so that it makes a single call $\Hash(\qry_x)$ rather than~$k$ such calls.
+We do this so that we can assume that a call~$\HashOracle(\qry_x)$ is pointless after a~$\TestOracle(\qry_x)$ call, and this will aid us in subsequent games.
+\fixme{for BF proof, this actually does more, it makes a hash query as good as a test query, because~$M$ is public.}  Thus, $\Prob{\game{2}(A) = 1} \leq \Prob{\game{3}(A) = 1}$.
 
+%tom here
+Game~$\game{4}$ contains some important changes from game~$\game{3}$, but we will argue that $\Prob{\game{3}(A) = 1} \leq \Prob{\game{4}(A) = 1}$.
+To begin, in game~$\game{4}$ we sample an $r$-subset of indices from~$\{1,2,\ldots,q_H+q_T\}$.
+(We will see why, shortly.)  Next, the $\TestOracle$ oracle on input~$\qry_x$ no longer computes its answer directly, but instead refers to a new table~$\mathrm{Ans}[x]$ which is populated upon calls to the $\HashOracle$ oracle.
+In particular, if $\mathrm{Ans}[x]$ is undefined, $\TestOracle$ makes a $\HashOracle(\qry_x)$ call; otherwise, it returns the contents of~$\mathrm{Ans}[x]$, which contains exactly the values that~$\TestOracle(\qry_x)$ would have returned in the previous game.
+The $\HashOracle$ oracle, on input~$\qry_y$ computes the random values~$v_1,v_2,\ldots,v_k$ as in $\game{3}$.
+(We no longer need to maintain the table~$T$ because hash values are only determined by~$\HashOracle$ calls, and these are never repeated under our no-pointless-query assumption.)  It then computes the answer that~$\TestOracle(\qry_x)$ would return, in game~$\game{3}$, and stores the answer in~$\mathrm{Ans}[x]$ for use by~$\TestOracle$.
+The $\HashOracle$ oracle also introduces a query counter~$c$, which is incremented whenever~$\HashOracle$ is called, either directly by~$A$ or via~$A$ having made a~$\TestOracle$ query on~$\qry_x$ where~$\mathrm{Ans}[x]$ had not been previously defined by a~$\HashOracle(\qry_x)$ call.
+\fixme{for BF proof, we can assume that $\TestOracle(\qry_x)$ is never made after a~$\HashOracle(\qry_x)$ call, because~$M$ is public.
+And vice versa.
+So the maximum value of~$c = q_T + q_H$.}  (Note that the maximum value of~$c$ is $q_T + q_H$.)  The set~$\calI$ contains a set of~$r$ distinct values from $\{1,2,\ldots,q_T+q_H\}$ and, intuitively, these are the game's ``guesses'' at the $\HashOracle$ queries that will result in a correctness error.
+If these~$r$ guesses are incorrect, then a boolean flag~$\bad$ is set, although in game~$\game{4}$ the value of~$\bad$ has no effect on the games execution; in particular, $\game{4}$ does \emph{not} contain the boxed ``Return 0'' statement.
+
+Games~$\game{4}$ and $\game{5}$ are identical except for this boxed statement.
+In particular, game~$\game{5}$ returns 1 exactly when~$\game{4}$ would return 1 \emph{and} the boolean~$\bad$ would have remained false in~$\game{4}$.
+This implies that~$game{4}$ managed to guess exactly the queries that would result in correctness errors, and hence
+$\Prob{\game{5}(A)=1} = \dfrac{1}{\binom{q_T + q_H}{r}}\Prob{\game{4}(A)=1}$.
+
+\fixme{Tom stopped his clean-up here.  Fix this last paragraph!}
 For $r=1$, $\game{5}$ exactly simulates the classical Bloom filter.
@@
 {
-\underline{\game{0}(A)}\\
+\underline{$\game{0}(A)$}\\
 $S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
 $(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
-$\bot \getsr A^{\TestOracle}(\pubaux)$\\
+$\bot \getsr A^{\TestOracle,\HashOracle}(\pubaux)$\\
 if $\err  < r$ then Return 0\\
@@
 for $j \in \{1,2,\ldots,k\}$\\
-\nudge $h_j \gets \HashOracle(j, x)$\\
+\nudge $h_j \gets \HashOracle(j, \qry_x)$\\
 \nudge if $M[h_j] \neq 1$ then Return 0\\
@@
 for $j \in \{1,2,\ldots,k\}$\\
-\nudge $h_j \gets \HashOracle(j, x)$\\
+\nudge $h_j \gets \HashOracle(j, \qry_x)$\\
 \nudge if $M[h_j] \neq 1$\\
@@
 $\calC \gets \calC \cup x$; $M \gets\pubaux$\\
-$(h_1, \ldots, h_{k}) \gets \HashOracle(x)$\\
+$(h_1, \ldots, h_{k}) \gets \HashOracle(\qry_x)$\\
 for $j \in \{1,2,\ldots,k\}$\\
@@
 }
-\caption{\ref{thm:bf-correctness}: Game playing argument}
+\caption{Games $\game{0}$-$\game{3}$ for the
+proof of Theorem~\ref{thm:bf-correctness}.}
 \label{fig:bf-correctness-games1}
@@
 {
-\underline{\game{4}(A)\fbox{\game{5}(A)}}\\
+\underline{$\game{4}(A)$\fbox{$\game{5}(A)$}}\\
 $c\gets 0$, $\bad \gets \false$, $\err \gets 0$;  $\calC \gets \emptyset$\\
-$S \getsr A$; $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
+$S \getsr A$; $\mathcal{I}\getsr [\{1,2,\ldots,q_T+q_H\}]^r$\\
 $(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
-$\bot \getsr A^{\TestOracle}(\pubaux)$\\
+$\bot \getsr A^{\TestOracle,\HashOracle}(\pubaux)$\\
 if $\bad = \true$ then \fbox{Return 0}\\
@@
 $\calC \gets \calC \cup x$\\
-if $\Ans[x] \neq \undefined$\\
-\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(x)$\\
+if $\Ans[x] = \undefined$\\
+\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(\qry_x)$\\
 Return $\Ans[x]$\\
@@
 }
-\caption{\ref{thm:bf-correctness}: $\game{4}$ and $\game{5}$ of game
-  playing argument}
+\caption{Games $\game{4}$-$\game{5}$ for the
+proof of Theorem~\ref{thm:bf-correctness}.}
 \label{fig:bf-correctness-games2}

### 2016-09-30 GBF-correctness-private-M.tex
cleaning bf and gbf still

@@
 \begin{proof}[Theorem~\ref{thm:gbf-correctness}]
-We use a game playing argument, please refer to Figures~\ref{fig:gbf-correctness-games1} and~\ref{gfig:bf-correctness-games2}.
+We use a game playing argument, please refer to Figures~\ref{fig:gbf-correctness-games1} and~\ref{fig:gbf-correctness-games2}.
 In game $\game{0}$, the $\Hash$ oracle performs lazy sampling of elements from $[m]$ to mimic a random oracle (RO).
@@
 The $\HashOracle$ oracle, on input~$\qry_y$ computes the random values~$v_1,v_2,\ldots,v_k$ as in $\game{3}$.
-We no longer need to maintain the table~$T$ because hash values are only determined by~$\HashOracle$ calls.
+(We no longer need to maintain the table~$T$ because hash values are only determined by~$\HashOracle$ calls, and these are never repeated under our no-pointless-query assumption.)  It then computes the answer that~$\TestOracle(\qry_x)$ would return, in game~$\game{3}$, and stores the answer in~$\mathrm{Ans}[x]$ for use by~$\TestOracle$.
+The $\HashOracle$ oracle also introduces a query counter~$c$, which is incremented whenever~$\HashOracle$ is called, either directly by~$A$ or via~$A$ having made a~$\TestOracle$ query on~$\qry_x$ where~$\mathrm{Ans}[x]$ had not been previously defined by a~$\HashOracle(\qry_x)$ call.
+\fixme{for BF proof, we can assume that $\TestOracle(\qry_x)$ is never made after a~$\HashOracle(\qry_x)$ call, because~$M$ is public.
+And vice versa.
+So the maximum value of~$c = q_T + q_H$.}  (Note that the maximum value of~$c$ is $q_T + q_H$.)  The set~$\calI$ contains a set of~$r$ distinct values from $\{1,2,\ldots,q_T+q_H\}$ and, intuitively, these are the game's ``guesses'' at the $\HashOracle$ queries that will result in a correctness error.
+If these~$r$ guesses are incorrect, then a boolean flag~$\bad$ is set, although in game~$\game{4}$ the value of~$\bad$ has no effect on the games execution; in particular, $\game{4}$ does \emph{not} contain the boxed ``Return 0'' statement.
 
-In $\game{4}$, assuming $A$ does not make any pointless queries, $\Hash$ returns $k$ random values (for each query) sampled from $[m]$.
-Also, we offload all of $\Test$'s computations to $\Hash$, which now maintains an $\Ans$ table to compute and save answers for each query.
-For any query, $\qry$, the $\Test$ oracle returns answer stored at $\Ans[\qry]$.
-We also introduce the $\bad$ flag in this game.
-Like in the earlier proofs,  $\bad$ is set to true, if queries indexed by the r-set $\calI$ fail to be false positives, or the other queries are false-positives.
-$\bad$ in fact does not affect the output of $\Hash$ or the game.
-So, $\Prob{\game{4}(A) = 1} = \Prob{\game{3}(A) = 1}$.
-
-$\game{5}$ is exactly same as $\game{4}$, but returns 0, if $\bad$ is set to true.
-It can be observed that, the total queries made to the $\Hash$ oracle by the adversary is the sum of queries($q_T$) made by the $\Test$ oracle, and adversary's direct queries($q_H$) to the RO.
-Using analyses and intermediate results of previous proofs, $\Prob{\game{5}(A)=1} = \dfrac{1}{\binom{q_T + q_H}{r}}\Prob{\game{4}(A)=1}$.
-
-For $r=1$, $\game{5}$ exactly simulates the classical Bloom filter.
-Since, $\Hash$ returns random values for each query, the event of getting a false-positive is independent of the index of the query.
-Using Kirsch and Mitzenmacher's upper bound on false positive probability of a classical Bloom filter, we have  $\Prob{\game{5}(A)=1} = \left( (1-e^{-kn/m})^k + O(1/n) \right)^r$.
+Games~$\game{4}$ and $\game{5}$ are identical except for this boxed statement.
+In particular, game~$\game{5}$ returns 1 exactly when~$\game{4}$ would return 1 \emph{and} the boolean~$\bad$ would have remained false in~$\game{4}$.
+This implies that~$game{4}$ managed to guess exactly the queries that would result in correctness errors, and hence
+$\Prob{\game{5}(A)=1} = \dfrac{1}{\binom{q_T + q_H}{r}}\Prob{\game{4}(A)=1}$.
 
@@
 {
-\underline{\game{4}(A)\fbox{\game{5}(A)}}\\
+\underline{$\game{4}(A)$\fbox{$\game{5}(A)$}}\\
 $c\gets 0$, $\bad \gets \false$\\
@@
 Return $\Ans[x]$\\
+}
+{
+\oracle{$\HashOracle(\qry_y)$}\\
+$c \gets c + 1$\\
+for $j \in \{1,2,\ldots,k\}$\\
+\nudge $v_j \getsr [m]$\\
+%
+$M \gets\privaux$\\
+$y' \gets M[v_1] \xor M[v_2] \xor \ldots \xor M[v_k]$\\
+if $y' \neq y$ then \\
+\nudge $\Ans[y] \gets (0, (v_1, \ldots, v_{k}) )$\\
+\nudge if $c \in \calI$ then $\bad \gets \true$\\
+\nudge Return $\left(v_1,\ldots,v_k\right)$\\
+if $c \notin \calI$ then $\bad \gets \true$\\
+$\err \gets \err +1$\\
+$\Ans[y] \gets (1, (v_1, \ldots, v_{k}))$\\
+Return $\left(v_1,\ldots,v_k\right)$
+}
+}
+%
+\fpage{.95}{
+\hpagessl{.4}{.5}
+{
+\underline{$\game{6}(A)$}}\\
+$c\gets 0$, $\bad \gets \false$\\
+$\err \gets 0$;  $\calC \gets \emptyset$\\
+$S \getsr A$\\
+$\mathcal{I}\getsr [\{1,2,\ldots,q_T + q_H\}]^r$\\
+$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+$\bot \getsr A^{\TestOracle}(\pubaux)$\\
+if $\bad = \true$ then \fbox{Return 0}\\
+if $\err  < r$ then Return 0\\
+Return 1\\
 
+\oracle{$\TestOracle(\qry_x)$}\\
+if $x \in \mathcal{C}$ then Return $\bot$\\
+$\calC \gets \calC \cup x$\\
+if $\Ans[x] = \undefined$\\
+\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(\qry_x)$\\
+Return $\Ans[x]$\\
 }

### 2016-09-30 GBF-correctness-private-M.tex
bf and gbf cleaning

@@
 {
-\underline{$\game{6}(A)$}}\\
+\underline{$\game{6}(A)$}\\
 $c\gets 0$, $\bad \gets \false$\\

### 2016-09-30 notions.tex
no message

@@
   the RO.  That's like letting $S$ depend on $\pub$ in the standard
-  model, but $\pub$ hasn't been fixed yet.  }
+  model, but $\pub$ hasn't been fixed yet.  } \jnote{I disagree. Plus if you do that, then
+  you put the simulator at an unfair disadvantage. (Consider a scheme that always appends
+  $H(0)$ to $\pubaux$, for every~$S$. The simulator will never be able to simulate that---even
+  if you give it~$S$!---simply because it can't guess~$H(0)$).}
 
@@
 any attacker $A$, there is an attacker
-$B$ running in about the same time for which
+$B$ \jnote{How do we describe the number of PRF queries $B$ makes? Note that it makes
+exactly $t$ queries, but $t$ depends on $|S|$ in a non-specified manner.} for which
 \[\AdvPrivSS{\setprim,{\sf leak}}{A} \leq {\sf Adv}_F^{\rm PRF}(B). \]

### 2016-09-30 results.tex
no message

@@
 for $x \in S$\\
-\jnote{Fix}\tsnote{Fix what?}\\
+%\jnote{Fix}\tsnote{Fix what?}\\
 \nudge for $j \in \{1,2,\ldots,k\}$\\
@@
 \nudge\nudge $M[h_j] \gets 1$\\
-$\pubaux \gets M$, $\privaux \gets \langle K \rangle$\\
-Return $(\pubaux,\privaux)$\\
+%$\pubaux \gets M$, $\privaux \gets \langle K \rangle$\\
+Return $(\pubaux=M,\privaux=K)$\\
 
 \medskip
-\algorithmv{$\Qry(\pubaux,\privaux,q_x)$}\\
-$M\gets\pubaux$, $K \gets \privaux$\\
-\jnote{Fix}\tsnote{Fix what?} \\
+\algorithmv{$\Qry(\pubaux=M,\privaux=K,q_x)$}\\
+%$M\gets\pubaux$, $K \gets \privaux$\\
+%\jnote{Fix}\tsnote{Fix what?} \\
 for $j \in \{1,2,\ldots,k\}$\\
@@
   data structure $\setprim_{\mathrm{lin}}$ {\bf Right:}
-The scheme from Niedermeyer et al.\cite{xxx}, $\setprim_{\bilin}$. The $\mathsf{bigram}$
-algorithm takes a string~$x=x_1,x_2,\ldots,x_\ell$ as input, and
-returns the set of bigrams for the left- and right-padded string
-$\sqcup x \sqcup$, i.e. $\{\sqcup x_1, x_1x_2,\ldots,x_{\ell-1}x_\ell,x_\ell\sqcup\}$.
-}
-\label{fig:lin-and-bi-lin}
+The scheme from Niedermeyer et al.\cite{xxx}, $\setprim_{\bilin}$.
+The $\mathsf{bigram}$ algorithm takes a
+string~$x=x_1,x_2,\ldots,x_\ell$ as input, and returns the set of
+bigrams for the left- and right-padded string $\sqcup x \sqcup$,
+i.e. $\{\sqcup x_1, x_1x_2,\ldots,x_{\ell-1}x_\ell,x_\ell\sqcup\}$.
+\jnote{I would emphasize that $F_K(\cdot)$ is computed only twice
+per inner loop (which is the whole point of this scheme) by moving
+that computation outside the loop.}} \label{fig:lin-and-bi-lin}
 \label{fig:niedermeyer}
@@
 \subsection{Bigram Domain-Separated PRF-Hash}
-We note that Niedermeyer et al.
-in~\cite{niedermeyer2014cryptanalysis} suggest replacing the linear-PRF hash functions in the previous construction with independently keyed PRFs as a countermeasure to their attack.
-In terms of SS-privacy, however, this change offers no help.
-The following theorem is proved via a nearly identical argument as Theorem~\ref{thm:bi-lin-ss}.
+
+\begin{figure}
+\centering
+\fpage{0.5}{
+\algorithmv{$\Rep(S)$}\\
+$\pubaux \gets \emptystring$, $K \getsr \calK$\\
+for each $x \in S$\\
+\nudge $M_x \gets 0^m$\\
+\nudge $B_x \gets \mathsf{bigram}(x)$\\
+\nudge for each $b \in B_x$\\
+\nudge\nudge for $j \in [k]$\\
+\nudge\nudge\nudge $i \gets F_{K}(\langle j, b\rangle) \bmod m$\\
+\nudge\nudge\nudge $M_x[i] \gets 1$\\
+\nudge $\pubaux \gets \langle\pubaux, M_x \rangle$\\
+$\privaux \gets K$\\
+Return $(\pubaux,\privaux)$\\
+
+\medskip
+\algorithmv{$\Qry(\pubaux,\privaux,q_x)$}\\
+$B \gets \mathsf{bigram}(x)$\\
+$\overline{M} \gets 0^m$\\
+for each $b \in B$\\
+\nudge for $j \in [k]$\\
+\nudge\nudge $i \gets F_{K}(\langle j,b \rangle) \bmod m$\\
+\nudge\nudge $\overline{M}[i] \gets 1$\\
+if $\overline{M} \in \pubaux$ then Return 1 \\
+Return 0} \caption{Bigram domain-separated PRF-hash.}
+\label{fig:DS-bigram}
+\end{figure}
+
+Niedermeyer et al.~\cite{niedermeyer2014cryptanalysis} suggest
+replacing the linear-PRF hash functions in the previous construction
+with independently keyed PRFs as a countermeasure to their attack.
+In terms of SS-privacy, however, this change offers no help.  The
+following theorem is proved via a nearly identical argument as
+Theorem~\ref{thm:bi-lin-ss}.
 
 \begin{theorem}[{\rm SS-privacy of bigram DS PRF-hash}]\label{thm:bi-ds-ss}
-Let $\setprim_{\bilin}= (\Rep, \Qry)$ be the set-membership data structure described in Figure~\ref{fig:lin-and-bi-lin}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.
-Let $\leak$ be the leakage function described just prior to Theorem~\ref{thm:bi-lin-ss}.
-Let~$\elts=\{\mathrm{a,b,c}\}^*$.
-Let $n=3$,  $m=3\alpha $ for integer $\alpha >> 1$, and let, $k = \lceil \ln(2) \alpha \rceil$.\tsnote{This value of~$k$ is from the classical analysis for minimizing the FP rate for a Bloom filter, and is set this way for compatibility with classical results.
-It isn't used in any essential way in the proof sketch.}  Let~$A$ be the adversary in Figure~\ref{fig:adv-bi-lin-ss}.
-Then for any simulator $\Sim$,
-the advantage $\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim}$ can be made arbitrarily close to $1/2$ by choice of~$\alpha$.
+Let $\setprim_{\bilin}= (\Rep, \Qry)$ be the set-membership data
+structure described in Figure~\ref{fig:DS-bigram}. Let $\leak$ be
+the leakage function described just prior to
+Theorem~\ref{thm:bi-lin-ss}. Let~$\elts=\{\mathrm{a,b,c}\}^*$. Let
+$n=3$,  $m=3\alpha $ for integer $\alpha >> 1$, and let $k = \lceil
+\ln(2) \alpha \rceil$.\tsnote{This value of~$k$ is from the
+classical analysis for minimizing the FP rate for a Bloom filter,
+and is set this way for compatibility with classical results.  It
+isn't used in any essential way in the proof sketch.}  Let~$A$ be
+the adversary in Figure~\ref{fig:adv-bi-lin-ss}.  Then for any
+simulator $\Sim$, the advantage
+$\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim}$ can be made
+arbitrarily close to $1/2$ by choice of~$\alpha$.
 \end{theorem}
 
-\todo{OW privacy proof? Attack? [JON]}
+On the other hand, we can show that this data structure \emph{is}
+semantically secure with respect to a different leakage function,
+namely, one that leaks the sizes of the intersections of the various
+bigram sets. Specifically, for a set $S$ define ${\sf leak}_\cap(S)$
+via the following algorithm:
+
+\begin{figure}[h]
+\centering
+\fpage{0.5}{
+\algorithmv{${\sf leak}_\cap(S)$}\\
+$L \gets \emptystring$\\
+for each $x \in S$\\
+\nudge $B_x \gets \mathsf{bigram}(x)$\\
+for each $S' \subseteq S$\\
+\nudge $L \gets \left\langle L, \; \left| \bigcap_{x \in S'} B_x \right| \right\rangle$\\
+Return $L$}
+%\caption{Bigram domain-separated PRF-hash.}
+\end{figure}
+
+\begin{theorem} %\label{thm:priv-ss}
+Let $\Pi$ be the set-representation data structure in
+Figure~\ref{fig:DS-bigram}. Then for any attacker $A$, there is an
+attacker $B$ \jnote{How do we describe the number of PRF queries $B$
+makes? Same problem as in Theorem~\ref{thm:priv-ss}.} for which
+\[\AdvPrivSS{\setprim,{\sf leak}_\cap}{A} \leq {\sf Adv}_F^{\rm PRF}(B). \]
+\end{theorem}
+\begin{proof}
+The proof follows the same high-level ideas as in the proof of
+Theorem~\ref{fig:DS-bigram}, based on the observation that ${\sf
+leak}_\cap(S)$ suffices to determine the overlap in calls to the
+pseudorandom function~$F$.
+
+Our simulator $\Sim$, on input $L = \{n_{S'}\}_{S' \subseteq S}$,
+proceeds as follows. Let $N = n_S$ denote the size of~$S$. The
+simulator constructs $N$ sets $B_1, \ldots, B_N \subset \{e_1,
+\ldots, e_{N'}\}$ of ``dummy elements'' $e_1, \ldots, e_{N'}$ (with
+$N' \leq N$), such that the sizes of the intersections of the
+$\{B_i\}$ are exactly that given by~$L$. (This can be done via a
+deterministic, incremental algorithm in which $\Sim$ first populates
+$B_1$ with $n_{\{x_1\}}$ dummy elements,and always populates the
+next set $B_i$ with old/new dummy elements as needed to maintain the
+correct intersection sizes.) It then chooses uniform values
+$y_{1,1}, \ldots, y_{1,k}, \ldots, y_{N',1}, \ldots, y_{N',k} \getsr
+\bool^{\ell_{out}}$ and computes
+
+\begin{figure}[h]
+\centering
+\fpage{0.5}{
+$\pubaux \gets \emptystring$\\
+for each $x \in [N]$\\
+\nudge for each $b \in [N']$\\
+\nudge \nudge if $e_b \in B_i$\\
+\nudge\nudge\nudge for $j \in [k]$\\
+\nudge\nudge\nudge\nudge $i \gets y_{b,j} \bmod m$\\
+\nudge\nudge\nudge\nudge $M_x[i] \gets 1$\\
+\nudge $\pubaux \gets \langle\pubaux, M_x \rangle$\\
+Return $\pubaux$
+}
+\end{figure}
+
+The proof that this provides a good simulation is identical to that
+of Theorem~\ref{fig:DS-bigram}. \hfill\qed
+\end{proof}
+
+We remark that the running time of the simulator is exponential in
+the size $|S|$ of the set, so the above is not entirely satisfactory
+unless $S$ is small. Nevertheless, it does convey the intuition that
+the \emph{only} information leaked by the data structure is the
+sizes of the various intersections of the~$\{B_x\}$ sets.
 

### 2016-09-30 GBF-correctness-private-M.tex
bf and gbf

@@
 $\Prob{\game{5}(A)=1} = \dfrac{1}{\binom{q_T + q_H}{r}}\Prob{\game{4}(A)=1}$.
+
+We note that since game~$\game{5}(A)$ returns iff~$A$ manages to find~$r$ errors the game managed to guess exactly which $\HashOracle$ queries would cause the errors, there is a zero-query adversary~$A_0$ that manages to find~$r$ errors.
+Namely, adversary~$A_0$
 
@@
 \begin{figure}[tp]
-\fpage{.95}{
-\hpagessl{.4}{.5}
+\fpage{.85}{
+\hpagessl{.45}{.5}
 {
@@
 $(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
-$\bot \getsr A^{\TestOracle}(\pubaux)$\\
+$\bot \getsr A^{\TestOracle,\HashOracle}(\pubaux)$\\
 if $\bad = \true$ then \fbox{Return 0}\\
@@
 %
-\fpage{.95}{
-\hpagessl{.4}{.5}
+\fpage{.85}{
+\hpagessl{.45}{.5}
 {
-\underline{$\game{6}(A)$}\\
-$c\gets 0$, $\bad \gets \false$\\
-$\err \gets 0$;  $\calC \gets \emptyset$\\
-$S \getsr A$\\
+\adversaryv{$A_0(\pubaux)$}\\
+$c\gets 0$, $\calY \gets \emptyset$\\
+$\calC \gets \emptyset$\\
 $\mathcal{I}\getsr [\{1,2,\ldots,q_T + q_H\}]^r$\\
-$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
-$\bot \getsr A^{\TestOracle}(\pubaux)$\\
-if $\bad = \true$ then \fbox{Return 0}\\
-if $\err  < r$ then Return 0\\
-Return 1\\
+$\bot \getsr A^{\TestOracle,\HashOracle}(\pubaux)$\\
+Return~$\calY$
 
@@
 %
-$M \gets\privaux$\\
-$y' \gets M[v_1] \xor M[v_2] \xor \ldots \xor M[v_k]$\\
-if $y' \neq y$ then \\
+if $c \not\in \calI$ then \\
 \nudge $\Ans[y] \gets (0, (v_1, \ldots, v_{k}) )$\\
-\nudge if $c \in \calI$ then $\bad \gets \true$\\
 \nudge Return $\left(v_1,\ldots,v_k\right)$\\
-if $c \notin \calI$ then $\bad \gets \true$\\
-$\err \gets \err +1$\\
+$\calY \gets \calY \cup \{y\}$\\
 $\Ans[y] \gets (1, (v_1, \ldots, v_{k}))$\\
@@
 }
-\caption{Games $\game{4}$-$\game{5}$ for the
+\caption{Games $\game{4}$-$\game{5}$ and zero-query adversary~$A_0$ for the
 proof of Theorem~\ref{thm:gbf-correctness}.}

### 2016-09-30 BF_correctness.tex
bf and gbf

@@
 
-\fixme{Tom stopped his clean-up here.  Fix this last paragraph!}
 For $r=1$, $\game{5}$ exactly simulates the classical Bloom filter.
-Since, $\Hash$ returns random values for each query, the event of getting a false-positive is independent of the index of the query.
+Since, $\HashOracle$ returns random values for each query, the event of getting a false-positive is independent of the index of the query.
 Using Kirsch and Mitzenmacher's upper bound on false positive probability of a classical Bloom filter, we have  $\Prob{\game{5}(A)=1} = \left( (1-e^{-kn/m})^k + O(1/n) \right)^r$.
-
 To summarize, 

### 2016-09-30 GBF-correctness-private-M.tex
bf and gbf

@@
 
-We note that since game~$\game{5}(A)$ returns iff~$A$ manages to find~$r$ errors the game managed to guess exactly which $\HashOracle$ queries would cause the errors, there is a zero-query adversary~$A_0$ that manages to find~$r$ errors.
-Namely, adversary~$A_0$
+We note that since game~$\game{5}(A)$ returns iff~$A$ manages to find~$r$ errors the game managed to guess exactly which $\HashOracle$ queries would cause the errors
 
@@
 {
-\adversaryv{$A_0(\pubaux)$}\\
+\adversaryv{$A_0\TestOracle,\HashOracle(\pubaux)$}\\
 $c\gets 0$, $\calY \gets \emptyset$\\
@@
 $\mathcal{I}\getsr [\{1,2,\ldots,q_T + q_H\}]^r$\\
-$\bot \getsr A^{\TestOracle,\HashOracle}(\pubaux)$\\
-Return~$\calY$
+$\bot \getsr A^{\mathsc{TEST},\mathsc{HASH}}(\pubaux)$\\
 
-\oracle{$\TestOracle(\qry_x)$}\\
+\oracle{$\mathsc{TEST}(\qry_x)$}\\
 if $x \in \mathcal{C}$ then Return $\bot$\\
@@
 {
-\oracle{$\HashOracle(\qry_y)$}\\
+\oracle{$\mathsc{HASH}(\qry_y)$}\\
 $c \gets c + 1$\\

### 2016-09-30 intro-old.tex
intro-old with citations

--- 2016-05-24 critique/intro.tex
@@
+%\jnote{Are we being too specific by focusing on hash-based
+%set-membership only? It would be nice to give general definitions
+%that apply to arbitrary data structures (constructed in arbitrary
+%ways) and then only later specialized to hash-based Bloom filters.
+%(Put this in an appendix for now, until we see how things play
+%out.)}
+
 \section{Introduction}
+We revisit the formalization of Bloom filters~\cite{bloom1970space} and closely
+related data structures as primitives with explicit security goals.
+Recently, Naor and Yogev~\cite{naor2015bloom} (hereafter NY) gave such a
+formalization, providing syntax for a generalized abstraction of
+Bloom filters, as well as casting the classical Bloom filter
+soundness condition as a security experiment admiting adaptive
+adversaries.  To briefly summarize, a Bloom filter is a data
+structure for compactly representing a set~$\mathcal{S}$ in a way
+that supports constant-time responses to set-membership queries. The
+representation of~$\mathcal{S}$ is a bit-array~$M$ of length~$m$,
+all initially set to~0.  To insert $x \in \mathcal{S}$ into~$M$, one
+computes indices $h_1(x),h_2(x),\ldots,h_k(x)$ where each $h_i
+\colon \mathcal{U} \to \{0,1,\ldots m-1\}$ maps from a
+universe~$\mathcal{U}$ (which contains $\mathcal{S}$) to indices
+of~$M$.  The bits at positions $h_1(x),h_2(x),\ldots,h_k(x)$ are set
+to 1; if a bit is already 1, due to inserting some previous element
+of~$\mathcal{S}$, then it is left alone.  After all elements
+of~$\mathcal{S}$ have been inserted, the resulting bit-array~$M$ is
+taken as the representation.  To test if $y \in \mathcal{S}$, one
+checks if \[(M[h_1(y)]=1 \wedge M[h_2(y)]=1 \wedge \cdots \wedge
+M[h_k(y)]=1),\] returning ``yes'' if so, and ``no'' otherwise. Bloom
+filters are correct, in the sense that if $y \in \mathcal{S}$, the
+set-membership test always returns ``yes''.  The classical soundness
+condition asserts that for all $\mathcal{S}$ and any $y
+\notin\mathcal{S}$, we have $\Prob{h_1,h_2,\ldots,h_k \getsr
+\mathrm{Func}(\mathcal{U},[m])\colon M[h_1(y)]=1 \wedge \cdots
+\wedge M[h_k(y)]=1} \leq \epsilon$ where $\epsilon$, the
+false-positive error, is a parameter of the Bloom filter.  (The
+values of~$\epsilon,m,k$, and $|\mathcal{S}|$ are related in a
+well-known way.) NY recast this soundness condition as a game in
+which an adversary~$A$ is given~$\mathcal{S}$ and an oracle for
+set-membership queries, and it attempts to find one or more false
+positives. The fact that~$A$ can \emph{adapt} its queries and its
+output based on what it learns from the set-membership oracle (but,
+as we will see, not upon the hash functions) is the key definitional
+contribution of~NY.
+
+Bloom filters have a broad range of practical applications, for example, in content-distribution networks, large database query processing, routing algorithms for peer-to-peer networks, protocols for establishing linkages between medical-record databases, fair routing of TCP packets, Bitcoin wallet synchonization.
+\tsnote{need citations} Given that NY is addressing such a useful real-world object, we find their formalism, both the syntax and security notions, to be less precise and useful than one would want.
+Let us explain.
+
+Syntactically, NY says a Bloom filter (with a steady representation) is a pair of algorithms $\mathbf{B}=(\mathbf{B}_1, \mathbf{B}_2)$.
+The setup algorithm~$\mathbf{B}_1$ is randomized, and on input a set~$\mathcal{S}$ it returns a representation~$M$ (from some undefined, implicit set of representations).
+The query algorithm~$\mathcal{B}_2$ is deterministic, and on input a representation~$M$ and an element~$x \in \mathcal{U}$, it returns a bit.
+For correctness they make the classical demand, that for all $x \in \mathcal{S}$ we have $\Prob{\mathbf{B}_2(\mathbf{B}_1(\mathcal{S}),x)=1}=1$.
+For soundness, adversary~$A$ plays the following game, ``Adversarial-resilient Bloom Filter with a steady representation''.
+First, $M \getsr \mathbf{B}_1(\mathcal{S})$ for some set $\mathcal{S}$ that can be adversarially chosen.
+Then the adversary may make queries $x_1,x_2,\ldots,x_q$ to an oracle for $\mathbf{B}_2(M,\cdot)$.
+At the end of its execution, the adversary outputs~$x^*$ and wins the game if (1) $x^* \not\in \mathcal{S} \cup \{x_1,x_2,\ldots,x_q\}$, and (2) $\mathbf{B}_2(M,x^*)=1$.
+
+First, we note that the security notion forbids~$A$ to win if it outputs $x^* \in \{x_1,x_2,\ldots,x_q\}$, even if one of these was a false positive.
+On one hand, this notion is unsatisfying because it would not say that an attacker wins by creating (say) a bogus email address, and then observing that it passes a spam filter that is based on a Bloom filter represention of a whitelist.\footnote{This is one of the motivating examples from NY.}  The attacker is only allowed to win if it finds a false-positive that it has not verified.
+On the other hand, the NY notion does seem to capture the intuition that finding additional false positives does not become easier as more are learned.
+Our notions will address both sides of this discussion.
+%
+%\jnote{We discussed this on the phone, but let me put it in writing here.
+I think this is actually a reasonable choice because it captures the notion that ``even after finding some false positives, it remains hard to find additional false positives.'' Note that in practice finding false positives is ``easy'' since $\epsilon$ might be $1/1000$ rather than negligible.}
+%
+%\tsnote{For me the question is: is security violated once the first FP is found, or the second?
+My answer, which is in line with the traditional soundness notion, is that the first FP is a security violation even if finding it isn't ``hard'' by cryptographic standards.
+But I do appreciate your point.
+A natural goal is to say that, in some sense, \emph{adaptivity doesn't make it any easier} to find a FP.
+Adapting to what, though?
+In the traditional notion, $x$~is picked before the coins of~$\mathbf{B}_1$ are flipped, i.e., before the hash functions are sampled.
+The direct non-adaptive generalization is to say that $x_1,x_2,\ldots,x_q$ are all picked up front.
+The direct \emph{adaptive} generalization would allow $x_1,x_2,\ldots,x_q$ to depend in the coins of~$\mathbf{B}_1$, i.e., the hash functions.
+The NY definition captures only indirect dependence: adversaries that can adapt to set-membership queries, but \emph{not} (directly) to the input-output behaviors of the hash functions.
+The three notions I've proposed in Figure 1 cover a spectrum of adaptivity: the first is adapting to set-membership queries only, the second to those and hash input-output behavior, the third to set-membership queries and full knowledge of the hash functions.
+Each has it's own associated (informal) security interpretation.}
+%\tsnote{Perhaps a more obvious way to capture the idea that ``finding some FPs doesn't help find additional ones'' is to parameterize my notion(s) with a number~$f$, and say that that the adversary wins iff it outputs~$f$ FPs (these may have been previously queried to the set-membership oracle).
+Note that in the ROM (and probably in practice) finding~$f>1$ FPs will require~$f$ times the work.
+Right?}
+%
+%\tsnote{FYI: this is how MAC security against multiple forgeries is defined.  See \texttt{https://eprint.iacr.org/2006/095.pdf} for details.}
+
+Second, we note that the NY syntax does not capture the size of~$M$
+as a parameter; \jnote{I think this is also reasonable; typically
+security is defined without regard for efficiency} \tsnote{My
+complaint isn't about efficiency. It's about the fact that, by not
+including $|M|$ in the definition, the trivial scheme I give (just
+below) is allowed, and is secure.  Anyway, as I say at the end of
+this paragraph, this is a small(er) complaint than what follows}.
+\jnote{I would say that the trivial scheme \emph{is} secure!}
+\tsnote{Okay, well then we need some way to ``rule out'' the trivial
+solution. Perhaps just in the text -- yes, the trivial scheme works,
+but it isn't interesting in practice. Also, in the concrete security
+bounds that we will prove, the size of the representation is going
+to come up, e.g.\ the number of bits in the BF array directly affect
+the FP rate. Hence it makes sense to say things like ``an
+$(n,k,m)$-filter\ldots'' where $m$ is the size of the
+representation.} \jnote{I still disagree: efficiency is orthogonal
+to functionality and security.} \fixme{
+Let's discuss this verbally, because I feel like we are talking past each other.}The surrounding text does say that
+$\mathbf{B}_1$ ``outputs a compressed representation [of
+$\mathcal{S}$] $\mathbf{B}_1(\mathcal{S})=M$'' but what exactly this
+means is never addressed. The formal syntax admits
+$\mathbf{B}_1(\mathcal{S})=\mathcal{S}$ and
+$\mathbf{B}_2(\mathcal{S},x)=1 \Leftrightarrow x \in \mathcal{S}$,
+which is also trivially secure by their definition.  These are both
+small, but important complaints. But a larger complaint, and one
+that is much harder to see, is that that it is not clear that the NY
+formalism actually captures real world Bloom filters.
+
+In particular, say we implement a classic Bloom filter.
+Then the hash functions $h_1, h_2, \ldots, h_k$ are either sampled from some family~$\mathcal{H}$ by~$\mathbf{B}_1$ (recall that this algorithm is randomized), or they are hard-coded into the description of~$\mathbf{B}_1$.
+Let's assume the former for the moment.
+In order for~$\mathbf{B}_2$ to be able to respond to set-membership queries, it must have $h_1,h_2,\ldots,h_k$ as well.
+Since~$\mathbf{B}_2$ receives only the representation~$M$ as input, it must be the case that $h_1,h_2,\ldots,h_k$ are encoded into~$M$ somehow.
+But the text strongly suggests, in several places, that~$M$ does \emph{not} include these.
+Both NY and classical analysis of Bloom filters speak of the number of bits used to represent the set~$\mathcal{S}$: the classical analysis means only the number of bits in the actual array, and NY make comparisons throughout between the number of bits~$m$ used by their instantiations and the classical bounds.
+Moreover, the Bloom filter they construct in one of their main positive results clearly \emph{does not} count as part of the representation size the hash functions used to indicate array locations.
+%Thus, if we assume that
+%$\mathbf{B}_1$ is sampling $h_1,h_2,\ldots,h_k$, it seems that their
+%formalization fails to capture the basic Bloom filter construction;
+%at best, it is hard to see clearly that it does.
+
+%\jnote{FWIW, I think the classical description of Bloom filters has the same problem.
+I.e., if the hash functions are not fixed, then their description should be counted as part of the length of the data structure.
+On the other hand, if they are fixed, then the false-positive rate is not well-defined (since there is no probability space to speak of).
+So in that sense, NY just carried over the problem from the classical literature.}
+%
+%\tsnote{One can suggest that it \emph{should} be counted in the classical description, but the fact is that it isn't :) And in the 30+ years since the original paper, no one saw fit to correct this?
+From an algorithmic perspective, I think the classical approach makes sense.
+The questions being answered are: how many bits do I need to store a representation of the set for a given FP rate, and how does this compare to the combinatorially computed lower-bound?
+The description length of the hash functions may be bigger or smaller, but the number of bits you need to hold the set representation is independent of that.
+(Imagine that you have long random bitstrings in the set~$\mathcal{S}$.
+Then whether your hash functions simply truncate, or they are random oracles, the size of the representation as a function of the target FP rate doesn't change.
+Yet the description lengths of the hash functions are drastically different.)}
+
+On the other hand, assume the hash functions are implicitly hard-coded into~$\mathbf{B}_1$ (and $\mathbf{B}_2$).
+Then we can treat~$\mathbf{B}_1$ as deterministic, since it will simply carry out the steps required to populate an array using these hash functions, and output the array~$M$ as the representation.
+If the descriptions of~$\mathbf{B}_1,\mathbf{B}_2$ are known to the adversary, who is also provided with~$\mathcal{S}$, then the adversary can compute~$M$ itself, as well as test for false positives itself.
+So it isn't clear how the security notion helps to reason about difficulty of finding a false-positive.
+Moreover, NY stresses (at least once) that the representation is \emph{not} given to the adversary in their notions.
+So it seems unlikely that they intended for $h_1,h_2,\ldots,h_k$ to be hard-coded into the algorithms.
+\jnote{Perhaps it is reasonable to consider a definition in which the set is not given to the adversary?}
+\tsnote{A FP security notion?
+Yes, perhaps so.
+It's probably a more realistic notion anyway -- is a spammer really going to know my whitelist a priori?
+(If he does, I probably have bigger problems in my system than receiving new spam email.) Or set of URLs cached by a CDN server?}
+
+Continuing on this point, it seems that the coins of~$\mathbf{B}_1$ (whatever their use) are intended to be kept secret from the adversary.
+Thus, to the extent that it addresses real Bloom filters at all, the NY security notion only addresses applications in which the representation is created using secret coins.
+But many real-world applications of Bloom filters have no secrets.
+NY point to web proxies, which use Bloom filters to compactly represent the objects they store locally, as motivation for their work.
+But real web proxies like Squid~\cite{xxx} do \emph{not} use secrets in their Bloom filters.
+Squid, in particular, uses the basic Bloom filter with four hash functions, defined as follows: $h_1(x) = \mathrm{MD5}(x)[0,\ldots,31]$, $h_2(x)=\mathrm{MD5}(x)[32,\ldots,63]$, $h_3(x)=\mathrm{MD5}(x)[64,\ldots,95]$, and $h_4(x)=\mathrm{MD5}(x)[96,\ldots,127]$.
+Likewise, there are no secrets in the Bloom filters used by Google's BigTable~\cite{xxx}, HBase~\cite{xxx}, \tsnote{make an impressive list.}
+
+There are applications in which the proposed Bloom filter instantiations do use secretly keyed hash functions, e.g.
+$h_j(x) = (f(K_0,x) + j\cdot g(K_1,x))\bmod m$, where $j\in[1,k]$, $m$ is the number of bits in the array, and where $f,g$ are PRFs keyed by secrets $K_0,K_1$.
+This particular ``encrypted Bloom filter'' instantiation was suggested for use in efficient linking of records across separate medical record databases~\cite{schnell2011novel}.
+(It was subsequently shown not to be secure by Niedermeier et al.~\cite{niedermeyer2014cryptanalysis}, where a clever use of frequency analysis recovered the last names of patients given access only to the Bloom filter array.)
+In any case, it is clear that the NY definition does not capture the most widely used applications of Bloom filters, e.g. CDN summary caches, P2P network routing algorithms, etc.
+%\tsnote{Could also point out that their positive results use constructions that have secret keys, and these are unlikely to be of any use in major applications like CDNs or P2P networks.
+But maybe the horse is sufficiently beaten by now...}
+
+%\tsnote{What about content-based routing, or whatever that field is calling itself now?  A Bloom filter seems likely to be used there, and you'd want privacy for at least the content-seeker.}
+
+\heading{Our contributions. }
+Given these shortcomings and the prevalent use of Bloom filters in practice, we revisit the matter of formalizing them as primitives with explicit security goals, these goals being abstracted from the attack surface they expose in practice.
+We begin by giving a new syntax for hash-based filters, which more clearly captures Bloom filters...
+
+We generalize this syntax to hash-based filters that are mutable,
+%\jnote{I find ``mutable'' a slightly awkward term, maybe because it makes me think of mutability in the context of programming languages.
+In much data structures literature, this is called the ``dynamic'' case, in contrast to the ``static'' case.}
+%
+%\tsnote{I adopted this term after reading it in some bloom filter paper(s).
+Ironically, I liked it for the same reason you think it is awkward :) My PL association to the term is that an immutable object is one whose state cannot be modified after it is created, and a mutable object is the opposite.
+But I don't really care too much.}
+in the sense
+that they allow for updating of the representation. This allows us
+to capture counting Bloom filters, spectral Bloom filters, stable
+Bloom filters, count-min sketches, and other compact set
+representation data structures...
+
+We provide various security notions for these primitives...
+FP with private, public representation coins; set privacy with private, public representation coins; FP/set privacy in the multi-representation setting (outsider attack, think CDNs); FP/set privacy in the multi-representation setting with corruptions (insider attack, think P2P networks) \tsnote{Those are just the ones that come to mind now.
+Could also consider authenicity of representations, think CDN or P2P settings.}
+
+We show that...
+
+\heading{Related work: attacks}
+\begin{itemize}
+\item Niedermayer et al., ``Cryptanalysis of Basic Bloom Filters Used for Privacy-Preserving Record Linkage'', breaking privacy of secret-hash-function Bloom filters.
+\tsnote{Journal of Privacy and Confidentiality, 2014}
+\item Gerbet, Kumar and Lauradoux, ``The power of evil choices in bloom filters''.  \tsnote{DSN'15: Looks like a real goldmine of related work!}
+\item Crosby and Wallach, ``Denial of Service via Algorithmic Complexity Attacks'' \tsnote{Gives attacks on Squid}
+\item Gao et al., ``Internet Cache Pollution Attacks and Countermeasures''
+\end{itemize}
+
+\heading{Related work: definitions(?)}
+\begin{itemize}
+\item Nojima and Kadobayashi, ``Cryptographically Secure Bloom Filters''.
+\tsnote{Gives some security definitions for privacy.
+Quick scan, not super clear what they achieve.
+The definition of client-privacy (Definition 1) for example, makes no sense to me.
+Actually, likewise for server-privacy (Definition 2).
+Both seem vague and thoroughly underspecified.}
+\item Naor and Yogev
+\item Eujin Goh, ``Secure Indexes'' \tsnote{A secure index can
+    be used for set membership.  Builds a secret-key data
+    structure (an Index) that allows searching for keyword~$w$
+    if one holds the trapdoor $T_w$ for~$w$, where the trapdoor
+    depends on the secret key.  Main construction uses
+    traditional Bloom filters and a PRF.  Construction appears
+    quite inefficient, needing a very long secret key, turning a
+    keyword~$w$ into a bunch of PRF outputs, and then storing
+    each of these PRF outputs in the BF.  Havent read the full
+    analysis; don't know if this was ever published. }
+    \jnote{Never published. I think this work uses Bloom filters
+    for encrypted search; I don't remember the paper having much
+    to say about Bloom filters themselves.}
+\end{itemize}
+
+\heading{Related work: constructions}
+\begin{itemize}
+\item Bellovin and Cheswick, ``Privacy-Enhanced Searches Using
+    Encrypted Bloom Filters''.
+\item Kerschbaum , ``Public-Key Encrypted Bloom Filters with Applications to Supply Chain Integrity''.
+\item S\"{a}rell\"{a} et al., ``BloomCasting: Security in Bloom Filter Based Multicast''.
+\item Dong, Chen, Wen, ``When Private Set Intersection Meets Big Data: An Efficient and Scaleable Protocol'' \tsnote{``garbled bloom filters'', which actually store the set element by storing~$k$ xor-shares, one at each of the~$k$ hash indices (with care for reusing shares if hash collisions occur); also and``oblivious bloom intersection''}\tsnote{If the filter and the hash functions are public, there is a naive attack that works for some interesting parameters.
+Pick~$k$ positions $i_1,i_2,\ldots,i_k$, xor strings at these positions to get a candidate~$x$.
+If $h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots \wedge h_k(x) = i_k$ then either $x \in S$ or~$x$ is a false-positive.
+(You don't have to do all~$k$ hashes, you can stop as soon as one fails to match the index.) Say you have a 1000-position filter ($m=1000$) and a 100-element set ($n=100$), and you are willing to tolerate a 1\% FP rate.
+Then you'd set $k=4$ (a la Squid).
+There are roughly $2^{35}$ subsets of 4 indices to consider, which is reasonable on a laptop these days.
+(Also, since $n=100$ the expected number of trials is roughly $2^{28}$.) With the FP rate of 1\%, if you find a winner then almost certainly it is in the set.
+Granted, this attack is naive, but notice that you \emph{cannot} mount it against a standard Bloom filter.
+Also notice that this attack might be significantly more efficient than brute force guessing over the universe of inputs (imagine that $U=\bits^{64}$), even if you know that the distribution deviates significantly from uniform.
+}
+\item Tarkoma, Rothenberg, Lagerspetz ``Theory and Practice of Bloom Filters in Distributed Systems'' \tsnote{Great high-level coverage.  Only found preprint version though.}
+\item Durham, Kantarcioglu, Xue, Kuzu, Malin ``Composite Bloom Filters for Secure Record Linkage'' \tsnote{Per-field BFs, sampled and composed into single BF that is then permuted by a secret random permtation.
+No clear statement of the problem that is being solved.
+Should pull full version and get details.}
+\end{itemize}
+
+\heading{Related work: tangential}
+\begin{itemize}
+\item Chang and Mitzenmacher ``Privacy Preserving Keyword Searches on Remote Encrypted Data''.
+\item Mitzenmacher and Vadhan. ``Why Simple Hash Functions Work: Exploiting the Entropy in a Data Stream''.
+\item Dodis et al.
+``Fuzzy Extractors: How to Generate Strong Keys from Biometrics and Other Noisy Data'' \tsnote{Introduces ``secure sketches'', which is a representation of a single-element set that is information theoretically private (up to some function of the min-entropy of the element); only tangentially related to ``sketches'' as defined in the Bloom filter literature.}
+\end{itemize}
+
+\if{0}
 \paragraph{Basic issues in Naor-Yogev. }

### 2016-09-30 notions.tex

@@
 The definition can be lifted to the random-oracle model by providing
-all algorithms (namely, $\Rep,\Qry$, and the adversary~$A$) with access to the
-random oracle. \fixme{I think we should *not* allow $S$ to depend on
-  the RO.  That's like letting $S$ depend on $\pub$ in the standard
-  model, but $\pub$ hasn't been fixed yet.  } \jnote{I disagree. Plus if you do that, then
-  you put the simulator at an unfair disadvantage. (Consider a scheme that always appends
-  $H(0)$ to $\pubaux$, for every~$S$. The simulator will never be able to simulate that---even
-  if you give it~$S$!---simply because it can't guess~$H(0)$).}
+algorithms $\Rep,\Qry$ with access to the
+random oracle, and providing $A$ with such access as well in the
+second stage of its execution. (We do not provide $A$ with access to
+the random oracle during the first stage when it selects~$S$, as that set
+should have no dependence on the random oracle.) \jnote{In ``practice'' wouldn't someone
+just use SHA as their random oracle, hence providing an attacker with the ability
+to make $S$ depend on the random oracle? This point needs to be justified a bit.}
 

### 2016-09-30 results.tex

@@
 unless $S$ is small. Nevertheless, it does convey the intuition that
-the \emph{only} information leaked by the data structure is the
-sizes of the various intersections of the~$\{B_x\}$ sets.
+the information leaked by the data structure is \emph{at most} the
+sizes of the various intersections of the~$\{B_x\}$.
 

### 2016-09-30 ds-correctness.tex
changes to GBF and BF
correctness proofs of lin and ds updated

@@
 
-\begin{proof}[Theorem~\ref{thm:xxx}]
+\begin{proof}[Theorem~\ref{thm:ds-correctness}]
 \fixme{Animesh: remove these Cref things and replace with references
   like I have them in the text.}
-We use a game playing argument (shown in \Cref{fig:2TGame}) similar to \Cref{thm1} to prove this theorem.
-In \game{0}, adversary attacks the correctness game with  hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpCorrect{\setprim_{\mathrm{ds}},r}{A}$.
+We use a game playing argument to prove this theorem.
+Please refer to Figure~\ref{fig:ds-correctness-games}.
+In game \game{0}, adversary, $A$ attacks the correctness game with  hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpCorrect{\setprim_{\mathrm{ds}},r}{A}$.
 \begin{equation}
-\AdvCorrect{\setprim_{\mathrm{ds}},r}{A} = \Prob{\game{0}(A)=1}\label{eq:2T0}
+\AdvCorrect{\setprim_{\mathrm{ds}},r}{A} = \Prob{\game{0}(A)=1}
 \end{equation}
 
-Let $B$ be a prf-adversary as shown in \Cref{fig:2TD}. Based on its challenge bit $b$, it exactly simulates $\game{0}$ or $\game{1}$. So,
+In game $\game{1}$, $A$ attacks a different filter $\tilde{\setprim}_\mathrm{ds}$, in which $F_K$ is replaced by a random function.
+Let $B$ be a prf-adversary as shown in Figure~\ref{fig:ds-correctness-adv}.
+Based on its challenge bit $b$, it exactly simulates $\game{0}$ or $\game{1}$.
+So,
 \begin{align*}
-\Prob{\ExpPRF{F}{B} = 1\,|\,b=1} &= \Prob{\game{0}(A)=1} \\%\label{eq:m1}\\
+\Prob{\ExpPRF{F}{B} = 1\,|\,b=1} &= \Prob{\game{0}(A)=1} \\
 \Prob{\ExpPRF{F}{B} = 1\,|\,b=0} &= 1-\Prob{\game{1}(A)=1}
@@
 By a standard conditioning of PRF advantage, we have
-
 \begin{equation*}
@@
 
-In $\game{1}$, $A$ attacks a different filter $\tilde{\setprim}_\mathrm{ds}$, in which $F_K$ is replaced by a random function.
-$\game{2}$ and $\game{3}$ on the other hand use lazy sampling in $\Hash$ to select random values from $[m]$.
-It can be observed that, except  $\Hash$, $\game{2}$ and $\game{3}$ are identical to $\game{3}$ and $\game{4}$ of previous theorem.
-Since, $\Hash$ in all of these games returns random values, the analyses and intermediate results of \Cref{thm1} apply to this theorem as well.
-Therefore,
-\begin{align*}
-\Prob{\game{1}(A)=1} = \Prob{\game{2}(A)=1}\\
-\Prob{\game{3}(A)=1} = \frac{1}{\dbinom{q}{r}}\Prob{\game{2}(A)=1}
-\end{align*}
+Coming back to the game playing argument, in game $\game{2}$, $\Hash$ returns random values sampled from $[m]$, assuming $A$ makes no pointless queries.
+In addition, the $\Test$ oracle keeps a counter, $c$ to keep track of the number of queries by $A$ to the $\Test$.
+It also sets a boolean $\bad$ flag to $\false$ if queries which are not indexed by the $r$-set $\calI$ are false-positives, and queries indexed by set $\calI$ are not false-positives.
+It must be noted that $\bad$ does not affect the output of the $\Test$ or the game.
+We argue that, $\Prob{\game{1}(A)=1} \leq \Prob{\game{2}(A)=1}$.
+Game $\game{3}$ is identical to $\game{2}$, except it returns 0 if $\bad$ is set to $\true$.
+$\game{3}$ returns 1 whenever $\game{2}$ would return 1, and $\bad$ remained false in $\game{2}$.
+So, basically $\game{3}$ guessed exactly the $r$ queries that results in errors.
+Hence, $\Prob{\game{3}(A)=1} = \frac{1}{\binom{q}{r}}\Prob{\game{2}(A)=1}$.
 
-Let $D$ be a zero-query adversary (shown in \Cref{fig:D}) that finds ~$r$ false positives against $\tilde{\setprim}_{\mathrm{ds}}$.
-Using explanations from previous theorem, if $A$ wins $\game{3}$, then $D$ wins $\ExpCorrect{\tilde{\setprim}_{\mathrm{ds}},r}{\cdot}$ game.
-So,
-\begin{equation*}
-\AdvCorrect{\tilde{\setprim}_{\mathrm{ds}},r}{D} = \Prob{\game{3}(A) = 1}\label{eq:2T8}
-\end{equation*}
+Let $D$ be a zero-query adversary(shown in Figure~\ref{fig:lin-correctness-zq-adv}) corresponding to $A$ attacking $\game{3}$; it finds $r$ false positives against $\tilde{\setprim}_{\mathrm{ds}}$.
+It simulates the~$\Test$ oracle by returning 1 on the guessed queries, and 0 otherwise; and it halts after finding $r$ FP's.
+Intuitively, it  guesses which~$r$ of~$A$'s queries will be false positives.
+So, $\AdvCorrect{\tilde{\setprim}_{\mathrm{ds}},r}{D} = \Prob{\game{3}(A) = 1}$.
 
-Note that like $\tilde{\setprim}_{\mathrm{lin}}$, $\tilde{\setprim}_{\mathrm{ds}}$ is the scheme that is analyzed in the classical Bloom filter literature.
-So, for a zero-query adversary $D$ and $r=1$, the upper bound on false-positive probability of a classical Bloom filter applies to $\tilde{\setprim}_{\mathrm{ds}}$ as well.
+It can be easily seen that  $\tilde{\setprim}_{\mathrm{ds}}$ is the scheme that is analyzed in the classical Bloom filter literature.
+So, for a zero-query adversary $D$ and $r=1$, advantage of $D$ to win $\ExpCorrect{\tilde{\setprim}_{\mathrm{ds}},r}$ will be upper bounded by the false-positive probability of a classical Bloom filter.
 For $r > 1$, based on the assumption that $A$ makes no pointless queries, the queries made by $A$ are distinct and not elements of the original set $S$.
-Also, since $\game{3}$ uses independent random functions, the event of getting a false positive is independent of the index of the query.
-So,
-\begin{equation*}
-\AdvCorrect{\tilde{\setprim}_{\mathrm{ds}},r}{D} =   {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
-\end{equation*}
+Also, since $\Hash$ in $\game{3}$ returns $k$ random values for each query, the event of getting a false positive is independent of the index of the query.
+So, $\AdvCorrect{\tilde{\setprim}_{\mathrm{ds}},r}{D} =   {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r$
+
 \noindent
@@
 \]
-which is the bound claimed in the theorem statement. %\hfill \qed
+which is the bound claimed in the theorem statement. \hfill \qed
 
@@
 if $\err  < r$ then Return 0\\
-Return 1\\\\
-%
+Return 1
+
+\medskip
 \oracle{$\TestOracle(\qry_x)$}\\
@@
 if $a \neq \qry_x(S)$ then $\err \gets \err + 1$\\
-Return~$a$\\\\
-%
+Return~$a$
+
+\medskip
 \oracle{$\HashOracle(x)$}\\
@@
 \underline{\game{2}(A)\fbox{\game{3}(A)}}\\
-$c\gets 0$, $\bad \gets \false$, $\err \gets 0$;  $\calC \gets \emptyset$\\
-$S \getsr \distr{\calS}{}$; $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
+$c\gets 0$; $\err \gets 0$\\
+$\bad \gets \false$\\
+$\calC \gets \emptyset$\\
+$S \getsr \distr{\calS}{}$\\
+$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
 $(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
@@
 if $v \neq \qry_x(S)$ then $\err \gets \err +1$\\
-Return~$v$\\\\
-%
+Return~$v$
+
+\medskip
 \oracle{$\HashOracle(x)$}\\
@@
 }
-\caption{\Cref{thm2}: Game playing argument}\label{fig:2TGame}
+\caption{Games $\game{0}$-$\game{3}$ for the
+proof of Theorem~\ref{thm:ds-correctness}.}
+\label{fig:ds-correctness-games}
 \fixme{Animesh: remove Crefs, fix captions to look like the classical
@@
 \centering
-\fpage{0.5}{
+\fpage{.8}{
+\hpagessl{.5}{.35}
+{
 $\adversaryv{B^{\calO}(S, \pubaux)}$\\
@@
 \nudge if $\err  < r$ then Return 0\\
-\nudge Return 1\\\\
-%
-%
+\nudge Return 1
+
+\medskip
 \oracle{$\HashOracle(x)$}\\
-\nudge Return $\OK$, for $j\in[1,k]$\\
+\nudge Return $\OK$, for $j\in[1,k]$
 }
-\caption{\Cref{thm2}: PRF adversary $B$ simulating $\game{1}(A)$ and
-  $\game{2}(A)$} \label{fig:2TD}
+{
+$\adversaryv{D(S, \pubaux)}$\\[4pt]
+$c \gets 0$\\%, $\calX \gets \emptyset$\\
+$\calC \gets \emptyset$; $\err \gets 0$\\
+$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
+Run $A(\pubaux)$\\
+When $A$ asks $\TestOracle(\qry_x)$:\\
+\nudge if $x \in \mathcal{C}$ then Return $\bot$\\
+\nudge $\calC \gets \calC \cup x$\\
+\nudge $c \gets c+1$\\
+\nudge $r \gets 0$\\
+\nudge if $c \in \mathcal{I}$\\
+\nudge \nudge $r \gets 1$\\
+\nudge \nudge $\err \gets \err + 1$\\
+\nudge Return $r$\\
+When $A$ halts:\\
+\nudge Return $\bot$
+}
+}
+\caption{Left: Adversary $B$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively for the
+proof of Theorem~\ref{thm:ds-correctness}.
+Right: Zero-query adversary $D$ for Theorems~\ref{thm:ds-correctness} and ~\ref{thm:lin-correctness}.}\label{fig:ds-correctness-adv}\label{fig:lin-correctness-zq-adv}
 \fixme{Animesh: remove Crefs, make caption refer to correct theorem}

### 2016-09-30 intro-old.tex
correctness proofs of lin and ds updated

@@
 NY point to web proxies, which use Bloom filters to compactly represent the objects they store locally, as motivation for their work.
-But real web proxies like Squid~\cite{xxx} do \emph{not} use secrets in their Bloom filters.
+But real web proxies like Squid~\cite{fan2000summary} do \emph{not} use secrets in their Bloom filters.
 Squid, in particular, uses the basic Bloom filter with four hash functions, defined as follows: $h_1(x) = \mathrm{MD5}(x)[0,\ldots,31]$, $h_2(x)=\mathrm{MD5}(x)[32,\ldots,63]$, $h_3(x)=\mathrm{MD5}(x)[64,\ldots,95]$, and $h_4(x)=\mathrm{MD5}(x)[96,\ldots,127]$.
-Likewise, there are no secrets in the Bloom filters used by Google's BigTable~\cite{xxx}, HBase~\cite{xxx}, \tsnote{make an impressive list.}
+Likewise, there are no secrets in the Bloom filters used by Google's BigTable~\cite{chang2008bigtable}, HBase~\cite{xxx}, \tsnote{make an impressive list.}
 

### 2016-09-30 lin-correctness.tex
lin correctness proof fixes
correctness proofs of lin and ds updated

@@
 \nudge if $\err  < r$ then Return 0\\
-\nudge Return 1\\\\
-%
+\nudge Return 1\\
+
+\medskip
 \oracle{$\HashOracle(x)$}\\
@@
 \nudge if $\err  < r$ then Return 0\\
-\nudge Return 1\\\\
-%
+\nudge Return 1
+
+\medskip
 \oracle{$\HashOracle(x)$}\\
@@
 Return 1\\
-%
+
+\medskip
 \oracle{$\TestOracle(\qry_x)$}\\
@@
 Return~$a$\\
-%
+
+\medskip
 \oracle{$\HashOracle(x)$}\\
@@
 if $a \neq \qry_x(S)$ then $\err \gets \err + 1$\\
-Return~$a$\\\\
-%
+Return~$a$\\
+
+\medskip
 \oracle{$\HashOracle(x)$}\\
@@
 Return~$v$\\
-%
+
+\medskip
 \oracle{$\HashOracle(x)$}\\
@@
 
-%\caption{Non-adaptive adversary $D$ simulating $\game{4}(A)$} \label{fig:D}
-\begin{figure}
-\centering
-\fpage{0.35}
-{
-$\adversaryv{D(S, \pubaux)}$\\[4pt]
-$c \gets 0$\\%, $\calX \gets \emptyset$\\
-$\calC \gets \emptyset$; $\err \gets 0$\\
-$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
-Run $A(\pubaux)$\\
-When $A$ asks $\TestOracle(\qry_x)$:\\
-\nudge if $x \in \mathcal{C}$ then Return $\bot$\\
-\nudge $\calC \gets \calC \cup x$\\
-\nudge $c \gets c+1$\\
-\nudge $r \gets 0$\\
-\nudge if $c \in \mathcal{I}$\\
-\nudge \nudge $r \gets 1$\\
-\nudge \nudge $\err \gets \err + 1$\\
-\nudge Return $r$\\
-When $A$ halts:\\
-\nudge Return $\bot$
-}
-\caption{Zero-query adversary $D$ for Theorem~\ref{thm:lin-correctness}.} \label{fig:lin-correctness-zq-adv}
-\fixme{For what theorem?}
-\end{figure}
-
 \end{proof}

### 2016-09-30 BF_correctness.tex
cheers

@@
 We use a game playing argument, please refer to Figures~\ref{fig:bf-correctness-games1} and~\ref{fig:bf-correctness-games2}.
-In game $\game{0}$, the $\Hash$ oracle performs lazy sampling of elements from $[m]$ to mimic a random oracle (RO).
-For every distinct query, $\Hash$ returns a random value sampled from $[m]$.
+In game $\game{0}$, the $\HashOracle$ oracle performs lazy sampling of elements from $[m]$ to mimic a random oracle (RO).
+For every distinct query, $\HashOracle$ returns a random value sampled from $[m]$.
 It can be seen that, game $\game{0}$ exactly simulates the correctness game of $\setprim_{\mathrm{gbf}}$.
@@
 
-%tom here
 Game~$\game{4}$ contains some important changes from game~$\game{3}$, but we will argue that $\Prob{\game{3}(A) = 1} \leq \Prob{\game{4}(A) = 1}$.

### 2016-09-30 GBF-correctness-private-M.tex
changes before going home
cheers

--- 2016-09-30 GBF-correctness-private-M.tex
@@
 We use a game playing argument, please refer to Figures~\ref{fig:gbf-correctness-games1} and~\ref{fig:gbf-correctness-games2}.
-In game $\game{0}$, the $\Hash$ oracle performs lazy sampling of elements from $[m]$ to mimic a random oracle (RO).
-For every distinct query, $\Hash$ returns a random value sampled from $[m]$.
+In game $\game{0}$, the $\HashOracle$ oracle performs lazy sampling of elements from $[m]$ to mimic a random oracle (RO).
+For every distinct query, $\HashOracle$ returns a random value sampled from $[m]$.
 It can be seen that, game $\game{0}$ exactly simulates the correctness game of $\setprim_{\mathrm{gbf}}$.
@@
 This results in adversary getting $(k-1)$ hash values ``for free'', as we charge the adversary only for a single query.
-We alter the $\TestOracle$ oracle accordingly, so that it makes a single call $\Hash(\qry_x)$ rather than~$k$ such calls.
+We alter the $\TestOracle$ oracle accordingly, so that it makes a single call $\HashOracle(\qry_x)$ rather than~$k$ such calls.
 We do this so that we can assume that a call~$\HashOracle(\qry_x)$ is pointless after a~$\TestOracle(\qry_x)$ call, and this will aid us in subsequent games.
@@
 
-We note that since game~$\game{5}(A)$ returns iff~$A$ manages to find~$r$ errors the game managed to guess exactly which $\HashOracle$ queries would cause the errors, there is a zero-query adversary~$A_0$ that manages to find~$r$ errors.
-Namely, adversary~$A_0$
+When~$r=1$, Game~$\game{5}$ exactly simulates the
 
@@
 }
-%
-\fpage{.85}{
-\hpagessl{.45}{.5}
-{
-\adversaryv{$A_0(\pubaux)$}\\
-$c\gets 0$, $\calY \gets \emptyset$\\
-$\calC \gets \emptyset$\\
-$\mathcal{I}\getsr [\{1,2,\ldots,q_T + q_H\}]^r$\\
-$\bot \getsr A^{\TestOracle,\HashOracle}(\pubaux)$\\
-Return~$\calY$
-
-\oracle{$\TestOracle(\qry_x)$}\\
-if $x \in \mathcal{C}$ then Return $\bot$\\
-$\calC \gets \calC \cup x$\\
-if $\Ans[x] = \undefined$\\
-\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(\qry_x)$\\
-Return $\Ans[x]$\\
-}
-{
-\oracle{$\HashOracle(\qry_y)$}\\
-$c \gets c + 1$\\
-for $j \in \{1,2,\ldots,k\}$\\
-\nudge $v_j \getsr [m]$\\
-%
-if $c \not\in \calI$ then \\
-\nudge $\Ans[y] \gets (0, (v_1, \ldots, v_{k}) )$\\
-\nudge Return $\left(v_1,\ldots,v_k\right)$\\
-$\calY \gets \calY \cup \{y\}$\\
-$\Ans[y] \gets (1, (v_1, \ldots, v_{k}))$\\
-Return $\left(v_1,\ldots,v_k\right)$
-}
-}
 \caption{Games $\game{4}$-$\game{5}$ and zero-query adversary~$A_0$ for the

### 2016-10-01 results.tex
Spell check

@@
 \end{theorem}
-\fixme{This result is pretty intutitive following the classic BF correctness result. Probably fine to just explain it and push an appendix, or even drop from camera ready if out of space.}
+\fixme{This result is pretty intuitive following the classic BF correctness result. Probably fine to just explain it and push an appendix, or even drop from camera ready if out of space.}
 We note that Kirsch and Mitzenmacher~\cite{kirsch2006less} show
@@
   data structure $\setprim_{\mathrm{lin}}$ {\bf Right:}
-The scheme from Niedermeyer et al.\cite{xxx}, $\setprim_{\bilin}$.
+The scheme from Niedermeyer et al.\cite{niedermeyer2014cryptanalysis}, $\setprim_{\bilin}$.
 The $\mathsf{bigram}$ algorithm takes a
@@
 The domain-separated PRF-hash requires~$k$ PRF evaluations per set-membership query, and this may be unattractive in certain use cases.
-Kirsch and Mitzenmacher~\cite{kirsch2006less} have shown that two PRF evaluations suffices, defining the hash functions to be $h_i(x)=F_K(\langle 1,x \rangle) + j\cdot F_K(\langle 2,x \rangle) \bmod m$, where~$m$ is the bitlength of the Bloom filter.\footnote{Actually, they define $h_i(x)=F_{K_1}(x)  + j\cdot F_{K_2}(x) \bmod m$, using distinct keys instead of domain-separation, but the constructions are equivalent with respect to security.} We call this the \emph{linear PRF-hash} Bloom Filter.
+Kirsch and Mitzenmacher~\cite{kirsch2006less} have shown that two PRF evaluations suffices, defining the hash functions to be $h_i(x)=F_K(\langle 1,x \rangle) + j\cdot F_K(\langle 2,x \rangle) \bmod m$, where~$m$ is the bit-length of the Bloom filter.\footnote{Actually, they define $h_i(x)=F_{K_1}(x)  + j\cdot F_{K_2}(x) \bmod m$, using distinct keys instead of domain-separation, but the constructions are equivalent with respect to security.} We call this the \emph{linear PRF-hash} Bloom Filter.
 In this section, we show that this scheme is both correct and private with respect to our SS notion.
@@
 
-%%%%%%%%%%%%%%%%% BIGRAM LINEAR-PRF (AKA "NEIDERMAYER")  %%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%% BIGRAM LINEAR-PRF (AKA "NIEDERMEYER")  %%%%%%%%%%%%%%%%%%%%
 \subsection{Bigram Linear-PRF Construction}
-%\heading{Bigram Linear-PRF construction (``Neidermayer''). }
+%\heading{Bigram Linear-PRF construction (``Niedermeyer''). }
 %\heading{Correctness.}
@@
 This construction is of practical interest, as it has been suggested as a way to address the privacy-preserving record-linkage problem, in particular for linking common records in medical databases~\cite{niedermeyer2014cryptanalysis,schnell2011novel}.
-We only address the privacy of this construction, as the correctness follows immediately from the correctness of the Linear-PRF contruction.
+We only address the privacy of this construction, as the correctness follows immediately from the correctness of the Linear-PRF construction.
 The privacy, however, does not.
@@
 \todo{OW privacy proof?
-Or just some text that says that Niedermeyer et al show something stronger~---OW-privacy violation---~albeit with $n=10000, m=10000\alpha$ for an $\alpha$ that I need to look up.}
+Or just some text that says that Niedermeyer et al.
+show something stronger~---OW-privacy violation---~albeit with $n=10000, m=10000\alpha$ for an $\alpha$ that I need to look up.}
 
@@
 bit~$z$, so at best it can cause~$A$ to output 1 with
-probabilility~$1/2$.  That is $\ExpPrivSSsim{\setprim_{\bilin}}{A,\Sim} \leq 1/2$. \hfill\qed
+probability~$1/2$.  That is $\ExpPrivSSsim{\setprim_{\bilin}}{A,\Sim} \leq 1/2$. \hfill\qed
 \end{proof}
@@
 client obtains a GBF for $S_1 \cap S_2$ (the server learns nothing).
-The authors note that the GBF is a new set-membership data strucure
+The authors note that the GBF is a new set-membership data structure
 that may be of general interest, so we explore its correctness and
@@
   this is independent of~$k,m,n$; although $k>1$ is required for the
-  xor shares.)  However, this analysis implicilty assumes that the potential false-positive string~$x$ is fixed
+  xor shares.)  However, this analysis implicitly assumes that the potential false-positive string~$x$ is fixed
 \emph{before}~$M$ is determined.  We will see that this carries over
@@
 set-membership query would be prohibitive in many applications, and a
-$2^{-80}$ false-postive rate would be typically considered overkill in
+$2^{-80}$ false-positive rate would be typically considered overkill in
 practice.\footnote{Note
 that, as described in~\cite{xxx}, $\lambda$ must be at least the
-bitlength of the longest element $x \in S$. \tsnote{This could be
+bit-length of the longest element $x \in S$. \tsnote{This could be
   handled with a slight change to the set membership test, by checking
@@
 
-\item Cast Neidermayer et al.\ attacks on the bigram/PRF-based double-hashing construction (see their paper) into our formalism.
+\item Cast Niedermeyer Niedermeyer et al.\ attacks on the bigram/PRF-based double-hashing construction (see their paper) into our formalism.
 \tsnote{Note that their attack would allow one to recover \emph{every} name, not just one.}
 
-\item Prove a privacy bound for the bigram/PRF-based double-hashing construction that Neidermayer et al.\ attacks.
+\item Prove a privacy bound for the bigram/PRF-based double-hashing construction that Niedermeyer et al.\ attacks.
 I expect that the provable security bound is considerably worse than the min-entropy because of the way the representation is made.
@@
 
-\item Prove privacy bounds of other suggestions, such as the record-level BF from Durham et al.?  This would be a nice pairing with the Neidermayer et al.\ results \tsnote{No time.}
+\item Prove privacy bounds of other suggestions, such as the record-level BF from Durham et al.?  This would be a nice pairing with the Niedermeyer et al.\ results \tsnote{No time.}
 

### 2016-10-01 tasks_and_ideas.tex
Spell checks

@@
 \tsnote{Not sure if this requires new syntax and/or notions.
-But basically this is what the Neidermayer et al.\ attacks exploit -- that medical records consist of multiple fields, and the record-linkage protocol produces a BF for each field.
+But basically this is what the Niedermeyer et al.\ attacks exploit -- that medical records consist of multiple fields, and the record-linkage protocol produces a BF for each field.
 (If you think of records as rows in a DB, there's a BF for each column.) One of the fields is the patient's surname, and the attack uses clever frequency analysis to recover surnames.}
@@
 Perhaps populate the filter with a random sampling of URLs from the Alexa top 1000.
-(How large a sample?)  Given access to the filter, we can probably use the same attacks leveraged by Niedermayer et al.\ to infer information about which URLs are cached.
+(How large a sample?)  Given access to the filter, we can probably use the same attacks leveraged by Niedermeyer et al.\ to infer information about which URLs are cached.
 Of course, there's a timing based attack, just pinging the Squid proxy with URLs.
@@
 
-\item Speaking of the Niedermayer et al.
+\item Speaking of the Niedermeyer et al.
 attacks, these exploit the fact that there are different bloom filters for different record identifiers (i.e.

### 2016-10-01 intro.tex
Spell check
spell check

@@
   theorem), and that often the most technically difficult part is
-  connnecting the adaptive setting to the zero-query setting.}
+  connecting the adaptive setting to the zero-query setting.}
 
@@
   hierarchical BFs, count-min-sketches, etc.); security of common
-  usages of BF and related data structrues (e.g. CDNs and other
+  usages of BF and related data structures (e.g. CDNs and other
   distributed storage, find more); more generally bringing to the
@@
     keyword~$w$ into a bunch of PRF outputs, and then storing
-    each of these PRF outputs in the BF.  Havent read the full
+    each of these PRF outputs in the BF.  Haven't read the full
     analysis; don't know if this was ever published. }

### 2016-10-01 GBF-correctness-private-M.tex
gbf still

@@
 }
+\fpage{.85}{
+\hpagessl{.45}{.5}
+{
+\underline{$\game{6}(A)$}\\
+$c\gets 0$, $\bad \gets \false$\\
+$\err \gets 0$;  $\calC \gets \emptyset$\\
+$S \getsr A$\\
+$\mathcal{I}\getsr [\{1,2,\ldots,q_T + q_H\}]^r$\\
+$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+$\bot \getsr A^{\TestOracle,\HashOracle}(\pubaux)$\\
+if $\bad = \true$ then Return 0\\
+if $\err  < r$ then Return 0\\
+Return 1\\
+
+\oracle{$\TestOracle(\qry_x)$}\\
+if $x \in \mathcal{C}$ then Return $\bot$\\
+$\calC \gets \calC \cup x$\\
+if $\Ans[x] = \undefined$\\
+\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(\qry_x)$\\
+Return $\Ans[x]$\\
+}
+{
+\oracle{$\HashOracle(\qry_y)$}\\
+$c \gets c + 1$\\
+for $j \in \{1,2,\ldots,k\}$\\
+\nudge $v_j \getsr [m]$\\
+%
+$M \gets\privaux$\\
+$y' \gets M[v_1] \xor M[v_2] \xor \ldots \xor M[v_k]$\\
+if $y' \neq y$ then \\
+\nudge $\Ans[y] \gets (0,y', (v_1, \ldots, v_{k}) )$\\
+\nudge if $c \in \calI$ then $\bad \gets \true$\\
+\nudge Return $\left(v_1,\ldots,v_k\right)$\\
+if $c \notin \calI$ then $\bad \gets \true$\\
+$\err \gets \err +1$\\
+$\Ans[y] \gets (1, (v_1, \ldots, v_{k}))$\\
+Return $\left(v_1,\ldots,v_k\right)$
+}
+}
 \caption{Games $\game{4}$-$\game{5}$ and zero-query adversary~$A_0$ for the

### 2016-10-01 lin-correctness.tex

@@
 We give this~$D$ in Figure~\ref{fig:lin-correctness-zq-adv}.
-Intuitively, adversary~$D$ guesses which~$r$ of~$A$'s queries will be false positives; it simulates the~$\Test$ oracle by returning 1 on the guessed queries, and 0 otherwise; and it halts after finding $r$ FP's.
+Intuitively, adversary~$D$ guesses which~$r$ of~$A$'s queries will be false positives; it simulates the~$\Test$ oracle by returning 1 on the guessed queries, and 0 otherwise; and it halts after finding $r$ false-positives.
 It must be noted that, by the no-pointless queries assumption and the fact that the hash functions in $D$ are instantiated with random functions, $\pubaux$ is information theoretically independent of elements not in $S$.
@@
 \nudge $h_i(x) = F_{K}(\langle 1,x \rangle) + i\cdot F_{K}(\langle 2,x \rangle) \bmod m$\\
-Ret $\left(h_1(x),\ldots,h_k(x)\right)$
+Return $\left(h_1(x),\ldots,h_k(x)\right)$
 }
@@
 \nudge $h_i(x) = F_{K}(\langle 1,x \rangle) + i \cdot \rho(x) \bmod m$\\
-Ret $\left(h_1(x),\ldots,h_k(x)\right)$
+Return $\left(h_1(x),\ldots,h_k(x)\right)$
 }
@@
 \nudge $h_i(x) = \rho_1(x) + i \cdot \rho_2(x) \bmod m$\\
-Ret $\left(h_1(x),\ldots,h_k(x)\right)$
+Return $\left(h_1(x),\ldots,h_k(x)\right)$
 }

### 2016-10-01 syntax.tex
cheers

@@
 $\langle x,y,\ldots \rangle$ for the encoding of values $x,y,\ldots$
-as a single bitstring, for some implicit and invertible encoding
+as a single bit-string, for some implicit and invertible encoding
 method. When $x$ is a string, we write $x[i]$ for the $i$-th element
 in that string, and $x[i:j]$ for the substring $x[i]x[i+1]\cdots
-x[j]$.
+x[j]$.  \tsnote{need subset of size~$r$ notation}
 
@@
 
-\todo{Words :)  Can compare the (normal) error probability to
-  the adversarial soundness probability.  Perhaps pull back some of
-  the previous example for building intuition about the difference
-  between the two.}
-
 \begin{definition}[Error probability and rate] \rm
@@
 \end{definition}
+\todo{Words :)  Can compare the (normal) error probability to
+  the adversarial soundness probability.  Perhaps pull back some of
+  the previous example for building intuition about the difference
+  between the two.}
 
@@
 Wen~\cite{dong2013private}. \todo{Details have to be filled in.}
-This stores xor-shares of bitstring~$x \in S$ at positions
+This stores xor-shares of bit-string~$x \in S$ at positions
 $h_1(x),h_2(x),\ldots,h_k(x)$ in an array. Similarly, the

### 2016-10-01 intro.tex
related work

@@
 adversarial soundness for Bloom filters and, indeed,
-their worked served as inspiration for our own. Our work extends
+their work served as inspiration for our own. Our work extends
 their work significantly in several directions. For starters, we
@@
 
-\heading{Related work.} \jnote{See the discussion of related work in
+\heading{Related work.} 
+\input{related-work}
+\jnote{See the discussion of related work in
 Naor-Yogev. We should cite [LN93]. I can't tell how relevant [MNS11]

### 2016-10-01 BF_correctness.tex
Spell check
changes to BF

@@
 \fixme{for BF proof, this actually does more, it makes a hash query as good as a test query, because~$M$ is public.} Thus, $\Prob{\game{2}(A) = 1} \leq \Prob{\game{3}(A) = 1}$.
+We assume from Game~$\game{3}$ and on that $\Rep$ is also appropriately modifed for the new behavior of~$\HashOracle$.
 
-Game~$\game{4}$ contains some important changes from game~$\game{3}$, but we will argue that $\Prob{\game{3}(A) = 1} \leq \Prob{\game{4}(A) = 1}$.
-To begin, in game~$\game{4}$ we sample an $r$-subset of indices from~$\{1,2,\ldots,q_H+q_T\}$.
-(We will see why, shortly.)  Next, the $\TestOracle$ oracle on input~$\qry_x$ no longer computes its answer directly, but instead refers to a new table~$\mathrm{Ans}[x]$ which is populated upon calls to the $\HashOracle$ oracle.
-In particular, if $\mathrm{Ans}[x]$ is undefined, $\TestOracle$ makes a $\HashOracle(\qry_x)$ call; otherwise, it returns the contents of~$\mathrm{Ans}[x]$, which contains exactly the values that~$\TestOracle(\qry_x)$ would have returned in the previous game.
-The $\HashOracle$ oracle, on input~$\qry_y$ computes the random values~$v_1,v_2,\ldots,v_k$ as in $\game{3}$.
-(We no longer need to maintain the table~$T$ because hash values are only determined by~$\HashOracle$ calls, and these are never repeated under our no-pointless-query assumption.)  It then computes the answer that~$\TestOracle(\qry_x)$ would return, in game~$\game{3}$, and stores the answer in~$\mathrm{Ans}[x]$ for use by~$\TestOracle$.
+Game~$\game{4}$ contains some important changes from game~$\game{3}$,
+but we will argue that $\Prob{\game{3}(A) = 1} \leq \Prob{\game{4}(A)
+  = 1}$.  To begin, in game~$\game{4}$ we sample an $r$-subset of
+indices from~$\{1,2,\ldots,q_H+q_T\}$.  (We will see why, shortly.)
+Next, the $\TestOracle$ oracle on input~$\qry_x$ no longer computes
+its answer directly, but instead refers to a new
+table~$\mathrm{Ans}[x]$ which is populated upon calls to the
+$\HashOracle$ oracle.  In particular, if $\mathrm{Ans}[x]$ is
+undefined, $\TestOracle$ makes a $\HashOracle(\qry_x)$ call;
+otherwise, it returns the contents of~$\mathrm{Ans}[x]$, which
+contains exactly the values that~$\TestOracle(\qry_x)$ would have
+returned in the previous game.  The $\HashOracle$ oracle, on
+input~$\qry_y$ computes the random values~$v_1,v_2,\ldots,v_k$ as in
+$\game{3}$.  
+%(We no longer need to maintain the table~$T$ because hash values are
+%only determined by~$\HashOracle$ calls, and these are never repeated
+%under our no-pointless-query assumption.)  
+It then computes the answer that~$\TestOracle(\qry_x)$ would return, in game~$\game{3}$, and stores the answer in~$\mathrm{Ans}[x]$ for use by~$\TestOracle$.
 The $\HashOracle$ oracle also introduces a query counter~$c$, which is incremented whenever~$\HashOracle$ is called, either directly by~$A$ or via~$A$ having made a~$\TestOracle$ query on~$\qry_x$ where~$\mathrm{Ans}[x]$ had not been previously defined by a~$\HashOracle(\qry_x)$ call.
@@
 In particular, game~$\game{5}$ returns 1 exactly when~$\game{4}$ would return 1 \emph{and} the boolean~$\bad$ would have remained false in~$\game{4}$.
-This implies that~$game{4}$ managed to guess exactly the queries that would result in correctness errors, and hence
+This implies that~$\game{4}$ managed to guess exactly the queries that would result in correctness errors, and hence
 $\Prob{\game{5}(A)=1} = \dfrac{1}{\binom{q_T + q_H}{r}}\Prob{\game{4}(A)=1}$.
@@
 $T[i,y] \gets v$\\
-Ret $v$
+Return $v$
 }
@@
 \nudge $T[j,y] \gets v_j$\\
-Ret $\left(v_1,\ldots,v_k\right)$
+Return $\left(v_1,\ldots,v_k\right)$
 }
@@
 \oracle{$\HashOracle(\qry_y)$}\\
-$c \gets c + 1$\\
 for $j \in \{1,2,\ldots,k\}$\\
 \nudge $v_j \getsr [m]$\\
+\nudge if $T[j,y] \neq \undefined$\\
+\nudge \nudge $v_j \gets T[j,y]$\\
+\nudge $T[j,y] \gets v_j$\\
+%\nudge $c \gets c + 1$\\
+%\nudge for $j \in \{1,2,\ldots,k\}$\\
+%\nudge $v_j \getsr [m]$\\
 %

### 2016-10-01 related-work.tex

Bloom filters are one of the most widely used data structures for set-membership queries. Hbase, a hadoop based NoSql database designed to handle large datasets has an implementation of Bloom filter and counting Bloom filter. Hbase is the open-source implementation of Google's BigTable storage system~\cite{chang2008bigtable}. Stochastic Fair Blue~\cite{feng2001stochastic} uses counting Bloom filter to manage non-responsive TCP traffic. The counting Bloom filters are used as accounting bins to maintain statistics of packets belonging to each bin based on their queue lengths. In Squid~\cite{fan2000summary}, each web proxy server uses a bloom filter(summary cache) corresponding to the set of URL's in its cache to perform membership look-up of incoming URL's. Also, it has bloom filters of its neighboring proxy servers. Reynolds and Vahdat~\cite{reynolds2003efficient} proposed an efficient distributed search engine that can be used to search for files that contain a particular keyword. This search engine maps the keywords of each file into a Bloom filter; a look-up of the keyword in the Bloom filter tells whether the node has files containing that keyword or not. Record linkage is very often required to collect and combine records from different databases. In absence of unique identification number of the records, privacy preserving record linkage(PPRL) is used. Schnell et. al.~\cite{schnell2011novel} proposed Cryptographic Longterm Key to carry out PPRL. They used secretly keyed hash functions to create a Bloom filter for each surname. The surname is broken into bigrams and mapped into the Bloom filter with secret hash functions.

Niedermeyer et al.~\cite{niedermeyer2014cryptanalysis} showed an attack on a database of German surnames which were stored in secretly hashed Bloom filters, similar to Cryptographic Longterm Key. A Bloom filter that uses $k$ hash functions will have minimum hamming weight of $k$. Using this fact, an adversary can filter out Bloom filters that have hamming weight less than 15. This is an example of how inherent properties of a data structure can be used by an adversary. Crossby and Walach~\cite{crosby2003denial} exploited hash collisions in Squid to increase the average URL load time. They carried out two experiments to show this attack. In experiment 1, around 143K random URL's were requested to the proxy server, whereas in experiment 2, same number of carefully chosen URL's (adaptive queries) that collide with the already present URL's in the hash-table were requested. They observed that the load time of random URL's was less than the chosen URL's, and hence can be used to degrade performance of a proxy server. Whenever there is a collision in a hash table, some amount of extra time is required for collision resolution. In an older paper, Lipton and Naughton~\cite{lipton1993clocked} showed how timing analysis of record insertion in a hash table can help an adversary to adapt and chose elements that take more time to be mapped into the hash table.

### 2016-10-01 BF_correctness.tex
fixing BF proof, ugh

@@
 Return 1\\
-%
+
 \oracle{$\HashOracle(i,\qry_y)$}\\
@@
 Return~$(1, (h_1, \ldots, h_{k}) )$\\
-%
+
 \oracle{$\HashOracle(i,\qry_y)$}\\
@@
 Return~$(1, (h_1, \ldots, h_{k}) )$\\
-%
+
 \oracle{$\HashOracle(\qry_y)$}\\
@@
 {
-\underline{$\game{4}(A)$\fbox{$\game{5}(A)$}}\\
-$c\gets 0$, $\bad \gets \false$, $\err \gets 0$;  $\calC \gets \emptyset$\\
-$S \getsr A$; $\mathcal{I}\getsr [\{1,2,\ldots,q_T+q_H\}]^r$\\
+\underline{$\game{4}(A)$} \\ %\fbox{$\game{5}(A)$}}\\
+$S \getsr A$; $\err \gets 0$;  $\calC \gets \emptyset$\\
+%$\mathcal{I}\getsr [\{1,2,\ldots,q_T+q_H\}]^r$\\
 $(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
 $\bot \getsr A^{\TestOracle,\HashOracle}(\pubaux)$\\
-if $\bad = \true$ then \fbox{Return 0}\\
+%if $\bad = \true$ then \fbox{Return 0}\\
 if $\err  < r$ then Return 0\\
@@
 \nudge \nudge $\Ans[y] \gets (0, (v_1, \ldots, v_{k}) )$\\
-\nudge \nudge if $c \in \calI$ then $\bad \gets \true$\\
+%\nudge \nudge if $c \in \calI$ then $\bad \gets \true$\\
 \nudge \nudge $\Break$\\
 if $j < k$ then Return $\left(v_1,\ldots,v_k\right)$\\
-if $c \notin \calI$ then $\bad \gets \true$\\
-$\err \gets \err +1$\\
+%if $c \notin \calI$ then $\bad \gets \true$\\
+if $y \not\in S$ then $\err \gets \err +1$\\
 $\Ans[y] \gets (1, (v_1, \ldots, v_{k}))$\\

### 2016-10-01 ds-correctness.tex
Spell check
fixing DS proof

@@
   like I have them in the text.}
-We use a game playing argument to prove this theorem.
-Please refer to Figure~\ref{fig:ds-correctness-games}.
-In game \game{0}, adversary, $A$ attacks the correctness game with  hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpCorrect{\setprim_{\mathrm{ds}},r}{A}$.
+We use a game playing argument to prove this theorem. Please refer to
+Figure~\ref{fig:ds-correctness-games}.
+In game \game{0} adversary $A$ attacks the xcorrectness game with  hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpCorrect{\setprim_{\mathrm{ds}},r}{A}$.
 \begin{equation}
@@
 
-In game $\game{1}$, $A$ attacks a different filter $\tilde{\setprim}_\mathrm{ds}$, in which $F_K$ is replaced by a random function.
+In game $\game{1}$, $A$ attacks a related data structure $\tilde{\setprim}_\mathrm{ds}$, in which $F_K$ is replaced by a random function.
 Let $B$ be a prf-adversary as shown in Figure~\ref{fig:ds-correctness-adv}.
@@
 
-Coming back to the game playing argument, in game $\game{2}$, $\Hash$ returns random values sampled from $[m]$, assuming $A$ makes no pointless queries.
+Coming back to the game playing argument, in game $\game{2}$, $\HashOracle$ returns random values sampled from $[m]$, assuming $A$ makes no pointless queries.
 In addition, the $\Test$ oracle keeps a counter, $c$ to keep track of the number of queries by $A$ to the $\Test$.
@@
 Let $D$ be a zero-query adversary(shown in Figure~\ref{fig:lin-correctness-zq-adv}) corresponding to $A$ attacking $\game{3}$; it finds $r$ false positives against $\tilde{\setprim}_{\mathrm{ds}}$.
-It simulates the~$\Test$ oracle by returning 1 on the guessed queries, and 0 otherwise; and it halts after finding $r$ FP's.
+It simulates the~$\Test$ oracle by returning 1 on the guessed queries, and 0 otherwise; and it halts after finding $r$ false-positives.
 Intuitively, it  guesses which~$r$ of~$A$'s queries will be false positives.
@@
 For $r > 1$, based on the assumption that $A$ makes no pointless queries, the queries made by $A$ are distinct and not elements of the original set $S$.
-Also, since $\Hash$ in $\game{3}$ returns $k$ random values for each query, the event of getting a false positive is independent of the index of the query.
+Also, since $\HashOracle$ in $\game{3}$ returns $k$ random values for each query, the event of getting a false positive is independent of the index of the query.
 So, $\AdvCorrect{\tilde{\setprim}_{\mathrm{ds}},r}{D} =   {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r$
@@
 if $x \in \mathcal{C}$ then Return $\bot$\\
-$\calC \gets \calC \cup x$\\
+$\calC \gets \calC \cup \{x\}$\\
 $a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
@@
 for $j = 1$ to $k$\\
-\nudge $h_j(x) =\FK $\\
+\nudge $h_j(x) \gets \FK $\\
 Return $\left(h_1(x),\ldots,h_k(x)\right)$
@@
 $\rho \getsr \Func{\univ,[m]}$\\
-$S \getsr \distr{\calS}{}$; $\calC \gets \emptyset$; $\err \gets 0$\\
+$S \getsr A$; $\calC \gets \emptyset$; $\err \gets 0$\\
 $(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
@@
 for $j=1$ to $k$\\
-\nudge $h_j(x) = \rhoK $\\
+\nudge $h_j(x) \gets \rhoK $\\
 Return $\left(h_1(x),\ldots,h_k(x)\right)$
@@
 $\calC \gets \emptyset$\\
-$S \getsr \distr{\calS}{}$\\
+$S\gets A$\\
 $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
@@
 if $x \in \mathcal{C}$ then Return $\bot$\\
-$\calC \gets \calC \cup x$\\
+$\calC \gets \calC \cup \{x\}$\\
 $c \gets c+1$\\
@@
 \label{fig:ds-correctness-games}
-\fixme{Animesh: remove Crefs, fix captions to look like the classical
-  BF games captions}
+
 \end{figure}
@@
 \fpage{.8}{
-\hpagessl{.5}{.35}
+\hpagessl{.5}{.45}
 {
-$\adversaryv{B^{\calO}(S, \pubaux)}$\\
-%$S \getsr A$\\
+$\adversaryv{B^{\calO}}$\\
+$S \getsr A$\\
 $\calC \gets \emptyset$; $\err \gets 0$\\
-%$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
 Run~$A(\pubaux)$\\
@@
 \nudge if $x \in \mathcal{C}$ then Return $\bot$\\
-\nudge $\calC \gets \calC \cup x$\\
+\nudge $\calC \gets \calC \cup \{x\}$\\
 \nudge $a \gets \Qry^{\HashOracle}(\pubaux,\privaux, x)$\\
@@
 {
-$\adversaryv{D(S, \pubaux)}$\\[4pt]
-$c \gets 0$\\%, $\calX \gets \emptyset$\\
-$\calC \gets \emptyset$; $\err \gets 0$\\
-$\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
-Run $A(\pubaux)$\\
-When $A$ asks $\TestOracle(\qry_x)$:\\
-\nudge if $x \in \mathcal{C}$ then Return $\bot$\\
-\nudge $\calC \gets \calC \cup x$\\
-\nudge $c \gets c+1$\\
-\nudge $r \gets 0$\\
-\nudge if $c \in \mathcal{I}$\\
-\nudge \nudge $r \gets 1$\\
-\nudge \nudge $\err \gets \err + 1$\\
-\nudge Return $r$\\
-When $A$ halts:\\
-\nudge Return $\bot$
+$\adversaryv{D^\TestOracle}$\\[4pt]
+On input $\emptystring$:\\
+\nudge $S \getsr A$\\
+\nudge Return~$S$\\
+On input $\pubaux$:\\
+\nudge $c \gets 0$, $\calC \gets \emptyset$, $\err \gets 0$\\
+\nudge $\mathcal{I}\getsr [\{1,2,\ldots,q\}]^r$\\
+\nudge Run $A(\pubaux)$\\
+\nudge When $A$ asks $\qry_x$:\\
+\nudge\nudge if $x \in \mathcal{C}$ then Return $\bot$\\
+\nudge\nudge $\calC \gets \calC \cup \{x\}$\\
+\nudge\nudge $c \gets c+1$; $r \gets 0$\\
+\nudge\nudge if $c \in \mathcal{I}$\\
+\nudge\nudge \nudge $r \gets \TestOracle(\qry_x)$\\
+\nudge\nudge Reply to~$A$ with $r$\\
+\nudge When $A$ halts:\\
+\nudge\nudge Return $\bot$
 }
 }
-\caption{Left: Adversary $B$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively for the
+\caption{Left: Adversary $B$ simulating $\game{0}(A)$ and $\game{1}(A)$ respectively for the
 proof of Theorem~\ref{thm:ds-correctness}.

### 2016-10-01 BF_correctness.tex
fixing BF proof

@@
 but we will argue that $\Prob{\game{3}(A) = 1} \leq \Prob{\game{4}(A)
-  = 1}$.  To begin, in game~$\game{4}$ we sample an $r$-subset of
-indices from~$\{1,2,\ldots,q_H+q_T\}$.  (We will see why, shortly.)
-Next, the $\TestOracle$ oracle on input~$\qry_x$ no longer computes
-its answer directly, but instead refers to a new
-table~$\mathrm{Ans}[x]$ which is populated upon calls to the
-$\HashOracle$ oracle.  In particular, if $\mathrm{Ans}[x]$ is
-undefined, $\TestOracle$ makes a $\HashOracle(\qry_x)$ call;
+  = 1}$. The $\TestOracle$ oracle on input~$\qry_x$ no longer computes
+its answer directly, but instead refers to a new table~$\mathrm{Ans}[x]$ which is populated upon calls to the
+$\HashOracle$ oracle.  In particular, if $\mathrm{Ans}[x]$ is undefined, $\TestOracle$ makes a $\HashOracle(\qry_x)$ call;
 otherwise, it returns the contents of~$\mathrm{Ans}[x]$, which
 contains exactly the values that~$\TestOracle(\qry_x)$ would have
-returned in the previous game.  The $\HashOracle$ oracle, on
-input~$\qry_y$ computes the random values~$v_1,v_2,\ldots,v_k$ as in
-$\game{3}$.  
+returned in the previous game.  The $\HashOracle$ oracle, on input~$\qry_y$ computes the random values~$v_1,v_2,\ldots,v_k$ as in
+$\game{3}$.  It maintains the table~$T$ because~$A$ is permitted to call~$\HashOracle$
 %(We no longer need to maintain the table~$T$ because hash values are
@@
 %under our no-pointless-query assumption.)  
-It then computes the answer that~$\TestOracle(\qry_x)$ would return, in game~$\game{3}$, and stores the answer in~$\mathrm{Ans}[x]$ for use by~$\TestOracle$.
-The $\HashOracle$ oracle also introduces a query counter~$c$, which is incremented whenever~$\HashOracle$ is called, either directly by~$A$ or via~$A$ having made a~$\TestOracle$ query on~$\qry_x$ where~$\mathrm{Ans}[x]$ had not been previously defined by a~$\HashOracle(\qry_x)$ call.
-\fixme{for BF proof, we can assume that $\TestOracle(\qry_x)$ is never made after a~$\HashOracle(\qry_x)$ call, because~$M$ is public.
-And vice versa.
-So the maximum value of~$c = q_T + q_H$.}  (Note that the maximum value of~$c$ is $q_T + q_H$.)  The set~$\calI$ contains a set of~$r$ distinct values from $\{1,2,\ldots,q_T+q_H\}$ and, intuitively, these are the game's ``guesses'' at the $\HashOracle$ queries that will result in a correctness error.
-If these~$r$ guesses are incorrect, then a boolean flag~$\bad$ is set, although in game~$\game{4}$ the value of~$\bad$ has no effect on the games execution; in particular, $\game{4}$ does \emph{not} contain the boxed ``Return 0'' statement.
+It then computes the answer that~$\TestOracle(\qry_x)$ would return in
+game~$\game{3}$, and stores the answer in~$\mathrm{Ans}[x]$ for use
+by~$\TestOracle$.  
+The $\HashOracle$ oracle also introduces a query counter~$c$, which is
+incremented whenever~$\HashOracle$ is called, either directly by~$A$
+or via~$A$ having made a~$\TestOracle$ query on~$\qry_x$
+where~$\mathrm{Ans}[x]$ had not been previously defined by
+a~$\HashOracle(\qry_x)$ call. 
+% \fixme{for BF proof, we can assume that $\TestOracle(\qry_x)$ is
+% never made after a~$\HashOracle(\qry_x)$ call, because~$M$ is
+% public.  And vice versa.  So the maximum value of~$c = q_T + q_H$.}
+% (Note that the maximum value of~$c$ is $q_T + q_H$.)  
+None of these changes alters the behavior of the game from the
+adversary's perspective.
 
-Games~$\game{4}$ and $\game{5}$ are identical except for this boxed statement.
-In particular, game~$\game{5}$ returns 1 exactly when~$\game{4}$ would return 1 \emph{and} the boolean~$\bad$ would have remained false in~$\game{4}$.
+At this point, we consider $\Prob{\game{4}{A}=1}$.  Note that is
+happens iff there are~$r$ calls to the $\HashOracle$ oracle that
+increment~$\err$, i.e., queries $y \not\in S$ such that
+$\bigwedge_{j=1}^{k} M[v_j]=1$.  We can assume without loss that~$A$
+does not call~$\HashOracle$ on $y \in S$ because the indices
+$v_1,v_2,\ldots,v_k$ that will correspond to any $y \not\in S$ will be
+\emph{independent} of those corrsponding to any of the $y \in S$.
+Thus these queries are wasted.  Now, there are at total of $q_T + q_H$
+queries make to~$\HashOracle$, either directly by~$A$ or indirectly
+by~$A$ calling~$\TestOracle$.  For $\game{4}{A}$ to return 1, there
+must be~$r$ among these that increment the counter.  We can assume
+WLOG that~$A$ halts as soon as~$\err=r$ (which it can easily track),
+so there are $\binom{q_T+q_H-1}{r-1}$ possible ``winning'' query
+patterns to consider.  As each error event is independent of all
+previous choices made by the~$\HashOracle$, we need only consider the
+probability of a single error. Using Kirsch and Mitzenmacher's upper
+bound on false positive probability of a classical Bloom filter, 
+we have  $\Prob{\game{4}(A)=1} = \binom{q_T+q_H-1}{r-1}\left( (1-e^{-kn/m})^k + O(1/n) \right)^r$.
+
 This implies that~$\game{4}$ managed to guess exactly the queries that would result in correctness errors, and hence
 $\Prob{\game{5}(A)=1} = \dfrac{1}{\binom{q_T + q_H}{r}}\Prob{\game{4}(A)=1}$.
-
-For $r=1$, $\game{5}$ exactly simulates the classical Bloom filter.
-Since, $\HashOracle$ returns random values for each query, the event of getting a false-positive is independent of the index of the query.
-Using Kirsch and Mitzenmacher's upper bound on false positive probability of a classical Bloom filter, we have  $\Prob{\game{5}(A)=1} = \left( (1-e^{-kn/m})^k + O(1/n) \right)^r$.
 To summarize, 
 \[
-\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H-1}{r-1}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
 \]

### 2016-10-01 results.tex
fixing BF proof

@@
 \[
-\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H-1}{r-1}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
 \]
@@
 of moving from the adaptive to the zero-query setting.
-Finally, $\binom{q_T+q_H}{r} \leq (q_T+q_H)^r$ (with reasonable tightness when~$r$ is small) in
+Finally, $\binom{q_T+q_H-1}{r-1} \leq (q_T+q_H)^r$ (with reasonable tightness when~$r$ is small) in
 which case the final term in the bound behaves as

### 2016-10-01 BF_correctness.tex
fixing BF proof

@@
 We do this so that we can assume that a call~$\HashOracle(\qry_x)$ is pointless after a~$\TestOracle(\qry_x)$ call, and this will aid us in subsequent games.
-\fixme{for BF proof, this actually does more, it makes a hash query as good as a test query, because~$M$ is public.} Thus, $\Prob{\game{2}(A) = 1} \leq \Prob{\game{3}(A) = 1}$.
+Thus, $\Prob{\game{2}(A) = 1} \leq \Prob{\game{3}(A) = 1}$.
 We assume from Game~$\game{3}$ and on that $\Rep$ is also appropriately modifed for the new behavior of~$\HashOracle$.
@@
 returned in the previous game.  The $\HashOracle$ oracle, on input~$\qry_y$ computes the random values~$v_1,v_2,\ldots,v_k$ as in
-$\game{3}$.  It maintains the table~$T$ because~$A$ is permitted to call~$\HashOracle$
+$\game{3}$.  It maintains the table~$T$ because~$A$ is permitted to
+call~$\HashOracle$ on $y \in S$.
 %(We no longer need to maintain the table~$T$ because hash values are
@@
 by~$\TestOracle$.  
-The $\HashOracle$ oracle also introduces a query counter~$c$, which is
-incremented whenever~$\HashOracle$ is called, either directly by~$A$
-or via~$A$ having made a~$\TestOracle$ query on~$\qry_x$
-where~$\mathrm{Ans}[x]$ had not been previously defined by
-a~$\HashOracle(\qry_x)$ call. 
-% \fixme{for BF proof, we can assume that $\TestOracle(\qry_x)$ is
-% never made after a~$\HashOracle(\qry_x)$ call, because~$M$ is
-% public.  And vice versa.  So the maximum value of~$c = q_T + q_H$.}
-% (Note that the maximum value of~$c$ is $q_T + q_H$.)  
 None of these changes alters the behavior of the game from the
@@
 
-At this point, we consider $\Prob{\game{4}{A}=1}$.  Note that is
+At this point, we consider $\Prob{\game{4}(A)=1}$.  Note that is
 happens iff there are~$r$ calls to the $\HashOracle$ oracle that
@@
 queries make to~$\HashOracle$, either directly by~$A$ or indirectly
-by~$A$ calling~$\TestOracle$.  For $\game{4}{A}$ to return 1, there
+by~$A$ calling~$\TestOracle$.  For $\game{4}(A)$ to return 1, there
 must be~$r$ among these that increment the counter.  We can assume

### 2016-10-01 BF_correctness.tex
fixing BF proof

@@
 Thus these queries are wasted.  Now, there are at total of $q_T + q_H$
-queries make to~$\HashOracle$, either directly by~$A$ or indirectly
+queries made to~$\HashOracle$, either directly by~$A$ or indirectly
 by~$A$ calling~$\TestOracle$.  For $\game{4}(A)$ to return 1, there
@@
 previous choices made by the~$\HashOracle$, we need only consider the
-probability of a single error. Using Kirsch and Mitzenmacher's upper
-bound on false positive probability of a classical Bloom filter, 
+probability of a single error. Using Kirsch and Mitzenmacher's~\cite{kirsch2006less} upperbound on false positive probability of a classical Bloom filter, 
 we have  $\Prob{\game{4}(A)=1} = \binom{q_T+q_H-1}{r-1}\left( (1-e^{-kn/m})^k + O(1/n) \right)^r$.
-
-This implies that~$\game{4}$ managed to guess exactly the queries that would result in correctness errors, and hence
-$\Prob{\game{5}(A)=1} = \dfrac{1}{\binom{q_T + q_H}{r}}\Prob{\game{4}(A)=1}$.
 To summarize, 

### 2016-10-01 ds-correctness.tex
proofs lin and ds

@@
 \begin{proof}[Theorem~\ref{thm:ds-correctness}]
-\fixme{Animesh: remove these Cref things and replace with references
+%\fixme{Animesh: remove these Cref things and replace with references
   like I have them in the text.}
@@
 Coming back to the game playing argument, in game $\game{2}$, $\HashOracle$ returns random values sampled from $[m]$, assuming $A$ makes no pointless queries.
-In addition, the $\Test$ oracle keeps a counter, $c$ to keep track of the number of queries by $A$ to the $\Test$.
+In addition, the $\TestOracle$ oracle keeps a counter, $c$ to keep track of the number of queries by $A$ to the $\TestOracle$.
 It also sets a boolean $\bad$ flag to $\false$ if queries which are not indexed by the $r$-set $\calI$ are false-positives, and queries indexed by set $\calI$ are not false-positives.
-It must be noted that $\bad$ does not affect the output of the $\Test$ or the game.
+It must be noted that $\bad$ does not affect the output of the $\TestOracle$ or the game.
 We argue that, $\Prob{\game{1}(A)=1} \leq \Prob{\game{2}(A)=1}$.
@@
 Let $D$ be a zero-query adversary(shown in Figure~\ref{fig:lin-correctness-zq-adv}) corresponding to $A$ attacking $\game{3}$; it finds $r$ false positives against $\tilde{\setprim}_{\mathrm{ds}}$.
-It simulates the~$\Test$ oracle by returning 1 on the guessed queries, and 0 otherwise; and it halts after finding $r$ false-positives.
+It simulates the~$\TestOracle$ oracle by returning 1 on the guessed queries, and 0 otherwise; and it halts after finding $r$ false-positives.
 Intuitively, it  guesses which~$r$ of~$A$'s queries will be false positives.
@@
 Right: Zero-query adversary $D$ for Theorems~\ref{thm:ds-correctness} and ~\ref{thm:lin-correctness}.}\label{fig:ds-correctness-adv}\label{fig:lin-correctness-zq-adv}
-\fixme{Animesh: remove Crefs, make caption refer to correct theorem}
+%\fixme{Animesh: remove Crefs, make caption refer to correct theorem}
 \end{figure}

### 2016-10-01 lin-correctness.tex

@@
 {
-$\adversaryv{B_1^{\calO}(S, \pubaux)}$\\
-%$S \getsr A$\\
+$\adversaryv{B_1^{\calO}}$\\
+$S \getsr A$\\
 $\calC \gets \emptyset$; $\err \gets 0$\\
-%$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
 Run~$A(\pubaux)$\\
@@
 {
-$\adversaryv{B_2^{\calO}(S, \pubaux)}$\\
-%$S \getsr A$\\
+$\adversaryv{B_2^{\calO}}$\\
+$S \getsr A$\\
 $\calC \gets \emptyset$; $\err \gets 0$\\
-%$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
 Run~$A(\pubaux)$\\
@@
 }
-\caption{Adversary $B_1, B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$ respectively for the
-proof of Theorem~\ref{thm:lin-correctness}.}\label{fig:lin-correctness-adv}
-\fixme{fix caption and Crefs}
+\caption{Adversary $B_1$ simulating $\game{0}(A)$ and $\game{1}(A)$, and $B_2$ simulating $\game{1}(A)$ and $\game{2}(A)$  respectively for the proof of Theorem~\ref{thm:lin-correctness}.}\label{fig:lin-correctness-adv}
+%\fixme{fix caption and Crefs}
 \end{figure}
@@
 %
-Also, the $\Test$ oracle now sets $\bad$ to $\true$ if the
+Also, the $\TestOracle$ oracle now sets $\bad$ to $\true$ if the
 queries indexed by the set $\mathcal{I}$ fail to be false-positives,
@@
 observed that the $\bad$ flag has no impact on the output of the
-$\Test$, nor does it affect  the value returned
+$\TestOracle$, nor does it affect  the value returned
 by~$\game{3}$. Thus we have $\Prob{\game{2}(A)=1} =
@@
 of the $\bad$-flag in games~$\game{3},\game{4}$.   Intuitively, if the index
-set~$\mathcal{I}$ exactly predicts which of the $\Test$ queries will be
+set~$\mathcal{I}$ exactly predicts which of the $\TestOracle$ queries will be
 false-positives (and, conversely, which will not be), then a
 zero-query FP-finding adversary can ``guess'' which of~$A$'s queries require it
-to return 1 when simulating the $\Test$, and which require it to
+to return 1 when simulating the $\TestOracle$, and which require it to
 return 0.  In this way, no queries ever actually need to be made.
@@
 happens iff the $r$-set~$\calI$ contains exactly the indices of
-$\Test$-queries that are false-positives.  Since the value
-of~$\bad$ does not alter the responses of~$\Test$, $\err$'s update
+$\TestOracle$-queries that are false-positives.  Since the value
+of~$\bad$ does not alter the responses of~$\TestOracle$, $\err$'s update
 and the set~$\calI$ are independent.
@@
 We give this~$D$ in Figure~\ref{fig:lin-correctness-zq-adv}.
-Intuitively, adversary~$D$ guesses which~$r$ of~$A$'s queries will be false positives; it simulates the~$\Test$ oracle by returning 1 on the guessed queries, and 0 otherwise; and it halts after finding $r$ false-positives.
+Intuitively, adversary~$D$ guesses which~$r$ of~$A$'s queries will be false positives; it simulates the~$\TestOracle$ oracle by returning 1 on the guessed queries, and 0 otherwise; and it halts after finding $r$ false-positives.
 It must be noted that, by the no-pointless queries assumption and the fact that the hash functions in $D$ are instantiated with random functions, $\pubaux$ is information theoretically independent of elements not in $S$.
@@
 \label{fig:lin-correctness-games}
-\fixme{fix caption and Crefs}
+%\fixme{fix caption and Crefs}
 \end{figure}

### 2016-10-01 ds-correctness.tex
proof

@@
 \begin{proof}[Theorem~\ref{thm:ds-correctness}]
-%\fixme{Animesh: remove these Cref things and replace with references
+\fixme{Animesh: remove these Cref things and replace with references
   like I have them in the text.}
@@
 Right: Zero-query adversary $D$ for Theorems~\ref{thm:ds-correctness} and ~\ref{thm:lin-correctness}.}\label{fig:ds-correctness-adv}\label{fig:lin-correctness-zq-adv}
-%\fixme{Animesh: remove Crefs, make caption refer to correct theorem}
+\fixme{Animesh: remove Crefs, make caption refer to correct theorem}
 \end{figure}

### 2016-10-01 ds-correctness.tex
proof
cheers

--- 2016-10-01 ds-correctness.tex
@@
 %\fixme{Animesh: remove these Cref things and replace with references
-  like I have them in the text.}
+%  like I have them in the text.}
 We use a game playing argument to prove this theorem. Please refer to
 Figure~\ref{fig:ds-correctness-games}.
-In game \game{0} adversary $A$ attacks the xcorrectness game with  hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpCorrect{\setprim_{\mathrm{ds}},r}{A}$.
+In game \game{0} adversary $A$ attacks the correctness game with hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpCorrect{\setprim_{\mathrm{ds}},r}{A}$.
 \begin{equation}
@@
 
-Let $D$ be a zero-query adversary(shown in Figure~\ref{fig:lin-correctness-zq-adv}) corresponding to $A$ attacking $\game{3}$; it finds $r$ false positives against $\tilde{\setprim}_{\mathrm{ds}}$.
+Let $D$ be a non-adaptive adversary(shown in Figure~\ref{fig:lin-correctness-zq-adv}) corresponding to $A$ attacking $\game{3}$; it finds $r$ false positives against $\tilde{\setprim}_{\mathrm{ds}}$.
 It simulates the~$\TestOracle$ oracle by returning 1 on the guessed queries, and 0 otherwise; and it halts after finding $r$ false-positives.

### 2016-10-01 results.tex
fixing lin-PRF and bigram lin-PRF descriptions
cheers

@@
 \end{theorem}
-\fixme{This result is pretty intuitive following the classic BF correctness result. Probably fine to just explain it and push an appendix, or even drop from camera ready if out of space.}
 We note that Kirsch and Mitzenmacher~\cite{kirsch2006less} show
@@
 %\jnote{Fix}\tsnote{Fix what?}\\
+\nudge $f_1 \gets F_{K}(\langle 1,x \rangle)$, $f_2 \gets F_{K}(\langle 2,x \rangle)$\\
 \nudge for $j \in \{1,2,\ldots,k\}$\\
-\nudge\nudge $h_j \gets F_{K}(\langle 1,x \rangle) + j\cdot F_{K}(\langle 2,x \rangle) \bmod m$\\
+\nudge\nudge $h_j \gets f_1 + j\cdot f_2 \bmod m$\\
 \nudge\nudge $M[h_j] \gets 1$\\
-%$\pubaux \gets M$, $\privaux \gets \langle K \rangle$\\
-Return $(\pubaux=M,\privaux=K)$\\
+$\pubaux \gets M$, $\privaux \gets \langle K \rangle$\\
+Return $(\pubaux,\privaux)$\\
 
 \medskip
-\algorithmv{$\Qry(\pubaux=M,\privaux=K,q_x)$}\\
-%$M\gets\pubaux$, $K \gets \privaux$\\
+\algorithmv{$\Qry(\pubaux,\privaux)$}\\
+$M\gets\pubaux$, $K \gets \privaux$\\
 %\jnote{Fix}\tsnote{Fix what?} \\
+$f_1 \gets F_{K}(\langle 1,x \rangle)$, $f_2 \gets F_{K}(\langle 2,x \rangle)$\\
 for $j \in \{1,2,\ldots,k\}$\\
-\nudge $h_j \gets F_{K}(\langle 1,x \rangle) + j\cdot F_{K}(\langle 2,x\rangle) \bmod m$\\
+\nudge $h_j \gets f_1 + j\cdot f_2 \bmod m$\\
 \nudge if $M[h_j] \neq 1$ then Return 0\\
@@
 \nudge for each $b \in B_x$\\
+\nudge\nudge $f_1 \gets F_{K}(\langle 1,b \rangle)$, $f_2 \gets F_{K}(\langle 2,b \rangle)$\\
 \nudge\nudge for $j \in [k]$\\
-\nudge\nudge\nudge $i \gets F_{K}(\langle 1, b\rangle)+j\cdot
-F_{K}(\langle 2, b  \rangle) \bmod m$\\
+\nudge\nudge\nudge $i \gets f_1+j\cdot f_2 \bmod m$\\
 \nudge\nudge\nudge $M_x[i] \gets 1$\\
@@
 \nudge for $j \in [k]$\\
-\nudge\nudge $i \gets F_{K}(\langle 1,b \rangle)+j\cdot F_{K}(\langle 2,b \rangle) \bmod m$\\
+\nudge\nudge $f_1 \gets F_{K}(\langle 1,b \rangle)$, $f_2 \gets F_{K}(\langle 2,b \rangle)$\\
+\nudge\nudge $i \gets f_1+j\cdot f_2 \bmod m$\\
 \nudge\nudge $\overline{M}[i] \gets 1$\\
@@
 i.e. $\{\sqcup x_1, x_1x_2,\ldots,x_{\ell-1}x_\ell,x_\ell\sqcup\}$.
-\jnote{I would emphasize that $F_K(\cdot)$ is computed only twice
-per inner loop (which is the whole point of this scheme) by moving
-that computation outside the loop.}} \label{fig:lin-and-bi-lin}
+Both schemes use a function family $F\colon \calK \times \bits^* \to [m]$.
+}\label{fig:lin-and-bi-lin}
 \label{fig:niedermeyer}
@@
 the multiplicative term $\binom{q}{r}$ arises when switching from the adaptive to zero-query settings.
-\input{lin-correctness}
+The proof will appear in the full version, but we note that it very
+closely follows the proof of correctness for the DS PRF-hash
+construction, Theorem~\ref{thm:ds-correctness}
+%\input{lin-correctness}
 

### 2016-10-01 results.tex
cheers

@@
 \subsection{Classical Bloom Filter in the Random-Oracle Model}
-
 Fix $n,k,m \geq 0$, and fix a set $\elts$.  Then the classical Bloom
@@
 aiming to find $r \geq 1$ errors (in this case, false-positives).
-The proof appears in Appendix~\ref{sec:thm3_fp}. \jnote{We seem to
-have plenty of space, so maybe start moving things from the appendix
-to the main body?}
 
@@
 \end{theorem}
-\todo{Typeset simple proof.  Result is on chalkboard.}
-\begin{proof}
-\begin{figure}[tp]
-\hfpagess{.45}{.45}
-{\underline{\game{0}($A$)}\\
-$S \getsr \distr{}{}$\\
-$(\pubaux,\privaux) \getsr \Rep(S)$\\
-$z \getsr A(\pubaux)$\\
-if $z \in S$ then return 1\\
-return 0\\
-
-\medskip
-\oracle{$\HashOracle(\qry_x)$}\\
-}
-{
-}
-\end{figure}
-\end{proof}
-
-%\jnote{Organize by scheme, not by security notions.}
+The straightforward proof will appear in the full version.
+Loosely, the $kqn/2^{\mu}$ term arises from the chance that random-oracle queries reveal an element of~$S$ (by the random oracle having
+been called on them in the execution of~$\Rep$), and the $n/2^\mu$
+term arises to simple guessing of an element of~$S$ should none of the
+random-oracle queries reveal an element of~$S$.
 
@@
 
-\begin{figure}
+\begin{figure}[tp]
 \centering
-\fpage{0.5}{
+\fpage{0.75}{
+\hpagess{.5}{.45}{
 \algorithmv{$\Rep(S)$}\\
@@
 Return $(\pubaux,\privaux)$\\
-
-\medskip
+}
+{
 \algorithmv{$\Qry(\pubaux,\privaux,q_x)$}\\
@@
 if $\overline{M} \in \pubaux$ then Return 1 \\
-Return 0} \caption{Bigram domain-separated PRF-hash.}
+Return 0
+}
+} 
+\caption{Bigram domain-separated PRF-hash.}
 \label{fig:DS-bigram}

### 2016-10-01 notions.tex
added query enumeration function to canonical rep syntax

@@
 A set-membership data structure $(\Rep, \Qry)$ is {\sf canonical} if
-there exist algorithms $\Rep_1, \Rep_2$, and a function
+there exist algorithms $\Rep_1, \Rep_2$, a query-enumeration
+function~$\ell\colon\mathbb{N}\to\mathbb{N}$,
+and a function family
 $F: \calK \times \bits^{\ell_{in}} \rightarrow \bits^{\ell_{out}}$
@@
 \item $\Rep_1$ takes as input a set $S$ and outputs distinct values $s_1, \ldots, s_t \in \bits^{\ell_{in}}$,
-where $t$ depends only on~$|S|$.
+where $t=\ell(|S|)$
 \item $\Rep_2$ takes as input $|S|$ and $y_1, \ldots, y_t \in \bits^{\ell_{out}}$, and outputs
@@
 \end{itemize}
-We call $(\Rep_1, \Rep_2, F)$ the {\sf canonical representation}
+We call $(\Rep_1, \Rep_2, \ell, F)$ the {\sf canonical representation}
 of algorithm~$\Rep$. \hfill\dqed
@@
 semantically secure with respect to leakage consisting of the size of the set.
-\jnote{Need notation for the advantage in the PRF
-  experiment.}\tsnote{Currently typeset in an appendix}
 
@@
 has canonical representation
-$(\Rep_1, \Rep_2, F)$. Then for ${\sf leak}(S) = |S|$ and
+$(\Rep_1, \Rep_2,\ell, F)$. Then for ${\sf leak}(S) = |S|$ and
 any attacker $A$, there is an attacker
-$B$ \jnote{How do we describe the number of PRF queries $B$ makes? Note that it makes
-exactly $t$ queries, but $t$ depends on $|S|$ in a non-specified manner.} for which
-\[\AdvPrivSS{\setprim,{\sf leak}}{A} \leq {\sf Adv}_F^{\rm PRF}(B). \]
+$B$, making $\ell(|S|)$ queries, for which
+\[\AdvPrivSS{\setprim,{\sf leak}}{A} \leq \AdvPRF{F}{B}\,. \]
 \end{theorem}

### 2016-10-01 ds-correctness.tex
proofs

--- 2016-10-01 ds-correctness.tex
@@
 Coming back to the game playing argument, in game $\game{2}$, $\HashOracle$ returns random values sampled from $[m]$, assuming $A$ makes no pointless queries.
-In addition, the $\TestOracle$ oracle keeps a counter, $c$ to keep track of the number of queries by $A$ to the $\TestOracle$.
+In addition, the $\Test$ oracle keeps a counter, $c$ to keep track of the number of queries by $A$ to the $\Test$.
 It also sets a boolean $\bad$ flag to $\false$ if queries which are not indexed by the $r$-set $\calI$ are false-positives, and queries indexed by set $\calI$ are not false-positives.
-It must be noted that $\bad$ does not affect the output of the $\TestOracle$ or the game.
+It must be noted that $\bad$ does not affect the output of the $\Test$ or the game.
 We argue that, $\Prob{\game{1}(A)=1} \leq \Prob{\game{2}(A)=1}$.
@@
 
-Let $D$ be a zero-query adversary(shown in Figure~\ref{fig:lin-correctness-zq-adv}) corresponding to $A$ attacking $\game{3}$; it finds $r$ false positives against $\tilde{\setprim}_{\mathrm{ds}}$.
-It simulates the~$\TestOracle$ oracle by returning 1 on the guessed queries, and 0 otherwise; and it halts after finding $r$ false-positives.
+Let $D$ be an adversary(shown in Figure~\ref{fig:lin-correctness-zq-adv}) corresponding to $A$ attacking $\game{3}$; it finds $r$ false positives against $\tilde{\setprim}_{\mathrm{ds}}$.
+It simulates the~$\Test$ oracle by returning 1 on the guessed queries, and 0 otherwise; and it halts after finding $r$ false-positives.
 Intuitively, it  guesses which~$r$ of~$A$'s queries will be false positives.
@@
 It can be easily seen that  $\tilde{\setprim}_{\mathrm{ds}}$ is the scheme that is analyzed in the classical Bloom filter literature.
-So, for a zero-query adversary $D$ and $r=1$, advantage of $D$ to win $\ExpCorrect{\tilde{\setprim}_{\mathrm{ds}},r}$ will be upper bounded by the false-positive probability of a classical Bloom filter.
+So, for an adversary $D$ and $r=1$, advantage of $D$ to win $\ExpCorrect{\tilde{\setprim}_{\mathrm{ds}},r}$ will be upper bounded by the false-positive probability of a classical Bloom filter.
 For $r > 1$, based on the assumption that $A$ makes no pointless queries, the queries made by $A$ are distinct and not elements of the original set $S$.

### 2016-10-01 ds-correctness.tex
remove fixme
cheers

--- 2016-10-01 ds-correctness.tex
@@
 \caption{Left: Adversary $B$ simulating $\game{0}(A)$ and $\game{1}(A)$ respectively for the
-proof of Theorem~\ref{thm:ds-correctness}.
-Right: Zero-query adversary $D$ for Theorems~\ref{thm:ds-correctness} and ~\ref{thm:lin-correctness}.}\label{fig:ds-correctness-adv}\label{fig:lin-correctness-zq-adv}
-\fixme{Animesh: remove Crefs, make caption refer to correct theorem}
+proof of Theorem~\ref{thm:ds-correctness}. Right: Zero-query adversary $D$ for Theorems~\ref{thm:ds-correctness} }\label{fig:ds-correctness-adv}\label{fig:lin-correctness-zq-adv}
+%\fixme{Animesh: remove Crefs, make caption refer to correct theorem}
 \end{figure}

### 2016-10-01 results.tex
cheers

@@
 \begin{theorem}[\rm{SS-privacy of DS PRF}]\label{thm:ds-ss}
-Fix $k,m,n>0$, a set~$\elts$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-membership data structure described in Figure~\ref{fig:bf-and-ds}.
-For any set~$S \in 2^\elts$, let $\leak(S)=|S|$.
-There exists a simulator~$\Sim$ and adversary~$B$ such that, for any adversary~$A$
+Fix $k,m,n>0$, a set~$\elts$, and let $\setprim_{\mathrm{ds}}= (\Rep,
+\Qry)$ be the set-membership data structure described in
+Figure~\ref{fig:bf-and-ds}.  For any set~$S \in 2^\elts$, let
+$\leak(S)=|S|$.  There exists a simulator~$\Sim$ and adversary~$B$
+(making~$kn$ queries) such that, for any adversary~$A$
 \[
-\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}\;.
+\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}\,.
 \]
@@
 \begin{theorem}[{\rm SS-privacy of linear-PRF}]\label{thm:lin-privacy}
-Fix $k,m,n,r>0$, a set $\elts$, and let $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-membership data structure (over~$\elts$) described in Figure~\ref{fig:lin-and-bi-lin}.
-For any set~$S \in 2^{\elts}$, let $\leak(S)=|S|$.
-There exists a simulator~$\Sim$ and an adversary~$B$ such that, for any adversary~$A$
+Fix $k,m,n,r>0$, a set $\elts$, and let $\setprim_{\mathrm{lin}}=
+(\Rep, \Qry)$ be the set-membership data structure (over~$\elts$)
+described in Figure~\ref{fig:lin-and-bi-lin}. For any set~$S \in
+2^{\elts}$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ and
+an adversary~$B$ (making $2n$ queries) such that, for any adversary~$A$
 \[
@@
 integer $\alpha >> 1$, and let, $k = \lceil \ln(2) \alpha
-\rceil$.\tsnote{This value of~$k$ is from the classical analysis for
+\rceil$.\footnote{This value of~$k$ is from the classical analysis for
 minimizing the FP rate for a Bloom filter, and is set this way for
@@
 \end{theorem}
-\begin{proof}\tsnote{still a bit sketchy but believable}
+\begin{proof}%\tsnote{still a bit sketchy but believable}
 On input the set~$S$ produced by~$A$, the $\Rep$ algorithm turns $x_1=$'cab', $x_2=$'bab' and $x_3$ into their respective bigram sets: $B_{x_1}=\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{b}\sqcup\}$, $B_{x_2}=\{\sqcup\mathrm{b},\mathrm{ba},\mathrm{ab}, \mathrm{b}\sqcup \}$; the set $B_{x_3}$ will be either $\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{ba}, \mathrm{a}\sqcup\}$, or $\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{bc}, \mathrm{c}\sqcup\}$, each with probability 1/2.
@@
 $n=3$,  $m=3\alpha $ for integer $\alpha >> 1$, and let $k = \lceil
-\ln(2) \alpha \rceil$.\tsnote{This value of~$k$ is from the
+\ln(2) \alpha \rceil$.\footnote{As before, this value of~$k$ is from the
 classical analysis for minimizing the FP rate for a Bloom filter,
@@
 Figure~\ref{fig:DS-bigram}. Then for any attacker $A$, there is an
-attacker $B$ \jnote{How do we describe the number of PRF queries $B$
-makes? Same problem as in Theorem~\ref{thm:priv-ss}.} for which
-\[\AdvPrivSS{\setprim,{\sf leak}_\cap}{A} \leq {\sf Adv}_F^{\rm PRF}(B). \]
+attacker $B$ 
+%\jnote{How do we describe the number of PRF queries $B$
+%makes? Same problem as in Theorem~\ref{thm:priv-ss}.} 
+for which
+$\AdvPrivSS{\setprim,{\sf leak}_\cap}{A} \leq \AdvPRF{F}{B}$.
 \end{theorem}
+
+We remark that the running time of the simulator is exponential in
+the size $|S|$ of the set, so the above is not entirely satisfactory
+unless $S$ is small. Nevertheless, it does convey the intuition that
+the information leaked by the data structure is \emph{at most} the
+sizes of the various intersections of the~$\{B_x\}$.
+
 \begin{proof}
@@
 \end{proof}
-
-We remark that the running time of the simulator is exponential in
-the size $|S|$ of the set, so the above is not entirely satisfactory
-unless $S$ is small. Nevertheless, it does convey the intuition that
-the information leaked by the data structure is \emph{at most} the
-sizes of the various intersections of the~$\{B_x\}$.
 
@@
 \label{thm:gbf-prf-privacy}
-Fix $k,m,n,r,\lambda>0$ and a function family~$F\colon \calK \times \bits^* \to [m]$.
-Let $\setprim_{\mathrm{gbf\mbox{-}prf}}= (\Rep, \Qry)$ be the garbled Bloom filter with hash functions $H_j(x)=F_K(\langle j,x \rangle)$ and $\privaux=\langle K \rangle$.
-For any set~$S$, let $\leak(S)=|S|$.
-There exists a simulator~$\Sim$ and an adversary~$B$ such that, for any adversary~$A$
+Fix $k,m,n,r,\lambda>0$ and a function family~$F\colon \calK \times
+\bits^* \to [m]$.  Let $\setprim_{\mathrm{gbf\mbox{-}prf}}= (\Rep,
+\Qry)$ be the garbled Bloom filter with hash functions
+$H_j(x)=F_K(\langle j,x \rangle)$ and $\privaux=\langle K \rangle$.
+For any set~$S$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$
+and an adversary~$B$ (making $kn$ queries) such that, for any adversary~$A$
 \[

### 2016-10-01 ds-correctness.tex

--- 2016-10-01 ds-correctness.tex
@@
 \begin{proof}[Theorem~\ref{thm:ds-correctness}]
-\fixme{Animesh: remove these Cref things and replace with references
-  like I have them in the text.}
+%\fixme{Animesh: remove these Cref things and replace with references
+  %like I have them in the text.}
 We use a game playing argument to prove this theorem. Please refer to

### 2016-10-01 ds-correctness.tex
fixing ds-correctness

@@
 
-Let $D$ be an adversary(shown in Figure~\ref{fig:lin-correctness-zq-adv}) corresponding to $A$ attacking $\game{3}$; it finds $r$ false positives against $\tilde{\setprim}_{\mathrm{ds}}$.
-It simulates the~$\Test$ oracle by returning 1 on the guessed queries, and 0 otherwise; and it halts after finding $r$ false-positives.
-Intuitively, it  guesses which~$r$ of~$A$'s queries will be false positives.
-So, $\AdvCorrect{\tilde{\setprim}_{\mathrm{ds}},r}{D} = \Prob{\game{3}(A) = 1}$.
+Let $D$ be an adversary shown in Figure~\ref{fig:lin-correctness-zq-adv}.
+It effectively simulates game~$game{3}$, guessing which~$r$ of~$A$'s queries to send to its own~$\TestOracle$.
+By its construction, if $\game{3}(A)=1$ then~$D$ will also find~$r$ errors in~$\tilde{\setprim}_{\mathrm{ds}}$.
+Thus, $\AdvCorrect{\tilde{\setprim}_{\mathrm{ds}},r}{D} = \Prob{\game{3}(A) = 1}$.
 
@@
 Also, since $\HashOracle$ in $\game{3}$ returns $k$ random values for each query, the event of getting a false positive is independent of the index of the query.
-So, $\AdvCorrect{\tilde{\setprim}_{\mathrm{ds}},r}{D} =   {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r$
+So, $\AdvCorrect{\tilde{\setprim}_{\mathrm{ds}},r}{D} =   {\binom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r$
 

### 2016-10-01 ny-def-comparison.tex
no message
fixing ds-correctness

--- 2016-09-27 ny-def-comparison.tex
@@
-\section{Comparison to the Naor-Yogev definition.}
+\section{Comparison to the Naor-Yogev Definition}
+\label{sec:compare-defs}
+%\fixme{Uses $(t,q,\epsilon)$-style notion and theorem statements.  May
+%be okay because this is a self contained appendix, but better if
+%consistent with the rest of the document.}
 The structure of the Naor-Yogev definition is different from ours.
-Lifting their definition\footnote{They focus specifically on set-representation data
-structures
-with no false negatives, and their data-structure syntax
-does not distinguish public and private portions of the representation. Nevertheless, it is straightforward
-to extend their definition to more closely match ours.}
-to our setting,
-the experiment is similar but the attacker
+They focus specifically on set-representation data
+structures with no false negatives, and their data-structure syntax
+does not distinguish public and private portions of the
+representation. Nevertheless, it is straightforward
+to extend their definition to more closely match ours; we do that next.
+Their experiment is similar but the attacker
 succeeds only if it outputs a (single) query $\qry$ for which
@@
 data structure~$\Pi$ is $(t,q,\epsilon)$-NY-correct if
-$\NYAdvCorrect{\Pi}{t,q} \leq \epsilon$. \jnote{This should all probably
-move to an appendix; it's a lot of notation to digest for something we never use again
-in the paper.}
+$\NYAdvCorrect{\Pi}{t,q} \leq \epsilon$. 
+%\jnote{This should all probably
+%move to an appendix; it's a lot of notation to digest for something we never use again
+%in the paper.}
 
@@
 \centering
-\fpage{.6}{
+\fpage{.65}{
 \hpagess{.5}{.45}
@@
 }
-\caption{The Naor-Yogev definition of
-correctness, adapted to our setting.}
+\caption{The Naor-Yogev definition of correctness, adapted to our setting.}
 \label{fig:NYcorrectness}
@@
 With the above in place we can now relate their definition to ours.
-
-\jnote{Do we have a compelling example of why the definition in Figure~\ref{fig:correctness}
-is ``better'' than the definition in
-Figure~\ref{fig:NYcorrectness}?}\tsnote{I don't know, but we do seem
-to have a compelling list of shortcomings of their notion, which ours
-doesn't seem to suffer. Anyway, it's a bit of an unfair comparison, in
-their favor.  You're lifting their notion to ours, which is more
-general.  And by the time we get to that, we have already done them
-the favor of cleaning up the syntax, so that their ``lifted'' notion
-looks better than it was.} \jnote{I agree, it's just that once we have ``lifted'' it
-appropriately, it's not clear what's wrong with it and why we introduce a different
-style of definition.}
-
 \begin{theorem}
@@
 
-\jnote{The above is tight, at least for $r=1$. Specifically, consider a scheme
+We note that the above is tight, at least for $r=1$. Specifically, consider a scheme
 in which every query is independently
@@
 for any $t, q$, however an adversary making $q=1/\epsilon$ queries has constant advantage
-under our correctness definition (for $r=1$).}
+under our correctness definition (for $r=1$).
 
@@
 
-\jnote{I'm not sure what to conclude from any of the results above. The proofs
-are also all trivial.} \tsnote{Trivial or not, it's all part of the
-overall contribution, which is putting this topic on a solid
-foundation.  We can move it all to an appendix, but I still see it as
-very worthwhile.} \jnote{It's worth having for completeness, I'm just not sure
-what we (or the reader) is supposed to do with it. It's not like we can draw
-any simple conclusions like ``our definition implies theirs'' or anything.}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2016-10-01 results.tex
fixing ds-correctness

@@
 
-\begin{theorem}[{\rm Correctness of private-$M$ GBF in the ROM}]\fixme{FINISH! (Animesh?)}\label{thm:gbf-correctness}
+\begin{theorem}[{\rm Correctness of private-$M$ GBF in the ROM}]\label{thm:gbf-correctness}
 Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the private-$M$ garbled Bloom filter.
@@
 \[
-\AdvCorrect{\setprim_{\mathrm{gbf}},r}{A} \leq  {\dbinom{q_T}{r}} \left( \dfrac{1}{2^{\lambda}} \right)^r\,.
+\AdvCorrect{\setprim_{\mathrm{gbf}},r}{A} \leq \mbox{\fixme{}}
 \]

### 2016-10-01 ds-correctness.tex
Proofs
typo

@@
 Figure~\ref{fig:ds-correctness-games}.
-In game \game{0} adversary $A$ attacks the xcorrectness game with  hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpCorrect{\setprim_{\mathrm{ds}},r}{A}$.
+In game \game{0} adversary $A$ attacks the correctness game with  hash functions $h_j(x) = \FK $, and hence exactly simulates $\ExpCorrect{\setprim_{\mathrm{ds}},r}{A}$.
 \begin{equation}
@@
 \caption{Left: Adversary $B$ simulating $\game{0}(A)$ and $\game{1}(A)$ respectively for the
-proof of Theorem~\ref{thm:ds-correctness}. Right: Zero-query adversary $D$ for Theorems~\ref{thm:ds-correctness} }\label{fig:ds-correctness-adv}\label{fig:lin-correctness-zq-adv}
+proof of Theorem~\ref{thm:ds-correctness}. Right: Adversary $D$ for Theorems~\ref{thm:ds-correctness} }\label{fig:ds-correctness-adv}\label{fig:lin-correctness-zq-adv}
 %\fixme{Animesh: remove Crefs, make caption refer to correct theorem}

### 2016-10-01 abstract.tex
adding abstract

We initiate a provable-security treatment of abstract data structures, by formalizing them as syntactic primitives, and considering their correctness and privacy first-class security properties.  Our syntax is quite broad, capturing a wide variety of in-use and academic data structures.  Concretely, we explore the security of several data structures that support (approximate) set-membership tests.  Our notion of correctness captures an adversaries ability to cause the data structure to err via its allowed set of queries.  Our main privacy notion neatly captures what is leaked by the public portion of the data structure.  As certain widely used set-membership data structures, like the Bloom filter, do not meet our notion, we consider a secondary notion of onewayness; essentially, capturing the inability to reproduce any element of the set given the public portion of the data structure.  We also compare our notions to recent work by Naor and Yogev (Crypto'15), which also considers Bloom-filter-like data structures, albeit in a much more limited way.  Our syntax and notions let us consider security under a variety of usage scenarios, by clearly surfacing the split between public and private portions of the data structure.

We see this work as laying the foundation for a number of follow-on efforts, for example to study dynamic data structures (e.g. Bloom filter variants whose representation changes over time), and the security of primitives built on top of abstract data structures.

### 2016-10-01 results.tex
adding abstract

@@
 
-\begin{theorem} %\label{thm:priv-ss}
+\begin{theorem} \label{thm:bi-ds-prf-priv-ss}
 Let $\Pi$ be the set-representation data structure in
@@
 
-Our simulator $\Sim$, on input $L = \{n_{S'}\}_{S' \subseteq S}$,
+Our simulator $\Sim$ (see Figure~\ref{lab:sim-bi-ds-prf}), on input $L = \{n_{S'}\}_{S' \subseteq S}$,
 proceeds as follows. Let $N = n_S$ denote the size of~$S$. The
@@
 
-\begin{figure}[h]
+\begin{figure}[th]
 \centering
 \fpage{0.5}{
+\algorithmv{$\Sim(\leak(S))$}\\
 $\pubaux \gets \emptystring$\\
@@
 }
+\caption{Simulator for the proof of Theorem~\ref{thm:bi-ds-prf-priv-ss} }
+\label{fig:sim-bi-ds-prf}
 \end{figure}
@@
 that, as described in~\cite{xxx}, $\lambda$ must be at least the
-bit-length of the longest element $x \in S$. \tsnote{This could be
+bit-length of the longest element $x \in S$. In practice, this could be
   handled with a slight change to the set membership test, by checking
 if the $\lambda$-bit shares xor to, say, the $\lambda$-bit truncation
-of~$x$.}}
+of~$x$.}
 Let us consider a practically interesting set of parameters. Say you have a 1000-position
 filter, $m=1000$, and a 100-element set, $n=100$,  and $k=4$ hash
-functions (a la Squid\cite{fan2000summary}).  This results in a false-positive rate of
+functions (a la Squid~\cite{fan2000summary}).  This results in a false-positive rate of
 approximately 1\% in a classical BF.  There are roughly $2^{35}$
@@
 Switching now to the case of a \emph{private}-$M$ GBF, i.e., $\pubaux=\emptystring, \privaux=\langle M \rangle$, we have the
-following correctness bound.
-
+following correctness bound. \fixme{Probably punt on this until the
+  full version}
+%
 \begin{theorem}[{\rm Correctness of private-$M$ GBF in the ROM}]\label{thm:gbf-correctness}

### 2016-10-01 abstract.tex
citation

@@
 As certain widely used set-membership data structures, like the Bloom filter, do not meet our notion, we consider a secondary notion of onewayness; essentially, capturing the inability to reproduce any element of the set given the public portion of the data structure.
-We also compare our notions to recent work by Naor and Yogev (Crypto'15), which also considers Bloom-filter-like data structures, albeit in a much more limited way.
+We also compare our notions to recent work by Naor and Yogev~\cite{naor2015bloom}, which also considers Bloom-filter-like data structures, albeit in a much more limited way.
 Our syntax and notions let us consider security under a variety of usage scenarios, by clearly surfacing the split between public and private portions of the data structure.

### 2016-10-01 results.tex
reference
cite

@@
 be the set-membership data structure defined on the right-hand side
-of Figure~\ref{fig:lin-and-ds}. As in the preceding theorem, the
+of Figure~\ref{fig:bf-and-ds}. As in the preceding theorem, the
 following says (informally) that if~$F$ is a secure PRF, then this
@@
 Let $\setprim_{\bilin}= (\Rep, \Qry)$ be the set-membership data
-structure described in Figure~\ref{fig:neidermayer}, but with
+structure described in Figure~\ref{fig:lin-and-bi-lin}, but with
 $F_{K}$ replaced by a random function~$\rho$. Let

### 2016-10-01 intro.tex
intro

@@
 to that same party. Existing definitions do not address privacy in
-this sense at~all.
+this sense at~all. The concerns outlined above motivate a careful, formal treatment of data structures in an adversarial setting, 
+where both \emph{correctness} and \emph{privacy} are considered. In this work we initiate such a
+treatment for abstract data structures.
 
-The concerns outlined above motivate a careful treatment of data
-structures in an adversarial setting, where both \emph{soundness}
-and \emph{privacy} are considered. In this work we initiate such a
-treatment for abstract data structures, and also explore the
+Loosely speaking, we formalize a data structure as a pair of algorithms $(\Rep,\Qry)$, the representation and query-evaluation algorithms, respectively.
+The randomized representation algorithm takes in an abstract object~$S$ and produces public representation data $\pubaux$ and private representation data $\privaux$.
+Intuitively, $\pubaux$ is considered public information, whereas $\privaux$ is meant to be known only to the party running $\Qry$.
+The deterministic query-evaluation algorithm uses $\pubaux$ and $\privaux$ in order to (approximately) evaluate permitted queries $\qry$, which are arbitrary functions over abstract objects.
+We say ``approximately''  evaluate permitted queries because $\pubaux$ and $\privaux$ may not contain all of the information sufficient to determine the true value of $\qry(S)$ for all~$S$.
+
+Let us give an example.
+Consider the classic Bloom filter~\cite{bloom1970space}, in which case $\pubaux$ will consist of the bit array~$M$ that represents a given set~$S$, as well as descriptions of the hash functions $H_1,H_2,\ldots,H_k$ used to produce~$M$; $\privaux$ will be empty.
+The permitted queries will be predicates of the form $\qry_x(S)=1$ iff $x \in S$.
+The~$\Qry$ algorithm, on input $M,H_1,H_2,\ldots,H_k$ and $\qry_x$, carries out the standard Bloom filter set-membership test to decide whether or not $x \in S$.
+It is well known that Bloom fiters admit false-positive errors, thus $\Qry$ only approximates the true set-membership test.
+Our correctness security notion will quantitatively capture the approximation error, but in the presense of attackers that adaptively try to induce one or more errors (false-positives, in this case).
+
+By shifting $H_1,H_2,\ldots,H_k$ from $\pubaux$ to $\privaux$, we do not change the functionality at all.
+But we may very well change the security profile of the resulting Bloom filter variant.
+Indeed, this is the case.
+When $H_1,H_2,\ldots,H_K$ are assumed to be good pseudorandom functions, we can prove that this variant achieves a kind of ``semantic security'' privacy guarantee: the bit array~$M$ is well known to leak a good approximation of~$|S|$, and our notion shows that it leaks nothing more than this.
+(Such a result is not possible for the standard Bloom filter, or any other data structure with empty~$\privaux$.)
+
+This example offers a hint at the broad range of abstract data structures our syntax supports.
+In this paper, we put the syntax and our security notions to work, analyzing Bloom filters in the random oracle model~\cite{broder2004network}, with PRFs for hash functions{niedermeyer2014cryptanalysis,naor2015bloom}, and with secret hash functions that fall short of being PRFs (so-called ``linear-PRF'' hash functions~\cite{kirsch2006less,niedermeyer2014cryptanalysis}), each representing an in-use or proposed Bloom filter variant.
+The linear-PRF Bloom filter provides an opportunity to see just how brittle constructions can be to their usage.
+When used to create a representation of a set, we prove that the linear-PRF Bloom filter offers both correctness and privacy.
+However, when applied to a multiset (effectively) privacy is lost.
+In fact, Niedermeyer et al.~\cite{niedermeyer2014cryptanalysis} show that the linear PRF Bloom filter, when applied to a collection of bigrams of German last names, admits a practical attack that reveals the names.
+Note that this is despite the fact that the hash functions are constructed from secretly-keyed PRFs in a way that has been suggested in recent literature on Bloom filter variants~\cite{kirsch2006less}.
+We also consider garbled Bloom filters, proposed by Dong et al.~\cite{dong2013private} as a key piece of a private set-intersection protocol.
+
+We see this work as laying the foundation for a number of follow-on studies.
+For example to study dynamic data structures, such as counting Bloom filters\cite{xxx}, stable Bloom filters~\cite{xxx}, count-min sketches~\cite{xxx}, hierachical Bloom filters~\cite{xxx}, to name just a few in the extended Bloom filter family.
+Another direction would be to explore the security of primitives built \emph{from} these sorts of data structures, such as content-distribution networks (where many servers propogate representations of their local cache to their neighbors)
+
+ and the security of primitives built on top of abstract data structures.
+
+We also explore the
+
 security of several specific data structures---that can all be
@@
   connecting the adaptive setting to the zero-query setting.}
+
+%Bloom filters have a broad range of practical applications, for
+%example, in content-distribution networks, large database query
+%processing, routing algorithms for peer-to-peer networks, protocols
+%for establishing linkages between medical-record databases, fair
+%routing of TCP packets, Bitcoin wallet synchonization~\cite{schnell2011novel,niedermeyer2014cryptanalysis,gervais2014privacy,nojima2009cryptographically,feng2001stochastic,reynolds2003efficient,byers2002informed,broder2004network}.
 

### 2016-10-01 intro.tex
intro

@@
 For example to study dynamic data structures, such as counting Bloom filters\cite{xxx}, stable Bloom filters~\cite{xxx}, count-min sketches~\cite{xxx}, hierachical Bloom filters~\cite{xxx}, to name just a few in the extended Bloom filter family.
-Another direction would be to explore the security of primitives built \emph{from} these sorts of data structures, such as content-distribution networks (where many servers propogate representations of their local cache to their neighbors)
-
- and the security of primitives built on top of abstract data structures.
-
-We also explore the
-
-security of several specific data structures---that can all be
-viewed as generalizations of Bloom
-filters~\cite{bloom1970space}---supporting (approximate)
-set-membership queries. Specifically, we show \ldots \todo{highlight
-that we are able surface ways in which constructions
-  are sensitive to use cases, i.e. schemes secure with secret hash
-  functions but not with public hash functions}
-\todo{Somewhere in the intro, might what to face the ``nothing hard''
-  criticism head on.  Perhaps mention that many of the results follow
-  a common pattern (which, for privacy, we tease out in a general
-  theorem), and that often the most technically difficult part is
-  connecting the adaptive setting to the zero-query setting.}
-
-%Bloom filters have a broad range of practical applications, for
-%example, in content-distribution networks, large database query
-%processing, routing algorithms for peer-to-peer networks, protocols
-%for establishing linkages between medical-record databases, fair
-%routing of TCP packets, Bitcoin wallet synchonization~\cite{schnell2011novel,niedermeyer2014cryptanalysis,gervais2014privacy,nojima2009cryptographically,feng2001stochastic,reynolds2003efficient,byers2002informed,broder2004network}.
+Another direction would be to explore the security of primitives built \emph{from} these sorts of data structures, such as content-distribution networks (where many servers propogate representations of their local cache to their neighbors), or cryptographic strike lists (a la early versions of the QUIC protocol~\cite{xxx}) for nonce-replay protection.
+The Bloom filter family alone has a wide range of practical applications, for example in large database query
+processing, routing algorithms for peer-to-peer networks, protocols
+for establishing linkages between medical-record databases, fair
+routing of TCP packets, and Bitcoin wallet synchonization~\cite{schnell2011novel,niedermeyer2014cryptanalysis,gervais2014privacy,nojima2009cryptographically,feng2001stochastic,reynolds2003efficient,byers2002informed,broder2004network}.
 
@@
 set-membership data structures), and consider privacy in addition to
-soundness. Even with respect to the specific case of soundness for
+correctness. Even with respect to the specific case of correctness for
 set-membership data structures, our work offers several advantages
@@
     we analyze Bloom filters in the random-oracle model.
-    \jnote{Which are widely used?}
 \end{itemize}
-\tsnote{I think we can say a bit more here about what they show, and
-  why their presentation is lacking, certainly as a work that anchors
-  an important area of study.  This feels a bit weak, at the moment.
-  For example, at the opening of this section we say they consider
-  ``adversarial soundness for Bloom filters'', but I assert that it
-  isn't clear that their syntax allows them to study Bloom filters at all.}
-  \jnote{I'm a little concerned about walking the line between
-  criticizing them and offending them. I also wouldn't say ``their
-  syntax doesn't allow them to study Bloom filters''; is that
-  because they don't deal with random oracles?}
-We give a more detailed comparison to, and criticism
-of~\cite{naor2015bloom} in Appendix~\ref{sec:xxx}. \jnote{Any
-comparison/criticism should be in the Intro. The Appendix is just a
-technical comparison of different styles of definition.}
+We give a technical comparison of our correctness notion and theirs (lifted to our more general syntax)
+in Appendix~\ref{sec:xxx}.
 

### 2016-10-01 intro.tex
cheers

@@
     portions of a data structure, something that was left
-    ambiguous in~\cite{naor2015bloom}. This allows us, for
+    ambiguous\footnote{In fact, it isn't clear that their formalization actually allows for standard Bloom filters, although fixing this ambiguity is straightforward once recognized.} in~\cite{naor2015bloom}.
+This allows us, for
     example, to distinguish between the hash-function keys and
@@
 \end{itemize}
+
 We give a technical comparison of our correctness notion and theirs (lifted to our more general syntax)
 in Appendix~\ref{sec:xxx}.
-
-\todo{Describe the BF variants we consider, and briefly why they are
-  natural/interesting.}
-\todo{Surface contribution of setting the stage for a bunch of future
-  work: dynamic data-structures (including counting BFs, stable BFs,
-  hierarchical BFs, count-min-sketches, etc.); security of common
-  usages of BF and related data structures (e.g. CDNs and other
-  distributed storage, find more); more generally bringing to the
-  attention of the community the need to give proper cryptographic
-  treatment to data structures (which may not have been conceived with
-  security-critical applications in mind but have been co-opted for
-  them (like BFs).}
-%false-positive error, is a parameter of the Bloom filter.  (The
-%values of~$\epsilon,m,k$, and $|\mathcal{S}|$ are related in a
-%well-known way.) NY recast this soundness condition as a game in
-%which an adversary~$A$ is given~$\mathcal{S}$ and an oracle for
-%set-membership queries, and it attempts to find one or more false
-%positives. The fact that~$A$ can \emph{adapt} its queries and its
-%output based on what it learns from the set-membership oracle (but,
-%as we will see, not upon the hash functions) is the key definitional
-%contribution of~NY.
-
-%Bloom filters have a broad range of practical applications, for
-%example, in content-distribution networks, large database query
-%processing, routing algorithms for peer-to-peer networks, protocols
-%for establishing linkages between medical-record databases, fair
-%routing of TCP packets, Bitcoin wallet synchonization~\cite{schnell2011novel,niedermeyer2014cryptanalysis,gervais2014privacy,nojima2009cryptographically,feng2001stochastic,reynolds2003efficient,byers2002informed,broder2004network}.
 

### 2016-10-01 results.tex
cheers

@@
 
-Our simulator $\Sim$ (see Figure~\ref{lab:sim-bi-ds-prf}), on input $L = \{n_{S'}\}_{S' \subseteq S}$,
+Our simulator $\Sim$ (see Figure~\ref{fig:sim-bi-ds-prf}), on input $L = \{n_{S'}\}_{S' \subseteq S}$,
 proceeds as follows. Let $N = n_S$ denote the size of~$S$. The
@@
 
-Switching now to the case of a \emph{private}-$M$ GBF, i.e., $\pubaux=\emptystring, \privaux=\langle M \rangle$, we have the
-following correctness bound. \fixme{Probably punt on this until the
-  full version}
+In the full version of this paper, we will give a correctness bound
+for the \emph{private}-$M$ GBF, i.e., $\pubaux=\emptystring,
+\privaux=\langle M \rangle$, in the random-oracle model.  
 %
-\begin{theorem}[{\rm Correctness of private-$M$ GBF in the ROM}]\label{thm:gbf-correctness}
-Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the private-$M$ garbled Bloom filter.
+%\begin{theorem}[{\rm Correctness of private-$M$ GBF in the ROM}]\label{thm:gbf-correctness}
+%Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the private-$M$ garbled Bloom filter.
 For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
-\[
-\AdvCorrect{\setprim_{\mathrm{gbf}},r}{A} \leq \mbox{\fixme{}}
-\]
-\end{theorem}
+%\[
+%\AdvCorrect{\setprim_{\mathrm{gbf}},r}{A} \leq \mbox{\fixme{}}
+%\]
+%\end{theorem}
 

### 2016-10-01 intro.tex
intro

@@
 This example offers a hint at the broad range of abstract data structures our syntax supports.
-In this paper, we put the syntax and our security notions to work, analyzing Bloom filters in the random oracle model~\cite{broder2004network}, with PRFs for hash functions{niedermeyer2014cryptanalysis,naor2015bloom}, and with secret hash functions that fall short of being PRFs (so-called ``linear-PRF'' hash functions~\cite{kirsch2006less,niedermeyer2014cryptanalysis}), each representing an in-use or proposed Bloom filter variant.
+In this paper, we put the syntax and our security notions to work, analyzing Bloom filters in the random oracle model~\cite{broder2004network}, with PRFs for hash functions~\cite{niedermeyer2014cryptanalysis,naor2015bloom}, and with secret hash functions that fall short of being PRFs (so-called ``linear-PRF'' hash functions~\cite{kirsch2006less,niedermeyer2014cryptanalysis}), each representing an in-use or proposed Bloom filter variant.
 The linear-PRF Bloom filter provides an opportunity to see just how brittle constructions can be to their usage.
@@
 We see this work as laying the foundation for a number of follow-on studies.
-For example to study dynamic data structures, such as counting Bloom filters\cite{xxx}, stable Bloom filters~\cite{xxx}, count-min sketches~\cite{xxx}, hierachical Bloom filters~\cite{xxx}, to name just a few in the extended Bloom filter family.
-Another direction would be to explore the security of primitives built \emph{from} these sorts of data structures, such as content-distribution networks (where many servers propogate representations of their local cache to their neighbors), or cryptographic strike lists (a la early versions of the QUIC protocol~\cite{xxx}) for nonce-replay protection.
+For example to study dynamic data structures, such as counting Bloom filters\cite{fan2000summary}, scalable Bloom filters~\cite{almeida2007scalable}, count-min sketches~\cite{cormode2005improved}, hierachical Bloom filters~\cite{zhu2004hierarchical}, to name just a few in the extended Bloom filter family.
+Another direction would be to explore the security of primitives built \emph{from} these sorts of data structures, such as content-distribution networks (where many servers propogate representations of their local cache to their neighbors), or cryptographic strike lists (a la early versions of the QUIC protocol) for nonce-replay protection.
 The Bloom filter family alone has a wide range of practical applications, for example in large database query

### 2016-10-01 intro.tex
intro
related work

--- 2016-10-01 intro.tex
@@
 \input{related-work}
-\jnote{See the discussion of related work in
-Naor-Yogev. We should cite [LN93]. I can't tell how relevant [MNS11]
-is. [HW13] seems relevant, though I don't think it is captured by
-our current definitions.}
+%\jnote{See the discussion of related work in
+%Naor-Yogev. We should cite [LN93]. I can't tell how relevant [MNS11]
+%is. [HW13] seems relevant, though I don't think it is captured by
+%our current definitions.}
 
-\jnote{Discuss use of BFs and BF variants in a security-oriented
-setting. Also some prior work formalizing BFs in an adversarial
-environment. See commented out portion of the .tex}
+%\jnote{Discuss use of BFs and BF variants in a security-oriented
+%setting. Also some prior work formalizing BFs in an adversarial
+%environment. See commented out portion of the .tex}
 

### 2016-10-01 related-work.tex
related work

@@
-Bloom filters are one of the most widely used data structures for set-membership queries.
+The Naor-Yogev paper~\cite{naor15bloom} served as inspiration for our work.
+We recommend reading the very good related work section contained in their paper for a discussion of related theory papers.
+Here we mention a few additional practical works, but stress that this only scratches the surface.
+
+As previously mentioned Bloom filters and their relatives are some of the most widely used data structures supporting set-membership queries.
+We give a few more, here.
 Hbase, a hadoop based NoSql database designed to handle large datasets has an implementation of Bloom filter and counting Bloom filter.
 Hbase is the open-source implementation of Google's BigTable storage system~\cite{chang2008bigtable}.
-Stochastic Fair Blue~\cite{feng2001stochastic} uses counting Bloom filter to manage non-responsive TCP traffic.
-The counting Bloom filters are used as accounting bins to maintain statistics of packets belonging to each bin based on their queue lengths.
-In Squid~\cite{fan2000summary}, each web proxy server uses a bloom filter(summary cache) corresponding to the set of URL's in its cache to perform membership look-up of incoming URL's.
-Also, it has bloom filters of its neighboring proxy servers.
+The Squid proxy~\cite{fan2000summary} uses a bloom filter as a ``summary cache'' of the set of URLs in its cache in order to web object retreival latency.
+Crossby and Walach~\cite{crosby2003denial} exploited hash collisions in Squid to increase the average URL load time.
+In an older paper, Lipton and Naughton~\cite{lipton1993clocked} showed how timing analysis of record insertion in a hash table can help an adversary to adapt and chose elements that take more time to be mapped into the hash table.
 Reynolds and Vahdat~\cite{reynolds2003efficient} proposed an efficient distributed search engine that can be used to search for files that contain a particular keyword.
@@
 Record linkage is very often required to collect and combine records from different databases.
-In absence of unique identification number of the records, privacy preserving record linkage(PPRL) is used.
+
 Schnell et.
-al.~\cite{schnell2011novel} proposed Cryptographic Longterm Key to carry out PPRL.
-They used secretly keyed hash functions to create a Bloom filter for each surname.
+al.~\cite{schnell2011novel} proposed the so-called ``Cryptographic Longterm Key'' as a way to support privacy-preserving record linkage.
+This uses secretly keyed hash functions to create a Bloom filter for each surname.
 The surname is broken into bigrams and mapped into the Bloom filter with secret hash functions.
+Subsequently, Niedermeyer et al.~\cite{niedermeyer2014cryptanalysis} showed an attack on a database of German surnames which were stored in secretly hashed Bloom filters, similar to Cryptographic Longterm Key.
 
-Niedermeyer et al.~\cite{niedermeyer2014cryptanalysis} showed an attack on a database of German surnames which were stored in secretly hashed Bloom filters, similar to Cryptographic Longterm Key.
-A Bloom filter that uses $k$ hash functions will have minimum hamming weight of $k$.
-Using this fact, an adversary can filter out Bloom filters that have hamming weight less than 15.
-This is an example of how inherent properties of a data structure can be used by an adversary.
-Crossby and Walach~\cite{crosby2003denial} exploited hash collisions in Squid to increase the average URL load time.
-They carried out two experiments to show this attack.
-In experiment 1, around 143K random URL's were requested to the proxy server, whereas in experiment 2, same number of carefully chosen URL's (adaptive queries) that collide with the already present URL's in the hash-table were requested.
-They observed that the load time of random URL's was less than the chosen URL's, and hence can be used to degrade performance of a proxy server.
-Whenever there is a collision in a hash table, some amount of extra time is required for collision resolution.
-In an older paper, Lipton and Naughton~\cite{lipton1993clocked} showed how timing analysis of record insertion in a hash table can help an adversary to adapt and chose elements that take more time to be mapped into the hash table.
+Stochastic Fair Blue~\cite{feng2001stochastic} uses counting Bloom filter to manage non-responsive TCP traffic.

### 2016-10-01 intro.tex

--- 2016-10-01 intro.tex
@@
 We give a technical comparison of our correctness notion and theirs (lifted to our more general syntax)
-in Appendix~\ref{sec:xxx}.
+in Appendix~\ref{sec:compare-defs}.
 

### 2016-10-01 results.tex

@@
 practice.\footnote{Note
-that, as described in~\cite{xxx}, $\lambda$ must be at least the
+that, as described in~\cite{dong2013private}, $\lambda$ must be at least the
 bit-length of the longest element $x \in S$. In practice, this could be

### 2016-10-01 results.tex
cheers

@@
 closely follows the proof of correctness for the DS PRF-hash
-construction, Theorem~\ref{thm:ds-correctness}
+construction, Theorem~\ref{thm:ds-correctness}.
 %\input{lin-correctness}
@@
 This construction is of practical interest, as it has been suggested as a way to address the privacy-preserving record-linkage problem, in particular for linking common records in medical databases~\cite{niedermeyer2014cryptanalysis,schnell2011novel}.
-We only address the privacy of this construction, as the correctness follows immediately from the correctness of the Linear-PRF construction.
-The privacy, however, does not.
-Here we exhibit an efficient SS-privacy attack even when simulator is provided nearly the entire set.
-Consider the following ``all-but-last'' leakage function.
-On input a set~$S=\{x_1,x_2,\ldots,x_n\}$, it assigns $x'_n \gets x_n[1:|x_n|-1]$ and returns $\mathsf{leak_{abl}}(S)=\{x_1,x_2,\ldots,x'_n\}$.
-\todo{OW privacy proof?
-Or just some text that says that Niedermeyer et al.
-show something stronger~---OW-privacy violation---~albeit with $n=10000, m=10000\alpha$ for an $\alpha$ that I need to look up.}
+We only address the privacy of this construction, as the correctness
+follows immediately from the correctness of the Linear-PRF
+construction.  The privacy, however, does not.  Here we exhibit an
+efficient SS-privacy attack even when simulator is provided nearly the
+entire set.  Consider the following ``all-but-last'' leakage function.
+On input a set~$S=\{x_1,x_2,\ldots,x_n\}$, it assigns $x'_n \gets
+x_n[1:|x_n|-1]$ and returns
+$\mathsf{leak_{abl}}(S)=\{x_1,x_2,\ldots,x'_n\}$.
 
@@
 \emph{before}~$M$ is determined.  We will see that this carries over
-\tsnote{I think?} to the case in which~$M$ is private (i.e.,
+ to the case in which~$M$ is private (i.e.,
 $\pubaux=\emptystring,\privaux=\langle M \rangle$), but when~$M$ is
@@
 Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the public-$M$ garbled Bloom filter, in the random-oracle model for~$H$.
-Then \fixme{This probability might not be correct...
+Then %\fixme{This probability might not be correct...
 verify when less tired.}

### 2016-10-01 results.tex
cheers

@@
 
-Looking ahead to the next section, we will analyze a closely related construction, which was attacked by Niedermeyer et al.~\cite{niedermeyer2014cryptanalysis} in the context of private medical-record linkage.
-It uses the same linear-PRF hash functions, but has a $\Rep$ algorithm that that does not ensure that the hash functions are called on \emph{distinct} values.
-We show that this is \emph{not} private with respect to our SS notion for a leakage function that leaks nearly the entire set~$S$.
-\todo{It would be better, perhaps, to show that it is not OW secure, since this implies it isn't SS secure, and OW security is what Niedermeyer et al.
-violate.}
+Looking ahead to the next section, we will analyze a closely related
+construction, which was attacked by Niedermeyer et
+al.~\cite{niedermeyer2014cryptanalysis} in the context of private
+medical-record linkage.  It uses the same linear-PRF hash functions,
+but has a $\Rep$ algorithm that that does not ensure that the hash
+functions are called on \emph{distinct} values.  We show that this is
+\emph{not} private with respect to our SS notion for a leakage
+function that leaks nearly the entire set~$S$. 
+%\todo{It would be better, perhaps, to show that it is not OW secure, since this implies it isn't SS secure, and OW security is what Niedermeyer et al. violate.}
 

### 2016-10-01 results.tex
cheers

@@
 \subsection{Domain-Separated PRF-Hash}
-\jnote{Give English-language description of scheme before turning to
-analysis of correctness.}
+Next we consider a natural, secret-key variant of the classic Bloom
+filter.  Here the (private) hash functions are instantiated via
+$H(j,x)=F_K(\langle j,x\rangle)$, using domain-separation to turn a
+PRF (with one secret key) into, effectively, multiple functions that
+are computationally indistinguishable from random.  We call this the
+domain-separated PRF-hash data structure.
 

### 2016-10-01 notions.tex
cheers

@@
 \label{sec:security-notions}
-Following NY, we are interested in defining an adaptive (i.e.,
-adversarial) notion of correctness.
-In addition to correctness, we establish notions of privacy for data structures.
-
-%\fixme{Do we say that all notions can be extended to the ROM by giving
-%all all algorithms to a RO~$H$?  Is this true for the SS-privacy
-%notion?  (It seems to make sense elsewhere.)} \jnote{I think there are subtleties for the SS notion.}
-
-\todo{flesh out opening text}
+Following NY, we are interested in defining an adaptive (i.e.,adversarial) notion of correctness.
+In addition to correctness, we establish two kinds of privacy notions for data structures.
 
@@
 the random oracle during the first stage when it selects~$S$, as that set
-should have no dependence on the random oracle.) \jnote{In ``practice'' wouldn't someone
-just use SHA as their random oracle, hence providing an attacker with the ability
-to make $S$ depend on the random oracle? This point needs to be justified a bit.}
+should have no dependence on the random oracle.)
 
@@
 any data structure that always ensures that there are exactly $r$ (easy to find)
-queries that cause an error will~do. \jnote{Not sure if it is worthwhile being more formal.}
+queries that cause an error will~do. %\jnote{Not sure if it is worthwhile being more formal.}
 We remark that the Naor-Yogev definition does not capture such distinctions
@@
 
-\subsubsection{A Simulation-Based Definition }
-
-\jnote{I like ``simulation-based security'' rather than ``semantic security.''}
-
+\heading{A Simulation-Based Definition. }
+%\jnote{I like ``simulation-based security'' rather than ``semantic security.''}
 Our simulation-based definition is given in
@@
 Finally, it is worth noting that the ``minimal'' leakage we consider in this work
-is leakage of the size of the data. (I.e., when $S$ is a set then we would
+is leakage of the size of the data. (i.e., when $S$ is a set then we would
 consider ${\sf leak}(S)=|S|$ as minimal leakage.) This is by analogy with encryption.
@@
 
-\subsubsection{``One-wayness''}
-
+\heading{``One-wayness''.}
 Here we specialize to the case of set-membership data structures.
@@
 %\end{figure}
-\todo{A simple theorem that says if $\privaux=\emptystring$ then
-  SS-privacy is unachievable for any leakage other than $\leak(S)=S$?
-It's at least worth a highlighted remark, I think.  Currently it is a
-remark in the classical BF section, but it seems worth ``pulling up''.} \jnote{Yes, agreed.}
-\todo{Since we mention what happens with $\privaux=\emptystring$, also
-mention what happens with $\pubaux=\emptystring$ :)}
+%\todo{A simple theorem that says if $\privaux=\emptystring$ then
+ % SS-privacy is unachievable for any leakage other than $\leak(S)=S$?
+%It's at least worth a highlighted remark, I think.  Currently it is a
+%remark in the classical BF section, but it seems worth ``pulling up''.} \jnote{Yes, agreed.}
+%\todo{Since we mention what happens with $\privaux=\emptystring$, also%
+%mention what happens with $\pubaux=\emptystring$ :)}
 
@@
 
-\subsubsection{Privacy of ``Canonical'' Data Structures }
+\heading{Privacy of ``Canonical'' Data Structures. }
 Here we prove a result that will be used in the next section

### 2016-10-01 results.tex
pus

--- 2016-10-01 results.tex
@@
 The proof follows the same high-level ideas as in the proof of
-Theorem~\ref{fig:DS-bigram}, based on the observation that ${\sf
+Theorem~\ref{thm:priv-ss}, based on the observation that ${\sf
 leak}_\cap(S)$ suffices to determine the overlap in calls to the
@@
 The proof that this provides a good simulation is identical to that
-of Theorem~\ref{fig:DS-bigram}. \hfill\qed
+of Theorem~\ref{thm:priv-ss}. \hfill\qed
 \end{proof}

### 2016-10-01 notions.tex
last

--- 2016-10-01 notions.tex
@@
 
-\todo{flesh out opening text}
+%\todo{flesh out opening text}
 
@@
 %\end{figure}
-\todo{A simple theorem that says if $\privaux=\emptystring$ then
-  SS-privacy is unachievable for any leakage other than $\leak(S)=S$?
-It's at least worth a highlighted remark, I think.  Currently it is a
-remark in the classical BF section, but it seems worth ``pulling up''.} \jnote{Yes, agreed.}
-\todo{Since we mention what happens with $\privaux=\emptystring$, also
-mention what happens with $\pubaux=\emptystring$ :)}
+%\todo{A simple theorem that says if $\privaux=\emptystring$ then
+%  SS-privacy is unachievable for any leakage other than $\leak(S)=S$?
+%It's at least worth a highlighted remark, I think.  Currently it is a
+%remark in the classical BF section, but it seems worth ``pulling up''.} \jnote{Yes, agreed.}
+%\todo{Since we mention what happens with $\privaux=\emptystring$, also
+%mention what happens with $\pubaux=\emptystring$ :)}
 

### 2016-10-12 EC17-submitted/ds-correctness.tex
EC17-submitted

--- 2016-10-01 ds-correctness.tex
@@
 Let $D$ be an adversary shown in Figure~\ref{fig:lin-correctness-zq-adv}.
-It effectively simulates game~$game{3}$, guessing which~$r$ of~$A$'s queries to send to its own~$\TestOracle$.
+It effectively simulates game~$\game{3}$, guessing which~$r$ of~$A$'s queries to send to its own~$\TestOracle$.
 By its construction, if $\game{3}(A)=1$ then~$D$ will also find~$r$ errors in~$\tilde{\setprim}_{\mathrm{ds}}$.

### 2016-10-12 EC17-submitted/syntax.tex
EC17-submitted

--- 2016-10-01 syntax.tex
@@
-\newcommand{\qry}{\mathsf{qry}}
 \section{Preliminaries}
@@
 in that string, and $x[i:j]$ for the substring $x[i]x[i+1]\cdots
-x[j]$.  \tsnote{need subset of size~$r$ notation}
+x[j]$.  %\tsnote{need subset of size~$r$ notation}
 
@@
 
-\todo{Insert discussion of syntax, if needed.  If we think it is
-  helpful to discuss the size of the representation, we can declare it
-as $|\pubaux|+|\privaux|$ and comment that if one wants to compare to
-classical size bounds, a more fine-grained separation of the output of
-$\Rep$ would allow this.}
-
 \begin{definition}[Error probability and rate] \rm
@@
 \end{definition}
-\todo{Words :)  Can compare the (normal) error probability to
-  the adversarial soundness probability.  Perhaps pull back some of
-  the previous example for building intuition about the difference
-  between the two.}
 
@@
 An important special case is a data structure that supports set-membership
-queries. \jnote{I changed this from multiplicity to membership.}
-
+queries. 
 \begin{definition} \rm

### 2016-10-12 EC17-submitted/GBF-correctness-private-M.tex
Copying files not used in submission to EC17-submitted

--- 2016-09-30 GBF-correctness-private-M.tex
@@
 \fixme{for BF proof, this actually does more, it makes a hash query as good as a test query, because~$M$ is public.}  Thus, $\Prob{\game{2}(A) = 1} \leq \Prob{\game{3}(A) = 1}$.
+We assume from Game~$\game{3}$ and on that $\Rep$ is also appropriately modifed for the new behavior of~$\HashOracle$.
 
@@
 In particular, game~$\game{5}$ returns 1 exactly when~$\game{4}$ would return 1 \emph{and} the boolean~$\bad$ would have remained false in~$\game{4}$.
-This implies that~$game{4}$ managed to guess exactly the queries that would result in correctness errors, and hence
+This implies that~$\game{4}$ managed to guess exactly the queries that would result in correctness errors, and hence
 $\Prob{\game{5}(A)=1} = \dfrac{1}{\binom{q_T + q_H}{r}}\Prob{\game{4}(A)=1}$.
 
-When~$r=1$, Game~$\game{5}$ exactly simulates the
+Game~$\game{6}$ alters $\HashOracle$ so that it returns what would
+previously have be stored in $\mathrm{Ans}[\cdot]$, so we can drop the
+$\TestOracle$ altogether.  Thus $\Prob{\game{5}(A)=1} =
+\Prob{\game{6}(A)=1}$.
+
+Let us now consider the probability that
 
@@
 }
+\fpage{.85}{
+\hpagessl{.5}{.45}
+{
+\underline{$\game{6}(A)$}\\
+$c\gets 0$, $\bad \gets \false$\\
+$\err \gets 0$;  $\calC \gets \emptyset$\\
+$S \getsr A$\\
+$\mathcal{I}\getsr [\{1,2,\ldots,q_T + q_H\}]^r$\\
+$(\pubaux,\privaux) \getsr \Rep^{\HashOracle}(S)$\\
+$\bot \getsr A^{\HashOracle}(\pubaux)$\\
+if $\bad = \true$ then Return 0\\
+if $\err  < r$ then Return 0\\
+Return 1\\
+
+%\oracle{$\TestOracle(\qry_x)$}\\
+%if $x \in \mathcal{C}$ then Return $\bot$\\
+%$\calC \gets \calC \cup x$\\
+%if $\Ans[x] = \undefined$\\
+%\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(\qry_x)$\\
+%Return $\Ans[x]$\\
+
+\oracle{$\HashOracle(\qry_y)$}\\
+$c \gets c + 1$\\
+for $j \in \{1,2,\ldots,k\}$\\
+\nudge $v_j \getsr [m]$\\
+%
+$M \gets\privaux$\\
+$y' \gets M[v_1] \xor M[v_2] \xor \ldots \xor M[v_k]$\\
+if $y' \neq y$ then \\
+\nudge if $c \in \calI$ then $\bad \gets \true$\\
+\nudge Return $\left(0,v_1,\ldots,v_k\right)$\\
+if $c \notin \calI$ then $\bad \gets \true$\\
+$\err \gets \err +1$\\
+Return $\left(1,v_1,\ldots,v_k\right)$
+}
+{
+}
+}
 \caption{Games $\game{4}$-$\game{5}$ and zero-query adversary~$A_0$ for the

### 2016-10-12 EC17-submitted/Theorem3_priv.tex
Copying files not used in submission to EC17-submitted

\begin{theorem}\label{thm3}
A classic Bloom filter is private in random oracle model(ROM), i.e. an adaptive adversary $A$ has low probability of winning the $\ExpPrivPubHashBB{B}{\distr{\univ}{n},A}$ game in ROM. For $q$ queries and min-entropy ($\mu$) of $\distr{\univ}{n}$,

\begin{equation}
\AdvPrivPubHashBB{B}{A} \leq  \frac{q}{2^\mu} + \frac{n}{\abs{\univ}}
\end{equation}

\end{theorem}

\begin{proof}[\Cref{thm3}]
As shown in \Cref{fig:GameT3}, $\game{0}(A)$ and $\game{1}(A)$ exactly simulate $\ExpPrivPubHashBB{B}{\distr{\univ}{n}, A}$ in ROM, except in $\game{1}(A)$, the random oracle always returns $k$ uniformly random values for any $x \in \univ$.
\begin{equation}
\AdvPrivPubHashBB{B}{A} = \Prob{\game{0}(A)=1}\label{eq:0T3}
\end{equation}
%\caption{Game playing argument}\label{fig:Game}
\begin{figure}
\centering
\fpage{.6}{
\hpagess{.4}{.45}
{
$\game{1}(A)$\\
\fbox{$\game{0}(A)$\\
}
$\\ \calS \getsr \distr{\univ}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
$x \getsr A^{\MemOracle,\QryOracle,\HashOracle}(M)$\\
if $x\in \calS$ then Ret 1\\
Ret 0
}
%
{
\oracle{$\MemOracle(x)$}\\
Ret $[x \in \calS]$\\

\medskip
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,\tau,x)$\\

\medskip
\oracle{$\HashOracle(x)$}\\
$\rho_i \getsr Func(\univ,[m])$, for $i\in[1,k]$\\
$z_{i} \gets \rho_i(x)$, for $i\in[1,k]$\\
if $T[x] \neq $ undefined\\
\nudge Bad $\gets$ true\\
\fbox{
$z_i \gets T[x]$, for $i\in[1,k]$
}
$\\T[x] \gets z_i$, for $i\in[1,k]$\\
Ret $z_i$, for $i\in[1,k]$\\
}
}
\caption{\Cref{thm3}: Game playing argument}\label{fig:GameT3}
\end{figure}

\noindent
It is evident from $\game{0}(A)$ and $\game{1}(A)$ that 
\begin{equation}
\Prob{\game{0}(A) : \mathrm{Bad}=\mathrm{true}} = \Prob{\game{1}(A) : \mathrm{Bad}=\mathrm{true}}\label{eq:1T3}
\end{equation}

\noindent
Using fundamental lemma of game playing argument and \Cref{eq:1T3}
\begin{eqnarray}
\nonumber \Prob{\game{0}(A)=1} & \leq & \Prob{\game{0}(A)=1 | \mathrm{Bad} \neq \mathrm{true}} + \Prob{\game{0}(A) : \mathrm{Bad}=\mathrm{true}}\\
&=& \Prob{\game{1}(A)=1} + \Prob{\game{1}(A) : \mathrm{Bad}=\mathrm{true}}\label{eq:2T3}
\end{eqnarray}

\noindent
Let the random oracle be modified to output $k$ uniformly random values without setting any Bad flag. Let's call it $\game{2}(A)$ which is shown in \Cref{fig:Game2T3}. It turns out that the  $\QryOracle$ is no more deterministic due to coins of the random oracle. Hence, the results of the $q$ queries by $A$ are mutually independent and random. So, neglecting the output of $A$, the game samples one of the elements queried by $A$, and returns 1/0.

\begin{equation}
\Prob{\game{1}(A)=1} = \Prob{\game{2}(A)=1} = \frac{q}{2^\mu}\label{eq:3T3}
\end{equation}

\begin{figure}
\centering
\fpage{.6}{
\hpagess{.5}{.5}
{
\underline{$\game{2}(A)$}\\
$\calZ \gets \emptyset$\\
$\calS \getsr \distr{\univ}{n}$\\
$(M,\tau) \getsr \Rep^{\HashOracle}(\calS)$\\
$x' \gets A^{\MemOracle,\QryOracle,\HashOracle}(M)$\\
$x \getsr \calZ$\\
if $x\in \calS $ then Ret 1\\
Ret 0
}
%
{
\oracle{$\MemOracle(x)$}\\
Ret $[x \in \calS]$\\

\medskip
\oracle{$\QryOracle(x)$}\\
Ret $\Qry^{\HashOracle}(M,\tau,x)$\\

\medskip
\oracle{$\HashOracle(x)$}\\
$\calZ \gets \calZ \cup x$\\ 
$\rho_i \getsr Func(\univ,[m])$, for $i\in[1,k]$\\
$z_i \gets \rho_i(x)$, for $i\in[1,k]$\\
Ret $z_i$, for $i\in[1,k]$\\
}
}
\caption{\Cref{thm3}: Game playing argument}\label{fig:Game2T3}
\end{figure}

In $\game{1}(A)$, $T[x]\neq$ undefined, if earlier $\Rep$ asked hash-indices of $x$. So,  Bad $\gets$ true if $A$ queries an element present in $\calS$. 
\begin{equation}
\Prob{\game{1}(A):\mathrm{Bad} = \mathrm{true}} = \frac{n}{\abs{\univ}}\label{eq:4T3}
\end{equation}

From \Cref{eq:0T3,eq:1T3,eq:2T3}, \Cref{eq:3T3} and \Cref{eq:4T3}

\begin{equation}
\AdvPrivPubHashBB{B}{A} \leq  \frac{q}{2^\mu} + \frac{n}{\abs{\univ}}
\end{equation}

\end{proof}

### 2016-10-12 EC17-submitted/TheoremGBF_correctnessUB.tex
Copying files not used in submission to EC17-submitted

--- 2016-09-27 TheoremGBF_correctnessUB.tex
@@
 \begin{theorem}\label{thm:gbf-correctnessUB}
-Fix $k,m,n,r>0$, and let $\Pi_{\mathrm{garb}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described.
+Fix $k,m,n,r>0$, and let $\setprim_{\mathrm{garb}}= (\calQ,\Rep, \Qry)$ be the set-multiplicity data structure just described.
 For any adversary~$A$ that makes a total of $q$ queries to the RO, and has time-complexity~$O(t)$,
 \[
-\AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A}  \leq \left(1 - e^{-n/m^k}\right)^{nr} + \dbinom{q}{r}\left(\dfrac{1}{2^\lambda}\right)^r
+\AdvCorrect{\setprim_{\mathrm{garb}},r}{A}  \leq \left(1 - e^{-n/m^k}\right)^{nr} + \dbinom{q}{r}\left(\dfrac{1}{2^\lambda}\right)^r
 \]
@@
 \[
-\AdvCorrect{\Pi_{\mathrm{garb}},\distr{\calS}{},r}{A}  \leq \left(1 - e^{-n/m^k}\right)^{nr} + \dbinom{q}{r}\left(\dfrac{1}{2^\lambda}\right)^r
+\AdvCorrect{\setprim_{\mathrm{garb}},r}{A}  \leq \left(1 - e^{-n/m^k}\right)^{nr} + \dbinom{q}{r}\left(\dfrac{1}{2^\lambda}\right)^r
 \]

### 2016-10-12 EC17-submitted/canonical-definition-instances.tex
Copying files not used in submission to EC17-submitted

\section{Instances of canonical set-multiplicity data structure}
We check whether various set-multiplicity data structures are captured in this definition. Fix set $S$ with elements $x_1, \ldots, x_t \in \bool^{\ell_{in}} $.

\heading{Classical Bloom filter in ROM}
 Fix $k,m > 0$. Define $F: \bool^{\ell_{in}} \rightarrow \bool^{m}}$ as the RO instance; it uses lazy sampling to mimic RO.
\begin{enumerate}
\item $x_1, \ldots, x_t \getsr \Rep_1(S)$.
\item $\pubaux \getsr \Rep_2(|S|,  F(x_1), \ldots, F(x_t))$.
\end{enumerate}

\heading{Linear-prf data structure}
Fix $k,m > 0$. Define $F: \bool^n \times \bool^{\ell_{in}} \rightarrow \bool^{\ell_{out}}$
such that the following hold:
\begin{itemize}
\item $\Rep_1$ takes as input a set $S$ and outputs distinct values $x_1, \ldots, x_t \in \bool^{\ell_{in}}$,
where $t$ depends only on~$|S|$.
\item $\Rep_2$ takes as input $|S|$ and $y_1, \ldots, y_t \in \bool^{\ell_{out}}$, and outputs
$\pubaux$.
\item For any $S$, the distribution on $\pubaux$ output by $\Rep(S)$ is identical to the distribution
on $\pubaux$ computing as follows:
\begin{enumerate}
\item $x_1, \ldots, x_t \getsr \Rep_1(S)$.
\item $k \getsr \bool^n$.
\item $\pubaux \getsr \Rep_2(|S|, F_k(x_1), \ldots, F_k(x_t))$.
\end{enumerate}
\end{itemize}

### 2016-10-12 EC17-submitted/ds-ss-proof.tex
Copying files not used in submission to EC17-submitted

--- 2016-09-06 ds-ss-proof.tex
@@
 When~$f=F_K$ then the simulation is perfect.
-When~$f=\rho$ then~$B$ simulates $\ExpPrivSSreal{\tilde{\Pi}_{\mathrm{ds}}}{A}$ where $\tilde{\Rep}$ effectively uses~$k$ independent random functions as the hash functions.
-But the $\pub$ produced by $\tilde{\Rep}$ has a distribution that depends only on the size of~$S$ ($n$) and the other public parameters~$m,k$.
-Thus, a simulator~$\Sim$ given only $\leak(S)=|S|=n$ can produce a correct~$\pub$ as follows: starting with an all-zeros array~$M$ of length~$m$, uniformly sample (with replacement)~$nk$ integers in~$[m]$ and set the resulting positions of~$M$ to 1.
+When~$f=\rho$ then~$B$ simulates $\ExpPrivSSreal{\overline{\Pi}_{\mathrm{ds}}}{A}$ where $\overline{\Rep}$ effectively uses~$k$ independent random functions as the hash functions.
+But the $\pub$ produced by $\overline{\Rep}$ has a distribution that depends only~$|S|=n$, not the specific elements of~$S$, and the other public parameters~$m,k$.
+Thus, a simulator~$\Sim$ given only $\leak(S)=|S|$ can produce a correct~$\pub$ as follows: starting with an all-zeros array~$M$ of length~$m$, uniformly sample (with replacement)~$nk$ integers in~$[m]$ and set the resulting positions of~$M$ to 1.
 \end{proof}

### 2016-10-12 EC17-submitted/intro-old.tex
Copying files not used in submission to EC17-submitted

--- 2016-09-30 intro-old.tex
@@
 
-Bloom filters have a broad range of practical applications, for example, in content-distribution networks, large database query processing, routing algorithms for peer-to-peer networks, protocols for establishing linkages between medical-record databases, fair routing of TCP packets, Bitcoin wallet synchonization.
+Bloom filters have a broad range of practical applications, for example, in content-distribution networks, large database query processing, routing algorithms for peer-to-peer networks, protocols for establishing linkages between medical-record databases, fair routing of TCP packets, Bitcoin wallet synchronization.
 \tsnote{need citations} Given that NY is addressing such a useful real-world object, we find their formalism, both the syntax and security notions, to be less precise and useful than one would want.
@@
 First, we note that the security notion forbids~$A$ to win if it outputs $x^* \in \{x_1,x_2,\ldots,x_q\}$, even if one of these was a false positive.
-On one hand, this notion is unsatisfying because it would not say that an attacker wins by creating (say) a bogus email address, and then observing that it passes a spam filter that is based on a Bloom filter represention of a whitelist.\footnote{This is one of the motivating examples from NY.}  The attacker is only allowed to win if it finds a false-positive that it has not verified.
+On one hand, this notion is unsatisfying because it would not say that an attacker wins by creating (say) a bogus email address, and then observing that it passes a spam filter that is based on a Bloom filter representation of a whitelist.\footnote{This is one of the motivating examples from NY.}  The attacker is only allowed to win if it finds a false-positive that it has not verified.
 On the other hand, the NY notion does seem to capture the intuition that finding additional false positives does not become easier as more are learned.
@@
 This particular ``encrypted Bloom filter'' instantiation was suggested for use in efficient linking of records across separate medical record databases~\cite{schnell2011novel}.
-(It was subsequently shown not to be secure by Niedermeier et al.~\cite{niedermeyer2014cryptanalysis}, where a clever use of frequency analysis recovered the last names of patients given access only to the Bloom filter array.)
+(It was subsequently shown not to be secure by Niedermeyer et al.~\cite{niedermeyer2014cryptanalysis}, where a clever use of frequency analysis recovered the last names of patients given access only to the Bloom filter array.)
 In any case, it is clear that the NY definition does not capture the most widely used applications of Bloom filters, e.g. CDN summary caches, P2P network routing algorithms, etc.
@@
 FP with private, public representation coins; set privacy with private, public representation coins; FP/set privacy in the multi-representation setting (outsider attack, think CDNs); FP/set privacy in the multi-representation setting with corruptions (insider attack, think P2P networks) \tsnote{Those are just the ones that come to mind now.
-Could also consider authenicity of representations, think CDN or P2P settings.}
+Could also consider authenticity of representations, think CDN or P2P settings.}
 
@@
 \begin{itemize}
-\item Niedermayer et al., ``Cryptanalysis of Basic Bloom Filters Used for Privacy-Preserving Record Linkage'', breaking privacy of secret-hash-function Bloom filters.
+\item Niedermeyer et al., ``Cryptanalysis of Basic Bloom Filters Used for Privacy-Preserving Record Linkage'', breaking privacy of secret-hash-function Bloom filters.
 \tsnote{Journal of Privacy and Confidentiality, 2014}
@@
 (I'll also point out that they explicitly say that $B_1$ outputs “compressed representation of [set $S$] $B_1(S)=M$”.
-But it would be easy to have small sets $S$ for which the bitsize of the array is smaller than the total bitsize of $S$, yet the combined bitsize of array + hash functions is larger.)
+But it would be easy to have small sets $S$ for which the bit-size of the array is smaller than the total bit-size of $S$, yet the combined bit-size of array + hash functions is larger.)
 %
@@
 \tsnote{UPDATE (5/20/16): I'm now convinced that what they call memory size~$m$, when applied to real Bloom filters, is \emph{only} the size of the bit array, and does \emph{not} include a description of the hash functions.
-The memory size comparisons that are made throughout the paper are to classical memory lowerbounds that account only for the bitsize of the array.
+The memory size comparisons that are made throughout the paper are to classical memory lowerbounds that account only for the bit-size of the array.
 Concretely: in the abstract they say ``...

### 2016-10-12 EC17-submitted/lin-correctness.tex
Copying files not used in submission to EC17-submitted

--- 2016-10-01 lin-correctness.tex
@@
 false-positives (and, conversely, which will not be), then a
-zero-query FP-finding adversary can ``guess'' which of~$A$'s queries require it
-to return 1 when simulating the $\TestOracle$, and which require it to
-return 0.  In this way, no queries ever actually need to be made.
-Moving to a zero-query setting will allow us to connect to classical
-results on the FP-rate of Bloom filters; more in a moment.
+ FP-finding adversary can ``guess'' which of~$A$'s queries require it
+to return 1 when simulating the $\TestOracle$, and which require it to return 0;
+%return 0.  In this way, no queries ever actually need to be made.
+%Moving to a zero-query setting will allow us to connect to classical
+%results on the FP-rate of Bloom filters; more in a moment.
 
@@
 %Under these assumptions,
-So, if $\game{4}(A)=1$, then there is a zero-query adversary~$D$ that finds~$r$ false positives against $\tilde{\setprim}_{\mathrm{lin}}$, which is $\setprim_{\mathrm{lin}}$ but with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$, respectively.
+So, if $\game{4}(A)=1$, then there is an adversary~$D$ that finds~$r$ false positives against $\tilde{\setprim}_{\mathrm{lin}}$, which is $\setprim_{\mathrm{lin}}$ but with $F_{K_1}$ and $F_{K_2}$ replaced by random functions $\rho_1$ and $\rho_2$, respectively.
 We give this~$D$ in Figure~\ref{fig:lin-correctness-zq-adv}.
-Intuitively, adversary~$D$ guesses which~$r$ of~$A$'s queries will be false positives; it simulates the~$\TestOracle$ oracle by returning 1 on the guessed queries, and 0 otherwise; and it halts after finding $r$ false-positives.
-It must be noted that, by the no-pointless queries assumption and the fact that the hash functions in $D$ are instantiated with random functions, $\pubaux$ is information theoretically independent of elements not in $S$.
-Thus we have
+Intuitively, adversary~$D$ guesses which~$r$ of~$A$'s queries will be false positives.
+It must be noted that, by the no-pointless queries assumption and the fact that $\HashOracle$ in $\game{3}$ returns $k$ random values for each query, $\pubaux$ is information theoretically independent of elements not in $S$.
+Thus, we have
 $\Prob{\game{4}(A)=1} =\Prob{\ExpCorrect{\tilde{\setprim}_{\mathrm{lin}},r}{D} = 1}$.
@@
 Note that $\tilde{\setprim}_{\mathrm{lin}}$ is the scheme that is analyzed in the classical Bloom filter literature ---the hash functions are modeled as independent random functions, and the parameters $k,m,n$  are set to achieve a target maximum false-positive probability (or rate).
-Kirsch and Mitzenmacher~\cite{kirsch2006less} show that the upperbound on false-positive probability for a zero-query adversary and $r=1$ is $\left( (1-e^{-kn/m})^k + O(1/n) \right)$.
+Kirsch and Mitzenmacher~\cite{kirsch2006less} show that the upperbound on false-positive probability for $r=1$ is $\left( (1-e^{-kn/m})^k + O(1/n) \right)$.
 For $r>1$, we observe that~$A$'s queries $x_1,x_2,\ldots,x_q$ are distinct and not elements of the original set~$S$, since we assume no pointless queries.

### 2016-10-12 EC17-submitted/mutable-filters.tex
Copying remaining files to EC17-submitted

--- 2016-07-06 mutable-filters.tex
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section{Security Results for Mutable Hash-Based Filters}
+\begin{itemize}
+\item Prove privacy of ``Stable'' Bloom Filters
+\item Ditto for count-min sketch (with and without conservative update)
+\item Ditto for scaling BF 
+\item Correctness and soundness bounds for these?  (Not sure this is possible without a lot of work; see what's already been done in the papers that propose them)
+\end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \if{0}

### 2016-11-28 intro.tex
added new headings to intro

@@
 where both \emph{correctness} and \emph{privacy} are considered. In this work we initiate such a
-treatment for abstract data structures.
+treatment.
 
-Loosely speaking, we formalize a data structure as a pair of algorithms $(\Rep,\Qry)$, the representation and query-evaluation algorithms, respectively.
+\heading{Formalizing abstract data structures.} Loosely speaking, we formalize a data structure as a pair of algorithms $(\Rep,\Qry)$, the representation and query-evaluation algorithms, respectively.
 The randomized representation algorithm takes in an abstract object~$S$ and produces public representation data $\pubaux$ and private representation data $\privaux$.
@@
 
+\heading{Case Studies.}
 This example offers a hint at the broad range of abstract data structures our syntax supports.

### 2016-11-28 intro.tex
intro touch ups

@@
 This example offers a hint at the broad range of abstract data structures our syntax supports.
-In this paper, we put the syntax and our security notions to work, analyzing Bloom filters in the random oracle model~\cite{broder2004network}, with PRFs for hash functions~\cite{niedermeyer2014cryptanalysis,naor2015bloom}, and with secret hash functions that fall short of being PRFs (so-called ``linear-PRF'' hash functions~\cite{kirsch2006less,niedermeyer2014cryptanalysis}), each representing an in-use or proposed Bloom filter variant.
+In this paper, we put the syntax and our security notions to work in several case studies.
+First, we analyze classical Bloom filters when the hash functions are modeled as public random oracles~\cite{broder2004network}, when the hash functions are secretly-keyed PRFs ~\cite{niedermeyer2014cryptanalysis,naor2015bloom}, and when the hash functions are secretly keyed but fall short of being PRFs, i.e., so-called ``linear-PRF'' hash functions~\cite{kirsch2006less,niedermeyer2014cryptanalysis}.
+Each of these represents an in-use or proposed Bloom filter variant.
+
 The linear-PRF Bloom filter provides an opportunity to see just how brittle constructions can be to their usage.
@@
 However, when applied to a multiset (effectively) privacy is lost.
-In fact, Niedermeyer et al.~\cite{niedermeyer2014cryptanalysis} show that the linear PRF Bloom filter, when applied to a collection of bigrams of German last names, admits a practical attack that reveals the names.
+In fact, Niedermeyer et al.~\cite{niedermeyer2014cryptanalysis} show that the linear-PRF Bloom filter, when applied to a collection of bigrams of German last names, admits a practical attack that reveals the names.
 Note that this is despite the fact that the hash functions are constructed from secretly-keyed PRFs in a way that has been suggested in recent literature on Bloom filter variants~\cite{kirsch2006less}.
+
 We also consider garbled Bloom filters, proposed by Dong et al.~\cite{dong2013private} as a key piece of a private set-intersection protocol.

### 2016-11-28 intro.tex
intro touch ups

@@
 
-Data structures are a fundamental tool used throughout computer
-science. Typically, when the behavior of a data structure (e.g., its
-running time or its error probability) is analyzed, the analysis is
-performed under the assumption that the input/queries to the data
-structure are chosen independently of the data structure itself, and
-in particular independent of any internal randomness used by the
-data structure. But, as recently highlighted by Naor and
-Yogev~\cite{naor2015bloom}, there are many natural scenarios in
-which the input/queries may be chosen \emph{adversarially} and
-\emph{adaptively} based on partial information and/or prior
-observations about the data structure.
+Data structures are a fundamental tool used throughout computerscience.
+Typically, when the behavior of a data structure (e.g., its running time or its error probability) is analyzed, the analysis is performed under the assumption that any inputs and queries to the data structure are chosen independently of the data structure itself.
+In particular, independent of any internal randomness used by the data structure.
+But as recently highlighted by Naor and Yogev~\cite{naor2015bloom}, there are many natural scenarios in which the input and queries may be chosen \emph{adversarially} and \emph{adaptively}, based on partial information and prior observations about the data structure.
 
-In addition, standard applications of data structures assume that
-the party querying the data structure is fully trusted, and hence
-privacy concerns do not arise. In some scenarios, however, it may be
-desirable to allow some party to pose (certain types of) queries to
-a data structure, but unacceptable to leak the data in its entirety
-to that same party. Existing definitions do not address privacy in
-this sense at~all. The concerns outlined above motivate a careful, formal treatment of data structures in an adversarial setting, 
+In addition, standard applications of data structures assume that the party querying the data structure is fully trusted.
+Hence, privacy concerns do not arise.
+But in many real-world scenarios, a data structure is built from sensitive data.
+Here one would like to know what information is leaked by queries to the data structure; minimally, to know that a reasonable number of queries to not effectively divulge the entire data.
+Existing definitions say nothing about privacy in this sense.
+
+These concerns motivate a careful and formal treatment of data structures in an adversarial setting, 
 where both \emph{correctness} and \emph{privacy} are considered. In this work we initiate such a
@@
 When used to create a representation of a set, we prove that the linear-PRF Bloom filter offers both correctness and privacy.
-However, when applied to a multiset (effectively) privacy is lost.
+However, when applied to (effectively) a multiset privacy is lost.
 In fact, Niedermeyer et al.~\cite{niedermeyer2014cryptanalysis} show that the linear-PRF Bloom filter, when applied to a collection of bigrams of German last names, admits a practical attack that reveals the names.

### 2016-12-07 EC17-submitted/notions.tex
EC17-submitted
pass...

--- 2016-10-01 notions.tex
@@
 \label{sec:security-notions}
-Following NY, we are interested in defining an adaptive (i.e.,adversarial) notion of correctness.
+Following NY, we are interested in defining an adaptive (i.e., adversarial) notion of correctness.
 In addition to correctness, we establish two kinds of privacy notions for data structures.
@@
 \item For any $S$, the distribution on $\pubaux$ output by $\Rep(S)$ is identical to the distribution
-on $\pubaux$ computing as follows:
+on $\pubaux$ computed as follows:
 (1) $s_1, \ldots, s_t \getsr \Rep_1(S)$;

### 2016-12-07 abstract.tex
typos
pass...

--- 2016-10-01 abstract.tex
@@
-We initiate a provable-security treatment of abstract data structures, by formalizing them as syntactic primitives, and considering their correctness and privacy first-class security properties.
-Our syntax is quite broad, capturing a wide variety of in-use and academic data structures.
-Concretely, we explore the security of several data structures that support (approximate) set-membership tests.
-Our notion of correctness captures an adversaries ability to cause the data structure to err via its allowed set of queries.
-Our main privacy notion neatly captures what is leaked by the public portion of the data structure.
-As certain widely used set-membership data structures, like the Bloom filter, do not meet our notion, we consider a secondary notion of onewayness; essentially, capturing the inability to reproduce any element of the set given the public portion of the data structure.
-We also compare our notions to recent work by Naor and Yogev (Crypto'15), which also considers Bloom-filter-like data structures, albeit in a much more limited way.
-Our syntax and notions let us consider security under a variety of usage scenarios, by clearly surfacing the split between public and private portions of the data structure.
+We initiate a provable-security treatment of abstract data
+structures by formalizing them as syntactic primitives and
+considering their correctness and privacy as first-class security
+properties.  Concretely, we explore the security of several data
+structures that support (approximate) set-membership tests.  Our
+notion of correctness captures an adversary's inability to cause a
+data structure to err via its allowed set of queries, and our
+privacy notion neatly captures what is leaked by the public portion
+of a data structure.  As certain widely used set-membership data
+structures, such as Bloom filters, do not meet our privacy notion,
+we consider a secondary notion of onewayness capturing the inability
+to recover any element of a high-entropy set given the public
+portion of the data structure. We also compare our notions to recent
+work by Naor and Yogev (Crypto 2015), which also considers
+Bloom-filter-like data structures, albeit in a much more limited
+way.  Our syntax and notions let us consider security under a
+variety of usage scenarios, by clearly surfacing the split between
+public and private portions of the data structure.
 
-We see this work as laying the foundation for a number of follow-on efforts, for example to study dynamic data structures (e.g.
-Bloom filter variants whose representation changes over time), and the security of primitives built on top of abstract data structures.
+%We see this work as laying the foundation for a number of follow-on
+%efforts, for example to study dynamic data structures (e.g., Bloom
+%filter variants whose representation changes over time), and the
+%security of primitives built on top of abstract data structures.

### 2016-12-07 intro.tex
pass...

@@
 
-Data structures are a fundamental tool used throughout computerscience.
-Typically, when the behavior of a data structure (e.g., its running time or its error probability) is analyzed, the analysis is performed under the assumption that any inputs and queries to the data structure are chosen independently of the data structure itself.
-In particular, independent of any internal randomness used by the data structure.
-But as recently highlighted by Naor and Yogev~\cite{naor2015bloom}, there are many natural scenarios in which the input and queries may be chosen \emph{adversarially} and \emph{adaptively}, based on partial information and prior observations about the data structure.
+Data structures are a fundamental tool used throughout computer
+science. Typically, when the behavior of a data structure (e.g., its
+running time or its error probability) is analyzed, the analysis is
+performed under the assumption that any inputs and queries to the
+data structure are chosen non-adversarially and, in particular, are
+independent of any internal randomness used by the data structure.
+But as recently highlighted by Naor and Yogev~\cite{C:NaoYog15},
+there are many natural scenarios where the input and/or queries may
+be chosen \emph{adversarially} and \emph{adaptively}, based on
+partial information and prior observations about the data structure.
 
-In addition, standard applications of data structures assume that the party querying the data structure is fully trusted.
-Hence, privacy concerns do not arise.
-But in many real-world scenarios, a data structure is built from sensitive data.
-Here one would like to know what information is leaked by queries to the data structure; minimally, to know that a reasonable number of queries to not effectively divulge the entire data.
+In addition to the above, standard applications of data structures
+assume that the party querying the data structure is fully trusted
+and hence privacy concerns do not arise. But in many real-world
+scenarios, a data structure is built from sensitive data.  Here, it
+is important to understand what information is leaked by public
+portions of the data structure and, minimally, to know that a
+reasonable number of queries will not divulge ``too much more
+information'' that was is implied by the answers to those queries.
 Existing definitions say nothing about privacy in this sense.
 
-These concerns motivate a careful and formal treatment of data structures in an adversarial setting, 
-where both \emph{correctness} and \emph{privacy} are considered. In this work we initiate such a
-treatment.
+These concerns motivate a careful and formal treatment of data
+structures in an adversarial setting, where both \emph{correctness}
+and \emph{privacy} are considered. We initiate such a treatment in
+this work.
 
-\heading{Formalizing abstract data structures.} Loosely speaking, we formalize a data structure as a pair of algorithms $(\Rep,\Qry)$, the representation and query-evaluation algorithms, respectively.
-The randomized representation algorithm takes in an abstract object~$S$ and produces public representation data $\pubaux$ and private representation data $\privaux$.
-Intuitively, $\pubaux$ is considered public information, whereas $\privaux$ is meant to be known only to the party running $\Qry$.
-The deterministic query-evaluation algorithm uses $\pubaux$ and $\privaux$ in order to (approximately) evaluate permitted queries $\qry$, which are arbitrary functions over abstract objects.
-We say ``approximately''  evaluate permitted queries because $\pubaux$ and $\privaux$ may not contain all of the information sufficient to determine the true value of $\qry(S)$ for all~$S$.
+\heading{Formalizing abstract data structures.} Loosely speaking, we
+formalize a data structure as a pair of algorithms $(\Rep,\Qry)$,
+the representation and query-evaluation algorithms, respectively.
+The randomized representation algorithm takes in an abstract
+object~$S$ and produces public representation data $\pubaux$ and
+private representation data $\privaux$.  Intuitively, $\pubaux$ is
+public information, whereas $\privaux$ is meant to be known only to
+the party running $\Qry$.  The deterministic query-evaluation
+algorithm uses $\pubaux$ and $\privaux$ in order to (approximately)
+evaluate a supported query $\qry$, which can in principle be an
+arbitrary function.
+%We say ``approximately'' evaluate permitted queries
+%because $\pubaux$ and $\privaux$ may not contain all of the
+%information sufficient to determine the true value of $\qry(S)$ for
+%all~$S$.
 
-Let us give an example.
-Consider the classic Bloom filter~\cite{bloom1970space}, in which case $\pubaux$ will consist of the bit array~$M$ that represents a given set~$S$, as well as descriptions of the hash functions $H_1,H_2,\ldots,H_k$ used to produce~$M$; $\privaux$ will be empty.
-The permitted queries will be predicates of the form $\qry_x(S)=1$ iff $x \in S$.
-The~$\Qry$ algorithm, on input $M,H_1,H_2,\ldots,H_k$ and $\qry_x$, carries out the standard Bloom filter set-membership test to decide whether or not $x \in S$.
-It is well known that Bloom fiters admit false-positive errors, thus $\Qry$ only approximates the true set-membership test.
-Our correctness security notion will quantitatively capture the approximation error, but in the presense of attackers that adaptively try to induce one or more errors (false-positives, in this case).
+As an example, consider the classic Bloom
+filter~\cite{bloom1970space}. Here, $\pubaux$ consists of a bit
+array~$M$ that represents a given set~$S$, as well as descriptions
+of the hash functions $H_1,H_2,\ldots,H_k$ used to produce~$M$;
+$\privaux$ is empty.  The supported queries are predicates of the
+form $\qry_x(S)=1$ iff $x \in S$. The~$\Qry$ algorithm, on input
+$M,H_1,\ldots,H_k$ and $\qry_x$, carries out the standard
+Bloom-filter test to determine if $x \in S$. It is well known that
+Bloom filters admit false-positive errors; thus, $\Qry$ only
+approximates the true set-membership test.  Our correctness notion
+will quantitatively capture the error, even in the presence of
+attackers that adaptively try to induce one or more errors
+(false-positives, in this case).
 
-By shifting $H_1,H_2,\ldots,H_k$ from $\pubaux$ to $\privaux$, we do not change the functionality at all.
-But we may very well change the security profile of the resulting Bloom filter variant.
-Indeed, this is the case.
-When $H_1,H_2,\ldots,H_K$ are assumed to be good pseudorandom functions, we can prove that this variant achieves a kind of ``semantic security'' privacy guarantee: the bit array~$M$ is well known to leak a good approximation of~$|S|$, and our notion shows that it leaks nothing more than this.
-(Such a result is not possible for the standard Bloom filter, or any other data structure with empty~$\privaux$.)
+By shifting $H_1,H_2,\ldots,H_k$ from $\pubaux$ to $\privaux$, we do
+not change the functionality, but we may very well change the
+security profile of the resulting Bloom-filter variant.  Indeed,
+this is the case.  When $H_1,H_2,\ldots,H_K$ are assumed to be
+pseudorandom functions, we can prove that this variant achieves a
+sort of ``semantic security'' privacy guarantee: the bit array~$M$
+leaks a good approximation of~$|S|$, but nothing more.  (Such a
+result is not possible for the standard Bloom filter, or any other
+data structure with empty~$\privaux$.)
 
-\heading{Case Studies.}
-This example offers a hint at the broad range of abstract data structures our syntax supports.
-In this paper, we put the syntax and our security notions to work in several case studies.
-First, we analyze classical Bloom filters when the hash functions are modeled as public random oracles~\cite{broder2004network}, when the hash functions are secretly-keyed PRFs ~\cite{niedermeyer2014cryptanalysis,naor2015bloom}, and when the hash functions are secretly keyed but fall short of being PRFs, i.e., so-called ``linear-PRF'' hash functions~\cite{kirsch2006less,niedermeyer2014cryptanalysis}.
-Each of these represents an in-use or proposed Bloom filter variant.
+\heading{Case studies.} The example above offers a hint at the broad
+range of abstract data structures our syntax supports.  In this
+paper, we put the syntax and our security notions to work in several
+case studies.  First, we analyze classical Bloom filters when the
+hash functions are modeled as public random
+oracles~\cite{broder2004network}, when the hash functions are
+secretly-keyed PRFs~\cite{niedermeyer2014cryptanalysis,C:NaoYog15},
+and when the hash functions are secretly keyed but fall short of
+being PRFs, i.e., so-called ``linear-PRF'' hash
+functions~\cite{kirsch2006less,niedermeyer2014cryptanalysis}.  Each
+of these represents an in-use or proposed Bloom-filter variant. We
+also consider garbled Bloom filters~\cite{CCS:DonCheWen13}, proposed
+as a key piece of a private set-intersection protocol.
 
-The linear-PRF Bloom filter provides an opportunity to see just how brittle constructions can be to their usage.
-When used to create a representation of a set, we prove that the linear-PRF Bloom filter offers both correctness and privacy.
-However, when applied to (effectively) a multiset privacy is lost.
-In fact, Niedermeyer et al.~\cite{niedermeyer2014cryptanalysis} show that the linear-PRF Bloom filter, when applied to a collection of bigrams of German last names, admits a practical attack that reveals the names.
-Note that this is despite the fact that the hash functions are constructed from secretly-keyed PRFs in a way that has been suggested in recent literature on Bloom filter variants~\cite{kirsch2006less}.
+The linear-PRF Bloom filter illustrates how brittle constructions
+can be depending on how they are used. When used to create a
+representation of a \emph{set}, we prove that the linear-PRF Bloom
+filter offers both correctness and privacy. However, when applied to
+a \emph{multiset}, privacy is lost.  In fact, Niedermeyer et
+al.~\cite{niedermeyer2014cryptanalysis} show that the linear-PRF
+Bloom filter, when applied to a collection of bigrams derived from
+German last names, admits a practical attack that reveals the names,
+despite the fact that the hash functions are constructed from
+secretly-keyed PRFs in a way that has been suggested in recent
+literature on Bloom-filter variants~\cite{kirsch2006less}.
 
-We also consider garbled Bloom filters, proposed by Dong et al.~\cite{dong2013private} as a key piece of a private set-intersection protocol.
-
-We see this work as laying the foundation for a number of follow-on studies.
-For example to study dynamic data structures, such as counting Bloom filters\cite{fan2000summary}, scalable Bloom filters~\cite{almeida2007scalable}, count-min sketches~\cite{cormode2005improved}, hierachical Bloom filters~\cite{zhu2004hierarchical}, to name just a few in the extended Bloom filter family.
-Another direction would be to explore the security of primitives built \emph{from} these sorts of data structures, such as content-distribution networks (where many servers propogate representations of their local cache to their neighbors), or cryptographic strike lists (a la early versions of the QUIC protocol) for nonce-replay protection.
-The Bloom filter family alone has a wide range of practical applications, for example in large database query
-processing, routing algorithms for peer-to-peer networks, protocols
-for establishing linkages between medical-record databases, fair
-routing of TCP packets, and Bitcoin wallet synchonization~\cite{schnell2011novel,niedermeyer2014cryptanalysis,gervais2014privacy,nojima2009cryptographically,feng2001stochastic,reynolds2003efficient,byers2002informed,broder2004network}.
-
-\heading{Comparison to~\cite{naor2015bloom}.} Naor and
-Yogev~\cite{naor2015bloom} recently considered the problem of
-adversarial soundness for Bloom filters and, indeed,
-their work served as inspiration for our own. Our work extends
-their work significantly in several directions. For starters, we
-consider abstract data structures (rather than only the case of
-set-membership data structures), and consider privacy in addition to
-correctness. Even with respect to the specific case of correctness for
-set-membership data structures, our work offers several advantages
-to the Naor-Yogev treatment:
-\begin{itemize}
-\item We explicitly distinguish between public and private
-    portions of a data structure, something that was left
-    ambiguous\footnote{In fact, it isn't clear that their formalization actually allows for standard Bloom filters, although fixing this ambiguity is straightforward once recognized.} in~\cite{naor2015bloom}.
-This allows us, for
-    example, to distinguish between the hash-function keys and
-    the bit array when discussing classical Bloom filters.
-\item The Naor-Yogev definition of soundness allows the
-    adversary to make several set-membership queries, some of
-    which may produce incorrect results, and the attacker then
-    succeeds if it can output a \emph{fresh} query which leads
-    to an error. We propose instead what we find to be a more
-    natural definition in which the attacker succeeds if it can
-    cause a certain number of incorrect results.
-\item Naor and Yogev analyze a new Bloom-filter construction of
-    their own design. In contrast, we are interested in
-    analyzing practical constructions that have been proposed in
-    prior work to understand how secure they are. In particular,
-    we analyze Bloom filters in the random-oracle model.
-\end{itemize}
-
-We give a technical comparison of our correctness notion and theirs (lifted to our more general syntax)
-in Appendix~\ref{sec:compare-defs}.
+%We see our work as laying the foundation for a number of follow-on
+%studies.  For example to study dynamic data structures, such as
+%counting Bloom filters\cite{fan2000summary}, scalable Bloom
+%filters~\cite{almeida2007scalable}, count-min
+%sketches~\cite{cormode2005improved}, hierarchical Bloom
+%filters~\cite{zhu2004hierarchical}, to name just a few in the
+%extended Bloom filter family.  Another direction would be to explore
+%the security of primitives built \emph{from} these sorts of data
+%structures, such as content-distribution networks (where many
+%servers propagate representations of their local cache to their
+%neighbors), or cryptographic strike lists (a la early versions of
+%the QUIC protocol) for nonce-replay protection.  The Bloom filter
+%family alone has a wide range of practical applications, for example
+%in large database query processing, routing algorithms for
+%peer-to-peer networks, protocols for establishing linkages between
+%medical-record databases, fair routing of TCP packets, and Bitcoin
+%wallet
+%synchronization~\cite{schnell2011novel,niedermeyer2014cryptanalysis,gervais2014privacy,nojima2009cryptographically,feng2001stochastic,reynolds2003efficient,byers2002informed,broder2004network}.
 

### 2016-12-07 related-work.tex
pass...

@@
-The Naor-Yogev paper~\cite{naor15bloom} served as inspiration for our work.
-We recommend reading the very good related work section contained in their paper for a discussion of related theory papers.
-Here we mention a few additional practical works, but stress that this only scratches the surface.
+Naor and Yogev~\cite{C:NaoYog15} recently considered the problem of
+adversarial soundness for Bloom filters and, indeed, their work
+served as inspiration for our own. Our work extends their work
+significantly in several directions. For starters, we consider
+abstract data structures (rather than only the case of
+set-membership data structures), and consider privacy in addition to
+correctness. Even with respect to the specific case of correctness
+for set-membership data structures, our work offers several
+advantages to the Naor-Yogev treatment:
+\begin{itemize}
+\item We explicitly distinguish between public and private
+    portions of a data structure, something they leave
+    ambiguous.\footnote{In fact, it isn't clear that their
+formalization actually allows for standard Bloom filters,
+    although fixing this ambiguity is straightforward once
+    recognized.} This allows us, for example, to distinguish
+    between the hash-function keys and the bit array when
+    discussing classical Bloom filters.
+\item The Naor-Yogev definition of soundness allows the
+    adversary to make several set-membership queries, some of
+    which may produce incorrect results, and the attacker then
+    succeeds if it can output a \emph{fresh} query which leads
+    to an error. We propose instead what we find to be a more
+    natural definition in which the attacker succeeds if it can
+    cause a certain number of incorrect results.
+\item Naor and Yogev analyze a new Bloom-filter construction of
+    their own design. In contrast, we are interested in
+    analyzing practical constructions that have been proposed in
+    prior work to understand their security. In particular, we
+    analyze Bloom filters in the random-oracle model, something
+    not considered by Naor and Yogev.
+\end{itemize}
 
-As previously mentioned Bloom filters and their relatives are some of the most widely used data structures supporting set-membership queries.
-We give a few more, here.
-Hbase, a hadoop based NoSql database designed to handle large datasets has an implementation of Bloom filter and counting Bloom filter.
-Hbase is the open-source implementation of Google's BigTable storage system~\cite{chang2008bigtable}.
-The Squid proxy~\cite{fan2000summary} uses a bloom filter as a ``summary cache'' of the set of URLs in its cache in order to web object retreival latency.
-Crossby and Walach~\cite{crosby2003denial} exploited hash collisions in Squid to increase the average URL load time.
-In an older paper, Lipton and Naughton~\cite{lipton1993clocked} showed how timing analysis of record insertion in a hash table can help an adversary to adapt and chose elements that take more time to be mapped into the hash table.
-Reynolds and Vahdat~\cite{reynolds2003efficient} proposed an efficient distributed search engine that can be used to search for files that contain a particular keyword.
-This search engine maps the keywords of each file into a Bloom filter; a look-up of the keyword in the Bloom filter tells whether the node has files containing that keyword or not.
-Record linkage is very often required to collect and combine records from different databases.
+%We give a technical comparison of our correctness notion and theirs (lifted to our more general syntax)
+%in Appendix~\ref{sec:compare-defs}.
 
-Schnell et.
-al.~\cite{schnell2011novel} proposed the so-called ``Cryptographic Longterm Key'' as a way to support privacy-preserving record linkage.
-This uses secretly keyed hash functions to create a Bloom filter for each surname.
-The surname is broken into bigrams and mapped into the Bloom filter with secret hash functions.
-Subsequently, Niedermeyer et al.~\cite{niedermeyer2014cryptanalysis} showed an attack on a database of German surnames which were stored in secretly hashed Bloom filters, similar to Cryptographic Longterm Key.
+We recommend reading the Naor-Yogev paper for a survey of related
+work and a discussion of related theory papers. Here we mention a
+few additional practical works, but stress that this only scratches
+the surface.
 
-Stochastic Fair Blue~\cite{feng2001stochastic} uses counting Bloom filter to manage non-responsive TCP traffic.
+\jnote{Rather random collection of papers using Bloom filters and
+variants. I removed it for now, since it's not clear that they have
+any particular relevance to us.}
+%As previously mentioned, Bloom
+%filters and their relatives are some of the most widely used data
+%structures supporting set-membership queries. As examples, Hbase,
+%the open-source implementation of Google's BigTable storage
+%system~\cite{chang2008bigtable},
+%%a Hadoop-based NoSql database designed to handle large datasets,
+%includes an implementation of Bloom filters and counting Bloom
+%filters, and the Squid proxy~\cite{fan2000summary} uses a Bloom
+%filter as a ``summary'' of the set of URLs in its cache in order to
+%improve latency for web-object retrieval. Reynolds and
+%Vahdat~\cite{reynolds2003efficient} proposed an efficient
+%distributed search engine that can be used to search for files
+%containing a particular keyword. Their search engine maps the
+%keywords of each file into a Bloom filter; a look-up of the keyword
+%in the Bloom filter tells whether the node has files containing that
+%keyword or not. Stochastic Fair Blue~\cite{feng2001stochastic} uses
+%counting Bloom filter to manage non-responsive TCP traffic.
+
+Lipton and Naughton~\cite{lipton1993clocked} showed how timing
+analysis of record insertion in a hash table can help an adversary
+to adaptively chose elements so as to increase the running time.
+Crosby and Walach~\cite{crosby2003denial} exploited hash collisions
+in Squid to increase the average URL load time.
+
+Schnell et al.~\cite{schnell2011novel} proposed a way to support
+privacy-preserving record linkage by using secretly keyed hash
+functions. Subsequently, Niedermeyer et
+al.~\cite{niedermeyer2014cryptanalysis} showed an attack on a
+similar system when used on a database of German surnames.
+\jnote{See Section~???}

### 2016-12-08 ec-17-rebuttal.txt
adding rebuttal text

We thank the reviewers for their comments, which mainly highlight our failure to make certain key points and contributions clear. We appreciate the opportunity to address the comments, and will improve our presentation in the final version.

Reviewer A: While not “flashy”, establishing good foundations for widely deployed primitives is very important. For various reasons, which we will better emphasize, the most directly related prior work falls short. Applying our syntax and notions to real and proposed constructions also reveals new security findings, e.g., what is leaked by public representations. We agree that our work raises multiple follow-on research questions in an area that is practically relevant yet underexplored.

Reviewer B: The separation of data-structure representations into (non-trivial) public and private parts is motivated by the fact that practical data structures (Bloom filter variants, in particular) DO have non-trivial public and private parts. This is essential in some applications, e.g., the use of so-called “encrypted” Bloom filters for medical-record linkage across hospital databases ([NSKS14]). Making this explicit also allows for weighing the costs/benefits to security, system design, and operational deployment. (Note also that the secure Bloom filter proposed by [NY] has public and private parts, though their syntax and security notion do not make this important distinction.) So, while it is true that one can always “push” the public part into the private part to achieve a security definition, this misses the point.

Similarly, one can make any data structure canonical by letting Rep_1 output all the elements of S, and letting F_K be the identity. What is important is whether a data structure has a canonical representation where F is a pseudorandom function. Perhaps a naming change will help.

Some of our results are information-theoretic, while some (including any that rely on a PRF) are computational. If we implied otherwise, please let us know and we can clarify it.

Reviewer C: If we have missed any relevant prior work on data structures in an adversarial environment, please provide specific references. We will be happy to add them to the related-work section.

Regarding the separation of representations into public and private parts, see the answer given to Reviewer B.

It is true that our correctness definition (in the ROM) does not allow the attacker to access the random oracle in the first part of the attack. We believe this provides a faithful model practice, where the set whose representation the honest party is computing is independent of the functions used to generate that representation. Note also that one could easily achieve independence by salting the hash function with a random sale before using it.

The question of composition is an interesting one that we leave for future work, though we expect that composition would hold as long as independent random oracles are used.

### 2016-12-09 BF_correctness.tex
fixing BF proof
continuing my pass, cleaning up the .bib files

@@
 \begin{proof}[Theorem~\ref{thm:bf-correctness}]
-We use a game playing argument, please refer to Figures~\ref{fig:bf-correctness-games1} and~\ref{fig:bf-correctness-games2}.
-In game $\game{0}$, the $\HashOracle$ oracle performs lazy sampling of elements from $[m]$ to mimic a random oracle (RO).
-For every distinct query, $\HashOracle$ returns a random value sampled from $[m]$.
-It can be seen that, game $\game{0}$ exactly simulates the correctness game of $\setprim_{\mathrm{gbf}}$.
-So, $\AdvCorrect{\setprim_{\mathrm{gbf}},r}{A} = \Prob{\game{0}(A) = 1}$.
+We use a game playing argument; please refer to
+Figures~\ref{fig:bf-correctness-games1}
+and~\ref{fig:bf-correctness-games2}. In game $\game{0}$, the
+$\HashOracle$ oracle performs lazy sampling of elements from $[m]$
+to mimic a random oracle (RO). For every distinct query,
+$\HashOracle$ returns a random value sampled from $[m]$. It can be
+seen that, game $\game{0}$ exactly simulates the correctness game of
+$\setprim_{\mathrm{gbf}}$.  So,
+$\AdvCorrect{\setprim_{\mathrm{gbf}},r}{A} = \Prob{\game{0}(A) =
+1}$.
 
@@
 }
-\caption{Games $\game{4}$-$\game{5}$ for the
+\caption{Game $\game{4}$ for the
 proof of Theorem~\ref{thm:bf-correctness}.}

### 2016-12-09 notions.tex
last
continuing my pass, cleaning up the .bib files

--- 2016-10-01 notions.tex
@@
 \label{sec:security-notions}
-Following NY, we are interested in defining an adaptive (i.e.,adversarial) notion of correctness.
-In addition to correctness, we establish two kinds of privacy notions for data structures.
+Following Naor and Yogev, we are interested in defining an adaptive (i.e., adversarial) notion of correctness.
+In addition to correctness, we also establish two notions of privacy.
 
@@
 
-We first define a notion of correctness for a data structure~$\Pi$. Our definition
+We first define a notion of (adversarial) correctness for a data structure~$\Pi$. Our definition
 considers an adversary $A$ who may have full information about the data~$S$ being stored (and, indeed,
@@
 
-In contrast to the style of definition considered by Naor and Yogev (and in addition
-to other differences between our definitions as discussed in the Introduction), we consider
-a more fine-grained definition parameterized by a value~$r$. The goal of the attacker
+In contrast to the definition considered by Naor and Yogev (and in addition
+to other differences between our definitions as discussed in the Introduction), our definition is
+parameterized by a value~$r$ that allows for a more fine-grained treatment. The goal of the attacker
 is to find $r$ (distinct) points on which the generated representation errs.
-Implications of this choice are discussed further below.
+Implications of this choice are discussed below.
 
-Formally, our definition is specified by an experiment called $\ExpCorrect{\setprim,r}{A}$
+Formally, our definition is specified by an experiment $\ExpCorrect{\setprim,r}{A}$
 given in Figure~\ref{fig:correctness}.
 Following an initialization step,
-the experiment begins by having the attacker $A$ outputs data $S \in \univ$.
+the experiment begins by having the attacker $A$ output $S \in \univ$.
 Then, $\Rep(S)$ is run to generate a representation $(\pubaux,\privaux)$ for that data.
@@
 a counter if this result is incorrect (and if $\qry$ is new).  The adversary succeeds if it
-manages to cause at least~$r>0$ such errors among its queries.
+manages to cause at least~$r$ such errors among its queries.
 The definition can be lifted to the random-oracle model by providing
@@
 the random oracle during the first stage when it selects~$S$, as that set
-should have no dependence on the random oracle.)
+should have no dependence on the random oracle. \jnote{Justify this.})
 
@@
 
-In this experiment we track the time complexity~$t$ (relative to some
+In the experiment we track the time complexity~$t$ (relative to some
 model of computation) and query complexity~$q$ (i.e., number of
 queries to $\TestOracle$) of~$A$.
-We define the advantage of adversary~$A$ in this experiment as
+We define the advantage of adversary~$A$ in the experiment as
 $\AdvCorrect{\setprim,r}{A} = \Prob{\ExpCorrect{\setprim,r}{A}=1}$.
@@
 
-\heading{The effect of $r$. }
-We observe that there is no definitive relation between
+\heading{Dependence on $r$. }
+We observe that there is no automatic relation between
 values of $\AdvCorrect{\setprim,r}{t,q}$ for different values of~$r$ (beyond
 the trivial observation that the advantage can only possibly decrease as $r$ increases.)
-In particular, for any $r$ it is not hard to construct a data structure
+In particular, for any $r>1$ it is not hard to construct a data structure
 for which
@@
 We also initiate a consideration of the orthogonal notion of \emph{privacy} for a data structure.
-We introduce two notions of privacy: a simulation-based, ``semantic-security''-style
-definition that is, in some sense, the strongest notion of privacy one could hope for.
-We also consider the weaker definition of ``one-wayness,'' specialized to the case
-of set-membership data structures, which requires that the public portion
-of the representation of some set should not allow an attacker to deduce any element of that set
-(better than what the attacker could have done without the public representation).
+We introduce two notions of privacy. The first is a simulation-based, ``semantic-security''-style
+definition that is, in some sense, the strongest notion of privacy one could hope for. The second
+is a weaker definition of ``one-wayness,'' specialized to the case
+of set-membership data structures, which requires that the public representation data
+of some set should not allow an attacker to deduce any element of that set
+(beyond what the attacker could have done without the public representation).
 This may suffice for many practical applications.
 
-\heading{A Simulation-Based Definition. }
+\heading{A simulation-based definition. }
 %\jnote{I like ``simulation-based security'' rather than ``semantic security.''}
@@
 Intuitively, this means that the public portion
-$\pubaux$ of the representation of a set~$S$ leaks~${\sf leak}(S)$ and nothing more.
+$\pubaux$ of the representation of~$S$ leaks~${\sf leak}(S)$ and nothing more.
 
@@
 }
-\caption{Experiments for the ``semantic-security'' privacy
+\caption{Experiments for a ``semantic-security''-style privacy
   definition.}
@@
 ideal world as well. But note that
-$A$ knows $S$ and so can compute answers $\qry(S)$ on its own (i.e., without a $\Qry$ oracle);
-thus, the only way the $\Qry$ oracle can possibly help $A$ is if $A$ finds queries
+$A$ knows $S$ and so can compute the true answer $\qry(S)$ on its own (i.e., without a $\Qry$ oracle);
+thus, the only way the $\Qry$ oracle can possibly help is if $A$ finds queries
 that lead to an error.
@@
 Finally, it is worth noting that the ``minimal'' leakage we consider in this work
-is leakage of the size of the data. (i.e., when $S$ is a set then we would
-consider ${\sf leak}(S)=|S|$ as minimal leakage.) This is by analogy with encryption.
+is leakage of the size of the data, i.e., when $S$ is a set then we would
+consider ${\sf leak}(S)=|S|$ as minimal leakage. This is by analogy with encryption,
 which generally leaks the length of the message being encrypted.
 
-\heading{``One-wayness''.}
+\heading{``One-wayness.''}
 Here we specialize to the case of set-membership data structures.
@@
 all algorithms (namely, $\Rep,\Qry$, and the adversary~$A$) with access to the
-random oracle.
+random oracle. (By analogy with the case of correctness, we do not allow the distribution
+$\mathcal{D}$ to depend on the random oracle.)
 
@@
 }
-\caption{Experiment for a ``one-way'' style privacy
+\caption{Experiment for a ``one-wayness''-style privacy
   definition.}
@@
 
-Before continuing, it will be useful to define a notion that captures the difficulty
+It will be useful to define a notion that captures the difficulty
 of guessing an element in a set chosen from some distribution.
-Let ${\cal D}$ be a distribution over subsets of some universe ${\cal X}$. The \emph{point-wise
+Let ${\cal D}$ be a distribution over subsets of a universe ${\cal X}$. The \emph{point-wise
 min-entropy} of ${\cal D}$ is defined as
 $H_\infty({\cal D}) \bydef -\log \max_{x \in {\cal X}} \Pr[S \getsr {\cal D} : x \in S]$.
-Note that an attacker can trivially achieve advantage
+An attacker can trivially achieve advantage
 $\AdvPrivOW{\setprim,\mathcal{D}}{A}=2^{-H_\infty({\cal D})}$ by outputting the element most likely to be in~$S$,
@@
 %$A$ running in time $t$, and let $\delta \bydef \AdvPrivOW{\setprim,\mathcal{D}}{A}$.
-Define $A'$ as follows: first, it samples a set $S$ according to
-distribution~${\cal D}$. Then, given $\pubaux$, it runs $A(\pubaux)$ to obtain an element~$z$.
+Define $A'$ as follows: first, it samples a set $S$ according to~${\cal D}$. Then, given $\pubaux$,
+it runs $A(\pubaux)$ to obtain~$z$.
 Finally, it outputs~1 if and only if $z \in S$.
@@
 The theorem follows. \hfill\qed
-\end{proof}
+\end{proof} \pagebreak[4]
 
@@
 
-\heading{Privacy of ``Canonical'' Data Structures. }
+\heading{Privacy of ``canonical'' data structures. }
 Here we prove a result that will be used in the next section
@@
 set-membership
-data structures satisfy our simulation-based notion of security
+data structures satisfy our simulation-based notion of privacy
 (with respect to leakage of the size of the set). Specifically, we prove that
-all such data structures of a certain type are private. We refer to such data structures
-as ``canonical,'' a term we define next.
+all ``canonical'' data structures are also private. We define what we mean by canonical next.
 
@@
 \begin{definition}
-A set-membership data structure $(\Rep, \Qry)$ is {\sf canonical} if
-there exist algorithms $\Rep_1, \Rep_2$, a query-enumeration
-function~$\ell\colon\mathbb{N}\to\mathbb{N}$,
-and a function family
+Let $\Pi = (\Rep, \Qry)$ be a set-membership data structure.
+Algorithms $\Rep_1, \Rep_2$ and functions $\ell\colon\mathbb{N}\to\mathbb{N}$,
+and
 $F: \calK \times \bits^{\ell_{in}} \rightarrow \bits^{\ell_{out}}$
-such that the following hold:
+are a \emph{factoring of $\Pi$} \jnote{Better name?}
+if the following hold:
 \begin{itemize}
-\item $\Rep_1$ takes as input a set $S$ and outputs distinct values $s_1, \ldots, s_t \in \bits^{\ell_{in}}$,
+\item $\Rep_1$ takes as input a set $S$ and outputs distinct $s_1, \ldots, s_t \in \bits^{\ell_{in}}$,
 where $t=\ell(|S|)$
@@
 \item For any $S$, the distribution on $\pubaux$ output by $\Rep(S)$ is identical to the distribution
-on $\pubaux$ computing as follows:
+on $\pubaux$ computed as follows:
 (1) $s_1, \ldots, s_t \getsr \Rep_1(S)$;
 (2) $K \getsr \calK$;
-(3) $\pubaux \getsr \Rep_2(|S|, F_{K}(s_1), \ldots,F_{K}(s_t))$.
+(3) $\pubaux \getsr \Rep_2(|S|, F_{K}(s_1), \ldots,F_{K}(s_t))$. \hfill\dqed
 %\item $K_1,K_2,\ldots,K_p \getsr \calK$ for some fixed number of keys~$p$;
@@
 \end{itemize}
-We call $(\Rep_1, \Rep_2, \ell, F)$ the {\sf canonical representation}
-of algorithm~$\Rep$. \hfill\dqed
+%We call $(\Rep_1, \Rep_2, \ell, F)$ the {\sf canonical representation}
+%of algorithm~$\Rep$.
 \end{definition}
@@
 
-We next show that any canonical data structure in which~$F$ is a pseudorandom function is
-semantically secure with respect to leakage consisting of the size of the set.
+$\Pi$ is \emph{canonical} if it has a factoring $\Rep_1, \Rep_2, \ell, F$ in which
+$F$ is a pseudorandom function (in which case we call $\Rep_1, \Rep_2, \ell, F$ a canonical factoring of~$\Pi$).
+We next show that any canonical data structure satisfies our simulation-based definition
+with respect to leakage consisting of the size of the set.
 
 \begin{theorem}\label{thm:priv-ss}
-Let $\setprim=(\Rep, \Qry)$ be a canonical data structure for which $\Rep$
-has canonical representation
+Let $\setprim=(\Rep, \Qry)$ have
+canonical factoring
 $(\Rep_1, \Rep_2,\ell, F)$. Then for ${\sf leak}(S) = |S|$ and
 any attacker $A$, there is an attacker
-$B$, making $\ell(|S|)$ queries, for which
+$B$ making $\ell(|S|)$ queries for which
 \[\AdvPrivSS{\setprim,{\sf leak}}{A} \leq \AdvPRF{F}{B}\,. \]
@@
 \begin{proof}
-We define a simulator $\Sim$ as follows. On input $n$, $\Sim$ fixes
-a set $S^*=\{e_1, \ldots, e_n\}$. It then computes $s_1,
-\ldots, s_t \getsr \Rep_1(S^*)$, chooses uniform values $y_1, \ldots, y_t \getsr \bool^{\ell_{out}}$,
+Define $\Sim$ as follows. On input $n$, $\Sim$ fixes
+$S^*=\{e_1, \ldots, e_n\}$, where the $e_i$ are arbitrary distinct values. It then computes $s_1,
+\ldots, s_t \getsr \Rep_1(S^*)$, chooses uniform $y_1, \ldots, y_t \getsr \bool^{\ell_{out}}$,
 and returns $\pubaux
@@
 
-Note that we can express $\Prob{\ExpPrivSSreal{\setprim}{A}=1}$ as the probability that $A$
+Note that because $\Pi$ is canonical, $\Prob{\ExpPrivSSreal{\setprim}{A}=1}$ is equal to the probability that $A$
 outputs~1 in
-the following experiment~$G0$:
-%\jnote{BTW, in class when I do this stuff I usually
-%say ``game'' and then correct myself and say ``\ldots but if you want to get funded,
-%call it an experiment.'' (Some light humor while you work.)}
+the following experiment~$G_0$:
 \begin{enumerate}
@@
 
-Now, consider an experiment $G1$ in which computation is done as follows:
+Now, consider an experiment $G_1$ in which computation is done as follows:
 \begin{enumerate}
@@
 It is immediate that the difference between the probability that $A$ outputs~1 in
-$G1$ and the probability that it outputs~1 in
-$G0$ is bounded by $\AdvPRF{F}{B}$, where $B$ performs the
+$G_1$ and the probability that it outputs~1 in
+$G_0$ is bounded by $\AdvPRF{F}{B}$, where $B$ performs the
 obvious simulation.
 
-Next, consider the following experiment $G2$:
+Next, consider the following experiment $G_2$:
 \begin{enumerate}
@@
 \end{enumerate}
-We claim that the probability with which $A$ outputs~1 in $G2$ is \emph{identical} to the
-probability with which it outputs~1 in $G1$.
+We claim that the probability with which $A$ outputs~1 in $G_2$ is \emph{identical} to the
+probability with which it outputs~1 in $G_1$.
 The follows immediately from the
-observation that the distribution on $t$ (in $G1$) is identical to the distribution on~$t^*$
-(in $G2$) by definition
-of what it means to be canonical, and it is clear that the distributions of everything
+observation that the distribution on $t$ (in $G_1$) is identical to the distribution on~$t^*$
+(in $G_2$) by definition
+of canonical, and it is clear that the distributions of everything
 else are the same as well.
 
-One can observe that $G2$ is identical to the following experiment:
+One can verify that $G_2$ is identical to the following experiment:
 \begin{enumerate}

### 2016-12-09 related-work.tex
continuing my pass, cleaning up the .bib files

@@
     ambiguous.\footnote{In fact, it isn't clear that their
-formalization actually allows for standard Bloom filters,
-    although fixing this ambiguity is straightforward once
-    recognized.} This allows us, for example, to distinguish
-    between the hash-function keys and the bit array when
-    discussing classical Bloom filters.
+formalization allows for standard Bloom filters, though fixing
+    this ambiguity is straightforward once recognized.} This
+    allows us, for example, to distinguish between the
+    hash-function keys and the bit array when discussing
+    classical Bloom filters.
 \item The Naor-Yogev definition of soundness allows the
@@
 variants. I removed it for now, since it's not clear that they have
-any particular relevance to us.}
+any particular relevance to us. I kept only the refs that seemed
+directly relevant.}
 %As previously mentioned, Bloom

### 2016-12-09 results.tex
continuing my pass, cleaning up the .bib files

@@
-\section{Case Studies}
+\section{Case Studies}\label{sec:case_studies}
 Here we explore various set-membership data structures that have been proposed
@@
 \nudge if $M[h_j] \neq 1$ then Return 0\\
-Return 1
-}
-\caption{{\bf Left:} $\Rep$ and $\Qry$ algorithms for classic Bloom
+Return 1 } \caption{{\bf Left:} $\Rep$ and $\Qry$ algorithms for
+classical Bloom
   filter $\setprim_{\mathrm{Bloom}}$ in the ROM for a hash function $H\colon \mathbb{N} \times
-  \elts \to [m]$. {\bf Right:} $\Rep$ and $\Qry$
+  \elts \to [m]$, where $|S| \leq n$. {\bf Right:} $\Rep$ and $\Qry$
   algorithms for the domain-separated PRF data structure
@@
 \subsection{Classical Bloom Filter in the Random-Oracle Model}
-Fix $n,k,m \geq 0$, and fix a set $\elts$.  Then the classical Bloom
+Fix $k,m,n \geq 0$ and a universe $\elts$.  Then the classical Bloom
 filter set-membership data structure $\setprim_{\mathrm{Bloom}}=
 (\Rep, \Qry)$ over~$\elts$ is defined as in
-Figure~\ref{fig:bf-and-ds} (left side).  We
-define~$\setprim_{\mathrm{Bloom}}$ in the random-oracle model
-(ROM), as the traditional analysis of Bloom filter correctness (as a
-function of $n,k,m$) is done in this model.\footnote{The standard
-model version would have $\Rep$ choose $H_1,H_2,\ldots,H_k$ from a
-hash function family, compute $h_j$ using these, and placing their
-description in $\pubaux$.}
+Figure~\ref{fig:bf-and-ds} (left side) for sets $S \subseteq \elts$
+of size at most $|S|\leq n$. We define~$\setprim_{\mathrm{Bloom}}$
+in the random-oracle model (ROM), as the traditional analysis of
+correctness (as a function of $n,k,m$) is done in this
+model.\footnote{The standard-model version would have $\Rep$ choose
+$H_1,\ldots,H_k$ from some function family, compute $h_j$ using
+these, and place their description in $\pubaux$.}
 
-\heading{Correctness. } The following theorem proves that the Bloom
-filter meets our correctness notion in the ROM.  Again, we stress
-that this correctness is with respect to adaptive adversaries,
-aiming to find $r \geq 1$ errors (in this case, false-positives).
+\heading{Correctness. } We prove that the Bloom filter meets our
+correctness notion in the ROM.  Again, we stress that this
+correctness is with respect to adaptive adversaries, aiming to find
+$r \geq 1$ errors (in this case, false-positives).
 
 \begin{theorem}\label{thm3}\label{thm:bf-correctness}
-Fix $k,m,n,r>0$ and a set~$\elts$, and let
-$\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be the classical Bloom
-filter (set-membership) data structure over~$\elts$. For any
-adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$
-oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
+Fix $k,m,n,r>0$ and~$\elts$, and let $\setprim_{\mathrm{Bloom}}=
+(\Rep, \Qry)$ be the classical Bloom filter (set-membership) data
+structure over~$\elts$. For any adversary~$A$ that makes a total
+of~$q_T$ queries to the $\Test$ oracle, $q_R$ queries to the random
+oracle, and has time-complexity~$O(t)$,
 \[
@@
 \end{theorem}
-We note that Kirsch and Mitzenmacher~\cite{kirsch2006less} show
-that the ($r=1$, zero-query) error-probability for~$\setprim_\mathrm{Bloom}$ is
-always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
-rate of convergence is faster than~$1/n$.  The multiplicative (``hybrid'') term arises as a result
-of moving from the adaptive to the zero-query setting.
-Finally, $\binom{q_T+q_H-1}{r-1} \leq (q_T+q_H)^r$ (with reasonable tightness when~$r$ is small) in
-which case the final term in the bound behaves as
-$((q_T+q_H) (1-e^{-kn/m})^k + O(q/n) )^r$; loosely, this is the bound one expects for
-trying to find a single correctness error (in this case, a false positive) in each of~$r$ independent``rounds'', each round
-consisting of~$(q_T+q_H)$ attempts.
+Note that Kirsch and Mitzenmacher~\cite{kirsch2006less} show that
+the ($r=1$, zero-query) error-probability
+for~$\setprim_\mathrm{Bloom}$ is %always within $O(1/n)$ of
+$(1-e^{-kn/m})^k+O(1/n)$. %, although the asymptotic rate of
+%convergence is faster than~$1/n$.
+The multiplicative %(``hybrid'')
+term arises as a result of moving from the zero-query to the
+adaptive setting. Also note that $\binom{q_T+q_H-1}{r-1} \leq
+(q_T+q_H)^r$ (with reasonable tightness when~$r$ is small), in which
+case the bound becomes
+\[\left((q_T+q_H) \cdot (1-e^{-kn/m})^k + O((q_T+q_H)/n) \right)^r;\]
+loosely, and ignoring the low-order term, this is the bound one
+expects if we view the attacker as trying to find an error in each
+of~$r$ independent``rounds,'' each round consisting of~$q_T+q_H$
+attempts. \jnote{But if the attacker makes $q=q_T+q_H$ queries
+overall, isn't it only making $q/r$ queries per round?}
+%JK
 \input{BF_correctness}

### 2016-12-09 syntax.tex
intro
continuing my pass, cleaning up the .bib files

@@
 When~$\univ$ is a set, we write $x \getsr \univ$ to denote sampling
-an element uniformly from~$\univ$ and assigning it to~$x$. We extend
+a uniform element from~$\univ$ and assigning it to~$x$. We extend
 this notation to randomized algorithms, so $x \getsr A(y)$ denotes
@@
     randomized \emph{representation algorithm}, taking as input
-    an element $S \in \univ$,
+    $S \in \univ$,
     and outputting %a \emph{representation} $M \in \Sigma^*$,
@@
 $\mathrm{Err}(S,\qry,\pubaux,\privaux)$ be  true iff
-$\Qry(\pubaux,\privaux, \qry) \neq \qry(S)$.  Then we define for
-$\setprim$ the quantities
+$\Qry(\pubaux,\privaux, \qry) \neq \qry(S)$.  Then we define
 \begin{align*}
@@
 \end{align*}
-which are the \emph{error probability} and \emph{error rate}, respectively.
+to be, respectively, the \emph{error probability} and \emph{error
+rate} of~$\Pi$.
 %
@@
 
-The above definition can be lifted to the random-oracle model by
-giving $\Rep, \Qry$ access to a random oracle. In that case, the
+The above definitions can be lifted to the random-oracle model by
+giving $\Rep, \Qry$ access to a random oracle. In that case, all
 probabilities are also taken over choice of the random oracle. We
 remark that, while our error probability and error rate do not
-distinguish among ``types'' of errors, they also do not preclude
-instantiations (like the classical Bloom filter) that admit only one
-type of error, e.g., false positives.
+distinguish among different ``types'' of errors, they also do not
+preclude instantiations (like the classical Bloom filter) that admit
+only one type of error, e.g., false positives.
 
@@
 %\heading{Data structures for set-membership queries.}
-An important special case is a data structure that supports set-membership
-queries. \jnote{I changed this from multiplicity to membership.}
-
+An important special case is a data structure for set-membership
+queries.
 \begin{definition} \rm
@@
 structure with $\univ \subseteq 2^\elts$, $\Gamma=\{0,1\}$, and
-$\calQ=\{\qry_x\}_{x \in \univ}$, where $\qry_x(S)$ is true iff $x
+$\calQ=\{\qry_x\}_{x \in \univ}$ where $\qry_x(S)$ is true iff $x
 \in S$. \hfill\dqed
@@
 sets up to some bounded size.
+
+\heading{The role of $\pubaux$.} One can always ``increase
+security'' by pushing all representation data into $\privaux$ and
+making $\pubaux$ empty. (This is true in a formal sense for the
+definitions given subsequently, but is intuitively true regardless.)
+But this misses the point. First, we are interested in analyzing
+existing data structures, some of which have a non-empty public
+portion. Moreover, for some applications a non-trivial $\pubaux$ is
+essential; this will become clear in Section~\ref{sec:case_studies}.
 

### 2016-12-12 BF_correctness.tex
no message

@@
 $\HashOracle$ returns a random value sampled from $[m]$. It can be
-seen that, game $\game{0}$ exactly simulates the correctness game of
-$\setprim_{\mathrm{gbf}}$.  So,
-$\AdvCorrect{\setprim_{\mathrm{gbf}},r}{A} = \Prob{\game{0}(A) =
+seen that game $\game{0}$ exactly simulates the correctness game of
+$\setprim_{\mathrm{Bloom}}$, and so
+$\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} = \Prob{\game{0}(A) =
 1}$.
 
-Game $\game{1}$ is exactly same as game $\game{0}$ except the $\Qry$ call (inside the $\TestOracle$ oracle) is replaced by the code of $\Qry$.
-Hence, $\Prob{\game{0}(A) = 1} = \Prob{\game{1}(A) = 1}$.
-
-In game $\game{2}$, the $\Test$ oracle is altered to return the hash values~$h_1,h_2,\ldots, h_k$ in addition to the result of executing the code of $\Qry$.
-As this only provides additional information to the adversary, $\Prob{\game{1}(A) = 1} \leq \Prob{\game{2}(A) = 1}$.
-
-In $\game{3}$, we modify the $\HashOracle$ oracle so that on query~$\qry_x$ it returns all of the~$k$ values that previously would have required calls $\HashOracle(1,\qry_y),\HashOracle(2,\qry_y),\ldots,\linebreak\HashOracle(k,\qry_y)$.
-This results in adversary getting $(k-1)$ hash values ``for free'', as we charge the adversary only for a single query.
-We alter the $\TestOracle$ oracle accordingly, so that it makes a single call $\Hash(\qry_x)$ rather than~$k$ such calls.
-We do this so that we can assume that a call~$\HashOracle(\qry_x)$ is pointless after a~$\TestOracle(\qry_x)$ call, and this will aid us in subsequent games.
-Thus, $\Prob{\game{2}(A) = 1} \leq \Prob{\game{3}(A) = 1}$.
-We assume from Game~$\game{3}$ and on that $\Rep$ is also appropriately modifed for the new behavior of~$\HashOracle$.
-
-Game~$\game{4}$ contains some important changes from game~$\game{3}$,
-but we will argue that $\Prob{\game{3}(A) = 1} \leq \Prob{\game{4}(A)
-  = 1}$. The $\TestOracle$ oracle on input~$\qry_x$ no longer computes
-its answer directly, but instead refers to a new table~$\mathrm{Ans}[x]$ which is populated upon calls to the
-$\HashOracle$ oracle.  In particular, if $\mathrm{Ans}[x]$ is undefined, $\TestOracle$ makes a $\HashOracle(\qry_x)$ call;
-otherwise, it returns the contents of~$\mathrm{Ans}[x]$, which
-contains exactly the values that~$\TestOracle(\qry_x)$ would have
-returned in the previous game.  The $\HashOracle$ oracle, on input~$\qry_y$ computes the random values~$v_1,v_2,\ldots,v_k$ as in
-$\game{3}$.  It maintains the table~$T$ because~$A$ is permitted to
-call~$\HashOracle$ on $y \in S$.
-%(We no longer need to maintain the table~$T$ because hash values are
-%only determined by~$\HashOracle$ calls, and these are never repeated
-%under our no-pointless-query assumption.)
-It then computes the answer that~$\TestOracle(\qry_x)$ would return in
-game~$\game{3}$, and stores the answer in~$\mathrm{Ans}[x]$ for use
-by~$\TestOracle$.
-None of these changes alters the behavior of the game from the
-adversary's perspective.
-
-At this point, we consider $\Prob{\game{4}(A)=1}$.  Note that is
-happens iff there are~$r$ calls to the $\HashOracle$ oracle that
-increment~$\err$, i.e., queries $y \not\in S$ such that
-$\bigwedge_{j=1}^{k} M[v_j]=1$.  We can assume without loss that~$A$
-does not call~$\HashOracle$ on $y \in S$ because the indices
-$v_1,v_2,\ldots,v_k$ that will correspond to any $y \not\in S$ will be
-\emph{independent} of those corrsponding to any of the $y \in S$.
-Thus these queries are wasted.  Now, there are at total of $q_T + q_H$
-queries made to~$\HashOracle$, either directly by~$A$ or indirectly
-by~$A$ calling~$\TestOracle$.  For $\game{4}(A)$ to return 1, there
-must be~$r$ among these that increment the counter.  We can assume
-WLOG that~$A$ halts as soon as~$\err=r$ (which it can easily track),
-so there are $\binom{q_T+q_H-1}{r-1}$ possible ``winning'' query
-patterns to consider.  As each error event is independent of all
-previous choices made by the~$\HashOracle$, we need only consider the
-probability of a single error. Using Kirsch and Mitzenmacher's~\cite{kirsch2006less} upperbound on false positive probability of a classical Bloom filter,
-we have  $\Prob{\game{4}(A)=1} = \binom{q_T+q_H-1}{r-1}\left( (1-e^{-kn/m})^k + O(1/n) \right)^r$.
-To summarize,
-\[
-\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H-1}{r-1}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
-\]
-which is the bound claimed in the theorem statement.
 \begin{figure}[tp]
@@
 
-\oracle{$\HashOracle(i,\qry_y)$}\\
+\oracle{$\HashOracle(i,y)$}\\
 $v \getsr [m]$\\
@@
 $T[i,y] \gets v$\\
-Return $v$
-}
-{
+Return $v$ } {
 \underline{$\game{1}(A)$}\\
@@
 for $j \in \{1,2,\ldots,k\}$\\
-\nudge $h_j \gets \HashOracle(j, \qry_x)$\\
+\nudge $h_j \gets \HashOracle(j, x)$\\
 \nudge if $M[h_j] \neq 1$ then Return 0\\
-$\err \gets \err + 1$\\
+if $x \not \in S$ then $\err \gets \err + 1$\\
 Return 1\\
 
-\oracle{$\HashOracle(i,\qry_y)$}\\
+\oracle{$\HashOracle(i,y)$}\\
 $v \getsr [m]$\\
@@
 $T[i,y] \gets v$\\
-Return $v$
-}
-}
-\fpage{.9}{
-\hpagessl{.45}{.5}
-{
+Return $v$ } } \fpage{.9}{ \hpagessl{.45}{.5} {
 \underline{$\game{2}(A)$}\\
@@
 for $j \in \{1,2,\ldots,k\}$\\
-\nudge $h_j \gets \HashOracle(j, \qry_x)$\\
+\nudge $h_j \gets \HashOracle(j, x)$\\
 \nudge if $M[h_j] \neq 1$\\
 \nudge \nudge Return $(0, (h_1, \ldots, h_j))$\\
-$\err \gets \err +1$\\
+if $x \not \in S$ then $\err \gets \err + 1$\\
 Return~$(1, (h_1, \ldots, h_{k}) )$\\
 
-\oracle{$\HashOracle(i,\qry_y)$}\\
+\oracle{$\HashOracle(i, y)$}\\
 $v \getsr [m]$\\
@@
 $T[i,y] \gets v$\\
-Return $v$
-}
-{
+Return $v$ } {
 \underline{$\game{3}(A)$}\\
@@
 $\calC \gets \calC \cup x$; $M \gets\pubaux$\\
-$(h_1, \ldots, h_{k}) \gets \HashOracle(\qry_x)$\\
+$(h_1, \ldots, h_{k}) \gets \HashOracle(x)$\\
 for $j \in \{1,2,\ldots,k\}$\\
@@
 \nudge \nudge Return~$(0, (h_1, \ldots, h_{k}) )$\\
-$\err \gets \err +1$\\
+if $x \not \in S$ then $\err \gets \err +1$\\
 Return~$(1, (h_1, \ldots, h_{k}) )$\\
 
-\oracle{$\HashOracle(\qry_y)$}\\
+\oracle{$\HashOracle(y)$}\\
 for $j \in \{1,2,\ldots,k\}$\\
@@
 \nudge $T[j,y] \gets v_j$\\
-Return $\left(v_1,\ldots,v_k\right)$
-}
-}
-\caption{Games $\game{0}$-$\game{3}$ for the
-proof of Theorem~\ref{thm:bf-correctness}.}
-\label{fig:bf-correctness-games1}
+Return $\left(v_1,\ldots,v_k\right)$ } } \caption{Games
+$\game{0}$--$\game{3}$ for the proof of
+Theorem~\ref{thm:bf-correctness}.} \label{fig:bf-correctness-games1}
 \end{figure}
+
+Game $\game{1}$ is exactly same as game $\game{0}$ except the $\Qry$
+call (inside the $\TestOracle$ oracle) is replaced by the code of
+$\Qry$.  Hence, $\Prob{\game{0}(A) = 1} = \Prob{\game{1}(A) = 1}$.
+
+In game $\game{2}$, the $\Test$ oracle is altered to return hash
+values~$h_1,\ldots$ in addition to the result of executing the code
+of $\Qry$.  As this only provides additional information to the
+adversary, $\Prob{\game{1}(A) = 1} \leq \Prob{\game{2}(A) = 1}$.
+\jnote{Actually this is not true\ldots what you want to say is that
+there is another adversary $A'$ making the same number of queries
+and with essentially the same running time such that
+$\Prob{\game{1}(A) = 1} \leq \Prob{\game{2}(A') = 1}$. Same comment
+applies to G3 below.}
+
+\jnote{This is a rather long-winded proof considering that nothing
+substantial changes in games G0--G3.}
+
+In $\game{3}$, we modify the $\HashOracle$ oracle so that on
+query~$x$ it returns the~$k$ values that previously would have
+required $k$ calls $\HashOracle(1,x), \ldots, \HashOracle(k,x)$. We
+alter the $\TestOracle$ oracle accordingly, so that it makes a
+single call to $\Hash$ rather than~$k$ such calls. (We assume that
+$\Rep$ is also appropriately modified for the new behavior
+of~$\HashOracle$.) We do this so we can assume that a
+call~$\HashOracle(x)$ is pointless after a~$\TestOracle(x)$ call has
+been made. This change results in the adversary getting $(k-1)$ hash
+values ``for free,'' as we charge the adversary only for a single
+query. \jnote{I don't see why we do this. The analysis is no easier,
+but now the attacker gets free queries.}  It is obvious that
+$\Prob{\game{2}(A) = 1} \leq \Prob{\game{3}(A) = 1}$.
+
+%JK
+Game~$\game{4}$ contains some important changes from
+game~$\game{3}$. In $\game{4}$ the $\TestOracle$ oracle no longer
+computes its answer directly, but instead refers to a
+table~$\mathrm{Ans}[x]$ that is populated upon calls to the
+$\HashOracle$ oracle.  In particular, if $\mathrm{Ans}[x]$ is
+undefined, $\TestOracle$ makes a call $\HashOracle(x)$; otherwise,
+it returns the contents of~$\mathrm{Ans}[x]$, which contains exactly
+the values that~$\TestOracle(\qry_x)$ would have returned in the
+previous game.  The $\HashOracle$ oracle, on input~$\qry_y$ computes
+the random values~$v_1,v_2,\ldots,v_k$ as in $\game{3}$. It
+maintains the table~$T$ because~$A$ is permitted to
+call~$\HashOracle$ on $y \in S$.
+%(We no longer need to maintain the table~$T$ because hash values are
+%only determined by~$\HashOracle$ calls, and these are never repeated
+%under our no-pointless-query assumption.)
+It then computes the answer that~$\TestOracle(\qry_x)$ would return in
+game~$\game{3}$, and stores the answer in~$\mathrm{Ans}[x]$ for use
+by~$\TestOracle$.
+None of these changes alters the behavior of the game from the
+adversary's perspective.
+
+ but we will argue that $\Prob{\game{3}(A) = 1} \leq
+\Prob{\game{4}(A)
+  = 1}$.
+
+At this point, we consider $\Prob{\game{4}(A)=1}$.  Note that is
+happens iff there are~$r$ calls to the $\HashOracle$ oracle that
+increment~$\err$, i.e., queries $y \not\in S$ such that
+$\bigwedge_{j=1}^{k} M[v_j]=1$.  We can assume without loss that~$A$
+does not call~$\HashOracle$ on $y \in S$ because the indices
+$v_1,v_2,\ldots,v_k$ that will correspond to any $y \not\in S$ will
+be \emph{independent} of those corresponding to any of the $y \in
+S$. Thus these queries are wasted.  Now, there are at total of $q_T
++ q_H$ queries made to~$\HashOracle$, either directly by~$A$ or
+indirectly by~$A$ calling~$\TestOracle$.  For $\game{4}(A)$ to
+return 1, there must be~$r$ among these that increment the counter.
+We can assume without loss of generality that~$A$ halts as soon
+as~$\err=r$ (which it can easily track), so there are
+$\binom{q_T+q_H-1}{r-1}$ possible ``winning'' query patterns to
+consider.  As each error event is independent of all previous
+choices made by the~$\HashOracle$, we need only consider the
+probability of a single error. Using Kirsch and
+Mitzenmacher's~\cite{kirsch2006less} upper bound on false positive
+probability of a classical Bloom filter, we have
+$\Prob{\game{4}(A)=1} = \binom{q_T+q_H-1}{r-1}\left( (1-e^{-kn/m})^k
++ O(1/n) \right)^r$. To summarize,
+\[
+\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H-1}{r-1}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\]
+which is the bound claimed in the theorem statement.
 \begin{figure}[tp]
@@
 if $\Ans[x] = \undefined$\\
-\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(\qry_x)$\\
+\nudge $(h_1, \ldots, h_{k}) \gets \HashOracle(x)$\\
 Return $\Ans[x]$\\

### 2016-12-12 results.tex
no message

@@
 \end{theorem}
-Note that Kirsch and Mitzenmacher~\cite{kirsch2006less} show that
-the ($r=1$, zero-query) error-probability
+Kirsch and Mitzenmacher~\cite{kirsch2006less} show that the ($r=1$,
+zero-query) error-probability
 for~$\setprim_\mathrm{Bloom}$ is %always within $O(1/n)$ of
@@
 adaptive setting. Also note that $\binom{q_T+q_H-1}{r-1} \leq
-(q_T+q_H)^r$ (with reasonable tightness when~$r$ is small), in which
+(eq/r)^r$ (letting $q=q_T+q_H$, and assuming $q\gg r$), in which
 case the bound becomes
-\[\left((q_T+q_H) \cdot (1-e^{-kn/m})^k + O((q_T+q_H)/n) \right)^r;\]
-loosely, and ignoring the low-order term, this is the bound one
-expects if we view the attacker as trying to find an error in each
-of~$r$ independent``rounds,'' each round consisting of~$q_T+q_H$
-attempts. \jnote{But if the attacker makes $q=q_T+q_H$ queries
-overall, isn't it only making $q/r$ queries per round?}
+\[\left(eq/r \cdot (1-e^{-kn/m})^k + O(q/rn) \right)^r.\]
+Loosely, and ignoring the low-order term, this is the bound expected
+by viewing the attacker as trying to find an error in each of~$r$
+independent``rounds,'' each round consisting of~$q/r$ attempts.
+\jnote{I didn't find the last two sentences helpful.}
 %JK

### 2016-12-13 BF_correctness.tex
continuing my pass...

@@
 $\HashOracle$ oracle performs lazy sampling of elements from $[m]$
-to mimic a random oracle (RO). For every distinct query,
-$\HashOracle$ returns a random value sampled from $[m]$. It can be
-seen that game $\game{0}$ exactly simulates the correctness game of
+to mimic a random oracle. For every distinct query, $\HashOracle$
+returns a random value sampled from $[m]$. It can be seen that game
+$\game{0}$ exactly simulates the correctness game of
 $\setprim_{\mathrm{Bloom}}$, and so
@@
 
-\oracle{$\TestOracle(\qry_x)$}\\
+\oracle{$\TestOracle(q_x)$}\\
 if $x \in \mathcal{C}$ then Return $\bot$\\
@@
 values ``for free,'' as we charge the adversary only for a single
-query. \jnote{I don't see why we do this. The analysis is no easier,
-but now the attacker gets free queries.}  It is obvious that
-$\Prob{\game{2}(A) = 1} \leq \Prob{\game{3}(A) = 1}$.
+query. \jnote{Can we do better by being more careful?} It is obvious
+that $\Prob{\game{2}(A) = 1} \leq \Prob{\game{3}(A) = 1}$.
 
-%JK
 Game~$\game{4}$ contains some important changes from
@@
 table~$\mathrm{Ans}[x]$ that is populated upon calls to the
-$\HashOracle$ oracle.  In particular, if $\mathrm{Ans}[x]$ is
-undefined, $\TestOracle$ makes a call $\HashOracle(x)$; otherwise,
-it returns the contents of~$\mathrm{Ans}[x]$, which contains exactly
-the values that~$\TestOracle(\qry_x)$ would have returned in the
-previous game.  The $\HashOracle$ oracle, on input~$\qry_y$ computes
-the random values~$v_1,v_2,\ldots,v_k$ as in $\game{3}$. It
-maintains the table~$T$ because~$A$ is permitted to
-call~$\HashOracle$ on $y \in S$.
+$\HashOracle$ oracle.  If $\mathrm{Ans}[x]$ is undefined,
+$\TestOracle$ makes a call $\HashOracle(x)$; otherwise, it returns
+the contents of~$\mathrm{Ans}[x]$, which contains exactly the values
+that~$\TestOracle(q_x)$ would have returned in the previous game.
+The $\HashOracle$ oracle, on input~$x$, computes
+values~$v_1,\ldots,v_k$ as in $\game{3}$. %It maintains the table~$T$
+%because~$A$ is permitted to call~$\HashOracle$ on $y \in S$.
 %(We no longer need to maintain the table~$T$ because hash values are
@@
 %under our no-pointless-query assumption.)
-It then computes the answer that~$\TestOracle(\qry_x)$ would return in
+It then computes the answer that~$\TestOracle(q_x)$ would return in
 game~$\game{3}$, and stores the answer in~$\mathrm{Ans}[x]$ for use
-by~$\TestOracle$.
-None of these changes alters the behavior of the game from the
-adversary's perspective.
+by~$\TestOracle$. None of these changes alters the view of~$A$, and
+so $\Prob{\game{3}(A) = 1} = \Prob{\game{4}(A)
+  = 1}$. \jnote{You had $\leq$ before.}
 
- but we will argue that $\Prob{\game{3}(A) = 1} \leq
-\Prob{\game{4}(A)
-  = 1}$.
-
-At this point, we consider $\Prob{\game{4}(A)=1}$.  Note that is
-happens iff there are~$r$ calls to the $\HashOracle$ oracle that
-increment~$\err$, i.e., queries $y \not\in S$ such that
-$\bigwedge_{j=1}^{k} M[v_j]=1$.  We can assume without loss that~$A$
-does not call~$\HashOracle$ on $y \in S$ because the indices
-$v_1,v_2,\ldots,v_k$ that will correspond to any $y \not\in S$ will
-be \emph{independent} of those corresponding to any of the $y \in
-S$. Thus these queries are wasted.  Now, there are at total of $q_T
-+ q_H$ queries made to~$\HashOracle$, either directly by~$A$ or
-indirectly by~$A$ calling~$\TestOracle$.  For $\game{4}(A)$ to
-return 1, there must be~$r$ among these that increment the counter.
-We can assume without loss of generality that~$A$ halts as soon
-as~$\err=r$ (which it can easily track), so there are
-$\binom{q_T+q_H-1}{r-1}$ possible ``winning'' query patterns to
-consider.  As each error event is independent of all previous
+Note that $\game{4}(A)=1$ iff there are~$r$ queries to the
+$\HashOracle$ oracle that increment~$\err$, i.e., queries $y \not\in
+S$ such that $\bigwedge_{j=1}^{k} M[v_j]=1$.
+%We can assume without
+%loss of generality that~$A$ does not call~$\HashOracle$ on $y \in S$
+%because the indices $v_1,v_2,\ldots,v_k$ that will correspond to any
+%$y \not\in S$ will be \emph{independent} of those corresponding to
+%any of the $y \in S$. Thus these queries are wasted.
+There are at total of $q_T + q_H$ queries made to~$\HashOracle$,
+either directly by~$A$ or indirectly when~$A$ calls~$\TestOracle$.
+For $\game{4}(A)$ to return~1, there must be~$r$ among these that
+increment~$\err$. %We can assume without loss of generality that~$A$
+%halts as soon as~$\err=r$ (which it can easily track), so
+There are $\binom{q_T+q_H}{r}$ possible ``winning'' query patterns
+to consider.  \jnote{I changed the bound; I don't think it was
+correct before.} As each error event is independent of all previous
 choices made by the~$\HashOracle$, we need only consider the
-probability of a single error. Using Kirsch and
-Mitzenmacher's~\cite{kirsch2006less} upper bound on false positive
-probability of a classical Bloom filter, we have
-$\Prob{\game{4}(A)=1} = \binom{q_T+q_H-1}{r-1}\left( (1-e^{-kn/m})^k
-+ O(1/n) \right)^r$. To summarize,
+probability of a single error. Using the upper bound on false
+positives for the classical Bloom filter shown by Kirsch and
+Mitzenmacher~\cite{kirsch2006less}, we have $\Prob{\game{4}(A)=1}
+\leq \binom{q_T+q_H}{r}\left( (1-e^{-kn/m})^k + O(1/n) \right)^r$.
+We conclude that
 \[
-\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H-1}{r-1}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,,
 \]
-which is the bound claimed in the theorem statement.
+as claimed.
 \begin{figure}[tp]
@@
 {
-\oracle{$\HashOracle(\qry_y)$}\\
+\oracle{$\HashOracle(y)$}\\
 for $j \in \{1,2,\ldots,k\}$\\
@@
 %\nudge \nudge if $c \in \calI$ then $\bad \gets \true$\\
-\nudge \nudge $\Break$\\
-if $j < k$ then Return $\left(v_1,\ldots,v_k\right)$\\
+\nudge \nudge Return $\left(v_1,\ldots,v_k\right)$\\
+%\nudge \nudge $\Break$\\
+%if $j < k$ then Return $\left(v_1,\ldots,v_k\right)$\\
 %if $c \notin \calI$ then $\bad \gets \true$\\

### 2016-12-13 ds-correctness.tex
continuing my pass...

@@
 
-\begin{proof}[Theorem~\ref{thm:ds-correctness}]
-%\fixme{Animesh: remove these Cref things and replace with references
-  %like I have them in the text.}
-We use a game playing argument to prove this theorem. Please refer to
+\begin{proof} \jnote{I did not check this proof; see my comment before the proof.}
+We use a game-playing argument to prove this theorem. Please refer to
 Figure~\ref{fig:ds-correctness-games}.
@@
 \end{equation}
-
-In game $\game{1}$, $A$ attacks a related data structure $\tilde{\setprim}_\mathrm{ds}$, in which $F_K$ is replaced by a random function.
-Let $B$ be a prf-adversary as shown in Figure~\ref{fig:ds-correctness-adv}.
-Based on its challenge bit $b$, it exactly simulates $\game{0}$ or $\game{1}$.
-So,
-\begin{align*}
-\Prob{\ExpPRF{F}{B} = 1\,|\,b=1} &= \Prob{\game{0}(A)=1} \\
-\Prob{\ExpPRF{F}{B} = 1\,|\,b=0} &= 1-\Prob{\game{1}(A)=1}
-\end{align*}
-
-By a standard conditioning of PRF advantage, we have
-\begin{equation*}
-\Prob{\game{0}(A)=1} = \AdvPRF{F}{B} + \Prob{\game{1}(A)=1}%\label{eq:13}
-\end{equation*}
-
-Coming back to the game playing argument, in game $\game{2}$, $\HashOracle$ returns random values sampled from $[m]$, assuming $A$ makes no pointless queries.
-In addition, the $\Test$ oracle keeps a counter, $c$ to keep track of the number of queries by $A$ to the $\Test$.
-It also sets a boolean $\bad$ flag to $\false$ if queries which are not indexed by the $r$-set $\calI$ are false-positives, and queries indexed by set $\calI$ are not false-positives.
-It must be noted that $\bad$ does not affect the output of the $\Test$ or the game.
-We argue that, $\Prob{\game{1}(A)=1} \leq \Prob{\game{2}(A)=1}$.
-Game $\game{3}$ is identical to $\game{2}$, except it returns 0 if $\bad$ is set to $\true$.
-$\game{3}$ returns 1 whenever $\game{2}$ would return 1, and $\bad$ remained false in $\game{2}$.
-So, basically $\game{3}$ guessed exactly the $r$ queries that results in errors.
-Hence, $\Prob{\game{3}(A)=1} = \frac{1}{\binom{q}{r}}\Prob{\game{2}(A)=1}$.
-
-Let $D$ be an adversary shown in Figure~\ref{fig:lin-correctness-zq-adv}.
-It effectively simulates game~$game{3}$, guessing which~$r$ of~$A$'s queries to send to its own~$\TestOracle$.
-By its construction, if $\game{3}(A)=1$ then~$D$ will also find~$r$ errors in~$\tilde{\setprim}_{\mathrm{ds}}$.
-Thus, $\AdvCorrect{\tilde{\setprim}_{\mathrm{ds}},r}{D} = \Prob{\game{3}(A) = 1}$.
-
-It can be easily seen that  $\tilde{\setprim}_{\mathrm{ds}}$ is the scheme that is analyzed in the classical Bloom filter literature.
-So, for an adversary $D$ and $r=1$, advantage of $D$ to win $\ExpCorrect{\tilde{\setprim}_{\mathrm{ds}},r}$ will be upper bounded by the false-positive probability of a classical Bloom filter.
-For $r > 1$, based on the assumption that $A$ makes no pointless queries, the queries made by $A$ are distinct and not elements of the original set $S$.
-Also, since $\HashOracle$ in $\game{3}$ returns $k$ random values for each query, the event of getting a false positive is independent of the index of the query.
-So, $\AdvCorrect{\tilde{\setprim}_{\mathrm{ds}},r}{D} =   {\binom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r$
-
-\noindent
-To summarize, we have
-\[
-\AdvCorrect{\setprim_{\mathrm{ds}},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
-\]
-which is the bound claimed in the theorem statement. \hfill \qed
 
@@
 \nudge $h_j(x) \gets \FK $\\
-Return $\left(h_1(x),\ldots,h_k(x)\right)$
-}
-{
+Return $\left(h_1(x),\ldots,h_k(x)\right)$ } {
 \underline{\game{1}(A)}\\
@@
 \nudge $h_j(x) \gets \rhoK $\\
-Return $\left(h_1(x),\ldots,h_k(x)\right)$
-}
-}
-\fpage{.9}{
-\hpagessl{.45}{.5}
-{
+Return $\left(h_1(x),\ldots,h_k(x)\right)$ } } \fpage{.9}{
+\hpagessl{.45}{.5} {
 \underline{\game{2}(A)\fbox{\game{3}(A)}}\\
@@
 if $\err  < r$ then Return 0\\
-Return 1
-}
+Return 1 }
 %
@@
 \nudge $v_j \getsr [m]$\\
-Return $\left(v_1,\ldots,v_k\right)$
-}
-}
-\caption{Games $\game{0}$-$\game{3}$ for the
-proof of Theorem~\ref{thm:ds-correctness}.}
-\label{fig:ds-correctness-games}
-
+Return $\left(v_1,\ldots,v_k\right)$ } } \caption{Games
+$\game{0}$--$\game{3}$ for the proof of
+Theorem~\ref{thm:ds-correctness}.} \label{fig:ds-correctness-games}
 \end{figure}
 
+In game $\game{1}$, $A$ attacks a related data structure
+$\tilde{\setprim}_\mathrm{ds}$, in which $F_K$ is replaced by a
+random function. Let $B$ be a prf-adversary as shown in
+Figure~\ref{fig:ds-correctness-adv}. Based on its challenge bit $b$,
+it exactly simulates $\game{0}$ or $\game{1}$. So,
+\begin{align*}
+\Prob{\ExpPRF{F}{B} = 1\,|\,b=1} &= \Prob{\game{0}(A)=1} \\
+\Prob{\ExpPRF{F}{B} = 1\,|\,b=0} &= 1-\Prob{\game{1}(A)=1}
+\end{align*}
+By a standard argument, we have
+\begin{equation*}
+\Prob{\game{0}(A)=1} = \AdvPRF{F}{B} + \Prob{\game{1}(A)=1}.%\label{eq:13}
+\end{equation*}
+
+In game $\game{2}$, $\HashOracle$ returns random values sampled from
+$[m]$, assuming $A$ makes no pointless queries. In addition, the
+$\TestOracle$ oracle keeps a counter, $c$ to keep track of the
+number of queries by $A$ to the $\TestOracle$. It also sets a
+boolean $\bad$ flag to $\false$ if queries which are not indexed by
+the $r$-set $\calI$ are false-positives, and queries indexed by set
+$\calI$ are not false-positives. It must be noted that $\bad$ does
+not affect the output of the $\TestOracle$ or the game. We argue
+that, $\Prob{\game{1}(A)=1} \leq \Prob{\game{2}(A)=1}$. Game
+$\game{3}$ is identical to $\game{2}$, except it returns 0 if $\bad$
+is set to $\true$. $\game{3}$ returns 1 whenever $\game{2}$ would
+return 1, and $\bad$ remained false in $\game{2}$. So, basically
+$\game{3}$ guessed exactly the $r$ queries that results in errors.
+Hence, $\Prob{\game{3}(A)=1} =
+\frac{1}{\binom{q}{r}}\Prob{\game{2}(A)=1}$.
+
+Let $D$ be the adversary shown in
+Figure~\ref{fig:lin-correctness-zq-adv}. It effectively simulates
+game~$\game{3}$, guessing which~$r$ of~$A$'s queries to send to its
+own~$\TestOracle$. By its construction, if $\game{3}(A)=1$ then~$D$
+will also find~$r$ errors in~$\tilde{\setprim}_{\mathrm{ds}}$. Thus,
+$\AdvCorrect{\tilde{\setprim}_{\mathrm{ds}},r}{D} =
+\Prob{\game{3}(A) = 1}$.
+
 %\caption{PRF adversary $B$ simulating $\game{1}(A)$ and $\game{2}(A)$
-\begin{figure}
+\begin{figure}[htb]
 \centering
@@
 \oracle{$\HashOracle(x)$}\\
-\nudge Return $\OK$, for $j\in[1,k]$
-}
-{
+\nudge Return $\OK$, for $j\in[1,k]$ } {
 $\adversaryv{D^\TestOracle}$\\[4pt]
@@
 \nudge When $A$ halts:\\
-\nudge\nudge Return $\bot$
-}
-}
-\caption{Left: Adversary $B$ simulating $\game{0}(A)$ and $\game{1}(A)$ respectively for the
-proof of Theorem~\ref{thm:ds-correctness}. Right: Adversary $D$ for Theorems~\ref{thm:ds-correctness} }\label{fig:ds-correctness-adv}\label{fig:lin-correctness-zq-adv}
+\nudge\nudge Return $\bot$ } } \caption{Left: Adversary $B$
+simulating $\game{0}(A)$ and $\game{1}(A)$ respectively for the
+proof of Theorem~\ref{thm:ds-correctness}. Right: Adversary $D$ for
+Theorem~\ref{thm:ds-correctness}.
+}\label{fig:ds-correctness-adv}\label{fig:lin-correctness-zq-adv}
 %\fixme{Animesh: remove Crefs, make caption refer to correct theorem}
@@
 
+It can be easily seen that $\tilde{\setprim}_{\mathrm{ds}}$ is the
+scheme analyzed in the classical Bloom-filter literature. So, for an
+adversary $D$ and $r=1$, advantage of $D$ to win
+$\ExpCorrect{\tilde{\setprim}_{\mathrm{ds}},r}$ will be upper
+bounded by the false-positive probability of a classical Bloom
+filter. For $r > 1$, based on the assumption that $A$ makes no
+pointless queries, the queries made by $A$ are distinct and not
+elements of the original set $S$. Also, since $\HashOracle$ in
+$\game{3}$ returns $k$ random values for each query, the event of
+getting a false positive is independent of the index of the query.
+So, $\AdvCorrect{\tilde{\setprim}_{\mathrm{ds}},r}{D} =
+{\binom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r$. To
+summarize, we have
+\[
+\AdvCorrect{\setprim_{\mathrm{ds}},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r
+\]
+which is the bound claimed in the theorem statement. \hfill \qed
 \end{proof}

### 2016-12-13 notions.tex
continuing my pass...

@@
 \heading{A simulation-based definition. }
-%\jnote{I like ``simulation-based security'' rather than ``semantic security.''}
+\jnote{I like ``simulation-based security'' rather than ``semantic security.''}
 Our simulation-based definition is given in
@@
 all algorithms with access to the
-random oracle.
+random oracle. \jnote{Including the simulator? So is this a non-programmable RO? We should comment in any case.}
 Informally, a scheme $\setprim$ is secure with respect to some leakage function ${\sf leak}$
@@
 }
-\caption{Experiments for a ``semantic-security''-style privacy
+\caption{Experiments for a simulation-based privacy
   definition.}
@@
 
-\heading{Relationships between the notions.}
-Intuition suggests that semantic security should imply one-wayness. And, indeed, this is
+\heading{Relationships between the notions. }
+Intuition suggests that our simulation-based definition should imply one-wayness. And, indeed, this is
 the case---provided one is careful with the technical details.
@@
 \begin{theorem}
-Let $\setprim$ be a set-membership data structure. For any distribution ${\cal D}$ and
-attacker~$A$, there is an attacker $A'$ running in about the same time with
+Let $\setprim$ be a set-membership data structure. For any distribution ${\cal D}$,
+attacker~$A$, and leakage function~${\sf leak}$, there is an attacker $A'$ running in about the same time as~$A$ with
 \[\AdvPrivOW{\setprim,\mathcal{D}}{A} \leq \AdvPrivSS{\setprim,{\sf
@@
 The theorem follows. \hfill\qed
-\end{proof} \pagebreak[4]
+\end{proof} \pagebreak[1]
 
@@
 
-$\Pi$ is \emph{canonical} if it has a factoring $\Rep_1, \Rep_2, \ell, F$ in which
-$F$ is a pseudorandom function (in which case we call $\Rep_1, \Rep_2, \ell, F$ a canonical factoring of~$\Pi$).
+Informally, we say that $\Pi$ is \emph{canonical} if it has a factoring $\Rep_1, \Rep_2, \ell, F$ in which
+$F$ is a pseudorandom function.
 We next show that any canonical data structure satisfies our simulation-based definition
@@
 Let $\setprim=(\Rep, \Qry)$ have
-canonical factoring
+factoring
 $(\Rep_1, \Rep_2,\ell, F)$. Then for ${\sf leak}(S) = |S|$ and
@@
 (in $G_2$) by definition
-of canonical, and it is clear that the distributions of everything
-else are the same as well.
+of canonical, and it is clear that the joint distribution of everything
+else is the same as well.
 

### 2016-12-13 results.tex
continuing my pass...

@@
 \nudge if $M[h_j] \neq 1$ then Return 0\\
-Return 1 } \caption{{\bf Left:} $\Rep$ and $\Qry$ algorithms for
+Return 1 } \caption{{\bf Left:} $\Rep$ and $\Qry$ algorithms for the
 classical Bloom
   filter $\setprim_{\mathrm{Bloom}}$ in the ROM for a hash function $H\colon \mathbb{N} \times
-  \elts \to [m]$, where $|S| \leq n$. {\bf Right:} $\Rep$ and $\Qry$
+  \elts \to [m]$, where $|S| \leq n$. \jnote{Both should abort if $|S|>n$.}
+  {\bf Right:} $\Rep$ and $\Qry$
   algorithms for the domain-separated PRF data structure
   $\setprim_{\mathrm{ds}}$, using function family $F \colon
-  \calK \times \elts \to [m]$.  Both constructions have query set is $\calQ=\{q_x\colon
+  \calK \times \elts \to [m]$.  Both constructions have query set $\calQ=\{q_x\colon
   \univ \to \bits\}$ where $q_x(S)=1 \Leftrightarrow x \in S$.  }
@@
 Figure~\ref{fig:bf-and-ds} (left side) for sets $S \subseteq \elts$
-of size at most $|S|\leq n$. We define~$\setprim_{\mathrm{Bloom}}$
-in the random-oracle model (ROM), as the traditional analysis of
-correctness (as a function of $n,k,m$) is done in this
-model.\footnote{The standard-model version would have $\Rep$ choose
-$H_1,\ldots,H_k$ from some function family, compute $h_j$ using
-these, and place their description in $\pubaux$.}
+of size at most $|S|\leq n$. \jnote{This should really be
+parameterized everywhere, e.g., as
+$\setprim_{\mathrm{Bloom}}^{k,m,n}$.} We
+define~$\setprim_{\mathrm{Bloom}}$ in the random-oracle model (ROM),
+as the traditional analysis of correctness (as a function of
+$n,k,m$) is done in this model.\footnote{The standard-model version
+would have $\Rep$ choose $H_1,\ldots,H_k$ from some function family,
+compute $h_j$ using these, and place their description in
+$\pubaux$.}
 
@@
 $r \geq 1$ errors (in this case, false-positives).
+
+\jnote{We should state the bound in the theorem in terms of resource
+bounds , rather than in terms of a fixed adversary~$A$ (i.e., bound
+$\Pi_{\mathrm{Bloom},r}(t,q_T, q_H)$ not
+$\Pi_{\mathrm{Bloom},r}(A)$---note we need to define the former in
+the ROM in Section~3). Same goes for all theorems.}
 
@@
 \[
-\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H-1}{r-1}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\AdvCorrect{\setprim_{\mathrm{Bloom}},r}{A} \leq  {\dbinom{q_T + q_H}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
 \]
 \end{theorem}
-Kirsch and Mitzenmacher~\cite{kirsch2006less} show that the ($r=1$,
-zero-query) error-probability
+Note that Kirsch and Mitzenmacher~\cite{kirsch2006less} show that
+the ($r=1$, zero-query) error-probability
 for~$\setprim_\mathrm{Bloom}$ is %always within $O(1/n)$ of
-$(1-e^{-kn/m})^k+O(1/n)$. %, although the asymptotic rate of
-%convergence is faster than~$1/n$.
+$(1-e^{-kn/m})^k+O(1/n)$, though the asymptotic rate of convergence
+is faster than~$1/n$.
 The multiplicative %(``hybrid'')
-term arises as a result of moving from the zero-query to the
-adaptive setting. Also note that $\binom{q_T+q_H-1}{r-1} \leq
-(eq/r)^r$ (letting $q=q_T+q_H$, and assuming $q\gg r$), in which
-case the bound becomes
+term is due to moving from the zero-query to the adaptive setting.
+Also note that $\binom{q_T+q_H}{r} \leq (eq/r)^r$ (letting
+$q=q_T+q_H$), in which case the bound becomes
 \[\left(eq/r \cdot (1-e^{-kn/m})^k + O(q/rn) \right)^r.\]
@@
 \jnote{I didn't find the last two sentences helpful.}
-%JK
 \input{BF_correctness}
 
-\heading{Privacy. }
-Turning to privacy, we observe immediately that the classical BF, in the
-ROM, does not meet our SS-privacy notion when the leakage function
-fails to reveal the entire set~$S$.  This is because the set~$S$ is
-adversarially chosen, and the adversary has access to the random
-oracle, i.e. the hash functions used to make~$\pubaux$.  Thus the
-adversary can simply check that the $\pubaux$ it receives is correct.
-Thus, unless $m,k,n$ are such that the false-positive rate is large,
-the simulator needs to call the random oracle on the points in~$S$ in order to ``fool'' the adversary.
+\heading{Privacy. } We observe that, intuitively, the classical
+Bloom filter does not meet our simulation-based privacy notion
+except in trivial cases (e.g., if the leakage function reveals the
+entire set, the false-positive rate is~1, or the attacker makes no
+$H$-queries). This is because the attacker knows the set~$S$; as
+long as the attacker can compute~$H$ (as it can in the ROM), it can
+simply check that the $\pubaux$ it receives is consistent with~$S$.
 %\tsnote{I'm still not completely comfortable with this.
@@
 This seems likely to me.}
+We note that this will be true for \emph{any} data structure for
+which $\privaux$ is empty, since in that case $\pubaux$ alone
+suffices to evaluate $\Qry(\pubaux,\privaux,\cdot)$. \jnote{In the
+ROM the attack requires that the attacker can query the ROM
+sufficiently many times.}
 
-We note that this will be true for \emph{any} data structure that returns an empty $\privaux$, because this implies that $\pubaux$ alone suffices to evaluate $\Qry(\pubaux,\privaux,\cdot)$.
+On the other hand, we can show that the classical Bloom filter does
+meet our notion of one-wayness in the~ROM:
 
-\begin{theorem}[{\rm OW-privacy of classic BF in the ROM}]\label{thm3}\label{thm:bf-ow}
-Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be the classical Bloom filter data structure over~$\elts$.
-Let $\distr{}{}$ be a distribution over subsets of universe~$\univ=2^\elts$, where $\mu = H_\infty(\distr{}{})$.
-For any adversary~$A$ that makes $q$~queries to its oracle
+\begin{theorem}%[{\rm OW-privacy of classic BF in the ROM}]
+%\label{thm3}
+\label{thm:bf-ow} Fix $k,m,n>0$ and~$\elts$, and let
+$\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be the classical Bloom
+filter data structure over~$\elts$. Let $\distr{}{}$ be a
+distribution over subsets of $\elts$ of size at most~$n$, and let
+$\mu = H_\infty(\distr{}{})$. Then for any adversary~$A$ that makes
+at most $q_H$~queries to~$H$,
 \[
-\AdvPrivOW{\setprim_{\mathrm{Bloom}},\distr{}{},r}{A} \leq  \frac{(kqn+n)}{2^{\mu}}\;.
+\AdvPrivOW{\setprim_{\mathrm{Bloom}},\distr{}{}}{A} \leq  \frac{(kq_H n+n)}{2^{\mu}}\;.
 \]
 \end{theorem}
-The straightforward proof will appear in the full version.
-Loosely, the $kqn/2^{\mu}$ term arises from the chance that random-oracle queries reveal an element of~$S$ (by the random oracle having
-been called on them in the execution of~$\Rep$), and the $n/2^\mu$
-term arises to simple guessing of an element of~$S$ should none of the
-random-oracle queries reveal an element of~$S$.
+\jnote{I don't see how you get the above bound. A gross upper bound
+is obtained by saying that the attacker wins if it ever makes a
+single query $H(\star, x)$ with $x \in S$. The probability of that
+is $q_H/2^\mu$, which is better than $kq_Hn/2^\mu$.} The
+straightforward proof will appear in the full version. Roughly, the
+$kqn/2^{\mu}$ term \jnote{Revisit later.} arises from the event that
+random-oracle queries reveal an element of~$S$, and the $n/2^\mu$
+term represents the probability that the attacker simply guesses an
+element of~$S$.
 
@@
 
-\subsection{Domain-Separated PRF-Hash}
-Next we consider a natural, secret-key variant of the classic Bloom
-filter.  Here the (private) hash functions are instantiated via
-$H(j,x)=F_K(\langle j,x\rangle)$, using domain-separation to turn a
-PRF (with one secret key) into, effectively, multiple functions that
-are computationally indistinguishable from random.  We call this the
-domain-separated PRF-hash data structure.
+\subsection{A Secret-Key Variant of the Bloom Filter}
+Next we consider a natural, secret-key variant of the classical
+Bloom filter where the (private) hash functions are instantiated via
+$H(j,x)=F_K(\langle j,x\rangle)$, where $F$ is a pseudorandom
+function (PRF), using domain separation to turn a PRF into,
+effectively, multiple (independent) random functions. (Refer to the
+right side of Figure~\ref{fig:bf-and-ds}.) We call this the
+\emph{domain-separated PRF data structure}.
+
+\jnote{Maybe just call it ``pseudorandom hash''?}
 
 %\heading{Construction of PRF with domain separation.}
-\heading{Correctness. } Let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$
-be the set-membership data structure defined on the right-hand side
-of Figure~\ref{fig:bf-and-ds}. As in the preceding theorem, the
-following says (informally) that if~$F$ is a secure PRF, then this
-domain-separated PRF construction is correct against adaptive
-adversaries.
+\heading{Correctness. } As in Theorem~\ref{thm3}, the following says
+(informally) that if~$F$ is a PRF, then the domain-separated PRF
+construction enjoys correct against adaptive adversaries.
 
@@
 
-\begin{theorem}[{\rm Correctness of DS-PRF}]\label{thm2}\label{thm:ds-correctness}
-Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-membership data structure (over~$\elts$) in Figure~\ref{fig:bf-and-ds}.
-For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exists a prf-adversary ~$B$ (explicitly constructed in the proof of this theorem) such that
+\jnote{As with the classical BF, this should always be
+parameterized, e.g., as $\setprim_{\mathrm{ds}}^{k,m,n}(F)$.}
+
+\begin{theorem}%[{\rm Correctness of DS-PRF}]
+\label{thm2}\label{thm:ds-correctness} Fix $k,m,n,r>0$ and~$\elts$,
+and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the
+domain-separated PRF data structure over $\elts$. Then
 \[
-\AdvCorrect{\setprim_{\mathrm{ds}},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\AdvCorrect{\setprim_{\mathrm{ds}},r}{t, q_T} \leq  \AdvPRF{F}{O(t+q_T m), q_T}  + {\dbinom{q_T}{r}} \cdot \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
 \]
-Here, $B$ asks $q$ queries, and has time complexity $O(t+qm)$.
 \end{theorem}
-We note that Kirsch and Mitzenmacher~\cite{kirsch2006less} show
-that the ($r=1$, zero-query) error-probability for~$\setprim_\mathrm{ds}$ is
-always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
-rate of convergence is faster than~$1/n$.   As before, the multiplicative term $\binom{q}{r}$ arises when switching from the adaptive to zero-query settings.
+\jnote{I don't think we ever define $\AdvPRF{F}{q, t}$.}
+
+%We note that Kirsch and Mitzenmacher~\cite{kirsch2006less} show
+%that the ($r=1$, zero-query) error-probability for~$\setprim_\mathrm{ds}$ is
+%always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
+%rate of convergence is faster than~$1/n$.   As before, the multiplicative term $\binom{q}{r}$ arises when switching from the adaptive to zero-query settings.
+\jnote{The proof of this theorem should be ``morally the same'' as
+the proof of Theorem~\ref{thm3} (unless I am missing some
+subtlety?). So I think we should omit this proof altogether. If not,
+then it should follow the same structure as the proof of
+Theorem~\ref{thm3} or else the reader is likely to be confused (as I
+was).}
+
 \input{ds-correctness}
 
-\heading{Privacy. }
-The privacy of $\setprim_{\mathrm{ds}}$ follows directly from our general result, Theorem~\ref{thm:priv-ss}.
-\begin{theorem}[\rm{SS-privacy of DS PRF}]\label{thm:ds-ss}
-Fix $k,m,n>0$, a set~$\elts$, and let $\setprim_{\mathrm{ds}}= (\Rep,
-\Qry)$ be the set-membership data structure described in
-Figure~\ref{fig:bf-and-ds}.  For any set~$S \in 2^\elts$, let
-$\leak(S)=|S|$.  There exists a simulator~$\Sim$ and adversary~$B$
-(making~$kn$ queries) such that, for any adversary~$A$
+\heading{Privacy. } In contrast to the case of classical Bloom
+filters (with public hash functions), the domain-separated PRF data
+structure achieves our simulation-based notion of privacy. Indeed,
+this follows directly from Theorem~\ref{thm:priv-ss}.
+
+\begin{theorem}%[\rm{SS-privacy of DS PRF}]
+\label{thm:ds-ss} Fix $k,m,n>0$ and ~$\elts$, and let
+$\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the domain-separated PRF
+data structure.  Let $\leak(S)=|S|$. Then
 \[
-\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}\,.
+\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq
+\AdvPRF{F}{B}\,.
 \]
@@
 \begin{proof}
-It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:priv-ss}.
-On input a set of distinct elements $S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, \ldots, s_k\langle k,x_1\rangle, s_{k+1}=\langle 1,x_2\rangle, \ldots,\linebreak s_{2k}=\langle k,x_2\rangle, \ldots ,s_{kn+1}=\langle 1,x_n\rangle, \ldots, s_{kn}=\langle k,x_n \rangle$.
-On input $n,F_K(s_1),\ldots,\linebreak F_K(s_{kn})$, algorithm $\Rep_2$ simply initializes an all-zero array~$M$ of~$m$-bits, and sets the positions $M[F_K(s_i)]$ to 1.
-It returns~$M$ as $\pubaux$.
+Let $\ell(n) = kn$. Let $\Rep_1$ be the algorithm that, on input a
+set $S=\{x_1,\ldots,x_n\}$, outputs $\{\langle i,x_j \rangle\}_{i\in
+{k}, j \in [n]}$. Let $\Rep_2$ be the algorithm that, on input
+$n,y_1, \ldots, y_{\ell(n)}$, initializes an $m$-bit array $M$ to~0
+and then sets $M[y_i] \gets 1$ for $i \in [\ell(n)]$. One can easily
+verify that $(\Rep_1, \Rep_2, \ell, F)$ is a factoring of~$\Pi$.
+Applying Theorem~\ref{thm:priv-ss} yields the claimed result.
 \hfill\qed
@@
 
+%JK
 \subsection{Linear PRF-hash Bloom Filter }
 %\heading{Linear-PRF construction. }
-The domain-separated PRF-hash requires~$k$ PRF evaluations per set-membership query, and this may be unattractive in certain use cases.
-Kirsch and Mitzenmacher~\cite{kirsch2006less} have shown that two PRF evaluations suffices, defining the hash functions to be $h_i(x)=F_K(\langle 1,x \rangle) + j\cdot F_K(\langle 2,x \rangle) \bmod m$, where~$m$ is the bit-length of the Bloom filter.\footnote{Actually, they define $h_i(x)=F_{K_1}(x)  + j\cdot F_{K_2}(x) \bmod m$, using distinct keys instead of domain-separation, but the constructions are equivalent with respect to security.} We call this the \emph{linear PRF-hash} Bloom Filter.
-In this section, we show that this scheme is both correct and private with respect to our SS notion.
+The domain-separated PRF-hash requires~$k$ PRF evaluations per
+set-membership query, and this may be unattractive in certain use
+cases.  Kirsch and Mitzenmacher~\cite{kirsch2006less} have shown
+that two PRF evaluations suffice, defining the hash functions to be
+$h_i(x)=F_K(\langle 1,x \rangle) + j\cdot F_K(\langle 2,x \rangle)
+\bmod m$, where~$m$ is the bit-length of the Bloom
+filter.\footnote{Actually, they define $h_i(x)=F_{K_1}(x)  + j\cdot
+F_{K_2}(x) \bmod m$, using distinct keys instead of
+domain-separation, but the constructions are equivalent with respect
+to security.} We call this the \emph{linear PRF-hash} Bloom filter.
+\jnote{Maybe call it ``Pairwise-independent hash''?} In this
+section, we show that this scheme is both correct and private.
 
@@
 
-Taken together, the results of this section and the next highlight how sensitive the privacy of linear PRF-hash constructions is to usage.
+Taken together, the results of this section and the next highlight
+the privacy of the linear PRF-hash construction can be sensitive to
+its usage.
 
@@
 Should follow pretty closely the one for ``plain'' linear-PRF.}\tsnote{Actually not sure this is that interesting, but for parallel structure one would want to give it.}
-\heading{Privacy. }
-Consider the set-membership data structure given in Figure~\ref{fig:lin-and-bi-lin} (right side), which we call the \emph{bigram linear-PRF} construction.
-This construction is of practical interest, as it has been suggested as a way to address the privacy-preserving record-linkage problem, in particular for linking common records in medical databases~\cite{niedermeyer2014cryptanalysis,schnell2011novel}.
+\heading{Privacy. } Consider the set-membership data structure given
+in Figure~\ref{fig:lin-and-bi-lin} (right side), which we call the
+\emph{bigram linear-PRF} construction.  This construction is of
+practical interest, as it has been suggested as a way to address the
+privacy-preserving record-linkage problem, in particular for linking
+common records in medical
+databases~\cite{niedermeyer2014cryptanalysis}. %,schnell2011novel}.
 We only address the privacy of this construction, as the correctness
@@
 construction.  The privacy, however, does not.  Here we exhibit an
-efficient SS-privacy attack even when simulator is provided nearly the
-entire set.  Consider the following ``all-but-last'' leakage function.
-On input a set~$S=\{x_1,x_2,\ldots,x_n\}$, it assigns $x'_n \gets
-x_n[1:|x_n|-1]$ and returns
+efficient SS-privacy attack even when simulator is provided nearly
+the entire set.  Consider the following ``all-but-last'' leakage
+function. On input a set~$S=\{x_1,x_2,\ldots,x_n\}$, it assigns
+$x'_n \gets x_n[1:|x_n|-1]$ and returns
 $\mathsf{leak_{abl}}(S)=\{x_1,x_2,\ldots,x'_n\}$.
@@
 On the other hand, we can show that this data structure \emph{is}
-semantically secure with respect to a different leakage function,
-namely, one that leaks the sizes of the intersections of the various
-bigram sets. Specifically, for a set $S$ define ${\sf leak}_\cap(S)$
-via the following algorithm:
+secure with respect to a different leakage function, namely, one
+that leaks the sizes of the intersections of the various bigram
+sets. Specifically, for a set $S$ define ${\sf leak}_\cap(S)$ via
+the following algorithm:
 
@@
 \end{figure}
-Dong, Chen and Wen~\cite{dong2013private} introduce a set-membership data
-structure called a \emph{garbled Bloom filter} (GBF).   Modulo some implementation
-details, a GBF is like a classical Bloom filter, but
-rather than storing a bit 1 at the indices determined by $H_j(x)$, the
-GBF stores xor-shares of~$x$.  Thus, if $x \in S$, then hashing~$x$
-and xoring together the strings stored at the indicated positions
-recovers~$x$. We give the pseudocode for the GBF $\Rep$ and $\Qry$
-algorithms in Figure~\ref{fig:gbf}.
+Dong, Chen and Wen~\cite{CCS:DonCheWen13} introduce a set-membership
+data structure called a \emph{garbled Bloom filter} (GBF).   Modulo
+some implementation details, a GBF is like a classical Bloom filter,
+but rather than storing a bit 1 at the indices determined by
+$H_j(x)$, the GBF stores xor-shares of~$x$.  Thus, if $x \in S$,
+then hashing~$x$ and xoring together the strings stored at the
+indicated positions recovers~$x$. We give the pseudocode for the GBF
+$\Rep$ and $\Qry$ algorithms in Figure~\ref{fig:gbf}.
 
@@
 
-Consider the adversary described in the left half of Figure~\ref{fig:adv-gbf}.  In one
-round of the for-loop, it pics~$k$ positions $i_1,i_2,\ldots,i_k$, and
-xors the strings at these positions to get a candidate~$x$.   If $x
-\in S$, which the adversary knows in the correctness experiment, then
-it moves on to a new set of positions.  If $x \not\in S$ and
-$h_{1}(x)=i_1 \wedge h_2(x)=i_2 \wedge \cdots \wedge h_k(x) = i_k$,
-then it \emph{must be} that $x$ is a false-positive.   Indeed, note
-that the probability of this (in the ROM) is precisely the
-false-positive rate of a classical BF using the same $(k,m,n)$ as the GBF.
+Consider the adversary described in the left half of
+Figure~\ref{fig:adv-gbf}.  In one round of the for-loop, it pics~$k$
+positions $i_1,i_2,\ldots,i_k$, and xors the strings at these
+positions to get a candidate~$x$.   If $x \in S$, which the
+adversary knows in the correctness experiment, then it moves on to a
+new set of positions.  If $x \not\in S$ and $h_{1}(x)=i_1 \wedge
+h_2(x)=i_2 \wedge \cdots \wedge h_k(x) = i_k$, then it \emph{must
+be} that $x$ is a false-positive.   Indeed, note that the
+probability of this (in the ROM) is precisely the false-positive
+rate of a classical Bloom filter using the same $(k,m,n)$ as the
+GBF.
 

### 2016-12-14 BF_correctness.tex
Continuing my pass...

@@
 \begin{figure}[tp]
-\fpage{.9}{
-\hpagessl{.45}{.5}
+\fpage{.8}{
+\hpagessl{.4}{.4}
 {
@@
 $\Ans[y] \gets (1, (v_1, \ldots, v_{k}))$\\
-Return $\left(v_1,\ldots,v_k\right)$
-}
-}
-\caption{Game $\game{4}$ for the
-proof of Theorem~\ref{thm:bf-correctness}.}
-\label{fig:bf-correctness-games2}
+Return $\left(v_1,\ldots,v_k\right)$ } } \caption{Game $\game{4}$
+for the proof of Theorem~\ref{thm:bf-correctness}. \jnote{The
+centering/spacing are not right.}} \label{fig:bf-correctness-games2}
 \end{figure}

### 2016-12-14 ds-correctness.tex
Continuing my pass...

@@
 $\game{0}$--$\game{3}$ for the proof of
-Theorem~\ref{thm:ds-correctness}.} \label{fig:ds-correctness-games}
+Theorem~\ref{thm:ds-correctness}. \jnote{Centering seems off?}} \label{fig:ds-correctness-games}
 \end{figure}
@@
 \nudge When $A$ halts:\\
-\nudge\nudge Return $\bot$ } } \caption{Left: Adversary $B$
+\nudge\nudge Return $\bot$ } } \caption{{\bf Left:} Adversary $B$
 simulating $\game{0}(A)$ and $\game{1}(A)$ respectively for the
-proof of Theorem~\ref{thm:ds-correctness}. Right: Adversary $D$ for
+proof of Theorem~\ref{thm:ds-correctness}. {\bf Right:} Adversary $D$ for
 Theorem~\ref{thm:ds-correctness}.

### 2016-12-14 results.tex
Continuing my pass...

@@
 \begin{theorem}%[\rm{SS-privacy of DS PRF}]
-\label{thm:ds-ss} Fix $k,m,n>0$ and ~$\elts$, and let
+\label{thm:ds-ss} Fix $k,m,n>0$ and~$\elts$, and let
 $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the domain-separated PRF
-data structure.  Let $\leak(S)=|S|$. Then
+data structure over~$\elts$.  Let $\leak(S)=|S|$. Then \jnote{Need
+to rewrite theorem statement.}
 \[
@@
 \begin{proof}
-Let $\ell(n) = kn$. Let $\Rep_1$ be the algorithm that, on input a
+Let $\ell(n) = kn$, let $\Rep_1$ be the algorithm that, on input a
 set $S=\{x_1,\ldots,x_n\}$, outputs $\{\langle i,x_j \rangle\}_{i\in
-{k}, j \in [n]}$. Let $\Rep_2$ be the algorithm that, on input
+{k}, j \in [n]}$, and let $\Rep_2$ be the algorithm that, on input
 $n,y_1, \ldots, y_{\ell(n)}$, initializes an $m$-bit array $M$ to~0
 and then sets $M[y_i] \gets 1$ for $i \in [\ell(n)]$. One can easily
-verify that $(\Rep_1, \Rep_2, \ell, F)$ is a factoring of~$\Pi$.
-Applying Theorem~\ref{thm:priv-ss} yields the claimed result.
-\hfill\qed
+verify that $(\Rep_1, \Rep_2, \ell, F)$ is a factoring
+of~$\Pi_{\mathrm{ds}}$. Applying Theorem~\ref{thm:priv-ss} yields
+the claimed result. \hfill\qed
 \end{proof}
@@
 \caption{{\bf Left:} $\Rep$ and $\Qry$ algorithms for the linear-PRF
-  data structure $\setprim_{\mathrm{lin}}$ {\bf Right:}
-The scheme from Niedermeyer et al.\cite{niedermeyer2014cryptanalysis}, $\setprim_{\bilin}$.
-The $\mathsf{bigram}$ algorithm takes a
-string~$x=x_1,x_2,\ldots,x_\ell$ as input, and returns the set of
-bigrams for the left- and right-padded string $\sqcup x \sqcup$,
-i.e. $\{\sqcup x_1, x_1x_2,\ldots,x_{\ell-1}x_\ell,x_\ell\sqcup\}$.
-Both schemes use a function family $F\colon \calK \times \bits^* \to [m]$.
-}\label{fig:lin-and-bi-lin}
-\label{fig:niedermeyer}
+  data structure $\setprim_{\mathrm{lin}}$. {\bf Right:}
+Data structure $\setprim_{\bilin}$ from Niedermeyer et
+al.~\cite{niedermeyer2014cryptanalysis}. The $\mathsf{bigram}$
+algorithm takes a string~$x=x_1,x_2,\ldots,x_\ell$ as input, and
+returns the set of bigrams for the left- and right-padded string
+$\sqcup x \sqcup$, i.e. $\{\sqcup x_1,
+x_1x_2,\ldots,x_{\ell-1}x_\ell,x_\ell\sqcup\}$. Both schemes use a
+function family $F\colon \calK \times \bits^* \to [m]$.
+}\label{fig:lin-and-bi-lin} \label{fig:niedermeyer}
 \end{figure}
 
-%JK
 \subsection{Linear PRF-hash Bloom Filter }
 %\heading{Linear-PRF construction. }
-The domain-separated PRF-hash requires~$k$ PRF evaluations per
-set-membership query, and this may be unattractive in certain use
-cases.  Kirsch and Mitzenmacher~\cite{kirsch2006less} have shown
-that two PRF evaluations suffice, defining the hash functions to be
-$h_i(x)=F_K(\langle 1,x \rangle) + j\cdot F_K(\langle 2,x \rangle)
-\bmod m$, where~$m$ is the bit-length of the Bloom
-filter.\footnote{Actually, they define $h_i(x)=F_{K_1}(x)  + j\cdot
-F_{K_2}(x) \bmod m$, using distinct keys instead of
-domain-separation, but the constructions are equivalent with respect
-to security.} We call this the \emph{linear PRF-hash} Bloom filter.
-\jnote{Maybe call it ``Pairwise-independent hash''?} In this
-section, we show that this scheme is both correct and private.
 
-Looking ahead to the next section, we will analyze a closely related
-construction, which was attacked by Niedermeyer et
-al.~\cite{niedermeyer2014cryptanalysis} in the context of private
-medical-record linkage.  It uses the same linear-PRF hash functions,
-but has a $\Rep$ algorithm that that does not ensure that the hash
-functions are called on \emph{distinct} values.  We show that this is
-\emph{not} private with respect to our SS notion for a leakage
-function that leaks nearly the entire set~$S$.
+\jnote{The BF, DS-PRF, and Linear PRF data structures are all the
+same underlying construction but using different instantiations of
+the hash functions. Can we just express them all as, e.g.,
+$\Pi_{BF}(H_1, \ldots, H_k)$ with different choices for the~$H$'s?
+Similarly, the names should be consistent; maybe ``RO Bloom
+filter,'' ``independent-PRF Bloom filter,'' and
+``pairwise-independent-PRF Bloom filter''?}
+
+The domain-separated PRF data structure requires~$k$ PRF evaluations
+per set-membership query.  Kirsch and
+Mitzenmacher~\cite{kirsch2006less} studied a variant, which uses
+just two PRF evaluations per query, in which the indices $h_j$ of
+the array that get set for a given element $x$ are (essentially)
+computed as $h_j = F_K(\langle 1,x \rangle) + j\cdot F_K(\langle 2,x
+\rangle) \bmod m$ (where $m$ is the length of the array); see
+Figure~\ref{fig:lin-and-bi-lin} (left side).
+%shown that two PRF evaluations suffice, defining the hash functions
+%to be $h_i(x)=F_K(\langle 1,x \rangle) + j\cdot F_K(\langle 2,x
+%\rangle) \bmod m$, where~$m$ is the bit-length of the Bloom
+%filter.\footnote{Actually, they define $h_i(x)=F_{K_1}(x)  + j\cdot
+%F_{K_2}(x) \bmod m$, using distinct keys instead of
+%domain-separation, but the constructions are equivalent with respect
+%to security.}
+We call this the \emph{linear PRF-hash} Bloom filter, and denote it
+by $\setprim_{\mathrm{lin}}$. \jnote{Maybe call it
+``Pairwise-independent hash''?} In this section, we show that this
+scheme is both correct and private.
+
+\jnote{I was not happy with the paragraph contrasting these results
+with those of the next section. The attack on by Niedermeyer has
+nothing to do with the hash functions used; it is due to the fact
+that they work on bigrams.}
+%Looking ahead, in the next section we
+%will analyze a closely related construction that was attacked by
+%Niedermeyer et al.~\cite{niedermeyer2014cryptanalysis}. That
+%construction computes indices $h_j$ in the same way, but does not
+%ensure that $F$ is evaluated on \emph{distinct} values; that
+%construction is \emph{not} private.
 %\todo{It would be better, perhaps, to show that it is not OW secure, since this implies it isn't SS secure, and OW security is what Niedermeyer et al. violate.}
+%This illustrates that the privacy of the linear PRF-hash
+%construction can be sensitive to its usage.
 
-Taken together, the results of this section and the next highlight
-the privacy of the linear PRF-hash construction can be sensitive to
-its usage.
+\heading{Correctness. } The following result shows, informally, that
+if~$F$ is a good PRF, then $\setprim_{\mathrm{lin}}$ is correct
+against adaptive error-finding adversaries.
 
-\heading{Correctness. }
-For now, let $n,k,m \geq 0$.
-Then $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ is defined as in Figure~\ref{fig:lin-and-bi-lin} (left side).
-The following result shows, informally, that if~$F$ is a good PRF, then $\setprim_{\mathrm{lin}}$ is correct against adaptive error-finding adversaries.
+\jnote{Again, the theorem should not refer to specific adversaries,
+but should instead refer to given resource bounds.}
 
-\begin{theorem}[{\rm Correctness of linear-PRF}]\label{thm1}\label{thm:lin-correctness}
-Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-membership data structure (over~$\elts$) described in Figure~\ref{fig:lin-and-bi-lin}.
-For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exist prf-adversaries~$B_1,B_2$ (explicitly constructed in the proof of this theorem) such that
+\begin{theorem}%[{\rm Correctness of linear-PRF}]
+\label{thm1}\label{thm:lin-correctness} Fix $k,m,n,r>0$ and~$\elts$,
+and let $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the
+set-membership data structure over~$\elts$.  For any adversary~$A$
+that makes a total of~$q_T$ queries to its $\Test$ oracle and runs
+in time~$t$, there exist~$B_1,B_2$ such that
 \[
-\AdvCorrect{\setprim_{\mathrm{lin}},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
+\AdvCorrect{\setprim_{\mathrm{lin}},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \cdot \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
 \]
-Here, $B_1$ and $B_2$, each ask~$q$ oracle queries and have time complexity~$O(t+qm)$.
+Here, $B_1$ and $B_2$ each ask~$q$ oracle queries and run in
+time~$O(t+qm)$.
 \end{theorem}
-Again, Kirsch and Mitzenmacher~\cite{kirsch2006less} show
-that the ($r=1$, zero-query) error-probability for~$\setprim_\mathrm{lin}$ is
-always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
-rate of convergence is faster than~$1/n$.
-the multiplicative term $\binom{q}{r}$ arises when switching from the adaptive to zero-query settings.
-The proof will appear in the full version, but we note that it very
-closely follows the proof of correctness for the DS PRF-hash
-construction, Theorem~\ref{thm:ds-correctness}.
+Kirsch and Mitzenmacher~\cite{kirsch2006less} show that the ($r=1$,
+zero-query) error-probability for~$\setprim_\mathrm{lin}$ is always
+within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic rate
+of convergence is faster than~$1/n$; the multiplicative term
+$\binom{q}{r}$ arises due to switching from the zero-query setting
+to the adaptive setting. A proof of the above will appear in the
+full version, but we remark that it closely follows the proof of
+Theorem~\ref{thm:bf-correctness}.
 %\input{lin-correctness}
 
-\heading{Privacy. }
-The SS-privacy of the linear-PRF hash construction follows directly from~Theorem~\ref{thm:priv-ss}.
-\begin{theorem}[{\rm SS-privacy of linear-PRF}]\label{thm:lin-privacy}
-Fix $k,m,n,r>0$, a set $\elts$, and let $\setprim_{\mathrm{lin}}=
-(\Rep, \Qry)$ be the set-membership data structure (over~$\elts$)
-described in Figure~\ref{fig:lin-and-bi-lin}. For any set~$S \in
-2^{\elts}$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ and
-an adversary~$B$ (making $2n$ queries) such that, for any adversary~$A$
+\heading{Privacy. } Simulation-based privacy of the linear PRF-hash
+construction follows from~Theorem~\ref{thm:priv-ss}.
+
+\begin{theorem}%[{\rm SS-privacy of linear-PRF}]
+\label{thm:lin-privacy} Fix $k,m,n>0$ and $\elts$, and let
+$\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-membership data
+structure over~$\elts$. Let $\leak(S)=|S|$.  Then \jnote{Need to
+rewrite theorem statement.}
 \[
@@
 \begin{proof}
-It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:priv-ss}.
-On input a set of distinct elements
-$S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, s_3 = \langle 1,x_2\rangle, s_4=\langle 2,x_2 \rangle,\ldots,\linebreak s_{2n-1}=\langle 1,x_n \rangle, s_{2n}=\langle 2,x_n \rangle$.
-
-On input $n,F_K(s_1),F_K(s_2),\ldots,F_K(s_{2n-1}) , F_K(s_{2n})$, algorithm $\Rep_2$ initializes an all-zero array~$M$ of~$m$-bits, and sets the positions $M[F_K(s_i)+j\cdot F_K(s_{i+1})\bmod m]$ to 1, for each $j \in [k]$.
-It returns~$M$ as $\pubaux$.
-\hfill\qed
+Let $\ell(n) = 2n$, let $\Rep_1$ be the algorithm that, on input a
+set $S=\{x_1,\ldots,x_n\}$, outputs $\{\langle b,x_i \rangle\}_{b\in
+\{1,2\}, i \in [n]}$, and let $\Rep_2$ be the algorithm that, on
+input $n,y_{1,1}, y_{2,1}, \ldots, y_{1,n}, y_{2,n}$,  initializes
+an $m$-bit array $M$ to~0 and then sets $M[y_{1,i}+j \cdot y_{2,i}
+\bmod m] \gets 1$ for $i \in [n]$ and $j \in [k]$. One can easily
+verify that $(\Rep_1, \Rep_2, \ell, F)$ is a factoring
+of~$\Pi_{\mathrm{ds}}$. Theorem~\ref{thm:priv-ss} yields the claimed
+result. \hfill\qed
 \end{proof}
 
+%JK
 %%%%%%%%%%%%%%%%% BIGRAM LINEAR-PRF (AKA "NIEDERMEYER")  %%%%%%%%%%%%%%%%%%%%
@@
 Should follow pretty closely the one for ``plain'' linear-PRF.}\tsnote{Actually not sure this is that interesting, but for parallel structure one would want to give it.}
-\heading{Privacy. } Consider the set-membership data structure given
-in Figure~\ref{fig:lin-and-bi-lin} (right side), which we call the
+Consider the set-membership data structure given in
+Figure~\ref{fig:lin-and-bi-lin} (right side), which we call the
 \emph{bigram linear-PRF} construction.  This construction is of
@@
 databases~\cite{niedermeyer2014cryptanalysis}. %,schnell2011novel}.
-We only address the privacy of this construction, as the correctness
-follows immediately from the correctness of the Linear-PRF
-construction.  The privacy, however, does not.  Here we exhibit an
-efficient SS-privacy attack even when simulator is provided nearly
-the entire set.  Consider the following ``all-but-last'' leakage
-function. On input a set~$S=\{x_1,x_2,\ldots,x_n\}$, it assigns
-$x'_n \gets x_n[1:|x_n|-1]$ and returns
+\jnote{We should really give more discussion, explaining the goal of
+``privacy-preserving record linkage'' and describing the protocol
+(at a high level).}
+
+\heading{Privacy. } We only address the privacy of this
+construction, as the correctness follows immediately from the
+correctness of the Linear-PRF construction.  The privacy, however,
+does not.  Here we exhibit an efficient SS-privacy attack even when
+simulator is provided nearly the entire set.  Consider the following
+``all-but-last'' leakage function. On input a
+set~$S=\{x_1,x_2,\ldots,x_n\}$, it assigns $x'_n \gets
+x_n[1:|x_n|-1]$ and returns
 $\mathsf{leak_{abl}}(S)=\{x_1,x_2,\ldots,x'_n\}$.

### 2016-12-16 intro.tex
no message

@@
 
-\heading{Formalizing abstract data structures.} Loosely speaking, we
-formalize a data structure as a pair of algorithms $(\Rep,\Qry)$,
+\heading{Formalizing abstract data structures. } Loosely speaking,
+we formalize a data structure as a pair of algorithms $(\Rep,\Qry)$,
 the representation and query-evaluation algorithms, respectively.
@@
 
-\heading{Case studies.} The example above offers a hint at the broad
-range of abstract data structures our syntax supports.  In this
-paper, we put the syntax and our security notions to work in several
-case studies.  First, we analyze classical Bloom filters when the
-hash functions are modeled as public random
+\heading{Case studies. } The example above offers a hint at the
+broad range of abstract data structures our syntax supports.  In
+this paper, we put the syntax and our security notions to work in
+several case studies.  First, we analyze classical Bloom filters
+when the hash functions are modeled as public random
 oracles~\cite{broder2004network}, when the hash functions are
@@
 
-\heading{Related work.}
+\heading{Related work. }
 \input{related-work}

### 2016-12-16 results.tex
no message

@@
 \centering
-\hfpagess{.5}{.5}
+\hfpagess{.45}{.45}
 {
@@
 \medskip
-\algorithmv{$\Qry(\pubaux,\privaux)$}\\
+\algorithmv{$\Qry(\pubaux,\privaux, q_x)$}\\
 $M\gets\pubaux$, $K \gets \privaux$\\
-%\jnote{Fix}\tsnote{Fix what?} \\
 $f_1 \gets F_{K}(\langle 1,x \rangle)$, $f_2 \gets F_{K}(\langle 2,x \rangle)$\\
@@
 \algorithmv{$\Rep(S)$}\\
-$\pubaux \gets \emptystring$\\
-$K_1,K_2, \getsr \calK$\\
+$\pubaux \gets \emptystring$; $K \getsr \calK$\\
 for each $x \in S$\\
@@
 \nudge\nudge $f_1 \gets F_{K}(\langle 1,b \rangle)$, $f_2 \gets F_{K}(\langle 2,b \rangle)$\\
-\nudge\nudge for $j \in [k]$\\
-\nudge\nudge\nudge $i \gets f_1+j\cdot f_2 \bmod m$\\
-\nudge\nudge\nudge $M_x[i] \gets 1$\\
+\nudge\nudge for $j \in \{1, 2, \ldots, k\}$\\
+\nudge\nudge\nudge $h_j \gets f_1+j\cdot f_2 \bmod m$\\
+\nudge\nudge\nudge $M_x[h_j] \gets 1$\\
 \nudge $\pubaux \gets \langle\pubaux, M_x \rangle$\\
-$\privaux \gets \langle K_1,K_2 \rangle$\\
+$\privaux \gets \langle K \rangle$\\
 Return $(\pubaux,\privaux)$\\
@@
 $B \gets \mathsf{bigram}(x)$\\
-$\overline{M} \gets 0^m$\\
+$M_x \gets 0^m$\\
 for each $b \in B$\\
-\nudge for $j \in [k]$\\
-\nudge\nudge $f_1 \gets F_{K}(\langle 1,b \rangle)$, $f_2 \gets F_{K}(\langle 2,b \rangle)$\\
-\nudge\nudge $i \gets f_1+j\cdot f_2 \bmod m$\\
-\nudge\nudge $\overline{M}[i] \gets 1$\\
-if $\overline{M} \in \pubaux$ then Return 1 \\
+\nudge $f_1 \gets F_{K}(\langle 1,b \rangle)$, $f_2 \gets F_{K}(\langle 2,b \rangle)$\\
+\nudge for $j \in \{1, 2, \ldots, k\}$\\
+\nudge\nudge $h_j \gets f_1+j\cdot f_2 \bmod m$\\
+\nudge\nudge $M_x[h_j] \gets 1$\\
+if $M_x \in \pubaux$ then Return 1 \\
 Return 0
@@
 Data structure $\setprim_{\bilin}$ from Niedermeyer et
-al.~\cite{niedermeyer2014cryptanalysis}. The $\mathsf{bigram}$
+al.~\cite{niedermeyer2014cryptanalysis}. \jnote{Can we not describe
+this in terms of $\setprim_{\mathrm{lin}}$?} The $\mathsf{bigram}$
 algorithm takes a string~$x=x_1,x_2,\ldots,x_\ell$ as input, and
-returns the set of bigrams for the left- and right-padded string
+returns the set of bigrams for the left-and-right-padded string
 $\sqcup x \sqcup$, i.e. $\{\sqcup x_1,
@@
 
-%JK
 %%%%%%%%%%%%%%%%% BIGRAM LINEAR-PRF (AKA "NIEDERMEYER")  %%%%%%%%%%%%%%%%%%%%
@@
 Figure~\ref{fig:lin-and-bi-lin} (right side), which we call the
-\emph{bigram linear-PRF} construction.  This construction is of
-practical interest, as it has been suggested as a way to address the
-privacy-preserving record-linkage problem, in particular for linking
-common records in medical
+\emph{bigram linear-PRF} construction. \jnote{Really a bad
+name\ldots} This construction is of interest as it has been
+suggested as a way to address the privacy-preserving record-linkage
+problem, in particular for linking common records in medical
 databases~\cite{niedermeyer2014cryptanalysis}. %,schnell2011novel}.
-\jnote{We should really give more discussion, explaining the goal of
+\jnote{We should really give more discussion, explaining the data
+structure in words, and also discussing the goal of
 ``privacy-preserving record linkage'' and describing the protocol
-(at a high level).}
+for doing so (at a high level).}
 
@@
 construction, as the correctness follows immediately from the
-correctness of the Linear-PRF construction.  The privacy, however,
-does not.  Here we exhibit an efficient SS-privacy attack even when
-simulator is provided nearly the entire set.  Consider the following
+correctness of the linear PRF-hash construction. \jnote{Well, with
+some loss of parameters.} The privacy, however, does not.
+%JK
+Here we
+exhibit an efficient SS-privacy attack even when simulator is
+provided nearly the entire set. Consider the following
 ``all-but-last'' leakage function. On input a

### 2016-12-19 results.tex
no message

@@
 $\binom{q}{r}$ arises due to switching from the zero-query setting
-to the adaptive setting. A proof of the above will appear in the
-full version, but we remark that it closely follows the proof of
-Theorem~\ref{thm:bf-correctness}.
+to the adaptive setting. A proof of the above closely follows the
+proof of Theorem~\ref{thm:bf-correctness}, and will appear in the
+full version.
 %\input{lin-correctness}
@@
 \heading{Privacy. } Simulation-based privacy of the linear PRF-hash
-construction follows from~Theorem~\ref{thm:priv-ss}.
+construction follows from~Theorem~\ref{thm:priv-ss}:
 
@@
 Should follow pretty closely the one for ``plain'' linear-PRF.}\tsnote{Actually not sure this is that interesting, but for parallel structure one would want to give it.}
-Consider the set-membership data structure given in
-Figure~\ref{fig:lin-and-bi-lin} (right side), which we call the
-\emph{bigram linear-PRF} construction. \jnote{Really a bad
-name\ldots} This construction is of interest as it has been
-suggested as a way to address the privacy-preserving record-linkage
-problem, in particular for linking common records in medical
-databases~\cite{niedermeyer2014cryptanalysis}. %,schnell2011novel}.
-\jnote{We should really give more discussion, explaining the data
-structure in words, and also discussing the goal of
+
+The set-membership data structure given on the right-hand side of
+Figure~\ref{fig:lin-and-bi-lin}, which we call the \emph{bigram
+linear-PRF} construction \jnote{Really a bad name\ldots}, was
+suggested as a way to allow for privacy-preserving
+linkage of medical records~\cite{niedermeyer2014cryptanalysis}. %,schnell2011novel}.
+\jnote{We should really give more discussion, explaining what the
+data structure does in words, and also discussing the goal of
 ``privacy-preserving record linkage'' and describing the protocol
-for doing so (at a high level).}
+for doing so (at a high level).} We only address the privacy of this
+construction, as the correctness follows immediately from the
+correctness of the linear PRF-hash construction. \jnote{Actually, it
+seems worth giving a proof of correctness just to get the parameters
+right.}
 
-\heading{Privacy. } We only address the privacy of this
-construction, as the correctness follows immediately from the
-correctness of the linear PRF-hash construction. \jnote{Well, with
-some loss of parameters.} The privacy, however, does not.
-%JK
-Here we
-exhibit an efficient SS-privacy attack even when simulator is
-provided nearly the entire set. Consider the following
-``all-but-last'' leakage function. On input a
-set~$S=\{x_1,x_2,\ldots,x_n\}$, it assigns $x'_n \gets
-x_n[1:|x_n|-1]$ and returns
-$\mathsf{leak_{abl}}(S)=\{x_1,x_2,\ldots,x'_n\}$.
+\heading{Privacy. }  Unfortunately, and in contrast to the linear
+PRF-hash construction on which it is based, the scheme does not
+achieve our simulation-based notion of privacy. In fact, we show
+that it fails severely: roughly, even a simulator given everything
+but the last character of one of the strings in~$S$ cannot simulate
+the public output.
 
-\begin{figure}[tp]
-\centering
-\fpage{.65}
-{
-\adversaryv{$A$}\\[1ex]
-On input $\emptystring$:\\
-\nudge $x_1 \gets \mathrm{cab}$\\
-\nudge $x_2 \gets \mathrm{bab}$\\
-\nudge $z \getsr \bits$\\
-\nudge if $z=1$ then $x_3 \gets \mathrm{caba}$\\
-\nudge else $x_3 \gets \mathrm{cabc}$\\
-\nudge Return $S=\{x_1,x_2,x_3\}$\\
-On input $\pub \neq \emptystring$:\\
-\nudge $M_1,M_2,M_3 \gets \pub$\\
-\nudge $M_{1,2} \gets M_1 \vee M_2$\\
-\nudge if $z=1 \wedge \left(3k < \mathsf{hamming}(M_{1,2} \wedge M_3) = 4k\right)$ then \\
-\nudge\nudge Return 1 \\
-\nudge if $z=0 \wedge \left(\mathsf{hamming}(M_{1,2} \wedge M_3) \leq 3k\right)$ then \\
-\nudge\nudge Return 1 \\
-\nudge Return 0
-}
-\caption{Adversary for Theorem~\ref{thm:bi-lin-ss}. The function $\mathsf{hamming}(M)$ returns the hamming weight of~$M$.}
-\label{fig:adv-bi-lin-ss}
-\end{figure}
+%\begin{figure}[tp]
+%\centering
+%\fpage{.65}
+%{
+%\adversaryv{$A$}\\[1ex]
+%On input $\emptystring$:\\
+%\nudge $x_1 \gets \mathrm{cab}$\\
+%\nudge $x_2 \gets \mathrm{bab}$\\
+%\nudge $z \getsr \bits$\\
+%\nudge if $z=1$ then $x_3 \gets \mathrm{caba}$\\
+%\nudge else $x_3 \gets \mathrm{cabc}$\\
+%\nudge Return $S=\{x_1,x_2,x_3\}$\\
+%On input $\pub \neq \emptystring$:\\
+%\nudge $M_1,M_2,M_3 \gets \pub$\\
+%\nudge $M_{1,2} \gets M_1 \vee M_2$\\
+%\nudge if $z=1 \wedge \left(3k < \mathsf{hamming}(M_{1,2} \wedge M_3) = 4k\right)$ then \\
+%\nudge\nudge Return 1 \\
+%\nudge if $z=0 \wedge \left(\mathsf{hamming}(M_{1,2} \wedge M_3) \leq 3k\right)$ then \\
+%\nudge\nudge Return 1 \\
+%\nudge Return 0
+%}
+%\caption{Adversary for Theorem~\ref{thm:bi-lin-ss}. The function $\mathsf{hamming}(M)$ returns the hamming weight of~$M$.}
+%\label{fig:adv-bi-lin-ss}
+%\end{figure}
 
-\begin{theorem}[{\rm SS-privacy of bigram linear-PRF}]\label{thm:bi-lin-ss}
-Let $\setprim_{\bilin}= (\Rep, \Qry)$ be the set-membership data
-structure described in Figure~\ref{fig:lin-and-bi-lin}, but with
-$F_{K}$ replaced by a random function~$\rho$. Let
-$\leak_{\mathsf{abl}}$ be the leakage function just described.
-Let~$\elts=\{\mathrm{a,b,c}\}^*$. Let $n=3$,  $m=3\alpha $ for
-integer $\alpha >> 1$, and let, $k = \lceil \ln(2) \alpha
-\rceil$.\footnote{This value of~$k$ is from the classical analysis for
-minimizing the FP rate for a Bloom filter, and is set this way for
-compatibility with classical results.  It isn't used in any
-essential way in the proof sketch.}  Let~$A$ be the adversary in
-Figure~\ref{fig:adv-bi-lin-ss}.  Then for any simulator $\Sim$, the
-advantage
-$\AdvPrivSS{\setprim_{\bilin},\leak_{\mathsf{abl}}}{A,\Sim}$ can be
-made arbitrarily close to $1/2$ by choice of~$\alpha$.
-\end{theorem}
+\jnote{Give intuition for why the attack works: the same ``hash
+functions'' are used for each ``Bloom filter,'' and this leaks
+information about bigrams shared among multiple strings.} \jnote{I
+simplified the attack.}
+
+Formally, consider sets of strings over $\bool$, and fix the leakage
+function $\leak_{\mathsf{abl}}$ defined by
+\[\leak_{\mathsf{abl}}(\{x_1, \ldots, x_n\}) = \{x_1, \ldots, x_{n-1},
+x'_n\},\] where $x_n$ is the lexicographically last string in the
+given set, and $x'_n$ is equal to $x_n$ with the last bit removed.
+Define an attacker $A$ as follows: it chooses a uniform bit~$b$; if
+$b=0$ then it outputs the set $S=\{1,111\}$, and if $b=1$ then it
+outputs the set $S=\{1, 101\}$. Next, given public information $\pub
+= \langle M_1, M_2 \rangle$ (where $M_2$ is the array with more bits
+set to~1), it counts the number of positions set to~1 in $M_2$ that
+are not set to~1 in~$M_1$. If this number is strictly greater
+than~$k$, then $A$ outputs~1; otherwise, it outputs~0.
+
+In analyzing the behavior of $A$, note first that $\Rep$ begins by
+mapping each of the strings in $S$ to their respective bigram sets,
+namely, $\{\sqcup 1, 1\sqcup\}$ for the first string, and either
+$\{\sqcup 1, 11, 1\sqcup\}$ or $\{\sqcup 1, 10, 01, 1\sqcup\}$ for
+the second string. It then produces the $m$-bit arrays $M_1, M_2$.
+Because the bigram set for the second string is, in either case, a
+strict superset of the bigram set for the first string, $M_2$ (which
+is the array with more bits set to~1) always corresponds to the
+second string.
+
+Now, when $b=0$ the bigram set for the second string contains
+exactly one more element than the bigram set for the first string,
+and so the number of positions set to~1 in $M_2$ that are \emph{not}
+set to~1 in $M_1$ is at most~$k$. On the other hand, when $b=1$ the
+bigram set for the second string contains exactly two more elements
+than the bigram set for the first string, and so with high
+probability the number of positions set to~1 in $M_2$ that are not
+set to~1 in $M_1$ exceeds~$k$. (Specifically, in the worst case
+there are $2k$ positions---call them~$I$---set to~1 in $M_1$, and
+then the number in question exceeds~$k$ as long as a strict majority
+of the $2k$ positions set to~1 by the extra bigrams $10, 01$ lie
+outside of~$I$. Pairwise independence of those $2k$ positions can be
+used to bound this probability. If $k\geq 4$ and $2k/m \leq 1/4$,
+this probability is at least %JK
+
+ implies that this happens except with
+probability at most $(4 \cdot (\frac{1}{2}- \leq 1/2$.)
+
+%\begin{theorem}%[{\rm SS-privacy of bigram linear-PRF}]
+%\label{thm:bi-lin-ss}
+%Let~$\elts=\{\mathrm{a,b,c}\}^*$. Let $n=3$,  $m=3\alpha $ for
+%integer $\alpha \gg 1$, and let, $k = \lceil \ln(2) \alpha
+%\rceil$.\footnote{This value of~$k$ is from the classical analysis
+%for minimizing the FP rate for a Bloom filter, and is set this way
+%for compatibility with classical results.  It isn't used in any
+%essential way in the proof sketch.}  Let~$A$ be the adversary in
+%Figure~\ref{fig:adv-bi-lin-ss}.  Then for any simulator $\Sim$, the
+%advantage
+%$\AdvPrivSS{\setprim_{\bilin},\leak_{\mathsf{abl}}}{A,\Sim}$ can be
+%made arbitrarily close to $1/2$ by choice of~$\alpha$.
+%\end{theorem}
 \begin{proof}%\tsnote{still a bit sketchy but believable}
-On input the set~$S$ produced by~$A$, the $\Rep$ algorithm turns $x_1=$'cab', $x_2=$'bab' and $x_3$ into their respective bigram sets: $B_{x_1}=\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{b}\sqcup\}$, $B_{x_2}=\{\sqcup\mathrm{b},\mathrm{ba},\mathrm{ab}, \mathrm{b}\sqcup \}$; the set $B_{x_3}$ will be either $\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{ba}, \mathrm{a}\sqcup\}$, or $\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{bc}, \mathrm{c}\sqcup\}$, each with probability 1/2.
-It then produces $\alpha$-bit arrays $M_1, M_2, M_3$ by hashing the corresponding bigram sets using the hash functions $h_j(s)=\rho_1(s)+ j\rho_2(s) \bmod m$.
-Note that for sufficiently large~$m$, each of $M_1,M_2$ will contain exactly $4k$ positions set to 1; this is with overwhelming probability, up to collisions in the hash functions for different bigrams within a given bigram set.
-Likewise, $M_{1,2}=M_1 \vee M_2$ will have exactly $6k$ positions set to 1, because $B_{x_1}$ and $B_{x_2}$ share $\mathrm{ab}$ and $\mathrm{a}\sqcup$.
-
-In the case that $B_{x_3}=\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{ba}, \mathrm{a}\sqcup\}$, only one of its elements ($\mathrm{a}\sqcup$) is not in either of $B_{x_1},B_{x_2}$.
-Hence, the hamming weight of $M_{1,2}\wedge M_3$ will be $4k$.
-On the other hand, when $B_{x_3} = \{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{bc}, \mathrm{c}\sqcup\}$, two of its elements ($\mathrm{bc}, \mathrm{c}\sqcup$) are not covered by $B_{x_1},B_{x_2}$.
-In this case, the hamming weight of $M_{1,2} \wedge M_3$ will be $3k$.
-Thus $\ExpPrivSSreal{\setprim_{\bilin}}{A}=1$ with overwhelming probability.
-
-On the other hand, the simulator~$\Sim$ is given 'cab','bab','cab' as
-input.  It can perfectly simulate $M_1,M_2$ by lazily sampling random
-function~$\rho$ itself.  However, it has no information about the
-bit~$z$, so at best it can cause~$A$ to output 1 with
-probability~$1/2$.  That is $\ExpPrivSSsim{\setprim_{\bilin}}{A,\Sim} \leq 1/2$. \hfill\qed
+On the other hand, the simulator~$\Sim$ is given 'cab','bab','cab'
+as input.  It can perfectly simulate $M_1,M_2$ by lazily sampling
+random function~$\rho$ itself.  However, it has no information about
+the bit~$z$, so at best it can cause~$A$ to output 1 with
+probability~$1/2$.  That is
+$\ExpPrivSSsim{\setprim_{\bilin}}{A,\Sim} \leq 1/2$. \hfill\qed
 \end{proof}

### 2016-12-20 results.tex
still doing a pass...

@@
 linear-PRF} construction \jnote{Really a bad name\ldots}, was
-suggested as a way to allow for privacy-preserving
-linkage of medical records~\cite{niedermeyer2014cryptanalysis}. %,schnell2011novel}.
-\jnote{We should really give more discussion, explaining what the
-data structure does in words, and also discussing the goal of
-``privacy-preserving record linkage'' and describing the protocol
-for doing so (at a high level).} We only address the privacy of this
-construction, as the correctness follows immediately from the
-correctness of the linear PRF-hash construction. \jnote{Actually, it
-seems worth giving a proof of correctness just to get the parameters
-right.}
+suggested as a way to allow for privacy-preserving linkage of
+medical records~\cite{schnell2011novel}. \jnote{We should really
+give more discussion, explaining what the data structure does in
+words, and also discussing the goal of ``privacy-preserving record
+linkage'' and describing the protocol for doing so (at a high
+level).} We only address the privacy of this construction, as the
+correctness follows immediately from the correctness of the linear
+PRF-hash construction. \jnote{Actually, it seems worth giving a
+proof of correctness just to get the parameters right.}
 
@@
 
-Formally, consider sets of strings over $\bool$, and fix the leakage
-function $\leak_{\mathsf{abl}}$ defined by
-\[\leak_{\mathsf{abl}}(\{x_1, \ldots, x_n\}) = \{x_1, \ldots, x_{n-1},
-x'_n\},\] where $x_n$ is the lexicographically last string in the
-given set, and $x'_n$ is equal to $x_n$ with the last bit removed.
-Define an attacker $A$ as follows: it chooses a uniform bit~$b$; if
-$b=0$ then it outputs the set $S=\{1,111\}$, and if $b=1$ then it
-outputs the set $S=\{1, 101\}$. Next, given public information $\pub
-= \langle M_1, M_2 \rangle$ (where $M_2$ is the array with more bits
-set to~1), it counts the number of positions set to~1 in $M_2$ that
-are not set to~1 in~$M_1$. If this number is strictly greater
-than~$k$, then $A$ outputs~1; otherwise, it outputs~0.
+Formally, consider sets of strings over $\bool$, and fix the
+``all-but-last'' leakage function $\leak_{\mathsf{abl}}$ defined by
+\[\leak_{\mathsf{abl}}(\{x_1, \ldots, x_n\}) = \{x_1, \ldots, x_{n-1}\},\]
+where $x_n$ is the lexicographically last string in the given set.
+\jnote{Could also give all-but-the-2nd bit of $x_n$, but does it
+matter?} Define an attacker $A$ as follows: it chooses a uniform
+bit~$b$; if $b=0$ then it outputs the set $S=\{1,111\}$, and if
+$b=1$ then it outputs the set $S=\{1, 101\}$. Next, given public
+information $\pub = \langle M_1, M_2 \rangle$ (where $M_2$ is the
+array with more bits set to~1), it counts the number of positions
+set to~1 in $M_2$ that are \emph{not} set to~1 in~$M_1$. If $b=0$
+and this number is $k$ or less, or if $b=1$ and this number if
+strictly greater than~$k$, then $A$ outputs~1; otherwise, it
+outputs~0.
 
@@
 than the bigram set for the first string, and so with high
-probability the number of positions set to~1 in $M_2$ that are not
-set to~1 in $M_1$ exceeds~$k$. (Specifically, in the worst case
-there are $2k$ positions---call them~$I$---set to~1 in $M_1$, and
-then the number in question exceeds~$k$ as long as a strict majority
-of the $2k$ positions set to~1 by the extra bigrams $10, 01$ lie
+probability there are more than $k$ positions set to~1 in $M_2$ that
+are not set to~1 in~$M_1$. (Specifically, in the worst case there
+are $2k$ positions---call them~$I$---set to~1 in $M_1$, and then the
+number in question exceeds~$k$ as long as a strict majority of the
+$2k$ positions set to~1 by the additional bigrams $10, 01$ lie
 outside of~$I$. Pairwise independence of those $2k$ positions can be
 used to bound this probability. If $k\geq 4$ and $2k/m \leq 1/4$,
-this probability is at least %JK
+this probability is at least~$1/2$.) \jnote{Check my math? Get
+tighter analysis?} We conclude that in the real experiment $A$
+outputs~1 with probability at least~3/4.
 
- implies that this happens except with
-probability at most $(4 \cdot (\frac{1}{2}- \leq 1/2$.)
+On the other hand, a simulator~$\Sim$ given ${\sf
+leak}_{\mathsf{abl}}(S) = \{1\}$ has no information about~$b$, and
+it is not hard to see that no $\Sim$ can cause $A$ to output~1 with
+probability better than~1/2.
 
@@
 %\end{theorem}
-\begin{proof}%\tsnote{still a bit sketchy but believable}
-On the other hand, the simulator~$\Sim$ is given 'cab','bab','cab'
-as input.  It can perfectly simulate $M_1,M_2$ by lazily sampling
-random function~$\rho$ itself.  However, it has no information about
-the bit~$z$, so at best it can cause~$A$ to output 1 with
-probability~$1/2$.  That is
-$\ExpPrivSSsim{\setprim_{\bilin}}{A,\Sim} \leq 1/2$. \hfill\qed
-\end{proof}
+%\begin{proof}%\tsnote{still a bit sketchy but believable}
+%\end{proof}
 
@@
 }
-\caption{Bigram domain-separated PRF-hash.}
+\caption{Bigram domain-separated PRF-hash. \jnote{There must be some better choice of notation to indicate that
+the only change is in the way the hash functions are instantiated. (This is a general comment that
+applies to the entire paper.)}}
 \label{fig:DS-bigram}
@@
 Niedermeyer et al.~\cite{niedermeyer2014cryptanalysis} suggest
-replacing the linear-PRF hash functions in the previous construction
-with independently keyed PRFs as a countermeasure to their attack.
-In terms of SS-privacy, however, this change offers no help.  The
-following theorem is proved via a nearly identical argument as
-Theorem~\ref{thm:bi-lin-ss}.
+replacing the hash functions in the previous construction with
+independently keyed PRFs as a countermeasure to their attack.
+\jnote{We don't even say what their attack is.} In terms of
+simulation-based privacy, however, it is not hard to see---using a
+similar attack as in the previous section---that this is of little
+help.
 
-\begin{theorem}[{\rm SS-privacy of bigram DS PRF-hash}]\label{thm:bi-ds-ss}
-Let $\setprim_{\bilin}= (\Rep, \Qry)$ be the set-membership data
-structure described in Figure~\ref{fig:DS-bigram}. Let $\leak$ be
-the leakage function described just prior to
-Theorem~\ref{thm:bi-lin-ss}. Let~$\elts=\{\mathrm{a,b,c}\}^*$. Let
-$n=3$,  $m=3\alpha $ for integer $\alpha >> 1$, and let $k = \lceil
-\ln(2) \alpha \rceil$.\footnote{As before, this value of~$k$ is from the
-classical analysis for minimizing the FP rate for a Bloom filter,
-and is set this way for compatibility with classical results.  It
-isn't used in any essential way in the proof sketch.}  Let~$A$ be
-the adversary in Figure~\ref{fig:adv-bi-lin-ss}.  Then for any
-simulator $\Sim$, the advantage
-$\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim}$ can be made
-arbitrarily close to $1/2$ by choice of~$\alpha$.
-\end{theorem}
+%\begin{theorem}[{\rm SS-privacy of bigram DS PRF-hash}]\label{thm:bi-ds-ss}
+%Let $\setprim_{\bilin}= (\Rep, \Qry)$ be the set-membership data
+%structure described in Figure~\ref{fig:DS-bigram}. Let $\leak$ be
+%the leakage function described just prior to
+%Theorem~\ref{thm:bi-lin-ss}. Let~$\elts=\{\mathrm{a,b,c}\}^*$. Let
+%$n=3$,  $m=3\alpha $ for integer $\alpha >> 1$, and let $k = \lceil
+%\ln(2) \alpha \rceil$.\footnote{As before, this value of~$k$ is from the
+%classical analysis for minimizing the FP rate for a Bloom filter,
+%and is set this way for compatibility with classical results.  It
+%isn't used in any essential way in the proof sketch.}  Let~$A$ be
+%the adversary in Figure~\ref{fig:adv-bi-lin-ss}.  Then for any
+%simulator $\Sim$, the advantage
+%$\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim}$ can be made
+%arbitrarily close to $1/2$ by choice of~$\alpha$.
+%\end{theorem}
 
-On the other hand, we can show that this data structure \emph{is}
-secure with respect to a different leakage function, namely, one
-that leaks the sizes of the intersections of the various bigram
-sets. Specifically, for a set $S$ define ${\sf leak}_\cap(S)$ via
-the following algorithm:
+On the other hand, we can show that this data structure \emph{does}
+achieve our notion of simulation-based privacy with respect to a
+different leakage function, namely, one that leaks the sizes of the
+intersections of the various bigram sets. Specifically, for a set
+$S$ define ${\sf leak}_\cap(S)$ via the following algorithm:
 
-\begin{figure}[h]
-\centering
-\fpage{0.5}{
+\medskip\begin{center}
 \algorithmv{${\sf leak}_\cap(S)$}\\
@@
 \nudge $L \gets \left\langle L, \; \left| \bigcap_{x \in S'} B_x \right| \right\rangle$\\
-Return $L$}
+Return $L$
 %\caption{Bigram domain-separated PRF-hash.}
-\end{figure}
+\end{center}
+
+\jnote{Fix indentation.}
+
+\jnote{I ran out of steam at this point\ldots}
 
@@
 Dong, Chen and Wen~\cite{CCS:DonCheWen13} introduce a set-membership
-data structure called a \emph{garbled Bloom filter} (GBF).   Modulo
-some implementation details, a GBF is like a classical Bloom filter,
-but rather than storing a bit 1 at the indices determined by
-$H_j(x)$, the GBF stores xor-shares of~$x$.  Thus, if $x \in S$,
-then hashing~$x$ and xoring together the strings stored at the
-indicated positions recovers~$x$. We give the pseudocode for the GBF
-$\Rep$ and $\Qry$ algorithms in Figure~\ref{fig:gbf}.
+data structure called a \emph{garbled Bloom filter} (GBF). Roughly,
+whereas for each element $x$ in a given input set a classical Bloom
+filter would set positions of an array to~1 as determined by
+$H_1(x), \ldots, H_k(x)$, a GBF stores a $k$-out-of-$k$
+secret-sharing of $x$ in those positions. (Thus, a GBF is an array
+of strings rather than an array of bits.) We provide the pseudocode
+in Figure~\ref{fig:gbf}.
 
-In~\cite{dong2013private} the GBF is a central piece of a private set-intersection
-scheme, in which the client computes a classical BF over its
-set~$S_1$, the server computes a GBF over its set~$S_2$, and then an
-oblivious transfer protocol is carried out, at the end of which the
-client obtains a GBF for $S_1 \cap S_2$ (the server learns nothing).
-The authors note that the GBF is a new set-membership data structure
-that may be of general interest, so we explore its correctness and
-privacy with respect to use case that may or may not make the
-representation~$M$ public. The pseudocode in Figure~\ref{fig:gbf}
-covers both possibilities.
+In~\cite{CCS:DonCheWen13} the GBF is a central piece of a private
+set-intersection scheme, in which the client computes a classical BF
+over its set~$S_1$, the server computes a GBF over its set~$S_2$,
+and then an oblivious transfer protocol is carried out, at the end
+of which the client obtains a GBF for $S_1 \cap S_2$ (the server
+learns nothing). The authors note that the GBF is a new
+set-membership data structure that may be of general interest, so we
+explore its correctness and privacy with respect to use case that
+may or may not make the representation~$M$ public. The pseudocode in
+Figure~\ref{fig:gbf} covers both possibilities.
 
-\heading{Correctness.}
-We note that~\cite{dong2013private} provides error-rate analysis, i.e., the
-probability of finding a single false-positive in a non-adaptive
-attack.  When $\lambda$ is the bit-length of the xor-shares, they
-argue that the error-rate is at most $2^{-\lambda}$, roughly because
-the xor-shares stored in~$M$ are random strings.  (Note that
+\heading{Correctness.} We note that~\cite{CCS:DonCheWen13} provides
+error-rate analysis, i.e., the probability of finding a single
+false-positive in a non-adaptive attack.  When $\lambda$ is the
+bit-length of the xor-shares, they argue that the error-rate is at
+most $2^{-\lambda}$, roughly because the xor-shares stored in~$M$
+are random strings.  (Note that
   this is independent of~$k,m,n$; although $k>1$ is required for the
@@
 
-Now, this adversary will find a false positive, if there is one, but in the worst case it will consider
-$\binom{m}{k} \approx m^k$ $k$-tuples of positions.  If both~$m$
-and~$k$ are large this is infeasible.  In~\cite{dong2013private} they suggest to
-set~$k=\lambda$, and test with $\lambda=80$.  Making 80 hash calls per
-set-membership query would be prohibitive in many applications, and a
-$2^{-80}$ false-positive rate would be typically considered overkill in
-practice.\footnote{Note
-that, as described in~\cite{dong2013private}, $\lambda$ must be at least the
-bit-length of the longest element $x \in S$. In practice, this could be
+Now, this adversary will find a false positive, if there is one, but
+in the worst case it will consider $\binom{m}{k} \approx m^k$
+$k$-tuples of positions.  If both~$m$ and~$k$ are large this is
+infeasible.  Dong et al.~\cite{CCS:DonCheWen13} suggest to
+set~$k=\lambda$, and test with $\lambda=80$.  Making 80 hash calls
+per set-membership query would be prohibitive in many applications,
+and a $2^{-80}$ false-positive rate would be typically considered
+overkill in practice.\footnote{Note that, as described
+in~\cite{CCS:DonCheWen13}, $\lambda$ must be at least the bit-length
+of the longest element $x \in S$. In practice, this could be
   handled with a slight change to the set membership test, by checking

### 2016-12-20 ny-def-comparison.tex
no message

@@
 %consistent with the rest of the document.}
-The structure of the Naor-Yogev definition is different from ours.
-They focus specifically on set-representation data
-structures with no false negatives, and their data-structure syntax
-does not distinguish public and private portions of the
+We briefly describe the differences between the Naor-Yogev definition of correctness and ours.
+For starters,
+they focus specifically on set-representation data
+structures with no false negatives, and (more importantly) their data-structure syntax
+does not distinguish between public and private portions of a
 representation. Nevertheless, it is straightforward
-to extend their definition to more closely match ours; we do that next.
-Their experiment is similar but the attacker
+to extend their definition to more closely match ours; we do that below.
+A more fundamental difference is that in
+their experiment for defining correctness, the attacker
 succeeds only if it outputs a (single) query $\qry$ for which
-$\Qry(\pubaux,\privaux, \qry) \neq \qry(S)$  \emph{subject to the restriction that it did not
+$\Qry(\pubaux,\privaux, \qry) \neq \qry(S)$  \emph{and for which it did not
 previously query $\qry$ to its $\TestOracle$ oracle}. We refer to
 Figure~\ref{fig:NYcorrectness} for a definition of the relevant experiment.
-We define the advantage of adversary~$A$ as
+We define the advantage of adversary~$A$ relative to their experiment
+as
 $\NYAdvCorrect{\Pi}{A} = \Prob{\NYExpCorrect{\Pi}{A}=1}$,
-and write $\NYAdvCorrect{\Pi,r}{t,q}$ for the maximum over
-all~$t$-time adversaries that ask at most~$q$ queries. We say that a
-data structure~$\Pi$ is $(t,q,\epsilon)$-NY-correct if
-$\NYAdvCorrect{\Pi}{t,q} \leq \epsilon$. 
+and let $\NYAdvCorrect{\Pi}{t,q}$ be the maximum of this value taken over
+all~$t$-time adversaries that ask at most~$q$ queries. %We say a
+%data structure~$\Pi$ is \emph{$(t,q,\epsilon)$-NY-correct} if
+%$\NYAdvCorrect{\Pi}{t,q} \leq \epsilon$.
 %\jnote{This should all probably
@@
 \begin{theorem}
-If $\Pi$ is $(t,q,\epsilon)$-NY-correct, then it is also
-$(t, q', r, q'\epsilon/r)$-correct for any $q' \leq q+1$ and $r\geq
-1$.
+Fix $\Pi$. If $\NYAdvCorrect{\Pi}{t,q} \leq \epsilon$, then for any $r \geq 1$ and $q' \leq q+1$ it holds that
+$\AdvCorrect{\setprim,r}{t,q'} \leq q'\epsilon/r$.
 \end{theorem}
 \begin{proof}
-Let $\Pi$ be a data structure that is $(t,q,\epsilon)$-NY-correct,
-and assume that for some $q' \leq q+1$ and
+Assume that for some $q' \leq q+1$ and
 $r \geq 1$
@@
 $\AdvCorrect{\Pi,r}{A} > q'\epsilon/r$.
-(Note that
-we may assume $A$ always makes exactly $q'$ queries without loss of generality.)
-With probability at least
+(Note
+we may assume that $A$ always makes exactly $q'$ queries without loss of generality.)
+This means that with probability at least
 $q'\epsilon/r$ in an execution of $\ExpCorrect{\Pi,r}{A}$, we have that
@@
 Since the running time of $A'$ is at most $t$, and it makes at most $q'-1 \leq q$ queries
-to its oracle, this is a contradiction.
+to its oracle, this is a contradiction. \hfill\qed
 \end{proof}
 
-We note that the above is tight, at least for $r=1$. Specifically, consider a scheme
+We remark that the above is tight, at least for $r=1$. Specifically, consider a scheme
 in which every query is independently
 answered incorrectly with probability~$\epsilon$. Such a
-scheme will be $(t,q,\epsilon)$-NY-correct
-for any $t, q$, however an adversary making $q=1/\epsilon$ queries has constant advantage
-under our correctness definition (for $r=1$).
+scheme satisfies $\NYAdvCorrect{\Pi}{t,q} \leq \epsilon$ for any $t, q$,
+however an adversary making $q=1/\epsilon$ queries has constant advantage
+with respect to our correctness definition (for $r=1$).
+
+In the other direction, we show:
 
 \begin{theorem}
-If $\Pi$ is $(t, q, 1, \epsilon)$-correct, then it is also $(t, q-1, \epsilon)$-NY-correct.
+Fix $\Pi$. If $\AdvCorrect{\setprim,1}{t,q} \leq \epsilon$, then
+$\NYAdvCorrect{\Pi}{t,q-1} \leq \epsilon$.
 \end{theorem}
-
 \begin{proof}
-Let $\Pi$ be a data structure that is $(t,q,1,\epsilon)$-correct,
-and assume
+Assume
 there is an adversary $A$ running in time~$t$
@@
 Let $A'$ be the algorithm that simply
-runs~$A$, passing the oracle queries of~$A$ to its own oracle, until~$A$ terminates
+runs~$A$, forwarding the oracle queries of~$A$ to its own oracle, until~$A$ terminates
 with output~$\qry$; then, $A'$ sends~$\qry$ to $\TestOracle$. It is immediate that $A'$ makes at most $q$ oracle queries, and
-$\AdvCorrect{\Pi,1}{A'} \geq \NYAdvCorrect{\Pi}{A}$, a contradiction.
+$\AdvCorrect{\Pi,1}{A'} \geq \NYAdvCorrect{\Pi}{A}$, a contradiction. \hfill\qed
 \end{proof}
@@
 \begin{theorem}
-There exists a data structure $\Pi$ that
-is $(t, q, 2, 0)$-correct, but is not $(t, 0, \epsilon)$-NY-correct
-for any $\epsilon<1$.
+There is a data structure $\Pi$ over ${\cal X}$
+for which $\AdvCorrect{\setprim,2}{t,q}=0$ for all $t, q$,
+but $\NYAdvCorrect{\Pi}{O(1),0} = 1$.
 \end{theorem}
 \begin{proof}
-Let $\Pi$ be the set-membership data structure in which $\Rep(S)$ outputs
+Let $x \in {\cal X}$ be
+an arbitrary fixed element.
+Define $\Pi$ such that $\Rep(S)$ outputs
 $\pubaux=\privaux=S$, and
-$\Qry(S, S, \qry_y)$ outputs $\qry_y(S)$ if $y \neq x$ but outputs $1-\qry_x(S)$ otherwise,
-where $x \in {\cal X}$ is a fixed element of the universe. This
-scheme always answers incorrectly for a single, fixed query, and answers
+$\Qry(S, S, \qry_y)$ outputs $\qry_y(S)$ if $y \neq x$ but outputs $1-\qry_x(S)$ otherwise.
+This scheme always answers incorrectly for a single, fixed query, and answers
 correctly for every other query. The theorem follows.

### 2017-02-27 intro.tex
Add .gitignore and macro \cpnote{...}.

@@
 security profile of the resulting Bloom-filter variant.  Indeed,
-this is the case.  When $H_1,H_2,\ldots,H_K$ are assumed to be
-pseudorandom functions, we can prove that this variant achieves a
-sort of ``semantic security'' privacy guarantee: the bit array~$M$
-leaks a good approximation of~$|S|$, but nothing more.  (Such a
-result is not possible for the standard Bloom filter, or any other
-data structure with empty~$\privaux$.)
+this is the case.  When $H_1,H_2,\ldots,H_K$
+%
+\cpnote{Is $K$ supposed to be $k$?}
+%
+are assumed to be pseudorandom functions, we can prove that this variant
+achieves a sort of ``semantic security'' privacy guarantee: the bit array~$M$
+leaks a good approximation of~$|S|$, but nothing more.  (Such a result is not
+possible for the standard Bloom filter, or any other data structure with
+empty~$\privaux$.)
 
@@
 
-\ignore{We provide various security notions for these primitives...
+ ignore{We provide various security notions for these primitives...
 FP with private, public representation coins; set privacy with
